### 2016-04-19 forgerard.tex
first commit

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}

\begin{document}
A model for a single object is that its intrinsic properties (captured by equivalent width) are drawn from a Normal distribution
\begin{equation}
\left(
\begin{matrix}
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
EW_{0, Si}\\ EW_{0, Ca}
\end{matrix}
\right)
,C_{EW}
\right),
\end{equation}
with global parameters $EW_{0, Si}$, $EW_{0, Ca}$, and the independent elements of $C_{EW}$.
The colors, which depend on the intrinsic properties and the extrinsic effect of dust, are modeled as
\begin{equation}
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k+ E(U-V) \\
c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +k +E(B-V) \\
c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k + E(V-R)\\
c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k +E(V-I)\\
\end{matrix}
\right)
,C_c
\right),
\end{equation}
where there are global parameters $\alpha_X$, $\beta_X$, $c_X$,  and the independent elements of $C_c$,
while each supernova has independent parameters $E(X-V)$ and intrinsic color parameter $k$.

The measurements are drawn from
\begin{equation}
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)_o \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C_o
\right),
\end{equation}
where $C_o$ is the observation covariance matrix.

Given enough supernovae to constrain the global parameters, the observed colors of each supernova are used to determine its
color excess parameters.
\end{document}

### 2016-04-19 model.py

@@ -1,0 +1,81 @@
+import pickle
+import numpy
+import pystan
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+
+#  The ordering is 'Ca','Si','U','B','V','R','I' 
+
+EW_obs = data['obs'][:,0:2]
+mag_obs = data['obs'][:,2:]
+
+nsne, nmags = mag_obs.shape
+color_obs = numpy.zeros((nsne,nmags-1))
+color_obs[:,0] = mag_obs[:,0]- mag_obs[:,2]
+color_obs[:,1] = mag_obs[:,1]- mag_obs[:,2]
+color_obs[:,2] = mag_obs[:,2]- mag_obs[:,3]
+color_obs[:,3] = mag_obs[:,2]- mag_obs[:,4]
+
+EW_cov = data['cov'][:,0:2,0:2]
+mag_cov = data['cov'][:,2:,2:]
+
+pkl_file.close()
+
+trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1]]
+trans = numpy.array(trans)
+color_cov = numpy.zeros((nsne,4,4))
+for i in xrange(nsne):
+    color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
+
+
+# renormalize the data
+EW_mn = EW_obs.mean(axis=0)
+EW_std = EW_obs.std(axis=0)
+
+EW_renorm = (EW_obs - EW_mn)/EW_std
+EW_cov_renorm = numpy.array(EW_cov)
+for i in xrange(nsne):
+    EW_cov_renorm[i] = EW_cov_renorm[i] /EW_std[None,:] / EW_std[:,None]
+
+color_mn = color_obs.mean(axis=0)
+color_std = color_obs.std(axis=0)
+
+color_renorm = (color_obs - color_mn)/color_std
+color_cov_renorm = numpy.array(color_cov)
+for i in xrange(nsne):
+    color_cov_renorm[i] = color_cov_renorm[i] /color_std[None,:] / color_std[:,None]
+
+
+data = {'D': nsne, 'N_colors': 4, 'N_EWs': 2, 'color_obs': color_renorm, \
+    'EW_obs': EW_renorm, 'EW_cov': EW_cov_renorm, 'color_cov':color_cov_renorm}
+
[…]

### 2016-05-03 forgerard.tex
fix redefinition of gamma_1

@@
 \begin{document}
+
+\begin{equation}
+\left(
+\begin{matrix}
+U-V\\B-V\\V-R\\V-I\\EW_{Si, o}\\ EW_{Ca, o}
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\left(
+\begin{matrix}
+c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k  \\
+c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +\gamma_1 k  \\
+c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k\\
+c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k\\
+EW_{Si}\\ EW_{Ca}
+\end{matrix}
+\right)
+,C
+\right),
+\end{equation}
+
 A model for a single object is that its intrinsic properties (captured by equivalent width) are drawn from a Normal distribution

### 2016-05-03 view.py

@@ -6,6 +6,8 @@ import corner
 from matplotlib.backends.backend_pdf import PdfPages
 import numpy
 
+color_std=0.272560118531
+
 f = open('temp.pkl','rb')
 fit = pickle.load(f)
 
@@ -22,12 +24,12 @@ with PdfPages('multipage_pdf.pdf') as pdf:
     # pdf.savefig()
     # plt.close()
     
-    plt.plot(fit['EW'][:,:10,0])
+    plt.plot(fit['EW'][::10,:10,0])
     plt.title('EW - 0')
     pdf.savefig()
     plt.close()
     
-    plt.plot(fit['EW'][:,:10,1])
+    plt.plot(fit['EW'][::10,:10,1])
     plt.title('EW - 1')
     pdf.savefig()
     plt.close()
@@ -37,17 +39,17 @@ with PdfPages('multipage_pdf.pdf') as pdf:
     pdf.savefig()
     plt.close()
     
-    plt.plot(fit['alpha'])
+    plt.plot(fit['alpha'][::10],alpha=0.5)
     plt.title('alpha')
     pdf.savefig()
     plt.close()
     
-    plt.plot(fit['beta'])
+    plt.plot(fit['beta'][::10],alpha=0.5)
     plt.title('beta')
     pdf.savefig()
     plt.close()
     
-    plt.plot(fit['gamma']*3.1)
+    plt.plot(fit['gamma'])
     plt.title('gamma')
     pdf.savefig()
     plt.close()
@@ -58,7 +60,7 @@ with PdfPages('multipage_pdf.pdf') as pdf:
     # pdf.savefig()
     # plt.close()
     
-    plt.plot(fit['k'][:,:10]/3.1)
+    plt.plot(fit['k'][::10,:10])
     plt.title('k')
     pdf.savefig()
     plt.close()
@@ -82,11 +84,18 @@ with PdfPages('multipage_pdf.pdf') as pdf:
 # [3701, 4601, 5744, 6948, 8403]
     rc('text', usetex=True)
     dif = numpy.array([1.545252680138557- 0.9512179494794494, 1.251613863650247- 0.9512179494794494, 0.9512179494794494-0.7582486105024363, 0.9512179494794494-0.5429015873250165]) 
-    dif = dif/dif[1]*3.1
+    dif = dif/dif[1]
+
     dum = [dif[0], dif[2], dif[3]]
[…]

### 2016-05-18 forgerard.tex
write proposal for next version of model

@@
 
+The simplified implemented model is
 \begin{equation}
@@
 \begin{matrix}
-U-V\\B-V\\V-R\\V-I\\EW_{Si, o}\\ EW_{Ca, o}
+U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\EW_{Si, o}\\ EW_{Ca, o}
 \end{matrix}
@@
 \end{equation}
+The data are the colors and equivalent widths on the left side.  There are global parameters $c$, $\alpha$, $\beta$, and $\gamma$.  Each
+supernova has parameters $EW_{Si}$, $EW_{Ca}$, and $k$.  To constrain the problem $\gamma_1=1$ and one supernova is selected to have
+$k=0$.
 
-A model for a single object is that its intrinsic properties (captured by equivalent width) are drawn from a Normal distribution
-\begin{equation}
-\left(
-\begin{matrix}
-EW_{Si}\\ EW_{Ca}
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\left(
-\begin{matrix}
-EW_{0, Si}\\ EW_{0, Ca}
-\end{matrix}
-\right)
-,C_{EW}
-\right),
-\end{equation}
-with global parameters $EW_{0, Si}$, $EW_{0, Ca}$, and the independent elements of $C_{EW}$.
-The colors, which depend on the intrinsic properties and the extrinsic effect of dust, are modeled as
+The next level of complexity to add is intrinsic dispersion through stochastic parameters that describe the global  covariance matrices
+$C_{c}$.  The model would then look like
 \begin{equation}
@@
 \begin{matrix}
-c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k+ E(U-V) \\
-c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +k +E(B-V) \\
-c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k + E(V-R)\\
-c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k +E(V-I)\\
+c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} \\
+c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  \\
+c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} \\
+c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} 
 \end{matrix}
 \right)
-,C_c
+,C_{c}
 \right),
 \end{equation}
-where there are global parameters $\alpha_X$, $\beta_X$, $c_X$,  and the independent elements of $C_c$,
-while each supernova has independent parameters $E(X-V)$ and intrinsic color parameter $k$.
 
-The measurements are drawn from
 \begin{equation}
@@
 \begin{matrix}
-U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
+U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\EW_{Si, o}\\ EW_{Ca, o}
 \end{matrix}
-\right)_o \sim \mathcal{N}
+\right) \sim \mathcal{N}
 \left(
@@
 \begin{matrix}
-U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
+U-V +\gamma_0 k \\B-V +\gamma_1 k \\V-R+\gamma_2 k\\V-I+\gamma_3 k\\
+EW_{Si}\\ EW_{Ca}
 \end{matrix}
 \right)
-,C_o
-\right),
+,C
+\right).
 \end{equation}
-where $C_o$ is the observation covariance matrix.
 
-Given enough supernovae to constrain the global parameters, the observed colors of each supernova are used to determine its
-color excess parameters.
+%
+%
+%A model for a single object is that its intrinsic properties (captured by equivalent width) are drawn from a Normal distribution
+%\begin{equation}
+%\left(
+%\begin{matrix}
+%EW_{Si}\\ EW_{Ca}
+%\end{matrix}
+%\right) \sim \mathcal{N}
+%\left(
+%\left(
+%\begin{matrix}
+%EW_{0, Si}\\ EW_{0, Ca}
+%\end{matrix}
+%\right)
+%,C_{EW}
+%\right),
+%\end{equation}
+%with global parameters $EW_{0, Si}$, $EW_{0, Ca}$, and the independent elements of $C_{EW}$.
+%The colors, which depend on the intrinsic properties and the extrinsic effect of dust, are modeled as
+%\begin{equation}
+%\left(
+%\begin{matrix}
+%U-V\\B-V\\V-R\\V-I
+%\end{matrix}
+%\right) \sim \mathcal{N}
+%\left(
+%\left(
+%\begin{matrix}
+%c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k+ E(U-V) \\
+%c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +k +E(B-V) \\
+%c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k + E(V-R)\\
+%c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k +E(V-I)\\
+%\end{matrix}
+%\right)
+%,C_c
+%\right),
+%\end{equation}
+%where there are global parameters $\alpha_X$, $\beta_X$, $c_X$,  and the independent elements of $C_c$,
+%while each supernova has independent parameters $E(X-V)$ and intrinsic color parameter $k$.
+%
+%The measurements are drawn from
+%\begin{equation}
+%\left(
+%\begin{matrix}
+%U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
+%\end{matrix}
+%\right)_o \sim \mathcal{N}
+%\left(
+%\left(
+%\begin{matrix}
+%U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
+%\end{matrix}
+%\right)
+%,C_o
+%\right),
+%\end{equation}
+%where $C_o$ is the observation covariance matrix.
+%
+%Given enough supernovae to constrain the global parameters, the observed colors of each supernova are used to determine its
+%color excess parameters.
 \end{document}

### 2016-06-15 forgerard.tex
latest version of model and next thinkg to do.

@@
 \end{equation}
-The data are the colors and equivalent widths on the left side.  There are global parameters $c$, $\alpha$, $\beta$, and $\gamma$.  Each
+The data are the colors and equivalent widths on the left side, $C$ is the corresponding measurement
+covariance.  There are global parameters $c$, $\alpha$, $\beta$, and $\gamma$.  Each
 supernova has parameters $EW_{Si}$, $EW_{Ca}$, and $k$.  To constrain the problem $\gamma_1=1$ and one supernova is selected to have
@@
 \begin{matrix}
-U-V\\B-V\\V-R\\V-I
+U-V\\B-V\\V-R\\V-I\\V
 \end{matrix}
@@
 c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} \\
-c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} 
+c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} \\
+c_4+\alpha_4 EW_{Si} + \beta_4 EW_{Ca}
 \end{matrix}
@@
 \begin{matrix}
-U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\EW_{Si, o}\\ EW_{Ca, o}
+U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\V_o\\EW_{Si, o}\\ EW_{Ca, o}
 \end{matrix}
@@
 \begin{matrix}
-U-V +\gamma_0 k \\B-V +\gamma_1 k \\V-R+\gamma_2 k\\V-I+\gamma_3 k\\
+U-V +\gamma_0 k \\B-V +\gamma_1 k \\V-R+\gamma_2 k\\V-I+\gamma_3 k\\V+\gamma_4 k\\
 EW_{Si}\\ EW_{Ca}

### 2016-07-05 model2.py
refining second model

@@ -5,58 +5,73 @@ import pystan
 
 pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)
+pkl_file.close()
 
 #  The ordering is 'Ca','Si','U','B','V','R','I'
 
 EW_obs = data['obs'][:,0:2]
 mag_obs = data['obs'][:,2:]
-
-nsne, nmags = mag_obs.shape
-color_obs = numpy.zeros((nsne,nmags))
-color_obs[:,0] = mag_obs[:,0]- mag_obs[:,2]
-color_obs[:,1] = mag_obs[:,1]- mag_obs[:,2]
-color_obs[:,2] = mag_obs[:,2]- mag_obs[:,3]
-color_obs[:,3] = mag_obs[:,2]- mag_obs[:,4]
-color_obs[:,4] = mag_obs[:,2]
-
 EW_cov = data['cov'][:,0:2,0:2]
 mag_cov = data['cov'][:,2:,2:]
 
-pkl_file.close()
+nsne, nmags = mag_obs.shape
+# color_obs = numpy.zeros((nsne,nmags))
+# color_obs[:,0] = mag_obs[:,0]- mag_obs[:,2]
+# color_obs[:,1] = mag_obs[:,1]- mag_obs[:,2]
+# color_obs[:,2] = mag_obs[:,2]- mag_obs[:,3]
+# color_obs[:,3] = mag_obs[:,2]- mag_obs[:,4]
+# color_obs[:,4] = mag_obs[:,2]
 
-trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1],[0.,0,1,0,0]]
-trans = numpy.array(trans)
-color_cov = numpy.zeros((nsne,5,5))
-for i in xrange(nsne):
-    color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
 
 
-# renormalize the data
+# trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1],[0.,0,1,0,0]]
+# trans = numpy.array(trans)
+# color_cov = numpy.zeros((nsne,5,5))
+# for i in xrange(nsne):
+#     color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
+
+
+# # renormalize the data
[…]

### 2016-07-08 forgerard.tex
refining second model
a new version doing coordinate transformation of alpha, beta, c in case this helps STAN solve these very correlated variables.

@@
 $C_{c}$.  The model would then look like
-\begin{equation}
+\begin{equation*}
 \left(
 \begin{matrix}
-U-V\\B-V\\V-R\\V-I\\V
+U\\B\\V\\R\\I
 \end{matrix}
@@
 \begin{matrix}
-c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} \\
-c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  \\
-c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} \\
-c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} \\
-c_4+\alpha_4 EW_{Si} + \beta_4 EW_{Ca}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
 \end{matrix}
@@
 \right),
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
 \left(
 \begin{matrix}
-U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\V_o\\EW_{Si, o}\\ EW_{Ca, o}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
 \end{matrix}
@@
 \begin{matrix}
-U-V +\gamma_0 k \\B-V +\gamma_1 k \\V-R+\gamma_2 k\\V-I+\gamma_3 k\\V+\gamma_4 k\\
+U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
 EW_{Si}\\ EW_{Ca}
@@
 \right).
-\end{equation}
-
+\end{equation*}
+For boundary conditions we set one supernova to have $k=0$ and we set $\gamma_2=1$.
 %

### 2016-07-08 model2.py

@@ -57,10 +57,11 @@ mag_renorm  = mag_obs-mag_mn
 #     'EW_obs': EW_renorm, 'EW_cov': EW_cov_renorm, 'color_cov':color_cov_renorm, 'color_std':color_std.astype('float'), 'color_mn':color_mn}
 data = {'D': nsne, 'N_mags': 5, 'N_EWs': 2, 'mag_obs': mag_renorm, 'EW_obs': EW_renorm, 'EW_cov': EW_cov, 'mag_cov':mag_cov}
 
-init = [{'EW' : EW_renorm, 'c': numpy.random.normal(0,0.02,size=5),\
-    'alpha': numpy.random.uniform(-0.01, 0.01, size= 5), 'beta':numpy.array([0.06,0.05,0.04,0.03,0.02])+numpy.random.normal(0,0.005,size=5),\
-    'gamma':numpy.array([1.4,1.2,0.85,0.7])+ numpy.random.normal(0,0.01,size=4), 'k':numpy.random.uniform(-0.02, 0.02, size=nsne-1), 'mag_int':\
-    mag_renorm+numpy.random.normal(0,0.02,size=(nsne,5)), 'L_sigma':numpy.random.uniform(-0.02, 0.02,size=5)+0.1,'L_Omega':numpy.identity(5)} \
+init = [{'EW' : EW_renorm, 'c': numpy.random.uniform(-0.25,-0.08,size=5), 'alpha': numpy.random.uniform(-0.01, 0.01, size= 5),\
+    'beta':numpy.array([0.04,0.035,0.03,0.025, 0.025])+ numpy.random.uniform(-0.002,0.002,size=5),\
+    'gamma':numpy.array([1.4,1.21,0.824,0.67])+ numpy.random.uniform(-0.01,0.01,size=4), \
+    'k':numpy.random.uniform(-0.05, 0.05, size=nsne-1), 'mag_int': mag_renorm+numpy.random.uniform(-0.02,0.02,size=(nsne,5)), \
+    'L_sigma':numpy.random.uniform(0.04, 0.08,size=5),'L_Omega':numpy.identity(5)} \
     for _ in range(4)]
 
 # init1 = {'EW' : EW_renorm, 'c': numpy.zeros(5), 'alpha': numpy.zeros(5), \
@@ -70,8 +71,8 @@ init = [{'EW' : EW_renorm, 'c': numpy.random.normal(0,0.02,size=5),\
 
 sm = pystan.StanModel(file='gerard2.stan')
[…]

### 2016-07-08 model3.py

@@ -50,25 +50,28 @@ EW_renorm = (EW_obs - EW_mn)
 # # for i in xrange(nsne):
 # #     color_cov_renorm[i] = color_cov_renorm[i] /color_std**2
 
-# mag_mn = mag_obs.mean(axis=0)
-# mag_renorm  = mag_obs-mag_mn
+mag_mn = mag_obs.mean(axis=0)
+mag_renorm  = mag_obs-mag_mn
 
 # data = {'D': nsne, 'N_colors': 5, 'N_EWs': 2, 'color_obs': color_renorm, \
 #     'EW_obs': EW_renorm, 'EW_cov': EW_cov_renorm, 'color_cov':color_cov_renorm, 'color_std':color_std.astype('float'), 'color_mn':color_mn}
-data = {'D': nsne, 'N_mags': 5, 'N_EWs': 2, 'mag_obs': mag_obs, 'EW_obs': EW_renorm, 'EW_cov': EW_cov, 'mag_cov':mag_cov}
+data = {'D': nsne, 'N_mags': 5, 'N_EWs': 2, 'mag_obs': mag_renorm, 'EW_obs': EW_renorm, 'EW_cov': EW_cov, 'mag_cov':mag_cov}
+
+k_simplex = numpy.random.random(size = nsne)
+k_simplex /= sum(k_simplex)
 
 init = [{'EW' : EW_renorm, \
-    'r_c': numpy.random.uniform(27*numpy.sqrt(5),29*numpy.sqrt(5)),\
+    'r_c': numpy.random.uniform(numpy.sqrt(5)-0.01,numpy.sqrt(5)+0.01),\
     'phi_c': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1, size= 3),\
     'phi_c_4': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1),\
-    'r_alpha': numpy.random.uniform(numpy.sqrt(5)-0.01,numpy.sqrt(5)+0.01),\
+    'r_alpha': numpy.random.uniform(numpy.sqrt(5)-0.001,numpy.sqrt(5)+0.001),\
     'phi_alpha': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1, size= 3),\
     'phi_alpha_4': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1),\
[…]

### 2016-07-08 view.py

@@ -27,7 +27,10 @@ with PdfPages('multipage_pdf.pdf') as pdf:
     gamma_median = numpy.median(fit['gamma'],axis=0)
     gamma_median = numpy.insert(gamma_median,2,1.)
 
-    k_median =  numpy.append(0.,numpy.median(fit['k'],axis=0))
+    dum = fit['k_simplex']*fit['k_scale'][:,None]
+    dum = dum - dum.mean(axis=1)[:,None]
+
+    k_median =  numpy.median(dum,axis=0)
     EW_median = numpy.median(fit['EW'],axis=0)
     beta_median = numpy.median(fit['beta'],axis=0)
     alpha_median = numpy.median(fit['alpha'],axis=0)
@@ -101,10 +104,10 @@ with PdfPages('multipage_pdf.pdf') as pdf:
     # pdf.savefig()
     # plt.close()
     
-    plt.plot(fit['k'][::10,:10])
-    plt.title('k')
-    pdf.savefig()
-    plt.close()
+    # plt.plot(fit['k'][::10,:10])
+    # plt.title('k')
+    # pdf.savefig()
+    # plt.close()
     
 
     # plt.plot(fit['EXY'][:,:10,1])
@@ -140,11 +143,11 @@ with PdfPages('multipage_pdf.pdf') as pdf:
     pdf.savefig()
     plt.close()
 
-    dum = numpy.median(fit['k'],axis=0)
-    plt.hist(dum)
-    plt.title('k')
-    pdf.savefig()
-    plt.close()
+    # dum = numpy.median(fit['k'],axis=0)
+    # plt.hist(dum)
+    # plt.title('k')
+    # pdf.savefig()
+    # plt.close()
 
     c_con = numpy.concatenate((fit['r_c'][:,None],fit['phi_c'],fit['phi_c_4'][:,None]),axis=1)
     figure = corner.corner(c_con,labels=["r", r"$\phi_0$",r"$\phi_1$",r"$\phi_2$",r"$\phi_3$"])

### 2016-07-08 model2.py
add grey dust to model2

@@ -64,7 +64,8 @@ init = [{'EW' : EW_renorm, 'c': numpy.random.normal(0,0.02,size=5),\
          'alpha': numpy.random.uniform(-0.01, 0.01, size= 5), 'beta':numpy.array([0.06,0.05,0.04,0.03,0.02])+numpy.random.normal(0,0.005,size=5),
          'gamma':numpy.array([1.4,1.2,0.85,0.7])+ numpy.random.normal(0,0.01,size=4), 'k_scale':0.1, 'k_simplex': k_simplex,
          'mag_int':
-         mag_renorm+numpy.random.normal(0,0.02,size=(nsne,5)), 'L_sigma':numpy.random.uniform(-0.02, 0.02,size=5)+0.1,'L_Omega':numpy.identity(5)}
+         mag_renorm+numpy.random.normal(0,0.02,size=(nsne,5)), 'L_sigma':numpy.random.uniform(-0.02, 0.02,size=5)+0.1,'L_Omega':numpy.identity(5), \
+         'Delta':numpy.zeros(nsne),'sigma_Delta': 0.08}
         for _ in range(4)]
 
 
@@ -76,7 +77,7 @@ init = [{'EW' : EW_renorm, 'c': numpy.random.normal(0,0.02,size=5),\
 sm = pystan.StanModel(file='gerard2.stan')
 # fit = sm.sampling(data=data, iter=200, chains=4,init=[init1,init1,init1,init1])
 control = {'stepsize':1.}
-fit = sm.sampling(data=data, iter=1000, chains=4,control=control,init=init, refresh = 10)
+fit = sm.sampling(data=data, iter=1000, chains=4,control=control,init=init)
 print fit
 
 output = open('temp2.pkl','wb')

### 2016-07-08 view2.py

@@ -1,0 +1,214 @@
+import pickle
+import pystan
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import corner
+from matplotlib.backends.backend_pdf import PdfPages
+import numpy
+import sncosmo
+
+color_std=0.272560118531
+
+f = open('temp2.pkl','rb')
+fit = pickle.load(f)
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+EW_obs = data['obs'][:,0:2]
+mag_obs = data['obs'][:,2:]
+EW_cov = data['cov'][:,0:2,0:2]
+mag_cov = data['cov'][:,2:,2:]
+
+
+with PdfPages('multipage_pdf.pdf') as pdf:
+
+    gamma_median = numpy.median(fit['gamma'],axis=0)
+    gamma_median = numpy.insert(gamma_median,2,1.)
+
+    dum = fit['k_simplex']*fit['k_scale'][:,None]
+    dum = dum - dum.mean(axis=1)[:,None]
+
+    k_median =  numpy.median(dum,axis=0)
+    EW_median = numpy.median(fit['EW'],axis=0)
+    beta_median = numpy.median(fit['beta'],axis=0)
+    alpha_median = numpy.median(fit['alpha'],axis=0)
+
+    filtname = ['U','B','V','R','I']
+    for i, fi in enumerate(filtname):
+        plt.hist([mag_obs[:, i], mag_obs[:, i] - gamma_median[i]*k_median, \
+            mag_obs[:, i] - gamma_median[i]*k_median -beta_median[i]*EW_median[:,1], \
+            mag_obs[:, i] - gamma_median[i]*k_median -beta_median[i]*EW_median[:,1]-alpha_median[i]*EW_median[:,0]], \
+            label=[r'$M_o$', r'$M_o - \gamma k$', r'$M_o - \gamma k - \beta EW_{Si}$', \
+            r'$M_o - \gamma k - \beta EW_{Si} - \alpha EW_{Ca}$'])
+        plt.legend()
+        plt.title('Filter {}'.format(fi))
+        pdf.savefig()
+        plt.close()
+
+
+    # plt.plot(fit['EW0'])
+    # plt.title('EW0')
+    # pdf.savefig()
+    # plt.close()
+
[…]

### 2016-07-11 forgerard.tex
add grey dust to model2
Remove requirement that grey dust have normal distribution

@@
 The next level of complexity to add is intrinsic dispersion through stochastic parameters that describe the global  covariance matrices
-$C_{c}$.  The model would then look like
+$C_{c}$ and a grey dust $\Delta$.  The model would then look like
 \begin{equation*}
@@
 \left(
+\Delta +
 \left(
@@
 c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
+\end{matrix}
+\right)
+,C_{c}
+\right),
+\end{equation*}
+\begin{equation*}
+\Delta \sim \mathcal{N}(0,\sigma^2_\Delta),
+\end{equation*}
+\begin{equation*}
+\left(
+\begin{matrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\left(
+\begin{matrix}
+U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+EW_{Si}\\ EW_{Ca}
+\end{matrix}
+\right)
+,C
+\right).
+\end{equation*}
+For boundary conditions we set  $\langle k \rangle=0$ and we set $\gamma_2=1$.
+
+The next level of complexity to add an intrinsic color variation modeled with a single parameter $d$.  The model would then look like
+\begin{equation*}
+\left(
+\begin{matrix}
+U\\B\\V\\R\\I
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\Delta +
+\left(
+\begin{matrix}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \delta_0 d \\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \delta_1 d\\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \delta_2 d\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \delta_3 d\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} + \delta_4 d
 \end{matrix}
@@
 \end{equation*}
-For boundary conditions we set one supernova to have $k=0$ and we set $\gamma_2=1$.
+For boundary conditions we set  $\langle k \rangle=0$,  $\langle \Delta \rangle=0$ and we set $\gamma_2=1$.
+
 %

### 2016-07-11 forgerard.tex
remove third model for now

@@
 c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
-\end{matrix}
-\right)
-,C_{c}
-\right),
-\end{equation*}
-\begin{equation*}
-\Delta \sim \mathcal{N}(0,\sigma^2_\Delta),
-\end{equation*}
-\begin{equation*}
-\left(
-\begin{matrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\left(
-\begin{matrix}
-U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
-EW_{Si}\\ EW_{Ca}
-\end{matrix}
-\right)
-,C
-\right).
-\end{equation*}
-For boundary conditions we set  $\langle k \rangle=0$ and we set $\gamma_2=1$.
-
-The next level of complexity to add an intrinsic color variation modeled with a single parameter $d$.  The model would then look like
-\begin{equation*}
-\left(
-\begin{matrix}
-U\\B\\V\\R\\I
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\Delta +
-\left(
-\begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \delta_0 d \\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \delta_1 d\\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \delta_2 d\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \delta_3 d\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} + \delta_4 d
 \end{matrix}

### 2016-07-12 forgerard.tex
work on note and separate figures

--- 2016-07-08 forgerard.tex
@@
 \begin{document}
-
-The simplified implemented model is
-\begin{equation}
-\left(
-\begin{matrix}
-U_o-V_o\\B_o-V_o\\V_o-R_o\\V_o-I_o\\EW_{Si, o}\\ EW_{Ca, o}
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\left(
-\begin{matrix}
-c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k  \\
-c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +\gamma_1 k  \\
-c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k\\
-c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k\\
-EW_{Si}\\ EW_{Ca}
-\end{matrix}
-\right)
-,C
-\right),
-\end{equation}
-The data are the colors and equivalent widths on the left side, $C$ is the corresponding measurement
-covariance.  There are global parameters $c$, $\alpha$, $\beta$, and $\gamma$.  Each
-supernova has parameters $EW_{Si}$, $EW_{Ca}$, and $k$.  To constrain the problem $\gamma_1=1$ and one supernova is selected to have
-$k=0$.
-
-The next level of complexity to add is intrinsic dispersion through stochastic parameters that describe the global  covariance matrices
-$C_{c}$.  The model would then look like
+The model for the intrinsic absolute magnitudes $U$, $B$, $V$, $R$, and $I$ is that they are drawn from a Normal distribution
 \begin{equation*}
@@
 ,C_{c}
-\right),
+\right).
 \end{equation*}
+The mean of the normal distribution linearly relates absolute magnitudes with
+individual spectral parameters  $EW_{Ca}$, and $EW_{Si}$ via the  global coefficients
+ $c_i$, $\alpha_i$, $\beta_i$.  Residual variations in absolute magnitude is described
+ by  $C_c$ the intrinsic dispersion of the Normal distribution.  To constrain the problem we
+ set $\langle \Delta \rangle=0$.
 
+The observed magnitudes  $U_o$, $B_o$, $V_o$, $R_o$, and $I_o$  and spectral features  $EW_{Ca,o}$, and $EW_{Si,o}$ are modeled
+as being drawn from a Normal distribution. 
 \begin{equation*}
@@
 \end{equation*}
-For boundary conditions we set one supernova to have $k=0$ and we set $\gamma_2=1$.
+The mean of the normal distribution is the intrinsic magnitudes plus an extrinsic magnitude change described by a parameter for each individual supernova
+$k$ and global parameters $\gamma_i$.  
+To constrain the problem we set  $\langle k \rangle=0$.  We also set  $\gamma_2=1$ meaning that $k$ can be interpreted as $A_V$.
+
+As I perform an Bayesian analysis some mention of priors is required.  A flat prior is used for all parameters except
+for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=2$  LKJ prior and standard
+deviations with
+ $\mu=0.1$, $\sigma=2.5$ Cauchy (Lorentz) distribution prior restricted to non-negative values.
+The nature of the LKJ prior is rather mysterious; one thing to note is that for $\nu=2$ the correlation prior is broad but
+approaches zero at the extremum.  The prior disfavors uniform correlations allowing grey offsets to be attributed to the $\Delta$ parameters.
+
+Figure~\ref{sigma:fig} shows the confidence regions for 
+ the overall scale off the grey offsets
+ ``$\Delta$ scale''
+and of the standard deviations of the $C_c$ diagonal.  This parameter subset is constrained and the  ``$\Delta$ scale'' parameter
+is not highly correlated with the others.  The average
+of the covariance matrix draws (there must be something better to use than this) is 
+\begin{equation}
+\begin{pmatrix}
+0.0050 & 0.0026 & 0.0017 & 0.0015 & 0.0010 \\
+0.0026 & 0.0038 & 0.0035 & 0.0029 & 0.0013 \\
+0.0017 & 0.0035 & 0.0052 & 0.0045 & 0.0032 \\
+0.0015 & 0.0029 & 0.0045 & 0.0046 & 0.0038 \\
+0.0010 & 0.0013 & 0.0032 & 0.0038 & 0.0055
+ \end{pmatrix}.
+ \end{equation}
+ In terms of colors $U-V$, $B-V$, $V-R$, and $V-I$ the covariance is
+\begin{equation}
+\begin{pmatrix}
+ 0.0068 & 0.0025 & -0.0005 & -0.0012 \\
+0.0025 & 0.0020 & -0.0000 & 0.0003 \\
+-0.0005 & -0.0000 & 0.0008 & 0.0012 \\
+-0.0012 & 0.0003 & 0.0012 & 0.0042
+  \end{pmatrix}.
+ \end{equation}
+These correlations indicate that intrinsic color parameters are available.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{output/sigma_corner.pdf} 
+   \caption{Confidence regions for the parameter ``$\Delta$ scale'' that describes the overall scale off the $\Delta$'s
+and of the standard deviations of the diagonal of $C_c$.}
+   \label{sigma:fig}
+\end{figure}
+
+The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{Delta_hist:fig}.  The intrinsic dispersion
+is given by the standard deviation of $0.10$ mag.  The distribution has a broad tail; a model assumption of a normal intrinsic dispersion
+would have been inappropriate.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{output/Delta_hist.pdf} 
+   \caption{Ideogram for the grey offset $\Delta$ for all supernovae.}
+   \label{Delta_hist:fig}
+\end{figure}
+
+To illustrate how the linear model reduces the dispersion in observed absolute magnitude, we take the
+observed $V_o$, and successive correction of $\gamma_2k$,  $\beta EW_{Si}$, and  $\alpha EW_{Ca}$, 
+where the 50\%-ile fit value (of the full model) is used for each parameter.  The histograms over the supernovae for these magnitudes are shown in
+Figure~\ref{magresidual:fig}.  The benefit of each  linear correction results in the reduction in dispersion.  The amount
+of successive reduction in dispersion is similar for all bands.  This is shown for illustration only: in my attempt to reproduce Gerard's previous
+work there were no supernovae reserved for out-of-sample model-comparison tests.  AIC and BIC can be computed.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{output/magresidual_V.pdf} 
+   \caption{Distributions of $V$-band corrected magnitudes.}
+   \label{magresidual:fig}
+\end{figure}
+
+The best-fit distributions for the parameters $\alpha$ and $\beta$, which describe the linear relation between absolute magnitude
+and $EW_{Ca}$ and $EW_{Si}$ respectively, are shown in Figure~\ref{alphabeta:fig}.  The 1-$\sigma$ 
+credible intervals are $\alpha_0=3.0e-3 \pm 8.6e-4$,
+$\alpha_1 = 4.7e-4  \pm 7.2e-4$, $\alpha_2 = 5.3e-4  \pm 5.9e-4$, $\alpha_3 = 7.0e-4  \pm 5.0e-4$,
+$\alpha_4 = 2.1e-3  \pm 4.4e-4$,  $\beta_0=0.03  \pm 2.8e-3$,
+$\beta_1 =0.03  \pm 2.4e-3$, $\beta_2 = 0.03  \pm 2.0e-3$, $\beta_3 =0.02  \pm 1.8e-3$,
+$\beta_4 =0.02  \pm 1.6e-3$.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.9in]{output/alpha_corner.pdf} 
+   \includegraphics[width=2.9in]{output/beta_corner.pdf} 
+   \caption{Distributions for $\alpha$ and $\beta$.}
+   \label{alphabeta:fig}
+\end{figure}
+
+The best-fit distribution for the parameters $\gamma$  and a comparison with the predictions for extrinsic
+magnitude changes being to CCM dust, are shown in Figure~\ref{gamma:fig}.  The 1-$\sigma$ 
+credible intervals are $\gamma_0=1.65 \pm 0.05$,
+$\gamma_1 = 1.33  \pm 0.03$, $\gamma_2 = 0.78  \pm 0.1$, $\gamma_3 = 0.57  \pm 0.3$.
+The CCM dust predictions are based 
+on the central wavelengths of the synthetic broad-band filters, and are expected to be shifted slightly.
+By eye the model fit results appear consistent with $R_V=3.1$, although $R_V=2.8$ appears to match better.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.9in]{output/gamma_corner.pdf} 
+   \includegraphics[width=2.9in]{output/ccm.pdf} 
+   \caption{Best-fit distribution for the parameters $\gamma$ and $\beta$, and a comparison with the predictions for extrinsic
+magnitude changes being to CCM dust.}
+   \label{gamma:fig}
+\end{figure}
+
 %

### 2016-07-12 view2.py

@@ -21,32 +21,82 @@ mag_obs = data['obs'][:,2:]
 EW_cov = data['cov'][:,0:2,0:2]
 mag_cov = data['cov'][:,2:,2:]
 
+dum = numpy.zeros(5,5)
+for x1, x2 in zip(fit['L_Omega'], fit['L_sigma']):
+    dum= dum+ numpy.dot(x2[:,None],x2[None,:])*numpy.dot(x1,x1.T)
+
+dum/= len(fit['L_Omega'])
+print " \\\\\n".join([" & ".join(map('{0:.4f}'.format, line)) for line in dum])
+
+trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1]]
+trans = numpy.array(trans)
+color_cov = numpy.dot(trans,numpy.dot(dum, trans.T))
+print " \\\\\n".join([" & ".join(map('{0:.4f}'.format, line)) for line in color_cov])
+
+
+
+gamma_median = numpy.median(fit['gamma'],axis=0)
+gamma_median = numpy.insert(gamma_median,2,1.)
+
+dum = fit['k_simplex']*fit['k_scale'][:,None]
+dum = dum - dum.mean(axis=1)[:,None]
+
+k_median =  numpy.median(dum,axis=0)
+EW_median = numpy.median(fit['EW'],axis=0)
+beta_median = numpy.median(fit['beta'],axis=0)
+alpha_median = numpy.median(fit['alpha'],axis=0)
+
+filtname = ['U','B','V','R','I']
+
+for i, fi in enumerate(filtname):
+    plt.hist([mag_obs[:, i], mag_obs[:, i] - gamma_median[i]*k_median, \
+        mag_obs[:, i] - gamma_median[i]*k_median -beta_median[i]*EW_median[:,1], \
+        mag_obs[:, i] - gamma_median[i]*k_median -beta_median[i]*EW_median[:,1]-alpha_median[i]*EW_median[:,0]], \
+        label=[r'$M_o$', r'$M_o - \gamma k$', r'$M_o - \gamma k - \beta EW_{Si}$', \
+        r'$M_o - \gamma k - \beta EW_{Si} - \alpha EW_{Ca}$'])
+    plt.legend()
+    plt.title('Filter {}'.format(fi))
+    pp = PdfPages('output/magresidual_{}.pdf'.format(fi))
+    plt.savefig(pp, format='pdf')
+    pp.close()
[…]

### 2016-07-12 forgerard.tex
Factor analysis model.

@@
    \centering
-   \includegraphics[width=4in]{output/sigma_corner.pdf} 
+   \includegraphics[width=4in]{output2/sigma_corner.pdf} 
    \caption{Confidence regions for the parameter ``$\Delta$ scale'' that describes the overall scale off the $\Delta$'s
@@
    \centering
-   \includegraphics[width=4in]{output/Delta_hist.pdf} 
+   \includegraphics[width=4in]{output2/Delta_hist.pdf} 
    \caption{Ideogram for the grey offset $\Delta$ for all supernovae.}
@@
    \centering
-   \includegraphics[width=4in]{output/magresidual_V.pdf} 
+   \includegraphics[width=4in]{output2/magresidual_V.pdf} 
    \caption{Distributions of $V$-band corrected magnitudes.}
@@
    \centering
-   \includegraphics[width=2.9in]{output/alpha_corner.pdf} 
-   \includegraphics[width=2.9in]{output/beta_corner.pdf} 
+   \includegraphics[width=2.9in]{output2/alpha_corner.pdf} 
+   \includegraphics[width=2.9in]{output2/beta_corner.pdf} 
    \caption{Distributions for $\alpha$ and $\beta$.}
@@
    \centering
-   \includegraphics[width=2.9in]{output/gamma_corner.pdf} 
-   \includegraphics[width=2.9in]{output/ccm.pdf} 
+   \includegraphics[width=2.9in]{output2/gamma_corner.pdf} 
+   \includegraphics[width=2.9in]{output2/ccm.pdf} 
    \caption{Best-fit distribution for the parameters $\gamma$ and $\beta$, and a comparison with the predictions for extrinsic
@@
 
+\begin{equation*}
+\left(
+\begin{matrix}
+U\\B\\V\\R\\I
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\Delta +
+\left(
+\begin{matrix}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_0 D \\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_1 D  \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_2 D \\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_3 D \\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_4 D 
+\end{matrix}
+\right)
+,C_{c}
+\right).
+\end{equation*}
+\begin{equation*}
+D \sim \mathcal{N}(0,1)
+\end{equation*}
+\begin{equation*}
+\left(
+\begin{matrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\left(
+\begin{matrix}
+U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+EW_{Si}\\ EW_{Ca}
+\end{matrix}
+\right)
+,C
+\right).
+\end{equation*}
+
+\begin{equation*}
+\begin{pmatrix}
+0.0060 & 0.0024 & -0.0003 & -0.0008 \\
+0.0024 & 0.0017 & -0.0001 & 0.0001 \\
+-0.0003 & -0.0001 & 0.0006 & 0.0007 \\
+-0.0008 & 0.0001 & 0.0007 & 0.0022
+  \end{pmatrix}.
+ \end{equation*}
 %

### 2016-07-12 model3.py

@@ -60,20 +60,14 @@ data = {'D': nsne, 'N_mags': 5, 'N_EWs': 2, 'mag_obs': mag_renorm, 'EW_obs': EW_
 k_simplex = numpy.random.random(size = nsne)
 k_simplex /= sum(k_simplex)
 
-init = [{'EW' : EW_renorm, \
-    'r_c': numpy.random.uniform(numpy.sqrt(5)-0.01,numpy.sqrt(5)+0.01),\
-    'phi_c': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1, size= 3),\
-    'phi_c_4': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1),\
-    'r_alpha': numpy.random.uniform(numpy.sqrt(5)-0.001,numpy.sqrt(5)+0.001),\
-    'phi_alpha': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1, size= 3),\
-    'phi_alpha_4': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1),\
-    'r_beta': numpy.random.uniform(numpy.sqrt(5)+0.03,numpy.sqrt(5)+0.08),\
-    'phi_beta': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1, size= 3),\
-    'phi_beta_4': numpy.random.uniform(numpy.pi/4-0.1, numpy.pi/4+0.1),\
-    'gamma':numpy.array([1.4,1.21,0.824,0.67])+ numpy.random.uniform(-0.01,0.01,size=4), \
-    'k_scale':0.1, 'k_simplex': k_simplex, 'mag_int': mag_renorm+numpy.random.uniform(-0.02,0.02,size=(nsne,5)), \
-    'L_sigma':numpy.random.uniform(0.04, 0.08,size=5),'L_Omega':numpy.identity(5)} \
-    for _ in range(4)]
+init = [{'EW' : EW_renorm, 'c': numpy.random.normal(0,0.02,size=5),\
+         'alpha': numpy.random.uniform(-0.01, 0.01, size= 5), 'beta':numpy.array([0.06,0.05,0.04,0.03,0.02])+numpy.random.normal(0,0.005,size=5),
+         'gamma':numpy.array([1.4,1.2,0.85,0.7])+ numpy.random.normal(0,0.01,size=4), 'k_scale':0.1, 'k_simplex': k_simplex,
+         'mag_int':
[…]

### 2016-07-15 forgerard.tex
quadratic model5

@@
 \begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_0 D \\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_1 D  \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_2 D \\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_3 D \\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_4 D 
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\rho_{00} R +\rho_{10} R^2\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\rho_{01} R  +\rho_{11} R^2\\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\rho_{02} R +\rho_{12} R^2\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\rho_{03} R +\rho_{13} R^2\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\rho_{04} R +\rho_{14} R^2
 \end{matrix}
@@
 \begin{equation*}
-D \sim \mathcal{N}(0,1)
+R \sim \mathcal{N}(\bar{R},1)
 \end{equation*}

### 2016-07-15 model5.py

@@ -1,0 +1,85 @@
+import pickle
+import numpy
+import pystan
+
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+#  The ordering is 'Ca','Si','U','B','V','R','I'
+
+EW_obs = data['obs'][:,0:2]
+mag_obs = data['obs'][:,2:]
+EW_cov = data['cov'][:,0:2,0:2]
+mag_cov = data['cov'][:,2:,2:]
+
+nsne, nmags = mag_obs.shape
+# color_obs = numpy.zeros((nsne,nmags))
+# color_obs[:,0] = mag_obs[:,0]- mag_obs[:,2]
+# color_obs[:,1] = mag_obs[:,1]- mag_obs[:,2]
+# color_obs[:,2] = mag_obs[:,2]- mag_obs[:,3]
+# color_obs[:,3] = mag_obs[:,2]- mag_obs[:,4]
+# color_obs[:,4] = mag_obs[:,2]
+
+
+
+# trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1],[0.,0,1,0,0]]
+# trans = numpy.array(trans)
+# color_cov = numpy.zeros((nsne,5,5))
+# for i in xrange(nsne):
+#     color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
+
+
+# # renormalize the data
+EW_mn = EW_obs.mean(axis=0)
+# EW_std = EW_obs.std(axis=0)
+# EW_renorm = (EW_obs - EW_mn)/EW_std
+EW_renorm = (EW_obs - EW_mn)
+
+# # EW_cov_renorm = numpy.array(EW_cov)
+# # for i in xrange(nsne):
+# #     EW_cov_renorm[i] = EW_cov_renorm[i] /EW_std[None,:] / EW_std[:,None]
+
+# color_mn = color_obs.mean(axis=0)
+# # color_std = color_obs[1].std()
+
+# # color_renorm = (color_obs - color_mn)/color_std
+# color_renorm = (color_obs - color_mn)
+# # color_cov_renorm = numpy.array(color_cov)
+# # for i in xrange(nsne):
+# #     color_cov_renorm[i] = color_cov_renorm[i] /color_std**2
+
+mag_mn = mag_obs.mean(axis=0)
+mag_renorm  = mag_obs-mag_mn
+
[…]

### 2016-07-15 view2.py

@@ -21,6 +21,9 @@ mag_obs = data['obs'][:,2:]
 EW_cov = data['cov'][:,0:2,0:2]
 mag_cov = data['cov'][:,2:,2:]
 
+nsne = len(mag_obs)
+nlinks = len(fit['L_sigma'])
+
 dum = numpy.zeros((5,5))
 for x1, x2 in zip(fit['L_Omega'], fit['L_sigma']):
     dum= dum+ numpy.dot(x2[:,None],x2[None,:])*numpy.dot(x1,x1.T)
@@ -205,13 +208,14 @@ with PdfPages('output2/multipage_pdf.pdf') as pdf:
     # plt.hist(fit['k_simplex'].flatten())
     # pdf.savefig()
     # plt.close()
+    dumgamma = numpy.concatenate((fit['gamma'][:,0:2],numpy.random.normal(1,0.0001,size=(nlinks,1)),fit['gamma'][:,2:]),axis=1)
 
-    mega = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['L_sigma']])
+    mega = numpy.array([fit['c'],fit['alpha'],fit['beta'],dumgamma,fit['L_sigma']])
     mega = numpy.transpose(mega)
 
     for index in xrange(5):
         figure = corner.corner(mega[index,:,:],labels=[r"$c_{}$".format(index),r"$\alpha_{}$".format(index),\
-            r"$\beta_{}$".format(index),r"$\sigma_{}$".format(index)])
+            r"$\beta_{}$".format(index),r"$\gamma_{}$".format(index),r"$\sigma_{}$".format(index)])
         pdf.savefig()
         plt.close()
 
@@ -253,7 +257,6 @@ for rv in rvs:
     axes[1,0].set_xlabel(r'B-V')
     axes[1,0].set_ylabel(r'U + spec correction')
 
-
 axes[0,1].scatter(mag_obs[:, 1]-mag_obs[:, 2],mag_obs[:, 4])
 xl = numpy.array(axes[0,0].get_xlim())* numpy.array([0.9, 0.6])
 yl = numpy.array(axes[0,0].get_ylim())
@@ -284,6 +287,87 @@ plt.tight_layout()
 pp = PdfPages('output2/colormag.pdf')
 plt.savefig(pp,format='pdf')
 pp.close()
+plt.close()
+
+fig, axes = plt.subplots(ncols=2)
[…]

### 2016-07-20 forgerard.tex
cleaning out old runs

--- 2016-07-12 forgerard.tex
@@
 \begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_0 D \\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_1 D  \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_2 D \\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_3 D \\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_4 D 
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{00} D +\delta_{10} D^2\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{01} D  +\delta_{11} D^2\\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{02} D +\delta_{12} D^2\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{03} D +\delta_{13} D^2\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_{04} D +\delta_{14} D^2
 \end{matrix}
@@
 \end{equation*}
-\begin{equation*}
-D \sim \mathcal{N}(0,1)
-\end{equation*}
+%\begin{equation*}
+%D \sim \mathcal{N}(\bar{D},1)
+%\end{equation*}
 \begin{equation*}
@@
 \end{equation*}
+$\langle \Delta \rangle=0$, $\langle k \rangle=0$, $\gamma_2=1$, $\langle D \rangle=0$, $\langle D^2 \rangle=1$.
 
-\begin{equation*}
-\begin{pmatrix}
-0.0060 & 0.0024 & -0.0003 & -0.0008 \\
-0.0024 & 0.0017 & -0.0001 & 0.0001 \\
--0.0003 & -0.0001 & 0.0006 & 0.0007 \\
--0.0008 & 0.0001 & 0.0007 & 0.0022
-  \end{pmatrix}.
- \end{equation*}
 %

### 2016-07-20 model2.py

@@ -2,6 +2,7 @@ import pickle
 import numpy
 import pystan
 
+# one color parameter model
 
 pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)

### 2016-07-20 model3.py

@@ -1,85 +1,0 @@
-import pickle
-import numpy
-import pystan
-
-
-pkl_file = open('gege_data.pkl', 'r')
-data = pickle.load(pkl_file)
-pkl_file.close()
-
-#  The ordering is 'Ca','Si','U','B','V','R','I'
-
-EW_obs = data['obs'][:,0:2]
-mag_obs = data['obs'][:,2:]
-EW_cov = data['cov'][:,0:2,0:2]
-mag_cov = data['cov'][:,2:,2:]
-
-nsne, nmags = mag_obs.shape
-# color_obs = numpy.zeros((nsne,nmags))
-# color_obs[:,0] = mag_obs[:,0]- mag_obs[:,2]
-# color_obs[:,1] = mag_obs[:,1]- mag_obs[:,2]
-# color_obs[:,2] = mag_obs[:,2]- mag_obs[:,3]
-# color_obs[:,3] = mag_obs[:,2]- mag_obs[:,4]
-# color_obs[:,4] = mag_obs[:,2]
-
-
-
-# trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1],[0.,0,1,0,0]]
-# trans = numpy.array(trans)
-# color_cov = numpy.zeros((nsne,5,5))
-# for i in xrange(nsne):
-#     color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
-
-
-# # renormalize the data
-EW_mn = EW_obs.mean(axis=0)
-# EW_std = EW_obs.std(axis=0)
-# EW_renorm = (EW_obs - EW_mn)/EW_std
-EW_renorm = (EW_obs - EW_mn)
-
-# # EW_cov_renorm = numpy.array(EW_cov)
-# # for i in xrange(nsne):
-# #     EW_cov_renorm[i] = EW_cov_renorm[i] /EW_std[None,:] / EW_std[:,None]
-
-# color_mn = color_obs.mean(axis=0)
-# # color_std = color_obs[1].std()
-
-# # color_renorm = (color_obs - color_mn)/color_std
-# color_renorm = (color_obs - color_mn)
-# # color_cov_renorm = numpy.array(color_cov)
-# # for i in xrange(nsne):
-# #     color_cov_renorm[i] = color_cov_renorm[i] /color_std**2
-
-mag_mn = mag_obs.mean(axis=0)
-mag_renorm  = mag_obs-mag_mn
-
[…]

### 2016-07-20 model4.py

@@ -1,92 +1,0 @@
-import pickle
-import numpy
-import pystan
-
-
-pkl_file = open('gege_data.pkl', 'r')
-data = pickle.load(pkl_file)
-pkl_file.close()
-
-#  The ordering is 'Ca','Si','U','B','V','R','I'
-
-EW_obs = data['obs'][:,0:2]
-mag_obs = data['obs'][:,2:]
-EW_cov = data['cov'][:,0:2,0:2]
-mag_cov = data['cov'][:,2:,2:]
-
-ok = (mag_obs[:,1]- mag_obs[:,2]) < -0.25
-
-EW_obs = EW_obs[ok,:]
-mag_obs = mag_obs[ok,:]
-EW_cov = EW_cov[ok,:]
-mag_cov =mag_cov[ok,:]
-
-nsne, nmags = mag_obs.shape
-# color_obs = numpy.zeros((nsne,nmags))
-# color_obs[:,0] = mag_obs[:,0]- mag_obs[:,2]
-# color_obs[:,1] = mag_obs[:,1]- mag_obs[:,2]
-# color_obs[:,2] = mag_obs[:,2]- mag_obs[:,3]
-# color_obs[:,3] = mag_obs[:,2]- mag_obs[:,4]
-# color_obs[:,4] = mag_obs[:,2]
-
-
-
-# trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1],[0.,0,1,0,0]]
-# trans = numpy.array(trans)
-# color_cov = numpy.zeros((nsne,5,5))
-# for i in xrange(nsne):
-#     color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
-
-
-# # renormalize the data
-EW_mn = EW_obs.mean(axis=0)
-# EW_std = EW_obs.std(axis=0)
-# EW_renorm = (EW_obs - EW_mn)/EW_std
-EW_renorm = (EW_obs - EW_mn)
-
-# # EW_cov_renorm = numpy.array(EW_cov)
-# # for i in xrange(nsne):
-# #     EW_cov_renorm[i] = EW_cov_renorm[i] /EW_std[None,:] / EW_std[:,None]
-
-# color_mn = color_obs.mean(axis=0)
-# # color_std = color_obs[1].std()
-
-# # color_renorm = (color_obs - color_mn)/color_std
[…]

### 2016-07-20 model5.py

@@ -2,6 +2,7 @@ import pickle
 import numpy
 import pystan
 
+# two color parameter model
 
 pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)
@@ -66,12 +67,13 @@ init = [{'EW' : EW_renorm, 'c': numpy.random.normal(0,0.02,size=5),\
          'alpha': numpy.random.uniform(-0.01, 0.01, size= 5), \
          'beta':numpy.array([0.06,0.05,0.04,0.03,0.02])+numpy.random.normal(0,0.005,size=5),
          'gamma_': numpy.random.uniform(.9,1.1,size=4), \
-         'k_unit': (-1.)**numpy.arange(nsne-1)/numpy.sqrt(nsne-1),\
+         'k_unit': k_simplex, 'k_scale': 15,\
          'mag_int': mag_renorm+numpy.random.normal(0,0.02,size=(nsne,5)), \
          'L_sigma':numpy.random.uniform(0.02, 0.06,size=5), \
-         'L_Omega':numpy.identity(5), 
-         'Delta_simplex':k_simplex,'Delta_scale': 15, \
-         'R_unit':(-1.)**numpy.arange(nsne-2)/numpy.sqrt(nsne-2), \
+         'L_Omega':numpy.identity(5), \
+         # 'Delta_simplex':k_simplex,'Delta_scale': 15, \
+         'Delta_unit':k_simplex, 'Delta_scale': 15, \
+         'R_unit':k_simplex, \
          'rho0':numpy.zeros(5),'rho1':numpy.zeros(5)}
         for _ in range(4)]
 
@@ -84,7 +86,7 @@ init = [{'EW' : EW_renorm, 'c': numpy.random.normal(0,0.02,size=5),\
 sm = pystan.StanModel(file='gerard5.stan')
 # fit = sm.sampling(data=data, iter=200, chains=4,init=[init1,init1,init1,init1])
 control = {'stepsize':1.}
-fit = sm.sampling(data=data, iter=1000, chains=4,control=control,init=init)
+fit = sm.sampling(data=data, iter=2000, chains=4,control=control,init=init)
 print fit
 
 output = open('temp5.pkl','wb')

### 2016-07-27 forgerard.tex
latest thing running

@@
 \begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
 \end{matrix}
@@
 individual spectral parameters  $EW_{Ca}$, and $EW_{Si}$ via the  global coefficients
- $c_i$, $\alpha_i$, $\beta_i$.  Residual variations in absolute magnitude is described
+ $\alpha_i$, $\beta_i$.  Residual variations in absolute magnitude is described
  by  $C_c$ the intrinsic dispersion of the Normal distribution.  To constrain the problem we
@@
 \begin{matrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
-\end{matrix}
+U_o -\langle U_o \rangle \\B_o-\langle B_o \rangle\\ V_o-\langle V_o \rangle\\R_o-\langle R_o \rangle\\I_o-\langle I_o \rangle\\EW_{Si, o}-\langle EW_{Si, o} \rangle\\ EW_{Ca, o}-\langle EW_{Ca, o} \end{matrix}
 \right) \sim \mathcal{N}
@@
 $k$ and global parameters $\gamma_i$.  
-To constrain the problem we set  $\langle k \rangle=0$.  We also set  $\gamma_2=1$ meaning that $k$ can be interpreted as $A_V$.
+To constrain the problem we set  $\langle k \rangle=0$, $\langle k^2 \rangle=1$, $\gamma_0 \ge 0$.
 
@@
    \centering
-   \includegraphics[width=4in]{output2/sigma_corner.pdf} 
+   \includegraphics[width=4in]{output7/sigma_corner.pdf} 
    \caption{Confidence regions for the parameter ``$\Delta$ scale'' that describes the overall scale off the $\Delta$'s
@@
    \centering
-   \includegraphics[width=4in]{output2/Delta_hist.pdf} 
+   \includegraphics[width=4in]{output7/Delta_hist.pdf} 
    \caption{Ideogram for the grey offset $\Delta$ for all supernovae.}
@@
    \centering
-   \includegraphics[width=4in]{output2/magresidual_V.pdf} 
+   \includegraphics[width=4in]{output7/colormag.pdf} 
    \caption{Distributions of $V$-band corrected magnitudes.}
@@
    \centering
-   \includegraphics[width=2.9in]{output2/alpha_corner.pdf} 
-   \includegraphics[width=2.9in]{output2/beta_corner.pdf} 
+   \includegraphics[width=2.9in]{output7/alpha_corner.pdf} 
+   \includegraphics[width=2.9in]{output7/beta_corner.pdf} 
    \caption{Distributions for $\alpha$ and $\beta$.}
@@
    \centering
-   \includegraphics[width=2.9in]{output2/gamma_corner.pdf} 
-   \includegraphics[width=2.9in]{output2/ccm.pdf} 
+   \includegraphics[width=2.9in]{output7/gamma_corner.pdf} 
+   \includegraphics[width=2.9in]{output7/ccm.pdf} 
    \caption{Best-fit distribution for the parameters $\gamma$ and $\beta$, and a comparison with the predictions for extrinsic
@@
 \begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{00} D +\delta_{10} D^2\\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{01} D  +\delta_{11} D^2\\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{02} D +\delta_{12} D^2\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{03} D +\delta_{13} D^2\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_{04} D +\delta_{14} D^2
+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{00} D +\delta_{10} D^2\\
+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{01} D  +\delta_{11} D^2\\
+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{02} D +\delta_{12} D^2\\
+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{03} D +\delta_{13} D^2\\
+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_{04} D +\delta_{14} D^2
 \end{matrix}
@@
 \begin{matrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
+U_o -\langle U_o \rangle \\B_o-\langle B_o \rangle\\ V_o-\langle V_o \rangle\\R_o-\langle R_o \rangle\\I_o-\langle I_o \rangle\\EW_{Si, o}-\langle EW_{Si, o} \rangle\\ EW_{Ca, o}-\langle EW_{Ca, o} 
 \end{matrix}
@@
 \end{equation*}
-$\langle \Delta \rangle=0$, $\langle k \rangle=0$, $\gamma_2=1$, $\langle D \rangle=0$, $\langle D^2 \rangle=1$.
-
+\begin{equation*}
+\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle D \rangle=0, \langle D^2 \rangle=1, \gamma_0 \ge 0, \delta_{04}\ge0.
+\end{equation*}
 %

### 2016-07-27 model5.py

@@ -16,78 +16,38 @@ EW_cov = data['cov'][:,0:2,0:2]
 mag_cov = data['cov'][:,2:,2:]
 
 nsne, nmags = mag_obs.shape
-# color_obs = numpy.zeros((nsne,nmags))
-# color_obs[:,0] = mag_obs[:,0]- mag_obs[:,2]
-# color_obs[:,1] = mag_obs[:,1]- mag_obs[:,2]
-# color_obs[:,2] = mag_obs[:,2]- mag_obs[:,3]
-# color_obs[:,3] = mag_obs[:,2]- mag_obs[:,4]
-# color_obs[:,4] = mag_obs[:,2]
-
-
-
-# trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1],[0.,0,1,0,0]]
-# trans = numpy.array(trans)
-# color_cov = numpy.zeros((nsne,5,5))
-# for i in xrange(nsne):
-#     color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
-
 
 # # renormalize the data
 EW_mn = EW_obs.mean(axis=0)
-# EW_std = EW_obs.std(axis=0)
-# EW_renorm = (EW_obs - EW_mn)/EW_std
 EW_renorm = (EW_obs - EW_mn)
-
-# # EW_cov_renorm = numpy.array(EW_cov)
-# # for i in xrange(nsne):
-# #     EW_cov_renorm[i] = EW_cov_renorm[i] /EW_std[None,:] / EW_std[:,None]
-
-# color_mn = color_obs.mean(axis=0)
-# # color_std = color_obs[1].std()
-
-# # color_renorm = (color_obs - color_mn)/color_std
-# color_renorm = (color_obs - color_mn)
-# # color_cov_renorm = numpy.array(color_cov)
-# # for i in xrange(nsne):
-# #     color_cov_renorm[i] = color_cov_renorm[i] /color_std**2
 
 mag_mn = mag_obs.mean(axis=0)
 mag_renorm  = mag_obs-mag_mn
 
-# data = {'D': nsne, 'N_colors': 5, 'N_EWs': 2, 'color_obs': color_renorm, \
-#     'EW_obs': EW_renorm, 'EW_cov': EW_cov_renorm, 'color_cov':color_cov_renorm, 'color_std':color_std.astype('float'), 'color_mn':color_mn}
[…]

### 2016-07-27 view6.py

@@ -134,11 +134,6 @@ with PdfPages('output6/multipage_pdf.pdf') as pdf:
     pdf.savefig()
     plt.close()
 
-    plt.plot(fit['k_scale'][::10])
-    plt.title('k_scale')
-    pdf.savefig()
-    plt.close()
-
     plt.plot(fit['Delta_scale'][::10])
     plt.title(r'$\Delta$ scale')
     pdf.savefig()
@@ -200,7 +195,7 @@ for i in xrange(len(filts)):
     axes[i].set_ylabel(r'{}'.format(filts[i]))
     offset  = numpy.mean(mag_obs[:, i] - numpy.median(fit['alpha'][:,i][:,None]*fit['EW'][:,:,0],axis=0))
     axes[i].plot(EW_obs[r,0],offset+numpy.median(fit['alpha'][:,i],axis=0)*EW_renorm[r,0] \
-        ,color='black',linewidth=2)
+        ,color='red',linewidth=2)
 axes[len(filts)-1].set_xlabel(r'EW(Ca)')
 fig.subplots_adjust(hspace=0.001)
 pp = PdfPages('output6/speccamag.pdf')
@@ -218,7 +213,7 @@ for i in xrange(len(filts)):
     axes[i].set_ylabel(r'{}'.format(filts[i]))
     offset  = numpy.mean(mag_obs[:, i] - numpy.median(fit['beta'][:,i][:,None]*fit['EW'][:,:,1],axis=0))
     axes[i].plot(EW_obs[r,1],offset+numpy.median(fit['beta'][:,i],axis=0)*EW_renorm[r,1] \
-        ,color='black',linewidth=2)
+        ,color='red',linewidth=2)
 axes[len(filts)-1].set_xlabel(r'EW(Si)')
 fig.subplots_adjust(hspace=0.001)
 pp = PdfPages('output6/specsimag.pdf')
@@ -237,7 +232,7 @@ for i in xrange(len(filts)):
     slope = numpy.median(fit['gamma'][:,i] / (fit['gamma'][:,1]-fit['gamma'][:,2]),axis=0)
     offset  = numpy.mean(mag_obs[:, i] - numpy.median(slope*(mag_obs[:,1]-mag_obs[:,2])))
     axes[i].plot(mag_obs[r,1]-mag_obs[r,2],offset+slope*(mag_obs[r,1]-mag_obs[r,2]) \
-        ,color='black',linewidth=2)
[…]

### 2016-07-27 view7.py

@@ -13,6 +13,14 @@ fit = pickle.load(f)
 for key in fit.keys():
     print key, fit[key].min(), fit[key].max()
 
+for i in xrange(5):
+    dum = numpy.percentile(fit['alpha'][:,i],(50,50-34,50+34))
+    print '$\\alpha_{} = {:6.4f}^{{{:6.4f}}}_{{{:6.4f}}}$'.format(i, dum[0], dum[2]-dum[0],dum[1]-dum[0] )
+
+for i in xrange(5):    
+    dum = numpy.percentile(fit['beta'][:,i],(50,50-34,50+34))
+    print '$\\beta_{} = {:5.3f}^{{{:5.3f}}}_{{{:5.3f}}}$'.format(i, dum[0], dum[2]-dum[0],dum[1]-dum[0] )
+
 pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)
 pkl_file.close()
@@ -189,7 +197,7 @@ for i in xrange(len(filts)):
     axes[i].set_ylabel(r'{}'.format(filts[i]))
     offset  = numpy.mean(mag_obs[:, i] - numpy.median(fit['alpha'][:,i][:,None]*fit['EW'][:,:,0],axis=0))
     axes[i].plot(EW_obs[r,0],offset+numpy.median(fit['alpha'][:,i],axis=0)*EW_renorm[r,0] \
-        ,color='black',linewidth=2)
+        ,color='red',linewidth=2)
 axes[len(filts)-1].set_xlabel(r'EW(Ca)')
 fig.subplots_adjust(hspace=0.001)
 pp = PdfPages('output7/speccamag.pdf')
@@ -207,7 +215,7 @@ for i in xrange(len(filts)):
     axes[i].set_ylabel(r'{}'.format(filts[i]))
     offset  = numpy.mean(mag_obs[:, i] - numpy.median(fit['beta'][:,i][:,None]*fit['EW'][:,:,1],axis=0))
     axes[i].plot(EW_obs[r,1],offset+numpy.median(fit['beta'][:,i],axis=0)*EW_renorm[r,1] \
-        ,color='black',linewidth=2)
+        ,color='red',linewidth=2)
 axes[len(filts)-1].set_xlabel(r'EW(Si)')
 fig.subplots_adjust(hspace=0.001)
 pp = PdfPages('output7/specsimag.pdf')
[…]

### 2016-08-02 forgerard.tex
writing the note

--- 2016-07-20 forgerard.tex
@@
 \begin{document}
-The model for the intrinsic absolute magnitudes $U$, $B$, $V$, $R$, and $I$ is that they are drawn from a Normal distribution
+\section{Data}
+The data set consists of synthetic $UBVRI$ peak brightnesses and Si and Ca equivalent widths at peak
+of 172 SNf supernovae.  The photometry is normalized to place all supernovae at a common distance, as
+inferred by redshift.
+The data was provided by Manu Gangler.
+
+\section{Model Fits}
+\subsection{One-Color Model}
+We hypothesize that Type Ia supernova spectral features are predictive of intrinsic
+magnitudes.  The intrinsic magnitudes are not perfectly deterministic, but have some intrinsic dispersion.
+An extrinsic physical process common to all supernovae can influence the propagation
+of light along the line of sight to incluence apparent magnitudes.
+
+\subsubsection{Setup}
+Specifically, we assume a linear relationship between the equivalent widths of the Ca and Si spectral features
+$EW_{Ca}$ and $EW_{Si}$, and the intrinsic $UBVRI$ magnitudes
+with residual Gaussian dispersion with covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
+to capture grey intrinsic dispersion and distance errors introduced in the normalization of the photometry.
+The  extrinsic process is also assumed to be linear.  The observables
+$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$ and $EW_{Si,o}$ have Gaussian uncertainty with covariance $C$.  The model can be expressed
 \begin{equation*}
@@
 ,C_{c}
-\right).
+\right)
 \end{equation*}
-The mean of the normal distribution linearly relates absolute magnitudes with
-individual spectral parameters  $EW_{Ca}$, and $EW_{Si}$ via the  global coefficients
- $c_i$, $\alpha_i$, $\beta_i$.  Residual variations in absolute magnitude is described
- by  $C_c$ the intrinsic dispersion of the Normal distribution.  To constrain the problem we
- set $\langle \Delta \rangle=0$.
-
-The observed magnitudes  $U_o$, $B_o$, $V_o$, $R_o$, and $I_o$  and spectral features  $EW_{Ca,o}$, and $EW_{Si,o}$ are modeled
-as being drawn from a Normal distribution. 
 \begin{equation*}
@@
 \begin{matrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\left(
+\begin{matrix}
+U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+EW_{Si}\\ EW_{Ca}
+\end{matrix}
+\right)
+,C
+\right)
+\end{equation*}
+The global parameters $c$, $\alpha$, and $\beta$ are the intercepts and slopes of the bilinear relationships between equivalent widths
+and intrinsic magnitudes.  The extrinsic piece is split into the properties $\gamma$ of the physical process and the per-supernova 
+parameters $k$ that indicate how much of that process each object undergoes.  To break the degeneracies inherent in the model we impose
+\begin{equation*}
+\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \gamma_0 \ge 0.
+\end{equation*}
+
+Having the intrinsic dispersion $C_c$ as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
+ascribed to $\Delta$ and $\gamma k$ could also be attributed to intrinsic dispersion.  There are several features of the model
+that drives the assignation of variations away from $C_c$:  The probability distribution functions decrease
+with increasing $\det{C_c}$ so growing $C_c$ is disfavored; The distributions of $\Delta$ and $k$ are turn out to
+be non-Gaussian, and so are not well described by a Normal covariance; The Bayesian prior selected for $C_c$ disfavors
+grey offsets.
+
+If interpreted as being due to dust, the extrinsic term could be associated with extinction $A_X = \gamma_X k$.  In
+this parlance $E(B-V) = (\gamma_1-\gamma_2) k$ and $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
+Note that these values of $A_X$, $E(B-V)$, and $R_X$ do not depend on the normalization condition $ \langle k^2 \rangle$, i.e.\
+are independent of the transformation $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1} k$.
+
+As I perform an Bayesian analysis some mention of priors is required.  A flat prior is used for all parameters except
+for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=2$  LKJ prior and standard
+deviations with
+ $\mu=0$, $\sigma=1$ Cauchy (Lorentz) distribution prior restricted to non-negative values.
+The nature of the LKJ prior is rather mysterious; one thing to note is that for $\nu=2$ the correlation prior is broad but
+approaches zero at the extremum.
+
+\subsubsection{Results}
+The 68\% intervals for the global parameters $\alpha$, $\beta$, $\gamma$, and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global:tab}.
+The two dimensional contours for the parameters of each filter are shown in Figure~\ref{global:fig}.  The Table does not show
+the results for $c$ as their values are not significant for the aims of this analysis, the Figure does show $c$ to indicate the convergence
+and correlations of these parameters in the fit.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+& $X=0$ &1&2&3&4\\ \hline
+$\alpha_X$
+&
+$0.0031^{0.0008}_{-0.0009}$
+&
+$0.0005^{0.0007}_{-0.0007}$
+&
+$0.0006^{0.0006}_{-0.0006}$
+&
+$0.0007^{0.0005}_{-0.0005}$
+&
+$0.0021^{0.0004}_{-0.0004}$
+\\
+$\beta_X$
+&
+$0.0345^{0.0027}_{-0.0029}$
+&
+$0.0274^{0.0022}_{-0.0025}$
+&
+$0.0274^{0.0021}_{-0.0021}$
+&
+$0.0223^{0.0018}_{-0.0018}$
+&
+$0.0213^{0.0016}_{-0.0017}$
+\\
+$\gamma_X$
+&
+$0.3818^{0.0138}_{-0.0132}$
+&
+$0.3108^{0.0117}_{-0.0113}$
+&
+$0.2342^{0.0118}_{-0.0115}$
+&
+$0.1827^{0.0107}_{-0.0111}$
+&
+$0.1357^{0.0110}_{-0.0119}$
+\\
+$\sigma_X$
+&
+$0.0693^{0.0157}_{-0.0152}$
+&
+$0.0575^{0.0099}_{-0.0089}$
+&
+$0.0679^{0.0083}_{-0.0080}$
+&
+$0.0639^{0.0073}_{-0.0069}$
+&
+$0.0703^{0.0075}_{-0.0075}$
+\\
+\hline
+\end{tabular}
+\caption{68\% Intervals for Global Fit Parameters \label{global:tab}}
+\end{table}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.5in]{output7/coeff0.pdf} 
+   \includegraphics[width=2.5in]{output7/coeff1.pdf} 
+   \includegraphics[width=2.5in]{output7/coeff2.pdf} 
+      \includegraphics[width=2.5in]{output7/coeff3.pdf} 
+         \includegraphics[width=2.5in]{output7/coeff4.pdf} 
+            \caption{Distributions for $c$, $\alpha$, $\beta$, $\gamma$, and $\sigma$ in each of the 5 bands.}
+   \label{global:fig}
+\end{figure}
+
+We find a small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
+magnitudes.  All bands show larger and significant non-zero values for $\beta$.  This confirms the part of our hypothesis that spectral indicators
+are tracers of supernova absolute magnitude.
+
+The best-fit distribution for the parameters $\gamma$  and our measurement of
+$\frac{\gamma_X}{\gamma_1-\gamma_2}$  compared with the predictions of CCM dust are shown in Figure~\ref{gamma:fig}:
+our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
+of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ has significantly smaller
+uncertainties and are consistent with $R_V=3.1$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.4in]{output7/gamma_corner.pdf} 
+   \includegraphics[width=3.3in]{output7/ccm.pdf} 
+   \caption{Left: Best-fit distribution for the parameters $\gamma$.  Right: 68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
+   predictions for different values of $R_V$.}
+   \label{gamma:fig}
+\end{figure}
+
+Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
+square root of the diagonal elements of $C_c$.
+A representative example is given by the matrix comprised by the average of each element in the Monte Carlo chain.
+For $UBVRI$ the matrix is
+\begin{equation}
+\begin{pmatrix}
+0.0050 & 0.0026 & 0.0017 & 0.0014 & 0.0009 \\
+0.0026 & 0.0034 & 0.0032 & 0.0026 & 0.0011 \\
+0.0017 & 0.0032 & 0.0047 & 0.0041 & 0.0029 \\
+0.0014 & 0.0026 & 0.0041 & 0.0042 & 0.0035 \\
+0.0009 & 0.0011 & 0.0029 & 0.0035 & 0.0050
+ \end{pmatrix}.
+ \end{equation}
+ In terms of colors $U-V$, $B-V$, $V-R$, and $V-I$ the covariance is
+\begin{equation}
+\begin{pmatrix}
+0.0064 & 0.0025 & -0.0004 & -0.0010 \\
+0.0025 & 0.0018 & -0.0000 & 0.0003 \\
+-0.0004 & -0.0000 & 0.0007 & 0.0011 \\
+-0.0010 & 0.0003 & 0.0011 & 0.0039
+  \end{pmatrix}.
+ \end{equation}
+ The $B-V$ and $V-R$ colors have small standard deviations of  0.04 mag and 0.03 mag with no correlation.  The
+ residuals not accounted by the
+ model are stronger in the $U-V$ and $V-I$ bands.
+
+ \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.4in]{output7/sigma_corner.pdf} 
+   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.}
+   \label{sigma:fig}
+\end{figure}
+
+The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
+is given by the standard deviation of $0.10$ mag.  The distribution is non-Gaussian, with a broad tail. 
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output7/Delta_hist.pdf} 
+   \includegraphics[width=2.8in]{output7/k_hist.pdf} 
+   \caption{Ideograms for Left: the grey offset $\Delta$; Right: the color term $k$ for all supernovae.}
+   \label{hist:fig}
+\end{figure}
+
+The ideogram for the color term  $k$ for all supernovae is shown in Figure~\ref{hist:fig}.The distribution is non-Gaussian, with a broad tail.
+
+To illustrate how the linear model reduces the dispersion in observed absolute magnitude, plot the observed colors as a
+function of the observed  $EW_{Ca, o}$, $EW_{Si,o}$ and $B_o-V_o$ in Fig.~\ref{magresidual:fig}.  Overplotted are lines with the
+best-fit slope.  The data in the color magnitude diagram indicate that the slope at bluer colors is different from that at redder colors
+and that our one-color linear model could be improved upon.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output7/speccamag.pdf} 
+      \includegraphics[width=2.8in]{output7/specsimag.pdf} 
+   \includegraphics[width=2.8in]{output7/colormag.pdf} 
+   \caption{Observed $UBVRI$ as a function of observed   $EW_{Ca, o}$ (top left), $EW_{Si,o}$ (top right) and $B_o-V_o$ (bottom).
+   Overplotted are lines with the best-fit slope from the model fit.}
+   \label{magresidual:fig}
+\end{figure}
+
+\subsubsection{Notes}
+Some equivalent widths go positive.  Is this an emission?
+
+Add Si line velocity.
+
+\subsection{Two-Color Model}
+Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
+Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
+with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
+that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
+
+\subsubsection{Setup}
+\begin{equation*}
+\left(
+\begin{matrix}
+U\\B\\V\\R\\I
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\Delta +
+\left(
+\begin{matrix}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
+\end{matrix}
+\right)
+,C_{c}
+\right).
+\end{equation*}
+%\begin{equation*}
+%D \sim \mathcal{N}(\bar{D},1)
+%\end{equation*}
+\begin{equation*}
+\left(
+\begin{matrix}
+U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
 \end{matrix}
@@
 \end{equation*}
-The mean of the normal distribution is the intrinsic magnitudes plus an extrinsic magnitude change described by a parameter for each individual supernova
-$k$ and global parameters $\gamma_i$.  
-To constrain the problem we set  $\langle k \rangle=0$.  We also set  $\gamma_2=1$ meaning that $k$ can be interpreted as $A_V$.
-
-As I perform an Bayesian analysis some mention of priors is required.  A flat prior is used for all parameters except
-for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=2$  LKJ prior and standard
-deviations with
- $\mu=0.1$, $\sigma=2.5$ Cauchy (Lorentz) distribution prior restricted to non-negative values.
-The nature of the LKJ prior is rather mysterious; one thing to note is that for $\nu=2$ the correlation prior is broad but
-approaches zero at the extremum.  The prior disfavors uniform correlations allowing grey offsets to be attributed to the $\Delta$ parameters.
-
-Figure~\ref{sigma:fig} shows the confidence regions for 
- the overall scale off the grey offsets
- ``$\Delta$ scale''
-and of the standard deviations of the $C_c$ diagonal.  This parameter subset is constrained and the  ``$\Delta$ scale'' parameter
-is not highly correlated with the others.  The average
-of the covariance matrix draws (there must be something better to use than this) is 
-\begin{equation}
-\begin{pmatrix}
-0.0050 & 0.0026 & 0.0017 & 0.0015 & 0.0010 \\
-0.0026 & 0.0038 & 0.0035 & 0.0029 & 0.0013 \\
-0.0017 & 0.0035 & 0.0052 & 0.0045 & 0.0032 \\
-0.0015 & 0.0029 & 0.0045 & 0.0046 & 0.0038 \\
-0.0010 & 0.0013 & 0.0032 & 0.0038 & 0.0055
- \end{pmatrix}.
- \end{equation}
- In terms of colors $U-V$, $B-V$, $V-R$, and $V-I$ the covariance is
-\begin{equation}
-\begin{pmatrix}
- 0.0068 & 0.0025 & -0.0005 & -0.0012 \\
-0.0025 & 0.0020 & -0.0000 & 0.0003 \\
--0.0005 & -0.0000 & 0.0008 & 0.0012 \\
--0.0012 & 0.0003 & 0.0012 & 0.0042
-  \end{pmatrix}.
- \end{equation}
-These correlations indicate that intrinsic color parameters are available.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=4in]{output2/sigma_corner.pdf} 
-   \caption{Confidence regions for the parameter ``$\Delta$ scale'' that describes the overall scale off the $\Delta$'s
-and of the standard deviations of the diagonal of $C_c$.}
-   \label{sigma:fig}
-\end{figure}
-
-The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{Delta_hist:fig}.  The intrinsic dispersion
-is given by the standard deviation of $0.10$ mag.  The distribution has a broad tail; a model assumption of a normal intrinsic dispersion
-would have been inappropriate.
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=4in]{output2/Delta_hist.pdf} 
-   \caption{Ideogram for the grey offset $\Delta$ for all supernovae.}
-   \label{Delta_hist:fig}
-\end{figure}
-
-To illustrate how the linear model reduces the dispersion in observed absolute magnitude, we take the
-observed $V_o$, and successive correction of $\gamma_2k$,  $\beta EW_{Si}$, and  $\alpha EW_{Ca}$, 
-where the 50\%-ile fit value (of the full model) is used for each parameter.  The histograms over the supernovae for these magnitudes are shown in
-Figure~\ref{magresidual:fig}.  The benefit of each  linear correction results in the reduction in dispersion.  The amount
-of successive reduction in dispersion is similar for all bands.  This is shown for illustration only: in my attempt to reproduce Gerard's previous
-work there were no supernovae reserved for out-of-sample model-comparison tests.  AIC and BIC can be computed.
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=4in]{output2/magresidual_V.pdf} 
-   \caption{Distributions of $V$-band corrected magnitudes.}
-   \label{magresidual:fig}
-\end{figure}
-
-The best-fit distributions for the parameters $\alpha$ and $\beta$, which describe the linear relation between absolute magnitude
-and $EW_{Ca}$ and $EW_{Si}$ respectively, are shown in Figure~\ref{alphabeta:fig}.  The 1-$\sigma$ 
-credible intervals are $\alpha_0=3.0e-3 \pm 8.6e-4$,
-$\alpha_1 = 4.7e-4  \pm 7.2e-4$, $\alpha_2 = 5.3e-4  \pm 5.9e-4$, $\alpha_3 = 7.0e-4  \pm 5.0e-4$,
-$\alpha_4 = 2.1e-3  \pm 4.4e-4$,  $\beta_0=0.03  \pm 2.8e-3$,
-$\beta_1 =0.03  \pm 2.4e-3$, $\beta_2 = 0.03  \pm 2.0e-3$, $\beta_3 =0.02  \pm 1.8e-3$,
-$\beta_4 =0.02  \pm 1.6e-3$.
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.9in]{output2/alpha_corner.pdf} 
-   \includegraphics[width=2.9in]{output2/beta_corner.pdf} 
-   \caption{Distributions for $\alpha$ and $\beta$.}
-   \label{alphabeta:fig}
-\end{figure}
-
-The best-fit distribution for the parameters $\gamma$  and a comparison with the predictions for extrinsic
-magnitude changes being to CCM dust, are shown in Figure~\ref{gamma:fig}.  The 1-$\sigma$ 
-credible intervals are $\gamma_0=1.65 \pm 0.05$,
-$\gamma_1 = 1.33  \pm 0.03$, $\gamma_2 = 0.78  \pm 0.1$, $\gamma_3 = 0.57  \pm 0.3$.
-The CCM dust predictions are based 
-on the central wavelengths of the synthetic broad-band filters, and are expected to be shifted slightly.
-By eye the model fit results appear consistent with $R_V=3.1$, although $R_V=2.8$ appears to match better.
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.9in]{output2/gamma_corner.pdf} 
-   \includegraphics[width=2.9in]{output2/ccm.pdf} 
-   \caption{Best-fit distribution for the parameters $\gamma$ and $\beta$, and a comparison with the predictions for extrinsic
-magnitude changes being to CCM dust.}
-   \label{gamma:fig}
-\end{figure}
-
 \begin{equation*}
-\left(
-\begin{matrix}
-U\\B\\V\\R\\I
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\Delta +
-\left(
-\begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{00} D +\delta_{10} D^2\\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{01} D  +\delta_{11} D^2\\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{02} D +\delta_{12} D^2\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{03} D +\delta_{13} D^2\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+\delta_{04} D +\delta_{14} D^2
-\end{matrix}
-\right)
-,C_{c}
-\right).
+\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
 \end{equation*}
-%\begin{equation*}
-%D \sim \mathcal{N}(\bar{D},1)
-%\end{equation*}
-\begin{equation*}
-\left(
-\begin{matrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\left(
-\begin{matrix}
-U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
-EW_{Si}\\ EW_{Ca}
-\end{matrix}
-\right)
-,C
-\right).
-\end{equation*}
-$\langle \Delta \rangle=0$, $\langle k \rangle=0$, $\gamma_2=1$, $\langle D \rangle=0$, $\langle D^2 \rangle=1$.
 

### 2016-08-02 view8.py

@@ -228,54 +228,21 @@ for edge in edges:
 # [3701, 4601, 5744, 6948, 8403]
 rc('text', usetex=True)
 
-
 rvs = [1.7,3.1,4.1]
 filts = ['U','B','V','R','I']
 
-fig, axes = plt.subplots(nrows=2, ncols=len(filts))
-for i in xrange(len(filts)):
-
-    axes[0,i].scatter(mag_obs[:, 1]-mag_obs[:, 2],mag_obs[:, i])
-    axes[0,i].set_xlabel(r'B-V')
-    axes[0,i].set_ylabel(r'{}'.format(filts[i]))
-
-    axes[1,i].scatter(mag_obs[:, 1]-mag_obs[:, 2],mag_obs[:, i]-correction_median[i,:])
-    axes[1,i].set_xlabel(r'B-V')
-    axes[1,i].set_ylabel(r'{} + correction'.format(filts[i]))
-
-
-plt.tight_layout()
-pp = PdfPages('output8/colormag.pdf')
-plt.savefig(pp,format='pdf')
-pp.close()
-plt.close()
-
-fig, axes = plt.subplots(nrows=2, ncols=len(filts))
-for i in xrange(len(filts)):
-    axes[0,i].scatter(EW_obs[:,1],mag_obs[:, i])
-    axes[0,i].set_xlabel(r'EW(Si)')
-    axes[0,i].set_ylabel(r'{}'.format(filts[i]))
-
-    axes[1,i].scatter(EW_obs[:,1],mag_obs[:, i]-correction_median[i,:])
-    axes[1,i].set_xlabel(r'EW(Si)')
-    axes[1,i].set_ylabel(r'{} + correction'.format(filts[i]))
-
-plt.tight_layout()
-pp = PdfPages('output8/specsimag.pdf')
-plt.savefig(pp,format='pdf')
-pp.close()
-plt.close()
 
 fig, axes = plt.subplots(nrows=len(filts),sharex=True)
+xerr = numpy.sqrt(EW_cov[:,0,0]) 
 for i in xrange(len(filts)):
     r = numpy.array( [numpy.argmin(EW_obs[:,0]), numpy.argmax(EW_obs[:,0])])
     yerr= numpy.sqrt(mag_cov[:,i,i])
-    xerr = numpy.sqrt(EW_cov[:,0,0])
     axes[i].errorbar(EW_obs[:,0],mag_obs[:, i], \
[…]

### 2016-08-03 forgerard.tex
two-population dust model

@@
 
-The best-fit distribution for the parameters $\gamma$  and our measurement of
-$\frac{\gamma_X}{\gamma_1-\gamma_2}$  compared with the predictions of CCM dust are shown in Figure~\ref{gamma:fig}:
+The best-fit distribution for the parameters $\gamma$ are shown in Figure~\ref{gamma:fig}.  Our measurement of
+$\frac{\gamma_X}{\gamma_1-\gamma_2}$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
 our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
-of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ has significantly smaller
+of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
 uncertainties and are consistent with $R_V=3.1$.
@@
    \centering
-   \includegraphics[width=2.4in]{output7/gamma_corner.pdf} 
-   \includegraphics[width=3.3in]{output7/ccm.pdf} 
-   \caption{Left: Best-fit distribution for the parameters $\gamma$.  Right: 68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
+   \includegraphics[width=3in]{output7/gamma_corner.pdf} 
+   \caption{Best-fit distribution for the parameters $\gamma$.  68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
    predictions for different values of $R_V$.}
    \label{gamma:fig}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output7/ccm.pdf}
+      \includegraphics[width=2.8in]{output7/ccm2.pdf} 
+   \caption{68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
+   predictions for these parameters are overlaid for different values of $R_V$.}
+   \label{ccm:fig}
 \end{figure}
@@
 Add Si line velocity.
-
-\subsection{Two-Color Model}
-Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
-Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
-with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
-that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
-
-\subsubsection{Setup}
-\begin{equation*}
-\left(
-\begin{matrix}
-U\\B\\V\\R\\I
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\Delta +
-\left(
-\begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
-\end{matrix}
-\right)
-,C_{c}
-\right).
-\end{equation*}
+%
+%\subsection{Two-Color Model}
+%Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
+%Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
+%with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
+%that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
+%
+%\subsubsection{Setup}
 %\begin{equation*}
-%D \sim \mathcal{N}(\bar{D},1)
+%\left(
+%\begin{matrix}
+%U\\B\\V\\R\\I
+%\end{matrix}
+%\right) \sim \mathcal{N}
+%\left(
+%\Delta +
+%\left(
+%\begin{matrix}
+%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
+%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
+%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
+%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
+%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
+%\end{matrix}
+%\right)
+%,C_{c}
+%\right).
 %\end{equation*}
-\begin{equation*}
-\left(
-\begin{matrix}
-U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
-\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\left(
-\begin{matrix}
-U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
-EW_{Si}\\ EW_{Ca}
-\end{matrix}
-\right)
-,C
-\right).
-\end{equation*}
-\begin{equation*}
-\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
-\end{equation*}
+%%\begin{equation*}
+%%D \sim \mathcal{N}(\bar{D},1)
+%%\end{equation*}
+%\begin{equation*}
+%\left(
+%\begin{matrix}
+%U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
+%\end{matrix}
+%\right) \sim \mathcal{N}
+%\left(
+%\left(
+%\begin{matrix}
+%U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+%EW_{Si}\\ EW_{Ca}
+%\end{matrix}
+%\right)
+%,C
+%\right).
+%\end{equation*}
+%\begin{equation*}
+%\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
+%\end{equation*}
 

### 2016-08-06 forgerard.tex
change subline line breaks.  Add a few env python.  Working toward 2-dust model

@@
 \section{Model Fits}
-\subsection{One-Color Model}
+\subsection{One-Color, One-Dust Model}
+\label{onecolor:sec}
 We hypothesize that Type Ia supernova spectral features are predictive of intrinsic
@@
 $U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$ and $EW_{Si,o}$ have Gaussian uncertainty with covariance $C$.  The model can be expressed
-\begin{equation*}
+\begin{equation}
 \left(
@@
 \right)
-\end{equation*}
-\begin{equation*}
+\label{ew:eqn}
+\end{equation}
+\begin{equation}
 \left(
@@
 ,C
-\right)
-\end{equation*}
+\right).
+\label{dust:eqn}
+\end{equation}
 The global parameters $c$, $\alpha$, and $\beta$ are the intercepts and slopes of the bilinear relationships between equivalent widths
@@
 
-The best-fit distribution for the parameters $\gamma$ are shown in Figure~\ref{gamma:fig}.  Our measurement of
-$\frac{\gamma_X}{\gamma_1-\gamma_2}$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
+The best-fit distribution for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Our measurement of
+$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
 our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
-of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
+of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
 uncertainties and are consistent with $R_V=3.1$.
@@
    \centering
-   \includegraphics[width=3in]{output7/gamma_corner.pdf} 
-   \caption{Best-fit distribution for the parameters $\gamma$.  68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
-   predictions for different values of $R_V$.}
-   \label{gamma:fig}
+   \includegraphics[width=3in]{output7/rx_corner.pdf} 
+   \caption{Best-fit distribution for the   $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$.
+   \label{rx:fig}}
 \end{figure}
@@
       \includegraphics[width=2.8in]{output7/ccm2.pdf} 
-   \caption{68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
+   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
    predictions for these parameters are overlaid for different values of $R_V$.}
@@
 Add Si line velocity.
+
+\subsection{Two-Dust Model}
+
+Motivated by the consistency of the external extinction with CCV $R_V=3.1$ dust, and the hint of the color-magnitude
+diagrams in Figure~\ref{magresidual:fig}  not following single slopes, we develop a new model in which
+each supernova encounters one of two sources of external extinction.
+
+\subsubsection{Setup}
+The model is identical to that of \S\ref{onecolor:sec} except with the addition of an alternative extrinsic source of extinction.
+The intrinsic magnitudes of the supernova are determined by the spectral properties expressed as Eqn.~\ref{ew:eqn}.
+One extrinsic source of extinction is modeled as before with Eqn.~\ref{dust:eqn};
+the second source of extinction
+is modeled similarly but with the introduction of new parameters $\gamma_{2X}$
+\begin{equation}
+\left(
+\begin{matrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\left(
+\begin{matrix}
+U +\gamma_{20} k \\B +\gamma_{21} k \\V+\gamma_{22} k\\R+\gamma_{23} k\\I+\gamma_{24} k\\
+EW_{Si}\\ EW_{Ca}
+\end{matrix}
+\right)
+,C
+\right).
+\label{dust2:eqn}
+\end{equation}
+The probability that a supernova experiences the first source of extinction is given by the free parameter $p_0$,
+the probability of the second is $1-p_0$.  
+The same $k$ parameters are used to describe supernovae in both extinction sources.  In order to do this we change
+some of the conditions that constrain the degeneracies of the model
+\begin{equation*}
+\langle \Delta \rangle=0, \gamma_1 = 1+\gamma_2, \gamma_{21}=1+\gamma_{22}.
+\end{equation*}
+These conditions are useful for interpreting the extinction as being due to dust, as $R_X = \gamma_X$,
+the color excess $E(B-V) \equiv (\gamma_1-\gamma_2)k =k$.
+The $c$ parameters  are fit such that both extinction models
+revert to the same intrinsic magnitudes for $k=0$: the $\langle k \rangle=0$ condition is removed.
+
+To alleviate the degeneracies inherent to mixture models, we set the range of $\gamma$'s for the first extinction source to be within
+a range of CCM possibilities.  No such restriction is placed on the $\gamma_{2X}$'s of the second source.
+
+\subsubsection{Results}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output9/rx_corner.pdf}
+      \includegraphics[width=2.8in]{output9/rx1_corner.pdf} 
+   \caption{Best-fit distribution for the first extinction source  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and
+   the second extinction source
+   $R_{2X}=\frac{\gamma_{2X}}{\gamma_{21}-\gamma_{22}}$ (right).
+   \label{rx:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output9/ccm.pdf}
+      \includegraphics[width=2.8in]{output9/ccm2.pdf} 
+         \includegraphics[width=2.8in]{output9/ccm12.pdf}
+      \includegraphics[width=2.8in]{output9/ccm22.pdf} 
+   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
+   predictions for these parameters are overlaid for different values of $R_V$.}
+   \label{ccm:fig}
+\end{figure}
+
 %

### 2016-08-25 forgerard.tex
add results for Si v

@@
 \section{Model Fits}
-\subsection{One-Color, One-Dust Model}
+\subsection{One Dust}
 \label{onecolor:sec}
@@
 An extrinsic physical process common to all supernovae can influence the propagation
-of light along the line of sight to incluence apparent magnitudes.
+of light along the line of sight to influence apparent magnitudes.
 
@@
 \subsubsection{Results}
-The 68\% intervals for the global parameters $\alpha$, $\beta$, $\gamma$, and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global:tab}.
+The 68\% intervals for the global parameters $\alpha$, $\beta$, $R$, and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global:tab}.
 The two dimensional contours for the parameters of each filter are shown in Figure~\ref{global:fig}.  The Table does not show
@@
 \\
-$\gamma_X$
+$R_X$
 &
-$0.3818^{0.0138}_{-0.0132}$
+$4.9882^{0.3399}_{-0.3031}$
 &
-$0.3108^{0.0117}_{-0.0113}$
+$4.0593^{0.2807}_{-0.2509}$
 &
-$0.2342^{0.0118}_{-0.0115}$
+$3.0604^{0.2355}_{-0.2142}$
 &
-$0.1827^{0.0107}_{-0.0111}$
+$2.3870^{0.2009}_{-0.1858}$
 &
-$0.1357^{0.0110}_{-0.0119}$
+$1.7696^{0.1833}_{-0.1713}$
 \\
@@
 \end{tabular}
-\caption{68\% Intervals for Global Fit Parameters \label{global:tab}}
+\caption{68\% Intervals for Global Fit Parameters for the One-Dust Model \label{global:tab}}
 \end{table}
@@
 
-Add Si line velocity.
+\subsection{One Dust With Si Velocity}
+\label{onecolor_si:sec}
+Sil$\lambda3655$ velocity is spectral indicator that has been identified to correlated with peak brightness.  The analysis is expanded to include
+this line. We use the weighted mean of all spectral measurements within 3 days of peak brightness.  A handful of supernovae do not have a
+spectrum that close to peak.
+\subsubsection{Setup}
+With the inclusion of SiII$\lambda3655$ velocity  $v_{Si}$ the model looks like
+\begin{equation}
+\left(
+\begin{matrix}
+U\\B\\V\\R\\I
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\Delta +
+\left(
+\begin{matrix}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si}\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si}\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si}\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si}
+\end{matrix}
+\right)
+,C_{c}
+\right)
+\label{ewsiv:eqn}
+\end{equation}
+\begin{equation}
+\left(
+\begin{matrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\left(
+\begin{matrix}
+U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+EW_{Si}\\ EW_{Ca} \\ v_{Si}
+\end{matrix}
+\right)
+,C
+\right).
+\label{dust:eqn}
+\end{equation}
+The global parameters $\eta$ are the slopes of the linear relationships between Si velocity
+and intrinsic magnitudes.
 
-\subsection{Two-Dust Model}
+\subsubsection{Results}
+The 68\% intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{globalvsi:tab}.
+The two dimensional contours for the parameters of each filter are shown in Figure~\ref{globalvsi:fig}.  
+All bands show large and significant non-zero values for $\eta$ with some non-trivial changes to $\beta$ and a lowering
+if $\sigma$.  The values
+of $\alpha$ are unchanged.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+& $X=0$ &1&2&3&4\\ \hline
+$\alpha_X$
+&
+$0.0031^{0.0009}_{-0.0009}$
+&
+$0.0005^{0.0008}_{-0.0007}$
+&
+$0.0006^{0.0006}_{-0.0006}$
+&
+$0.0008^{0.0005}_{-0.0005}$
+&
+$0.0020^{0.0005}_{-0.0004}$
+\\
+$\beta_X$
+&
+$0.0375^{0.0030}_{-0.0030}$
+&
+$0.0303^{0.0026}_{-0.0025}$
+&
+$0.0298^{0.0023}_{-0.0021}$
+&
+$0.0243^{0.0020}_{-0.0019}$
+&
+$0.0224^{0.0017}_{-0.0017}$
+\\
+$\eta_X$
+&
+$0.0032^{0.0011}_{-0.0011}$
+&
+$0.0024^{0.0009}_{-0.0009}$
+&
+$0.0022^{0.0008}_{-0.0008}$
+&
+$0.0019^{0.0007}_{-0.0007}$
+&
+$0.0011^{0.0006}_{-0.0006}$
+\\
+$R_X$
+&
+$5.1004^{0.2929}_{-0.2517}$
+&
+$4.1677^{0.2656}_{-0.2272}$
+&
+$3.1677^{0.2656}_{-0.2272}$
+&
+$2.4828^{0.2327}_{-0.1964}$
+&
+$1.8320^{0.2050}_{-0.1838}$
+\\
+$\sigma_X$
+&
+$0.0537^{0.0162}_{-0.0185}$
+&
+$0.0405^{0.0107}_{-0.0131}$
+&
+$0.0565^{0.0093}_{-0.0109}$
+&
+$0.0538^{0.0084}_{-0.0084}$
+&
+$0.0636^{0.0076}_{-0.0079}$
+\\
+\hline
+\end{tabular}
+\caption{68\% Intervals for Global Fit Parameters for the One-Dust Model with $v_{Si}$  \label{globalvsi:tab}}
+\end{table}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.5in]{output10/coeff0.pdf} 
+   \includegraphics[width=2.5in]{output10/coeff1.pdf} 
+   \includegraphics[width=2.5in]{output10/coeff2.pdf} 
+      \includegraphics[width=2.5in]{output10/coeff3.pdf} 
+         \includegraphics[width=2.5in]{output10/coeff4.pdf} 
+            \caption{Distributions for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, and $\sigma$ in each of the 5 bands.}
+   \label{globalvsi:fig}
+\end{figure}
+
+The best-fit distribution for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rxsiv:fig}.  Our measurement of
+$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
+our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3in]{output10/gamma_corner.pdf} 
+   \caption{Best-fit distribution for the   $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$.
+   \label{rxsiv:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output10/ccm.pdf}
+      \includegraphics[width=2.8in]{output10/ccm2.pdf} 
+   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
+   predictions for these parameters are overlaid for different values of $R_V$.}
+   \label{ccmsiv:fig}
+\end{figure}
+
+ \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.4in]{output10/sigma_corner.pdf} 
+   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.}
+   \label{sigmasiv:fig}
+\end{figure}
+
+The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{histsiv:fig}.  The intrinsic dispersion
+is given by the standard deviation of $0.09$ mag.  The distribution is non-Gaussian, with a broad tail. 
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output10/Delta_hist.pdf} 
+   \includegraphics[width=2.8in]{output10/k_hist.pdf} 
+   \caption{Ideograms for Left: the grey offset $\Delta$; Right: the color term $k$ for all supernovae.}
+   \label{histsiv:fig}
+\end{figure}
+
+\subsection{Two Dust}
 
@@
 The intrinsic magnitudes of the supernova are determined by the spectral properties expressed as Eqn.~\ref{ew:eqn}.
-One extrinsic source of extinction is modeled as before with Eqn.~\ref{dust:eqn};
-the second source of extinction
+One extrinsic source of extinction  (Dust 1) is modeled as before with Eqn.~\ref{dust:eqn};
+the second source of extinction (Dust 2)
 is modeled similarly but with the introduction of new parameters $\gamma_{2X}$
@@
 \end{equation}
-The probability that a supernova experiences the first source of extinction is given by the free parameter $p_0$,
-the probability of the second is $1-p_0$.  
+The probability that a supernova experiences  Dust 1 is given by the free parameter $p_0$,
+the probability of Dust 2 is $1-p_0$.  
 The same $k$ parameters are used to describe supernovae in both extinction sources.  In order to do this we change
-some of the conditions that constrain the degeneracies of the model
+some of the conditions that constrain the degeneracies of the model:
 \begin{equation*}
@@
 
-To alleviate the degeneracies inherent to mixture models, we set the range of $\gamma$'s for the first extinction source to be within
-a range of CCM possibilities.  No such restriction is placed on the $\gamma_{2X}$'s of the second source.
+To alleviate the degeneracies inherent to mixture models, we restrict the range of $\alpha$, $\beta$, and $\gamma$ (the parameters for Dust 1)
+to be in the neighborhood of the pdf's of \S\ref{onecolor:sec}.  The one-dust model is embedded in the two-dust model when $p_0=1$.
+We therefore do not claim to find the global optimum of the parameter
+pdf, but we can conclude whether the two-dust model is preferred over the one-dust model.
+The intrinsic covariance $C_c$ is taken to be diagonal.
 
@@
 
+The probability of an object experiencing the first dust is   $p_0=0.3334^{0.0532}_{-0.0721}$,
+with the pdf shown in Figure~\ref{prob0:fig}.
+A single dust with properties centered around the one-dust parameter optimum is not only disfavored, but is most likely the
+minority component.  
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
    \centering
-   \includegraphics[width=2.8in]{output9/rx_corner.pdf}
-      \includegraphics[width=2.8in]{output9/rx1_corner.pdf} 
-   \caption{Best-fit distribution for the first extinction source  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and
-   the second extinction source
-   $R_{2X}=\frac{\gamma_{2X}}{\gamma_{21}-\gamma_{22}}$ (right).
-   \label{rx:fig}}
+   \includegraphics[width=3.3in]{output9/prob0.pdf}
+   \caption{pdf of $p_0$, the probability that a supernova experiences Dust 1.  \label{prob0:fig}}
 \end{figure}
 
+The 68\% intervals for the global parameters $\alpha$, $\beta$, $R$, $R_2$ and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global2:tab}.
+The two dimensional contours for the parameters of each filter are shown in Figure~\ref{global2:fig}.  
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+& $X=0$ &1&2&3&4\\ \hline
+$\alpha_{X}$
+&
+$0.0077^{0.0014}_{-0.0018}$
+&
+$0.0040^{0.0011}_{-0.0013}$
+&
+$0.0025^{0.0008}_{-0.0008}$
+&
+$0.0020^{0.0006}_{-0.0007}$
+&
+$0.0027^{0.0006}_{-0.0006}$
+\\
+$\beta_{X}$
+&
+$0.0276^{0.0048}_{-0.0053}$
+&
+$0.0225^{0.0037}_{-0.0042}$
+&
+$0.0249^{0.0025}_{-0.0026}$
+&
+$0.0213^{0.0019}_{-0.0020}$
+&
+$0.0216^{0.0015}_{-0.0016}$
+\\
+$R_{X}$
+&
+$5.0878^{0.4233}_{-0.4082}$
+&
+$4.3163^{0.3615}_{-0.3327}$
+&
+$3.3163^{0.3615}_{-0.3327}$
+&
+$2.6600^{0.2685}_{-0.2691}$
+&
+$1.9355^{0.2604}_{-0.2474}$
+\\
+$R_{2X}$
+&
+$2.2199^{0.2110}_{-0.2301}$
+&
+$1.5919^{0.1801}_{-0.2246}$
+&
+$0.5919^{0.1801}_{-0.2246}$
+&
+$0.2486^{0.1650}_{-0.1788}$
+&
+$-0.1484^{0.1802}_{-0.1472}$
+\\
+$\sigma_{X}$
+&
+$0.0570^{0.0042}_{-0.0040}$
+&
+$0.0103^{0.0059}_{-0.0048}$
+&
+$0.0229^{0.0021}_{-0.0018}$
+&
+$0.0094^{0.0031}_{-0.0039}$
+&
+$0.0418^{0.0031}_{-0.0030}$
+\\
+\hline
+\end{tabular}
+\caption{68\% Intervals for Global Fit Parameters for the Two-Dust Model \label{global2:tab}}
+\end{table}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.5in]{output9/coeff0.pdf} 
+   \includegraphics[width=2.5in]{output9/coeff1.pdf} 
+   \includegraphics[width=2.5in]{output9/coeff2.pdf} 
+      \includegraphics[width=2.5in]{output9/coeff3.pdf} 
+         \includegraphics[width=2.5in]{output9/coeff4.pdf} 
+            \caption{Distributions for $c$, $\alpha$, $\beta$, $\gamma$, $\gamma_2$, and $\sigma$ in each of the 5 bands.}
+   \label{global2:fig}
+\end{figure}
+
+Our determinations of $R$ and $R_2$ are compared to the expectations of CCM dust in Figure~\ref{ccm2:fig}.
+Within the context of this model there are two distinct types of dust: Dust 1 behaves similarly to $R_V=3.1$ CCM dust.
+In contrast, Dust 2 is more consistent with extremely low values of $R_V$.  Negative values of $R_V$ are unphysical.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
       \includegraphics[width=2.8in]{output9/ccm22.pdf} 
-   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
+   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right)
+   for Dust 1 (top row) and Dust 2 (bottom row).  CCM
    predictions for these parameters are overlaid for different values of $R_V$.}
-   \label{ccm:fig}
+   \label{ccm2:fig}
 \end{figure}
 
-%
-%\subsection{Two-Color Model}
-%Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
-%Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
-%with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
-%that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
-%
-%\subsubsection{Setup}
+While the values for $\beta$ are consistent between the one- and two-dust models, the $\alpha$ values change significantly.
+This implies a correlation between $EW_{Ca}$ and the dust environment.
+
+\subsection{One Dust, Intrinsic Color}
+Another viable model is to assign each supernova an intrinsic color parameter $D$ to describe color variation not attributed to spectral features,
+in addition to the external source of extinction.
+
+\subsubsection{Setup}
+
+A second color parameter $D$ is introduced to be quadratically related with magnitude.
+
+\begin{equation*}
+\left(
+\begin{matrix}
+U\\B\\V\\R\\I
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\Delta +
+\left(
+\begin{matrix}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si}  +0.5 \delta_{10} D^2\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  +0.5 \delta_{11} D^2\\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +0.5 \delta_{12} D^2\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si}  +0.5 \delta_{13} D^2\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}  +0.5 \delta_{14} D^2
+\end{matrix}
+\right)
+,C_{c}
+\right).
+\end{equation*}
 %\begin{equation*}
-%\left(
-%\begin{matrix}
-%U\\B\\V\\R\\I
-%\end{matrix}
-%\right) \sim \mathcal{N}
-%\left(
-%\Delta +
-%\left(
-%\begin{matrix}
-%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
-%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
-%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
-%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
-%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
-%\end{matrix}
-%\right)
-%,C_{c}
-%\right).
+%D \sim \mathcal{N}(\bar{D},1)
 %\end{equation*}
-%%\begin{equation*}
-%%D \sim \mathcal{N}(\bar{D},1)
-%%\end{equation*}
-%\begin{equation*}
-%\left(
-%\begin{matrix}
-%U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
-%\end{matrix}
-%\right) \sim \mathcal{N}
-%\left(
-%\left(
-%\begin{matrix}
-%U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
-%EW_{Si}\\ EW_{Ca}
-%\end{matrix}
-%\right)
-%,C
-%\right).
-%\end{equation*}
-%\begin{equation*}
-%\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
-%\end{equation*}
+\begin{equation*}
+\left(
+\begin{matrix}
+U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
+\end{matrix}
+\right) \sim \mathcal{N}
+\left(
+\left(
+\begin{matrix}
+U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+EW_{Si}\\ EW_{Ca}
+\end{matrix}
+\right)
+,C
+\right).
+\end{equation*}
+The choice of the $\delta$'s are such that $0.5 \delta_{1X} D^2 \sim \delta_{1X} D$ to first order.
+No linear dependence on $D$ is included as it nearly degenerate with the linear dependence on the external $k$ parameters.
+The intrinsic covariance $C_c$ is taken to be diagonal.
+Degeneracies are constrained by the boundary conditions
+\begin{equation*}
+\langle \Delta \rangle=0, \langle k \rangle=0, \gamma_1=1+\gamma_2, \delta_{11}=1+\delta_{12},
+\end{equation*}
+making the light assumption that $\delta_{11} \ne \delta_{12}$ which is later seen to be borne out in the fits.
+
+As the intrinsic and extrinsic colors can be similar, we restrict ourselves to probing regions of $\alpha$, $\beta$, and $\gamma$
+in the area of the optimum of the one-dust model.
+
+\subsubsection{Results}
+
+The 68\% intervals for the global parameters $\alpha$, $\beta$, $R$, $R_2$ and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global3:tab}.
+The two dimensional contours for the parameters of each filter are shown in Figure~\ref{global3:fig}.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+& $X=0$ &1&2&3&4\\ \hline
+
+\hline
+\end{tabular}
+\caption{68\% Intervals for Global Fit Parameters for the Two-Dust Model \label{global3:tab}}
+\end{table}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.5in]{output5/coeff0.pdf} 
+   \includegraphics[width=2.5in]{output5/coeff1.pdf} 
+   \includegraphics[width=2.5in]{output5/coeff2.pdf} 
+      \includegraphics[width=2.5in]{output5/coeff3.pdf} 
+         \includegraphics[width=2.5in]{output5/coeff4.pdf} 
+            \caption{Distributions for $c$, $\alpha$, $\beta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.}
+   \label{global3:fig}
+\end{figure}
 

### 2016-08-30 forgerard.tex
This all makes sense and is a "frozen" version

--- 2016-08-03 forgerard.tex
@@
 \section{Data}
-The data set consists of synthetic $UBVRI$ peak brightnesses and Si and Ca equivalent widths at peak
+The data set consists of synthetic $UBVRI$ (whether SNF or Nico system yet to be elucidated)
+peak brightnesses and Si and Ca equivalent widths at peak
 of 172 SNf supernovae.  The photometry is normalized to place all supernovae at a common distance, as
@@
 
+The SiII$\lambda6355$ velocity within 3-days of peak brightness is taken from the file phrenology\_2016\_12\_01\_CABALLOv1.pkl.
+We use the weighted sum for supernovae with multiple velocity measurements.  A subset of 163
+supernovae have this velocity measurement.
+
 \section{Model Fits}
-\subsection{One-Color Model}
+
 We hypothesize that Type Ia supernova spectral features are predictive of intrinsic
-magnitudes.  The intrinsic magnitudes are not perfectly deterministic, but have some intrinsic dispersion.
+magnitudes.  We use feature statistics that are insensitive to broad-band reddening.
+The intrinsic magnitudes are not perfectly deterministic, but have some intrinsic dispersion.
 An extrinsic physical process common to all supernovae can influence the propagation
-of light along the line of sight to incluence apparent magnitudes.
+of light along the line of sight to influence apparent magnitudes.
+We allow for additional color variation left unaccounted for by the spectral features and external extinction.
 
-\subsubsection{Setup}
-Specifically, we assume a linear relationship between the equivalent widths of the Ca and Si spectral features
-$EW_{Ca}$ and $EW_{Si}$, and the intrinsic $UBVRI$ magnitudes
-with residual Gaussian dispersion with covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
+\subsection{Setup}
+We assume 
+that  intrinsic $UBVRI$ magnitudes are linearly dependent
+on the equivalent widths of the Ca and Si spectral features
+$EW_{Ca}$, $EW_{Si}$,
+the SiII$\lambda6355$ velocity $v_{Si}$, and an intrinsic color-variation parameter $D$.
+Residual Gaussian dispersion is described by covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
 to capture grey intrinsic dispersion and distance errors introduced in the normalization of the photometry.
-The  extrinsic process is also assumed to be linear.  The observables
-$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$ and $EW_{Si,o}$ have Gaussian uncertainty with covariance $C$.  The model can be expressed
-\begin{equation*}
+The observed magnitudes are linearly dependent on an
+extrinsic color-variation parameter $k$  parameter.  The observables
+$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian uncertainty with covariance $C$.  The model is written as
+\begin{equation}
 \left(
@@
 \begin{matrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si} + \delta_0 D\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} + \delta_1 D \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si} + \delta_2 D\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si} + \delta_3 D\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si} + \delta_4 D
 \end{matrix}
@@
 \right)
-\end{equation*}
-\begin{equation*}
+\label{ewsiv:eqn}
+\end{equation}
+\begin{equation}
 \left(
 \begin{matrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}\end{matrix}
 \right) \sim \mathcal{N}
@@
 U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
-EW_{Si}\\ EW_{Ca}
+EW_{Si}\\ EW_{Ca} \\ v_{Si}
 \end{matrix}
@@
 ,C
-\right)
-\end{equation*}
-The global parameters $c$, $\alpha$, and $\beta$ are the intercepts and slopes of the bilinear relationships between equivalent widths
-and intrinsic magnitudes.  The extrinsic piece is split into the properties $\gamma$ of the physical process and the per-supernova 
-parameters $k$ that indicate how much of that process each object undergoes.  To break the degeneracies inherent in the model we impose
+\right).
+\label{dust:eqn}
+\end{equation}
+The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the bilinear relationships between the spectral
+features and intrinsic color with intrinsic magnitudes.  The extrinsic piece is split into the properties $\gamma$ of the physical process and the per-supernova 
+parameters $k$.  To break the degeneracies inherent in the model we impose
 \begin{equation*}
-\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \gamma_0 \ge 0.
+\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 \ge 0, \delta_0\le0.
 \end{equation*}
@@
 Having the intrinsic dispersion $C_c$ as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
-ascribed to $\Delta$ and $\gamma k$ could also be attributed to intrinsic dispersion.  There are several features of the model
+ascribed to $\Delta$, $\delta D$, and $\gamma k$ could also be attributed to intrinsic dispersion.  There are several features of the model
 that drives the assignation of variations away from $C_c$:  The probability distribution functions decrease
@@
 If interpreted as being due to dust, the extrinsic term could be associated with extinction $A_X = \gamma_X k$.  In
-this parlance $E(B-V) = (\gamma_1-\gamma_2) k$ and $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
-Note that these values of $A_X$, $E(B-V)$, and $R_X$ do not depend on the normalization condition $ \langle k^2 \rangle$, i.e.\
-are independent of the transformation $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1} k$.
+this parlance the color excess
+is $E(B-V) = (\gamma_1-\gamma_2) k$ and $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
+Similarly we introduce for the intrinsic color term $E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.
 
 As I perform an Bayesian analysis some mention of priors is required.  A flat prior is used for all parameters except
-for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=2$  LKJ prior and standard
+for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior and standard
 deviations with
- $\mu=0$, $\sigma=1$ Cauchy (Lorentz) distribution prior restricted to non-negative values.
-The nature of the LKJ prior is rather mysterious; one thing to note is that for $\nu=2$ the correlation prior is broad but
+ $\mu=0.1 $, $\sigma=0.1$ Cauchy (Lorentz) distribution prior restricted to non-negative values.
+The nature of the LKJ prior is rather mysterious; one thing to note is that for $\nu=4$ the correlation prior is broad but
 approaches zero at the extremum.
@@
 \subsubsection{Results}
-The 68\% intervals for the global parameters $\alpha$, $\beta$, $\gamma$, and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global:tab}.
-The two dimensional contours for the parameters of each filter are shown in Figure~\ref{global:fig}.  The Table does not show
+STAN is used to determine the parameter posteriors.  Visual inspection of the posterior and the $\hat{R}$ and $N_{eff}$ statistics
+show no signs for non-convergence or sparse sampling.
+The $\hat{R}$ statistic is equal to $1.00$ for almost all the parameters, the largest value is $1.03$ for one of the parameters describing the covariance matrix $C_c$;  $N_{eff} \gg 100$ for all parameters, as recommended.
+
+The 68\% intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma = \sqrt{C_{c,ii}}$
+for each of the five filters are given in Table~\ref{global:tab}.
+The two dimensional contours for the parameters, grouped by filter, are shown in Figure~\ref{global:fig}.  The Table does not show
 the results for $c$ as their values are not significant for the aims of this analysis, the Figure does show $c$ to indicate the convergence
@@
 & $X=0$ &1&2&3&4\\ \hline
-$\alpha_X$
+$\alpha_{X}$
 &
-$0.0031^{0.0008}_{-0.0009}$
+$0.0042^{0.0009}_{-0.0009}$
 &
-$0.0005^{0.0007}_{-0.0007}$
+$0.0014^{0.0007}_{-0.0008}$
 &
-$0.0006^{0.0006}_{-0.0006}$
+$0.0014^{0.0006}_{-0.0006}$
 &
-$0.0007^{0.0005}_{-0.0005}$
+$0.0014^{0.0005}_{-0.0005}$
 &
-$0.0021^{0.0004}_{-0.0004}$
+$0.0025^{0.0005}_{-0.0005}$
 \\
-$\beta_X$
+$\beta_{X}$
 &
-$0.0345^{0.0027}_{-0.0029}$
+$0.0335^{0.0031}_{-0.0031}$
 &
-$0.0274^{0.0022}_{-0.0025}$
+$0.0267^{0.0025}_{-0.0026}$
 &
-$0.0274^{0.0021}_{-0.0021}$
+$0.0266^{0.0022}_{-0.0022}$
 &
-$0.0223^{0.0018}_{-0.0018}$
+$0.0214^{0.0019}_{-0.0019}$
 &
-$0.0213^{0.0016}_{-0.0017}$
+$0.0200^{0.0018}_{-0.0017}$
 \\
-$\gamma_X$
+$\eta_{X}$
 &
-$0.3818^{0.0138}_{-0.0132}$
+$0.0010^{0.0012}_{-0.0013}$
 &
-$0.3108^{0.0117}_{-0.0113}$
+$0.0006^{0.0010}_{-0.0011}$
 &
-$0.2342^{0.0118}_{-0.0115}$
+$0.0008^{0.0008}_{-0.0009}$
 &
-$0.1827^{0.0107}_{-0.0111}$
+$0.0008^{0.0007}_{-0.0008}$
 &
-$0.1357^{0.0110}_{-0.0119}$
+$0.0002^{0.0006}_{-0.0007}$
 \\
-$\sigma_X$
+$R_{X}$
 &
-$0.0693^{0.0157}_{-0.0152}$
+$4.8715^{0.4826}_{-0.4296}$
 &
-$0.0575^{0.0099}_{-0.0089}$
+$3.9642^{0.3953}_{-0.3528}$
 &
-$0.0679^{0.0083}_{-0.0080}$
+$2.9644^{0.3118}_{-0.2801}$
 &
-$0.0639^{0.0073}_{-0.0069}$
+$2.2869^{0.2559}_{-0.2322}$
 &
-$0.0703^{0.0075}_{-0.0075}$
+$1.6395^{0.2112}_{-0.1939}$
+\\
+$R_{\delta X}$
+&
+$-2.6978^{1.3200}_{-2.4424}$
+&
+$-3.4586^{1.2929}_{-2.6501}$
+&
+$-4.4569^{1.4269}_{-3.1109}$
+&
+$-4.2020^{1.3152}_{-2.8944}$
+&
+$-3.8012^{1.2005}_{-2.6141}$
+\\
+$\sigma_{X}$
+&
+$0.0592^{0.0124}_{-0.0112}$
+&
+$0.0315^{0.0069}_{-0.0073}$
+&
+$0.0201^{0.0041}_{-0.0055}$
+&
+$0.0127^{0.0069}_{-0.0079}$
+&
+$0.0425^{0.0051}_{-0.0044}$
 \\
@@
    \centering
-   \includegraphics[width=2.5in]{output7/coeff0.pdf} 
-   \includegraphics[width=2.5in]{output7/coeff1.pdf} 
-   \includegraphics[width=2.5in]{output7/coeff2.pdf} 
-      \includegraphics[width=2.5in]{output7/coeff3.pdf} 
-         \includegraphics[width=2.5in]{output7/coeff4.pdf} 
-            \caption{Distributions for $c$, $\alpha$, $\beta$, $\gamma$, and $\sigma$ in each of the 5 bands.}
-   \label{global:fig}
+   \includegraphics[width=2.5in]{output11/coeff0.pdf} 
+   \includegraphics[width=2.5in]{output11/coeff1.pdf} 
+   \includegraphics[width=2.5in]{output11/coeff2.pdf} 
+      \includegraphics[width=2.5in]{output11/coeff3.pdf} 
+         \includegraphics[width=2.5in]{output11/coeff4.pdf} 
+            \caption{Distributions for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.   \label{global:fig}}
+
 \end{figure}
@@
 magnitudes.  All bands show larger and significant non-zero values for $\beta$.  This confirms the part of our hypothesis that spectral indicators
-are tracers of supernova absolute magnitude.
+are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ are consistent with zero within one sigma.
 
-The best-fit distribution for the parameters $\gamma$ are shown in Figure~\ref{gamma:fig}.  Our measurement of
-$\frac{\gamma_X}{\gamma_1-\gamma_2}$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
-our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
-of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
-uncertainties and are consistent with $R_V=3.1$.
+The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Our measurement of
+$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
+the $R_X$ are consistent with the  $R_V=3.1$ CCM model (assuming we are using
+SNf synthetic magnitudes).  The uncertainties in the 5 measurements
+of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
+uncertainties and are also consistent with $R_V=3.1$.
 
@@
    \centering
-   \includegraphics[width=3in]{output7/gamma_corner.pdf} 
-   \caption{Best-fit distribution for the parameters $\gamma$.  68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
-   predictions for different values of $R_V$.}
-   \label{gamma:fig}
+   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
+      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
+   \caption{Best-fit distribution for (left)  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ and (right)  $R_{\rho X}=\frac{\delta_X}{\delta_1-\delta_2}$.
+   \label{rx:fig}}
 \end{figure}
@@
    \centering
-   \includegraphics[width=2.8in]{output7/ccm.pdf}
-      \includegraphics[width=2.8in]{output7/ccm2.pdf} 
-   \caption{68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
-   predictions for these parameters are overlaid for different values of $R_V$.}
-   \label{ccm:fig}
+   \includegraphics[width=2.8in]{output11/ccm.pdf}
+      \includegraphics[width=2.8in]{output11/ccm2.pdf} 
+   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
+   predictions for these parameters are overlaid for different values of $R_V$.
+   \label{ccm:fig}}
 \end{figure}
 
+The best-fit distribution for $R_{\rho X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
+Although the posteriors of $\delta$ are fairly circular, $\delta_1-\delta_2$ can get close to zero, resulting in the
+elongated tail in negative  $R_{\rho X}$.
+All values are inconsistent with zero and negative: a color excess in $B-V$ produces a brightening of the supernova.
+The smallest (most negative) value is for the $V$ band with  values increasing in both bluer and redder directions; an
+example consequence is that
+a reddening in $B-V$ comes with a blueing in $V-R$.
+These are not the behaviors expected from normal dust or a blackbody in the Raleigh-Jeans tail and so may be indicative of
+more complicated underlying physics.
+
+The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
+ $E_\rho(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
+Recall that given our boundary conditions the means of both distributions are equal to zero. 
+The standard deviation of $E(B-V)$ is 0.074 mag while that of $E_\rho(B-V)$ is 0.019 mag.
+Both distributions are non-Gaussian extended tails in the red.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/ebv.pdf}
+   \caption{Histograms of $E(B-V) =(\gamma_1-\gamma_2)k$ and
+   $E_\rho(B-V) = (\delta_1-\delta_2)D$.
+   \label{ebv:fig}}
+\end{figure}
+
+Let us conflate the two separate color effects into a single effective extinction with
+\begin{equation}
+R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}.
+\end{equation}
+The distribution for $R_{V,eff}$ is shown in Figure~\ref{rveff:fig}
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/rveff.pdf}
+   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}$,
+   \label{rveff:fig}}
+\end{figure}
+with  $R_{V,eff}  = 1.52 \pm 0.24$.  This may explain why previous analyses have produced low $R_V$ values.
+
 Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
-square root of the diagonal elements of $C_c$.
-A representative example is given by the matrix comprised by the average of each element in the Monte Carlo chain.
-For $UBVRI$ the matrix is
-\begin{equation}
-\begin{pmatrix}
-0.0050 & 0.0026 & 0.0017 & 0.0014 & 0.0009 \\
-0.0026 & 0.0034 & 0.0032 & 0.0026 & 0.0011 \\
-0.0017 & 0.0032 & 0.0047 & 0.0041 & 0.0029 \\
-0.0014 & 0.0026 & 0.0041 & 0.0042 & 0.0035 \\
-0.0009 & 0.0011 & 0.0029 & 0.0035 & 0.0050
- \end{pmatrix}.
- \end{equation}
- In terms of colors $U-V$, $B-V$, $V-R$, and $V-I$ the covariance is
-\begin{equation}
-\begin{pmatrix}
-0.0064 & 0.0025 & -0.0004 & -0.0010 \\
-0.0025 & 0.0018 & -0.0000 & 0.0003 \\
--0.0004 & -0.0000 & 0.0007 & 0.0011 \\
--0.0010 & 0.0003 & 0.0011 & 0.0039
-  \end{pmatrix}.
- \end{equation}
- The $B-V$ and $V-R$ colors have small standard deviations of  0.04 mag and 0.03 mag with no correlation.  The
- residuals not accounted by the
- model are stronger in the $U-V$ and $V-I$ bands.
+square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion is quite small, ranging from 0.01 to 0.06 mag.
+
+%A representative example is given by the matrix comprised by the average of each element in the Monte Carlo chain.
+%For $UBVRI$ the matrix is
+%\begin{equation}
+%\begin{pmatrix}
+%0.0050 & 0.0026 & 0.0017 & 0.0014 & 0.0009 \\
+%0.0026 & 0.0034 & 0.0032 & 0.0026 & 0.0011 \\
+%0.0017 & 0.0032 & 0.0047 & 0.0041 & 0.0029 \\
+%0.0014 & 0.0026 & 0.0041 & 0.0042 & 0.0035 \\
+%0.0009 & 0.0011 & 0.0029 & 0.0035 & 0.0050
+% \end{pmatrix}.
+% \end{equation}
+% In terms of colors $U-V$, $B-V$, $V-R$, and $V-I$ the covariance is
+%\begin{equation}
+%\begin{pmatrix}
+%0.0064 & 0.0025 & -0.0004 & -0.0010 \\
+%0.0025 & 0.0018 & -0.0000 & 0.0003 \\
+%-0.0004 & -0.0000 & 0.0007 & 0.0011 \\
+%-0.0010 & 0.0003 & 0.0011 & 0.0039
+%  \end{pmatrix}.
+% \end{equation}
+% The $B-V$ and $V-R$ colors have small standard deviations of  0.04 mag and 0.03 mag with no correlation.  The
+% residuals not accounted by the
+% model are stronger in the $U-V$ and $V-I$ bands.
 
@@
    \centering
-   \includegraphics[width=2.4in]{output7/sigma_corner.pdf} 
-   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.}
-   \label{sigma:fig}
+   \includegraphics[width=3.2in]{output11/sigma_corner.pdf} 
+   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
+   \label{sigma:fig}}
 \end{figure}
@@
 The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
-is given by the standard deviation of $0.10$ mag.  The distribution is non-Gaussian, with a broad tail. 
+is given by the standard deviation of $0.096$ mag.  The distribution is non-Gaussian, with a broad tail. 
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
    \centering
-   \includegraphics[width=2.8in]{output7/Delta_hist.pdf} 
-   \includegraphics[width=2.8in]{output7/k_hist.pdf} 
-   \caption{Ideograms for Left: the grey offset $\Delta$; Right: the color term $k$ for all supernovae.}
-   \label{hist:fig}
+   \includegraphics[width=3.2in]{output11/Delta_hist.pdf} 
+   \caption{Ideogram for the grey offset $\Delta$.
+   \label{hist:fig}}
 \end{figure}
 
-The ideogram for the color term  $k$ for all supernovae is shown in Figure~\ref{hist:fig}.The distribution is non-Gaussian, with a broad tail.
-
-To illustrate how the linear model reduces the dispersion in observed absolute magnitude, plot the observed colors as a
-function of the observed  $EW_{Ca, o}$, $EW_{Si,o}$ and $B_o-V_o$ in Fig.~\ref{magresidual:fig}.  Overplotted are lines with the
-best-fit slope.  The data in the color magnitude diagram indicate that the slope at bluer colors is different from that at redder colors
-and that our one-color linear model could be improved upon.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output7/speccamag.pdf} 
-      \includegraphics[width=2.8in]{output7/specsimag.pdf} 
-   \includegraphics[width=2.8in]{output7/colormag.pdf} 
-   \caption{Observed $UBVRI$ as a function of observed   $EW_{Ca, o}$ (top left), $EW_{Si,o}$ (top right) and $B_o-V_o$ (bottom).
-   Overplotted are lines with the best-fit slope from the model fit.}
-   \label{magresidual:fig}
-\end{figure}
-
-\subsubsection{Notes}
-Some equivalent widths go positive.  Is this an emission?
-
-Add Si line velocity.
 %
-%\subsection{Two-Color Model}
-%Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
-%Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
-%with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
-%that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
+%To illustrate how the linear model reduces the dispersion in observed absolute magnitude, plot the observed colors as a
+%function of the observed  $EW_{Ca, o}$, $EW_{Si,o}$ and $B_o-V_o$ in Fig.~\ref{magresidual:fig}.  Overplotted are lines with the
+%best-fit slope.  The data in the color magnitude diagram indicate that the slope at bluer colors is different from that at redder colors
+%and that our one-color linear model could be improved upon.
 %
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output7/speccamag.pdf} 
+%      \includegraphics[width=2.8in]{output7/specsimag.pdf} 
+%   \includegraphics[width=2.8in]{output7/colormag.pdf} 
+%   \caption{Observed $UBVRI$ as a function of observed   $EW_{Ca, o}$ (top left), $EW_{Si,o}$ (top right) and $B_o-V_o$ (bottom).
+%   Overplotted are lines with the best-fit slope from the model fit.}
+%   \label{magresidual:fig}
+%\end{figure}
+%
+%\subsubsection{Notes}
+%Some equivalent widths go positive.  Is this an emission?
+%
+%
+%\subsection{One Dust With Si Velocity}
+%\label{onecolor_si:sec}
+%Sil$\lambda3655$ velocity is spectral indicator that has been identified to correlated with peak brightness.  The analysis is expanded to include
+%this line. We use the weighted mean of all spectral measurements within 3 days of peak brightness.  A handful of supernovae do not have a
+%spectrum that close to peak.
 %\subsubsection{Setup}
-%\begin{equation*}
+%With the inclusion of SiII$\lambda3655$ velocity  $v_{Si}$ the model looks like
+%\begin{equation}
 %\left(
@@
 %\begin{matrix}
-%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
-%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
-%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
-%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
-%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
+%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si}\\
+%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} \\
+%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si}\\
+%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si}\\
+%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si}
 %\end{matrix}
@@
 %,C_{c}
-%\right).
-%\end{equation*}
-%%\begin{equation*}
-%%D \sim \mathcal{N}(\bar{D},1)
-%%\end{equation*}
-%\begin{equation*}
+%\right)
+%\label{ewsiv:eqn}
+%\end{equation}
+%\begin{equation}
 %\left(
 %\begin{matrix}
-%U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
-%\end{matrix}
+%U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}\end{matrix}
 %\right) \sim \mathcal{N}
@@
 %U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+%EW_{Si}\\ EW_{Ca} \\ v_{Si}
+%\end{matrix}
+%\right)
+%,C
+%\right).
+%\label{dust:eqn}
+%\end{equation}
+%The global parameters $\eta$ are the slopes of the linear relationships between Si velocity
+%and intrinsic magnitudes. 
+%
+%\subsubsection{Results}
+%The 68\% intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{globalvsi:tab}.
+%The two dimensional contours for the parameters of each filter are shown in Figure~\ref{globalvsi:fig}.  
+%All bands show large and significant non-zero values for $\eta$ with some non-trivial changes to $\beta$ and a lowering
+%if $\sigma$.  The values
+%of $\alpha$ are unchanged.
+%
+%\begin{table}
+%\centering
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%& $X=0$ &1&2&3&4\\ \hline
+%$\alpha_X$
+%&
+%$0.0031^{0.0009}_{-0.0009}$
+%&
+%$0.0005^{0.0008}_{-0.0007}$
+%&
+%$0.0006^{0.0006}_{-0.0006}$
+%&
+%$0.0008^{0.0005}_{-0.0005}$
+%&
+%$0.0020^{0.0005}_{-0.0004}$
+%\\
+%$\beta_X$
+%&
+%$0.0375^{0.0030}_{-0.0030}$
+%&
+%$0.0303^{0.0026}_{-0.0025}$
+%&
+%$0.0298^{0.0023}_{-0.0021}$
+%&
+%$0.0243^{0.0020}_{-0.0019}$
+%&
+%$0.0224^{0.0017}_{-0.0017}$
+%\\
+%$\eta_X$
+%&
+%$0.0032^{0.0011}_{-0.0011}$
+%&
+%$0.0024^{0.0009}_{-0.0009}$
+%&
+%$0.0022^{0.0008}_{-0.0008}$
+%&
+%$0.0019^{0.0007}_{-0.0007}$
+%&
+%$0.0011^{0.0006}_{-0.0006}$
+%\\
+%$R_X$
+%&
+%$5.1004^{0.2929}_{-0.2517}$
+%&
+%$4.1677^{0.2656}_{-0.2272}$
+%&
+%$3.1677^{0.2656}_{-0.2272}$
+%&
+%$2.4828^{0.2327}_{-0.1964}$
+%&
+%$1.8320^{0.2050}_{-0.1838}$
+%\\
+%$\sigma_X$
+%&
+%$0.0537^{0.0162}_{-0.0185}$
+%&
+%$0.0405^{0.0107}_{-0.0131}$
+%&
+%$0.0565^{0.0093}_{-0.0109}$
+%&
+%$0.0538^{0.0084}_{-0.0084}$
+%&
+%$0.0636^{0.0076}_{-0.0079}$
+%\\
+%\hline
+%\end{tabular}
+%\caption{68\% Intervals for Global Fit Parameters for the One-Dust Model with $v_{Si}$  \label{globalvsi:tab}}
+%\end{table}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.5in]{output10/coeff0.pdf} 
+%   \includegraphics[width=2.5in]{output10/coeff1.pdf} 
+%   \includegraphics[width=2.5in]{output10/coeff2.pdf} 
+%      \includegraphics[width=2.5in]{output10/coeff3.pdf} 
+%         \includegraphics[width=2.5in]{output10/coeff4.pdf} 
+%            \caption{Distributions for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, and $\sigma$ in each of the 5 bands.}
+%   \label{globalvsi:fig}
+%\end{figure}
+%
+%
+%
+%The best-fit distribution for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rxsiv:fig}.  Our measurement of
+%$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
+%our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=3in]{output10/gamma_corner.pdf} 
+%   \caption{Best-fit distribution for the   $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$.
+%   \label{rxsiv:fig}}
+%\end{figure}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output10/ccm.pdf}
+%      \includegraphics[width=2.8in]{output10/ccm2.pdf} 
+%   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
+%   predictions for these parameters are overlaid for different values of $R_V$.}
+%   \label{ccmsiv:fig}
+%\end{figure}
+%
+% \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.4in]{output10/sigma_corner.pdf} 
+%   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.}
+%   \label{sigmasiv:fig}
+%\end{figure}
+%
+%The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{histsiv:fig}.  The intrinsic dispersion
+%is given by the standard deviation of $0.09$ mag.  The distribution is non-Gaussian, with a broad tail. 
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output10/Delta_hist.pdf} 
+%   \includegraphics[width=2.8in]{output10/k_hist.pdf} 
+%   \caption{Ideograms for Left: the grey offset $\Delta$; Right: the color term $k$ for all supernovae.}
+%   \label{histsiv:fig}
+%\end{figure}
+%
+%\subsection{Two Dust}
+%
+%Motivated by the consistency of the external extinction with CCV $R_V=3.1$ dust, and the hint of the color-magnitude
+%diagrams in Figure~\ref{magresidual:fig}  not following single slopes, we develop a new model in which
+%each supernova encounters one of two sources of external extinction.
+%
+%\subsubsection{Setup}
+%The model is identical to that of \S\ref{onecolor:sec} except with the addition of an alternative extrinsic source of extinction.
+%The intrinsic magnitudes of the supernova are determined by the spectral properties expressed as Eqn.~\ref{ew:eqn}.
+%One extrinsic source of extinction  (Dust 1) is modeled as before with Eqn.~\ref{dust:eqn};
+%the second source of extinction (Dust 2)
+%is modeled similarly but with the introduction of new parameters $\gamma_{2X}$
+%\begin{equation}
+%\left(
+%\begin{matrix}
+%U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
+%\right) \sim \mathcal{N}
+%\left(
+%\left(
+%\begin{matrix}
+%U +\gamma_{20} k \\B +\gamma_{21} k \\V+\gamma_{22} k\\R+\gamma_{23} k\\I+\gamma_{24} k\\
 %EW_{Si}\\ EW_{Ca}
@@
 %\right).
+%\label{dust2:eqn}
+%\end{equation}
+%The probability that a supernova experiences  Dust 1 is given by the free parameter $p_0$,
+%the probability of Dust 2 is $1-p_0$.  
+%The same $k$ parameters are used to describe supernovae in both extinction sources.  In order to do this we change
+%some of the conditions that constrain the degeneracies of the model:
+%\begin{equation*}
+%\langle \Delta \rangle=0, \gamma_1 = 1+\gamma_2, \gamma_{21}=1+\gamma_{22}.
 %\end{equation*}
-%\begin{equation*}
-%\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
-%\end{equation*}
-
+%These conditions are useful for interpreting the extinction as being due to dust, as $R_X = \gamma_X$,
+%the color excess $E(B-V) \equiv (\gamma_1-\gamma_2)k =k$.
+%The $c$ parameters  are fit such that both extinction models
+%revert to the same intrinsic magnitudes for $k=0$: the $\langle k \rangle=0$ condition is removed. 
+%
+%To alleviate the degeneracies inherent to mixture models, we restrict the range of $\alpha$, $\beta$, and $\gamma$ (the parameters for Dust 1)
+%to be in the neighborhood of the pdf's of \S\ref{onecolor:sec}.  The one-dust model is embedded in the two-dust model when $p_0=1$.
+%We therefore do not claim to find the global optimum of the parameter
+%pdf, but we can conclude whether the two-dust model is preferred over the one-dust model.
+%The intrinsic covariance $C_c$ is taken to be diagonal.
+%
+%\subsubsection{Results}
+%
+%The probability of an object experiencing the first dust is   $p_0=0.3334^{0.0532}_{-0.0721}$,
+%with the pdf shown in Figure~\ref{prob0:fig}.
+%A single dust with properties centered around the one-dust parameter optimum is not only disfavored, but is most likely the
+%minority component.  
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=3.3in]{output9/prob0.pdf}
+%   \caption{pdf of $p_0$, the probability that a supernova experiences Dust 1.  \label{prob0:fig}}
+%\end{figure}
 %
 %
-%A model for a single object is that its intrinsic properties (captured by equivalent width) are drawn from a Normal distribution
-%\begin{equation}
-%\left(
-%\begin{matrix}
-%EW_{Si}\\ EW_{Ca}
-%\end{matrix}
-%\right) \sim \mathcal{N}
-%\left(
-%\left(
-%\begin{matrix}
-%EW_{0, Si}\\ EW_{0, Ca}
-%\end{matrix}
-%\right)
-%,C_{EW}
-%\right),
-%\end{equation}
-%with global parameters $EW_{0, Si}$, $EW_{0, Ca}$, and the independent elements of $C_{EW}$.
-%The colors, which depend on the intrinsic properties and the extrinsic effect of dust, are modeled as
-%\begin{equation}
-%\left(
-%\begin{matrix}
-%U-V\\B-V\\V-R\\V-I
-%\end{matrix}
-%\right) \sim \mathcal{N}
-%\left(
-%\left(
-%\begin{matrix}
-%c_0+\alpha_0 EW_{Si} + \beta_0 EW_{Ca} +\gamma_0 k+ E(U-V) \\
-%c_1+\alpha_1 EW_{Si} + \beta_1 EW_{Ca}  +k +E(B-V) \\
-%c_2+\alpha_2 EW_{Si} + \beta_2 EW_{Ca} +\gamma_2 k + E(V-R)\\
-%c_3+\alpha_3 EW_{Si} + \beta_3 EW_{Ca} +\gamma_3 k +E(V-I)\\
-%\end{matrix}
-%\right)
-%,C_c
-%\right),
-%\end{equation}
-%where there are global parameters $\alpha_X$, $\beta_X$, $c_X$,  and the independent elements of $C_c$,
-%while each supernova has independent parameters $E(X-V)$ and intrinsic color parameter $k$.
+%The 68\% intervals for the global parameters $\alpha$, $\beta$, $R$, $R_2$ and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global2:tab}.
+%The two dimensional contours for the parameters of each filter are shown in Figure~\ref{global2:fig}.  
+%\begin{table}
+%\centering
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\hline
+%& $X=0$ &1&2&3&4\\ \hline
+%$\alpha_{X}$
+%&
+%$0.0077^{0.0014}_{-0.0018}$
+%&
+%$0.0040^{0.0011}_{-0.0013}$
+%&
+%$0.0025^{0.0008}_{-0.0008}$
+%&
+%$0.0020^{0.0006}_{-0.0007}$
+%&
+%$0.0027^{0.0006}_{-0.0006}$
+%\\
+%$\beta_{X}$
+%&
+%$0.0276^{0.0048}_{-0.0053}$
+%&
+%$0.0225^{0.0037}_{-0.0042}$
+%&
+%$0.0249^{0.0025}_{-0.0026}$
+%&
+%$0.0213^{0.0019}_{-0.0020}$
+%&
+%$0.0216^{0.0015}_{-0.0016}$
+%\\
+%$R_{X}$
+%&
+%$5.0878^{0.4233}_{-0.4082}$
+%&
+%$4.3163^{0.3615}_{-0.3327}$
+%&
+%$3.3163^{0.3615}_{-0.3327}$
+%&
+%$2.6600^{0.2685}_{-0.2691}$
+%&
+%$1.9355^{0.2604}_{-0.2474}$
+%\\
+%$R_{2X}$
+%&
+%$2.2199^{0.2110}_{-0.2301}$
+%&
+%$1.5919^{0.1801}_{-0.2246}$
+%&
+%$0.5919^{0.1801}_{-0.2246}$
+%&
+%$0.2486^{0.1650}_{-0.1788}$
+%&
+%$-0.1484^{0.1802}_{-0.1472}$
+%\\
+%$\sigma_{X}$
+%&
+%$0.0570^{0.0042}_{-0.0040}$
+%&
+%$0.0103^{0.0059}_{-0.0048}$
+%&
+%$0.0229^{0.0021}_{-0.0018}$
+%&
+%$0.0094^{0.0031}_{-0.0039}$
+%&
+%$0.0418^{0.0031}_{-0.0030}$
+%\\
+%\hline
+%\end{tabular}
+%\caption{68\% Intervals for Global Fit Parameters for the Two-Dust Model \label{global2:tab}}
+%\end{table}
 %
-%The measurements are drawn from
-%\begin{equation}
-%\left(
-%\begin{matrix}
-%U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
-%\end{matrix}
-%\right)_o \sim \mathcal{N}
-%\left(
-%\left(
-%\begin{matrix}
-%U-V\\B-V\\V-R\\V-I\\EW_{Si}\\ EW_{Ca}
-%\end{matrix}
-%\right)
-%,C_o
-%\right),
-%\end{equation}
-%where $C_o$ is the observation covariance matrix.
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.5in]{output9/coeff0.pdf} 
+%   \includegraphics[width=2.5in]{output9/coeff1.pdf} 
+%   \includegraphics[width=2.5in]{output9/coeff2.pdf} 
+%      \includegraphics[width=2.5in]{output9/coeff3.pdf} 
+%         \includegraphics[width=2.5in]{output9/coeff4.pdf} 
+%            \caption{Distributions for $c$, $\alpha$, $\beta$, $\gamma$, $\gamma_2$, and $\sigma$ in each of the 5 bands.}
+%   \label{global2:fig}
+%\end{figure}
 %
-%Given enough supernovae to constrain the global parameters, the observed colors of each supernova are used to determine its
-%color excess parameters.
+%Our determinations of $R$ and $R_2$ are compared to the expectations of CCM dust in Figure~\ref{ccm2:fig}.
+%Within the context of this model there are two distinct types of dust: Dust 1 behaves similarly to $R_V=3.1$ CCM dust.
+%In contrast, Dust 2 is more consistent with extremely low values of $R_V$.  Negative values of $R_V$ are unphysical.
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output9/ccm.pdf}
+%      \includegraphics[width=2.8in]{output9/ccm2.pdf} 
+%         \includegraphics[width=2.8in]{output9/ccm12.pdf}
+%      \includegraphics[width=2.8in]{output9/ccm22.pdf} 
+%   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right)
+%   for Dust 1 (top row) and Dust 2 (bottom row).  CCM
+%   predictions for these parameters are overlaid for different values of $R_V$.}
+%   \label{ccm2:fig}
+%\end{figure}
+%
+%While the values for $\beta$ are consistent between the one- and two-dust models, the $\alpha$ values change significantly.
+%This implies a correlation between $EW_{Ca}$ and the dust environment.
+%
 \end{document}

### 2016-09-01 forgerard.tex
Put together writeup

@@
 \\
+$\alpha_X/\alpha_2-1$
+&
+$   2.0^{   1.3}_{  -0.6}$
+&
+$   0.0^{   0.1}_{  -0.2}$
+&
+$   0.0^{   0.0}_{   0.0}$
+&
+$   0.0^{   0.2}_{  -0.1}$
+&
+$   0.8^{   0.9}_{  -0.4}$
+\\
 $\beta_{X}$
 &
-$0.0335^{0.0031}_{-0.0031}$
+$ 0.033^{ 0.003}_{-0.003}$
 &
-$0.0267^{0.0025}_{-0.0026}$
+$ 0.027^{ 0.003}_{-0.003}$
 &
-$0.0266^{0.0022}_{-0.0022}$
+$ 0.027^{ 0.002}_{-0.002}$
 &
-$0.0214^{0.0019}_{-0.0019}$
+$ 0.021^{ 0.002}_{-0.002}$
 &
-$0.0200^{0.0018}_{-0.0017}$
+$ 0.020^{ 0.002}_{-0.002}$
+\\
+$\beta_X/\beta_2-1$
+&
+$  0.26^{  0.05}_{ -0.05}$
+&
+$  0.00^{  0.03}_{ -0.03}$
+&
+$  0.00^{  0.00}_{  0.00}$
+&
+$ -0.19^{  0.01}_{ -0.01}$
+&
+$ -0.25^{  0.03}_{ -0.03}$
 \\
@@
 \\
+$\eta_X/\eta_2-1$
+&
+$  0.26^{  0.65}_{ -0.65}$
+&
+$ -0.09^{  0.53}_{ -0.55}$
+&
+$  0.00^{  0.00}_{  0.00}$
+&
+$ -0.08^{  0.24}_{ -0.21}$
+&
+$ -0.57^{  0.51}_{ -0.59}$
+\\
 $R_{X}$
 &
-$4.8715^{0.4826}_{-0.4296}$
+$  4.87^{  0.48}_{ -0.43}$
 &
-$3.9642^{0.3953}_{-0.3528}$
+$  3.96^{  0.40}_{ -0.35}$
 &
-$2.9644^{0.3118}_{-0.2801}$
+$  2.96^{  0.31}_{ -0.28}$
 &
-$2.2869^{0.2559}_{-0.2322}$
+$  2.29^{  0.26}_{ -0.23}$
 &
-$1.6395^{0.2112}_{-0.1939}$
+$  1.64^{  0.21}_{ -0.19}$
 \\
@@
 &
-$-2.6978^{1.3200}_{-2.4424}$
+$ -2.70^{  1.32}_{ -2.44}$
 &
-$-3.4586^{1.2929}_{-2.6501}$
+$ -3.46^{  1.29}_{ -2.65}$
 &
-$-4.4569^{1.4269}_{-3.1109}$
+$ -4.46^{  1.43}_{ -3.11}$
 &
-$-4.2020^{1.3152}_{-2.8944}$
+$ -4.20^{  1.32}_{ -2.89}$
 &
-$-3.8012^{1.2005}_{-2.6141}$
+$ -3.80^{  1.20}_{ -2.61}$
 \\
@@
 &
-$0.0592^{0.0124}_{-0.0112}$
+$ 0.059^{ 0.012}_{-0.011}$
 &
-$0.0315^{0.0069}_{-0.0073}$
+$ 0.031^{ 0.007}_{-0.007}$
 &
-$0.0201^{0.0041}_{-0.0055}$
+$ 0.020^{ 0.004}_{-0.006}$
 &
-$0.0127^{0.0069}_{-0.0079}$
+$ 0.013^{ 0.007}_{-0.008}$
 &
-$0.0425^{0.0051}_{-0.0044}$
+$ 0.043^{ 0.005}_{-0.004}$
 \\
@@
 \end{tabular}
-\caption{68\% Intervals for Global Fit Parameters for the One-Dust Model \label{global:tab}}
+\caption{68\% Intervals for Global Fit Parameters  \label{global:tab}}
 \end{table}
@@
 are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ are consistent with zero within one sigma.
+The effect in color can be seen in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$.
+Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically, while
+$v_{Si}$ does not have a significant affect on colors.
 
-The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Our measurement of
-$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
+The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Figure~\ref{ccm:fig}
+shows the expectation of CCM dust, plotted together with our measurements of
+$R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the central wavelength of the synthetic bands.
 the $R_X$ are consistent with the  $R_V=3.1$ CCM model (assuming we are using
@@
       \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
-   \caption{Best-fit distribution for (left)  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ and (right)  $R_{\rho X}=\frac{\delta_X}{\delta_1-\delta_2}$.
+   \caption{Best-fit distribution for (left)  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ and (right)  $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$.
    \label{rx:fig}}
@@
 
-The best-fit distribution for $R_{\rho X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
+The best-fit distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
 Although the posteriors of $\delta$ are fairly circular, $\delta_1-\delta_2$ can get close to zero, resulting in the
-elongated tail in negative  $R_{\rho X}$.
+elongated tail in negative  $R_{\delta X}$.
 All values are inconsistent with zero and negative: a color excess in $B-V$ produces a brightening of the supernova.
-The smallest (most negative) value is for the $V$ band with  values increasing in both bluer and redder directions; an
-example consequence is that
+The smallest (most negative) value is $R_{\delta V}$  with  values increasing in both bluer and redder directions; a consequence
+of which is that
 a reddening in $B-V$ comes with a blueing in $V-R$.
-These are not the behaviors expected from normal dust or a blackbody in the Raleigh-Jeans tail and so may be indicative of
-more complicated underlying physics.
+These are not the behaviors expected from normal dust or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
+more complicated underlying supernova physics.
 
 The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
- $E_\rho(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
+ $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
 Recall that given our boundary conditions the means of both distributions are equal to zero. 
-The standard deviation of $E(B-V)$ is 0.074 mag while that of $E_\rho(B-V)$ is 0.019 mag.
+The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
+The range of $B-V$ colors is almost 4 times larger for the external contribution:
+extreme colors can thus be attributed to the external source. 
 Both distributions are non-Gaussian extended tails in the red.
@@
    \caption{Histograms of $E(B-V) =(\gamma_1-\gamma_2)k$ and
-   $E_\rho(B-V) = (\delta_1-\delta_2)D$.
+   $E_\delta(B-V) = (\delta_1-\delta_2)D$.
    \label{ebv:fig}}
@@
 
-Let us conflate the two separate color effects into a single effective extinction with
+The two separate color effects are conflated into a combined color excess with a single effective extinction behavior
 \begin{equation}
@@
    \includegraphics[width=3.2in]{output11/rveff.pdf}
-   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}$,
+   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}$,
    \label{rveff:fig}}
 \end{figure}
-with  $R_{V,eff}  = 1.52 \pm 0.24$.  This may explain why previous analyses have produced low $R_V$ values.
+and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
+Rerunning the posterior calculation with initial conditions for $\gamma$  near $R_{X,eff}$ reproduced the original results, indicating that
+the effective and true $R$ values are not separated by local posterior extrema.
 
 Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
-square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion is quite small, ranging from 0.01 to 0.06 mag.
+square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
+than the dispersion in $\Delta$.
 
@@
 \end{figure}
+
+Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
+$\Delta$: the distributions (for all Monte Carlo chain links for all supernovae) are shown in Figure~\ref{perobject:fig}.
+There is a core distribution within the supernova parameter-space, with around ten objects that live on the outskirts of that
+distribution.  Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
+heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
+Otherwise the distribution in $EW_{Ca}$--$v_{Si}$ space is the view that
+shows the most outliers.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
+   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
+$\Delta$.
+   \label{perobject:fig}}
+\end{figure}
+
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are shown in the matrix
+\begin{equation}
+\begin{pmatrix}
+1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
+-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
+-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
+-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
+0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
+0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
+\end{pmatrix}.
+\end{equation}
+Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
+$EW_{Si}$--$v_{Si}$, which are statistics that describe the same spectral feature.
+External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
+0.04.  Although $E(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.
 

### 2016-09-01 table11.py

@@ -31,25 +31,40 @@ dum/= len(fit['L_Omega'])
 # color_cov = numpy.dot(trans,numpy.dot(dum, trans.T))
 print " \\\\\n".join([" & ".join(map('{0:.4f}'.format, line)) for line in dum])
 
-pars = ['alpha','beta','eta','gamma','rho1','L_sigma']
-pars_n = ['\\alpha_{','\\beta_{','\\eta_{','R_{','R_{\\delta ','\\sigma_{']
-for p,pn in zip(pars,pars_n):
+pars = ['alpha','alpha','beta','beta','eta','eta','gamma','rho1','L_sigma']
+pars_n = ['\\alpha_{','{\\alpha ','\\beta_{','{\\beta ','\\eta_{','{\\eta ','R_{','R_{\\delta ','\\sigma_{']
+sigfig = [4,1,3,2,4,2,2,2,3]
+for p,pn, s in zip(pars,pars_n,sigfig):
     print '${}X}}$'.format(pn)
     for i in xrange(5):
         print '&'
-
-        if pn == 'R_{' or pn == 'R_{\\delta ':
+        if pn[0] == 'R':
             dum = numpy.percentile(fit[p][:,i]/(fit[p][:,1]-fit[p][:,2])[:,None],(50,50-34,50+34)) 
+        elif pn[0] == '{':
+            dum = numpy.percentile(fit[p][:,i]/fit[p][:,2]-1,(50,50-34,50+34)) 
         else :
             dum = numpy.percentile(fit[p][:,i],(50,50-34,50+34))            
-        print  '${:6.4f}^{{{:6.4f}}}_{{{:6.4f}}}$'.format(dum[0], dum[2]-dum[0],dum[1]-dum[0] )
+        print  '${1:6.{0}f}^{{{2:6.{0}f}}}_{{{3:6.{0}f}}}$'.format(s,dum[0], dum[2]-dum[0],dum[1]-dum[0] )
     print '\\\\'
 
 
-temp = numpy.array([(fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['R'], (fit['rho1'][:,1]-fit['rho1'][:,2])[:,None]*fit['R']])
-print numpy.std(temp[0]),numpy.std(temp[1])
+filts = ['U','B','V','R','I']
+for i in xrange(5):
+    for j in xrange(i+1,5):
[…]

### 2016-09-01 view11.py

@@ -62,7 +62,7 @@ correction_median = numpy.median(correction,axis=1)
 # print 'EW1', numpy.median(fit['EW'][:,outlier[0],1],axis=0), EW_renorm[outlier[0],1]
 
 plt.hist(fit['Delta'].flatten(),normed=True,bins=20)
-plt.title(r'$\Delta$')
+plt.xlabel(r'$\Delta$')
 pp = PdfPages('output11/Delta_hist.pdf')
 plt.savefig(pp,format='pdf')
 pp.close()
@@ -82,9 +82,9 @@ plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
 
-plt.hist([(fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['R'], (fit['rho1'][:,1]-fit['rho1'][:,2])[:,None]*fit['R']],normed=True,bins=20,
+plt.hist([(fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['k'], (fit['rho1'][:,1]-fit['rho1'][:,2])[:,None]*fit['R']],normed=True,bins=20,
     label=[r'$E(B-V)$',r'$E_\delta(B-V)$'],range=(-0.1,0.4))
-# plt.title(r'$E(B-V)$')
+plt.xlabel(r'$E(B-V)$')
 plt.legend()
 pp = PdfPages('output11/ebv.pdf')
 plt.savefig(pp,format='pdf')
@@ -281,18 +281,21 @@ nlinks = fit['gamma'].shape[0]
 mega = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['rho1'],fit['L_sigma']])
 mega = numpy.transpose(mega)
 
+rvs = [1.7,3.1,4.1]
+filts = ['U','B','V','R','I']
+
+
 for index in xrange(5):
     figure = corner.corner(mega[index,:,:],labels=[r"$c_{}$".format(index), r"$\alpha_{}$".format(index),\
                     r"$\beta_{}$".format(index),r"$\eta_{}$".format(index),r"$\gamma_{}$".format(index),\
                     r"$\delta_{{1{}}}$".format(index), r"$\sigma_{}$".format(index)])
+    figure.suptitle(filts[index],fontsize=28)
     pp = PdfPages('output11/coeff{}.pdf'.format(index))
[…]

### 2016-09-02 forgerard.tex
continuing to work on article

@@
-\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
+\documentclass{aastex}   	% use "amsart" instead of "article" for AMSLaTeX format
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
@@
 								% TeX will automatically convert eps --> pdf in pdflatex		
-\usepackage{amssymb}
+%\usepackage{amssymb}
 \usepackage{amsmath}
+\usepackage{natbib}
+\usepackage{lineno}
+\linenumbers
 
 \begin{document}
+
+\title{text}
+\author
+{
+    G.~Aldering,\altaffilmark{2}
+    P.~Antilogus,\altaffilmark{4}
+    S.~Bailey,\altaffilmark{2}
+    C.~Baltay,\altaffilmark{5}
+    K.~Barbary,\altaffilmark{3}
+    D.~Baugh,\altaffilmark{6}
+    K.~Boone,\altaffilmark{2,3}
+    S.~Bongard,\altaffilmark{4}
+    C.~Buton,\altaffilmark{7}
+    J.~Chen,\altaffilmark{6}
+    N.~Chotard,\altaffilmark{7}
+    Y.~Copin,\altaffilmark{7}
+    P.~Fagrelius,\altaffilmark{2,3}
+    H.~K.~Fakhouri,\altaffilmark{2,3}
+    U.~Feindt,\altaffilmark{9}
+    D.~Fouchez,\altaffilmark{10}
+    E.~Gangler,\altaffilmark{11}  
+    B.~Hayden,\altaffilmark{2}
+    W.~Hillebrandt,\altaffilmark{16}
+    A.~G.~Kim,\altaffilmark{2}
+    M.~Kowalski,\altaffilmark{9,12}
+    P.-F.~Leget,\altaffilmark{11}
+    S.~Lombardo,\altaffilmark{9}
+    J.~Nordin,\altaffilmark{2,9}
+    R.~Pain,\altaffilmark{4} 
+    E.~Pecontal,\altaffilmark{13}
+    R.~Pereira,\altaffilmark{7}
+    S.~Perlmutter,\altaffilmark{2,3}
+    D.~Rabinowitz,\altaffilmark{5}
+    M.~Rigault,\altaffilmark{9} 
+    D.~Rubin,\altaffilmark{2,14}
+    K.~Runge,\altaffilmark{2}
+    C.~Saunders,\altaffilmark{2,3}
+   R.~Scalzo,\altaffilmark{8}
+    G.~Smadja,\altaffilmark{7} 
+    C.~Sofiatti,\altaffilmark{2,3} 
+    A.~Stocker,\altaffilmark{1}
+    N.~Suzuki,\altaffilmark{2}
+    S.~Taubenberger,\altaffilmark{16}
+    C.~Tao,\altaffilmark{6,10}
+    R.~C.~Thomas,\altaffilmark{15} \\
+    (The Nearby Supernova Factory)
+}
+
+\altaffiltext{2}
+{
+    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720
+}
+\altaffiltext{3}
+{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300
+}
+\altaffiltext{4}
+{
+    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
+    Universit\'e Pierre et Marie Curie Paris 6, Universit\'e Paris Diderot Paris 7, CNRS-IN2P3, 
+    4 place Jussieu, 75252 Paris Cedex 05, France
+}
+\altaffiltext{5}
+{
+    Department of Physics, Yale University, 
+    New Haven, CT, 06250-8121
+}
+\altaffiltext{6}
+{
+    Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China 
+}
+\altaffiltext{7}
+{
+    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
+    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon.
+}
+\altaffiltext{8}
+{
+    Research School of Astronomy and Astrophysics,
+    Australian National University,
+    Canberra, ACT 2611, Australia
+}
+\altaffiltext{9}
+{
+    Institut fur Physik,  Humboldt-Universitat zu Berlin,
+    Newtonstr. 15, 12489 Berlin
+}
+\altaffiltext{10}
+{
+    Centre de Physique des Particules de Marseille, 
+    Aix-Marseille Universit\'e , CNRS/IN2P3, 
+    163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France
+}
+\altaffiltext{11}
+{
+    Clermont Universit\'e, Universit\'e Blaise Pascal, CNRS/IN2P3, Laboratoire de Physique Corpusculaire,
+    BP 10448, F-63000 Clermont-Ferrand, France
+}
+\altaffiltext{12}
+{
+    DESY, D-15735 Zeuthen, Germany
+}
+\altaffiltext{13}
+{
+    Centre de Recherche Astronomique de Lyon, Universit\'e Lyon 1,
+    9 Avenue Charles Andr\'e, 69561 Saint Genis Laval Cedex, France
+}
+\altaffiltext{14}
+{
+    Department of Physics, Florida State University,
+    315 Keen Building, Tallahassee, FL 32306-4350
+}
+\altaffiltext{15}
+{
+    Computational Cosmology Center, Computational Research Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road MS 50B-4206, Berkeley, CA, 94720
+}
+
+\altaffiltext{16}
+{
+    Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1,
+D-85748 Garching, Germany
+}
+
+\begin{abstract}
+abstract text
+\end{abstract}
+
+\keywords{text}
+
+\section{Introduction}
+Type~Ia supernovae (SNe~Ia) form a homogenous set of astronomical objects and as such were recognized as a powerful distance indicator 
+and probe of cosmology \citep{1992ARA&A..30..359B}.  After further careful consideration of supernova data, it was recognized
+that SN~Ia light-curve shapes \citep{1984SvA....28..658P, 1993ApJ...413L.105P} and colors \citep{1998A&A...331..815T} exhibit subtle signs of heterogeneity,
+which need to be considered when inferring SN~Ia distances.  Empirical models parameterizing SNe~Ia by their light-curve shape
+and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} to enable distance measurements of cosmological supernovae
+that subsequently were used in the discovery of the accelerating expansion of the Universe \citep{1998AJ....116.1009R,1999ApJ...517..565P}.
+
+The two most commonly used supernova light-curve fitters for cosmological purposes today are SALT2 \citep{2007A&A...466...11G} and MLCS2k2
+\citep{2007ApJ...659..122J}.\footnote{More flexible light-curve fitters
+\citep[e.g.][]{2011AJ....141...19B} are used to study SN~Ia heterogeneity.}
+They remain two-parameter models, with one parameter characterizing light-curve shape and the other
+supernova color.  SALT2 training extracts color variation empirically from SNe that span a wide range of colors whereas MLCS2k2
+attributes color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation that
+both intrinsic and extrinsic color variation may occur.
+
+There is evidence that supports the expectation that one parameter in insufficient to describe the full range
+of supernova color behavior.  One approach to look for color diversity is to find correlations between color and spectral features.
+\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations with differing $B_{max}-V_{max}$ identified by Si velocity.
+\citet{2015MNRAS.451.1973S}
+find that high-velocity Si II$\lambda$6355 are found in objects that have red ultraviolet/optical colors near maximum brightness.
+Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find on average values for $R_V \ll 3.1$,
+much smaller than that of diffuse Milky Way dust, though the dispersion is large.
+The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
+plays a role in observed supernova colors \citep{2005ApJ...635L..33W, 2008ApJ...686L.103G}.
+In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
+the standard $R_V=3.1$ is recovered.
+
+In this article we use the idea that spectral indicators carry information on intrinsic supernova colors,
+and allow for the possibility of there being two further color parameters, one intrinsic and the other
+extrinsic.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
+\S\ref{model:sec} and results are given in \S\ref{results:sec}.  In \S\ref{sn2014j:sec} our results are applied to the out-of-sample
+supernova SN2014J that has been previously identified as having extreme color properties.
+We finish with conclusions in \S\ref{conclusions:sec}.
+
 \section{Data}
-The data set consists of synthetic $UBVRI$ (whether SNF or Nico system yet to be elucidated)
-peak brightnesses and Si and Ca equivalent widths at peak
-of 172 SNf supernovae.  The photometry is normalized to place all supernovae at a common distance, as
-inferred by redshift.
-The data was provided by Manu Gangler.
+\label{data:sec}
 
-The SiII$\lambda6355$ velocity within 3-days of peak brightness is taken from the file phrenology\_2016\_12\_01\_CABALLOv1.pkl.
-We use the weighted sum for supernovae with multiple velocity measurements.  A subset of 163
-supernovae have this velocity measurement.
+Our analysis uses the spectrophotometric data set obtained by
+the SNfactory with the SuperNova Integral Field
+Spectrograph \citep[SNIFS,][]{2004SPIE.5249..146L}.  SNIFS is a fully integrated
+instrument optimized for automated observation of point sources on a
+structured background over the full ground-based optical window at
+moderate spectral resolution ($R \sim 500$).  It consists of a
+high-throughput wide-band pure-lenslet integral field spectrograph
+\citep[IFS, ``\`a la TIGER;''][]{1995A&AS..113..347B,2000ASPC..195..173B,2001MNRAS.326...23B}, a
+multi-filter photometric channel to image the field in the vicinity of
+the IFS for atmospheric transmission monitoring simultaneous with
+spectroscopy, and an acquisition/guiding channel.  The IFS possesses a
+fully-filled $6\farcs 4 \times 6\farcs 4$ spectroscopic field of view
+subdivided into a grid of $15 \times 15$ spatial elements, a
+dual-channel spectrograph covering 3200--5200~\AA\ and 5100--10000~\AA\
+simultaneously, and an internal calibration unit (continuum and arc
+lamps).  SNIFS is mounted on the south bent Cassegrain port of the
+University of Hawaii 2.2~m telescope on Mauna Kea, and is operated
+remotely.  Observations are reduced using the SNfactory's dedicated data
+reduction pipeline, similar to that presented in \S4 of \citet{2001MNRAS.326...23B}.
+A discussion of the software pipeline is presented in
+\citet{2006ApJ...650..510A} and is updated in \citet{2010ApJ...713.1073S}.  A detailed
+description of host-galaxy subtraction is given in \citet{2011MNRAS.418..258B}.
 
-\section{Model Fits}
+The spectral time-series used are corrected for Milky Way dust
+extinction \citep{1989ApJ...345..245C,1998ApJ...500..525S} but not for the
+effects of circumstellar or host galaxy dust extinction.  
+Each spectral time series is
+blue-shifted to rest-frame, and the fluxes normalized to represent that
+observed at a common distance for all supernovae --- thus, ratios
+in flux between supernovae can be interpreted as ratios in
+luminosity or equivalently differences in absolute magnitude.
 
-We hypothesize that Type Ia supernova spectral features are predictive of intrinsic
-magnitudes.  We use feature statistics that are insensitive to broad-band reddening.
-The intrinsic magnitudes are not perfectly deterministic, but have some intrinsic dispersion.
-An extrinsic physical process common to all supernovae can influence the propagation
-of light along the line of sight to influence apparent magnitudes.
-We allow for additional color variation left unaccounted for by the spectral features and external extinction.
+Supernova-frame synthetic photometry is generated for the top-hat filter system
+described in \citet{2011A&A...529L...4C}, which is comprised of five logarithmically-spaced bands spanning
+3276--8635 \AA; the bands have approximate correspondence to $UBVRI$ and are thus referred to as such.
+For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
+The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
+in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.
 
-\subsection{Setup}
+There are 163 supernovae that have spectroscopic data within three days of peak brightness:
+these constitute our analysis sample.  The data are given in Table~\ref{data:tab}.
+The peak magnitude uncertainties do have covariance, which are accounted
+for in the analysis; only the variance is included in the table.
+
+\begin{deluxetable}{ccccccccc}
+\tabletypesize{\tiny}
+\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Datat\label{data:tab}}
+\tablehead{
+\colhead{$n$} & \colhead{$EW_{Ca}$} & \colhead{$EW_{Si}$} & \colhead{$v_{Si}$} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} \\
+\multicolumn{3}{c}{} &  \colhead{(km s$^{-1}$)} & \multicolumn{5}{c}{}
+}
+\startdata
+0 & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
+1 & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6139 \pm   2$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
+2 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6131 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
+3 & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   2$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
+4 & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ \\
+5 & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ \\
+6 & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6140 \pm   4$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+7 & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6099 \pm   4$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+8 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ \\
+9 & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6099 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
+10 & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6144 \pm   2$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
+11 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ \\
+12 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6112 \pm   4$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
+13 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6115 \pm   2$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
+14 & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6116 \pm   3$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
+15 & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm   4$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
+16 & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6134 \pm   4$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
+17 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6125 \pm   1$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
+18 & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6155 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
+19 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6127 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
+20 & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6132 \pm   1$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
+21 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6130 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
+22 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ \\
+23 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6148 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
+24 & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6116 \pm   2$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
+25 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6118 \pm   3$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+26 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6099 \pm   4$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
+27 & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6122 \pm   2$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
+28 & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6128 \pm   1$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
+29 & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6125 \pm   3$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
+30 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6120 \pm   2$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
+31 & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6112 \pm   3$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
+32 & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6141 \pm   3$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
+33 & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6113 \pm   2$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
+34 & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6104 \pm   4$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
+35 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6108 \pm   5$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
+36 & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6130 \pm   3$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+37 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6125 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
+38 & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6168 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
+39 & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6088 \pm   2$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
+40 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6122 \pm   4$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
+41 & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6068 \pm   4$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
+42 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6102 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
+43 & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6122 \pm   3$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
+44 & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6169 \pm   3$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
+45 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6098 \pm   1$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
+46 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6150 \pm   2$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
+47 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
+48 & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6142 \pm   2$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
+49 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
+50 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
+51 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
+52 & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6142 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
+53 & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm   8$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
+54 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   3$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
+55 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6140 \pm   3$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
+56 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6095 \pm   5$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
+57 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6151 \pm   4$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
+58 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6123 \pm   2$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
+59 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6135 \pm   4$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
+60 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6132 \pm   2$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
+61 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ \\
+62 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6112 \pm   3$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
+63 & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6128 \pm   3$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
+64 & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6100 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
+65 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6108 \pm   4$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
+66 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
+67 & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6130 \pm   1$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
+68 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6127 \pm   2$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
+69 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
+70 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6118 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
+71 & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6150 \pm   4$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
+72 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
+73 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
+74 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6109 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
+75 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6142 \pm   2$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
+76 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6084 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
+77 & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6133 \pm   2$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
+78 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6137 \pm   3$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
+79 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6133 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
+80 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6132 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
+81 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+82 & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
+83 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
+84 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   2$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
+85 & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6144 \pm   2$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
+86 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   3$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
+87 & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6142 \pm   3$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
+88 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
+89 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
+90 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+91 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6162 \pm   4$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+92 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6134 \pm   2$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
+93 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6142 \pm   5$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
+94 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6137 \pm   4$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
+95 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6127 \pm   3$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
+96 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6117 \pm   4$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
+97 & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6097 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
+98 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
+99 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6168 \pm   2$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
+100 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
+101 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6134 \pm   5$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
+102 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6197 \pm   7$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
+103 & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6134 \pm   3$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
+104 & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6076 \pm   6$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
+105 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6111 \pm   2$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
+106 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6141 \pm   3$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
+107 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
+108 & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6118 \pm   2$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
+109 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6122 \pm   4$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
+110 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6131 \pm   4$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
+111 & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6126 \pm   2$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
+112 & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
+113 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6108 \pm   4$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
+114 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
+115 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6147 \pm   4$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
+116 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6127 \pm   2$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
+117 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
+118 & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6120 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+119 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
+120 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
+121 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6155 \pm   2$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
+122 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   3$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
+123 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   3$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
+124 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6112 \pm   4$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
+125 & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6100 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
+126 & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6133 \pm   3$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
+127 & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6114 \pm   2$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
+128 & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6111 \pm   3$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
+129 & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6139 \pm   3$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
+130 & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6120 \pm   2$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
+131 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6120 \pm   5$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
+132 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
+133 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
+134 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
+135 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6131 \pm   3$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
+136 & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6121 \pm   2$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
+137 & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6134 \pm   3$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
+138 & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6139 \pm   3$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
+139 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6128 \pm   6$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
+140 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
+141 & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6113 \pm   2$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
+142 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+143 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6090 \pm   2$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
+144 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6118 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
+145 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
+146 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6119 \pm   3$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
+147 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6140 \pm   3$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
+148 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
+149 & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6129 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
+150 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
+151 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6143 \pm   4$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
+152 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
+153 & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6103 \pm   4$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
+154 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6149 \pm   4$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
+155 & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6126 \pm   2$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
+156 & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6135 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+157 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6124 \pm   2$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
+158 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6116 \pm   3$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
+159 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6146 \pm   4$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
+160 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6157 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
+161 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6112 \pm   3$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
+162 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6153 \pm   4$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\\enddata
+\end{deluxetable}
+
+\section{Supernova Model}
+\label{model:sec}
+We hypothesize that at peak brightness
+Type Ia supernova broadband magnitudes and colors are correlated with
+spectral features; equivalent widths and line velocities, being insensitive to broadband color effects, are considered.
+Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
+of intrinsic variation is allowed.
+The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some dispersion.
+An extrinsic physical process (i.e.\ dust) subsequently determines the apparent magnitudes.
+
 We assume 
@@
 $EW_{Ca}$, $EW_{Si}$,
-the SiII$\lambda6355$ velocity $v_{Si}$, and an intrinsic color-variation parameter $D$.
-Residual Gaussian dispersion is described by covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
-to capture grey intrinsic dispersion and distance errors introduced in the normalization of the photometry.
+the SiII$\lambda6355$ velocity $v_{Si}$:
+these spectral features have been previously associated with SN~Ia diversity  
+\citep{2006PASP..118..560B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F,2009A&A...500L..17B}.
+Note that $EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
+\citep{2011A&A...529L...4C}. 
+A color-variation parameter $D$ describes further magnitude/color variation unaccounted for by the spectral features.
+Residual dispersion is described by a Normal distribution with (unknown) covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
+to capture intrinsic dispersion and distance errors introduced when normalizing the supernovae to be at a common distance.
 The observed magnitudes are linearly dependent on an
 extrinsic color-variation parameter $k$  parameter.  The observables
-$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian uncertainty with covariance $C$.  The model is written as
+$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian measurement uncertainty with covariance $C$; these have
+been presented in \S\ref{data:sec}.
+The model is written as
 \begin{equation}
-\left(
-\begin{matrix}
+\begin{pmatrix}
 U\\B\\V\\R\\I
-\end{matrix}
-\right) \sim \mathcal{N}
+\end{pmatrix}
+\sim \mathcal{N}
 \left(
 \Delta +
-\left(
-\begin{matrix}
+\begin{pmatrix}
 c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si} + \delta_0 D\\
@@
 c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si} + \delta_4 D
-\end{matrix}
-\right)
+\end{pmatrix}
 ,C_{c}
@@
 \begin{equation}
+\begin{pmatrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
+\end{pmatrix}
+\sim \mathcal{N}
 \left(
-\begin{matrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}\end{matrix}
-\right) \sim \mathcal{N}
-\left(
-\left(
-\begin{matrix}
+\begin{pmatrix}
 U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
 EW_{Si}\\ EW_{Ca} \\ v_{Si}
-\end{matrix}
-\right)
+\end{pmatrix}
 ,C
@@
 \end{equation}
-The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the bilinear relationships between the spectral
-features and intrinsic color with intrinsic magnitudes.  The extrinsic piece is split into the properties $\gamma$ of the physical process and the per-supernova 
-parameters $k$.  To break the degeneracies inherent in the model we impose
-\begin{equation*}
+The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships between the spectral
+features and intrinsic colors (encoded in $D$),  with intrinsic magnitudes.  The global parameters $\gamma$ are the slopes that connect the extrinsic colors
+(encoded in $k$) and observed magnitude.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
+\begin{equation}
 \langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 \ge 0, \delta_0\le0.
-\end{equation*}
+\end{equation}
+The first two are imposed to constrain the definition of zero color (i.e. $E(B-V)=0$).    The latter two exclude degenerate posterior space
+associated
+with  simultaneous sign flips of
+$\delta$--$D$ and $\gamma$--$k$.
 
@@
 ascribed to $\Delta$, $\delta D$, and $\gamma k$ could also be attributed to intrinsic dispersion.  There are several features of the model
-that drives the assignation of variations away from $C_c$:  The probability distribution functions decrease
-with increasing $\det{C_c}$ so growing $C_c$ is disfavored; The distributions of $\Delta$ and $k$ are turn out to
-be non-Gaussian, and so are not well described by a Normal covariance; The Bayesian prior selected for $C_c$ disfavors
-grey offsets.
+that drives the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$;
+The distributions of $\Delta$ and $k$ turn out to
+be non-Gaussian, and so are not well described by a Normal covariance; Grey offsets would appear as a constant
+in all elements of the covariance matrix, which is disfavored for the Bayesian prior selected for $C_c$.
 
 If interpreted as being due to dust, the extrinsic term could be associated with extinction $A_X = \gamma_X k$.  In
-this parlance the color excess
-is $E(B-V) = (\gamma_1-\gamma_2) k$ and $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
+this parlance our parameters can be re-expressed as the more familiar color excess
+$E(B-V) = (\gamma_1-\gamma_2) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
 Similarly we introduce for the intrinsic color term $E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.
 
-As I perform an Bayesian analysis some mention of priors is required.  A flat prior is used for all parameters except
-for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior and standard
-deviations with
- $\mu=0.1 $, $\sigma=0.1$ Cauchy (Lorentz) distribution prior restricted to non-negative values.
-The nature of the LKJ prior is rather mysterious; one thing to note is that for $\nu=4$ the correlation prior is broad but
-approaches zero at the extremum.
+In a Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
+for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior
+\citep{Lewandowski20091989} and standard
+deviations with a  Cauchy distribution prior with
+ $\mu=0.1$, $\sigma=0.1$ mag and restricted to non-negative values.
 
-\subsubsection{Results}
-STAN is used to determine the parameter posteriors.  Visual inspection of the posterior and the $\hat{R}$ and $N_{eff}$ statistics
-show no signs for non-convergence or sparse sampling.
-The $\hat{R}$ statistic is equal to $1.00$ for almost all the parameters, the largest value is $1.03$ for one of the parameters describing the covariance matrix $C_c$;  $N_{eff} \gg 100$ for all parameters, as recommended.
+\section{Results}
+\label{results:sec}
+The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo as implemented in
+STAN \citep{stan}. STAN provides output statistics to assess
+the convergence of the Markov chains.  The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
+output also gives  $N_{eff} \gg 100$ for all parameters, indicating that there is no evidence for sparse sampling of the parameter space.
+Empirically, the confidence regions are localized and unimodal as can be seen in  Figure~\ref{global:fig}.  There is no evidence that
+the Monte Carlo chains have not converged to the stationary posterior distribution.
 
-The 68\% intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma = \sqrt{C_{c,ii}}$
-for each of the five filters are given in Table~\ref{global:tab}.
-The two dimensional contours for the parameters, grouped by filter, are shown in Figure~\ref{global:fig}.  The Table does not show
-the results for $c$ as their values are not significant for the aims of this analysis, the Figure does show $c$ to indicate the convergence
-and correlations of these parameters in the fit.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.5in]{output11/coeff0.pdf} 
+   \includegraphics[width=2.5in]{output11/coeff1.pdf} 
+   \includegraphics[width=2.5in]{output11/coeff2.pdf} 
+      \includegraphics[width=2.5in]{output11/coeff3.pdf} 
+         \includegraphics[width=2.5in]{output11/coeff4.pdf} 
+            \caption{Distributions for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.   \label{global:fig}}
+\end{figure}
+
+For each of the five filters, the 68\% intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma = \sqrt{C_{c,ii}}$
+(and other interesting derived parameters)
+are given in Table~\ref{global:tab}.
+The two dimensional contours for the parameters, grouped by filter, are shown in Figure~\ref{global:fig}.
 
@@
 &
-$   0.0^{   0.0}_{   0.0}$
+0
 &
@@
 &
-$  0.00^{  0.00}_{  0.00}$
+0
 &
@@
 $ -0.57^{  0.51}_{ -0.59}$
+\\
+$\frac{\gamma_X}{\gamma_2}-1$
+&
+$  0.64^{  0.05}_{ -0.05}$
+&
+$  0.34^{  0.03}_{ -0.03}$
+&
+0
+&
+$ -0.23^{  0.01}_{ -0.01}$
+&
+$ -0.45^{  0.03}_{ -0.03}$
 \\
@@
 $  1.64^{  0.21}_{ -0.19}$
+\\
+$\frac{\delta_X}{\delta_2}-1$
+&
+$-0.393^{ 0.182}_{-0.208}$
+&
+$-0.224^{ 0.101}_{-0.117}$
+&
+0
+&
+$-0.056^{ 0.051}_{-0.046}$
+&
+$-0.147^{ 0.096}_{-0.089}$
 \\
@@
 
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.5in]{output11/coeff0.pdf} 
-   \includegraphics[width=2.5in]{output11/coeff1.pdf} 
-   \includegraphics[width=2.5in]{output11/coeff2.pdf} 
-      \includegraphics[width=2.5in]{output11/coeff3.pdf} 
-         \includegraphics[width=2.5in]{output11/coeff4.pdf} 
-            \caption{Distributions for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.   \label{global:fig}}
-
-\end{figure}
-
-We find a small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
-magnitudes.  All bands show larger and significant non-zero values for $\beta$.  This confirms the part of our hypothesis that spectral indicators
+We find small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
+magnitudes.  All bands show larger and significant non-zero values for $\beta$, indicating the importance of
+$EW_{Si}$.  This confirms the part of our hypothesis that spectral indicators
 are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ are consistent with zero within one sigma.
-The effect in color can be seen in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$.
-Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically, while
-$v_{Si}$ does not have a significant affect on colors.
+How spectral features affect color can be seen in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$.
+Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically.
+We do not detect a significant association between
+$v_{Si}$ and color.
 
 The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Figure~\ref{ccm:fig}
-shows the expectation of CCM dust, plotted together with our measurements of
-$R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the central wavelength of the synthetic bands.
-the $R_X$ are consistent with the  $R_V=3.1$ CCM model (assuming we are using
-SNf synthetic magnitudes).  The uncertainties in the 5 measurements
+shows the expectation of the \citet{1999PASP..111...63F} dust model through its parameter $R^F_V$, plotted together with our measurements of
+$R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the effective wavelength of the supernova flux that passes
+through the synthetic bands.
+The $R_X$ are consistent with an  $R_V=2.5$.  The uncertainties in the 5 measurements
 of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
-uncertainties and are also consistent with $R_V=3.1$.
+uncertainties and are consistent with $R_V=2.5$.
 
@@
       \includegraphics[width=2.8in]{output11/ccm2.pdf} 
-   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
-   predictions for these parameters are overlaid for different values of $R_V$.
+   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right). \citet{1999PASP..111...63F} dust
+   predictions for these parameters are overlaid for different values of the dust-parameter $R^F_V$.
    \label{ccm:fig}}
@@
 The best-fit distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
-Although the posteriors of $\delta$ are fairly circular, $\delta_1-\delta_2$ can get close to zero, resulting in the
+Although the posteriors of $\delta$ are fairly circular, $\delta_1-\delta_2$ can approach zero, resulting in the
 elongated tail in negative  $R_{\delta X}$.
-All values are inconsistent with zero and negative: a color excess in $B-V$ produces a brightening of the supernova.
-The smallest (most negative) value is $R_{\delta V}$  with  values increasing in both bluer and redder directions; a consequence
+All values are negative and inconsistent with zero: a color excess in $B-V$ produces a brightening of the supernova.
+The values of $\delta_X/\delta_V-1$ are not monotonic with color: they increase from the $U$ to $V$, and then decrease
+from $V$ to $I$,
+a consequence
 of which is that
@@
 extreme colors can thus be attributed to the external source. 
-Both distributions are non-Gaussian extended tails in the red.
+Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
    \includegraphics[width=3.2in]{output11/ebv.pdf}
-   \caption{Histograms of $E(B-V) =(\gamma_1-\gamma_2)k$ and
-   $E_\delta(B-V) = (\delta_1-\delta_2)D$.
+   \caption{Histograms of the contributions to color excess from external $E(B-V) =(\gamma_1-\gamma_2)k$ and
+   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$ effects for the supernovae in our sample.
    \label{ebv:fig}}
@@
 \end{equation}
-The distribution for $R_{V,eff}$ is shown in Figure~\ref{rveff:fig}
+The distribution for $R_{V,eff}$ for the supernovae in our sample is shown in Figure~\ref{rveff:fig}
+and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
+Rerunning the posterior calculation with initial conditions for $\gamma$  that correspond to $R_{X,eff}$ reproduced the original results, indicating that
+the effective and true $R$ values are not separated by local posterior extrema.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
    \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}$,
+   for the supernovae in our sample.
    \label{rveff:fig}}
 \end{figure}
-and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
-Rerunning the posterior calculation with initial conditions for $\gamma$  near $R_{X,eff}$ reproduced the original results, indicating that
-the effective and true $R$ values are not separated by local posterior extrema.
-
-Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
-square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
-than the dispersion in $\Delta$.
 
@@
 
- \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/sigma_corner.pdf} 
-   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
-   \label{sigma:fig}}
-\end{figure}
-
 The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
@@
    \label{hist:fig}}
+\end{figure}
+
+Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
+square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
+than the dispersion in $\Delta$.
+
+ \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/sigma_corner.pdf} 
+   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
+   \label{sigma:fig}}
 \end{figure}
@@
 Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
-$EW_{Si}$--$v_{Si}$, which are statistics that describe the same spectral feature.
+$EW_{Si}$--$v_{Si}$, which are statistics both associated with SiII.
 External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
 0.04.  Although $E(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.
+
+\section{SN 2014J}
+\label{sn2014j:sec}
+
+SN~2014J \citep{2014ApJ...788L..21A}  is one of several SNe~Ia that exhibits colors that are inconsistent with low $R_V<2.0$.
+It is spectroscopically normal, having a spectral evolution similar to SN~2011fe (though SN~2014J does show
+overall higher photospheric velocities).  As SN~2011fe suffers low Galactic and host reddening, it serves as a good template
+for the measurement of color excess nulling out the effects of Ca and Si equivalent width.  SN~2014J is not part of the SNfactory
+sample.
+
+We take the color excesses  in $UBRi$  relative to $V$
+of \citet{2014ApJ...788L..21A}, following their prescription of taking the average of data within 5-days of peak $B$ magnitude.
+
+[ 2.55835177 -1.57193957] [[ 0.05797162  0.05911801]
+ [ 0.05911801  0.20369998]]
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/sn2014j.pdf} 
+   \caption{
+   \label{sn2014j:fig}}
+\end{figure}
+
+\section{Conclusions}
+\label{conclusions:sec}
+
+Large $E(B-V)$ does not mean extinction.
+
+\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} $v_{Si}$.
+
+$R^F_V=2.5$.
+
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}  $R_V=1.4$ to $R_V=3$.
+
+Standard candle.
+\acknowledgments
 
@@
 %
+\bibliographystyle{apj}
+\bibliography{/Users/akim/Documents/alex}
+
 \end{document}

### 2016-09-02 sn2014j.py

@@ -44,13 +44,14 @@ g = numpy.array([sum(exv*gammam1/e_exv), sum(exv*deltam1/e_exv)])
 ans = numpy.dot(u,g)
 print ans, u
 
-
+fiterr = numpy.sqrt(gammam1**2 * u[0,0] + 2*deltam1*gammam1*u[0,1] + deltam1**2 * u[1,1])
 
 import sncosmo
 
 
 plt.errorbar(elam,exv,yerr=[e_exv,e_exv],fmt='.',label='SN2014J',color='black')
-plt.scatter(elam, gammam1*ans[0]+deltam1*ans[1],label='Best-fit Model',color='red')
+plt.errorbar(elam, gammam1*ans[0]+deltam1*ans[1],yerr=[fiterr,fiterr],label='Best-fit Model',color='red',fmt='.')
+print  gammam1*ans[0], deltam1*ans[1]
 
 lambdas = numpy.arange(3500.,8000,100)
 rvs=[1.4, 3.1]

### 2016-09-02 table11.py

@@ -1,6 +1,7 @@
 #!/usr/bin/env python
 
 import pickle
+import cPickle
 import numpy
 
 
@@ -31,8 +32,8 @@ dum/= len(fit['L_Omega'])
 # color_cov = numpy.dot(trans,numpy.dot(dum, trans.T))
 print " \\\\\n".join([" & ".join(map('{0:.4f}'.format, line)) for line in dum])
 
-pars = ['alpha','alpha','beta','beta','eta','eta','gamma','rho1','L_sigma']
-pars_n = ['\\alpha_{','{\\alpha ','\\beta_{','{\\beta ','\\eta_{','{\\eta ','R_{','R_{\\delta ','\\sigma_{']
+pars = ['alpha','alpha','beta','beta','eta','eta','gamma','gamma','rho1','rho1','L_sigma']
+pars_n = ['\\alpha_{','{\\alpha ','\\beta_{','{\\beta ','\\eta_{','{\\eta ', '{\\frac{\\gamma}','R_{', '{\\frac{\\delta}','R_{\\delta ','\\sigma_{']
 sigfig = [4,1,3,2,4,2,2,2,3]
 for p,pn, s in zip(pars,pars_n,sigfig):
     print '${}X}}$'.format(pn)
@@ -79,3 +80,60 @@ for p,pn, s in zip(pars,pars_n,sigfig):
         dum = numpy.percentile(fit[p][:,i]/fit[p][:,2]-1,(50,50-34,50+34))            
         print  '${1:6.{0}f}^{{{2:6.{0}f}}}_{{{3:6.{0}f}}}$'.format(s,dum[0], dum[2]-dum[0],dum[1]-dum[0] )
     print '\\\\'
+
+
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+dic_phreno=cPickle.load(open("phrenology_2016_12_01_CABALLOv1.pkl"))
+
+dic_meta=cPickle.load(open("META.pkl"))
+
+sivel=[]
+sivel_err=[]
+for sn in data['snlist']:
+   if sn in dic_meta.keys() and sn in dic_phreno.keys():
+      meta = dic_meta[sn]
+      vSiII_6355_lbd=0.
+      vSiII_6355_lbd_err=0.
+      counter  = 0
+      for sp in dic_phreno[sn]["spectra"]:
[…]

### 2016-09-02 view11.py

@@ -262,14 +262,17 @@ with PdfPages('output11/multipage_pdf.pdf') as pdf:
     #     pdf.savefig()
     #     plt.close()
 
-    # filter wavelengthsr = numpy.log(8635./3276.)
-#edges= 3276.*numpy.exp(numpy.arange(6)*r/5.)
-edges = numpy.array([[3300., 4102], [4102, 5100], [5200, 6289], [6289, 7607], [7607, 9200]])
-efflam = []
-for i in xrange(5):
-    # efflam.append((edges[i+1]-edges[i])/2+edges[i])
-    efflam.append((edges[i][1]-edges[i][0])/2+edges[i][0])
+    # filter wavelengths
+# r = numpy.log(8635./3276.)
+# edges= 3276.*numpy.exp(numpy.arange(6)*r/5.)
+# # edges = numpy.array([[3300., 4102], [4102, 5100], [5200, 6289], [6289, 7607], [7607, 9200]])
+# efflam = []
+# for i in xrange(5):
+#     efflam.append((edges[i+1]-edges[i])/2+edges[i])
+#     # efflam.append((edges[i][1]-edges[i][0])/2+edges[i][0])
 
+#from manu
+efflam = numpy.array([ 3693.16777627,  4369.37505509,  5287.48667023,  6319.19906153,7610.89305298])
 # [3701, 4601, 5744, 6948, 8403]
 rc('text', usetex=True)
 
@@ -281,7 +284,7 @@ nlinks = fit['gamma'].shape[0]
 mega = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['rho1'],fit['L_sigma']])
 mega = numpy.transpose(mega)
 
-rvs = [1.7,3.1,4.1]
+rvs = [1.5,2.5,3.1]
 filts = ['U','B','V','R','I']
 
 
@@ -299,10 +302,18 @@ for index in xrange(5):
 
 lambdas = numpy.arange(3000.,9000,100)
 for rv in rvs:
-    A_ = sncosmo._extinction.ccm89(lambdas, 1., rv)
-    norm  = sncosmo._extinction.ccm89(numpy.array([efflam[1]]), 1., rv)-sncosmo._extinction.ccm89(numpy.array([efflam[2]]), 1., rv)
+
[…]

### 2016-09-03 forgerard.tex
more edits

@@
 supernova SN2014J that has been previously identified as having extreme color properties.
-We finish with conclusions in \S\ref{conclusions:sec}.
+We finish with a discussion of our findings in \S\ref{discussion:sec}.
 
@@
 
-%A representative example is given by the matrix comprised by the average of each element in the Monte Carlo chain.
-%For $UBVRI$ the matrix is
-%\begin{equation}
-%\begin{pmatrix}
-%0.0050 & 0.0026 & 0.0017 & 0.0014 & 0.0009 \\
-%0.0026 & 0.0034 & 0.0032 & 0.0026 & 0.0011 \\
-%0.0017 & 0.0032 & 0.0047 & 0.0041 & 0.0029 \\
-%0.0014 & 0.0026 & 0.0041 & 0.0042 & 0.0035 \\
-%0.0009 & 0.0011 & 0.0029 & 0.0035 & 0.0050
-% \end{pmatrix}.
-% \end{equation}
-% In terms of colors $U-V$, $B-V$, $V-R$, and $V-I$ the covariance is
-%\begin{equation}
-%\begin{pmatrix}
-%0.0064 & 0.0025 & -0.0004 & -0.0010 \\
-%0.0025 & 0.0018 & -0.0000 & 0.0003 \\
-%-0.0004 & -0.0000 & 0.0007 & 0.0011 \\
-%-0.0010 & 0.0003 & 0.0011 & 0.0039
-%  \end{pmatrix}.
-% \end{equation}
-% The $B-V$ and $V-R$ colors have small standard deviations of  0.04 mag and 0.03 mag with no correlation.  The
-% residuals not accounted by the
-% model are stronger in the $U-V$ and $V-I$ bands.
-
 The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
@@
 than the dispersion in $\Delta$.
+The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix: selecting new Cholesky factors baased
+on their distributions generally will not satisfy the condition of representing a correlation matrix.  
+As a representation of a typical posterior draw of $C_c$ we present a matrix that element-by-element
+is the mean of all covariance realizations.
+For $UBVRI$ the matrix is
+\begin{equation}
+\begin{pmatrix}
+0.0037 & 0.0010 & -0.0001 & -0.0001 & 0.0003 \\
+0.0010 & 0.0010 & 0.0002 & -0.0000 & -0.0004 \\
+-0.0001 & 0.0002 & 0.0004 & 0.0001 & -0.0001 \\
+-0.0001 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
+0.0003 & -0.0004 & -0.0001 & 0.0002 & 0.0019
+ \end{pmatrix} \text{mag}^2.
+ \end{equation}
+Similarly the typical color covariance, in terms of colors $U-V$, $B-V$, $V-R$, and $V-I$, can
+be expressed as having standard deviations $(0.066 , 0.033 , 0.022 , 0.050)$ mag with
+ correlations
+ \begin{equation}
+\begin{pmatrix}
+1.000 & 0.634 & -0.256 & -0.300 \\
+0.634 & 1.000 & -0.203 & 0.032 \\
+-0.256 & -0.203 & 1.000 & 0.604 \\
+-0.300 & 0.032 & 0.604 & 1.000
+  \end{pmatrix}.
+ \end{equation}
 
@@
 
-\section{Conclusions}
-\label{conclusions:sec}
-
-Large $E(B-V)$ does not mean extinction.
+\section{Discussion}
+\label{discussion:sec}
+The model favors spectral features as indicating supernova magnitude and color, and the existence of an internal supernova parameter
+that affects colors, in addition to external (dust) colors.
+
+The extrinsic dust gives $R^F_V=2.5$. Intrinsic cannot be associated with dust.
+
+Could affect distance determinations.  Large $E(B-V)$ does not mean extinction.
 
@@
 
-$R^F_V=2.5$.
+Getting $R_V=1.5$ not surprising.
 
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}  $R_V=1.4$ to $R_V=3$.
+
+Room for more color effects.  Dispersion in $R_V$.   With negative and positive correlations can't be explained by dust.
+
+Anti-connection between $EW(Ca)$ and $v_{Si}$.  Intermediate mass
 

### 2016-09-04 forgerard.tex
Keep on going with article

@@
 much smaller than that of diffuse Milky Way dust, though the dispersion is large.
+The also confirm the \citet{2011ApJ...729...55F} finding hat low $R_V$ is associated with high-extinction supernovae.
 The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
@@
 in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.
+For  SiII$\lambda 6355$ the weighted mean from phases within 3 days of maximum light is used.
+(What is done for EW?)
 
@@
 \begin{equation}
-\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 \ge 0, \delta_0\le0.
+\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 > 0, \delta_0 < 0.
 \end{equation}
@@
 $\delta$--$D$ and $\gamma$--$k$.
+Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
+each other,
+as confirmed after recalculation of the posterior with exchange of the initial conditions and boundary conditions of $\delta$ and $\gamma$.
+The $\delta$ and $\gamma$ values of a single run cannot definitively be attributed as being intrinsic or extrinsic; we break the degeneracy
+by assigning the parameter whose values that are more consistent with dust as $\gamma$ and the other parameter as $\delta$.
 
@@
 \\
-$\frac{\gamma_X}{\gamma_2}-1$
+$\gamma_X/\gamma_2-1$
 &
@@
 \\
-$\frac{\delta_X}{\delta_2}-1$
+$\delta_X/\delta_2-1$
 &
@@
 through the synthetic bands.
-The $R_X$ are consistent with an  $R_V=2.5$.  The uncertainties in the 5 measurements
+The $R_X$ are consistent with an  $R^F_V=2.5$.  The uncertainties in the 5 measurements
 of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
-uncertainties and are consistent with $R_V=2.5$.
+uncertainties and are also consistent with $R^F_V=2.5$.
 
@@
 The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
-The range of $B-V$ colors is almost 4 times larger for the external contribution:
+The range of $B-V$ colors is $\sim 4$ times larger for the external contribution:
 extreme colors can thus be attributed to the external source. 
@@
 
-The two separate color effects are conflated into a combined color excess with a single effective extinction behavior
+The two separate color effects are conflated into a combined color excess with a single effective total-to-selective extinction
 \begin{equation}
-R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)R}.
+R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}.
+\label{RVeff:eqn}
 \end{equation}
@@
 and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
-Rerunning the posterior calculation with initial conditions for $\gamma$  that correspond to $R_{X,eff}$ reproduced the original results, indicating that
+Rerunning the posterior calculation with initial conditions for $\gamma$  that correspond to $R_{X,eff}$ 
+and $\delta=0$ (technically $\delta_0 = -\epsilon$ due to the $\delta_0<0$ condition)
+reproduces the original results, indicating that
 the effective and true $R$ values are not separated by local posterior extrema.
@@
 The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
-is given by the standard deviation of $0.096$ mag.  The distribution is non-Gaussian, with a broad tail. 
+is given by the standard deviation of $0.096$ mag.  The distribution is non-Gaussian, with a broad tail in the positive (fainter) direction.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 than the dispersion in $\Delta$.
-The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix: selecting new Cholesky factors baased
-on their distributions generally will not satisfy the condition of representing a correlation matrix.  
-As a representation of a typical posterior draw of $C_c$ we present a matrix that element-by-element
-is the mean of all covariance realizations.
+The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix: assembling
+a new set of Cholesky factors based on the distributions of each individual factor will not generally satisfy the condition of representing a correlation matrix.  
+To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
+chain, element by element.
 For $UBVRI$ the matrix is
@@
 Similarly the typical color covariance, in terms of colors $U-V$, $B-V$, $V-R$, and $V-I$, can
-be expressed as having standard deviations $(0.066 , 0.033 , 0.022 , 0.050)$ mag with
+be expressed as having standard deviations and
  correlations
+ \begin{equation}
+ \begin{pmatrix}
+0.066 , 0.033 , 0.022 , 0.050 
+  \end{pmatrix} \text{mag}
+ \label{color_sd:eqn}
+   \end{equation}
  \begin{equation}
@@
   \end{pmatrix}.
+  \label{color_cor:eqn}
  \end{equation}
@@
 Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
-$\Delta$: the distributions (for all Monte Carlo chain links for all supernovae) are shown in Figure~\ref{perobject:fig}.
-There is a core distribution within the supernova parameter-space, with around ten objects that live on the outskirts of that
-distribution.  Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
+$\Delta$: their distributions for all Monte Carlo chain links for all supernovae, are shown in Figure~\ref{perobject:fig}.
+There is a core concentration in the  parameter-space, with around ten objects occupy its outskirts.
+Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
 heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
-Otherwise the distribution in $EW_{Ca}$--$v_{Si}$ space is the view that
-shows the most outliers.
+Outliers in  $EW_{Ca}$--$v_{Si}$ parameters are also clearly distinguished.
 
@@
 
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are shown in the matrix
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are given in the matrix
 \begin{equation}
@@
 Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
-$EW_{Si}$--$v_{Si}$, which are statistics both associated with SiII.
+$EW_{Si}$--$v_{Si}$.
 External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
@@
 
-SN~2014J \citep{2014ApJ...788L..21A}  is one of several SNe~Ia that exhibits colors that are inconsistent with low $R_V<2.0$.
-It is spectroscopically normal, having a spectral evolution similar to SN~2011fe (though SN~2014J does show
-overall higher photospheric velocities).  As SN~2011fe suffers low Galactic and host reddening, it serves as a good template
-for the measurement of color excess nulling out the effects of Ca and Si equivalent width.  SN~2014J is not part of the SNfactory
-sample.
-
-We take the color excesses  in $UBRi$  relative to $V$
-of \citet{2014ApJ...788L..21A}, following their prescription of taking the average of data within 5-days of peak $B$ magnitude.
-
-[ 2.55835177 -1.57193957] [[ 0.05797162  0.05911801]
- [ 0.05911801  0.20369998]]
+SN~2014J \citep{2014ApJ...788L..21A}  is one of several SNe~Ia that exhibits a low $R_V<2.0$.
+It is spectroscopically normal, having a spectral evolution similar to SN~2011fe.
+As SN~2011fe suffers low Galactic and host reddening, it serves as a good template
+for the measurement of color excess, nulling out the effects of Ca and Si equivalent width.
+SN~2014J does show
+overall higher photospheric velocities than SN~2011fe, but the results in \S\ref{results:sec} show that this is unimportant.
+Note that SN~2014J is not part of the data sample described in \S\ref{data:sec}.
+
+Data of SN~2014J are now analyzed using our model and the training with the SNfactory sample.
+The data are the color excesses  in $UBRi$  relative to $V$ at peak brightness  taken from \citet{2014ApJ...788L..21A}
+following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
+Their values 
+$E^o(U-V) =   2.23 \pm   0.03$,
+$E^o(B-V) =   1.28 \pm   0.04$,
+$E^o(R-V) =  -0.47 \pm   0.03$,
+$E^o(i-V) =  -0.92 \pm   0.03$
+are plotted in Figure~\ref{sn2014j:fig}.
+These data are fit to the model
+\begin{equation}
+E^o(X-V) =  \left(\frac{\gamma_X}{\gamma_2}-1\right)k +  \left(\frac{\delta_X}{\delta_2}-1\right)D,
+\end{equation}
+where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.
 
@@
    \includegraphics[width=3.2in]{output11/sn2014j.pdf} 
-   \caption{
+   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and  \citet{2014ApJ...788L..21A}  
    \label{sn2014j:fig}}
@@
 
+The best-fit parameters for SN~2014J are $k= 2.56$, $ D=-1.57$ with covariance
+\begin{equation}
+\begin{pmatrix}
+0.058 & 0.059 \\
+0.059 & 0.204
+\end{pmatrix}.
+\end{equation}
+The predicted values of observed $E^o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
+overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
+UV through NIR data,
+a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
+is also plotted.  Our model gives significantly smaller deviations from the data.
+
+In our model, the observed color excess is attributed to contributions from extrinsic
+$E(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ origins.
+Among the supernovae in the SNfactory training set, the highest median value for 
+$E(B-V)$ is $  0.33^{  +0.04}_{ -0.04}$ and for $E_\delta(B-V)$ is
+$  0.07^{  +0.03}_{ -0.03}$ 
+(see Figure~\ref{ebv:fig}).
+In both parameters SN~2014J lives well outside the range of supernovae used to train the coefficients of the model.
+
 \section{Discussion}
 \label{discussion:sec}
-The model favors spectral features as indicating supernova magnitude and color, and the existence of an internal supernova parameter
-that affects colors, in addition to external (dust) colors.
-
-The extrinsic dust gives $R^F_V=2.5$. Intrinsic cannot be associated with dust.
+We model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and distinct intrinsic and
+extrinsic color parameters.  Analyzing SNfactory data using the model, we find significant evidence that the above parameters do
+affect supernova magnitudes and colors.  The external color parameter has behavior consistent with $R^F_V=2.5$ \citet{1999PASP..111...63F} dust,
+whereas the internal color parameter is inconsistent with dust or a blackbody.
+
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
+Our model can explain a wide range of effective total-to-selective extinction with a single fixed set of $\gamma$ parameters, consistent
+with $R^F_V=2.5$.  The reality is that a range of dust behaviors is expected; while this cannot accommodated in our model, it could be by
+introducing hierarchical 
+modeling of the $\gamma$ distribution.
+For the moment, we assert that variations in extrinsic dust are limited in
+size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within \ref{color_cor:eqn}.
+
+\citet{2011ApJ...729...55F, 2014ApJ...789...32B, 2015MNRAS.453.3300A} find that supernovae with large $E^o(B-V)$ 
+preferentially exhibit low $R^F_V$.  This is natural in our model, as for a fixed extrinsic dust, $R_{V,eff}$ decreases with increasing $E^o(B-V)$ when
+both are positive.
+
+\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, whereas
+our values of $\eta$ are consistent with zero.  Recall that we find a correlation between $v_{Si}$ and $EW_{Ca}$;
+removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
+non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  predict that a reanalysis of the previous data using equivalent width in place
+of SiII velocity would also show correlations with color.
+
+Anti-connection between $EW(Ca)$ and $v_{Si}$.  Intermediate mass
+
+We find an intrinsic supernova parameter that does not have a monotonic influence on supernova magnitudes as a function
+of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes.  Line opacities
+that operate over broad bands are the most obvious candidate for producing this behavior and so warrant further study.
+
+The model and results presented here
+carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represent Hubble residuals after
+application of the model, and its  $0.096$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
+measurement uncertainties.  It is also subject to overtraining.
+The  analysis of this article was intended to model the color behavior of supernovae in our dataset,
+and is not appropriate for inferring the intrinsic dispersion.  A separate analysis is required to determine how
+well this model can be used to measure supernova distances.
+
+Low correlation coefficient means that the contribution of $E_\delta$ is not systematic, no high $E(B-V)$ bias.
 
 Could affect distance determinations.  Large $E(B-V)$ does not mean extinction.
-
-\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} $v_{Si}$.
-
-Getting $R_V=1.5$ not surprising.
-
-\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}  $R_V=1.4$ to $R_V=3$.
-
-Room for more color effects.  Dispersion in $R_V$.   With negative and positive correlations can't be explained by dust.
-
-Anti-connection between $EW(Ca)$ and $v_{Si}$.  Intermediate mass
 

### 2016-09-04 view11.py

@@ -84,7 +84,7 @@ plt.close()
 
 plt.hist([(fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['k'], (fit['rho1'][:,1]-fit['rho1'][:,2])[:,None]*fit['R']],normed=True,bins=20,
     label=[r'$E(B-V)$',r'$E_\delta(B-V)$'],range=(-0.1,0.4))
-plt.xlabel(r'$E(B-V)$')
+plt.xlabel(r'$E(X-V)$')
 plt.legend()
 pp = PdfPages('output11/ebv.pdf')
 plt.savefig(pp,format='pdf')

### 2016-09-04 forgerard.tex
plowing along

@@
 
-\title{text}
+\title{Evidence for an Intrinsic Color Parameter in Type~Ia Supernovae}
 \author
 {
+    A.~G.~Kim,\altaffilmark{2}
+    G.~Smadja,\altaffilmark{7} 
     G.~Aldering,\altaffilmark{2}
@@
     W.~Hillebrandt,\altaffilmark{16}
-    A.~G.~Kim,\altaffilmark{2}
     M.~Kowalski,\altaffilmark{9,12}
@@
    R.~Scalzo,\altaffilmark{8}
-    G.~Smadja,\altaffilmark{7} 
     C.~Sofiatti,\altaffilmark{2,3} 
-    A.~Stocker,\altaffilmark{1}
     N.~Suzuki,\altaffilmark{2}
@@
 
-\keywords{text}
+\keywords{supernovae: general}
 
 \section{Introduction}
-Type~Ia supernovae (SNe~Ia) form a homogenous set of astronomical objects and as such were recognized as a powerful distance indicator 
+Type~Ia supernovae (SNe~Ia) form a homogenous set of exploding stars and as such were early recognized as a powerful distance indicator 
 and probe of cosmology \citep{1992ARA&A..30..359B}.  After further careful consideration of supernova data, it was recognized
 that SN~Ia light-curve shapes \citep{1984SvA....28..658P, 1993ApJ...413L.105P} and colors \citep{1998A&A...331..815T} exhibit subtle signs of heterogeneity,
-which need to be considered when inferring SN~Ia distances.  Empirical models parameterizing SNe~Ia by their light-curve shape
-and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} to enable distance measurements of cosmological supernovae
-that subsequently were used in the discovery of the accelerating expansion of the Universe \citep{1998AJ....116.1009R,1999ApJ...517..565P}.
-
-The two most commonly used supernova light-curve fitters for cosmological purposes today are SALT2 \citep{2007A&A...466...11G} and MLCS2k2
+which being correlated with absolute magnitude
+need to be considered when inferring distances.  Empirical models parameterizing SNe~Ia by their light-curve shape
+and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} that enabled distance measurements of cosmological supernovae,
+which 
+were subsequently used in the discovery of the accelerating expansion of the Universe \citep{1998AJ....116.1009R,1999ApJ...517..565P}.
+
+The two most commonly used supernova-cosmology light-curve fitters today are SALT2 \citep{2007A&A...466...11G} and MLCS2k2
 \citep{2007ApJ...659..122J}.\footnote{More flexible light-curve fitters
-\citep[e.g.][]{2011AJ....141...19B} are used to study SN~Ia heterogeneity.}
+\citep[e.g.][]{2008ApJ...681..482C, 2011AJ....141...19B} are used to study SN~Ia heterogeneity.}
 They remain two-parameter models, with one parameter characterizing light-curve shape and the other
-supernova color.  SALT2 training extracts color variation empirically from SNe that span a wide range of colors whereas MLCS2k2
-attributes color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation that
-both intrinsic and extrinsic color variation may occur.
-
-There is evidence that supports the expectation that one parameter in insufficient to describe the full range
+supernova color.  The physical cause of the color diversity is viewed differently by the two sets of authors: 
+\citet{2007A&A...466...11G} pragmatically extract color variation empirically from SNe that span a wide range of colors, with no attribution of
+that variation to intrinsic or extrinsic origins;
+\citet{2007ApJ...659..122J}
+attribute changes in color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation that
+both intrinsic and extrinsic color variation can occur independently.
+
+There is evidence that supports the expectation that a single parameter cannot describe the full range
 of supernova color behavior.  One approach to look for color diversity is to find correlations between color and spectral features.
-\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations with differing $B_{max}-V_{max}$ identified by Si velocity.
+\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations distinguished
+by Si velocity with differing $B_{max}-V_{max}$.
 \citet{2015MNRAS.451.1973S}
@@
 Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
-\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find on average values for $R_V \ll 3.1$,
-much smaller than that of diffuse Milky Way dust, though the dispersion is large.
-The also confirm the \citet{2011ApJ...729...55F} finding hat low $R_V$ is associated with high-extinction supernovae.
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find a wide
+range of total-to-selective extinction with average values significantly lower than $R_V = 3.1$,
+the canonical value for diffuse Milky Way dust.
+The also confirm the \citet{2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
 The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
@@
 this parlance our parameters can be re-expressed as the more familiar color excess
-$E(B-V) = (\gamma_1-\gamma_2) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
+$E_\gamma(B-V) = (\gamma_1-\gamma_2) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
 Similarly we introduce for the intrinsic color term $E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.
@@
 
-The distribution of color excess $E(B-V) =(\gamma_1-\gamma_2)k$ and
+The distribution of color excess $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
  $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
@@
    \includegraphics[width=3.2in]{output11/ebv.pdf}
-   \caption{Histograms of the contributions to color excess from external $E(B-V) =(\gamma_1-\gamma_2)k$ and
+   \caption{Histograms of the contributions to color excess from external $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
    internal $E_\delta(B-V) = (\delta_1-\delta_2)D$ effects for the supernovae in our sample.
@@
 
-The two separate color effects are conflated into a combined color excess with a single effective total-to-selective extinction
-\begin{equation}
-R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}.
-\label{RVeff:eqn}
-\end{equation}
-The distribution for $R_{V,eff}$ for the supernovae in our sample is shown in Figure~\ref{rveff:fig}
-and has mean and standard deviation  $R_{V,eff}  = 1.52 \pm 0.24$.  
-Rerunning the posterior calculation with initial conditions for $\gamma$  that correspond to $R_{X,eff}$ 
-and $\delta=0$ (technically $\delta_0 = -\epsilon$ due to the $\delta_0<0$ condition)
-reproduces the original results, indicating that
-the effective and true $R$ values are not separated by local posterior extrema.
+For each supernova, the two separate color effects are conflated into an effective color excess
+$E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
+$A_{B, eff} = \gamma_1 k + \delta_1D$.  These values for the SNf sample
+shown in Figure~\ref{rveff:fig}, overplotted with the expected relationship for color-excess 
+purely due to the extrinsic $\gamma$ term.
+Recall that  $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ respectively were arbitrarily assigned to the average $k$ and $D$ values of our distribution;
+for convenience, we shift the zero of  $E_{eff}(B-V)$ so that the extrinsic dust expectation qualitatively forms a ridge line
+bounding the high-extinction side of the distribution.
+In the right plot of Figure~\ref{rveff:fig}, we show the difference between $E_{eff}(B-V)$ and that ridge line.
+Over all effective color excesses, the inferred $R_B$  is capped by the canonical extrinsic value.
+However, with increasing effective color excess there is a broadening of the distribution toward low inferred $R_B$,
+accompanied by a decrease in average  $R_B$.
+Supernovae with extremely red $E_{eff}(B-V)$ on average have significantly lower inferred $R_V$ that their counterparts with bluer $E_{eff}(B-V)$.
+Conversely, supernovae with extreme
+blue  $E_{eff}(B-V)$ fall slightly but noticeably above the ridge line, which would lead to an inferred $R_B$ slightly
+larger than the extrinsic expectation.
+
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
    \centering
-   \includegraphics[width=3.2in]{output11/rveff.pdf}
-   \caption{The effective dust law of the two color terms combined $R_{V,eff}  = \frac{\gamma_1 k + \delta_1 D}{(\gamma_1-\gamma_2) k + (\delta_1-\delta_2)D}$,
-   for the supernovae in our sample.
+   \includegraphics[width=2.8in]{output11/rveff.pdf}
+   \includegraphics[width=2.8in]{output11/rveffres.pdf}
+   \caption{Left: $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band``extinction''
+$A_{B, eff} = \gamma_1 k + \delta_1D$ for the SNf sample.  Overplotted is the expected relationship for color-excess
+purely due to the intrinsic $\gamma$ term.  we shift the zero of  $E_{eff}(B-V)$  so that the  the extrinsic dust expectation qualitatively forms a ridge line
+bounding the high-extinction side of the distribution.
+Right: The difference between $E_{eff}(B-V)$ and that ridge line.
    \label{rveff:fig}}
@@
 
-Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
+Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
 $\Delta$: their distributions for all Monte Carlo chain links for all supernovae, are shown in Figure~\ref{perobject:fig}.
 There is a core concentration in the  parameter-space, with around ten objects occupy its outskirts.
-Many outliers appear in the red tail of $E(B-V)$, as would be expected in the infrequent selection of supernovae
+Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected in the infrequent selection of supernovae
 heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
@@
    \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
-   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
+   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
 $\Delta$.
@@
 
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E(B-V)$, and $E_\delta(B-V)$ are given in the matrix
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$ are given in the matrix
 \begin{equation}
@@
 $EW_{Si}$--$v_{Si}$.
-External $E(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
-0.04.  Although $E(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.
+External $E_\gamma(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
+0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.
 
@@
 In our model, the observed color excess is attributed to contributions from extrinsic
-$E(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ origins.
+$E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ origins.
 Among the supernovae in the SNfactory training set, the highest median value for 
-$E(B-V)$ is $  0.33^{  +0.04}_{ -0.04}$ and for $E_\delta(B-V)$ is
+$E_\gamma(B-V)$ is $  0.33^{  +0.04}_{ -0.04}$ and for $E_\delta(B-V)$ is
 $  0.07^{  +0.03}_{ -0.03}$ 
@@
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
-Our model can explain a wide range of effective total-to-selective extinction with a single fixed set of $\gamma$ parameters, consistent
-with $R^F_V=2.5$.  The reality is that a range of dust behaviors is expected; while this cannot accommodated in our model, it could be by
-introducing hierarchical 
-modeling of the $\gamma$ distribution.
-For the moment, we assert that variations in extrinsic dust are limited in
-size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within \ref{color_cor:eqn}.
-
-\citet{2011ApJ...729...55F, 2014ApJ...789...32B, 2015MNRAS.453.3300A} find that supernovae with large $E^o(B-V)$ 
-preferentially exhibit low $R^F_V$.  This is natural in our model, as for a fixed extrinsic dust, $R_{V,eff}$ decreases with increasing $E^o(B-V)$ when
-both are positive.
+\citet{2011ApJ...729...55F} and the above authors
+find that supernovae with large $E^o(B-V)$ 
+preferentially exhibit low $R^F_V$. 
+Our model predicts both of these effects with a single set of extrinsic dust parameters, as is borne out by the
+SNf sample as shown in Figure~\ref{rveff:fig}. 
+Our model also predicts that the converse also holds: supernovae with the smallest $E^o(B-V)$ due to intrinsic color
+will appear overly faint when analyzed within the context of a canonical dust.
+The trend in Figure~\ref{rveff:fig} showing an increased range of brighter-than-expected magnitudes  with increasing $E_{eff}(B-V)$  can
+be compared
+to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of color from \citet{2014A&A...568A..22B}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/betoule.pdf} 
+   \caption{Best-fit SN~Ia  $B$-band Hubble residuals as a function of the best-fit color parameter $C$ from the cosmology analysis of \citet{2014A&A...568A..22B}.
+   \label{betoule:fig}}
+\end{figure}
 
@@
 removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
-non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  predict that a reanalysis of the previous data using equivalent width in place
-of SiII velocity would also show correlations with color.
-
-Anti-connection between $EW(Ca)$ and $v_{Si}$.  Intermediate mass
+non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  anticipate that for the in the previous analysis, equivalent widths of $CaII$ and
+$SiII$ would also have shown correlations with color.
 
@@
 measurement uncertainties.  It is also subject to overtraining.
-The  analysis of this article was intended to model the color behavior of supernovae in our dataset,
-and is not appropriate for inferring the intrinsic dispersion.  A separate analysis is required to determine how
+The  analysis of this article was intended to model the color behavior of supernovae in our dataset.
+A separate analysis is required to determine how
 well this model can be used to measure supernova distances.
-
-Low correlation coefficient means that the contribution of $E_\delta$ is not systematic, no high $E(B-V)$ bias.
-
-Could affect distance determinations.  Large $E(B-V)$ does not mean extinction.
-
-Standard candle.
+We wait for this analysis to explore correlations between Hubble residuals, host-galaxy parameters (e.g.\ mass,
+local star formation rate) and the intrinsic $D$ parameter.
+
+The model introduced in this article is limited, in that it doesn't accommodate the expected diversity
+in extrinsic dust properties that supernovae in different hosts may encounter.  Extending our model to 
+include  a parameterized  $\gamma$ distribution would consider a range of host-dust behavior, and
+is a direction of further study.
+For the moment, we assert that variations in extrinsic dust are limited in
+size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within Eqn.~\ref{color_cor:eqn}.
+
 \acknowledgments

### 2016-09-04 view11.py

@@ -12,21 +12,21 @@ import sncosmo
 f = open('temp11.pkl','rb')
 (fit,_) = pickle.load(f)
 
-for key in fit.keys():
-    print key, fit[key].min(), fit[key].max()
+# for key in fit.keys():
+#     print key, fit[key].min(), fit[key].max()
 
-pkl_file = open('gege_data.pkl', 'r')
-data = pickle.load(pkl_file)
-pkl_file.close()
+# pkl_file = open('gege_data.pkl', 'r')
+# data = pickle.load(pkl_file)
+# pkl_file.close()
 
-EW_obs = data['obs'][:,0:2]
-mag_obs = data['obs'][:,2:]
-EW_cov = data['cov'][:,0:2,0:2]
-mag_cov = data['cov'][:,2:,2:]
+# EW_obs = data['obs'][:,0:2]
+# mag_obs = data['obs'][:,2:]
+# EW_cov = data['cov'][:,0:2,0:2]
+# mag_cov = data['cov'][:,2:,2:]
 
-# # renormalize the data
-EW_mn = EW_obs.mean(axis=0)
-EW_renorm = (EW_obs - EW_mn)
+# # # renormalize the data
+# EW_mn = EW_obs.mean(axis=0)
+# EW_renorm = (EW_obs - EW_mn)
 
 # dum = numpy.zeros((5,5))
 # for x1, x2 in zip(fit['L_Omega'], fit['L_sigma']):
@@ -40,14 +40,14 @@ EW_renorm = (EW_obs - EW_mn)
 # color_cov = numpy.dot(trans,numpy.dot(dum, trans.T))
 # print " \\\\\n".join([" & ".join(map('{0:.4f}'.format, line)) for line in color_cov])
 
-correction = [ fit['alpha'][:,i][:,None]*fit['EW'][:,:, 0] \
-    + fit['beta'][:,i][:,None]*fit['EW'][:,:, 1] \
-    + fit['gamma'][:,i][:,None]*fit['k'] \
-    + fit['Delta'] \
-    for i in xrange(5)]
+# correction = [ fit['alpha'][:,i][:,None]*fit['EW'][:,:, 0] \
+#     + fit['beta'][:,i][:,None]*fit['EW'][:,:, 1] \
+#     + fit['gamma'][:,i][:,None]*fit['k'] \
[…]

### 2016-09-05 forgerard.tex
continuing to write

@@
 The also confirm the \citet{2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
-The above evidence has lead to the hypothesis that multiple scattering from circumstellar dust
-plays a role in observed supernova colors \citep{2005ApJ...635L..33W, 2008ApJ...686L.103G}.
 In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
-the standard $R_V=3.1$ is recovered.
-
-In this article we use the idea that spectral indicators carry information on intrinsic supernova colors,
-and allow for the possibility of there being two further color parameters, one intrinsic and the other
-extrinsic.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
+the standard $R_V=3.1$ is recovered for supernovae on average.
+
+The Nearby Supernova Factory \citep[SNfactory;][]{2004SPIE.5249..146L} has collected  
+spectrophotometric time series of $z<0.08$ SNe~Ia.   The $3200$--$10000$~\AA\ spectral coverage
+provides measurements of an array of supernova spectral features while also providing synthetic broadband photometry
+spanning near-UV to near-IR SN-frame wavelengths, while over a hundred the supernovae have temporal coverage over
+peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia properties.
+
+In this article we use the idea that spectral indicators carry information on intrinsic supernova colors at peak magnitude.
+We allow for two independent color parameters, one due to intrinsic supernova
+properties and the other due to
+extrinsic processes.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
 \S\ref{model:sec} and results are given in \S\ref{results:sec}.  In \S\ref{sn2014j:sec} our results are applied to the out-of-sample
-supernova SN2014J that has been previously identified as having extreme color properties.
-We finish with a discussion of our findings in \S\ref{discussion:sec}.
+supernova SN2014J that has been previously identified as having extreme total-to-selective extinction behavior.
+We conclude with a discussion of our findings in \S\ref{discussion:sec}.
 
@@
 
-The spectral time-series used are corrected for Milky Way dust
+The spectral time-series  are corrected for Milky Way dust
 extinction \citep{1989ApJ...345..245C,1998ApJ...500..525S} but not for the
-effects of circumstellar or host galaxy dust extinction.  
+effects of circumstellar or host-galaxy dust extinction.  
 Each spectral time series is
-blue-shifted to rest-frame, and the fluxes normalized to represent that
-observed at a common distance for all supernovae --- thus, ratios
-in flux between supernovae can be interpreted as ratios in
-luminosity or equivalently differences in absolute magnitude.
+blue-shifted to rest-frame, and the fluxes converted to luminosity assuming
+distances expected for the supernova redshifts given [which cosmological parameters?].
 
@@
 in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.
-For  SiII$\lambda 6355$ the weighted mean from phases within 3 days of maximum light is used.
-(What is done for EW?)
-
-There are 163 supernovae that have spectroscopic data within three days of peak brightness:
-these constitute our analysis sample.  The data are given in Table~\ref{data:tab}.
+The weighted mean from phases within 3 days of maximum light is used for SiII$\lambda 6355$.
+[What is done for EW?]
+
+The 163 supernovae that have the photometric and spectroscopic statistics described above
+constitute our analysis sample.  The data are given in Table~\ref{data:tab}.
 The peak magnitude uncertainties do have covariance, which are accounted
@@
 We hypothesize that at peak brightness
-Type Ia supernova broadband magnitudes and colors are correlated with
-spectral features; equivalent widths and line velocities, being insensitive to broadband color effects, are considered.
+SN~Ia broadband magnitudes and colors are correlated with
+spectral features: equivalent widths and line velocities, being insensitive to broadband color effects, are considered.
 Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
-of intrinsic variation is allowed.
+of intrinsic variation is accommodated.
 The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some dispersion.
@@
 We assume 
-that  intrinsic $UBVRI$ magnitudes are linearly dependent
-on the equivalent widths of the Ca and Si spectral features
+that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
+on the equivalent widths of the CaII H\&K and SiII$\lambda$ 4141 spectral features
 $EW_{Ca}$, $EW_{Si}$,
 the SiII$\lambda6355$ velocity $v_{Si}$:
-these spectral features have been previously associated with SN~Ia diversity  
+these spectral features are associated with SN~Ia  spectroscopic diversity  
 \citep{2006PASP..118..560B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F,2009A&A...500L..17B}.
-Note that $EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
+$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
 \citep{2011A&A...529L...4C}. 
-A color-variation parameter $D$ describes further magnitude/color variation unaccounted for by the spectral features.
+An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
 Residual dispersion is described by a Normal distribution with (unknown) covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
@@
 The observed magnitudes are linearly dependent on an
-extrinsic color-variation parameter $k$  parameter.  The observables
-$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian measurement uncertainty with covariance $C$; these have
-been presented in \S\ref{data:sec}.
+extrinsic-color parameter $k$.  The observables
+$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian measurement uncertainty with covariance $C$,
+shown in Table~\ref{data:tab}.
 The model is written as
@@
 \end{equation}
-The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships between the spectral
-features and intrinsic colors (encoded in $D$),  with intrinsic magnitudes.  The global parameters $\gamma$ are the slopes that connect the extrinsic colors
-(encoded in $k$) and observed magnitude.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
+The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
+relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.  The global parameters $\gamma$ are the slopes that connect the extrinsic-color
+parameter and observed magnitude.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
 \begin{equation}
@@
 \end{equation}
-The first two are imposed to constrain the definition of zero color (i.e. $E(B-V)=0$).    The latter two exclude degenerate posterior space
+The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
 associated
@@
 each other,
-as confirmed after recalculation of the posterior with exchange of the initial conditions and boundary conditions of $\delta$ and $\gamma$.
-The $\delta$ and $\gamma$ values of a single run cannot definitively be attributed as being intrinsic or extrinsic; we break the degeneracy
-by assigning the parameter whose values that are more consistent with dust as $\gamma$ and the other parameter as $\delta$.
+as confirmed by recalculation of the posterior after exchange of the initial conditions and boundary conditions of $\delta$ and $\gamma$.
+We break the degeneracy
+by assigning the parameters whose values are consistent with dust to $\gamma$ and the other parameters to $\delta$.
 
@@
 In the right plot of Figure~\ref{rveff:fig}, we show the difference between $E_{eff}(B-V)$ and that ridge line.
+The Pearson correlation between color excess and extinction excess is -0.26.
 Over all effective color excesses, the inferred $R_B$  is capped by the canonical extrinsic value.
@@
 
-SN~2014J \citep{2014ApJ...788L..21A}  is one of several SNe~Ia that exhibits a low $R_V<2.0$.
+SN~2014J   is one of several SNe~Ia that exhibits a low $R_V<2.0$.
+The colors of this supernova can be studied by comparison with similar unreddened objects
+\citep[e.g.][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
 It is spectroscopically normal, having a spectral evolution similar to SN~2011fe.
@@
 overall higher photospheric velocities than SN~2011fe, but the results in \S\ref{results:sec} show that this is unimportant.
-Note that SN~2014J is not part of the data sample described in \S\ref{data:sec}.
 
@@
 be compared
-to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of color from \citet{2014A&A...568A..22B}.
+to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of the color $C$ parameter from \citet{2014A&A...568A..22B}:
+the Pearson correlation coefficient between the two variables is $-0.33$.
 
@@
 removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
-non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  anticipate that for the in the previous analysis, equivalent widths of $CaII$ and
-$SiII$ would also have shown correlations with color.
+non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  anticipate that for the in the previous analysis, equivalent widths of CaII and
+SiII would also have shown correlations with color.
 
@@
 
-%
-%To illustrate how the linear model reduces the dispersion in observed absolute magnitude, plot the observed colors as a
-%function of the observed  $EW_{Ca, o}$, $EW_{Si,o}$ and $B_o-V_o$ in Fig.~\ref{magresidual:fig}.  Overplotted are lines with the
-%best-fit slope.  The data in the color magnitude diagram indicate that the slope at bluer colors is different from that at redder colors
-%and that our one-color linear model could be improved upon.
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output7/speccamag.pdf} 
-%      \includegraphics[width=2.8in]{output7/specsimag.pdf} 
-%   \includegraphics[width=2.8in]{output7/colormag.pdf} 
-%   \caption{Observed $UBVRI$ as a function of observed   $EW_{Ca, o}$ (top left), $EW_{Si,o}$ (top right) and $B_o-V_o$ (bottom).
-%   Overplotted are lines with the best-fit slope from the model fit.}
-%   \label{magresidual:fig}
-%\end{figure}
-%
-%\subsubsection{Notes}
-%Some equivalent widths go positive.  Is this an emission?
-%
-%
-%\subsection{One Dust With Si Velocity}
-%\label{onecolor_si:sec}
-%Sil$\lambda3655$ velocity is spectral indicator that has been identified to correlated with peak brightness.  The analysis is expanded to include
-%this line. We use the weighted mean of all spectral measurements within 3 days of peak brightness.  A handful of supernovae do not have a
-%spectrum that close to peak.
-%\subsubsection{Setup}
-%With the inclusion of SiII$\lambda3655$ velocity  $v_{Si}$ the model looks like
-%\begin{equation}
-%\left(
-%\begin{matrix}
-%U\\B\\V\\R\\I
-%\end{matrix}
-%\right) \sim \mathcal{N}
-%\left(
-%\Delta +
-%\left(
-%\begin{matrix}
-%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si}\\
-%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} \\
-%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si}\\
-%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si}\\
-%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si}
-%\end{matrix}
-%\right)
-%,C_{c}
-%\right)
-%\label{ewsiv:eqn}
-%\end{equation}
-%\begin{equation}
-%\left(
-%\begin{matrix}
-%U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}\end{matrix}
-%\right) \sim \mathcal{N}
-%\left(
-%\left(
-%\begin{matrix}
-%U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
-%EW_{Si}\\ EW_{Ca} \\ v_{Si}
-%\end{matrix}
-%\right)
-%,C
-%\right).
-%\label{dust:eqn}
-%\end{equation}
-%The global parameters $\eta$ are the slopes of the linear relationships between Si velocity
-%and intrinsic magnitudes. 
-%
-%\subsubsection{Results}
-%The 68\% intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{globalvsi:tab}.
-%The two dimensional contours for the parameters of each filter are shown in Figure~\ref{globalvsi:fig}.  
-%All bands show large and significant non-zero values for $\eta$ with some non-trivial changes to $\beta$ and a lowering
-%if $\sigma$.  The values
-%of $\alpha$ are unchanged.
-%
-%\begin{table}
-%\centering
-%\begin{tabular}{|c|c|c|c|c|c|}
-%\hline
-%& $X=0$ &1&2&3&4\\ \hline
-%$\alpha_X$
-%&
-%$0.0031^{0.0009}_{-0.0009}$
-%&
-%$0.0005^{0.0008}_{-0.0007}$
-%&
-%$0.0006^{0.0006}_{-0.0006}$
-%&
-%$0.0008^{0.0005}_{-0.0005}$
-%&
-%$0.0020^{0.0005}_{-0.0004}$
-%\\
-%$\beta_X$
-%&
-%$0.0375^{0.0030}_{-0.0030}$
-%&
-%$0.0303^{0.0026}_{-0.0025}$
-%&
-%$0.0298^{0.0023}_{-0.0021}$
-%&
-%$0.0243^{0.0020}_{-0.0019}$
-%&
-%$0.0224^{0.0017}_{-0.0017}$
-%\\
-%$\eta_X$
-%&
-%$0.0032^{0.0011}_{-0.0011}$
-%&
-%$0.0024^{0.0009}_{-0.0009}$
-%&
-%$0.0022^{0.0008}_{-0.0008}$
-%&
-%$0.0019^{0.0007}_{-0.0007}$
-%&
-%$0.0011^{0.0006}_{-0.0006}$
-%\\
-%$R_X$
-%&
-%$5.1004^{0.2929}_{-0.2517}$
-%&
-%$4.1677^{0.2656}_{-0.2272}$
-%&
-%$3.1677^{0.2656}_{-0.2272}$
-%&
-%$2.4828^{0.2327}_{-0.1964}$
-%&
-%$1.8320^{0.2050}_{-0.1838}$
-%\\
-%$\sigma_X$
-%&
-%$0.0537^{0.0162}_{-0.0185}$
-%&
-%$0.0405^{0.0107}_{-0.0131}$
-%&
-%$0.0565^{0.0093}_{-0.0109}$
-%&
-%$0.0538^{0.0084}_{-0.0084}$
-%&
-%$0.0636^{0.0076}_{-0.0079}$
-%\\
-%\hline
-%\end{tabular}
-%\caption{68\% Intervals for Global Fit Parameters for the One-Dust Model with $v_{Si}$  \label{globalvsi:tab}}
-%\end{table}
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.5in]{output10/coeff0.pdf} 
-%   \includegraphics[width=2.5in]{output10/coeff1.pdf} 
-%   \includegraphics[width=2.5in]{output10/coeff2.pdf} 
-%      \includegraphics[width=2.5in]{output10/coeff3.pdf} 
-%         \includegraphics[width=2.5in]{output10/coeff4.pdf} 
-%            \caption{Distributions for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, and $\sigma$ in each of the 5 bands.}
-%   \label{globalvsi:fig}
-%\end{figure}
-%
-%
-%
-%The best-fit distribution for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rxsiv:fig}.  Our measurement of
-%$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
-%our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=3in]{output10/gamma_corner.pdf} 
-%   \caption{Best-fit distribution for the   $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$.
-%   \label{rxsiv:fig}}
-%\end{figure}
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output10/ccm.pdf}
-%      \includegraphics[width=2.8in]{output10/ccm2.pdf} 
-%   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
-%   predictions for these parameters are overlaid for different values of $R_V$.}
-%   \label{ccmsiv:fig}
-%\end{figure}
-%
-% \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.4in]{output10/sigma_corner.pdf} 
-%   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.}
-%   \label{sigmasiv:fig}
-%\end{figure}
-%
-%The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{histsiv:fig}.  The intrinsic dispersion
-%is given by the standard deviation of $0.09$ mag.  The distribution is non-Gaussian, with a broad tail. 
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output10/Delta_hist.pdf} 
-%   \includegraphics[width=2.8in]{output10/k_hist.pdf} 
-%   \caption{Ideograms for Left: the grey offset $\Delta$; Right: the color term $k$ for all supernovae.}
-%   \label{histsiv:fig}
-%\end{figure}
-%
-%\subsection{Two Dust}
-%
-%Motivated by the consistency of the external extinction with CCV $R_V=3.1$ dust, and the hint of the color-magnitude
-%diagrams in Figure~\ref{magresidual:fig}  not following single slopes, we develop a new model in which
-%each supernova encounters one of two sources of external extinction.
-%
-%\subsubsection{Setup}
-%The model is identical to that of \S\ref{onecolor:sec} except with the addition of an alternative extrinsic source of extinction.
-%The intrinsic magnitudes of the supernova are determined by the spectral properties expressed as Eqn.~\ref{ew:eqn}.
-%One extrinsic source of extinction  (Dust 1) is modeled as before with Eqn.~\ref{dust:eqn};
-%the second source of extinction (Dust 2)
-%is modeled similarly but with the introduction of new parameters $\gamma_{2X}$
-%\begin{equation}
-%\left(
-%\begin{matrix}
-%U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
-%\right) \sim \mathcal{N}
-%\left(
-%\left(
-%\begin{matrix}
-%U +\gamma_{20} k \\B +\gamma_{21} k \\V+\gamma_{22} k\\R+\gamma_{23} k\\I+\gamma_{24} k\\
-%EW_{Si}\\ EW_{Ca}
-%\end{matrix}
-%\right)
-%,C
-%\right).
-%\label{dust2:eqn}
-%\end{equation}
-%The probability that a supernova experiences  Dust 1 is given by the free parameter $p_0$,
-%the probability of Dust 2 is $1-p_0$.  
-%The same $k$ parameters are used to describe supernovae in both extinction sources.  In order to do this we change
-%some of the conditions that constrain the degeneracies of the model:
-%\begin{equation*}
-%\langle \Delta \rangle=0, \gamma_1 = 1+\gamma_2, \gamma_{21}=1+\gamma_{22}.
-%\end{equation*}
-%These conditions are useful for interpreting the extinction as being due to dust, as $R_X = \gamma_X$,
-%the color excess $E(B-V) \equiv (\gamma_1-\gamma_2)k =k$.
-%The $c$ parameters  are fit such that both extinction models
-%revert to the same intrinsic magnitudes for $k=0$: the $\langle k \rangle=0$ condition is removed. 
-%
-%To alleviate the degeneracies inherent to mixture models, we restrict the range of $\alpha$, $\beta$, and $\gamma$ (the parameters for Dust 1)
-%to be in the neighborhood of the pdf's of \S\ref{onecolor:sec}.  The one-dust model is embedded in the two-dust model when $p_0=1$.
-%We therefore do not claim to find the global optimum of the parameter
-%pdf, but we can conclude whether the two-dust model is preferred over the one-dust model.
-%The intrinsic covariance $C_c$ is taken to be diagonal.
-%
-%\subsubsection{Results}
-%
-%The probability of an object experiencing the first dust is   $p_0=0.3334^{0.0532}_{-0.0721}$,
-%with the pdf shown in Figure~\ref{prob0:fig}.
-%A single dust with properties centered around the one-dust parameter optimum is not only disfavored, but is most likely the
-%minority component.  
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=3.3in]{output9/prob0.pdf}
-%   \caption{pdf of $p_0$, the probability that a supernova experiences Dust 1.  \label{prob0:fig}}
-%\end{figure}
-%
-%
-%The 68\% intervals for the global parameters $\alpha$, $\beta$, $R$, $R_2$ and $\sigma = \sqrt{C_{c,ii}}$  are given in Table~\ref{global2:tab}.
-%The two dimensional contours for the parameters of each filter are shown in Figure~\ref{global2:fig}.  
-%\begin{table}
-%\centering
-%\begin{tabular}{|c|c|c|c|c|c|}
-%\hline
-%& $X=0$ &1&2&3&4\\ \hline
-%$\alpha_{X}$
-%&
-%$0.0077^{0.0014}_{-0.0018}$
-%&
-%$0.0040^{0.0011}_{-0.0013}$
-%&
-%$0.0025^{0.0008}_{-0.0008}$
-%&
-%$0.0020^{0.0006}_{-0.0007}$
-%&
-%$0.0027^{0.0006}_{-0.0006}$
-%\\
-%$\beta_{X}$
-%&
-%$0.0276^{0.0048}_{-0.0053}$
-%&
-%$0.0225^{0.0037}_{-0.0042}$
-%&
-%$0.0249^{0.0025}_{-0.0026}$
-%&
-%$0.0213^{0.0019}_{-0.0020}$
-%&
-%$0.0216^{0.0015}_{-0.0016}$
-%\\
-%$R_{X}$
-%&
-%$5.0878^{0.4233}_{-0.4082}$
-%&
-%$4.3163^{0.3615}_{-0.3327}$
-%&
-%$3.3163^{0.3615}_{-0.3327}$
-%&
-%$2.6600^{0.2685}_{-0.2691}$
-%&
-%$1.9355^{0.2604}_{-0.2474}$
-%\\
-%$R_{2X}$
-%&
-%$2.2199^{0.2110}_{-0.2301}$
-%&
-%$1.5919^{0.1801}_{-0.2246}$
-%&
-%$0.5919^{0.1801}_{-0.2246}$
-%&
-%$0.2486^{0.1650}_{-0.1788}$
-%&
-%$-0.1484^{0.1802}_{-0.1472}$
-%\\
-%$\sigma_{X}$
-%&
-%$0.0570^{0.0042}_{-0.0040}$
-%&
-%$0.0103^{0.0059}_{-0.0048}$
-%&
-%$0.0229^{0.0021}_{-0.0018}$
-%&
-%$0.0094^{0.0031}_{-0.0039}$
-%&
-%$0.0418^{0.0031}_{-0.0030}$
-%\\
-%\hline
-%\end{tabular}
-%\caption{68\% Intervals for Global Fit Parameters for the Two-Dust Model \label{global2:tab}}
-%\end{table}
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.5in]{output9/coeff0.pdf} 
-%   \includegraphics[width=2.5in]{output9/coeff1.pdf} 
-%   \includegraphics[width=2.5in]{output9/coeff2.pdf} 
-%      \includegraphics[width=2.5in]{output9/coeff3.pdf} 
-%         \includegraphics[width=2.5in]{output9/coeff4.pdf} 
-%            \caption{Distributions for $c$, $\alpha$, $\beta$, $\gamma$, $\gamma_2$, and $\sigma$ in each of the 5 bands.}
-%   \label{global2:fig}
-%\end{figure}
-%
-%Our determinations of $R$ and $R_2$ are compared to the expectations of CCM dust in Figure~\ref{ccm2:fig}.
-%Within the context of this model there are two distinct types of dust: Dust 1 behaves similarly to $R_V=3.1$ CCM dust.
-%In contrast, Dust 2 is more consistent with extremely low values of $R_V$.  Negative values of $R_V$ are unphysical.
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output9/ccm.pdf}
-%      \includegraphics[width=2.8in]{output9/ccm2.pdf} 
-%         \includegraphics[width=2.8in]{output9/ccm12.pdf}
-%      \includegraphics[width=2.8in]{output9/ccm22.pdf} 
-%   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right)
-%   for Dust 1 (top row) and Dust 2 (bottom row).  CCM
-%   predictions for these parameters are overlaid for different values of $R_V$.}
-%   \label{ccm2:fig}
-%\end{figure}
-%
-%While the values for $\beta$ are consistent between the one- and two-dust models, the $\alpha$ values change significantly.
-%This implies a correlation between $EW_{Ca}$ and the dust environment.
-%
 \bibliographystyle{apj}

### 2016-09-06 forgerard.tex
more writing

@@
 description of host-galaxy subtraction is given in \citet{2011MNRAS.418..258B}.
+A recent description of the current status of the data is given in \citet{2015ApJ...815...58F}.
 
@@
 blue-shifted to rest-frame, and the fluxes converted to luminosity assuming
-distances expected for the supernova redshifts given [which cosmological parameters?].
+distances expected for the supernova redshifts given a flat
+$\Lambda$CDM cosmology with $\Omega_M = 0.28$ (but with an arbitrarily selected
+$H_0$ since we are interested in relative magnitudes).
 
@@
 in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.
+Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
+closest to maximum is used \citep{chotard:thesis}. [This is what Nico did in his thesis, is this true of the data Manu gave me?]
 The weighted mean from phases within 3 days of maximum light is used for SiII$\lambda 6355$.
-[What is done for EW?]
 
@@
 The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
-relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.  The global parameters $\gamma$ are the slopes that connect the extrinsic-color
+relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
+(In this article these parameters are equivalently subscripted with $01234$ or $UBVRI$.)
+The global parameters $\gamma$ are the slopes that connect the extrinsic-color
 parameter and observed magnitude.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
@@
 as confirmed by recalculation of the posterior after exchange of the initial conditions and boundary conditions of $\delta$ and $\gamma$.
-We break the degeneracy
-by assigning the parameters whose values are consistent with dust to $\gamma$ and the other parameters to $\delta$.
+As the model cannot break the degeneracy, we do so
+by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.
 
@@
 If interpreted as being due to dust, the extrinsic term could be associated with extinction $A_X = \gamma_X k$.  In
-this parlance our parameters can be re-expressed as the more familiar color excess
+this parlance our parameters can be re-expressed as the  familiar color excess
 $E_\gamma(B-V) = (\gamma_1-\gamma_2) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
-Similarly we introduce for the intrinsic color term $E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.
+Similar reparameterizatons of the intrinsic color parameters are
+$E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.
 
@@
 \citep{Lewandowski20091989} and standard
-deviations with a  Cauchy distribution prior with
- $\mu=0.1$, $\sigma=0.1$ mag and restricted to non-negative values.
+deviations denoted by $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
+ $0.1$ and scale $0.1$ mag restricted to positive values.
 
@@
 STAN \citep{stan}. STAN provides output statistics to assess
-the convergence of the Markov chains.  The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
-output also gives  $N_{eff} \gg 100$ for all parameters, indicating that there is no evidence for sparse sampling of the parameter space.
-Empirically, the confidence regions are localized and unimodal as can be seen in  Figure~\ref{global:fig}.  There is no evidence that
+the convergence of the output Markov chains.  The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
+output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
+Empirically, the confidence regions are localized and unimodal as can be seen in  Figure~\ref{global:fig}.  We find no evidence that
 the Monte Carlo chains have not converged to the stationary posterior distribution.
@@
          \includegraphics[width=2.5in]{output11/coeff4.pdf} 
-            \caption{Distributions for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.   \label{global:fig}}
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.   \label{global:fig}}
 \end{figure}
 
-For each of the five filters, the 68\% intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma = \sqrt{C_{c,ii}}$
+For each of the five filters, the 68\% credible equal-tailed intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma$
 (and other interesting derived parameters)
@@
 \end{tabular}
-\caption{68\% Intervals for Global Fit Parameters \label{global:tab}}
+\caption{68\% credible Intervals for the Global Fit Parameters \label{global:tab}}
 \end{table}
@@
 magnitudes.  All bands show larger and significant non-zero values for $\beta$, indicating the importance of
-$EW_{Si}$.  This confirms the part of our hypothesis that spectral indicators
-are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ are consistent with zero within one sigma.
-How spectral features affect color can be seen in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$.
+$EW_{Si}$.  This validates our hypothesis that spectral indicators
+are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $v_{Si}$) are consistent with zero within one sigma.
+The effect of spectral parameters on color is shown in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$:
+values of zero signify no color changes.
 Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically.
@@
 
-The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Figure~\ref{ccm:fig}
-shows the expectation of the \citet{1999PASP..111...63F} dust model through its parameter $R^F_V$, plotted together with our measurements of
+The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  
+Our measurements of
 $R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the effective wavelength of the supernova flux that passes
-through the synthetic bands.
-The $R_X$ are consistent with an  $R^F_V=2.5$.  The uncertainties in the 5 measurements
-of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
-uncertainties and are also consistent with $R^F_V=2.5$.
+through the synthetic bands are shown in
+Figure~\ref{ccm:fig},
+along with the expectation of the \citet{1999PASP..111...63F} dust model.
+The $R_X$ are consistent with a dust-model parameter  $R^F_V=2.5$.  The 
+$R_X$ parameters are correlated: the alternative parameterization
+ of $\gamma_X/\gamma_2$ has significantly smaller
+uncertainties and is also consistent with $R^F_V=2.5$.
 
@@
       \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
-   \caption{Best-fit distribution for (left)  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ and (right)  $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$.
+   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$.
    \label{rx:fig}}
@@
       \includegraphics[width=2.8in]{output11/ccm2.pdf} 
-   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right). \citet{1999PASP..111...63F} dust
+   \caption{68\% credible intervals of Left: $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$; Right: $\frac{\gamma_X}{\gamma_2}$. 
+   \citet{1999PASP..111...63F} dust
    predictions for these parameters are overlaid for different values of the dust-parameter $R^F_V$.
@@
 
-The distribution of color excess $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
+The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
  $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
@@
 The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
-The range of $B-V$ colors is $\sim 4$ times larger for the external contribution:
-extreme colors can thus be attributed to the external source. 
+The range of $B-V$ colors is $\sim 4$ times larger for the external contribution. 
 Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red.
@@
    \includegraphics[width=3.2in]{output11/ebv.pdf}
-   \caption{Histograms of the contributions to color excess from external $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
-   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$ effects for the supernovae in our sample.
+   \caption{Ideograms of the external $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
+   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$  contributions to color excess  for the supernovae in our sample.
    \label{ebv:fig}}
@@
 $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
-$A_{B, eff} = \gamma_1 k + \delta_1D$.  These values for the SNf sample
-shown in Figure~\ref{rveff:fig}, overplotted with the expected relationship for color-excess 
-purely due to the extrinsic $\gamma$ term.
-Recall that  $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ respectively were arbitrarily assigned to the average $k$ and $D$ values of our distribution;
-for convenience, we shift the zero of  $E_{eff}(B-V)$ so that the extrinsic dust expectation qualitatively forms a ridge line
-bounding the high-extinction side of the distribution.
-In the right plot of Figure~\ref{rveff:fig}, we show the difference between $E_{eff}(B-V)$ and that ridge line.
-The Pearson correlation between color excess and extinction excess is -0.26.
-Over all effective color excesses, the inferred $R_B$  is capped by the canonical extrinsic value.
-However, with increasing effective color excess there is a broadening of the distribution toward low inferred $R_B$,
-accompanied by a decrease in average  $R_B$.
-Supernovae with extremely red $E_{eff}(B-V)$ on average have significantly lower inferred $R_V$ that their counterparts with bluer $E_{eff}(B-V)$.
-Conversely, supernovae with extreme
-blue  $E_{eff}(B-V)$ fall slightly but noticeably above the ridge line, which would lead to an inferred $R_B$ slightly
-larger than the extrinsic expectation.
+$A_{B, eff} = \gamma_1 k + \delta_1D$.
+Recall that in our model the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrary
+fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$.
+Therefore, our model does not specify a unique $R_{B,eff} = A_{B, eff} /E_{eff}(B-V)$.
+
+We plot $E_{eff}(B-V) + const$ versus
+$A_{B, eff}$ for the SNf sample in Figure~\ref{rveff:fig}.
+Overplotted is the expected extinction due to a pure extrinsic extinction with $\gamma_1$ slope.
+The constant added to the effective color excess
+corresponds to specifying a specific color as having zero extinction, and is chosen for qualitatively to form a ridge line 
+bounding the high-extinction side of the data; the discussion that follows does not depend on the specific choice of the constant.
+The right plot of Figure~\ref{rveff:fig} shows (relatively) how much more extinction is
+observed compared to the expected extinction from extrinsic dust for the corresponding effective color excess,
+ $\Delta A_B =  A_{B,eff}- \gamma_1 E_{eff}(B-V)$.
+Over all effective color excesses the difference is capped by the ridge line, except for extremely
+blue supernovae that lie slightly but noticeably above the ridge line.
+However, with increasing effective color excess there is a broadening of the distribution toward lower observed extinctions.
+A linear fit between $E_{eff}(B-V)$  and $\Delta A_B$ gives a slope of $-0.33$.
+Although our model does not fix $R_{B,eff}$, it does show that it decreases on average with increasing effective color excess.
 
@@
 $A_{B, eff} = \gamma_1 k + \delta_1D$ for the SNf sample.  Overplotted is the expected relationship for color-excess
-purely due to the intrinsic $\gamma$ term.  we shift the zero of  $E_{eff}(B-V)$  so that the  the extrinsic dust expectation qualitatively forms a ridge line
+purely due to the intrinsic $\gamma$ term.   The zero of  $E_{eff}(B-V)$  is shifted so that the  the extrinsic dust expectation qualitatively forms a ridge line
 bounding the high-extinction side of the distribution.
-Right: The difference between $E_{eff}(B-V)$ and that ridge line.
+Right:  The observed extinction compared to that expected  from extrinsic dust $\Delta A_B =  A_{B,eff}- \gamma_1 E_{eff}(B-V)$.
    \label{rveff:fig}}
@@
 
-Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for the
+Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the
 square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
 than the dispersion in $\Delta$.
-The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix: assembling
+The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix.
+Assembling
 a new set of Cholesky factors based on the distributions of each individual factor will not generally satisfy the condition of representing a correlation matrix.  
@@
  \end{equation}
-Similarly the typical color covariance, in terms of colors $U-V$, $B-V$, $V-R$, and $V-I$, can
-be expressed as having standard deviations and
- correlations
+The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
+expressed as the standard deviations and
+ correlation matrix
  \begin{equation}
@@
    \includegraphics[width=3.2in]{output11/sigma_corner.pdf} 
-   \caption{Best-fit distribution for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
+   \caption{Posterior contours for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
    \label{sigma:fig}}
@@
 Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
-$\Delta$: their distributions for all Monte Carlo chain links for all supernovae, are shown in Figure~\ref{perobject:fig}.
-There is a core concentration in the  parameter-space, with around ten objects occupy its outskirts.
-Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected in the infrequent selection of supernovae
+$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
+There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
+Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected for the infrequent selection of supernovae
 heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
@@
    \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
-   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
+   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as the grey offset
 $\Delta$.
@@
 \end{equation}
-Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  The second strongest is in
-$EW_{Si}$--$v_{Si}$.
-External $E_\gamma(B-V)$ dust most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation stronger with internal parameters stronger than
+Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  
+External $E_\gamma(B-V)$ dust is
+most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation  with internal parameters stronger than
 0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.
+An extensive analysis of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}.
 
-\section{SN 2014J}
+\section{SN 2014J in the Context of Our Model}
 \label{sn2014j:sec}
@@
 SN~2014J   is one of several SNe~Ia that exhibits a low $R_V<2.0$.
-The colors of this supernova can be studied by comparison with similar unreddened objects
+The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
+spectral evolution that 
+suffers low Galactic and host reddening
 \citep[e.g.][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
-It is spectroscopically normal, having a spectral evolution similar to SN~2011fe.
-As SN~2011fe suffers low Galactic and host reddening, it serves as a good template
-for the measurement of color excess, nulling out the effects of Ca and Si equivalent width.
-SN~2014J does show
-overall higher photospheric velocities than SN~2011fe, but the results in \S\ref{results:sec} show that this is unimportant.
+The overall higher photospheric velocities of
+SN~2014J are unimportant  based on the findings of  \S\ref{results:sec}.
 
-Data of SN~2014J are now analyzed using our model and the training with the SNfactory sample.
-The data are the color excesses  in $UBRi$  relative to $V$ at peak brightness  taken from \citet{2014ApJ...788L..21A}
-following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
+Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
+The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
+following their perscription of averaging measurements within 5-days of peak $B$ magnitude.
 Their values 
-$E^o(U-V) =   2.23 \pm   0.03$,
-$E^o(B-V) =   1.28 \pm   0.04$,
-$E^o(R-V) =  -0.47 \pm   0.03$,
-$E^o(i-V) =  -0.92 \pm   0.03$
+$E_o(U-V) =   2.23 \pm   0.03$,
+$E_o(B-V) =   1.28 \pm   0.04$,
+$E_o(R-V) =  -0.47 \pm   0.03$,
+$E_o(i-V) =  -0.92 \pm   0.03$
 are plotted in Figure~\ref{sn2014j:fig}.
@@
 \begin{equation}
-E^o(X-V) =  \left(\frac{\gamma_X}{\gamma_2}-1\right)k +  \left(\frac{\delta_X}{\delta_2}-1\right)D,
+E_o(X-V) =  \left(\frac{\gamma_X}{\gamma_2}-1\right)k +  \left(\frac{\delta_X}{\delta_2}-1\right)D,
 \end{equation}
@@
 \end{equation}
-The predicted values of observed $E^o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
+The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
 overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
@@
 a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
-is also plotted.  Our model gives significantly smaller deviations from the data.
+is also plotted.  Our model has significantly smaller deviations from the data.
 
-In our model, the observed color excess is attributed to contributions from extrinsic
-$E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ origins.
+In our model, the observed color excess is attributed to   extrinsic
+$E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ contributions.
 Among the supernovae in the SNfactory training set, the highest median value for 
-$E_\gamma(B-V)$ is $  0.33^{  +0.04}_{ -0.04}$ and for $E_\delta(B-V)$ is
-$  0.07^{  +0.03}_{ -0.03}$ 
+$E_\gamma(B-V)$ is $  0.33 \pm 0.04$ and for $E_\delta(B-V)$ is
+$  0.07 \pm 0.03$ 
 (see Figure~\ref{ebv:fig}).
@@
 We model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and distinct intrinsic and
-extrinsic color parameters.  Analyzing SNfactory data using the model, we find significant evidence that the above parameters do
+extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
 affect supernova magnitudes and colors.  The external color parameter has behavior consistent with $R^F_V=2.5$ \citet{1999PASP..111...63F} dust,
-whereas the internal color parameter is inconsistent with dust or a blackbody.
+whereas the internal color parameter is inconsistent with dust or a blackbody.  This model  does an excellent job in
+describing SN~2014J, a supernova not used in the training that has atypical colors.
 
@@
 \citet{2011ApJ...729...55F} and the above authors
-find that supernovae with large $E^o(B-V)$ 
+find that supernovae with large $E_o(B-V)$ 
 preferentially exhibit low $R^F_V$. 
-Our model predicts both of these effects with a single set of extrinsic dust parameters, as is borne out by the
-SNf sample as shown in Figure~\ref{rveff:fig}. 
-Our model also predicts that the converse also holds: supernovae with the smallest $E^o(B-V)$ due to intrinsic color
+Our model predicts both of these effects with a single form of extrinsic dust, as is borne out by the
+SNf sample shown in Figure~\ref{rveff:fig}. 
+Our model also predicts that the converse also holds: supernovae with the smallest $E_o(B-V)$ due to intrinsic color
 will appear overly faint when analyzed within the context of a canonical dust.
@@
 be compared
-to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of the color $C$ parameter from \citet{2014A&A...568A..22B}:
-the Pearson correlation coefficient between the two variables is $-0.33$.
+to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of the color $C$ parameter (directly
+comparable to $E(B-V)$ from \citet{2014A&A...568A..22B}.
+A linear fit for the relationship between color and Hubble residual gives a slope of $-0.67$.
 
@@
 removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
-non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  anticipate that for the in the previous analysis, equivalent widths of CaII and
+non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  anticipate that in the previous analysis, equivalent widths of CaII and
 SiII would also have shown correlations with color.
@@
 of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes.  Line opacities
-that operate over broad bands are the most obvious candidate for producing this behavior and so warrant further study.
+that operate over broad bands are the most obvious candidate for producing this behavior.
 
 The model and results presented here
-carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represent Hubble residuals after
+carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represents Hubble residuals after
 application of the model, and its  $0.096$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
@@
 in extrinsic dust properties that supernovae in different hosts may encounter.  Extending our model to 
-include  a parameterized  $\gamma$ distribution would consider a range of host-dust behavior, and
+include  a parameterized  $\gamma$ distribution would allow a range of host-dust behavior, and
 is a direction of further study.
@@
 \acknowledgments
+We thank the STAN team for providing the statistical tool without which this analysis would not have been possible,
+and Michael Betancourt specifically for his helpful guidance.
+This work was supported by the Director, Office of Science, Office of High Energy Physics, 
+of the U.S.\ Department of Energy under Contract No. DE-AC02-05CH11231.
 

### 2016-09-06 sn2014j.py

@@ -91,7 +91,7 @@ for rv in rvs:
 plt.legend()
 plt.xlim((3200,8000))
 plt.ylim((-2,3))
-plt.ylabel(r'$E^o(X-V)$')
+plt.ylabel(r'$E_o(X-V)$')
 plt.xlabel(r'Wavelength (\AA)')
 pp = PdfPages('output11/sn2014j.pdf')
 plt.savefig(pp,format='pdf')

### 2016-09-06 forgerard.tex
First draft?

@@
 {
-    A.~G.~Kim,\altaffilmark{2}
-    G.~Smadja,\altaffilmark{7} 
-    G.~Aldering,\altaffilmark{2}
+    A.~G.~Kim,\altaffilmark{1}
+    G.~Smadja,\altaffilmark{2} 
+    G.~Aldering,\altaffilmark{1}
     P.~Antilogus,\altaffilmark{4}
-    S.~Bailey,\altaffilmark{2}
+    S.~Bailey,\altaffilmark{1}
     C.~Baltay,\altaffilmark{5}
@@
     D.~Baugh,\altaffilmark{6}
-    K.~Boone,\altaffilmark{2,3}
+    K.~Boone,\altaffilmark{1,3}
     S.~Bongard,\altaffilmark{4}
-    C.~Buton,\altaffilmark{7}
+    C.~Buton,\altaffilmark{2}
     J.~Chen,\altaffilmark{6}
-    N.~Chotard,\altaffilmark{7}
-    Y.~Copin,\altaffilmark{7}
-    P.~Fagrelius,\altaffilmark{2,3}
-    H.~K.~Fakhouri,\altaffilmark{2,3}
+    N.~Chotard,\altaffilmark{2}
+    Y.~Copin,\altaffilmark{2}
+    P.~Fagrelius,\altaffilmark{1,3}
+    H.~K.~Fakhouri,\altaffilmark{1,3}
     U.~Feindt,\altaffilmark{9}
@@
     E.~Gangler,\altaffilmark{11}  
-    B.~Hayden,\altaffilmark{2}
+    B.~Hayden,\altaffilmark{1}
     W.~Hillebrandt,\altaffilmark{16}
@@
     S.~Lombardo,\altaffilmark{9}
-    J.~Nordin,\altaffilmark{2,9}
+    J.~Nordin,\altaffilmark{1,9}
     R.~Pain,\altaffilmark{4} 
     E.~Pecontal,\altaffilmark{13}
-    R.~Pereira,\altaffilmark{7}
-    S.~Perlmutter,\altaffilmark{2,3}
+    R.~Pereira,\altaffilmark{2}
+    S.~Perlmutter,\altaffilmark{1,3}
     D.~Rabinowitz,\altaffilmark{5}
     M.~Rigault,\altaffilmark{9} 
-    D.~Rubin,\altaffilmark{2,14}
-    K.~Runge,\altaffilmark{2}
-    C.~Saunders,\altaffilmark{2,3}
+    D.~Rubin,\altaffilmark{1,14}
+    K.~Runge,\altaffilmark{1}
+    C.~Saunders,\altaffilmark{1,3}
    R.~Scalzo,\altaffilmark{8}
-    C.~Sofiatti,\altaffilmark{2,3} 
-    N.~Suzuki,\altaffilmark{2}
+    C.~Sofiatti,\altaffilmark{1,3} 
+    N.~Suzuki,\altaffilmark{1}
     S.~Taubenberger,\altaffilmark{16}
     C.~Tao,\altaffilmark{6,10}
-    R.~C.~Thomas,\altaffilmark{15} \\
+    R.~C.~Thomas,\altaffilmark{1} \\
     (The Nearby Supernova Factory)
@@
 
-\altaffiltext{2}
+\altaffiltext{1}
 {
@@
 }
+
+\altaffiltext{2}
+{
+    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
+    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon.
+}
+
 \altaffiltext{3}
@@
 }
-\altaffiltext{7}
-{
-    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
-    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon.
-}
+
 \altaffiltext{8}
@@
 \begin{abstract}
-abstract text
+An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
+is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be significantly
+dependent on the spectral equivalent widths, and two independent color parameters.  One parameter, interpreted as due to extrinsic host-galaxy
+dust extinction, is consistent with an $R_V=2.5$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
+is inferred to have origins intrinsic to supernovae.  Our model explains features of external data, such as the wide range of inferred $R_V$ among
+SNe~Ia, the low  $R_V$ of redder supernovae, the colors of SN~2014J, and the color-dependent residuals in Hubble diagrams.
 \end{abstract}
@@
 \section{Introduction}
-Type~Ia supernovae (SNe~Ia) form a homogenous set of exploding stars and as such were early recognized as a powerful distance indicator 
-and probe of cosmology \citep{1992ARA&A..30..359B}.  After further careful consideration of supernova data, it was recognized
-that SN~Ia light-curve shapes \citep{1984SvA....28..658P, 1993ApJ...413L.105P} and colors \citep{1998A&A...331..815T} exhibit subtle signs of heterogeneity,
+Type~Ia supernovae (SNe~Ia) form a homogenous set of exploding stars and as such were early recognized and utilized as a powerful distance indicator 
+and probe of cosmology \citep[e.g.][]{1992ARA&A..30..359B, 1993ApJ...415....1S}.  After further careful consideration of supernova data, it was recognized
+that SN~Ia light-curve shapes \citep{1993ApJ...413L.105P} and colors \citep{1998A&A...331..815T} exhibit subtle signs of heterogeneity,
 which being correlated with absolute magnitude
 need to be considered when inferring distances.  Empirical models parameterizing SNe~Ia by their light-curve shape
-and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} that enabled distance measurements of cosmological supernovae,
+and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} that enabled absolute magnitude corrections
+and distance measurements of cosmological supernovae,
 which 
@@
 The two most commonly used supernova-cosmology light-curve fitters today are SALT2 \citep{2007A&A...466...11G} and MLCS2k2
-\citep{2007ApJ...659..122J}.\footnote{More flexible light-curve fitters
+\citep{2007ApJ...659..122J}.\footnote{Light-curve fitters with more flexible degrees of freedom
 \citep[e.g.][]{2008ApJ...681..482C, 2011AJ....141...19B} are used to study SN~Ia heterogeneity.}
 They remain two-parameter models, with one parameter characterizing light-curve shape and the other
-supernova color.  The physical cause of the color diversity is viewed differently by the two sets of authors: 
-\citet{2007A&A...466...11G} pragmatically extract color variation empirically from SNe that span a wide range of colors, with no attribution of
-that variation to intrinsic or extrinsic origins;
+ color.  The physical cause of the color diversity is treated differently by the two sets of authors: 
+\citet{2007A&A...466...11G} pragmatically extract color variation empirically from SNe that span a wide range of colors, with no attribution
+to either intrinsic or extrinsic origins;
 \citet{2007ApJ...659..122J}
-attribute changes in color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation that
-both intrinsic and extrinsic color variation can occur independently.
+attribute changes in color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation of independent
+intrinsic and extrinsic color variability.
 
 There is evidence that supports the expectation that a single parameter cannot describe the full range
-of supernova color behavior.  One approach to look for color diversity is to find correlations between color and spectral features.
+of colors seen in the SN~Ia population.  One approach to look for color diversity is to find correlations between color and spectral features.
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations distinguished
@@
 \citet{2015MNRAS.451.1973S}
-find that high-velocity Si II$\lambda$6355 are found in objects that have red ultraviolet/optical colors near maximum brightness.
+find that high-velocity SiII$\lambda$6355 is found in objects that have red ultraviolet/optical colors near maximum brightness.
 Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
@@
 The Nearby Supernova Factory \citep[SNfactory;][]{2004SPIE.5249..146L} has collected  
-spectrophotometric time series of $z<0.08$ SNe~Ia.   The $3200$--$10000$~\AA\ spectral coverage
+spectrophotometric time series of hundreds of Hubble-flow $0.03<z<0.08$ SNe~Ia.   The $3200$--$10000$~\AA\ spectral coverage
 provides measurements of an array of supernova spectral features while also providing synthetic broadband photometry
-spanning near-UV to near-IR SN-frame wavelengths, while over a hundred the supernovae have temporal coverage over
-peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia properties.
+spanning near-UV to near-IR SN-frame wavelengths.  Well over a hundred these supernovae have temporal coverage over
+peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia colors and spectral features together.
 
@@
 properties and the other due to
-extrinsic processes.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
+extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
 \S\ref{model:sec} and results are given in \S\ref{results:sec}.  In \S\ref{sn2014j:sec} our results are applied to the out-of-sample
@@
 description of host-galaxy subtraction is given in \citet{2011MNRAS.418..258B}.
-A recent description of the current status of the data is given in \citet{2015ApJ...815...58F}.
-
+
+The current status of the data and its treatment s presented in \citet{2015ApJ...815...58F}.
+We provide a brief summary of the points important for this analysis.
 The spectral time-series  are corrected for Milky Way dust
@@
 distances expected for the supernova redshifts given a flat
-$\Lambda$CDM cosmology with $\Omega_M = 0.28$ (but with an arbitrarily selected
-$H_0$ since we are interested in relative magnitudes).
+$\Lambda$CDM cosmology with $\Omega_M = 0.28$ (with an arbitrarily selected
+$H_0$ since the current analysis does not depend on the absolute magnitude scale).
 
@@
 Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
-closest to maximum is used \citep{chotard:thesis}. [This is what Nico did in his thesis, is this true of the data Manu gave me?]
-The weighted mean from phases within 3 days of maximum light is used for SiII$\lambda 6355$.
-
-The 163 supernovae that have the photometric and spectroscopic statistics described above
-constitute our analysis sample.  The data are given in Table~\ref{data:tab}.
+closest to maximum is used \citep{chotard:thesis}. [Confirm!]
+The weighted mean from phases within 3 days of maximum light is used for the  SiII$\lambda 6355$ velocity.
+
+Our analysis sample is constituted with the  163 supernovae that have the data coverage to 
+give photometric and spectroscopic statistics described above.
+The data are given in Table~\ref{data:tab}.
 The peak magnitude uncertainties do have covariance, which are accounted
@@
 
+Absolute photometric calibration is of extreme importance for the SNfactory.  This analysis, however, is confined to the relative colors for a low-redshift set of supernovae
+and is thus insensitive to uncertainties in these zeropoints.
+
 \section{Supernova Model}
@@
 SN~Ia broadband magnitudes and colors are correlated with
-spectral features: equivalent widths and line velocities, being insensitive to broadband color effects, are considered.
+spectral features: equivalent widths and line velocities are considered as statistics localized in wavelength that are insensitive to variations in
+broadband colors.
 Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
@@
 that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
-on the equivalent widths of the CaII H\&K and SiII$\lambda$ 4141 spectral features
+on the equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
 $EW_{Ca}$, $EW_{Si}$,
@@
 these spectral features are associated with SN~Ia  spectroscopic diversity  
-\citep{2006PASP..118..560B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F,2009A&A...500L..17B}.
+\citep{2006PASP..118..560B,2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
 $EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
@@
 An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
-Residual dispersion is described by a Normal distribution with (unknown) covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
-to capture intrinsic dispersion and distance errors introduced when normalizing the supernovae to be at a common distance.
+Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
+$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
+to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
 The observed magnitudes are linearly dependent on an
 extrinsic-color parameter $k$.  The observables
-$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$ have Gaussian measurement uncertainty with covariance $C$,
-shown in Table~\ref{data:tab}.
+$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
+shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
 The model is written as
@@
 relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
-(In this article these parameters are equivalently subscripted with $01234$ or $UBVRI$.)
+(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
 The global parameters $\gamma$ are the slopes that connect the extrinsic-color
-parameter and observed magnitude.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
+parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
 \begin{equation}
@@
 each other,
-as confirmed by recalculation of the posterior after exchange of the initial conditions and boundary conditions of $\delta$ and $\gamma$.
-As the model cannot break the degeneracy, we do so
+as confirmed by recalculation of the posterior after exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
+As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
 by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.
@@
 
-If interpreted as being due to dust, the extrinsic term could be associated with extinction $A_X = \gamma_X k$.  In
+When interpreted as being due to dust, the extrinsic terms are associated with extinction $A_X = \gamma_X k$.  In
 this parlance our parameters can be re-expressed as the  familiar color excess
@@
 \citep{Lewandowski20091989} and standard
-deviations denoted by $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
+deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
  $0.1$ and scale $0.1$ mag restricted to positive values.
@@
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
-Empirically, the confidence regions are localized and unimodal as can be seen in  Figure~\ref{global:fig}.  We find no evidence that
+Empirically, the confidence regions are localized and unimodal as is seen in  Figure~\ref{global:fig}.  We find no evidence that
 the Monte Carlo chains have not converged to the stationary posterior distribution.
@@
          \includegraphics[width=2.5in]{output11/coeff4.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.   \label{global:fig}}
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.
+            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution, not to 68\%, 95\%, etc.\
+            enclosed probability.  \label{global:fig}}
 \end{figure}
 
-For each of the five filters, the 68\% credible equal-tailed intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma$
+For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma$
 (and other interesting derived parameters)
 are given in Table~\ref{global:tab}.
-The two dimensional contours for the parameters, grouped by filter, are shown in Figure~\ref{global:fig}.
+Contours of the posterior surface for parameter pairs grouped by filter are shown in Figure~\ref{global:fig}.
 
@@
 We find small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
-magnitudes.  All bands show larger and significant non-zero values for $\beta$, indicating the importance of
+magnitudes.  All bands show larger and significant non-zero values for $\beta$, indicating their sensitivity to
 $EW_{Si}$.  This validates our hypothesis that spectral indicators
@@
 The effect of spectral parameters on color is shown in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$:
-values of zero signify no color changes.
+values of zero signify no color changes associated with magnitude changes.
 Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically.
@@
 Our measurements of
-$R_X$ and $\frac{\gamma_X}{\gamma_2}$ placed at the effective wavelength of the supernova flux that passes
-through the synthetic bands are shown in
-Figure~\ref{ccm:fig},
-along with the expectation of the \citet{1999PASP..111...63F} dust model.
-The $R_X$ are consistent with a dust-model parameter  $R^F_V=2.5$.  The 
-$R_X$ parameters are correlated: the alternative parameterization
+$R_X$ and $\frac{\gamma_X}{\gamma_2}$, placed at the effective wavelength of the supernova flux that passes
+through the synthetic bands, are shown in
+Figure~\ref{ccm:fig}.
+Also plotted are the expectations of the \citet{1999PASP..111...63F} dust model for different values of its parameter $R^F_V$.
+The $R_X$ are consistent with  $R^F_V=2.5$.  The 
+ alternative parameterization
  of $\gamma_X/\gamma_2$ has significantly smaller
@@
 The best-fit distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
-Although the posteriors of $\delta$ are fairly circular, $\delta_1-\delta_2$ can approach zero, resulting in the
+Although the posteriors of $\delta$ are close to Gaussian, $\delta_1-\delta_2$ can approach zero, resulting in the
 elongated tail in negative  $R_{\delta X}$.
@@
 a reddening in $B-V$ comes with a blueing in $V-R$.
-These are not the behaviors expected from normal dust or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
+These are not the behaviors expected from normal dust,
+circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
 more complicated underlying supernova physics.
@@
 The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
- $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown in Figure~\ref{ebv:fig}.
-Recall that given our boundary conditions the means of both distributions are equal to zero. 
-The standard deviation of $E(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
+ $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
+Recall that our boundary conditions set the means of both distributions to zero. 
+The standard deviation of $E_\gamma(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
 The range of $B-V$ colors is $\sim 4$ times larger for the external contribution. 
-Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red.
+Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red, consistent
+with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.
+
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 
-For each supernova, the two separate color effects are conflated into an effective color excess
+Our model predicts that internal and external effects for each supernova  conflate into an effective color excess
 $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
@@
 fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$.
-Therefore, our model does not specify a unique $R_{B,eff} = A_{B, eff} /E_{eff}(B-V)$.
+Our model does not provide a unique value for the statistic $R_{B,eff} = A_{B, eff} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
+However, the model can show that  $R_{B,eff}$  decreases on average with increasing effective color excess.
 
@@
 $A_{B, eff}$ for the SNf sample in Figure~\ref{rveff:fig}.
-Overplotted is the expected extinction due to a pure extrinsic extinction with $\gamma_1$ slope.
+Overplotted is the expected extinction due to a pure extrinsic extinction with slope equal to $\gamma_1$.
 The constant added to the effective color excess
-corresponds to specifying a specific color as having zero extinction, and is chosen for qualitatively to form a ridge line 
+corresponds to specifying a specific color as having zero extinction, and is chosen  qualitatively to form a ridge line 
 bounding the high-extinction side of the data; the discussion that follows does not depend on the specific choice of the constant.
-The right plot of Figure~\ref{rveff:fig} shows (relatively) how much more extinction is
+The right plot of Figure~\ref{rveff:fig} shows  how much more extinction (relatively) is
 observed compared to the expected extinction from extrinsic dust for the corresponding effective color excess,
@@
 A linear fit between $E_{eff}(B-V)$  and $\Delta A_B$ gives a slope of $-0.33$.
-Although our model does not fix $R_{B,eff}$, it does show that it decreases on average with increasing effective color excess.
 
@@
    \includegraphics[width=2.8in]{output11/rveffres.pdf}
-   \caption{Left: $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band``extinction''
+   \caption{Left: Effective color excess $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and effective $B$-band ``extinction''
 $A_{B, eff} = \gamma_1 k + \delta_1D$ for the SNf sample.  Overplotted is the expected relationship for color-excess
 purely due to the intrinsic $\gamma$ term.   The zero of  $E_{eff}(B-V)$  is shifted so that the  the extrinsic dust expectation qualitatively forms a ridge line
-bounding the high-extinction side of the distribution.
+bounding the high-extinction side of the data.
 Right:  The observed extinction compared to that expected  from extrinsic dust $\Delta A_B =  A_{B,eff}- \gamma_1 E_{eff}(B-V)$.
@@
 
-The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The intrinsic dispersion
-is given by the standard deviation of $0.096$ mag.  The distribution is non-Gaussian, with a broad tail in the positive (fainter) direction.
+The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
+has a standard deviation of $0.096$ mag, and a broad tail in the positive (fainter) direction.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected for the infrequent selection of supernovae
-heavily extinguished by host-galaxy dust; note that $E_\delta(B-V)$ does not have an analogous tail.
-Outliers in  $EW_{Ca}$--$v_{Si}$ parameters are also clearly distinguished.
+heavily extinguished by host-galaxy dust.
+Outliers  are also clearly distinguished in  $EW_{Ca}$--$v_{Si}$ space.
 
@@
 External $E_\gamma(B-V)$ dust is
-most strongly correlated with $EW_{Si}$, while the internal $E_\delta(B-V)$  has no correlation  with internal parameters stronger than
-0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062.
+most strongly correlated with $EW_{Si}$; recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy properties
+\citep{2003MNRAS.340.1057S}.
+The internal $E_\delta(B-V)$  has no correlation  with internal parameters stronger than
+0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062;
+this low correlation, and the broad distribution in $E_\delta(B-V)$ for low $E_\gamma(B-V)$,  indicate that what we have been calling intrinsic
+indeed is not related to extrinsic dust.
 An extensive analysis of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}.
@@
 
-SN~2014J   is one of several SNe~Ia that exhibits a low $R_V<2.0$.
+SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 2015ApJ...805...74B}.
 The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
@@
 a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
-is also plotted.  Our model has significantly smaller deviations from the data.
-
-In our model, the observed color excess is attributed to   extrinsic
+is also plotted.  Our model predictions provide a significantly better match to the data.
+
+In the fit to our model, the observed color excess is attributed to   extrinsic
 $E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ contributions.
-Among the supernovae in the SNfactory training set, the highest median value for 
+Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the highest median value for 
 $E_\gamma(B-V)$ is $  0.33 \pm 0.04$ and for $E_\delta(B-V)$ is
@@
 to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of the color $C$ parameter (directly
-comparable to $E(B-V)$ from \citet{2014A&A...568A..22B}.
-A linear fit for the relationship between color and Hubble residual gives a slope of $-0.67$.
+comparable to $E(B-V)$) from the Hubble diagram analysis of \citet{2014A&A...568A..22B}.
+A linear fit for the relationship between color and Hubble residual has a significant slope ($-0.67$), as expected.
 
@@
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, whereas
-our values of $\eta$ are consistent with zero.  Recall that we find a correlation between $v_{Si}$ and $EW_{Ca}$;
-removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
-non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We  anticipate that in the previous analysis, equivalent widths of CaII and
+our values of $\eta$ are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant affect on color, not particularly 
+surprising as they
+are strong features in the $B$ band.
+Recall that we find a correlation between $v_{Si}$ and $EW_{Ca}$
+Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
+non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, just not as strongly as the equivalent widths,
+and  anticipate that in the previous analysis the equivalent widths of CaII and 
 SiII would also have shown correlations with color.
@@
 that operate over broad bands are the most obvious candidate for producing this behavior.
+\citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
+from doubly and singly ionized states, making the gas phosphorescent and efficient in redistributing energy from the UV/blue to redder
+wavelengths.  Qualitatively this would result in the structure for $\gamma_X/\gamma_2-1$ that we measure.
+We conjecture that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth
+of the reionization front with respect to the core of the ejecta, yielding the wavelength-dependent color behavior
+detected in this analysis.
+
+The model introduced in this article is limited, in that it doesn't accommodate the expected diversity
+in extrinsic dust properties that supernovae in different hosts may encounter.  Extending our model to 
+include  a parameterized  $\gamma$ distribution would allow a range of host-dust behavior, and
+offers a direction of further study.
+For the moment, we assert that variations in extrinsic dust across supernovae are limited in
+size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within Eqn.~\ref{color_cor:eqn}.
 
@@
 The  analysis of this article was intended to model the color behavior of supernovae in our dataset.
-A separate analysis is required to determine how
-well this model can be used to measure supernova distances.
-We wait for this analysis to explore correlations between Hubble residuals, host-galaxy parameters (e.g.\ mass,
-local star formation rate) and the intrinsic $D$ parameter.
-
-The model introduced in this article is limited, in that it doesn't accommodate the expected diversity
-in extrinsic dust properties that supernovae in different hosts may encounter.  Extending our model to 
-include  a parameterized  $\gamma$ distribution would allow a range of host-dust behavior, and
-is a direction of further study.
-For the moment, we assert that variations in extrinsic dust are limited in
-size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within Eqn.~\ref{color_cor:eqn}.
+We defer to a new model to determine how
+well this model can be used to measure supernova distances
+and examine correlations between its Hubble residuals host-galaxy parameters, e.g.\ mass,
+local star formation rate \citep{2010ApJ...715..743K, 2013A&A...560A..66R}.
 
@@
 We thank the STAN team for providing the statistical tool without which this analysis would not have been possible,
-and Michael Betancourt specifically for his helpful guidance.
+and Michael Betancourt specifically for his helpful guidance.  We thank Danny Goldstein for useful discussions.
 This work was supported by the Director, Office of Science, Office of High Energy Physics, 

### 2016-09-07 forgerard.tex
respond to Greg comments

@@
     C.~Saunders,\altaffilmark{1,3}
-   R.~Scalzo,\altaffilmark{8}
     C.~Sofiatti,\altaffilmark{1,3} 
@@
 
-\altaffiltext{8}
-{
-    Research School of Astronomy and Astrophysics,
-    Australian National University,
-    Canberra, ACT 2611, Australia
-}
 \altaffiltext{9}
@@
 
-\keywords{supernovae: general}
+\keywords{supernovae: genera; supernovae:SN 2014J}
 
@@
 \colhead{$n$} & \colhead{$EW_{Ca}$} & \colhead{$EW_{Si}$} & \colhead{$v_{Si}$} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} \\
-\multicolumn{3}{c}{} &  \colhead{(km s$^{-1}$)} & \multicolumn{5}{c}{}
+ & (\AA) & (\AA)&  \colhead{(km s$^{-1}$)} & \multicolumn{5}{c}{}
 }
@@
 These are not the behaviors expected from normal dust,
-circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
+circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
+2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
 more complicated underlying supernova physics.
@@
 However, with increasing effective color excess there is a broadening of the distribution toward lower observed extinctions.
-A linear fit between $E_{eff}(B-V)$  and $\Delta A_B$ gives a slope of $-0.33$.
+A linear fit between $E_{eff}(B-V)$  and $\Delta A_B$ gives a slope of $-0.45 \pm 0.11$.
 
@@
 
+The range of SiII equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA.  
+The implied span in $B$ magnitude based on $\beta_1$ is 0.54~mag.  Therefore $\beta_1$ cannot wholly be attributed to the line itself.
+Similarly, the CaII equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
+701~\AA.  The implied span in $U$ magnitude is is 0.21~mag, so $\alpha_0$ cannot be completely due to the line iteslf.
+
 \section{SN 2014J in the Context of Our Model}
@@
 
-SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 2015ApJ...805...74B}.
+SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
+2014ApJ...795L...4K, 2015ApJ...805...74B}.
 The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
@@
 comparable to $E(B-V)$) from the Hubble diagram analysis of \citet{2014A&A...568A..22B}.
-A linear fit for the relationship between color and Hubble residual has a significant slope ($-0.67$), as expected.
+A linear fit for the relationship between color and Hubble residual has a significant slope ($-0.57 \pm 0.07$), consistent with the slope
+found for the SNfactory data.
 

### 2016-09-08 forgerard.tex
comments after videocon addressed.

@@
 \usepackage{lineno}
+
 \linenumbers
@@
 
-\title{Evidence for an Intrinsic Color Parameter in Type~Ia Supernovae}
+\title{Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory}
 \author
@@
 An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
-is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be significantly
-dependent on the spectral equivalent widths, and two independent color parameters.  One parameter, interpreted as due to extrinsic host-galaxy
+is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
+dependent on the spectral equivalent widths, and two independent color parameters with better than 0.999 confidence.
+One parameter, interpreted as due to extrinsic host-galaxy
 dust extinction, is consistent with an $R_V=2.5$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
-is inferred to have origins intrinsic to supernovae.  Our model explains features of external data, such as the wide range of inferred $R_V$ among
-SNe~Ia, the low  $R_V$ of redder supernovae, the colors of SN~2014J, and the color-dependent residuals in Hubble diagrams.
+is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: the wide range and
+the low values of inferred $R_V$ among
+SNe~Ia, and the colors of SN~2014J.
 \end{abstract}
 
-\keywords{supernovae: genera; supernovae:SN 2014J}
+\keywords{supernovae: general; supernovae: SN 2014J}
 
@@
 The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
-in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.
+in \citet{2008A&A...477..717B} and the  velocity of SiII$\lambda 6355$ (expressed as the
+observed location of the feature $\lambda_{Si} = (1+v_{Si}/c) 6355$\AA)
+as in \citet{chotard:thesis}.
 Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
@@
 \tablehead{
-\colhead{$n$} & \colhead{$EW_{Ca}$} & \colhead{$EW_{Si}$} & \colhead{$v_{Si}$} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} \\
- & (\AA) & (\AA)&  \colhead{(km s$^{-1}$)} & \multicolumn{5}{c}{}
+\colhead{$n$} & \colhead{$EW_{Ca}$} & \colhead{$EW_{Si}$} & \colhead{$\lambda_{Si}$} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} \\
+ & (\AA) & (\AA)&  \colhead{(\AA)} & \multicolumn{5}{c}{}
 }
@@
 $EW_{Ca}$, $EW_{Si}$,
-the SiII$\lambda6355$ velocity $v_{Si}$:
+the SiII$\lambda6355$ position $\lambda_{Si}$ (so also linear with $v_{Si}$):
 these spectral features are associated with SN~Ia  spectroscopic diversity  
@@
 \begin{pmatrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si} + \delta_0 D\\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} + \delta_1 D \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si} + \delta_2 D\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si} + \delta_3 D\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si} + \delta_4 D
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
 \end{pmatrix}
@@
 U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
-EW_{Si}\\ EW_{Ca} \\ v_{Si}
+EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
 \end{pmatrix}
@@
 In a Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
-for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior
+for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior\footnote{
+Visualization of the LKJ correlation distribution can be found in \url{http://www.psychstatistics.com/2014/12/27/d-lkj-priors/}.}
 \citep{Lewandowski20091989} and standard
 deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
- $0.1$ and scale $0.1$ mag restricted to positive values.
+ $0.1$ and scale $0.1$ mag restricted to positive values.  (We find that imposing a stricter assumption of a
+ diagonal covariance matrix, with no reference to a correlation matrix with LKJ prior, yields the same parameter distributions within
+ uncertainty).
 
@@
 the Monte Carlo chains have not converged to the stationary posterior distribution.
+We have rurun the analysis with a variety of initial conditions, including one with all the $\gamma$'s and $\delta$'s equal to zero, except for a small positive 
+$\gamma_0$ and small negative $\delta_0$ to satisfy our limit conditions.  Parameter credible intervals
+remain consistent within uncertainty.
 
@@
 $EW_{Si}$.  This validates our hypothesis that spectral indicators
-are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $v_{Si}$) are consistent with zero within one sigma.
+are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero within one sigma.
 The effect of spectral parameters on color is shown in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$:
@@
 We do not detect a significant association between
-$v_{Si}$ and color.
+$\lambda_{Si}$ and color.
 
@@
 
-The best-fit distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
+None of the 4000 links of
+our Monte Carlo chains for $\delta$ exceed 0 (see Figure~\ref{global:fig}), we thus claim detection of an affect of the
+intrinsic parameter on supernova magnitudes
+with probability $>3999/4000$. 
+The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
 Although the posteriors of $\delta$ are close to Gaussian, $\delta_1-\delta_2$ can approach zero, resulting in the
 elongated tail in negative  $R_{\delta X}$.
-All values are negative and inconsistent with zero: a color excess in $B-V$ produces a brightening of the supernova.
+All values are negative and inconsistent meaning a color excess in $B-V$ produces a brightening of the supernova.
 The values of $\delta_X/\delta_V-1$ are not monotonic with color: they increase from the $U$ to $V$, and then decrease
@@
 $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
-$A_{B, eff} = \gamma_1 k + \delta_1D$.
+$A_{V, eff} = \gamma_1 k + \delta_1D$.
 Recall that in our model the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrary
 fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$.
-Our model does not provide a unique value for the statistic $R_{B,eff} = A_{B, eff} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
-However, the model can show that  $R_{B,eff}$  decreases on average with increasing effective color excess.
-
-We plot $E_{eff}(B-V) + const$ versus
-$A_{B, eff}$ for the SNf sample in Figure~\ref{rveff:fig}.
-Overplotted is the expected extinction due to a pure extrinsic extinction with slope equal to $\gamma_1$.
-The constant added to the effective color excess
-corresponds to specifying a specific color as having zero extinction, and is chosen  qualitatively to form a ridge line 
-bounding the high-extinction side of the data; the discussion that follows does not depend on the specific choice of the constant.
-The right plot of Figure~\ref{rveff:fig} shows  how much more extinction (relatively) is
-observed compared to the expected extinction from extrinsic dust for the corresponding effective color excess,
- $\Delta A_B =  A_{B,eff}- \gamma_1 E_{eff}(B-V)$.
-Over all effective color excesses the difference is capped by the ridge line, except for extremely
-blue supernovae that lie slightly but noticeably above the ridge line.
-However, with increasing effective color excess there is a broadening of the distribution toward lower observed extinctions.
-A linear fit between $E_{eff}(B-V)$  and $\Delta A_B$ gives a slope of $-0.45 \pm 0.11$.
+Our model does not provide a unique value for the statistic $R_{V,eff} = A_{V, eff} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
+
+To impose specificity for qualitative discussion, we add offsets to $A_{B, eff}$ and $E_{eff}(B-V)$ to  set the
+blue/bright corner of the distribution to roughly $E_{eff}(B-V)=0$ and $A_{B, eff}=0$  as shown in Figure~\ref{rveff:fig}.
+Overplotted is the expected extinction due to a pure extrinsic extinction with slope equal to $\gamma_2$.
+The right plot of Figure~\ref{rveff:fig} shows 
+the effective total-to-selective extinction $R_{V,eff} = A_{V, eff}/E_{eff}(B-V)$.
+Over all effective color-excess, $R_{V,eff}$ is bounded by a maximum value.  At blue colors there is a wide range of $R_{eff,V}$
+but with large uncertainties.  At redder colors, the spread in $R_{eff,V}$ decreases but the uncertainties also decrease to 
+show a number of per-supernova
+inconsistencies with the maximum bound.
 
@@
    \includegraphics[width=2.8in]{output11/rveff.pdf}
-   \includegraphics[width=2.8in]{output11/rveffres.pdf}
+   \includegraphics[width=2.8in]{output11/rveff2.pdf}
    \caption{Left: Effective color excess $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and effective $B$-band ``extinction''
-$A_{B, eff} = \gamma_1 k + \delta_1D$ for the SNf sample.  Overplotted is the expected relationship for color-excess
-purely due to the intrinsic $\gamma$ term.   The zero of  $E_{eff}(B-V)$  is shifted so that the  the extrinsic dust expectation qualitatively forms a ridge line
-bounding the high-extinction side of the data.
-Right:  The observed extinction compared to that expected  from extrinsic dust $\Delta A_B =  A_{B,eff}- \gamma_1 E_{eff}(B-V)$.
+$A_{V, eff} = \gamma_1 k + \delta_1D$ for the SNfactory sample.  Overplotted is the expected relationship for color-excess
+purely due to the intrinsic $\gamma$ term. 
+Right:  The inferred $R_{V,eff} = A_{V, eff}/E_{eff}(B-V)$.
    \label{rveff:fig}}
@@
 
-Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
+Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
 $\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
@@
 heavily extinguished by host-galaxy dust.
-Outliers  are also clearly distinguished in  $EW_{Ca}$--$v_{Si}$ space.
+Outliers  are also clearly distinguished in  $EW_{Ca}$--$\lambda_{Si}$ space.
 
@@
    \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
-   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as the grey offset
+   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as the grey offset
 $\Delta$.
@@
 
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$ are given in the matrix
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$ are given in the matrix
 \begin{equation}
@@
 \end{equation}
-Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  
+Again  $EW_{Ca}$--$\lambda_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  
 External $E_\gamma(B-V)$ dust is
@@
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
-\citet{2011ApJ...729...55F} and the above authors
+Our model predicts an observed range of effective $R_V$ from a single form of extrinsic dust, as is borne out by the
+SNf sample shown in Figure~\ref{rveff:fig}. 
+\citet{2011ApJ...731..120M, 2011ApJ...729...55F} and the above authors
 find that supernovae with large $E_o(B-V)$ 
 preferentially exhibit low $R^F_V$. 
-Our model predicts both of these effects with a single form of extrinsic dust, as is borne out by the
-SNf sample shown in Figure~\ref{rveff:fig}. 
-Our model also predicts that the converse also holds: supernovae with the smallest $E_o(B-V)$ due to intrinsic color
-will appear overly faint when analyzed within the context of a canonical dust.
-The trend in Figure~\ref{rveff:fig} showing an increased range of brighter-than-expected magnitudes  with increasing $E_{eff}(B-V)$  can
-be compared
-to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of the color $C$ parameter (directly
-comparable to $E(B-V)$) from the Hubble diagram analysis of \citet{2014A&A...568A..22B}.
-A linear fit for the relationship between color and Hubble residual has a significant slope ($-0.57 \pm 0.07$), consistent with the slope
-found for the SNfactory data.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/betoule.pdf} 
-   \caption{Best-fit SN~Ia  $B$-band Hubble residuals as a function of the best-fit color parameter $C$ from the cosmology analysis of \citet{2014A&A...568A..22B}.
-   \label{betoule:fig}}
-\end{figure}
-
-\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, whereas
-our values of $\eta$ are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant affect on color, not particularly 
+Our model does predict low effective $R_V$ in the red, though less so then in the blue.  
+We remark though that for fixed measurement uncertainty, the highest color-excess supernovae have the highest signal-to-noise
+in the measurement of $R_V$.
+
+%The trend in Figure~\ref{rveff:fig} showing an increased range of brighter-than-expected magnitudes  with increasing $E_{eff}(B-V)$  can
+%be compared
+%to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of the color $C$ parameter (directly
+%comparable to $E(B-V)$) from the Hubble diagram analysis of \citet{2014A&A...568A..22B}.
+%A linear fit for the relationship between color and Hubble residual has a significant slope ($-0.57 \pm 0.07$), consistent with the slope
+%found for the SNfactory data.
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=3.2in]{output11/betoule.pdf} 
+%   \caption{Best-fit SN~Ia  $B$-band Hubble residuals as a function of the best-fit color parameter $C$ from the cosmology analysis of \citet{2014A&A...568A..22B}.
+%   \label{betoule:fig}}
+%\end{figure}
+
+\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
+\citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
+The values of $\eta$ in this article are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant affect on color, not particularly 
 surprising as they
 are strong features in the $B$ band.
-Recall that we find a correlation between $v_{Si}$ and $EW_{Ca}$
+Recall that we find a correlation between $\lambda_{Si}$ and $EW_{Ca}$
 Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover

### 2016-09-09 forgerard.tex
make better RV red color argument

@@
 
+\usepackage{color}
 \linenumbers
@@
 dust extinction, is consistent with an $R_V=2.5$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
-is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: the wide range and
-the low values of inferred $R_V$ among
-SNe~Ia, and the colors of SN~2014J.
+is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: 
+\textcolor{red}{
+the wide range of inferred $R_V$ among
+SNe~Ia, the systematically lower $R_V$ of redder supernovae relative to the upper bound of the full population,} and the colors of SN~2014J.
 \end{abstract}
@@
 
+\color{red}
+
+The differences between observed colors and the colors predicted from the analysis are shown in Figure~\ref{residual:fig}.
+There are no apparent systematic trends over the span of colors.  The intrinsic color dispersions from our model are described
+later in our discussion of the inferred $C_c$.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5in]{output11/residual.pdf} 
+            \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
+            of predicted colors.  For reference a dotted line is plotted at zero difference.}
+            \label{residual:fig}}
+\end{figure}
+
+\color{black}
+
 For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma$
@@
    \label{ebv:fig}}
-\end{figure}
-
-Our model predicts that internal and external effects for each supernova  conflate into an effective color excess
-$E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
-$A_{V, eff} = \gamma_1 k + \delta_1D$.
-Recall that in our model the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrary
-fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$.
-Our model does not provide a unique value for the statistic $R_{V,eff} = A_{V, eff} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
-
-To impose specificity for qualitative discussion, we add offsets to $A_{B, eff}$ and $E_{eff}(B-V)$ to  set the
-blue/bright corner of the distribution to roughly $E_{eff}(B-V)=0$ and $A_{B, eff}=0$  as shown in Figure~\ref{rveff:fig}.
-Overplotted is the expected extinction due to a pure extrinsic extinction with slope equal to $\gamma_2$.
-The right plot of Figure~\ref{rveff:fig} shows 
-the effective total-to-selective extinction $R_{V,eff} = A_{V, eff}/E_{eff}(B-V)$.
-Over all effective color-excess, $R_{V,eff}$ is bounded by a maximum value.  At blue colors there is a wide range of $R_{eff,V}$
-but with large uncertainties.  At redder colors, the spread in $R_{eff,V}$ decreases but the uncertainties also decrease to 
-show a number of per-supernova
-inconsistencies with the maximum bound.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output11/rveff.pdf}
-   \includegraphics[width=2.8in]{output11/rveff2.pdf}
-   \caption{Left: Effective color excess $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and effective $B$-band ``extinction''
-$A_{V, eff} = \gamma_1 k + \delta_1D$ for the SNfactory sample.  Overplotted is the expected relationship for color-excess
-purely due to the intrinsic $\gamma$ term. 
-Right:  The inferred $R_{V,eff} = A_{V, eff}/E_{eff}(B-V)$.
-   \label{rveff:fig}}
 \end{figure}
@@
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
-Our model predicts an observed range of effective $R_V$ from a single form of extrinsic dust, as is borne out by the
-SNf sample shown in Figure~\ref{rveff:fig}. 
 \citet{2011ApJ...731..120M, 2011ApJ...729...55F} and the above authors
@@
 preferentially exhibit low $R^F_V$. 
-Our model does predict low effective $R_V$ in the red, though less so then in the blue.  
-We remark though that for fixed measurement uncertainty, the highest color-excess supernovae have the highest signal-to-noise
-in the measurement of $R_V$.
+\color{red}
+In our model internal and external effects for each supernova  conflate into an effective color excess
+$E_{eff}(X-V) = E_\gamma(X-V) + E_\delta(X-V)$ and effective $V$ extinction $A_{eff,V} = \gamma_2 k  + \delta_2 D$ 
+Recall that the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrarily
+fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$:
+there is no unique value for the statistic $R_{eff,V} = A_{eff,V} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
+For specificity in the current qualitative discussion, 
+let us consider a set of SNe~Ia  with parameters set to the median fit values of the SNfactory sample.
+We specify   $E_{eff}(U-V)$  and $E_{eff}(B-V)$ by
+assigning the blue-extreme colors of this set close to  zero color excess, 
+as shown in bottom-left corner in the left plot of Figure~\ref{rveff:fig}.
+For this choice of color zeropoints,
+$R_{eff,U} - R_{eff,V} = E_{eff}(U-V) /E_{eff}(B-V)$ is plotted
+in the right of Figure~\ref{rveff:fig}.
+At extreme blue effective color there is a tight range of  $R_{eff,U} - R_{eff,V}$ values.  The distribution spreads to significantly 
+lower   $R_{eff,U} - R_{eff,V}$ as supernovae appear redder but
+then reconverge to higher, tighter values at extreme red effective color.
+The variation in  $R_{eff,U} - R_{eff,V}$ is attributed to the varying contributions of internal and external color excess: the bottom plot of
+Figure~\ref{rveff:fig} shows that the shift to lower values occurs when the effective color excess is dominated by the internal contribution. 
+Since the standard deviation of the $E_\delta(B-V)$ distribution is  narrow compared to that of
+ $E_\gamma(B-V)$, low values of $R_{eff,U} - R_{eff,V}$ can only occur
+at low $E_{eff}(X-V)$.
+ The  \citet{1999PASP..111...63F} dust model interprets
+ low values of $R_{eff,U} - R_{eff,V}$ as implying high values of $R_V$ (see Figure~\ref{ebv:fig}),   and would hence infer a
+ broad range of  $R_V$ at bluer colors, and a narrow range of low $R_V$  for the reddest supernovae.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/rveff.pdf}
+   \includegraphics[width=2.8in]{output11/rveff2.pdf}
+   \includegraphics[width=2.8in]{output11/rveff3.pdf}
+      \caption{\textcolor{red}{Left: Effective color excess $E_{eff}(B-V)$ versus $E_{eff}(U-V)$
+   where $E_{eff}(X-V)   = E_\gamma(X-V) + E_\delta(X-V) - z_X$
+   for a set of SNe with parameters set to those of the medians of the objects in our analysis.
+   The $z_X$ represents a choice of colors at zero color-excess so that the lower left corner points have values approaching zero. 
+Right:  The inferred $R_{eff,U}- R_{eff,V} = E_{eff}(U-V)/E_{eff}(B-V)$.
+Bottom:  $R_{eff,U}- R_{eff,V}$ as a function of the relative contributions of extrinsic and intrinsic color effects $E_\gamma(B-V)/E_\delta(B-V)$.}
+   \label{rveff:fig}}
+\end{figure}
+\color{black}
 

### 2016-09-10 forgerard.tex
forging on

@@
 One parameter, interpreted as due to extrinsic host-galaxy
-dust extinction, is consistent with an $R_V=2.5$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
+dust extinction, is consistent with an $R_V=3.06$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
 is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: 
@@
 $\delta$--$D$ and $\gamma$--$k$.
+\color{red}
+We assign $k$ and $D$ identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ is non-trivial.
 Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
-each other,
-as confirmed by recalculation of the posterior after exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
+each other, as is apparent after 
+running the Monte Carlo with exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
+The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
+otherwise identical initial conditions for $\gamma$, $\delta$ give them identical posteriors
+with broader credible intervals and lower maximum likelihood than when the initial conditions are different.
+\color{black}
 As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
@@
 
-The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  
-Our measurements of
-$R_X$ and $\frac{\gamma_X}{\gamma_2}$, placed at the effective wavelength of the supernova flux that passes
-through the synthetic bands, are shown in
-Figure~\ref{ccm:fig}.
-Also plotted are the expectations of the \citet{1999PASP..111...63F} dust model for different values of its parameter $R^F_V$.
-The $R_X$ are consistent with  $R^F_V=2.5$.  The 
- alternative parameterization
- of $\gamma_X/\gamma_2$ has significantly smaller
-uncertainties and is also consistent with $R^F_V=2.5$.
+\color{red}
+The 68\% credible intervals of $\gamma$ are shown in Figure~\ref{fitz:fig}.
+A fit of the output $\gamma$ parameters to the dust model of \citet{1999PASP..111...63F} gives $R^F_V=3.06\pm 0.18$.
+\color{black}
 
@@
    \centering
-   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
-      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
-   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$.
-   \label{rx:fig}}
+   \includegraphics[width=3.2in]{output11/fitz.pdf}
+   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=3.06$.}
+   \label{fitz:fig}}
 \end{figure}
 
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output11/ccm.pdf}
-      \includegraphics[width=2.8in]{output11/ccm2.pdf} 
-   \caption{68\% credible intervals of Left: $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$; Right: $\frac{\gamma_X}{\gamma_2}$. 
-   \citet{1999PASP..111...63F} dust
-   predictions for these parameters are overlaid for different values of the dust-parameter $R^F_V$.
-   \label{ccm:fig}}
-\end{figure}
+%
+%The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  
+%Our measurements of
+%$R_X$ and $\frac{\gamma_X}{\gamma_2}$, placed at the effective wavelength of the supernova flux that passes
+%through the synthetic bands, are shown in
+%Figure~\ref{ccm:fig}.
+%
+%
+
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output11/ccm.pdf}
+%      \includegraphics[width=2.8in]{output11/ccm2.pdf} 
+%   \caption{68\% credible intervals of Left: $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$; Right: $\frac{\gamma_X}{\gamma_2}$. 
+%   \label{ccm:fig}}
+%\end{figure}
 
@@
 
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
+      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
+   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$.
+   \label{rx:fig}}
+\end{figure}
+
 The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
@@
 \end{figure}
+
+\color{red}
+The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
+for our sample, as shown in Figure~\ref{x1:fig}.
+On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$.  We conclude that the
+intrinsic parameter does not arise to compensate for the fact that light-curve shape is not explicitly
+contained in our model.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/x1si.pdf}
+   \includegraphics[width=2.8in]{output11/x1D.pdf}
+    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
+   \label{x1:fig}}
+\end{figure}
+
+\color{black}
 
@@
 $E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ contributions.
-Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the highest median value for 
-$E_\gamma(B-V)$ is $  0.33 \pm 0.04$ and for $E_\delta(B-V)$ is
+Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the
+\color{red}
+extreme median values for 
+$E_\gamma(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
+and for $E_\delta(B-V)$ $-0.01 \pm 0.01$  and
 $  0.07 \pm 0.03$ 
+\color{black}
 (see Figure~\ref{ebv:fig}).
-In both parameters SN~2014J lives well outside the range of supernovae used to train the coefficients of the model.
+\textcolor{red}{In both parameters (which are relative to SN~2011fe), SN~2014J lives well outside the 
+span} of supernovae used to train the coefficients of the model.
 
@@
 extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
-affect supernova magnitudes and colors.  The external color parameter has behavior consistent with $R^F_V=2.5$ \citet{1999PASP..111...63F} dust,
+affect supernova magnitudes and colors.  The external color parameter has behavior consistent with $R^F_V=3.06$ \citet{1999PASP..111...63F} dust,
 whereas the internal color parameter is inconsistent with dust or a blackbody.  This model  does an excellent job in
@@
 We specify   $E_{eff}(U-V)$  and $E_{eff}(B-V)$ by
-assigning the blue-extreme colors of this set close to  zero color excess, 
+assigning zero color excess close to the blue-extreme colors of this set, 
 as shown in bottom-left corner in the left plot of Figure~\ref{rveff:fig}.
@@
 in the right of Figure~\ref{rveff:fig}.
-At extreme blue effective color there is a tight range of  $R_{eff,U} - R_{eff,V}$ values.  The distribution spreads to significantly 
+Around $E_{eff}(B-V) \sim 0$ the $R_{eff,U} - R_{eff,V}$ values are high, but this is also the regime where their observational  uncertainties 
+blow up due to a division of a number close to zero.
+The distribution spreads to significantly 
 lower   $R_{eff,U} - R_{eff,V}$ as supernovae appear redder but
-then reconverge to higher, tighter values at extreme red effective color.
-The variation in  $R_{eff,U} - R_{eff,V}$ is attributed to the varying contributions of internal and external color excess: the bottom plot of
-Figure~\ref{rveff:fig} shows that the shift to lower values occurs when the effective color excess is dominated by the internal contribution. 
+then reconverge to higher, tighter values red effective color, with asymptote  $R_{eff,U} - R_{eff,V} >1.8$.
+This cause of this asymptotic behavior is due to the relatively higher contribution of extrinsic over intrinsic color excess to the effective color excess, as
+seen in the bottom plot of
+Figure~\ref{rveff:fig}. 
 Since the standard deviation of the $E_\delta(B-V)$ distribution is  narrow compared to that of
@@
  The  \citet{1999PASP..111...63F} dust model interprets
- low values of $R_{eff,U} - R_{eff,V}$ as implying high values of $R_V$ (see Figure~\ref{ebv:fig}),   and would hence infer a
- broad range of  $R_V$ at bluer colors, and a narrow range of low $R_V$  for the reddest supernovae.
-
+ low values of $R_{eff,U} - R_{eff,V}$ as implying high values of $R_V$,
+for example $R_{eff,U} - R_{eff,V}=1.70$ for $R_V=3.06$,  $R_{eff,U} - R_{eff,V}=1.81$ for $R_V=1.5$ (see Figure~\ref{ebv:fig}).
+The $R_V$ inferred for the reddest supernovae would be $R_V<1.5$, even though their colors are dominated by 
+extrinsic $R^F_V=3.06$ dust; this is due our zero colors being (qualitatively) assigned to supernovae that have bluest extrinsic AND intrinsic color excess.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page

### 2016-09-11 forgerard.tex
plowing on

@@
 
-\color{red}
-The 68\% credible intervals of $\gamma$ are shown in Figure~\ref{fitz:fig}.
-A fit of the output $\gamma$ parameters to the dust model of \citet{1999PASP..111...63F} gives $R^F_V=3.06\pm 0.18$.
-\color{black}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/fitz.pdf}
-   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=3.06$.}
-   \label{fitz:fig}}
-\end{figure}
-
 %
@@
 
-\color{red}
-The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
-for our sample, as shown in Figure~\ref{x1:fig}.
-On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$.  We conclude that the
-intrinsic parameter does not arise to compensate for the fact that light-curve shape is not explicitly
-contained in our model.
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output11/x1si.pdf}
-   \includegraphics[width=2.8in]{output11/x1D.pdf}
-    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
-   \label{x1:fig}}
-\end{figure}
-
-\color{black}
-
 The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
@@
  \end{pmatrix} \text{mag}^2.
+ \label{mag_cov:eqn}
  \end{equation}
@@
 describing SN~2014J, a supernova not used in the training that has atypical colors.
+
+\color{red}
+Our model does not explicitly include light-curve shape, which is known to track SN~Ia diversity.
+The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
+for our sample, as shown in Figure~\ref{x1:fig}.
+On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
+Our magnitude residuals  given in Eqn.~\ref{mag_cov:eqn} are comparable to those of SALT2
+\citep[Fig.\ 8 of][]{2010A&A...523A...7G}, showing no obvious disadvantage from not using $X_1$.
+Figure~\ref{x1res:fig} shows the difference between observed and model-predicted colors,
+as a function of $X_1$.  For all colors, there appear non-linear correlations between $X_1$ and color residuals,
+with a negative slope for $X_1<0$ and positive slope for $X_1>0$.
+The SN~Ia time evolution does convey information not captured by the peak-magnitude spectral features used in
+the current analysis, and  a linear model may be incapable of doing so.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/x1si.pdf}
+   \includegraphics[width=2.8in]{output11/x1D.pdf}
+    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
+   \label{x1:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5in]{output11/residualx1.pdf}
+    \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
+            of the SALT2 light-curve shape parameter $X_1$.  For reference a dotted line is plotted at zero difference.}
+   \label{x1res:fig}}
+\end{figure}
+
+\color{black}
+
+\color{red}
+The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model.
+The posteriors of $\gamma$ are fit to the dust model of \citet{1999PASP..111...63F}, giving
+$R^F_V=3.06\pm 0.18$;  Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and the
+result of the fit.  Note that  unlike the $R_V$ posteriors, 
+the posteriors of $\gamma$ are well-approximated by a normal distribution, which is used for the fit.
+\color{black}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/fitz.pdf}
+   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=3.06$.}
+   \label{fitz:fig}}
+\end{figure}
 
@@
 Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
-non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, just not as strongly as the equivalent widths,
+non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, 
+\textcolor{red}{but the equivalent-width corrections are preferred as they give lower residual dispersions $C_c$},
 and  anticipate that in the previous analysis the equivalent widths of CaII and 

### 2016-09-11 view11.py

@@ -710,6 +710,26 @@ pp = PdfPages(filename)
 plt.savefig(pp,format='pdf')
 pp.close()
 plt.clf()
+
+cind=[0,1,3,4]
+cname = ['U','B','R','I']
+fig, axes = plt.subplots(nrows=4)
+for i in xrange(4):
+    (y, ymin, ymax) = numpy.percentile(correction[cind[i],:,:],(50,50-34,50+34),axis=0)
+    err = numpy.sqrt(color_cov[:,i,i] + ((ymax-ymin)/2)**2)
+    axes[i].errorbar(x1,color_obs[:,i]-y,xerr=[x1_err,x1_err], yerr=[err,err],fmt='.')
+    axes[i].set_xlabel(r'$X_1$'.format(cname[i]))
+    lname = r'$({0}_o-V_o) - ({0}-V)_{{model}}$'.format(cname[i])
+    axes[i].set_ylabel(lname)
+    axes[i].axhline(y=0,linestyle=':')
+fig.subplots_adjust(hspace=.3)
+fig.set_size_inches(8,11)
+filename = 'output11/residualx1.pdf'
+pp = PdfPages(filename)
+plt.savefig(pp,format='pdf')
+pp.close()
+plt.clf()
+
 # fig, axes = plt.subplots(nrows=len(filts),sharex=True)
 # xerr = numpy.sqrt(EW_cov[:,0,0]) 
 # for i in xrange(len(filts)):

### 2016-09-12 forgerard.tex
more changes

@@
 \end{figure}
+
+An alternative way to specify $R_V$ is to consider colors relative to a canonical supernova,
+ the model prediction being
+\begin{equation}
+R_{eff, V} = \frac{\gamma_1  (k-k_0) + \delta_1 (D-D_0) }{(\gamma_1-\gamma_2) (k-k_0) + (\delta_1-\delta_2) (D-D_0) },
+\end{equation}
+where $k_0$ and $D_0$ are the parameter values of the canonical supernova.
+If $D = D_0$, the $R_V = \gamma_1/(\gamma_1-\gamma_2)$ of the extrinsic contribution is recovered:
+this is not the case when $D \ne D_0$.  Again considering a set of SNe~Ia  with parameters set to the median fit values of the SNfactory sample,
+the values for $R_{eff,V}$ choosing a canonical supernova with $k_0=0$, $\delta_0=0$  is shown in Figure~\ref{rv4:fig}.
+The reddest supernovae exhibit a range of $1.5< R_{eff,V}<3.5$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/rveff4.pdf}
+      \caption{\textcolor{red}{Effective total-to-selective extinction $R_{eff, V}$
+      with color excess defined relative to  a
+      $k_0=0$, $\delta_0=0$ supernove,  for  a set of SNe~Ia  with parameters set to the median fit values of the SNfactory sample.}
+   \label{rv4:fig}}
+\end{figure}
+
 \color{black}

### 2016-09-12 view11.py

@@ -128,8 +128,24 @@ offset = 0.01
 au = fit['gamma'][:,0][:,None]*fit['k'] + fit['rho1'][:,0][:,None]*fit['R']
 ab = fit['gamma'][:,1][:,None]*fit['k'] + fit['rho1'][:,1][:,None]*fit['R']
 av = fit['gamma'][:,2][:,None]*fit['k'] + fit['rho1'][:,2][:,None]*fit['R']
+
+
 (x, xmin, xmax) = numpy.percentile(ab-av,(50,50-34,50+34),axis=0)
 (y, ymin, ymax) = numpy.percentile(au-av,(50,50-34,50+34),axis=0)
+
+plt.scatter(x ,numpy.median(av/(ab-av),axis=0))
+plt.ylim((-2,6))
+plt.xlim((-0.1,.4))
+plt.ylabel(r'$R_{eff,V}$')
+plt.xlabel(r'$E_{eff}(B-V)$')
+pp = PdfPages("output11/Rveff4.pdf")
+plt.savefig(pp,format='pdf')
+pp.close()
+plt.close()
+
+wefew
+
+
 x=x-x.min()-offset*1.3
 y=y-y.min()-offset
 plt.scatter(x,y)
@@ -166,6 +182,8 @@ pp = PdfPages("output11/Rveff3.pdf")
 plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
+
+
 
 # plt.scatter(numpy.median((fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['k'],axis=0), mag_obs[:,2])
 # x=numpy.array([-0.08, 0.37])

### 2016-09-12 forgerard.tex
a stable version before vacation

--- 2016-09-11 forgerard.tex
@@
 the wide range of inferred $R_V$ among
-SNe~Ia, the systematically lower $R_V$ of redder supernovae relative to the upper bound of the full population,} and the colors of SN~2014J.
+SNe~Ia, the systematically lower inferred $R_V$ of redder supernovae relative to the upper bound of the full population,} and the colors of SN~2014J.
 \end{abstract}
@@
 
-Supernova-frame synthetic photometry is generated for the top-hat filter system
-described in \citet{2011A&A...529L...4C}, which is comprised of five logarithmically-spaced bands spanning
-3276--8635 \AA; the bands have approximate correspondence to $UBVRI$ and are thus referred to as such.
+Supernova-frame synthetic photometry is generated for a top-hat filter system
+comprised of five 
+\color{red}
+bands with the following wavelength ranges: $U$ $[3300.00 - 3978.02]$\AA;
+$B$ $[3978.02-4795.35]$\AA;
+$V$ $[4795.35-5780.60]$\AA;
+$R$ $[5780.60-6968.29]$\AA;
+$I$ $[6968.29-8400.00]$\AA.
+\color{black}
 For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
@@
 The global parameters $\gamma$ are the slopes that connect the extrinsic-color
-parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
+parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose that
+\color{red}
+each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ are the number of objects in our sample: these
+conditions break the 
+degeneracies  $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1}k$ and $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
+Furthermore we impose
+\color{black} 
 \begin{equation}
@@
 with  simultaneous sign flips of
-$\delta$--$D$ and $\gamma$--$k$.
+$\delta$--$D$ and $\gamma$--$k$
 \color{red}
-We assign $k$ and $D$ identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ is non-trivial.
+(when running our fits, $k$ and $D$ are set to
+identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ is non-trivial.)
 Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
@@
 The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
-otherwise identical initial conditions for $\gamma$, $\delta$ give them identical posteriors
-with broader credible intervals and lower maximum likelihood than when the initial conditions are different.
+otherwise identical initial conditions for $\gamma$, $\delta$ produce indistinguishable posteriors
+with relatively broader credible intervals and lower maximum likelihood.
 \color{black}
@@
 
-The differences between observed colors and the colors predicted from the analysis are shown in Figure~\ref{residual:fig}.
-There are no apparent systematic trends over the span of colors.  The intrinsic color dispersions from our model are described
-later in our discussion of the inferred $C_c$.
+The differences between observed and model-predicted supernova colors are shown in Figure~\ref{residual:fig}:
+no systematic trends are apparent (in \S\ref{discussion:sec} we look for trends with light-curve shape.) 
+The scatters in the plots, i.e.\ the residual intrinsic color dispersions from our model, are described
+later when we discuss the inferred $C_c$.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
    \includegraphics[width=5in]{output11/residual.pdf} 
-            \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
+            \caption{\textcolor{red}{Differences between observed and  model-predicted supernova colors  as a function
             of predicted colors.  For reference a dotted line is plotted at zero difference.}
@@
 &
-$-0.393^{ 0.182}_{-0.208}$
-&
-$-0.224^{ 0.101}_{-0.117}$
+$ -0.39^{  0.18}_{ -0.21}$
+&
+$ -0.22^{  0.10}_{ -0.12}$
 &
@@
 &
-$-0.056^{ 0.051}_{-0.046}$
-&
-$-0.147^{ 0.096}_{-0.089}$
+$ -0.06^{  0.05}_{ -0.05}$
+&
+$ -0.15^{  0.10}_{ -0.09}$
 \\
@@
 (see Figure~\ref{ebv:fig}).
-\textcolor{red}{In both parameters (which are relative to SN~2011fe), SN~2014J lives well outside the 
+\textcolor{red}{The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
 span} of supernovae used to train the coefficients of the model.
@@
 On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
-Our magnitude residuals  given in Eqn.~\ref{mag_cov:eqn} are comparable to those of SALT2
-\citep[Fig.\ 8 of][]{2010A&A...523A...7G}, showing no obvious disadvantage from not using $X_1$.
+Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
+\citep{2010A&A...523A...7G}, suffering no  disadvantage from the neglect of $X_1$.
 Figure~\ref{x1res:fig} shows the difference between observed and model-predicted colors,
-as a function of $X_1$.  For all colors, there appear non-linear correlations between $X_1$ and color residuals,
+as a function of $X_1$: for all colors, there appear non-linear correlations 
 with a negative slope for $X_1<0$ and positive slope for $X_1>0$.
-The SN~Ia time evolution does convey information not captured by the peak-magnitude spectral features used in
-the current analysis, and  a linear model may be incapable of doing so.
+We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$; the credible intervals
+from this analysis are given in Table~\ref{globalx1:tab}.  
+The $\sigma_X$ values decrease at the per-mil level and there $<1\sigma$
+shifts in parameters as compared to the previous results. 
+The light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: the most significant non-zero values for
+$\zeta$ are in the $V$ and $I$ bands at less than $1.5 \sigma$, while the $\alpha$'s and $\beta$'s remain significantly
+non-zero.  This finding could be due to a deficiency of our model, 
+as it  is incapable of capturing the non-linear trends in $X_1$ in Figure~\ref{x1res:fig}.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+& $X=0$ &1&2&3&4\\ \hline
+$\alpha_{X}$
+&
+$0.0039^{0.0010}_{-0.0010}$
+&
+$0.0013^{0.0008}_{-0.0008}$
+&
+$0.0015^{0.0007}_{-0.0007}$
+&
+$0.0014^{0.0006}_{-0.0006}$
+&
+$0.0026^{0.0005}_{-0.0005}$
+\\
+${\alpha_X/\alpha_2-1}$
+&
+$   1.6^{   1.1}_{  -0.5}$
+&
+$  -0.1^{   0.2}_{  -0.3}$
+&
+0
+&
+$  -0.1^{   0.1}_{  -0.1}$
+&
+$   0.8^{   0.9}_{  -0.4}$
+\\
+$\beta_{X}$
+&
+$ 0.036^{ 0.005}_{-0.005}$
+&
+$ 0.027^{ 0.004}_{-0.004}$
+&
+$ 0.023^{ 0.004}_{-0.004}$
+&
+$ 0.020^{ 0.003}_{-0.003}$
+&
+$ 0.017^{ 0.003}_{-0.003}$
+\\
+${\beta_X/\beta_2-1}$
+&
+$  0.56^{  0.12}_{ -0.10}$
+&
+$  0.18^{  0.06}_{ -0.06}$
+&
+0
+&
+$ -0.13^{  0.03}_{ -0.02}$
+&
+$ -0.29^{  0.06}_{ -0.06}$
+\\
+$\eta_{X}$
+&
+$0.0013^{0.0012}_{-0.0012}$
+&
+$0.0009^{0.0010}_{-0.0010}$
+&
+$0.0011^{0.0008}_{-0.0008}$
+&
+$0.0010^{0.0007}_{-0.0007}$
+&
+$0.0004^{0.0006}_{-0.0006}$
+\\
+${\eta_X/\eta_2-1}$
+&
+$  0.23^{  0.49}_{ -0.51}$
+&
+$ -0.10^{  0.26}_{ -0.43}$
+&
+0
+&
+$ -0.10^{  0.17}_{ -0.12}$
+&
+$ -0.58^{  0.28}_{ -0.49}$
+\\
+$\zeta_{X}$
+&
+$ 0.012^{ 0.040}_{-0.040}$
+&
+$-0.002^{ 0.033}_{-0.034}$
+&
+$-0.032^{ 0.028}_{-0.028}$
+&
+$-0.014^{ 0.024}_{-0.025}$
+&
+$-0.029^{ 0.021}_{-0.022}$
+\\
+${\zeta_X-\zeta_2-1}$
+&
+$  -0.9^{   0.8}_{  -2.2}$
+&
+$  -0.7^{   0.5}_{  -1.4}$
+&
+0
+&
+$  -0.4^{   0.2}_{  -0.5}$
+&
+$  -0.1^{   0.5}_{  -0.4}$
+
+\\
+${\gamma_X/\gamma_2-1}$
+&
+$  0.61^{  0.05}_{ -0.05}$
+&
+$  0.33^{  0.03}_{ -0.03}$
+&
+0
+&
+$ -0.23^{  0.01}_{ -0.01}$
+&
+$ -0.45^{  0.03}_{ -0.03}$
+\\
+$R_{X}$
+&
+$  4.93^{  0.52}_{ -0.46}$
+&
+$  4.06^{  0.43}_{ -0.38}$
+&
+$  3.06^{  0.34}_{ -0.30}$
+&
+$  2.35^{  0.28}_{ -0.25}$
+&
+$  1.67^{  0.23}_{ -0.20}$
+\\
+${\delta_X/\delta_2-1}$
+&
+$ -0.45^{  0.17}_{ -0.19}$
+&
+$ -0.29^{  0.10}_{ -0.11}$
+&
+0
+&
+$ -0.05^{  0.05}_{ -0.04}$
+&
+$ -0.13^{  0.10}_{ -0.08}$
+\\
+$R_{\delta X}$
+&
+$ -1.92^{  0.90}_{ -1.30}$
+&
+$ -2.48^{  0.82}_{ -1.30}$
+&
+$ -3.48^{  0.90}_{ -1.52}$
+&
+$ -3.30^{  0.83}_{ -1.42}$
+&
+$ -3.03^{  0.78}_{ -1.31}$
+\\
+$\sigma_{X}$
+&
+$ 0.058^{ 0.012}_{-0.011}$
+&
+$ 0.030^{ 0.007}_{-0.007}$
+&
+$ 0.017^{ 0.004}_{-0.007}$
+&
+$ 0.013^{ 0.006}_{-0.008}$
+&
+$ 0.042^{ 0.005}_{-0.004}$
+\\
+\hline
+\end{tabular}
+\caption{68\% credible Intervals for the Global Fit Parameters including $X_1$ \label{globalx1:tab}}
+\end{table}
+
 \color{black}
@@
 \color{red}
-The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model.
-The posteriors of $\gamma$ are fit to the dust model of \citet{1999PASP..111...63F}, giving
-$R^F_V=3.06\pm 0.18$;  Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and the
-result of the fit.  Note that  unlike the $R_V$ posteriors, 
-the posteriors of $\gamma$ are well-approximated by a normal distribution, which is used for the fit.
+The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model
+we now do so in a fit to the 
+model of \citet{1999PASP..111...63F},
+assuming the fixed 3693,  4369,  5287,  6319, 7611 \AA\  for the effective wavelengths of the supernova flux through the bands.
+Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
+$R^F_V=3.06\pm 0.18$.  
+We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
 \color{black}
@@
 there is no unique value for the statistic $R_{eff,V} = A_{eff,V} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
+
 For specificity in the current qualitative discussion, 
@@
 in the right of Figure~\ref{rveff:fig}.
-Around $E_{eff}(B-V) \sim 0$ the $R_{eff,U} - R_{eff,V}$ values are high, but this is also the regime where their observational  uncertainties 
-blow up due to a division of a number close to zero.
+Around $E_{eff}(B-V) \sim 0$ the $R_{eff,U} - R_{eff,V}$ values are high, but this is also the regime where their  uncertainties 
+blow up due to a division of an uncertain quantity with value close to zero.
 The distribution spreads to significantly 
@@
 \end{figure}
+
+An alternative way to specify $R_V$ is to consider colors relative to a canonical supernova,
+ the model prediction being
+\begin{equation}
+R_{eff, V} = \frac{\gamma_1  (k-k_0) + \delta_1 (D-D_0) }{(\gamma_1-\gamma_2) (k-k_0) + (\delta_1-\delta_2) (D-D_0) },
+\end{equation}
+where $k_0$ and $D_0$ are the parameter values of the canonical supernova.
+If $D = D_0$, the $R_V = \gamma_1/(\gamma_1-\gamma_2)$ of the extrinsic contribution is recovered, but this does not hold true
+when $D \ne D_0$.  Again considering a set of SNe~Ia  with parameters equal to the median fit values of the SNfactory sample,
+the values for $R_{eff,V}$ choosing a canonical supernova with $k_0=0$, $\delta_0=0$  is shown in Figure~\ref{rv4:fig}.
+The reddest supernovae exhibit a range of $1.5< R_{eff,V}<3.5$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/rveff4.pdf}
+      \caption{\textcolor{red}{Effective total-to-selective extinction $R_{eff, V}$
+      with color excess defined relative to  a
+      $k_0=0$, $\delta_0=0$ supernove,  for  a set of SNe~Ia  with parameters equal to the median fit values of the SNfactory sample.}
+   \label{rv4:fig}}
+\end{figure}
+
 \color{black}

### 2016-09-15 forgerard.tex
mass step

@@
 the wide range of inferred $R_V$ among
-SNe~Ia, the systematically lower inferred $R_V$ of redder supernovae relative to the upper bound of the full population,} and the colors of SN~2014J.
+SNe~Ia, the systematically lower inferred $R_V$ of redder supernovae relative to the upper bound of the full population,}
+and the colors of SN~2014J,.
+\textcolor{red}{
+The emergence of a new parameter previously accounted for 
+provides an avenue to interpret current Hubble-residual correlations with host-galaxy properties,}
 \end{abstract}
@@
 STAN \citep{stan}. STAN provides output statistics to assess
-the convergence of the output Markov chains.  The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
+the convergence of the output Markov chains.
+\textcolor{red}{
+Define the statistics.
+}
+The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
@@
 as it  is incapable of capturing the non-linear trends in $X_1$ in Figure~\ref{x1res:fig}.
+Note that as we use Monte Carlo methods (as opposed to linear algebra) to evaluate our model, 
+it is straightforward to add and analyze non-linear terms to the model.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 
+51 supernova in Childress
+$  -0.0061 \pm    0.0017$
+$  -0.0052 \pm    0.0015$
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/childress.pdf}
+      \caption{\textcolor{red}{Effective total-to-selective extinction $R_{eff, V}$
+      with color excess defined relative to  a
+      $k_0=0$, $\delta_0=0$ supernove,  for  a set of SNe~Ia  with parameters equal to the median fit values of the SNfactory sample.}
+   \label{childress:fig}}
+\end{figure}
+
 We find an intrinsic supernova parameter that does not have a monotonic influence on supernova magnitudes as a function

### 2016-09-15 childress.py

@@ -1,0 +1,104 @@
+#!/usr/bin/env python
+import numpy
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import rc
+import pickle
+import cPickle
+
+f = open('MJC_compile_SNdata.pkl','r')
+gal= pickle.load(f)
+
+f = open('temp11.pkl','rb')
+(fit, _) = pickle.load(f)
+f.close()
+
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+dic_phreno=cPickle.load(open("phrenology_2016_12_01_CABALLOv1.pkl"))
+
+dic_meta=cPickle.load(open("META.pkl"))
+
+sivel=[]
+sivel_err=[]
+for sn in data['snlist']:
+   if sn in dic_meta.keys() and sn in dic_phreno.keys():
+      meta = dic_meta[sn]
+      vSiII_6355_lbd=0.
+      vSiII_6355_lbd_err=0.
+      counter  = 0
+      for sp in dic_phreno[sn]["spectra"]:
+         if sp in meta['spectra'].keys() and  numpy.abs(meta['spectra'][sp]['salt2.phase'] < 3):
+            vSiII_6355_lbd += dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
+            vSiII_6355_lbd_err += 1/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
+            counter +=1
+      if counter !=0:
+         sivel.append(vSiII_6355_lbd / vSiII_6355_lbd_err)
+         sivel_err.append(1./numpy.sqrt(vSiII_6355_lbd_err))
+      else:
+         sivel.append(float('nan'))
+         sivel_err.append(float('nan'))
+   else:
+      sivel.append(float('nan'))
+      sivel_err.append(float('nan'))
+
+sivel = numpy.array(sivel)
[…]

### 2016-09-18 forgerard.tex
run longer changing day window for velocity

--- 2016-09-12 forgerard.tex
@@
     H.~K.~Fakhouri,\altaffilmark{1,3}
-    U.~Feindt,\altaffilmark{9}
+    U.~Feindt,\altaffilmark{17}
     D.~Fouchez,\altaffilmark{10}
@@
 
+\altaffiltext{16}
+{
+The Oskar Klein Centre, Department of Physics, AlbaNova, Stockholm University, SE-106 91 Stockholm, Sweden
+}
+
 \begin{abstract}
@@
 is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
-dependent on the spectral equivalent widths, and two independent color parameters with better than 0.999 confidence.
+dependent on the spectral equivalent widths, and two independent color parameters with better than 
+%-----
+ $(1-10^{-5})$
+%------
+confidence.
 One parameter, interpreted as due to extrinsic host-galaxy
-dust extinction, is consistent with an $R_V=3.06$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
+dust extinction, is consistent with a \citet{1999PASP..111...63F} dust model with
+%-----
+$R_V=2.97\ \pm 0.18$.
+%------
+ The second parameter is inconsistent with dust and
 is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: 
 \textcolor{red}{
+indirect evidence for intrinsic color dispersion from Hubble residuals;
 the wide range of inferred $R_V$ among
-SNe~Ia, the systematically lower inferred $R_V$ of redder supernovae relative to the upper bound of the full population,} and the colors of SN~2014J.
+SNe~Ia; the systematically lower inferred $R_V$ of redder supernovae relative to the upper bound of the full population;}
+and the colors of SN~2014J,.
+\textcolor{red}{
+The emergence of a new parameter
+provides an avenue to interpret  Hubble-residual correlations with host-galaxy properties,}
 \end{abstract}
@@
 \citep{2007ApJ...659..122J}.\footnote{Light-curve fitters with more flexible degrees of freedom
-\citep[e.g.][]{2008ApJ...681..482C, 2011AJ....141...19B} are used to study SN~Ia heterogeneity.}
+\citep[e.g.][]{2008ApJ...681..482C, 2011AJ....141...19B, 2011ApJ...731..120M} are available and have for
+the most part been used to study SN~Ia heterogeneity.}
 They remain two-parameter models, with one parameter characterizing light-curve shape and the other
@@
 find that high-velocity SiII$\lambda$6355 is found in objects that have red ultraviolet/optical colors near maximum brightness.
-Another approach to probe color diversity is to use multiple colors of a single supernova to infer individual differential reddening. 
+
+\textcolor{red}{
+Another approach to probe color diversity is through multiple colors (at least 3 filters)
+of a single supernova.  Colors are insensitive to the absolute normalization of the incoming flux,
+and their relative values are sensitive to processes of the responsible physics.   For example,
+relative dust absorption varies as a function of wavelength depending on grain size and shape,
+independent (to first order) of the amount of dust along the line of sight.
+}
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find a wide
@@
 the canonical value for diffuse Milky Way dust.
-The also confirm the \citet{2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
+They also confirm the \citet{2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
 In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
-the standard $R_V=3.1$ is recovered for supernovae on average.
+the standard $R_V=3.1$ is recovered on average
+\textcolor{red}{after excluding their $>3 \sigma$ reddest supernovae.}
+
+\textcolor{red}
+{
+Hierarchical modeling has recently opened
+the study of intrinsic supernova color from SN~Ia Hubble diagrams.
+\citet{2016arXiv160904470M} find that the distribution of
+observed supernova magnitudes is better explained by a combination of intrinsic color dispersion and
+$R_V=3.7$ dust, over dust with no color dispersion.
+The introduction of intrinsic dispersion eliminates the apparent bias in Hubble residuals between SNe in low- versus
+high-mass hosts.  They were able to draw these conclusions by using only one
+derived ``color'', the SALT2 fit parameter.
+}
 
@@
 
-The current status of the data and its treatment s presented in \citet{2015ApJ...815...58F}.
+The current status of the data and its treatment is presented in \citet{2015ApJ...815...58F}.
 We provide a brief summary of the points important for this analysis.
@@
 Each spectral time series is
-blue-shifted to rest-frame, and the fluxes converted to luminosity assuming
+blue-shifted to rest-frame, and the fluxes are converted to luminosity assuming
 distances expected for the supernova redshifts given a flat
@@
 as in \citet{chotard:thesis}.
-Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
+Equivalent widths and the
+\textcolor{red}{SiII$\lambda 6355$ wavelength at minimum are taken from spectra  within $\pm 2.5$ days from maximum, in the case of multiple spectra the one
 closest to maximum is used \citep{chotard:thesis}. [Confirm!]
-The weighted mean from phases within 3 days of maximum light is used for the  SiII$\lambda 6355$ velocity.
-
-Our analysis sample is constituted with the  163 supernovae that have the data coverage to 
+The weighted mean is used for the  SiII$\lambda 6355$ wavelength.}
+
+Our analysis sample is comprised by the
+166
+supernovae that have the data coverage to 
 give photometric and spectroscopic statistics described above.
@@
 \startdata
-0 & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
-1 & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6139 \pm   2$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
-2 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6131 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
-3 & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   2$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
+0 & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
+1 & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
+2 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
+3 & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
 4 & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ \\
 5 & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ \\
-6 & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6140 \pm   4$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-7 & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6099 \pm   4$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+6 & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+7 & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
 8 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ \\
-9 & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6099 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
-10 & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6144 \pm   2$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
+9 & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
+10 & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
 11 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ \\
-12 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6112 \pm   4$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
-13 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6115 \pm   2$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
-14 & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6116 \pm   3$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
-15 & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm   4$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
-16 & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6134 \pm   4$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
-17 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6125 \pm   1$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
-18 & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6155 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
-19 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6127 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
-20 & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6132 \pm   1$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
-21 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6130 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
+12 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
+13 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
+14 & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
+15 & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
+16 & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6141 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
+17 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
+18 & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
+19 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
+20 & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
+21 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
 22 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ \\
-23 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6148 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
-24 & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6116 \pm   2$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
-25 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6118 \pm   3$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-26 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6099 \pm   4$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
-27 & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6122 \pm   2$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
-28 & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6128 \pm   1$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
-29 & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6125 \pm   3$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
-30 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6120 \pm   2$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
-31 & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6112 \pm   3$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
-32 & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6141 \pm   3$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
-33 & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6113 \pm   2$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
-34 & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6104 \pm   4$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
-35 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6108 \pm   5$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
-36 & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6130 \pm   3$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-37 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6125 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
-38 & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6168 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
-39 & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6088 \pm   2$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
-40 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6122 \pm   4$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
-41 & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6068 \pm   4$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
-42 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6102 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
-43 & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6122 \pm   3$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
-44 & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6169 \pm   3$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
-45 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6098 \pm   1$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
-46 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6150 \pm   2$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
-47 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
-48 & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6142 \pm   2$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
-49 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
-50 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
-51 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
-52 & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6142 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
-53 & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm   8$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
-54 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   3$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
-55 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6140 \pm   3$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
-56 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6095 \pm   5$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
-57 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6151 \pm   4$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
-58 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6123 \pm   2$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
-59 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6135 \pm   4$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
-60 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6132 \pm   2$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
-61 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ \\
-62 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6112 \pm   3$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
-63 & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6128 \pm   3$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
-64 & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6100 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
-65 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6108 \pm   4$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
-66 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
-67 & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6130 \pm   1$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
-68 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6127 \pm   2$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
-69 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
-70 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6118 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
-71 & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6150 \pm   4$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
-72 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
-73 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
-74 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6109 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
-75 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6142 \pm   2$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
-76 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6084 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
-77 & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6133 \pm   2$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
-78 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6137 \pm   3$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
-79 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6133 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
-80 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6132 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
-81 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-82 & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
-83 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
-84 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   2$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
-85 & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6144 \pm   2$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
-86 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   3$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
-87 & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6142 \pm   3$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
-88 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
-89 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
-90 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-91 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6162 \pm   4$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-92 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6134 \pm   2$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
-93 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6142 \pm   5$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
-94 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6137 \pm   4$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
-95 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6127 \pm   3$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
-96 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6117 \pm   4$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
-97 & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6097 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
-98 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
-99 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6168 \pm   2$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
-100 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
-101 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6134 \pm   5$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
-102 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6197 \pm   7$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
-103 & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6134 \pm   3$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
-104 & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6076 \pm   6$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
-105 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6111 \pm   2$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
-106 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6141 \pm   3$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
-107 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
-108 & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6118 \pm   2$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
-109 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6122 \pm   4$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
-110 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6131 \pm   4$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
-111 & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6126 \pm   2$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
-112 & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
-113 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6108 \pm   4$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
-114 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
-115 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6147 \pm   4$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
-116 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6127 \pm   2$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
-117 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
-118 & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6120 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
-119 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
-120 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
-121 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6155 \pm   2$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
-122 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   3$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
-123 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   3$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
-124 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6112 \pm   4$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
-125 & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6100 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
-126 & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6133 \pm   3$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
-127 & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6114 \pm   2$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
-128 & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6111 \pm   3$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
-129 & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6139 \pm   3$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
-130 & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6120 \pm   2$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
-131 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6120 \pm   5$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
-132 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
-133 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
-134 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
-135 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6131 \pm   3$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
-136 & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6121 \pm   2$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
-137 & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6134 \pm   3$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
-138 & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6139 \pm   3$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
-139 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6128 \pm   6$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
-140 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
-141 & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6113 \pm   2$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
-142 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-143 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6090 \pm   2$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
-144 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6118 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
-145 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
-146 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6119 \pm   3$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
-147 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6140 \pm   3$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
-148 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
-149 & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6129 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
-150 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
-151 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6143 \pm   4$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
-152 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
-153 & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6103 \pm   4$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
-154 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6149 \pm   4$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
-155 & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6126 \pm   2$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
-156 & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6135 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-157 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6124 \pm   2$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
-158 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6116 \pm   3$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
-159 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6146 \pm   4$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
-160 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6157 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
-161 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6112 \pm   3$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
-162 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6153 \pm   4$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\\enddata
+23 & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ \\
+24 & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ \\
+25 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
+26 & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
+27 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+28 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
+29 & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
+30 & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
+31 & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
+32 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
+33 & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
+34 & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
+35 & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
+36 & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6114 \pm   9$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
+37 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
+38 & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+39 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
+40 & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6168 \pm   6$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
+41 & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
+42 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
+43 & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
+44 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
+45 & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
+46 & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
+47 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
+48 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
+49 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
+50 & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
+51 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
+52 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
+53 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
+54 & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
+55 & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
+56 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
+57 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
+58 & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ \\
+59 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
+60 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
+61 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
+62 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
+63 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
+64 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
+65 & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
+66 & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
+67 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
+68 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6127 \pm  10$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
+69 & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6144 \pm   2$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
+70 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
+71 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   4$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
+72 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
+73 & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
+74 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
+75 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
+76 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
+77 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
+78 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
+79 & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
+80 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
+81 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
+82 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
+83 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+84 & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
+85 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
+86 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
+87 & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
+88 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
+89 & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
+90 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
+91 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
+92 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+93 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+94 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
+95 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
+96 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
+97 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
+98 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
+99 & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
+100 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
+101 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
+102 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
+103 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
+104 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
+105 & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
+106 & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
+107 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6112 \pm   2$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
+108 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
+109 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
+110 & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
+111 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
+112 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
+113 & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
+114 & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
+115 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
+116 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
+117 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6148 \pm   4$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
+118 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
+119 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
+120 & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+121 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
+122 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
+123 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
+124 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
+125 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6129 \pm   7$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
+126 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
+127 & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
+128 & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
+129 & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
+130 & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
+131 & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
+132 & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
+133 & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
+134 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
+135 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
+136 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
+137 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
+138 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
+139 & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
+140 & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
+141 & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
+142 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
+143 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
+144 & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
+145 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+146 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
+147 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
+148 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
+149 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
+150 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
+151 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
+152 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
+153 & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
+154 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
+155 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
+156 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
+157 & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
+158 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
+159 & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
+160 & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+161 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
+162 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
+163 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
+164 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
+165 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
+166 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\\enddata
 \end{deluxetable}
@@
 of intrinsic variation is accommodated.
-The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some dispersion.
-An extrinsic physical process (i.e.\ dust) subsequently determines the apparent magnitudes.
+The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
+\textcolor{red}{The intrinsic magnitudes are then
+modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
 
@@
 that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
-on the equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
+on the
+ equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
 $EW_{Ca}$, $EW_{Si}$,
-the SiII$\lambda6355$ position $\lambda_{Si}$ (so also linear with $v_{Si}$):
+\textcolor{red}{ and the 
+the SiII$\lambda6355$ wavelength at minimum $\lambda_{Si}$ (which varies linearly with $v_{Si}$)}:
 these spectral features are associated with SN~Ia  spectroscopic diversity  
-\citep{2006PASP..118..560B,2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
+\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
 $EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
-\citep{2011A&A...529L...4C}. 
+\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
 An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
@@
 otherwise identical initial conditions for $\gamma$, $\delta$ produce indistinguishable posteriors
-with relatively broader credible intervals and lower maximum likelihood.
+with relatively broad credible intervals and lower maximum likelihood.
 \color{black}
@@
 STAN \citep{stan}. STAN provides output statistics to assess
-the convergence of the output Markov chains.  The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
+the convergence of the output Markov chains.
+\textcolor{red}{The 
+potential scale reduction statistic, $\hat{R}$ \citep{Gelman92}, measures the convergence of the target distribution
+in iterative simulations 
+by using multilple sequences to estimate how much that distribution would sharpen if the simulations were run longer.
+$N_{eff}$ is an estimate of the number of independent draws.
+The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
+}
 Empirically, the confidence regions are localized and unimodal as is seen in  Figure~\ref{global:fig}.  We find no evidence that
@@
 & $X=0$ &1&2&3&4\\ \hline
-$\alpha_{X}$
-&
-$0.0042^{0.0009}_{-0.0009}$
-&
-$0.0014^{0.0007}_{-0.0008}$
-&
-$0.0014^{0.0006}_{-0.0006}$
-&
-$0.0014^{0.0005}_{-0.0005}$
-&
-$0.0025^{0.0005}_{-0.0005}$
-\\
-$\alpha_X/\alpha_2-1$
-&
-$   2.0^{   1.3}_{  -0.6}$
-&
-$   0.0^{   0.1}_{  -0.2}$
+$\alpha_X$
+&
+$0.0043^{0.0009}_{-0.0009}$
+&
+$0.0016^{0.0007}_{-0.0007}$
+&
+$0.0015^{0.0006}_{-0.0006}$
+&
+$0.0015^{0.0005}_{-0.0005}$
+&
+$0.0026^{0.0004}_{-0.0005}$
+\\
+${\alpha_X/\alpha_2-1}$
+&
+$   1.9^{   1.0}_{  -0.5}$
+&
+$   0.1^{   0.1}_{  -0.2}$
 &
@@
 &
-$   0.0^{   0.2}_{  -0.1}$
-&
-$   0.8^{   0.9}_{  -0.4}$
-\\
-$\beta_{X}$
-&
-$ 0.033^{ 0.003}_{-0.003}$
-&
-$ 0.027^{ 0.003}_{-0.003}$
-&
-$ 0.027^{ 0.002}_{-0.002}$
-&
-$ 0.021^{ 0.002}_{-0.002}$
+$  -0.0^{   0.1}_{  -0.1}$
+&
+$   0.7^{   0.7}_{  -0.3}$
+\\
+$\beta_X$
+&
+$ 0.032^{ 0.003}_{-0.003}$
+&
+$ 0.025^{ 0.003}_{-0.002}$
+&
+$ 0.025^{ 0.002}_{-0.002}$
 &
 $ 0.020^{ 0.002}_{-0.002}$
-\\
-$\beta_X/\beta_2-1$
-&
-$  0.26^{  0.05}_{ -0.05}$
-&
-$  0.00^{  0.03}_{ -0.03}$
+&
+$ 0.019^{ 0.002}_{-0.002}$
+\\
+${\beta_X/\beta_2-1}$
+&
+$  0.25^{  0.05}_{ -0.05}$
+&
+$ -0.01^{  0.03}_{ -0.03}$
 &
@@
 &
-$ -0.25^{  0.03}_{ -0.03}$
-\\
-$\eta_{X}$
-&
-$0.0010^{0.0012}_{-0.0013}$
-&
-$0.0006^{0.0010}_{-0.0011}$
-&
-$0.0008^{0.0008}_{-0.0009}$
-&
-$0.0008^{0.0007}_{-0.0008}$
-&
-$0.0002^{0.0006}_{-0.0007}$
-\\
-$\eta_X/\eta_2-1$
-&
-$  0.26^{  0.65}_{ -0.65}$
-&
-$ -0.09^{  0.53}_{ -0.55}$
+$ -0.23^{  0.03}_{ -0.03}$
+\\
+$\eta_X$
+&
+$-0.0002^{0.0011}_{-0.0011}$
+&
+$0.0001^{0.0009}_{-0.0009}$
+&
+$0.0005^{0.0008}_{-0.0008}$
+&
+$0.0005^{0.0007}_{-0.0007}$
+&
+$-0.0003^{0.0006}_{-0.0006}$
+\\
+${\eta_X/\eta_2-1}$
+&
+$ -0.38^{  2.21}_{ -1.84}$
+&
+$ -0.32^{  1.51}_{ -1.15}$
 &
@@
 &
-$ -0.08^{  0.24}_{ -0.21}$
-&
-$ -0.57^{  0.51}_{ -0.59}$
-\\
-$\gamma_X/\gamma_2-1$
-&
-$  0.64^{  0.05}_{ -0.05}$
-&
-$  0.34^{  0.03}_{ -0.03}$
+$ -0.11^{  0.28}_{ -0.26}$
+&
+$ -0.86^{  1.69}_{ -1.24}$
+\\
+${\gamma_X/\gamma_2-1}$
+&
+$  0.66^{  0.06}_{ -0.05}$
+&
+$  0.35^{  0.03}_{ -0.03}$
 &
@@
 \\
-$R_{X}$
-&
-$  4.87^{  0.48}_{ -0.43}$
-&
-$  3.96^{  0.40}_{ -0.35}$
-&
-$  2.96^{  0.31}_{ -0.28}$
-&
-$  2.29^{  0.26}_{ -0.23}$
-&
-$  1.64^{  0.21}_{ -0.19}$
-\\
-$\delta_X/\delta_2-1$
-&
-$ -0.39^{  0.18}_{ -0.21}$
-&
-$ -0.22^{  0.10}_{ -0.12}$
+$R_X$
+&
+$  4.79^{  0.49}_{ -0.43}$
+&
+$  3.88^{  0.40}_{ -0.35}$
+&
+$  2.88^{  0.31}_{ -0.28}$
+&
+$  2.22^{  0.25}_{ -0.23}$
+&
+$  1.60^{  0.21}_{ -0.20}$
+\\
+${\delta_X/\delta_2-1}$
+&
+$ -0.31^{  0.18}_{ -0.19}$
+&
+$ -0.17^{  0.10}_{ -0.10}$
 &
@@
 &
-$ -0.06^{  0.05}_{ -0.05}$
-&
-$ -0.15^{  0.10}_{ -0.09}$
-\\
-$R_{\delta X}$
-&
-$ -2.70^{  1.32}_{ -2.44}$
-&
-$ -3.46^{  1.29}_{ -2.65}$
-&
-$ -4.46^{  1.43}_{ -3.11}$
-&
-$ -4.20^{  1.32}_{ -2.89}$
-&
-$ -3.80^{  1.20}_{ -2.61}$
-\\
-$\sigma_{X}$
-&
-$ 0.059^{ 0.012}_{-0.011}$
-&
-$ 0.031^{ 0.007}_{-0.007}$
-&
-$ 0.020^{ 0.004}_{-0.006}$
+$ -0.07^{  0.05}_{ -0.04}$
+&
+$ -0.17^{  0.10}_{ -0.09}$
+\\
+$R_{\delta_X}$
+&
+$ -4.06^{  1.97}_{ -4.44}$
+&
+$ -4.92^{  2.03}_{ -4.95}$
+&
+$ -5.89^{  2.22}_{ -5.67}$
+&
+$ -5.48^{  2.04}_{ -5.24}$
+&
+$ -4.86^{  1.82}_{ -4.66}$
+\\
+$\sigma_X$
+&
+$ 0.061^{ 0.013}_{-0.012}$
+&
+$ 0.034^{ 0.007}_{-0.007}$
+&
+$ 0.021^{ 0.004}_{-0.006}$
 &
@@
 &
-$ 0.043^{ 0.005}_{-0.004}$
+$ 0.044^{ 0.005}_{-0.004}$
 \\
@@
 
-We find small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
-magnitudes.  All bands show larger and significant non-zero values for $\beta$, indicating their sensitivity to
-$EW_{Si}$.  This validates our hypothesis that spectral indicators
+\textcolor{red}{
+We find significant non-zero values for $\alpha$ and $\beta$, indicating that $EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
+magnitudes.}
+This validates our hypothesis that spectral indicators
 are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero within one sigma.
@@
 
-None of the 4000 links of
-our Monte Carlo chains for $\delta$ exceed 0 (see Figure~\ref{global:fig}), we thus claim detection of an affect of the
+None of the 20000 links of 
+our Monte Carlo chains for $\delta$ exceed 0 (see Figure~\ref{global:fig}), we thus claim detection of an effect of the
 intrinsic parameter on supernova magnitudes
-with probability $>3999/4000$. 
+with probability $(1-5\times 10^{-5})$.
 The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
@@
 elongated tail in negative  $R_{\delta X}$.
-All values are negative and inconsistent meaning a color excess in $B-V$ produces a brightening of the supernova.
+All values are significantly negative meaning a color excess in $B-V$ produces a brightening of the supernova.
 The values of $\delta_X/\delta_V-1$ are not monotonic with color: they increase from the $U$ to $V$, and then decrease
@@
 Recall that our boundary conditions set the means of both distributions to zero. 
-The standard deviation of $E_\gamma(B-V)$ is 0.078 mag while that of $E_\delta(B-V)$ is 0.019 mag.
-The range of $B-V$ colors is $\sim 4$ times larger for the external contribution. 
+The standard deviations of $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
+%-----
+0.079
+and 0.015
+%-----
+mag respectively.
+The range of $B-V$ colors is $\sim 5$ times larger for the external contribution. 
 Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red, consistent
@@
 The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
-has a standard deviation of $0.096$ mag, and a broad tail in the positive (fainter) direction.
+has a standard deviation of
+%-----
+$0.10$
+%-----
+mag, and a broad tail in the positive (fainter) direction.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the
-square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from 0.01 to 0.06 mag, significantly smaller
+square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from
+$\sim 0.01$ to 0.06 mag, significantly smaller
 than the dispersion in $\Delta$.
@@
 \begin{pmatrix}
-0.0037 & 0.0010 & -0.0001 & -0.0001 & 0.0003 \\
-0.0010 & 0.0010 & 0.0002 & -0.0000 & -0.0004 \\
--0.0001 & 0.0002 & 0.0004 & 0.0001 & -0.0001 \\
--0.0001 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
-0.0003 & -0.0004 & -0.0001 & 0.0002 & 0.0019
+0.0040 & 0.0011 & -0.0002 & -0.0000 & 0.0003 \\
+0.0011 & 0.0012 & 0.0002 & -0.0000 & -0.0006 \\
+-0.0002 & 0.0002 & 0.0004 & 0.0001 & -0.0002 \\
+-0.0000 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
+0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
  \end{pmatrix} \text{mag}^2.
@@
  \begin{pmatrix}
-0.066 , 0.033 , 0.022 , 0.050 
+0.069 , 0.035 , 0.023 , 0.053
   \end{pmatrix} \text{mag}
@@
 \begin{pmatrix}
-1.000 & 0.634 & -0.256 & -0.300 \\
-0.634 & 1.000 & -0.203 & 0.032 \\
--0.256 & -0.203 & 1.000 & 0.604 \\
--0.300 & 0.032 & 0.604 & 1.000
+1.000 & 0.624 & -0.318 & -0.287 \\
+0.624 & 1.000 & -0.180 & 0.104 \\
+-0.318 & -0.180 & 1.000 & 0.629 \\
+-0.287 & 0.104 & 0.629 & 1.000
   \end{pmatrix}.
@@
 \begin{pmatrix}
-1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
--0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
--0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
--0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
-0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
-0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
+1.000 & 0.001 & -0.059 & -0.045 & 0.105 & 0.007 \\
+0.001 & 1.000 & 0.115 & -0.252 & -0.066 & -0.003 \\
+-0.059 & 0.115 & 1.000 & -0.140 & -0.163 & -0.024 \\
+-0.045 & -0.252 & -0.140 & 1.000 & 0.040 & 0.027 \\
+0.105 & -0.066 & -0.163 & 0.040 & 1.000 & 0.055 \\
+0.007 & -0.003 & -0.024 & 0.027 & 0.055 & 1.000
 \end{pmatrix}.
 \end{equation}
-Again  $EW_{Ca}$--$\lambda_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  
-External $E_\gamma(B-V)$ dust is
-most strongly correlated with $EW_{Si}$; recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy properties
+\color{red}
+We find weak correlations between our color-excess parameters and the input features, the strongest being $-0.163$ between
+$E_\gamma(B-V)$ and $EW_{Si}$;
+\color{black}
+recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
 \citep{2003MNRAS.340.1057S}.
-The internal $E_\delta(B-V)$  has no correlation  with internal parameters stronger than
-0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062;
+Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062;
 this low correlation, and the broad distribution in $E_\delta(B-V)$ for low $E_\gamma(B-V)$,  indicate that what we have been calling intrinsic
 indeed is not related to extrinsic dust.
-An extensive analysis of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}.
+An extensive analysis of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
+and \citet{leget:thesis}.
 
@@
 SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
+2014arXiv1411.3332J,
 2014ApJ...795L...4K, 2015ApJ...805...74B}.
@@
 
-The best-fit parameters for SN~2014J are $k= 2.56$, $ D=-1.57$ with covariance
+The best-fit parameters for SN~2014J are 
+%----
+$k= 2.67$, $ D=-1.63$ with covariance
+%----
 \begin{equation}
 \begin{pmatrix}
-0.058 & 0.059 \\
-0.059 & 0.204
+0.047 & 0.044 \\
+0.044 & 0.247
 \end{pmatrix}.
@@
 In the fit to our model, the observed color excess is attributed to   extrinsic
-$E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ contributions.
+%----
+$E_\gamma(B-V)=  0.93 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.27 \pm   0.08$
+%-----
+contributions.
 Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the
@@
 extreme median values for 
+%---
 $E_\gamma(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
 and for $E_\delta(B-V)$ $-0.01 \pm 0.01$  and
-$  0.07 \pm 0.03$ 
+$  0.06 \pm 0.03$ 
+%---
 \color{black}
@@
 extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
-affect supernova magnitudes and colors.  The external color parameter has behavior consistent with $R^F_V=3.06$ \citet{1999PASP..111...63F} dust,
+affect supernova magnitudes and colors.  The external color parameter has behavior consistent with  $R^F_V=2.97$ \citet{1999PASP..111...63F} dust,
 whereas the internal color parameter is inconsistent with dust or a blackbody.  This model  does an excellent job in
@@
 &
-$0.0039^{0.0010}_{-0.0010}$
-&
-$0.0013^{0.0008}_{-0.0008}$
-&
-$0.0015^{0.0007}_{-0.0007}$
-&
-$0.0014^{0.0006}_{-0.0006}$
-&
-$0.0026^{0.0005}_{-0.0005}$
+$0.0041^{0.0010}_{-0.0010}$
+&
+$0.0015^{0.0008}_{-0.0008}$
+&
+$0.0016^{0.0007}_{-0.0007}$
+&
+$0.0015^{0.0006}_{-0.0006}$
+&
+$0.0027^{0.0005}_{-0.0005}$
 \\
@@
 &
-$   1.6^{   1.1}_{  -0.5}$
-&
-$  -0.1^{   0.2}_{  -0.3}$
-&
-0
+$   1.6^{   0.9}_{  -0.4}$
+&
+$  -0.1^{   0.1}_{  -0.2}$
+&
+$   0.0^{   0.0}_{   0.0}$
 &
@@
 &
-$   0.8^{   0.9}_{  -0.4}$
+$   0.7^{   0.8}_{  -0.3}$
 \\
@@
 &
-$ 0.036^{ 0.005}_{-0.005}$
-&
-$ 0.027^{ 0.004}_{-0.004}$
-&
-$ 0.023^{ 0.004}_{-0.004}$
-&
-$ 0.020^{ 0.003}_{-0.003}$
-&
-$ 0.017^{ 0.003}_{-0.003}$
+$ 0.033^{ 0.006}_{-0.006}$
+&
+$ 0.025^{ 0.005}_{-0.005}$
+&
+$ 0.022^{ 0.004}_{-0.004}$
+&
+$ 0.019^{ 0.003}_{-0.004}$
+&
+$ 0.016^{ 0.003}_{-0.003}$
 \\
@@
 &
-$  0.56^{  0.12}_{ -0.10}$
-&
-$  0.18^{  0.06}_{ -0.06}$
-&
-0
-&
-$ -0.13^{  0.03}_{ -0.02}$
-&
-$ -0.29^{  0.06}_{ -0.06}$
+$  0.50^{  0.13}_{ -0.12}$
+&
+$  0.14^{  0.07}_{ -0.07}$
+&
+$  0.00^{  0.00}_{  0.00}$
+&
+$ -0.14^{  0.03}_{ -0.03}$
+&
+$ -0.28^{  0.06}_{ -0.06}$
 \\
@@
 &
-$0.0013^{0.0012}_{-0.0012}$
-&
-$0.0009^{0.0010}_{-0.0010}$
-&
-$0.0011^{0.0008}_{-0.0008}$
-&
-$0.0010^{0.0007}_{-0.0007}$
-&
-$0.0004^{0.0006}_{-0.0006}$
+$0.0001^{0.0011}_{-0.0011}$
+&
+$0.0003^{0.0009}_{-0.0009}$
+&
+$0.0008^{0.0008}_{-0.0007}$
+&
+$0.0007^{0.0006}_{-0.0006}$
+&
+$-0.0001^{0.0006}_{-0.0006}$
 \\
@@
 &
-$  0.23^{  0.49}_{ -0.51}$
-&
-$ -0.10^{  0.26}_{ -0.43}$
-&
-0
-&
-$ -0.10^{  0.17}_{ -0.12}$
-&
-$ -0.58^{  0.28}_{ -0.49}$
+$ -0.51^{  0.80}_{ -1.49}$
+&
+$ -0.40^{  0.45}_{ -0.96}$
+&
+$  0.00^{  0.00}_{  0.00}$
+&
+$ -0.14^{  0.18}_{ -0.17}$
+&
+$ -0.84^{  0.47}_{ -0.98}$
 \\
@@
 &
-$ 0.012^{ 0.040}_{-0.040}$
-&
-$-0.002^{ 0.033}_{-0.034}$
-&
-$-0.032^{ 0.028}_{-0.028}$
-&
-$-0.014^{ 0.024}_{-0.025}$
-&
-$-0.029^{ 0.021}_{-0.022}$
-\\
-${\zeta_X-\zeta_2-1}$
-&
-$  -0.9^{   0.8}_{  -2.2}$
-&
-$  -0.7^{   0.5}_{  -1.4}$
-&
-0
-&
-$  -0.4^{   0.2}_{  -0.5}$
-&
-$  -0.1^{   0.5}_{  -0.4}$
-
-\\
-${\gamma_X/\gamma_2-1}$
-&
-$  0.61^{  0.05}_{ -0.05}$
-&
-$  0.33^{  0.03}_{ -0.03}$
-&
-0
-&
-$ -0.23^{  0.01}_{ -0.01}$
+$ 0.004^{ 0.040}_{-0.041}$
+&
+$-0.004^{ 0.033}_{-0.035}$
+&
+$-0.028^{ 0.028}_{-0.029}$
+&
+$-0.013^{ 0.024}_{-0.025}$
+&
+$-0.029^{ 0.021}_{-0.023}$
+\\
+${\zeta_X/\zeta_2-1}$
+&
+$  -0.7^{   1.2}_{  -1.8}$
+&
+$  -0.5^{   0.7}_{  -1.2}$
+&
+$   0.0^{   0.0}_{   0.0}$
+&
+$  -0.4^{   0.3}_{  -0.5}$
+&
+$  -0.1^{   0.6}_{  -0.5}$
+\\
+${\gamma_{X}/\gamma_2-1}$
+&
+$  0.64^{  0.06}_{ -0.05}$
+&
+$  0.34^{  0.03}_{ -0.03}$
+&
+$  0.00^{  0.00}_{  0.00}$
+&
+$ -0.23^{  0.01}_{ -0.02}$
 &
@@
 &
-$  4.93^{  0.52}_{ -0.46}$
-&
-$  4.06^{  0.43}_{ -0.38}$
-&
-$  3.06^{  0.34}_{ -0.30}$
-&
-$  2.35^{  0.28}_{ -0.25}$
-&
-$  1.67^{  0.23}_{ -0.20}$
-\\
-${\delta_X/\delta_2-1}$
-&
-$ -0.45^{  0.17}_{ -0.19}$
-&
-$ -0.29^{  0.10}_{ -0.11}$
-&
-0
-&
-$ -0.05^{  0.05}_{ -0.04}$
-&
-$ -0.13^{  0.10}_{ -0.08}$
-\\
-$R_{\delta X}$
-&
-$ -1.92^{  0.90}_{ -1.30}$
-&
-$ -2.48^{  0.82}_{ -1.30}$
-&
-$ -3.48^{  0.90}_{ -1.52}$
-&
-$ -3.30^{  0.83}_{ -1.42}$
-&
-$ -3.03^{  0.78}_{ -1.31}$
+$  4.77^{  0.51}_{ -0.44}$
+&
+$  3.91^{  0.42}_{ -0.36}$
+&
+$  2.91^{  0.33}_{ -0.29}$
+&
+$  2.23^{  0.27}_{ -0.24}$
+&
+$  1.59^{  0.22}_{ -0.20}$
+\\
+${\delta_{X}/\delta_2-1}$
+&
+$ -0.38^{  0.17}_{ -0.18}$
+&
+$ -0.22^{  0.09}_{ -0.10}$
+&
+$  0.00^{  0.00}_{  0.00}$
+&
+$ -0.07^{  0.04}_{ -0.04}$
+&
+$ -0.17^{  0.09}_{ -0.08}$
+\\
+$R_{\delta_X}$
+&
+$ -2.79^{  1.21}_{ -2.15}$
+&
+$ -3.50^{  1.19}_{ -2.30}$
+&
+$ -4.49^{  1.32}_{ -2.70}$
+&
+$ -4.17^{  1.20}_{ -2.48}$
+&
+$ -3.73^{  1.09}_{ -2.23}$
 \\
@@
 &
-$ 0.058^{ 0.012}_{-0.011}$
-&
-$ 0.030^{ 0.007}_{-0.007}$
-&
-$ 0.017^{ 0.004}_{-0.007}$
-&
-$ 0.013^{ 0.006}_{-0.008}$
-&
-$ 0.042^{ 0.005}_{-0.004}$
+$ 0.060^{ 0.013}_{-0.012}$
+&
+$ 0.032^{ 0.007}_{-0.007}$
+&
+$ 0.018^{ 0.005}_{-0.008}$
+&
+$ 0.014^{ 0.006}_{-0.008}$
+&
+$ 0.044^{ 0.006}_{-0.005}$
 \\
@@
 Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
-$R^F_V=3.06\pm 0.18$.  
+$R^F_V=2.97\ \pm 0.18$.  
 We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
@@
 \color{red}
+\citet{2016arXiv160904470M} demonstrate how biased $R_V$ determinations can arise from unaccounted intrinsic color dispersion.
 In our model internal and external effects for each supernova  conflate into an effective color excess
@@
  low values of $R_{eff,U} - R_{eff,V}$ as implying high values of $R_V$,
-for example $R_{eff,U} - R_{eff,V}=1.70$ for $R_V=3.06$,  $R_{eff,U} - R_{eff,V}=1.81$ for $R_V=1.5$ (see Figure~\ref{ebv:fig}).
+for example $R_{eff,U} - R_{eff,V}=1.70$ for $R_V=2.97$,  $R_{eff,U} - R_{eff,V}=1.81$ for $R_V=1.5$ (see Figure~\ref{ebv:fig}).
 The $R_V$ inferred for the reddest supernovae would be $R_V<1.5$, even though their colors are dominated by 
@@
 \citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
-The values of $\eta$ in this article are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant affect on color, not particularly 
+The values of $\eta$ in this article are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color, not particularly 
 surprising as they
 are strong features in the $B$ band.
-Recall that we find a correlation between $\lambda_{Si}$ and $EW_{Ca}$
+Recall that we find a correlation between $\lambda_{Si}$ and $EW_{Ca}$.
 Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
@@
 SiII would also have shown correlations with color.
+
+\color{red}
+A correlation between Hubble residual and host-galaxy mass
+was first noted by \citet{2010ApJ...715..743K,2010MNRAS.406..782S}, and \citet{2013ApJ...770..108C} confirmed that the same
+effect is visible in the SNfactory sample.
+This host-bass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
+\citet{2016arXiv160904470M} find that effect disappears in a model with random intrinsic color dispersion.
+To explore this possibility we plot in Figure~\ref{childress:fig} our intrinsic color excess $E_\gamma(B-V)$  versus host mass for the 51 supernovae
+in common with 
+\citet{2013ApJ...770..107C}.  Choosing the same mass cut as  \citet{2013ApJ...770..108C}, $\log{M/M_\sun)}=10$, we calculate the average
+color excess for low- (high)-mass hosts to be
+$  -0.0061 \pm    0.0017$
+($  -0.0052 \pm    0.0015$).  
+The ideograms for the low- and high-mass samples is shown in Figure~\ref{childress:fig}.
+The 2-sample Kolmogorov-Smirnov test of whether the two distributions are drawn
+from a common one gives a p-value of 0.0. 
+Using the SNfactory sample,
+\citet{2013A&A...560A..66R} find that there is a bias in Hubble residuals as a function of local star formation rate.
+\color{black}
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/childress.pdf}
+      \includegraphics[width=2.8in]{output11/childress2.pdf}
+      \caption{\textcolor{red}{Left: Intrinsic parameter $E_\gamma(B-V)$  versus host mass for the 51 supernovae
+in common with 
+\citet{2013ApJ...770..107C}.
+Right: Histograms of  $E_\gamma(B-V)$ for supernovae in $\log{M/M_\sun)}<10$ and $\log{M/M_\sun)}>10$ hosts. 
+}
+   \label{childress:fig}}
+\end{figure}
 
@@
 carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represents Hubble residuals after
-application of the model, and its  $0.096$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
+application of the model, and its  $0.10$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
 measurement uncertainties.  It is also subject to overtraining.
@@
 We defer to a new model to determine how
-well this model can be used to measure supernova distances
-and examine correlations between its Hubble residuals host-galaxy parameters, e.g.\ mass,
-local star formation rate \citep{2010ApJ...715..743K, 2013A&A...560A..66R}.
+well this model can be used to measure supernova distances.
 

### 2016-09-18 table11.py

@@ -8,7 +8,7 @@ import sncosmo
 
 efflam = numpy.array([ 3693.16777627,  4369.37505509,  5287.48667023,  6319.19906153,7610.89305298])
 
-f99 = sncosmo.F99Dust(r_v =3.06)
+f99 = sncosmo.F99Dust(r_v =2.97)
 f99.set(ebv=1.37)
 A_ = f99.propagate(efflam,1.)
 A_ = -2.5*numpy.log10(A_)
@@ -37,36 +37,37 @@ for key in fit.keys():
 
 
 
-# print 'fit data to Fitzpatrick'
-gamma =  fit['gamma']
-gammacov = numpy.cov(gamma,rowvar=False)
-gamma = numpy.mean(gamma,axis=0)
-gammainvcov = numpy.linalg.inv(gammacov)
+# # print 'fit data to Fitzpatrick'
+# gamma =  fit['gamma']
+# gammacov = numpy.cov(gamma,rowvar=False)
+# gamma = numpy.mean(gamma,axis=0)
+# gammainvcov = numpy.linalg.inv(gammacov)
 
-def lnprob(p, x, y ,yerr):
-  # p is ebv and r_v
-  f99 = sncosmo.F99Dust(r_v =p[1])
-  f99.set(ebv=p[0])
-  A_ = f99.propagate(x,1.)
-  A_ = -2.5*numpy.log10(A_)
-  dum = y-A_
-  ans = -0.5*numpy.dot(dum, numpy.dot(yerr, dum))
-  return ans
+# def lnprob(p, x, y ,yerr):
+#   # p is ebv and r_v
+#   f99 = sncosmo.F99Dust(r_v =p[1])
+#   f99.set(ebv=p[0])
+#   A_ = f99.propagate(x,1.)
+#   A_ = -2.5*numpy.log10(A_)
+#   dum = y-A_
+#   ans = -0.5*numpy.dot(dum, numpy.dot(yerr, dum))
+#   return ans
 
-efflam = numpy.array([ 3693.16777627,  4369.37505509,  5287.48667023,  6319.19906153,7610.89305298])
-ndim, nwalkers = 2, 100
-pos = [numpy.array([12., 2.5]) + 1e-4*numpy.random.randn(ndim) for i in range(nwalkers)]
-import emcee
-sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(efflam, gamma, gammainvcov))
-sampler.run_mcmc(pos,1000)
[…]

### 2016-09-19 forgerard.tex
keep on going...

@@
     G.~Aldering,\altaffilmark{1}
-    P.~Antilogus,\altaffilmark{4}
+    P.~Antilogus,\altaffilmark{3}
     S.~Bailey,\altaffilmark{1}
-    C.~Baltay,\altaffilmark{5}
-    K.~Barbary,\altaffilmark{3}
+    C.~Baltay,\altaffilmark{4}
+    K.~Barbary,\altaffilmark{5}
     D.~Baugh,\altaffilmark{6}
-    K.~Boone,\altaffilmark{1,3}
-    S.~Bongard,\altaffilmark{4}
+    K.~Boone,\altaffilmark{1,5}
+    S.~Bongard,\altaffilmark{3}
     C.~Buton,\altaffilmark{2}
@@
     Y.~Copin,\altaffilmark{2}
-    P.~Fagrelius,\altaffilmark{1,3}
-    H.~K.~Fakhouri,\altaffilmark{1,3}
-    U.~Feindt,\altaffilmark{17}
-    D.~Fouchez,\altaffilmark{10}
-    E.~Gangler,\altaffilmark{11}  
+    P.~Fagrelius,\altaffilmark{1,5}
+    H.~K.~Fakhouri,\altaffilmark{1,5}
+    U.~Feindt,\altaffilmark{7}
+    D.~Fouchez,\altaffilmark{8}
+    E.~Gangler,\altaffilmark{9}  
     B.~Hayden,\altaffilmark{1}
-    W.~Hillebrandt,\altaffilmark{16}
-    M.~Kowalski,\altaffilmark{9,12}
-    P.-F.~Leget,\altaffilmark{11}
-    S.~Lombardo,\altaffilmark{9}
-    J.~Nordin,\altaffilmark{1,9}
-    R.~Pain,\altaffilmark{4} 
+    W.~Hillebrandt,\altaffilmark{10}
+    M.~Kowalski,\altaffilmark{11,12}
+    P.-F.~Leget,\altaffilmark{9}
+    S.~Lombardo,\altaffilmark{11}
+    J.~Nordin,\altaffilmark{11}
+    R.~Pain,\altaffilmark{3} 
     E.~Pecontal,\altaffilmark{13}
     R.~Pereira,\altaffilmark{2}
-    S.~Perlmutter,\altaffilmark{1,3}
-    D.~Rabinowitz,\altaffilmark{5}
-    M.~Rigault,\altaffilmark{9} 
+    S.~Perlmutter,\altaffilmark{1,5}
+    D.~Rabinowitz,\altaffilmark{4}
+    M.~Rigault,\altaffilmark{11} 
     D.~Rubin,\altaffilmark{1,14}
     K.~Runge,\altaffilmark{1}
-    C.~Saunders,\altaffilmark{1,3}
-    C.~Sofiatti,\altaffilmark{1,3} 
+    C.~Saunders,\altaffilmark{1,5}
+    C.~Sofiatti,\altaffilmark{1,5} 
     N.~Suzuki,\altaffilmark{1}
-    S.~Taubenberger,\altaffilmark{16}
-    C.~Tao,\altaffilmark{6,10}
-    R.~C.~Thomas,\altaffilmark{1} \\
+    S.~Taubenberger,\altaffilmark{10}
+    C.~Tao,\altaffilmark{6,8}
+    R.~C.~Thomas,\altaffilmark{15} \\
     (The Nearby Supernova Factory)
@@
 \altaffiltext{3}
-{
-    Department of Physics, University of California Berkeley,
-    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300
-}
-\altaffiltext{4}
 {
@@
 }
-\altaffiltext{5}
+
+\altaffiltext{4}
 {
@@
 }
+
+\altaffiltext{5}
+{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300
+}
+
 \altaffiltext{6}
@@
 
-\altaffiltext{9}
-{
-    Institut fur Physik,  Humboldt-Universitat zu Berlin,
-    Newtonstr. 15, 12489 Berlin
-}
-\altaffiltext{10}
+\altaffiltext{7}
+{
+The Oskar Klein Centre, Department of Physics, AlbaNova, Stockholm University, SE-106 91 Stockholm, Sweden
+}
+
+\altaffiltext{8}
 {
@@
 }
-\altaffiltext{11}
+
+\altaffiltext{9}
 {
@@
 }
+
+\altaffiltext{10}
+{
+    Institut fur Physik,  Humboldt-Universitat zu Berlin,
+    Newtonstr. 15, 12489 Berlin
+}
+
+\altaffiltext{11}
+{
+    Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1,
+D-85748 Garching, Germany
+}
+
 \altaffiltext{12}
@@
     1 Cyclotron Road MS 50B-4206, Berkeley, CA, 94720
-}
-
-\altaffiltext{16}
-{
-    Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1,
-D-85748 Garching, Germany
-}
-
-\altaffiltext{16}
-{
-The Oskar Klein Centre, Department of Physics, AlbaNova, Stockholm University, SE-106 91 Stockholm, Sweden
 }
@@
 is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
-dependent on the spectral equivalent widths, and two independent color parameters with better than 
+dependent on the spectral equivalent widths and two independent color parameters, with better than 
 %-----
@@
 the wide range of inferred $R_V$ among
-SNe~Ia; the systematically lower inferred $R_V$ of redder supernovae relative to the upper bound of the full population;}
+SNe~Ia; the systematically lower inferred $R_V$ of redder supernovae;}
 and the colors of SN~2014J,.
 \textcolor{red}{
-The emergence of a new parameter
-provides an avenue to interpret  Hubble-residual correlations with host-galaxy properties,}
+The new parameter
+provides a handle with which to interpret  Hubble-residual correlations with host-galaxy properties,}
 \end{abstract}
@@
 and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} that enabled absolute magnitude corrections
-and distance measurements of cosmological supernovae,
+and accurate distance measurements of cosmological supernovae,
 which 
@@
 They remain two-parameter models, with one parameter characterizing light-curve shape and the other
- color.  The physical cause of the color diversity is treated differently by the two sets of authors: 
+ color.  The physical cause of the color diversity is interpreted differently by the two sets of authors: 
 \citet{2007A&A...466...11G} pragmatically extract color variation empirically from SNe that span a wide range of colors, with no attribution
@@
 \citet{2007ApJ...659..122J}
-attribute changes in color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation of independent
+attribute changes in color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation of both independent
 intrinsic and extrinsic color variability.
@@
 of colors seen in the SN~Ia population.  One approach to look for color diversity is to find correlations between color and spectral features.
-\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two populations distinguished
+\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two subpopulations distinguished
 by Si velocity with differing $B_{max}-V_{max}$.
@@
 \textcolor{red}{
-Another approach to probe color diversity is through multiple colors (at least 3 filters)
-of a single supernova.  Colors are insensitive to the absolute normalization of the incoming flux,
-and their relative values are sensitive to processes of the responsible physics.   For example,
+Another approach to probe color diversity is through multiple colors (at least 3 bands)
+of a single supernova.  Colors ratios are sensitive to processes of the responsible physics.   For example,
 relative dust absorption varies as a function of wavelength depending on grain size and shape,
@@
 }
-\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find a wide
-range of total-to-selective extinction with average values significantly lower than $R_V = 3.1$,
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find wide
+ranges of total-to-selective extinction with average values significantly lower than $R_V = 3.1$,
 the canonical value for diffuse Milky Way dust.
@@
 the standard $R_V=3.1$ is recovered on average
-\textcolor{red}{after excluding their $>3 \sigma$ reddest supernovae.}
+\textcolor{red}{though only after excluding their $>3 \sigma$ reddest supernovae.}
 
@@
 Hierarchical modeling has recently opened
-the study of intrinsic supernova color from SN~Ia Hubble diagrams.
+the study of intrinsic supernova color based on SN~Ia Hubble diagrams.
 \citet{2016arXiv160904470M} find that the distribution of
@@
 $R_V=3.7$ dust, over dust with no color dispersion.
-The introduction of intrinsic dispersion eliminates the apparent bias in Hubble residuals between SNe in low- versus
-high-mass hosts.  They were able to draw these conclusions by using only one
+They draw these conclusions by using only one
 derived ``color'', the SALT2 fit parameter.
@@
 provides measurements of an array of supernova spectral features while also providing synthetic broadband photometry
-spanning near-UV to near-IR SN-frame wavelengths.  Well over a hundred these supernovae have temporal coverage over
+spanning near-UV to near-IR SN-frame wavelengths.  Well over a hundred of these supernovae have temporal coverage over
 peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia colors and spectral features together.
@@
 \S\ref{model:sec} and results are given in \S\ref{results:sec}.  In \S\ref{sn2014j:sec} our results are applied to the out-of-sample
-supernova SN2014J that has been previously identified as having extreme total-to-selective extinction behavior.
+supernova SN2014J that has been previously identified as having extreme total-to-selective extinction.
 We conclude with a discussion of our findings in \S\ref{discussion:sec}.
@@
 The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
-in \citet{2008A&A...477..717B} and the  velocity of SiII$\lambda 6355$ (expressed as the
-observed location of the feature $\lambda_{Si} = (1+v_{Si}/c) 6355$\AA)
+in \citet{2008A&A...477..717B} and the 
+\textcolor{red}{wavelength of the SiII$\lambda 6355$ feature}
 as in \citet{chotard:thesis}.
 Equivalent widths and the
-\textcolor{red}{SiII$\lambda 6355$ wavelength at minimum are taken from spectra  within $\pm 2.5$ days from maximum, in the case of multiple spectra the one
+\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from maximum, in the case of multiple spectra the one
 closest to maximum is used \citep{chotard:thesis}. [Confirm!]
@@
 The peak magnitude uncertainties do have covariance, which are accounted
-for in the analysis; only the variance is included in the table.
+for in the analysis; only the standard deviation is included in the table.
 
@@
 SN~Ia broadband magnitudes and colors are correlated with
-spectral features: equivalent widths and line velocities are considered as statistics localized in wavelength that are insensitive to variations in
+spectral features: equivalent widths and line positions are considered as statistics localized in wavelength that are insensitive to variations in
 broadband colors.
@@
 $EW_{Ca}$, $EW_{Si}$,
-\textcolor{red}{ and the 
-the SiII$\lambda6355$ wavelength at minimum $\lambda_{Si}$ (which varies linearly with $v_{Si}$)}:
+\textcolor{red}{ and $\lambda_{Si}$ the wavelength of the minimum of 
+the SiII$\lambda6355$ feature}:
 these spectral features are associated with SN~Ia  spectroscopic diversity  
@@
 The global parameters $\gamma$ are the slopes that connect the extrinsic-color
-parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose that
+parameter and observed magnitudes.
+
+To constrain the degrees of freedom and degeneracies inherent in the model we impose that
 \color{red}
-each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ are the number of objects in our sample: these
+each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
 conditions break the 
@@
 (when running our fits, $k$ and $D$ are set to
-identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ is non-trivial.)
+identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ distinguishes the two.)
 Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
@@
 The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
-output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
-}
+output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.}
 Empirically, the confidence regions are localized and unimodal as is seen in  Figure~\ref{global:fig}.  We find no evidence that
@@
 The differences between observed and model-predicted supernova colors are shown in Figure~\ref{residual:fig}:
-no systematic trends are apparent (in \S\ref{discussion:sec} we look for trends with light-curve shape.) 
+no systematic trends are apparent.
 The scatters in the plots, i.e.\ the residual intrinsic color dispersions from our model, are described
-later when we discuss the inferred $C_c$.
+later when we discuss the inferred residual covariance matrix $C_c$.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 \\
-$R_{\delta_X}$
+$R_{\delta X}$
 &
@@
 This validates our hypothesis that spectral indicators
-are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero within one sigma.
+are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero
+to  within one sigma.
 The effect of spectral parameters on color is shown in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$:
@@
 $\lambda_{Si}$ and color.
+
+\color{red}
+The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model:
+we now do so in a fit to the 
+model of \citet{1999PASP..111...63F},
+taking the fixed 3693,  4369,  5287,  6319, 7611 \AA\  for the effective wavelengths of the supernova flux through the bands.
+Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
+$R^F_V=2.97\ \pm 0.18$.  
+We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
+\color{black}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/fitz.pdf}
+   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=2.97$.}
+   \label{fitz:fig}}
+\end{figure}
 
@@
 None of the 20000 links of 
-our Monte Carlo chains for $\delta$ exceed 0 (see Figure~\ref{global:fig}), we thus claim detection of an effect of the
+our Monte Carlo chains for $\delta$ exceed 0 (see Figure~\ref{global:fig}), we thus claim detection of the
 intrinsic parameter on supernova magnitudes
@@
 this low correlation, and the broad distribution in $E_\delta(B-V)$ for low $E_\gamma(B-V)$,  indicate that what we have been calling intrinsic
-indeed is not related to extrinsic dust.
-An extensive analysis of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
+is not related to extrinsic dust.
+An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
 and \citet{leget:thesis}.
@@
 suffers low Galactic and host reddening
-\citep[e.g.][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
+\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
 The overall higher photospheric velocities of
@@
 \color{red}
-extreme median values for 
+objects with the extreme median values have 
 %---
@@
 Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
-\citep{2010A&A...523A...7G}, suffering no  disadvantage from the neglect of $X_1$.
-Figure~\ref{x1res:fig} shows the difference between observed and model-predicted colors,
-as a function of $X_1$: for all colors, there appear non-linear correlations 
-with a negative slope for $X_1<0$ and positive slope for $X_1>0$.
+\citep{2010A&A...523A...7G}, showing that our model exhibits no clear loss from the neglect of $X_1$.
 We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$; the credible intervals
-from this analysis are given in Table~\ref{globalx1:tab}.  
-The $\sigma_X$ values decrease at the per-mil level and there $<1\sigma$
-shifts in parameters as compared to the previous results. 
-The light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: the most significant non-zero values for
-$\zeta$ are in the $V$ and $I$ bands at less than $1.5 \sigma$, while the $\alpha$'s and $\beta$'s remain significantly
-non-zero.  This finding could be due to a deficiency of our model, 
-as it  is incapable of capturing the non-linear trends in $X_1$ in Figure~\ref{x1res:fig}.
-Note that as we use Monte Carlo methods (as opposed to linear algebra) to evaluate our model, 
-it is straightforward to add and analyze non-linear terms to the model.
+from this analysis are given in Table~\ref{globalx1:tab}; no significant changes are seen. 
+In fact, light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: the values
+for
+$\zeta$ are consistent with zero to $2\sigma$, while the $\alpha$'s and $\beta$'s remain significantly
+non-zero.  
+Nevertheless, there 
+appear to be non-linear correlations 
+between $X_1$ and the residuals between observed and model-predicted colors, as seen in
+Figure~\ref{x1res:fig}.
+Extending our model to include non-linear terms is a direction for future work.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 & $X=0$ &1&2&3&4\\ \hline
-$\alpha_{X}$
+$\alpha_X$
 &
@@
 \\
-$\beta_{X}$
+$\beta_X$
 &
@@
 &
-$ 0.019^{ 0.003}_{-0.004}$
+$ 0.019^{ 0.003}_{-0.003}$
 &
@@
 \\
-$\eta_{X}$
+$\eta_X$
 &
@@
 &
-$0.0008^{0.0008}_{-0.0007}$
-&
-$0.0007^{0.0006}_{-0.0006}$
+$0.0008^{0.0008}_{-0.0008}$
+&
+$0.0007^{0.0007}_{-0.0007}$
 &
@@
 &
-$ -0.51^{  0.80}_{ -1.49}$
-&
-$ -0.40^{  0.45}_{ -0.96}$
+$ -0.49^{  1.15}_{ -1.55}$
+&
+$ -0.39^{  0.84}_{ -0.99}$
 &
@@
 &
-$ -0.14^{  0.18}_{ -0.17}$
-&
-$ -0.84^{  0.47}_{ -0.98}$
-\\
-$\zeta_{X}$
-&
-$ 0.004^{ 0.040}_{-0.041}$
-&
-$-0.004^{ 0.033}_{-0.035}$
-&
-$-0.028^{ 0.028}_{-0.029}$
-&
-$-0.013^{ 0.024}_{-0.025}$
-&
-$-0.029^{ 0.021}_{-0.023}$
+$ -0.14^{  0.19}_{ -0.18}$
+&
+$ -0.83^{  0.78}_{ -0.96}$
+\\
+$\zeta_X$
+&
+$ 0.004^{ 0.039}_{-0.040}$
+&
+$-0.005^{ 0.033}_{-0.033}$
+&
+$-0.028^{ 0.028}_{-0.028}$
+&
+$-0.013^{ 0.024}_{-0.024}$
+&
+$-0.029^{ 0.021}_{-0.021}$
 \\
@@
 &
-$  -0.7^{   1.2}_{  -1.8}$
-&
-$  -0.5^{   0.7}_{  -1.2}$
+$  -0.7^{   1.1}_{  -1.7}$
+&
+$  -0.5^{   0.6}_{  -1.2}$
 &
@@
 &
-$  -0.1^{   0.6}_{  -0.5}$
-\\
-${\gamma_{X}/\gamma_2-1}$
+$  -0.1^{   0.6}_{  -0.4}$
+\\
+${\gamma_X/\gamma_2-1}$
 &
@@
 &
-$ -0.23^{  0.01}_{ -0.02}$
+$ -0.23^{  0.01}_{ -0.01}$
 &
@@
 \\
-$R_{X}$
-&
-$  4.77^{  0.51}_{ -0.44}$
-&
-$  3.91^{  0.42}_{ -0.36}$
+$R_X$
+&
+$  4.78^{  0.52}_{ -0.45}$
+&
+$  3.91^{  0.42}_{ -0.37}$
 &
@@
 &
-$  1.59^{  0.22}_{ -0.20}$
-\\
-${\delta_{X}/\delta_2-1}$
-&
-$ -0.38^{  0.17}_{ -0.18}$
-&
-$ -0.22^{  0.09}_{ -0.10}$
+$  1.60^{  0.22}_{ -0.20}$
+\\
+${\delta_X/\delta_2-1}$
+&
+$ -0.38^{  0.17}_{ -0.19}$
+&
+$ -0.23^{  0.10}_{ -0.10}$
 &
@@
 &
-$ -0.17^{  0.09}_{ -0.08}$
-\\
-$R_{\delta_X}$
-&
-$ -2.79^{  1.21}_{ -2.15}$
-&
-$ -3.50^{  1.19}_{ -2.30}$
-&
-$ -4.49^{  1.32}_{ -2.70}$
-&
-$ -4.17^{  1.20}_{ -2.48}$
-&
-$ -3.73^{  1.09}_{ -2.23}$
-\\
-$\sigma_{X}$
+$ -0.17^{  0.09}_{ -0.09}$
+\\
+$R_{\delta X}$
+&
+$ -2.78^{  1.23}_{ -2.20}$
+&
+$ -3.49^{  1.22}_{ -2.38}$
+&
+$ -4.49^{  1.35}_{ -2.78}$
+&
+$ -4.17^{  1.23}_{ -2.55}$
+&
+$ -3.72^{  1.12}_{ -2.28}$
+\\
+$\sigma_X$
 &
@@
 &
-$ 0.032^{ 0.007}_{-0.007}$
+$ 0.033^{ 0.007}_{-0.007}$
 &
@@
 \color{black}
-
-\color{red}
-The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model
-we now do so in a fit to the 
-model of \citet{1999PASP..111...63F},
-assuming the fixed 3693,  4369,  5287,  6319, 7611 \AA\  for the effective wavelengths of the supernova flux through the bands.
-Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
-$R^F_V=2.97\ \pm 0.18$.  
-We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
-\color{black}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/fitz.pdf}
-   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=3.06$.}
-   \label{fitz:fig}}
-\end{figure}
 
@@
 In our model internal and external effects for each supernova  conflate into an effective color excess
-$E_{eff}(X-V) = E_\gamma(X-V) + E_\delta(X-V)$ and effective $V$ extinction $A_{eff,V} = \gamma_2 k  + \delta_2 D$ 
+$E_{eff}(X-V) = E_\gamma(X-V) + E_\delta(X-V)$ and effective $V$ extinction $A_{eff,V} = \gamma_2 k  + \delta_2 D$.
 Recall that the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrarily
@@
 
+One choice of boundary condition is to zero the color at the blue extremes of the distributions.
 For specificity in the current qualitative discussion, 
@@
 in the right of Figure~\ref{rveff:fig}.
-Around $E_{eff}(B-V) \sim 0$ the $R_{eff,U} - R_{eff,V}$ values are high, but this is also the regime where their  uncertainties 
-blow up due to a division of an uncertain quantity with value close to zero.
+Around $E_{eff}(B-V) \sim 0$, where attempts to measure extinction properties would suffer large uncertainties,
+the $R_{eff,U} - R_{eff,V}$ values are high.
 The distribution spreads to significantly 
@@
 The $R_V$ inferred for the reddest supernovae would be $R_V<1.5$, even though their colors are dominated by 
-extrinsic $R^F_V=3.06$ dust; this is due our zero colors being (qualitatively) assigned to supernovae that have bluest extrinsic AND intrinsic color excess.
+extrinsic $R^F_V=2.97$ dust; this is due our zero colors being (qualitatively) assigned to supernovae that have bluest extrinsic AND intrinsic color excess.
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 \citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
-The values of $\eta$ in this article are consistent with zero. Instead,  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color, not particularly 
-surprising as they
-are strong features in the $B$ band.
-Recall that we find a correlation between $\lambda_{Si}$ and $EW_{Ca}$.
+\textcolor{red}{The $\lambda_{Si} = (1+v_{Si}/c) \lambda_{Si,0} $ treated in this article varies linearly with $v_{Si}$.}
+The values of $\eta$ in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
+and in turn $\lambda_{Si}$ is correlated with $EW_{Ca}$.
 Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
 non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, 
-\textcolor{red}{but the equivalent-width corrections are preferred as they give lower residual dispersions $C_c$},
+\textcolor{red}{but the equivalent-width corrections give higher likelihood as they give lower residual dispersions $C_c$},
 and  anticipate that in the previous analysis the equivalent widths of CaII and 
@@
 A correlation between Hubble residual and host-galaxy mass
-was first noted by \citet{2010ApJ...715..743K,2010MNRAS.406..782S}, and \citet{2013ApJ...770..108C} confirmed that the same
-effect is visible in the SNfactory sample.
-This host-bass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
-\citet{2016arXiv160904470M} find that effect disappears in a model with random intrinsic color dispersion.
-To explore this possibility we plot in Figure~\ref{childress:fig} our intrinsic color excess $E_\gamma(B-V)$  versus host mass for the 51 supernovae
-in common with 
-\citet{2013ApJ...770..107C}.  Choosing the same mass cut as  \citet{2013ApJ...770..108C}, $\log{M/M_\sun)}=10$, we calculate the average
+was first noted by \citet{2010ApJ...715..743K,2010MNRAS.406..782S}, a signal confirmed to exist in the SNfactory
+sample \citep{2013ApJ...770..108C}.
+This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
+\citet{2016arXiv160904470M} find that with intrinsic color scatter, the null mass-step effect falls on the 95\%-level of their posterior.
+To explore this possibility we plot in Figure~\ref{childress:fig} our intrinsic color excess $E_\gamma(B-V)$  versus host mass 
+\citep{2016rigault}.  Choosing the same mass cut as  \citet{2013ApJ...770..108C}, $\log{(M/M_\sun)}=10$, we calculate the average
 color excess for low- (high)-mass hosts to be
-$  -0.0061 \pm    0.0017$
-($  -0.0052 \pm    0.0015$).  
+$  -0.0043 \pm    0.0022$
+($  -0.0072 \pm    0.0073$).  
 The ideograms for the low- and high-mass samples is shown in Figure~\ref{childress:fig}.
-The 2-sample Kolmogorov-Smirnov test of whether the two distributions are drawn
-from a common one gives a p-value of 0.0. 
+The 2-sample Kolmogorov-Smirnov test of the medians gives a $p$-value of
+%---
+0.29.
+%---
+From the above evidence, we cannot show that low- and high-mass hosts produce SNe~Ia with difference $E_\gamma(B-V)$ distributions. 
 Using the SNfactory sample,
-\citet{2013A&A...560A..66R} find that there is a bias in Hubble residuals as a function of local star formation rate.
+\citet{2013A&A...560A..66R} find that step in Hubble residuals as better related to local star formation rate, rather than host mass.
+The connection between our intrinsic parameter and local star formation and other host properties is deferred to
+\citet{2016rigault}.
 \color{black}
@@
    \centering
-   \includegraphics[width=2.8in]{output11/childress.pdf}
-      \includegraphics[width=2.8in]{output11/childress2.pdf}
-      \caption{\textcolor{red}{Left: Intrinsic parameter $E_\gamma(B-V)$  versus host mass for the 51 supernovae
-in common with 
-\citet{2013ApJ...770..107C}.
-Right: Histograms of  $E_\gamma(B-V)$ for supernovae in $\log{M/M_\sun)}<10$ and $\log{M/M_\sun)}>10$ hosts. 
+   \includegraphics[width=2.8in]{output11/rigault3.pdf}
+      \includegraphics[width=2.8in]{output11/rigault2.pdf}
+      \caption{\textcolor{red}{Left: Intrinsic parameter $E_\gamma(B-V)$  versus host mass.  Hosts too faint for a mass measurement
+      are assigned a mass of 5.
+Right: Ideograms of  $E_\gamma(B-V)$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
 }
@@
 The  analysis of this article was intended to model the color behavior of supernovae in our dataset.
-We defer to a new model to determine how
+\color{red}
+A new analysis insensitive to overtraining is required to robustly determine how
 well this model can be used to measure supernova distances.
+\color{black}
 

### 2016-09-21 forgerard.tex
plowing forward

@@
-\documentclass{aastex}   	% use "amsart" instead of "article" for AMSLaTeX format
+\documentclass{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
@@
 \title{Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory}
-\author
-{
-    A.~G.~Kim,\altaffilmark{1}
-    G.~Smadja,\altaffilmark{2} 
-    G.~Aldering,\altaffilmark{1}
-    P.~Antilogus,\altaffilmark{3}
-    S.~Bailey,\altaffilmark{1}
-    C.~Baltay,\altaffilmark{4}
-    K.~Barbary,\altaffilmark{5}
-    D.~Baugh,\altaffilmark{6}
-    K.~Boone,\altaffilmark{1,5}
-    S.~Bongard,\altaffilmark{3}
-    C.~Buton,\altaffilmark{2}
-    J.~Chen,\altaffilmark{6}
-    N.~Chotard,\altaffilmark{2}
-    Y.~Copin,\altaffilmark{2}
-    P.~Fagrelius,\altaffilmark{1,5}
-    H.~K.~Fakhouri,\altaffilmark{1,5}
-    U.~Feindt,\altaffilmark{7}
-    D.~Fouchez,\altaffilmark{8}
-    E.~Gangler,\altaffilmark{9}  
-    B.~Hayden,\altaffilmark{1}
-    W.~Hillebrandt,\altaffilmark{10}
-    M.~Kowalski,\altaffilmark{11,12}
-    P.-F.~Leget,\altaffilmark{9}
-    S.~Lombardo,\altaffilmark{11}
-    J.~Nordin,\altaffilmark{11}
-    R.~Pain,\altaffilmark{3} 
-    E.~Pecontal,\altaffilmark{13}
-    R.~Pereira,\altaffilmark{2}
-    S.~Perlmutter,\altaffilmark{1,5}
-    D.~Rabinowitz,\altaffilmark{4}
-    M.~Rigault,\altaffilmark{11} 
-    D.~Rubin,\altaffilmark{1,14}
-    K.~Runge,\altaffilmark{1}
-    C.~Saunders,\altaffilmark{1,5}
-    C.~Sofiatti,\altaffilmark{1,5} 
-    N.~Suzuki,\altaffilmark{1}
-    S.~Taubenberger,\altaffilmark{10}
-    C.~Tao,\altaffilmark{6,8}
-    R.~C.~Thomas,\altaffilmark{15} \\
-    (The Nearby Supernova Factory)
-}
-
-\altaffiltext{1}
-{
-    Physics Division, Lawrence Berkeley National Laboratory, 
-    1 Cyclotron Road, Berkeley, CA, 94720
-}
-
-\altaffiltext{2}
-{
-    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
-    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon.
-}
-
-\altaffiltext{3}
-{
-    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
+\author{A.~G.~Kim}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+
+\author{     G.~Smadja}
+\affiliation{    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
+    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}
+
+\author{     G.~Aldering}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+
+\author{     P.~Antilogus}
+\affiliation{    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
     Universit\'e Pierre et Marie Curie Paris 6, Universit\'e Paris Diderot Paris 7, CNRS-IN2P3, 
-    4 place Jussieu, 75252 Paris Cedex 05, France
-}
-
-\altaffiltext{4}
-{
-    Department of Physics, Yale University, 
-    New Haven, CT, 06250-8121
-}
-
-\altaffiltext{5}
-{
+    4 place Jussieu, 75252 Paris Cedex 05, France}
+
+\author{     S.~Bailey}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+
+\author{     C.~Baltay}
+\affiliation{    Department of Physics, Yale University, 
+    New Haven, CT, 06250-8121}
+
+\author{     K.~Barbary}
+\affiliation{
     Department of Physics, University of California Berkeley,
-    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300
-}
-
-\altaffiltext{6}
-{
-    Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China 
-}
-
-\altaffiltext{7}
-{
-The Oskar Klein Centre, Department of Physics, AlbaNova, Stockholm University, SE-106 91 Stockholm, Sweden
-}
-
-\altaffiltext{8}
-{
-    Centre de Physique des Particules de Marseille, 
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
+
+\author{    D.~Baugh}
+\affiliation{   Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China }
+
+\author{     K.~Boone}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+\affiliation{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
+
+\author{     S.~Bongard}
+\affiliation{    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
+    Universit\'e Pierre et Marie Curie Paris 6, Universit\'e Paris Diderot Paris 7, CNRS-IN2P3, 
+    4 place Jussieu, 75252 Paris Cedex 05, France}
+
+\author{     C.~Buton}
+\affiliation{    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
+    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}
+
+\author{     J.~Chen}
+\affiliation{   Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China }
+
+\author{     N.~Chotard}
+\affiliation{    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
+    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}
+
+\author{     Y.~Copin}
+\affiliation{    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
+    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}
+
+\author{     P.~Fagrelius}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+\affiliation{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
+
+\author{     H.~K.~Fakhouri}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+  \affiliation{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
+
+\author{     U.~Feindt}
+\affiliation{The Oskar Klein Centre, Department of Physics, AlbaNova, Stockholm University, SE-106 91 Stockholm, Sweden}
+
+\author{     D.~Fouchez}
+\affiliation{    Centre de Physique des Particules de Marseille, 
     Aix-Marseille Universit\'e , CNRS/IN2P3, 
-    163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France
-}
-
-\altaffiltext{9}
-{
-    Clermont Universit\'e, Universit\'e Blaise Pascal, CNRS/IN2P3, Laboratoire de Physique Corpusculaire,
-    BP 10448, F-63000 Clermont-Ferrand, France
-}
-
-\altaffiltext{10}
-{
-    Institut fur Physik,  Humboldt-Universitat zu Berlin,
-    Newtonstr. 15, 12489 Berlin
-}
-
-\altaffiltext{11}
-{
-    Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1,
-D-85748 Garching, Germany
-}
-
-\altaffiltext{12}
-{
-    DESY, D-15735 Zeuthen, Germany
-}
-\altaffiltext{13}
-{
-    Centre de Recherche Astronomique de Lyon, Universit\'e Lyon 1,
-    9 Avenue Charles Andr\'e, 69561 Saint Genis Laval Cedex, France
-}
-\altaffiltext{14}
-{
-    Department of Physics, Florida State University,
-    315 Keen Building, Tallahassee, FL 32306-4350
-}
-\altaffiltext{15}
-{
-    Computational Cosmology Center, Computational Research Division, Lawrence Berkeley National Laboratory, 
-    1 Cyclotron Road MS 50B-4206, Berkeley, CA, 94720
-}
+    163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France}
+
+\author{     E.~Gangler}  
+\affiliation{    Clermont Universit\'e, Universit\'e Blaise Pascal, CNRS/IN2P3, Laboratoire de Physique Corpusculaire,
+    BP 10448, F-63000 Clermont-Ferrand, France}
+
+\author{     B.~Hayden}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+
+\author{     W.~Hillebrandt}
+\affiliation{    Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1,
+D-85748 Garching, Germany}
+
+\author{     M.~Kowalski}
+\affiliation{    Institut fur Physik,  Humboldt-Universitat zu Berlin,
+    Newtonstr. 15, 12489 Berlin}
+\affiliation{ DESY, D-15735 Zeuthen, Germany}
+
+\author{     P.-F.~Leget}
+\affiliation{    Clermont Universit\'e, Universit\'e Blaise Pascal, CNRS/IN2P3, Laboratoire de Physique Corpusculaire,
+    BP 10448, F-63000 Clermont-Ferrand, France}
+
+\author{     S.~Lombardo}
+\affiliation{    Institut fur Physik,  Humboldt-Universitat zu Berlin,
+    Newtonstr. 15, 12489 Berlin}
+
+\author{     J.~Nordin}
+\affiliation{    Institut fur Physik,  Humboldt-Universitat zu Berlin,
+    Newtonstr. 15, 12489 Berlin}
+
+\author{     R.~Pain}
+\affiliation{    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
+    Universit\'e Pierre et Marie Curie Paris 6, Universit\'e Paris Diderot Paris 7, CNRS-IN2P3, 
+    4 place Jussieu, 75252 Paris Cedex 05, France}
+
+\author{     E.~Pecontal}
+\affiliation{   Centre de Recherche Astronomique de Lyon, Universit\'e Lyon 1,
+    9 Avenue Charles Andr\'e, 69561 Saint Genis Laval Cedex, France}
+
+\author{    R.~Pereira}
+ \affiliation{    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
+    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}
+
+ \author{    S.~Perlmutter}
+ \affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720} 
+\affiliation{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
+
+ \author{    D.~Rabinowitz}
+ \affiliation{    Department of Physics, Yale University, 
+    New Haven, CT, 06250-8121}
+
+ \author{    M.~Rigault} 
+\affiliation{    Institut fur Physik,  Humboldt-Universitat zu Berlin,
+    Newtonstr. 15, 12489 Berlin}
+
+ \author{    D.~Rubin}
+ \affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+    \affiliation{    Department of Physics, Florida State University,
+    315 Keen Building, Tallahassee, FL 32306-4350}
+
+ \author{    K.~Runge}
+ \affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+
+ \author{    C.~Saunders}
+ \affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+
+\author{    C.~Sofiatti}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720} 
+\affiliation{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
+
+\author{    N.~Suzuki}
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road, Berkeley, CA, 94720}
+
+\author{     S.~Taubenberger}
+\affiliation{    Max-Planck-Institut f\"ur Astrophysik, Karl-Schwarzschild-Str. 1,
+D-85748 Garching, Germany}
+
+\author{     C.~Tao}
+\affiliation{   Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China }
+\affiliation{    Centre de Physique des Particules de Marseille, 
+    Aix-Marseille Universit\'e , CNRS/IN2P3, 
+    163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France}
+
+\author{     R.~C.~Thomas}
+\affiliation{    Computational Cosmology Center, Computational Research Division, Lawrence Berkeley National Laboratory, 
+    1 Cyclotron Road MS 50B-4206, Berkeley, CA, 94720}
+
+\collaboration{(The Nearby Supernova Factory)}
 
@@
 %-----
-$R_V=2.97\ \pm 0.18$.
+$R_V=2.97^{+0.18}_{-0.17}$.
 %------
@@
 
+\startlongtable
 \begin{deluxetable}{ccccccccc}
 \tabletypesize{\tiny}
-\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Datat\label{data:tab}}
+\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data\label{data:tab}}
 \tablehead{
-\colhead{$n$} & \colhead{$EW_{Ca}$} & \colhead{$EW_{Si}$} & \colhead{$\lambda_{Si}$} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} \\
- & (\AA) & (\AA)&  \colhead{(\AA)} & \multicolumn{5}{c}{}
+\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$}
 }
 \startdata
-0 & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
-1 & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
-2 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
-3 & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
-4 & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ \\
-5 & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ \\
-6 & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-7 & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
-8 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ \\
-9 & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
-10 & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
-11 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ \\
-12 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
-13 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
-14 & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
-15 & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
-16 & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6141 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
-17 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
-18 & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
-19 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
-20 & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
-21 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
-22 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ \\
-23 & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ \\
-24 & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ \\
-25 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
-26 & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
-27 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-28 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
-29 & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
-30 & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
-31 & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
-32 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
-33 & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
-34 & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
-35 & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
-36 & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6114 \pm   9$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
-37 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
-38 & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-39 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
-40 & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6168 \pm   6$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
-41 & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
-42 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
-43 & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
-44 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
-45 & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
-46 & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
-47 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
-48 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
-49 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
-50 & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
-51 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
-52 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
-53 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
-54 & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
-55 & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
-56 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
-57 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
-58 & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ \\
-59 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
-60 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
-61 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
-62 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
-63 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
-64 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
-65 & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
-66 & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
-67 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
-68 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6127 \pm  10$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
-69 & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6144 \pm   2$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
-70 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
-71 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   4$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
-72 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
-73 & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
-74 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
-75 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
-76 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
-77 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
-78 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
-79 & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
-80 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
-81 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
-82 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
-83 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-84 & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
-85 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
-86 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
-87 & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
-88 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
-89 & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
-90 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
-91 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
-92 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-93 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-94 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
-95 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
-96 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
-97 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
-98 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
-99 & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
-100 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
-101 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
-102 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
-103 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
-104 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
-105 & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
-106 & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
-107 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6112 \pm   2$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
-108 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
-109 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
-110 & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
-111 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
-112 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
-113 & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
-114 & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
-115 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
-116 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
-117 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6148 \pm   4$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
-118 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
-119 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
-120 & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
-121 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
-122 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
-123 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
-124 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
-125 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6129 \pm   7$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
-126 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
-127 & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
-128 & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
-129 & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
-130 & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
-131 & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
-132 & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
-133 & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
-134 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
-135 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
-136 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
-137 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
-138 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
-139 & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
-140 & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
-141 & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
-142 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
-143 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
-144 & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
-145 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-146 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
-147 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
-148 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
-149 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
-150 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
-151 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
-152 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
-153 & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
-154 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
-155 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
-156 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
-157 & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
-158 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
-159 & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
-160 & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-161 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
-162 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
-163 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
-164 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
-165 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
-166 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\\enddata
+SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
+PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
+SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
+PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
+SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ \\
+PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ \\
+PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ \\
+PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
+PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
+SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ \\
+SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
+SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
+SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
+PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
+PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6141 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
+SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
+PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
+SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
+PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
+SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
+SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ \\
+PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ \\
+PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ \\
+SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
+LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
+SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
+PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
+PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
+SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
+SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
+LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
+PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
+PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
+PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6114 \pm   9$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
+SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
+PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
+PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6168 \pm   6$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
+PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
+SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
+SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
+SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
+PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
+PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
+CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
+SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
+SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
+PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
+SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
+SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
+SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
+PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
+PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
+SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
+SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
+SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ \\
+SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
+SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
+SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
+SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
+SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
+SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
+PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
+PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
+SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
+SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6127 \pm  10$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
+SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6144 \pm   2$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
+CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
+SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   4$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
+SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
+PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
+SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
+SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
+SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
+SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
+SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
+SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
+SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
+CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
+SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
+SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
+SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
+SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
+PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
+SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
+PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
+SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
+SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
+SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
+SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
+SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
+SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
+SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
+SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
+SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
+SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
+SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
+SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
+SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
+PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
+PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
+SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6112 \pm   2$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
+SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
+SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
+SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
+SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
+SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
+SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
+SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
+SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
+SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
+SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6148 \pm   4$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
+SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
+SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
+PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
+SNF20070725-001 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
+SNF20071108-021 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
+SNF20080914-001 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
+SNF20060609-002 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6129 \pm   7$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
+SNF20050624-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
+SNF20060618-023 & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
+SNF20080531-000 & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
+SN2006do & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
+PTF12ikt & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
+SN2006dm & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
+PTF13azs & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
+SN2005hj & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
+PTF12iiq & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
+PTF10ndc & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
+SNF20080919-002 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
+SNPGC027923 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
+SNF20070330-024 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
+SNF20061030-010 & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
+SNhunt46 & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
+SN2005hc & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
+LSQ12dbr & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
+LSQ12hjm & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
+SNF20060521-001 & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
+SNF20070630-006 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+PTF11drz & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
+SNF20080323-009 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
+SNF20071021-000 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
+SNNGC0927 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
+SNF20060526-003 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
+SNF20080806-002 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
+SNF20080803-000 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
+SNF20080822-005 & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
+SNF20060618-014 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
+PTF12ghy & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
+SNF20070531-011 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
+SNF20070831-015 & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
+SNF20070417-002 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
+PTF11cao & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
+SNF20080522-000 & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+PTF10qjq & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
+PTF12dxm & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
+SNF20061021-003 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
+SNF20080510-005 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
+SNF20080507-000 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
+SNF20080913-031 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\
+\enddata
 \end{deluxetable}
@@
 this parlance our parameters can be re-expressed as the  familiar color excess
-$E_\gamma(B-V) = (\gamma_1-\gamma_2) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_1-\gamma_2}$.
+$E_\gamma(B-V) = (\gamma_B-\gamma_V) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_B-\gamma_V}$.
 Similar reparameterizatons of the intrinsic color parameters are
-$E_\delta(B-V) = (\delta_1-\delta_2) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_1-\delta_2}$.
+$E_\delta(B-V) = (\delta_B-\delta_V) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_B-\delta_V}$.
 
@@
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.}
-Empirically, the confidence regions are localized and unimodal as is seen in  Figure~\ref{global:fig}.  We find no evidence that
+Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig}, \ref{global2:fig}, \ref{global3:fig}, \ref{global4:fig},
+\ref{global5:fig}.  We find no evidence that
 the Monte Carlo chains have not converged to the stationary posterior distribution.
@@
    \centering
-   \includegraphics[width=2.5in]{output11/coeff0.pdf} 
-   \includegraphics[width=2.5in]{output11/coeff1.pdf} 
-   \includegraphics[width=2.5in]{output11/coeff2.pdf} 
-      \includegraphics[width=2.5in]{output11/coeff3.pdf} 
-         \includegraphics[width=2.5in]{output11/coeff4.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in each of the 5 bands.
+   \includegraphics[width=5.5in]{output11/coeff0.pdf} 
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $U$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution, not to 68\%, 95\%, etc.\
-            enclosed probability.  \label{global:fig}}
+            enclosed probability.  \label{global1:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.5in]{output11/coeff1.pdf} 
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $B$ band.
+ \label{global2:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.5in]{output11/coeff2.pdf} 
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $V$ band.
+ \label{global3:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.5in]{output11/coeff3.pdf} 
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $R$ band.
+ \label{global4:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+         \includegraphics[width=5.5in]{output11/coeff4.pdf} 
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $I$ band.
+ \label{global5:fig}}
 \end{figure}
@@
    \centering
-   \includegraphics[width=5in]{output11/residual.pdf} 
+   \includegraphics[width=5.5in]{output11/residual.pdf} 
             \caption{\textcolor{red}{Differences between observed and  model-predicted supernova colors  as a function
@@
 are given in Table~\ref{global:tab}.
-Contours of the posterior surface for parameter pairs grouped by filter are shown in Figure~\ref{global:fig}.
+Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig} .
 
@@
 \hline
-& $X=0$ &1&2&3&4\\ \hline
+& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
 $\alpha_X$
@@
 \\
-${\alpha_X/\alpha_2-1}$
+${\alpha_X/\alpha_V-1}$
 &
@@
 \\
-${\beta_X/\beta_2-1}$
+${\beta_X/\beta_V-1}$
 &
@@
 \\
-${\eta_X/\eta_2-1}$
+${\eta_X/\eta_V-1}$
 &
@@
 \\
-${\gamma_X/\gamma_2-1}$
+${\gamma_X/\gamma_V-1}$
 &
@@
 \\
-${\delta_X/\delta_2-1}$
+${\delta_X/\delta_V-1}$
 &
@@
 \color{red}
+
 The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model:
@@
 Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
-$R^F_V=2.97\ \pm 0.18$.  
+$R_V=2.97^{+0.18}_{-0.17}$..  
 We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
+The posterior distributions for $R_{\gamma X}=\frac{\gamma_X}{\gamma_B-\gamma_V}$ are shown in Figure~\ref{rx:fig}.
 \color{black}
@@
    \label{fitz:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
+      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
+   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_B-\gamma_V}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$.
+   \label{rx:fig}}
 \end{figure}
@@
 None of the 20000 links of 
-our Monte Carlo chains for $\delta$ exceed 0 (see Figure~\ref{global:fig}), we thus claim detection of the
+our Monte Carlo chains for $\delta$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
 intrinsic parameter on supernova magnitudes
 with probability $(1-5\times 10^{-5})$.
-The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
-Although the posteriors of $\delta$ are close to Gaussian, $\delta_1-\delta_2$ can approach zero, resulting in the
-elongated tail in negative  $R_{\delta X}$.
-All values are significantly negative meaning a color excess in $B-V$ produces a brightening of the supernova.
-The values of $\delta_X/\delta_V-1$ are not monotonic with color: they increase from the $U$ to $V$, and then decrease
+\textcolor{red}{
+The values of $\delta_X/\delta_V$, plotted in  Figure~\ref{deltaratio:fig}, are not monotonic with color: they increase from the $U$ to $V$, and then decrease
 from $V$ to $I$,
@@
 a reddening in $B-V$ comes with a blueing in $V-R$.
+Also apparent is that a reddening of $B-V$ is associated with a brightening of the supernova.
+The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$ are shown in Figure~\ref{rx:fig}.
+Although the posteriors of $\delta$ are close to Gaussian, $\delta_B-\delta_V$ can approach zero, resulting in the
+elongated tail in negative  $R_{\delta X}$.
+All values are significantly negative.}
 These are not the behaviors expected from normal dust,
@@
    \centering
-   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
-      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
-   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$.
-   \label{rx:fig}}
-\end{figure}
-
-The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
- $E_\delta(B-V) = (\delta_1-\delta_2)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
+   \includegraphics[width=3.2in]{output11/deltaratio.pdf}
+   \caption{68\% credible intervals of $\frac{\delta_X}{\delta_V}$ at the effective wavelengths of the corresponding bands.
+   \label{deltaratio:fig}}
+\end{figure}
+
+The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
+ $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
 Recall that our boundary conditions set the means of both distributions to zero. 
@@
    \includegraphics[width=3.2in]{output11/ebv.pdf}
-   \caption{Ideograms of the external $E_\gamma(B-V) =(\gamma_1-\gamma_2)k$ and
-   internal $E_\delta(B-V) = (\delta_1-\delta_2)D$  contributions to color excess  for the supernovae in our sample.
+   \caption{Ideograms of the external $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
+   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
    \label{ebv:fig}}
@@
 \begin{pmatrix}
-0.0040 & 0.0011 & -0.0002 & -0.0000 & 0.0003 \\
-0.0011 & 0.0012 & 0.0002 & -0.0000 & -0.0006 \\
--0.0002 & 0.0002 & 0.0004 & 0.0001 & -0.0002 \\
--0.0000 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \\
+0.0040 & 0.0011 & -0.0002 & -0.0000 & 0.0003 \cr
+0.0011 & 0.0012 & 0.0002 & -0.0000 & -0.0006 \cr
+-0.0002 & 0.0002 & 0.0004 & 0.0001 & -0.0002 \cr
+-0.0000 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \cr
 0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
@@
 \begin{pmatrix}
-1.000 & 0.624 & -0.318 & -0.287 \\
-0.624 & 1.000 & -0.180 & 0.104 \\
--0.318 & -0.180 & 1.000 & 0.629 \\
+1.000 & 0.624 & -0.318 & -0.287 \cr
+0.624 & 1.000 & -0.180 & 0.104 \cr
+-0.318 & -0.180 & 1.000 & 0.629 \cr
 -0.287 & 0.104 & 0.629 & 1.000
@@
    \centering
-   \includegraphics[width=3.2in]{output11/sigma_corner.pdf} 
+   \includegraphics[width=5.5in]{output11/sigma_corner.pdf} 
    \caption{Posterior contours for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
@@
    \centering
-   \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
+   \includegraphics[width=5.5in]{output11/perobject_corner.pdf} 
    \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as the grey offset
-$\Delta$.
+$\Delta$.  All links are plotted, so that each supernova contributes a cloud of points.
    \label{perobject:fig}}
@@
 \begin{pmatrix}
-1.000 & 0.001 & -0.059 & -0.045 & 0.105 & 0.007 \\
-0.001 & 1.000 & 0.115 & -0.252 & -0.066 & -0.003 \\
--0.059 & 0.115 & 1.000 & -0.140 & -0.163 & -0.024 \\
--0.045 & -0.252 & -0.140 & 1.000 & 0.040 & 0.027 \\
-0.105 & -0.066 & -0.163 & 0.040 & 1.000 & 0.055 \\
+1.000 & 0.001 & -0.059 & -0.045 & 0.105 & 0.007 \cr
+0.001 & 1.000 & 0.115 & -0.252 & -0.066 & -0.003 \cr
+-0.059 & 0.115 & 1.000 & -0.140 & -0.163 & -0.024 \cr
+-0.045 & -0.252 & -0.140 & 1.000 & 0.040 & 0.027 \cr
+0.105 & -0.066 & -0.163 & 0.040 & 1.000 & 0.055 \cr
 0.007 & -0.003 & -0.024 & 0.027 & 0.055 & 1.000
@@
 \begin{equation}
-E_o(X-V) =  \left(\frac{\gamma_X}{\gamma_2}-1\right)k +  \left(\frac{\delta_X}{\delta_2}-1\right)D,
+E_o(X-V) =  \left(\frac{\gamma_X}{\gamma_V}-1\right)k +  \left(\frac{\delta_X}{\delta_V}-1\right)D,
 \end{equation}
@@
 \\
-${\zeta_X/\zeta_2-1}$
+${\zeta_X/\zeta_V-1}$
 &
@@
 In our model internal and external effects for each supernova  conflate into an effective color excess
-$E_{eff}(X-V) = E_\gamma(X-V) + E_\delta(X-V)$ and effective $V$ extinction $A_{eff,V} = \gamma_2 k  + \delta_2 D$.
+$E_{eff}(X-V) = E_\gamma(X-V) + E_\delta(X-V)$ and effective $V$ extinction $A_{eff,V} = \gamma_V k  + \delta_V D$.
 Recall that the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrarily
@@
 \begin{equation}
-R_{eff, V} = \frac{\gamma_1  (k-k_0) + \delta_1 (D-D_0) }{(\gamma_1-\gamma_2) (k-k_0) + (\delta_1-\delta_2) (D-D_0) },
+R_{eff, V} = \frac{\gamma_1  (k-k_0) + \delta_1 (D-D_0) }{(\gamma_B-\gamma_V) (k-k_0) + (\delta_B-\delta_V) (D-D_0) },
 \end{equation}
 where $k_0$ and $D_0$ are the parameter values of the canonical supernova.
-If $D = D_0$, the $R_V = \gamma_1/(\gamma_1-\gamma_2)$ of the extrinsic contribution is recovered, but this does not hold true
+If $D = D_0$, the $R_V = \gamma_B/(\gamma_B-\gamma_V)$ of the extrinsic contribution is recovered, but this does not hold true
 when $D \ne D_0$.  Again considering a set of SNe~Ia  with parameters equal to the median fit values of the SNfactory sample,
@@
 from doubly and singly ionized states, making the gas phosphorescent and efficient in redistributing energy from the UV/blue to redder
-wavelengths.  Qualitatively this would result in the structure for $\gamma_X/\gamma_2-1$ that we measure.
+wavelengths.  Qualitatively this would result in the structure for $\gamma_X/\gamma_V-1$ that we measure.
 We conjecture that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth

### 2016-09-21 table11.py

@@ -36,7 +36,6 @@ for key in fit.keys():
 
 
 
-
 # # print 'fit data to Fitzpatrick'
 # gamma =  fit['gamma']
 # gammacov = numpy.cov(gamma,rowvar=False)
@@ -99,23 +98,23 @@ print "standard deviations of E(B-V)"
 print numpy.std(fit['k']*((fit['gamma'][:,1]-fit['gamma'][:,2]))[:,None])
 print numpy.std(fit['R']*((fit['rho1'][:,1]-fit['rho1'][:,2]))[:,None])
 
-pars = ['alpha','alpha','beta','beta','eta','eta','gamma','gamma','rho1','rho1','L_sigma']
-pars_n = ['\\alpha_X','{\\alpha_X/\\alpha_2-1}','\\beta_X','{\\beta_X/\\beta_2-1}',\
-  '\\eta_X','{\\eta_X/\\eta_2-1}', '{\\gamma_X/\gamma_2-1}','R_X', '{\\delta_X/\\delta_2-1}',\
-    'R_{\\delta X}','\\sigma_X']
-sigfig = [4,1,3,2,4,2,2,2,2,2,3]
-for p,pn, s in zip(pars,pars_n,sigfig):
-    print '${}$'.format(pn)
-    for i in xrange(5):
-        print '&'
-        if pn[0] == 'R':
-            dum = numpy.percentile(fit[p][:,i]/(fit[p][:,1]-fit[p][:,2])[:,None],(50,50-34,50+34)) 
-        elif pn[0] == '{':
-            dum = numpy.percentile(fit[p][:,i]/fit[p][:,2]-1,(50,50-34,50+34)) 
-        else :
-            dum = numpy.percentile(fit[p][:,i],(50,50-34,50+34))            
-        print  '${1:6.{0}f}^{{{2:6.{0}f}}}_{{{3:6.{0}f}}}$'.format(s,dum[0], dum[2]-dum[0],dum[1]-dum[0] )
-    print '\\\\'
+# pars = ['alpha','alpha','beta','beta','eta','eta','gamma','gamma','rho1','rho1','L_sigma']
+# pars_n = ['\\alpha_X','{\\alpha_X/\\alpha_2-1}','\\beta_X','{\\beta_X/\\beta_2-1}',\
[…]

### 2016-09-23 forgerard.tex
logging on ahead

@@
 
+\section{Interpreting $k$ and $D$ As Parameters of a Single Dust Model}
+%ipdb> print y, y-ymin, ymax-y
+%2.23720862938 0.00612061774367 0.00623996846008
+%ipdb> (y,ymin,ymax)  = numpy.percentile(samples[:,1],(50,50-34,50+34)) 
+%ipdb> print y, y-ymin, ymax-y
+%-3.46707773157e-05 0.000555359008477 0.000616592111953
+Until now we have considered $k$ and $D$ as independent external and internal parameters.  However, they may be both
+parameters of a single underlying dust.  Indeed the CCM dust law can be exactly written as a two-parameter linear model
+\begin{equation}
+A_X = A_V a(X) + E(B-V) b(X).
+\end{equation}
+The Fitzpatrick model can also approximately be described by a linear model in the range of $R_V$ and wavelength under consideration:
+the results shown here vary only at the percent level when making this approximation.
+
+In our model, variations in $k$ and $D$ affect magnitudes in two directions in magnitude space
+$\frac{\partial A}{\partial E_\delta(B-V)}$, $\frac{\partial A}{\partial E_\gamma(B-V)}$.  In the Fitzpatrick model
+variations on $E^F(B-V)$ and $A^F_V=R^F_VE^F(B-V)$ induce magnitude changes in
+in directions
+$\frac{\partial A}{\partial E^F(B-V)}$, $\frac{\partial A}{\partial A^F_V}$.
+The planes in magnitude-space defined by each pair of vectors are nearly parallel, in that
+\begin{equation}
+\begin{pmatrix}
+\frac{\partial A}{\partial E_\delta(B-V)} \\
+\frac{\partial A}{\partial E_\gamma(B-V)}
+\end{pmatrix}=
+\begin{pmatrix}
+0.74 & -5.45 \\
+1.15 & 2.84
+\end{pmatrix} 
+\begin{pmatrix}
+\frac{\partial A}{\partial R^F_V} \\
+\frac{\partial A}{\partial A^F_V}
+\end{pmatrix}+
+\vec{\epsilon},
+\end{equation}
+where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
+contribute  5\% and 2\% to the total  length of the vector.
+
+The projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
+onto the Fitzpatrick plane
+have corresponding values of $E^F(B-V)$ and $A^F$, up to a constant.  These are shown in Figure~\ref{avebv:fig}.
+The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.5$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5in]{output11/avebv_synth.pdf}
+    \caption{\textcolor{red}{Projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
+onto the Fitzpatrick plane.}
+   \label{avebv:fig}}
+\end{figure}
+
+The linear fit produces the zeropoint (which happens to be consistent with zero) along with the slope, allowing us to determine $R^F_V$ for each supernova,
+as shown in Figure~\ref{avrv:fig}.  An interesting feature is that the distribution at extreme blue colors seems to be different from the distribution for redder objects.
+I will contemplate whether this could mean anything.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5in]{output11/avrv_synth.pdf}
+    \caption{\textcolor{red}{$R^F_V$ for each supernova.}
+   \label{avrv:fig}}
+\end{figure}
+
+The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
+parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
+external dust is responsible for most of our $k$ and $D$ parameters.
+
 \section{Discussion}

### 2016-09-23 d2.py

@@ -78,7 +78,7 @@ f.close()
 
 
 av=0.1
-ebv=0.1/3.1
+ebv=0.1/2.24
 A1=getFitzExt(efflam, av , ebv)
 
 A2=getFitzExt(efflam, av+0.01 , ebv)
@@ -130,31 +130,56 @@ ebvav = numpy.dot(tmat,ebv)
 
 coeffs, cov = numpy.polyfit(ebvav[0,:],ebvav[1,:], 1,cov=True)
 
+ebv  = ((fit['rho1'][:,1]-fit['rho1'][:,2])[:,None] * fit['R'])
+ebv = numpy.array([ebv,((fit['gamma'][:,1]-fit['gamma'][:,2])[:,None] * fit['k'])])
+
+ebvav=[]
+for ind in xrange(ebv.shape[2]):
+  ebvav.append(numpy.dot(tmat,ebv[:,:,ind]))
+
+ebvav=numpy.array(ebvav)
+
+ebvav_s = numpy.percentile(ebvav,(50,50-34,50+34),axis=2)
+
 # ebv  = numpy.median((fit['rho1'][:,1]-fit['rho1'][:,2])[:,None] * fit['R'],axis=0)
 # ebv = numpy.array([ebv,numpy.median((fit['gamma'][:,1]-fit['gamma'][:,2])[:,None] * fit['k'],axis=0)])
 # ebvav = numpy.dot(tmat,ebv)
-plt.scatter(ebvav[0,::1000],ebvav[1,::1000],marker='.')
-plt.xlabel(r'$A_{V,eff}+ const $')
-plt.ylabel(r'$E(B-V)_{eff} + const$')
-x = numpy.array([-0.1,0.4])
-plt.plot(x, coeffs[1]+coeffs[0]*x,label=r'$R_V={:6.2f}$'.format(coeffs[0]))
+
+plt.errorbar(ebvav_s[0,:,0], ebvav_s[0,:,1], \
+ xerr=(ebvav_s[0,:,0]-ebvav_s[1,:,0], ebvav_s[2,:,0]-ebvav_s[0,:,0]),\
+ yerr=(ebvav_s[0,:,1]-ebvav_s[1,:,1], ebvav_s[2,:,1]-ebvav_s[0,:,1]),fmt='o',alpha=0.4)
+# plt.scatter(ebvav[0,::1000],ebvav[1,::1000],marker='.')
+plt.ylabel(r'$A^F_{V,eff}+ const $')
[…]

### 2016-09-27 forgerard.tex
plowing on

@@
 &
-$0.0026^{0.0004}_{-0.0005}$
-\\
-${\alpha_X/\alpha_V-1}$
+$0.0026^{0.0005}_{-0.0004}$
+\\
+${\alpha_X/\alpha_2-1}$
 &
@@
 &
-0
+$   0.0^{   0.0}_{   0.0}$
 &
@@
 &
-$ 0.025^{ 0.003}_{-0.002}$
+$ 0.025^{ 0.002}_{-0.003}$
 &
@@
 \\
-${\beta_X/\beta_V-1}$
-&
-$  0.25^{  0.05}_{ -0.05}$
+${\beta_X/\beta_2-1}$
+&
+$  0.26^{  0.05}_{ -0.05}$
 &
@@
 &
-0
+$  0.00^{  0.00}_{  0.00}$
 &
@@
 &
-$ -0.23^{  0.03}_{ -0.03}$
+$ -0.24^{  0.03}_{ -0.03}$
 \\
@@
 &
-$-0.0002^{0.0011}_{-0.0011}$
-&
-$0.0001^{0.0009}_{-0.0009}$
+$-0.0002^{0.0012}_{-0.0011}$
+&
+$-0.0000^{0.0010}_{-0.0009}$
 &
@@
 \\
-${\eta_X/\eta_V-1}$
-&
-$ -0.38^{  2.21}_{ -1.84}$
-&
-$ -0.32^{  1.51}_{ -1.15}$
-&
-0
-&
-$ -0.11^{  0.28}_{ -0.26}$
-&
-$ -0.86^{  1.69}_{ -1.24}$
-\\
-${\gamma_X/\gamma_V-1}$
+${\eta_X/\eta_2-1}$
+&
+$ -0.40^{  2.33}_{ -1.90}$
+&
+$ -0.34^{  1.60}_{ -1.20}$
+&
+$  0.00^{  0.00}_{  0.00}$
+&
+$ -0.11^{  0.29}_{ -0.27}$
+&
+$ -0.84^{  1.66}_{ -1.27}$
+\\
+${\gamma^0_X/\gamma^0_2-1}$
 &
@@
 \\
-$R_X$
-&
-$  4.79^{  0.49}_{ -0.43}$
-&
-$  3.88^{  0.40}_{ -0.35}$
-&
-$  2.88^{  0.31}_{ -0.28}$
-&
-$  2.22^{  0.25}_{ -0.23}$
-&
-$  1.60^{  0.21}_{ -0.20}$
-\\
-${\delta_X/\delta_V-1}$
-&
-$ -0.31^{  0.18}_{ -0.19}$
-&
-$ -0.17^{  0.10}_{ -0.10}$
-&
-0
+$R^_{\gamma^0 X}$
+&
+$  4.78^{  0.47}_{ -0.42}$
+&
+$  3.87^{  0.38}_{ -0.34}$
+&
+$  2.87^{  0.30}_{ -0.27}$
+&
+$  2.21^{  0.25}_{ -0.23}$
+&
+$  1.58^{  0.21}_{ -0.19}$
+\\
+${\gamma^1_X/\gamma^1_2-1}$
+&
+$ -0.31^{  0.17}_{ -0.18}$
+&
+$ -0.17^{  0.09}_{ -0.10}$
+&
+$  0.00^{  0.00}_{  0.00}$
 &
@@
 \\
-$R_{\delta X}$
-&
-$ -4.06^{  1.97}_{ -4.44}$
-&
-$ -4.92^{  2.03}_{ -4.95}$
-&
-$ -5.89^{  2.22}_{ -5.67}$
-&
-$ -5.48^{  2.04}_{ -5.24}$
-&
-$ -4.86^{  1.82}_{ -4.66}$
+$R_{\gamma^1 X}$
+&
+$ -4.02^{  1.87}_{ -4.10}$
+&
+$ -4.87^{  1.93}_{ -4.54}$
+&
+$ -5.84^{  2.11}_{ -5.21}$
+&
+$ -5.45^{  1.94}_{ -4.83}$
+&
+$ -4.86^{  1.75}_{ -4.32}$
 \\
@@
 &
-$ 0.061^{ 0.013}_{-0.012}$
-&
-$ 0.034^{ 0.007}_{-0.007}$
+$ 0.060^{ 0.012}_{-0.012}$
+&
+$ 0.033^{ 0.007}_{-0.007}$
 &
@@
 &
-$ 0.013^{ 0.007}_{-0.008}$
+$ 0.012^{ 0.007}_{-0.008}$
 &
@@
 
+\section{Supernova Model Part 2}
+\label{model2:sec}
+We hypothesize that at peak brightness
+SN~Ia broadband magnitudes and colors are correlated with
+spectral features: equivalent widths and line positions are considered as statistics localized in wavelength that are insensitive to variations in
+broadband colors.
+Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
+of intrinsic variation is accommodated.
+The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
+\textcolor{red}{The intrinsic magnitudes are then
+modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
+
+We assume 
+that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
+on the
+ equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
+$EW_{Ca}$, $EW_{Si}$,
+\textcolor{red}{ and $\lambda_{Si}$ the wavelength of the minimum of 
+the SiII$\lambda6355$ feature}:
+these spectral features are associated with SN~Ia  spectroscopic diversity  
+\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
+$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
+\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
+An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
+Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
+$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
+to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
+The observed magnitudes are linearly dependent on an
+extrinsic-color parameter $k$.  The observables
+$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
+shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
+The model is written as
+\begin{equation}
+\begin{pmatrix}
+U\\B\\V\\R\\I
+\end{pmatrix}
+\sim \mathcal{N}
+\left(
+\Delta +
+\begin{pmatrix}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
+\end{pmatrix}
+,C_{c}
+\right)
+\label{ewsiv:eqn}
+\end{equation}
+\begin{equation}
+\begin{pmatrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
+\end{pmatrix}
+\sim \mathcal{N}
+\left(
+\begin{pmatrix}
+U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
+V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
+EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
+\end{pmatrix}
+,C
+\right).
+\label{dust:eqn}
+\end{equation}
+The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
+relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
+(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
+The global parameters $\gamma$ are the slopes that connect the extrinsic-color
+parameter and observed magnitudes.
+
+To constrain the degrees of freedom and degeneracies inherent in the model we impose that
+\color{red}
+each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
+conditions break the 
+degeneracies  $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1}k$ and $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
+Furthermore we impose
+\color{black} 
+\begin{equation}
+\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \langle D \rangle=0, \gamma^0_{0} > 0, \gamma^1_{0} < 0, \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
+\end{equation}
+The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
+associated
+with  simultaneous sign flips of
+$\delta$--$D$ and $\gamma$--$k$
+\color{red}
+(when running our fits, $k$ and $D$ are set to
+identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ distinguishes the two.)
+Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
+each other, as is apparent after 
+running the Monte Carlo with exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
+The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
+otherwise identical initial conditions for $\gamma$, $\delta$ produce indistinguishable posteriors
+with relatively broad credible intervals and lower maximum likelihood.
+\color{black}
+As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
+by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.
+
 \section{SN 2014J in the Context of Our Model}
@@
 \begin{equation}
-A_X = A_V a(X) + E(B-V) b(X).
+A_X = a(X)  A_V + b(X) E(B-V).
 \end{equation}
@@
 the results shown here vary only at the percent level when making this approximation.
+Similarly our model can be expressed as
+\begin{equation}
+A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2}  E_{\gamma^1}(B-V).
+\end{equation}
 
@@
 \begin{pmatrix}
-\frac{\partial A}{\partial E_\delta(B-V)} \\
-\frac{\partial A}{\partial E_\gamma(B-V)}
+ \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
+\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
 \end{pmatrix}=
 \begin{pmatrix}
-0.74 & -5.45 \\
-1.15 & 2.84
+1.16 & 2.82 \\
+0.74 & -5.43
 \end{pmatrix} 
 \begin{pmatrix}
-\frac{\partial A}{\partial R^F_V} \\
-\frac{\partial A}{\partial A^F_V}
+a(X) \\
+b(X)
 \end{pmatrix}+
@@
 where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
-contribute  5\% and 2\% to the total  length of the vector.
+contribute  2\% and 5\% to the total  length of the vector.
 
@@
    \centering
-   \includegraphics[width=2.8in]{output11/rigault3.pdf}
-      \includegraphics[width=2.8in]{output11/rigault2.pdf}
+%   \includegraphics[width=2.8in]{output11/rigault3.pdf}
+%      \includegraphics[width=2.8in]{output11/rigault2.pdf}
       \caption{\textcolor{red}{Left: Intrinsic parameter $E_\gamma(B-V)$  versus host mass.  Hosts too faint for a mass measurement

### 2016-09-27 fitz15.py

@@ -16,66 +16,9 @@ def getFitzExt(efflam,av, ebv):
 
 efflam = numpy.array([ 3693.16777627,  4369.37505509,  5287.48667023,  6319.19906153,7610.89305298])
 
-f = open('temp11.pkl','rb')
+f = open('temp15.pkl','rb')
 (fit, _) = pickle.load(f)
 f.close()
-
-# f99 = sncosmo.F99Dust(r_v =2.97)
-# f99.set(ebv=1.)
-# A_ = f99.propagate(efflam,1.)
-# A1 = -2.5*numpy.log10(A_)
-# A1 = A1/A1[2]
-
-
-
-# dum = fit['gamma'][:,None,:] + fit['R'][:,:,None]/fit['k'][:,:,None] * fit['rho1'][:,None,:]
-# dum = dum/dum[:,:,2][:,:,None]
-# B1=[]
-# for i in xrange(5):
-#   B1.append(numpy.percentile(dum[:,:,i],(50,50-34,50+34)))
-
-# B1=numpy.array(B1)
-# plt.errorbar(efflam,B1[:,0],yerr=(B1[:,0]-B1[:,1],B1[:,2]-B1[:,0]),fmt='o',color='blue',label='Model')
-# plt.scatter(efflam,A1,color='red',label='Fitzpatrick')
-# plt.legend()
-# pp = PdfPages("output11/rvvector.pdf")
-# plt.savefig(pp,format='pdf')
-# pp.close()
-# plt.close()
-
-# x, xmin, xmax = numpy.percentile((dum[:,:,1]-1),(50,50-34,50+34),axis=0)
-# y, ymin, ymax = numpy.percentile(1./(dum[:,:,1]-1),(50,50-34,50+34),axis=0)
-# # plt.hist(numpy.median(1./(dum[:,:,1]-1),axis=0))
-# plt.errorbar(x,y,xerr=(x-xmin,xmax-x),yerr=(y-ymin,ymax-y),fmt='.',alpha=0.4)
-# plt.xlim((-1,2))
-# plt.ylim((-7,10))
-# plt.xlabel(r'$E(B-V)$')
-# plt.ylabel(r'$R_V$')
-# pp = PdfPages("output11/embrv.pdf")
-# plt.savefig(pp,format='pdf')
-# pp.close()
-# plt.close()
-
[…]

### 2016-09-27 table11.py

@@ -3,7 +3,7 @@
 import pickle
 import cPickle
 import numpy
-
+import sivel
 import sncosmo
 
 efflam = numpy.array([ 3693.16777627,  4369.37505509,  5287.48667023,  6319.19906153,7610.89305298])
@@ -100,8 +100,8 @@ print numpy.std(fit['R']*((fit['rho1'][:,1]-fit['rho1'][:,2]))[:,None])
 
 # pars = ['alpha','alpha','beta','beta','eta','eta','gamma','gamma','rho1','rho1','L_sigma']
 # pars_n = ['\\alpha_X','{\\alpha_X/\\alpha_2-1}','\\beta_X','{\\beta_X/\\beta_2-1}',\
-#   '\\eta_X','{\\eta_X/\\eta_2-1}', '{\\gamma_X/\gamma_2-1}','R_X', '{\\delta_X/\\delta_2-1}',\
-#     'R_{\\delta X}','\\sigma_X']
+#   '\\eta_X','{\\eta_X/\\eta_2-1}', '{\\gamma^0_X/\gamma^0_2-1}','R_{\gamma^0 X}', '{\\gamma^1_X/\\gamma^1_2-1}',\
+#     'R_{\\gamma^1 X}','\\sigma_X']
 # sigfig = [4,1,3,2,4,2,2,2,2,2,3]
 # for p,pn, s in zip(pars,pars_n,sigfig):
 #     print '${}$'.format(pn)
@@ -167,37 +167,7 @@ pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)
 pkl_file.close()
 
-dic_phreno=cPickle.load(open("phrenology_2016_12_01_CABALLOv1.pkl"))
-
-dic_meta=cPickle.load(open("META.pkl"))
-
-sivel=[]
-sivel_err=[]
-snname=[]
-for sn in data['snlist']:
-   if sn in dic_meta.keys() and sn in dic_phreno.keys():
-      meta = dic_meta[sn]
-      vSiII_6355_lbd=0.
-      vSiII_6355_lbd_err=0.
-      counter  = 0
-      for sp in dic_phreno[sn]["spectra"]:
-         if sp in meta['spectra'].keys() and  numpy.abs(meta['spectra'][sp]['salt2.phase']) < 2.5 and numpy.isfinite(dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]):
[…]

### 2016-09-29 forgerard.tex
making progress

@@
 %-----
- $(1-10^{-5})$
+ $98$\%
 %------
@@
 SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
-SNF20070725-001 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
-SNF20071108-021 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
-SNF20080914-001 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
-SNF20060609-002 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6129 \pm   7$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
-SNF20050624-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
-SNF20060618-023 & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
-SNF20080531-000 & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
-SN2006do & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
-PTF12ikt & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
-SN2006dm & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
-PTF13azs & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
-SN2005hj & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
-PTF12iiq & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
-PTF10ndc & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
-SNF20080919-002 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
-SNPGC027923 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
-SNF20070330-024 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
-SNF20061030-010 & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
-SNhunt46 & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
-SN2005hc & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
-LSQ12dbr & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
-LSQ12hjm & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
-SNF20060521-001 & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
-SNF20070630-006 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-PTF11drz & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
-SNF20080323-009 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
-SNF20071021-000 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
-SNNGC0927 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
-SNF20060526-003 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
-SNF20080806-002 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
-SNF20080803-000 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
-SNF20080822-005 & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
-SNF20060618-014 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
-PTF12ghy & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
-SNF20070531-011 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
-SNF20070831-015 & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
-SNF20070417-002 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
-PTF11cao & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
-SNF20080522-000 & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-PTF10qjq & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
-PTF12dxm & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
-SNF20061021-003 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
-SNF20080510-005 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
-SNF20080507-000 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
-SNF20080913-031 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\
+SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ \\
+SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
+SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
+SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
+SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6129 \pm   7$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
+SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
+SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
+PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
+SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
+PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
+SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
+PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
+PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
+SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
+SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
+SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
+SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
+SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
+SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
+LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
+LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
+SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
+SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
+PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
+SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
+SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
+SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
+SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
+SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
+SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
+SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
+PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
+SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
+SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
+SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
+PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
+SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
+PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
+PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
+SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
+SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
+SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
+SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
+SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\
 \enddata
@@
 
-\section{Supernova Model}
+\section{Supernova Model: Two Extrinsic Parameters}
 \label{model:sec}
+
 We hypothesize that at peak brightness
@@
 broadband colors.
-Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
-of intrinsic variation is accommodated.
-The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
+%Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
+%of intrinsic variation is accommodated.
+The intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
 \textcolor{red}{The intrinsic magnitudes are then
 modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
-
+\subsection{Model}
 We assume 
@@
 \citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
-$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
+\textcolor{red}{
+The explicit omission of light-curve shape in our model is compensated by its proxy
+$EW_{Si}$ at peak brightness}
 \citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
-An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
+% An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
 Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
@@
 to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
-The observed magnitudes are linearly dependent on an
-extrinsic-color parameter $k$.  The observables
-$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
+The observed magnitudes are linearly dependent on the
+extrinsic-color parameters $k_0$ and $k_1$.  The observables
+$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
 shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
@@
 \begin{pmatrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
 \end{pmatrix}
@@
 \begin{pmatrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
 \end{pmatrix}
@@
 \begin{pmatrix}
-U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
+U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
+V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
@@
 \end{equation}
-The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
-relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
+The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
+relate intrinsic magnitudes with the spectral-feature parameters.
 (In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
-The global parameters $\gamma$ are the slopes that connect the extrinsic-color
+The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
 parameter and observed magnitudes.
@@
 \color{red}
-each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
+each of the vectors $k_0+1/N$ and $k_1+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
 conditions break the 
-degeneracies  $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1}k$ and $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
+degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$.
 Furthermore we impose
@@
 \begin{equation}
-\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 > 0, \delta_0 < 0.
+\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_0 > 0, \gamma^1_0 < 0.
 \end{equation}
@@
 with  simultaneous sign flips of
-$\delta$--$D$ and $\gamma$--$k$
+$\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
 \color{red}
-(when running our fits, $k$ and $D$ are set to
-identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ distinguishes the two.)
-Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
-each other, as is apparent after 
-running the Monte Carlo with exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
-The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
-otherwise identical initial conditions for $\gamma$, $\delta$ produce indistinguishable posteriors
+(when running our fits, $k_0$ and $k_1$ are set to
+identical initial conditions, so the difference in the signs of $\gamma^0_0$ and $\gamma^1_0$ distinguishes the two.)
+As  $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
+each other,
+the different initial and boundary conditions for $\gamma^0_0$ and $\gamma^1_0$ break the degeneracy of our mixture model;
+otherwise identical initial conditions for $\gamma^0$, $\gamma^1$ produce indistinguishable posteriors
 with relatively broad credible intervals and lower maximum likelihood.
+
 \color{black}
-As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
-by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.
 
 Having the intrinsic dispersion $C_c$ as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
-ascribed to $\Delta$, $\delta D$, and $\gamma k$ could also be attributed to intrinsic dispersion.  There are several features of the model
+ascribed to $\Delta$, $\gamma^0 k_0$, and $\gamma^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
 that drives the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$;
-The distributions of $\Delta$ and $k$ turn out to
+The distributions of $\Delta$, $k_0$, and $k_1$ turn out to
 be non-Gaussian, and so are not well described by a Normal covariance; Grey offsets would appear as a constant
 in all elements of the covariance matrix, which is disfavored for the Bayesian prior selected for $C_c$.
-
-When interpreted as being due to dust, the extrinsic terms are associated with extinction $A_X = \gamma_X k$.  In
-this parlance our parameters can be re-expressed as the  familiar color excess
-$E_\gamma(B-V) = (\gamma_B-\gamma_V) k$ and total-to-selective extinction $R_X = \frac{\gamma_X}{\gamma_B-\gamma_V}$.
-Similar reparameterizatons of the intrinsic color parameters are
-$E_\delta(B-V) = (\delta_B-\delta_V) D$ and $R_{\delta X} = \frac{\delta_X}{\delta_B-\delta_V}$.
 
@@
 
-\section{Results}
+\subsection{Results}
 \label{results:sec}
@@
    \includegraphics[width=5.5in]{output11/coeff0.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $U$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution, not to 68\%, 95\%, etc.\
@@
    \includegraphics[width=5.5in]{output11/coeff1.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $B$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $B$ band.
  \label{global2:fig}}
@@
    \includegraphics[width=5.5in]{output11/coeff2.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $V$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $V$ band.
  \label{global3:fig}}
@@
       \includegraphics[width=5.5in]{output11/coeff3.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $R$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $R$ band.
  \label{global4:fig}}
@@
          \includegraphics[width=5.5in]{output11/coeff4.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma$, $\delta$, and $\sigma$ in the $I$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $I$ band.
  \label{global5:fig}}
@@
 are given in Table~\ref{global:tab}.
+\color{red}
+As the $\gamma$ parameters are free up to a multiplicative constant and the highly non-zero values of $\gamma^i_V$,
+their results are also shown in terms of $\gamma^i_X/\gamma^i_V-1$.
+\color{black}
 Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig} .
@@
 &
-$   0.0^{   0.0}_{   0.0}$
+$   0$
 &
@@
 &
-$  0.00^{  0.00}_{  0.00}$
+$  0$
 &
@@
 \\
-${\gamma^0_X/\gamma^0_2-1}$
+$\gamma^0_X$
+&
+$ 62.16^{  3.68}_{ -3.52}$
+&
+$ 50.39^{  3.05}_{ -2.96}$
+&
+$ 37.38^{  2.58}_{ -2.52}$
+&
+$ 28.71^{  2.31}_{ -2.25}$
+&
+$ 20.61^{  2.15}_{ -2.11}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
 &
@@
 \\
-$R^_{\gamma^0 X}$
-&
-$  4.78^{  0.47}_{ -0.42}$
-&
-$  3.87^{  0.38}_{ -0.34}$
-&
-$  2.87^{  0.30}_{ -0.27}$
-&
-$  2.21^{  0.25}_{ -0.23}$
-&
-$  1.58^{  0.21}_{ -0.19}$
+$\gamma^1_X$
+&
+$ -9.75^{  3.39}_{ -4.14}$
+&
+$-11.82^{  2.78}_{ -3.35}$
+&
+$-14.26^{  2.38}_{ -2.73}$
+&
+$-13.35^{  2.09}_{ -2.30}$
+&
+$-11.91^{  2.01}_{ -2.15}$
 \\
@@
 $ -0.17^{  0.10}_{ -0.09}$
-\\
-$R_{\gamma^1 X}$
-&
-$ -4.02^{  1.87}_{ -4.10}$
-&
-$ -4.87^{  1.93}_{ -4.54}$
-&
-$ -5.84^{  2.11}_{ -5.21}$
-&
-$ -5.45^{  1.94}_{ -4.83}$
-&
-$ -4.86^{  1.75}_{ -4.32}$
 \\

### 2016-09-30 forgerard.tex
commit

@@
 the Monte Carlo chains have not converged to the stationary posterior distribution.
-We have rurun the analysis with a variety of initial conditions, including one with all the $\gamma$'s and $\delta$'s equal to zero, except for a small positive 
-$\gamma_0$ and small negative $\delta_0$ to satisfy our limit conditions.  Parameter credible intervals
+We have rurun the analysis with a variety of initial conditions, including one with all the $\gamma$'s equal to zero, except for a small positive 
+$\gamma^0_0$ and small negative $\gamma^1_0$ to satisfy our limit conditions.  Parameter credible intervals
 remain consistent within uncertainty.
@@
 
-For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $R$, $R_\delta$, and $\sigma$
-(and other interesting derived parameters)
+For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$
 are given in Table~\ref{global:tab}.
 \color{red}
-As the $\gamma$ parameters are free up to a multiplicative constant and the highly non-zero values of $\gamma^i_V$,
+As the $\gamma$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_V$,
 their results are also shown in terms of $\gamma^i_X/\gamma^i_V-1$.
@@
 
-\color{red}
-
-The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model:
-we now do so in a fit to the 
-model of \citet{1999PASP..111...63F},
-taking the fixed 3693,  4369,  5287,  6319, 7611 \AA\  for the effective wavelengths of the supernova flux through the bands.
-Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
-$R_V=2.97^{+0.18}_{-0.17}$..  
-We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
-The posterior distributions for $R_{\gamma X}=\frac{\gamma_X}{\gamma_B-\gamma_V}$ are shown in Figure~\ref{rx:fig}.
-\color{black}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/fitz.pdf}
-   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=2.97$.}
-   \label{fitz:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
-      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
-   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_B-\gamma_V}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$.
-   \label{rx:fig}}
-\end{figure}
-
-%
-%The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  
-%Our measurements of
-%$R_X$ and $\frac{\gamma_X}{\gamma_2}$, placed at the effective wavelength of the supernova flux that passes
-%through the synthetic bands, are shown in
-%Figure~\ref{ccm:fig}.
-%
-%
-
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output11/ccm.pdf}
-%      \includegraphics[width=2.8in]{output11/ccm2.pdf} 
-%   \caption{68\% credible intervals of Left: $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$; Right: $\frac{\gamma_X}{\gamma_2}$. 
-%   \label{ccm:fig}}
-%\end{figure}
-
-None of the 20000 links of 
-our Monte Carlo chains for $\delta$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
-intrinsic parameter on supernova magnitudes
-with probability $(1-5\times 10^{-5})$.
-\textcolor{red}{
-The values of $\delta_X/\delta_V$, plotted in  Figure~\ref{deltaratio:fig}, are not monotonic with color: they increase from the $U$ to $V$, and then decrease
-from $V$ to $I$,
-a consequence
-of which is that
-a reddening in $B-V$ comes with a blueing in $V-R$.
-Also apparent is that a reddening of $B-V$ is associated with a brightening of the supernova.
-The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$ are shown in Figure~\ref{rx:fig}.
-Although the posteriors of $\delta$ are close to Gaussian, $\delta_B-\delta_V$ can approach zero, resulting in the
-elongated tail in negative  $R_{\delta X}$.
-All values are significantly negative.}
-These are not the behaviors expected from normal dust,
-circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
-2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
-more complicated underlying supernova physics.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/deltaratio.pdf}
-   \caption{68\% credible intervals of $\frac{\delta_X}{\delta_V}$ at the effective wavelengths of the corresponding bands.
-   \label{deltaratio:fig}}
-\end{figure}
-
-The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
- $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
-Recall that our boundary conditions set the means of both distributions to zero. 
-The standard deviations of $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
-%-----
-0.079
-and 0.015
-%-----
-mag respectively.
-The range of $B-V$ colors is $\sim 5$ times larger for the external contribution. 
-Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red, consistent
-with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/ebv.pdf}
-   \caption{Ideograms of the external $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
-   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
-   \label{ebv:fig}}
-\end{figure}
-
 The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
@@
 
-Non-trivial residual magnitude dispersions are captured in $C_c$.   Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the
-square root of the diagonal elements of $C_c$.  The residual intrinsic dispersion ranges from
+Non-trivial residual magnitude dispersions are captured in $C_c$.
+% Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the square root of the diagonal elements of $C_c$. 
+The residual intrinsic dispersion ranges from
 $\sim 0.01$ to 0.06 mag, significantly smaller
@@
 \begin{pmatrix}
-0.0040 & 0.0011 & -0.0002 & -0.0000 & 0.0003 \cr
-0.0011 & 0.0012 & 0.0002 & -0.0000 & -0.0006 \cr
--0.0002 & 0.0002 & 0.0004 & 0.0001 & -0.0002 \cr
--0.0000 & -0.0000 & 0.0001 & 0.0002 & 0.0002 \cr
+0.0038 & 0.0010 & -0.0002 & -0.0000 & 0.0003 \\
+0.0010 & 0.0011 & 0.0002 & -0.0000 & -0.0006 \\
+-0.0002 & 0.0002 & 0.0004 & 0.0000 & -0.0002 \\
+-0.0000 & -0.0000 & 0.0000 & 0.0002 & 0.0002 \\
 0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
@@
  \begin{pmatrix}
-0.069 , 0.035 , 0.023 , 0.053
+0.068 , 0.034 , 0.023 , 0.053
   \end{pmatrix} \text{mag}
@@
 \begin{pmatrix}
-1.000 & 0.624 & -0.318 & -0.287 \cr
-0.624 & 1.000 & -0.180 & 0.104 \cr
--0.318 & -0.180 & 1.000 & 0.629 \cr
--0.287 & 0.104 & 0.629 & 1.000
-  \end{pmatrix}.
+1.000 & 0.615 & -0.334 & -0.296 \\
+0.615 & 1.000 & -0.193 & 0.099 \\
+-0.334 & -0.193 & 1.000 & 0.634 \\
+-0.296 & 0.099 & 0.634 & 1.000  \end{pmatrix}.
   \label{color_cor:eqn}
@@
 
- \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.5in]{output11/sigma_corner.pdf} 
-   \caption{Posterior contours for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
-   \label{sigma:fig}}
-\end{figure}
-
-Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
+% \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=5.5in]{output11/sigma_corner.pdf} 
+%   \caption{Posterior contours for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
+%   \label{sigma:fig}}
+%\end{figure}
+
+Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k$, and
+$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
 $\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
 There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
-Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected for the infrequent selection of supernovae
+Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the infrequent selection of supernovae
 heavily extinguished by host-galaxy dust.
@@
    \includegraphics[width=5.5in]{output11/perobject_corner.pdf} 
-   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as the grey offset
+   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
 $\Delta$.  All links are plotted, so that each supernova contributes a cloud of points.
@@
 \citep{2003MNRAS.340.1057S}.
-Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062;
-this low correlation, and the broad distribution in $E_\delta(B-V)$ for low $E_\gamma(B-V)$,  indicate that what we have been calling intrinsic
-is not related to extrinsic dust.
 An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
@@
 701~\AA.  The implied span in $U$ magnitude is is 0.21~mag, so $\alpha_0$ cannot be completely due to the line iteslf.
+
+\subsection{Two Extrinsic Parameters}
+\color{red}
+The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
+\color{black}
+None of the 20000 links of 
+our Monte Carlo chains for $\delta$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
+influence of $k$ and $k_1$  on supernova magnitudes
+with probability $(1-5\times 10^{-5})$.
+
+\color{red}
+Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k + \gamma^1_X k_1$
+and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
+which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
+estimate $R_V=A_V/(E(B-V)-zeropoint$ per supernova.  These values are shown in Figure~\ref{avebv:fig}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.5in]{output11/avebv.pdf}
+   \includegraphics[width=2.5in]{output11/rv.pdf}
+   \caption{\textcolor{red}{Left: $A_V$ versus $E(B-V)$ and Right: $R_V=A_V/(E(B-V)-zeropoint$\
+   versus $E(B-V)$ for the supernova sample.}
+   \label{avebv:fig}}
+\end{figure}
+
+Until now we have considered $k$ and $D$ as independent external and internal parameters.  However, they may be both
+parameters of a single underlying dust.  Indeed the CCM dust law can be exactly written as a two-parameter linear model
+\begin{equation}
+A_X = a(X)  A_V + b(X) E(B-V).
+\end{equation}
+The Fitzpatrick model can also approximately be described by a linear model in the range of $R_V$ and wavelength under consideration:
+the results shown here vary only at the percent level when making this approximation.
+Similarly our model can be expressed as
+\begin{equation}
+A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2}  E_{\gamma^1}(B-V).
+\end{equation}
+
+In our model, variations in $k$ and $D$ affect magnitudes in two directions in magnitude space
+$\frac{\partial A}{\partial E_\delta(B-V)}$, $\frac{\partial A}{\partial E_\gamma(B-V)}$.  In the Fitzpatrick model
+variations on $E^F(B-V)$ and $A^F_V=R^F_VE^F(B-V)$ induce magnitude changes in
+in directions
+$\frac{\partial A}{\partial E^F(B-V)}$, $\frac{\partial A}{\partial A^F_V}$.
+The planes in magnitude-space defined by each pair of vectors are nearly parallel, in that
+\begin{equation}
+\begin{pmatrix}
+ \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
+\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
+\end{pmatrix}=
+\begin{pmatrix}
+1.16 & 2.82 \\
+0.74 & -5.43
+\end{pmatrix} 
+\begin{pmatrix}
+a(X) \\
+b(X)
+\end{pmatrix}+
+\vec{\epsilon},
+\end{equation}
+where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
+contribute  2\% and 5\% to the total  length of the vector.
+
+The projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
+onto the Fitzpatrick plane
+have corresponding values of $E^F(B-V)$ and $A^F$, up to a constant.  These are shown in Figure~\ref{avebv:fig}.
+The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.5$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5in]{output11/avebv_synth.pdf}
+    \caption{\textcolor{red}{Projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
+onto the Fitzpatrick plane.}
+   \label{avebv:fig}}
+\end{figure}
+
+The linear fit produces the zeropoint (which happens to be consistent with zero) along with the slope, allowing us to determine $R^F_V$ for each supernova,
+as shown in Figure~\ref{avrv:fig}.  An interesting feature is that the distribution at extreme blue colors seems to be different from the distribution for redder objects.
+I will contemplate whether this could mean anything.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5in]{output11/avrv_synth.pdf}
+    \caption{\textcolor{red}{$R^F_V$ for each supernova.}
+   \label{avrv:fig}}
+\end{figure}
+
+The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
+parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
+external dust is responsible for most of our $k$ and $D$ parameters.
+
+%
+%
+%The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model:
+%we now do so in a fit to the 
+%model of \citet{1999PASP..111...63F},
+%taking the fixed 3693,  4369,  5287,  6319, 7611 \AA\  for the effective wavelengths of the supernova flux through the bands.
+%Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
+%$R_V=2.97^{+0.18}_{-0.17}$..  
+%We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
+%The posterior distributions for $R_{\gamma X}=\frac{\gamma_X}{\gamma_B-\gamma_V}$ are shown in Figure~\ref{rx:fig}.
+%\color{black}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=3.2in]{output11/fitz.pdf}
+%   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=2.97$.}
+%   \label{fitz:fig}}
+%\end{figure}
+%
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
+%      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
+%   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_B-\gamma_V}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$.
+%   \label{rx:fig}}
+%\end{figure}
+
+%
+%The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  
+%Our measurements of
+%$R_X$ and $\frac{\gamma_X}{\gamma_2}$, placed at the effective wavelength of the supernova flux that passes
+%through the synthetic bands, are shown in
+%Figure~\ref{ccm:fig}.
+%
+%
+
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output11/ccm.pdf}
+%      \includegraphics[width=2.8in]{output11/ccm2.pdf} 
+%   \caption{68\% credible intervals of Left: $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$; Right: $\frac{\gamma_X}{\gamma_2}$. 
+%   \label{ccm:fig}}
+%\end{figure}
+
+\textcolor{red}{
+The values of $\delta_X/\delta_V$, plotted in  Figure~\ref{deltaratio:fig}, are not monotonic with color: they increase from the $U$ to $V$, and then decrease
+from $V$ to $I$,
+a consequence
+of which is that
+a reddening in $B-V$ comes with a blueing in $V-R$.
+Also apparent is that a reddening of $B-V$ is associated with a brightening of the supernova.
+The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$ are shown in Figure~\ref{rx:fig}.
+Although the posteriors of $\delta$ are close to Gaussian, $\delta_B-\delta_V$ can approach zero, resulting in the
+elongated tail in negative  $R_{\delta X}$.
+All values are significantly negative.}
+These are not the behaviors expected from normal dust,
+circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
+2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
+more complicated underlying supernova physics.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/deltaratio.pdf}
+   \caption{68\% credible intervals of $\frac{\delta_X}{\delta_V}$ at the effective wavelengths of the corresponding bands.
+   \label{deltaratio:fig}}
+\end{figure}
+
+The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
+ $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
+Recall that our boundary conditions set the means of both distributions to zero. 
+The standard deviations of $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
+%-----
+0.079
+and 0.015
+%-----
+mag respectively.
+The range of $B-V$ colors is $\sim 5$ times larger for the external contribution. 
+Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red, consistent
+with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.2in]{output11/ebv.pdf}
+   \caption{Ideograms of the external $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
+   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
+   \label{ebv:fig}}
+\end{figure}
 
@@
 
-\section{Interpreting $k$ and $D$ As Parameters of a Single Dust Model}
-%ipdb> print y, y-ymin, ymax-y
-%2.23720862938 0.00612061774367 0.00623996846008
-%ipdb> (y,ymin,ymax)  = numpy.percentile(samples[:,1],(50,50-34,50+34)) 
-%ipdb> print y, y-ymin, ymax-y
-%-3.46707773157e-05 0.000555359008477 0.000616592111953
-Until now we have considered $k$ and $D$ as independent external and internal parameters.  However, they may be both
-parameters of a single underlying dust.  Indeed the CCM dust law can be exactly written as a two-parameter linear model
-\begin{equation}
-A_X = a(X)  A_V + b(X) E(B-V).
-\end{equation}
-The Fitzpatrick model can also approximately be described by a linear model in the range of $R_V$ and wavelength under consideration:
-the results shown here vary only at the percent level when making this approximation.
-Similarly our model can be expressed as
-\begin{equation}
-A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2}  E_{\gamma^1}(B-V).
-\end{equation}
-
-In our model, variations in $k$ and $D$ affect magnitudes in two directions in magnitude space
-$\frac{\partial A}{\partial E_\delta(B-V)}$, $\frac{\partial A}{\partial E_\gamma(B-V)}$.  In the Fitzpatrick model
-variations on $E^F(B-V)$ and $A^F_V=R^F_VE^F(B-V)$ induce magnitude changes in
-in directions
-$\frac{\partial A}{\partial E^F(B-V)}$, $\frac{\partial A}{\partial A^F_V}$.
-The planes in magnitude-space defined by each pair of vectors are nearly parallel, in that
-\begin{equation}
-\begin{pmatrix}
- \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
-\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
-\end{pmatrix}=
-\begin{pmatrix}
-1.16 & 2.82 \\
-0.74 & -5.43
-\end{pmatrix} 
-\begin{pmatrix}
-a(X) \\
-b(X)
-\end{pmatrix}+
-\vec{\epsilon},
-\end{equation}
-where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
-contribute  2\% and 5\% to the total  length of the vector.
-
-The projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
-onto the Fitzpatrick plane
-have corresponding values of $E^F(B-V)$ and $A^F$, up to a constant.  These are shown in Figure~\ref{avebv:fig}.
-The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.5$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5in]{output11/avebv_synth.pdf}
-    \caption{\textcolor{red}{Projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
-onto the Fitzpatrick plane.}
-   \label{avebv:fig}}
-\end{figure}
-
-The linear fit produces the zeropoint (which happens to be consistent with zero) along with the slope, allowing us to determine $R^F_V$ for each supernova,
-as shown in Figure~\ref{avrv:fig}.  An interesting feature is that the distribution at extreme blue colors seems to be different from the distribution for redder objects.
-I will contemplate whether this could mean anything.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5in]{output11/avrv_synth.pdf}
-    \caption{\textcolor{red}{$R^F_V$ for each supernova.}
-   \label{avrv:fig}}
-\end{figure}
-
-The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
-parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
-external dust is responsible for most of our $k$ and $D$ parameters.
-
 \section{Discussion}

### 2016-09-30 fitz11.py

@@ -14,71 +14,15 @@ def getFitzExt(efflam,av, ebv):
   A1_ = -2.5*numpy.log10(A_)
   return A1_
 
+
 efflam = numpy.array([ 3693.16777627,  4369.37505509,  5287.48667023,  6319.19906153,7610.89305298])
 
 f = open('temp11.pkl','rb')
 (fit, _) = pickle.load(f)
 f.close()
 
-# f99 = sncosmo.F99Dust(r_v =2.97)
-# f99.set(ebv=1.)
-# A_ = f99.propagate(efflam,1.)
-# A1 = -2.5*numpy.log10(A_)
-# A1 = A1/A1[2]
-
-
-
-# dum = fit['gamma'][:,None,:] + fit['R'][:,:,None]/fit['k'][:,:,None] * fit['rho1'][:,None,:]
-# dum = dum/dum[:,:,2][:,:,None]
-# B1=[]
-# for i in xrange(5):
-#   B1.append(numpy.percentile(dum[:,:,i],(50,50-34,50+34)))
-
-# B1=numpy.array(B1)
-# plt.errorbar(efflam,B1[:,0],yerr=(B1[:,0]-B1[:,1],B1[:,2]-B1[:,0]),fmt='o',color='blue',label='Model')
-# plt.scatter(efflam,A1,color='red',label='Fitzpatrick')
-# plt.legend()
-# pp = PdfPages("output11/rvvector.pdf")
-# plt.savefig(pp,format='pdf')
-# pp.close()
-# plt.close()
-
-# x, xmin, xmax = numpy.percentile((dum[:,:,1]-1),(50,50-34,50+34),axis=0)
-# y, ymin, ymax = numpy.percentile(1./(dum[:,:,1]-1),(50,50-34,50+34),axis=0)
-# # plt.hist(numpy.median(1./(dum[:,:,1]-1),axis=0))
-# plt.errorbar(x,y,xerr=(x-xmin,xmax-x),yerr=(y-ymin,ymax-y),fmt='.',alpha=0.4)
-# plt.xlim((-1,2))
-# plt.ylim((-7,10))
-# plt.xlabel(r'$E(B-V)$')
-# plt.ylabel(r'$R_V$')
-# pp = PdfPages("output11/embrv.pdf")
-# plt.savefig(pp,format='pdf')
-# pp.close()
[…]

### 2016-09-30 view11.py

@@ -692,8 +692,8 @@ mega = numpy.transpose(mega)
 
 for index in xrange(5):
     figure = corner.corner(mega[index,:,:],labels=[r"$c_{}$".format(index), r"$\alpha_{}$".format(index),\
-                    r"$\beta_{}$".format(index),r"$\eta_{}$".format(index),r"$\gamma_{}$".format(index),\
-                    r"$\delta_{{1{}}}$".format(index), r"$\sigma_{}$".format(index)])
+                    r"$\beta_{}$".format(index),r"$\eta_{}$".format(index),r"$\gamma^0_{}$".format(index),\
+                    r"$\gamma^1_{{1{}}}$".format(index), r"$\sigma_{}$".format(index)])
     figure.suptitle(filts[index],fontsize=28)
     pp = PdfPages('output11/coeff{}.pdf'.format(index))
     plt.savefig(pp,format='pdf')
@@ -766,7 +766,7 @@ mega = numpy.array([fit['Delta'].flatten(),fit['EW'][:,:,0].flatten(),fit['EW'][
 mega = numpy.transpose(mega)
 mega=mega[::50,:]
 
-figure = corner.corner(mega,labels=[r"$\Delta$",r"$EW_{Ca}$",r"$EW_{Si}$",r"$\lambda_{Si}$",r"$E_\gamma(B-V)$",r"$E_\delta(B-V)$"],range=numpy.zeros(6)+1.)
+figure = corner.corner(mega,labels=[r"$\Delta$",r"$EW_{Ca}$",r"$EW_{Si}$",r"$\lambda_{Si}$",r"$E_{\gamma^0}(B-V)$",r"$E_{\gamma^1}(B-V)$"],range=numpy.zeros(6)+1.)
 pp = PdfPages('output11/perobject_corner.pdf')
 plt.savefig(pp,format='pdf')
 pp.close()

### 2016-10-03 forgerard.tex
forging ahead

@@
 
-Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k$, and
+Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k_0$, and
 $E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
@@
 
-\subsection{Two Extrinsic Parameters}
+\subsection{Two Extrinsic Parameters $k_0$ and $k_1$}
 \color{red}
@@
 None of the 20000 links of 
-our Monte Carlo chains for $\delta$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
-influence of $k$ and $k_1$  on supernova magnitudes
+our Monte Carlo chains for $\gamma$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
+influence of $k_0$ and $k_1$  on supernova magnitudes
 with probability $(1-5\times 10^{-5})$.
@@
 \color{red}
-Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k + \gamma^1_X k_1$
+Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k_0 + \gamma^1_X k_1$
 and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
 which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
-estimate $R_V=A_V/(E(B-V)-zeropoint$ per supernova.  These values are shown in Figure~\ref{avebv:fig}.
+estimate $R_V=A_V/(E(B-V)-zeropoint)$ per supernova, shown in Figure~\ref{avebv:fig}.
+Extremely blue supernovae ($E(B-V) + const <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
+whereas the extreme red objects ($E(B-V) + const >0.1$) have $R_V=  2.52 \pm   0.08$, indicating that different physics
+operate in these regimes.
 
@@
 
-Until now we have considered $k$ and $D$ as independent external and internal parameters.  However, they may be both
-parameters of a single underlying dust.  Indeed the CCM dust law can be exactly written as a two-parameter linear model
+Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
+parameters of a single  dust model.  Indeed the \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
 \begin{equation}
@@
 \end{equation}
-The Fitzpatrick model can also approximately be described by a linear model in the range of $R_V$ and wavelength under consideration:
-the results shown here vary only at the percent level when making this approximation.
-Similarly our model can be expressed as
+The \citet{1999PASP..111...63F} model is also approximately described by a linear model in the range of $R_V$ and wavelength under consideration:
+the results to follow vary at the percent level when making this approximation.
+Our model can be expressed as
 \begin{equation}
@@
 
-In our model, variations in $k$ and $D$ affect magnitudes in two directions in magnitude space
-$\frac{\partial A}{\partial E_\delta(B-V)}$, $\frac{\partial A}{\partial E_\gamma(B-V)}$.  In the Fitzpatrick model
-variations on $E^F(B-V)$ and $A^F_V=R^F_VE^F(B-V)$ induce magnitude changes in
-in directions
-$\frac{\partial A}{\partial E^F(B-V)}$, $\frac{\partial A}{\partial A^F_V}$.
-The planes in magnitude-space defined by each pair of vectors are nearly parallel, in that
+For the linear 2-parameter model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
+It turns out that the planes for both our and the Fitzpatrick dust model are nearly parallel, in that
 \begin{equation}
@@
 \begin{pmatrix}
-1.16 & 2.82 \\
-0.74 & -5.43
+1.15 & 2.82 \\
+0.75 & -5.43
 \end{pmatrix} 
@@
 
-The projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
-onto the Fitzpatrick plane
-have corresponding values of $E^F(B-V)$ and $A^F$, up to a constant.  These are shown in Figure~\ref{avebv:fig}.
-The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.5$.
+The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
+are projected onto the Fitzpatrick values of $E^F(B-V)$ and $A^F$, up to a constant:  these are shown in Figure~\ref{avebv:fig}.
+The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.43^{+0.16}_{-0.17}$.  
+The linear fit also produces the zeropoint, allowing us to determine $R^F_V$ for each supernova,
+which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
+the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.
 
@@
    \centering
-   \includegraphics[width=5in]{output11/avebv_synth.pdf}
-    \caption{\textcolor{red}{Projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
-onto the Fitzpatrick plane.}
-   \label{avebv:fig}}
-\end{figure}
-
-The linear fit produces the zeropoint (which happens to be consistent with zero) along with the slope, allowing us to determine $R^F_V$ for each supernova,
-as shown in Figure~\ref{avrv:fig}.  An interesting feature is that the distribution at extreme blue colors seems to be different from the distribution for redder objects.
-I will contemplate whether this could mean anything.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5in]{output11/avrv_synth.pdf}
-    \caption{\textcolor{red}{$R^F_V$ for each supernova.}
-   \label{avrv:fig}}
+   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
+   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
+    \caption{\textcolor{red}{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
+onto the Fitzpatrick plane.  Right: $R^F_V$ for each supernova.}
+   \label{avebv_synth:fig}}
 \end{figure}
@@
 parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
-external dust is responsible for most of our $k$ and $D$ parameters.
+external dust is responsible for most of our $k_0$ and $k_1$ parameters.
 
@@
 
-\textcolor{red}{
-The values of $\delta_X/\delta_V$, plotted in  Figure~\ref{deltaratio:fig}, are not monotonic with color: they increase from the $U$ to $V$, and then decrease
-from $V$ to $I$,
-a consequence
-of which is that
-a reddening in $B-V$ comes with a blueing in $V-R$.
-Also apparent is that a reddening of $B-V$ is associated with a brightening of the supernova.
-The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$ are shown in Figure~\ref{rx:fig}.
-Although the posteriors of $\delta$ are close to Gaussian, $\delta_B-\delta_V$ can approach zero, resulting in the
-elongated tail in negative  $R_{\delta X}$.
-All values are significantly negative.}
-These are not the behaviors expected from normal dust,
-circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
-2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
-more complicated underlying supernova physics.
+\subsection{SN 2014J in the Context of Our Model}
+\label{sn2014j:sec}
+
+SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
+2014arXiv1411.3332J,
+2014ApJ...795L...4K, 2015ApJ...805...74B}.
+The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
+spectral evolution that 
+suffers low Galactic and host reddening
+\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
+The overall higher photospheric velocities of
+SN~2014J are unimportant  based on the findings of  \S\ref{results:sec}.
+
+Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
+The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
+following their perscription of averaging measurements within 5-days of peak $B$ magnitude.
+Their values 
+$E_o(U-V) =   2.23 \pm   0.03$,
+$E_o(B-V) =   1.28 \pm   0.04$,
+$E_o(R-V) =  -0.47 \pm   0.03$,
+$E_o(i-V) =  -0.92 \pm   0.03$
+are plotted in Figure~\ref{sn2014j:fig}.
+These data are fit to the model
+\begin{equation}
+E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)k_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)k_1,
+\end{equation}
+where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.
 
@@
    \centering
-   \includegraphics[width=3.2in]{output11/deltaratio.pdf}
-   \caption{68\% credible intervals of $\frac{\delta_X}{\delta_V}$ at the effective wavelengths of the corresponding bands.
-   \label{deltaratio:fig}}
+   \includegraphics[width=3.2in]{output11/sn2014j.pdf} 
+   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and  \citet{2014ApJ...788L..21A}  
+   \label{sn2014j:fig}}
 \end{figure}
+
+The best-fit parameters for SN~2014J are 
+%----
+$k_0= 2.65$, $ k_1=-1.64$ with covariance
+%----
+\begin{equation}
+\begin{pmatrix}
+0.048 & 0.047 \\
+0.047 & 0.248
+\end{pmatrix}.
+\end{equation}
+The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
+overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
+UV through NIR data,
+a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
+is also plotted.  Our model predictions provide a significantly better match to the data.
+
+In the fit to our model, the observed color excess is attributed to   extrinsic
+%----
+$E_{\gamma^0}(B-V)=  0.92 \pm   0.08$ and intrinsic $E_{\gamma_1}(B-V)=  0.28 \pm   0.08$
+%-----
+contributions.
+Among the supernovae in the SNfactory  set used to determine $\gamma^0$ and $\gamma^1$, the
+\color{red}
+objects with the extreme median values have 
+%---
+$E_{\gamma^0}(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
+and for $E_{\gamma^1}(B-V)$ $-0.01 \pm 0.01$  and
+$  0.06 \pm 0.03$ 
+%---
+(see Figure~\ref{ebv:fig}).
+The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
+span of supernovae used to train the coefficients of the model, which is not unexpected if
+attributed to dust.
+
+\section{Intrinsic Color}
+\label{model2:sec}
+Analysis of the data using the model presented in \S\ref{model:sec} drew out parameter values consistent
+with two-parameter dust models.  We now consider an extension to the model that accommodate an additional
+color parameter.
+The new model is written as
+\begin{equation}
+\begin{pmatrix}
+U\\B\\V\\R\\I
+\end{pmatrix}
+\sim \mathcal{N}
+\left(
+\Delta +
+\begin{pmatrix}
+c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
+c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
+c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
+c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
+c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
+\end{pmatrix}
+,C_{c}
+\right)
+\label{ewsiv:eqn}
+\end{equation}
+\begin{equation}
+\begin{pmatrix}
+U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
+\end{pmatrix}
+\sim \mathcal{N}
+\left(
+\begin{pmatrix}
+U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
+V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
+EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
+\end{pmatrix}
+,C
+\right).
+\label{dust:eqn}
+\end{equation}
+In all aspects it is identical to the previous model except for the addition of the term $\delta D$ to the absolute magnitudes.
+Each supernova has an intrinsic $D$ parameter that influences absolute magnitudes through $\delta$. 
+Although
+this term is introduced through the absolute rather than observed magnitude,
+practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
+degeneracy, for convenience we refer to this term as ``intrinsic''.
+
+To constrain the new degrees of freedom and degeneracies inherent in the model we impose that
+$D+1/N$ be a simplex to break the 
+degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
+Furthermore we impose
+\begin{equation}
+\langle D\rangle=0,  \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
+\end{equation}
+The first specifies the definition of zero color.   The latter two confine possible magnitude
+variations to those unattributablabe to 
+the $\gamma k$ terms (i.e.\ dust); without this pragmatic condition $\delta D$  
+was degenerate and tended toward $\gamma k$ in the fit.  The initial conditions for
+$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}.
+
+The resulting posteriors of our parameters are given in Table~\ref{}
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+\hline
+\end{tabular}
+\caption{68\% credible Intervals for the Global Fit Parameters \label{global2:tab}}
+\end{table}
+
+For dust and our model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
+It turns out that the planes for both models are nearly parallel, in that
+\begin{equation}
+\begin{pmatrix}
+ \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
+\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
+\end{pmatrix}=
+\begin{pmatrix}
+1.16 & 2.82 \\
+0.74 & -5.43
+\end{pmatrix} 
+\begin{pmatrix}
+a(X) \\
+b(X)
+\end{pmatrix}+
+\vec{\epsilon},
+\end{equation}
+where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
+contribute  2\% and 5\% to the total  length of the vector.
 
@@
 \end{figure}
-
-\section{Supernova Model Part 2}
-\label{model2:sec}
-We hypothesize that at peak brightness
-SN~Ia broadband magnitudes and colors are correlated with
-spectral features: equivalent widths and line positions are considered as statistics localized in wavelength that are insensitive to variations in
-broadband colors.
-Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
-of intrinsic variation is accommodated.
-The intrinsic spectral and color parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
-\textcolor{red}{The intrinsic magnitudes are then
-modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
-
-We assume 
-that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
-on the
- equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
-$EW_{Ca}$, $EW_{Si}$,
-\textcolor{red}{ and $\lambda_{Si}$ the wavelength of the minimum of 
-the SiII$\lambda6355$ feature}:
-these spectral features are associated with SN~Ia  spectroscopic diversity  
-\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
-$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
-\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
-An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
-Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
-$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
-to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
-The observed magnitudes are linearly dependent on an
-extrinsic-color parameter $k$.  The observables
-$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
-shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
-The model is written as
-\begin{equation}
-\begin{pmatrix}
-U\\B\\V\\R\\I
-\end{pmatrix}
-\sim \mathcal{N}
-\left(
-\Delta +
-\begin{pmatrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
-\end{pmatrix}
-,C_{c}
-\right)
-\label{ewsiv:eqn}
-\end{equation}
-\begin{equation}
-\begin{pmatrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
-\end{pmatrix}
-\sim \mathcal{N}
-\left(
-\begin{pmatrix}
-U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
-V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
-EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
-\end{pmatrix}
-,C
-\right).
-\label{dust:eqn}
-\end{equation}
-The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
-relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
-(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
-The global parameters $\gamma$ are the slopes that connect the extrinsic-color
-parameter and observed magnitudes.
-
-To constrain the degrees of freedom and degeneracies inherent in the model we impose that
-\color{red}
-each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
-conditions break the 
-degeneracies  $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1}k$ and $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
-Furthermore we impose
-\color{black} 
-\begin{equation}
-\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \langle D \rangle=0, \gamma^0_{0} > 0, \gamma^1_{0} < 0, \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
-\end{equation}
-The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
-associated
-with  simultaneous sign flips of
-$\delta$--$D$ and $\gamma$--$k$
-\color{red}
-(when running our fits, $k$ and $D$ are set to
-identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ distinguishes the two.)
-Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
-each other, as is apparent after 
-running the Monte Carlo with exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
-The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
-otherwise identical initial conditions for $\gamma$, $\delta$ produce indistinguishable posteriors
-with relatively broad credible intervals and lower maximum likelihood.
-\color{black}
-As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
-by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.
-
-\section{SN 2014J in the Context of Our Model}
-\label{sn2014j:sec}
-
-SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
-2014arXiv1411.3332J,
-2014ApJ...795L...4K, 2015ApJ...805...74B}.
-The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
-spectral evolution that 
-suffers low Galactic and host reddening
-\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
-The overall higher photospheric velocities of
-SN~2014J are unimportant  based on the findings of  \S\ref{results:sec}.
-
-Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
-The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
-following their perscription of averaging measurements within 5-days of peak $B$ magnitude.
-Their values 
-$E_o(U-V) =   2.23 \pm   0.03$,
-$E_o(B-V) =   1.28 \pm   0.04$,
-$E_o(R-V) =  -0.47 \pm   0.03$,
-$E_o(i-V) =  -0.92 \pm   0.03$
-are plotted in Figure~\ref{sn2014j:fig}.
-These data are fit to the model
-\begin{equation}
-E_o(X-V) =  \left(\frac{\gamma_X}{\gamma_V}-1\right)k +  \left(\frac{\delta_X}{\delta_V}-1\right)D,
-\end{equation}
-where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/sn2014j.pdf} 
-   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and  \citet{2014ApJ...788L..21A}  
-   \label{sn2014j:fig}}
-\end{figure}
-
-The best-fit parameters for SN~2014J are 
-%----
-$k= 2.67$, $ D=-1.63$ with covariance
-%----
-\begin{equation}
-\begin{pmatrix}
-0.047 & 0.044 \\
-0.044 & 0.247
-\end{pmatrix}.
-\end{equation}
-The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
-overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
-UV through NIR data,
-a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
-is also plotted.  Our model predictions provide a significantly better match to the data.
-
-In the fit to our model, the observed color excess is attributed to   extrinsic
-%----
-$E_\gamma(B-V)=  0.93 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.27 \pm   0.08$
-%-----
-contributions.
-Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the
-\color{red}
-objects with the extreme median values have 
-%---
-$E_\gamma(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
-and for $E_\delta(B-V)$ $-0.01 \pm 0.01$  and
-$  0.06 \pm 0.03$ 
-%---
-\color{black}
-(see Figure~\ref{ebv:fig}).
-\textcolor{red}{The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
-span} of supernovae used to train the coefficients of the model.
 

### 2016-10-03 forgerard.tex
Moving on...

@@
 \end{tabular}
-\caption{68\% credible Intervals for the Global Fit Parameters \label{global:tab}}
+\caption{68\% credible Intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model \label{global:tab}}
 \end{table}
@@
 \label{model2:sec}
-Analysis of the data using the model presented in \S\ref{model:sec} drew out parameter values consistent
-with two-parameter dust models.  We now consider an extension to the model that accommodate an additional
+Analysis of the data using the model presented in \S\ref{model:sec} draws out parameter values consistent
+with two-parameter dust models.  We now consider an extension to our model that accommodates an additional
 color parameter.
@@
 \end{equation}
-In all aspects it is identical to the previous model except for the addition of the term $\delta D$ to the absolute magnitudes.
-Each supernova has an intrinsic $D$ parameter that influences absolute magnitudes through $\delta$. 
+In all aspects it is identical to the previous model except for the addition of the term $\delta D$ toward the mean
+absolute magnitudes.
+Each supernova has an intrinsic $D$ parameter that influences absolute magnitudes with strength $\delta$. 
 Although
-this term is introduced through the absolute rather than observed magnitude,
+this term is introduced through the absolute rather than observed magnitudes,
 practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
-degeneracy, for convenience we refer to this term as ``intrinsic''.
+degeneracy, this term is referred to as ``intrinsic''.
 
@@
 The first specifies the definition of zero color.   The latter two confine possible magnitude
-variations to those unattributablabe to 
-the $\gamma k$ terms (i.e.\ dust); without this pragmatic condition $\delta D$  
-was degenerate and tended toward $\gamma k$ in the fit.  The initial conditions for
+variations to those that cannot be attributed to 
+the $\gamma k$ terms (i.e.\ dust); practically it is difficult to break the degeneracies between $\delta D$  
+and $\gamma k$ in the fit. 
+Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_0$,
+so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
+In the running of the Monte Carlo, the initial conditions for
 $\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}.
 
-The resulting posteriors of our parameters are given in Table~\ref{}
+The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
+results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that common parameters
+are consistent well within 1$\sigma$ uncertainties.  The most significant changes of note are in the standard
+deviations of the residuals in the $V$ and $I$ bands.
 \begin{table}
@@
 & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+$\alpha_X$
+&
+$0.0044^{0.0009}_{-0.0009}$
+&
+$0.0016^{0.0007}_{-0.0007}$
+&
+$0.0016^{0.0006}_{-0.0006}$
+&
+$0.0015^{0.0005}_{-0.0005}$
+&
+$0.0026^{0.0005}_{-0.0005}$
+\\
+${\alpha_X/\alpha_V-1}$
+&
+$   1.8^{   0.9}_{  -0.4}$
+&
+$   0.0^{   0.1}_{  -0.2}$
+&
+$   0$
+&
+$  -0.0^{   0.1}_{  -0.1}$
+&
+$   0.6^{   0.6}_{  -0.3}$
+\\
+$\beta_X$
+&
+$ 0.032^{ 0.003}_{-0.003}$
+&
+$ 0.025^{ 0.002}_{-0.003}$
+&
+$ 0.025^{ 0.002}_{-0.002}$
+&
+$ 0.020^{ 0.002}_{-0.002}$
+&
+$ 0.019^{ 0.002}_{-0.002}$
+\\
+${\beta_X/\beta_V-1}$
+&
+$  0.26^{  0.05}_{ -0.05}$
+&
+$ -0.01^{  0.03}_{ -0.03}$
+&
+$  0$
+&
+$ -0.19^{  0.01}_{ -0.02}$
+&
+$ -0.24^{  0.03}_{ -0.03}$
+\\
+$\eta_X$
+&
+$-0.0002^{0.0012}_{-0.0011}$
+&
+$0.0000^{0.0010}_{-0.0009}$
+&
+$0.0005^{0.0008}_{-0.0008}$
+&
+$0.0005^{0.0007}_{-0.0007}$
+&
+$-0.0003^{0.0006}_{-0.0006}$
+\\
+${\eta_X/\eta_V-1}$
+&
+$ -0.40^{  2.19}_{ -1.84}$
+&
+$ -0.36^{  1.57}_{ -1.19}$
+&
+$  0$
+&
+$ -0.12^{  0.27}_{ -0.25}$
+&
+$ -0.89^{  1.72}_{ -1.35}$
+\\
+$\gamma^0_X$
+&
+$ 62.53^{  3.64}_{ -3.63}$
+&
+$ 50.74^{  3.08}_{ -3.03}$
+&
+$ 37.67^{  2.62}_{ -2.60}$
+&
+$ 28.89^{  2.32}_{ -2.33}$
+&
+$ 20.62^{  2.15}_{ -2.16}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
+&
+$  0.66^{  0.06}_{ -0.05}$
+&
+$  0.35^{  0.03}_{ -0.03}$
+&
+$  0$
+&
+$ -0.23^{  0.01}_{ -0.01}$
+&
+$ -0.45^{  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+&
+$ -9.93^{  3.53}_{ -4.16}$
+&
+$-11.80^{  2.91}_{ -3.44}$
+&
+$-14.25^{  2.45}_{ -2.72}$
+&
+$-13.39^{  2.15}_{ -2.29}$
+&
+$-12.05^{  1.97}_{ -2.14}$
+\\
+${\gamma^1_X/\gamma^1_2-1}$
+&
+$ -0.30^{  0.18}_{ -0.19}$
+&
+$ -0.17^{  0.09}_{ -0.10}$
+&
+$  0$
+&
+$ -0.06^{  0.05}_{ -0.04}$
+&
+$ -0.16^{  0.10}_{ -0.08}$
+\\
+${{\delta_X/\delta_I-1}}$
+&
+$ -0.61^{  0.47}_{ -0.18}$
+&
+$ -1.21^{  0.25}_{ -0.77}$
+&
+$ -1.76^{  0.16}_{ -0.20}$
+&
+$ -1.17^{  0.29}_{ -0.20}$
+&
+$  0$
+\\
+$\sigma_X$
+&
+$ 0.059^{ 0.013}_{-0.013}$
+&
+$ 0.031^{ 0.007}_{-0.008}$
+&
+$ 0.017^{ 0.005}_{-0.007}$
+&
+$ 0.012^{ 0.006}_{-0.007}$
+&
+$ 0.039^{ 0.005}_{-0.005}$
+\\
 \hline
 \end{tabular}
-\caption{68\% credible Intervals for the Global Fit Parameters \label{global2:tab}}
+\caption{68\% credible Intervals for the Global Fit Parameters of the Intrinsic-Extrinsic Model\label{global2:tab}}
 \end{table}
 
-For dust and our model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
-It turns out that the planes for both models are nearly parallel, in that
+We find that the newly fitted $\delta$ parameters have almost identical association with the Fitzpatrick dust law, in that
 \begin{equation}
@@
 
-The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
+The distribution of both sources of color excess $E(B-V)$ and
  $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
@@
 %-----
-0.079
-and 0.015
+0.081
+and 0.010
 %-----
 mag respectively.
-The range of $B-V$ colors is $\sim 5$ times larger for the external contribution. 
-Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red, consistent
+The range of $B-V$ colors is $\sim 8$ times larger for the external contribution. 
+Both distributions are non-Gaussian, that of $E(B-V)$ has a sharp rise in the blue and an extended tail in the red, consistent
 with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.
@@
    \centering
-   \includegraphics[width=3.2in]{output11/ebv.pdf}
-   \caption{Ideograms of the external $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
+   \includegraphics[width=2.8in]{output15/ebv.pdf}
+   \includegraphics[width=2.8in]{output15/ebv_delta.pdf}
+      \caption{Left: Ideograms of the external $E(B-V)$ and
    internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
+   Right: Ideogram of $E_\delta(B-V)$ on an enlarged scale.
    \label{ebv:fig}}
 \end{figure}
+The significance of the $\delta$ parameters is shown pictorially
+in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which is bimodal due to the parity symmetry.  The probability
+of the null result $\delta_X=0$ for all $X$, lies on a
+$>98\%$-contour.  The right plot shows values of $\delta_X/\delta_I-1$, which nulls out the parity symmetry and has significant non-zero values.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output15/delta_corner.pdf}
+      \includegraphics[width=2.8in]{output15/deltaratio.pdf}
+   \caption{Significance of the non-zero values of $\delta$.  Left: Posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
+   Right: $\delta_X/\delta_I-1$, which as a ratio is insensitive to the degeneracy.
+   \label{deltacorner:fig}}
+\end{figure}
 
@@
 \label{discussion:sec}
-We model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and distinct intrinsic and
+We model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
 extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
-affect supernova magnitudes and colors.  The external color parameter has behavior consistent with  $R^F_V=2.97$ \citet{1999PASP..111...63F} dust,
-whereas the internal color parameter is inconsistent with dust or a blackbody.  This model  does an excellent job in
-describing SN~2014J, a supernova not used in the training that has atypical colors.
+affect supernova magnitudes and colors.  The external color parameters are consistent with \citet{1999PASP..111...63F} dust
+with $R^F_V=2.43$.  This model  does an excellent job in
+describing SN~2014J, a supernova not used in the training that has atypical colors.  An extended version
+of the model retains the features of the first model, but now with strong evidence for a new parameter related to supernova
+colors.
 
 \color{red}
-Our model does not explicitly include light-curve shape, which is known to track SN~Ia diversity.
+Our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
+We now examine this in more depth using the intrinsic--extrinsic model of \S\ref{model2:sec}.
 The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
@@
 from this analysis are given in Table~\ref{globalx1:tab}; no significant changes are seen. 
-In fact, light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: the values
-for
-$\zeta$ are consistent with zero to $2\sigma$, while the $\alpha$'s and $\beta$'s remain significantly
-non-zero.  
-Nevertheless, there 
-appear to be non-linear correlations 
-between $X_1$ and the residuals between observed and model-predicted colors, as seen in
-Figure~\ref{x1res:fig}.
-Extending our model to include non-linear terms is a direction for future work.
+In fact, light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: only $\zeta_R/\zeta_V$
+has a non-zero value at $>2\sigma$.
+The parameters that describe intrinsic color $\delta$ remain significantly non-zero.
+
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
    \centering
-   \includegraphics[width=2.8in]{output11/x1si.pdf}
-   \includegraphics[width=2.8in]{output11/x1D.pdf}
+   \includegraphics[width=2.8in]{output15/x1si.pdf}
+   \includegraphics[width=2.8in]{output15/x1D.pdf}
     \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
@@
    \centering
-   \includegraphics[width=5in]{output11/residualx1.pdf}
+   \includegraphics[width=5in]{output15/residualx1.pdf}
     \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
@@
 &
-$0.0041^{0.0010}_{-0.0010}$
-&
-$0.0015^{0.0008}_{-0.0008}$
-&
-$0.0016^{0.0007}_{-0.0007}$
-&
-$0.0015^{0.0006}_{-0.0006}$
-&
-$0.0027^{0.0005}_{-0.0005}$
+$0.0044^{0.0010}_{-0.0010}$
+&
+$0.0016^{0.0008}_{-0.0008}$
+&
+$0.0017^{0.0006}_{-0.0007}$
+&
+$0.0015^{0.0005}_{-0.0005}$
+&
+$0.0028^{0.0005}_{-0.0005}$
 \\
@@
 &
-$   1.6^{   0.9}_{  -0.4}$
-&
-$  -0.1^{   0.1}_{  -0.2}$
-&
-$   0.0^{   0.0}_{   0.0}$
+$   1.6^{   0.8}_{  -0.4}$
+&
+$  -0.0^{   0.1}_{  -0.2}$
+&
+$   0$
 &
@@
 &
-$   0.7^{   0.8}_{  -0.3}$
+$   0.7^{   0.7}_{  -0.3}$
 \\
@@
 &
-$ 0.019^{ 0.003}_{-0.003}$
+$ 0.019^{ 0.004}_{-0.003}$
 &
@@
 &
-$  0.50^{  0.13}_{ -0.12}$
+$  0.52^{  0.13}_{ -0.12}$
 &
@@
 &
-$  0.00^{  0.00}_{  0.00}$
-&
-$ -0.14^{  0.03}_{ -0.03}$
-&
-$ -0.28^{  0.06}_{ -0.06}$
+$  0$
+&
+$ -0.13^{  0.03}_{ -0.03}$
+&
+$ -0.27^{  0.06}_{ -0.06}$
 \\
@@
 &
-$0.0001^{0.0011}_{-0.0011}$
-&
-$0.0003^{0.0009}_{-0.0009}$
-&
-$0.0008^{0.0008}_{-0.0008}$
-&
-$0.0007^{0.0007}_{-0.0007}$
-&
-$-0.0001^{0.0006}_{-0.0006}$
+$0.0004^{0.0011}_{-0.0011}$
+&
+$0.0005^{0.0010}_{-0.0010}$
+&
+$0.0009^{0.0008}_{-0.0008}$
+&
+$0.0009^{0.0007}_{-0.0007}$
+&
+$0.0001^{0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.49^{  1.15}_{ -1.55}$
-&
-$ -0.39^{  0.84}_{ -0.99}$
-&
-$  0.00^{  0.00}_{  0.00}$
-&
-$ -0.14^{  0.19}_{ -0.18}$
-&
-$ -0.83^{  0.78}_{ -0.96}$
+$ -0.34^{  0.58}_{ -1.20}$
+&
+$ -0.36^{  0.35}_{ -0.86}$
+&
+$  0$
+&
+$ -0.10^{  0.20}_{ -0.14}$
+&
+$ -0.74^{  0.35}_{ -0.75}$
 \\
@@
 &
-$ 0.004^{ 0.039}_{-0.040}$
-&
-$-0.005^{ 0.033}_{-0.033}$
-&
-$-0.028^{ 0.028}_{-0.028}$
-&
-$-0.013^{ 0.024}_{-0.024}$
-&
-$-0.029^{ 0.021}_{-0.021}$
+$  0.00^{  0.04}_{ -0.04}$
+&
+$ -0.01^{  0.03}_{ -0.03}$
+&
+$ -0.03^{  0.03}_{ -0.03}$
+&
+$ -0.01^{  0.02}_{ -0.02}$
+&
+$ -0.03^{  0.02}_{ -0.02}$
 \\
@@
 &
-$  -0.7^{   1.1}_{  -1.7}$
-&
-$  -0.5^{   0.6}_{  -1.2}$
-&
-$   0.0^{   0.0}_{   0.0}$
-&
-$  -0.4^{   0.3}_{  -0.5}$
-&
-$  -0.1^{   0.6}_{  -0.4}$
-\\
-${\gamma_X/\gamma_V-1}$
-&
-$  0.64^{  0.06}_{ -0.05}$
-&
-$  0.34^{  0.03}_{ -0.03}$
-&
-$  0.00^{  0.00}_{  0.00}$
-&
-$ -0.23^{  0.01}_{ -0.01}$
-&
-$ -0.45^{  0.03}_{ -0.03}$
-\\
-$R_X$
-&
-$  4.78^{  0.52}_{ -0.45}$
-&
-$  3.91^{  0.42}_{ -0.37}$
-&
-$  2.91^{  0.33}_{ -0.29}$
-&
-$  2.23^{  0.27}_{ -0.24}$
-&
-$  1.60^{  0.22}_{ -0.20}$
-\\
-${\delta_X/\delta_V-1}$
-&
-$ -0.38^{  0.17}_{ -0.19}$
-&
-$ -0.23^{  0.10}_{ -0.10}$
-&
-$  0.00^{  0.00}_{  0.00}$
-&
-$ -0.07^{  0.04}_{ -0.04}$
-&
-$ -0.17^{  0.09}_{ -0.09}$
-\\
-$R_{\delta X}$
-&
-$ -2.78^{  1.23}_{ -2.20}$
-&
-$ -3.49^{  1.22}_{ -2.38}$
-&
-$ -4.49^{  1.35}_{ -2.78}$
-&
-$ -4.17^{  1.23}_{ -2.55}$
-&
-$ -3.72^{  1.12}_{ -2.28}$
+$ -0.76^{  0.78}_{ -1.78}$
+&
+$ -0.50^{  0.47}_{ -1.06}$
+&
+$  0$
+&
+$ -0.46^{  0.21}_{ -0.50}$
+&
+$ -0.16^{  0.45}_{ -0.34}$
+\\
+$\gamma^0_X$
+&
+$ 61.49^{  3.67}_{ -3.71}$
+&
+$ 50.34^{  3.09}_{ -3.07}$
+&
+$ 37.28^{  2.63}_{ -2.59}$
+&
+$ 28.38^{  2.35}_{ -2.28}$
+&
+$ 20.03^{  2.16}_{ -2.16}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
+&
+$  0.65^{  0.06}_{ -0.05}$
+&
+$  0.35^{  0.03}_{ -0.03}$
+&
+$  0$
+&
+$ -0.24^{  0.01}_{ -0.01}$
+&
+$ -0.46^{  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+&
+$ -8.99^{  3.28}_{ -3.68}$
+&
+$-11.21^{  2.72}_{ -3.18}$
+&
+$-14.76^{  2.34}_{ -2.63}$
+&
+$-13.88^{  2.00}_{ -2.23}$
+&
+$-12.57^{  1.92}_{ -2.06}$
+\\
+${\gamma^1_X/\gamma^1_2-1}$
+&
+$ -0.39^{  0.16}_{ -0.17}$
+&
+$ -0.24^{  0.09}_{ -0.10}$
+&
+$  0$
+&
+$ -0.06^{  0.04}_{ -0.03}$
+&
+$ -0.15^{  0.09}_{ -0.08}$
+\\
+${{\delta_X/\delta_I-1}}$
+&
+$  0.04^{  0.48}_{ -0.31}$
+&
+$ -2.16^{  0.36}_{ -0.64}$
+&
+$ -1.94^{  0.23}_{ -0.42}$
+&
+$ -0.63^{  0.56}_{ -0.29}$
+&
+$  0$
 \\
@@
 &
-$ 0.060^{ 0.013}_{-0.012}$
-&
-$ 0.033^{ 0.007}_{-0.007}$
-&
-$ 0.018^{ 0.005}_{-0.008}$
-&
-$ 0.014^{ 0.006}_{-0.008}$
-&
-$ 0.044^{ 0.006}_{-0.005}$
+$ 0.050^{ 0.014}_{-0.012}$
+&
+$ 0.027^{ 0.008}_{-0.008}$
+&
+$ 0.015^{ 0.004}_{-0.005}$
+&
+$ 0.008^{ 0.006}_{-0.005}$
+&
+$ 0.041^{ 0.005}_{-0.004}$
 \\
@@
 \end{table}
-
-\color{black}
-
-\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
-\citet{2011ApJ...731..120M, 2011ApJ...729...55F} and the above authors
-find that supernovae with large $E_o(B-V)$ 
-preferentially exhibit low $R^F_V$. 
-\color{red}
-\citet{2016arXiv160904470M} demonstrate how biased $R_V$ determinations can arise from unaccounted intrinsic color dispersion.
-In our model internal and external effects for each supernova  conflate into an effective color excess
-$E_{eff}(X-V) = E_\gamma(X-V) + E_\delta(X-V)$ and effective $V$ extinction $A_{eff,V} = \gamma_V k  + \delta_V D$.
-Recall that the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrarily
-fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$:
-there is no unique value for the statistic $R_{eff,V} = A_{eff,V} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
-
-One choice of boundary condition is to zero the color at the blue extremes of the distributions.
-For specificity in the current qualitative discussion, 
-let us consider a set of SNe~Ia  with parameters set to the median fit values of the SNfactory sample.
-We specify   $E_{eff}(U-V)$  and $E_{eff}(B-V)$ by
-assigning zero color excess close to the blue-extreme colors of this set, 
-as shown in bottom-left corner in the left plot of Figure~\ref{rveff:fig}.
-For this choice of color zeropoints,
-$R_{eff,U} - R_{eff,V} = E_{eff}(U-V) /E_{eff}(B-V)$ is plotted
-in the right of Figure~\ref{rveff:fig}.
-Around $E_{eff}(B-V) \sim 0$, where attempts to measure extinction properties would suffer large uncertainties,
-the $R_{eff,U} - R_{eff,V}$ values are high.
-The distribution spreads to significantly 
-lower   $R_{eff,U} - R_{eff,V}$ as supernovae appear redder but
-then reconverge to higher, tighter values red effective color, with asymptote  $R_{eff,U} - R_{eff,V} >1.8$.
-This cause of this asymptotic behavior is due to the relatively higher contribution of extrinsic over intrinsic color excess to the effective color excess, as
-seen in the bottom plot of
-Figure~\ref{rveff:fig}. 
-Since the standard deviation of the $E_\delta(B-V)$ distribution is  narrow compared to that of
- $E_\gamma(B-V)$, low values of $R_{eff,U} - R_{eff,V}$ can only occur
-at low $E_{eff}(X-V)$.
- The  \citet{1999PASP..111...63F} dust model interprets
- low values of $R_{eff,U} - R_{eff,V}$ as implying high values of $R_V$,
-for example $R_{eff,U} - R_{eff,V}=1.70$ for $R_V=2.97$,  $R_{eff,U} - R_{eff,V}=1.81$ for $R_V=1.5$ (see Figure~\ref{ebv:fig}).
-The $R_V$ inferred for the reddest supernovae would be $R_V<1.5$, even though their colors are dominated by 
-extrinsic $R^F_V=2.97$ dust; this is due our zero colors being (qualitatively) assigned to supernovae that have bluest extrinsic AND intrinsic color excess.
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output11/rveff.pdf}
-   \includegraphics[width=2.8in]{output11/rveff2.pdf}
-   \includegraphics[width=2.8in]{output11/rveff3.pdf}
-      \caption{\textcolor{red}{Left: Effective color excess $E_{eff}(B-V)$ versus $E_{eff}(U-V)$
-   where $E_{eff}(X-V)   = E_\gamma(X-V) + E_\delta(X-V) - z_X$
-   for a set of SNe with parameters set to those of the medians of the objects in our analysis.
-   The $z_X$ represents a choice of colors at zero color-excess so that the lower left corner points have values approaching zero. 
-Right:  The inferred $R_{eff,U}- R_{eff,V} = E_{eff}(U-V)/E_{eff}(B-V)$.
-Bottom:  $R_{eff,U}- R_{eff,V}$ as a function of the relative contributions of extrinsic and intrinsic color effects $E_\gamma(B-V)/E_\delta(B-V)$.}
-   \label{rveff:fig}}
-\end{figure}
-
-An alternative way to specify $R_V$ is to consider colors relative to a canonical supernova,
- the model prediction being
-\begin{equation}
-R_{eff, V} = \frac{\gamma_1  (k-k_0) + \delta_1 (D-D_0) }{(\gamma_B-\gamma_V) (k-k_0) + (\delta_B-\delta_V) (D-D_0) },
-\end{equation}
-where $k_0$ and $D_0$ are the parameter values of the canonical supernova.
-If $D = D_0$, the $R_V = \gamma_B/(\gamma_B-\gamma_V)$ of the extrinsic contribution is recovered, but this does not hold true
-when $D \ne D_0$.  Again considering a set of SNe~Ia  with parameters equal to the median fit values of the SNfactory sample,
-the values for $R_{eff,V}$ choosing a canonical supernova with $k_0=0$, $\delta_0=0$  is shown in Figure~\ref{rv4:fig}.
-The reddest supernovae exhibit a range of $1.5< R_{eff,V}<3.5$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.2in]{output11/rveff4.pdf}
-      \caption{\textcolor{red}{Effective total-to-selective extinction $R_{eff, V}$
-      with color excess defined relative to  a
-      $k_0=0$, $\delta_0=0$ supernove,  for  a set of SNe~Ia  with parameters equal to the median fit values of the SNfactory sample.}
-   \label{rv4:fig}}
-\end{figure}
 
@@
 color excess for low- (high)-mass hosts to be
-$  -0.0043 \pm    0.0022$
-($  -0.0072 \pm    0.0073$).  
+$   0.0042 \pm    0.0014$
+$   0.0031 \pm    0.0017$.
 The ideograms for the low- and high-mass samples is shown in Figure~\ref{childress:fig}.
@@
    \centering
-%   \includegraphics[width=2.8in]{output11/rigault3.pdf}
-%      \includegraphics[width=2.8in]{output11/rigault2.pdf}
-      \caption{\textcolor{red}{Left: Intrinsic parameter $E_\gamma(B-V)$  versus host mass.  Hosts too faint for a mass measurement
+   \includegraphics[width=2.8in]{output15/rigault3.pdf}
+s     \includegraphics[width=2.8in]{output15/rigault2.pdf}
+      \caption{\textcolor{red}{Intrinsic parameter $E_\gamma(B-V)$  versus host mass.  Hosts too faint for a mass measurement
       are assigned a mass of 5.

### 2016-10-03 rigault15.py

@@ -62,14 +62,6 @@ plt.close()
 
 # wefwe
 
-# i=3
-# plt.errorbar(rdata[indr,3*i],x[inda],xerr=[rdata[indr,3*i+2], rdata[indr,3*i+1]], yerr=[x[inda]-xmin[inda],xmax[inda]-x[inda]],fmt='o')
-# plt.ylabel(r'$E_\delta(B-V)$')
-# plt.xlabel(r'$\log{(M/M_\odot)}$')
-# pp = PdfPages("output15/rigault3.pdf")
-# plt.savefig(pp,format='pdf')
-# pp.close()
-# plt.close()
 
 # i=2
 # plt.errorbar(rdata[indr,3*i],x[inda],xerr=[rdata[indr,3*i+2], rdata[indr,3*i+1]], yerr=[x[inda]-xmin[inda],xmax[inda]-x[inda]],fmt='o')
@@ -85,8 +77,9 @@ wm = numpy.where(rdata[indr,9] < 10)[0]
 (x, xmin, xmax) = numpy.percentile(fit['rho1'][:,4][:,None]*fit['R'][:,inda[wm]],(50,50-34,50+34),axis=0)
 dx = (xmax-xmin)/2.
 dx2 = numpy.sum(1/dx**2)
+low1 = numpy.sum(x/dx**2)/dx2
+dlow1=  1/numpy.sqrt(dx2)
 print r"${:9.4f} \pm {:9.4f}$".format(numpy.sum(x/dx**2)/dx2, 1/numpy.sqrt(dx2)) 
-low = (((fit['rho1'][:,1]-fit['rho1'][:,2])[:,None])*fit['R'][:,wm]).flatten()
 
 
 wm = numpy.where(rdata[indr,9] > 10)[0]
@@ -94,18 +87,56 @@ wm = numpy.where(rdata[indr,9] > 10)[0]
 (x, xmin, xmax) = numpy.percentile(fit['rho1'][:,4][:,None]*fit['R'][:,inda[wm]],(50,50-34,50+34),axis=0)
 dx = (xmax-xmin)/2.
 dx2 = numpy.sum(1/dx**2)
+high1 = numpy.sum(x/dx**2)/dx2
+dhigh1=  1/numpy.sqrt(dx2)
 print r"${:9.4f} \pm {:9.4f}$".format(numpy.sum(x/dx**2)/dx2, 1/numpy.sqrt(dx2)) 
 
 
[…]

### 2016-10-03 view15.py

@@ -367,7 +367,7 @@ plt.close()
 #     label=[r'$E_\gamma(B-V)$',r'$E_{\gamma_1}(B-V)$',r'$E_\delta(B-V)$'],range=(-0.1,0.4))
 plt.hist([(fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['k'] + 
   (fit['gamma1'][:,1]-fit['gamma1'][:,2])[:,None]*fit['k1'], (fit['rho1'][:,1]-fit['rho1'][:,2])[:,None]*fit['R']],normed=True,bins=20,
-  label=[r'$E_{ext}(B-V)$',r'$E_\delta(B-V)$'])
+  label=[r'$E(B-V)$',r'$E_\delta(B-V)$'])
 plt.xlabel(r'$E(B-V)$')
 plt.legend()
 pp = PdfPages('output15/ebv.pdf')
@@ -376,7 +376,7 @@ pp.close()
 plt.close()
 
 plt.hist( ((fit['rho1'][:,1]-fit['rho1'][:,2])[:,None]*fit['R']).flatten(),normed=True,bins=20,
-  label=[r'$E_\delta(B-V)$'],range=(-0.06,.06))
+  label=[r'$E_\delta(B-V)$'],range=(-0.06,.06),color='green')
 plt.xlabel(r'$E(B-V)$')
 plt.xlim((-.06,.06))
 plt.legend()
@@ -799,10 +799,10 @@ pp.close()
 plt.close()
 
 (y, ymin, ymax) = numpy.percentile(fit['rho1']/fit['rho1'][:,4][:,None],(50,50-34,50+34),axis=0)
-plt.errorbar(efflam,y,yerr=[y-ymin,ymax-y],fmt='o')
+plt.errorbar(efflam,y-1,yerr=[y-ymin,ymax-y],fmt='o')
 plt.legend()
 plt.xlabel(r'Wavelength (\AA)')
-plt.ylabel(r'$\frac{\delta_X}{\delta_4}$')
+plt.ylabel(r'$\frac{\delta_X}{\delta_4}-1$')
 pp = PdfPages('output15/deltaratio.pdf')
 plt.savefig(pp,format='pdf')
 pp.close()

### 2016-10-03 forgerard.tex
almost done with this draft

@@
 The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix.
-Assembling
-a new set of Cholesky factors based on the distributions of each individual factor will not generally satisfy the condition of representing a correlation matrix.  
+The average over Monte Carlo links of the
+Cholesky factors will not  generally yield a correlation matrix.  
 To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
@@
 \label{model2:sec}
-Analysis of the data using the model presented in \S\ref{model:sec} draws out parameter values consistent
-with two-parameter dust models.  We now consider an extension to our model that accommodates an additional
+In \S\ref{model:sec} we show that the SNf data analyzed with an agnostic 2-parameter model produces
+results consistent
+with two-parameter dust models.  An extension to our model is now added to accommodate
+a possible additional
 color parameter.
@@
 \end{equation}
-In all aspects it is identical to the previous model except for the addition of the term $\delta D$ toward the mean
-absolute magnitudes.
-Each supernova has an intrinsic $D$ parameter that influences absolute magnitudes with strength $\delta$. 
+In all aspects it is identical to the previous model except for the addition of the term $\delta D$,
+which affects the mean
+absolute magnitudes:
+each supernova has an intrinsic $D$ parameter that is linearly related to
+absolute magnitudes through global coefficients $\delta$. 
 Although
@@
 variations to those that cannot be attributed to 
-the $\gamma k$ terms (i.e.\ dust); practically it is difficult to break the degeneracies between $\delta D$  
-and $\gamma k$ in the fit. 
+the $\gamma k$ terms (i.e.\ dust); this condition breaks the degeneracies between $\delta D$  
+and $\gamma k$. 
 Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_0$,
@@
 deviations of the residuals in the $V$ and $I$ bands.
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
-$\alpha_X$
-&
-$0.0044^{0.0009}_{-0.0009}$
-&
-$0.0016^{0.0007}_{-0.0007}$
-&
-$0.0016^{0.0006}_{-0.0006}$
-&
-$0.0015^{0.0005}_{-0.0005}$
-&
-$0.0026^{0.0005}_{-0.0005}$
-\\
-${\alpha_X/\alpha_V-1}$
-&
-$   1.8^{   0.9}_{  -0.4}$
-&
-$   0.0^{   0.1}_{  -0.2}$
-&
-$   0$
-&
-$  -0.0^{   0.1}_{  -0.1}$
-&
-$   0.6^{   0.6}_{  -0.3}$
-\\
-$\beta_X$
-&
-$ 0.032^{ 0.003}_{-0.003}$
-&
-$ 0.025^{ 0.002}_{-0.003}$
-&
-$ 0.025^{ 0.002}_{-0.002}$
-&
-$ 0.020^{ 0.002}_{-0.002}$
-&
-$ 0.019^{ 0.002}_{-0.002}$
-\\
-${\beta_X/\beta_V-1}$
-&
-$  0.26^{  0.05}_{ -0.05}$
-&
-$ -0.01^{  0.03}_{ -0.03}$
-&
-$  0$
-&
-$ -0.19^{  0.01}_{ -0.02}$
-&
-$ -0.24^{  0.03}_{ -0.03}$
-\\
-$\eta_X$
-&
-$-0.0002^{0.0012}_{-0.0011}$
-&
-$0.0000^{0.0010}_{-0.0009}$
-&
-$0.0005^{0.0008}_{-0.0008}$
-&
-$0.0005^{0.0007}_{-0.0007}$
-&
-$-0.0003^{0.0006}_{-0.0006}$
-\\
-${\eta_X/\eta_V-1}$
-&
-$ -0.40^{  2.19}_{ -1.84}$
-&
-$ -0.36^{  1.57}_{ -1.19}$
-&
-$  0$
-&
-$ -0.12^{  0.27}_{ -0.25}$
-&
-$ -0.89^{  1.72}_{ -1.35}$
-\\
-$\gamma^0_X$
-&
-$ 62.53^{  3.64}_{ -3.63}$
-&
-$ 50.74^{  3.08}_{ -3.03}$
-&
-$ 37.67^{  2.62}_{ -2.60}$
-&
-$ 28.89^{  2.32}_{ -2.33}$
-&
-$ 20.62^{  2.15}_{ -2.16}$
-\\
-${\gamma^0_X/\gamma^0_V-1}$
-&
-$  0.66^{  0.06}_{ -0.05}$
-&
-$  0.35^{  0.03}_{ -0.03}$
-&
-$  0$
-&
-$ -0.23^{  0.01}_{ -0.01}$
-&
-$ -0.45^{  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-&
-$ -9.93^{  3.53}_{ -4.16}$
-&
-$-11.80^{  2.91}_{ -3.44}$
-&
-$-14.25^{  2.45}_{ -2.72}$
-&
-$-13.39^{  2.15}_{ -2.29}$
-&
-$-12.05^{  1.97}_{ -2.14}$
-\\
-${\gamma^1_X/\gamma^1_2-1}$
-&
-$ -0.30^{  0.18}_{ -0.19}$
-&
-$ -0.17^{  0.09}_{ -0.10}$
-&
-$  0$
-&
-$ -0.06^{  0.05}_{ -0.04}$
-&
-$ -0.16^{  0.10}_{ -0.08}$
-\\
-${{\delta_X/\delta_I-1}}$
-&
-$ -0.61^{  0.47}_{ -0.18}$
-&
-$ -1.21^{  0.25}_{ -0.77}$
-&
-$ -1.76^{  0.16}_{ -0.20}$
-&
-$ -1.17^{  0.29}_{ -0.20}$
-&
-$  0$
-\\
-$\sigma_X$
-&
-$ 0.059^{ 0.013}_{-0.013}$
-&
-$ 0.031^{ 0.007}_{-0.008}$
-&
-$ 0.017^{ 0.005}_{-0.007}$
-&
-$ 0.012^{ 0.006}_{-0.007}$
-&
-$ 0.039^{ 0.005}_{-0.005}$
-\\
-\hline
-\end{tabular}
-\caption{68\% credible Intervals for the Global Fit Parameters of the Intrinsic-Extrinsic Model\label{global2:tab}}
-\end{table}
-
-We find that the newly fitted $\delta$ parameters have almost identical association with the Fitzpatrick dust law, in that
+The newly fitted $\delta$ parameters have an almost identical association with the Fitzpatrick dust law, in that
 \begin{equation}
@@
 
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+$\alpha_X$
+&
+$0.0044^{0.0009}_{-0.0009}$
+&
+$0.0016^{0.0007}_{-0.0007}$
+&
+$0.0016^{0.0006}_{-0.0006}$
+&
+$0.0015^{0.0005}_{-0.0005}$
+&
+$0.0026^{0.0005}_{-0.0005}$
+\\
+${\alpha_X/\alpha_V-1}$
+&
+$   1.8^{   0.9}_{  -0.4}$
+&
+$   0.0^{   0.1}_{  -0.2}$
+&
+$   0$
+&
+$  -0.0^{   0.1}_{  -0.1}$
+&
+$   0.6^{   0.6}_{  -0.3}$
+\\
+$\beta_X$
+&
+$ 0.032^{ 0.003}_{-0.003}$
+&
+$ 0.025^{ 0.002}_{-0.003}$
+&
+$ 0.025^{ 0.002}_{-0.002}$
+&
+$ 0.020^{ 0.002}_{-0.002}$
+&
+$ 0.019^{ 0.002}_{-0.002}$
+\\
+${\beta_X/\beta_V-1}$
+&
+$  0.26^{  0.05}_{ -0.05}$
+&
+$ -0.01^{  0.03}_{ -0.03}$
+&
+$  0$
+&
+$ -0.19^{  0.01}_{ -0.02}$
+&
+$ -0.24^{  0.03}_{ -0.03}$
+\\
+$\eta_X$
+&
+$-0.0002^{0.0012}_{-0.0011}$
+&
+$0.0000^{0.0010}_{-0.0009}$
+&
+$0.0005^{0.0008}_{-0.0008}$
+&
+$0.0005^{0.0007}_{-0.0007}$
+&
+$-0.0003^{0.0006}_{-0.0006}$
+\\
+${\eta_X/\eta_V-1}$
+&
+$ -0.40^{  2.19}_{ -1.84}$
+&
+$ -0.36^{  1.57}_{ -1.19}$
+&
+$  0$
+&
+$ -0.12^{  0.27}_{ -0.25}$
+&
+$ -0.89^{  1.72}_{ -1.35}$
+\\
+$\gamma^0_X$
+&
+$ 62.53^{  3.64}_{ -3.63}$
+&
+$ 50.74^{  3.08}_{ -3.03}$
+&
+$ 37.67^{  2.62}_{ -2.60}$
+&
+$ 28.89^{  2.32}_{ -2.33}$
+&
+$ 20.62^{  2.15}_{ -2.16}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
+&
+$  0.66^{  0.06}_{ -0.05}$
+&
+$  0.35^{  0.03}_{ -0.03}$
+&
+$  0$
+&
+$ -0.23^{  0.01}_{ -0.01}$
+&
+$ -0.45^{  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+&
+$ -9.93^{  3.53}_{ -4.16}$
+&
+$-11.80^{  2.91}_{ -3.44}$
+&
+$-14.25^{  2.45}_{ -2.72}$
+&
+$-13.39^{  2.15}_{ -2.29}$
+&
+$-12.05^{  1.97}_{ -2.14}$
+\\
+${\gamma^1_X/\gamma^1_2-1}$
+&
+$ -0.30^{  0.18}_{ -0.19}$
+&
+$ -0.17^{  0.09}_{ -0.10}$
+&
+$  0$
+&
+$ -0.06^{  0.05}_{ -0.04}$
+&
+$ -0.16^{  0.10}_{ -0.08}$
+\\
+${{\delta_X/\delta_I-1}}$
+&
+$ -0.61^{  0.47}_{ -0.18}$
+&
+$ -1.21^{  0.25}_{ -0.77}$
+&
+$ -1.76^{  0.16}_{ -0.20}$
+&
+$ -1.17^{  0.29}_{ -0.20}$
+&
+$  0$
+\\
+$\sigma_X$
+&
+$ 0.059^{ 0.013}_{-0.013}$
+&
+$ 0.031^{ 0.007}_{-0.008}$
+&
+$ 0.017^{ 0.005}_{-0.007}$
+&
+$ 0.012^{ 0.006}_{-0.007}$
+&
+$ 0.039^{ 0.005}_{-0.005}$
+\\
+\hline
+\end{tabular}
+\caption{68\% credible Intervals for the Global Fit Parameters of the Intrinsic-Extrinsic Model\label{global2:tab}}
+\end{table}
+
 The distribution of both sources of color excess $E(B-V)$ and
- $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
+ $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
 Recall that our boundary conditions set the means of both distributions to zero. 
@@
 mag respectively.
-The range of $B-V$ colors is $\sim 8$ times larger for the external contribution. 
+The range of $B-V$ colors is $\sim 8$ times larger for the external contribution; variation in $B-V$ color due to the intrinsic term is dwarfed by the extrinsic process. 
 Both distributions are non-Gaussian, that of $E(B-V)$ has a sharp rise in the blue and an extended tail in the red, consistent
@@
 The significance of the $\delta$ parameters is shown pictorially
-in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which is bimodal due to the parity symmetry.  The probability
-of the null result $\delta_X=0$ for all $X$, lies on a
-$>98\%$-contour.  The right plot shows values of $\delta_X/\delta_I-1$, which nulls out the parity symmetry and has significant non-zero values.
+in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which is bimodal due to the sign-flip degeneracy.  The probability
+of the null result $\delta_X=0$ for all $X$ is $>98\%$, determined through
+the population of its bin in a 5-dimensional histogram.
+The right plot shows values of $\delta_X/\delta_I-1$ that  have significant non-zero values.   An interesting feature
+is that the shift in magnitude is not monotonic in redshift, but rather decreases from $U$ to $V$, and then increases from $V$
+to $I$.
+These are not the behaviors expected from normal dust,
+circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
+2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
+more complicated underlying supernova physics.
 
@@
    \centering
-   \includegraphics[width=2.8in]{output15/delta_corner.pdf}
-      \includegraphics[width=2.8in]{output15/deltaratio.pdf}
+   \includegraphics[height=2.5in]{output15/delta_corner.pdf}
+      \includegraphics[height=2.5in]{output15/deltaratio.pdf}
    \caption{Significance of the non-zero values of $\delta$.  Left: Posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
@@
 \label{discussion:sec}
-We model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
+To summarize, we model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
 extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
@@
 with $R^F_V=2.43$.  This model  does an excellent job in
-describing SN~2014J, a supernova not used in the training that has atypical colors.  An extended version
-of the model retains the features of the first model, but now with strong evidence for a new parameter related to supernova
-colors.
-
-\color{red}
+describing SN~2014J, a supernova not used in the training that has extreme colors.  An extended version
+of the model retains the features of the first model, and gives strong evidence for a new parameter that affects supernova
+colors distinct from dust.
+
 Our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
@@
 Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
-\citep{2010A&A...523A...7G}, showing that our model exhibits no clear loss from the neglect of $X_1$.
-We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$; the credible intervals
+\citep{2010A&A...523A...7G}, showing that our model exhibits no clear loss in our ability to standardize
+magnitudes although $X_1$ is neglected.
+There is no apparent correlation
+between $X_1$ and the residuals between observed and model-predicted colors, as seen in
+Figure~\ref{x1res:fig}. 
+We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$ to the 
+intrinsic magnitude; the credible intervals
 from this analysis are given in Table~\ref{globalx1:tab}; no significant changes are seen. 
@@
 has a non-zero value at $>2\sigma$.
-The parameters that describe intrinsic color $\delta$ remain significantly non-zero.
+The evidence for a non-zero $\delta$ remains, meaning that it is not an artifact of
+having neglected light-curve shape.
 
@@
 $   0.0042 \pm    0.0014$
-$   0.0031 \pm    0.0017$.
+($   0.0031 \pm    0.0017$).  A significant difference is not found.
 The ideograms for the low- and high-mass samples is shown in Figure~\ref{childress:fig}.
-The 2-sample Kolmogorov-Smirnov test of the medians gives a $p$-value of
-%---
-0.29.
-%---
 From the above evidence, we cannot show that low- and high-mass hosts produce SNe~Ia with difference $E_\gamma(B-V)$ distributions. 
@@
 s     \includegraphics[width=2.8in]{output15/rigault2.pdf}
-      \caption{\textcolor{red}{Intrinsic parameter $E_\gamma(B-V)$  versus host mass.  Hosts too faint for a mass measurement
-      are assigned a mass of 5.
+      \caption{\textcolor{red}{Left: Intrinsic parameter $A_I=\delta_I D$  versus host mass.  Hosts too faint for a mass measurement
+      are assigned a mass of 5.  Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
+      less than and greater than  $10 \log{(M/M_\sun)}$.
 Right: Ideograms of  $E_\gamma(B-V)$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
@@
 
-The model introduced in this article is limited, in that it doesn't accommodate the expected diversity
-in extrinsic dust properties that supernovae in different hosts may encounter.  Extending our model to 
-include  a parameterized  $\gamma$ distribution would allow a range of host-dust behavior, and
-offers a direction of further study.
-For the moment, we assert that variations in extrinsic dust across supernovae are limited in
-size by Eqn.~\ref{color_sd:eqn} and positive correlations possible within Eqn.~\ref{color_cor:eqn}.
-
 The model and results presented here

### 2016-10-04 forgerard.tex
version for collaboration resubmission

@@
 
-\title{Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory}
+\title{Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory}
 \author{A.~G.~Kim}
@@
 \begin{abstract}
+\color{red}
 An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
-is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
-dependent on the spectral equivalent widths and two independent color parameters, with better than 
+is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
+broadband photometry and their colors are found to be 
+dependent on the spectral equivalent widths and two independent color parameters, to better than 
 %-----
- $98$\%
+$(1-5\times10^{-5})$
 %------
 confidence.
-One parameter, interpreted as due to extrinsic host-galaxy
-dust extinction, is consistent with a \citet{1999PASP..111...63F} dust model with
+The two parameters exhibit the behavior expected from the two-parameter
+\citet{1999PASP..111...63F} dust model with a per-supernova scatter in
+total-to-selective extinction, an effective
 %-----
-$R_V=2.97^{+0.18}_{-0.17}$.
+$R^F_V=2.43^{+0.16}_{-0.17}$
 %------
- The second parameter is inconsistent with dust and
-is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: 
-\textcolor{red}{
-indirect evidence for intrinsic color dispersion from Hubble residuals;
-the wide range of inferred $R_V$ among
-SNe~Ia; the systematically lower inferred $R_V$ of redder supernovae;}
-and the colors of SN~2014J,.
-\textcolor{red}{
-The new parameter
-provides a handle with which to interpret  Hubble-residual correlations with host-galaxy properties,}
+for the full sample, and a difference in the average $R^F_V$ between extremely blue and red supernovae .  The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J.
+Extending the model to allow three color parameters gives a detection of a third parameter at  $>98$\% confidence.
+\color{black}
 \end{abstract}
@@
 \textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from maximum, in the case of multiple spectra the one
-closest to maximum is used \citep{chotard:thesis}. [Confirm!]
+closest to maximum is used \citep{chotard:thesis}.
 The weighted mean is used for the  SiII$\lambda 6355$ wavelength.}
@@
 The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
-parameter and observed magnitudes.
+parameters to observed magnitudes.
 
@@
 conditions break the 
-degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$.
+degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$
+up to the $\pm$ sign.
 Furthermore we impose
@@
 \\
-${\gamma^1_X/\gamma^1_2-1}$
+${\gamma^1_X/\gamma^1_V-1}$
 &
@@
 \end{tabular}
-\caption{68\% credible Intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model \label{global:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model \label{global:tab}}
 \end{table}
@@
 
-\subsection{Two Extrinsic Parameters $k_0$ and $k_1$}
+\subsection{The Two Extrinsic Parameters $k_0$ and $k_1$}
 \color{red}
@@
 which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
-estimate $R_V=A_V/(E(B-V)-zeropoint)$ per supernova, shown in Figure~\ref{avebv:fig}.
+estimate $R_V=(A_V-zeropoint)/E(B-V)$ per supernova, shown in Figure~\ref{avebv:fig}.
 Extremely blue supernovae ($E(B-V) + const <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
@@
 
-For the linear 2-parameter model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
+For a linear 2-parameter model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
 It turns out that the planes for both our and the Fitzpatrick dust model are nearly parallel, in that
@@
 The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
-are projected onto the Fitzpatrick values of $E^F(B-V)$ and $A^F$, up to a constant:  these are shown in Figure~\ref{avebv:fig}.
+are projected onto the Fitzpatrick values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
 The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.43^{+0.16}_{-0.17}$.  
-The linear fit also produces the zeropoint, allowing us to determine $R^F_V$ for each supernova,
+The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
 which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
@@
 The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
-parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
-external dust is responsible for most of our $k_0$ and $k_1$ parameters.
+parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$, lead us to conclude that 
+$k_0$, $k_1$, $\gamma^0$, $\gamma^1$ describe for the most part
+external dust.
 
@@
 The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
-following their perscription of averaging measurements within 5-days of peak $B$ magnitude.
+following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
 Their values 
@@
 \begin{equation}
-E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)k_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)k_1,
+E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)x_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)x_1,
 \end{equation}
-where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab}.
+where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab} and the fit
+parameters $x_i $.
 
@@
 %----
-$k_0= 2.65$, $ k_1=-1.64$ with covariance
+$x_0= 2.65$, $ x_1=-1.64$ with covariance
 %----
@@
 \label{model2:sec}
-In \S\ref{model:sec} we show that the SNf data analyzed with an agnostic 2-parameter model produces
+In \S\ref{model:sec} we show that the SNf data analyzed with an agnostic model with
+two extrinsic parameters produce
 results consistent
@@
 Although
-this term is introduced through the absolute rather than observed magnitudes,
+this term is introduced through absolute rather than observed magnitudes,
 practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
-degeneracy, this term is referred to as ``intrinsic''.
+degeneracy, for convenience this term is referred to as ``intrinsic''.
 
@@
 In the running of the Monte Carlo, the initial conditions for
-$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}.
+$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
+to maintain their correspondence between the two models.
 
 The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
-results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that common parameters
+results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
 are consistent well within 1$\sigma$ uncertainties.  The most significant changes of note are in the standard
 deviations of the residuals in the $V$ and $I$ bands.
-The newly fitted $\delta$ parameters have an almost identical association with the Fitzpatrick dust law, in that
+The newly fitted $\delta$ parameters have an almost identical association with the Fitzpatrick dust law, in that now
 \begin{equation}
@@
 where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
-contribute  2\% and 5\% to the total  length of the vector.
+contribute similar 2\% and 5\% to the total  length of the vector.
 
@@
 \end{tabular}
-\caption{68\% credible Intervals for the Global Fit Parameters of the Intrinsic-Extrinsic Model\label{global2:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters of the Intrinsic-Extrinsic Model\label{global2:tab}}
 \end{table}
 
-The distribution of both sources of color excess $E(B-V)$ and
+The distributions of both sources of color excess $E(B-V)$ and
  $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
-Recall that our boundary conditions set the means of both distributions to zero. 
 The standard deviations of $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
@@
 The range of $B-V$ colors is $\sim 8$ times larger for the external contribution; variation in $B-V$ color due to the intrinsic term is dwarfed by the extrinsic process. 
-Both distributions are non-Gaussian, that of $E(B-V)$ has a sharp rise in the blue and an extended tail in the red, consistent
+Both distributions are non-Gaussian, that of $E(B-V)$ having a sharp rise in the blue and an extended tail in the red, consistent
 with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.
@@
 The significance of the $\delta$ parameters is shown pictorially
-in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which is bimodal due to the sign-flip degeneracy.  The probability
-of the null result $\delta_X=0$ for all $X$ is $>98\%$, determined through
+in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which are bimodal due to the sign-flip degeneracy.  The probability
+of the null result $\delta_X=0$ for all $X$ is $<98\%$, determined through
 the population of its bin in a 5-dimensional histogram.
 The right plot shows values of $\delta_X/\delta_I-1$ that  have significant non-zero values.   An interesting feature
-is that the shift in magnitude is not monotonic in redshift, but rather decreases from $U$ to $V$, and then increases from $V$
+is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
 to $I$.
@@
    \caption{Significance of the non-zero values of $\delta$.  Left: Posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
-   Right: $\delta_X/\delta_I-1$, which as a ratio is insensitive to the degeneracy.
+   Right: $\delta_X/\delta_I-1$, which is insensitive to the sign-flip degeneracy.
    \label{deltacorner:fig}}
@@
 
-\section{Discussion}
+\section{Summary and Discussion}
 \label{discussion:sec}
@@
 with $R^F_V=2.43$.  This model  does an excellent job in
-describing SN~2014J, a supernova not used in the training that has extreme colors.  An extended version
+describing SN~2014J, a supernova with extreme colors not used in the training.  An extended version
 of the model retains the features of the first model, and gives strong evidence for a new parameter that affects supernova
-colors distinct from dust.
+colors in a manner that is distinct from  the expectations from dust.
 
@@
 The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
-for our sample, as shown in Figure~\ref{x1:fig}.
-On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
+for our sample.
+On the other hand, there is no such correlation seen between $A_{\delta I} = \delta_I D$ and $X_1$, as shown in Figure~\ref{x1:fig}. 
 Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
-\citep{2010A&A...523A...7G}, showing that our model exhibits no clear loss in our ability to standardize
+\citep{2010A&A...523A...7G}, showing that our model exhibits no loss in its ability to standardize
 magnitudes although $X_1$ is neglected.
@@
 intrinsic magnitude; the credible intervals
-from this analysis are given in Table~\ref{globalx1:tab}; no significant changes are seen. 
-In fact, light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: only $\zeta_R/\zeta_V$
+from this analysis are given in Table~\ref{globalx1:tab}; there are no significant changes with respect to the reference model. 
+Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: only $\zeta_R/\zeta_V$
 has a non-zero value at $>2\sigma$.
@@
    \includegraphics[width=2.8in]{output15/x1D.pdf}
-    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
+    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $A_{\delta I}  = \delta_I D$.}
    \label{x1:fig}}
@@
 \end{tabular}
-\caption{68\% credible Intervals for the Global Fit Parameters including $X_1$ \label{globalx1:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters including $X_1$ \label{globalx1:tab}}
 \end{table}
@@
 \citet{2016arXiv160904470M} find that with intrinsic color scatter, the null mass-step effect falls on the 95\%-level of their posterior.
-To explore this possibility we plot in Figure~\ref{childress:fig} our intrinsic color excess $E_\gamma(B-V)$  versus host mass 
-\citep{2016rigault}.  Choosing the same mass cut as  \citet{2013ApJ...770..108C}, $\log{(M/M_\sun)}=10$, we calculate the average
-color excess for low- (high)-mass hosts to be
+To explore this possibility we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
+\citep{2016rigault}, and their ideograms for two samples separated by a host mass of  $10 \log{(M/M_\sun)}$
+used by  \citet{2013ApJ...770..108C}.
+Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta I}$, the difference is
+not significant; we calculate the average $A_{\delta I}$
+for low- (high)-mass hosts to be
 $   0.0042 \pm    0.0014$
-($   0.0031 \pm    0.0017$).  A significant difference is not found.
-The ideograms for the low- and high-mass samples is shown in Figure~\ref{childress:fig}.
-From the above evidence, we cannot show that low- and high-mass hosts produce SNe~Ia with difference $E_\gamma(B-V)$ distributions. 
+($   0.0031 \pm    0.0017$). 
 Using the SNfactory sample,
-\citet{2013A&A...560A..66R} find that step in Hubble residuals as better related to local star formation rate, rather than host mass.
+\citet{2013A&A...560A..66R} find that step in Hubble residuals is better related to local star formation rate, rather than host mass.
 The connection between our intrinsic parameter and local star formation and other host properties is deferred to
@@
 s     \includegraphics[width=2.8in]{output15/rigault2.pdf}
-      \caption{\textcolor{red}{Left: Intrinsic parameter $A_I=\delta_I D$  versus host mass.  Hosts too faint for a mass measurement
+      \caption{\textcolor{red}{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host mass.  Hosts too faint for a mass measurement
       are assigned a mass of 5.  Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
       less than and greater than  $10 \log{(M/M_\sun)}$.
-Right: Ideograms of  $E_\gamma(B-V)$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
+Right: Ideograms of  $A_{\delta I}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
 }

### 2016-10-05 forgerard.tex
more stuff

@@
    \includegraphics[width=3.2in]{output11/sn2014j.pdf} 
-   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and  \citet{2014ApJ...788L..21A}  
+   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and  \citet{2014ApJ...788L..21A}.
    \label{sn2014j:fig}}
@@
 
-In the fit to our model, the observed color excess is attributed to   extrinsic
+In the fit to our model, the observed color excess is attributed to 
 %----
-$E_{\gamma^0}(B-V)=  0.92 \pm   0.08$ and intrinsic $E_{\gamma_1}(B-V)=  0.28 \pm   0.08$
+$E_{\gamma^0}(B-V)=  0.92 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.28 \pm   0.08$
 %-----
@@
 attributed to dust. 
+%The projection of our median parameter values onto the Fitzpatrick plane gives
+%$A^F=1.27$, $E^F(B-V)=1.07$, and thus $R^F_V=1.18.$
 

### 2016-10-10 forgerard.tex
responding to Greg's comments

@@
 %------
-for the full sample, and a difference in the average $R^F_V$ between extremely blue and red supernovae .  The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J.
-Extending the model to allow three color parameters gives a detection of a third parameter at  $>98$\% confidence.
+for the full sample, and a difference in the average $R^F_V$ between extremely blue and red supernovae .
+The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the Fitzpatrick dust model.
+Extending the model to allow three color parameters gives almost identical results for
+the two parameters, plus a detection of a third parameter at  $>98$\% confidence.
 \color{black}
@@
 and probe of cosmology \citep[e.g.][]{1992ARA&A..30..359B, 1993ApJ...415....1S}.  After further careful consideration of supernova data, it was recognized
-that SN~Ia light-curve shapes \citep{1993ApJ...413L.105P} and colors \citep{1998A&A...331..815T} exhibit subtle signs of heterogeneity,
+that SN~Ia light-curve shapes \citep{1993ApJ...413L.105P} and colors \citep{1996ApJ...473...88R, 1998A&A...331..815T} exhibit subtle signs of heterogeneity,
 which being correlated with absolute magnitude
-need to be considered when inferring distances.  Empirical models parameterizing SNe~Ia by their light-curve shape
-and color were developed \citep{1996ApJ...473...88R, 1999ApJ...517..565P} that enabled absolute magnitude corrections
+need to be considered when inferring distances.  Empirical models parameterizing SNe~Ia by their light-curve shape \citep{1996ApJ...473...88R,
+1997ApJ...483..565P,
+1999ApJ...517..565P}
+and color  \citep{1996ApJ...473...88R}  were developed that enabled absolute magnitude corrections
 and accurate distance measurements of cosmological supernovae,
@@
 They remain two-parameter models, with one parameter characterizing light-curve shape and the other
- color.  The physical cause of the color diversity is interpreted differently by the two sets of authors: 
+ color.
+ \textcolor{red}{In SALT2 the light curve shapes are described by a multiplicative scaling (``stretch'')  of the time evolution,
+ whereas MLCS2k2 varies shape with additive corrections to magnitudes.}
+ The physical cause of the color diversity is interpreted differently by the two sets of authors: 
 \citet{2007A&A...466...11G} pragmatically extract color variation empirically from SNe that span a wide range of colors, with no attribution
@@
 \citet{2007ApJ...659..122J}
-attribute changes in color to the attenuation of light from host-galaxy dust. Neither model accommodates the naive expectation of both independent
-intrinsic and extrinsic color variability.
-
-There is evidence that supports the expectation that a single parameter cannot describe the full range
+attribute changes in color
+\textcolor{red}{partially to intrinsic variations connected to light-curve shape, and partially}
+to the attenuation of light from host-galaxy dust.
+
+There is evidence that supports the expectation that a single parameter beyond light-curve shape  cannot describe the full range
 of colors seen in the SN~Ia population.  One approach to look for color diversity is to find correlations between color and spectral features.
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two subpopulations distinguished
-by Si velocity with differing $B_{max}-V_{max}$.
+by Si velocity with differing $B_{max}-V_{max}$; this color correlation, \textcolor{red}{ in addition to one with $B-R$, is confirmed by
+\citet{2014ApJ...797...75M}.
+}
 \citet{2015MNRAS.451.1973S}
 find that high-velocity SiII$\lambda$6355 is found in objects that have red ultraviolet/optical colors near maximum brightness.
+\textcolor{red}{
+\citet{2011MNRAS.413.3075M} argue that viewing angle is an important determinant in controlling supernova color, which is
+traced by wavelength shifts in nebular emission lines; such correlations are also seen by \citet{2011A&A...534L..15C}.
+}
 
@@
 independent (to first order) of the amount of dust along the line of sight.
-}
+\citet{2013ApJ...779...23M} find diversity in SNe~Ia UV emission, which they use to distinguish subclasses based on UV-optical colors.}
+\textcolor{red}{
+Such studies measuring $R_V$ are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
+\citep[e.g.][]{2011ApJ...731..120M}.}
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find wide
@@
 the canonical value for diffuse Milky Way dust.
-They also confirm the \citet{2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
+They also confirm the \citet{2011ApJ...731..120M, 2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
 In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
-the standard $R_V=3.1$ is recovered on average
-\textcolor{red}{though only after excluding their $>3 \sigma$ reddest supernovae.}
+the standard $R_V=3.1$ is recovered on average.
 
@@
 Hierarchical modeling has recently opened
-the study of intrinsic supernova color based on SN~Ia Hubble diagrams.
-\citet{2016arXiv160904470M} find that the distribution of
+the study of intrinsic supernova color based on SN~Ia Hubble diagrams; latent parameters that are not directly tied to observables,
+such as multiple parameters that simultaneously influence color, can be determined.
+\citet{2016arXiv160904470M} take the approach of modeling the distribution of their parameters, to find that the distribution of
 observed supernova magnitudes is better explained by a combination of intrinsic color dispersion and
-$R_V=3.7$ dust, over dust with no color dispersion.
-They draw these conclusions by using only one
-derived ``color'', the SALT2 fit parameter.
+$R_B=3.7$ dust, over dust with no color dispersion.
+They draw these conclusions by using only the SALT2 fit $X_1$ parameter as the summary statistic that describes color.
 }
 
-The Nearby Supernova Factory \citep[SNfactory;][]{2004SPIE.5249..146L} has collected  
+The Nearby Supernova Factory \citep[SNfactory;][]{2002SPIE.4836...61A} has systematically observed the
 spectrophotometric time series of hundreds of Hubble-flow $0.03<z<0.08$ SNe~Ia.   The $3200$--$10000$~\AA\ spectral coverage
 provides measurements of an array of supernova spectral features while also providing synthetic broadband photometry
-spanning near-UV to near-IR SN-frame wavelengths.  Well over a hundred of these supernovae have temporal coverage over
+spanning near-UV to near-IR SN-frame wavelengths.  \textcolor{red}{SNfactory specifically targeted objects
+early in their temporal evolution, so} that well over a hundred of these supernovae have  coverage over
 peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia colors and spectral features together.
@@
 In this article we use the idea that spectral indicators carry information on intrinsic supernova colors at peak magnitude.
-We allow for two independent color parameters, one due to intrinsic supernova
-properties and the other due to
-extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.  Our supernova model is presented in
-\S\ref{model:sec} and results are given in \S\ref{results:sec}.  In \S\ref{sn2014j:sec} our results are applied to the out-of-sample
+We allow for \textcolor{red}{three independent color parameters, one attributed to intrinsic supernova
+properties and two  attributed} to
+extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.  \textcolor{red}{A
+first analysis omitting the intrinsic parameter is presented in
+\S\ref{model:sec}, where we show that the properties of the two extrinsic parameters
+are consistent with the expectations of Milky Way-parameterized dust, and do an excellent job of fitting the data of the out-of-sample
 supernova SN2014J that has been previously identified as having extreme total-to-selective extinction.
-We conclude with a discussion of our findings in \S\ref{discussion:sec}.
+In \S\ref{model2:sec} we add to analysis the third intrinsic parameter, and find strong evidence for its influence on observed magnitudes.
+We summarize our findings, and relate our results with light-curve shape, SiII velocity, and the ``mass step'' in SN~Ia Hubble
+residuals in \S\ref{discussion:sec}.}
 
@@
 moderate spectral resolution ($R \sim 500$).  It consists of a
-high-throughput wide-band pure-lenslet integral field spectrograph
-\citep[IFS, ``\`a la TIGER;''][]{1995A&AS..113..347B,2000ASPC..195..173B,2001MNRAS.326...23B}, a
+high-throughput wide-band lenslet integral field spectrograph, a
 multi-filter photometric channel to image the field in the vicinity of
@@
 A discussion of the software pipeline is presented in
-\citet{2006ApJ...650..510A} and is updated in \citet{2010ApJ...713.1073S}.  A detailed
+\citet{2006ApJ...650..510A} and is updated in \citet{2010ApJ...713.1073S}. 
+The flux calibration is presented in \citet{2013A&A...549A...8B}.  A detailed
 description of host-galaxy subtraction is given in \citet{2011MNRAS.418..258B}.
 
-The current status of the data and its treatment is presented in \citet{2015ApJ...815...58F}.
+A recent description of the data is presented in \citet{2015ApJ...815...58F}.
 We provide a brief summary of the points important for this analysis.
 The spectral time-series  are corrected for Milky Way dust
-extinction \citep{1989ApJ...345..245C,1998ApJ...500..525S} but not for the
-effects of circumstellar or host-galaxy dust extinction.  
+extinction \citep{1989ApJ...345..245C,1998ApJ...500..525S}.  
 Each spectral time series is
-blue-shifted to rest-frame, and the fluxes are converted to luminosity assuming
+blue-shifted to rest-frame
+based on the systemic redshift of the host \citep[c.f.][]{2013ApJ...770..107C}, and the fluxes are converted to luminosity assuming
 distances expected for the supernova redshifts given a flat
@@
 
-Supernova-frame synthetic photometry is generated for a top-hat filter system
+Supernova-frame synthetic supernova-frame photometry is generated for a top-hat filter system
 comprised of five 
@@
 $I$ $[6968.29-8400.00]$\AA.
+For each supernova, the magnitudes at peak brightness are regressed from data within 5-days of peak brightness
+using single-band SALT2 fits.
 \color{black}
-For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
 The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
@@
 Equivalent widths and the
-\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from maximum, in the case of multiple spectra the one
-closest to maximum is used \citep{chotard:thesis}.
-The weighted mean is used for the  SiII$\lambda 6355$ wavelength.}
+\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from maximum.}
 
@@
 The data are given in Table~\ref{data:tab}.
-The peak magnitude uncertainties do have covariance, which are accounted
+The peak magnitude uncertainties do have covariance, which is accounted
 for in the analysis; only the standard deviation is included in the table.
@@
 \tabletypesize{\tiny}
-\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data\label{data:tab}}
+\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data \textcolor{red}{TABLE MAY GO IF THERE IS A NICO PAPER}
+\label{data:tab}}
 \tablehead{
@@
 
-Absolute photometric calibration is of extreme importance for the SNfactory.  This analysis, however, is confined to the relative colors for a low-redshift set of supernovae
-and is thus insensitive to uncertainties in these zeropoints.
-
-\section{Supernova Model: Two Extrinsic Parameters}
+%Absolute photometric calibration is of extreme importance for the supernova cosmology.
+%This analysis, however, is confined to the relative colors for a low-redshift set of supernovae
+%and is thus insensitive to uncertainties in these zeropoints.
+
+\section{Supernova Model I: Two Extrinsic Parameters}
 \label{model:sec}
@@
 %of intrinsic variation is accommodated.
-The intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
+These intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
 \textcolor{red}{The intrinsic magnitudes are then
@@
 Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
-$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
+$C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
 to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
@@
 \end{equation}
-The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
+The first two conditions specify the definition of zero color relative to which the color excess is measured:
+in a linear model this value is arbitrary.    The latter two exclude degenerate posterior space
 associated
@@
 
-Having the intrinsic dispersion $C_c$ as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
+Having the intrinsic dispersion, $C_c$, as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
 ascribed to $\Delta$, $\gamma^0 k_0$, and $\gamma^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
-that drives the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$;
+that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$;
 The distributions of $\Delta$, $k_0$, and $k_1$ turn out to
-be non-Gaussian, and so are not well described by a Normal covariance; Grey offsets would appear as a constant
+be non-Gaussian, and so are not well described by the Normal covariance we impose in $C_c$; the grey magnitude offsets, $\Delta$, would appear as a constant
 in all elements of the covariance matrix, which is disfavored for the Bayesian prior selected for $C_c$.
 
-In a Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
+In a Bayesian analysis such as this the priors must be described.  A flat prior is used for all parameters except
 for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior\footnote{
@@
 deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
- $0.1$ and scale $0.1$ mag restricted to positive values.  (We find that imposing a stricter assumption of a
+ $0.1$ and scale $0.1$ mag restricted to positive values.
+ \textcolor{red}{This prior for a covariance matrix is recommended by STAN.}
+ (We find that imposing a stricter assumption of a
  diagonal covariance matrix, with no reference to a correlation matrix with LKJ prior, yields the same parameter distributions within
@@
 in iterative simulations 
-by using multilple sequences to estimate how much that distribution would sharpen if the simulations were run longer.
-$N_{eff}$ is an estimate of the number of independent draws.
-The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
+by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
+$N_{eff}$ is an estimate of the number of independent draws.  \textcolor{red}{We run four chains, each with 10000 iterations of which
+half are used for warmup.}
+The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.}
@@
 $\gamma^0_0$ and small negative $\gamma^1_0$ to satisfy our limit conditions.  Parameter credible intervals
-remain consistent within uncertainty.
+remain consistent within the 68\% credible intervals.
 
@@
             \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
-            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution, not to 68\%, 95\%, etc.\
+            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
+            projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
             enclosed probability.  \label{global1:fig}}
@@
 \hline
-& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+Parameter & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
 $\alpha_X$
 &
-$0.0043^{0.0009}_{-0.0009}$
-&
-$0.0016^{0.0007}_{-0.0007}$
-&
-$0.0015^{0.0006}_{-0.0006}$
-&
-$0.0015^{0.0005}_{-0.0005}$
-&
-$0.0026^{0.0005}_{-0.0004}$
+$0.0043^{+0.0009}_{-0.0009}$
+&
+$0.0016^{+0.0007}_{-0.0007}$
+&
+$0.0015^{+0.0006}_{-0.0006}$
+&
+$0.0015^{+0.0005}_{-0.0005}$
+&
+$0.0026^{+0.0005}_{-0.0004}$
 \\
@@
 &
-$   1.9^{   1.0}_{  -0.5}$
-&
-$   0.1^{   0.1}_{  -0.2}$
-&
-$   0$
-&
-$  -0.0^{   0.1}_{  -0.1}$
-&
-$   0.7^{   0.7}_{  -0.3}$
+$   1.9^{+   1.0}_{  -0.5}$
+&
+$   0.1^{+   0.1}_{  -0.2}$
+&
+\ldots
+&
+$  -0.0^{+   0.1}_{  -0.1}$
+&
+$   0.7^{+   0.7}_{  -0.3}$
 \\
@@
 &
-$ 0.032^{ 0.003}_{-0.003}$
-&
-$ 0.025^{ 0.002}_{-0.003}$
-&
-$ 0.025^{ 0.002}_{-0.002}$
-&
-$ 0.020^{ 0.002}_{-0.002}$
-&
-$ 0.019^{ 0.002}_{-0.002}$
+$ 0.032^{+ 0.003}_{-0.003}$
+&
+$ 0.025^{+ 0.002}_{-0.003}$
+&
+$ 0.025^{+ 0.002}_{-0.002}$
+&
+$ 0.020^{+ 0.002}_{-0.002}$
+&
+$ 0.019^{+ 0.002}_{-0.002}$
 \\
@@
 &
-$  0.26^{  0.05}_{ -0.05}$
-&
-$ -0.01^{  0.03}_{ -0.03}$
-&
-$  0$
-&
-$ -0.19^{  0.01}_{ -0.01}$
-&
-$ -0.24^{  0.03}_{ -0.03}$
+$  0.26^{+  0.05}_{ -0.05}$
+&
+$ -0.01^{+  0.03}_{ -0.03}$
+&
+\ldots
+&
+$ -0.19^{+  0.01}_{ -0.01}$
+&
+$ -0.24^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$-0.0002^{0.0012}_{-0.0011}$
-&
-$-0.0000^{0.0010}_{-0.0009}$
-&
-$0.0005^{0.0008}_{-0.0008}$
-&
-$0.0005^{0.0007}_{-0.0007}$
-&
-$-0.0003^{0.0006}_{-0.0006}$
+$-0.0002^{+0.0012}_{-0.0011}$
+&
+$-0.0000^{+0.0010}_{-0.0009}$
+&
+$0.0005^{+0.0008}_{-0.0008}$
+&
+$0.0005^{+0.0007}_{-0.0007}$
+&
+$-0.0003^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.40^{  2.33}_{ -1.90}$
-&
-$ -0.34^{  1.60}_{ -1.20}$
-&
-$  0$
-&
-$ -0.11^{  0.29}_{ -0.27}$
-&
-$ -0.84^{  1.66}_{ -1.27}$
-\\
-$\gamma^0_X$
-&
-$ 62.16^{  3.68}_{ -3.52}$
-&
-$ 50.39^{  3.05}_{ -2.96}$
-&
-$ 37.38^{  2.58}_{ -2.52}$
-&
-$ 28.71^{  2.31}_{ -2.25}$
-&
-$ 20.61^{  2.15}_{ -2.11}$
+$ -0.40^{+  2.33}_{ -1.90}$
+&
+$ -0.34^{+  1.60}_{ -1.20}$
+&
+\ldots
+&
+$ -0.11^{+  0.29}_{ -0.27}$
+&
+$ -0.84^{+  1.66}_{ -1.27}$
 \\
@@
 &
-$  0.66^{  0.06}_{ -0.05}$
-&
-$  0.35^{  0.03}_{ -0.03}$
-&
-$  0$
-&
-$ -0.23^{  0.01}_{ -0.01}$
-&
-$ -0.45^{  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-&
-$ -9.75^{  3.39}_{ -4.14}$
-&
-$-11.82^{  2.78}_{ -3.35}$
-&
-$-14.26^{  2.38}_{ -2.73}$
-&
-$-13.35^{  2.09}_{ -2.30}$
-&
-$-11.91^{  2.01}_{ -2.15}$
+$  0.66^{+  0.06}_{ -0.05}$
+&
+$  0.35^{+  0.03}_{ -0.03}$
+&
+\ldots
+&
+$ -0.23^{+  0.01}_{ -0.01}$
+&
+$ -0.45^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$ -0.31^{  0.17}_{ -0.18}$
-&
-$ -0.17^{  0.09}_{ -0.10}$
-&
-$  0$
-&
-$ -0.07^{  0.05}_{ -0.04}$
-&
-$ -0.17^{  0.10}_{ -0.09}$
+$ -0.31^{+  0.17}_{ -0.18}$
+&
+$ -0.17^{+  0.09}_{ -0.10}$
+&
+\ldots
+&
+$ -0.07^{+  0.05}_{ -0.04}$
+&
+$ -0.17^{+  0.10}_{ -0.09}$
 \\
@@
 &
-$ 0.060^{ 0.012}_{-0.012}$
-&
-$ 0.033^{ 0.007}_{-0.007}$
-&
-$ 0.021^{ 0.004}_{-0.006}$
-&
-$ 0.012^{ 0.007}_{-0.008}$
-&
-$ 0.044^{ 0.005}_{-0.004}$
+$ 0.060^{+ 0.012}_{-0.012}$
+&
+$ 0.033^{+ 0.007}_{-0.007}$
+&
+$ 0.021^{+ 0.004}_{-0.006}$
+&
+$ 0.012^{+ 0.007}_{-0.008}$
+&
+$ 0.044^{+ 0.005}_{-0.004}$
 \\
@@
 are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero
-to  within one sigma.
-The effect of spectral parameters on color is shown in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$:
+to  within one standard deviation.
+The effect of spectral parameters on color is shown in the rows of $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$
+in Table~\ref{global:tab}:
 values of zero signify no color changes associated with magnitude changes.
-Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically.
+Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes, though not in $B-V$ specifically.
 We do not detect a significant association between
@@
 
-The ideogram for the grey offsets $\Delta$ for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
+The ideogram for the grey offsets, $\Delta$, for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
 has a standard deviation of
@@
    \includegraphics[width=3.2in]{output11/Delta_hist.pdf} 
-   \caption{Ideogram for the grey offset $\Delta$.
+   \caption{Ideogram for the grey offset $\Delta$, normalized to have area equal 1.
    \label{hist:fig}}
@@
 
-Non-trivial residual magnitude dispersions are captured in $C_c$.
+Non-trivial residual magnitude dispersions are captured in $C_c$.  The diagonal elements are captured by the $\sigma$ parameters;
 % Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the square root of the diagonal elements of $C_c$. 
-The residual intrinsic dispersion ranges from
+the residual intrinsic dispersion ranges from
 $\sim 0.01$ to 0.06 mag, significantly smaller
-than the dispersion in $\Delta$.
-The off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix.
-The average over Monte Carlo links of the
+than the dispersion in $\Delta$.  Given that the 
+off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix rather than the matrix elements themselves,
+it is not straightforward to present correlation matrix confidences:
+the average over Monte Carlo links of the
 Cholesky factors will not  generally yield a correlation matrix.  
@@
 \begin{equation}
-\begin{pmatrix}
+C_c=
+\begin{pmatrix}
+\begin{array}{rrrrr}
 0.0038 & 0.0010 & -0.0002 & -0.0000 & 0.0003 \\
@@
 0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
+\end{array}
  \end{pmatrix} \text{mag}^2.
@@
  \begin{pmatrix}
-0.068 , 0.034 , 0.023 , 0.053
+0.068 & 0.034& 0.023 & 0.053
   \end{pmatrix} \text{mag}
@@
 \begin{pmatrix}
+\begin{array}{rrrr}
 1.000 & 0.615 & -0.334 & -0.296 \\
@@
 -0.334 & -0.193 & 1.000 & 0.634 \\
--0.296 & 0.099 & 0.634 & 1.000  \end{pmatrix}.
+-0.296 & 0.099 & 0.634 & 1.000 
+\end{array}
+\end{pmatrix}.
   \label{color_cor:eqn}
  \end{equation}
+Where quoted, corresponding color variances are smaller than those derived by \citet{2003A&A...404..901N, 2007ApJ...659..122J}
 
@@
 There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
-Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the infrequent selection of supernovae
+Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
 heavily extinguished by host-galaxy dust.
-Outliers  are also clearly distinguished in  $EW_{Ca}$--$\lambda_{Si}$ space.
+Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.
 
@@
    \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
-$\Delta$.  All links are plotted, so that each supernova contributes a cloud of points.
+$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
    \label{perobject:fig}}
@@
 
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$ are given in the matrix
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
 \begin{equation}
 \begin{pmatrix}
+\begin{array}{rrrrrr}
 1.000 & 0.001 & -0.059 & -0.045 & 0.105 & 0.007 \cr
@@
 0.007 & -0.003 & -0.024 & 0.027 & 0.055 & 1.000
+\end{array}
 \end{pmatrix}.
@@
 We find weak correlations between our color-excess parameters and the input features, the strongest being $-0.163$ between
-$E_\gamma(B-V)$ and $EW_{Si}$;
+$E_\gamma(B-V)$ and $EW_{Si}$.
 \color{black}
-recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
-\citep{2003MNRAS.340.1057S}.
+Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
+\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
 An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
@@
 
-The range of SiII equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA.  
-The implied span in $B$ magnitude based on $\beta_1$ is 0.54~mag.  Therefore $\beta_1$ cannot wholly be attributed to the line itself.
-Similarly, the CaII equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
-701~\AA.  The implied span in $U$ magnitude is is 0.21~mag, so $\alpha_0$ cannot be completely due to the line iteslf.
+The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that the affect on magnitude
+is
+$2.5 \log{20/850} \sim 0.03$ mag.  
+The implied span in $B$ magnitude based on $\beta_1$ is 0.54~mag.  Therefore $\beta_1$ cannot wholly be attributed to the flux deficit
+from the line itself.
+Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
+701~\AA, so that the affect on magnitude
+is
+$2.5 \log{50/701} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_0$ cannot be completely due to the line iteslf.
 
@@
 Extremely blue supernovae ($E(B-V) + const <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
-whereas the extreme red objects ($E(B-V) + const >0.1$) have $R_V=  2.52 \pm   0.08$, indicating that different physics
+whereas the extreme red objects ($E(B-V) + const >0.1$) have $R_V=  2.96 \pm   0.11$, indicating that different physical mechanisms
 operate in these regimes.
@@
 \end{equation}
-The \citet{1999PASP..111...63F} model is also approximately described by a linear model in the range of $R_V$ and wavelength under consideration:
+The \citet{1999PASP..111...63F} model is also approximately described by a linear model in the ranges of $R_V$ and wavelength under consideration:
 the results to follow vary at the percent level when making this approximation.
@@
 
-For a linear 2-parameter model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
+For a linear 2-parameter model, possible magnitudes are confined to a plane in the 5-dimensional UBVRI magnitude space.
 It turns out that the planes for both our and the Fitzpatrick dust model are nearly parallel, in that
@@
 \begin{pmatrix}
+\begin{array}{rr}
 1.15 & 2.82 \\
 0.75 & -5.43
+\end{array}
 \end{pmatrix} 
@@
 parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$, lead us to conclude that 
-$k_0$, $k_1$, $\gamma^0$, $\gamma^1$ describe for the most part
-external dust.
+$\{k_0, k_1\}$, describe, for the most part that behaves like the $\{ E(B-V), R_V\}$
+in standard models of Milky Way dust.
 
@@
 spectral evolution that 
-suffers low Galactic and host reddening
+suffers very low galactic and host reddening
 \citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
@@
 
-Data of SN~2014J are  analyzed using our model and the parameter values found with the SNfactory sample.
+Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
 The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
@@
    \centering
-   \includegraphics[width=3.2in]{output11/sn2014j.pdf} 
-   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and  \citet{2014ApJ...788L..21A}.
+   \includegraphics[width=4.5in]{output11/sn2014j.pdf} 
+   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and from  \citet{2014ApJ...788L..21A}.
    \label{sn2014j:fig}}
@@
 \begin{pmatrix}
+\begin{array}{rr}
 0.048 & 0.047 \\
 0.047 & 0.248
+\end{array}
 \end{pmatrix}.
@@
 The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
-overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} using
+overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} model using
 UV through NIR data,
@@
 
-\section{Intrinsic Color}
+\section{Supernova Model II: Two Extrinsic Parameter, One Intrinsic Parameter}
 \label{model2:sec}
-In \S\ref{model:sec} we show that the SNf data analyzed with an agnostic model with
+In \S\ref{model:sec} we show that the Nearby Supernova Factory data analyzed with an agnostic model with
 two extrinsic parameters produce
@@
 \begin{pmatrix}
+\begin{array}{rr}
 1.16 & 2.82 \\
 0.74 & -5.43
+\end{array}
 \end{pmatrix} 
@@
 \hline
-& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+Parameters& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
 $\alpha_X$
 &
-$0.0044^{0.0009}_{-0.0009}$
-&
-$0.0016^{0.0007}_{-0.0007}$
-&
-$0.0016^{0.0006}_{-0.0006}$
-&
-$0.0015^{0.0005}_{-0.0005}$
-&
-$0.0026^{0.0005}_{-0.0005}$
+$0.0044^{+0.0009}_{-0.0009}$
+&
+$0.0016^{+0.0007}_{-0.0007}$
+&
+$0.0016^{+0.0006}_{-0.0006}$
+&
+$0.0015^{+0.0005}_{-0.0005}$
+&
+$0.0026^{+0.0005}_{-0.0005}$
 \\
@@
 &
-$   1.8^{   0.9}_{  -0.4}$
-&
-$   0.0^{   0.1}_{  -0.2}$
-&
-$   0$
-&
-$  -0.0^{   0.1}_{  -0.1}$
-&
-$   0.6^{   0.6}_{  -0.3}$
+$   1.8^{+   0.9}_{  -0.4}$
+&
+$   0.0^{+   0.1}_{  -0.2}$
+&
+\ldots
+&
+$  -0.0^{+   0.1}_{  -0.1}$
+&
+$   0.6^{+   0.6}_{  -0.3}$
 \\
@@
 &
-$  0.26^{  0.05}_{ -0.05}$
-&
-$ -0.01^{  0.03}_{ -0.03}$
-&
-$  0$
-&
-$ -0.19^{  0.01}_{ -0.02}$
-&
-$ -0.24^{  0.03}_{ -0.03}$
+$  0.26^{+  0.05}_{ -0.05}$
+&
+$ -0.01^{+  0.03}_{ -0.03}$
+&
+\ldots
+&
+$ -0.19^{+  0.01}_{ -0.02}$
+&
+$ -0.24^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$-0.0002^{0.0012}_{-0.0011}$
-&
-$0.0000^{0.0010}_{-0.0009}$
-&
-$0.0005^{0.0008}_{-0.0008}$
-&
-$0.0005^{0.0007}_{-0.0007}$
-&
-$-0.0003^{0.0006}_{-0.0006}$
+$-0.0002^{+0.0012}_{-0.0011}$
+&
+$0.0000^{+0.0010}_{-0.0009}$
+&
+$0.0005^{+0.0008}_{-0.0008}$
+&
+$0.0005^{+0.0007}_{-0.0007}$
+&
+$-0.0003^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.40^{  2.19}_{ -1.84}$
-&
-$ -0.36^{  1.57}_{ -1.19}$
-&
-$  0$
-&
-$ -0.12^{  0.27}_{ -0.25}$
-&
-$ -0.89^{  1.72}_{ -1.35}$
-\\
-$\gamma^0_X$
-&
-$ 62.53^{  3.64}_{ -3.63}$
-&
-$ 50.74^{  3.08}_{ -3.03}$
-&
-$ 37.67^{  2.62}_{ -2.60}$
-&
-$ 28.89^{  2.32}_{ -2.33}$
-&
-$ 20.62^{  2.15}_{ -2.16}$
+$ -0.40^{+  2.19}_{ -1.84}$
+&
+$ -0.36^{+  1.57}_{ -1.19}$
+&
+\ldots
+&
+$ -0.12^{+  0.27}_{ -0.25}$
+&
+$ -0.89^{+  1.72}_{ -1.35}$
 \\
@@
 &
-$  0.66^{  0.06}_{ -0.05}$
-&
-$  0.35^{  0.03}_{ -0.03}$
-&
-$  0$
-&
-$ -0.23^{  0.01}_{ -0.01}$
-&
-$ -0.45^{  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-&
-$ -9.93^{  3.53}_{ -4.16}$
-&
-$-11.80^{  2.91}_{ -3.44}$
-&
-$-14.25^{  2.45}_{ -2.72}$
-&
-$-13.39^{  2.15}_{ -2.29}$
-&
-$-12.05^{  1.97}_{ -2.14}$
+$  0.66^{+  0.06}_{ -0.05}$
+&
+$  0.35^{+  0.03}_{ -0.03}$
+&
+\ldots
+&
+$ -0.23^{+  0.01}_{ -0.01}$
+&
+$ -0.45^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$ -0.30^{  0.18}_{ -0.19}$
-&
-$ -0.17^{  0.09}_{ -0.10}$
-&
-$  0$
-&
-$ -0.06^{  0.05}_{ -0.04}$
-&
-$ -0.16^{  0.10}_{ -0.08}$
+$ -0.30^{+  0.18}_{ -0.19}$
+&
+$ -0.17^{+  0.09}_{ -0.10}$
+&
+\ldots
+&
+$ -0.06^{+  0.05}_{ -0.04}$
+&
+$ -0.16^{+  0.10}_{ -0.08}$
 \\
@@
 &
-$ -0.61^{  0.47}_{ -0.18}$
-&
-$ -1.21^{  0.25}_{ -0.77}$
-&
-$ -1.76^{  0.16}_{ -0.20}$
-&
-$ -1.17^{  0.29}_{ -0.20}$
-&
-$  0$
+$ -0.61^{+  0.47}_{ -0.18}$
+&
+$ -1.21^{+  0.25}_{ -0.77}$
+&
+$ -1.76^{+  0.16}_{ -0.20}$
+&
+$ -1.17^{+  0.29}_{ -0.20}$
+&
+\ldots
 \\
@@
 &
-$ 0.059^{ 0.013}_{-0.013}$
-&
-$ 0.031^{ 0.007}_{-0.008}$
-&
-$ 0.017^{ 0.005}_{-0.007}$
-&
-$ 0.012^{ 0.006}_{-0.007}$
-&
-$ 0.039^{ 0.005}_{-0.005}$
+$ 0.059^{+ 0.013}_{-0.013}$
+&
+$ 0.031^{+ 0.007}_{-0.008}$
+&
+$ 0.017^{+ 0.005}_{-0.007}$
+&
+$ 0.012^{+ 0.006}_{-0.007}$
+&
+$ 0.039^{+ 0.005}_{-0.005}$
 \\
@@
 
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}$ are given in the matrix.
+\begin{equation}
+\begin{pmatrix}
+\begin{array}{rrrrrrr}
+1.000 & 0.007 & -0.059 & -0.046 & 0.111 & 0.010 & -0.033 \\
+0.007 & 1.000 & 0.114 & -0.256 & -0.072 & -0.002 & 0.052 \\
+-0.059 & 0.114 & 1.000 & -0.142 & -0.171 & -0.027 & -0.016 \\
+-0.046 & -0.256 & -0.142 & 1.000 & 0.039 & 0.028 & 0.014 \\
+0.111 & -0.072 & -0.171 & 0.039 & 1.000 & 0.056 & 0.028 \\
+0.010 & -0.002 & -0.027 & 0.028 & 0.056 & 1.000 & -0.004 \\
+-0.033 & 0.052 & -0.016 & 0.014 & 0.028 & -0.004 & 1.000
+\end{array}
+\end{pmatrix}.
+\end{equation}
+\color{red}
+The intrinsic parameter $A_{\delta I}$ is uncorrelated with the all the other parameters, including the parameters attributed
+to extrinsic dust.
+
 \section{Summary and Discussion}
@@
 with $R^F_V=2.43$.  This model  does an excellent job in
-describing SN~2014J, a supernova with extreme colors not used in the training.  An extended version
-of the model retains the features of the first model, and gives strong evidence for a new parameter that affects supernova
+describing SN~2014J, a supernova with extreme colors not used in the training.  
+This work represents the first determination of the dust extinction curve outside the Local Group
+derived entirely independently of assumptions about the shape of the extinction curve and/or assumptions about the
+distribution of $A_V$.  An extended version
+of the model retains the features of the first model, and gives the first identification of  a new parameter that affects supernova
 colors in a manner that is distinct from  the expectations from dust.
@@
 \hline
-& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+Parameters & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
 $\alpha_X$
 &
-$0.0044^{0.0010}_{-0.0010}$
-&
-$0.0016^{0.0008}_{-0.0008}$
-&
-$0.0017^{0.0006}_{-0.0007}$
-&
-$0.0015^{0.0005}_{-0.0005}$
-&
-$0.0028^{0.0005}_{-0.0005}$
+$0.0044^{+0.0010}_{-0.0010}$
+&
+$0.0016^{+0.0008}_{-0.0008}$
+&
+$0.0017^{+0.0006}_{-0.0007}$
+&
+$0.0015^{+0.0005}_{-0.0005}$
+&
+$0.0028^{+0.0005}_{-0.0005}$
 \\
@@
 &
-$   1.6^{   0.8}_{  -0.4}$
-&
-$  -0.0^{   0.1}_{  -0.2}$
-&
-$   0$
-&
-$  -0.1^{   0.1}_{  -0.1}$
-&
-$   0.7^{   0.7}_{  -0.3}$
+$   1.6^{+   0.8}_{  -0.4}$
+&
+$  -0.0^{+   0.1}_{  -0.2}$
+&
+/ldots
+&
+$  -0.1^{+   0.1}_{  -0.1}$
+&
+$   0.7^{+   0.7}_{  -0.3}$
 \\
@@
 &
-$ 0.033^{ 0.006}_{-0.006}$
-&
-$ 0.025^{ 0.005}_{-0.005}$
-&
-$ 0.022^{ 0.004}_{-0.004}$
-&
-$ 0.019^{ 0.004}_{-0.003}$
-&
-$ 0.016^{ 0.003}_{-0.003}$
+$ 0.033^{+ 0.006}_{-0.006}$
+&
+$ 0.025^{+ 0.005}_{-0.005}$
+&
+$ 0.022^{+ 0.004}_{-0.004}$
+&
+$ 0.019^{+ 0.004}_{-0.003}$
+&
+$ 0.016^{+ 0.003}_{-0.003}$
 \\
@@
 &
-$  0.52^{  0.13}_{ -0.12}$
-&
-$  0.14^{  0.07}_{ -0.07}$
-&
-$  0$
-&
-$ -0.13^{  0.03}_{ -0.03}$
-&
-$ -0.27^{  0.06}_{ -0.06}$
+$  0.52^{+  0.13}_{ -0.12}$
+&
+$  0.14^{+  0.07}_{ -0.07}$
+&
+\ldots
+&
+$ -0.13^{+  0.03}_{ -0.03}$
+&
+$ -0.27^{+  0.06}_{ -0.06}$
 \\
@@
 &
-$0.0004^{0.0011}_{-0.0011}$
-&
-$0.0005^{0.0010}_{-0.0010}$
-&
-$0.0009^{0.0008}_{-0.0008}$
-&
-$0.0009^{0.0007}_{-0.0007}$
-&
-$0.0001^{0.0006}_{-0.0006}$
+$0.0004^{+0.0011}_{-0.0011}$
+&
+$0.0005^{+0.0010}_{-0.0010}$
+&
+$0.0009^{+0.0008}_{-0.0008}$
+&
+$0.0009^{+0.0007}_{-0.0007}$
+&
+$0.0001^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.34^{  0.58}_{ -1.20}$
-&
-$ -0.36^{  0.35}_{ -0.86}$
-&
-$  0$
-&
-$ -0.10^{  0.20}_{ -0.14}$
-&
-$ -0.74^{  0.35}_{ -0.75}$
+$ -0.34^{+  0.58}_{ -1.20}$
+&
+$ -0.36^{+  0.35}_{ -0.86}$
+&
+\ldots
+&
+$ -0.10^{+  0.20}_{ -0.14}$
+&
+$ -0.74^{+  0.35}_{ -0.75}$
 \\
@@
 &
-$  0.00^{  0.04}_{ -0.04}$
-&
-$ -0.01^{  0.03}_{ -0.03}$
-&
-$ -0.03^{  0.03}_{ -0.03}$
-&
-$ -0.01^{  0.02}_{ -0.02}$
-&
-$ -0.03^{  0.02}_{ -0.02}$
+$  0.00^{+  0.04}_{ -0.04}$
+&
+$ -0.01^{+  0.03}_{ -0.03}$
+&
+$ -0.03^{+  0.03}_{ -0.03}$
+&
+$ -0.01^{+  0.02}_{ -0.02}$
+&
+$ -0.03^{+  0.02}_{ -0.02}$
 \\
@@
 &
-$ -0.76^{  0.78}_{ -1.78}$
-&
-$ -0.50^{  0.47}_{ -1.06}$
-&
-$  0$
-&
-$ -0.46^{  0.21}_{ -0.50}$
-&
-$ -0.16^{  0.45}_{ -0.34}$
-\\
-$\gamma^0_X$
-&
-$ 61.49^{  3.67}_{ -3.71}$
-&
-$ 50.34^{  3.09}_{ -3.07}$
-&
-$ 37.28^{  2.63}_{ -2.59}$
-&
-$ 28.38^{  2.35}_{ -2.28}$
-&
-$ 20.03^{  2.16}_{ -2.16}$
+$ -0.76^{+  0.78}_{ -1.78}$
+&
+$ -0.50^{+  0.47}_{ -1.06}$
+&
+\ldots
+&
+$ -0.46^{+  0.21}_{ -0.50}$
+&
+$ -0.16^{+  0.45}_{ -0.34}$
 \\
@@
 &
-$  0.65^{  0.06}_{ -0.05}$
-&
-$  0.35^{  0.03}_{ -0.03}$
-&
-$  0$
-&
-$ -0.24^{  0.01}_{ -0.01}$
-&
-$ -0.46^{  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-&
-$ -8.99^{  3.28}_{ -3.68}$
-&
-$-11.21^{  2.72}_{ -3.18}$
-&
-$-14.76^{  2.34}_{ -2.63}$
-&
-$-13.88^{  2.00}_{ -2.23}$
-&
-$-12.57^{  1.92}_{ -2.06}$
+$  0.65^{+  0.06}_{ -0.05}$
+&
+$  0.35^{+  0.03}_{ -0.03}$
+&
+\ldots
+&
+$ -0.24^{+  0.01}_{ -0.01}$
+&
+$ -0.46^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$ -0.39^{  0.16}_{ -0.17}$
-&
-$ -0.24^{  0.09}_{ -0.10}$
-&
-$  0$
-&
-$ -0.06^{  0.04}_{ -0.03}$
-&
-$ -0.15^{  0.09}_{ -0.08}$
+$ -0.39^{+  0.16}_{ -0.17}$
+&
+$ -0.24^{+  0.09}_{ -0.10}$
+&
+\ldots
+&
+$ -0.06^{+  0.04}_{ -0.03}$
+&
+$ -0.15^{+  0.09}_{ -0.08}$
 \\
@@
 &
-$  0.04^{  0.48}_{ -0.31}$
-&
-$ -2.16^{  0.36}_{ -0.64}$
-&
-$ -1.94^{  0.23}_{ -0.42}$
-&
-$ -0.63^{  0.56}_{ -0.29}$
-&
-$  0$
+$  0.04^{+  0.48}_{ -0.31}$
+&
+$ -2.16^{+  0.36}_{ -0.64}$
+&
+$ -1.94^{+  0.23}_{ -0.42}$
+&
+$ -0.63^{+  0.56}_{ -0.29}$
+&
+\ldots
 \\
@@
 &
-$ 0.050^{ 0.014}_{-0.012}$
-&
-$ 0.027^{ 0.008}_{-0.008}$
-&
-$ 0.015^{ 0.004}_{-0.005}$
-&
-$ 0.008^{ 0.006}_{-0.005}$
-&
-$ 0.041^{ 0.005}_{-0.004}$
+$ 0.050^{+ 0.014}_{-0.012}$
+&
+$ 0.027^{+ 0.008}_{-0.008}$
+&
+$ 0.015^{+ 0.004}_{-0.005}$
+&
+$ 0.008^{+ 0.006}_{-0.005}$
+&
+$ 0.041^{+ 0.005}_{-0.004}$
 \\

### 2016-10-10 table14.py

@@ -97,7 +97,7 @@ print numpy.std(fit['R']*((fit['rho1'][:,1]-fit['rho1'][:,2]))[:,None])
 
 pars = ['alpha','alpha','beta','beta','eta','eta','zeta','zeta','gamma','gamma','gamma1','gamma1','rho1','rho1','L_sigma']
 pars_n = ['\\alpha_X','{\\alpha_X/\\alpha_V-1}','\\beta_X','{\\beta_X/\\beta_V-1}',\
-  '\\eta_X','{\\eta_X/\\eta_V-1}', '\\zeta_X','{\\zeta_X/\\zeta_V-1}', '\\gamma^0_X', '{\\gamma^0_X/\gamma^0_V-1}', '\\gamma^1_X','{\\gamma^1_X/\\gamma^1_2-1}',\
+  '\\eta_X','{\\eta_X/\\eta_V-1}', '\\zeta_X','{\\zeta_X/\\zeta_V-1}', '\\gamma^0_X', '{\\gamma^0_X/\gamma^0_V-1}', '\\gamma^1_X','{\\gamma^1_X/\\gamma^1_V-1}',\
    '\\delta_X','{{\\delta_X/\\delta_I-1}}','\\sigma_X']
 sigfig = [4,1,3,2,4,2,2,2,2,2,2,2,2,2,3]
 for p,pn, s in zip(pars,pars_n,sigfig):
@@ -112,7 +112,7 @@ for p,pn, s in zip(pars,pars_n,sigfig):
             dum = numpy.percentile(fit[p][:,i]/fit[p][:,2]-1,(50,50-34,50+34)) 
         else :
             dum = numpy.percentile(fit[p][:,i],(50,50-34,50+34))            
-        print  '${1:6.{0}f}^{{{2:6.{0}f}}}_{{{3:6.{0}f}}}$'.format(s,dum[0], dum[2]-dum[0],dum[1]-dum[0] )
+        print  '${1:6.{0}f}^{{+{2:6.{0}f}}}_{{{3:6.{0}f}}}$'.format(s,dum[0], dum[2]-dum[0],dum[1]-dum[0] )
     print '\\\\'
 
 wefwe

### 2016-10-10 table15.py

@@ -97,7 +97,7 @@ print numpy.std(fit['R']*((fit['rho1'][:,1]-fit['rho1'][:,2]))[:,None])
 
 pars = ['alpha','alpha','beta','beta','eta','eta','gamma','gamma','gamma1','gamma1','rho1','rho1','L_sigma']
 pars_n = ['\\alpha_X','{\\alpha_X/\\alpha_V-1}','\\beta_X','{\\beta_X/\\beta_V-1}',\
-  '\\eta_X','{\\eta_X/\\eta_V-1}', '\\gamma^0_X', '{\\gamma^0_X/\gamma^0_V-1}', '\\gamma^1_X','{\\gamma^1_X/\\gamma^1_2-1}',\
+  '\\eta_X','{\\eta_X/\\eta_V-1}', '\\gamma^0_X', '{\\gamma^0_X/\gamma^0_V-1}', '\\gamma^1_X','{\\gamma^1_X/\\gamma^1_V-1}',\
    '\\delta_X','{{\\delta_X/\\delta_I-1}}','\\sigma_X']
 sigfig = [4,1,3,2,4,2,2,2,2,2,2,2,3]
 for p,pn, s in zip(pars,pars_n,sigfig):
@@ -112,7 +112,7 @@ for p,pn, s in zip(pars,pars_n,sigfig):
             dum = numpy.percentile(fit[p][:,i]/fit[p][:,2]-1,(50,50-34,50+34)) 
         else :
             dum = numpy.percentile(fit[p][:,i],(50,50-34,50+34))            
-        print  '${1:6.{0}f}^{{{2:6.{0}f}}}_{{{3:6.{0}f}}}$'.format(s,dum[0], dum[2]-dum[0],dum[1]-dum[0] )
+        print  '${1:6.{0}f}^{{+{2:6.{0}f}}}_{{{3:6.{0}f}}}$'.format(s,dum[0], dum[2]-dum[0],dum[1]-dum[0] )
     print '\\\\'
 
 filts = ['U','B','V','R','I']

### 2016-10-11 forgerard.tex
more Greg comments

@@
 The observed magnitudes are linearly dependent on the
-extrinsic-color parameters $k_0$ and $k_1$.  The observables
+extrinsic-color parameters $k_0$ and $k_1$.  
+The observables
 $U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
 shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
+\textcolor{red}{Unlike the parameters associated with
+the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  $k_0$ and $k_1$ are latent parameters with no
+directly associated observables.}
 The model is written as
@@
 two extrinsic parameters produce
-results consistent
-with two-parameter dust models.  An extension to our model is now added to accommodate
+magnitudes consistent
+with two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
+An extension to our model is now added to explore the possibility of
 a possible additional
-color parameter.
-The new model is written as
+color parameter that could have its origins in supernova astrophysics.
+The extended model is written as
 \begin{equation}
@@
 each supernova has an intrinsic $D$ parameter that is linearly related to
-absolute magnitudes through global coefficients $\delta$. 
+absolute magnitudes through global coefficients $\delta$.  Note that $D$ is a latent supernova characteristic whose existence is inferred from
+its effects on broadband magnitudes.
 Although
@@
 \end{equation}
-The first specifies the definition of zero color.   The latter two confine possible magnitude
+The first constraint specifies the definition of zero color.   The latter two confine possible magnitude
 variations to those that cannot be attributed to 
@@
 are consistent well within 1$\sigma$ uncertainties.  The most significant changes of note are in the standard
-deviations of the residuals in the $V$ and $I$ bands.
-The newly fitted $\delta$ parameters have an almost identical association with the Fitzpatrick dust law, in that now
+deviations of the residuals in the $V$ and $I$ bands, which are now reduced.
+The newly fitted $\gamma$ parameters have an almost identical association with the Fitzpatrick dust law, in that now
 \begin{equation}
@@
 \end{equation}
-where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
+where the residual vectors $\vec{\epsilon}$ are perpendicular to the Fitzpatrick plane and
 contribute similar 2\% and 5\% to the total  length of the vector.
@@
 mag respectively.
-The range of $B-V$ colors is $\sim 8$ times larger for the external contribution; variation in $B-V$ color due to the intrinsic term is dwarfed by the extrinsic process. 
+The range of $B-V$ colors is $\sim 8$ times larger for the external contribution; variation in $B-V$ color due to the intrinsic term is dwarfed by the extrinsic dust
+component. 
 Both distributions are non-Gaussian, that of $E(B-V)$ having a sharp rise in the blue and an extended tail in the red, consistent
-with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.
+with the expectation of dust considering the distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
 
@@
 in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which are bimodal due to the sign-flip degeneracy.  The probability
-of the null result $\delta_X=0$ for all $X$ is $<98\%$, determined through
+of the null result $\delta_X=0$ for all $X$ is $<98\%$, as determined through
 the population of its bin in a 5-dimensional histogram.
@@
 circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
-2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
-more complicated underlying supernova physics.
+2015ApJ...807L..26G} and so may be indicative of underlying supernova physics beyond that captured by $EW_{Ca}$, $EW_{Si}$ and
+$\lambda_{Si}$.
 

### 2016-10-11 forgerard.tex
finish with Greg's comments

@@
 \usepackage{natbib}
+
 \usepackage{lineno}
@@
 \usepackage{color}
+\defcitealias{1999PASP..111...63F}{F99}
 \linenumbers
@@
 broadband photometry and their colors are found to be 
-dependent on the spectral equivalent widths and two independent color parameters, to better than 
+dependent on the spectral equivalent widths and the color parameters, to better than 
 %-----
@@
 confidence.
-The two parameters exhibit the behavior expected from the two-parameter
-\citet{1999PASP..111...63F} dust model with a per-supernova scatter in
+The two color parameters exhibit the behavior expected from the two-parameter
+\citet{1999PASP..111...63F} dust model, yielding a per-supernova scatter in
 total-to-selective extinction, an effective
 %-----
-$R^F_V=2.43^{+0.16}_{-0.17}$
+$R^F_V=2.24 \pm 0.16$
 %------
 for the full sample, and a difference in the average $R^F_V$ between extremely blue and red supernovae .
-The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the Fitzpatrick dust model.
-Extending the model to allow three color parameters gives almost identical results for
-the two parameters, plus a detection of a third parameter at  $>98$\% confidence.
+The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
+Extending the model to three color parameters gives almost identical results for
+the two parameters
+%-----
+$R^F_V=2.23 \pm 0.16$,
+%------
+plus a detection of a third parameter at  $>98$\% confidence; this new parameter is responsible for supernova color diversity
+beyond those tracked by the spectral features and dust.
 \color{black}
@@
  \textcolor{red}{In SALT2 the light curve shapes are described by a multiplicative scaling (``stretch'')  of the time evolution,
- whereas MLCS2k2 varies shape with additive corrections to magnitudes.}
+ whereas MLCS2k2 varies shapes through additive corrections to magnitudes.}
  The physical cause of the color diversity is interpreted differently by the two sets of authors: 
@@
 attribute changes in color
-\textcolor{red}{partially to intrinsic variations connected to light-curve shape, and partially}
+\textcolor{red}{partially to intrinsic variations linked to light-curve shape, and partially}
 to the attenuation of light from host-galaxy dust.
@@
 \textcolor{red}{
-\citet{2011MNRAS.413.3075M} argue that viewing angle is an important determinant in controlling supernova color, which is
-traced by wavelength shifts in nebular emission lines; such correlations are also seen by \citet{2011A&A...534L..15C}.
+\citet{2011MNRAS.413.3075M} show evidence that supernova asymmetry and viewing angle,
+traced by wavelength shifts in nebular emission lines, is an important determinant in controlling supernova color; such correlations are also seen by \citet{2011A&A...534L..15C}.
 }
@@
 Another approach to probe color diversity is through multiple colors (at least 3 bands)
-of a single supernova.  Colors ratios are sensitive to processes of the responsible physics.   For example,
+of individual supernovae.  Color ratios are sensitive to processes of the responsible physics.   For example,
 relative dust absorption varies as a function of wavelength depending on grain size and shape,
@@
 \textcolor{red}{
-Such studies measuring $R_V$ are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
+Such measurements of $R_V$ are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
 \citep[e.g.][]{2011ApJ...731..120M}.}
@@
 Hierarchical modeling has recently opened
-the study of intrinsic supernova color based on SN~Ia Hubble diagrams; latent parameters that are not directly tied to observables,
-such as multiple parameters that simultaneously influence color, can be determined.
-\citet{2016arXiv160904470M} take the approach of modeling the distribution of their parameters, to find that the distribution of
-observed supernova magnitudes is better explained by a combination of intrinsic color dispersion and
-$R_B=3.7$ dust, over dust with no color dispersion.
-They draw these conclusions by using only the SALT2 fit $X_1$ parameter as the summary statistic that describes color.
+the study of intrinsic supernova color based on SN~Ia Hubble diagrams. Latent parameters that are not directly tied to observables,
+such as multiple parameters that simultaneously influence color, can be included in the model.
+\citet{2016arXiv160904470M} take the approach of modeling the distribution of their parameters, to find that
+scatter in the Hubble diagram is better explained by a combination of intrinsic color dispersion and
+$R_B=3.7$ dust, rather than by dust with no color dispersion.
+They draw these conclusions by using only the SALT2 $x_1$ parameter as the summary statistic that describes color.
 }
@@
 properties and two  attributed} to
-extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.  \textcolor{red}{A
-first analysis omitting the intrinsic parameter is presented in
-\S\ref{model:sec}, where we show that the properties of the two extrinsic parameters
-are consistent with the expectations of Milky Way-parameterized dust, and do an excellent job of fitting the data of the out-of-sample
-supernova SN2014J that has been previously identified as having extreme total-to-selective extinction.
-In \S\ref{model2:sec} we add to analysis the third intrinsic parameter, and find strong evidence for its influence on observed magnitudes.
+extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.  \textcolor{red}{
+In \S\ref{model:sec} we present a
+first analysis with two extrinsic parameters and omitting the intrinsic parameter.  The properties of the two extrinsic parameters
+are consistent with the expectations of parameterized dust designed for the Milky Way, and do an excellent job of fitting the data of the out-of-sample
+supernova SN2014J that has an extreme total-to-selective extinction.
+In \S\ref{model2:sec} we add to analysis the intrinsic parameter, and find strong evidence for its influence on observed magnitudes.
 We summarize our findings, and relate our results with light-curve shape, SiII velocity, and the ``mass step'' in SN~Ia Hubble
@@
 \citet{2006ApJ...650..510A} and is updated in \citet{2010ApJ...713.1073S}. 
-The flux calibration is presented in \citet{2013A&A...549A...8B}.  A detailed
+\textcolor{red}{The flux calibration is presented in \citet{2013A&A...549A...8B}. }
+A detailed
 description of host-galaxy subtraction is given in \citet{2011MNRAS.418..258B}.
@@
 $I$ $[6968.29-8400.00]$\AA.
-For each supernova, the magnitudes at peak brightness are regressed from data within 5-days of peak brightness
+For each supernova, the data magnitudes within 5-days of peak brightness are used to regress the peak magnitude
 using single-band SALT2 fits.
@@
 Equivalent widths and the
-\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from maximum.}
+\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from $B$-band maximum;
+the average is used  in cases where there are multiple spectral measurements within that time window.}
 
 Our analysis sample is comprised by the
-166
+168
 supernovae that have the data coverage to 
 give photometric and spectroscopic statistics described above.
-The data are given in Table~\ref{data:tab}.
+The data are given in Table~\ref{data:tab} \textcolor{red}{[TABLE CAN GO IF THERE IS A NICO PAPER]}.
 The peak magnitude uncertainties do have covariance, which is accounted
@@
 \startlongtable
-\begin{deluxetable}{ccccccccc}
+\begin{deluxetable}{crrrrrrrr}
 \tabletypesize{\tiny}
-\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data \textcolor{red}{TABLE MAY GO IF THERE IS A NICO PAPER}
+\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data
 \label{data:tab}}
@@
 %of intrinsic variation is accommodated.
-These intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
-\textcolor{red}{The intrinsic magnitudes are then
+These intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion,
+\textcolor{red}{which in this section is not yet associated with a parameter. The intrinsic magnitudes are then
 modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
@@
 \textcolor{red}{Unlike the parameters associated with
-the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  $k_0$ and $k_1$ are latent parameters with no
-directly associated observables.}
+the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
+parameters $k_0$ and $k_1$ are not directly associated
+with observables but are rather drawn from the set of peak magnitudes.}
 The model is written as
@@
 relate intrinsic magnitudes with the spectral-feature parameters.
-(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
+(In this article we freely interchange the parameter indices with  $01234$ and $UBVRI$.)
 The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
@@
 \color{red}
-each of the vectors $k_0+1/N$ and $k_1+1/N$ are simplexes, where $N$ is the number of objects in our sample: these
+each of the vectors $k_0+1/N$ and $k_1+1/N$ are simplexes (all elements are $\ge 0$ and sum to one),
+where $N$ is the number of objects in our sample: these
 conditions break the 
 degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$
-up to the $\pm$ sign.
+up to a $\pm$ sign.
 Furthermore we impose
@@
 The first two conditions specify the definition of zero color relative to which the color excess is measured:
-in a linear model this value is arbitrary.    The latter two exclude degenerate posterior space
+\textcolor{red}{in a linear model this value is arbitrary.} 
+The latter two exclude degenerate posterior space
 associated
-with  simultaneous sign flips of
+with the $\pm$ sign, i.e.\ simultaneous sign flips of
 $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
@@
  $0.1$ and scale $0.1$ mag restricted to positive values.
- \textcolor{red}{This prior for a covariance matrix is recommended by STAN.}
- (We find that imposing a stricter assumption of a
- diagonal covariance matrix, with no reference to a correlation matrix with LKJ prior, yields the same parameter distributions within
- uncertainty).
+ \textcolor{red}{This covariance matrix prior is recommended by STAN, the Monte Carlo we use to evaluate the model.}
+ We find that imposing a stricter assumption of a
+ diagonal covariance matrix, with no reference to a correlation matrix with LKJ prior, produces little change in the posteriors of
+ the other parameters.
 
@@
 The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo as implemented in
-STAN \citep{stan}. STAN provides output statistics to assess
+STAN \citep{stan}.  \textcolor{red}{We run four chains, each with 10000 iterations of which
+half are used for warmup.}
+STAN provides output statistics to assess
 the convergence of the output Markov chains.
@@
 by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
-$N_{eff}$ is an estimate of the number of independent draws.  \textcolor{red}{We run four chains, each with 10000 iterations of which
-half are used for warmup.}
-The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
+$N_{eff}$ is an estimate of the number of independent draws. The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.}
@@
 
-The differences between observed and model-predicted supernova colors are shown in Figure~\ref{residual:fig}:
-no systematic trends are apparent.
-The scatters in the plots, i.e.\ the residual intrinsic color dispersions from our model, are described
-later when we discuss the inferred residual covariance matrix $C_c$.
+The model-predicted versus observed supernova colors are shown in Figure~\ref{residual:fig}.
+The points lie along a line with slope equal to one, and show no evidence of a catastrophic fit nor of extreme
+outlying data.
+
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
    \includegraphics[width=5.5in]{output11/residual.pdf} 
-            \caption{\textcolor{red}{Differences between observed and  model-predicted supernova colors  as a function
-            of predicted colors.  For reference a dotted line is plotted at zero difference.}
+            \caption{\textcolor{red}{Predicted versus observed colors.  Overplotted is a line with slope equal to one.}
             \label{residual:fig}}
@@
 As the $\gamma$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_V$,
-their results are also shown in terms of $\gamma^i_X/\gamma^i_V-1$.
+their results are shown in terms of $\gamma^i_X/\gamma^i_V-1$.
 \color{black}
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model \label{global:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model in \S\ref{model:sec}.\label{global:tab}}
 \end{table}
@@
 We find significant non-zero values for $\alpha$ and $\beta$, indicating that $EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
-magnitudes.}
+peak magnitudes.}
 This validates our hypothesis that spectral indicators
@@
    \centering
-   \includegraphics[width=3.2in]{output11/Delta_hist.pdf} 
-   \caption{Ideogram for the grey offset $\Delta$, normalized to have area equal 1.
+   \includegraphics[width=5.5in]{output11/Delta_hist.pdf} 
+   \caption{Ideogram for the grey offset $\Delta$.  This and other ideograms plotted in this article are normalized to have unit area.
    \label{hist:fig}}
@@
 \begin{equation}
-C_c=
+C_c(U,B,V,R,I)=
 \begin{pmatrix}
@@
  \begin{equation}
+ \sigma(U-V, B-V, V-R, V-I)=
  \begin{pmatrix}
@@
  \begin{equation}
+ Cor(U-V, B-V, V-R, V-I)=
 \begin{pmatrix}
@@
  \end{equation}
-Where quoted, corresponding color variances are smaller than those derived by \citet{2003A&A...404..901N, 2007ApJ...659..122J}
-
+ \textcolor{red}{
+These color variances are smaller than those derived by \citet{2003A&A...404..901N, 2007ApJ...659..122J}, for cases where direct comparison can be made.
+} 
 % \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
-\begin{equation}
+\begin{multline}
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
 \begin{pmatrix}
 \begin{array}{rrrrrr}
-1.000 & 0.001 & -0.059 & -0.045 & 0.105 & 0.007 \cr
-0.001 & 1.000 & 0.115 & -0.252 & -0.066 & -0.003 \cr
--0.059 & 0.115 & 1.000 & -0.140 & -0.163 & -0.024 \cr
--0.045 & -0.252 & -0.140 & 1.000 & 0.040 & 0.027 \cr
-0.105 & -0.066 & -0.163 & 0.040 & 1.000 & 0.055 \cr
-0.007 & -0.003 & -0.024 & 0.027 & 0.055 & 1.000
+1.00 & 0.00 & -0.06 & -0.05 & 0.11 & 0.01 \\
+0.00 & 1.00 & 0.11 & -0.25 & -0.07 & -0.00 \\
+-0.06 & 0.11 & 1.00 & -0.14 & -0.16 & -0.03 \\
+-0.05 & -0.25 & -0.14 & 1.00 & 0.04 & 0.03 \\
+0.11 & -0.07 & -0.16 & 0.04 & 1.00 & 0.06 \\
+0.01 & -0.00 & -0.03 & 0.03 & 0.06 & 1.00
 \end{array}
 \end{pmatrix}.
-\end{equation}
+\end{multline}
 \color{red}
-We find weak correlations between our color-excess parameters and the input features, the strongest being $-0.163$ between
+We find weak correlations between our color-excess parameters and the input features, the strongest being $-0.16$ between
 $E_\gamma(B-V)$ and $EW_{Si}$.
@@
 
-The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that the affect on magnitude
+\color{red}
+The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its affect on magnitude
 is
-$2.5 \log{20/850} \sim 0.03$ mag.  
+$2.5 \log{(20/850)} \sim 0.03$ mag.  
 The implied span in $B$ magnitude based on $\beta_1$ is 0.54~mag.  Therefore $\beta_1$ cannot wholly be attributed to the flux deficit
@@
 Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
-701~\AA, so that the affect on magnitude
+701~\AA, so that its affect on magnitude
 is
-$2.5 \log{50/701} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_0$ cannot be completely due to the line iteslf.
+$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_0$ cannot be completely due to the line itself.
+\color{black}
 
@@
    \centering
-   \includegraphics[width=2.5in]{output11/avebv.pdf}
-   \includegraphics[width=2.5in]{output11/rv.pdf}
+   \includegraphics[width=2.8in]{output11/avebv.pdf}
+   \includegraphics[width=2.8in]{output11/rv.pdf}
    \caption{\textcolor{red}{Left: $A_V$ versus $E(B-V)$ and Right: $R_V=A_V/(E(B-V)-zeropoint$\
@@
 \end{equation}
-The \citet{1999PASP..111...63F} model is also approximately described by a linear model in the ranges of $R_V$ and wavelength under consideration:
-the results to follow vary at the percent level when making this approximation.
+The \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F}) model is approximately described by a linear model with
+the above form, with
+$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ for the case of
+$R^F_V=2.5$ and the updated
+\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak.  This linear approximation
+is good in the ranges of $R^F_V$ and wavelength under consideration, in that these vectors vary by $<5$\% over the range $1.9<R^F_V<3.1$.
+
 Our model can be expressed as
@@
 \end{equation}
-
-For a linear 2-parameter model, possible magnitudes are confined to a plane in the 5-dimensional UBVRI magnitude space.
-It turns out that the planes for both our and the Fitzpatrick dust model are nearly parallel, in that
+Our best-fit values for the $\gamma$ coefficients (from Table~\ref{global:tab}) can expressed in terms of the $a(X)$ and $b(X)$ vectors:
 \begin{equation}
@@
 \begin{array}{rr}
-1.15 & 2.82 \\
-0.75 & -5.43
+1.22 & 2.75 \\
+0.81 & -5.50
 \end{array}
@@
 \end{pmatrix}+
-\vec{\epsilon},
+\begin{pmatrix}
+\vec{\epsilon}_a \\
+\vec{\epsilon}_b
+\end{pmatrix},
 \end{equation}
-where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
-contribute  2\% and 5\% to the total  length of the vector.
+where the two residual $\vec{\epsilon}$ vectors are perpendicular to both $a(X)$ and $b(X)$ and
+contribute  3\% and 4\% respectively to the total  length of the $\gamma$ vectors.
+This result indicates that
+the allowed variation of $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are almost identical.
 
 The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
-are projected onto the Fitzpatrick values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
-The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.43^{+0.16}_{-0.17}$.  
+are projected onto the  \citetalias{1999PASP..111...63F} values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
+The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.24 \pm 0.16$.  
 The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
@@
     \caption{\textcolor{red}{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
-onto the Fitzpatrick plane.  Right: $R^F_V$ for each supernova.}
+onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
+covariance between the parameters. Right: $R^F_V$ for each supernova.}
    \label{avebv_synth:fig}}
@@
 
-The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
-parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$, lead us to conclude that 
-$\{k_0, k_1\}$, describe, for the most part that behaves like the $\{ E(B-V), R_V\}$
+The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our the individual supernova
+parameters translate to  \citetalias{1999PASP..111...63F} parameters consistent with a distribution expected for a narrow range of $R^F_V$, lead us to conclude that 
+$\{k_0, k_1\}$, describe, for the most part the $\{ E(B-V), R_V\}$ parameters used
 in standard models of Milky Way dust.
@@
    \centering
-   \includegraphics[width=4.5in]{output11/sn2014j.pdf} 
+   \includegraphics[width=5.5in]{output11/sn2014j.pdf} 
    \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and from  \citet{2014ApJ...788L..21A}.
@@
 
-\section{Supernova Model II: Two Extrinsic Parameter, One Intrinsic Parameter}
+\section{Supernova Model II: Two Extrinsic Parameters, One Intrinsic Parameter}
 \label{model2:sec}
-In \S\ref{model:sec} we show that the Nearby Supernova Factory data analyzed with an agnostic model with
+In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
 two extrinsic parameters produce
@@
 each supernova has an intrinsic $D$ parameter that is linearly related to
-absolute magnitudes through global coefficients $\delta$.  Note that $D$ is a latent supernova characteristic whose existence is inferred from
+absolute magnitudes through global coefficients $\delta$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
 its effects on broadband magnitudes.
 Although
-this term is introduced through absolute rather than observed magnitudes,
+this term is introduced as part of the  absolute rather than observed magnitudes,
 practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
@@
 deviations of the residuals in the $V$ and $I$ bands, which are now reduced.
-The newly fitted $\gamma$ parameters have an almost identical association with the Fitzpatrick dust law, in that now
+The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust law, in that now
 \begin{equation}
@@
 \begin{array}{rr}
-1.16 & 2.82 \\
-0.74 & -5.43
+1.22 & 2.75 \\
+0.80 & -5.51
 \end{array}
@@
 \end{pmatrix}+
-\vec{\epsilon},
+\begin{pmatrix}
+\vec{\epsilon}_a \\
+\vec{\epsilon}_b
+\end{pmatrix},
 \end{equation}
-where the residual vectors $\vec{\epsilon}$ are perpendicular to the Fitzpatrick plane and
-contribute similar 2\% and 5\% to the total  length of the vector.
+where the residual vectors $\vec{\epsilon}$ are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
+contribute similar 3\% and 4\% to the total  length of the vector.
+The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.
 
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters of the Intrinsic-Extrinsic Model\label{global2:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters of the Extrinsic--Intrinsic Model in \S\ref{model2:sec}.\label{global2:tab}}
 \end{table}
@@
 Both distributions are non-Gaussian, that of $E(B-V)$ having a sharp rise in the blue and an extended tail in the red, consistent
-with the expectation of dust considering the distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
+with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
 
@@
 \end{figure}
-The significance of the $\delta$ parameters is shown pictorially
-in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which are bimodal due to the sign-flip degeneracy.  The probability
+The significance of the $\delta$ parameters is shown pictorially.
+Figure~\ref{deltacorner:fig} shows the $\delta$ posteriors, which are bimodal due to the $\pm$ sign degeneracy.  The probability
 of the null result $\delta_X=0$ for all $X$ is $<98\%$, as determined through
 the population of its bin in a 5-dimensional histogram.
-The right plot shows values of $\delta_X/\delta_I-1$ that  have significant non-zero values.   An interesting feature
+Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values.   An interesting feature
 is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
@@
    \centering
-   \includegraphics[height=2.5in]{output15/delta_corner.pdf}
-      \includegraphics[height=2.5in]{output15/deltaratio.pdf}
-   \caption{Significance of the non-zero values of $\delta$.  Left: Posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
-   Right: $\delta_X/\delta_I-1$, which is insensitive to the sign-flip degeneracy.
+   \includegraphics[width=4.5in]{output15/delta_corner.pdf}
+   \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
    \label{deltacorner:fig}}
@@
 
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.5in]{output15/deltaratio.pdf}
+   \caption{Significance of the non-zero values of $\delta$ seen through $\delta_X/\delta_I-1$, which is insensitive to the $\pm$ sign degeneracy.
+   \label{deltaratio:fig}}
+\end{figure}
+
 The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}$ are given in the matrix.
-\begin{equation}
+\begin{multline}
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta I}) =\\
 \begin{pmatrix}
 \begin{array}{rrrrrrr}
-1.000 & 0.007 & -0.059 & -0.046 & 0.111 & 0.010 & -0.033 \\
-0.007 & 1.000 & 0.114 & -0.256 & -0.072 & -0.002 & 0.052 \\
--0.059 & 0.114 & 1.000 & -0.142 & -0.171 & -0.027 & -0.016 \\
--0.046 & -0.256 & -0.142 & 1.000 & 0.039 & 0.028 & 0.014 \\
-0.111 & -0.072 & -0.171 & 0.039 & 1.000 & 0.056 & 0.028 \\
-0.010 & -0.002 & -0.027 & 0.028 & 0.056 & 1.000 & -0.004 \\
--0.033 & 0.052 & -0.016 & 0.014 & 0.028 & -0.004 & 1.000
+1.00 & 0.01 & -0.06 & -0.05 & 0.11 & 0.01 & -0.03 \\
+0.01 & 1.00 & 0.11 & -0.26 & -0.07 & -0.00 & 0.05 \\
+-0.06 & 0.11 & 1.00 & -0.14 & -0.17 & -0.03 & -0.02 \\
+-0.05 & -0.26 & -0.14 & 1.00 & 0.04 & 0.03 & 0.01 \\
+0.11 & -0.07 & -0.17 & 0.04 & 1.00 & 0.06 & 0.03 \\
+0.01 & -0.00 & -0.03 & 0.03 & 0.06 & 1.00 & -0.00 \\
+-0.03 & 0.05 & -0.02 & 0.01 & 0.03 & -0.00 & 1.00
 \end{array}
 \end{pmatrix}.
-\end{equation}
+\end{multline}
 \color{red}
-The intrinsic parameter $A_{\delta I}$ is uncorrelated with the all the other parameters, including the parameters attributed
+The intrinsic parameter $A_{\delta I}$ has correlations $<0.05$ with respect to all the other parameters, including those attributed
 to extrinsic dust.
@@
 \label{discussion:sec}
+\subsection{Summary}
 To summarize, we model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
@@
 affect supernova magnitudes and colors.  The external color parameters are consistent with \citet{1999PASP..111...63F} dust
-with $R^F_V=2.43$.  This model  does an excellent job in
-describing SN~2014J, a supernova with extreme colors not used in the training.  
+with $R^F_V=2.24 \pm 0.16$.  This model  does an excellent job in
+describing SN~2014J, a supernova with extreme colors that was not used in the training.  
 This work represents the first determination of the dust extinction curve outside the Local Group
@@
 of the model retains the features of the first model, and gives the first identification of  a new parameter that affects supernova
-colors in a manner that is distinct from  the expectations from dust.
-
+colors in a manner that is distinct from  the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
+
+\subsection{Light Curve Shape}
 Our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
 We now examine this in more depth using the intrinsic--extrinsic model of \S\ref{model2:sec}.
-The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
+The correlation between $EW_{Si}$ and the SALT2 $x_1$ light-curve shape parameter is verified
 for our sample.
-On the other hand, there is no such correlation seen between $A_{\delta I} = \delta_I D$ and $X_1$, as shown in Figure~\ref{x1:fig}. 
-Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
-\citep{2010A&A...523A...7G}, showing that our model exhibits no loss in its ability to standardize
-magnitudes although $X_1$ is neglected.
+On the other hand, there is no such correlation seen between $A_{\delta I} = \delta_I D$ and $x_1$, as shown in Figure~\ref{x1:fig}. 
+Our magnitude residuals, $\sigma_X$, are comparable to the residuals after SALT2 training
+\citep{2010A&A...523A...7G}, showing that our model exhibits little loss in its ability to standardize
+magnitudes although $x_1$ is neglected.
 There is no apparent correlation
-between $X_1$ and the residuals between observed and model-predicted colors, as seen in
+between $x_1$ and the residuals between observed and model-predicted colors, as seen in
 Figure~\ref{x1res:fig}. 
-We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$ to the 
+We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta x_1$ to the 
 intrinsic magnitude; the credible intervals
@@
    \includegraphics[width=2.8in]{output15/x1D.pdf}
-    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $A_{\delta I}  = \delta_I D$.}
+    \caption{\textcolor{red}{Left: SALT2 $x_1$ versus $EW_{Si}$.  Right: $x_1$ versus $A_{\delta I}  = \delta_I D$.}
    \label{x1:fig}}
@@
    \centering
-   \includegraphics[width=5in]{output15/residualx1.pdf}
+   \includegraphics[width=5.5in]{output15/residualx1.pdf}
     \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
-            of the SALT2 light-curve shape parameter $X_1$.  For reference a dotted line is plotted at zero difference.}
+            of the SALT2 light-curve shape parameter $x_1$.  For reference a dotted line is plotted at zero difference.}
    \label{x1res:fig}}
@@
 &
-/ldots
+\ldots
 &
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters including $X_1$ \label{globalx1:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters including the light-curve shape parameter $x_1$ \label{globalx1:tab}}
 \end{table}
@@
 
+\subsection{SiII Line Velocity}
+
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
 \citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
-\textcolor{red}{The $\lambda_{Si} = (1+v_{Si}/c) \lambda_{Si,0} $ treated in this article varies linearly with $v_{Si}$.}
+\textcolor{red}{The $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.}
 The values of $\eta$ in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
@@
 non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, 
-\textcolor{red}{but the equivalent-width corrections give higher likelihood as they give lower residual dispersions $C_c$},
-and  anticipate that in the previous analysis the equivalent widths of CaII and 
-SiII would also have shown correlations with color.
-
+\textcolor{red}{but this correlation
+is absorbed into the equivalent-width corrections, which give higher likelihood as they give lower residual dispersions $C_c$}.
+
+\subsection{Host-Galaxy Mass}
 \color{red}
@@
 This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
-\citet{2016arXiv160904470M} find that with intrinsic color scatter, the null mass-step effect falls on the 95\%-level of their posterior.
-To explore this possibility we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
-\citep{2016rigault}, and their ideograms for two samples separated by a host mass of  $10 \log{(M/M_\sun)}$
+\citet{2016arXiv160904470M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
+To explore whether the Hubble residual may be due to unaccounted color,
+we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
+\citep{2016rigault}, and their ideograms for two samples divided by a host mass of  $\log{(M/M_\sun)}=10$
 used by  \citet{2013ApJ...770..108C}.
 Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta I}$, the difference is
-not significant; we calculate the average $A_{\delta I}$
-for low- (high)-mass hosts to be
-$   0.0042 \pm    0.0014$
-($   0.0031 \pm    0.0017$). 
+not significant; we calculate  average $\langle A_{\delta I} \rangle=   0.0042 \pm    0.0014$,
+$\langle A_{\delta I} \rangle=   0.0031 \pm    0.0017 $ for low- and high-mass hosts respectively. 
 Using the SNfactory sample,
 \citet{2013A&A...560A..66R} find that step in Hubble residuals is better related to local star formation rate, rather than host mass.
-The connection between our intrinsic parameter and local star formation and other host properties is deferred to
+A deeper exploration of the possible connection between our intrinsic parameter and local star formation and other host properties is deferred to
 \citet{2016rigault}.
@@
       are assigned a mass of 5.  Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
-      less than and greater than  $10 \log{(M/M_\sun)}$.
+      less than and greater than  $\log{(M/M_\sun)}=10$.
 Right: Ideograms of  $A_{\delta I}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
@@
 
+\subsection{Physical Motivation}
+
 We find an intrinsic supernova parameter that does not have a monotonic influence on supernova magnitudes as a function
-of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes.  Line opacities
-that operate over broad bands are the most obvious candidate for producing this behavior.
+of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes
+for this component.  Absorption and re-emission of light
+over broad bands are the most obvious candidate for producing this behavior.
 \citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
@@
 We conjecture that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth
-of the reionization front with respect to the core of the ejecta, yielding the wavelength-dependent color behavior
+of the reionization front with respect to the core of the ejecta at peak, yielding the wavelength-dependent color behavior
 detected in this analysis.
 
+\subsection{Improving SNe~Ia as Standard Candles}
 The model and results presented here
@@
 and Michael Betancourt specifically for his helpful guidance.  We thank Danny Goldstein for useful discussions.
-This work was supported by the Director, Office of Science, Office of High Energy Physics, 
-of the U.S.\ Department of Energy under Contract No. DE-AC02-05CH11231.
+We thank Dan Birchall for observing assistance, the technical and
+scientific staffs of the Palomar Observatory, the High Performance
+Wireless Radio Network (HPWREN), and the University of Hawaii 2.2~m
+telescope.  We recognize the significant cultural role of Mauna Kea
+within the indigenous Hawaiian community, and we appreciate the
+opportunity to conduct observations from this revered site.  This
+work was supported in part by the Director, Office of Science,
+Office of High Energy Physics, of the U.S. Department of Energy
+under Contract No. DE-AC02- 05CH11231.  Support in France was
+provided by CNRS/IN2P3, CNRS/INSU, and PNC; LPNHE acknowledges
+support from LABEX ILP, supported by French state funds managed by
+the ANR within the Investissements d'Avenir programme under reference
+ANR-11-IDEX-0004-02.  NC is grateful to the LABEX Lyon Institute
+of Origins (ANR-10-LABX-0066) of the Universit\'e de Lyon for its
+financial support within the program ``Investissements d'Avenir''
+(ANR-11-IDEX-0007) of the French government operated by the National
+Research Agency (ANR).  Support in Germany was provided by the DFG
+through TRR33 ``The Dark Universe;'' and in China from Tsinghua
+University 985 grant and NSFC grant No~11173017.  Some results were
+obtained using resources and support from the National Energy
+Research Scientific Computing Center, supported by the Director,
+Office of Science, Office of Advanced Scientific Computing Research,
+of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231.
+HPWREN is funded by National Science Foundation Grant Number
+ANI-0087344, and the University of California, San Diego.
 

### 2016-10-11 fitz11.py

@@ -17,7 +17,7 @@ f.close()
 
 # Partial derivatives with respect to av and ebv
 av=0.1
-ebv=0.1/2.24
+ebv=0.1/2.5
 A1= f99_band.A_X(r_v=av/ebv, ebv=ebv)
 
 A2= f99_band.A_X(r_v=(av+0.01)/ebv, ebv=ebv)
@@ -26,6 +26,34 @@ dAdAv = (A2 - A1)/0.01
 A3= f99_band.A_X(r_v=av/(ebv+0.001), ebv=ebv+0.001)
 dAdebv = (A3 - A1)/0.001
 
+print '{0[0]:6.2f}, {0[1]:6.2f}, {0[2]:6.2f}, {0[3]:6.2f}, {0[4]:6.2f}'.format(dAdAv)
+print '{0[0]:6.2f}, {0[1]:6.2f}, {0[2]:6.2f}, {0[3]:6.2f}, {0[4]:6.2f}'.format(dAdebv)
+
+# av=0.1
+# ebv=0.1/3.1
+# A1= f99_band.A_X(r_v=av/ebv, ebv=ebv)
+
+# A2= f99_band.A_X(r_v=(av+0.01)/ebv, ebv=ebv)
+# dAdAv = (A2 - A1)/0.01
+
+# A3= f99_band.A_X(r_v=av/(ebv+0.001), ebv=ebv+0.001)
+# dAdebv = (A3 - A1)/0.001
+
+# print '{0[0]:6.2f}, {0[1]:6.2f}, {0[2]:6.2f}, {0[3]:6.2f}, {0[4]:6.2f}'.format(dAdAv)
+# print '{0[0]:6.2f}, {0[1]:6.2f}, {0[2]:6.2f}, {0[3]:6.2f}, {0[4]:6.2f}'.format(dAdebv)
+
+# av=0.1
+# ebv=0.1/1.9
+# A1= f99_band.A_X(r_v=av/ebv, ebv=ebv)
+
+# A2= f99_band.A_X(r_v=(av+0.01)/ebv, ebv=ebv)
+# dAdAv = (A2 - A1)/0.01
+
+# A3= f99_band.A_X(r_v=av/(ebv+0.001), ebv=ebv+0.001)
+# dAdebv = (A3 - A1)/0.001
+
+# print '{0[0]:6.2f}, {0[1]:6.2f}, {0[2]:6.2f}, {0[3]:6.2f}, {0[4]:6.2f}'.format(dAdAv)
[…]

### 2016-10-19 apj.tex
submit version

--- 2016-10-11 forgerard.tex
@@
 \geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
-%\geometry{landscape}                		% Activate for rotated page geometry
-%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
 \usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
-								% TeX will automatically convert eps --> pdf in pdflatex		
-%\usepackage{amssymb}
 \usepackage{amsmath}
 \usepackage{natbib}
-
 \usepackage{lineno}
-
 \usepackage{color}
@@
     1 Cyclotron Road, Berkeley, CA, 94720}
-
-\author{     G.~Smadja}
-\affiliation{    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
-    CNRS/IN2P3, Institut de Physique Nucl\'eaire de Lyon}
 
@@
 \begin{abstract}
-\color{red}
 An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
@@
 plus a detection of a third parameter at  $>98$\% confidence; this new parameter is responsible for supernova color diversity
-beyond those tracked by the spectral features and dust.
-\color{black}
+beyond those tracked by the spectral features and two-parameter dust models.
 \end{abstract}
@@
  color.
- \textcolor{red}{In SALT2 the light curve shapes are described by a multiplicative scaling (``stretch'')  of the time evolution,
- whereas MLCS2k2 varies shapes through additive corrections to magnitudes.}
+In SALT2 the light curve shapes are described by a multiplicative scaling (``stretch'')  of the time evolution,
+ whereas MLCS2k2 varies shapes through additive corrections to magnitudes.
 The physical cause of the color diversity is interpreted differently by the two sets of authors: 
@@
 attribute changes in color
-\textcolor{red}{partially to intrinsic variations linked to light-curve shape, and partially}
+partially to intrinsic variations linked to light-curve shape, and partially
 to the attenuation of light from host-galaxy dust.
@@
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two subpopulations distinguished
-by Si velocity with differing $B_{max}-V_{max}$; this color correlation, \textcolor{red}{ in addition to one with $B-R$, is confirmed by
+by Si velocity with differing $B_{max}-V_{max}$; this color correlation, in addition to one with $B-R$, is confirmed by
 \citet{2014ApJ...797...75M}.
-}
 \citet{2015MNRAS.451.1973S}
 find that high-velocity SiII$\lambda$6355 is found in objects that have red ultraviolet/optical colors near maximum brightness.
-\textcolor{red}{
 \citet{2011MNRAS.413.3075M} show evidence that supernova asymmetry and viewing angle,
 traced by wavelength shifts in nebular emission lines, is an important determinant in controlling supernova color; such correlations are also seen by \citet{2011A&A...534L..15C}.
-}
-
-\textcolor{red}{
+
 Another approach to probe color diversity is through multiple colors (at least 3 bands)
@@
 independent (to first order) of the amount of dust along the line of sight.
-\citet{2013ApJ...779...23M} find diversity in SNe~Ia UV emission, which they use to distinguish subclasses based on UV-optical colors.}
-\textcolor{red}{
+\citet{2013ApJ...779...23M} find diversity in SNe~Ia UV emission, which they use to distinguish subclasses based on UV-optical colors.
 Such measurements of $R_V$ are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
-\citep[e.g.][]{2011ApJ...731..120M}.}
+\citep[e.g.][]{2011ApJ...731..120M}.
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} find wide
@@
 
-\textcolor{red}
-{
 Hierarchical modeling has recently opened
@@
 They draw these conclusions by using only the SALT2 $x_1$ parameter as the summary statistic that describes color.
-}
 
@@
 provides measurements of an array of supernova spectral features while also providing synthetic broadband photometry
-spanning near-UV to near-IR SN-frame wavelengths.  \textcolor{red}{SNfactory specifically targeted objects
-early in their temporal evolution, so} that well over a hundred of these supernovae have  coverage over
+spanning near-UV to near-IR SN-frame wavelengths.  SNfactory specifically targeted objects
+early in their temporal evolution, so that well over a hundred of these supernovae have  coverage over
 peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia colors and spectral features together.
@@
 In this article we use the idea that spectral indicators carry information on intrinsic supernova colors at peak magnitude.
-We allow for \textcolor{red}{three independent color parameters, one attributed to intrinsic supernova
-properties and two  attributed} to
-extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.  \textcolor{red}{
+We allow for three independent color parameters, one attributed to intrinsic supernova
+properties and two  attributed to
+extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.
 In \S\ref{model:sec} we present a
@@
 We summarize our findings, and relate our results with light-curve shape, SiII velocity, and the ``mass step'' in SN~Ia Hubble
-residuals in \S\ref{discussion:sec}.}
+residuals in \S\ref{discussion:sec}.
 
@@
 \citet{2006ApJ...650..510A} and is updated in \citet{2010ApJ...713.1073S}. 
-\textcolor{red}{The flux calibration is presented in \citet{2013A&A...549A...8B}. }
+The flux calibration is presented in \citet{2013A&A...549A...8B}.
 A detailed
@@
 comprised of five 
-\color{red}
 bands with the following wavelength ranges: $U$ $[3300.00 - 3978.02]$\AA;
@@
 using single-band SALT2 fits.
-\color{black}
 The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
 in \citet{2008A&A...477..717B} and the 
-\textcolor{red}{wavelength of the SiII$\lambda 6355$ feature}
+wavelength of the SiII$\lambda 6355$ feature
 as in \citet{chotard:thesis}.
 Equivalent widths and the
-\textcolor{red}{SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from $B$-band maximum;
-the average is used  in cases where there are multiple spectral measurements within that time window.}
+SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from $B$-band maximum;
+the average is used  in cases where there are multiple spectral measurements within that time window.
 
@@
 
-%Absolute photometric calibration is of extreme importance for the supernova cosmology.
-%This analysis, however, is confined to the relative colors for a low-redshift set of supernovae
-%and is thus insensitive to uncertainties in these zeropoints.
-
 \section{Supernova Model I: Two Extrinsic Parameters}
@@
 broadband colors.
-%Spectra may not efficiently capture all variations in broadband magnitude, so an additional source
-%of intrinsic variation is accommodated.
 These intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion,
-\textcolor{red}{which in this section is not yet associated with a parameter. The intrinsic magnitudes are then
-modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.}
+which in this section is not yet associated with a parameter. The intrinsic magnitudes are then
+modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.
+
 \subsection{Model}
@@
 $EW_{Ca}$, $EW_{Si}$,
-\textcolor{red}{ and $\lambda_{Si}$ the wavelength of the minimum of 
-the SiII$\lambda6355$ feature}:
+and $\lambda_{Si}$ the wavelength of the minimum of 
+the SiII$\lambda6355$ feature:
 these spectral features are associated with SN~Ia  spectroscopic diversity  
 \citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
-\textcolor{red}{
 The explicit omission of light-curve shape in our model is compensated by its proxy
-$EW_{Si}$ at peak brightness}
+$EW_{Si}$ at peak brightness
 \citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
-% An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
 Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
@@
 shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
-\textcolor{red}{Unlike the parameters associated with
+Unlike the parameters associated with
 the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
 parameters $k_0$ and $k_1$ are not directly associated
-with observables but are rather drawn from the set of peak magnitudes.}
+with observables but are rather drawn from the set of peak magnitudes.
 The model is written as
@@
 To constrain the degrees of freedom and degeneracies inherent in the model we impose that
-\color{red}
 each of the vectors $k_0+1/N$ and $k_1+1/N$ are simplexes (all elements are $\ge 0$ and sum to one),
@@
 Furthermore we impose
-\color{black} 
 \begin{equation}
@@
 The first two conditions specify the definition of zero color relative to which the color excess is measured:
-\textcolor{red}{in a linear model this value is arbitrary.} 
+in a linear model this value is arbitrary.
 The latter two exclude degenerate posterior space
@@
 $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
-\color{red}
 (when running our fits, $k_0$ and $k_1$ are set to
@@
 
-\color{black}
-
 Having the intrinsic dispersion, $C_c$, as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
@@
  $0.1$ and scale $0.1$ mag restricted to positive values.
- \textcolor{red}{This covariance matrix prior is recommended by STAN, the Monte Carlo we use to evaluate the model.}
+This covariance matrix prior is recommended by STAN, the Monte Carlo we use to evaluate the model.
  We find that imposing a stricter assumption of a
@@
 The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo as implemented in
-STAN \citep{stan}.  \textcolor{red}{We run four chains, each with 10000 iterations of which
-half are used for warmup.}
+STAN \citep{stan}.  We run four chains, each with 10000 iterations of which
+half are used for warmup.
 STAN provides output statistics to assess
 the convergence of the output Markov chains.
-\textcolor{red}{The 
+The 
 potential scale reduction statistic, $\hat{R}$ \citep{Gelman92}, measures the convergence of the target distribution
@@
 $N_{eff}$ is an estimate of the number of independent draws. The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
-output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.}
+output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
 Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig}, \ref{global2:fig}, \ref{global3:fig}, \ref{global4:fig},
@@
 
-\color{red}
-
 The model-predicted versus observed supernova colors are shown in Figure~\ref{residual:fig}.
@@
    \includegraphics[width=5.5in]{output11/residual.pdf} 
-            \caption{\textcolor{red}{Predicted versus observed colors.  Overplotted is a line with slope equal to one.}
+            \caption{Predicted versus observed colors.  Overplotted is a line with slope equal to one.
             \label{residual:fig}}
@@
 
-\color{black}
-
 For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$
 are given in Table~\ref{global:tab}.
-\color{red}
 As the $\gamma$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_V$,
 their results are shown in terms of $\gamma^i_X/\gamma^i_V-1$.
-\color{black}
 Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig} .
@@
 
-\textcolor{red}{
 We find significant non-zero values for $\alpha$ and $\beta$, indicating that $EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
-peak magnitudes.}
+peak magnitudes.
 This validates our hypothesis that spectral indicators
@@
 Non-trivial residual magnitude dispersions are captured in $C_c$.  The diagonal elements are captured by the $\sigma$ parameters;
-% Figure~\ref{sigma:fig} shows the confidence regions for $\sigma$, the square root of the diagonal elements of $C_c$. 
 the residual intrinsic dispersion ranges from
@@
  \end{equation}
- \textcolor{red}{
 These color variances are smaller than those derived by \citet{2003A&A...404..901N, 2007ApJ...659..122J}, for cases where direct comparison can be made.
-} 
-% \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=5.5in]{output11/sigma_corner.pdf} 
-%   \caption{Posterior contours for the parameters $\sigma$, the square root of the diagonal elements of $C_c$.
-%   \label{sigma:fig}}
-%\end{figure}
 
@@
 \end{multline}
-\color{red}
 We find weak correlations between our color-excess parameters and the input features, the strongest being $-0.16$ between
 $E_\gamma(B-V)$ and $EW_{Si}$.
-\color{black}
 Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
@@
 
-\color{red}
 The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its affect on magnitude
@@
 $2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_0$ cannot be completely due to the line itself.
-\color{black}
 
 \subsection{The Two Extrinsic Parameters $k_0$ and $k_1$}
-\color{red}
 The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
-\color{black}
 None of the 20000 links of 
@@
 
-\color{red}
 Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k_0 + \gamma^1_X k_1$
@@
    \includegraphics[width=2.8in]{output11/rv.pdf}
-   \caption{\textcolor{red}{Left: $A_V$ versus $E(B-V)$ and Right: $R_V=A_V/(E(B-V)-zeropoint$\
-   versus $E(B-V)$ for the supernova sample.}
+   \caption{Left: $A_V$ versus $E(B-V)$ and Right: $R_V=A_V/(E(B-V)-zeropoint$\
+   versus $E(B-V)$ for the supernova sample.
    \label{avebv:fig}}
@@
    \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
-    \caption{\textcolor{red}{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
+    \caption{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
 onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
-covariance between the parameters. Right: $R^F_V$ for each supernova.}
+covariance between the parameters. Right: $R^F_V$ for each supernova.
    \label{avebv_synth:fig}}
@@
 in standard models of Milky Way dust.
-
-%
-%
-%The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model:
-%we now do so in a fit to the 
-%model of \citet{1999PASP..111...63F},
-%taking the fixed 3693,  4369,  5287,  6319, 7611 \AA\  for the effective wavelengths of the supernova flux through the bands.
-%Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
-%$R_V=2.97^{+0.18}_{-0.17}$..  
-%We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
-%The posterior distributions for $R_{\gamma X}=\frac{\gamma_X}{\gamma_B-\gamma_V}$ are shown in Figure~\ref{rx:fig}.
-%\color{black}
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=3.2in]{output11/fitz.pdf}
-%   \caption{\textcolor{red}{68\% credible intervals of $\gamma_X$ and the best-fit to the  \citet{1999PASP..111...63F}  model $R^F_V=2.97$.}
-%   \label{fitz:fig}}
-%\end{figure}
-%
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output11/rx_corner.pdf}
-%      \includegraphics[width=2.8in]{output11/rxdelta_corner.pdf} 
-%   \caption{Posterior contours for Left:  $R_X=\frac{\gamma_X}{\gamma_B-\gamma_V}$;  Right:  $R_{\delta X}=\frac{\delta_X}{\delta_B-\delta_V}$.
-%   \label{rx:fig}}
-%\end{figure}
-
-%
-%The best-fit distributions for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  
-%Our measurements of
-%$R_X$ and $\frac{\gamma_X}{\gamma_2}$, placed at the effective wavelength of the supernova flux that passes
-%through the synthetic bands, are shown in
-%Figure~\ref{ccm:fig}.
-%
-%
-
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output11/ccm.pdf}
-%      \includegraphics[width=2.8in]{output11/ccm2.pdf} 
-%   \caption{68\% credible intervals of Left: $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$; Right: $\frac{\gamma_X}{\gamma_2}$. 
-%   \label{ccm:fig}}
-%\end{figure}
 
@@
 are plotted in Figure~\ref{sn2014j:fig}.
-These data are fit to the model
+\color{red}
+The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
+wavelengths 
+3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  With the approximate correspondence between the filter sets,
+\color{black}
+these data are fit to the model
 \begin{equation}
@@
    \includegraphics[width=5.5in]{output11/sn2014j.pdf} 
-   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article and from  \citet{2014ApJ...788L..21A}.
+   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article. 
+   \color{red}
+   This can be compared with the best-fit results of
+   \citet{2014ApJ...788L..21A} shown in their Figure~3.
+   \color{black}
    \label{sn2014j:fig}}
@@
 UV through NIR data,
-a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$, 
-is also plotted.  Our model predictions provide a significantly better match to the data.
+a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$
+\color{red}
+is shown in their Figure 3.
+\color{black}
+Our model predictions provide a significantly better match to the data.
 
@@
 Among the supernovae in the SNfactory  set used to determine $\gamma^0$ and $\gamma^1$, the
-\color{red}
 objects with the extreme median values have 
@@
 attributed to dust.
-%The projection of our median parameter values onto the Fitzpatrick plane gives
-%$A^F=1.27$, $E^F(B-V)=1.07$, and thus $R^F_V=1.18.$
 
@@
 \end{multline}
-\color{red}
 The intrinsic parameter $A_{\delta I}$ has correlations $<0.05$ with respect to all the other parameters, including those attributed
@@
    \includegraphics[width=2.8in]{output15/x1D.pdf}
-    \caption{\textcolor{red}{Left: SALT2 $x_1$ versus $EW_{Si}$.  Right: $x_1$ versus $A_{\delta I}  = \delta_I D$.}
+    \caption{Left: SALT2 $x_1$ versus $EW_{Si}$.  Right: $x_1$ versus $A_{\delta I}  = \delta_I D$.
    \label{x1:fig}}
@@
    \includegraphics[width=5.5in]{output15/residualx1.pdf}
-    \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
-            of the SALT2 light-curve shape parameter $x_1$.  For reference a dotted line is plotted at zero difference.}
+    \caption{Differences between observed colors and the colors predicted from the analysis, as a function
+            of the SALT2 light-curve shape parameter $x_1$.  For reference a dotted line is plotted at zero difference.
    \label{x1res:fig}}
@@
 
-\color{black}
-
-%The trend in Figure~\ref{rveff:fig} showing an increased range of brighter-than-expected magnitudes  with increasing $E_{eff}(B-V)$  can
-%be compared
-%to Figure~\ref{betoule:fig}, which shows the $B$-band  Hubble residuals as a function of the color $C$ parameter (directly
-%comparable to $E(B-V)$) from the Hubble diagram analysis of \citet{2014A&A...568A..22B}.
-%A linear fit for the relationship between color and Hubble residual has a significant slope ($-0.57 \pm 0.07$), consistent with the slope
-%found for the SNfactory data.
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=3.2in]{output11/betoule.pdf} 
-%   \caption{Best-fit SN~Ia  $B$-band Hubble residuals as a function of the best-fit color parameter $C$ from the cosmology analysis of \citet{2014A&A...568A..22B}.
-%   \label{betoule:fig}}
-%\end{figure}
-
 \subsection{SiII Line Velocity}
@@
 \citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
-\textcolor{red}{The $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.}
+The $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.
 The values of $\eta$ in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
@@
 non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, 
-\textcolor{red}{but this correlation
-is absorbed into the equivalent-width corrections, which give higher likelihood as they give lower residual dispersions $C_c$}.
+but this correlation
+is absorbed into the equivalent-width corrections, which give higher likelihood as they give lower residual dispersions $C_c$.
 
 \subsection{Host-Galaxy Mass}
-\color{red}
 A correlation between Hubble residual and host-galaxy mass
@@
 s     \includegraphics[width=2.8in]{output15/rigault2.pdf}
-      \caption{\textcolor{red}{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host mass.  Hosts too faint for a mass measurement
+      \caption{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host mass.  Hosts too faint for a mass measurement
       are assigned a mass of 5.  Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
@@
 Right: Ideograms of  $A_{\delta I}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
-}
    \label{childress:fig}}
@@
 
-We find an intrinsic supernova parameter that does not have a monotonic influence on supernova magnitudes as a function
+We find a third supernova parameter that does not have a monotonic influence on supernova magnitudes as a function
 of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes
@@
 over broad bands are the most obvious candidate for producing this behavior.
+
 \citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
@@
 
+Although the $D$ parameter has ben referred to as ``intrinsic'', do to its placement in the model and the correspondence
+of the $k$ parameters with those of extrinsic two-parameter dust models, the analysis cannot quantitatively distinguish
+whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
+
 \subsection{Improving SNe~Ia as Standard Candles}
@@
 The  analysis of this article was intended to model the color behavior of supernovae in our dataset.
-\color{red}
 A new analysis insensitive to overtraining is required to robustly determine how
 well this model can be used to measure supernova distances.
-\color{black}
 

### 2016-10-21 apj.tex
pushing forward.

@@
 \title{Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory}
-\author{A.~G.~Kim}
+\author[0000-0001-6315-8743]{A.~G.~Kim}
 \affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
@@
 %-----
-$R^F_V=2.24 \pm 0.16$
+$R^F_V \sim 2.4$
 %------
@@
 the two parameters
-%-----
-$R^F_V=2.23 \pm 0.16$,
-%------
 plus a detection of a third parameter at  $>98$\% confidence; this new parameter is responsible for supernova color diversity
@@
 and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
-which a linear fit gives a slope of $R_V=2.51^{+0.23}_{-0.21}$.  The fit also gives the zeropoint, which we use to 
+which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.  The fit also gives the zeropoint, which we use to 
 estimate $R_V=(A_V-zeropoint)/E(B-V)$ per supernova, shown in Figure~\ref{avebv:fig}.
-Extremely blue supernovae ($E(B-V) + const <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
-whereas the extreme red objects ($E(B-V) + const >0.1$) have $R_V=  2.96 \pm   0.11$, indicating that different physical mechanisms
+Extremely blue supernovae ($E(B-V) <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
+whereas the extreme red objects ($E(B-V) >0.1$) have $R_V=  2.96 \pm   0.11$, indicating that different physical mechanisms
 operate in these regimes.
@@
 Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
-parameters of a single  dust model.  Indeed the \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
+parameters of a single  dust model.
+\color{red}
+Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R_V$ for $R^F_V=1.9, 2.4, 3.1$
+within the context of the \citetalias{1999PASP..111...63F} model.
+Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
+non-linear, and $R_V$ is not constant, for a fixed value of $R^F_V$.
+\color{black}
+
+The \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
 \begin{equation}
@@
 \begin{equation}
-A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2}  E_{\gamma^1}(B-V).
+A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
 \end{equation}
@@
 \begin{pmatrix}
- \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
-\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
+ \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
+\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
 \end{pmatrix}=
@@
 
-The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
-are projected onto the  \citetalias{1999PASP..111...63F} values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
-The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.24 \pm 0.16$.  
-The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
-which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
-the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.
+\color{red}
+To help visualize the above result, Figure~\ref{plane:fig} shows two perspectives in $UVI$-space
+of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model,
+and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model.
+The left plot shows that none of the four vectors are closely aligned with another, while the right plot shows that
+the planes defined by our model (solid lines) and the  \citetalias{1999PASP..111...63F} model (dashed lines) are nearly coplanar.
+If $R^F_V=2.4$ were constant in our sample, then $A_X = A_V\left(a(X) + \frac{b(X)}{2.4}\right)$;  this combination of $a$ and $b$ is
+almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, as shown in the dot-dashed line.  
+The $\gamma^1$ terms capture the remaining magnitude variations due to the fact that $R^F_V$ is not constant in the sample.
 
@@
    \centering
-   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
-   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
-    \caption{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
-onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
-covariance between the parameters. Right: $R^F_V$ for each supernova.
-   \label{avebv_synth:fig}}
+   \includegraphics[width=2.8in]{output11/plane0.pdf}
+   \includegraphics[width=2.8in]{output11/plane1.pdf}
+   \caption{Two different perspectives in $UVI$-space of the vectors $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
+   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.4$ is shown in the dot-dashed
+   line.
+   \label{plane:fig}}
 \end{figure}
+
+\color{black}
+
+%
+%The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
+%are projected onto the  \citetalias{1999PASP..111...63F} values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
+%The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.24 \pm 0.16$.  
+%The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
+%which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
+%the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
+%   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
+%    \caption{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
+%onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
+%covariance between the parameters. Right: $R^F_V$ for each supernova.
+%   \label{avebv_synth:fig}}
+%\end{figure}
+%
 

### 2016-10-21 apj.tex
respond to Greg and Gerard's VC comments

@@
 \citet{1999PASP..111...63F} dust model, yielding a per-supernova scatter in
-total-to-selective extinction, an effective
-%-----
-$R^F_V \sim 2.4$
-%------
-for the full sample, and a difference in the average $R^F_V$ between extremely blue and red supernovae .
-The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
+total-to-selective extinction.  The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
 Extending the model to three color parameters gives almost identical results for
@@
 
-Combining the effects of both parameters, we can define a total $X$-band extinction $A_X=\gamma^0_X k_0 + \gamma^1_X k_1$
-and a corresponding $E(B-V) = A_B-A_V$.  Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
-which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.  The fit also gives the zeropoint, which we use to 
-estimate $R_V=(A_V-zeropoint)/E(B-V)$ per supernova, shown in Figure~\ref{avebv:fig}.
-Extremely blue supernovae ($E(B-V) <-0.05$ on the plot) have an average $R_V=1.88 \pm   0.13$,
-whereas the extreme red objects ($E(B-V) >0.1$) have $R_V=  2.96 \pm   0.11$, indicating that different physical mechanisms
-operate in these regimes.
+\color{red}
+Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
+mean of $k_0$ and $k_1$ of the distribution to zero.
+There is an unconstrained $k_0^0$, $k_1^0$ that corresponds to an intrinsic supernova.  The true extinction is
+$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
+The true color excess is $E^T(B-V) = A^T_B-A^T_V$.
+Despite this ambiguity, a linear slope relating the $E^T(B-V)$ and $A^T_V$ for a set of supernova is the same slope
+relating $A_V$ and $E(B-V)$.
+\color{black}
+Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
+which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$,
+\color{red}
+which is the observed broad-band total-to-selective extinction exhibited by our sample.
+In contrast, the quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
+For ta qualitative view, we choose $k_0$  and $k_1$ such that the bluest supernova roughly correspond to $E(B-V)=0$.
+With this ansatz, we
+estimate $R^T_V$ per supernova as shown in Figure~\ref{avebv:fig}.
+
+\color{black}
 
@@
    \includegraphics[width=2.8in]{output11/rv.pdf}
-   \caption{Left: $A_V$ versus $E(B-V)$ and Right: $R_V=A_V/(E(B-V)-zeropoint$\
-   versus $E(B-V)$ for the supernova sample.
+   \caption{
+	\color{red}
+   Left: $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data. Right: Shown for qualitative purposes,
+   $R^T_V=A^T_V/E^T(B-V)$ 
+   versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova.  Overplotted is the mean and standard deviation of those points in equally divided bins.
+   On both plots are overplotted the expected values for the \citetalias{1999PASP..111...63F} model
+   for specific choices of $R^F_V$, normalized to have $A_V=0$ at $E(B-V)=0$.  Note that these lines are not straight on the left plot, and are not constant on the plot to the right.
+   \color{black}
    \label{avebv:fig}}
@@
 \color{red}
-Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R_V$ for $R^F_V=1.9, 2.4, 3.1$
+Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R^T_V$ for $R^F_V=1.1, 1.9, 2.5, 3.1$
 within the context of the \citetalias{1999PASP..111...63F} model.
 Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
-non-linear, and $R_V$ is not constant, for a fixed value of $R^F_V$.
+non-linear, and $R^T_V$ is not constant, for a fixed value of $R^F_V$.
 \color{black}
@@
    \includegraphics[width=2.8in]{output11/plane1.pdf}
-   \caption{Two different perspectives in $UVI$-space of the vectors $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
+   \caption{
+   \color{red}
+   Two different perspectives in $UVI$-space of the vectors $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
    and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.4$ is shown in the dot-dashed
-   line.
+   line, almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
+   \color{black}
    \label{plane:fig}}
@@
 contribute similar 3\% and 4\% to the total  length of the vector.
-The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.
+%The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.
 

### 2016-10-21 fitz11.py

@@ -193,22 +193,23 @@ ebvav_s = numpy.percentile(ebv,(50,50-34,50+34),axis=1)
 
 plt.errorbar(ebvav_s[0,0,:], ebvav_s[0,1,:], \
  xerr=(ebvav_s[0,0,:]-ebvav_s[1,0,:], ebvav_s[2,0,:]-ebvav_s[0,0,:]),\
- yerr=(ebvav_s[0,1,:]-ebvav_s[1,1,:], ebvav_s[2,1,:]-ebvav_s[0,1,:]),fmt='o',alpha=0.4,color='blue')
+ yerr=(ebvav_s[0,1,:]-ebvav_s[1,1,:], ebvav_s[2,1,:]-ebvav_s[0,1,:]),fmt='o',alpha=0.4,color='orange')
 plt.ylabel(r'$A_{V}$')
 plt.xlabel(r'$E(B-V)$')
 x = numpy.array([-0.15,0.45])
 plt.plot(x, rbv[1]+rbv[0]*x,label=r'$R_V={:6.2f}_{{-{:6.2f}}}^{{+{:6.2f}}}$'.format(rbv[0],rbv[0]-mrbv[0],prbv[0]-rbv[0]),color='black')
-rbvs = [1.9,2.4,3.1]
-for rbv in rbvs:
+rbvs = [1.1,1.9,2.5,3.1]
+for rbv_ in rbvs:
   x=[]
   y=[]
   for ebv in numpy.arange(-0.15,0.5,0.02):
-    A1= f99_band.A_X(r_v=rbv, ebv=ebv)
+    A1= f99_band.A_X(r_v=rbv_, ebv=ebv)
     x.append(A1[1]-A1[2])
     y.append(A1[2])
-  plt.plot(x,y,label=r'$R^F_V={:6.1f}$'.format(rbv))
+  plt.plot(x,y,label=r'$R^F_V={:6.1f}$'.format(rbv_))
 plt.legend(loc=2)
 plt.xlim((-0.1,0.4))
+plt.ylim((-0.7,1.2))
 pp = PdfPages("output11/avebv.pdf")
 plt.savefig(pp,format='pdf')
 pp.close()
@@ -216,41 +217,65 @@ plt.close()
 
 
 # Calculation of native RV
-rv=(fit['gamma'][:,2][:,None]*fit['k'] + fit['rho1'][:,2][:,None]*fit['R'])/ \
[…]

### 2016-10-21 view11.py

@@ -109,18 +109,18 @@ for i in xrange(nsne):
 
 
 
-# figure = corner.corner(EW_obs,labels=[r"$EW_{Ca,o}$",r"$EW_{Si,o}$",r"$\lambda_{Si,o}$"])
-# for ax in figure.get_axes():
-#     for tick in ax.xaxis.get_major_ticks():
-#         tick.label.set_fontsize(18) 
-#     for tick in ax.yaxis.get_major_ticks():
-#         tick.label.set_fontsize(18)
-        
-# pp = PdfPages('output11/feature_corner.pdf')
-# plt.savefig(pp,format='pdf')
-# pp.close()
-# plt.close()
 
+figure = corner.corner(numpy.concatenate((EW_obs,sivel[:,None]),axis=1),labels=[r"$EW_{Ca,o}$",r"$EW_{Si,o}$",r"$\lambda_{Si,o}$"])
+for ax in figure.get_axes():
+    for tick in ax.xaxis.get_major_ticks():
+        tick.label.set_fontsize(18) 
+    for tick in ax.yaxis.get_major_ticks():
+        tick.label.set_fontsize(18)
+        
+pp = PdfPages('output11/feature_corner.pdf')
+plt.savefig(pp,format='pdf')
+pp.close()
+plt.close()
 
 
 (x, xmin, xmax) = numpy.percentile( ((fit['gamma'][:,1] - fit['gamma'][:,2])[:,None]*fit['k']),(50,50-34,50+34),axis=0)

### 2016-10-21 view15.py

@@ -409,6 +409,16 @@ plt.close()
 # plt.close()
 
 
+# plt.hist(((fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['k'] + 
+#   (fit['gamma1'][:,1]-fit['gamma1'][:,2])[:,None]*fit['k1']).flatten(),normed=True,bins=20,
+#   label=r'$E(B-V)$')
+# plt.xlabel(r'Color Excess')
+# # plt.legend()
+# pp = PdfPages('output15/greg.pdf')
+# plt.savefig(pp,format='pdf')
+# pp.close()
+# plt.close()
+# wefe
 
 # plt.hist([(fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['k'], (fit['gamma1'][:,1]-fit['gamma1'][:,2])[:,None]*fit['k1'], (fit['rho1'][:,1]-fit['rho1'][:,2])[:,None]*fit['R']],normed=True,bins=20,
 #     label=[r'$E_\gamma(B-V)$',r'$E_{\gamma_1}(B-V)$',r'$E_\delta(B-V)$'],range=(-0.1,0.4))

### 2016-10-29 apj.tex
fixing zeropoint

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{natbib}
@@
 with observables but are rather drawn from the set of peak magnitudes.
-The model is written as
+The model 
+\color{red}
+likelihood
+\color{black}
+is written as
 \begin{equation}
@@
 Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
-which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$,
+which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.
 \color{red}
-which is the observed broad-band total-to-selective extinction exhibited by our sample.
-In contrast, the quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
-For ta qualitative view, we choose $k_0$  and $k_1$ such that the bluest supernova roughly correspond to $E(B-V)=0$.
+The full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
+on a ridge line, and having a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
+but can have values that extend toward lower values.
+
+The quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
+For a qualitative view, we choose the zeros for $V$-band extinction and color-excess such that the bluest supernova roughly correspond to $E(B-V)=0$,
+$A_V=0$, and such that the ridge line is close to flat.
 With this ansatz, we
-estimate $R^T_V$ per supernova as shown in Figure~\ref{avebv:fig}.
-
+estimate $R^T_V$ per supernova as shown in Figure~\ref{avebv:fig}, with the expectations of the
+ \citetalias{1999PASP..111...63F} model for fixed $R^F_V$ overplotted.
+With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
+We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
+of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
+A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
+for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
 \color{black}
@@
    $R^T_V=A^T_V/E^T(B-V)$ 
-   versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova.  Overplotted is the mean and standard deviation of those points in equally divided bins.
+   versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
+   %Overplotted is the mean and standard deviation of those points in equally divided bins.
    On both plots are overplotted the expected values for the \citetalias{1999PASP..111...63F} model
@@
 its effects on broadband magnitudes.
-Although
-this term is introduced as part of the  absolute rather than observed magnitudes,
-practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
-degeneracy, for convenience this term is referred to as ``intrinsic''.
+
+\color{red}
+The $\delta D$ terms contribute to the mean of the Normal distribution in Eqn.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
+it is for this reason that for convenience these terms are referred to as ``intrinsic''.
+However, we emphasize now that we have also run the alternative case  of placing the
+$\delta D$ terms in mean of the Normal distribution in Eqn.~\ref{dust:eqn}, i.e.\ as extrinsic contributions.
+Analyses of the two different models give practically identical results, meaning that data are not constraining enough
+to identify $\delta D$ as being physically intrinsic or extrinsic.
+\color{black}
 
@@
 The significance of the $\delta$ parameters is shown pictorially.
-Figure~\ref{deltacorner:fig} shows the $\delta$ posteriors, which are bimodal due to the $\pm$ sign degeneracy.  The probability
+Figure~\ref{deltacorner:fig} shows the $\delta$ posteriors, which are bimodal due to the $\pm$ sign degeneracy.
+\color{red}
+Recall that fixing $\delta_X=0$ reverts this model into the two external-parameter model of \S\ref{model:sec}.
+\color{black}
+The probability
 of the null result $\delta_X=0$ for all $X$ is $<98\%$, as determined through
 the population of its bin in a 5-dimensional histogram.
-Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values.   An interesting feature
+Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values. 
+\color{red}
+While the signal of the internal parameter is strong within the context of this model, ``model testing'' (comparing the
+performance  between this model
+and that of \S\ref{model:sec}), is challenging for Bayesian Monte Carlo analysis.  Evidence calculations are planned
+for the next generation of STAN and the development of robust algorithms is a subject of theoretical work.
+\color{black}
+
+An interesting feature
 is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
@@
 Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
-non-zero $\eta$ values at  $\gtrsim 2\sigma$.  We conclude that $v_{Si}$ is correlated with color, 
+non-zero $\eta$ values at  $\gtrsim 2\sigma$.
+\color{red}
+The Ca and Si responsible for the equivalent widths and wavelength of our selected spectral features
+are expected to be produced together in the thermonuclear burning into intermediate mass elements.
+\color{black}
+We conclude that $v_{Si}$ is correlated with color, 
 but this correlation
@@
 application of the model, and its  $0.10$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
-measurement uncertainties.  It is also subject to overtraining.
-The  analysis of this article was intended to model the color behavior of supernovae in our dataset.
-A new analysis insensitive to overtraining is required to robustly determine how
-well this model can be used to measure supernova distances.
+measurement uncertainties.
+\color{red}
+The purpose of this analysis was designed to mine information from the SNfactory data set, and so the results presented here
+are specific to it both in terms of its population distribution and potentially noise.  This is the approach taken by previous
+exploratory work.
+A new analysis that explicitly measures out-of-sample performance is required to robustly determine how
+well the addition of third parameter inferred from supernova magnitudes can be used to measure supernova distances.
+\color{black}
 

### 2016-10-29 apj.tex
clean up for, should be ready for another collaboration release.

@@
 The two color parameters exhibit the behavior expected from the two-parameter
-\citet{1999PASP..111...63F} dust model, yielding a per-supernova scatter in
-total-to-selective extinction.  The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
+\citet{1999PASP..111...63F} dust model.
+The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
 Extending the model to three color parameters gives almost identical results for
@@
 \color{red}
-likelihood
+likelihood density
 \color{black}
@@
 Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
-mean of $k_0$ and $k_1$ of the distribution to zero.
-There is an unconstrained $k_0^0$, $k_1^0$ that corresponds to an intrinsic supernova.  The true extinction is
+means of $k_0$ and $k_1$ to zero.
+There are unconstrained $k_0^0$, $k_1^0$ that correspond to an intrinsic supernova.  The true extinction is
 $A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
@@
 The full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
-on a ridge line, and having a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
+on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
 but can have values that extend toward lower values.
@@
 For a qualitative view, we choose the zeros for $V$-band extinction and color-excess such that the bluest supernova roughly correspond to $E(B-V)=0$,
-$A_V=0$, and such that the ridge line is close to flat.
+$A_V=0$, and such that the ridge line is close to constant.
 With this ansatz, we
-estimate $R^T_V$ per supernova as shown in Figure~\ref{avebv:fig}, with the expectations of the
+estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
  \citetalias{1999PASP..111...63F} model for fixed $R^F_V$ overplotted.
@@
 Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
-non-linear, and $R^T_V$ is not constant, for a fixed value of $R^F_V$.
+non-linear, and $R^T_V$ is not constant for a fixed value of $R^F_V$.
 \color{black}
@@
 $a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ for the case of
-$R^F_V=2.5$ and the updated
-\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak.  This linear approximation
-is good in the ranges of $R^F_V$ and wavelength under consideration, in that these vectors vary by $<5$\% over the range $1.9<R^F_V<3.1$.
+$R^F_V=2.5$
+\color{red}
+and $A^F_V=0.1$,
+for the measurement of the updated
+\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak as seen through our synthetic passbands.
+\color{black}
+This linear approximation
+is good in the ranges of
+\color{red}
+ $R^F_V$ and $A^F_V$,
+\color{black}
+and wavelengths under consideration, in that the values of the components  vary by $<5$\%.
 
@@
 \end{equation}
-Our best-fit values for the $\gamma$ coefficients (from Table~\ref{global:tab}) can expressed in terms of the $a(X)$ and $b(X)$ vectors:
+\color{red}
+Our median-fit values for the $\gamma$ coefficients,
+$\frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  =\{4.78,   3.88,   2.88,   2.21,   1.59\}$ and
+$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.85,   -4.69,   -5.69,  -5.33,  -4.77\}$,
+\color{black}
+can expressed in terms of the $a(X)$ and $b(X)$ vectors:
 \begin{equation}
@@
 wavelengths 
-3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  With the approximate correspondence between the filter sets,
-\color{black}
-these data are fit to the model
+3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  Despite the imperfect correspondence our synthetic passbands
+and those used for the observations,
+\color{black}
+these data are fit to our model
 \begin{equation}
@@
 \color{black}
-Our model predictions provide a significantly better match to the data.
+Our model predictions provide a significantly better match to the data
+\color{red}
+despite the only approximate correspondence of the model and observer passbands.
+\color{black}
 
@@
 A new analysis that explicitly measures out-of-sample performance is required to robustly determine how
-well the addition of third parameter inferred from supernova magnitudes can be used to measure supernova distances.
+well the addition of third parameter inferred from one data set can be used to measure supernova distances
+of an independent set.
 \color{black}

### 2016-10-29 fitz11.py

@@ -74,6 +74,7 @@ c_n = []
 cs = []
 for s in ['gamma','rho1']:
   c, cmin, cmax = numpy.percentile(fit[s]/((fit[s][:,1]-fit[s][:,2])[:,None]),(50,50-34,50+34),axis=0)
+  print c
   cs.append(c)
   c_norm = numpy.linalg.norm(c)
   c_n.append(c_norm)
@@ -84,6 +85,8 @@ for s in ['gamma','rho1']:
   tmat.append(ans)
   ans = c-ans[0]*dAdebv - ans[1]*dAdAv
   res.append(ans)
+
+wefew
 
 tmat = numpy.array(tmat)
 res= numpy.array(res)

### 2016-11-03 apj.tex
write out epsilon vectors

@@
  \end{equation}
+\color{red}
+The average correlation matrix is
+\begin{equation}
+Cor(U,B,V,R,I)=
+\begin{pmatrix}
+\begin{array}{rrrrr}
+1.00 & 0.43 & -0.17 & -0.06 & 0.10 \\
+0.43 & 1.00 & 0.24 & -0.09 & -0.41 \\
+-0.17 & 0.24 & 1.00 & 0.09 & -0.22 \\
+-0.06 & -0.09 & 0.09 & 1.00 & 0.25 \\
+0.10 & -0.41 & -0.22 & 0.25 & 1.00
+\end{array}
+ \end{pmatrix}.
+ \end{equation}
+ \color{black}
 The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
@@
 \end{equation}
-where the two residual $\vec{\epsilon}$ vectors are perpendicular to both $a(X)$ and $b(X)$ and
+where the two residual vectors are
+\color{red}
+\begin{align}
+\vec{\epsilon}_a &=\{0.14, -0.15, -0.07,  0.04, 0.07\}, \\
+\vec{\epsilon}_b & =\{0.12, -0.06, -0.30, 0.30, -0.06\}:
+\end{align}
+\color{black}
+both are perpendicular to $a(X)$ and $b(X)$ and
 contribute  3\% and 4\% respectively to the total  length of the $\gamma$ vectors.
@@
 \end{equation}
-where the residual vectors $\vec{\epsilon}$ are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
+where the residual vectors 
+\color{red}
+\begin{align}
+\vec{\epsilon}_a &=\{0.13, -0.15, -0.07,  0.04,  0.06\},\\
+\vec{\epsilon}_b &=\{ 0.10, -0.04,  -0.28,  0.31, -0.09\}
+\end{align}
+\color{black}
+are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
 contribute similar 3\% and 4\% to the total  length of the vector.

### 2016-11-03 fitz15.py

@@ -62,6 +62,8 @@ res= numpy.array(res)
 #print the matrix and the residues
 print tmat
 print numpy.linalg.norm(res,axis=1)/numpy.array(c_n)
+print res
+
 
 # The matrix to transform the per-SN parameters from gamma to fitzpatrick
 # A= gamma0 k0 + gamma1 k1 = ans00 F0 k0 + ans01 F1 k0 + ans10 F0 k1 + ans11 F1 k1 

### 2016-11-08 apj.tex
finishing up Gerard's comments

@@
 In this article we use the idea that spectral indicators carry information on intrinsic supernova colors at peak magnitude.
-We allow for three independent color parameters, one attributed to intrinsic supernova
-properties and two  attributed to
-extrinsic processes, which we attribute to dust.  The data used in this analysis are described in \S\ref{data:sec}.
+\color{red}
+This approach is taken by \citet{2011A&A...529L...4C}, who find that after standardization based on Ca and Si features, remaining residual color
+variation is consistent with Milky Way dust laws.
+We accommodate  three independent color parameters: the model is constructed such that one is attributed to intrinsic supernova
+properties and the two others to
+extrinsic processes that are attributed to dust.
+\color{black}
+The data used in this analysis are described in \S\ref{data:sec}.
 In \S\ref{model:sec} we present a
@@
 
+\color{red}
+For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
+color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
+$C_c$.  For $N=168$ supernovae, there are 1344 observables and 1043 top-level parameters.
+\color{black}
+
 Having the intrinsic dispersion, $C_c$, as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
@@
 \color{red}
-The full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
+The slope uncertainties are the $68$\% credible interval from the Bayesian analysis and does not incorporated goodness
+ of fit.  Indeed,
+the full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
 on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
@@
 almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, as shown in the dot-dashed line.  
-The $\gamma^1$ terms capture the remaining magnitude variations due to the fact that $R^F_V$ is not constant in the sample.
+The $\gamma^1$ terms capture the remaining magnitude variations due to the fact that $R^F_V$ is not constant in the sample:
+if the $\gamma$'s are due to  \citetalias{1999PASP..111...63F} dust, the only way our analysis could recover
+both $\gamma^0$ and $\gamma^1$ is for there to be variation in $R^F_V$.
 
@@
 \color{red}
+For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
+color parameters, $(N-1)$ magnitude offsets,  $5 \times 7$ global coefficients, and $10$ parameters that describe the intrinsic
+$C_c$.  For $N=168$ supernovae, there are 1344 observables and 1214 top-level parameters.
+\color{black}
+
+\color{red}
 The $\delta D$ terms contribute to the mean of the Normal distribution in Eqn.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
@@
 to extrinsic dust.
+
+\color{red}
+The per-supernova color parameters are not strongly correlated,
+\begin{equation}
+Cor(k_0, k_1, D) =
+\begin{pmatrix}
+\begin{array}{rrr}
+1.00 & 0.06 & -0.01 \\
+0.06 & 1.00 & 0.00 \\
+-0.01 & 0.00 & 1.00
+\end{array}
+\end{pmatrix}.
+\end{equation}
+In particular, the Pearson correlation coefficients between the ``intrinsic'' $D$ and ``extrinsic'' $k$ parameters are $-0.01$ and $0.00$.
+So while in principle a single physical color effect can affect both intrinsic and extrinsic parameters, from the correlations
+there is no evidence
+that this occurs in our fits.
+
+The distributions for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, 
+$E_{\gamma^1}(B-V)$, and
+$E_{\delta}(B-V)$ for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.5in]{output15/perobject_corner.pdf} 
+   \caption{
+   \color{red}
+   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$,  $E_{\gamma^1}(B-V)$,  and $E_{\delta}(B-V)$, as well as the grey offset
+$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
+\color{black}
+   \label{perobject2:fig}}
+\end{figure}
+
+Our code is validated
+though the analysis of a simulated dataset: the input parameters are recovered within  uncertainties.
+\color{black}
 

### 2016-11-10 apj.tex
more changes for Gerard and myself

@@
 \begin{pmatrix}
-U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
+U +\gamma^0_{1} k_0 +\gamma^1_{0} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
 V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
@@
 
+\color{blue}
+There remains degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
+ $\gamma^0 \rightarrow \gamma^0  + \epsilon_{\gamma^0}$, $\gamma^1 \rightarrow \gamma^1 + \epsilon_{\gamma^1}$under the condition
+$$
+\epsilon_\Delta  +  \epsilon_{\gamma^0} k_0+  \epsilon_{\gamma^1} k_1=0,
+$$
+i.e.\ shifts in the global coefficients $\gamma$ can be compensated by shifts in $\Delta$ for each supernova while maintaining 
+$\langle \Delta \rangle=0$.
+Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
+$\alpha \rightarrow \alpha - \gamma \epsilon$, $c \rightarrow c + \langle EW_{Ca}\rangle \epsilon$, i.e. the
+linear external terms can leak into the linear spectral feature corrections.
+These degeneracies are not broken within the model, but rather are constrained by the priors, for which the
+per-supernova parameters
+$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.
+\color{black}
+
 \subsection{Results}
@@
 values of zero signify no color changes associated with magnitude changes.
-Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes, though not in $B-V$ specifically.
+Both $EW_{Ca}$ and $EW_{Si}$ are associated with color changes, though not in $B-V$ specifically.
 We do not detect a significant association between
@@
 estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
- \citetalias{1999PASP..111...63F} model for fixed $R^F_V$ overplotted.
+ \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
 With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
@@
 \color{red}
+Our model for broadband photometry does not specify how spectral features and color parameters affect the supernova spectrum, information
+necessary to predict the magnitude extinction of dust models.
+\color{blue}
+The lack of correspondence between dust models and broadband extinction is quantified when we apply an $R^F_V=2.5$ SN-frame dust to the
+observed spectra used in our sample, to yield a distribution in the quantity $R_V=A_V/(A_B-A_V)$ with mean and standard deviation of $3.11 \pm 0.35$.
+While an accurate study of fundamental dust properties would incorporate the dust law within the model itself, we now proceed nonetheless
+in making a connection between our model outputs and dust.
+
+\color{red}
 Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R^T_V$ for $R^F_V=1.1, 1.9, 2.5, 3.1$
@@
 \end{equation}
-The \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F}) model is approximately described by a linear model with
+The \citetalias{1999PASP..111...63F} model is approximately described by a linear model with
 the above form, with
@@
 \begin{pmatrix}
-U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
+U +\gamma^0_{0} k_0 +\gamma^1_{0} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
 V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\

### 2016-11-11 apj.tex
working on Jakob's comments

@@
 
-The quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
-For a qualitative view, we choose the zeros for $V$-band extinction and color-excess such that the bluest supernova roughly correspond to $E(B-V)=0$,
-$A_V=0$, and such that the ridge line is close to constant.
+\color{blue}
+Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
+For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
+$A_V=0$, and such that the ridge line 
+has close to constant $R^T_V$.
+\color{black}
 With this ansatz, we
@@
 The \citetalias{1999PASP..111...63F} model is approximately described by a linear model with
-the above form, with
-$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ for the case of
-$R^F_V=2.5$
-\color{red}
-and $A^F_V=0.1$,
-for the measurement of the updated
-\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak as seen through our synthetic passbands.
+the above form:
+\color{red}
+for the case of
+$R^F_V=2.5$ and $A^F_V=0.1$,
+and the measurement of the updated
+\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak as seen through our synthetic passbands,
+$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ 
 \color{black}
@@
 Our median-fit values for the $\gamma$ coefficients,
-$\frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  =\{4.78,   3.88,   2.88,   2.21,   1.59\}$ and
+$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.78,   3.88,   2.88,   2.21,   1.59\}$ and
 $ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.85,   -4.69,   -5.69,  -5.33,  -4.77\}$,
@@
 almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, as shown in the dot-dashed line. 
+\color{blue}
+Note that the specific directions of $\gamma^0$ and
+ $\gamma^1$  within their plane are based on the prior that $k_0$ and $k_1$ are uncorrelated.
+\color{black}
 The $\gamma^1$ terms capture the remaining magnitude variations due to the fact that $R^F_V$ is not constant in the sample:

### 2016-11-11 apj.tex
finish Jakob's comments

@@
 \end{multline}
-The intrinsic parameter $A_{\delta I}$ has correlations $<0.05$ with respect to all the other parameters, including those attributed
+The intrinsic parameter $A_{\delta I} =\delta_I D$ has correlations $<0.05$ with respect to all the other parameters, including those attributed
 to extrinsic dust.

### 2016-11-14 apj.tex
making the paper better.

@@
 linear external terms can leak into the linear spectral feature corrections.
-These degeneracies are not broken within the model, but rather are constrained by the priors, for which the
+These degeneracies are not broken within the model, but rather are constrained by the priors, in which the
 per-supernova parameters
-$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.
+$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.  It is important to emphasize that the latent parameters $k$ and $\Delta$
+are non-trivially specified by these priors.
 \color{black}
@@
 A_X = a(X)  A_V + b(X) E(B-V).
+\label{f99:eqn}
 \end{equation}
@@
 the planes defined by our model (solid lines) and the  \citetalias{1999PASP..111...63F} model (dashed lines) are nearly coplanar.
-If $R^F_V=2.4$ were constant in our sample, then $A_X = A_V\left(a(X) + \frac{b(X)}{2.4}\right)$;  this combination of $a$ and $b$ is
-almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, as shown in the dot-dashed line. 
+
 \color{blue}
-Note that the specific directions of $\gamma^0$ and
- $\gamma^1$  within their plane are based on the prior that $k_0$ and $k_1$ are uncorrelated.
-\color{black}
-The $\gamma^1$ terms capture the remaining magnitude variations due to the fact that $R^F_V$ is not constant in the sample:
-if the $\gamma$'s are due to  \citetalias{1999PASP..111...63F} dust, the only way our analysis could recover
-both $\gamma^0$ and $\gamma^1$ is for there to be variation in $R^F_V$.
+Recall that degeneracies in the values of $\gamma$ and $k$ are broken by the prior that $k_0$, $k_1$, and the other SN parameters are uncorrelated. 
+The combination  $\left(a(X) + \frac{b(X)}{2.4}\right)$ is
+almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ while $b$ alone is almost perfectly aligned with $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$,
+as shown in the dot-dashed and dotted lines of  Figure~\ref{plane:fig}.
+Rewriting the \citetalias{1999PASP..111...63F} model in Eqn.~\ref{f99:eqn} as
+\begin{equation}
+A_X =  A_V^F\left(a(X)+\frac{b(X)}{2.4} \right) +  \left(\frac{ A_V^F}{R^F_V} - \frac{ A_V^F}{2.4}\right)b(X),
+\end{equation}
+we see the correspondence between $k_0$ with $A^F_V$, and $k_1$ with $\frac{A^F_V}{R^F_V}-\frac{A^F_V}{2.4}$.
+Reasoning in the opposite direction, our results are motivated by a prior that ultimately turned out to be, based on our ultimate solution, 
+\begin{align}
+\text{cov}\left(A^F_V, \frac{A^F_V}{R^F_V}\right) & = \frac{1}{2.4} \text{var}(A^F_V).
+\end{align}
+Independent variations in $A^F_V$ and  $A^F_V/R^F_V$ within the data allowed the data analysis to detect
+$\gamma^{0,1}$ and $k_{0,1}$ at high significance.
+\color{black}
 
@@
    and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.4$ is shown in the dot-dashed
-   line, almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
+   line, almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, while $b(X)$ shown in the dotted line is
+   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$.  
    \color{black}
@@
    \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
+ \color{blue}
+ Three of the chains converged to one solution while the remaining chain converged to the other, resulting in the different normalizations of the two peaks.
+ \color{black}
    \label{deltacorner:fig}}

### 2016-12-18 apj.tex
reassembling note

@@
 the two parameters
-plus a detection of a third parameter at  $>98$\% confidence; this new parameter is responsible for supernova color diversity
+plus a detection of a third parameter at
+%--- table.py
+$>95$\% confidence;
+%-----
+this new parameter is responsible for supernova color diversity
 beyond those tracked by the spectral features and two-parameter dust models.
@@
 \startdata
-SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
+SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
 PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
@@
 PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
-PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6141 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
+PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
 SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
@@
 PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
+PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ \\
 SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
@@
 PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
-PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6114 \pm   9$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
+PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
 SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
@@
 SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
-PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6168 \pm   6$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
+PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
 PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
@@
 CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
+SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ \\
 SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
@@
 SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
+SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ \\
 SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
@@
 SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
-SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6127 \pm  10$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
-SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6144 \pm   2$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
+SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
+SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
 CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
-SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   4$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
+SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
 SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
@@
 PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
-SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6112 \pm   2$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
+SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
 SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
@@
 SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
-SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6148 \pm   4$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
+SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
 SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
@@
 SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
-SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6129 \pm   7$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
+SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
+SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ \\
 SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
@@
 \end{deluxetable}
-
 \section{Supernova Model I: Two Extrinsic Parameters}
@@
 &
-$0.0016^{+0.0007}_{-0.0007}$
+$0.0016^{+0.0008}_{-0.0007}$
 &
@@
 &
-$0.0026^{+0.0005}_{-0.0004}$
+$0.0027^{+0.0005}_{-0.0005}$
 \\
@@
 &
-$   1.9^{+   1.0}_{  -0.5}$
+$   1.9^{+   1.1}_{  -0.5}$
 &
@@
 &
-\ldots
-&
-$  -0.0^{+   0.1}_{  -0.1}$
-&
-$   0.7^{+   0.7}_{  -0.3}$
+$\dots$
+&
+$   0.0^{+   0.1}_{  -0.1}$
+&
+$   0.8^{+   0.8}_{  -0.3}$
 \\
@@
 &
-$ 0.025^{+ 0.002}_{-0.003}$
-&
-$ 0.025^{+ 0.002}_{-0.002}$
+$ 0.026^{+ 0.002}_{-0.002}$
+&
+$ 0.026^{+ 0.002}_{-0.002}$
+&
+$ 0.021^{+ 0.002}_{-0.002}$
 &
 $ 0.020^{+ 0.002}_{-0.002}$
-&
-$ 0.019^{+ 0.002}_{-0.002}$
 \\
@@
 &
-$  0.26^{+  0.05}_{ -0.05}$
+$  0.25^{+  0.05}_{ -0.05}$
 &
@@
 &
-\ldots
+$\dots$
 &
@@
 &
-$ -0.24^{+  0.03}_{ -0.03}$
+$ -0.23^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$-0.0000^{+0.0010}_{-0.0009}$
+$0.0000^{+0.0010}_{-0.0009}$
 &
@@
 &
-$0.0005^{+0.0007}_{-0.0007}$
-&
-$-0.0003^{+0.0006}_{-0.0006}$
+$0.0006^{+0.0007}_{-0.0007}$
+&
+$-0.0002^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.40^{+  2.33}_{ -1.90}$
-&
-$ -0.34^{+  1.60}_{ -1.20}$
-&
-\ldots
-&
-$ -0.11^{+  0.29}_{ -0.27}$
-&
-$ -0.84^{+  1.66}_{ -1.27}$
+$ -0.39^{+  2.22}_{ -1.82}$
+&
+$ -0.35^{+  1.58}_{ -1.20}$
+&
+$\dots$
+&
+$ -0.09^{+  0.29}_{ -0.28}$
+&
+$ -0.78^{+  1.48}_{ -1.11}$
+\\
+$\gamma^0_X$
+&
+$ 63.46^{+  3.70}_{ -3.66}$
+&
+$ 51.40^{+  3.09}_{ -3.07}$
+&
+$ 38.15^{+  2.70}_{ -2.63}$
+&
+$ 29.26^{+  2.40}_{ -2.35}$
+&
+$ 20.94^{+  2.24}_{ -2.25}$
 \\
@@
 &
-\ldots
-&
-$ -0.23^{+  0.01}_{ -0.01}$
+$\dots$
+&
+$ -0.23^{+  0.01}_{ -0.02}$
 &
@@
 \\
+$\gamma^1_X$
+&
+$-10.34^{+  3.61}_{ -4.29}$
+&
+$-11.89^{+  2.95}_{ -3.56}$
+&
+$-14.48^{+  2.47}_{ -2.89}$
+&
+$-13.71^{+  2.14}_{ -2.45}$
+&
+$-12.51^{+  2.10}_{ -2.23}$
+\\
 ${\gamma^1_X/\gamma^1_V-1}$
 &
-$ -0.31^{+  0.17}_{ -0.18}$
-&
-$ -0.17^{+  0.09}_{ -0.10}$
-&
-\ldots
-&
-$ -0.07^{+  0.05}_{ -0.04}$
-&
-$ -0.17^{+  0.10}_{ -0.09}$
+$ -0.28^{+  0.17}_{ -0.19}$
+&
+$ -0.18^{+  0.10}_{ -0.10}$
+&
+$\dots$
+&
+$ -0.05^{+  0.05}_{ -0.04}$
+&
+$ -0.14^{+  0.10}_{ -0.09}$
 \\
@@
 &
-$ 0.021^{+ 0.004}_{-0.006}$
-&
-$ 0.012^{+ 0.007}_{-0.008}$
+$ 0.021^{+ 0.004}_{-0.005}$
+&
+$ 0.011^{+ 0.008}_{-0.007}$
 &
@@
 \begin{array}{rrrrr}
-1.00 & 0.43 & -0.17 & -0.06 & 0.10 \\
-0.43 & 1.00 & 0.24 & -0.09 & -0.41 \\
--0.17 & 0.24 & 1.00 & 0.09 & -0.22 \\
--0.06 & -0.09 & 0.09 & 1.00 & 0.25 \\
-0.10 & -0.41 & -0.22 & 0.25 & 1.00
+1.00 & 0.42 & -0.18 & -0.05 & 0.12 \\
+0.42 & 1.00 & 0.26 & -0.09 & -0.39 \\
+-0.18 & 0.26 & 1.00 & 0.09 & -0.22 \\
+-0.05 & -0.09 & 0.09 & 1.00 & 0.27 \\
+0.12 & -0.39 & -0.22 & 0.27 & 1.00
 \end{array}
@@
  \begin{pmatrix}
-0.068 & 0.034& 0.023 & 0.053
+0.068 & 0.034 & 0.023 & 0.053
   \end{pmatrix} \text{mag}
@@
 \begin{array}{rrrr}
-1.000 & 0.615 & -0.334 & -0.296 \\
-0.615 & 1.000 & -0.193 & 0.099 \\
--0.334 & -0.193 & 1.000 & 0.634 \\
--0.296 & 0.099 & 0.634 & 1.000 
+1.000 & 0.602 & -0.353 & -0.317 \\
+0.602 & 1.000 & -0.197 & 0.082 \\
+-0.353 & -0.197 & 1.000 & 0.647 \\
+-0.317 & 0.082 & 0.647 & 1.000
 \end{array}
@@
 1.00 & 0.00 & -0.06 & -0.05 & 0.11 & 0.01 \\
-0.00 & 1.00 & 0.11 & -0.25 & -0.07 & -0.00 \\
--0.06 & 0.11 & 1.00 & -0.14 & -0.16 & -0.03 \\
--0.05 & -0.25 & -0.14 & 1.00 & 0.04 & 0.03 \\
-0.11 & -0.07 & -0.16 & 0.04 & 1.00 & 0.06 \\
-0.01 & -0.00 & -0.03 & 0.03 & 0.06 & 1.00
+0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.01 \\
+-0.06 & 0.10 & 1.00 & -0.14 & -0.17 & -0.03 \\
+-0.05 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 \\
+0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 \\
+0.01 & -0.01 & -0.03 & 0.03 & 0.05 & 1.00
 \end{array}
@@
 \end{multline}
-We find weak correlations between our color-excess parameters and the input features, the strongest being $-0.16$ between
+We find weak correlations between our color-excess parameters and the input features, the strongest being
+%---
+$-0.17$
+%---
+ between
 $E_\gamma(B-V)$ and $EW_{Si}$.
@@
 
-\color{red}
-Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
-means of $k_0$ and $k_1$ to zero.
-There are unconstrained $k_0^0$, $k_1^0$ that correspond to an intrinsic supernova.  The true extinction is
+\color{blue}
+Recall that there are degeneracies between the intrinsic (Eqn.~\ref{ewsiv:eqn}) and
+extrinsic (Eqn.~\ref{dust:eqn}) parameters of our model.  Part of that degeneracy is
+broken by imposing $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$,
+but this choice does not specify the $k_0^0$, $k_1^0$ corresponding to supernovae experiencing no extrinsic effects.  The true extrinsic
+extinction is
 $A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
-The true color excess is $E^T(B-V) = A^T_B-A^T_V$.
-Despite this ambiguity, a linear slope relating the $E^T(B-V)$ and $A^T_V$ for a set of supernova is the same slope
-relating $A_V$ and $E(B-V)$.
+The true extrinsic color excess is $E^T(B-V) = A^T_B-A^T_V$, so that the total-to-selective extinction is $R^T_V=A^T_V/E^T(B-V)$.
+Our model as analyzed cannot directly determine the above extrinsic properties per supernova.
+
+Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
+written as
+$$A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
+$$
+Making the assumption that $R^T_V$ is the same for all supernovae (shown later to be approximately true for dust laws),
+it can be determined as the slope of the relation between $A_X$ and $E(B-V)$.
 \color{black}
 Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
-which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.
-\color{red}
+which a linear fit gives a slope of
+%----- fitz11.py
+$R_V=2.77 \pm 0.08$.
+%----
+\color{blue}
 The slope uncertainties are the $68$\% credible interval from the Bayesian analysis and does not incorporated goodness
@@
 
-\color{blue}
-Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
-For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
-$A_V=0$, and such that the ridge line 
-has close to constant $R^T_V$.
-\color{black}
-With this ansatz, we
-estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
- \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
-With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
-We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
-of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
-A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
-for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
-\color{black}
-
+%\begin{comment}
+%\color{blue}
+%Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
+%For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
+%$A_V=0$, and such that the ridge line 
+%has close to constant $R^T_V$.
+%\color{black}
+%With this ansatz, we
+%estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
+% \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
+%With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
+%We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
+%of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
+%A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
+%for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
+%\color{black}
+%
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
    \centering
-   \includegraphics[width=2.8in]{output11/avebv.pdf}
-   \includegraphics[width=2.8in]{output11/rv.pdf}
+   \includegraphics[width=5.2in]{output11/avebv.pdf}
+   %\includegraphics[width=2.8in]{output11/rv.pdf}
    \caption{
 	\color{red}
-   Left: $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data. Right: Shown for qualitative purposes,
-   $R^T_V=A^T_V/E^T(B-V)$ 
-   versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
+   $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
+   %Right: Shown for qualitative purposes,
+   %$R^T_V=A^T_V/E^T(B-V)$ 
+   %versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
    %Overplotted is the mean and standard deviation of those points in equally divided bins.
-   On both plots are overplotted the expected values for the \citetalias{1999PASP..111...63F} model
-   for specific choices of $R^F_V$, normalized to have $A_V=0$ at $E(B-V)=0$.  Note that these lines are not straight on the left plot, and are not constant on the plot to the right.
+   Overplotted the expected values for the \citetalias{1999PASP..111...63F} model
+   for specific choices of $R^F$.  Note that these lines are not straight on the left plot.
    \color{black}
@@
 \end{figure}
-
-Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
-parameters of a single  dust model.
-\color{red}
-Our model for broadband photometry does not specify how spectral features and color parameters affect the supernova spectrum, information
-necessary to predict the magnitude extinction of dust models.
-\color{blue}
-The lack of correspondence between dust models and broadband extinction is quantified when we apply an $R^F_V=2.5$ SN-frame dust to the
-observed spectra used in our sample, to yield a distribution in the quantity $R_V=A_V/(A_B-A_V)$ with mean and standard deviation of $3.11 \pm 0.35$.
-While an accurate study of fundamental dust properties would incorporate the dust law within the model itself, we now proceed nonetheless
-in making a connection between our model outputs and dust.
-
-\color{red}
-Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R^T_V$ for $R^F_V=1.1, 1.9, 2.5, 3.1$
-within the context of the \citetalias{1999PASP..111...63F} model.
-Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
-non-linear, and $R^T_V$ is not constant for a fixed value of $R^F_V$.
-\color{black}
+%\end{comment}
+
+We now compare our model and its color-parameters $k_0$ and $k_1$ with the expectations of  dust laws,
+in contrast to  empirical properties derived from our model.
+A direct analysis of the  \citetalias{1999PASP..111...63F} dust model is presented later
+in \S\ref{model0:sec}.
+
+%Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
+%parameters of a single  dust model.
+%\color{red}
+%Our model for broadband photometry does not specify how spectral features and color parameters affect the supernova spectrum, information
+%necessary to predict the magnitude extinction of dust models.
+%\color{blue}
+%The lack of correspondence between dust models and broadband extinction is quantified when we apply an $R^F_V=2.5$ SN-frame dust to the
+%observed spectra used in our sample, to yield a distribution in the quantity $R_V=A_V/(A_B-A_V)$ with mean and standard deviation of $3.11 \pm 0.35$.
+%While an accurate study of fundamental dust properties would incorporate the dust law within the model itself, we now proceed nonetheless
+%in making a connection between our model outputs and dust.
 
@@
 for the case of
-$R^F_V=2.5$ and $A^F_V=0.1$,
+$R^F=2.5$ and $A^F_V=0.1$,
 and the measurement of the updated
@@
 \color{black}
-This linear approximation
-is good in the ranges of
-\color{red}
- $R^F_V$ and $A^F_V$,
-\color{black}
-and wavelengths under consideration, in that the values of the components  vary by $<5$\%.
+Over the ranges of
+\color{red}
+ $R^F$ and $A^F_V$,
+\color{black}
+and wavelengths under consideration,  the values of the components  vary by $<5$\%.
 
@@
 Our median-fit values for the $\gamma$ coefficients,
-$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.78,   3.88,   2.88,   2.21,   1.59\}$ and
-$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.85,   -4.69,   -5.69,  -5.33,  -4.77\}$,
+%---- fitz11.py
+$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
+$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
+%----
 \color{black}
@@
 
+\color{red}
+Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$ for $R^F=1.1, 1.9, 2.5, 3.1$
+within the context of the \citetalias{1999PASP..111...63F} model.
+Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
+non-linear.
+Qualitatively, the $R^F \sim 2.4$  most closely matches our linear model fit.  
+\color{black}
+
 The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our the individual supernova
@@
    \centering
-   \includegraphics[width=2.8in]{output15/ebv.pdf}
-   \includegraphics[width=2.8in]{output15/ebv_delta.pdf}
+   \includegraphics[width=2.8in]{output23/ebv.pdf}
+   \includegraphics[width=2.8in]{output23/ebv_delta.pdf}
       \caption{Left: Ideograms of the external $E(B-V)$ and
@@
    \centering
-   \includegraphics[width=4.5in]{output15/delta_corner.pdf}
+   \includegraphics[width=4.5in]{output23/delta_corner.pdf}
    \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
@@
    \centering
-      \includegraphics[width=5.5in]{output15/deltaratio.pdf}
+      \includegraphics[width=5.5in]{output23/deltaratio.pdf}
    \caption{Significance of the non-zero values of $\delta$ seen through $\delta_X/\delta_I-1$, which is insensitive to the $\pm$ sign degeneracy.
@@
    \centering
-   \includegraphics[width=5.5in]{output15/perobject_corner.pdf} 
+   \includegraphics[width=5.5in]{output23/perobject_corner.pdf} 
    \caption{
@@
 \color{black}
+
+\section{Supernova Model 0: Fitzpatrick Dust}
+\label{model0:sec}
+We analyze our data with a model that incorporates attenuation due to host-galaxy dust.
+The dust model of  \citet{1999PASP..111...63F} is considered:
+while commonly used dust
+models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
+does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.
+
+The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R$ and $E(B-V)$.  The first, $R$,
+specifies the wavelength-dependent  attenuation  notated by the function $A/E(B-V)$.  The second, $E(B-V)$, specifies the normalization
+of that attenuation.  The dust model is expressed as
+\begin{equation}
+A(\lambda; E(B-V), R) = E(B-V) \frac{A}{E(B-V)}\left(\lambda; R \right).
+\end{equation}
+Those two parameters can be combined to define a third dependent parameter $A_V \equiv R E(B-V)$.
+
+In the broadband photometry of a source with SED $f(\lambda)$ observed in a filter with transmission $X$, the attenuation $A_X$ is
+\begin{equation}
+A_X\left(A_V, E(B-V)  \right) = 2.5 \log{\left(\frac{\int d\lambda f(\lambda) X(\lambda)}{\int d\lambda 10^{-0.4 A\left(\lambda; E(B-V), R=\frac{A_V}{E(B-V)}\right)} f(\lambda) X(\lambda)}\right)},
+\end{equation}
+which is to first order
+\begin{equation}
+A_X\left(A_V, E(B-V)  \right) = \frac{\int d\lambda A\left(\lambda; E(B-V), R=\frac{A_V}{E(B-V)}\right)f(\lambda) X(\lambda)}{\int d\lambda f(\lambda) X(\lambda)}.
+\end{equation}
+
+In our model for broadband magnitudes, the SEDs of supernovae $f(x)$ are not specified.  In its place we use the 
+updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
+SALT2 template yields similar results.)
+For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
+$0\le A_V \le 1.8$, $1 \le R \le 8$ with a third-order polynomial in $A_V$ and $E(B-V)$.  The residuals between the model and
+the approximation for $A_V=1.8$ are  shown in Figure~\ref{dfitz:fig}.  The amplitude residuals in $B$ through
+$I$ are $< 0.001$ mag; in $U$  for $R>1$ the residuals are $<0.004$ mag
+and increase to $0.01$ mag as $R$ decreases to $1$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.5in]{output18/dfitz.pdf}
+    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
+    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
+   \label{dfitz:fig}}
+\end{figure}
+
+Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first, $R$ is held the same for all supernovae (labeled
+as $R=const$).  In the second,
+the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$ (labeled as $\ln{R} \sim \mathcal{N}$).
+In the third, $A_V$ and $R$ are free for
+each supernova, with a uniform prior $0\le A_V \le 1.8$, $1 \le R \le 8$ (labeled as $R$-free).
+
+The posteriors for the spectral parameters are similar to the ones already
+presented; we therefore focus on the posteriors for the dust parameters, the results of which
+are shown in Figure~\ref{AVRV:fig}.  The left plot shows histograms for the median $A_V$ determined for
+each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a normal distribution, and $R$ from a uniform distribution $1 \le R \le 8$.
+The right plot shows the posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
+the median $R$ determined for each supernova in the $R$-free analysis.  (The  $\ln{R} \sim \mathcal{N}$-case draws $R$ from
+the Normal distributions specified by individual links.)
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
+   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
+    \caption{Left: Histograms for the median $A_V$ determined for
+each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a Normal distribution, and $R$ from a uniform distribution $1 \le R \le 8$.
+Right: Posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
+the median $R$ determine for each supernova in the $R$-free analysis.
+   \label{AVRV:fig}}
+\end{figure}
+
+Both the distributions in $A_V$ and $R$ are dependent on the assumptions on the distribution of $R$.
+The mode in the $A_V$ histogram shifts from $\sim 0.2$ mag 
+for the $R$-free case, to $\sim 0.4$ mag for  $R=const$, and to $\sim 0.6$ for  $\ln{R} \sim \mathcal{N}$.
+The  posterior of $R$ is skinnier and biased for $R=const$ relative to the $R$ distributions found by the $R$-free and  $\ln{R} \sim \mathcal{N}$
+cases.
+
+The distributions of $A_V$ and $R$ are not as one would expect for an $R=3.1$ Milky Way dust.  While the $R=const$ case give $R \sim 3.5$, its
+distribution of $A_V$ has a slower rise from zero and a non-zero mode of $\sim 0.4$ mag, inconsistent with the expectation of a large fraction of supernovae
+experiencing no dust, with a tail in $A_V$ for those that do \citep{1998ApJ...502..177H}.
+The $\ln{R} \sim \mathcal{N}$ distribution for $A_V$ is shifted and a mode of  $R$
+larger that $4$.
+While for $R$-free the  $A_V$ distribution mode is centered somewhat closer to zero, the distribution of $R$ is shifted to even higher values.
+
+The Hsiao template does not perfectly represent the underlying spectrum of a supernova.  Consider the SED to be the sum of the template and an offset
+\begin{equation}
+f(\lambda) = f_0(\lambda) + \delta f(\lambda).
+\end{equation}
+To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
+extinction.  Heterogeneity in the true spectrum amongst supernovae yield scatter in those corrections.
 
@@
    \centering
-   \includegraphics[width=2.8in]{output15/x1si.pdf}
-   \includegraphics[width=2.8in]{output15/x1D.pdf}
+   \includegraphics[width=2.8in]{output23/x1si.pdf}
+   \includegraphics[width=2.8in]{output23/x1D.pdf}
     \caption{Left: SALT2 $x_1$ versus $EW_{Si}$.  Right: $x_1$ versus $A_{\delta I}  = \delta_I D$.
@@
    \centering
-   \includegraphics[width=5.5in]{output15/residualx1.pdf}
+   \includegraphics[width=5.5in]{output23/residualx1.pdf}
     \caption{Differences between observed colors and the colors predicted from the analysis, as a function
@@
    \centering
-   \includegraphics[width=2.8in]{output15/rigault3.pdf}
-s     \includegraphics[width=2.8in]{output15/rigault2.pdf}
+   \includegraphics[width=2.8in]{output23/rigault3.pdf}
+s     \includegraphics[width=2.8in]{output23/rigault2.pdf}
       \caption{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host mass.  Hosts too faint for a mass measurement

### 2016-12-18 fitz11.py

@@ -74,7 +74,7 @@ c_n = []
 cs = []
 for s in ['gamma','rho1']:
   c, cmin, cmax = numpy.percentile(fit[s]/((fit[s][:,1]-fit[s][:,2])[:,None]),(50,50-34,50+34),axis=0)
-  print c
+  print "{:6.2f}, {:6.2f}, {:6.2f}, {:6.2f}, {:6.2f}".format(c[0],c[1],c[2],c[3],c[4])
   cs.append(c)
   c_norm = numpy.linalg.norm(c)
   c_n.append(c_norm)
@@ -189,7 +189,8 @@ sm = pystan.StanModel(file='rv.stan')
 fit1 = sm.sampling(data=data, iter=1000, chains=4,init=[init1,init1,init1,init1])
 links = fit1.extract(('x1','x0'))
 rbv, mrbv, prbv= numpy.percentile([links['x1'],links['x0']],(50,50-34,50+34),axis=1)
-
+print "Fit RV"
+print "${:6.2f}_{:6.2f}^{:6.2f}$".format(rbv[0],rbv[0]-mrbv[0],prbv[0]-rbv[0])
 # # RV is calculated as a Monte Carlo, i.e RV is calculated for each link
 # coeffs = []
 # for i in xrange(ebv.shape[1]):
@@ -217,7 +218,7 @@ for rbv_ in rbvs:
     A1= f99_band.A_X(r_v=rbv_, ebv=ebv)
     x.append(A1[1]-A1[2])
     y.append(A1[2])
-  plt.plot(x,y,label=r'$R^F_V={:6.1f}$'.format(rbv_))
+  plt.plot(x,y,label=r'$R^F={:6.1f}$'.format(rbv_))
 plt.legend(loc=2)
 plt.xlim((-0.1,0.4))
 plt.ylim((-0.7,1.2))
@@ -273,7 +274,7 @@ for rbv in rbvs:
     A1= f99_band.A_X(r_v=rbv, ebv=ebv)
     x.append(A1[1]-A1[2])
     y.append(A1[2]/(A1[1]-A1[2]))
-  plt.plot(x,y,label=r'$R^F_V={:6.1f}$'.format(rbv))
+  plt.plot(x,y,label=r'$R^F={:6.1f}$'.format(rbv))
 plt.xlim((-0.02,0.45))
[…]

### 2016-12-18 table11.py

@@ -181,9 +181,9 @@ mag_cov=mag_cov[use]
 #   print s,a,b
 
 
-# snname=numpy.array(data['snlist'])[use]
+snname=numpy.array(data['snlist'])[use]
 
-# for i in xrange(len(sivel)):
-#     print '{0} & ${1:5.1f} \pm {2:3.1f}$ & ${3:5.1f} \pm {4:3.1f}$& ${7:5.0f} \pm {8:3.0f}$ & ${5[0]:6.2f} \pm {6[0]:6.2f}$ & ${5[1]:6.2f} \pm {6[1]:6.2f}$& ${5[2]:6.2f} \pm {6[2]:6.2f}$& ${5[3]:6.2f} \pm {6[3]:6.2f}$& ${5[4]:6.2f} \pm {6[4]:6.2f}$ \\\\'.format(snname[i], EW_obs[i,0], numpy.sqrt(EW_cov[i,0,0]),
-#         EW_obs[i,1], numpy.sqrt(EW_cov[i,1,1]), mag_obs[i,:], numpy.sqrt(numpy.diagonal(mag_cov[i,:,:])),sivel[i],sivel_err[i])
+for i in xrange(len(sivel)):
+    print '{0} & ${1:5.1f} \pm {2:3.1f}$ & ${3:5.1f} \pm {4:3.1f}$& ${7:5.0f} \pm {8:3.0f}$ & ${5[0]:6.2f} \pm {6[0]:6.2f}$ & ${5[1]:6.2f} \pm {6[1]:6.2f}$& ${5[2]:6.2f} \pm {6[2]:6.2f}$& ${5[3]:6.2f} \pm {6[3]:6.2f}$& ${5[4]:6.2f} \pm {6[4]:6.2f}$ \\\\'.format(snname[i], EW_obs[i,0], numpy.sqrt(EW_cov[i,0,0]),
+        EW_obs[i,1], numpy.sqrt(EW_cov[i,1,1]), mag_obs[i,:], numpy.sqrt(numpy.diagonal(mag_cov[i,:,:])),sivel[i],sivel_err[i])
 

### 2016-12-21 apj.tex
new version for limited viewing

@@
 confidence.
-The two color parameters exhibit the behavior expected from the two-parameter
-\citet{1999PASP..111...63F} dust model.
 The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
 Extending the model to three color parameters gives almost identical results for
-the two parameters
+all the parameters in common,
 plus a detection of a third parameter at
 %--- table.py
-$>95$\% confidence;
+$(1-5\times10^{-4})$
 %-----
+confidence;
 this new parameter is responsible for supernova color diversity
@@
 Our analysis sample is comprised by the
-168
+172
 supernovae that have the data coverage to 
@@
 color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
-$C_c$.  For $N=168$ supernovae, there are 1344 observables and 1043 top-level parameters.
+$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level parameters.
 \color{black}
@@
 The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo as implemented in
-STAN \citep{stan}.  We run four chains, each with 10000 iterations of which
+STAN \citep{stan}.  We run eight chains, each with 5000 iterations of which
 half are used for warmup.
@@
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
-Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig}, \ref{global2:fig}, \ref{global3:fig}, \ref{global4:fig},
-\ref{global5:fig}.  We find no evidence that
+Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig} -- \ref{global5:fig}.  We find no evidence that
 the Monte Carlo chains have not converged to the stationary posterior distribution.
 We have rurun the analysis with a variety of initial conditions, including one with all the $\gamma$'s equal to zero, except for a small positive 
-$\gamma^0_0$ and small negative $\gamma^1_0$ to satisfy our limit conditions.  Parameter credible intervals
-remain consistent within the 68\% credible intervals.
+$\gamma^0_0$ and small negative $\gamma^1_0$; the 68\% credible intervals
+remain consistent.
 
@@
    \centering
-   \includegraphics[width=5.5in]{output11/coeff0.pdf} 
+   \includegraphics[width=5.2in]{output11/coeff0.pdf} 
             \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
@@
    \centering
-   \includegraphics[width=5.5in]{output11/coeff1.pdf} 
+   \includegraphics[width=5.2in]{output11/coeff1.pdf} 
             \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $B$ band.
@@
    \centering
-   \includegraphics[width=5.5in]{output11/coeff2.pdf} 
+   \includegraphics[width=5.2in]{output11/coeff2.pdf} 
             \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $V$ band.
@@
    \centering
-      \includegraphics[width=5.5in]{output11/coeff3.pdf} 
+      \includegraphics[width=5.2in]{output11/coeff3.pdf} 
             \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $R$ band.
@@
    \centering
-         \includegraphics[width=5.5in]{output11/coeff4.pdf} 
+         \includegraphics[width=5.2in]{output11/coeff4.pdf} 
             \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $I$ band.
@@
    \centering
-   \includegraphics[width=5.5in]{output11/residual.pdf} 
+   \includegraphics[width=5.2in]{output11/residual.pdf} 
             \caption{Predicted versus observed colors.  Overplotted is a line with slope equal to one.
@@
    \centering
-   \includegraphics[width=5.5in]{output11/Delta_hist.pdf} 
+   \includegraphics[width=5.2in]{output11/Delta_hist.pdf} 
    \caption{Ideogram for the grey offset $\Delta$.  This and other ideograms plotted in this article are normalized to have unit area.
@@
 0.068 & 0.034 & 0.023 & 0.053
-  \end{pmatrix} \text{mag}
+  \end{pmatrix} \text{mag},
  \label{color_sd:eqn}
@@
    \centering
-   \includegraphics[width=5.5in]{output11/perobject_corner.pdf} 
+   \includegraphics[width=5.2in]{output11/perobject_corner.pdf} 
    \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
@@
  between
-$E_\gamma(B-V)$ and $EW_{Si}$.
+$E_{\gamma^0}(B-V)$ and $EW_{Si}$.
 Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
@@
 \subsection{The Two Extrinsic Parameters $k_0$ and $k_1$}
+\color{blue}
 The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
@@
 
-\color{blue}
-Recall that there are degeneracies between the intrinsic (Eqn.~\ref{ewsiv:eqn}) and
-extrinsic (Eqn.~\ref{dust:eqn}) parameters of our model.  Part of that degeneracy is
-broken by imposing $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$,
-but this choice does not specify the $k_0^0$, $k_1^0$ corresponding to supernovae experiencing no extrinsic effects.  The true extrinsic
+There is a pair of parameter values,  $k_0^0$ and $k_1^0$, that correspond to supernovae experiencing no extrinsic effect.
+The true extrinsic
 extinction is
@@
 The true extrinsic color excess is $E^T(B-V) = A^T_B-A^T_V$, so that the total-to-selective extinction is $R^T_V=A^T_V/E^T(B-V)$.
-Our model as analyzed cannot directly determine the above extrinsic properties per supernova.
+Our $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$ constraints
+do not determine $k_0^0$ and $k_1^0$, and so the extrinsic extinction and color excess per supernova are not products of our analysis.
+
+%our analysis does not specify their values.
+%Recall that there are degeneracies between the intrinsic (Eqn.~\ref{ewsiv:eqn}) and
+%extrinsic (Eqn.~\ref{dust:eqn}) parameters of our model.  Part of that degeneracy is
+%broken by imposing $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$,
+%but this choice does not specify the parameter values.
 
 Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
-written as
+rearranged as
 $$A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
 $$
-Making the assumption that $R^T_V$ is the same for all supernovae (shown later to be approximately true for dust laws),
-it can be determined as the slope of the relation between $A_X$ and $E(B-V)$.
-\color{black}
-Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
-which a linear fit gives a slope of
-%----- fitz11.py
-$R_V=2.77 \pm 0.08$.
-%----
-\color{blue}
-The slope uncertainties are the $68$\% credible interval from the Bayesian analysis and does not incorporated goodness
- of fit.  Indeed,
-the full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
+Making the assumption that it is the same for all supernovae ,
+ $R^T_V$  can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.
+
+Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$.
+The full set of supernovae does not coincide with the expectations of a single linear law; rather the supernova population is peaked
 on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
 but can have values that extend toward lower values.
+The assumption of a constant $R^T_V$ is not altogether correct; still we perform a linear fit that gives a slope of
+%----- fitz11.py
+$R^T_V=2.77 \pm 0.08$,
+%----
+where the uncertainty is the $68$\% credible interval and does not include goodness
+ of fit.
 
@@
    \caption{
-	\color{red}
    $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
@@
    Overplotted the expected values for the \citetalias{1999PASP..111...63F} model
-   for specific choices of $R^F$.  Note that these lines are not straight on the left plot.
-   \color{black}
+   for specific choices of $R^F$. Note that these lines are not straight, which is apparent when comparing to the straight black $R_V=2.78$ line.
    \label{avebv:fig}}
@@
 
-We now compare our model and its color-parameters $k_0$ and $k_1$ with the expectations of  dust laws,
-in contrast to  empirical properties derived from our model.
+We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust laws.
 A direct analysis of the  \citetalias{1999PASP..111...63F} dust model is presented later
@@
 
-The \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
+The 2-parameter linear model
 \begin{equation}
-A_X = a(X)  A_V + b(X) E(B-V).
+A_X = a(X)  A_V + b(X) E(B-V)
 \label{f99:eqn}
 \end{equation}
-The \citetalias{1999PASP..111...63F} model is approximately described by a linear model with
-the above form:
-\color{red}
-for the case of
+approximately describes dust laws.
+For the case of
 $R^F=2.5$ and $A^F_V=0.1$,
 and the measurement of the updated
-\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak as seen through our synthetic passbands,
-$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ 
-\color{black}
+\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
+gives
+$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$.
+The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
 Over the ranges of
-\color{red}
  $R^F$ and $A^F_V$,
-\color{black}
-and wavelengths under consideration,  the values of the components  vary by $<5$\%.
+and the wavelengths under consideration,  the values of the components  vary by $<5$\%.
 
@@
 \begin{equation}
-A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
+A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
 \end{equation}
-\color{red}
 Our median-fit values for the $\gamma$ coefficients,
@@
 %----
-\color{black}
-can expressed in terms of the $a(X)$ and $b(X)$ vectors:
+can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors, and a residual vectors perpendicular to $a$ and $b$.
+The result is
 \begin{equation}
@@
 \end{equation}
-where the two residual vectors are
-\color{red}
+where the two residual vectors
 \begin{align}
 \vec{\epsilon}_a &=\{0.14, -0.15, -0.07,  0.04, 0.07\}, \\
-\vec{\epsilon}_b & =\{0.12, -0.06, -0.30, 0.30, -0.06\}:
+\vec{\epsilon}_b & =\{0.12, -0.06, -0.30, 0.30, -0.06\}
 \end{align}
-\color{black}
-both are perpendicular to $a(X)$ and $b(X)$ and
 contribute  3\% and 4\% respectively to the total  length of the $\gamma$ vectors.
 This result indicates that
-the allowed variation of $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are almost identical.
-
-\color{red}
-To help visualize the above result, Figure~\ref{plane:fig} shows two perspectives in $UVI$-space
+the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.
+
+To visualize the above result, Figure~\ref{plane:fig} shows two perspectives in $UVI$-space
 of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model,
 and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model.
-The left plot shows that none of the four vectors are closely aligned with another, while the right plot shows that
+The left plot shows that the four vectors point in different directions, while the right plot shows that
 the planes defined by our model (solid lines) and the  \citetalias{1999PASP..111...63F} model (dashed lines) are nearly coplanar.
 
-\color{blue}
-Recall that degeneracies in the values of $\gamma$ and $k$ are broken by the prior that $k_0$, $k_1$, and the other SN parameters are uncorrelated. 
-The combination  $\left(a(X) + \frac{b(X)}{2.4}\right)$ is
+The specific directions of $\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}$ and
+$\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}$ within the plane they define are not arbitrary, but are determined by the prior that
+$k_0$ and  $k_1$ are uncorrelated. 
+In order to understand these directions in the context of the dust model,
+we
+rewrite the \citetalias{1999PASP..111...63F} model in Eqn.~\ref{f99:eqn} as
+\begin{equation}
+A_X =  A_V^F\left(a(X)+\frac{b(X)}{r} \right) +  \left( E^F(B-V) - \frac{ A_V^F}{r}\right)b(X).
+\end{equation}
+Assigning $r=2.4$, we find that the combination  $\left(a(X) + \frac{b(X)}{2.4}\right)$ is
 almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ while $b$ alone is almost perfectly aligned with $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$,
-as shown in the dot-dashed and dotted lines of  Figure~\ref{plane:fig}.
-Rewriting the \citetalias{1999PASP..111...63F} model in Eqn.~\ref{f99:eqn} as
-\begin{equation}
-A_X =  A_V^F\left(a(X)+\frac{b(X)}{2.4} \right) +  \left(\frac{ A_V^F}{R^F_V} - \frac{ A_V^F}{2.4}\right)b(X),
-\end{equation}
-we see the correspondence between $k_0$ with $A^F_V$, and $k_1$ with $\frac{A^F_V}{R^F_V}-\frac{A^F_V}{2.4}$.
-Reasoning in the opposite direction, our results are motivated by a prior that ultimately turned out to be, based on our ultimate solution, 
-\begin{align}
-\text{cov}\left(A^F_V, \frac{A^F_V}{R^F_V}\right) & = \frac{1}{2.4} \text{var}(A^F_V).
-\end{align}
-Independent variations in $A^F_V$ and  $A^F_V/R^F_V$ within the data allowed the data analysis to detect
-$\gamma^{0,1}$ and $k_{0,1}$ at high significance.
-\color{black}
+as shown in the dot-dashed and dotted lines of  Figure~\ref{plane:fig}.  This implies a correspondence of $k_0$ with $A^F_V$,
+and $k_1$ with $  \left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$.
+Our prior of a non-correlation between $k_0$ and $k_1$ has lead to an $r \sim 2.4$  that optimizes the
+non-correlation between $A^F_V$ and $  \left( E^F(B-V) - \frac{ A_V^F}{r}\right)$.
 
@@
    \caption{
-   \color{red}
    Two different perspectives in $UVI$-space of the vectors $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
@@
    almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$.  
-   \color{black}
    \label{plane:fig}}
@@
 
-\color{black}
-
+Given the association of  our parameter $\gamma^0_2 k_0$ with the $A^F_V$ of an $R^F \sim 2.4$ dust model ,
+the former's distribution can be compared to the expectation for the latter.
+Figure~\ref{k0_med:fig} shows the histogram of
+median values of $\gamma^0_2 k_0$.
+The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red, consistent
+with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
+
+Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_2 k_1$, which is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
+extinction corrections due to deviations away from the $R=2.4$ value.   The distribution has a long
+negative tail and is peaked at its positive edge, and by construction has a mean of zero.
+The implication is that while the bulk of supernovae have positive values associated with $R>2.4$, there is a tail
+of negative values associated with $R<2.4$.  The plot of   $\gamma^0_2 k_0$ versus $\gamma^1_2 k_1$  shown in Figure~\ref{kk:fig} shows that
+the positive edge in $\gamma^1_2 k_1$ persists over the full range of  $\gamma^0_2 k_0$. On the other hand, lower values of $\gamma^1_2 k_1$
+occur at larger values of  $\gamma^0_2 k_0$.
+These findings are consistent with previous results:
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
+\citet{2011ApJ...729...55F} and the above authors
+find that supernovae with large extinction 
+preferentially exhibit low $R^F$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/gamma0_med.pdf}
+   \includegraphics[width=2.8in]{output11/gamma1_med.pdf}
+      \caption{ Histogram of
+median values of Left: $\gamma^0_2 k_0$, which is associated with the $A^F_V$ of an $R^F \sim 2.4$ dust model; Right: $\gamma^1_2 k_1$,
+which  is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
+extinction corrections due to deviations away from the $R=2.4$ value.
+   \label{k0_med:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output11/kk.pdf}
+      \caption{ $\gamma^0_2 k_0$ versus $\gamma^1_2 k_1$.
+   \label{kk:fig}}
+\end{figure}
 %
@@
 
-\color{red}
-Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$ for $R^F=1.1, 1.9, 2.5, 3.1$
-within the context of the \citetalias{1999PASP..111...63F} model.
+Another comparison between our model predictions with those of dust is presented in
+Figure~\ref{avebv:fig}, which shows the expectations for measured $A(V)$, $E(B-V)$ for $R^F=1.1, 1.9, 2.5, 3.1$.
 Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
@@
 Qualitatively, the $R^F \sim 2.4$  most closely matches our linear model fit.
+
+The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our  supernova
+parameters translate to  \citetalias{1999PASP..111...63F} parameters with consistent distributions, lead us to conclude that 
+$\{k_0, k_1\}$, describe for the most part the $\{ E(B-V), R\}$ parameters used
+in standard models of Milky Way dust.
 \color{black}
-
-The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our the individual supernova
-parameters translate to  \citetalias{1999PASP..111...63F} parameters consistent with a distribution expected for a narrow range of $R^F_V$, lead us to conclude that 
-$\{k_0, k_1\}$, describe, for the most part the $\{ E(B-V), R_V\}$ parameters used
-in standard models of Milky Way dust.
 
@@
 \label{sn2014j:sec}
-
 SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
@@
    \centering
-   \includegraphics[width=5.5in]{output11/sn2014j.pdf} 
+   \includegraphics[width=5.2in]{output11/sn2014j.pdf} 
    \caption{Measured color excess for SN~2014J and the best-fit predictions from this article. 
@@
 %----
-$x_0= 2.65$, $ x_1=-1.64$ with covariance
+$x_0= 2.60$, $ x_1=-1.89$ with covariance
 %----
@@
 \begin{array}{rr}
-0.048 & 0.047 \\
-0.047 & 0.248
+0.050 & 0.058 \\
+0.058 & 0.315
 \end{array}
@@
 %----
-$E_{\gamma^0}(B-V)=  0.92 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.28 \pm   0.08$
+$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
 %-----
@@
 color parameters, $(N-1)$ magnitude offsets,  $5 \times 7$ global coefficients, and $10$ parameters that describe the intrinsic
-$C_c$.  For $N=168$ supernovae, there are 1344 observables and 1214 top-level parameters.
+$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1242 top-level parameters.
 \color{black}
@@
 so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
+\color{blue}
+We apply the condition $\delta_4>0$ to break this degeneracy,
+and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
+\color{black}
 In the running of the Monte Carlo, the initial conditions for
@@
 results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
-are consistent well within 1$\sigma$ uncertainties.  The most significant changes of note are in the standard
-deviations of the residuals in the $V$ and $I$ bands, which are now reduced.
+are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the slight reduction of the standard
+deviations of the magnitude residuals.
 The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust law, in that now
@@
 \begin{array}{rr}
-1.22 & 2.75 \\
-0.80 & -5.51
+1.22 & 2.73 \\
+0.77 & -4.98
 \end{array}
@@
 \begin{align}
-\vec{\epsilon}_a &=\{0.13, -0.15, -0.07,  0.04,  0.06\},\\
-\vec{\epsilon}_b &=\{ 0.10, -0.04,  -0.28,  0.31, -0.09\}
+\vec{\epsilon}_a &=\{0.13, -0.15, -0.06,  0.04,  0.06\},\\
+\vec{\epsilon}_b &=\{ -0.04, 0.09,  -0.18,  0.28, -0.19\}
 \end{align}
@@
 &
-$0.0044^{+0.0009}_{-0.0009}$
-&
-$0.0016^{+0.0007}_{-0.0007}$
-&
-$0.0016^{+0.0006}_{-0.0006}$
+$0.0045^{+0.0009}_{-0.0010}$
+&
+$0.0017^{+0.0008}_{-0.0008}$
+&
+$0.0015^{+0.0006}_{-0.0006}$
 &
@@
 &
-$0.0026^{+0.0005}_{-0.0005}$
+$0.0027^{+0.0005}_{-0.0005}$
 \\
@@
 &
-$   1.8^{+   0.9}_{  -0.4}$
-&
-$   0.0^{+   0.1}_{  -0.2}$
-&
-\ldots
-&
-$  -0.0^{+   0.1}_{  -0.1}$
-&
-$   0.6^{+   0.6}_{  -0.3}$
+$   1.9^{+   1.1}_{  -0.5}$
+&
+$   0.1^{+   0.1}_{  -0.2}$
+&
+$ \ldots$
+&
+$   0.0^{+   0.1}_{  -0.1}$
+&
+$   0.8^{+   0.8}_{  -0.3}$
 \\
@@
 &
-$ 0.032^{+ 0.003}_{-0.003}$
-&
-$ 0.025^{+ 0.002}_{-0.003}$
-&
-$ 0.025^{+ 0.002}_{-0.002}$
+$ 0.033^{+ 0.003}_{-0.003}$
+&
+$ 0.026^{+ 0.002}_{-0.002}$
+&
+$ 0.026^{+ 0.002}_{-0.002}$
+&
+$ 0.021^{+ 0.002}_{-0.002}$
 &
 $ 0.020^{+ 0.002}_{-0.002}$
-&
-$ 0.019^{+ 0.002}_{-0.002}$
 \\
@@
 &
-$  0.26^{+  0.05}_{ -0.05}$
-&
-$ -0.01^{+  0.03}_{ -0.03}$
-&
-\ldots
-&
-$ -0.19^{+  0.01}_{ -0.02}$
+$  0.25^{+  0.04}_{ -0.05}$
+&
+$ -0.01^{+  0.02}_{ -0.03}$
+&
+$  \ldots$
+&
+$ -0.19^{+  0.01}_{ -0.01}$
 &
@@
 &
-$-0.0002^{+0.0012}_{-0.0011}$
-&
-$0.0000^{+0.0010}_{-0.0009}$
-&
-$0.0005^{+0.0008}_{-0.0008}$
-&
-$0.0005^{+0.0007}_{-0.0007}$
-&
-$-0.0003^{+0.0006}_{-0.0006}$
+$0.0002^{+0.0012}_{-0.0012}$
+&
+$0.0002^{+0.0010}_{-0.0010}$
+&
+$0.0007^{+0.0008}_{-0.0008}$
+&
+$0.0007^{+0.0007}_{-0.0007}$
+&
+$0.0000^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.40^{+  2.19}_{ -1.84}$
-&
-$ -0.36^{+  1.57}_{ -1.19}$
-&
-\ldots
-&
-$ -0.12^{+  0.27}_{ -0.25}$
-&
-$ -0.89^{+  1.72}_{ -1.35}$
+$ -0.25^{+  1.35}_{ -1.38}$
+&
+$ -0.34^{+  1.21}_{ -1.04}$
+&
+$  \ldots$
+&
+$ -0.05^{+  0.34}_{ -0.29}$
+&
+$ -0.70^{+  0.84}_{ -0.88}$
+\\
+$\gamma^0_X$
+&
+$ 64.01^{+  3.79}_{ -3.69}$
+&
+$ 51.96^{+  3.18}_{ -3.10}$
+&
+$ 38.49^{+  2.70}_{ -2.63}$
+&
+$ 29.38^{+  2.40}_{ -2.33}$
+&
+$ 20.86^{+  2.19}_{ -2.22}$
 \\
@@
 &
-\ldots
-&
-$ -0.23^{+  0.01}_{ -0.01}$
-&
-$ -0.45^{+  0.03}_{ -0.03}$
+$  \ldots$
+&
+$ -0.24^{+  0.01}_{ -0.02}$
+&
+$ -0.46^{+  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+&
+$-10.18^{+  3.53}_{ -3.92}$
+&
+$-11.64^{+  2.95}_{ -3.23}$
+&
+$-14.42^{+  2.45}_{ -2.72}$
+&
+$-13.73^{+  2.09}_{ -2.31}$
+&
+$-12.70^{+  2.03}_{ -2.16}$
 \\
@@
 &
-$ -0.30^{+  0.18}_{ -0.19}$
-&
-$ -0.17^{+  0.09}_{ -0.10}$
-&
-\ldots
-&
-$ -0.06^{+  0.05}_{ -0.04}$
-&
-$ -0.16^{+  0.10}_{ -0.08}$
+$ -0.29^{+  0.16}_{ -0.18}$
+&
+$ -0.19^{+  0.09}_{ -0.10}$
+&
+$  \ldots$
+&
+$ -0.05^{+  0.05}_{ -0.04}$
+&
+$ -0.12^{+  0.10}_{ -0.09}$
+\\
+$\delta_X$
+&
+$  2.07^{+  0.69}_{ -0.74}$
+&
+$ -2.25^{+  0.78}_{ -0.66}$
+&
+$ -1.85^{+  0.63}_{ -0.60}$
+&
+$  0.41^{+  0.53}_{ -0.57}$
+&
+$  2.02^{+  0.97}_{ -1.08}$
 \\
@@
 &
-$ -0.61^{+  0.47}_{ -0.18}$
-&
-$ -1.21^{+  0.25}_{ -0.77}$
-&
-$ -1.76^{+  0.16}_{ -0.20}$
-&
-$ -1.17^{+  0.29}_{ -0.20}$
-&
-\ldots
+$  0.04^{+  0.52}_{ -0.27}$
+&
+$ -2.09^{+  0.27}_{ -0.62}$
+&
+$ -1.92^{+  0.25}_{ -0.56}$
+&
+$ -0.80^{+  0.68}_{ -0.26}$
+&
+$\ldots$
 \\
@@
 &
-$ 0.059^{+ 0.013}_{-0.013}$
-&
-$ 0.031^{+ 0.007}_{-0.008}$
-&
-$ 0.017^{+ 0.005}_{-0.007}$
-&
-$ 0.012^{+ 0.006}_{-0.007}$
-&
-$ 0.039^{+ 0.005}_{-0.005}$
+$ 0.053^{+ 0.013}_{-0.012}$
+&
+$ 0.029^{+ 0.008}_{-0.009}$
+&
+$ 0.018^{+ 0.004}_{-0.005}$
+&
+$ 0.009^{+ 0.007}_{-0.006}$
+&
+$ 0.042^{+ 0.005}_{-0.004}$
 \\
@@
 component.
-Both distributions are non-Gaussian, that of $E(B-V)$ having a sharp rise in the blue and an extended tail in the red, consistent
-with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
 
@@
 \end{figure}
-The significance of the $\delta$ parameters is shown pictorially.
-Figure~\ref{deltacorner:fig} shows the $\delta$ posteriors, which are bimodal due to the $\pm$ sign degeneracy.
+The significance of the $\delta$ parameters is shown pictorially in
+Figure~\ref{deltacorner:fig}, which shows the $\delta$ posteriors.
 \color{red}
-Recall that fixing $\delta_X=0$ reverts this model into the two external-parameter model of \S\ref{model:sec}.
+Recall that fixing $\delta_X=0$ reverts this model into the two extrinsic-parameter model of \S\ref{model:sec}.
 \color{black}
-The probability
-of the null result $\delta_X=0$ for all $X$ is $<98\%$, as determined through
-the population of its bin in a 5-dimensional histogram.
+Assigning the Monte Carlo links to bins of width 0.5 in each $\delta$ parameter, the maximum number of links in a single bin is 303, the number of bins
+with at least one element is 1987, and the bin that contains $\delta=0$ for all bands has zero elements; we thus claim a detection
+of a third color-parameter at $> (1-5\times 10^{-4})$.
 Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values.
@@
    \centering
-   \includegraphics[width=4.5in]{output23/delta_corner.pdf}
-   \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
- \color{blue}
- Three of the chains converged to one solution while the remaining chain converged to the other, resulting in the different normalizations of the two peaks.
- \color{black}
+   \includegraphics[width=5.2in]{output23/delta_corner.pdf}
+   \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.
    \label{deltacorner:fig}}
@@
    \centering
-      \includegraphics[width=5.5in]{output23/deltaratio.pdf}
-   \caption{Significance of the non-zero values of $\delta$ seen through $\delta_X/\delta_I-1$, which is insensitive to the $\pm$ sign degeneracy.
+      \includegraphics[width=5.2in]{output23/deltaratio.pdf}
+   \caption{Significance of the non-zero values of $\delta$ seen through $\delta_X/\delta_I-1$.
    \label{deltaratio:fig}}
@@
 \begin{array}{rrrrrrr}
-1.00 & 0.01 & -0.06 & -0.05 & 0.11 & 0.01 & -0.03 \\
-0.01 & 1.00 & 0.11 & -0.26 & -0.07 & -0.00 & 0.05 \\
--0.06 & 0.11 & 1.00 & -0.14 & -0.17 & -0.03 & -0.02 \\
--0.05 & -0.26 & -0.14 & 1.00 & 0.04 & 0.03 & 0.01 \\
-0.11 & -0.07 & -0.17 & 0.04 & 1.00 & 0.06 & 0.03 \\
-0.01 & -0.00 & -0.03 & 0.03 & 0.06 & 1.00 & -0.00 \\
--0.03 & 0.05 & -0.02 & 0.01 & 0.03 & -0.00 & 1.00
+1.00 & 0.00 & -0.07 & -0.04 & 0.11 & 0.01 & -0.06 \\
+0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.02 & -0.02 \\
+-0.07 & 0.10 & 1.00 & -0.14 & -0.17 & -0.04 & 0.04 \\
+-0.04 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 & -0.07 \\
+0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 & 0.06 \\
+0.01 & -0.02 & -0.04 & 0.03 & 0.05 & 1.00 & 0.01 \\
+-0.06 & -0.02 & 0.04 & -0.07 & 0.06 & 0.01 & 1.00
 \end{array}
@@
 \end{multline}
-The intrinsic parameter $A_{\delta I} =\delta_I D$ has correlations $<0.05$ with respect to all the other parameters, including those attributed
-to extrinsic dust.
-
-\color{red}
-The per-supernova color parameters are not strongly correlated,
-\begin{equation}
-Cor(k_0, k_1, D) =
-\begin{pmatrix}
-\begin{array}{rrr}
-1.00 & 0.06 & -0.01 \\
-0.06 & 1.00 & 0.00 \\
--0.01 & 0.00 & 1.00
-\end{array}
-\end{pmatrix}.
-\end{equation}
-In particular, the Pearson correlation coefficients between the ``intrinsic'' $D$ and ``extrinsic'' $k$ parameters are $-0.01$ and $0.00$.
-So while in principle a single physical color effect can affect both intrinsic and extrinsic parameters, from the correlations
+The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are $0.06$ and $0.01$.
+This has two important implications:
+First, while in principle a single physical color effect can affect both intrinsic and extrinsic parameters, from the correlations
 there is no evidence
-that this occurs in our fits.
+that this occurs.
+Second, the intrinsic term does not a second-order extrinsic correction.
 
@@
    \centering
-   \includegraphics[width=5.5in]{output23/perobject_corner.pdf} 
+   \includegraphics[width=5.2in]{output23/perobject_corner.pdf} 
    \caption{
@@
 
-Our code is validated
-though the analysis of a simulated dataset: the input parameters are recovered within  uncertainties.
+The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
 \color{black}
 
-\section{Supernova Model 0: Fitzpatrick Dust}
+\section{Supernova Model 3: Fitzpatrick Dust}
 \label{model0:sec}
-We analyze our data with a model that incorporates attenuation due to host-galaxy dust.
+\color{blue}
+We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
+except that dust
+is used in place of  the linear two-color-parameter  model.
 The dust model of  \citet{1999PASP..111...63F} is considered:
@@
 The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R$ and $E(B-V)$.  The first, $R$,
-specifies the wavelength-dependent  attenuation  notated by the function $A/E(B-V)$.  The second, $E(B-V)$, specifies the normalization
-of that attenuation.  The dust model is expressed as
+specifies the wavelength-dependent  attenuation  that we notate as $A/E(B-V)$.  The second, $E(B-V)$, specifies the normalization
+of that attenuation.  These two parameters can be combined to define a third dependent parameter $A_V \equiv R E(B-V)$.
+The dust model is expressed as
 \begin{equation}
@@
 \end{equation}
-Those two parameters can be combined to define a third dependent parameter $A_V \equiv R E(B-V)$.
 
@@
 \end{equation}
-which is to first order
+whose first-order approximation
 \begin{equation}
-A_X\left(A_V, E(B-V)  \right) = \frac{\int d\lambda A\left(\lambda; E(B-V), R=\frac{A_V}{E(B-V)}\right)f(\lambda) X(\lambda)}{\int d\lambda f(\lambda) X(\lambda)}.
+A_X\left(A_V, E(B-V)  \right) = \frac{\int d\lambda A\left(\lambda; E(B-V), R=\frac{A_V}{E(B-V)}\right)f(\lambda) X(\lambda)}{\int d\lambda f(\lambda) X(\lambda)}
 \end{equation}
-
-In our model for broadband magnitudes, the SEDs of supernovae $f(x)$ are not specified.  In its place we use the 
+is easy to interpret as an effective extinction.
+
+In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
 updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
 SALT2 template yields similar results.)
+The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
+of model error.  Consider the SED to be the sum of the template and an offset
+\begin{equation}
+f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
+\end{equation}
+To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
+extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.
+
 For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
-$0\le A_V \le 1.8$, $1 \le R \le 8$ with a third-order polynomial in $A_V$ and $E(B-V)$.  The residuals between the model and
-the approximation for $A_V=1.8$ are  shown in Figure~\ref{dfitz:fig}.  The amplitude residuals in $B$ through
+$0\le A_V \le 1.8$, $1 \le R \le 8$ with a third-order polynomial in $A_V$ and $E(B-V)$.
+% The residuals between the model and
+the approximation for $A_V=1.8$ are  shown in Figure~\ref{dfitz:fig}. 
+The amplitude residuals in $B$ through
 $I$ are $< 0.001$ mag; in $U$  for $R>1$ the residuals are $<0.004$ mag
@@
 
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.5in]{output18/dfitz.pdf}
-    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
-    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
-   \label{dfitz:fig}}
-\end{figure}
-
-Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first, $R$ is held the same for all supernovae (labeled
-as $R=const$).  In the second,
-the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$ (labeled as $\ln{R} \sim \mathcal{N}$).
-In the third, $A_V$ and $R$ are free for
-each supernova, with a uniform prior $0\le A_V \le 1.8$, $1 \le R \le 8$ (labeled as $R$-free).
+%
+%
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
+%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
+%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
+%   \label{dfitz:fig}}
+%\end{figure}
+%
+Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
+as $R=const$), $R$ is held the same for all supernovae .  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
+the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
+In the third (denoted as $R$-free), $A_V$ and $R$ are free for
+each supernova, with a uniform prior $0\le A_V \le 1.8$, $1 \le R \le 8$.
 
@@
 are shown in Figure~\ref{AVRV:fig}.  The left plot shows histograms for the median $A_V$ determined for
-each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a normal distribution, and $R$ from a uniform distribution $1 \le R \le 8$.
+each supernova, for the three $R$ distributions.
 The right plot shows the posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
-the median $R$ determined for each supernova in the $R$-free analysis.  (The  $\ln{R} \sim \mathcal{N}$-case draws $R$ from
-the Normal distributions specified by individual links.)
+the median $R$ determined for each supernova in the $R$-free analysis.  The  $\ln{R} \sim \mathcal{N}$-case draws $R$ from
+the Normal distributions specified by individual links.
 
@@
     \caption{Left: Histograms for the median $A_V$ determined for
-each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a Normal distribution, and $R$ from a uniform distribution $1 \le R \le 8$.
+each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a Normal distribution, and $R$ from a uniform distribution.
+To contrast, the corresponding $\gamma_0 k_0$ medians from our 2-parameter model is also shown.
 Right: Posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
@@
 
-The distributions of $A_V$ and $R$ are not as one would expect for an $R=3.1$ Milky Way dust.  While the $R=const$ case give $R \sim 3.5$, its
-distribution of $A_V$ has a slower rise from zero and a non-zero mode of $\sim 0.4$ mag, inconsistent with the expectation of a large fraction of supernovae
+The distributions of $A_V$ and $R$ are not as one would expect for an $R=3.1$ Milky Way dust.  While the $R=const$ case gives $R \sim 3.5$, its
+$A_V$ distribution  has a slower rise from zero and a non-zero mode of $\sim 0.4$ mag, inconsistent with the expectation of a large fraction of supernovae
 experiencing no dust, with a tail in $A_V$ for those that do \citep{1998ApJ...502..177H}.
@@
 
-The Hsiao template does not perfectly represent the underlying spectrum of a supernova.  Consider the SED to be the sum of the template and an offset
-\begin{equation}
-f(\lambda) = f_0(\lambda) + \delta f(\lambda).
-\end{equation}
-To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
-extinction.  Heterogeneity in the true spectrum amongst supernovae yield scatter in those corrections.
-
+The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models, we therefore
+refrain from making absolute conclusions based on our results.  We do emphasize the sensitivity of our results when using the total-to-selective extinction
+$R$ parameter.
+
+\color{black}
 \section{Summary and Discussion}
@@
 extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
-affect supernova magnitudes and colors.  The external color parameters are consistent with \citet{1999PASP..111...63F} dust
-with $R^F_V=2.24 \pm 0.16$.  This model  does an excellent job in
+affect supernova magnitudes and colors.  This model  does an excellent job in
 describing SN~2014J, a supernova with extreme colors that was not used in the training.  
@@
    \centering
-   \includegraphics[width=5.5in]{output23/residualx1.pdf}
+   \includegraphics[width=5.2in]{output23/residualx1.pdf}
     \caption{Differences between observed colors and the colors predicted from the analysis, as a function
@@
 &
-$0.0044^{+0.0010}_{-0.0010}$
+$0.0043^{+0.0009}_{-0.0010}$
 &
@@
 &
-$0.0017^{+0.0006}_{-0.0007}$
-&
-$0.0015^{+0.0005}_{-0.0005}$
+$0.0016^{+0.0007}_{-0.0007}$
+&
+$0.0015^{+0.0006}_{-0.0005}$
 &
@@
 &
-$   1.6^{+   0.8}_{  -0.4}$
+$   1.7^{+   0.9}_{  -0.4}$
 &
@@
 &
-\ldots
+$ \ldots$
 &
@@
 &
-$ 0.033^{+ 0.006}_{-0.006}$
-&
-$ 0.025^{+ 0.005}_{-0.005}$
-&
-$ 0.022^{+ 0.004}_{-0.004}$
-&
-$ 0.019^{+ 0.004}_{-0.003}$
-&
-$ 0.016^{+ 0.003}_{-0.003}$
+$ 0.035^{+ 0.005}_{-0.005}$
+&
+$ 0.026^{+ 0.004}_{-0.004}$
+&
+$ 0.023^{+ 0.004}_{-0.004}$
+&
+$ 0.020^{+ 0.003}_{-0.003}$
+&
+$ 0.017^{+ 0.003}_{-0.003}$
 \\
@@
 &
-$  0.52^{+  0.13}_{ -0.12}$
-&
-$  0.14^{+  0.07}_{ -0.07}$
-&
-\ldots
-&
-$ -0.13^{+  0.03}_{ -0.03}$
-&
-$ -0.27^{+  0.06}_{ -0.06}$
+$  0.54^{+  0.12}_{ -0.10}$
+&
+$  0.16^{+  0.06}_{ -0.06}$
+&
+$ \ldots$
+&
+$ -0.12^{+  0.03}_{ -0.03}$
+&
+$ -0.26^{+  0.06}_{ -0.06}$
 \\
@@
 &
-$0.0004^{+0.0011}_{-0.0011}$
-&
-$0.0005^{+0.0010}_{-0.0010}$
-&
-$0.0009^{+0.0008}_{-0.0008}$
-&
-$0.0009^{+0.0007}_{-0.0007}$
-&
-$0.0001^{+0.0006}_{-0.0006}$
+$0.0007^{+0.0012}_{-0.0012}$
+&
+$0.0006^{+0.0010}_{-0.0010}$
+&
+$0.0011^{+0.0008}_{-0.0008}$
+&
+$0.0010^{+0.0007}_{-0.0007}$
+&
+$0.0003^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.34^{+  0.58}_{ -1.20}$
-&
-$ -0.36^{+  0.35}_{ -0.86}$
-&
-\ldots
-&
-$ -0.10^{+  0.20}_{ -0.14}$
-&
-$ -0.74^{+  0.35}_{ -0.75}$
+$ -0.24^{+  0.47}_{ -0.98}$
+&
+$ -0.32^{+  0.30}_{ -0.76}$
+&
+$ \ldots$
+&
+$ -0.08^{+  0.20}_{ -0.13}$
+&
+$ -0.66^{+  0.29}_{ -0.58}$
 \\
@@
 &
-$  0.00^{+  0.04}_{ -0.04}$
+$  0.01^{+  0.04}_{ -0.04}$
 &
@@
 &
-$ -0.76^{+  0.78}_{ -1.78}$
-&
-$ -0.50^{+  0.47}_{ -1.06}$
-&
-\ldots
-&
-$ -0.46^{+  0.21}_{ -0.50}$
-&
-$ -0.16^{+  0.45}_{ -0.34}$
+$ -0.91^{+  0.75}_{ -1.78}$
+&
+$ -0.62^{+  0.46}_{ -1.15}$
+&
+$ \ldots$
+&
+$ -0.50^{+  0.21}_{ -0.53}$
+&
+$ -0.18^{+  0.41}_{ -0.32}$
+\\
+$\gamma^0_X$
+&
+$ 62.57^{+  3.71}_{ -3.66}$
+&
+$ 51.36^{+  3.12}_{ -3.13}$
+&
+$ 38.26^{+  2.67}_{ -2.69}$
+&
+$ 29.03^{+  2.36}_{ -2.39}$
+&
+$ 20.40^{+  2.21}_{ -2.26}$
 \\
@@
 &
-$  0.65^{+  0.06}_{ -0.05}$
-&
-$  0.35^{+  0.03}_{ -0.03}$
-&
-\ldots
-&
-$ -0.24^{+  0.01}_{ -0.01}$
-&
-$ -0.46^{+  0.03}_{ -0.03}$
+$  0.63^{+  0.06}_{ -0.05}$
+&
+$  0.34^{+  0.03}_{ -0.03}$
+&
+$ \ldots$
+&
+$ -0.24^{+  0.01}_{ -0.02}$
+&
+$ -0.47^{+  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+&
+$ -9.27^{+  3.50}_{ -3.75}$
+&
+$-11.08^{+  2.92}_{ -3.18}$
+&
+$-14.99^{+  2.38}_{ -2.66}$
+&
+$-14.28^{+  2.05}_{ -2.22}$
+&
+$-13.27^{+  1.91}_{ -2.09}$
 \\
@@
 &
-$ -0.39^{+  0.16}_{ -0.17}$
-&
-$ -0.24^{+  0.09}_{ -0.10}$
-&
-\ldots
-&
-$ -0.06^{+  0.04}_{ -0.03}$
-&
-$ -0.15^{+  0.09}_{ -0.08}$
+$ -0.38^{+  0.15}_{ -0.18}$
+&
+$ -0.26^{+  0.09}_{ -0.11}$
+&
+$ \ldots$
+&
+$ -0.05^{+  0.04}_{ -0.04}$
+&
+$ -0.12^{+  0.09}_{ -0.08}$
+\\
+$\delta_X$
+&
+$  1.98^{+  0.52}_{ -0.50}$
+&
+$ -2.13^{+  0.55}_{ -0.54}$
+&
+$ -1.84^{+  0.51}_{ -0.52}$
+&
+$  0.70^{+  0.33}_{ -0.35}$
+&
+$  1.72^{+  0.75}_{ -0.73}$
 \\
@@
 &
-$  0.04^{+  0.48}_{ -0.31}$
-&
-$ -2.16^{+  0.36}_{ -0.64}$
-&
-$ -1.94^{+  0.23}_{ -0.42}$
-&
-$ -0.63^{+  0.56}_{ -0.29}$
-&
-\ldots
+$  0.17^{+  0.50}_{ -0.27}$
+&
+$ -2.23^{+  0.30}_{ -0.64}$
+&
+$ -2.08^{+  0.25}_{ -0.44}$
+&
+$ -0.60^{+  0.54}_{ -0.24}$
+&
+$ \ldots$
 \\
@@
 &
-$ 0.050^{+ 0.014}_{-0.012}$
-&
-$ 0.027^{+ 0.008}_{-0.008}$
-&
-$ 0.015^{+ 0.004}_{-0.005}$
+$ 0.048^{+ 0.012}_{-0.011}$
+&
+$ 0.027^{+ 0.007}_{-0.007}$
+&
+$ 0.014^{+ 0.004}_{-0.005}$
 &
@@
 Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta I}$, the difference is
-not significant; we calculate  average $\langle A_{\delta I} \rangle=   0.0042 \pm    0.0014$,
-$\langle A_{\delta I} \rangle=   0.0031 \pm    0.0017 $ for low- and high-mass hosts respectively. 
+not significant; we calculate  average
+%---
+$\langle A_{\delta I} \rangle=    -0.0026 \pm    0.0010$,
+$\langle A_{\delta I} \rangle=  -0.0037 \pm    0.0010 $ 
+for low- and high-mass hosts respectively. 
 Using the SNfactory sample,
 \citet{2013A&A...560A..66R} find that step in Hubble residuals is better related to local star formation rate, rather than host mass.
-A deeper exploration of the possible connection between our intrinsic parameter and local star formation and other host properties is deferred to
-\citet{2016rigault}.
+
 \color{black}

### 2017-01-03 apj.tex
polishing up

@@
 each supernova, with a uniform prior $0\le A_V \le 1.8$, $1 \le R \le 8$.
+(Note that for $R<2.2$, the model extrapolates beyond the range of the training set upon which it was trained.)
 
@@
 each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a Normal distribution, and $R$ from a uniform distribution.
-To contrast, the corresponding $\gamma_0 k_0$ medians from our 2-parameter model is also shown.
+To contrast, the corresponding $\gamma_0 k_0$ medians from our 2-parameter model is also shown.  The means of the measurement
+uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
 Right: Posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
@@
 $R$ parameter.
+
+The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
+$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
+The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
+non-zero.  Insofar that the $A_V$ and $R_V$
+parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
+is important.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
+    \caption{Difference between per-supernova
+$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
+   \label{CCMF99:fig}}
+\end{figure}
 

### 2017-01-27 apj.tex
new table
compare salt2 and Hsiao

@@
 \geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
-\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
+\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
 \usepackage{amsmath}
@@
 \author{     G.~Aldering}
-\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, ?out???½
     1 Cyclotron Road, Berkeley, CA, 94720}
@@
 $R^F=2.5$ and $A^F_V=0.1$,
-and the measurement of the updated
-\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
+and the measurement of the SALT2
+\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
 gives
-$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$.
+$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
 The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
@@
 \begin{array}{rr}
-1.22 & 2.75 \\
-0.81 & -5.50
+1.15 & 2.82 \\
+0.72 & -5.27
 \end{array}
@@
 \begin{align}
-\vec{\epsilon}_a &=\{0.14, -0.15, -0.07,  0.04, 0.07\}, \\
-\vec{\epsilon}_b & =\{0.12, -0.06, -0.30, 0.30, -0.06\}
+\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
+\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
 \end{align}
-contribute  3\% and 4\% respectively to the total  length of the $\gamma$ vectors.
+contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.
 This result indicates that
@@
 
-Given the association of  our parameter $\gamma^0_2 k_0$ with the $A^F_V$ of an $R^F \sim 2.4$ dust model ,
+Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 2.4$ dust model ,
 the former's distribution can be compared to the expectation for the latter.
 Figure~\ref{k0_med:fig} shows the histogram of
-median values of $\gamma^0_2 k_0$.
+median values of $\gamma^0_V k_0$.
 The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red, consistent
@@
 
-Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_2 k_1$, which is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
+Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
 extinction corrections due to deviations away from the $R=2.4$ value.   The distribution has a long
@@
 The implication is that while the bulk of supernovae have positive values associated with $R>2.4$, there is a tail
-of negative values associated with $R<2.4$.  The plot of   $\gamma^0_2 k_0$ versus $\gamma^1_2 k_1$  shown in Figure~\ref{kk:fig} shows that
-the positive edge in $\gamma^1_2 k_1$ persists over the full range of  $\gamma^0_2 k_0$. On the other hand, lower values of $\gamma^1_2 k_1$
-occur at larger values of  $\gamma^0_2 k_0$.
+of negative values associated with $R<2.4$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
+the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$. On the other hand, lower values of $\gamma^1_V k_1$
+occur at larger values of  $\gamma^0_V k_0$.
 These findings are consistent with previous results:
@@
       \caption{ Histogram of
-median values of Left: $\gamma^0_2 k_0$, which is associated with the $A^F_V$ of an $R^F \sim 2.4$ dust model; Right: $\gamma^1_2 k_1$,
+median values of Left: $\gamma^0_V k_0$, which is associated with the $A^F_V$ of an $R^F \sim 2.4$ dust model; Right: $\gamma^1_V k_1$,
 which  is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
@@
    \includegraphics[width=5.2in]{output11/kk.pdf}
-      \caption{ $\gamma^0_2 k_0$ versus $\gamma^1_2 k_1$.
+      \caption{ $\gamma^0_V k_0$ versus $\gamma^1_V k_1$.
    \label{kk:fig}}
@@
 Parameters& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+
 $\alpha_X$
@@
 &
-$\ldots$
+$  \ldots$
 \\
@@
 \color{blue}
-We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
-except that dust
-is used in place of  the linear two-color-parameter  model.
+Dust models can explain the extrinsic magnitude and color variations found in
+the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we replace the $\gamma k$ color terms with extinction
+terms predicted by a dust model.  
+%
+%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
+%except that dust
+%is used in place of  the linear two-color-parameter  model.      
 The dust model of  \citet{1999PASP..111...63F} is considered:
@@
 
-In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
-updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
-SALT2 template yields similar results.)
-The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
-of model error.  Consider the SED to be the sum of the template and an offset
-\begin{equation}
-f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
-\end{equation}
-To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
-extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.
-
-For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
-$0\le A_V \le 1.8$, $1 \le R \le 8$ with a third-order polynomial in $A_V$ and $E(B-V)$.
-% The residuals between the model and
-the approximation for $A_V=1.8$ are  shown in Figure~\ref{dfitz:fig}. 
-The amplitude residuals in $B$ through
-$I$ are $< 0.001$ mag; in $U$  for $R>1$ the residuals are $<0.004$ mag
-and increase to $0.01$ mag as $R$ decreases to $1$.
+We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
+the SED of the SALT2, $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
+SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the unextincted
+supernova.
+The SALT2 SED determines the values of $A_X$ and the
+intrinsic colors.
+
+This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections:  the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
+Relative to SALT2, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
+Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
+The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
+while simultaneously showing no color excess is $B-R$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
+   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
+    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
+    relative to SALT2.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
+allowed by \citetalias{1999PASP..111...63F} dust.
+Right:    \label{model1118:fig}}
+\end{figure}
+
+%
+%We emphasize now that our broadband magnitude model does not ambiguously specify $A_X$, which depend
+%on the SED of the source.  
+%In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
+%updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
+%SALT2 template yields similar results.)
+%The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
+%of model error.  Consider the SED to be the sum of the template and an offset
+%\begin{equation}
+%f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
+%\end{equation}
+%To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
+%extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.
+
+%For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
+%$-0.21 \le A_V \le 1.8$, $2.1 \le R \le 6.9$ with a third-order polynomial in $A_V$ and $E(B-V)$.   The limits in $R$ represent the range of
+%values that enter the dust-model training.
+%The differences between the extinction and the polynomial approximation are small relative to  $\partial A_X/ \partial R$ over the scales of
+%$R$ of interest.
 
@@
 %
-Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
-as $R=const$), $R$ is held the same for all supernovae .  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
-the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
-In the third (denoted as $R$-free), $A_V$ and $R$ are free for
-each supernova, with a uniform prior $0\le A_V \le 1.8$, $1 \le R \le 8$.
-(Note that for $R<2.2$, the model extrapolates beyond the range of the training set upon which it was trained.)
-
-The posteriors for the spectral parameters are similar to the ones already
-presented; we therefore focus on the posteriors for the dust parameters, the results of which
-are shown in Figure~\ref{AVRV:fig}.  The left plot shows histograms for the median $A_V$ determined for
-each supernova, for the three $R$ distributions.
-The right plot shows the posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
-the median $R$ determined for each supernova in the $R$-free analysis.  The  $\ln{R} \sim \mathcal{N}$-case draws $R$ from
-the Normal distributions specified by individual links.
+
+The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
+and
+\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 model,
+and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
+and there is one global $R$ parameter.
+
+%
+%
+%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
+%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
+%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
+%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
+%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.
+
+The presentation of our results from evaluating this model with SNf data
+begins with further evidence of the inconsistency between the ansatz and the models of the previous section.
+The current analysis sets the magnitude of an $A_V=0$ supernova, so now  magnitudes in addition to colors of the canonical
+supernova in \S\ref{model:sec} can be compared relative to expectations of the dust model.  The magnitude difference
+is the difference between the $c_X$ parameters of the two analyses, denoted as $\Delta c_X$.
+Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
+corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
+to SALT2: these values are plotted in
+Figure~\ref{model1118:fig}.
+The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.
+
+The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram for the median $A_V$ determined for
+each supernova. The
+$A_V$ distribution  has a slow rise from zero,  compared to the equivalent $\gamma^0_V k_0$
+from the linear model of \S\ref{model:sec} that has the sharp rise expected from of a large fraction of supernovae
+experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
+$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
+While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
+to $R=3.17^{0.20}_{-0.17}$.
 
@@
    \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
-    \caption{Left: Histograms for the median $A_V$ determined for
-each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a Normal distribution, and $R$ from a uniform distribution.
-To contrast, the corresponding $\gamma_0 k_0$ medians from our 2-parameter model is also shown.  The means of the measurement
+    \caption{Left: histogram for the median $A_V$ determined for
+each supernova.  The $\gamma^0_V k_0$ medians from our 2-parameter model of \S\ref{model:sec} is also shown.  The means of the measurement
 uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
-Right: Posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
-the median $R$ determine for each supernova in the $R$-free analysis.
+Right: Posteriors for $R$.  Results for both the SALT2 supernova model and the updated \citet{2007ApJ...663.1187H} are shown.
    \label{AVRV:fig}}
 \end{figure}
-
-Both the distributions in $A_V$ and $R$ are dependent on the assumptions on the distribution of $R$.
-The mode in the $A_V$ histogram shifts from $\sim 0.2$ mag 
-for the $R$-free case, to $\sim 0.4$ mag for  $R=const$, and to $\sim 0.6$ for  $\ln{R} \sim \mathcal{N}$.
-The  posterior of $R$ is skinnier and biased for $R=const$ relative to the $R$ distributions found by the $R$-free and  $\ln{R} \sim \mathcal{N}$
-cases.
-
-The distributions of $A_V$ and $R$ are not as one would expect for an $R=3.1$ Milky Way dust.  While the $R=const$ case gives $R \sim 3.5$, its
-$A_V$ distribution  has a slower rise from zero and a non-zero mode of $\sim 0.4$ mag, inconsistent with the expectation of a large fraction of supernovae
-experiencing no dust, with a tail in $A_V$ for those that do \citep{1998ApJ...502..177H}.
-The $\ln{R} \sim \mathcal{N}$ distribution for $A_V$ is shifted and a mode of  $R$
-larger that $4$.
-While for $R$-free the  $A_V$ distribution mode is centered somewhat closer to zero, the distribution of $R$ is shifted to even higher values.
 

### 2017-01-27 intrinsic_colors.py

@@ -1,0 +1,178 @@
+#!/usr/bin/env python
+
+import pickle
+import pystan
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import corner
+from matplotlib.backends.backend_pdf import PdfPages
+import numpy
+import sncosmo
+import scipy
+import cPickle
+import matplotlib as mpl
+import sivel
+
+ext=''
+
+f = open('temp18'+ext+'.pkl','rb')
+(fit18,_) = pickle.load(f)
+
+
+
+f = open('temp11'+ext+'.pkl','rb')
+(fit11,_) = pickle.load(f)
+
+# for key in fit.keys():
+#     print key, fit[key].min(), fit[key].max()
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+sivel,sivel_err,x1,x1_err, _, _ = sivel.sivel(data)
+use = numpy.isfinite(sivel)
+
+#  The ordering is 'Ca','Si','U','B','V','R','I'
+
+EW_obs = data['obs'][:,0:2]
+mag_obs = data['obs'][:,2:]
+EW_cov = data['cov'][:,0:2,0:2]
+mag_cov = data['cov'][:,2:,2:]
+
+sivel=sivel[use]
+sivel_err = sivel_err[use]
+x1=x1[use]
+x1_err = x1_err[use]
+EW_obs=EW_obs[use]
+mag_obs=mag_obs[use]
+EW_cov= EW_cov[use]
+mag_cov=mag_cov[use]
+
+EW_mn = EW_obs.mean(axis=0)
+EW_renorm = (EW_obs - EW_mn)
+
+mag_mn = mag_obs.mean(axis=0)
+mag_renorm  = mag_obs-mag_mn
+
+sivel_mn = sivel.mean()
+sivel_renorm = sivel-sivel_mn
+
+nsne, nmags = mag_obs.shape
+color_obs = numpy.zeros((nsne,nmags-1))
+color_obs[:,0] = mag_renorm[:,0]- mag_renorm[:,2]
+color_obs[:,1] = mag_renorm[:,1]- mag_renorm[:,2]
+color_obs[:,2] = mag_renorm[:,3]- mag_renorm[:,2]
+color_obs[:,3] = mag_renorm[:,4]- mag_renorm[:,2]
+
+pkl_file.close()
+
[…]

### 2017-01-27 viewfitz.py

@@ -1,0 +1,177 @@
+#!/usr/bin/env python
+
+import pickle
+import pystan
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import corner
+from matplotlib.backends.backend_pdf import PdfPages
+import numpy
+import sncosmo
+import scipy
+import cPickle
+import matplotlib as mpl
+import sivel
+
+ext=''
+
+f = open('temp18'+ext+'.pkl','rb')
+(fit18,_) = pickle.load(f)
+f = open('temp18'+ext+'_free.pkl','rb')
+(fit18_free,_) = pickle.load(f)
+f = open('temp18'+ext+'_salt2.pkl','rb')
+(fit18_salt2,_) = pickle.load(f)
+f = open('temp19'+ext+'.pkl','rb')
+(fit19,_) = pickle.load(f)
+f = open('temp20'+ext+'.pkl','rb')
+(fit20,_) = pickle.load(f)
+f = open('temp20'+ext+'_salt2.pkl','rb')
+(fit20_salt2,_) = pickle.load(f)
+f = open('temp20_ccm.pkl','rb')
+(fit20_ccm,_) = pickle.load(f)
+f = open('temp11'+ext+'.pkl','rb')
+(fit11,_) = pickle.load(f)
+
+
+
+
+plt.hist(fit18_salt2['AV'].flatten(),histtype='step', stacked='false', \
+    label=r'$R=const$ SALT2',bins=numpy.arange(-.25,1.8,0.1),normed=True)
+plt.hist(fit18['AV'].flatten(),histtype='step', stacked='false', \
+    label=r'$R=const$ Hsiao',bins=numpy.arange(-.25,1.8,0.1),normed=True)
+# plt.hist(fit18_free['AV'].flatten(),histtype='step', stacked='false', \
+#     label=r'$R=const$ free',bins=numpy.arange(-.25,1.8,0.1),normed=True)
+# plt.hist(fit19['AV'].flatten(),histtype='step', stacked='false', \
+#     label=r'$\ln{R}\sim \mathcal{N}$',bins=numpy.arange(-.25,1.8,0.1),normed=True)
+# plt.hist(fit20['AV'].flatten(),histtype='step', stacked='false', \
[…]

### 2017-01-29 apj.tex
Painful rewriting of a section

@@
 
+\author{ S.~Dixon}
+\affiliation{
+    Department of Physics, University of California Berkeley,
+    366 LeConte Hall MC 7300, Berkeley, CA, 94720-7300}
+
 \author{     P.~Fagrelius}
@@
     1 Cyclotron Road, Berkeley, CA, 94720}
-    \affiliation{    Department of Physics, Florida State University,
-    315 Keen Building, Tallahassee, FL 32306-4350}
+    \affiliation{   Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
 
@@
 %-----
-$(1-5\times10^{-5})$
+$1-5\times10^{-5}$
 %------
 confidence.
-The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
+The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
 Extending the model to three color parameters gives almost identical results for
@@
 %--- table.py
-$(1-5\times10^{-4})$
+$1-5\times10^{-4}$
 %-----
 confidence;
-this new parameter is responsible for supernova color diversity
-beyond those tracked by the spectral features and two-parameter dust models.
+this new parameter represents supernova color diversity
+beyond that tracked by the spectral features and two-parameter dust models.
 \end{abstract}
@@
 \begin{pmatrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
+c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} \\
+c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si}  \\
+c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} \\
+c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} \\
+c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si}
 \end{pmatrix}
@@
 \begin{pmatrix}
-U +\gamma^0_{1} k_0 +\gamma^1_{0} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
-V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
+U +\gamma^0_{U} k_0 +\gamma^1_{U} k_1 \\B +\gamma^0_{B} k_0 +\gamma^1_{B} k_1 \\
+V+\gamma^0_{V} k_0+\gamma^1_{V} k_1\\R+\gamma^0_{R} k_0 + \gamma^1_{R} k_1\\I+\gamma^0_{I} k_0+\gamma^1_{I} k_1\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
@@
 \begin{equation}
-\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_0 > 0, \gamma^1_0 < 0.
+\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_U > 0, \gamma^1_U < 0.
 \end{equation}
@@
 (when running our fits, $k_0$ and $k_1$ are set to
-identical initial conditions, so the difference in the signs of $\gamma^0_0$ and $\gamma^1_0$ distinguishes the two.)
+identical initial conditions, so the difference in the signs of $\gamma^0_U$ and $\gamma^1_U$ distinguishes the two.)
 As  $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
 each other,
-the different initial and boundary conditions for $\gamma^0_0$ and $\gamma^1_0$ break the degeneracy of our mixture model;
+the different initial and boundary conditions for $\gamma^0_U$ and $\gamma^1_U$ break the degeneracy of our mixture model;
 otherwise identical initial conditions for $\gamma^0$, $\gamma^1$ produce indistinguishable posteriors
@@
 $2.5 \log{(20/850)} \sim 0.03$ mag.  
-The implied span in $B$ magnitude based on $\beta_1$ is 0.54~mag.  Therefore $\beta_1$ cannot wholly be attributed to the flux deficit
+The implied span in $B$ magnitude based on $\beta_B$ is 0.54~mag.  Therefore $\beta_B$ cannot wholly be attributed to the flux deficit
 from the line itself.
@@
 is
-$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_0$ cannot be completely due to the line itself.
+$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the line itself.
 
@@
 
-To visualize the above result, Figure~\ref{plane:fig} shows two perspectives in $UVI$-space
-of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model,
-and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model.
-The left plot shows that the four vectors point in different directions, while the right plot shows that
-the planes defined by our model (solid lines) and the  \citetalias{1999PASP..111...63F} model (dashed lines) are nearly coplanar.
-
-The specific directions of $\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}$ and
-$\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}$ within the plane they define are not arbitrary, but are determined by the prior that
-$k_0$ and  $k_1$ are uncorrelated. 
-In order to understand these directions in the context of the dust model,
-we
-rewrite the \citetalias{1999PASP..111...63F} model in Eqn.~\ref{f99:eqn} as
-\begin{equation}
-A_X =  A_V^F\left(a(X)+\frac{b(X)}{r} \right) +  \left( E^F(B-V) - \frac{ A_V^F}{r}\right)b(X).
-\end{equation}
-Assigning $r=2.4$, we find that the combination  $\left(a(X) + \frac{b(X)}{2.4}\right)$ is
-almost perfectly aligned with $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ while $b$ alone is almost perfectly aligned with $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$,
-as shown in the dot-dashed and dotted lines of  Figure~\ref{plane:fig}.  This implies a correspondence of $k_0$ with $A^F_V$,
-and $k_1$ with $  \left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$.
-Our prior of a non-correlation between $k_0$ and $k_1$ has lead to an $r \sim 2.4$  that optimizes the
-non-correlation between $A^F_V$ and $  \left( E^F(B-V) - \frac{ A_V^F}{r}\right)$.
+To visualize the above result, Figure~\ref{plane:fig} shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
+of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
+and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  
+The two perspectives show that while the four vectors point in different directions for each band combination,
+they are almost coplanar in $UVI$, and close to coplanar in $BVR$.
 
@@
    \centering
-   \includegraphics[width=2.8in]{output11/plane0.pdf}
-   \includegraphics[width=2.8in]{output11/plane1.pdf}
+   \includegraphics[width=2.95in]{output11/plane0.pdf}
+   \includegraphics[width=2.95in]{output11/plane1.pdf}
+   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
+   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
    \caption{
-   Two different perspectives in $UVI$-space of the vectors $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
-   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.4$ is shown in the dot-dashed
-   line, almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$, while $b(X)$ shown in the dotted line is
-   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$.  
+   Two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
+of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
+   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combinations $a(X)+b(X)/2.4$ and  $a(X)+b(X)/2.6$ are shown in the dotted
+   lines: thy are almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ for $UVI$ and $BVR$ respectively.  $b(X)$ shown in the dotted line is
+   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$ in $UVI$ but is clearly distinct in $BVR$.  
    \label{plane:fig}}
@@
 
-Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 2.4$ dust model ,
+A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and led to the specification of the directions of
+the vectors $\gamma^0$ and $\gamma^1$.  Suppose that that the data were described by a dust model.  A \citetalias{1999PASP..111...63F}  dust model 
+can be written as 
+%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
+%be expressed in terms of new basis vectors parametrized by $\kappa$:
+\begin{equation}
+A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
+\end{equation}
+with the parameters $\kappa_1$ and $\kappa_2$ providing the freedom of choice in the directions of the two basis vectors.  In the analysis,
+the arbitrarity is broken and the $\kappa$'s specified, by the  prior of  
+zero covariance between $(A^F_V - \kappa_2 E^F(B-V))$ and  $(-\kappa_1 A^F_V + E^F(B-V))$.
+The preferred values for $\kappa$ from the linear model in \S\ref{model:sec} are shown qualitatively in
+Figure~\ref{plane:fig}.  For $\kappa_1=1/2.4$, $\kappa_2=-6.8$
+the vector $\gamma^0_X$ is  aligned with 
+the dust vector $\left(a(X)+\kappa_1 b(X) \right)$  and $\gamma^1_X$
+is aligned with $(\kappa_2 a(X) + b(X))$ for $X=UVI$.  Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply for  $X=BVR$.
+
+An intuitive understanding of $\kappa_1$ can be obtained by considering what would happen if
+all supernovae were to experience dust with the same $R^F$.   The zero-covariance
+prior would be satisfied by  $\kappa_1=1/R^F$ and any arbitrary $\kappa_2$.
+The combination  $\gamma^0_V k_0$ would correspond to  $A^F_V$.  Intrinsically $k_1=0$  and $\gamma^1$ would be unconstrained.
+A slight relaxation away from the constant $R^F$ assumption would result in non-zero $k_1$ and a $\gamma^1$ in a direction that satisfies
+the prior condition, as parameterized by $\kappa_2$.
+
+Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model ,
 the former's distribution can be compared to the expectation for the latter.
@@
 
-Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
-extinction corrections due to deviations away from the $R=2.4$ value.   The distribution has a long
+Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which is associated with 
+extinction corrections due to deviations away from the canonical $R^F$ value.   The distribution has a long
 negative tail and is peaked at its positive edge, and by construction has a mean of zero.
-The implication is that while the bulk of supernovae have positive values associated with $R>2.4$, there is a tail
-of negative values associated with $R<2.4$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
+The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
+of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
 the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$. On the other hand, lower values of $\gamma^1_V k_1$
@@
 $\{k_0, k_1\}$, describe for the most part the $\{ E(B-V), R\}$ parameters used
-in standard models of Milky Way dust.
+in standard models of Milky Way dust.  There do remain some small inconsistencies between our numbers and expectations from dust models.
 \color{black}
@@
 \begin{pmatrix}
-c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
-c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
-c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
-c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
-c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
+c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} + \delta_0 D\\
+c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si} + \delta_1 D \\
+c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} + \delta_2 D\\
+c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} + \delta_3 D\\
+c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si} + \delta_4 D
 \end{pmatrix}
@@
 \begin{pmatrix}
-U +\gamma^0_{0} k_0 +\gamma^1_{0} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
-V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
+U +\gamma^0_{U} k_0 +\gamma^1_{B} k_1 \\B +\gamma^0_{B} k_0 +\gamma^1_{B} k_1 \\
+V+\gamma^0_{V} k_0+\gamma^1_{V} k_1\\R+\gamma^0_{R} k_0 + \gamma^1_{R} k_1\\I+\gamma^0_{I} k_0+\gamma^1_{I} k_1\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}

### 2017-01-29 apj.tex
plowing on

@@
  $R^F$ and $A^F_V$,
-and the wavelengths under consideration,  the values of the components  vary by $<5$\%.
+and the wavelengths under consideration,  the values $a$ and $b$ change but only by $<5$\%.
 
@@
 %----
-can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors, and a residual vectors perpendicular to $a$ and $b$.
+can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
 The result is
@@
 
-To visualize the above result, Figure~\ref{plane:fig} shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
-of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
+The above result is visualized in Figure~\ref{plane:fig}, which  shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
+of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
 and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  
@@
 
-A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and led to the specification of the directions of
+A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
 the vectors $\gamma^0$ and $\gamma^1$.  Suppose that that the data were described by a dust model.  A \citetalias{1999PASP..111...63F}  dust model 
@@
 \end{equation}
-with the parameters $\kappa_1$ and $\kappa_2$ providing the freedom of choice in the directions of the two basis vectors.  In the analysis,
-the arbitrarity is broken and the $\kappa$'s specified, by the  prior of  
+with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.  In the analysis,
+the $\kappa$'s are specified by the  prior of  
 zero covariance between $(A^F_V - \kappa_2 E^F(B-V))$ and  $(-\kappa_1 A^F_V + E^F(B-V))$.
-The preferred values for $\kappa$ from the linear model in \S\ref{model:sec} are shown qualitatively in
+The preferred values for $\kappa$ are shown qualitatively in
 Figure~\ref{plane:fig}.  For $\kappa_1=1/2.4$, $\kappa_2=-6.8$
@@
 the dust vector $\left(a(X)+\kappa_1 b(X) \right)$  and $\gamma^1_X$
-is aligned with $(\kappa_2 a(X) + b(X))$ for $X=UVI$.  Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply for  $X=BVR$.
-
-An intuitive understanding of $\kappa_1$ can be obtained by considering what would happen if
-all supernovae were to experience dust with the same $R^F$.   The zero-covariance
+is aligned with $(\kappa_2 a(X) + b(X))$  $UVI$-space.  Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply in $BVR$-space.
+
+To gain an intuitive understanding of $\kappa_1$, consider the hypothetical case where
+all supernovae experience dust with the same $R^F$.   The zero-covariance
 prior would be satisfied by  $\kappa_1=1/R^F$ and any arbitrary $\kappa_2$.
-The combination  $\gamma^0_V k_0$ would correspond to  $A^F_V$.  Intrinsically $k_1=0$  and $\gamma^1$ would be unconstrained.
-A slight relaxation away from the constant $R^F$ assumption would result in non-zero $k_1$ and a $\gamma^1$ in a direction that satisfies
-the prior condition, as parameterized by $\kappa_2$.
-
-Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model ,
+The combination  $\gamma^0_V k_0$ would correspond to  $A^F_V$.  Both $k_1=0$  and $\gamma^1$ would be unconstrained.
+A slight relaxation away from the constant $R^F$ assumption would result in $\kappa_2$ no longer being arbitrary but determined by the prior, and a
+non-zero $k_1$ and a $\gamma^1$.
+
+Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model,
 the former's distribution can be compared to the expectation for the latter.
@@
 $\{k_0, k_1\}$, describe for the most part the $\{ E(B-V), R\}$ parameters used
-in standard models of Milky Way dust.  There do remain some small inconsistencies between our numbers and expectations from dust models.
+in standard models of Milky Way dust.  Yet there do remain some small inconsistencies between our numbers and expectations from dust models.
 \color{black}
@@
 the SED of the SALT2, $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
-SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the unextincted
+SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
+parameter values of an unextincted
 supernova.
@@
 
-This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections:  the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
-Relative to SALT2, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
+This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections in that the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
+Taking the SALT2 template as the unextincted supernova, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
 Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
@@
     \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
-    relative to SALT2.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
+    taking the SALT2 template as an unextinced supernova.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
 allowed by \citetalias{1999PASP..111...63F} dust.
-Right:    \label{model1118:fig}}
+Right:    $A_X/E(X-V)$ of the best-fit $c$'s 
+    relative to SALT2. \label{model1118:fig}}
 \end{figure}
@@
 and
-\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 model,
+\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 template,
 and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
 and there is one global $R$ parameter.  
-
 %
@@
 
-The presentation of our results from evaluating this model with SNf data
-begins with further evidence of the inconsistency between the ansatz and the models of the previous section.
-The current analysis sets the magnitude of an $A_V=0$ supernova, so now  magnitudes in addition to colors of the canonical
-supernova in \S\ref{model:sec} can be compared relative to expectations of the dust model.  The magnitude difference
-is the difference between the $c_X$ parameters of the two analyses, denoted as $\Delta c_X$.
+Results from evaluating this model with SNf data
+provide further evidence of the inconsistency between the ansatz and the models of the previous section.
+The dust-model analysis of this section sets the magnitude of an $A_V=0$ supernova, so now  magnitudes of the canonical
+supernova in \S\ref{model:sec} can also be compared (along with color) to the expectations of the dust model.  The magnitude difference, $\Delta c_X$,
+is the difference between the $c_X$ parameters of the two analyses.
 Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
@@
 each supernova. The
-$A_V$ distribution  has a slow rise from zero,  compared to the equivalent $\gamma^0_V k_0$
-from the linear model of \S\ref{model:sec} that has the sharp rise expected from of a large fraction of supernovae
+$A_V$ distribution  has a slow rise from zero; recall that the equivalent $\gamma^0_V k_0$
+from the linear model of \S\ref{model:sec} has the sharp rise expected from of a large fraction of supernovae
 experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
@@
 
-The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models, we therefore
-refrain from making absolute conclusions based on our results.  We do emphasize the sensitivity of our results when using the total-to-selective extinction
-$R$ parameter.
-
-The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
-$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
-The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
-non-zero.  Insofar that the $A_V$ and $R_V$
-parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
-is important.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
-    \caption{Difference between per-supernova
-$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
-   \label{CCMF99:fig}}
-\end{figure}
+The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models,
+and our ansatz for incorporating dust is limited systematically in measuring 
+the total-to-selective extinction.  We emphasize also that $R^F$ determined in this section are based on  both absolute extinction and color,
+whereas the $\gamma$'s (and resulting $\kappa_1$) in \S\ref{model:sec} do not depend on absolute extinction, i.e. the extra model constraint  of the
+zero-extinction supernova.
+
+%
+%The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
+%$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
+%The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
+%non-zero.  Insofar that the $A_V$ and $R_V$
+%parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
+%is important.
+%
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
+%    \caption{Difference between per-supernova
+%$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
+%   \label{CCMF99:fig}}
+%\end{figure}
 

### 2017-01-31 apj.tex
forging on with edits

@@
 and probe of cosmology \citep[e.g.][]{1992ARA&A..30..359B, 1993ApJ...415....1S}.  After further careful consideration of supernova data, it was recognized
-that SN~Ia light-curve shapes \citep{1993ApJ...413L.105P} and colors \citep{1996ApJ...473...88R, 1998A&A...331..815T} exhibit subtle signs of heterogeneity,
-which being correlated with absolute magnitude
-need to be considered when inferring distances.  Empirical models parameterizing SNe~Ia by their light-curve shape \citep{1996ApJ...473...88R,
+that SN~Ia light-curve shapes \citep{1993ApJ...413L.105P} and colors \citep{1996ApJ...473...88R, 1998A&A...331..815T} exhibit subtle signs of heterogeneity
+that are correlated with absolute magnitude, and must be considered when inferring distances.  Empirical models parameterizing SNe~Ia by their light-curve shape \citep{1996ApJ...473...88R,
 1997ApJ...483..565P,
@@
 In SALT2 the light curve shapes are described by a multiplicative scaling (``stretch'')  of the time evolution,
- whereas MLCS2k2 varies shapes through additive corrections to magnitudes.
+ whereas MLCS2k2 varies shapes through additive time-dependent corrections to magnitudes.
 The physical cause of the color diversity is interpreted differently by the two sets of authors: 
@@
 partially to intrinsic variations linked to light-curve shape, and partially
-to the attenuation of light from host-galaxy dust.
+to the reddening of light from host-galaxy dust.  Differences between these models produce differences in the results of
+analysis of both low-redshift \citep{2007ApJ...664L..13C} and high-redshift \citep{2009ApJS..185...32K} supernovae.
 
@@
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two subpopulations distinguished
-by Si velocity with differing $B_{max}-V_{max}$; this color correlation, in addition to one with $B-R$, is confirmed by
+by SiII velocity with differing $B_{max}-V_{max}$; this color correlation, in addition to one with $B-R$, is confirmed by
 \citet{2014ApJ...797...75M}.
@@
 \citet{2013ApJ...779...23M} find diversity in SNe~Ia UV emission, which they use to distinguish subclasses based on UV-optical colors.
-Such measurements of $R_V$ are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
+Measurements of color ratios are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
 \citep[e.g.][]{2011ApJ...731..120M}.
@@
 In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
-the standard $R_V=3.1$ is recovered on average.
+the $R_V=3.1$ measured for the diffuse Milky Way dust is recovered on average and \citet{2017arXiv170101422H}
+find $R_V=2.95 \pm 0.08$ for SN~2012cu.
 
@@
 scatter in the Hubble diagram is better explained by a combination of intrinsic color dispersion and
-$R_B=3.7$ dust, rather than by dust with no color dispersion.
-They draw these conclusions by using only the SALT2 $x_1$ parameter as the summary statistic that describes color.
+$R_B \equiv R_V+1=3.7$ dust, rather than by dust with no color dispersion.
+They draw these conclusions by using only the SALT2 (v2.4) $x_1$ parameter as the summary statistic that describes color.
 
@@
 This approach is taken by \citet{2011A&A...529L...4C}, who find that after standardization based on Ca and Si features, remaining residual color
-variation is consistent with Milky Way dust laws.
-We accommodate  three independent color parameters: the model is constructed such that one is attributed to intrinsic supernova
-properties and the two others to
-extrinsic processes that are attributed to dust.
+variation is consistent with Milky Way dust models.
+We accommodate  three independent color parameters: the model is constructed such that 
+two are attributed to extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
+properties.
 \color{black}
@@
 supernova SN2014J that has an extreme total-to-selective extinction.
-In \S\ref{model2:sec} we add to analysis the intrinsic parameter, and find strong evidence for its influence on observed magnitudes.
-We summarize our findings, and relate our results with light-curve shape, SiII velocity, and the ``mass step'' in SN~Ia Hubble
+In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
+We summarize our findings, and relate our results with light-curve shape, SiII velocity, and the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
 residuals in \S\ref{discussion:sec}.
@@
 the SNfactory with the SuperNova Integral Field
-Spectrograph \citep[SNIFS,][]{2004SPIE.5249..146L}.  SNIFS is a fully integrated
+Spectrograph \citep[SNIFS,][]{2002SPIE.4836...61A, 2004SPIE.5249..146L}.  SNIFS is a fully integrated
 instrument optimized for automated observation of point sources on a
@@
 moderate spectral resolution ($R \sim 500$).  It consists of a
-high-throughput wide-band lenslet integral field spectrograph, a
-multi-filter photometric channel to image the field in the vicinity of
+high-throughput wide-band lenslet integral field spectrograph, a mult-band
+imager that covers the field in the vicinity of
 the IFS for atmospheric transmission monitoring simultaneous with
@@
 
-Supernova-frame synthetic supernova-frame photometry is generated for a top-hat filter system
+Synthetic supernova-frame photometry is generated for a top-hat filter system
 comprised of five 
@@
 $I$ $[6968.29-8400.00]$\AA.
-For each supernova, the data magnitudes within 5-days of peak brightness are used to regress the peak magnitude
-using single-band SALT2 fits.
+For each supernova, the magnitudes within 5-days of peak brightness are used to regress single-band magnitudes
+at $B$-band peak brightness.
 The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
@@
 wavelength of the SiII$\lambda 6355$ feature
-as in \citet{chotard:thesis}.
+as in \citet{chotard:thesis, 2017Chotard}.
 Equivalent widths and the
@@
 give photometric and spectroscopic statistics described above.
+\textcolor{red}{FOR INTERNAL REFERENCE: The CABALLO2 validation and training sets are used with SN2012cu, SNF20061108-001, SNF20080905-005, SNNGC7589 excised
+based on data problems identified by Manu.}
 The data are given in Table~\ref{data:tab} \textcolor{red}{[TABLE CAN GO IF THERE IS A NICO PAPER]}.
@@
 \citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
-The explicit omission of light-curve shape in our model is compensated by its proxy
-$EW_{Si}$ at peak brightness
+The explicit omission of light-curve shape in our model is compensated by its proxy,
+$EW_{Si}$, at peak brightness
 \citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
@@
 \end{equation}
-The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
+The global parameters $c_X$, $\alpha_i$, $\beta_i$,  and $\eta_i$,  are the intercepts and slopes of the linear relationships that
 relate intrinsic magnitudes with the spectral-feature parameters.
-(In this article we freely interchange the parameter indices with  $01234$ and $UBVRI$.)
 The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
@@
 To constrain the degrees of freedom and degeneracies inherent in the model we impose that
-each of the vectors $k_0+1/N$ and $k_1+1/N$ are simplexes (all elements are $\ge 0$ and sum to one),
-where $N$ is the number of objects in our sample: these
+each of the vectors $k_0+1/N$ and $k_1+1/N$,  where $N$ is the number of objects in our sample, are element-wise $\ge 0$ and sum to one, i.e.\
+these vectors are simplexes.
+These
 conditions break the 
@@
  $0.1$ and scale $0.1$ mag restricted to positive values.
-This covariance matrix prior is recommended by STAN, the Monte Carlo we use to evaluate the model.
+This covariance matrix prior is recommended by STAN \citep{stan}, the Monte Carlo we use to evaluate the model.
  We find that imposing a stricter assumption of a
@@
 output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
-Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig} -- \ref{global5:fig}.  We find no evidence that
+Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig} -- \ref{global5:fig}.  In these tests there is no evidence that
 the Monte Carlo chains have not converged to the stationary posterior distribution.
@@
             projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.  \label{global1:fig}}
+            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ are to guide the eye.
+            \label{global1:fig}}
 \end{figure}
@@
 
-The model-predicted versus observed supernova colors are shown in Figure~\ref{residual:fig}.
-The points lie along a line with slope equal to one, and show no evidence of a catastrophic fit nor of extreme
+Differences between the model-predicted versus observed supernova colors are shown in Figure~\ref{residual:fig}.
+There is no evidence of a catastrophic fit nor of extreme
 outlying data.
@@
    \includegraphics[width=5.2in]{output11/residual.pdf} 
-            \caption{Predicted versus observed colors.  Overplotted is a line with slope equal to one.
+            \caption{Difference between predicted versus observed colors versus the observed color.
             \label{residual:fig}}
@@
 The effect of spectral parameters on color is shown in the rows of $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$
-in Table~\ref{global:tab}:
-values of zero signify no color changes associated with magnitude changes.
+in Table~\ref{global:tab}.
+Values of zero signify no color changes associated with magnitude changes.
 Both $EW_{Ca}$ and $EW_{Si}$ are associated with color changes, though not in $B-V$ specifically.
 We do not detect a significant association between
-$\lambda_{Si}$ and color.
-
-The ideogram for the grey offsets, $\Delta$, for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
+$\lambda_{Si}$ and color with this model.
+
+The histogram of the medians of the grey offsets, $\Delta$, for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
 has a standard deviation of
@@
    \centering
-   \includegraphics[width=5.2in]{output11/Delta_hist.pdf} 
-   \caption{Ideogram for the grey offset $\Delta$.  This and other ideograms plotted in this article are normalized to have unit area.
+   \includegraphics[width=5.2in]{output11/Delta_med_hist.pdf} 
+   \caption{Histogram of the medians of the grey offset $\Delta$. 
    \label{hist:fig}}
@@
  \end{equation}
-These color variances are smaller than those derived by \citet{2003A&A...404..901N, 2007ApJ...659..122J}, for cases where direct comparison can be made.
+These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where direct comparison can be made.
 
@@
 \end{multline}
+
+The  strong correlation between $EW_{Ca}$ and $\lambda_{Si}$ is not surprising.   Si~II velocities have been
+suggested as being able to distinguish two distinct SN~Ia populations
+\citep{2009ApJ...699L.139W, 2013Sci...340..170W}.  CaII~H\&K, and more cleanly CaII~NIR photospheric features
+(and 
+high-velocity features if present), have been found to trend with light-curve shape  \citep{2012MNRAS.426.2359M}.
+\citet{2014MNRAS.437..338C, 2014MNRAS.444.3258M} found a strong correlation between Si~II velocities and the
+CaII~NIR photometric velocity feature, and found that the correlation is sensitive to the presence of high-velocity features.
+
 We find weak correlations between our color-excess parameters and the input features, the strongest being
@@
 
-We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust laws.
+We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
 A direct analysis of the  \citetalias{1999PASP..111...63F} dust model is presented later
@@
 \end{equation}
-approximately describes dust laws.
+approximately describes dust models.
 For the case of
@@
 deviations of the magnitude residuals.
-The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust law, in that now
+The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust model, in that now
 \begin{equation}
@@
 
-The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram for the median $A_V$ determined for
+The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram of the median $A_V$ determined for
 each supernova. The
@@
    \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
-    \caption{Left: histogram for the median $A_V$ determined for
+    \caption{Left: Histogram of the median $A_V$ determined for
 each supernova.  The $\gamma^0_V k_0$ medians from our 2-parameter model of \S\ref{model:sec} is also shown.  The means of the measurement

### 2017-02-01 apj.tex
rework dust stuff

@@
 
+\color{red}
+[Greg asked for discussion but I think the spectral correlations should go in Chotard et al.\ 2017.]
 The  strong correlation between $EW_{Ca}$ and $\lambda_{Si}$ is not surprising.   Si~II velocities have been
@@
 CaII~NIR photometric velocity feature, and found that the correlation is sensitive to the presence of high-velocity features.
+\color{black}
 
@@
 
-The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its affect on magnitude
+The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its direct affect on magnitude
 is
@@
 Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
-701~\AA, so that its affect on magnitude
+701~\AA, so that its direct affect on magnitude
 is
-$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the line itself.
-
-\subsection{The Two Extrinsic Parameters $k_0$ and $k_1$}
+$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the 
+presence of the line itself.
+
+\subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
 \color{blue}
@@
 None of the 20000 links of 
-our Monte Carlo chains for $\gamma$ exceed 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
+our Monte Carlo chains for $\gamma$ extend to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
 influence of $k_0$ and $k_1$  on supernova magnitudes
-with probability $(1-5\times 10^{-5})$.
+with probability $1-5\times 10^{-5}$.
 
@@
 rearranged as
-$$A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
-$$
-Making the assumption that it is the same for all supernovae ,
- $R^T_V$  can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.
+\begin{equation}
+A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
+\end{equation}
+Making the assumption that $R^T_V$ is the same for all supernovae,
+its value can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.
 
 Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$.
-The full set of supernovae does not coincide with the expectations of a single linear law; rather the supernova population is peaked
+The full set of supernovae does not coincide with the expectations of a single linear relation; rather the supernova population is peaked
 on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
@@
 %----
-where the uncertainty is the $68$\% credible interval and does not include goodness
- of fit.
+where the uncertainty is the $68$\% credible interval and does not include model error.
 
@@
    %Overplotted is the mean and standard deviation of those points in equally divided bins.
-   Overplotted the expected values for the \citetalias{1999PASP..111...63F} model
+   Overplotted are the expected curves for the \citetalias{1999PASP..111...63F} model
    for specific choices of $R^F$. Note that these lines are not straight, which is apparent when comparing to the straight black $R_V=2.78$ line.
@@
  $R^F$ and $A^F_V$,
-and the wavelengths under consideration,  the values $a$ and $b$ change but only by $<5$\%.
+and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%.
 
@@
 contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.
+
 This result indicates that
 the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.
+That is to say, with no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
+2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by  \citetalias{1999PASP..111...63F} dust.
 
@@
 of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
-and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  
+and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\gamma$ vectors are chosen to intersect the origin.
 The two perspectives show that while the four vectors point in different directions for each band combination,
-they are almost coplanar in $UVI$, and close to coplanar in $BVR$.
+they are almost coplanar in $UVI$, and close to coplanar in $BVR$.  The $a$ and $b$ vectors and the $\gamma^0$ and $\gamma^1$
+vectors are bases for almost the same plane in the 5-dimensional color space, and can be transformed between themselves through rotation.
 
@@
 
+When fixing the origin of the $\gamma$'s to zero, the are found to be coplanar with $a$ and $b$.
+However the linear model does not specify zero dust so the origin of gamma is unspecified.
+The general result is that the magnitude planes of the linear and dust models are parallel.
+Color changes are consistent between the two models but there is no specification of the relation between $k^0$ and $k^1$ with $A_V$ and $E(B-V)$.
+
 A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
@@
 \end{equation}
-with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.  In the analysis,
-the $\kappa$'s are specified by the  prior of  
-zero covariance between $(A^F_V - \kappa_2 E^F(B-V))$ and  $(-\kappa_1 A^F_V + E^F(B-V))$.
+with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.
+The vector $a(X)+\kappa_1 b(X)$ represents extinction that can occur with fixed $R^F_0=1/\kappa_1$ and unconstrained $\kappa_2$.
+%While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
+%perturbations from a fixed $R^F_0$ is
+%\begin{equation}
+%A_X = A_V \left(a(X) + \left(\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0} \right) b(X) \right).
+%\end{equation}
+%Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.
+
 The preferred values for $\kappa$ are shown qualitatively in
@@
 the vector $\gamma^0_X$ is  aligned with 
-the dust vector $\left(a(X)+\kappa_1 b(X) \right)$  and $\gamma^1_X$
-is aligned with $(\kappa_2 a(X) + b(X))$  $UVI$-space.  Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply in $BVR$-space.
-
-To gain an intuitive understanding of $\kappa_1$, consider the hypothetical case where
-all supernovae experience dust with the same $R^F$.   The zero-covariance
-prior would be satisfied by  $\kappa_1=1/R^F$ and any arbitrary $\kappa_2$.
-The combination  $\gamma^0_V k_0$ would correspond to  $A^F_V$.  Both $k_1=0$  and $\gamma^1$ would be unconstrained.
-A slight relaxation away from the constant $R^F$ assumption would result in $\kappa_2$ no longer being arbitrary but determined by the prior, and a
-non-zero $k_1$ and a $\gamma^1$.
-
-Given the association of  our parameter $\gamma^0_V k_0$ with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model,
+the dust vector $a(X)+\kappa_1 b(X)$  and $\gamma^1_X$
+is aligned with $\kappa_2 a(X) + b(X)$  $UVI$-space.  
+%With these values of $\kappa$, the dust parameters are $R^F_0=2.4$ and $\Delta R^F=1.4$.
+Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply in $BVR$-space.
+%, which correspond to  $R^F_0=2.6$ and $\Delta R^F=1.4$.
+
+To gain an intuitive understanding of how the $\kappa$ values are determined, consider the hypothetical case where
+all supernovae experience dust with the same $R^F$.   There is only one free parameter $A^F_V$ and magnitudes are
+constrained to move along the vector $a(X)+b(X)/R^F$.  In the fit of the linear model, the zero-covariance condition is satisfied when
+$-\kappa_1 A^F_V + E^F(B-V)=0$,  i.e.\ when $\kappa_1=1/R^F$.  
+Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
+$\gamma^0$ is aligned with  $a(X)+b(X)/R^F$, and $\gamma^1$ is unconstrained.
+
+Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
+can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
+The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
+Our analysis yields an angle of 154\arcdeg between  $\gamma^0$ and $\gamma^1$.
+The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
+
+Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
 the former's distribution can be compared to the expectation for the latter.
@@
 median values of $\gamma^0_V k_0$.
-The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red, consistent
+The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
 with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
+This distribution is given by the data, in that it is independent of any knowledge or prior
+for the distribution of dust extinction the SN population is expected to suffer.
 
 Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which is associated with 
-extinction corrections due to deviations away from the canonical $R^F$ value.   The distribution has a long
+extinction corrections due to deviations away from the canonical $\kappa_1$ value.   The distribution has a long
 negative tail and is peaked at its positive edge, and by construction has a mean of zero.
@@
       \caption{ Histogram of
-median values of Left: $\gamma^0_V k_0$, which is associated with the $A^F_V$ of an $R^F \sim 2.4$ dust model; Right: $\gamma^1_V k_1$,
-which  is associated with $\left( E^F(B-V) - \frac{ A_V^F}{2.4}\right)$, i.e.\
-extinction corrections due to deviations away from the $R=2.4$ value.
+median values of Left: $\gamma^0_V k_0$, which is associated up to an offset with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model; Right: $\gamma^1_V k_1$,
+which  is associated with extinction corrections due to deviations away from the canonical $\kappa_1$ value.
    \label{k0_med:fig}}
@@
    \includegraphics[width=5.2in]{output11/kk.pdf}
-      \caption{ $\gamma^0_V k_0$ versus $\gamma^1_V k_1$.
+      \caption{$\gamma^1_V k_1$ versus $\gamma^0_V k_0$.
    \label{kk:fig}}

### 2017-02-02 apj.tex
forging through Greg's comments

@@
 
-Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which is associated with 
+Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which can be attributed to 
 extinction corrections due to deviations away from the canonical $\kappa_1$ value.   The distribution has a long
@@
 suffers very low galactic and host reddening
-\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A}.
+\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A,
+2017arXiv170101422H}.
 The overall higher photospheric velocities of
@@
 \begin{equation}
-E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)x_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)x_1,
+E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
 \end{equation}
 where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab} and the fit
-parameters $x_i $.
+parameters $e_i $.
 
@@
    \includegraphics[width=5.2in]{output11/sn2014j.pdf} 
-   \caption{Measured color excess for SN~2014J and the best-fit predictions from this article. 
+   \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.   Bottom: Residual color excess
+   between the data and model.
    \color{red}
@@
 The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
-overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} model using
-UV through NIR data,
-a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$
+overlap with the data within the error bars.   
+Our results can be compared with those of  \citet{2014ApJ...788L..21A} (Figure 3), who 
+use
+UV through NIR data to fit \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$.
 \color{red}
-is shown in their Figure 3.
 \color{black}
@@
 Among the supernovae in the SNfactory  set used to determine $\gamma^0$ and $\gamma^1$, the
-objects with the extreme median values have 
+objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
 %---
-$E_{\gamma^0}(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
-and for $E_{\gamma^1}(B-V)$ $-0.01 \pm 0.01$  and
+$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have$-0.01 \pm 0.01$  and
 $  0.06 \pm 0.03$ 
@@
 span of supernovae used to train the coefficients of the model, which is not unexpected if
-attributed to dust.
+attributable to dust.
 

### 2017-02-28 apj.tex
fix caption

@@
    \includegraphics[width=5.2in]{output11/coeff0.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
+            \caption{Model~I posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
@@
    \includegraphics[width=5.2in]{output11/coeff1.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $B$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $B$ band, from Model~I.
  \label{global2:fig}}
@@
    \includegraphics[width=5.2in]{output11/coeff2.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $V$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $V$ band, from Model~I.
  \label{global3:fig}}
@@
       \includegraphics[width=5.2in]{output11/coeff3.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $R$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $R$ band, from Model~I.
  \label{global4:fig}}
@@
          \includegraphics[width=5.2in]{output11/coeff4.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $I$ band.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $I$ band, from Model~I.
  \label{global5:fig}}
@@
    \includegraphics[width=5.2in]{output11/residual.pdf} 
-            \caption{Difference between predicted versus observed colors versus the observed color.
+            \caption{Differences between predicted versus observed colors versus the observed color.  For each color, the ideogram of the color differences is
+            shown on the right.
             \label{residual:fig}}
@@
 \end{pmatrix},
+\label{trans_I:eqn}
 \end{equation}
@@
 \vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
+\label{res_I:eqn}
 \end{align}
@@
 The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
+Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\gamma^0$.
 
@@
 \begin{pmatrix}
-c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} + \delta_0 D\\
-c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si} + \delta_1 D \\
-c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} + \delta_2 D\\
-c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} + \delta_3 D\\
-c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si} + \delta_4 D
+c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} + \delta_U D\\
+c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si} + \delta_B D \\
+c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} + \delta_V D\\
+c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} + \delta_R D\\
+c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si} + \delta_I D
 \end{pmatrix}
@@
 which affects the mean
-absolute magnitudes:
-each supernova has an intrinsic $D$ parameter that is linearly related to
+absolute magnitudes.  Thus
+each supernova is given an intrinsic $D$ parameter that is linearly related to
 absolute magnitudes through global coefficients $\delta$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
@@
 \color{red}
-For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
+In Model II, for $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
 color parameters, $(N-1)$ magnitude offsets,  $5 \times 7$ global coefficients, and $10$ parameters that describe the intrinsic
@@
 \color{red}
-The $\delta D$ terms contribute to the mean of the Normal distribution in Eqn.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
+The $\delta D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
 it is for this reason that for convenience these terms are referred to as ``intrinsic''.
-However, we emphasize now that we have also run the alternative case  of placing the
-$\delta D$ terms in mean of the Normal distribution in Eqn.~\ref{dust:eqn}, i.e.\ as extrinsic contributions.
+However, we emphasize now that we have also run the alternative case  of switching the placement of the
+$\delta D$ terms from Eq.~\ref{ewsiv:eqn} to Eq.~\ref{dust:eqn}, i.e.\ from intrinsic to extrinsic contributions.
 Analyses of the two different models give practically identical results, meaning that data are not constraining enough
@@
 
-To constrain the new degrees of freedom and degeneracies inherent in the model we impose that
+To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints.  We first
+require that
 $D+1/N$ be a simplex to break the 
@@
 \begin{equation}
-\langle D\rangle=0,  \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
+\langle D\rangle=0,\,  \delta \cdot \gamma^0=0,\, \delta \cdot \gamma^1=0.
 \end{equation}
-The first constraint specifies the definition of zero color.   The latter two confine possible magnitude
-variations to those that cannot be attributed to 
+The first of these constraints specifies the definition of zero color.   The latter two confine possible magnitude
+variations to be those that cannot be attributed to 
 the $\gamma k$ terms (i.e.\ dust); this condition breaks the degeneracies between $\delta D$  
 and $\gamma k$. 
-Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_0$,
+Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_U$,
 so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
 \color{blue}
-We apply the condition $\delta_4>0$ to break this degeneracy,
+We apply the condition $\delta_I>0$ to break this degeneracy,
 and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
 \color{black}
-In the running of the Monte Carlo, the initial conditions for
+In the running of the Monte Carlo fit, the initial conditions for
 $\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
@@
 are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the slight reduction of the standard
-deviations of the magnitude residuals.
+deviations of the magnitude residuals $\sigma_X$.
 The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust model, in that now
@@
 \begin{array}{rr}
-1.22 & 2.73 \\
-0.77 & -4.98
+1.15 & 2.79 \\
+0.71 & -4.95
 \end{array}
@@
 \begin{align}
-\vec{\epsilon}_a &=\{0.13, -0.15, -0.06,  0.04,  0.06\},\\
-\vec{\epsilon}_b &=\{ -0.04, 0.09,  -0.18,  0.28, -0.19\}
+\vec{\epsilon}_a &=\{0.05, -0.06, -0.06,  0.06,  0.07\},\\
+\vec{\epsilon}_b &=\{ -0.10, 0.20,  -0.19,  0.32, -0.30\}
 \end{align}
@@
 are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
-contribute similar 3\% and 4\% to the total  length of the vector.
+contribute similar 2\% and 4\% to the total  length of the vector.
+(These can be compared to the results of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.)
 %The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters of the Extrinsic--Intrinsic Model in \S\ref{model2:sec}.\label{global2:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
 \end{table}
@@
 to $I$.
-These are not the behaviors expected from normal dust,
+These are not the behaviors expected from normal dust, or
 circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
@@
    \includegraphics[width=5.2in]{output23/delta_corner.pdf}
-   \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.
+   \caption{Significance of the non-zero values of $\delta$ as demonstrated by the posterior contours for $\delta$ for Model~II.
+   Lines for $\delta=0$ are overplotted.
    \label{deltacorner:fig}}
@@
       \includegraphics[width=5.2in]{output23/deltaratio.pdf}
-   \caption{Significance of the non-zero values of $\delta$ seen through $\delta_X/\delta_I-1$.
+   \caption{Significance of the non-zero values of $\delta$ as demonstrated by the best-fit values of $\delta_X/\delta_I-1$ for $\delta$ for Model~II.
    \label{deltaratio:fig}}
@@
 
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}$ are given in the matrix.
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix.
 \begin{multline}
@@
 that this occurs.
-Second, the intrinsic term does not a second-order extrinsic correction.
+Second, the intrinsic term is not a second-order extrinsic correction.
 
@@
 
-\section{Supernova Model 3: Fitzpatrick Dust}
+\section{Supernova Model III: Fitzpatrick Dust}
 \label{model0:sec}
@@
 Dust models can explain the extrinsic magnitude and color variations found in
-the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we replace the $\gamma k$ color terms with extinction
-terms predicted by a dust model.  
+the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
+perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
+terms predicted by a dust extinction model from the literature.  
 %
@@
 
-The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R$ and $E(B-V)$.  The first, $R$,
-specifies the wavelength-dependent  attenuation  that we notate as $A/E(B-V)$.  The second, $E(B-V)$, specifies the normalization
-of that attenuation.  These two parameters can be combined to define a third dependent parameter $A_V \equiv R E(B-V)$.
+The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R^F$ and $E^F(B-V)$.  The first, $R^F$,
+specifies the wavelength-dependent  attenuation  that we notate as $A^F/E^F(B-V)$.  The second, $E^F(B-V)$, specifies the normalization
+of that attenuation.  These two parameters can be combined to define a third dependent parameter $A^F_V \equiv R^F E^F(B-V)$.
 The dust model is expressed as
 \begin{equation}
-A(\lambda; E(B-V), R) = E(B-V) \frac{A}{E(B-V)}\left(\lambda; R \right).
+A(\lambda; E^F(B-V), R^F) = E^F(B-V) \frac{A^F}{E^F(B-V)}\left(\lambda; R^F \right).
 \end{equation}
@@
 \begin{equation}
-A_X\left(A_V, E(B-V)  \right) = 2.5 \log{\left(\frac{\int d\lambda f(\lambda) X(\lambda)}{\int d\lambda 10^{-0.4 A\left(\lambda; E(B-V), R=\frac{A_V}{E(B-V)}\right)} f(\lambda) X(\lambda)}\right)},
+A_X\left(A^F_V, E^F(B-V)  \right) = 2.5 \log{\left(\frac{\int f(\lambda) X(\lambda)d\lambda}{\int 10^{-0.4 A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)} f(\lambda) X(\lambda)d\lambda } \right)},
 \end{equation}
@@
 \begin{equation}
-A_X\left(A_V, E(B-V)  \right) = \frac{\int d\lambda A\left(\lambda; E(B-V), R=\frac{A_V}{E(B-V)}\right)f(\lambda) X(\lambda)}{\int d\lambda f(\lambda) X(\lambda)}
+A_X\left(A^F_V, E^F(B-V)  \right) = \frac{\int  A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)f(\lambda) X(\lambda)d\lambda}{\int  f(\lambda) X(\lambda)d\lambda}
 \end{equation}
@@
 We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
-the SED of the SALT2, $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
+the SED of the SALT2 (v2.4), $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
 SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
@@
 \color{black}
-\section{Summary and Discussion}
+\section{Discussion and Summary}
 \label{discussion:sec}
-\subsection{Summary}
-To summarize, we model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
-extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
-affect supernova magnitudes and colors.  This model  does an excellent job in
-describing SN~2014J, a supernova with extreme colors that was not used in the training.  
-This work represents the first determination of the dust extinction curve outside the Local Group
-derived entirely independently of assumptions about the shape of the extinction curve and/or assumptions about the
-distribution of $A_V$.  An extended version
-of the model retains the features of the first model, and gives the first identification of  a new parameter that affects supernova
-colors in a manner that is distinct from  the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
 
@@
 The correlation between $EW_{Si}$ and the SALT2 $x_1$ light-curve shape parameter is verified
-for our sample.
+for our sample \citep{2017Chotard}.
 On the other hand, there is no such correlation seen between $A_{\delta I} = \delta_I D$ and $x_1$, as shown in Figure~\ref{x1:fig}. 
@@
 \citep{2010A&A...523A...7G}, showing that our model exhibits little loss in its ability to standardize
-magnitudes although $x_1$ is neglected.
+magnitudes even though $x_1$ is neglected.
 There is no apparent correlation
 between $x_1$ and the residuals between observed and model-predicted colors, as seen in
-Figure~\ref{x1res:fig}. 
+Figure~\ref{x1res:fig},
+\color{blue}
+though there is a hint of nonlinearity in the $B-V$ and $R-V$ colors.
+\color{red}
 We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta x_1$ to the 
@@
 has a non-zero value at $>2\sigma$.
-The evidence for a non-zero $\delta$ remains, meaning that it is not an artifact of
+The evidence for a non-zero $\delta$ remains as seen in the values of $\delta_X/\delta_I-1$ in Table~\ref{globalx1:tab}, meaning that it is not an artifact of
 having neglected light-curve shape.
@@
    \centering
-   \includegraphics[width=2.8in]{output23/x1si.pdf}
-   \includegraphics[width=2.8in]{output23/x1D.pdf}
-    \caption{Left: SALT2 $x_1$ versus $EW_{Si}$.  Right: $x_1$ versus $A_{\delta I}  = \delta_I D$.
+%   \includegraphics[width=2.8in]{output23/x1si.pdf}
+   \includegraphics[width=5in]{output23/x1D.pdf}
+    \caption{The SALT2 $x_1$ versus $A_{\delta I}  = \delta_I D$.
    \label{x1:fig}}
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters including the light-curve shape parameter $x_1$ \label{globalx1:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters including the light-curve shape parameter, $x_1$ \label{globalx1:tab}}
 \end{table}
@@
 \citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
-The $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.
+To first order, the $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.
 The values of $\eta$ in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
@@
 we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
-\citep{2016rigault}, and their ideograms for two samples divided by a host mass of  $\log{(M/M_\sun)}=10$
-used by  \citet{2013ApJ...770..108C}.
+\citep{2016rigault}, and their ideograms for two samples divided at host mass of  $\log{(M/M_\sun)}=10$
+as in  \citet{2013ApJ...770..108C}.
 Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta I}$, the difference is
@@
 Using the SNfactory sample,
-\citet{2013A&A...560A..66R} find that step in Hubble residuals is better related to local star formation rate, rather than host mass.
+\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star formation rate, rather than
+global host mass.
 
@@
 s     \includegraphics[width=2.8in]{output23/rigault2.pdf}
-      \caption{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host mass.  Hosts too faint for a mass measurement
-      are assigned a mass of 5.  Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
+      \caption{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
       less than and greater than  $\log{(M/M_\sun)}=10$.
@@
 
-We find a third supernova parameter that does not have a monotonic influence on supernova magnitudes as a function
+Our third supernova parameter does not have a monotonic influence on supernova magnitudes as a function
 of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes
@@
 wavelengths.  Qualitatively this would result in the structure for $\gamma_X/\gamma_V-1$ that we measure.
-We conjecture that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth
+We speculate that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth
 of the reionization front with respect to the core of the ejecta at peak, yielding the wavelength-dependent color behavior
@@
 
-Although the $D$ parameter has ben referred to as ``intrinsic'', do to its placement in the model and the correspondence
+Although the $D$ parameter has ben referred to as ``intrinsic'', due to its placement in the model and the correspondence
 of the $k$ parameters with those of extrinsic two-parameter dust models, the analysis cannot quantitatively distinguish
@@
 \color{red}
-The purpose of this analysis was designed to mine information from the SNfactory data set, and so the results presented here
+This analysis was designed to mine information from the SNfactory data set, and so the results presented here
 are specific to it both in terms of its population distribution and potentially noise.  This is the approach taken by previous
@@
 of an independent set.
+\color{black}
+
+\subsection{Summary}
+To summarize, we model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
+extrinsic color parameters.  Analyzing SNfactory data with this model, we find significant evidence that the above parameters do
+affect supernova magnitudes and colors.  This model  does an excellent job in
+describing SN~2014J, a supernova with extreme colors that was not used in the training.  
+This work represents the first determination of the dust extinction curve outside the Local Group
+derived entirely independently of assumptions about the shape of the extinction curve and/or assumptions about the
+distribution of $A_V$.  An extended version
+of the model retains the features of the first model, and gives the first identification of  a new parameter that affects supernova
+colors in a manner that is distinct from  the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
+
+\color{blue}
+An interesting direction for future work is to use narrower bands for generating synthetic photometry.  When the bandwidth were small enough
+to resolve spectral features, the analysis would produce a spectroscopic model.   Higher resolution would allow us to forego 
+the use of a fiducial template necessary to predict broadband fluxes generated by dust models.
 \color{black}

### 2017-03-22 apj.tex
more simulation

@@
 %-----
-$1-5\times10^{-5}$
+$(1-5\times10^{-5})$
 %------
 confidence.
+The color changes allowed by the model are almost parallel to the color changes allowed by the dust model of  \citet{1999PASP..111...63F} with floating
+total-to-selective extinction parameter $R^F$.  The prior of no parameter covariance used in the training, and the deduced extinctions and color excess
+are both qualitatively consistent with $R^F \sim 2.4$.
 The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
-Extending the model to three color parameters gives almost identical results for
+Inspired that our  two-parameter model, with no conditioning that would steer it toward a dust model, produces behavior similar to that expected from Galactic dust, we extend  the model to three color parameters.
+In this new case we obtain consistent results for
 all the parameters in common,
@@
 %--- table.py
-$1-5\times10^{-4}$
+$(1-5\times10^{-4})$
 %-----
@@
 beyond that tracked by the spectral features and two-parameter dust models.
+A direct incorporation of dust models into our formalism is impossible. An indirect incorporation of dust
+yields in constant-$R^F$ model $R^F \sim 3$, but the implementation is sensitive to systematic uncertainties that arise
+from the need to specify the colors of an unextincted supernova and its use of absolute extinction, neither of which is used in our original model.
 \end{abstract}
@@
 
+\color{black}
 The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
-\color{black}
-
+\color{blue}
+We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
+Ten realizations of simulated data are generated based on the data covariances, and then analyzed separately.   The posteriors of the ten realizations
+are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered well
+within the 68\% credible interval.  There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
+the uncertainties in the predictor variable, which in turn lead to 
+regression dilution.  Our analysis is susceptible to this bias because we do consciously do not include distributions
+of supernova parameters as part of our model.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output23_sim/coeff0.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $U$ band of ten independent simulated data sets.
+Lines show the values of the input values.
+            \label{simglobal1:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output23_sim/coeff1.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $B$ band of ten independent simulated data sets.
+Lines show the values of the input values.
+ \label{simglobal2:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output23_sim/coeff2.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $V$ band of ten independent simulated data sets.
+Lines show the values of the input values.
+ \label{simglobal3:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.2in]{output23_sim/coeff3.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $R$ band of ten independent simulated data sets.
+Lines show the values of the input values.
+\label{simglobal4:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+         \includegraphics[width=5.2in]{output23_sim/coeff4.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $I$ band of ten independent simulated data sets.
+Lines show the values of the input values.
+ \label{simglobal5:fig}}
+\end{figure}
+
+\color{black}
 \section{Supernova Model III: Fitzpatrick Dust}
@@
 whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
+
+\color{blue}
+We stress that our $\delta$ vector does not capture the full behavior of the observable effects of the $D$ parameter, but rather only
+the contribution perpendicular to the $\gamma$ vectors.
+\color{black}
 

### 2017-03-22 simdata.py

@@ -6,92 +6,100 @@ import numpy
 import pystan
 import sivel as sivel2
 
+
+# two color parameter model
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+
+f = open('temp23.pkl','rb')
+(fit,_) = pickle.load(f)
+f.close()
+
+sivel,sivel_err,x1,x1_err,zcmb,zerr = sivel2.sivel(data)
+
+
+
+use = numpy.isfinite(sivel)
+
+#  The ordering is 'Ca','Si','U','B','V','R','I'
+
+EW_obs = data['obs'][:,0:2]
+mag_obs = data['obs'][:,2:]
+EW_cov = data['cov'][:,0:2,0:2]
+mag_cov = data['cov'][:,2:,2:]
+
+sivel=sivel[use]
+sivel_err = sivel_err[use]
+EW_obs=EW_obs[use]
+mag_obs=mag_obs[use]
+EW_cov= EW_cov[use]
+mag_cov=mag_cov[use]
+
+nsne, nmags = mag_obs.shape
+
+# # renormalize the data
+EW_mn = EW_obs.mean(axis=0)
+EW_renorm = (EW_obs - EW_mn)
+
+mag_mn = mag_obs.mean(axis=0)
+mag_renorm  = mag_obs-mag_mn
+
+sivel_mn = sivel.mean()
+sivel_renorm = sivel-sivel_mn
+
+# Truth
+
+# c = numpy.zeros(5)
+# alpha = numpy.array([0.005, 0.002,0.002,0.002,0.003])
+# beta = numpy.array([0.03, 0.03,0.03,0.02,0.02])
+# eta = numpy.array([0.0001,1.5e-4,0.0005,0.0005,-0.00003])
+# gamma = numpy.array([64.1,51.9,38.5,29.3,20.8])
+# gamma1 = numpy.array([-10.5,-11.9,-14.6,-13.9,-12.9])
+# delta = numpy.array([2.13, -2.30,-1.87,0.38,2.09])
+# delta = delta.transpose()
+# y=numpy.array([numpy.dot(delta, gamma), numpy.dot(delta, gamma1)])
+# A=numpy.zeros((2,2))
+# A[0,0] = numpy.dot(gamma,gamma)
+# A[1,1] = numpy.dot(gamma1,gamma1)
+# A[0,1] = numpy.dot(gamma,gamma1)
+# A[1,0] = A[0,1];
[…]

### 2017-03-22 view23_scoeff.py

@@ -1,0 +1,120 @@
+#!/usr/bin/env python
+
+import pickle
+import pystan
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import corner
+from matplotlib.backends.backend_pdf import PdfPages
+import numpy
+import sncosmo
+import scipy
+import cPickle
+import matplotlib as mpl
+import sivel
+
+f = open('temp23_sim0.pkl','rb')
+(fit,_) = pickle.load(f)
+
+mega = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['gamma1'],fit['rho1'],fit['L_sigma']])
+
+print mega.shape
+for index in xrange(1,10):
+    f = open('temp23_sim{}.pkl'.format(index),'rb')
+    (fit,_) = pickle.load(f)
+    mega_ = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['gamma1'],fit['rho1'],fit['L_sigma']])
+
+    mega = numpy.concatenate((mega,mega_),axis=1)
+
+mega = numpy.transpose(mega)
+
+
+
+f = open('temp23.pkl','rb')
+(fit_input,_) = pickle.load(f)
+
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+sivel,sivel_err,x1,x1_err,zcmb,zerr = sivel.sivel(data)
+
+use = numpy.isfinite(sivel)
+
+
+filts = ['U','B','V','R','I']
+
+#  The ordering is 'Ca','Si','U','B','V','R','I'
+
+EW_obs = data['obs'][:,0:2]
+mag_obs = data['obs'][:,2:]
+EW_cov = data['cov'][:,0:2,0:2]
+mag_cov = data['cov'][:,2:,2:]
+
+sivel=sivel[use]
+sivel_err = sivel_err[use]
+x1=x1[use]
+x1_err = x1_err[use]
+EW_obs=EW_obs[use]
+mag_obs=mag_obs[use]
+EW_cov= EW_cov[use]
+mag_cov=mag_cov[use]
+
+EW_mn = EW_obs.mean(axis=0)
+EW_renorm = (EW_obs - EW_mn)
+
+mag_mn = mag_obs.mean(axis=0)
+mag_renorm  = mag_obs-mag_mn
+
+sivel_mn = sivel.mean()
[…]

### 2017-03-26 apj.tex
simulated model 11

@@
 beyond that tracked by the spectral features and two-parameter dust models.
-A direct incorporation of dust models into our formalism is impossible. An indirect incorporation of dust
-yields in constant-$R^F$ model $R^F \sim 3$, but the implementation is sensitive to systematic uncertainties that arise
-from the need to specify the colors of an unextincted supernova and its use of absolute extinction, neither of which is used in our original model.
+%A direct incorporation of dust models into our formalism is impossible. An indirect incorporation of dust
+%yields in constant-$R^F$ model $R^F \sim 3$, but the implementation is sensitive to systematic uncertainties that arise
+%from the need to specify the colors of an unextincted supernova and its use of absolute extinction, neither of which is used in our original model.
 \end{abstract}
@@
 
-We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
-A direct analysis of the  \citetalias{1999PASP..111...63F} dust model is presented later
-in \S\ref{model0:sec}.
-
 %Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
@@
 
+We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
 The 2-parameter linear model
@@
    and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combinations $a(X)+b(X)/2.4$ and  $a(X)+b(X)/2.6$ are shown in the dotted
-   lines: thy are almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ for $UVI$ and $BVR$ respectively.  $b(X)$ shown in the dotted line is
+   lines: they are almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ for $UVI$ and $BVR$ respectively.  $b(X)$ shown in the dotted line is
    almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$ in $UVI$ but is clearly distinct in $BVR$.  
@@
 The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
-Our analysis yields an angle of 154\arcdeg between  $\gamma^0$ and $\gamma^1$.
+Our analysis yields an angle of 154\arcdeg\ between  $\gamma^0$ and $\gamma^1$.
 The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
 Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\gamma^0$.
+
+As a check of the above interpretation, we generate a simulated dataset with the same numbers and uncertainties as our data, based on a
+SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
+are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample, and $R^F$ values drawn from a log-normal
+distribution with a mean of $2.4$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
+measurement uncertainty are the only sources of variation in magnitudes.  As with the analysis of our data, we find that the
+$\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector consistent with
+$\kappa_1=1/2.3$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
+   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
+   \caption{
+   Two perspectives of $UVI$- spaces
+of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
+   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
+   input $R^F$ drawn from a log-normal distribution  with a mean of $2.4$ and 0.05 standard deviation.
+   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
+   lines, the former is 
+   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
+   \label{plane_sim:fig}}
+\end{figure}
 
@@
 Ten realizations of simulated data are generated based on the data covariances, and then analyzed separately.   The posteriors of the ten realizations
-are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered well
-within the 68\% credible interval.  There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
+are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
+relative to the statistical uncertainties.  There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
 the uncertainties in the predictor variable, which in turn lead to 
@@
 \color{black}
-\section{Supernova Model III: Fitzpatrick Dust}
-\label{model0:sec}
-\color{blue}
-Dust models can explain the extrinsic magnitude and color variations found in
-the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
-perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
-terms predicted by a dust extinction model from the literature.  
-%
-%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
-%except that dust
-%is used in place of  the linear two-color-parameter  model.      
-The dust model of  \citet{1999PASP..111...63F} is considered:
-while commonly used dust
-models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
-does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.
-
-The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R^F$ and $E^F(B-V)$.  The first, $R^F$,
-specifies the wavelength-dependent  attenuation  that we notate as $A^F/E^F(B-V)$.  The second, $E^F(B-V)$, specifies the normalization
-of that attenuation.  These two parameters can be combined to define a third dependent parameter $A^F_V \equiv R^F E^F(B-V)$.
-The dust model is expressed as
-\begin{equation}
-A(\lambda; E^F(B-V), R^F) = E^F(B-V) \frac{A^F}{E^F(B-V)}\left(\lambda; R^F \right).
-\end{equation}
-
-In the broadband photometry of a source with SED $f(\lambda)$ observed in a filter with transmission $X$, the attenuation $A_X$ is
-\begin{equation}
-A_X\left(A^F_V, E^F(B-V)  \right) = 2.5 \log{\left(\frac{\int f(\lambda) X(\lambda)d\lambda}{\int 10^{-0.4 A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)} f(\lambda) X(\lambda)d\lambda } \right)},
-\end{equation}
-whose first-order approximation
-\begin{equation}
-A_X\left(A^F_V, E^F(B-V)  \right) = \frac{\int  A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)f(\lambda) X(\lambda)d\lambda}{\int  f(\lambda) X(\lambda)d\lambda}
-\end{equation}
-is easy to interpret as an effective extinction.
-
-We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
-the SED of the SALT2 (v2.4), $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
-SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
-parameter values of an unextincted
-supernova.
-The SALT2 SED determines the values of $A_X$ and the
-intrinsic colors.
-
-This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections in that the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
-Taking the SALT2 template as the unextincted supernova, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
-Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
-The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
-while simultaneously showing no color excess is $B-R$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
-   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
-    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
-    taking the SALT2 template as an unextinced supernova.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
-allowed by \citetalias{1999PASP..111...63F} dust.
-Right:    $A_X/E(X-V)$ of the best-fit $c$'s 
-    relative to SALT2. \label{model1118:fig}}
-\end{figure}
-
-%
-%We emphasize now that our broadband magnitude model does not ambiguously specify $A_X$, which depend
-%on the SED of the source.  
-%In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
-%updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
-%SALT2 template yields similar results.)
-%The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
-%of model error.  Consider the SED to be the sum of the template and an offset
+%\section{Supernova Model III: Fitzpatrick Dust}
+%\label{model0:sec}
+%\color{blue}
+%Dust models can explain the extrinsic magnitude and color variations found in
+%the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
+%perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
+%terms predicted by a dust extinction model from the literature.  
+%%
+%%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
+%%except that dust
+%%is used in place of  the linear two-color-parameter  model.      
+%The dust model of  \citet{1999PASP..111...63F} is considered:
+%while commonly used dust
+%models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
+%does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.
+%
+%
+%The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R^F$ and $E^F(B-V)$.  The first, $R^F$,
+%specifies the wavelength-dependent  attenuation  that we notate as $A^F/E^F(B-V)$.  The second, $E^F(B-V)$, specifies the normalization
+%of that attenuation.  These two parameters can be combined to define a third dependent parameter $A^F_V \equiv R^F E^F(B-V)$.
+%The dust model is expressed as
 %\begin{equation}
-%f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
+%A(\lambda; E^F(B-V), R^F) = E^F(B-V) \frac{A^F}{E^F(B-V)}\left(\lambda; R^F \right).
 %\end{equation}
-%To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
-%extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.
-
-%For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
-%$-0.21 \le A_V \le 1.8$, $2.1 \le R \le 6.9$ with a third-order polynomial in $A_V$ and $E(B-V)$.   The limits in $R$ represent the range of
-%values that enter the dust-model training.
-%The differences between the extinction and the polynomial approximation are small relative to  $\partial A_X/ \partial R$ over the scales of
-%$R$ of interest.
-
-%
-%
+%
+%In the broadband photometry of a source with SED $f(\lambda)$ observed in a filter with transmission $X$, the attenuation $A_X$ is
+%\begin{equation}
+%A_X\left(A^F_V, E^F(B-V)  \right) = 2.5 \log{\left(\frac{\int f(\lambda) X(\lambda)d\lambda}{\int 10^{-0.4 A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)} f(\lambda) X(\lambda)d\lambda } \right)},
+%\end{equation}
+%whose first-order approximation
+%\begin{equation}
+%A_X\left(A^F_V, E^F(B-V)  \right) = \frac{\int  A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)f(\lambda) X(\lambda)d\lambda}{\int  f(\lambda) X(\lambda)d\lambda}
+%\end{equation}
+%is easy to interpret as an effective extinction.
+%
+%
+%We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
+%the SED of the SALT2 (v2.4), $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
+%SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
+%parameter values of an unextincted
+%supernova.
+%The SALT2 SED determines the values of $A_X$ and the
+%intrinsic colors. 
+%
+%This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections in that the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
+%Taking the SALT2 template as the unextincted supernova, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
+%Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
+%The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
+%while simultaneously showing no color excess is $B-R$.
 % 
@@
 %   \centering
-%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
-%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
-%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
-%   \label{dfitz:fig}}
+%   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
+%   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
+%    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
+%    taking the SALT2 template as an unextinced supernova.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
+%allowed by \citetalias{1999PASP..111...63F} dust.
+%Right:    $A_X/E(X-V)$ of the best-fit $c$'s 
+%    relative to SALT2. \label{model1118:fig}}
 %\end{figure}
 %
-
-The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
-and
-\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 template,
-and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
-and there is one global $R$ parameter.  
-%
-%
-%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
-%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
-%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
-%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
-%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.
-
-Results from evaluating this model with SNf data
-provide further evidence of the inconsistency between the ansatz and the models of the previous section.
-The dust-model analysis of this section sets the magnitude of an $A_V=0$ supernova, so now  magnitudes of the canonical
-supernova in \S\ref{model:sec} can also be compared (along with color) to the expectations of the dust model.  The magnitude difference, $\Delta c_X$,
-is the difference between the $c_X$ parameters of the two analyses.
-Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
-corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
-to SALT2: these values are plotted in
-Figure~\ref{model1118:fig}.
-The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.
-
-The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram of the median $A_V$ determined for
-each supernova. The
-$A_V$ distribution  has a slow rise from zero; recall that the equivalent $\gamma^0_V k_0$
-from the linear model of \S\ref{model:sec} has the sharp rise expected from of a large fraction of supernovae
-experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
-$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
-While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
-to $R=3.17^{0.20}_{-0.17}$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
-   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
-    \caption{Left: Histogram of the median $A_V$ determined for
-each supernova.  The $\gamma^0_V k_0$ medians from our 2-parameter model of \S\ref{model:sec} is also shown.  The means of the measurement
-uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
-Right: Posteriors for $R$.  Results for both the SALT2 supernova model and the updated \citet{2007ApJ...663.1187H} are shown.
-   \label{AVRV:fig}}
-\end{figure}
-
-The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models,
-and our ansatz for incorporating dust is limited systematically in measuring 
-the total-to-selective extinction.  We emphasize also that $R^F$ determined in this section are based on  both absolute extinction and color,
-whereas the $\gamma$'s (and resulting $\kappa_1$) in \S\ref{model:sec} do not depend on absolute extinction, i.e. the extra model constraint  of the
-zero-extinction supernova.
-
-%
-%The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
-%$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
-%The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
-%non-zero.  Insofar that the $A_V$ and $R_V$
-%parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
-%is important.
+%
+%%
+%%We emphasize now that our broadband magnitude model does not ambiguously specify $A_X$, which depend
+%%on the SED of the source.  
+%%In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
+%%updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
+%%SALT2 template yields similar results.)
+%%The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
+%%of model error.  Consider the SED to be the sum of the template and an offset
+%%\begin{equation}
+%%f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
+%%\end{equation}
+%%To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
+%%extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.
+%
+%%For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
+%%$-0.21 \le A_V \le 1.8$, $2.1 \le R \le 6.9$ with a third-order polynomial in $A_V$ and $E(B-V)$.   The limits in $R$ represent the range of
+%%values that enter the dust-model training.
+%%The differences between the extinction and the polynomial approximation are small relative to  $\partial A_X/ \partial R$ over the scales of
+%%$R$ of interest.
+%
+%%
+%%
+%%
+%%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%%   \centering
+%%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
+%%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
+%%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
+%%   \label{dfitz:fig}}
+%%\end{figure}
+%%
+%
+%
+%The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
+%and
+%\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 template,
+%and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
+%and there is one global $R$ parameter.  
+%%
+%%
+%%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
+%%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
+%%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
+%%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
+%%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.
+%
+%Results from evaluating this model with SNf data
+%provide further evidence of the inconsistency between the ansatz and the models of the previous section.
+%The dust-model analysis of this section sets the magnitude of an $A_V=0$ supernova, so now  magnitudes of the canonical
+%supernova in \S\ref{model:sec} can also be compared (along with color) to the expectations of the dust model.  The magnitude difference, $\Delta c_X$,
+%is the difference between the $c_X$ parameters of the two analyses.
+%Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
+%corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
+%to SALT2: these values are plotted in
+%Figure~\ref{model1118:fig}.
+%The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.
+%
+%The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram of the median $A_V$ determined for
+%each supernova. The
+%$A_V$ distribution  has a slow rise from zero; recall that the equivalent $\gamma^0_V k_0$
+%from the linear model of \S\ref{model:sec} has the sharp rise expected from of a large fraction of supernovae
+%experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
+%$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
+%While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
+%to $R=3.17^{0.20}_{-0.17}$.
 %
@@
 %   \centering
-%   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
-%    \caption{Difference between per-supernova
-%$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
-%   \label{CCMF99:fig}}
+%   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
+%   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
+%    \caption{Left: Histogram of the median $A_V$ determined for
+%each supernova.  The $\gamma^0_V k_0$ medians from our 2-parameter model of \S\ref{model:sec} is also shown.  The means of the measurement
+%uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
+%Right: Posteriors for $R$.  Results for both the SALT2 supernova model and the updated \citet{2007ApJ...663.1187H} are shown.
+%   \label{AVRV:fig}}
 %\end{figure}
-
-\color{black}
+%
+%The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models,
+%and our ansatz for incorporating dust is limited systematically in measuring 
+%the total-to-selective extinction.  We emphasize also that $R^F$ determined in this section are based on  both absolute extinction and color,
+%whereas the $\gamma$'s (and resulting $\kappa_1$) in \S\ref{model:sec} do not depend on absolute extinction, i.e. the extra model constraint  of the
+%zero-extinction supernova.
+%
+%
+%%
+%%The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
+%%$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
+%%The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
+%%non-zero.  Insofar that the $A_V$ and $R_V$
+%%parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
+%%is important.
+%%
+%%
+%%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%%   \centering
+%%   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
+%%    \caption{Difference between per-supernova
+%%$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
+%%   \label{CCMF99:fig}}
+%%\end{figure}
+%
+%
+%\color{black}
 \section{Discussion and Summary}
@@
 to resolve spectral features, the analysis would produce a spectroscopic model.   Higher resolution would allow us to forego 
-the use of a fiducial template necessary to predict broadband fluxes generated by dust models.
+the use of a fiducial template necessary to predict broadband fluxes generated by dust models, and also allow direct incorporation
+of dust models into our framework.
 \color{black}

### 2017-03-26 fitz11_sim.py

@@ -1,0 +1,467 @@
+#!/usr/bin/env python
+import pickle
+import numpy
+import sncosmo
+import scipy
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.pyplot as plt
+import f99_band
+import emcee
+import matplotlib as mpl
+
+mpl.rcParams['font.size'] = 14
+
+# Get the data
+f = open('temp11_sim.pkl','rb')
+(fit, _) = pickle.load(f)
+f.close()
+
+# Determine the plane approximaion for Fitzpatrick
+
+# Partial derivatives with respect to av and ebv
+av=0.1
+ebv=0.1/2.5
+A1= f99_band.A_X(r_v=av/ebv, ebv=ebv)
+
+# pkl_file = open('fitz.pkl', 'r')
+# a=pickle.load(pkl_file)
+# pkl_file.close()
+
+# AX = a[0]* av + a[1] * av**2 \
+#   + a[2]* ebv+ a[3] * ebv**2 \
+#   + a[4] * av* ebv \
+#   + a[5]* av**3 \
+#   + a[6] * ebv**3 \
+#   + a[7] * (av**2) * ebv \
+#   + a[8] * av * (ebv**2)
+
+# plt.plot(A1-AX)
+
+# plt.show()
+
+# wefe
+A2= f99_band.A_X(r_v=(av+0.01)/ebv, ebv=ebv)
+dAdAv = (A2 - A1)/0.01
+
+A3= f99_band.A_X(r_v=av/(ebv+0.001), ebv=ebv+0.001)
+dAdebv = (A3 - A1)/0.001
+
+print '{0[0]:6.2f}, {0[1]:6.2f}, {0[2]:6.2f}, {0[3]:6.2f}, {0[4]:6.2f}'.format(dAdAv)
+print '{0[0]:6.2f}, {0[1]:6.2f}, {0[2]:6.2f}, {0[3]:6.2f}, {0[4]:6.2f}'.format(dAdebv)
+
+# av=0.1
+# ebv=0.1/3.1
+# A1= f99_band.A_X(r_v=av/ebv, ebv=ebv)
+
+# A2= f99_band.A_X(r_v=(av+0.01)/ebv, ebv=ebv)
+# dAdAv = (A2 - A1)/0.01
+
+# A3= f99_band.A_X(r_v=av/(ebv+0.001), ebv=ebv+0.001)
[…]

### 2017-03-26 simdata_gerard.py

@@ -100,7 +100,7 @@ for i in xrange(nsne):
     # model0.parameters[2]=x0
     # model0.parameters[3]=x1
     # model0.parameters[4]=c
-    model = sncosmo.Model(source='hsiao', effects=[dust], effect_names=['host'], effect_frames=['rest'])
+    model = sncosmo.Model(source='salt2', effects=[dust], effect_names=['host'], effect_frames=['rest'])
     # model.parameters[2]=x0
     # model.parameters[3]=x1
     # model.parameters[4]=c

### 2017-03-26 view11_sim.py

@@ -1,0 +1,926 @@
+#!/usr/bin/env python
+
+import pickle
+import pystan
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import corner
+from matplotlib.backends.backend_pdf import PdfPages
+import numpy
+import sncosmo
+import scipy
+import cPickle
+import matplotlib as mpl
+import sivel
+mpl.rcParams['font.size'] = 18
+
+f = open('temp11_sim.pkl','rb')
+(fit,_) = pickle.load(f)
+
+# for key in fit.keys():
+#     print key, fit[key].min(), fit[key].max()
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+# dic_phreno=cPickle.load(open("phrenology_2016_12_01_CABALLOv1.pkl"))
+
+# dic_meta=cPickle.load(open("META.pkl"))
+
+# sivel=[]
+# sivel_err=[]
+# x1 = []
+# x1_err = []
+# for sn in data['snlist']:
+#    if sn in dic_meta.keys() and sn in dic_phreno.keys():
+#       meta = dic_meta[sn]
+#       vSiII_6355_lbd=0.
+#       vSiII_6355_lbd_err=0.
+#       counter  = 0
+#       for sp in dic_phreno[sn]["spectra"]:
+#          if sp in meta['spectra'].keys() and  numpy.abs(meta['spectra'][sp]['salt2.phase']) < 2.5  and numpy.isfinite(dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]):
+#             vSiII_6355_lbd += dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
+#             vSiII_6355_lbd_err += 1/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
+#             counter +=1
+#       if counter !=0:
[…]

### 2017-03-27 apj.tex
committing everything that changed for the request for comments

@@
 are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample, and $R^F$ values drawn from a log-normal
-distribution with a mean of $2.4$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
+distribution with a mean of $\ln{2.4}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
 measurement uncertainty are the only sources of variation in magnitudes.  As with the analysis of our data, we find that the
-$\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector consistent with
-$\kappa_1=1/2.3$.
+$\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector almost consistent with
+$\kappa_1^{-1}=2.4$, as expected given the mean of $\ln{2.4}$ of the input log-normal distribution.
 
@@
    and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
-   input $R^F$ drawn from a log-normal distribution  with a mean of $2.4$ and 0.05 standard deviation.
+   input $R^F$ drawn from a log-normal distribution  with a mean of $\ln{2.4}$ and 0.05 standard deviation.
    The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted

### 2017-03-27 fitz11.py

@@ -106,7 +106,6 @@ for s in ['gamma','rho1']:
   ans = c-ans[0]*dAdebv - ans[1]*dAdAv
   res.append(ans)
 
-
 tmat = numpy.array(tmat)
 res= numpy.array(res)
 
@@ -141,7 +140,12 @@ ax.plot([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum],label=r'$a(X)+b(X)/2.4$'
 crap = -6.8*dAdAv + dAdebv
 dum  = numpy.sqrt(crap[0]**2+crap[2]**2+crap[4]**2)
 ax.plot([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum],label=r'$-6.8a(X)+b(X)$',ls=':',color='black')
-crap = dAdAv + dAdebv/2.6
+
+# crap = -16*dAdAv - dAdebv
+# dum  = numpy.sqrt(crap[0]**2+crap[2]**2+crap[4]**2)
+# ax.plot([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum],label=r'$-6.8a(X)-b(X)$',ls=':',color='black')
+
+# crap = dAdAv + dAdebv/2.6
 # dum  = numpy.sqrt(crap[0]**2+crap[2]**2+crap[4]**2)
 # ax.plot([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum],label=r'$a(X)+b(X)/2.6$',ls=':',color='black')
 #crap = dAdebv

### 2017-03-29 apj.tex
more simulations for model 11

@@
 
+\color{orange}
+For brevity, we do not present here the analysis of simulated data used to validate and bias quantify bias in our results.
+The simulation tests in \S\ref{model2:sec} are representative for both Model~1 of this Section and Model~2 of the subsequent section.
+\color{black}
+
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
@@
 There is a pair of parameter values,  $k_0^0$ and $k_1^0$, that correspond to supernovae experiencing no extrinsic effect.
+\color{orange}
+For observer filters $X$ and $Y$, we define $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$, $E(X-Y)=A_X-A_Y$.
 The true extrinsic
 extinction is
-$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
+$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$.
+\color{blue}
 The true extrinsic color excess is $E^T(B-V) = A^T_B-A^T_V$, so that the total-to-selective extinction is $R^T_V=A^T_V/E^T(B-V)$.
@@
    \includegraphics[width=2.95in]{output11/plane1.pdf}
-   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
-   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
+%   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
+%   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
    \caption{
-   Two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
+   \color{orange}
+   Two perspectives (left and right columns) of the $UVI$-space
 of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
-   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combinations $a(X)+b(X)/2.4$ and  $a(X)+b(X)/2.6$ are shown in the dotted
-   lines: they are almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ for $UVI$ and $BVR$ respectively.  $b(X)$ shown in the dotted line is
-   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$ in $UVI$ but is clearly distinct in $BVR$.  
+   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.44$ is shown in the dotted red
+   line: it is almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.   The combination $-7.31a(X)+b(X)$ is shown in the dotted blue
+   line: it is
+   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$ in $UVI$.  
    \label{plane:fig}}
@@
 
-The preferred values for $\kappa$ are shown qualitatively in
-Figure~\ref{plane:fig}.  For $\kappa_1=1/2.4$, $\kappa_2=-6.8$
-the vector $\gamma^0_X$ is  aligned with 
-the dust vector $a(X)+\kappa_1 b(X)$  and $\gamma^1_X$
-is aligned with $\kappa_2 a(X) + b(X)$  $UVI$-space.  
-%With these values of $\kappa$, the dust parameters are $R^F_0=2.4$ and $\Delta R^F=1.4$.
-Slightly shifted values of $\kappa_1=1/2.6$, $\kappa_2=-6.1$ apply in $BVR$-space.
-%, which correspond to  $R^F_0=2.6$ and $\Delta R^F=1.4$.
+\color{orange}
+The preferred values for $\kappa^{-1}$ can be determined from the matrix elements of Eqn.~\ref{model11trans:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa^{-1}_2=-5.27/0.72=-7.31$.
+The directions of the $\gamma$ vectors, and  the expectations from  \citetalias{1999PASP..111...63F} with $R=\kappa^{-1}$, are shown in 
+Figure~\ref{plane:fig}.  There is almost perfect alignment between $\gamma^0$ and $R=2.44$ dust.
+ From the Monte Carlo chains, we find a 68\% credible interval for $\kappa^{-1}_1$ of 2.26--2.63.
+\color{blue}
 
@@
 distribution with a mean of $\ln{2.4}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
-measurement uncertainty are the only sources of variation in magnitudes.  As with the analysis of our data, we find that the
+measurement uncertainty are the only sources of variation in magnitudes.  
+From the Monte Carlo chains, we find a 68\% credible interval for $\kappa^{-1}_1$ of 2.18--2.40.
+As with the analysis of our data, we find that the
 $\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector almost consistent with
@@
 \end{align}
+\label{model11trans:eqn}
 \color{black}

### 2017-03-30 apj.tex
Remove zero-color discussion

@@
 The color changes allowed by the model are almost parallel to the color changes allowed by the dust model of  \citet{1999PASP..111...63F} with floating
-total-to-selective extinction parameter $R^F$.  The prior of no parameter covariance used in the training, and the deduced extinctions and color excess
-are both qualitatively consistent with $R^F \sim 2.4$.
+total-to-selective extinction parameter $R^F$.  The prior of no parameter covariance used in the training, and the deduced color excess
+is consistent with $R^F = 2.44$.
 The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
@@
 with probability $1-5\times 10^{-5}$.
-
-There is a pair of parameter values,  $k_0^0$ and $k_1^0$, that correspond to supernovae experiencing no extrinsic effect.
-\color{orange}
-For observer filters $X$ and $Y$, we define $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$, $E(X-Y)=A_X-A_Y$.
-The true extrinsic
-extinction is
-$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$.
-\color{blue}
-The true extrinsic color excess is $E^T(B-V) = A^T_B-A^T_V$, so that the total-to-selective extinction is $R^T_V=A^T_V/E^T(B-V)$.
-Our $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$ constraints
-do not determine $k_0^0$ and $k_1^0$, and so the extrinsic extinction and color excess per supernova are not products of our analysis.
-
-%our analysis does not specify their values.
-%Recall that there are degeneracies between the intrinsic (Eqn.~\ref{ewsiv:eqn}) and
-%extrinsic (Eqn.~\ref{dust:eqn}) parameters of our model.  Part of that degeneracy is
-%broken by imposing $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$,
-%but this choice does not specify the parameter values.
-
-Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
-rearranged as
-\begin{equation}
-A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
-\end{equation}
-Making the assumption that $R^T_V$ is the same for all supernovae,
-its value can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.
-
-Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$.
-The full set of supernovae does not coincide with the expectations of a single linear relation; rather the supernova population is peaked
-on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
-but can have values that extend toward lower values.
-The assumption of a constant $R^T_V$ is not altogether correct; still we perform a linear fit that gives a slope of
-%----- fitz11.py
-$R^T_V=2.77 \pm 0.08$,
-%----
-where the uncertainty is the $68$\% credible interval and does not include model error.
-
-%\begin{comment}
+%
+%There is a pair of parameter values,  $k_0^0$ and $k_1^0$, that correspond to supernovae experiencing no extrinsic effect.
+%\color{orange}
+%For observer filters $X$ and $Y$, we define $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$, $E(X-Y)=A_X-A_Y$.
+%The true extrinsic
+%extinction is
+%$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$.
 %\color{blue}
-%Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
-%For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
-%$A_V=0$, and such that the ridge line 
-%has close to constant $R^T_V$.
-%\color{black}
-%With this ansatz, we
-%estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
-% \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
-%With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
-%We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
-%of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
-%A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
-%for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
-%\color{black}
-%
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output11/avebv.pdf}
-   %\includegraphics[width=2.8in]{output11/rv.pdf}
-   \caption{
-   $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
-   %Right: Shown for qualitative purposes,
-   %$R^T_V=A^T_V/E^T(B-V)$ 
-   %versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
-   %Overplotted is the mean and standard deviation of those points in equally divided bins.
-   Overplotted are the expected curves for the \citetalias{1999PASP..111...63F} model
-   for specific choices of $R^F$. Note that these lines are not straight, which is apparent when comparing to the straight black $R_V=2.78$ line.
-   \label{avebv:fig}}
-\end{figure}
-%\end{comment}
-
+%The true extrinsic color excess is $E^T(B-V) = A^T_B-A^T_V$, so that the total-to-selective extinction is $R^T_V=A^T_V/E^T(B-V)$.
+%Our $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$ constraints
+%do not determine $k_0^0$ and $k_1^0$, and so the extrinsic extinction and color excess per supernova are not products of our analysis.
+%
+%%our analysis does not specify their values.
+%%Recall that there are degeneracies between the intrinsic (Eqn.~\ref{ewsiv:eqn}) and
+%%extrinsic (Eqn.~\ref{dust:eqn}) parameters of our model.  Part of that degeneracy is
+%%broken by imposing $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$,
+%%but this choice does not specify the parameter values.
+%
+%
+%Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
+%rearranged as
+%\begin{equation}
+%A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
+%\end{equation}
+%Making the assumption that $R^T_V$ is the same for all supernovae,
+%its value can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.
+%
+%Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$.
+%The full set of supernovae does not coincide with the expectations of a single linear relation; rather the supernova population is peaked
+%on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
+%but can have values that extend toward lower values.
+%The assumption of a constant $R^T_V$ is not altogether correct; still we perform a linear fit that gives a slope of
+%%----- fitz11.py
+%$R^T_V=2.77 \pm 0.08$,
+%%----
+%where the uncertainty is the $68$\% credible interval and does not include model error.  
+%
+%%\begin{comment}
+%%\color{blue}
+%%Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
+%%For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
+%%$A_V=0$, and such that the ridge line 
+%%has close to constant $R^T_V$.
+%%\color{black}
+%%With this ansatz, we
+%%estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
+%% \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
+%%With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
+%%We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
+%%of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
+%%A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
+%%for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
+%%\color{black}
+%%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=5.2in]{output11/avebv.pdf}
+%   %\includegraphics[width=2.8in]{output11/rv.pdf}
+%   \caption{
+%   $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
+%   %Right: Shown for qualitative purposes,
+%   %$R^T_V=A^T_V/E^T(B-V)$ 
+%   %versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
+%   %Overplotted is the mean and standard deviation of those points in equally divided bins.
+%   Overplotted are the expected curves for the \citetalias{1999PASP..111...63F} model
+%   for specific choices of $R^F$. Note that these lines are not straight, which is apparent when comparing to the straight black $R_V=2.78$ line.
+%   \label{avebv:fig}}
+%\end{figure}
+%%\end{comment}
+%
+%
 %Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
@@
 
-We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
+We compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
 The 2-parameter linear model
@@
 
-As a check of the above interpretation, we generate a simulated dataset with the same numbers and uncertainties as our data, based on a
+\color{orange}
+As a check of the above interpretation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
 SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
 are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample, and $R^F$ values drawn from a log-normal
-distribution with a mean of $\ln{2.4}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
-measurement uncertainty are the only sources of variation in magnitudes.  
-From the Monte Carlo chains, we find a 68\% credible interval for $\kappa^{-1}_1$ of 2.18--2.40.
-As with the analysis of our data, we find that the
-$\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector almost consistent with
-$\kappa_1^{-1}=2.4$, as expected given the mean of $\ln{2.4}$ of the input log-normal distribution.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
-   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
-   \caption{
-   Two perspectives of $UVI$- spaces
-of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
-   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
-   input $R^F$ drawn from a log-normal distribution  with a mean of $\ln{2.4}$ and 0.05 standard deviation.
-   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
-   lines, the former is 
-   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
-   \label{plane_sim:fig}}
-\end{figure}
+distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
+measurement uncertainty are the only sources of variation in magnitudes.  The input 2.5 is centered
+within the 68\% credible interval for $\kappa^{-1}_1$ of 2.38--2.69 from the results of the stacked 10 simulations.
+\color{blue}
+
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
+%   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
+%   \caption{
+%   Two perspectives of $UVI$- spaces
+%of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
+%   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
+%   input $R^F$ drawn from a log-normal distribution  with a mean of $\ln{2.4}$ and 0.05 standard deviation.
+%   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
+%   lines, the former is 
+%   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
+%   \label{plane_sim:fig}}
+%\end{figure}
+%
 
@@
 
-Another comparison between our model predictions with those of dust is presented in
-Figure~\ref{avebv:fig}, which shows the expectations for measured $A(V)$, $E(B-V)$ for $R^F=1.1, 1.9, 2.5, 3.1$.
-Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
-non-linear.
-Qualitatively, the $R^F \sim 2.4$  most closely matches our linear model fit.
+%
+%Another comparison between our model predictions with those of dust is presented in
+%Figure~\ref{avebv:fig}, which shows the expectations for measured $A(V)$, $E(B-V)$ for $R^F=1.1, 1.9, 2.5, 3.1$.
+%Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
+%non-linear.
+%Qualitatively, the $R^F \sim 2.4$  most closely matches our linear model fit.
 

### 2017-04-10 apj.tex
new cor matrix

@@
 \geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
-\usepackage{graphicx}				% Use pdf, png, jpg, or epsÂ§ with pdflatex; use eps in DVI mode
+\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
 \usepackage{amsmath}
@@
 \author{     G.~Aldering}
-\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, ?out???½
+\affiliation{    Physics Division, Lawrence Berkeley National Laboratory, 
     1 Cyclotron Road, Berkeley, CA, 94720}
@@
 
-To constrain the degrees of freedom and degeneracies inherent in the model we impose that
+To constrain the degrees of freedom and degeneracies inherent in the model we
+\color{orange}
+implement
+\color{black}
 each of the vectors $k_0+1/N$ and $k_1+1/N$,  where $N$ is the number of objects in our sample, are element-wise $\ge 0$ and sum to one, i.e.\
@@
 The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
+\color{orange}
 \begin{multline}
@@
 \begin{array}{rrrrrr}
-1.00 & 0.00 & -0.06 & -0.05 & 0.11 & 0.01 \\
-0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.01 \\
--0.06 & 0.10 & 1.00 & -0.14 & -0.17 & -0.03 \\
--0.05 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 \\
-0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 \\
-0.01 & -0.01 & -0.03 & 0.03 & 0.05 & 1.00
+1.00 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
+0.00^{+0.06}_{-0.06} & 1.00 & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
+-0.07^{+0.07}_{-0.06} & 0.10^{+0.03}_{-0.03} & 1.00 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
+-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1.00 & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
+0.10^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1.00 & 0.06^{+0.08}_{-0.08} \\
+-0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.04^{+0.08}_{-0.07} & 0.03^{+0.08}_{-0.08} & 0.06^{+0.08}_{-0.08} & 1.00 \\
 \end{array}
@@
 \end{multline}
+\color{black}
 
@@
 To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints.  We first
-require that
-$D+1/N$ be a simplex to break the 
+\color{orange}
+implement
+\color{black}
+$D+1/N$ as a simplex to
+\color{orange}
+help
+\color{black}
+break the 
 degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
@@
 
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix.
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix
+\color{orange}
 \begin{multline}
@@
 \begin{array}{rrrrrrr}
-1.00 & 0.00 & -0.07 & -0.04 & 0.11 & 0.01 & -0.06 \\
-0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.02 & -0.02 \\
--0.07 & 0.10 & 1.00 & -0.14 & -0.17 & -0.04 & 0.04 \\
--0.04 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 & -0.07 \\
-0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 & 0.06 \\
-0.01 & -0.02 & -0.04 & 0.03 & 0.05 & 1.00 & 0.01 \\
--0.06 & -0.02 & 0.04 & -0.07 & 0.06 & 0.01 & 1.00
+1.00 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.06}_{-0.07} & -0.04^{+0.06}_{-0.06} & 0.11^{+0.07}_{-0.07} & -0.00^{+0.07}_{-0.07} & -0.06^{+0.07}_{-0.06} \\
+0.00^{+0.06}_{-0.06} & 1.00 & 0.11^{+0.03}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
+-0.07^{+0.06}_{-0.07} & 0.11^{+0.03}_{-0.04} & 1.00 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.07} \\
+-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1.00 & 0.03^{+0.06}_{-0.06} & 0.04^{+0.07}_{-0.08} & -0.08^{+0.10}_{-0.09} \\
+0.11^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.06}_{-0.06} & 1.00 & 0.06^{+0.08}_{-0.07} & 0.06^{+0.08}_{-0.07} \\
+-0.00^{+0.07}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.08} & 0.06^{+0.08}_{-0.07} & 1.00 & 0.01^{+0.08}_{-0.07} \\
+-0.06^{+0.07}_{-0.06} & -0.01^{+0.08}_{-0.08} & 0.04^{+0.07}_{-0.07} & -0.08^{+0.10}_{-0.09} & 0.06^{+0.08}_{-0.07} & 0.01^{+0.08}_{-0.07} & 1.00 \\
 \end{array}
@@
 \end{multline}
+\color{black}
 The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are $0.06$ and $0.01$.

### 2017-04-15 apj.tex
responses to CWR

@@
 \begin{abstract}
-An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
-is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
+\color{orange}
+Empirical modeling has led to precise determinations of the peak absolute magnitudes of Type~Ia supernovae (SNe~Ia), making this class
+of object an excellent distance indicator.  Improved modeling of SN~Ia absolute magnitudes may account for physical effects that
+are expected but not included
+in current models, lead to more precise per-supernova distances, and further constrain systematic uncertainties.  In this article, we present the
+results of    
+\color{black}
+an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
+as applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
 broadband photometry and their colors are found to be 
@@
 %------
-confidence.
-The color changes allowed by the model are almost parallel to the color changes allowed by the dust model of  \citet{1999PASP..111...63F} with floating
-total-to-selective extinction parameter $R^F$.  The prior of no parameter covariance used in the training, and the deduced color excess
-is consistent with $R^F = 2.44$.
+confidence
+\color{orange}
+based on the posterior.
+\color{black}
+The color changes allowed by the model are almost parallel to the color changes allowed by the extinction model of  \citet{1999PASP..111...63F} with floating
+total-to-selective extinction parameter $R^F$.  The deduced color excess
+is consistent with an effective $R^F = 2.44$.
 The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
@@
 of individual supernovae.  Color ratios are sensitive to processes of the responsible physics.   For example,
-relative dust absorption varies as a function of wavelength depending on grain size and shape,
+relative dust absorption varies as a function of wavelength depending on grain size, distribution, composition and shape,
 independent (to first order) of the amount of dust along the line of sight.
@@
 the $R_V=3.1$ measured for the diffuse Milky Way dust is recovered on average and \citet{2017arXiv170101422H}
-find $R_V=2.95 \pm 0.08$ for SN~2012cu.
+find $R_V=2.95 \pm 0.08$ for the highly-extincted SN~2012cu.
 
@@
 the study of intrinsic supernova color based on SN~Ia Hubble diagrams. Latent parameters that are not directly tied to observables,
-such as multiple parameters that simultaneously influence color, can be included in the model.
+such as multiple parameters that simultaneously influence color, can be included in such models.
 \citet{2016arXiv160904470M} take the approach of modeling the distribution of their parameters, to find that
@@
 In this article we use the idea that spectral indicators carry information on intrinsic supernova colors at peak magnitude.
-\color{red}
 This approach is taken by \citet{2011A&A...529L...4C}, who find that after standardization based on Ca and Si features, remaining residual color
@@
 We accommodate  three independent color parameters: the model is constructed such that 
-two are attributed to extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
+two are assigned as extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
 properties.
-\color{black}
 The data used in this analysis are described in \S\ref{data:sec}.
@@
 first analysis with two extrinsic parameters and omitting the intrinsic parameter.  The properties of the two extrinsic parameters
-are consistent with the expectations of parameterized dust designed for the Milky Way, and do an excellent job of fitting the data of the out-of-sample
+are consistent with the expectations of parameterized Milky Way extinction models, and do an excellent job of fitting the data of the out-of-sample
 supernova SN2014J that has an extreme total-to-selective extinction.
 In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
-We summarize our findings, and relate our results with light-curve shape, SiII velocity, and the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
+We summarize our findings, and relate our results to light-curve shape, SiII velocity, and the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
 residuals in \S\ref{discussion:sec}.
@@
 give photometric and spectroscopic statistics described above.
-\textcolor{red}{FOR INTERNAL REFERENCE: The CABALLO2 validation and training sets are used with SN2012cu, SNF20061108-001, SNF20080905-005, SNNGC7589 excised
-based on data problems identified by Manu.}
-The data are given in Table~\ref{data:tab} \textcolor{red}{[TABLE CAN GO IF THERE IS A NICO PAPER]}.
-The peak magnitude uncertainties do have covariance, which is accounted
-for in the analysis; only the standard deviation is included in the table.
-
-\startlongtable
-\begin{deluxetable}{crrrrrrrr}
-\tabletypesize{\tiny}
-\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data
-\label{data:tab}}
-\tablehead{
-\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$}
-}
-\startdata
-SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
-PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
-SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
-PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
-SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ \\
-PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ \\
-PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
-SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ \\
-PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
-PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
-SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ \\
-SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
-SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
-SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
-PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
-PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
-SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
-PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
-SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
-PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
-PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ \\
-SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
-SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ \\
-PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ \\
-PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ \\
-SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
-LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
-SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
-PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
-PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
-SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
-SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
-LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
-PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
-PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
-PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
-SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
-PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
-PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
-PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
-SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
-SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
-SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
-PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
-PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
-CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
-SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ \\
-SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
-SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
-PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
-SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
-SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
-SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
-PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
-PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
-SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
-SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
-SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ \\
-SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
-SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
-SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
-SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
-SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
-SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ \\
-SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
-PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
-PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
-SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
-SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
-SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
-CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
-SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
-SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
-PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
-SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
-SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
-SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
-SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
-SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
-SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
-SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
-CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
-SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
-SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
-SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
-SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
-PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
-SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
-PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
-SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
-SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
-SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
-SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
-SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
-SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
-SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
-SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
-SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
-SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
-SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
-SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
-SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
-PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
-PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
-SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
-SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
-SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
-SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
-SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
-SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
-SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
-SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
-SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
-SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
-SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
-SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
-SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
-PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
-SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
-SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ \\
-SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
-SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
-SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
-SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
-SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ \\
-SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
-SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
-PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
-SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
-PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
-SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
-PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
-PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
-SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
-SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
-SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
-SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
-SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
-SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
-LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
-LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
-SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
-SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
-PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
-SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
-SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
-SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
-SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
-SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
-SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
-SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
-PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
-SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
-SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
-SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
-PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
-SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
-PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
-PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
-SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
-SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
-SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
-SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
-SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\
-\enddata
-\end{deluxetable}
+%\textcolor{red}{FOR INTERNAL REFERENCE: The CABALLO2 validation and training sets are used with SN2012cu, SNF20061108-001, SNF20080905-005, SNNGC7589 excised
+%based on data problems identified by Manu.}
+The data are given in \citet{2017Chotard}.
+%
+%
+%Table~\ref{data:tab} \textcolor{red}{[TABLE CAN GO IF THERE IS A NICO PAPER]}.
+%The peak magnitude uncertainties do have covariance, which is accounted
+%for in the analysis; only the standard deviation is included in the table.
+%
+%\startlongtable
+%\begin{deluxetable}{crrrrrrrr}
+%\tabletypesize{\tiny}
+%\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data
+%\label{data:tab}}
+%\tablehead{
+%\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$}
+%}
+%\startdata
+%SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
+%PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
+%SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
+%PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
+%SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ \\
+%PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ \\
+%PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+%PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+%SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ \\
+%PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
+%PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
+%SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ \\
+%SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
+%SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
+%SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
+%PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
+%PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
+%SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
+%PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
+%SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
+%PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
+%PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ \\
+%SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
+%SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ \\
+%PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ \\
+%PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ \\
+%SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
+%LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
+%SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+%SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
+%PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
+%PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
+%SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
+%SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
+%LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
+%PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
+%PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
+%PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
+%SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
+%PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
+%SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
+%PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
+%PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
+%SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
+%SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
+%SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
+%PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
+%PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
+%CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
+%SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ \\
+%SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
+%SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
+%PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
+%SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
+%SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
+%SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
+%PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
+%PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
+%SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
+%SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
+%SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ \\
+%SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
+%SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
+%SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
+%SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
+%SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
+%SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ \\
+%SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
+%PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
+%PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
+%SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
+%SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
+%SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
+%CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
+%SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
+%SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
+%PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
+%SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
+%SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
+%SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
+%SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
+%SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
+%SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
+%SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
+%CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
+%SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
+%SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+%SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
+%SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
+%SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
+%PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
+%SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
+%PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
+%SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
+%SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
+%SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
+%SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+%CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
+%SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
+%SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
+%SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
+%SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
+%SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
+%SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
+%SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
+%SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
+%SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
+%SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
+%PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
+%PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
+%SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
+%SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
+%SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
+%SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
+%SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
+%SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
+%SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
+%SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
+%SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
+%SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
+%SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
+%SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
+%SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
+%PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
+%SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
+%SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ \\
+%SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
+%SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
+%SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
+%SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
+%SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ \\
+%SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
+%SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
+%PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
+%SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
+%PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
+%SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
+%PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
+%PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
+%SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
+%SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
+%SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
+%SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
+%SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
+%SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
+%LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
+%LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
+%SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
+%SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
+%PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
+%SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
+%SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
+%SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
+%SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
+%SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
+%SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
+%SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
+%SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
+%PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
+%SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
+%SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
+%SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
+%PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
+%SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
+%PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
+%PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
+%SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
+%SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
+%SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
+%SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
+%SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
+%SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\
+%\enddata
+%\end{deluxetable}
 \section{Supernova Model I: Two Extrinsic Parameters}
@@
 SN~Ia broadband magnitudes and colors are correlated with
-spectral features: equivalent widths and line positions are considered as statistics localized in wavelength that are insensitive to variations in
+spectral features: equivalent widths and line positions are considered as statistics localized in wavelength whose measurements are insensitive to variations in
 broadband colors.
@@
 The model 
-\color{red}
 likelihood density
-\color{black}
 is written as
@@
 
-To constrain the degrees of freedom and degeneracies inherent in the model we
 \color{orange}
-implement
-\color{black}
-each of the vectors $k_0+1/N$ and $k_1+1/N$,  where $N$ is the number of objects in our sample, are element-wise $\ge 0$ and sum to one, i.e.\
-these vectors are simplexes.
-These
-conditions break the 
-degeneracies  $\gamma ^0\rightarrow a\gamma^0$, $k_0 \rightarrow a^{-1}k_0$ and $\gamma^1 \rightarrow a\gamma^1$, $k_1 \rightarrow a^{-1}k_1$
-up to a $\pm$ sign.
-Furthermore we impose
+We impose
 \begin{equation}
-\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0, \gamma^0_U > 0, \gamma^1_U < 0.
+\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0.
 \end{equation}
-The first two conditions specify the definition of zero color relative to which the color excess is measured:
-in a linear model this value is arbitrary.
-The latter two exclude degenerate posterior space
+These conditions specify the definition of absolute magnitude and zero color relative to which the color excess is measured:
+in a linear model these values are arbitrary.
+\color{orange}
+As a technical aside whose effect will be noted later, we highlight a choice of model parameterization that enables the efficient evaluation of the
+posterior by the software package
+STAN \citep{stan}.  Given $N$ supernovae, each of the above conditions reduce the number of degrees of freedom by one,
+for example  the $N$ $\Delta$ values are specified by $N-1$ independent parameters. 
+Our implementations
+with $N-1$ independent parameters do not converge efficiently, presumably because the highly correlated parameters result in
+no single ``mass'' in the Hamiltonian Monte Carlo being appropriate over the full parameter space.  
+Based on the recommendation in the STAN User's Guide
+and reinforced by our own experience, each of the above vectors is described by $N$ parameters.  While this introduces an unconstrained
+degree of freedom, it improves the efficiency in evaluating the posterior in the other parameters of interest.
+
+We impose 
+\begin{equation}
+\gamma^0_U > 0, \gamma^1_U < 0.
+\end{equation}
+to exclude degenerate posterior space
 associated
@@
 identical initial conditions, so the difference in the signs of $\gamma^0_U$ and $\gamma^1_U$ distinguishes the two.)
-As  $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
-each other,
-the different initial and boundary conditions for $\gamma^0_U$ and $\gamma^1_U$ break the degeneracy of our mixture model;
-otherwise identical initial conditions for $\gamma^0$, $\gamma^1$ produce indistinguishable posteriors
-with relatively broad credible intervals and lower maximum likelihood.
-
-\color{red}
+
+Under exchange of the 0 and 1 indices, $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
+each other.  That is, the solution for $\gamma^0$ of a subset of the chains is the solution for $\gamma^1$ of the remaining chains, and vice versa.
+We find that a putting initial conditions for $\gamma^0$ that are consistent across all chains is sufficient to break the degeneracy of our mixture model.
+\color{black}
+
 For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
 color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
-$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level parameters.
-\color{black}
+$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level independent parameters.
 
@@
  $0.1$ and scale $0.1$ mag restricted to positive values.
-This covariance matrix prior is recommended by STAN \citep{stan}, the Monte Carlo we use to evaluate the model.
+This covariance matrix prior is recommended by STAN \citep{stan}, the Monte Carlo program we use to evaluate the model.
  We find that imposing a stricter assumption of a
@@
 
-\color{blue}
-There remains degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
+There remain degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
  $\gamma^0 \rightarrow \gamma^0  + \epsilon_{\gamma^0}$, $\gamma^1 \rightarrow \gamma^1 + \epsilon_{\gamma^1}$under the condition
@@
 are non-trivially specified by these priors.
-\color{black}
 
@@
             projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ are to guide the eye.
+            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ are shown for reference --
+            in many cases they are outside the range of the plot.
             \label{global1:fig}}
@@
 
-Differences between the model-predicted versus observed supernova colors are shown in Figure~\ref{residual:fig}.
+Differences between the model-predicted versus
+\color{orange}
+predicted
+\color{black}
+ supernova colors are shown in Figure~\ref{residual:fig}.
 There is no evidence of a catastrophic fit nor of extreme
@@
    \includegraphics[width=5.2in]{output11/residual.pdf} 
-            \caption{Differences between predicted versus observed colors versus the observed color.  For each color, the ideogram of the color differences is
+            \caption{Differences between predicted versus predicted colors versus the \color{orange}
+predicted
+\color{black} color.  For each color, the ideogram of the color differences is
             shown on the right.
@@
 mag, and a broad tail in the positive (fainter) direction. 
+\color{orange}
+We remind the reader that in our construction of the model, the $\Delta$'s have one extra unconstrained degree of freedom.
+The effect of this degree of freedom can be discerned in the overplotted ideogram, which shows the large uncertainties associated 
+with the $\Delta$'s in the tail of the distribution.
+\color{black}
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
    \centering
-   \includegraphics[width=5.2in]{output11/Delta_med_hist.pdf} 
-   \caption{Histogram of the medians of the grey offset $\Delta$. 
+   \includegraphics[width=5.2in]{output11/Delta_hist.pdf} 
+   \caption{Normalized ideogram and histogram of the medians of the grey offset $\Delta$. 
    \label{hist:fig}}
@@
  \end{equation}
-\color{red}
 The average correlation matrix is
@@
  \end{equation}
- \color{black}
 The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
@@
 
-\color{red}
-[Greg asked for discussion but I think the spectral correlations should go in Chotard et al.\ 2017.]
-The  strong correlation between $EW_{Ca}$ and $\lambda_{Si}$ is not surprising.   Si~II velocities have been
-suggested as being able to distinguish two distinct SN~Ia populations
-\citep{2009ApJ...699L.139W, 2013Sci...340..170W}.  CaII~H\&K, and more cleanly CaII~NIR photospheric features
-(and 
-high-velocity features if present), have been found to trend with light-curve shape  \citep{2012MNRAS.426.2359M}.
-\citet{2014MNRAS.437..338C, 2014MNRAS.444.3258M} found a strong correlation between Si~II velocities and the
-CaII~NIR photometric velocity feature, and found that the correlation is sensitive to the presence of high-velocity features.
+We find weak correlations between our color-excess parameters and the input features, the 
+\color{orange}
+only of significance much larger than $1 \sigma$
 \color{black}
-
-We find weak correlations between our color-excess parameters and the input features, the strongest being
+being
 %---
@@
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
-\color{blue}
 The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
@@
  From the Monte Carlo chains, we find a 68\% credible interval for $\kappa^{-1}_1$ of 2.26--2.63.
-\color{blue}
+
+\color{black}
 
@@
 within the 68\% credible interval for $\kappa^{-1}_1$ of 2.38--2.69 from the results of the stacked 10 simulations.
-\color{blue}
-
+
+\color{black}
 %
@@
 negative tail and is peaked at its positive edge, and by construction has a mean of zero.
+\color{orange}
+Note that the extreme outlier has large uncertainties, and is a manifestation of the unconstrained degree of freedom in this parameter set.
+\color{black}
 The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
@@
    \includegraphics[width=2.8in]{output11/gamma1_med.pdf}
-      \caption{ Histogram of
+      \caption{
+      \color{orange} Normalized ideogram and histogram 
+      \color{black}
+      of
 median values of Left: $\gamma^0_V k_0$, which is associated up to an offset with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model; Right: $\gamma^1_V k_1$,
@@
 in standard models of Milky Way dust.  Yet there do remain some small inconsistencies between our numbers and expectations from dust models.
-\color{black}
 
@@
 are plotted in Figure~\ref{sn2014j:fig}.
-\color{red}
 The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
@@
 and those used for the observations,
-\color{black}
 these data are fit to our model
@@
    between the data and model.
-   \color{red}
    This can be compared with the best-fit results of
    \citet{2014ApJ...788L..21A} shown in their Figure~3.
-   \color{black}
    \label{sn2014j:fig}}
@@
 UV through NIR data to fit \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$.
-\color{red}
-\color{black}
 Our model predictions provide a significantly better match to the data
-\color{red}
 despite the only approximate correspondence of the model and observer passbands.
-\color{black}
 
@@
 
-\color{red}
 In Model II, for $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
@@
 $C_c$.  For $N=172$ supernovae, there are 1376 observables and 1242 top-level parameters.
-\color{black}
-
-\color{red}
+
 The $\delta D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
@@
 to identify $\delta D$ as being physically intrinsic or extrinsic.
-\color{black}
-
-To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints.  We first
-\color{orange}
-implement
-\color{black}
-$D+1/N$ as a simplex to
-\color{orange}
-help
-\color{black}
-break the 
-degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
-Furthermore we impose
+
+To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints. We impose
 \begin{equation}
@@
 so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
-\color{blue}
 We apply the condition $\delta_I>0$ to break this degeneracy,
 and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
-\color{black}
 In the running of the Monte Carlo fit, the initial conditions for
@@
 where the residual vectors 
-\color{red}
 \begin{align}
@@
 \label{model11trans:eqn}
-\color{black}
 are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
@@
 Figure~\ref{deltacorner:fig}, which shows the $\delta$ posteriors.
-\color{red}
 Recall that fixing $\delta_X=0$ reverts this model into the two extrinsic-parameter model of \S\ref{model:sec}.
-\color{black}
 Assigning the Monte Carlo links to bins of width 0.5 in each $\delta$ parameter, the maximum number of links in a single bin is 303, the number of bins
@@
 Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values.
-\color{red}
 While the signal of the internal parameter is strong within the context of this model, ``model testing'' (comparing the
@@
 for the next generation of STAN and the development of robust algorithms is a subject of theoretical work.
-\color{black}
 
@@
 \color{black}
-The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are $0.06$ and $0.01$.
+The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are
+\color{orange}
+not of statistical significance.
+\color{black}
 This has two important implications:
@@
    \caption{
-   \color{red}
    Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$,  $E_{\gamma^1}(B-V)$,  and $E_{\delta}(B-V)$, as well as the grey offset
 $\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
-\color{black}
    \label{perobject2:fig}}
@@
 The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
-\color{blue}
 We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
@@
 
-\color{black}
 %\section{Supernova Model III: Fitzpatrick Dust}
@@
 Figure~\ref{x1res:fig},
-\color{blue}
 though there is a hint of nonlinearity in the $B-V$ and $R-V$ colors.
-\color{red}
 We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta x_1$ to the 
@@
 non-zero $\eta$ values at  $\gtrsim 2\sigma$.
-\color{red}
 The Ca and Si responsible for the equivalent widths and wavelength of our selected spectral features
 are expected to be produced together in the thermonuclear burning into intermediate mass elements.
-\color{black}
 We conclude that $v_{Si}$ is correlated with color, 
@@
 
-\color{black}
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
 
-\color{blue}
 We stress that our $\delta$ vector does not capture the full behavior of the observable effects of the $D$ parameter, but rather only
 the contribution perpendicular to the $\gamma$ vectors.
-\color{black}
 
@@
 measurement uncertainties.
-\color{red}
 This analysis was designed to mine information from the SNfactory data set, and so the results presented here
@@
 of an independent set.
-\color{black}
 
@@
 
-\color{blue}
 An interesting direction for future work is to use narrower bands for generating synthetic photometry.  When the bandwidth were small enough
@@
 of dust models into our framework.
-\color{black}
 

### 2017-04-15 view11.py

@@ -140,7 +140,14 @@ plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
 
-plt.hist(numpy.median((fit['gamma'][:,2])[:,None]*fit['k'],axis=0),bins=20)
+
+# bins = numpy.arange(-0.2,0.8001,0.02)
+# plt.hist(fit['Delta'].flatten(),bins,label='ideogram',normed=True,alpha=0.5)
+# plt.hist(numpy.median(fit['Delta'],axis=0),bins,label='median',normed=True,alpha=0.5,width=0.01)
+
+bins=numpy.arange(-0.3,1,0.05)
+plt.hist(numpy.median((fit['gamma'][:,2])[:,None]*fit['k'],axis=0),bins,label='median',normed=True,alpha=0.5,width=0.02)
+plt.hist(((fit['gamma'][:,2])[:,None]*fit['k']).flatten(),bins,label='ideogram',normed=True,alpha=0.5)
 plt.xlabel(r'$\gamma^0_2 k_0$')
 plt.legend()
 plt.tight_layout()
@@ -149,14 +156,17 @@ plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
 
-plt.hist(numpy.median((fit['rho1'][:,2])[:,None]*fit['R'],axis=0),bins=20)
+bins=numpy.arange(-0.35,0.1,0.02)
+plt.hist(numpy.median((fit['rho1'][:,2])[:,None]*fit['R'],axis=0),bins,label='median',normed=True,alpha=0.5,width=0.01)
+plt.hist(((fit['rho1'][:,2])[:,None]*fit['R']).flatten(),bins,label='ideogram',normed=True,alpha=0.5)
 plt.xlabel(r'$\gamma^1_2 k_1$')
-plt.legend()
+plt.legend(loc=2)
 plt.tight_layout()
 pp = PdfPages('output11/gamma1_med.pdf')
 plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
+
 
 (x, xmin, xmax) = numpy.percentile(fit['gamma'][:,2][:,None]*fit['k'],(50,50-34,50+34),axis=0)
 (y, ymin, ymax) = numpy.percentile(fit['rho1'][:,2][:,None]*fit['R'],(50,50-34,50+34),axis=0)
@@ -202,9 +212,9 @@ plt.close()
[…]

### 2017-04-17 apj.tex
more changes from Greg's comments

@@
 
-Differences between the model-predicted versus
 \color{orange}
-predicted
+Observed versus deduced colors for four selected colors, and the histogram of their differences,
 \color{black}
- supernova colors are shown in Figure~\ref{residual:fig}.
+are shown in Figure~\ref{residual:fig}.
 There is no evidence of a catastrophic fit nor of extreme
@@
    \includegraphics[width=5.2in]{output11/residual.pdf} 
-            \caption{Differences between predicted versus predicted colors versus the \color{orange}
-predicted
-\color{black} color.  For each color, the ideogram of the color differences is
-            shown on the right.
+            \caption{
+            \color{orange}
+            Observed versus deduced colors for four selected colors.
+On the right for each color is plotted the histogram of the difference between the observations and deductions.
+\color{black}
             \label{residual:fig}}
@@
 \color{orange}
-For brevity, we do not present here the analysis of simulated data used to validate and bias quantify bias in our results.
+For brevity, we do not present here the analysis of simulated data used to validate and quantify bias in our results.
 The simulation tests in \S\ref{model2:sec} are representative for both Model~1 of this Section and Model~2 of the subsequent section.
@@
 \end{equation}
-approximately describes dust models.
+approximately describes dust models \citep[e.g][]{1989ApJ...345..245C}.
 For the case of
@@
 $a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
-The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
+The $F$ superscript is added to distinguish parameters of the \citetalias{1999PASP..111...63F} model.
 Over the ranges of
@@
 That is to say, with no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
-2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by  \citetalias{1999PASP..111...63F} dust.
+2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.
 
@@
 
-When fixing the origin of the $\gamma$'s to zero, the are found to be coplanar with $a$ and $b$.
+When fixing the origin of the $\gamma$'s to zero, the $\gamma$ vectors are found to be coplanar with $a$ and $b$.
 However the linear model does not specify zero dust so the origin of gamma is unspecified.
@@
 A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
-the vectors $\gamma^0$ and $\gamma^1$.  Suppose that that the data were described by a dust model.  A \citetalias{1999PASP..111...63F}  dust model 
+the vectors $\gamma^0$ and $\gamma^1$.  Suppose that the data were described by a dust model.  Then a \citetalias{1999PASP..111...63F}  dust model 
 can be written as 
@@
 SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
-are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample, and $R^F$ values drawn from a log-normal
+are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample
+(making an approximative correspondence between observed colors measured in our top-hat filters and the 
+model parameter $E^F(B-V)$) , and $R^F$ values drawn from a log-normal
 distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
-measurement uncertainty are the only sources of variation in magnitudes.  The input 2.5 is centered
+measurement uncertainty are the only sources of variation in magnitudes.  The input $R^F=2.5$ is centered
 within the 68\% credible interval for $\kappa^{-1}_1$ of 2.38--2.69 from the results of the stacked 10 simulations.
@@
 of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
-the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$. On the other hand, lower values of $\gamma^1_V k_1$
-occur at larger values of  $\gamma^0_V k_0$.
+the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$
+%\color{orange}
+%While at low  $\gamma^0_V k_0$
+%\color{black}
+%On the other hand, lower values of $\gamma^1_V k_1$
+%occur at larger values of  $\gamma^0_V k_0$.
 These findings are consistent with previous results:
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
-\citet{2011ApJ...729...55F} and the above authors
-find that supernovae with large extinction 
-preferentially exhibit low $R^F$.
+%\citet{2011ApJ...729...55F} and the above authors
+%find that supernovae with large extinction 
+%preferentially exhibit low $R^F$.
 
@@
       of
-median values of Left: $\gamma^0_V k_0$, which is associated up to an offset with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model; Right: $\gamma^1_V k_1$,
+median values of Left: $\gamma^0_V k_0$, which is associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model; Right: $\gamma^1_V k_1$,
 which  is associated with extinction corrections due to deviations away from the canonical $\kappa_1$ value.
@@
 \label{sn2014j:sec}
-SN~2014J   is one of several SNe~Ia that exhibits colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
+SN~2014J   is one of several SNe~Ia that exhibit colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
 2014arXiv1411.3332J,
@@
 Their values 
-$E_o(U-V) =   2.23 \pm   0.03$,
-$E_o(B-V) =   1.28 \pm   0.04$,
-$E_o(R-V) =  -0.47 \pm   0.03$,
-$E_o(i-V) =  -0.92 \pm   0.03$
-are plotted in Figure~\ref{sn2014j:fig}.
+$E(U_o-V_o) =   2.23 \pm   0.03$,
+$E(B_o-V_o) =   1.28 \pm   0.04$,
+$E(R_o-V)_o =  -0.47 \pm   0.03$,
+$E(i_o-V_o) =  -0.92 \pm   0.03$
+are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ emphasizes that this is an observed color excess.
 The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
@@
 \begin{equation}
-E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
+E(X_o-V_o) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
 \end{equation}
@@
    \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.   Bottom: Residual color excess
-   between the data and model.
+   between the data and model, with a line at zero shown for reference.
    This can be compared with the best-fit results of
@@
 %----
-$x_0= 2.60$, $ x_1=-1.89$ with covariance
+$e_0= 2.60$, $ e_1=-1.89$ with covariance
 %----
@@
 \end{equation}
-The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
+The predicted values of observed $E(B_o-V_o)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
 overlap with the data within the error bars.   
@@
 Our model predictions provide a significantly better match to the data
-despite the only approximate correspondence of the model and observer passbands.
+despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
 
@@
 color parameter that could have its origins in supernova astrophysics.
-The extended model is written as
+The extended model referred to as Model~II is written as
 \begin{equation}
@@
 \end{equation}
-The first of these constraints specifies the definition of zero color.   The latter two confine possible magnitude
+The first of these constraints specifies the (arbitrary) definition of zero color.   The latter two confine possible magnitude
 variations to be those that cannot be attributed to 
@@
    internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
-   Right: Ideogram of $E_\delta(B-V)$ on an enlarged scale.
+   Right: Ideogram and histogram of the medians of $E_\delta(B-V)$ on an enlarged scale.
    \label{ebv:fig}}
@@
 and that of \S\ref{model:sec}), is challenging for Bayesian Monte Carlo analysis.  Evidence calculations are planned
-for the next generation of STAN and the development of robust algorithms is a subject of theoretical work.
+for the next generation of STAN and the development of robust evidence algorithms is a subject of theoretical work.
 
@@
    \caption{Significance of the non-zero values of $\delta$ as demonstrated by the best-fit values of $\delta_X/\delta_I-1$ for $\delta$ for Model~II.
+   A line at zero is shown for reference.
    \label{deltaratio:fig}}
@@
 the uncertainties in the predictor variable, which in turn lead to 
-regression dilution.  Our analysis is susceptible to this bias because we do consciously do not include distributions
+regression dilution.  Our analysis is susceptible to this bias because we consciously do not include distributions
 of supernova parameters as part of our model.
@@
 %\color{black}
-\section{Discussion and Summary}
+\section{Discussion}
 \label{discussion:sec}

### 2017-04-17 view11.py

@@ -171,13 +171,20 @@ plt.close()
 (x, xmin, xmax) = numpy.percentile(fit['gamma'][:,2][:,None]*fit['k'],(50,50-34,50+34),axis=0)
 (y, ymin, ymax) = numpy.percentile(fit['rho1'][:,2][:,None]*fit['R'],(50,50-34,50+34),axis=0)
 plt.errorbar(x, y, xerr=[x-xmin,xmax-x],yerr=[y-ymin,ymax-ymin],fmt='o')
-plt.xlabel(r'$\gamma^0_2 k_0$')
-plt.ylabel(r'$\gamma^1_2 k_1$')
+plt.xlabel(r'$\gamma^0_V k_0$')
+plt.ylabel(r'$\gamma^1_V k_1$')
 pp = PdfPages("output11/kk.pdf")
 plt.tight_layout()
 plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
+
+crap=fit['rho1'][:,2][:,None]*fit['R']
+med = numpy.percentile(x,(25,75))
+plt.hist([crap[:,x<=med[0]].flatten(),crap[:,x>med[1]].flatten()],label=[r'Low $\gamma^0_V k_0$', r'High $\gamma^0_V k_0$'])
+plt.legend(loc=2)
+# plt.show()
+plt.clf()
 
 # kappa1=1/2.4
 # kappa2 = -6.8
@@ -335,14 +342,15 @@ cind=[0,1,3,4]
 cname = ['U','B','R','I']
 mpl.rcParams['font.size'] = 14
 
-fig, axes = plt.subplots(nrows=4,ncols=2,gridspec_kw={'width_ratios':[1,.2]})
+fig, axes = plt.subplots(nrows=4,ncols=2,gridspec_kw={'width_ratios':[.8,.2]})
 for i in xrange(4):
     (y, ymin, ymax) = numpy.percentile(correction[cind[i],:,:],(50,50-34,50+34),axis=0)
     err = numpy.sqrt(color_cov[:,i,i] + ((ymax-ymin)/2)**2)
-    axes[i,0].errorbar(y,y-color_obs[:,i],xerr=[((ymax-ymin)/2),((ymax-ymin)/2)], yerr=[err,err],fmt='.',alpha=0.4)
+    #axes[i,0].errorbar(y,y-color_obs[:,i],xerr=[((ymax-ymin)/2),((ymax-ymin)/2)], yerr=[err,err],fmt='.',alpha=0.4)
[…]

### 2017-04-17 view23.py

@@ -233,25 +233,38 @@ correction = [fit['c'][:,i][:,None] + fit['alpha'][:,i][:,None]*fit['EW'][:,:, 0
     + fit['beta'][:,i][:,None]*fit['EW'][:,:, 1] + fit['eta'][:,i][:,None]*fit['sivel']\
     + fit['gamma'][:,i][:,None]*fit['k'] + fit['gamma1'][:,i][:,None]*fit['k1'] + fit['rho1'][:,i][:,None]*fit['R']\
     for i in xrange(5)]
-
 correction = numpy.array(correction)
 correction = correction - correction[2,:,:]
 # correction_median = numpy.median(correction,axis=1)
-
+from matplotlib.ticker import NullFormatter
 cind=[0,1,3,4]
 cname = ['U','B','R','I']
-fig, axes = plt.subplots(nrows=4)
+mpl.rcParams['font.size'] = 14
+
+fig, axes = plt.subplots(nrows=4,ncols=2,gridspec_kw={'width_ratios':[1,.2]})
 for i in xrange(4):
     (y, ymin, ymax) = numpy.percentile(correction[cind[i],:,:],(50,50-34,50+34),axis=0)
     err = numpy.sqrt(color_cov[:,i,i] + ((ymax-ymin)/2)**2)
-    axes[i].errorbar(y+mag_mn[cind[i]]-mag_mn[2],color_obs[:,i]-y,xerr=[y-ymin,ymax-y], yerr=[err,err],fmt='.',alpha=0.4)
-    axes[i].set_xlabel(r'$({0}-V)_{{model}}$'.format(cname[i]))
-    lname = r'$({0}_o-V_o) - ({0}-V)_{{model}}$'.format(cname[i])
-    axes[i].set_ylabel(lname)
-    axes[i].axhline(y=0,linestyle=':')
-# fig.subplots_adjust(hspace=.3)
+    axes[i,0].errorbar(color_obs[:,i],color_obs[:,i]-y,xerr=[numpy.sqrt(color_cov[:,i,i]),numpy.sqrt(color_cov[:,i,i])], yerr=[err,err],fmt='.',alpha=0.4)
+
+    # axes[i,0].errorbar(y+mag_mn[cind[i]]-mag_mn[2],color_obs[:,i]-y,xerr=[y-ymin,ymax-y], yerr=[err,err],fmt='.',alpha=0.4)
[…]

### 2017-04-17 view23_scoeff.py

@@ -12,6 +12,7 @@ import scipy
 import cPickle
 import matplotlib as mpl
 import sivel
+mpl.rcParams['font.size'] = 18
 
 f = open('temp23_sim0.pkl','rb')
 (fit,_) = pickle.load(f)
@@ -109,7 +110,7 @@ for index in xrange(5):
     figure = corner.corner(mega[index,:,:],labels=[r"$c_{}$".format(index), r"$\alpha_{}$".format(index),\
                     r"$\beta_{}$".format(index),r"$\eta_{}$".format(index),r"$\gamma^0_{}$".format(index),\
                     r"$\gamma^1_{}$".format(index),r"$\delta_{{{}}}$".format(index), r"$\sigma_{}$".format(index)],\
-                    truths=[c[index], alpha[index],beta[index],eta[index],gamma[index], gamma1[index],delta[index],numpy.sqrt(cov[index,index])])
+                    truths=[c[index], alpha[index],beta[index],eta[index],gamma[index], gamma1[index],delta[index],numpy.sqrt(cov[index,index])],label_kwargs={'fontsize':20})
     figure.suptitle(filts[index],fontsize=28)
     pp = PdfPages('output23_sim/coeff{}.pdf'.format(index))
     plt.savefig(pp,format='pdf')

### 2017-04-17 view23_sim.py

@@ -12,7 +12,7 @@ import scipy
 import cPickle
 import matplotlib as mpl
 import sivel
-
+mpl.rcParams['font.size'] = 18
 f = open('temp23_sim0.pkl','rb')
 (fit,_) = pickle.load(f)
 
@@ -99,363 +99,81 @@ mag_cov = data['cov'][:,2:,2:]
 
 pkl_file.close()
 
-plt.plot(fit['rho1'][::10,:])
-plt.title(r'$\delta')
-pp = PdfPages("output23_sim/delta_chain.pdf")
-plt.savefig(pp,format='pdf')
-pp.close()
-plt.close()
-
-trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1]]
-trans = numpy.array(trans)
-color_cov = numpy.zeros((nsne,4,4))
-for i in xrange(nsne):
-    color_cov[i] = numpy.dot(trans,numpy.dot(mag_cov[i], trans.T))
-
-
-
-(x, xmin, xmax) = numpy.percentile( ((fit['gamma'][:,1] - fit['gamma'][:,2])[:,None]*fit['k']),(50,50-34,50+34),axis=0)
-(y, ymin, ymax) = numpy.percentile(((fit['rho1'][:,1] - fit['rho1'][:,2])[:,None]*fit['R']),(50,50-34,50+34),axis=0)
-
-plt.errorbar(x,y,xerr=(x-xmin,xmax-x), yerr=(y-ymin,ymax-y),fmt='o')
-plt.xlim((-0.08,0.05))
-# plt.ylim((-0.02,0.05))
-plt.xlabel(r'$E_\gamma(B-V)$')
-plt.ylabel(r'$E_\delta(B-V)$')
-pp = PdfPages("output23_sim/egammaedelta_corner.pdf")
-plt.savefig(pp,format='pdf')
-pp.close()
-plt.close()
-
-
-(y, ymin, ymax) = numpy.percentile(fit['EW'][:,:,1],(50,50-34,50+34),axis=0)
-plt.errorbar(x1, y, xerr=[x1_err,x1_err],yerr=[y-ymin,ymax-ymin],fmt='o')
-plt.xlabel(r'$x_1$')
-plt.ylabel(r'$EW_{Si}$')
-pp = PdfPages("output23_sim/x1si.pdf")
-plt.savefig(pp,format='pdf')
-pp.close()
-plt.close()
-
[…]

### 2017-04-17 apj.tex
brian comment

@@
 
-We find weak correlations between our color-excess parameters and the input features, the 
+We find weak correlations between our color-excess parameters and the input features; 
 \color{orange}
-only of significance much larger than $1 \sigma$
+only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}(B-V)$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
 \color{black}
-being
-%---
-$-0.17$
-%---
- between
-$E_{\gamma^0}(B-V)$ and $EW_{Si}$.
 Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
@@
    \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.   Bottom: Residual color excess
-   between the data and model, with a line at zero shown for reference.
+   between the data and model, with a dotted line at zero shown for reference.
    This can be compared with the best-fit results of
@@
    \caption{Significance of the non-zero values of $\delta$ as demonstrated by the best-fit values of $\delta_X/\delta_I-1$ for $\delta$ for Model~II.
-   A line at zero is shown for reference.
+   A dotted line at zero is shown for reference.
    \label{deltaratio:fig}}
@@
 are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
-relative to the statistical uncertainties.  There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
-the uncertainties in the predictor variable, which in turn lead to 
-regression dilution.  Our analysis is susceptible to this bias because we consciously do not include distributions
-of supernova parameters as part of our model.
+relative to the statistical uncertainties.   Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
+with the extracted distributions.
+%There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
+%the uncertainties in the predictor variable, which in turn lead to 
+%regression dilution.  Our analysis is susceptible to this bias because we consciously do not include distributions
+%of supernova parameters as part of our model.
 
@@
     \caption{Differences between observed colors and the colors predicted from the analysis, as a function
-            of the SALT2 light-curve shape parameter $x_1$.  For reference a dotted line is plotted at zero difference.
+            of the SALT2 light-curve shape parameter $x_1$.  Our model does not explicitly use $x_1$.  For reference a dotted line is plotted at zero difference.
    \label{x1res:fig}}
@@
 To first order, the $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.
-The values of $\eta$ in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
+The values of the $v_{Si}$ coefficient, $\eta$, in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
 and in turn $\lambda_{Si}$ is correlated with $EW_{Ca}$.
@@
 
-Although the $D$ parameter has ben referred to as ``intrinsic'', due to its placement in the model and the correspondence
+Although the $D$ parameter has been referred to as ``intrinsic'', due to its placement in the model and the correspondence
 of the $k$ parameters with those of extrinsic two-parameter dust models, the analysis cannot quantitatively distinguish
@@
 
-\subsection{Summary}
+\subsection{Conclusion}
 To summarize, we model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
@@
 derived entirely independently of assumptions about the shape of the extinction curve and/or assumptions about the
-distribution of $A_V$.  An extended version
-of the model retains the features of the first model, and gives the first identification of  a new parameter that affects supernova
+distribution of $A_V$.  
+\color{orange}
+Nesting this model in an extended model produces a result that 
+\color{black}
+disfavors the original model and gives the first identification of  a new parameter that affects supernova
 colors in a manner that is distinct from the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
 
-An interesting direction for future work is to use narrower bands for generating synthetic photometry.  When the bandwidth were small enough
+An interesting direction for future work is to use narrower bands for generating synthetic photometry
+from the SNfactory spectrophotometry.  When the bandwidth becomes small enough
 to resolve spectral features, the analysis would produce a spectroscopic model.   Higher resolution would allow us to forego 

### 2017-04-19 apj.tex
error bars on intrinsic covariance matrix

@@
 $\sim 0.01$ to 0.06 mag, significantly smaller
-than the dispersion in $\Delta$.  Given that the 
-off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix rather than the matrix elements themselves,
-it is not straightforward to present correlation matrix confidences:
-the average over Monte Carlo links of the
-Cholesky factors will not  generally yield a correlation matrix.  
-To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
-chain, element by element.
-For $UBVRI$ the matrix is
+than the dispersion in $\Delta$.
+\color{orange}
+Of particular interest in $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in $V$ and colors with respect to $V$ are
 \begin{equation}
-C_c(U,B,V,R,I)=
+\sigma(V,U-V,B-V,V-R,V-I)=
+%\begin{pmatrix}
+%\begin{array}{rrrrr}
+\left(
+0.021^{+0.004}_{-0.005} ,
+0.067^{+0.010}_{-0.010},
+0.034^{+0.005}_{-0.005},
+0.023^{+0.002}_{-0.002},
+0.053^{+0.004}_{-0.004}
+\right)
+%\end{array}
+% \end{pmatrix} 
+ \text{mag}.
+ \label{sig_intrinsic:eqn}
+ \end{equation}
+The correlations between these parameters are
+\begin{equation}
+Cor(V,U-V,B-V,V-R,V-I)=
 \begin{pmatrix}
 \begin{array}{rrrrr}
-0.0038 & 0.0010 & -0.0002 & -0.0000 & 0.0003 \\
-0.0010 & 0.0011 & 0.0002 & -0.0000 & -0.0006 \\
--0.0002 & 0.0002 & 0.0004 & 0.0000 & -0.0002 \\
--0.0000 & -0.0000 & 0.0000 & 0.0002 & 0.0002 \\
-0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
-\end{array}
- \end{pmatrix} \text{mag}^2.
- \label{mag_cov:eqn}
- \end{equation}
-The average correlation matrix is
-\begin{equation}
-Cor(U,B,V,R,I)=
-\begin{pmatrix}
-\begin{array}{rrrrr}
-1.00 & 0.42 & -0.18 & -0.05 & 0.12 \\
-0.42 & 1.00 & 0.26 & -0.09 & -0.39 \\
--0.18 & 0.26 & 1.00 & 0.09 & -0.22 \\
--0.05 & -0.09 & 0.09 & 1.00 & 0.27 \\
-0.12 & -0.39 & -0.22 & 0.27 & 1.00
+1 & -0.48^{+0.20}_{-0.18} & -0.34^{+0.21}_{-0.22} & 0.88^{+0.10}_{-0.25} & 0.60^{+0.11}_{-0.19} \\
+-0.48^{+0.20}_{-0.18} & 1 & 0.60^{+0.10}_{-0.13} & -0.38^{+0.18}_{-0.17} & -0.33^{+0.15}_{-0.14} \\
+-0.34^{+0.21}_{-0.22} & 0.60^{+0.10}_{-0.13} & 1 & -0.21^{+0.17}_{-0.17} & 0.08^{+0.14}_{-0.15} \\
+0.88^{+0.10}_{-0.25} & -0.38^{+0.18}_{-0.17} & -0.21^{+0.17}_{-0.17} & 1 & 0.65^{+0.06}_{-0.07} \\
+0.60^{+0.11}_{-0.19} & -0.33^{+0.15}_{-0.14} & 0.08^{+0.14}_{-0.15} & 0.65^{+0.06}_{-0.07} & 1 \\
 \end{array}
  \end{pmatrix}.
+ \label{cor_intrinsic:eqn}
  \end{equation}
-The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
-expressed as the standard deviations and
-correlation matrix
- \begin{equation}
- \sigma(U-V, B-V, V-R, V-I)=
- \begin{pmatrix}
-0.068 & 0.034 & 0.023 & 0.053
-  \end{pmatrix} \text{mag},
- \label{color_sd:eqn}
- \end{equation}
- \begin{equation}
- Cor(U-V, B-V, V-R, V-I)=
-\begin{pmatrix}
-\begin{array}{rrrr}
-1.000 & 0.602 & -0.353 & -0.317 \\
-0.602 & 1.000 & -0.197 & 0.082 \\
--0.353 & -0.197 & 1.000 & 0.647 \\
--0.317 & 0.082 & 0.647 & 1.000
-\end{array}
-\end{pmatrix}.
-  \label{color_cor:eqn}
- \end{equation}
+
+\color{black}
+%
+%Given that the 
+%off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix rather than the matrix elements themselves,
+%it is not straightforward to present correlation matrix confidences:
+%the average over Monte Carlo links of the
+%Cholesky factors will not  generally yield a correlation matrix.  
+%To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
+%chain, element by element.
+%For $UBVRI$ the matrix is
+%\begin{equation}
+%C_c(U,B,V,R,I)=
+%\begin{pmatrix}
+%\begin{array}{rrrrr}
+%0.0038 & 0.0010 & -0.0002 & -0.0000 & 0.0003 \\
+%0.0010 & 0.0011 & 0.0002 & -0.0000 & -0.0006 \\
+%-0.0002 & 0.0002 & 0.0004 & 0.0000 & -0.0002 \\
+%-0.0000 & -0.0000 & 0.0000 & 0.0002 & 0.0002 \\
+%0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
+%\end{array}
+% \end{pmatrix} \text{mag}^2.
+% \label{mag_cov:eqn}
+% \end{equation}
+%The average correlation matrix is
+%\begin{equation}
+%Cor(U,B,V,R,I)=
+%\begin{pmatrix}
+%\begin{array}{rrrrr}
+%1.00 & 0.42 & -0.18 & -0.05 & 0.12 \\
+%0.42 & 1.00 & 0.26 & -0.09 & -0.39 \\
+%-0.18 & 0.26 & 1.00 & 0.09 & -0.22 \\
+%-0.05 & -0.09 & 0.09 & 1.00 & 0.27 \\
+%0.12 & -0.39 & -0.22 & 0.27 & 1.00
+%\end{array}
+% \end{pmatrix}.
+% \end{equation}
+%The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
+%expressed as the standard deviations and
+%correlation matrix
+% \begin{equation}
+% \sigma(U-V, B-V, V-R, V-I)=
+% \begin{pmatrix}
+%0.068 & 0.034 & 0.023 & 0.053
+%  \end{pmatrix} \text{mag},
+% \label{color_sd:eqn}
+% \end{equation}
+% \begin{equation}
+% Cor(U-V, B-V, V-R, V-I)=
+%\begin{pmatrix}
+%\begin{array}{rrrr}
+%1.000 & 0.602 & -0.353 & -0.317 \\
+%0.602 & 1.000 & -0.197 & 0.082 \\
+%-0.353 & -0.197 & 1.000 & 0.647 \\
+%-0.317 & 0.082 & 0.647 & 1.000
+%\end{array}
+%\end{pmatrix}.
+%  \label{color_cor:eqn}
+% \end{equation}
 These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where direct comparison can be made.
+\color{orange}
+%model11_rubin.py
+Having no intrinsic color dispersion is disfavored, and not allowing for them can have important consequences.
+Running an analysis assuming no intrinsic dispersion (replacing the probabilistic intrinsic magnitudes in Eqn.~\ref{ewsiv:eqn}
+with a strict equality), we find significant shifts in the inferred slopes and smaller statistical uncertainties.
+\color{black}
 
@@
 \right)
-\label{ewsiv:eqn}
+\label{ewsiv2:eqn}
 \end{equation}
@@
 \right).
-\label{dust:eqn}
+\label{dust2:eqn}
 \end{equation}
@@
 
-The $\delta D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
+The $\delta D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms:
 it is for this reason that for convenience these terms are referred to as ``intrinsic''.
 However, we emphasize now that we have also run the alternative case  of switching the placement of the
-$\delta D$ terms from Eq.~\ref{ewsiv:eqn} to Eq.~\ref{dust:eqn}, i.e.\ from intrinsic to extrinsic contributions.
+$\delta D$ terms from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from intrinsic to extrinsic contributions.
 Analyses of the two different models give practically identical results, meaning that data are not constraining enough

### 2017-04-19 apj.tex
fitzpatrick parameters for sn2011fe

@@
 \color{orange}
-We remind the reader that in our construction of the model, the $\Delta$'s have one extra unconstrained degree of freedom.
-The effect of this degree of freedom can be discerned in the overplotted ideogram, which shows the large uncertainties associated 
-with the $\Delta$'s in the tail of the distribution.
+Of the three extreme outliers, the supernovae with largest and third largest $\Delta$'s have  heliocentric redshifts of 
+ $0.0015$ and $0.0085$ respectively, and so have peculiar velocities that can contribute significantly to $\Delta$.
 \color{black}
@@
 \begin{array}{rrrrrr}
-1.00 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
-0.00^{+0.06}_{-0.06} & 1.00 & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
--0.07^{+0.07}_{-0.06} & 0.10^{+0.03}_{-0.03} & 1.00 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
--0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1.00 & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
-0.10^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1.00 & 0.06^{+0.08}_{-0.08} \\
--0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.04^{+0.08}_{-0.07} & 0.03^{+0.08}_{-0.08} & 0.06^{+0.08}_{-0.08} & 1.00 \\
+1 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
+0.00^{+0.06}_{-0.06} & 1 & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
+-0.07^{+0.07}_{-0.06} & 0.10^{+0.03}_{-0.03} & 1 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
+-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1 & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
+0.10^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1 & 0.06^{+0.08}_{-0.08} \\
+-0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.04^{+0.08}_{-0.07} & 0.03^{+0.08}_{-0.08} & 0.06^{+0.08}_{-0.08} & 1 \\
 \end{array}
@@
 despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
+
+\color{orange}
+Our model and its fit parameters can be associated with the extinction model of  \citetalias{1999PASP..111...63F} using Eqn.\ref{trans_I:eqn}
+and the assumption that  SN~2011fe has zero extinction.  The inferred  \citetalias{1999PASP..111...63F} parameters
+are $A^F_V=1.28$ and $E^F(B-V)=0.77$ (which together imply $R^F=1.66$) with covariance
+\begin{equation}
+\begin{pmatrix}
+\begin{array}{rr}
+0.007 & -0.004 \\
+-0.004 & 0.430
+\end{array}
+\end{pmatrix}.
+\end{equation}
+\color{black}
 

### 2017-04-19 sn2014j11.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 from matplotlib.backends.backend_pdf import PdfPages
 from matplotlib import rc
 import pickle
-
+import f99_band
 import matplotlib as mpl
 mpl.rcParams['font.size'] = 16
 
@@ -66,22 +66,34 @@ print '${0[0]:6.2f}$, ${0[1]:6.2f}$'.format(ans)
 print " \\\\\n".join([" & ".join(map('{0:.3f}'.format, line)) for line in u])
 
 
+# in fundamental units
+tvec = [numpy.median(fit['gamma'][:,1]/fit['gamma'][:,2]-1,axis=0),numpy.median(fit['rho1'][:,1]/fit['rho1'][:,2]-1,axis=0)]
+Egamma = ans* tvec
+ugamma=u*numpy.outer(tvec,tvec)
+# print numpy.outer(tvec,tvec)
+# print Egamma
+# print ugamma
+
+
 fiterr = numpy.sqrt(gammam1**2 * u[0,0] + 2*deltam1*gammam1*u[0,1] + deltam1**2 * u[1,1])
 ebvext= gammam1[1]*ans[0]
 ebvint = deltam1[1]*ans[1]
-print "$E(B-V)={:6.2f} \\pm {:6.2f}$, $E_\delta(B-V)={:6.2f} \\pm {:6.2f}$".format(ebvext,numpy.sqrt(u[0,0])*gammam1[1], ebvint,numpy.sqrt(u[1,1])*numpy.abs(deltam1[1]))
+# print "$E(B-V)={:6.2f} \\pm {:6.2f}$, $E_\delta(B-V)={:6.2f} \\pm {:6.2f}$".format(ebvext,numpy.sqrt(u[0,0])*gammam1[1], ebvint,numpy.sqrt(u[1,1])*numpy.abs(deltam1[1]))
 
 
 dum = numpy.percentile((fit['gamma'][:,1]-fit['gamma'][:,2])[:,None]*fit['k'],(50,50-34,50+34),axis=0)
 imax = numpy.argmin(dum,axis=1)[0]
-print '${:6.2f}^{{{:6.2f}}}_{{{:6.2f}}}$'.format(dum[0][imax],dum[2][imax]-dum[0][imax],dum[1][imax]-dum[0][imax])
[…]

### 2017-04-19 apj.tex
more modifications for Greg's comments

@@
 \color{orange}
-As a technical aside whose effect will be noted later, we highlight a choice of model parameterization that enables the efficient evaluation of the
-posterior by the software package
-STAN \citep{stan}.  Given $N$ supernovae, each of the above conditions reduce the number of degrees of freedom by one,
-for example  the $N$ $\Delta$ values are specified by $N-1$ independent parameters. 
-Our implementations
-with $N-1$ independent parameters do not converge efficiently, presumably because the highly correlated parameters result in
-no single ``mass'' in the Hamiltonian Monte Carlo being appropriate over the full parameter space.  
-Based on the recommendation in the STAN User's Guide
-and reinforced by our own experience, each of the above vectors is described by $N$ parameters.  While this introduces an unconstrained
-degree of freedom, it improves the efficiency in evaluating the posterior in the other parameters of interest.
-
 We impose 
@@
 negative tail and is peaked at its positive edge, and by construction has a mean of zero.
-\color{orange}
-Note that the extreme outlier has large uncertainties, and is a manifestation of the unconstrained degree of freedom in this parameter set.
-\color{black}
 The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
@@
 we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
-\citep{2016rigault}, and their ideograms for two samples divided at host mass of  $\log{(M/M_\sun)}=10$
-as in  \citet{2013ApJ...770..108C}.
+\color{orange}
+for the subset of supernovae whose hosts are given in \citet{2013ApJ...770..108C}.
+Also plotted  are ideograms of $A_{\delta I}$ for the two subsamples obtained by dividing the full sample at a host mass of  $\log{(M/M_\sun)}=10$.
 Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta I}$, the difference is
@@
 %---
-$\langle A_{\delta I} \rangle=    -0.0026 \pm    0.0010$,
-$\langle A_{\delta I} \rangle=  -0.0037 \pm    0.0010 $ 
+$\langle A_{\delta I} \rangle=   -0.0026 \pm    0.0014$,
+$\langle A_{\delta I} \rangle=-0.0035 \pm    0.0010$ 
 for low- and high-mass hosts respectively. 
@@
    \centering
-   \includegraphics[width=2.8in]{output23/rigault3.pdf}
-s     \includegraphics[width=2.8in]{output23/rigault2.pdf}
+   \includegraphics[width=2.8in]{output23/childress.pdf}
+s     \includegraphics[width=2.8in]{output23/childress2.pdf}
       \caption{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
       less than and greater than  $\log{(M/M_\sun)}=10$.
-Right: Ideograms of  $A_{\delta I}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
+Right: Normalized ideograms of  $A_{\delta I}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
    \label{childress:fig}}
@@
 
+\color{black}
 \subsection{Physical Motivation}

### 2017-04-19 view23_dilute.py

@@ -20,7 +20,7 @@ f = open('temp23_dilute0.pkl','rb')
 mega = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['gamma1'],fit['rho1'],fit['L_sigma']])
 
 print mega.shape
-for index in xrange(1,4):
+for index in xrange(1,10):
     f = open('temp23_dilute{}.pkl'.format(index),'rb')
     (fit,_) = pickle.load(f)
     mega_ = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['gamma1'],fit['rho1'],fit['L_sigma']])

### 2017-04-20 apj.tex
finish new draft

@@
 \color{orange}
-Empirical modeling has led to precise determinations of the peak absolute magnitudes of Type~Ia supernovae (SNe~Ia), making this class
-of object an excellent distance indicator.  Improved modeling of SN~Ia absolute magnitudes may account for physical effects that
-are expected but not included
-in current models, lead to more precise per-supernova distances, and further constrain systematic uncertainties.  In this article, we present the
+Through empirical modeling, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined 
+based on its observed signal, making SNe~Ia  excellent distance indicators.  Improved modeling of SN~Ia absolute magnitudes can account for
+further physical
+diversity that is expected but not included
+in current models, and so consequently can lead to more precise per-object distances with tighter systematic uncertainties.  In this article, we present the
 results of    
@@
 These conditions specify the definition of absolute magnitude and zero color relative to which the color excess is measured:
-in a linear model these values are arbitrary.
+in our linear model these values are unconstrained.
 \color{orange}
@@
 
-Under exchange of the 0 and 1 indices, $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
-each other.  That is, the solution for $\gamma^0$ of a subset of the chains is the solution for $\gamma^1$ of the remaining chains, and vice versa.
-We find that a putting initial conditions for $\gamma^0$ that are consistent across all chains is sufficient to break the degeneracy of our mixture model.
+The combinations $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
+each other under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
+we break that degeneracy  by setting consistent initial conditions that succeed in keeping indices consistent over all analysis chains.  
 \color{black}
@@
 \color{orange}
-Observed versus deduced colors for four selected colors, and the histogram of their differences,
+For four selected colors, a plot of the
+observed versus deduced colors and the histogram of their differences
 \color{black}
@@
             \color{orange}
-            Observed versus deduced colors for four selected colors.
-On the right for each color is plotted the histogram of the difference between the observations and deductions.
+            Observed versus deduced colors for four selected colors.  Plotted on the right for each color
+is the histogram of the difference between the observed and deduced colors.
 \color{black}
@@
 Of the three extreme outliers, the supernovae with largest and third largest $\Delta$'s have  heliocentric redshifts of 
- $0.0015$ and $0.0085$ respectively, and so have peculiar velocities that can contribute significantly to $\Delta$.
+ $0.0015$ and $0.0085$ respectively, and so have peculiar velocities that can cause a significant magnitude offset.
 \color{black}
@@
 \color{orange}
-Of particular interest in $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in $V$ and colors with respect to $V$ are
+Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in $V$ and colors with respect to $V$ are
 \begin{equation}
@@
  \end{equation}
-
 \color{black}
@@
 \begin{array}{rr}
-1.15 & 2.82 \\
-0.72 & -5.27
+2.82 & 1.15  \\
+-5.27 & 0.72
 \end{array}
@@
 \color{orange}
-The preferred values for $\kappa^{-1}$ can be determined from the matrix elements of Eqn.~\ref{model11trans:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa^{-1}_2=-5.27/0.72=-7.31$.
+The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{model11trans:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa_2=-5.27/0.72=-7.31$.
 The directions of the $\gamma$ vectors, and  the expectations from  \citetalias{1999PASP..111...63F} with $R=\kappa^{-1}$, are shown in 
@@
 \color{orange}
-As a check of the above interpretation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
+As a check of our analysis implementation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
 SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
 are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample
-(making an approximative correspondence between observed colors measured in our top-hat filters and the 
+(making an approximative correspondence between our observed top-hat filter colors and the 
 model parameter $E^F(B-V)$) , and $R^F$ values drawn from a log-normal
 distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
-measurement uncertainty are the only sources of variation in magnitudes.  The input $R^F=2.5$ is centered
-within the 68\% credible interval for $\kappa^{-1}_1$ of 2.38--2.69 from the results of the stacked 10 simulations.
+measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations: the input $R^F=2.5$ is centered
+within the 68\% credible interval for $\kappa^{-1}_1$ of 2.38--2.69.
 
@@
    \includegraphics[width=5.2in]{output11/sn2014j.pdf} 
-   \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.   Bottom: Residual color excess
-   between the data and model, with a dotted line at zero shown for reference.
-   This can be compared with the best-fit results of
-   \citet{2014ApJ...788L..21A} shown in their Figure~3.
+   \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.
+   \color{orange}
+   In addition to the prediction
+   of our model, also shown is the prediction from the projection
+   of our results onto the \citetalias{1999PASP..111...63F} extinction model.  Bottom: Residual color excess
+   between the data and models, with a dotted line at zero shown for reference.
+   \color{black}
    \label{sn2014j:fig}}
@@
 overlap with the data within the error bars.
-Our results can be compared with those of  \citet{2014ApJ...788L..21A} (Figure 3), who 
-use
-UV through NIR data to fit \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$.
-Our model predictions provide a significantly better match to the data
-despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
-
-\color{orange}
-Our model and its fit parameters can be associated with the extinction model of  \citetalias{1999PASP..111...63F} using Eqn.\ref{trans_I:eqn}
-and the assumption that  SN~2011fe has zero extinction.  The inferred  \citetalias{1999PASP..111...63F} parameters
-are $A^F_V=1.28$ and $E^F(B-V)=0.77$ (which together imply $R^F=1.66$) with covariance
-\begin{equation}
-\begin{pmatrix}
-\begin{array}{rr}
-0.007 & -0.004 \\
--0.004 & 0.430
-\end{array}
-\end{pmatrix}.
-\end{equation}
-\color{black}
 
@@
 attributable to dust.
+
+\color{orange}
+Our model can be associated with the extinction model of  \citetalias{1999PASP..111...63F} using Eqn.\ref{trans_I:eqn}
+and the assumption that  SN~2011fe has zero extinction.  Transforming our parameters to those
+of   \citetalias{1999PASP..111...63F}, we obtain
+$A^F_V=0.77$ and $E^F(B-V)=1.28$ (which together imply $R^F=0.60$) with covariance
+\begin{equation}
+\begin{pmatrix}
+\begin{array}{rr}
+0.430 & -0.004 \\
+-0.004 & 0.007
+\end{array}
+\end{pmatrix}.
+\end{equation}
+The color excesses predicted by these values are shown in Figure~\ref{sn2014j:fig}.
+
+The imperfect correspondence between our model and that of   \citetalias{1999PASP..111...63F} is seen in the Figure.
+While both models reproduce the observed color excesses at the extreme $U$ and $I$ bands, that of  \citetalias{1999PASP..111...63F} 
+is unable to match the central colors.
+The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
+in Figure 3 of  \citet{2014ApJ...788L..21A}.  (They use
+UV through NIR data to fit \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$.)
+Our model predictions provide a significantly better match to the data
+despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
+
+\color{black}
 
@@
 \begin{array}{rr}
-1.15 & 2.79 \\
-0.71 & -4.95
+2.79 & 1.15 \\
+-4.95 & 0.71
 \end{array}
@@
 \begin{array}{rrrrrrr}
-1.00 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.06}_{-0.07} & -0.04^{+0.06}_{-0.06} & 0.11^{+0.07}_{-0.07} & -0.00^{+0.07}_{-0.07} & -0.06^{+0.07}_{-0.06} \\
-0.00^{+0.06}_{-0.06} & 1.00 & 0.11^{+0.03}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
--0.07^{+0.06}_{-0.07} & 0.11^{+0.03}_{-0.04} & 1.00 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.07} \\
--0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1.00 & 0.03^{+0.06}_{-0.06} & 0.04^{+0.07}_{-0.08} & -0.08^{+0.10}_{-0.09} \\
-0.11^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.06}_{-0.06} & 1.00 & 0.06^{+0.08}_{-0.07} & 0.06^{+0.08}_{-0.07} \\
--0.00^{+0.07}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.08} & 0.06^{+0.08}_{-0.07} & 1.00 & 0.01^{+0.08}_{-0.07} \\
--0.06^{+0.07}_{-0.06} & -0.01^{+0.08}_{-0.08} & 0.04^{+0.07}_{-0.07} & -0.08^{+0.10}_{-0.09} & 0.06^{+0.08}_{-0.07} & 0.01^{+0.08}_{-0.07} & 1.00 \\
+1& 0.00^{+0.06}_{-0.06} & -0.07^{+0.06}_{-0.07} & -0.04^{+0.06}_{-0.06} & 0.11^{+0.07}_{-0.07} & -0.00^{+0.07}_{-0.07} & -0.06^{+0.07}_{-0.06} \\
+0.00^{+0.06}_{-0.06} & 1 & 0.11^{+0.03}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
+-0.07^{+0.06}_{-0.07} & 0.11^{+0.03}_{-0.04} & 1 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.07} \\
+-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1 & 0.03^{+0.06}_{-0.06} & 0.04^{+0.07}_{-0.08} & -0.08^{+0.10}_{-0.09} \\
+0.11^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.06}_{-0.06} & 1 & 0.06^{+0.08}_{-0.07} & 0.06^{+0.08}_{-0.07} \\
+-0.00^{+0.07}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.08} & 0.06^{+0.08}_{-0.07} & 1 & 0.01^{+0.08}_{-0.07} \\
+-0.06^{+0.07}_{-0.06} & -0.01^{+0.08}_{-0.08} & 0.04^{+0.07}_{-0.07} & -0.08^{+0.10}_{-0.09} & 0.06^{+0.08}_{-0.07} & 0.01^{+0.08}_{-0.07} & 1 \\
 \end{array}
@@
 \color{orange}
-not of statistical significance.
+not statistically significant.
 \color{black}
@@
 are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
-relative to the statistical uncertainties.   Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
-with the extracted distributions.
-%There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
-%the uncertainties in the predictor variable, which in turn lead to 
-%regression dilution.  Our analysis is susceptible to this bias because we consciously do not include distributions
-%of supernova parameters as part of our model.
+relative to the statistical uncertainties. 
+\color{orange}
+Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
+with the extracted distributions.  Also, 
+there is a tendency for the slope parameters associated with the spectral features to be slightly underestimated, which is an expected consequence of 
+the uncertainties in the predictor variable that lead to 
+regression dilution \citep{spearman04}. 
+\color{black}
 
@@
 \color{orange}
-for the subset of supernovae whose hosts are given in \citet{2013ApJ...770..108C}.
+for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
 Also plotted  are ideograms of $A_{\delta I}$ for the two subsamples obtained by dividing the full sample at a host mass of  $\log{(M/M_\sun)}=10$.
@@
 for low- and high-mass hosts respectively. 
-Using the SNfactory sample,
-\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star formation rate, rather than
-global host mass.
+%Using the SNfactory sample,
+%\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star formation rate, rather than
+%global host mass.
 

### 2017-05-01 apj.tex
complete new version that sets length of R vector

@@
 \begin{abstract}
-\color{orange}
+\color{purple}
 Through empirical modeling, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined 
@@
 %------
-confidence
-\color{orange}
-based on the posterior.
-\color{black}
+confidence.
 The color changes allowed by the model are almost parallel to the color changes allowed by the extinction model of  \citet{1999PASP..111...63F} with floating
@@
 
-\color{orange}
+\color{purple}
 We impose
@@
 in our linear model these values are unconstrained.
-\color{orange}
+\color{purple}
 We impose 
@@
 
-\color{orange}
+\color{purple}
 For four selected colors, a plot of the
-observed versus deduced colors and the histogram of their differences
+observed versus deduced intrinsic colors and the histogram of their differences
 \color{black}
@@
             \caption{
-            \color{orange}
-            Observed versus deduced colors for four selected colors.  Plotted on the right for each color
-is the histogram of the difference between the observed and deduced colors.
+            \color{purple}
+            Observed versus deduced intrinsic colors for four selected colors.  Plotted on the right for each color
+is the histogram of the difference between the observed and intrinsic colors.
 \color{black}
@@
 
-The histogram of the medians of the grey offsets, $\Delta$, for all supernovae is shown in Figure~\ref{hist:fig}.  The distribution is non-Gaussian, 
+\color{purple}
+The fit $\Delta$'s are highly correlated between supernovae.  To aid in visualization, we remove much of this
+correlation by subtracting out the $\Delta|_0$ of  an arbitrary supernova.
+The histogram of the medians of these relative  grey offsets $\Delta-\Delta|_0$,
+is shown in Figure~\ref{hist:fig}.  The distribution
 has a standard deviation of
 %-----
-$0.10$
+$0.08$
 %-----
-mag, and a broad tail in the positive (fainter) direction. 
-\color{orange}
+mag, and a tail in the positive (fainter) direction. 
 Of the three extreme outliers, the supernovae with largest and third largest $\Delta$'s have  heliocentric redshifts of 
@@
    \centering
-   \includegraphics[width=5.2in]{output11/Delta_hist.pdf} 
-   \caption{Normalized ideogram and histogram of the medians of the grey offset $\Delta$. 
+   \includegraphics[width=5.2in]{output11/deltaDelta_hist.pdf} 
+   \caption{
+   \color{purple}
+   Normalized ideogram and histogram of the medians of the grey offset relative to one arbitrary supernova, $\Delta-\Delta|_0$.  
+   \color{black}
    \label{hist:fig}}
@@
 than the dispersion in $\Delta$.
-\color{orange}
+\color{purple}
 Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in $V$ and colors with respect to $V$ are
@@
 These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where direct comparison can be made.
-\color{orange}
+\color{purple}
 %model11_rubin.py
@@
 The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
-\color{orange}
+\color{purple}
 \begin{multline}
@@
 We find weak correlations between our color-excess parameters and the input features; 
-\color{orange}
+\color{purple}
 only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}(B-V)$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
@@
 
-\color{orange}
+\color{purple}
 For brevity, we do not present here the analysis of simulated data used to validate and quantify bias in our results.
@@
 %There is a pair of parameter values,  $k_0^0$ and $k_1^0$, that correspond to supernovae experiencing no extrinsic effect.
-%\color{orange}
+%\color{purple}
 %For observer filters $X$ and $Y$, we define $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$, $E(X-Y)=A_X-A_Y$.
@@
    \caption{
-   \color{orange}
+   \color{purple}
    Two perspectives (left and right columns) of the $UVI$-space
@@
 
-\color{orange}
+\color{purple}
 The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{model11trans:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa_2=-5.27/0.72=-7.31$.
@@
 
-\color{orange}
+\color{purple}
 As a check of our analysis implementation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
@@
 Figure~\ref{k0_med:fig} shows the histogram of
-median values of $\gamma^0_V k_0$.
+median values of $\gamma^0_V k_0$ 
+\color{purple}
+relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
+()
+\color{black}
 The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
@@
 the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$
-%\color{orange}
+%\color{purple}
 %While at low  $\gamma^0_V k_0$
@@
    \centering
-   \includegraphics[width=2.8in]{output11/gamma0_med.pdf}
-   \includegraphics[width=2.8in]{output11/gamma1_med.pdf}
+   \includegraphics[width=2.8in]{output11/deltagamma0_med.pdf}
+   \includegraphics[width=2.8in]{output11/deltagamma1_med.pdf}
       \caption{
-      \color{orange} Normalized ideogram and histogram 
+      \color{purple} Normalized ideogram and histogram 
+      of
+median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which is associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
+(left) : $\gamma^1_V k_1-\gamma^1_V k_1|_0$,
+which  is associated with extinction corrections due to deviations away from the canonical $\kappa_1$ value (right).
       \color{black}
-      of
-median values of Left: $\gamma^0_V k_0$, which is associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model; Right: $\gamma^1_V k_1$,
-which  is associated with extinction corrections due to deviations away from the canonical $\kappa_1$ value.
    \label{k0_med:fig}}
@@
    \centering
-   \includegraphics[width=5.2in]{output11/kk.pdf}
-      \caption{$\gamma^1_V k_1$ versus $\gamma^0_V k_0$.
+   \includegraphics[width=5.2in]{output11/deltakk.pdf}
+      \caption{
+      \color{purple}
+      $\gamma^1_V k_1-\gamma^0_V k_0|_0$ versus $\gamma^0_V k_0-\gamma^1_V k_1|_0$.
+      \color{black}
    \label{kk:fig}}
@@
    \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.
-   \color{orange}
+   \color{purple}
    In addition to the prediction
@@
 
-\color{orange}
+\color{purple}
 Our model can be associated with the extinction model of  \citetalias{1999PASP..111...63F} using Eqn.\ref{trans_I:eqn}
@@
 
-The imperfect correspondence between our model and that of   \citetalias{1999PASP..111...63F} is seen in the Figure.
-While both models reproduce the observed color excesses at the extreme $U$ and $I$ bands, that of  \citetalias{1999PASP..111...63F} 
-is unable to match the central colors.
+The imperfect correspondence between our model and that of   \citetalias{1999PASP..111...63F} is seen in Figure~\ref{sn2014j:fig}.
+While both models reproduce the observed color excesses at the extreme $U$ and $I$ bands,  \citetalias{1999PASP..111...63F}'s
+does not simultaneously match the central colors.
 The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
@@
 The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix
-\color{orange}
+\color{purple}
 \begin{multline}
@@
 The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are
-\color{orange}
+\color{purple}
 not statistically significant.
@@
 relative to the statistical uncertainties. 
-\color{orange}
+\color{purple}
 Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
@@
 we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
-\color{orange}
+\color{purple}
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
@@
    \includegraphics[width=2.8in]{output23/childress.pdf}
-s     \includegraphics[width=2.8in]{output23/childress2.pdf}
+   \includegraphics[width=2.8in]{output23/childress2.pdf}
       \caption{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
@@
 distribution of $A_V$.  
-\color{orange}
+\color{purple}
 Nesting this model in an extended model produces a result that 
@@
 colors in a manner that is distinct from the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
+
+\color{purple}
+The current data does not show a statistically significant difference in the values of our new parameter for supernovae
+in low- and high-mass host-galaxies.
+Using the SNfactory sample,
+\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star formation rate, rather than
+global host mass.  The search for a correlation between our parameter and local star formation rate is planned for future work.
+\color{black}
 

### 2017-05-01 sn2014j11.py

@@ -252,9 +252,9 @@ axes[1].set_xlabel(r'Wavelength (\AA)')
 
 plt.setp(axes[0].get_xticklabels(),visible=False)
 
-axes[1].errorbar(elam,exv-(gammam1*ans[0]+deltam1*ans[1]), \
+axes[1].errorbar(elam,-(exv-(gammam1*ans[0]+deltam1*ans[1])), \
   yerr=[numpy.sqrt(e_exv**2+fiterr**2),numpy.sqrt(e_exv**2+fiterr**2)],fmt='.',color='red')
-axes[1].errorbar(elam,exv-tempperc[0], \
+axes[1].errorbar(elam,-(exv-tempperc[0]), \
   yerr=[numpy.sqrt(e_exv**2+((tempperc[2]-tempperc[1])/2)**2),numpy.sqrt(e_exv**2+((tempperc[2]-tempperc[1])/2)**2)],fmt='.', color='blue')
 axes[1].axhline(0,linestyle=':')
 axes[1].set_ylabel(r'$\Delta E_o(X-V)$')

### 2017-05-10 apj.tex
housekeeping

@@
    \centering
-   \includegraphics[width=2.8in]{output23/ebv.pdf}
-   \includegraphics[width=2.8in]{output23/ebv_delta.pdf}
+   \includegraphics[width=2.8in]{output25/ebv.pdf}
+   \includegraphics[width=2.8in]{output25/ebv_delta.pdf}
       \caption{Left: Ideograms of the external $E(B-V)$ and
@@
    \centering
-   \includegraphics[width=5.2in]{output23/delta_corner.pdf}
+   \includegraphics[width=5.2in]{output25/delta_corner.pdf}
    \caption{Significance of the non-zero values of $\delta$ as demonstrated by the posterior contours for $\delta$ for Model~II.
@@
    \centering
-      \includegraphics[width=5.2in]{output23/deltaratio.pdf}
+      \includegraphics[width=5.2in]{output25/deltaratio.pdf}
    \caption{Significance of the non-zero values of $\delta$ as demonstrated by the best-fit values of $\delta_X/\delta_I-1$ for $\delta$ for Model~II.
@@
 \begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta I}) =\\
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta U}) =\\
 \begin{pmatrix}
 \begin{array}{rrrrrrr}
-1& 0.00^{+0.06}_{-0.06} & -0.07^{+0.06}_{-0.07} & -0.04^{+0.06}_{-0.06} & 0.11^{+0.07}_{-0.07} & -0.00^{+0.07}_{-0.07} & -0.06^{+0.07}_{-0.06} \\
-0.00^{+0.06}_{-0.06} & 1 & 0.11^{+0.03}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
--0.07^{+0.06}_{-0.07} & 0.11^{+0.03}_{-0.04} & 1 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.07} \\
--0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1 & 0.03^{+0.06}_{-0.06} & 0.04^{+0.07}_{-0.08} & -0.08^{+0.10}_{-0.09} \\
-0.11^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.06}_{-0.06} & 1 & 0.06^{+0.08}_{-0.07} & 0.06^{+0.08}_{-0.07} \\
--0.00^{+0.07}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.05^{+0.08}_{-0.07} & 0.04^{+0.07}_{-0.08} & 0.06^{+0.08}_{-0.07} & 1 & 0.01^{+0.08}_{-0.07} \\
--0.06^{+0.07}_{-0.06} & -0.01^{+0.08}_{-0.08} & 0.04^{+0.07}_{-0.07} & -0.08^{+0.10}_{-0.09} & 0.06^{+0.08}_{-0.07} & 0.01^{+0.08}_{-0.07} & 1 \\
+1 & 0.01^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.07} & 0.10^{+0.07}_{-0.06} & 0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} \\
+0.01^{+0.06}_{-0.06} & 1 & 0.10^{+0.04}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.04^{+0.06}_{-0.06} & -0.00^{+0.07}_{-0.08} & -0.00^{+0.08}_{-0.08} \\
+-0.07^{+0.07}_{-0.06} & 0.10^{+0.04}_{-0.04} & 1 & -0.14^{+0.03}_{-0.03} & -0.16^{+0.05}_{-0.05} & -0.03^{+0.08}_{-0.08} & 0.01^{+0.08}_{-0.08} \\
+-0.04^{+0.06}_{-0.07} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.03}_{-0.03} & 1 & 0.03^{+0.05}_{-0.06} & 0.02^{+0.07}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
+0.10^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & -0.16^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1 & 0.05^{+0.08}_{-0.08} & -0.01^{+0.07}_{-0.07} \\
+0.00^{+0.08}_{-0.07} & -0.00^{+0.07}_{-0.08} & -0.03^{+0.08}_{-0.08} & 0.02^{+0.07}_{-0.08} & 0.05^{+0.08}_{-0.08} & 1 & -0.00^{+0.07}_{-0.08} \\
+-0.01^{+0.08}_{-0.08} & -0.00^{+0.08}_{-0.08} & 0.01^{+0.08}_{-0.08} & -0.01^{+0.08}_{-0.08} & -0.01^{+0.07}_{-0.07} & -0.00^{+0.07}_{-0.08} & 1 \\
 \end{array}
@@
    \centering
-   \includegraphics[width=5.2in]{output23/perobject_corner.pdf} 
+   \includegraphics[width=5.2in]{output25/perobject_corner.pdf} 
    \caption{
@@
    \centering
-   \includegraphics[width=5.2in]{output23_sim/coeff0.pdf} 
+   \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $U$ band of ten independent simulated data sets.
@@
    \centering
-   \includegraphics[width=5.2in]{output23_sim/coeff1.pdf} 
+   \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $B$ band of ten independent simulated data sets.
@@
    \centering
-   \includegraphics[width=5.2in]{output23_sim/coeff2.pdf} 
+   \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $V$ band of ten independent simulated data sets.
@@
    \centering
-      \includegraphics[width=5.2in]{output23_sim/coeff3.pdf} 
+      \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $R$ band of ten independent simulated data sets.
@@
    \centering
-         \includegraphics[width=5.2in]{output23_sim/coeff4.pdf} 
+         \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $I$ band of ten independent simulated data sets.
@@
    \centering
-%   \includegraphics[width=2.8in]{output23/x1si.pdf}
-   \includegraphics[width=5in]{output23/x1D.pdf}
+%   \includegraphics[width=2.8in]{output25/x1si.pdf}
+   \includegraphics[width=5in]{output25/x1D.pdf}
     \caption{The SALT2 $x_1$ versus $A_{\delta I}  = \delta_I D$.
@@
    \centering
-   \includegraphics[width=5.2in]{output23/residualx1.pdf}
+   \includegraphics[width=5.2in]{output25/residualx1.pdf}
     \caption{Differences between observed colors and the colors predicted from the analysis, as a function
@@
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-Also plotted  are ideograms of $A_{\delta I}$ for the two subsamples obtained by dividing the full sample at a host mass of  $\log{(M/M_\sun)}=10$.
-Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta I}$, the difference is
+Also plotted  are ideograms of $A_{\delta U}$ for the two subsamples obtained by dividing the full sample at a host mass of  $\log{(M/M_\sun)}=10$.
+Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta U}$, the difference is
 not significant; we calculate  average
 %---
-$\langle A_{\delta I} \rangle=   -0.0026 \pm    0.0014$,
-$\langle A_{\delta I} \rangle=-0.0035 \pm    0.0010$ 
+$\langle A_{\delta I} \rangle=   -0.0021 \pm    0.007$,
+$\langle A_{\delta I} \rangle= -0.0034 \pm    0.0064$ 
 for low- and high-mass hosts respectively. 
@@
    \centering
-   \includegraphics[width=2.8in]{output23/childress.pdf}
-   \includegraphics[width=2.8in]{output23/childress2.pdf}
-      \caption{Left: Intrinsic parameter $A_{\delta I}=\delta_I D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
+   \includegraphics[width=2.8in]{output25/childress.pdf}
+   \includegraphics[width=2.8in]{output25/childress2.pdf}
+      \caption{Left: Intrinsic parameter $A_{\delta U}=\delta_U D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
       less than and greater than  $\log{(M/M_\sun)}=10$.
-Right: Normalized ideograms of  $A_{\delta I}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
+Right: Normalized ideograms of  $A_{\delta U}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
    \label{childress:fig}}

### 2017-05-10 view25_scoeff.py

@@ -12,24 +12,24 @@ import scipy
 import cPickle
 import matplotlib as mpl
 import sivel
-# mpl.rcParams['font.size'] = 18
+import flip
 
-f = open('temp25_sim_null0.pkl','rb')
+# mpl.rcParams['font.size'] = 18
+tag="_null"
+f = open('temp25_sim'+tag+'0.pkl','rb')
 (fit,_) = pickle.load(f)
 
 mega = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['gamma1'],fit['rho1'],fit['L_sigma']])
 
 print mega.shape
-for index in xrange(1,7):
-    f = open('temp25_sim_null{}.pkl'.format(index),'rb')
+for index in xrange(0):
+    f = open('temp25_sim'+tag+'{}.pkl'.format(index),'rb')
     (fit,_) = pickle.load(f)
     mega_ = numpy.array([fit['c'],fit['alpha'],fit['beta'],fit['eta'],fit['gamma'],fit['gamma1'],fit['rho1'],fit['L_sigma']])
 
     mega = numpy.concatenate((mega,mega_),axis=1)
 
 mega = numpy.transpose(mega)
-
-
 
 f = open('temp25.pkl','rb')
 (fit_input,_) = pickle.load(f)
@@ -97,8 +97,18 @@ beta = numpy.median(fit_input['beta'],axis=0)
 eta = numpy.median(fit_input['eta'],axis=0)
 gamma = numpy.median(fit_input['gamma'],axis=0)
 gamma1 = numpy.median(fit_input['gamma1'],axis=0)
-delta = numpy.median(fit_input['rho1'],axis=0)
 
+
+temprho1,_ = flip.flip(fit_input)
+
+
+H,edges  = numpy.histogramdd(temprho1,bins=30)
+w = numpy.argmax(H)
+w = numpy.unravel_index(w,H.shape)
+delta=numpy.array([edges[0][w[0]],edges[1][w[1]],edges[2][w[2]],edges[3][w[3]],edges[4][w[4]]])
+
+if tag == '_null':
+    delta[:]=0
 
 cov = numpy.zeros((5,5))
 for x1, x2 in zip(fit_input['L_Omega'], fit_input['L_sigma']):
@@ -119,17 +129,35 @@ for index in xrange(5):
[…]

### 2017-07-10 apj.tex
more

@@
 $U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
-shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
+%shown in Table~\ref{data:tab}
+have Gaussian measurement uncertainty with covariance $C$.
 Unlike the parameters associated with
@@
 relate intrinsic magnitudes with the spectral-feature parameters.
-The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
+The global parameters $\pmb{\gamma}^0$, $\pmb{\gamma}^1$  are the slopes that connect the extrinsic-color
 parameters to observed magnitudes.
@@
 These conditions specify the definition of absolute magnitude and zero color relative to which the color excess is measured:
-in our linear model these values are unconstrained.
-\color{purple}
-We impose 
+in our linear model these values are otherwise unconstrained.
+The model contains terms like $\pmb{\gamma} k$, which lead to the degeneracy $\pmb{\gamma} \rightarrow a\pmb{\gamma}$, $k \rightarrow a^{-1} k$.
+While the physical results are independent of this scaling, we impose a prior on the rms of $k$ to aid the convergence during model fitting.
+This prior does not specify the sign of $a$, which leaves a degeneracy.  As will be seen, the signal-to-noise in $\pmb{\gamma}$ is sufficiently
+high that our finite MCMC chains do not migrate between the degenerate solutions; for convenience
+we impose 
 \begin{equation}
@@
 associated
-with the $\pm$ sign, i.e.\ simultaneous sign flips of
-$\gamma^0$--$k_0$ and $\gamma^1$--$k_1$
-(when running our fits, $k_0$ and $k_1$ are set to
-identical initial conditions, so the difference in the signs of $\gamma^0_U$ and $\gamma^1_U$ distinguishes the two.)
-
-The combinations $\gamma^0$--$k_0$ and $\gamma^1$--$k_1$ are degenerate with
+with the $\pm$ sign.
+
+The combinations $\pmb{\gamma}^0$--$k_0$ and $\pmb{\gamma}^1$--$k_1$ are degenerate with
 each other under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
@@
 Having the intrinsic dispersion, $C_c$, as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
-ascribed to $\Delta$, $\gamma^0 k_0$, and $\gamma^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
+ascribed to $\Delta$, $\pmb{\gamma}^0 k_0$, and $\pmb{\gamma}^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
 that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$;
@@
 There remain degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
- $\gamma^0 \rightarrow \gamma^0  + \epsilon_{\gamma^0}$, $\gamma^1 \rightarrow \gamma^1 + \epsilon_{\gamma^1}$under the condition
+ $\pmb{\gamma}^0 \rightarrow \pmb{\gamma}^0  + \epsilon_{\pmb{\gamma}^0}$, $\pmb{\gamma}^1 \rightarrow \pmb{\gamma}^1 + \epsilon_{\pmb{\gamma}^1}$under the condition
 $$
-\epsilon_\Delta  +  \epsilon_{\gamma^0} k_0+  \epsilon_{\gamma^1} k_1=0,
+\epsilon_\Delta  +  \epsilon_{\pmb{\gamma}^0} k_0+  \epsilon_{\pmb{\gamma}^1} k_1=0,
 $$
-i.e.\ shifts in the global coefficients $\gamma$ can be compensated by shifts in $\Delta$ for each supernova while maintaining 
+i.e.\ shifts in the global coefficients $\pmb{\gamma}$ can be compensated by shifts in $\Delta$ for each supernova while maintaining 
 $\langle \Delta \rangle=0$.
 Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
-$\alpha \rightarrow \alpha - \gamma \epsilon$, $c \rightarrow c + \langle EW_{Ca}\rangle \epsilon$, i.e. the
+$\alpha \rightarrow \alpha - \pmb{\gamma} \epsilon$, $c \rightarrow c + \langle EW_{Ca}\rangle \epsilon$, i.e. the
 linear external terms can leak into the linear spectral feature corrections.
@@
 the Monte Carlo chains have not converged to the stationary posterior distribution.
-We have rurun the analysis with a variety of initial conditions, including one with all the $\gamma$'s equal to zero, except for a small positive 
+We have rurun the analysis with a variety of initial conditions, including one with $\pmb{\gamma}$ equal to zero, except for a small positive 
 $\gamma^0_0$ and small negative $\gamma^1_0$; the 68\% credible intervals
@@
    \includegraphics[width=5.2in]{output11/coeff0.pdf} 
-            \caption{Model~I posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
+            \caption{Model~I posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $U$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
             projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ are shown for reference --
+            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ are shown for reference --
             in many cases they are outside the range of the plot.
@@
    \includegraphics[width=5.2in]{output11/coeff1.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $B$ band, from Model~I.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $B$ band, from Model~I.
  \label{global2:fig}}
@@
    \includegraphics[width=5.2in]{output11/coeff2.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $V$ band, from Model~I.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $V$ band, from Model~I.
  \label{global3:fig}}
@@
       \includegraphics[width=5.2in]{output11/coeff3.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $R$ band, from Model~I.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $R$ band, from Model~I.
  \label{global4:fig}}
@@
          \includegraphics[width=5.2in]{output11/coeff4.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $I$ band, from Model~I.
+            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $I$ band, from Model~I.
  \label{global5:fig}}
@@
 
-For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$
+For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$
 are given in Table~\ref{global:tab}.
-As the $\gamma$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_V$,
+As the $\pmb{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_V$,
 their results are shown in terms of $\gamma^i_X/\gamma^i_V-1$.
@@
 Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in $V$ and colors with respect to $V$ are
-\begin{equation}
-\sigma(V,U-V,B-V,V-R,V-I)=
+\begin{multline}
+\sigma(V,U-V,B-V,V-R,V-I)=\\
 %\begin{pmatrix}
@@
  \label{sig_intrinsic:eqn}
- \end{equation}
+ \end{multline}
 The correlations between these parameters are
-\begin{equation}
-Cor(V,U-V,B-V,V-R,V-I)=
+\begin{multline}
+Cor(V,U-V,B-V,V-R,V-I)=\\
 \begin{pmatrix}
@@
  \label{cor_intrinsic:eqn}
- \end{equation}
+ \end{multline}
 \color{black}
@@
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
-The two sets of  $\gamma^i$ parameters  are significantly non-zero. 
+The two sets of  $\pmb{\gamma}^i$ parameters  are significantly non-zero. 
 None of the 20000 links of 
-our Monte Carlo chains for $\gamma$ extend to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
+our Monte Carlo chains for $\pmb{\gamma}$ extend to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
 influence of $k_0$ and $k_1$  on supernova magnitudes
@@
 
-We compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
+We compare our model and its color-coefficient parameters $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ with the expectations of  dust models.
 The 2-parameter linear model
@@
  $R^F$ and $A^F_V$,
-and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%.
+and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%;
+\color{red}
+for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error amplitude in Eqn.~\ref{f99:eqn} is $<0.008$ mag.
+\color{black}
 
@@
 \end{equation}
-Our median-fit values for the $\gamma$ coefficients,
+Our median-fit values for the $\pmb{\gamma}$ coefficients,
 %---- fitz11.py
@@
 \begin{pmatrix}
-\vec{\epsilon}_a \\
-\vec{\epsilon}_b
+\vec{\epsilon}_{\gamma^0} \\
+\vec{\epsilon}_{\gamma^1}
 \end{pmatrix},
@@
 \begin{align}
-\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
-\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
+\begin{split}
+\vec{\epsilon}_{\gamma^0} &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
+\vec{\epsilon}_{\gamma^1} & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
+\end{split}
 \label{res_I:eqn}
 \end{align}
-contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.
+quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.
 
@@
 of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
-and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\gamma$ vectors are chosen to intersect the origin.
+and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\pmb{\gamma}$ vectors are chosen to intersect the origin.
 The two perspectives show that while the four vectors point in different directions for each band combination,
-they are almost coplanar in $UVI$, and close to coplanar in $BVR$.  The $a$ and $b$ vectors and the $\gamma^0$ and $\gamma^1$
+they are almost coplanar in $UVI$, and close to coplanar in $BVR$.  The $a$ and $b$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
 vectors are bases for almost the same plane in the 5-dimensional color space, and can be transformed between themselves through rotation.
@@
    \color{purple}
-   Two perspectives (left and right columns) of the $UVI$-space
-of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
-   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combination $a(X)+b(X)/2.44$ is shown in the dotted red
-   line: it is almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.   The combination $-7.31a(X)+b(X)$ is shown in the dotted blue
-   line: it is
-   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$ in $UVI$.  
+   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
+   magnitudes in 5-bands $UBVRI$ this visualization shows only $UVI$.   The left and right plots show the same information from
+   two different perspectives.
+   Our model is shown in solid-line unit vectors in the directions of $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$. The only possible magnitudes possible
+   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
+   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
+   in the directions of  $a(X)$, $b(X)$; the only possible magnitudes possible are confined to the plane that contains both.
+   The perspective on the right visually show that all four vectors are nearly coplanar.  
+   The combination $a(X)+b(X)/2.44$ is shown in the dotted red
+   line: it is almost perfectly superimposed on $\pmb{\gamma}^0$.
    \label{plane:fig}}
@@
 
-When fixing the origin of the $\gamma$'s to zero, the $\gamma$ vectors are found to be coplanar with $a$ and $b$.
+When fixing the origin of $\pmb{\gamma}$ to zero, the $\pmb{\gamma}$ vectors are found to be coplanar with $a$ and $b$.
 However the linear model does not specify zero dust so the origin of gamma is unspecified.
@@
 A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
-the vectors $\gamma^0$ and $\gamma^1$.  Suppose that the data were described by a dust model.  Then a \citetalias{1999PASP..111...63F}  dust model 
+the vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.  Suppose that the data were described by a dust model.  Then a \citetalias{1999PASP..111...63F}  dust model 
 can be written as 
@@
 \color{purple}
-The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{model11trans:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa_2=-5.27/0.72=-7.31$.
-The directions of the $\gamma$ vectors, and  the expectations from  \citetalias{1999PASP..111...63F} with $R=\kappa^{-1}$, are shown in 
-Figure~\ref{plane:fig}.  There is almost perfect alignment between $\gamma^0$ and $R=2.44$ dust.
+The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa_2=-5.27/0.72=-7.31$.
+The directions of the $\pmb{\gamma}$ vectors, and  the expectations from  \citetalias{1999PASP..111...63F} with $R=\kappa^{-1}$, are shown in 
+Figure~\ref{plane:fig}.  There is almost perfect alignment between $\pmb{\gamma}^0$ and $R=2.44$ dust.
  From the Monte Carlo chains, we find a 68\% credible interval for $\kappa^{-1}_1$ of 2.26--2.63.
@@
 Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
-$\gamma^0$ is aligned with  $a(X)+b(X)/R^F$, and $\gamma^1$ is unconstrained.
+$\pmb{\gamma}^0$ is aligned with  $a(X)+b(X)/R^F$, and $\pmb{\gamma}^1$ is unconstrained.
 
@@
 can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
-The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
-Our analysis yields an angle of 154\arcdeg\ between  $\gamma^0$ and $\gamma^1$.
+The zero-correlation condition, which determines the direction of $\pmb{\gamma}^1$,  is for the coordinate values along $\pmb{\gamma}^0$ to be uncorrelated with the coordinate values along $\pmb{\gamma}^1$.
+Our analysis yields an angle of 154\arcdeg\ between  $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
 The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
-Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\gamma^0$.
+Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\pmb{\gamma}^0$.
 
@@
       of
-median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which is associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
+median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
 (left) : $\gamma^1_V k_1-\gamma^1_V k_1|_0$,
@@
 \end{equation}
-where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab} and the fit
+where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and the fit
 parameters $e_i $.
@@
 contributions.
-Among the supernovae in the SNfactory  set used to determine $\gamma^0$ and $\gamma^1$, the
+Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
 objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
@@
 of   \citetalias{1999PASP..111...63F}, we obtain
-$A^F_V=0.77$ and $E^F(B-V)=1.28$ (which together imply $R^F=0.60$) with covariance
+$A^F_V=0.77$ and $E^F(B-V)=1.28$ with covariance
 \begin{equation}
@@
 \end{array}
-\end{pmatrix}.
+\end{pmatrix},
 \end{equation}
+which implies $R^F= 0.59^{+ 0.53}_{-0.48}$.
 The color excesses predicted by these values are shown in Figure~\ref{sn2014j:fig}.
@@
 two extrinsic parameters produce
-magnitudes consistent
-with two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
+magnitudes similar
+to two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
 An extension to our model is now added to explore the possibility of
 a possible additional
-color parameter that could have its origins in supernova astrophysics.
+color parameter.
 The extended model referred to as Model~II is written as
@@
 \end{equation}
-In all aspects it is identical to the previous model except for the addition of the term $\delta D$,
+In all aspects it is identical to the previous model except for the addition of the term $\pmb{\delta} D$,
 which affects the mean
-absolute magnitudes.  Thus
-each supernova is given an intrinsic $D$ parameter that is linearly related to
-absolute magnitudes through global coefficients $\delta$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
+absolute magnitudes.  
+Each supernova has an intrinsic $D$ parameter that is linearly related to
+absolute magnitudes through global coefficients $\pmb{\delta}$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
 its effects on broadband magnitudes.
+
+The $\pmb{\delta} D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms:
+for convenience these terms are referred to as ``intrinsic''.
+However, switching the placement of the
+$\pmb{\delta} D$ terms from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from intrinsic to extrinsic contributions,
+does not significantly affect the results, meaning that data are not constraining enough
+to identify $\pmb{\delta} D$ as being physically intrinsic or extrinsic.
+
+\color{red}
+We impose
+$\langle D\rangle=0$
+to specify the (arbitrary) definition of zero color.  We assign a prior on the ensemble amplitudes of $D$ to break the
+degeneracy $\pmb{\delta} \rightarrow a\pmb{\delta}$, $D \rightarrow a^{-1}D$.  A sign degeneracy in $a$ remains.
+In contrast to $\pmb{\gamma}$, our MCMC chains migrate between these degenerate solutions in  $\pmb{\delta}$.  This
+degeneracy is preserved in the model.
+In the running of the Monte Carlo fit, the initial conditions and ranges for
+$\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
+to maintain their correspondence between the two models. 
+\color{black}
 
@@
 
-The $\delta D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms:
-it is for this reason that for convenience these terms are referred to as ``intrinsic''.
-However, we emphasize now that we have also run the alternative case  of switching the placement of the
-$\delta D$ terms from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from intrinsic to extrinsic contributions.
-Analyses of the two different models give practically identical results, meaning that data are not constraining enough
-to identify $\delta D$ as being physically intrinsic or extrinsic.
-
-To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints. We impose
-\begin{equation}
-\langle D\rangle=0,\,  \delta \cdot \gamma^0=0,\, \delta \cdot \gamma^1=0.
-\end{equation}
-The first of these constraints specifies the (arbitrary) definition of zero color.   The latter two confine possible magnitude
-variations to be those that cannot be attributed to 
-the $\gamma k$ terms (i.e.\ dust); this condition breaks the degeneracies between $\delta D$  
-and $\gamma k$. 
-Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_U$,
-so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
-We apply the condition $\delta_I>0$ to break this degeneracy,
-and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
-In the running of the Monte Carlo fit, the initial conditions for
-$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
-to maintain their correspondence between the two models.
-
 The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
 results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
-are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the slight reduction of the standard
-deviations of the magnitude residuals $\sigma_X$.
-The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust model, in that now
-\begin{equation}
-\begin{pmatrix}
- \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
-\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
-\end{pmatrix}=
-\begin{pmatrix}
-\begin{array}{rr}
-2.79 & 1.15 \\
--4.95 & 0.71
-\end{array}
-\end{pmatrix} 
-\begin{pmatrix}
-a(X) \\
-b(X)
-\end{pmatrix}+
-\begin{pmatrix}
-\vec{\epsilon}_a \\
-\vec{\epsilon}_b
-\end{pmatrix},
-\end{equation}
-where the residual vectors 
-\begin{align}
-\vec{\epsilon}_a &=\{0.05, -0.06, -0.06,  0.06,  0.07\},\\
-\vec{\epsilon}_b &=\{ -0.10, 0.20,  -0.19,  0.32, -0.30\}
-\end{align}
-\label{model11trans:eqn}
-are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
-contribute similar 2\% and 4\% to the total  length of the vector.
-(These can be compared to the results of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.)
-%The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.
+are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the reduction of the standard
+deviations of the magnitude residuals $\sigma_X$,
+\color{red}
+particularly in the $U$ and $B$ bands.
+\color{black}
 
@@
 Parameters& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
-
 $\alpha_X$
 &
-$0.0045^{+0.0009}_{-0.0010}$
-&
-$0.0017^{+0.0008}_{-0.0008}$
-&
-$0.0015^{+0.0006}_{-0.0006}$
-&
-$0.0015^{+0.0005}_{-0.0005}$
-&
-$0.0027^{+0.0005}_{-0.0005}$
+$0.0039^{+0.0009}_{-0.0009}$
+&
+$0.0013^{+0.0008}_{-0.0007}$
+&
+$0.0013^{+0.0006}_{-0.0006}$
+&
+$0.0013^{+0.0005}_{-0.0005}$
+&
+$0.0025^{+0.0005}_{-0.0004}$
 \\
@@
 &
-$   1.9^{+   1.1}_{  -0.5}$
-&
-$   0.1^{+   0.1}_{  -0.2}$
-&
-$  \ldots$
-&
-$   0.0^{+   0.1}_{  -0.1}$
-&
-$   0.8^{+   0.8}_{  -0.3}$
+$   2.1^{+   1.4}_{  -0.6}$
+&
+$   0.0^{+   0.1}_{  -0.2}$
+&
+$  \dots $
+&
+$   0.0^{+   0.2}_{  -0.1}$
+&
+$   1.0^{+   1.1}_{  -0.5}$
 \\
@@
 &
-$ 0.033^{+ 0.003}_{-0.003}$
+$ 0.032^{+ 0.003}_{-0.003}$
+&
+$ 0.025^{+ 0.002}_{-0.002}$
 &
@@
 &
-$ 0.026^{+ 0.002}_{-0.002}$
-&
 $ 0.021^{+ 0.002}_{-0.002}$
@@
 &
-$  0.25^{+  0.04}_{ -0.05}$
-&
-$ -0.01^{+  0.02}_{ -0.03}$
-&
-$  \ldots$
+$  0.24^{+  0.05}_{ -0.05}$
+&
+$ -0.02^{+  0.03}_{ -0.03}$
+&
+$   \dots$
 &
@@
 &
-$0.0002^{+0.0012}_{-0.0012}$
-&
-$0.0002^{+0.0010}_{-0.0010}$
-&
-$0.0007^{+0.0008}_{-0.0008}$
-&
-$0.0007^{+0.0007}_{-0.0007}$
-&
-$0.0000^{+0.0006}_{-0.0006}$
+$-0.0002^{+0.0011}_{-0.0011}$
+&
+$-0.0000^{+0.0009}_{-0.0009}$
+&
+$0.0005^{+0.0008}_{-0.0008}$
+&
+$0.0005^{+0.0007}_{-0.0007}$
+&
+$-0.0002^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.25^{+  1.35}_{ -1.38}$
-&
-$ -0.34^{+  1.21}_{ -1.04}$
-&
-$  \ldots$
-&
-$ -0.05^{+  0.34}_{ -0.29}$
-&
-$ -0.70^{+  0.84}_{ -0.88}$
+$ -0.41^{+  2.27}_{ -1.94}$
+&
+$ -0.37^{+  1.59}_{ -1.26}$
+&
+$   \dots$
+&
+$ -0.10^{+  0.30}_{ -0.29}$
+&
+$ -0.80^{+  1.54}_{ -1.29}$
 \\
@@
 &
-$ 64.01^{+  3.79}_{ -3.69}$
-&
-$ 51.96^{+  3.18}_{ -3.10}$
-&
-$ 38.49^{+  2.70}_{ -2.63}$
-&
-$ 29.38^{+  2.40}_{ -2.33}$
-&
-$ 20.86^{+  2.19}_{ -2.22}$
+$ 61.66^{+  3.97}_{ -3.86}$
+&
+$ 50.09^{+  3.25}_{ -3.16}$
+&
+$ 37.41^{+  2.69}_{ -2.60}$
+&
+$ 28.81^{+  2.35}_{ -2.31}$
+&
+$ 20.76^{+  2.17}_{ -2.12}$
 \\
@@
 &
-$  0.66^{+  0.06}_{ -0.05}$
-&
-$  0.35^{+  0.03}_{ -0.03}$
-&
-$  \ldots$
-&
-$ -0.24^{+  0.01}_{ -0.02}$
-&
-$ -0.46^{+  0.03}_{ -0.03}$
+$  0.65^{+  0.06}_{ -0.05}$
+&
+$  0.34^{+  0.03}_{ -0.03}$
+&
+$   \dots$
+&
+$ -0.23^{+  0.01}_{ -0.01}$
+&
+$ -0.45^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$-10.18^{+  3.53}_{ -3.92}$
-&
-$-11.64^{+  2.95}_{ -3.23}$
-&
-$-14.42^{+  2.45}_{ -2.72}$
-&
-$-13.73^{+  2.09}_{ -2.31}$
-&
-$-12.70^{+  2.03}_{ -2.16}$
+$ -9.47^{+  3.70}_{ -4.37}$
+&
+$-11.09^{+  3.02}_{ -3.57}$
+&
+$-13.59^{+  2.47}_{ -2.81}$
+&
+$-12.82^{+  2.14}_{ -2.40}$
+&
+$-11.66^{+  2.25}_{ -2.32}$
 \\
@@
 &
-$ -0.29^{+  0.16}_{ -0.18}$
-&
-$ -0.19^{+  0.09}_{ -0.10}$
-&
-$  \ldots$
-&
-$ -0.05^{+  0.05}_{ -0.04}$
-&
-$ -0.12^{+  0.10}_{ -0.09}$
-\\
-$\delta_X$
-&
-$  2.07^{+  0.69}_{ -0.74}$
-&
-$ -2.25^{+  0.78}_{ -0.66}$
-&
-$ -1.85^{+  0.63}_{ -0.60}$
-&
-$  0.41^{+  0.53}_{ -0.57}$
-&
-$  2.02^{+  0.97}_{ -1.08}$
-\\
-${{\delta_X/\delta_I-1}}$
-&
-$  0.04^{+  0.52}_{ -0.27}$
-&
-$ -2.09^{+  0.27}_{ -0.62}$
-&
-$ -1.92^{+  0.25}_{ -0.56}$
-&
-$ -0.80^{+  0.68}_{ -0.26}$
-&
-$  \ldots$
+$ -0.30^{+  0.19}_{ -0.21}$
+&
+$ -0.18^{+  0.11}_{ -0.12}$
+&
+$   \dots$
+&
+$ -0.06^{+  0.06}_{ -0.06}$
+&
+$ -0.15^{+  0.12}_{ -0.12}$
+\\
+${{\delta_X/\delta_U-1}}$
+&
+$   \dots$
+&
+$ -0.22^{+  0.35}_{ -0.32}$
+&
+$ -0.73^{+  0.51}_{ -0.61}$
+&
+$ -0.91^{+  0.43}_{ -0.69}$
+&
+$ -1.17^{+  0.46}_{ -0.93}$
 \\
@@
 &
-$ 0.053^{+ 0.013}_{-0.012}$
-&
-$ 0.029^{+ 0.008}_{-0.009}$
-&
-$ 0.018^{+ 0.004}_{-0.005}$
-&
-$ 0.009^{+ 0.007}_{-0.006}$
-&
-$ 0.042^{+ 0.005}_{-0.004}$
+$ 0.053^{+ 0.009}_{-0.011}$
+&
+$ 0.018^{+ 0.012}_{-0.012}$
+&
+$ 0.020^{+ 0.004}_{-0.005}$
+&
+$ 0.010^{+ 0.008}_{-0.007}$
+&
+$ 0.040^{+ 0.006}_{-0.005}$
 \\
@@
 
+\color{red}
+
+The significance of the $\pmb{\delta}$ parameters is shown pictorially in
+Figure~\ref{deltacorner:fig}, which shows their posteriors.
+Recall that fixing $\delta_X=0$ reverts this model into the two extrinsic-parameter model of \S\ref{model:sec},
+this null result lies on the 85\%-ile contour.
+Recall that
+the model has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ that results in the bimodal peaks in the distribution.
+To aid in the visualization of the results,
+we break this degeneracy by imposing  that the one supernova with the highest signal-to-noise in $D$ be positive.
+The resulting posterior contours of $\pmb{\delta}$ with this additional
+condition are shown in Figure~\ref{deltacorner:fig}.
+The modes of $\pmb{\delta}$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output25/delta_corner.pdf}
+     \includegraphics[width=2.8in]{output25/delta_corner_flipped.pdf}
+   \caption{Left:  Posterior contours for $\pmb{\delta}$ for Model~II.
+   Right: The same posteriors after imposing that  the one supernova with the highest signal-to-noise has positive value of $D$.
+     Lines for $\pmb{\delta}=0$ are overplotted.
+   \label{deltacorner:fig}}
+\end{figure}
+
+An alternative visualization of the $\pmb{\delta}$ results can be seen in Figure~\ref{deltaratio:fig}, which
+shows  values of $\delta_X/\delta_U-1$, statistics insensitive to the scaling (including the sign) degeneracy.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.2in]{output25/deltaratio.pdf}
+   \caption{Median values of $\delta_X/\delta_U$ in the 5 bands and corresponding 68\% intervals for for Model~II.
+   A dotted line at zero is shown for reference.
+   \label{deltaratio:fig}}
+\end{figure}
+
+\color{black}
+
+%The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.
+
 The distributions of both sources of color excess $E(B-V)$ and
  $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
-The standard deviations of $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
+ (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
+The standard deviations of  the median $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
 %-----
-0.081
-and 0.010
+0.075
+and 0.014
 %-----
 mag respectively.
-The range of $B-V$ colors is $\sim 8$ times larger for the external contribution; variation in $B-V$ color due to the intrinsic term is dwarfed by the extrinsic dust
+The range of $B-V$ colors is $> 5$ times larger for the external contribution; variation in $B-V$ color due to the intrinsic term is dwarfed by the extrinsic dust
 component.
@@
 \end{figure}
-The significance of the $\delta$ parameters is shown pictorially in
-Figure~\ref{deltacorner:fig}, which shows the $\delta$ posteriors.
-Recall that fixing $\delta_X=0$ reverts this model into the two extrinsic-parameter model of \S\ref{model:sec}.
-Assigning the Monte Carlo links to bins of width 0.5 in each $\delta$ parameter, the maximum number of links in a single bin is 303, the number of bins
-with at least one element is 1987, and the bin that contains $\delta=0$ for all bands has zero elements; we thus claim a detection
-of a third color-parameter at $> (1-5\times 10^{-4})$.
-Figure~\ref{deltaratio:fig} shows  values of $\delta_X/\delta_I-1$ that  have significant non-zero values.
-While the signal of the internal parameter is strong within the context of this model, ``model testing'' (comparing the
-performance  between this model
-and that of \S\ref{model:sec}), is challenging for Bayesian Monte Carlo analysis.  Evidence calculations are planned
-for the next generation of STAN and the development of robust evidence algorithms is a subject of theoretical work.
-
-An interesting feature
-is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
-to $I$.
-These are not the behaviors expected from normal dust, or
-circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
-2015ApJ...807L..26G} and so may be indicative of underlying supernova physics beyond that captured by $EW_{Ca}$, $EW_{Si}$ and
-$\lambda_{Si}$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output25/delta_corner.pdf}
-   \caption{Significance of the non-zero values of $\delta$ as demonstrated by the posterior contours for $\delta$ for Model~II.
-   Lines for $\delta=0$ are overplotted.
-   \label{deltacorner:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-      \includegraphics[width=5.2in]{output25/deltaratio.pdf}
-   \caption{Significance of the non-zero values of $\delta$ as demonstrated by the best-fit values of $\delta_X/\delta_I-1$ for $\delta$ for Model~II.
-   A dotted line at zero is shown for reference.
-   \label{deltaratio:fig}}
-\end{figure}
-
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix
+
+The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta U}=\delta_U D$ are given in the matrix
 \color{purple}
@@
 Second, the intrinsic term is not a second-order extrinsic correction.
-
 The distributions for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, 
@@
 
-\color{black}
-The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
+\color{red}
+The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$ for better signal-to-noise) can be expressed as
+\color{black}
+\begin{equation}
+\begin{pmatrix}
+ \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
+\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} \\
+\frac{\delta_X}{\delta_U} \\
+\end{pmatrix}=
+\begin{pmatrix}
+\begin{array}{rr}
+2.88 & 1.16 \\
+-5.00 & 0.73 \\
+0.24 & 0.46
+\end{array}
+\end{pmatrix} 
+\begin{pmatrix}
+a(X) \\
+b(X)
+\end{pmatrix}+
+\begin{pmatrix}
+\vec{\epsilon}_{\gamma^0} \\
+\vec{\epsilon}_{\gamma^1} \\
+\vec{\epsilon}_{\delta}
+\end{pmatrix},
+\label{model2trans:eqn}
+\end{equation}
+where the residual vectors are 
+\begin{align}
+\begin{split}
+\vec{\epsilon}_{\gamma^0} &=\{0.07, -0.07, -0.07,  0.06,  0.02\},\\
+\vec{\epsilon}_{\gamma^1} &=\{ -0.04, 0.14,  -0.24,  0.32, -0.22\},\\
+\vec{\epsilon}_{\delta} &=\{ -0.05, 0.08,  -0.03,  -0.09, -0.12\}
+\end{split}
+\label{model2res:eqn}
+\end{align}
+The $\pmb{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
+$\vec{\epsilon}_{\gamma^1} $
+quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that most
+of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
+(These are the same values found in the results of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.)
+\color{red}
+The $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
+\color{black}
+
+\color{red}
+The analysis is evaluated using simulated datasets.
+For one set of tests, we realize 20 random realizations of data with input  parameters equal to the median values found in
+\S\ref{model:sec} and the same noise as our data.  The input values of $\pmb{\delta}$ are set to zero.
+The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
+biases in the best fit value, and is shown in Figure~\ref{simnulldelta:fig}.  The correlations between the parameters
+and the bimodality of each posterior results in biases in the stack, with
+modes at $\mp 0.67$, $\pm0.14$, $\pm0.13$,  $\mp0.03$, $\mp0.52$.
+The input length of $\pmb{\delta}$ is zero, therefore any statistical
+fluctuation biases the value high.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output25_sim_null/delta_corner.pdf} 
+            \caption{Stacked $\pmb{\delta}$ posterior contours for 20 independent simulated data sets with input $\pmb{\delta}=0$.
+            \label{simnulldelta:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.9in]{output25_sim_null/pvalues_delta2.pdf} 
+  \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
+            \caption{ $\pmb{\delta}^2$ $\delta_\perp^2/\delta^2$ for 20 independent simulated data sets with input $\delta=0$.
+            \label{pvalues_delta2:fig}}
+\end{figure}
+
 We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
@@
 relative to the statistical uncertainties. 
-\color{purple}
 Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
@@
    \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $U$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $U$ band of ten independent simulated data sets.
 Lines show the values of the input values.
@@
    \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $B$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $B$ band of ten independent simulated data sets.
 Lines show the values of the input values.
@@
    \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $V$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $V$ band of ten independent simulated data sets.
 Lines show the values of the input values.
@@
       \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $R$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $R$ band of ten independent simulated data sets.
 Lines show the values of the input values.
@@
          \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $I$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $I$ band of ten independent simulated data sets.
 Lines show the values of the input values.
@@
 has a non-zero value at $>2\sigma$.
-The evidence for a non-zero $\delta$ remains as seen in the values of $\delta_X/\delta_I-1$ in Table~\ref{globalx1:tab}, meaning that it is not an artifact of
+The evidence for a non-zero $\pmb{\delta}$ remains as seen in the values of $\delta_X/\delta_I-1$ in Table~\ref{globalx1:tab}, meaning that it is not an artifact of
 having neglected light-curve shape.
@@
    \includegraphics[width=5in]{output25/x1D.pdf}
-    \caption{The SALT2 $x_1$ versus $A_{\delta I}  = \delta_I D$.
+    \caption{The SALT2 $x_1$ versus $A_{\delta U}  = \delta_U D$.
    \label{x1:fig}}
@@
    \includegraphics[width=2.8in]{output25/childress.pdf}
-   \includegraphics[width=2.8in]{output25/childress2.pdf}
+   \includegraphics[width=2.8in]{output25/childress_pvalue.pdf}
       \caption{Left: Intrinsic parameter $A_{\delta U}=\delta_U D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
       less than and greater than  $\log{(M/M_\sun)}=10$.
-Right: Normalized ideograms of  $A_{\delta U}$ for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
+Right: Normalized histograms of  $A_{\delta U}$ medians for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
    \label{childress:fig}}
@@
 
-\citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
-from doubly and singly ionized states, making the gas phosphorescent and efficient in redistributing energy from the UV/blue to redder
-wavelengths.  Qualitatively this would result in the structure for $\gamma_X/\gamma_V-1$ that we measure.
-We speculate that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth
-of the reionization front with respect to the core of the ejecta at peak, yielding the wavelength-dependent color behavior
-detected in this analysis.
+\color{red}
+Speculate on third parameter.
+\color{black}
 
@@
 
-We stress that our $\delta$ vector does not capture the full behavior of the observable effects of the $D$ parameter, but rather only
-the contribution perpendicular to the $\gamma$ vectors.
+We stress that our $\pmb{\delta}$ vector does not capture the full behavior of the observable effects of the $D$ parameter, but rather only
+the contribution perpendicular to the $\pmb{\gamma}$ vectors.
 

### 2017-07-10 fitz11.py

@@ -9,6 +9,20 @@ import f99_band
 import emcee
 import matplotlib as mpl
 
+from matplotlib.patches import FancyArrowPatch
+from mpl_toolkits.mplot3d import proj3d
+
+class Arrow3D(FancyArrowPatch):
+    def __init__(self, xs, ys, zs, *args, **kwargs):
+        FancyArrowPatch.__init__(self, (0,0), (0,0), *args, **kwargs)
+        self._verts3d = xs, ys, zs
+
+    def draw(self, renderer):
+        xs3d, ys3d, zs3d = self._verts3d
+        xs, ys, zs = proj3d.proj_transform(xs3d, ys3d, zs3d, renderer.M)
+        self.set_positions((xs[0],ys[0]),(xs[1],ys[1]))
+        FancyArrowPatch.draw(self, renderer)
+
 mpl.rcParams['font.size'] = 14
 
 # Get the data
@@ -135,25 +149,83 @@ kappa2 = tmat[1,0]/tmat[1,1]
 tmat = numpy.transpose(tmat)
 
 
+
+
+r1 = []
+r2 = []
+for ind in xrange(fit['gamma'].shape[0]):
+  tmat = []
+  cs = []
+  for s in ['gamma','rho1']:
+    c = fit[s][ind,:]/((fit[s][ind,1]-fit[s][ind,2]))
+    cs.append(c)
+
+    y = numpy.array([numpy.dot(c,dAdAv),numpy.dot(c,dAdebv)])
+
+    ans = numpy.linalg.solve(a,y)
+
+    tmat.append(ans)
+
+  tmat = numpy.array(tmat)
+  r1.append(tmat[0,1]/tmat[0,0])
+  
+
+# print numpy.percentile(r1,(50,50-34,50+34))
+# plt.hist(r1)
+# plt.show()
+
+
+
 # Plot vectors in UVI
 from mpl_toolkits.mplot3d import Axes3D
 from matplotlib import rcParams
 fig = plt.figure()
 ax = fig.gca(projection='3d')
 dum  = numpy.sqrt(cs[0][0]**2+cs[0][2]**2+cs[0][4]**2)
[…]

### 2017-07-10 view25.py

@@ -518,6 +518,35 @@ pp.close()
 plt.close()
 
 
+
+bins=numpy.arange(-0.3,1,0.05)
+crap = fit['gamma'][:,2][:,None]*fit['k']
+crap = crap-crap[:,0][:,None]
+plt.hist(numpy.median(crap,axis=0),bins,label='median',normed=True,alpha=0.5,width=0.025)
+plt.hist(crap.flatten(),bins,label='ideogram',normed=True,alpha=0.5)
+plt.xlabel(r'$\gamma^0_2 k_0 - \gamma^0_2 k_0|_0\approx A^F_V|_{R^F=2.44}$')
+plt.legend()
+plt.tight_layout()
+pp = PdfPages(dirname+'/deltagamma0_med.pdf')
+plt.savefig(pp,format='pdf')
+pp.close()
+plt.close()
+
+bins=numpy.arange(-0.35,0.1,0.02)
+crap2 = fit['gamma1'][:,2][:,None]*fit['k1']
+crap2 = crap2-crap2[:,0][:,None]
+plt.hist(numpy.median(crap2,axis=0),bins,label='median',normed=True,alpha=0.5,width=0.01)
+plt.hist(crap2.flatten(),bins,label='ideogram',normed=True,alpha=0.5)
+plt.xlabel(r'$\gamma^1_2 k_1 - \gamma^1_2 k_1|_0$')
+plt.legend(loc=2)
+plt.tight_layout()
+pp = PdfPages(dirname+'/deltagamma1_med.pdf')
+plt.savefig(pp,format='pdf')
+pp.close()
+plt.close()
+
+wefwe
+
 bins = numpy.arange(-0.1,0.121,0.01)
 # # plt.hist(fit['Delta'].flatten(),bins,label='ideogram',normed=True,alpha=0.5)
 # # plt.hist(numpy.median(fit['Delta'],axis=0),bins,label='median',normed=True,alpha=0.5,width=0.01)

### 2017-07-19 apj.tex
improving readability

@@
 
+We refer to this model as Model~I.
+
 \subsection{Results}
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model in \S\ref{model:sec}.\label{global:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model~I in \S\ref{model:sec}.\label{global:tab}}
 \end{table}
@@
 In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
-two extrinsic parameters produce
-magnitudes similar
-to two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
-An extension to our model is now added to explore the possibility of
-a possible additional
+two extrinsic parameters yield magnitude variations
+similar
+to those from  two-parameter dust models established for stars in the Milky Way, LMC, and SMC.
+In this Section, our model is extended
+to probe the existence of
+an additional
 color parameter.
-The extended model referred to as Model~II is written as
+The extended model, referred to as Model~II, is written as
 \begin{equation}
@@
 \end{equation}
-In all aspects it is identical to the previous model except for the addition of the term $\pmb{\delta} D$,
-which affects the mean
-absolute magnitudes.  
-Each supernova has an intrinsic $D$ parameter that is linearly related to
-absolute magnitudes through global coefficients $\pmb{\delta}$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
+In all aspects Model~II is identical to the Model~I except for the addition of the term $\pmb{\delta} D$,
+which enters in the mean intrinsic
+absolute magnitudes.  Model~I is nested in Model~II at $\pmb{\delta}=0$.
+Each supernova has an intrinsic $D$ parameter that is linearly related to the intrinsic
+absolute magnitudes through the global coefficients $\pmb{\delta}$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
 its effects on broadband magnitudes.
 
-The $\pmb{\delta} D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms:
-for convenience these terms are referred to as ``intrinsic''.
-However, switching the placement of the
-$\pmb{\delta} D$ terms from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from intrinsic to extrinsic contributions,
+The $\pmb{\delta} D$ term contributes to the means of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms.
+However, switching the placement of 
+$\pmb{\delta} D$ term from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from an intrinsic to extrinsic contribution,
 does not significantly affect the results, meaning that data are not constraining enough
-to identify $\pmb{\delta} D$ as being physically intrinsic or extrinsic.
+to identify $\pmb{\delta} D$ as being physically intrinsic or extrinsic.  Nevertheless, $\pmb{\delta} D$ is referred to as ``intrinsic''  for convenience.
 
@@
 $\langle D\rangle=0$
-to specify the (arbitrary) definition of zero color.  We assign a prior on the ensemble amplitudes of $D$ to break the
-degeneracy $\pmb{\delta} \rightarrow a\pmb{\delta}$, $D \rightarrow a^{-1}D$.  A sign degeneracy in $a$ remains.
-In contrast to $\pmb{\gamma}$, our MCMC chains migrate between these degenerate solutions in  $\pmb{\delta}$.  This
-degeneracy is preserved in the model.
+to specify the (arbitrary in our linear model) definition of zero color.  We assign a prior on the ensemble amplitudes of $D$ to break the
+degeneracy $\pmb{\delta} \rightarrow a\pmb{\delta}$, $D \rightarrow a^{-1}D$: as described
+in \S\ref{model:sec} this prior does not affect physics but aids in the convergence of fitting $D$ and $\pmb{\delta}$ as independent parameters.
+A sign degeneracy in $a$ remains.
+In contrast to $\pmb{\gamma}$, our MCMC chains migrate between sign-degenerate solutions in  $\pmb{\delta}$.  We make
+no attempt to resolve this degeneracy in the model.
 In the running of the Monte Carlo fit, the initial conditions and ranges for
-$\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
-to maintain their correspondence between the two models. 
+$\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ were set to be in the neighborhood of the best fit of Model~I
+to maintain their correspondence between the two models. Our finite MCMC chains do not migrate away from these ranges.
 \color{black}
@@
 are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the reduction of the standard
-deviations of the magnitude residuals $\sigma_X$,
+deviations of the magnitude residuals $\sigma_X$
 \color{red}
-particularly in the $U$ and $B$ bands.
+in the $U$ and $B$ bands.  The   $<1\sigma$ changes in $\pmb{\gamma}$ lead to a slight increase in the 
+ \citetalias{1999PASP..111...63F}
+$R^F$-parameter 68\% credible interval
+from $2.26$--$2.63$ to $2.31$--$2.69$.
 \color{black}
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
+\caption{68\% credible intervals for the global fit Parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
 \end{table}
@@
 
-The significance of the $\pmb{\delta}$ parameters is shown pictorially in
-Figure~\ref{deltacorner:fig}, which shows their posteriors.
-Recall that fixing $\delta_X=0$ reverts this model into the two extrinsic-parameter model of \S\ref{model:sec},
-this null result lies on the 85\%-ile contour.
-Recall that
-the model has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ that results in the bimodal peaks in the distribution.
+The posteriors of the $\pmb{\delta}$ parameters are shown  in
+Figure~\ref{deltacorner:fig}.
+In the full 5-dimensional space,
+the point $\delta_X=0$  lies on the 85\%-ile contour.
+Model~II has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ that results in the bimodal peaks in the distribution.
 To aid in the visualization of the results,
-we break this degeneracy by imposing  that the one supernova with the highest signal-to-noise in $D$ be positive.
+we break this degeneracy by imposing  that the $D$ of the one supernova with the highest signal-to-noise be positive.
 The resulting posterior contours of $\pmb{\delta}$ with this additional
 condition are shown in Figure~\ref{deltacorner:fig}.
-The modes of $\pmb{\delta}$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$.
+The modes of $\pmb{\delta}$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in $UBVRI$ respectively.
+The values of $\delta_X/\delta_U-1$, statistics insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
 
@@
    \caption{Left:  Posterior contours for $\pmb{\delta}$ for Model~II.
-   Right: The same posteriors after imposing that  the one supernova with the highest signal-to-noise has positive value of $D$.
+   Right: The same posteriors after imposing that  the one supernova with  the $D$ of the one supernova with the highest signal-to-noise be positive.
      Lines for $\pmb{\delta}=0$ are overplotted.
@@
 \end{figure}
-
-An alternative visualization of the $\pmb{\delta}$ results can be seen in Figure~\ref{deltaratio:fig}, which
-shows  values of $\delta_X/\delta_U-1$, statistics insensitive to the scaling (including the sign) degeneracy.
 
@@
 mag respectively.
-The range of $B-V$ colors is $> 5$ times larger for the external contribution; variation in $B-V$ color due to the intrinsic term is dwarfed by the extrinsic dust
+The range of $B-V$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
 component.
@@
 \color{black}
+The distributions for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, 
+$E_{\gamma^1}(B-V)$, and
+$E_{\delta}(B-V)$ for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
+
 The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are
@@
 This has two important implications:
-First, while in principle a single physical color effect can affect both intrinsic and extrinsic parameters, from the correlations
+First, while the degeneracies in the model could allow a single physical color effect to be
+distributed between both intrinsic and extrinsic parameters, from the correlations
 there is no evidence
 that this occurs.
-Second, the intrinsic term is not a second-order extrinsic correction.
-The distributions for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, 
-$E_{\gamma^1}(B-V)$, and
-$E_{\delta}(B-V)$ for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
+Second, the intrinsic term cannot be attributed to non-linearity that is inherent to the broad-band extinction in dust models, since
+in that case a correlation between the  $k$'s and $D$ would be expected.
 
@@
 of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
-(These are the same values found in the results of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.)
+These results are similar to those of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.
 \color{red}
@@
 \color{red}
-The analysis is evaluated using simulated datasets.
-For one set of tests, we realize 20 random realizations of data with input  parameters equal to the median values found in
+The significance of the results is evaluated using simulated datasets.
+For one set of tests, we realize 50 random realizations of data with input  parameters equal to the median values found in
 \S\ref{model:sec} and the same noise as our data.  The input values of $\pmb{\delta}$ are set to zero.
+In Figure~\ref{pvalues_delta2:fig}, the squared amplitudes  $\pmb{\delta}^2$
+from the null realizations are compared with that of our fit to the data.  Depending on the choice either the  $-1$, 0, or $1$-sigma
+value, the data value is at the 90--98\%-ile.  Contrast these $p$-values with the 85\%-ile contour on which $\pmb{\delta}=0$ lies
+in the Bayesian posterior.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.9in]{output25_sim_null/pvalues_delta2.pdf} 
+  \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
+            \caption{ The squared length $\pmb{\delta}^2$ (left) and relative length perpendicular to the plane defined by $\pmb{\gamma}$ $\delta_\perp^2/\delta^2$ for 50 independent simulated data sets with input $\delta=0$.
+The fits
+            are ordered by the median value, the null realizations are shown in blue and the result from our data is shown in red.
+            \label{pvalues_delta2:fig}}
+\end{figure}
+
+The significance of the close projection of $\pmb{\delta}$ onto the plane defined by the $\pmb{\gamma}$'s is shown
+in  Figure~\ref{pvalues_delta2:fig}, which plots the relative amplitude projected out of the plane $\delta_\perp^2/\delta^2$ for the null realizations
+and our data.  Our data has smaller value than all the realizations for $-1$, 0, or $1$-sigma values.  This alleviates
+the concern that our model and sampling spuriously produce $\pmb{\delta}$ closely aligned with the $\pmb{\gamma}$--plane, i.e.\
+the small  $\delta_\perp^2/\delta^2$ of our data is not expected to be due to noise at 98\%.
+
 The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
-biases in the best fit value, and is shown in Figure~\ref{simnulldelta:fig}.  The correlations between the parameters
+biases in the best fit value.  The stack of   $\pmb{\delta}$ is shown in Figure~\ref{simnulldelta:fig}.  The correlations between the parameters
 and the bimodality of each posterior results in biases in the stack, with
@@
    \centering
-   \includegraphics[width=5.2in]{output25_sim_null/delta_corner.pdf} 
+   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
             \caption{Stacked $\pmb{\delta}$ posterior contours for 20 independent simulated data sets with input $\pmb{\delta}=0$.
@@
 \end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.9in]{output25_sim_null/pvalues_delta2.pdf} 
-  \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
-            \caption{ $\pmb{\delta}^2$ $\delta_\perp^2/\delta^2$ for 20 independent simulated data sets with input $\delta=0$.
-            \label{pvalues_delta2:fig}}
-\end{figure}
-
 We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.

### 2017-07-20 apj.tex
a study plot and removal of comment

@@
 \color{red}
-in the $U$ and $B$ bands.  The   $<1\sigma$ changes in $\pmb{\gamma}$ lead to a slight increase in the 
- \citetalias{1999PASP..111...63F}
-$R^F$-parameter 68\% credible interval
-from $2.26$--$2.63$ to $2.31$--$2.69$.
+in the $U$ and $B$ bands.
 \color{black}
@@
 \end{tabular}
-\caption{68\% credible intervals for the global fit Parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
+\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
 \end{table}
@@
 In the full 5-dimensional space,
-the point $\delta_X=0$  lies on the 85\%-ile contour.
-Model~II has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ that results in the bimodal peaks in the distribution.
+the point $\delta_X=0$, i.e.\ no effect on magnitude by a third parameter,  lies on the 85\%-ile contour.
+Model~II has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ degeneracy that results in a bimodal posterior.
 To aid in the visualization of the results,
 we break this degeneracy by imposing  that the $D$ of the one supernova with the highest signal-to-noise be positive.
-The resulting posterior contours of $\pmb{\delta}$ with this additional
+The new posterior contours of $\pmb{\delta}$ with this added
 condition are shown in Figure~\ref{deltacorner:fig}.
-The modes of $\pmb{\delta}$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in $UBVRI$ respectively.
-The values of $\delta_X/\delta_U-1$, statistics insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
+The shapes of the new $\pmb{\delta}$ posteriors are somewhat distorted compared to the original.
+Despite its relatively strong signal-to-noise, the original posterior for $D$ for the selected supernova does have significance on both sides of zero,
+resulting in changes in the shape of the $\pmb{\delta}$ posteriors when  $D$ to forced to be positive.   
+The modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in for $X=UBVRI$ respectively.
+The values of $\delta_X/\delta_U-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
 
@@
      \includegraphics[width=2.8in]{output25/delta_corner_flipped.pdf}
-   \caption{Left:  Posterior contours for $\pmb{\delta}$ for Model~II.
-   Right: The same posteriors after imposing that  the one supernova with  the $D$ of the one supernova with the highest signal-to-noise be positive.
+   \caption{Left:  Model~II posterior contours for $\pmb{\delta}$.
+   Right: The same posteriors after imposing that $D$ of the one supernova with highest signal-to-noise be positive.
      Lines for $\pmb{\delta}=0$ are overplotted.
@@
       \includegraphics[width=5.2in]{output25/deltaratio.pdf}
-   \caption{Median values of $\delta_X/\delta_U$ in the 5 bands and corresponding 68\% intervals for for Model~II.
+   \caption{Model~II median values  and corresponding 68\% intervals for $\delta_X/\delta_U$ in the 5 bands.
    A dotted line at zero is shown for reference.
@@
 The distributions of both sources of color excess $E(B-V)$ and
- $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
+ $E_\delta(B-V) \equiv   (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
  (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
@@
 The range of $B-V$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
-component.
+component.   The $E_\delta(B-V)$ standard deviation is comparable to its measurement uncertainty per-supernova, showing that
+the significance of $\pmb{\delta}$
+is drawn from the ensemble of objects and
+would be difficult to deduce from the color excess of individual supernovae.
 
@@
       \caption{Left: Ideograms of the external $E(B-V)$ and
-   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
+   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
    Right: Ideogram and histogram of the medians of $E_\delta(B-V)$ on an enlarged scale.
@@
 
-The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are
+The correlation coefficients between the ``intrinsic''  ($A_{\delta U}$) and ``extrinsic''
+($E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$)  parameters are
 \color{purple}
-not statistically significant.
-\color{black}
-This has two important implications:
-First, while the degeneracies in the model could allow a single physical color effect to be
-distributed between both intrinsic and extrinsic parameters, from the correlations
-there is no evidence
-that this occurs.
-Second, the intrinsic term cannot be attributed to non-linearity that is inherent to the broad-band extinction in dust models, since
-in that case a correlation between the  $k$'s and $D$ would be expected.
+consistent with zero.
+Their independence implies that a single physical parameter is not being artificially attributed to two
+model parameters.  One could have expected this to occur since our linear model does not precisely
+describe broad-band magnitudes that are non-linear with respect to dust parameters. A strong
+correlation between the parameters would of complicated any claims of the detection of a third independent supernova parameter.
+\color{black}
 
@@
 \color{red}
-The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$ for better signal-to-noise) can be expressed as
+The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$) can be expressed 
+in terms of the $a$ and $b$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
 \color{black}
@@
 \end{equation}
-where the residual vectors are 
+where the residual vectors
 \begin{align}
@@
 \end{align}
+are perpendicular to $a$ and $b$.
 The $\pmb{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
@@
 of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
-These results are similar to those of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.
 \color{red}
-The $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
+ $\pmb{\delta}$ too
+has a significant projection onto the dust plane, as the $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
+The transformation yields
+a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, slightly shifted higher relative to the results of Model~I.
 \color{black}
@@
 The significance of the results is evaluated using simulated datasets.
-For one set of tests, we realize 50 random realizations of data with input  parameters equal to the median values found in
-\S\ref{model:sec} and the same noise as our data.  The input values of $\pmb{\delta}$ are set to zero.
-In Figure~\ref{pvalues_delta2:fig}, the squared amplitudes  $\pmb{\delta}^2$
-from the null realizations are compared with that of our fit to the data.  Depending on the choice either the  $-1$, 0, or $1$-sigma
-value, the data value is at the 90--98\%-ile.  Contrast these $p$-values with the 85\%-ile contour on which $\pmb{\delta}=0$ lies
-in the Bayesian posterior.
+For one set of tests, we realize 50 random realizations of data with input  parameters equal to the median values of the 
+parameter posteriors found in
+\S\ref{model:sec}, and using the same noise as our data.  The input $\pmb{\delta}$-vector is set to zero.
+Figure~\ref{pvalues_delta2:fig} shows results of fits of these null-realizations in comparison to the results using the real data.
+The influence of the third parameter on magnitudes is measured by the squared amplitude  $\delta^2$.
+Depending on the choice between the  $-1$, 0, or $1$-sigma
+value of  $\delta^2$, the data value is in the largest 90--98\%-ile.  Recall that in the Bayesian posterior
+$\pmb{\delta}=0$ lies on the 85\%-ile contour.
 
@@
   \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
-            \caption{ The squared length $\pmb{\delta}^2$ (left) and relative length perpendicular to the plane defined by $\pmb{\gamma}$ $\delta_\perp^2/\delta^2$ for 50 independent simulated data sets with input $\delta=0$.
+            \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\pmb{\gamma}$, $\delta_\perp^2/\delta^2$, for 50 independent simulated data sets with input $\delta=0$.
 The fits
@@
 
-The significance of the close projection of $\pmb{\delta}$ onto the plane defined by the $\pmb{\gamma}$'s is shown
-in  Figure~\ref{pvalues_delta2:fig}, which plots the relative amplitude projected out of the plane $\delta_\perp^2/\delta^2$ for the null realizations
-and our data.  Our data has smaller value than all the realizations for $-1$, 0, or $1$-sigma values.  This alleviates
-the concern that our model and sampling spuriously produce $\pmb{\delta}$ closely aligned with the $\pmb{\gamma}$--plane, i.e.\
-the small  $\delta_\perp^2/\delta^2$ of our data is not expected to be due to noise at 98\%.
-
-The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
-biases in the best fit value.  The stack of   $\pmb{\delta}$ is shown in Figure~\ref{simnulldelta:fig}.  The correlations between the parameters
-and the bimodality of each posterior results in biases in the stack, with
-modes at $\mp 0.67$, $\pm0.14$, $\pm0.13$,  $\mp0.03$, $\mp0.52$.
-The input length of $\pmb{\delta}$ is zero, therefore any statistical
-fluctuation biases the value high.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
-            \caption{Stacked $\pmb{\delta}$ posterior contours for 20 independent simulated data sets with input $\pmb{\delta}=0$.
-            \label{simnulldelta:fig}}
-\end{figure}
-We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
-Ten realizations of simulated data are generated based on the data covariances, and then analyzed separately.   The posteriors of the ten realizations
-are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
+Figure~\ref{pvalues_delta2:fig} also shows the 
+relative projection of $\pmb{\delta}$  perpendicular to the plane defined by the $\pmb{\gamma}$'s, $\delta_\perp^2/\delta^2$,
+for the 50 null realizations
+and our data.  The data gives smaller value than all the realizations for $-1$, 0, or $1$-sigma values.  
+Our model and analysis are unlikely to spuriously produce a $\pmb{\delta}$ as closely aligned with the $\pmb{\gamma}$--plane
+as derived from our data, as its small  $\delta_\perp^2/\delta^2$  is not expected from a null signal at $>98$\%.
+
+Parameter biases that arise as part of our analysis methodology are measured through simulation.
+We realize 50 random realizations of data with input  parameters equal to the median values found in
+this Section, except for $\pmb{\delta}$ which is assigned the modes presented earlier, and the same noise as our data.
+The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.
+The stack is sensitive to
+biases in the best fit value.
+The stack of  $\pmb{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias in the
+modes from the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ relative to the stacked modes $(-1.10, -0.98, -0.41, -0.09, 0.40)$
+that is smaller than the statistical uncertainty of a single analysis.
+The posterior stacks for the other global parameters 
+are shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
 relative to the statistical uncertainties. 
@@
    \centering
+   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
+            \caption{Stacked $\pmb{\delta}$ posterior contours for 50 independent simulated data sets with input $\pmb{\delta}=0$.
+            The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
+            \label{simdelta:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
    \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $U$ band of ten independent simulated data sets.
-Lines show the values of the input values.
+The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
             \label{simglobal1:fig}}
@@
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $B$ band of ten independent simulated data sets.
-Lines show the values of the input values.
+The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
  \label{simglobal2:fig}}
@@
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $V$ band of ten independent simulated data sets.
-Lines show the values of the input values.
+The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
 \label{simglobal3:fig}}
@@
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $R$ band of ten independent simulated data sets.
-Lines show the values of the input values.
+The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
 \label{simglobal4:fig}}
@@
             \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $I$ band of ten independent simulated data sets.
-Lines show the values of the input values.
+The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
  \label{simglobal5:fig}}
@@
 
-\color{black}
 \subsection{Physical Motivation}
 
-Our third supernova parameter does not have a monotonic influence on supernova magnitudes as a function
-of wavelength but rather has an inflection in the $V$ band.  In addition, red $B-V$ colors imply brighter magnitudes
-for this component.  Absorption and re-emission of light
-over broad bands are the most obvious candidate for producing this behavior.
-
-\color{red}
-Speculate on third parameter.
-\color{black}
-
-Although the $D$ parameter has been referred to as ``intrinsic'', due to its placement in the model and the correspondence
-of the $k$ parameters with those of extrinsic two-parameter dust models, the analysis cannot quantitatively distinguish
-whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
-
-We stress that our $\pmb{\delta}$ vector does not capture the full behavior of the observable effects of the $D$ parameter, but rather only
-the contribution perpendicular to the $\pmb{\gamma}$ vectors.
+A straightforward explanation for the third parameter is that it describes the absorption due to some form of dust. 
+Supernova light may encounter two types
+of dust, an interstellar form  that resembles the \citetalias{1999PASP..111...63F} model, and a second
+circumstellar dust that deviates from the model and can produce low visual-to-selective extinction
+\citep{2008ApJ...686L.103G}.
+The $D$ and $\pmb{\delta}$ parameters could be attributed to the second form form of dust.
+Qualitatively,  the decrease in magnitude change toward redder wavelengths, seen in Figure~\ref{deltaratio:fig}, matches the 
+expectation for dust.  The projection of  $\pmb{\delta}$ onto the plane expected by dust is significant at the $>98$\% level.  However, we
+lack the signal-to-noise to show that  all the  $\delta_X$ share the same sign, indeed the posterior median of $\delta_I/\delta_U$ is negative.
+Confining ourselves to the 98\% of   $\pmb{\delta}$ that lies on the dust plane, associating 
+$D$ with $A_V$ would imply an unphysical $R^F=0.5$.
+
+Alternatively, the $D$ and $\pmb{\delta}$ parameters can represent an added contribution to a dust law, rather than alone
+describing a form of dust.  The extra degree-of-freedom could be associated with the skewness in the distribution of dust grains, as an increase of smaller dust grains
+can flatten extinction in the red and enhanced steepness in the UV relative to standard dust models  \citep[Figure~3 in][]{2015ApJ...807L..26G,
+2017ApJ...836...13H}.
+
+Based on the above models, a dust-based identification and explanation of the extra color parameter would be greatly enhanced with
+extended wavelength coverage into the UV.
 
@@
 We thank the STAN team for providing the statistical tool without which this analysis would not have been possible,
-and Michael Betancourt specifically for his helpful guidance.  We thank Danny Goldstein for useful discussions.
+and Michael Betancourt specifically for his helpful guidance.  We thank Danny Goldstein and
+Xiaosheng Huang for useful discussions.
 We thank Dan Birchall for observing assistance, the technical and

### 2017-07-20 view25.py

@@ -545,8 +545,6 @@ plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
 
-wefwe
-
 bins = numpy.arange(-0.1,0.121,0.01)
 # # plt.hist(fit['Delta'].flatten(),bins,label='ideogram',normed=True,alpha=0.5)
 # # plt.hist(numpy.median(fit['Delta'],axis=0),bins,label='median',normed=True,alpha=0.5,width=0.01)
@@ -1091,12 +1089,28 @@ ax.errorbar(numpy.arange(5),y,yerr=[y-ymin,ymax-y],fmt='o')
 ax.xaxis.set_major_formatter(FuncFormatter(format_fn2))
 ax.xaxis.set_major_locator(MaxNLocator(integer=True))
 ax.axhline(0,linestyle=':')
-ax.set_xlim((-0.5,4.5))
 ax.set_xlabel(r'Band $X$')
+ax.set_xlim((-0.5,4.5))
 ax.set_ylabel(r'$\frac{\delta_X}{\delta_U}$')
 ax.set_ylim((-1.5,1.2))
 plt.tight_layout()
 pp = PdfPages(dirname+'/deltaratio.pdf')
+plt.savefig(pp,format='pdf')
+pp.close()
+plt.close()
+
+efflam = numpy.array([ 3693.16777627,  4369.37505509,  5287.48667023,  6319.19906153,7610.89305298])
+(y, ymin, ymax) = numpy.percentile(fit['rho1']/fit['rho1'][:,0][:,None],(50,50-34,50+34),axis=0)
+fig = plt.figure()
+ax = fig.add_subplot(111)
+ax.errorbar(1e4/efflam,y,yerr=[y-ymin,ymax-y],fmt='o')
+ax.axhline(0,linestyle=':')
+
+ax.set_xlabel(r'$\lambda^{-1}$')
+ax.set_ylabel(r'$\frac{\delta_X}{\delta_U}$')
+ax.set_ylim((-1.5,1.2))
+plt.tight_layout()
+pp = PdfPages(dirname+'/deltaratiov2.pdf')
 plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()

### 2017-07-25 apj.tex
more edits and another simulation for x1

@@
 SN~Ia broadband magnitudes and colors are correlated with
-spectral features: equivalent widths and line positions are considered as statistics localized in wavelength whose measurements are insensitive to variations in
-broadband colors.
-These intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion,
-which in this section is not yet associated with a parameter. The intrinsic magnitudes are then
-modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes.
+spectral features: equivalent widths and line positions are considered in the model because their localization in wavelength
+makes their values insensitive to 
+broadband color variations.
+These intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
+The per-supernova intrinsic magnitudes are then
+modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes that are subsequently measured by the observer.
 
 \subsection{Model}
-We assume 
-that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
-on the
+In what is what is referred to as Model~I, we assume 
+that  peak intrinsic $UBVRI$ magnitudes of a supernova are linearly dependent
+on its
  equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
-$EW_{Ca}$, $EW_{Si}$,
-and $\lambda_{Si}$ the wavelength of the minimum of 
-the SiII$\lambda6355$ feature:
+$EW_{Ca}$ and $EW_{Si}$,
+and the wavelength of the minimum of 
+the SiII$\lambda6355$ feature $\lambda_{Si}$:
 these spectral features are associated with SN~Ia  spectroscopic diversity  
@@
 $EW_{Si}$, at peak brightness
-\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
-Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
+\citep{2008A&A...492..535A, 2011A&A...529L...4C}. On top of these feature-dependent magnitudes, intrinsic dispersion
+gives each supernova a magnitude contribution drawn from a Normal distribution with a parameterized covariance matrix
 $C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
-to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
-The observed magnitudes are linearly dependent on the
+to capture band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
+flux data to luminosity.
+The apparent magnitudes are the sum of the intrinsic magnitudes plus additional terms that are linearly dependent on the
 extrinsic-color parameters $k_0$ and $k_1$.  
@@
 parameters $k_0$ and $k_1$ are not directly associated
-with observables but are rather drawn from the set of peak magnitudes.
-The model 
-likelihood density
-is written as
+with observables but rather are inferred as part of the analysis.
+The
+likelihood density for the described model
+is
 \begin{equation}
@@
 \end{equation}
-The global parameters $c_X$, $\alpha_i$, $\beta_i$,  and $\eta_i$,  are the intercepts and slopes of the linear relationships that
+The global parameter vectors
+$\mathbf{c}$ (where $\mathbf{c}=(c_U, c_B, c_V, c_R, c_I) $),
+$\pmb{\alpha}$, $\pmb{\beta}$,  and $\pmb{\eta}$,  are the intercepts and slopes of the linear relationships that
 relate intrinsic magnitudes with the spectral-feature parameters.
-The global parameters $\pmb{\gamma}^0$, $\pmb{\gamma}^1$  are the slopes that connect the extrinsic-color
-parameters to observed magnitudes.
+The global parameter vectors $\pmb{\gamma}^0$, $\pmb{\gamma}^1$  are the slopes that connect the extrinsic-color
+parameters to apparent magnitudes.
 
 \color{purple}
-We impose
+The model as written  has degeneracies that need to be constrained.
+The model does not specify the absolute magnitude nor the intrinsic color of a supernova that has no extrinsic color contribution,
+so we fix them to the samples by imposing
 \begin{equation}
@@
 \end{equation}
-These conditions specify the definition of absolute magnitude and zero color relative to which the color excess is measured:
-in our linear model these values are otherwise unconstrained.
-The model contains terms like $\pmb{\gamma} k$, which lead to the degeneracy $\pmb{\gamma} \rightarrow a\pmb{\gamma}$, $k \rightarrow a^{-1} k$.
-While the physical results are independent of this scaling, we impose a prior on the rms of $k$ to aid the convergence during model fitting.
-This prior does not specify the sign of $a$, which leaves a degeneracy.  As will be seen, the signal-to-noise in $\pmb{\gamma}$ is sufficiently
-high that our finite MCMC chains do not migrate between the degenerate solutions; for convenience
-we impose 
+The model contains products of latent parameters,
+like $\pmb{\gamma} k$, which lead to the degeneracy $\pmb{\gamma} \rightarrow a\pmb{\gamma}$, $k \rightarrow a^{-1} k$.
+To aid in the convergence of $\pmb{\gamma}$ and $k$ we impose a prior on the rms of $k$, but
+our physical interpretations are independent of this scaling.
+This prior does not specify the sign of $a$, which leaves a parity degeneracy.  As will be seen, the signal-to-noise in $\pmb{\gamma}$ is sufficiently
+high that our finite MCMC chains do not migrate between the degenerate solutions so practically this is not a problem; for convenience
+we thus impose 
 \begin{equation}
@@
 \end{equation}
-to exclude degenerate posterior space
-associated
-with the $\pm$ sign.
-
-The combinations $\pmb{\gamma}^0$--$k_0$ and $\pmb{\gamma}^1$--$k_1$ are degenerate with
-each other under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
+%to exclude degenerate posterior space
+%associated
+%with the $\pm$ sign.
+As  in mixture models, the combinations $\pmb{\gamma}^0 k_0$ and $\pmb{\gamma}^1 k_1$ terms are degenerate under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
 we break that degeneracy  by setting consistent initial conditions that succeed in keeping indices consistent over all analysis chains.  
@@
 
-For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
-color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
-$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level independent parameters.
-
-Having the intrinsic dispersion, $C_c$, as fit parameters seemingly introduces degeneracy in the model, as magnitude and color variation
+There remain degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
+ $\pmb{\gamma}^0 \rightarrow \pmb{\gamma}^0  + \epsilon_{\gamma^0}$, $\pmb{\gamma}^1 \rightarrow \pmb{\gamma}^1 + \epsilon_{\gamma^1}$
+ under the condition
+$$
+\epsilon_\Delta  +  \epsilon_{\gamma^0} k_0+  \epsilon_{\gamma^1} k_1=0,
+$$
+i.e.\ shifts in the global coefficients $\pmb{\gamma}$ can be compensated by shifts in $\pmb{\Delta}$ for each supernova while maintaining 
+$\langle \Delta \rangle=0$.
+Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
+$\pmb{\alpha} \rightarrow \pmb{\alpha} - \pmb{\gamma} \epsilon$, $\mathbf{c} \rightarrow \mathbf{c} + \langle EW_{Ca}\rangle \epsilon$, i.e. the
+linear external terms can leak into the linear spectral feature corrections.
+These degeneracies are not broken within the model, but rather are constrained by the priors, in which the
+per-supernova parameters
+$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.
+
+The parameterized intrinsic dispersion, $C_c$, seemingly introduces degeneracy in the model, as magnitude and color variation
 ascribed to $\Delta$, $\pmb{\gamma}^0 k_0$, and $\pmb{\gamma}^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
@@
 in all elements of the covariance matrix, which is disfavored for the Bayesian prior selected for $C_c$.
+
+For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
+color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
+$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level independent parameters.
 
@@
  the other parameters.
-
-There remain degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
- $\pmb{\gamma}^0 \rightarrow \pmb{\gamma}^0  + \epsilon_{\pmb{\gamma}^0}$, $\pmb{\gamma}^1 \rightarrow \pmb{\gamma}^1 + \epsilon_{\pmb{\gamma}^1}$under the condition
-$$
-\epsilon_\Delta  +  \epsilon_{\pmb{\gamma}^0} k_0+  \epsilon_{\pmb{\gamma}^1} k_1=0,
-$$
-i.e.\ shifts in the global coefficients $\pmb{\gamma}$ can be compensated by shifts in $\Delta$ for each supernova while maintaining 
-$\langle \Delta \rangle=0$.
-Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
-$\alpha \rightarrow \alpha - \pmb{\gamma} \epsilon$, $c \rightarrow c + \langle EW_{Ca}\rangle \epsilon$, i.e. the
-linear external terms can leak into the linear spectral feature corrections.
-These degeneracies are not broken within the model, but rather are constrained by the priors, in which the
-per-supernova parameters
-$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.  It is important to emphasize that the latent parameters $k$ and $\Delta$
-are non-trivially specified by these priors.
-
-We refer to this model as Model~I.
 
@@
    \includegraphics[width=5.2in]{output11/coeff0.pdf} 
-            \caption{Model~I posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $U$ band.
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $U$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
             projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ are shown for reference --
-            in many cases they are outside the range of the plot.
+            enclosed probability.  Lines for zero value for $\alpha_U$, $\beta_U$, $\eta$, $\gamma_U^0$, $\gamma_U^1$, and $\sigma_U$ are shown for reference --
+            in most cases they are outside the range of the plot.
             \label{global1:fig}}
@@
    \includegraphics[width=5.2in]{output11/coeff1.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $B$ band, from Model~I.
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $B$ band.
  \label{global2:fig}}
@@
    \includegraphics[width=5.2in]{output11/coeff2.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $V$ band, from Model~I.
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $V$ band.
  \label{global3:fig}}
@@
       \includegraphics[width=5.2in]{output11/coeff3.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $R$ band, from Model~I.
+            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $R$ band.
  \label{global4:fig}}
@@
          \includegraphics[width=5.2in]{output11/coeff4.pdf} 
-            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $I$ band, from Model~I.
+            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $I$ band.
  \label{global5:fig}}
@@
 are shown in Figure~\ref{residual:fig}. 
-There is no evidence of a catastrophic fit nor of extreme
+There is no evidence of a catastrophically poor model predictions nor of extreme
 outlying data.
@@
 We do not detect a significant association between
-$\lambda_{Si}$ and color with this model.
+$\lambda_{Si}$ and color.
 
@@
 
-Non-trivial residual magnitude dispersions are captured in $C_c$.  The diagonal elements are captured by the $\sigma$ parameters;
-the residual intrinsic dispersion ranges from
+Non-trivial residual magnitude dispersions are captured in $C_c$.  The square
+root of the diagonal elements are denoted as $\sigma$, which
+range from
 $\sim 0.01$ to 0.06 mag, significantly smaller
@@
 Running an analysis assuming no intrinsic dispersion (replacing the probabilistic intrinsic magnitudes in Eqn.~\ref{ewsiv:eqn}
-with a strict equality), we find significant shifts in the inferred slopes and smaller statistical uncertainties.
+with a strict equality), we find significant shifts in all slope parameters  and smaller statistical uncertainties.
 \color{black}
@@
 Our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
-We now examine this in more depth using the intrinsic--extrinsic model of \S\ref{model2:sec}.
+We now examine this in more depth using the intrinsic--extrinsic Model~II of \S\ref{model2:sec}.
 The correlation between $EW_{Si}$ and the SALT2 $x_1$ light-curve shape parameter is verified

### 2017-07-25 model25_x1.py

@@ -1,0 +1,191 @@
+#!/usr/bin/env python
+
+import pickle
+import cPickle
+import numpy
+import pystan
+import sivel
+import matplotlib.pyplot as plt
+import corner
+
+# provide stan 3 eigenvectors with respect to try to align delta vector
+f = open('temp11.pkl','rb')
+(fit,_) = pickle.load(f)
+
+gamma0 = numpy.median(fit['gamma'],axis=0)
+gamma1 = numpy.median(fit['rho1'],axis=0)
+gamma0_cov = numpy.cov(fit['gamma'],rowvar=False)
+gamma1_cov = numpy.cov(fit['rho1'],rowvar=False)
+
+
+_, gamma0_ev = numpy.linalg.eigh(gamma0_cov)
+
+# print gamma0_ev[:,0]
+
+gamma0_eval = numpy.array(fit['gamma'])
+for i in xrange(gamma0_eval.shape[0]):
+   for j in xrange(5):
+      gamma0_eval[i,j]=numpy.dot(fit['gamma'][i,:], gamma0_ev[:,j])
+
+gamma0_min = numpy.min(gamma0_eval,axis=0)-0.05
+gamma0_max = numpy.max(gamma0_eval,axis=0)+0.05
+
+# for i in xrange(5):
+#    plt.hist(gamma0_eval[:,i])
+#    plt.show()
+
+_, gamma1_ev = numpy.linalg.eigh(gamma1_cov)
+
+gamma1_eval = numpy.array(fit['rho1'])
+for i in xrange(gamma1_eval.shape[0]):
+   for j in xrange(5):
+      gamma1_eval[i,j]=numpy.dot(fit['rho1'][i,:], gamma1_ev[:,j])
+
+gamma1_min = numpy.min(gamma1_eval,axis=0)-0.05
+gamma1_max = numpy.max(gamma1_eval,axis=0)+0.05
+
+# for i in xrange(5):
+#    plt.hist(gamma1_eval[:,i])
+#    plt.show()
+
+
+gamma0median = numpy.median(gamma0_eval,axis=0)
+gamma1median = numpy.median(gamma1_eval,axis=0)
+
+fit=None
+
+m = numpy.zeros((2,5))
+m[0]=gamma0
+m[1]=gamma1
+m=m.T
+
+q, r = numpy.linalg.qr(m,mode='complete')
+q=q.T
+
+# two color parameter model
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
[…]

### 2017-07-25 apj.tex
writing more stuff

@@
 
-\color{purple}
-For brevity, we do not present here the analysis of simulated data used to validate and quantify bias in our results.
-The simulation tests in \S\ref{model2:sec} are representative for both Model~1 of this Section and Model~2 of the subsequent section.
-\color{black}
-
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
@@
 \end{equation}
-approximately describes dust models \citep[e.g][]{1989ApJ...345..245C}.
+approximately describes dust models \citep[e.g.][]{1989ApJ...345..245C}.
 For the case of
-$R^F=2.5$ and $A^F_V=0.1$,
-and the measurement of the SALT2
+$R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
 \citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
 gives
-$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
-The $F$ superscript is added to distinguish parameters of the \citetalias{1999PASP..111...63F} model.
+$\mathbf{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\mathbf{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
+The $F$ superscript distinguishes parameters of the \citetalias{1999PASP..111...63F} model.
 Over the ranges of
@@
 \color{red}
-for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error amplitude in Eqn.~\ref{f99:eqn} is $<0.008$ mag.
-\color{black}
-
-Our model can be expressed as
+for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in Eqn.~\ref{f99:eqn} has amplitude $<0.008$ mag.
+\color{black}
+
+The extrinsic contribution to our model can be re-expressed to have a similar parameterization
 \begin{equation}
-A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
+A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V),
 \end{equation}
-Our median-fit values for the $\pmb{\gamma}$ coefficients,
+where $E_{\gamma^i}(B-V) \equiv  (\gamma^i_B-\gamma^i_V)k_i$.
+Our median-fit values for the $\pmb{\gamma}$ coefficients are
 %---- fitz11.py
-$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
-$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
+$\frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V}  =(4.80 ,   3.89,   2.89,   2.22,   1.59)$ and
+$ \frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V}=(-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71)$.
 %----
-can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
+
+Our model $\gamma$-based vectors can be written in terms of the 
+dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\mathbf{a}$ and $\mathbf{b}$.
 The result is
@@
 \begin{pmatrix}
- \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
-\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
+ \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
+\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} 
 \end{pmatrix}=
@@
 \begin{pmatrix}
-a(X) \\
-b(X)
+\mathbf{a} \\
+\mathbf{b}
 \end{pmatrix}+
 \begin{pmatrix}
-\vec{\epsilon}_{\gamma^0} \\
-\vec{\epsilon}_{\gamma^1}
+\pmb{\epsilon}_{\gamma^0} \\
+\pmb{\epsilon}_{\gamma^1}
 \end{pmatrix},
@@
 \begin{split}
-\vec{\epsilon}_{\gamma^0} &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
-\vec{\epsilon}_{\gamma^1} & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
+\pmb{\epsilon}_{\gamma^0} &=(0.06, -0.07, -0.07,  0.07, 0.02), \\
+\pmb{\epsilon}_{\gamma^1} & =(-0.06, 0.16, -0.22, 0.33, -0.26)
 \end{split}
@@
 quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.
-
 This result indicates that
-the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.
-That is to say, with no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
+the allowed variations in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to near-parallel 2-dimensional
+planes within
+the 5-dimensional magnitude space.
+Wiith no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
 2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.
 
-The above result is visualized in Figure~\ref{plane:fig}, which  shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
-of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
-and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\pmb{\gamma}$ vectors are chosen to intersect the origin.
+The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the $UVI$-subspace two perspectives (left and right columns)
+of the unit vectors corresponding to $\pmb{\gamma}^0$ and  $\pmb{\gamma}^1$ of our model (solid lines),
+and $\mathbf{a}$, $\mathbf{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\pmb{\gamma}$ vectors are chosen to intersect the origin.
 The two perspectives show that while the four vectors point in different directions for each band combination,
-they are almost coplanar in $UVI$, and close to coplanar in $BVR$.  The $a$ and $b$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
-vectors are bases for almost the same plane in the 5-dimensional color space, and can be transformed between themselves through rotation.
+they are almost coplanar in $UVI$ (they are slightly less coplanar in $BVR$).  The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
+vectors span near-parallel planes in the 5-dimensional color space, and hence each pair can be almost entirely expressed in  terms of
+the other pair.
 
@@
    The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
-   in the directions of  $a(X)$, $b(X)$; the only possible magnitudes possible are confined to the plane that contains both.
+   in the directions of  $\mathbf{a}$, $\mathbf{b}$; the only possible magnitudes possible are confined to the plane that contains both.
    The perspective on the right visually show that all four vectors are nearly coplanar.  
-   The combination $a(X)+b(X)/2.44$ is shown in the dotted red
+   The combination $\mathbf{a}+\mathbf{b}/2.44$ is shown in the dotted red
    line: it is almost perfectly superimposed on $\pmb{\gamma}^0$.
@@
 
-When fixing the origin of $\pmb{\gamma}$ to zero, the $\pmb{\gamma}$ vectors are found to be coplanar with $a$ and $b$.
-However the linear model does not specify zero dust so the origin of gamma is unspecified.
-The general result is that the magnitude planes of the linear and dust models are parallel.
-Color changes are consistent between the two models but there is no specification of the relation between $k^0$ and $k^1$ with $A_V$ and $E(B-V)$.
-
-A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
-the vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.  Suppose that the data were described by a dust model.  Then a \citetalias{1999PASP..111...63F}  dust model 
-can be written as 
+%When fixing the origin of $\pmb{\gamma}$ to zero, the $\pmb{\gamma}$ vectors are found to be coplanar with $\mathbf{a}$ and $\mathbf{b}$.
+%While the  $\gamma$ vectors define a plane,  is unspecified.
+%The linear model does not specify zero dust so the origin of the $\gamma$'s is unspecified.
+%The general result is that the magnitude planes of the linear and dust models are parallel.
+%Color changes are consistent between the two models but there is no specification of the relation between $k^0$ and $k^1$ with $A_V$ and $E(B-V)$.
+
+%The dust model expressed in Eqn.~\ref{f99:eqn} can be reparameterized as
+%\begin{equation}
+%A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
+%\label{f99:eqn}
+%\end{equation}
+%where $R=A_V/E(B-V)$.
+
+Suppose that the data were due to a dust model with constant $R \equiv A_V/E(B-V)$.
+The  $A_V$ and $E(B-V)$ parameters of the dust model in Eqn.~\ref{f99:eqn} would then be correlated.
+An alternative parameterization 
+\begin{equation}
+A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
+\end{equation}
+
+A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models.
+These determine the choice of directions of
+the vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
+and so the $\gamma$'s
+
+   Then a \citetalias{1999PASP..111...63F}  dust model 
+can be written in a new basis
 %To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
@@
 \end{equation}
-with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.
+with the parameters $\kappa_1$ and $\kappa_2$ parameterizing the directions of the two new basis vectors.
 The vector $a(X)+\kappa_1 b(X)$ represents extinction that can occur with fixed $R^F_0=1/\kappa_1$ and unconstrained $\kappa_2$.
@@
 The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$) can be expressed 
-in terms of the $a$ and $b$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
+in terms of the $\mathbf{a}$ and $\mathbf{b}$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
 \color{black}
@@
 \begin{pmatrix}
- \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
-\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} \\
+ \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
+\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} \\
 \frac{\delta_X}{\delta_U} \\
@@
 \begin{pmatrix}
-a(X) \\
-b(X)
+\mathbf{a} \\
+\mathbf{b}
 \end{pmatrix}+
 \begin{pmatrix}
-\vec{\epsilon}_{\gamma^0} \\
-\vec{\epsilon}_{\gamma^1} \\
-\vec{\epsilon}_{\delta}
+\pmb{\epsilon}_{\gamma^0} \\
+\pmb{\epsilon}_{\gamma^1} \\
+\pmb{\epsilon}_{\delta}
 \end{pmatrix},
@@
 \begin{split}
-\vec{\epsilon}_{\gamma^0} &=\{0.07, -0.07, -0.07,  0.06,  0.02\},\\
-\vec{\epsilon}_{\gamma^1} &=\{ -0.04, 0.14,  -0.24,  0.32, -0.22\},\\
-\vec{\epsilon}_{\delta} &=\{ -0.05, 0.08,  -0.03,  -0.09, -0.12\}
+\pmb{\epsilon}_{\gamma^0} &=(0.07, -0.07, -0.07,  0.06,  0.02),\\
+\pmb{\epsilon}_{\gamma^1} &=( -0.04, 0.14,  -0.24,  0.32, -0.22),\\
+\pmb{\epsilon}_{\delta} &=(-0.05, 0.08,  -0.03,  -0.09, -0.12)
 \end{split}
@@
 are perpendicular to $a$ and $b$.
-The $\pmb{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
-$\vec{\epsilon}_{\gamma^1} $
+The $\pmb{\gamma}$ residuals $\pmb{\epsilon}_{\gamma^0}$ and
+$\pmb{\epsilon}_{\gamma^1} $
 quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that most
@@
  $\pmb{\delta}$ too
-has a significant projection onto the dust plane, as the $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
+has a significant projection onto the dust plane, as the $\pmb{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
 The transformation yields
@@
 &
-$0.0043^{+0.0009}_{-0.0010}$
-&
-$0.0016^{+0.0008}_{-0.0008}$
-&
-$0.0016^{+0.0007}_{-0.0007}$
-&
-$0.0015^{+0.0006}_{-0.0005}$
-&
-$0.0028^{+0.0005}_{-0.0005}$
+$0.0037^{+0.0010}_{-0.0010}$
+&
+$0.0011^{+0.0008}_{-0.0008}$
+&
+$0.0013^{+0.0007}_{-0.0007}$
+&
+$0.0013^{+0.0006}_{-0.0006}$
+&
+$0.0026^{+0.0005}_{-0.0005}$
 \\
@@
 &
-$   1.7^{+   0.9}_{  -0.4}$
-&
-$  -0.0^{+   0.1}_{  -0.2}$
-&
-$ \ldots$
-&
-$  -0.1^{+   0.1}_{  -0.1}$
-&
-$   0.7^{+   0.7}_{  -0.3}$
+$   1.7^{+   1.3}_{  -0.5}$
+&
+$  -0.1^{+   0.2}_{  -0.4}$
+&
+$   0.0^{+   0.0}_{   0.0}$
+&
+$  -0.0^{+   0.2}_{  -0.1}$
+&
+$   1.0^{+   1.2}_{  -0.5}$
 \\
@@
 &
-$ 0.035^{+ 0.005}_{-0.005}$
-&
-$ 0.026^{+ 0.004}_{-0.004}$
+$ 0.034^{+ 0.006}_{-0.005}$
+&
+$ 0.026^{+ 0.005}_{-0.005}$
 &
@@
 &
-$  0.54^{+  0.12}_{ -0.10}$
-&
-$  0.16^{+  0.06}_{ -0.06}$
-&
-$ \ldots$
+$  0.50^{+  0.11}_{ -0.10}$
+&
+$  0.15^{+  0.06}_{ -0.06}$
+&
+$  0.00^{+  0.00}_{  0.00}$
 &
@@
 &
-$0.0007^{+0.0012}_{-0.0012}$
-&
-$0.0006^{+0.0010}_{-0.0010}$
-&
-$0.0011^{+0.0008}_{-0.0008}$
-&
-$0.0010^{+0.0007}_{-0.0007}$
-&
-$0.0003^{+0.0006}_{-0.0006}$
+$0.0002^{+0.0011}_{-0.0011}$
+&
+$0.0004^{+0.0009}_{-0.0009}$
+&
+$0.0009^{+0.0008}_{-0.0008}$
+&
+$0.0008^{+0.0007}_{-0.0007}$
+&
+$0.0000^{+0.0006}_{-0.0006}$
 \\
@@
 &
-$ -0.24^{+  0.47}_{ -0.98}$
-&
-$ -0.32^{+  0.30}_{ -0.76}$
-&
-$ \ldots$
-&
-$ -0.08^{+  0.20}_{ -0.13}$
-&
-$ -0.66^{+  0.29}_{ -0.58}$
+$ -0.47^{+  0.69}_{ -1.37}$
+&
+$ -0.39^{+  0.41}_{ -0.93}$
+&
+$  0.00^{+  0.00}_{  0.00}$
+&
+$ -0.12^{+  0.19}_{ -0.16}$
+&
+$ -0.78^{+  0.42}_{ -0.88}$
 \\
@@
 &
-$ -0.01^{+  0.03}_{ -0.03}$
+$ -0.00^{+  0.03}_{ -0.03}$
 &
@@
 &
-$ -0.91^{+  0.75}_{ -1.78}$
-&
-$ -0.62^{+  0.46}_{ -1.15}$
-&
-$ \ldots$
-&
-$ -0.50^{+  0.21}_{ -0.53}$
-&
-$ -0.18^{+  0.41}_{ -0.32}$
+$ -0.78^{+  1.55}_{ -1.96}$
+&
+$ -0.62^{+  1.21}_{ -1.33}$
+&
+$  0.00^{+  0.00}_{  0.00}$
+&
+$ -0.46^{+  0.45}_{ -0.52}$
+&
+$ -0.14^{+  0.51}_{ -0.42}$
 \\
@@
 &
-$ 62.57^{+  3.71}_{ -3.66}$
-&
-$ 51.36^{+  3.12}_{ -3.13}$
-&
-$ 38.26^{+  2.67}_{ -2.69}$
-&
-$ 29.03^{+  2.36}_{ -2.39}$
-&
-$ 20.40^{+  2.21}_{ -2.26}$
+$ 59.51^{+  4.09}_{ -4.09}$
+&
+$ 49.02^{+  3.32}_{ -3.30}$
+&
+$ 36.96^{+  2.69}_{ -2.70}$
+&
+$ 28.37^{+  2.36}_{ -2.36}$
+&
+$ 20.35^{+  2.16}_{ -2.16}$
 \\
@@
 &
-$  0.63^{+  0.06}_{ -0.05}$
-&
-$  0.34^{+  0.03}_{ -0.03}$
-&
-$ \ldots$
-&
-$ -0.24^{+  0.01}_{ -0.02}$
-&
-$ -0.47^{+  0.03}_{ -0.03}$
+$  0.61^{+  0.06}_{ -0.05}$
+&
+$  0.33^{+  0.03}_{ -0.03}$
+&
+$  0.00^{+  0.00}_{  0.00}$
+&
+$ -0.23^{+  0.01}_{ -0.01}$
+&
+$ -0.45^{+  0.03}_{ -0.03}$
 \\
@@
 &
-$ -9.27^{+  3.50}_{ -3.75}$
-&
-$-11.08^{+  2.92}_{ -3.18}$
-&
-$-14.99^{+  2.38}_{ -2.66}$
-&
-$-14.28^{+  2.05}_{ -2.22}$
-&
-$-13.27^{+  1.91}_{ -2.09}$
+$ -7.57^{+  3.75}_{ -4.06}$
+&
+$ -9.63^{+  2.90}_{ -3.27}$
+&
+$-13.65^{+  2.36}_{ -2.60}$
+&
+$-12.98^{+  2.08}_{ -2.27}$
+&
+$-12.16^{+  2.08}_{ -2.19}$
 \\
@@
 &
-$ -0.38^{+  0.15}_{ -0.18}$
-&
-$ -0.26^{+  0.09}_{ -0.11}$
-&
-$ \ldots$
-&
-$ -0.05^{+  0.04}_{ -0.04}$
-&
-$ -0.12^{+  0.09}_{ -0.08}$
+$ -0.44^{+  0.19}_{ -0.24}$
+&
+$ -0.30^{+  0.11}_{ -0.13}$
+&
+$  0.00^{+  0.00}_{  0.00}$
+&
+$ -0.05^{+  0.05}_{ -0.05}$
+&
+$ -0.11^{+  0.11}_{ -0.10}$
 \\
@@
 &
-$  1.98^{+  0.52}_{ -0.50}$
-&
-$ -2.13^{+  0.55}_{ -0.54}$
-&
-$ -1.84^{+  0.51}_{ -0.52}$
-&
-$  0.70^{+  0.33}_{ -0.35}$
-&
-$  1.72^{+  0.75}_{ -0.73}$
-\\
-${{\delta_X/\delta_I-1}}$
-&
-$  0.17^{+  0.50}_{ -0.27}$
-&
-$ -2.23^{+  0.30}_{ -0.64}$
-&
-$ -2.08^{+  0.25}_{ -0.44}$
-&
-$ -0.60^{+  0.54}_{ -0.24}$
-&
-$ \ldots$
+$  0.14^{+  1.13}_{ -1.41}$
+&
+$  0.11^{+  0.91}_{ -1.10}$
+&
+$  0.04^{+  0.56}_{ -0.60}$
+&
+$  0.01^{+  0.43}_{ -0.43}$
+&
+$ -0.02^{+  0.43}_{ -0.41}$
+\\
+${{\delta_X/\delta_U-1}}$
+&
+$  0.00^{+  0.00}_{  0.00}$
+&
+$ -0.22^{+  0.28}_{ -0.21}$
+&
+$ -0.63^{+  0.33}_{ -0.36}$
+&
+$ -0.82^{+  0.30}_{ -0.44}$
+&
+$ -1.05^{+  0.35}_{ -0.63}$
 \\
@@
 &
-$ 0.048^{+ 0.012}_{-0.011}$
-&
-$ 0.027^{+ 0.007}_{-0.007}$
-&
-$ 0.014^{+ 0.004}_{-0.005}$
-&
-$ 0.008^{+ 0.006}_{-0.005}$
-&
-$ 0.041^{+ 0.005}_{-0.004}$
+$ 0.053^{+ 0.008}_{-0.011}$
+&
+$ 0.018^{+ 0.011}_{-0.011}$
+&
+$ 0.017^{+ 0.004}_{-0.006}$
+&
+$ 0.010^{+ 0.007}_{-0.007}$
+&
+$ 0.040^{+ 0.006}_{-0.005}$
 \\

### 2017-07-27 apj.tex
edit text

@@
 \end{align}
-quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.
+quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.  The most significant
+deviation away from the plane is in the $R$-band.
 This result indicates that
@@
 %where $R=A_V/E(B-V)$.
-
-Suppose that the data were due to a dust model with constant $R \equiv A_V/E(B-V)$.
-The  $A_V$ and $E(B-V)$ parameters of the dust model in Eqn.~\ref{f99:eqn} would then be correlated.
-An alternative parameterization 
-\begin{equation}
-A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
-\end{equation}
-
-A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models.
-These determine the choice of directions of
-the vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
-and so the $\gamma$'s
-
-   Then a \citetalias{1999PASP..111...63F}  dust model 
-can be written in a new basis
+\color{purple}
+In principle, our linear model could accommodate for $\gamma$ any two independent vectors that span
+the plane.  We begin discussion on the specific choice of $\gamma$ returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model. 
+While
+Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\mathbf{a}$ and $\mathbf{b}$ and
+their corresponding parameters 
+$A_V$ and 
+$E(B-V)$, the linear dust model could be written in terms of any two other basis vectors  $\mathbf{a}+\kappa_1 \mathbf{b}$
+and $\kappa_2 \mathbf{a} + \mathbf{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
+In this basis, the model is then
 %To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
@@
 \end{equation}
-with the parameters $\kappa_1$ and $\kappa_2$ parameterizing the directions of the two new basis vectors.
-The vector $a(X)+\kappa_1 b(X)$ represents extinction that can occur with fixed $R^F_0=1/\kappa_1$ and unconstrained $\kappa_2$.
+with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  proportional to  linear combinations of the original parameters.
+
+Our model includes a prior that the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
+If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
+to the non-correlation of   $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ in the supernova sample.
+A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
+All color changes would then be confined to the $a(X)+\kappa_1 b(X)$ direction.
+This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$ .
+We use this interpretation to assign  $R^F_{eff} = \kappa_1^{-1}$ as
+the effective total-to-selective extinction of our sample.
+\color{purple}
+The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$.
+Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\pmb{\gamma}^0$ and  $\mathbf{a}+\mathbf{b}/2.44$.
+From the Monte Carlo chains, we find a 68\% credible interval for  $R^F_{eff}$ of 2.26--2.63.
+
+Different supernovae are expected to encounter dust with different $R^F$.
+Let us introduce a new per-supernova vector $\delta R$ such that $R^F = R^F_{eff}(1+  \delta R)$.
+Variations in the value of $R^F$ (and hence $\delta R$) lead 
+the prior to impose
+\begin{equation}
+\kappa_2 = R^F_{eff} \left(1- \frac{\mbox{Var}(\delta R\, E^F(B-V))}{\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))}\right).
+\end{equation}
+From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R\, E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))$.
+This result indicates that there is a small but significant covariance between  extinction contributions due to
+deviations from an effective $R^F$ and
+the color-excess parameter $E^F(B-V)$.
+
+%
+%Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
+%can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
+%The zero-correlation condition, which determines the direction of $\pmb{\gamma}^1$,  is for the coordinate values along $\pmb{\gamma}^0$ to be uncorrelated with the coordinate values along $\pmb{\gamma}^1$.
+%Our analysis yields an angle of 154\arcdeg\ between  $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
+%The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
+%Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\pmb{\gamma}^0$.
+%
+%
 %While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
@@
 %Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.
-
-\color{purple}
-The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$, $\kappa_2=-5.27/0.72=-7.31$.
-The directions of the $\pmb{\gamma}$ vectors, and  the expectations from  \citetalias{1999PASP..111...63F} with $R=\kappa^{-1}$, are shown in 
-Figure~\ref{plane:fig}.  There is almost perfect alignment between $\pmb{\gamma}^0$ and $R=2.44$ dust.
- From the Monte Carlo chains, we find a 68\% credible interval for $\kappa^{-1}_1$ of 2.26--2.63.
-
-\color{black}
-
-To gain an intuitive understanding of how the $\kappa$ values are determined, consider the hypothetical case where
-all supernovae experience dust with the same $R^F$.   There is only one free parameter $A^F_V$ and magnitudes are
-constrained to move along the vector $a(X)+b(X)/R^F$.  In the fit of the linear model, the zero-covariance condition is satisfied when
-$-\kappa_1 A^F_V + E^F(B-V)=0$,  i.e.\ when $\kappa_1=1/R^F$.  
-Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
-$\pmb{\gamma}^0$ is aligned with  $a(X)+b(X)/R^F$, and $\pmb{\gamma}^1$ is unconstrained.
-
-Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
-can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
-The zero-correlation condition, which determines the direction of $\pmb{\gamma}^1$,  is for the coordinate values along $\pmb{\gamma}^0$ to be uncorrelated with the coordinate values along $\pmb{\gamma}^1$.
-Our analysis yields an angle of 154\arcdeg\ between  $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
-The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
-Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\pmb{\gamma}^0$.
-
-\color{purple}
+%
+
+%To gain an intuitive understanding of how the $\kappa$ values are determined, consider the hypothetical case where
+%all supernovae experience dust with the same $R^F$.   There is only one free parameter $A^F_V$ and magnitudes are
+%constrained to move along the vector $a(X)+b(X)/R^F$.  In the fit of the linear model, the zero-covariance condition is satisfied when
+%$-\kappa_1 A^F_V + E^F(B-V)=0$,  i.e.\ when $\kappa_1=1/R^F$.  
+%Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
+%$\pmb{\gamma}^0$ is aligned with  $a(X)+b(X)/R^F$, and $\pmb{\gamma}^1$ is unconstrained.
+
 As a check of our analysis implementation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
@@
 distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
-measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations: the input $R^F=2.5$ is centered
-within the 68\% credible interval for $\kappa^{-1}_1$ of 2.38--2.69.
+measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations which yield a median
+$R^F_{eff}$ of 2.53, which is close to
+ the input $R^F=2.5$.
 
@@
 relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
-()
+(Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
 \color{black}
 The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
-with the expectation of dust considering the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
+with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
 This distribution is given by the data, in that it is independent of any knowledge or prior
@@
 
-Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$, which can be attributed to 
-extinction corrections due to deviations away from the canonical $\kappa_1$ value.   The distribution has a long
-negative tail and is peaked at its positive edge, and by construction has a mean of zero.
+Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$
+relative to that of an arbitrary supernova  $\gamma^1_V k_1|_0$, which can be attributed to 
+extinction corrections due to deviations away from the canonical $R^F_{eff}$ value.   The distribution has a long
+negative tail and is peaked at its positive edge. Recall that our model constraints force 
+the distribution of $\gamma^1_V k_1$ has a mean of zero.
 The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
@@
 %---
-$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have$-0.01 \pm 0.01$  and
+$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
 $  0.06 \pm 0.03$ 
@@
 \color{purple}
-Our model can be associated with the extinction model of  \citetalias{1999PASP..111...63F} using Eqn.\ref{trans_I:eqn}
-and the assumption that  SN~2011fe has zero extinction.  Transforming our parameters to those
-of   \citetalias{1999PASP..111...63F}, we obtain
-$A^F_V=0.77$ and $E^F(B-V)=1.28$ with covariance
+The model parameters can be transformed into  the 
+\citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
+assuming that  SN~2011fe has zero extinction.  The colors predicted by this \citetalias{1999PASP..111...63F}--component
+of our model are  shown in Figure~\ref{sn2014j:fig}. 
+Our model predictions provide a significantly better match to the data
+despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
+Differences in the color predictions between our model and the pure dust model are
+apparent,
+particularly in the $B-V$ and  $R-V$ colors.  Our model has shallower decline in color excess with increasing wavelength.
+(Refer to  Eqn.~\ref{res_I:eqn} to see the deviation in magnitude of our model away from the dust model.)
+The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
+in Figure 3 of  \citet{2014ApJ...788L..21A}, who fit
+UV through NIR data to obtain $R_V^F=1.4$ and $E^F(B-V)=1.37$.
+Notwithstanding their bias respect to the data, we present the transformed dust parameters
+$A^F_V=0.77$ and $E^F(B-V)=1.28$ and covariance
 \begin{equation}
@@
 \end{equation}
-which implies $R^F= 0.59^{+ 0.53}_{-0.48}$.
-The color excesses predicted by these values are shown in Figure~\ref{sn2014j:fig}.
-
-The imperfect correspondence between our model and that of   \citetalias{1999PASP..111...63F} is seen in Figure~\ref{sn2014j:fig}.
-While both models reproduce the observed color excesses at the extreme $U$ and $I$ bands,  \citetalias{1999PASP..111...63F}'s
-does not simultaneously match the central colors.
-The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
-in Figure 3 of  \citet{2014ApJ...788L..21A}.  (They use
-UV through NIR data to fit \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$.)
-Our model predictions provide a significantly better match to the data
-despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
+which imply $R^F= 0.59^{+ 0.53}_{-0.48}$.
 

### 2017-07-28 apj.tex
fix range of childress plots

@@
 condition are shown in Figure~\ref{deltacorner:fig}.
-The shapes of the new $\pmb{\delta}$ posteriors are somewhat distorted compared to the original.
-Despite its relatively strong signal-to-noise, the original posterior for $D$ for the selected supernova does have significance on both sides of zero,
+The shapes of the new $\pmb{\delta}$ posteriors are somewhat distorted compared to the original;
+despite its relatively strong signal-to-noise, the original posterior for $D$ for the selected supernova does have significance on both sides of zero,
 resulting in changes in the shape of the $\pmb{\delta}$ posteriors when  $D$ to forced to be positive.   
@@
 
-%\section{Supernova Model III: Fitzpatrick Dust}
-%\label{model0:sec}
-%\color{blue}
-%Dust models can explain the extrinsic magnitude and color variations found in
-%the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
-%perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
-%terms predicted by a dust extinction model from the literature.  
-%%
-%%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
-%%except that dust
-%%is used in place of  the linear two-color-parameter  model.      
-%The dust model of  \citet{1999PASP..111...63F} is considered:
-%while commonly used dust
-%models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
-%does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.
-%
-%
-%The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R^F$ and $E^F(B-V)$.  The first, $R^F$,
-%specifies the wavelength-dependent  attenuation  that we notate as $A^F/E^F(B-V)$.  The second, $E^F(B-V)$, specifies the normalization
-%of that attenuation.  These two parameters can be combined to define a third dependent parameter $A^F_V \equiv R^F E^F(B-V)$.
-%The dust model is expressed as
-%\begin{equation}
-%A(\lambda; E^F(B-V), R^F) = E^F(B-V) \frac{A^F}{E^F(B-V)}\left(\lambda; R^F \right).
-%\end{equation}
-%
-%In the broadband photometry of a source with SED $f(\lambda)$ observed in a filter with transmission $X$, the attenuation $A_X$ is
-%\begin{equation}
-%A_X\left(A^F_V, E^F(B-V)  \right) = 2.5 \log{\left(\frac{\int f(\lambda) X(\lambda)d\lambda}{\int 10^{-0.4 A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)} f(\lambda) X(\lambda)d\lambda } \right)},
-%\end{equation}
-%whose first-order approximation
-%\begin{equation}
-%A_X\left(A^F_V, E^F(B-V)  \right) = \frac{\int  A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)f(\lambda) X(\lambda)d\lambda}{\int  f(\lambda) X(\lambda)d\lambda}
-%\end{equation}
-%is easy to interpret as an effective extinction.
-%
-%
-%We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
-%the SED of the SALT2 (v2.4), $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
-%SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
-%parameter values of an unextincted
-%supernova.
-%The SALT2 SED determines the values of $A_X$ and the
-%intrinsic colors. 
-%
-%This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections in that the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
-%Taking the SALT2 template as the unextincted supernova, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
-%Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
-%The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
-%while simultaneously showing no color excess is $B-R$.
-% 
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
-%   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
-%    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
-%    taking the SALT2 template as an unextinced supernova.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
-%allowed by \citetalias{1999PASP..111...63F} dust.
-%Right:    $A_X/E(X-V)$ of the best-fit $c$'s 
-%    relative to SALT2. \label{model1118:fig}}
-%\end{figure}
-%
-%
-%%
-%%We emphasize now that our broadband magnitude model does not ambiguously specify $A_X$, which depend
-%%on the SED of the source.  
-%%In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
-%%updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
-%%SALT2 template yields similar results.)
-%%The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
-%%of model error.  Consider the SED to be the sum of the template and an offset
-%%\begin{equation}
-%%f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
-%%\end{equation}
-%%To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
-%%extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.
-%
-%%For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
-%%$-0.21 \le A_V \le 1.8$, $2.1 \le R \le 6.9$ with a third-order polynomial in $A_V$ and $E(B-V)$.   The limits in $R$ represent the range of
-%%values that enter the dust-model training.
-%%The differences between the extinction and the polynomial approximation are small relative to  $\partial A_X/ \partial R$ over the scales of
-%%$R$ of interest.
-%
-%%
-%%
-%%
-%%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%%   \centering
-%%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
-%%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
-%%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
-%%   \label{dfitz:fig}}
-%%\end{figure}
-%%
-%
-%
-%The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
-%and
-%\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 template,
-%and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
-%and there is one global $R$ parameter.  
-%%
-%%
-%%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
-%%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
-%%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
-%%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
-%%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.
-%
-%Results from evaluating this model with SNf data
-%provide further evidence of the inconsistency between the ansatz and the models of the previous section.
-%The dust-model analysis of this section sets the magnitude of an $A_V=0$ supernova, so now  magnitudes of the canonical
-%supernova in \S\ref{model:sec} can also be compared (along with color) to the expectations of the dust model.  The magnitude difference, $\Delta c_X$,
-%is the difference between the $c_X$ parameters of the two analyses.
-%Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
-%corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
-%to SALT2: these values are plotted in
-%Figure~\ref{model1118:fig}.
-%The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.
-%
-%The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram of the median $A_V$ determined for
-%each supernova. The
-%$A_V$ distribution  has a slow rise from zero; recall that the equivalent $\gamma^0_V k_0$
-%from the linear model of \S\ref{model:sec} has the sharp rise expected from of a large fraction of supernovae
-%experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
-%$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
-%While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
-%to $R=3.17^{0.20}_{-0.17}$.
-%
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
-%   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
-%    \caption{Left: Histogram of the median $A_V$ determined for
-%each supernova.  The $\gamma^0_V k_0$ medians from our 2-parameter model of \S\ref{model:sec} is also shown.  The means of the measurement
-%uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
-%Right: Posteriors for $R$.  Results for both the SALT2 supernova model and the updated \citet{2007ApJ...663.1187H} are shown.
-%   \label{AVRV:fig}}
-%\end{figure}
-%
-%The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models,
-%and our ansatz for incorporating dust is limited systematically in measuring 
-%the total-to-selective extinction.  We emphasize also that $R^F$ determined in this section are based on  both absolute extinction and color,
-%whereas the $\gamma$'s (and resulting $\kappa_1$) in \S\ref{model:sec} do not depend on absolute extinction, i.e. the extra model constraint  of the
-%zero-extinction supernova.
-%
-%
-%%
-%%The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
-%%$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
-%%The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
-%%non-zero.  Insofar that the $A_V$ and $R_V$
-%%parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
-%%is important.
-%%
-%%
-%%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%%   \centering
-%%   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
-%%    \caption{Difference between per-supernova
-%%$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
-%%   \label{CCMF99:fig}}
-%%\end{figure}
-%
-%
-%\color{black}
+\color{purple}
+The Model~II fit of SN~2014J \citet{2014ApJ...788L..21A}  data 
+gives $k_0$ and $k_1$ that qualitatively similar to  those from the fit to Model~I but with much larger uncertainties.
+These parameters are now highly correlated with $D$, which itself is consistent with zero.  The results resemble those of
+Model~I shown in Figure~\ref{sn2014j:fig}, except for larger error bars for the color excesses projected onto the dust model.
+\color{black}
+
 \section{Discussion}
@@
 \subsection{Light Curve Shape}
-Our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
+The motivation of our analyses was to standardize supernovae based on spectral features and colors around peak brightness.
+As such, our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
 We now examine this in more depth using the intrinsic--extrinsic Model~II of \S\ref{model2:sec}.
-The correlation between $EW_{Si}$ and the SALT2 $x_1$ light-curve shape parameter is verified
+The connection between the spectrum at peak and the light-curve decline rate, seen through
+the correlation between $EW_{Si}$ and the SALT2 $x_1$ light-curve shape parameter, is verified
 for our sample \citep{2017Chotard}.
@@
 though there is a hint of nonlinearity in the $B-V$ and $R-V$ colors.
+
 We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta x_1$ to the 
@@
 from this analysis are given in Table~\ref{globalx1:tab}; there are no significant changes with respect to the reference model. 
-Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: only $\zeta_R/\zeta_V$
-has a non-zero value at $>2\sigma$.
+Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: $\zeta_R/\zeta_V$
+has the largest significance at at $1\sigma$.
 The evidence for a non-zero $\pmb{\delta}$ remains as seen in the values of $\delta_X/\delta_I-1$ in Table~\ref{globalx1:tab}, meaning that it is not an artifact of
@@
 &
-$   0.0^{+   0.0}_{   0.0}$
+$  \ldots$
 &
@@
 &
-$  0.00^{+  0.00}_{  0.00}$
+$  \ldots$
 &
@@
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-Also plotted  are ideograms of $A_{\delta U}$ for the two subsamples obtained by dividing the full sample at a host mass of  $\log{(M/M_\sun)}=10$.
-Although by eye it appears that the high-mass hosts tend the have lower $A_{\delta U}$, the difference is
+The difference between high-mass hosts is
 not significant; we calculate  average
 %---
-$\langle A_{\delta I} \rangle=   -0.0021 \pm    0.007$,
-$\langle A_{\delta I} \rangle= -0.0034 \pm    0.0064$ 
+$\langle A_{\delta I} \rangle=     -0.0002 \pm    0.0089 $,
+$\langle A_{\delta I} \rangle= 0.0025 \pm   0.0073 $ 
 for low- and high-mass hosts respectively.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output25/childress.pdf}
+   \includegraphics[width=2.8in]{output25/childress_pvalue.pdf}
+      \caption{Left: Intrinsic parameter $A_{\delta U}=\delta_U D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
+      less than and greater than  $\log{(M/M_\sun)}=10$.
+Right: Histogram of the two-tailed p-value from  the Kolmogorov-Smirnov test applied to all links in the Monte Carlo chains.
+   \label{childress:fig}}
+\end{figure}
+
+The Kolmogorov-Smirnov test is applied on the distribution of $A_{\delta I}$ of both low- and high-mass samples for
+each Monte Carlo link.  The resulting distribution of the two-tailed p-value (a high value meaning that we cannot
+reject the hypothesis of the samples are the same) over all chains is shown in Figure~\ref{childress:fig}. The distribution is broad
+over the range from 0 to 1.  We are thus unable to distinguish the $A_{\delta I}$ distributions from low- and high-mass samples.
+
 %Using the SNfactory sample,
@@
 %global host mass.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output25/childress.pdf}
-   \includegraphics[width=2.8in]{output25/childress_pvalue.pdf}
-      \caption{Left: Intrinsic parameter $A_{\delta U}=\delta_U D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ values for supernovae with hosts
-      less than and greater than  $\log{(M/M_\sun)}=10$.
-Right: Normalized histograms of  $A_{\delta U}$ medians for supernovae in $\log{(M/M_\sun)}<10$ and $\log{(M/M_\sun)}>10$ hosts. 
-   \label{childress:fig}}
-\end{figure}
-
 \subsection{Physical Motivation}
 
-A straightforward explanation for the third parameter is that it describes the absorption due to some form of dust. 
-Supernova light may encounter two types
-of dust, an interstellar form  that resembles the \citetalias{1999PASP..111...63F} model, and a second
-circumstellar dust that deviates from the model and can produce low visual-to-selective extinction
-\citep{2008ApJ...686L.103G}.
-The $D$ and $\pmb{\delta}$ parameters could be attributed to the second form form of dust.
+A straightforward explanation for the third color term $\pmb{\delta} D$ is that it describes the absorption due to some form of dust
+that does not obey the  \citetalias{1999PASP..111...63F} model.
+Supernova light may encounter two
+dusts, first a 
+circumstellar dust that can produce lower visual-to-selective extinction
+\citep{2008ApJ...686L.103G} and then
+an interstellar form  that resembles the \citetalias{1999PASP..111...63F} model.
 Qualitatively,  the decrease in magnitude change toward redder wavelengths, seen in Figure~\ref{deltaratio:fig}, matches the 
-expectation for dust.  The projection of  $\pmb{\delta}$ onto the plane expected by dust is significant at the $>98$\% level.  However, we
-lack the signal-to-noise to show that  all the  $\delta_X$ share the same sign, indeed the posterior median of $\delta_I/\delta_U$ is negative.
+expectation for the circumstellar form of dust.
+The projection of  $\pmb{\delta}$ onto the plane expected by dust is significant at the $>98$\% level.  However, we
+lack the signal-to-noise to show consistency with this explanation.
+Our best-fit  $\delta_X$ do not share the same sign, as expected for dust.
 Confining ourselves to the 98\% of   $\pmb{\delta}$ that lies on the dust plane, associating 
@@
 
-Alternatively, the $D$ and $\pmb{\delta}$ parameters can represent an added contribution to a dust law, rather than alone
-describing a form of dust.  The extra degree-of-freedom could be associated with the skewness in the distribution of dust grains, as an increase of smaller dust grains
+An alternative explanation for the $\pmb{\delta} D$ term is that it captures an intrinsic dust parameter that is independent of $R^F$.
+Supernova light encounters one dust with a degree of freedom beyond that modeled by \citetalias{1999PASP..111...63F}.
+The extra degree-of-freedom could be associated with the skewness in the distribution of dust grains, as an increase of smaller dust grains
 can flatten extinction in the red and enhanced steepness in the UV relative to standard dust models  \citep[Figure~3 in][]{2015ApJ...807L..26G,
-2017ApJ...836...13H}.
+2017ApJ...836...13H}.  Unfortunately, our signal-to-noise for $\pmb{\delta}$ is insufficient to test these physically-motivated
+dust models.
 

### 2017-07-30 apj.tex
smoothing out text

@@
 \color{purple}
-Through empirical modeling, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined 
-based on its observed signal, making SNe~Ia  excellent distance indicators.  Improved modeling of SN~Ia absolute magnitudes can account for
+Through empirical modeling of its observed signal, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined,
+making SNe~Ia  excellent distance indicators.  Improved modeling of SN~Ia absolute magnitudes can account for
 further physical
 diversity that is expected but not included
-in current models, and so consequently can lead to more precise per-object distances with tighter systematic uncertainties.  In this article, we present the
-results of    
+in current models, and so consequently can lead to more precise per-object distances with smaller systematic uncertainties.  In this article, we present   
 \color{black}
@@
 confidence.
-The color changes allowed by the model are almost parallel to the color changes allowed by the extinction model of  \citet{1999PASP..111...63F} with floating
-total-to-selective extinction parameter $R^F$.  The deduced color excess
-is consistent with an effective $R^F = 2.44$.
-The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
-Inspired that our  two-parameter model, with no conditioning that would steer it toward a dust model, produces behavior similar to that expected from Galactic dust, we extend  the model to three color parameters.
+The color changes allowed by the model are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F} with a free
+total-to-selective extinction parameter $R^F$.  As an ensemble, the supernova sample has an effective
+%-----
+$R^F = 2.44$.
+%-----
+Our model
+ is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
+Inspired that with no conditioning our  two-parameter model produces behavior similar to that expected from Galactic dust,
+we extend  the model to three color parameters.
 In this new case we obtain consistent results for
@@
 %--- table.py
-$(1-5\times10^{-4})$
+$\sim 90\%$
 %-----
@@
 beyond that tracked by the spectral features and two-parameter dust models.
-%A direct incorporation of dust models into our formalism is impossible. An indirect incorporation of dust
-%yields in constant-$R^F$ model $R^F \sim 3$, but the implementation is sensitive to systematic uncertainties that arise
-%from the need to specify the colors of an unextincted supernova and its use of absolute extinction, neither of which is used in our original model.
 \end{abstract}
@@
 In SALT2 the light curve shapes are described by a multiplicative scaling (``stretch'')  of the time evolution,
- whereas MLCS2k2 varies shapes through additive time-dependent corrections to magnitudes.
+ whereas MLCS2k2 varies shapes through additive time-dependent magnitude corrections.
 The physical cause of the color diversity is interpreted differently by the two sets of authors: 
@@
 to the reddening of light from host-galaxy dust.  Differences between these models produce differences in the results of
-analysis of both low-redshift \citep{2007ApJ...664L..13C} and high-redshift \citep{2009ApJS..185...32K} supernovae.
+analyses of both low-redshift \citep{2007ApJ...664L..13C} and high-redshift \citep{2009ApJS..185...32K} supernovae.
 
@@
 Hierarchical modeling has recently opened
-the study of intrinsic supernova color based on SN~Ia Hubble diagrams. Latent parameters that are not directly tied to observables,
-such as multiple parameters that simultaneously influence color, can be included in such models.
+the study of intrinsic supernova color based on SN~Ia Hubble diagrams. Latent parameters that are not directly tied to observables
+but  influence color can be included in such models.
 \citet{2016arXiv160904470M} take the approach of modeling the distribution of their parameters, to find that
 scatter in the Hubble diagram is better explained by a combination of intrinsic color dispersion and
-$R_B \equiv R_V+1=3.7$ dust, rather than by dust with no color dispersion.
+$R_V=2.7$ dust, rather than by dust with no color dispersion.
 They draw these conclusions by using only the SALT2 (v2.4) $x_1$ parameter as the summary statistic that describes color.
@@
 spectrophotometric time series of hundreds of Hubble-flow $0.03<z<0.08$ SNe~Ia.   The $3200$--$10000$~\AA\ spectral coverage
-provides measurements of an array of supernova spectral features while also providing synthetic broadband photometry
+provides measurements of an array of supernova spectral features while also enablng synthetic broadband photometry
 spanning near-UV to near-IR SN-frame wavelengths.  SNfactory specifically targeted objects
 early in their temporal evolution, so that well over a hundred of these supernovae have  coverage over
-peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia colors and spectral features together.
+peak brightness.  This dataset provides a homogenous sample with which to study SN~Ia colors and spectral features simultaneously.
 
@@
 variation is consistent with Milky Way dust models.
-We accommodate  three independent color parameters: the model is constructed such that 
+We accommodate up to  three independent color parameters: the model is constructed such that 
 two are assigned as extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
-properties.
+properties.  (We subsequently find that extrinsic and intrinsic properties cannot be distinguished with our data.)
 The data used in this analysis are described in \S\ref{data:sec}.
@@
 are consistent with the expectations of parameterized Milky Way extinction models, and do an excellent job of fitting the data of the out-of-sample
-supernova SN2014J that has an extreme total-to-selective extinction.
+supernova SN2014J that has an extremely low total-to-selective extinction.
 In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
@@
 $\Lambda$CDM cosmology with $\Omega_M = 0.28$ (with an arbitrarily selected
-$H_0$ since the current analysis does not depend on the absolute magnitude scale).
+$H_0$ since the current analysis does not depend on absolute magnitude).
 
@@
 
-We hypothesize that at peak brightness
+In what is  referred to as Model~I, we hypothesize that at peak brightness
 SN~Ia broadband magnitudes and colors are correlated with
@@
 \subsection{Model}
-In what is what is referred to as Model~I, we assume 
+We assume 
 that  peak intrinsic $UBVRI$ magnitudes of a supernova are linearly dependent
@@
 to capture band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
-flux data to luminosity.
+fluxes to luminosites.
 The apparent magnitudes are the sum of the intrinsic magnitudes plus additional terms that are linearly dependent on the
+per-supernova
 extrinsic-color parameters $k_0$ and $k_1$.  
+Unlike the parameters associated with
+the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
+parameters $k_0$ and $k_1$ are not directly associated
+with observables but rather are inferred as part of the analysis.
 The observables
@@
 have Gaussian measurement uncertainty with covariance $C$.
-Unlike the parameters associated with
-the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
-parameters $k_0$ and $k_1$ are not directly associated
-with observables but rather are inferred as part of the analysis.
 The
@@
 \end{equation}
-The global parameter vectors
+The global parameter vectors that describe the SN~Ia population
 $\mathbf{c}$ (where $\mathbf{c}=(c_U, c_B, c_V, c_R, c_I) $),
-$\pmb{\alpha}$, $\pmb{\beta}$,  and $\pmb{\eta}$,  are the intercepts and slopes of the linear relationships that
-relate intrinsic magnitudes with the spectral-feature parameters.
-The global parameter vectors $\pmb{\gamma}^0$, $\pmb{\gamma}^1$  are the slopes that connect the extrinsic-color
-parameters to apparent magnitudes.
+$\pmb{\alpha}$, $\pmb{\beta}$,  and $\pmb{\eta}$,  are the intercept and slopes of the linear relationships that
+relate spectral-feature parameters with intrinsic magnitudes.
+The global parameter vectors $\pmb{\gamma}^0$, $\pmb{\gamma}^1$  are the slopes that relate 
+the latent extrinsic-color parameters with apparent magnitudes.
 
 \color{purple}
-The model as written  has degeneracies that need to be constrained.
+The model as written has degeneracies that need to be constrained in order for fits to converge.
 The model does not specify the absolute magnitude nor the intrinsic color of a supernova that has no extrinsic color contribution,
-so we fix them to the samples by imposing
+in their place the zeropoints of the per-supernova magnitude and color parameters are set to the sample means
 \begin{equation}
@@
 \end{equation}
-The model contains products of latent parameters,
-like $\pmb{\gamma} k$, which lead to the degeneracy $\pmb{\gamma} \rightarrow a\pmb{\gamma}$, $k \rightarrow a^{-1} k$.
-To aid in the convergence of $\pmb{\gamma}$ and $k$ we impose a prior on the rms of $k$, but
-our physical interpretations are independent of this scaling.
+The model contains the product of latent parameters
+$\pmb{\gamma} k$, which leads to the degeneracy $\pmb{\gamma} \rightarrow a\pmb{\gamma}$, $k \rightarrow a^{-1} k$.
+To aid in the convergence of $\pmb{\gamma}$ and $k$ we impose a prior on the rms of $k$, though
+our physical interpretations are ultimately independent of this scaling.
 This prior does not specify the sign of $a$, which leaves a parity degeneracy.  As will be seen, the signal-to-noise in $\pmb{\gamma}$ is sufficiently
-high that our finite MCMC chains do not migrate between the degenerate solutions so practically this is not a problem; for convenience
-we thus impose 
+high that our finite MCMC chains do not migrate between the degenerate solutions; to simplify the merging of multiple chains
+we impose one of the degenerate solutions
 \begin{equation}
@@
 
-There remain degeneracies in the model.  One is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
+Another form of degeneracy is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
  $\pmb{\gamma}^0 \rightarrow \pmb{\gamma}^0  + \epsilon_{\gamma^0}$, $\pmb{\gamma}^1 \rightarrow \pmb{\gamma}^1 + \epsilon_{\gamma^1}$
@@
 linear external terms can leak into the linear spectral feature corrections.
-These degeneracies are not broken within the model, but rather are constrained by the priors, in which the
+These degeneracies are not broken within the model, but rather are constrained by the priors in which the
 per-supernova parameters
@@
 
-For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
-color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
-$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level independent parameters.
-
-In a Bayesian analysis such as this the priors must be described.  A flat prior is used for all parameters except
+In our Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
 for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior\footnote{
@@
 This covariance matrix prior is recommended by STAN \citep{stan}, the Monte Carlo program we use to evaluate the model.
- We find that imposing a stricter assumption of a
- diagonal covariance matrix, with no reference to a correlation matrix with LKJ prior, produces little change in the posteriors of
+ \color{purple}
+ We find that a simpler intrinsic dispersion model with no correlations between bands
+ (i.e.\ a  diagonal covariance matrix) produces little change in the posteriors of
  the other parameters.
+\color{black}
+
+For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
+color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
+$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level independent parameters.
 
@@
 \label{results:sec}
-The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo as implemented in
+The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo with a No-U-Turn
+Sampler as implemented in
 STAN \citep{stan}.  We run eight chains, each with 5000 iterations of which
 half are used for warmup.
+Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig} .
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output11/coeff0.pdf} 
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $U$ band.
+            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
+            projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
+            enclosed probability.  Lines for zero value for $\alpha_U$, $\beta_U$, $\eta$, $\gamma_U^0$, $\gamma_U^1$, and $\sigma_U$ are shown for reference --
+            in most cases they are outside the range of the plot.
+            \label{global1:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output11/coeff1.pdf} 
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $B$ band.
+ \label{global2:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output11/coeff2.pdf} 
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $V$ band.
+ \label{global3:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.2in]{output11/coeff3.pdf} 
+            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $R$ band.
+ \label{global4:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+         \includegraphics[width=5.2in]{output11/coeff4.pdf} 
+            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $I$ band.
+ \label{global5:fig}}
+\end{figure}
+
+Tests have revealed no evidence for the non-convergence of the MCMC run.
 STAN provides output statistics to assess
@@
 the Monte Carlo chains have not converged to the stationary posterior distribution.
+\color{purple}
+For four selected colors, a plot of the
+observed versus deduced intrinsic colors and the histogram of their differences
+\color{black}
+are shown in Figure~\ref{residual:fig}. 
+There is no evidence of a catastrophically poor model predictions nor of extreme
+outlying data.
 We have rurun the analysis with a variety of initial conditions, including one with $\pmb{\gamma}$ equal to zero, except for a small positive 
@@
 remain consistent.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output11/coeff0.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $U$ band.
-            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
-            projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.  Lines for zero value for $\alpha_U$, $\beta_U$, $\eta$, $\gamma_U^0$, $\gamma_U^1$, and $\sigma_U$ are shown for reference --
-            in most cases they are outside the range of the plot.
-            \label{global1:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output11/coeff1.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $B$ band.
- \label{global2:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output11/coeff2.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $V$ band.
- \label{global3:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-      \includegraphics[width=5.2in]{output11/coeff3.pdf} 
-            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $R$ band.
- \label{global4:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-         \includegraphics[width=5.2in]{output11/coeff4.pdf} 
-            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $I$ band.
- \label{global5:fig}}
-\end{figure}
-
-\color{purple}
-For four selected colors, a plot of the
-observed versus deduced intrinsic colors and the histogram of their differences
-\color{black}
-are shown in Figure~\ref{residual:fig}. 
-There is no evidence of a catastrophically poor model predictions nor of extreme
-outlying data.
 
@@
 their results are shown in terms of $\gamma^i_X/\gamma^i_V-1$.
-Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig} .
 
@@
 
-We find significant non-zero values for $\alpha$ and $\beta$, indicating that $EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
+We find significant non-zero values for $\pmb{\alpha}$ and $\pmb{\beta}$, indicating that $EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
 peak magnitudes.
@@
 to  within one standard deviation.
-The effect of spectral parameters on color is shown in the rows of $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$
+The effect of spectral parameters on color (as opposed to magnitude)
+is shown in the rows of $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$
 in Table~\ref{global:tab}.
@@
 $\lambda_{Si}$ and color.
+
+The signal in  $\pmb{\alpha}$ and $\pmb{\beta}$ cannot be attributed to the equivalent widths themselves.
+The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its direct affect on magnitude
+is
+$2.5 \log{(20/850)} \sim 0.03$ mag.  
+The implied span in $B$ magnitude based on $\beta_B$ is 0.54~mag.  Therefore $\beta_B$ cannot wholly be attributed to the flux deficit
+from the line itself.
+Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
+701~\AA, so that its direct affect on magnitude
+is
+$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the 
+presence of the line itself.
 
@@
 \color{black}
-%
-%Given that the 
-%off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix rather than the matrix elements themselves,
-%it is not straightforward to present correlation matrix confidences:
-%the average over Monte Carlo links of the
-%Cholesky factors will not  generally yield a correlation matrix.  
-%To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
-%chain, element by element.
-%For $UBVRI$ the matrix is
-%\begin{equation}
-%C_c(U,B,V,R,I)=
-%\begin{pmatrix}
-%\begin{array}{rrrrr}
-%0.0038 & 0.0010 & -0.0002 & -0.0000 & 0.0003 \\
-%0.0010 & 0.0011 & 0.0002 & -0.0000 & -0.0006 \\
-%-0.0002 & 0.0002 & 0.0004 & 0.0000 & -0.0002 \\
-%-0.0000 & -0.0000 & 0.0000 & 0.0002 & 0.0002 \\
-%0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
-%\end{array}
-% \end{pmatrix} \text{mag}^2.
-% \label{mag_cov:eqn}
-% \end{equation}
-%The average correlation matrix is
-%\begin{equation}
-%Cor(U,B,V,R,I)=
-%\begin{pmatrix}
-%\begin{array}{rrrrr}
-%1.00 & 0.42 & -0.18 & -0.05 & 0.12 \\
-%0.42 & 1.00 & 0.26 & -0.09 & -0.39 \\
-%-0.18 & 0.26 & 1.00 & 0.09 & -0.22 \\
-%-0.05 & -0.09 & 0.09 & 1.00 & 0.27 \\
-%0.12 & -0.39 & -0.22 & 0.27 & 1.00
-%\end{array}
-% \end{pmatrix}.
-% \end{equation}
-%The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
-%expressed as the standard deviations and
-%correlation matrix
-% \begin{equation}
-% \sigma(U-V, B-V, V-R, V-I)=
-% \begin{pmatrix}
-%0.068 & 0.034 & 0.023 & 0.053
-%  \end{pmatrix} \text{mag},
-% \label{color_sd:eqn}
-% \end{equation}
-% \begin{equation}
-% Cor(U-V, B-V, V-R, V-I)=
-%\begin{pmatrix}
-%\begin{array}{rrrr}
-%1.000 & 0.602 & -0.353 & -0.317 \\
-%0.602 & 1.000 & -0.197 & 0.082 \\
-%-0.353 & -0.197 & 1.000 & 0.647 \\
-%-0.317 & 0.082 & 0.647 & 1.000
-%\end{array}
-%\end{pmatrix}.
-%  \label{color_cor:eqn}
-% \end{equation}
-These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where direct comparison can be made.
+These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where
+a direct comparison can be made.
 \color{purple}
@@
 
-The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its direct affect on magnitude
-is
-$2.5 \log{(20/850)} \sim 0.03$ mag.  
-The implied span in $B$ magnitude based on $\beta_B$ is 0.54~mag.  Therefore $\beta_B$ cannot wholly be attributed to the flux deficit
-from the line itself.
-Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
-701~\AA, so that its direct affect on magnitude
-is
-$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the 
-presence of the line itself.
-
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
-The two sets of  $\pmb{\gamma}^i$ parameters  are significantly non-zero. 
+All elements of the two $\pmb{\gamma}$ parameter vectors  are significantly non-zero. 
 None of the 20000 links of 
@@
 with probability $1-5\times 10^{-5}$.
-%
-%There is a pair of parameter values,  $k_0^0$ and $k_1^0$, that correspond to supernovae experiencing no extrinsic effect.
-%\color{purple}
-%For observer filters $X$ and $Y$, we define $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$, $E(X-Y)=A_X-A_Y$.
-%The true extrinsic
-%extinction is
-%$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$.
-%\color{blue}
-%The true extrinsic color excess is $E^T(B-V) = A^T_B-A^T_V$, so that the total-to-selective extinction is $R^T_V=A^T_V/E^T(B-V)$.
-%Our $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$ constraints
-%do not determine $k_0^0$ and $k_1^0$, and so the extrinsic extinction and color excess per supernova are not products of our analysis.
-%
-%%our analysis does not specify their values.
-%%Recall that there are degeneracies between the intrinsic (Eqn.~\ref{ewsiv:eqn}) and
-%%extrinsic (Eqn.~\ref{dust:eqn}) parameters of our model.  Part of that degeneracy is
-%%broken by imposing $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$,
-%%but this choice does not specify the parameter values.
-%
-%
-%Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
-%rearranged as
-%\begin{equation}
-%A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
-%\end{equation}
-%Making the assumption that $R^T_V$ is the same for all supernovae,
-%its value can be determined as the slope of the linear relation between $A_X$ and $E(B-V)$.
-%
-%Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$.
-%The full set of supernovae does not coincide with the expectations of a single linear relation; rather the supernova population is peaked
-%on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
-%but can have values that extend toward lower values.
-%The assumption of a constant $R^T_V$ is not altogether correct; still we perform a linear fit that gives a slope of
-%%----- fitz11.py
-%$R^T_V=2.77 \pm 0.08$,
-%%----
-%where the uncertainty is the $68$\% credible interval and does not include model error.  
-%
-%%\begin{comment}
-%%\color{blue}
-%%Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
-%%For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
-%%$A_V=0$, and such that the ridge line 
-%%has close to constant $R^T_V$.
-%%\color{black}
-%%With this ansatz, we
-%%estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
-%% \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
-%%With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
-%%We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
-%%of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
-%%A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
-%%for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
-%%\color{black}
-%%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=5.2in]{output11/avebv.pdf}
-%   %\includegraphics[width=2.8in]{output11/rv.pdf}
-%   \caption{
-%   $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
-%   %Right: Shown for qualitative purposes,
-%   %$R^T_V=A^T_V/E^T(B-V)$ 
-%   %versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
-%   %Overplotted is the mean and standard deviation of those points in equally divided bins.
-%   Overplotted are the expected curves for the \citetalias{1999PASP..111...63F} model
-%   for specific choices of $R^F$. Note that these lines are not straight, which is apparent when comparing to the straight black $R_V=2.78$ line.
-%   \label{avebv:fig}}
-%\end{figure}
-%%\end{comment}
-%
-%
-%Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
-%parameters of a single  dust model.
-%\color{red}
-%Our model for broadband photometry does not specify how spectral features and color parameters affect the supernova spectrum, information
-%necessary to predict the magnitude extinction of dust models.
-%\color{blue}
-%The lack of correspondence between dust models and broadband extinction is quantified when we apply an $R^F_V=2.5$ SN-frame dust to the
-%observed spectra used in our sample, to yield a distribution in the quantity $R_V=A_V/(A_B-A_V)$ with mean and standard deviation of $3.11 \pm 0.35$.
-%While an accurate study of fundamental dust properties would incorporate the dust law within the model itself, we now proceed nonetheless
-%in making a connection between our model outputs and dust.
-
-We compare our model and its color-coefficient parameters $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ with the expectations of  dust models.
+
+We compare our model's parameter vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ with the expectations of  dust models.
 The 2-parameter linear model
@@
 \end{equation}
-approximately describes dust models \citep[e.g.][]{1989ApJ...345..245C}.
+approximately describes dust models \citep[for example, the wavelength dependent model of ][is linear,
+though its linearity is lost when integrated over broad-band filters]{1989ApJ...345..245C}.
 For the case of
 $R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
-\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
+\citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
 gives
 $\mathbf{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\mathbf{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
-The $F$ superscript distinguishes parameters of the \citetalias{1999PASP..111...63F} model.
+The $F$ superscript is used to distinguish parameters of the \citetalias{1999PASP..111...63F} model.
 Over the ranges of
  $R^F$ and $A^F_V$,
-and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%;
+and the wavelengths under consideration,  the values of the elements of $a$ and $b$ vary by $<5$\%;
 \color{red}
-for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in Eqn.~\ref{f99:eqn} has amplitude $<0.008$ mag.
+for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in extinction from the linear approximation of
+Eqn.~\ref{f99:eqn} has amplitude $<0.008$ mag.
 \color{black}
@@
 \end{equation}
-where $E_{\gamma^i}(B-V) \equiv  (\gamma^i_B-\gamma^i_V)k_i$.
+with $E_{\gamma^i}(B-V) \equiv  (\gamma^i_B-\gamma^i_V)k_i$ as defined in \S\ref{results:sec}.
 Our median-fit values for the $\pmb{\gamma}$ coefficients are
@@
 
-Our model $\gamma$-based vectors can be written in terms of the 
+Our model $\gamma$ vectors can be written in terms of the 
 dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\mathbf{a}$ and $\mathbf{b}$.
@@
 This result indicates that
-the allowed variations in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to near-parallel 2-dimensional
+the allowed variations in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to almost identical
+2-dimensional
 planes within
@@
 of the unit vectors corresponding to $\pmb{\gamma}^0$ and  $\pmb{\gamma}^1$ of our model (solid lines),
-and $\mathbf{a}$, $\mathbf{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\pmb{\gamma}$ vectors are chosen to intersect the origin.
+and $\mathbf{a}$, $\mathbf{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All  vectors are set to intersect the origin.
 The two perspectives show that while the four vectors point in different directions for each band combination,
 they are almost coplanar in $UVI$ (they are slightly less coplanar in $BVR$).  The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
-vectors span near-parallel planes in the 5-dimensional color space, and hence each pair can be almost entirely expressed in  terms of
-the other pair.
+vectors span near-parallel planes in the 5-dimensional color space, and hence the latter can be almost entirely expressed in terms of
+the former.
 
@@
 
-%When fixing the origin of $\pmb{\gamma}$ to zero, the $\pmb{\gamma}$ vectors are found to be coplanar with $\mathbf{a}$ and $\mathbf{b}$.
-%While the  $\gamma$ vectors define a plane,  is unspecified.
-%The linear model does not specify zero dust so the origin of the $\gamma$'s is unspecified.
-%The general result is that the magnitude planes of the linear and dust models are parallel.
-%Color changes are consistent between the two models but there is no specification of the relation between $k^0$ and $k^1$ with $A_V$ and $E(B-V)$.
-
-%The dust model expressed in Eqn.~\ref{f99:eqn} can be reparameterized as
-%\begin{equation}
-%A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
-%\label{f99:eqn}
-%\end{equation}
-%where $R=A_V/E(B-V)$.
 \color{purple}
-In principle, our linear model could accommodate for $\gamma$ any two independent vectors that span
-the plane.  We begin discussion on the specific choice of $\gamma$ returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model. 
+Our linear model would be satisfied by any two independent vectors  that span
+the plane defined by the $\pmb{\gamma}$ vectors.
+We begin discussion on the specific choice of $\pmb{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model.
 While
@@
 \end{equation}
-with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  proportional to  linear combinations of the original parameters.
-
-Our model includes a prior that the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
+with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  equal to  linear combinations of the original parameters.
+
+Our posterior
+includes a prior in which the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
+The parameters $\kappa_1$ and $\kappa_2$ are set by this prior.
 If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
-to the non-correlation of   $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ in the supernova sample.
+to    $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ being uncorrelated in the supernova sample.
 A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
 All color changes would then be confined to the $a(X)+\kappa_1 b(X)$ direction.
-This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$ .
+This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
 We use this interpretation to assign  $R^F_{eff} = \kappa_1^{-1}$ as
@@
 Variations in the value of $R^F$ (and hence $\delta R$) lead 
-the prior to impose
+the prior to  determine $\kappa_2$ as 
 \begin{equation}
@@
 This result indicates that there is a small but significant covariance between  extinction contributions due to
-deviations from an effective $R^F$ and
+fractional deviations from an effective $R^F$ and
 the color-excess parameter $E^F(B-V)$.
 
-%
-%Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
-%can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
-%The zero-correlation condition, which determines the direction of $\pmb{\gamma}^1$,  is for the coordinate values along $\pmb{\gamma}^0$ to be uncorrelated with the coordinate values along $\pmb{\gamma}^1$.
-%Our analysis yields an angle of 154\arcdeg\ between  $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
-%The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
-%Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\pmb{\gamma}^0$.
-%
-%
-%While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
-%perturbations from a fixed $R^F_0$ is
-%\begin{equation}
-%A_X = A_V \left(a(X) + \left(\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0} \right) b(X) \right).
-%\end{equation}
-%Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.
-%
-
-%To gain an intuitive understanding of how the $\kappa$ values are determined, consider the hypothetical case where
-%all supernovae experience dust with the same $R^F$.   There is only one free parameter $A^F_V$ and magnitudes are
-%constrained to move along the vector $a(X)+b(X)/R^F$.  In the fit of the linear model, the zero-covariance condition is satisfied when
-%$-\kappa_1 A^F_V + E^F(B-V)=0$,  i.e.\ when $\kappa_1=1/R^F$.  
-%Supernova magnitudes do not vary along the $\kappa_2 a(X) + b(X)$ direction.  Consequently
-%$\pmb{\gamma}^0$ is aligned with  $a(X)+b(X)/R^F$, and $\pmb{\gamma}^1$ is unconstrained.
-
-As a check of our analysis implementation, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
+As a check of our analysis implementation and our
+interpretation of $R^F_{eff}$, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
 SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
@@
 distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
-measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations which yield a median
-$R^F_{eff}$ of 2.53, which is close to
- the input $R^F=2.5$.
+measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations that together yield a median
+$R^F_{eff}$ of 2.53, showing that our effective value is close to the  $R^F=2.5$ input into the simulations.
 
@@
 global host mass.  The search for a correlation between our parameter and local star formation rate is planned for future work.
+
+XXX Analysis picks out preferered correlated.
+
 \color{black}

### 2017-08-01 apj.tex
forging onward

@@
 
-Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k_0$, and
-$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
-$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
-There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
-Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
-heavily extinguished by host-galaxy dust.
-Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output11/perobject_corner.pdf} 
-   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
-$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
-   \label{perobject:fig}}
-\end{figure}
-
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
+%Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k_0$, and
+%$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
+%$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
+%There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
+%Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
+%heavily extinguished by host-galaxy dust.
+%Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.   
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=5.2in]{output11/perobject_corner.pdf} 
+%   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
+%$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
+%   \label{perobject:fig}}
+%\end{figure}
+
+Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$.
+Their Pearson correlation coefficients  are given in the matrix
 \color{purple}
@@
 \color{black}
-Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
+The feature $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
 \citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
@@
 
+\color{purple}
 The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the $UVI$-subspace two perspectives (left and right columns)
@@
 
-\color{purple}
 Our linear model would be satisfied by any two independent vectors  that span
@@
 A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
+\label{newdust:eqn}
 \end{equation}
@@
 the effective total-to-selective extinction of our sample.
-\color{purple}
 The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$.
@@
 
-Different supernovae are expected to encounter dust with different $R^F$.
-Let us introduce a new per-supernova vector $\delta R$ such that $R^F = R^F_{eff}(1+  \delta R)$.
-Variations in the value of $R^F$ (and hence $\delta R$) lead 
-the prior to  determine $\kappa_2$ as 
+Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
+the former's distribution can be compared to the expectation for the latter.
+Figure~\ref{k0_med:fig} shows the histogram of
+median values and the ideogram of $\gamma^0_V k_0$ 
+relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
+(Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
+The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
+with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
+This distribution is given by the data, and so is not dependent of any knowledge or prior
+for the distribution of dust extinction the SN population is expected to suffer.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output11/deltagamma0_med.pdf}
+   \includegraphics[width=2.8in]{output11/deltagamma1_med.pdf}
+      \caption{
+      \color{purple} Normalized ideogram and histogram 
+      of
+median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
+(left) : $\gamma^1_V k_1-\gamma^1_V k_1|_0$,
+which  is associated with extinction corrections due to deviations away from the canonical $R^F_{eff}$ value (right).
+      \color{black}
+   \label{k0_med:fig}}
+\end{figure}
+
+We now consider the direction of $\pmb{\gamma}^1$. 
+Different supernovae are expected to encounter dust with different $R^F$;
+having  associated $\pmb{\gamma}^0$ with an $R^F_{eff}$, $\pmb{\gamma}^1$ is associated with perturbations
+away that effective value.
+Let us introduce a new parameter for each supernova $\delta R$ such that its $R^F = R^F_{eff}(1+  \delta R)$.
+Variations in the value of $R^F$ (and hence $\delta R$) with the prior of the non-correlation between $k_0$ and $k_1$ lead 
+to 
 \begin{equation}
@@
 the color-excess parameter $E^F(B-V)$.
+Figure~\ref{k0_med:fig} shows the histogram of median values and ideogram of $\gamma^1_V k_1$
+relative to that of an arbitrary supernova  $\gamma^1_V k_1|_0$.
+
+Perhaps a more instructive way to consider $k_1$ is to not view it in isolation, but rather as part of a $\{k_0,k_1\}$ pair.
+A matrix such as the one in  Eqn.~\ref{trans_I:eqn} is used to transform this pair into an $\{A_V^F, E^F(B-V)\}$ pair
+(modulo additive constants)  for each link in the Monte Carlo chains. A plot showing the expected values and 68\% credible intervals of these parameters
+for our supernova
+sample is shown in Figure~\ref{kk:fig}. 
+For reference, a line that represents $R^V_{eff}=2.44$ is overplotted.  The majority of supernovae lie within a narrow range above the line
+meaning they have $R^F > R^V_{eff}$,
+while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{eff}$.  
+These findings are consistent with previous results:
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
+A per supernova determination $R^F$ requires the specification of the magnitude and colors of supernovae that experience
+no dust, which is unspecified in our model.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output11/avebv_synth.pdf}
+      \caption{
+      \color{purple}
+      Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $k_0$ and $k_1$ parameters, for the supernova in our sample.
+      Overplotted is a line with the slope expected for $R^F=2.44$.
+      \color{black}
+   \label{kk:fig}}
+\end{figure}
 
@@
 
-\color{black}
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
-%   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
-%   \caption{
-%   Two perspectives of $UVI$- spaces
-%of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
-%   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
-%   input $R^F$ drawn from a log-normal distribution  with a mean of $\ln{2.4}$ and 0.05 standard deviation.
-%   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
-%   lines, the former is 
-%   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
-%   \label{plane_sim:fig}}
-%\end{figure}
-%
-
-Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
-the former's distribution can be compared to the expectation for the latter.
-Figure~\ref{k0_med:fig} shows the histogram of
-median values of $\gamma^0_V k_0$ 
-\color{purple}
-relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
-(Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
-\color{black}
-The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
-with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
-This distribution is given by the data, in that it is independent of any knowledge or prior
-for the distribution of dust extinction the SN population is expected to suffer.
-
-Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$
-relative to that of an arbitrary supernova  $\gamma^1_V k_1|_0$, which can be attributed to 
-extinction corrections due to deviations away from the canonical $R^F_{eff}$ value.   The distribution has a long
-negative tail and is peaked at its positive edge. Recall that our model constraints force 
-the distribution of $\gamma^1_V k_1$ has a mean of zero.
-The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
-of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
-the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$
-%\color{purple}
-%While at low  $\gamma^0_V k_0$
-%\color{black}
-%On the other hand, lower values of $\gamma^1_V k_1$
-%occur at larger values of  $\gamma^0_V k_0$.
-These findings are consistent with previous results:
-\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
-%\citet{2011ApJ...729...55F} and the above authors
-%find that supernovae with large extinction 
-%preferentially exhibit low $R^F$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{output11/deltagamma0_med.pdf}
-   \includegraphics[width=2.8in]{output11/deltagamma1_med.pdf}
-      \caption{
-      \color{purple} Normalized ideogram and histogram 
-      of
-median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
-(left) : $\gamma^1_V k_1-\gamma^1_V k_1|_0$,
-which  is associated with extinction corrections due to deviations away from the canonical $\kappa_1$ value (right).
-      \color{black}
-   \label{k0_med:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output11/deltakk.pdf}
-      \caption{
-      \color{purple}
-      $\gamma^1_V k_1-\gamma^0_V k_0|_0$ versus $\gamma^0_V k_0-\gamma^1_V k_1|_0$.
-      \color{black}
-   \label{kk:fig}}
-\end{figure}
-%
-%The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
-%are projected onto the  \citetalias{1999PASP..111...63F} values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
-%The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.24 \pm 0.16$.  
-%The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
-%which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
-%the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
-%   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
-%    \caption{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
-%onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
-%covariance between the parameters. Right: $R^F_V$ for each supernova.
-%   \label{avebv_synth:fig}}
-%\end{figure}
-%
-
-%
-%Another comparison between our model predictions with those of dust is presented in
-%Figure~\ref{avebv:fig}, which shows the expectations for measured $A(V)$, $E(B-V)$ for $R^F=1.1, 1.9, 2.5, 3.1$.
-%Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
-%non-linear.
-%Qualitatively, the $R^F \sim 2.4$  most closely matches our linear model fit.
-
-The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our  supernova
-parameters translate to  \citetalias{1999PASP..111...63F} parameters with consistent distributions, lead us to conclude that 
-$\{k_0, k_1\}$, describe for the most part the $\{ E(B-V), R\}$ parameters used
-in standard models of Milky Way dust.  Yet there do remain some small inconsistencies between our numbers and expectations from dust models.
+To summarize, in this subsection
+we conclude that the combination of
+$\{k_0, k_1\}$ describe for the most part the combination of the $\{A^F_V, E^F(B-V)\}$ parameters used
+in standard models of Milky Way dust.  
+This conclusion is based on the
+near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that 
+the distribution of $k_0$ is consistent with the expected distribution of $A^F_V$.
+Nevertheless, there do remain some small inconsistencies between our numbers and expectations from dust models.
+\color{black}
 
@@
 $E(i_o-V_o) =  -0.92 \pm   0.03$
-are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ emphasizes that this is an observed color excess.
+are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ denotes that this is an observed color excess.
 The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
@@
 \end{equation}
-where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and the fit
-parameters $e_i $.
+where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and $e_i $ are the fit
+parameters.
 
@@
 $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
-$  0.06 \pm 0.03$ 
+$  0.06 \pm 0.03$. 
 %---
-(see Figure~\ref{ebv:fig}).
 The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
@@
 \color{purple}
-The model parameters can be transformed into  the 
+The  parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)=  0.34$ can be transformed into  the 
 \citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
@@
 of our model are  shown in Figure~\ref{sn2014j:fig}. 
-Our model predictions provide a significantly better match to the data
-despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
-Differences in the color predictions between our model and the pure dust model are
-apparent,
-particularly in the $B-V$ and  $R-V$ colors.  Our model has shallower decline in color excess with increasing wavelength.
-(Refer to  Eqn.~\ref{res_I:eqn} to see the deviation in magnitude of our model away from the dust model.)
+Significant differences between the projection and the data is apparent
+in the $B-V$ and  $R-V$ colors.
+The data and the full model both have shallower decline in color excess with increasing wavelength.
 The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
@@
 \end{equation}
-which imply $R^F= 0.59^{+ 0.53}_{-0.48}$.
-
+which together give $R^F= 0.59^{+ 0.53}_{-0.48}$.
 \color{black}
@@
 \end{equation}
-In all aspects Model~II is identical to the Model~I except for the addition of the term $\pmb{\delta} D$,
-which enters in the mean intrinsic
-absolute magnitudes.  Model~I is nested in Model~II at $\pmb{\delta}=0$.
-Each supernova has an intrinsic $D$ parameter that is linearly related to the intrinsic
+In all aspects Model~II is identical to Model~I except for the addition of the term $\pmb{\delta} D$: for $\pmb{\delta}=0$ and arbitrary $D$, Model II
+and Model~I are the same.
+The new term contributes to the mean intrinsic
+absolute magnitudes. 
+Each supernova has an intrinsic $D$ parameter that is linearly related to
 absolute magnitudes through the global coefficients $\pmb{\delta}$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
@@
 $\langle D\rangle=0$
-to specify the (arbitrary in our linear model) definition of zero color.  We assign a prior on the ensemble amplitudes of $D$ to break the
+to specify the zeropoint color.  We assign a prior on the amplitude of the ensemble of $D$ to break the
 degeneracy $\pmb{\delta} \rightarrow a\pmb{\delta}$, $D \rightarrow a^{-1}D$: as described
@@
 A sign degeneracy in $a$ remains.
-In contrast to $\pmb{\gamma}$, our MCMC chains migrate between sign-degenerate solutions in  $\pmb{\delta}$.  We make
+In contrast to our previous experience with $\pmb{\gamma}$ in Model~I, our MCMC chains migrate between
+the sign-degenerate solutions in  $\pmb{\delta}$.  We make
 no attempt to resolve this degeneracy in the model.
@@
 $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ were set to be in the neighborhood of the best fit of Model~I
-to maintain their correspondence between the two models. Our finite MCMC chains do not migrate away from these ranges.
+to maintain their correspondence between the two models.
+Our finite MCMC chains do not migrate away from these ranges.
+The initial condition of $\pmb{\delta}$ is set to zero.
 \color{black}
@@
 results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
-are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the reduction of the standard
+are consistent  to well within 1$\sigma$ uncertainties.  The most significant change is in the reduction of the standard
 deviations of the magnitude residuals $\sigma_X$
@@
 In the full 5-dimensional space,
-the point $\delta_X=0$, i.e.\ no effect on magnitude by a third parameter,  lies on the 85\%-ile contour.
+the point $\delta_X=0$, i.e.\ the nested Model~I with no effect on magnitude by a third parameter,  lies on the 85\%-ile contour.
 Model~II has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ degeneracy that results in a bimodal posterior.
@@
 The distributions of both sources of color excess $E(B-V)$ and
- $E_\delta(B-V) \equiv   (\delta_B-\delta_V)D$ are shown in the ideograms in Figure~\ref{ebv:fig}.
+ $E_\delta(B-V) \equiv   (\delta_B-\delta_V)D$ are shown in the ideograms 
+ and histogram in Figure~\ref{ebv:fig}.
  (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
+The range of $B-V$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
+component.  
 The standard deviations of  the median $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
@@
 mag respectively.
-The range of $B-V$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
-component.   The $E_\delta(B-V)$ standard deviation is comparable to its measurement uncertainty per-supernova, showing that
-the significance of $\pmb{\delta}$
-is drawn from the ensemble of objects and
-would be difficult to deduce from the color excess of individual supernovae.
+The $E_\delta(B-V)$ standard deviation is comparable to its measurement uncertainty per-supernova.
+The color excesses of individual supernovae have low signal-to-noise 
+and the significance of $\pmb{\delta}$
+is drawn from the ensemble of objects.
 
@@
 
-The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta U}=\delta_U D$ are given in the matrix
+Each supernova is described by its parameters
+ $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta U}=\delta_U D$.
+ Their Pearson correlation coefficients are given in the matrix
 \color{purple}
@@
 \color{black}
-The distributions for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, 
-$E_{\gamma^1}(B-V)$, and
-$E_{\delta}(B-V)$ for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
+Their values for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
+There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
+Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
+heavily extinguished by host-galaxy dust.
+Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.
+
+%The distributions for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, 
+%$E_{\gamma^1}(B-V)$, and
+%$E_{\delta}(B-V)$ for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
 
@@
 \color{purple}
-consistent with zero.
+directed by the prior and are ultimately consistent with zero.
 Their independence implies that a single physical parameter is not being artificially attributed to two
 model parameters.  One could have expected this to occur since our linear model does not precisely
-describe broad-band magnitudes that are non-linear with respect to dust parameters. A strong
-correlation between the parameters would of complicated any claims of the detection of a third independent supernova parameter.
+describe the non-linearity between broad-band magnitudes and dust parameters. A
+correlation 
+between the parameters despite the prior would of complicated any claims of the detection of a third independent supernova parameter.
 \color{black}
@@
 $\pmb{\epsilon}_{\gamma^1} $
-quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that most
+quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that just as in Model~I most
 of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
@@
 has a significant projection onto the dust plane, as the $\pmb{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
-The transformation yields
+The transformation between the new set of $\pmb{\gamma}$'s and dust parameters yields
 a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, slightly shifted higher relative to the results of Model~I.

### 2017-08-01 fitz11.py

@@ -108,7 +108,7 @@ norm_dAdAv = numpy.dot(dAdAv, dAdAv)
 cross = numpy.dot(dAdebv, dAdAv)
 
 a = numpy.array([[norm_dAdAv,cross],[cross,norm_dAdebv]])
-
+a_save = numpy.array(a)
 tmat = []
 res = []
 c_n = []
@@ -464,26 +464,28 @@ for i in xrange(ebv.shape[2]):
 
 # # Transform native parameters onto the Fitzpatrick plane
 
-# # The native E(B-V) parameters
+# The native E(B-V) parameters
 # ebv  = (fit['gamma'][:,1]-fit['gamma'][:,2])[:,None] * fit['k']
 # ebv = numpy.array([ebv,(fit['rho1'][:,1]-fit['rho1'][:,2])[:,None] * fit['R']])
-
-# # For each link recalculate the transformation matrix and get the Fitzpatrick values
-# ebvav=[]
-# for i in xrange(ebv.shape[1]):
-#   tmat_=[]
-#   for s in ['gamma','rho1']:
-#     ga=fit[s][i,:]
-#     y = numpy.array([numpy.dot(ga,dAdebv),numpy.dot(ga,dAdAv)])
-#     ans = numpy.linalg.solve(a,y)
-#     tmat_.append(ans)
-#   tmat_=numpy.array(tmat_)
-#   tmat_ = numpy.transpose(tmat_)
-#   inner = []
-#   for j in xrange(ebv.shape[2]):
-#     inner.append(numpy.dot(tmat_,ebv[:,i,j]))
-#   ebvav.append(inner)
-# ebvav = numpy.array(ebvav)
+ebv  = fit['k']
+ebv = numpy.array([ebv,fit['R']])
+a=a_save
+# For each link recalculate the transformation matrix and get the Fitzpatrick values
+ebvav=[]
+for i in xrange(ebv.shape[1]):
+  tmat_=[]
+  for s in ['gamma','rho1']:
+    ga=fit[s][i,:]
+    y = numpy.array([numpy.dot(ga,dAdAv),numpy.dot(ga,dAdebv)])
+    ans = numpy.linalg.solve(a,y)
+    tmat_.append(ans)
+  tmat_=numpy.array(tmat_)
[…]

### 2017-08-01 view11.py

@@ -169,7 +169,7 @@ crap = fit['gamma'][:,2][:,None]*fit['k']
 crap = crap-crap[:,0][:,None]
 plt.hist(numpy.median(crap,axis=0),bins,label='median',normed=True,alpha=0.5,width=0.025)
 plt.hist(crap.flatten(),bins,label='ideogram',normed=True,alpha=0.5)
-plt.xlabel(r'$\gamma^0_2 k_0 - \gamma^0_2 k_0|_0\approx A^F_V|_{R^F=2.44}$')
+plt.xlabel(r'$\gamma^0_2 k_0 - \gamma^0_2 k_0|_0\approx A^F_V|_{R^F_{eff}=2.44}$')
 plt.legend()
 plt.tight_layout()
 pp = PdfPages('output11/deltagamma0_med.pdf')
@@ -189,6 +189,22 @@ pp = PdfPages('output11/deltagamma1_med.pdf')
 plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
+
+# #conversion to Fitzpatrick parameters A and E(B-V)
+# tmat= numpy.array([[2.82,1.15],[-5.27,0.72]])
+# tmat = tmat.T
+# shit=[]
+# for i in xrange(fit['k'].shape[1]):
+#     knorm =  numpy.median(fit['k'][:,i]*(fit['gamma'][:,1]-fit['gamma'][:,2]))
+#     Rnorm = numpy.median(fit['R'][:,i]*(fit['rho1'][:,1]-fit['rho1'][:,2]))
+#     shit.append(numpy.dot(tmat,numpy.array([knorm,Rnorm])))
+# shit=numpy.array(shit)
+# print shit.shape
+# plt.scatter(shit[:,1],shit[:,0])
+# plt.plot([-.1,.5],[-2.44*.1,2.44*.5])
+# plt.show()
+
+# wefwe
 
 bins=numpy.arange(-0.35,0.1,0.02)
 plt.hist(numpy.median((fit['rho1'][:,2])[:,None]*fit['R'],axis=0),bins,label='median',normed=True,alpha=0.5,width=0.01)
@@ -213,6 +229,7 @@ plt.tight_layout()
 plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
+
 
[…]

### 2017-08-02 apj.tex
Fire!

@@
 The transformation between the new set of $\pmb{\gamma}$'s and dust parameters yields
-a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, slightly shifted higher relative to the results of Model~I.
-\color{black}
-
-\color{red}
-The significance of the results is evaluated using simulated datasets.
+a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, shifted to slightly  higher values relative to the results of Model~I.
+
+The significance of the $\pmb{\delta}$ measurement is evaluated using simulated datasets.
 For one set of tests, we realize 50 random realizations of data with input  parameters equal to the median values of the 
 parameter posteriors found in
-\S\ref{model:sec}, and using the same noise as our data.  The input $\pmb{\delta}$-vector is set to zero.
-Figure~\ref{pvalues_delta2:fig} shows results of fits of these null-realizations in comparison to the results using the real data.
-The influence of the third parameter on magnitudes is measured by the squared amplitude  $\delta^2$.
-Depending on the choice between the  $-1$, 0, or $1$-sigma
-value of  $\delta^2$, the data value is in the largest 90--98\%-ile.  Recall that in the Bayesian posterior
+\S\ref{model:sec}, and using the same noise as our data.  To represent the null hypothesis, the input $\pmb{\delta}$-vector is set to zero.
+Figure~\ref{pvalues_delta2:fig} shows results of fits of these null-realizations next  to the results from the real data.
+One statistic shown is the median and 68\% credible interval of the squared amplitude  $\delta^2$.
+As $\delta^2$ measures the magnitude response due to the third parameter, it is expected to have a small value
+when such a new parameter is not relevant.
+Comparing separately the  $-1$, 0, and $1$-sigma
+values of  the credible interval of our data relative to those from the simulations, we obtain
+three different $p$-values ranging from 0.90--0.98, indicating that the data result is incompatible with the null hypothesis. 
+As a point of comparison, recall that in the Bayesian posterior
+the null result
 $\pmb{\delta}=0$ lies on the 85\%-ile contour.
@@
 
-Figure~\ref{pvalues_delta2:fig} also shows the 
+An interesting feature of $\pmb{\delta}$ is that its direction lies close to the plane defined by the
+$\pmb{\gamma}$ vectors.
+This leads to the concern that our model and analysis  could spontaneously generate a third
+vector almost degenerate with the others, despite the prior for the independence of $k_0$, $k_1$, and $D$.
+This hypothesis is tested using the 
 relative projection of $\pmb{\delta}$  perpendicular to the plane defined by the $\pmb{\gamma}$'s, $\delta_\perp^2/\delta^2$,
-for the 50 null realizations
-and our data.  The data gives smaller value than all the realizations for $-1$, 0, or $1$-sigma values.  
-Our model and analysis are unlikely to spuriously produce a $\pmb{\delta}$ as closely aligned with the $\pmb{\gamma}$--plane
-as derived from our data, as its small  $\delta_\perp^2/\delta^2$  is not expected from a null signal at $>98$\%.
-
-Parameter biases that arise as part of our analysis methodology are measured through simulation.
+for the same 50 null simulations that were just described.
+Figure~\ref{pvalues_delta2:fig} shows  that for none of the simulations does our analysis produce 
+ $\delta_\perp^2/\delta^2$ as low as that from our data.  The $p$-values $>0.98$ indicate that the result from our data
+ is incompatible with the null hypothesis.
+
+Potential biases in our results are measured through simulation.
 We realize 50 random realizations of data with input  parameters equal to the median values found in
-this Section, except for $\pmb{\delta}$ which is assigned the modes presented earlier, and the same noise as our data.
+this Section, except for $\pmb{\delta}$ which is assigned the, and the same noise as our data.
 The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.
@@
 biases in the best fit value.
-The stack of  $\pmb{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias in the
-modes from the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ relative to the stacked modes $(-1.10, -0.98, -0.41, -0.09, 0.40)$
-that is smaller than the statistical uncertainty of a single analysis.
+The stack of  $\pmb{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias between
+the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ and the mode of  the stacks $(-1.06, -0.95, -0.41, -0.11, 0.40)$.
+We do not consider this bias to be an issue in our detection of a third parameter, as the difference is significantly
+smaller than the statistical uncertainty of a single analysis and the length of the vector changes by $< 3\%$.
 The posterior stacks for the other global parameters 
@@
 regression dilution \citep{spearman04}.
-\color{black}
 
@@
    \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
-            \caption{Stacked $\pmb{\delta}$ posterior contours for 50 independent simulated data sets with input $\pmb{\delta}=0$.
+            \caption{Stacked $\pmb{\delta}$ posterior contours for 50 independent simulated data sets.
             The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
@@
 
-\color{purple}
 The Model~II fit of SN~2014J \citet{2014ApJ...788L..21A}  data 
-gives $k_0$ and $k_1$ that qualitatively similar to  those from the fit to Model~I but with much larger uncertainties.
+gives $k_0$ and $k_1$ that are qualitatively similar to  those from the fit to Model~I but with much larger uncertainties.
 These parameters are now highly correlated with $D$, which itself is consistent with zero.  The results resemble those of
@@
 \subsection{Light Curve Shape}
-The motivation of our analyses was to standardize supernovae based on spectral features and colors around peak brightness.
+The motivation of our analyses was to standardize supernovae based on spectral features and colors at peak brightness.
 As such, our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
-We now examine this in more depth using the intrinsic--extrinsic Model~II of \S\ref{model2:sec}.
+We now examine the effect of shape in more depth using the intrinsic--extrinsic Model~II of \S\ref{model2:sec}.
 The connection between the spectrum at peak and the light-curve decline rate, seen through
 the correlation between $EW_{Si}$ and the SALT2 $x_1$ light-curve shape parameter, is verified
-for our sample \citep{2017Chotard}.
+for our sample in \citet{2017Chotard}.
 On the other hand, there is no such correlation seen between $A_{\delta I} = \delta_I D$ and $x_1$, as shown in Figure~\ref{x1:fig}. 
@@
 
-We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta x_1$ to the 
-intrinsic magnitude; the credible intervals
+A direct consideration of light-curve shape is
+performed by explicitly adding to Model~II a new linear term $\zeta x_1$ to the 
+intrinsic magnitude. The credible intervals
 from this analysis are given in Table~\ref{globalx1:tab}; there are no significant changes with respect to the reference model. 
 Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: $\zeta_R/\zeta_V$
-has the largest significance at at $1\sigma$.
-The evidence for a non-zero $\pmb{\delta}$ remains as seen in the values of $\delta_X/\delta_I-1$ in Table~\ref{globalx1:tab}, meaning that it is not an artifact of
-having neglected light-curve shape.
+has the largest significance  at $1\sigma$.
+The evidence for the effect of a third parameter persists in the significant  non-zero  $\delta_X/\delta_I-1$ values
+in Table~\ref{globalx1:tab}, reinforcing the evidence that the $D$ of Model~II is not primarily related to light-curve shape.
 
@@
       less than and greater than  $\log{(M/M_\sun)}=10$.
-Right: Histogram of the two-tailed p-value from  the Kolmogorov-Smirnov test applied to all links in the Monte Carlo chains.
+Right: Histogram of the two-tailed $p$-value from  the Kolmogorov-Smirnov test applied to all links in the Monte Carlo chains.
    \label{childress:fig}}
@@
 The Kolmogorov-Smirnov test is applied on the distribution of $A_{\delta I}$ of both low- and high-mass samples for
-each Monte Carlo link.  The resulting distribution of the two-tailed p-value (a high value meaning that we cannot
+each Monte Carlo link.  The resulting distribution of the two-tailed $p$-value (a high value meaning that we cannot
 reject the hypothesis of the samples are the same) over all chains is shown in Figure~\ref{childress:fig}. The distribution is broad

### 2017-08-03 apj.tex
version to send to collaboration

@@
 \subsection{Light Curve Shape}
+\label{shape:sec}
 The motivation of our analyses was to standardize supernovae based on spectral features and colors at peak brightness.
@@
 \subsection{SiII Line Velocity}
-
+\label{velocity:sec}
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
@@
 but this correlation
-is absorbed into the equivalent-width corrections, which give higher likelihood as they give lower residual dispersions $C_c$.
+is absorbed into the equivalent-width corrections.
+
+\color{red}
+The results from  \S\ref{shape:sec} and this subsection demonstrate the model handling simultaneous
+magnitude corrections 
+of  correlated observables.  The model prefers corrections that reduce intrinsic dispersion.
+The free parameters that describe the intrinsic dispersion enter the model likelihood through  the term $(\det{C_c})^{-0.5}$, which gives higher likelihood 
+for lower dispersions. This leads to magnitude corrections being preferentially
+attributed to $EW_{Ca}$ over $v_{Si}$, and  $EW_{Si}$ over SALT2 $x_1$.
+\color{black}
 
@@
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-The difference between high-mass hosts is
-not significant; we calculate  average
+The average $A_{\delta I}$'s of the two subsamples are
 %---
-$\langle A_{\delta I} \rangle=     -0.0002 \pm    0.0089 $,
-$\langle A_{\delta I} \rangle= 0.0025 \pm   0.0073 $ 
-for low- and high-mass hosts respectively.
+$\langle A_{\delta I} \rangle=     -0.0002 \pm    0.0089$ mag,
+$\langle A_{\delta I} \rangle= 0.0025 \pm   0.0073 $ mag
+for low- and high-mass hosts respectively: there is no significant difference between them.
 
@@
 The Kolmogorov-Smirnov test is applied on the distribution of $A_{\delta I}$ of both low- and high-mass samples for
-each Monte Carlo link.  The resulting distribution of the two-tailed $p$-value (a high value meaning that we cannot
-reject the hypothesis of the samples are the same) over all chains is shown in Figure~\ref{childress:fig}. The distribution is broad
-over the range from 0 to 1.  We are thus unable to distinguish the $A_{\delta I}$ distributions from low- and high-mass samples.
-
-%Using the SNfactory sample,
-%\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star formation rate, rather than
-%global host mass.
-\subsection{Physical Motivation}
-
-A straightforward explanation for the third color term $\pmb{\delta} D$ is that it describes the absorption due to some form of dust
-that does not obey the  \citetalias{1999PASP..111...63F} model.
-Supernova light may encounter two
+each Monte Carlo link.
+The resulting distribution of the two-tailed $p$-value  over all chains spans the possible range from 0 to 1, as shown in Figure~\ref{childress:fig}.
+We are unable to perform a constraining test of whether the $A_{\delta I}$ distributions from low- and high-mass samples
+are drawn from a common distribution.
+
+A more pertinent test is to see if a host-mass bias persists in Hubble diagram residuals
+derived from a recalibration of SN~Ia absolute magnitudes using the parameters of the current article.
+The calibration of absolute magnitudes goes beyond the design of our model and analysis (see \S\ref{standard:sec}), so this test
+in not presented here.
+
+\subsection{Improving SNe~Ia as Standard Candles}
+\label{standard:sec}
+The approach of our analysis is to mine for new supernova properties based on colors and spectral features.
+Our model and results do carry information on absolute magnitude but are not tailored for its study.
+The grey parameter $\Delta$ with its $0.10$ mag dispersion, while containing information on absolute magnitude, 
+also conflates
+contributions from peculiar velocities and measurement uncertainties.  Studies
+focused on improving SNe~Ia as standard candles should modify  our model to
+distinguish between these sources of greyness and dispersion.
+Our
+mining exercise uses all supernovae that pass quality cuts, the approach taken by previous
+exploratory work.  In contrast, the calibration of SNe~Ia as standard candles needs procedures such
+as cross-validation to avoid overtraining.
+An absolute magnitude calibration using the parameters identified in this analysis is left to future work.
+
+\subsection{Physical Interpretation of the Intrinsic Color Parameter}
+
+Based on its direction, a straightforward explanation for the third color term $\pmb{\delta} D$ is that it describes the absorption due to some form of dust
+that does not exactly obey the  \citetalias{1999PASP..111...63F} model.
+In one scenario,
+supernova light can encounter two
 dusts, first a 
-circumstellar dust that can produce lower visual-to-selective extinction
+circumstellar dust that produces relatively low visual-to-selective extinction
 \citep{2008ApJ...686L.103G} and then
 an interstellar form  that resembles the \citetalias{1999PASP..111...63F} model.
-Qualitatively,  the decrease in magnitude change toward redder wavelengths, seen in Figure~\ref{deltaratio:fig}, matches the 
+To first order $\pmb{\delta}$ behaves like standard dust;   $>98$\% of its length projects onto the expectation of  \citetalias{1999PASP..111...63F}
+with constant $R^F$.
+The departure from   \citetalias{1999PASP..111...63F}
+can be seen qualitatively; the decrease in magnitude change toward redder wavelengths, seen in Figure~\ref{deltaratio:fig}, matches the 
 expectation for the circumstellar form of dust.
-The projection of  $\pmb{\delta}$ onto the plane expected by dust is significant at the $>98$\% level.  However, we
+However, we
 lack the signal-to-noise to show consistency with this explanation.
-Our best-fit  $\delta_X$ do not share the same sign, as expected for dust.
+The best-fit elements $\delta_X$ do not all share the same sign, as would have been expected for dust.
 Confining ourselves to the 98\% of   $\pmb{\delta}$ that lies on the dust plane, associating 
@@
 
-An alternative explanation for the $\pmb{\delta} D$ term is that it captures an intrinsic dust parameter that is independent of $R^F$.
-Supernova light encounters one dust with a degree of freedom beyond that modeled by \citetalias{1999PASP..111...63F}.
+An alternative scenario is that supernova light encounters one dust with a degree of freedom beyond that modeled by \citetalias{1999PASP..111...63F}.
+The $\pmb{\delta} D$ term represents an intrinsic dust parameter that is independent of $R^F$.
 The extra degree-of-freedom could be associated with the skewness in the distribution of dust grains, as an increase of smaller dust grains
@@
 dust models.
-
-Based on the above models, a dust-based identification and explanation of the extra color parameter would be greatly enhanced with
-extended wavelength coverage into the UV.
-
-\subsection{Improving SNe~Ia as Standard Candles}
-The model and results presented here
-carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represents Hubble residuals after
-application of the model, and its  $0.10$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
-measurement uncertainties.
-This analysis was designed to mine information from the SNfactory data set, and so the results presented here
-are specific to it both in terms of its population distribution and potentially noise.  This is the approach taken by previous
-exploratory work.
-A new analysis that explicitly measures out-of-sample performance is required to robustly determine how
-well the addition of third parameter inferred from one data set can be used to measure supernova distances
-of an independent set.
 
@@
 \color{black}
-disfavors the original model and gives the first identification of  a new parameter that affects supernova
+gives the first identification of  a new parameter that affects supernova
 colors in a manner that is distinct from the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
@@
 global host mass.  The search for a correlation between our parameter and local star formation rate is planned for future work.
-
-XXX Analysis picks out preferered correlated.
 

### 2017-09-05 apj.tex
new version after responses

@@
 \begin{abstract}
-\color{purple}
 Through empirical modeling of its observed signal, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined,
@@
 in current models, and so consequently can lead to more precise per-object distances with smaller systematic uncertainties.  In this article, we present   
-\color{black}
 an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
@@
 but  influence color can be included in such models.
-\citet{2016arXiv160904470M} take the approach of modeling the distribution of their parameters, to find that
+\citet{2017ApJ...842...93M} take the approach of modeling the distribution of their parameters, to find that
 scatter in the Hubble diagram is better explained by a combination of intrinsic color dispersion and
@@
 
-\color{purple}
 The model as written has degeneracies that need to be constrained in order for fits to converge.
@@
 we break that degeneracy  by setting consistent initial conditions that succeed in keeping indices consistent over all analysis chains.
-\color{black}
 
@@
 This covariance matrix prior is recommended by STAN \citep{stan}, the Monte Carlo program we use to evaluate the model.
- \color{purple}
  We find that a simpler intrinsic dispersion model with no correlations between bands
@@
  the other parameters.
-\color{black}
 
@@
 the Monte Carlo chains have not converged to the stationary posterior distribution.
-\color{purple}
 For four selected colors, a plot of the
 observed versus deduced intrinsic colors and the histogram of their differences
-\color{black}
 are shown in Figure~\ref{residual:fig}. 
@@
             \caption{
-            \color{purple}
             Observed versus deduced intrinsic colors for four selected colors.  Plotted on the right for each color
 is the histogram of the difference between the observed and intrinsic colors.
-\color{black}
             \label{residual:fig}}
@@
 
-\color{purple}
 The fit $\Delta$'s are highly correlated between supernovae.  To aid in visualization, we remove much of this
@@
  $0.0015$ and $0.0085$ respectively, and so have peculiar velocities that can cause a significant magnitude offset.
-\color{black}
+
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
    \caption{
-   \color{purple}
    Normalized ideogram and histogram of the medians of the grey offset relative to one arbitrary supernova, $\Delta-\Delta|_0$.  
-   \color{black}
    \label{hist:fig}}
@@
 than the dispersion in $\Delta$.
-\color{purple}
 Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in $V$ and colors with respect to $V$ are
@@
  \end{multline}
-\color{black}
 These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where
 a direct comparison can be made.
-\color{purple}
 %model11_rubin.py
@@
 with a strict equality), we find significant shifts in all slope parameters  and smaller statistical uncertainties.
-\color{black}
 
@@
 Their Pearson correlation coefficients  are given in the matrix
-\color{purple}
 \begin{multline}
@@
 \end{multline}
-\color{black}
 
 We find weak correlations between our color-excess parameters and the input features; 
-\color{purple}
 only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}(B-V)$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
-\color{black}
 The feature $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
@@
 and the wavelengths under consideration,  the values of the elements of $a$ and $b$ vary by $<5$\%;
-\color{red}
 for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in extinction from the linear approximation of
 Eqn.~\ref{f99:eqn} has amplitude $<0.008$ mag.
-\color{black}
 
@@
 
-\color{purple}
 The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the $UVI$-subspace two perspectives (left and right columns)
@@
    \caption{
-   \color{purple}
    Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
@@
       \caption{
-      \color{purple} Normalized ideogram and histogram 
+      Normalized ideogram and histogram 
       of
@@
 which  is associated with extinction corrections due to deviations away from the canonical $R^F_{eff}$ value (right).
-      \color{black}
    \label{k0_med:fig}}
@@
       \caption{
-      \color{purple}
       Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $k_0$ and $k_1$ parameters, for the supernova in our sample.
       Overplotted is a line with the slope expected for $R^F=2.44$.
-      \color{black}
    \label{kk:fig}}
@@
 Nevertheless, there do remain some small inconsistencies between our numbers and expectations from dust models.
-\color{black}
-
-\subsection{SN 2014J in the Context of Our Model}
-\label{sn2014j:sec}
-SN~2014J   is one of several SNe~Ia that exhibit colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
-2014arXiv1411.3332J,
-2014ApJ...795L...4K, 2015ApJ...805...74B}.
-The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
-spectral evolution that 
-suffers very low galactic and host reddening
-\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A,
-2017arXiv170101422H}.
-The overall higher photospheric velocities of
-SN~2014J are unimportant  based on the findings of  \S\ref{results:sec}.
-
-Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
-The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
-following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
-Their values 
-$E(U_o-V_o) =   2.23 \pm   0.03$,
-$E(B_o-V_o) =   1.28 \pm   0.04$,
-$E(R_o-V)_o =  -0.47 \pm   0.03$,
-$E(i_o-V_o) =  -0.92 \pm   0.03$
-are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ denotes that this is an observed color excess.
-The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
-wavelengths 
-3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  Despite the imperfect correspondence our synthetic passbands
-and those used for the observations,
-these data are fit to our model
-\begin{equation}
-E(X_o-V_o) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
-\end{equation}
-where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and $e_i $ are the fit
-parameters.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output11/sn2014j.pdf} 
-   \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.
-   \color{purple}
-   In addition to the prediction
-   of our model, also shown is the prediction from the projection
-   of our results onto the \citetalias{1999PASP..111...63F} extinction model.  Bottom: Residual color excess
-   between the data and models, with a dotted line at zero shown for reference.
-   \color{black}
-   \label{sn2014j:fig}}
-\end{figure}
-
-The best-fit parameters for SN~2014J are 
-%----
-$e_0= 2.60$, $ e_1=-1.89$ with covariance
-%----
-\begin{equation}
-\begin{pmatrix}
-\begin{array}{rr}
-0.050 & 0.058 \\
-0.058 & 0.315
-\end{array}
-\end{pmatrix}.
-\end{equation}
-The predicted values of observed $E(B_o-V_o)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
-overlap with the data within the error bars.
-
-In the fit to our model, the observed color excess is attributed to 
-%----
-$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
-%-----
-contributions.
-Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
-objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
-%---
-$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
-$  0.06 \pm 0.03$. 
-%---
-The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
-span of supernovae used to train the coefficients of the model, which is not unexpected if
-attributable to dust.
-
-\color{purple}
-The  parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)=  0.34$ can be transformed into  the 
-\citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
-assuming that  SN~2011fe has zero extinction.  The colors predicted by this \citetalias{1999PASP..111...63F}--component
-of our model are  shown in Figure~\ref{sn2014j:fig}. 
-Significant differences between the projection and the data is apparent
-in the $B-V$ and  $R-V$ colors.
-The data and the full model both have shallower decline in color excess with increasing wavelength.
-The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
-in Figure 3 of  \citet{2014ApJ...788L..21A}, who fit
-UV through NIR data to obtain $R_V^F=1.4$ and $E^F(B-V)=1.37$.
-Notwithstanding their bias respect to the data, we present the transformed dust parameters
-$A^F_V=0.77$ and $E^F(B-V)=1.28$ and covariance
-\begin{equation}
-\begin{pmatrix}
-\begin{array}{rr}
-0.430 & -0.004 \\
--0.004 & 0.007
-\end{array}
-\end{pmatrix},
-\end{equation}
-which together give $R^F= 0.59^{+ 0.53}_{-0.48}$.
-\color{black}
+
+%
+%\subsection{SN 2014J in the Context of Our Model}
+%\label{sn2014j:sec}
+%SN~2014J   is one of several SNe~Ia that exhibit colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
+%2014arXiv1411.3332J,
+%2014ApJ...795L...4K, 2015ApJ...805...74B}.
+%The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
+%spectral evolution that 
+%suffers very low galactic and host reddening
+%\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A,
+%2017arXiv170101422H}.
+%The overall higher photospheric velocities of
+%SN~2014J are unimportant  based on the findings of  \S\ref{results:sec}.
+%
+%Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
+%The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
+%following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
+%Their values 
+%$E(U_o-V_o) =   2.23 \pm   0.03$,
+%$E(B_o-V_o) =   1.28 \pm   0.04$,
+%$E(R_o-V)_o =  -0.47 \pm   0.03$,
+%$E(i_o-V_o) =  -0.92 \pm   0.03$
+%are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ denotes that this is an observed color excess.
+%The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
+%wavelengths 
+%3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  Despite the imperfect correspondence our synthetic passbands
+%and those used for the observations,
+%these data are fit to our model
+%\begin{equation}
+%E(X_o-V_o) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
+%\end{equation}
+%where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and $e_i $ are the fit
+%parameters.
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=5.2in]{output11/sn2014j.pdf} 
+%   \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.
+%   \color{purple}
+%   In addition to the prediction
+%   of our model, also shown is the prediction from the projection
+%   of our results onto the \citetalias{1999PASP..111...63F} extinction model.  Bottom: Residual color excess
+%   between the data and models, with a dotted line at zero shown for reference.
+%   \color{black}
+%   \label{sn2014j:fig}}
+%\end{figure}
+%
+%The best-fit parameters for SN~2014J are 
+%%----
+%$e_0= 2.60$, $ e_1=-1.89$ with covariance
+%%----
+%\begin{equation}
+%\begin{pmatrix}
+%\begin{array}{rr}
+%0.050 & 0.058 \\
+%0.058 & 0.315
+%\end{array}
+%\end{pmatrix}.
+%\end{equation}
+%The predicted values of observed $E(B_o-V_o)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
+%overlap with the data within the error bars. 
+%
+%
+%
+%In the fit to our model, the observed color excess is attributed to 
+%%----
+%$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
+%%-----
+%contributions.
+%Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
+%objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
+%%---
+%$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
+%$  0.06 \pm 0.03$. 
+%%---
+%The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
+%span of supernovae used to train the coefficients of the model, which is not unexpected if
+%attributable to dust. 
+%
+%\color{purple}
+%The  parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)=  0.34$ can be transformed into  the 
+%\citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
+%assuming that  SN~2011fe has zero extinction.  The colors predicted by this \citetalias{1999PASP..111...63F}--component
+%of our model are  shown in Figure~\ref{sn2014j:fig}. 
+%Significant differences between the projection and the data is apparent
+%in the $B-V$ and  $R-V$ colors.
+%The data and the full model both have shallower decline in color excess with increasing wavelength.
+%The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
+%in Figure 3 of  \citet{2014ApJ...788L..21A}, who fit
+%UV through NIR data to obtain $R_V^F=1.4$ and $E^F(B-V)=1.37$.
+%Notwithstanding their bias respect to the data, we present the transformed dust parameters
+%$A^F_V=0.77$ and $E^F(B-V)=1.28$ and covariance
+%\begin{equation}
+%\begin{pmatrix}
+%\begin{array}{rr}
+%0.430 & -0.004 \\
+%-0.004 & 0.007
+%\end{array}
+%\end{pmatrix},
+%\end{equation}
+%which together give $R^F= 0.59^{+ 0.53}_{-0.48}$.
+%\color{black}
+%
 
@@
 
-\color{red}
 We impose
@@
 The initial condition of $\pmb{\delta}$ is set to zero.
-\color{black}
 
@@
 deviations of the magnitude residuals $\sigma_X$
-\color{red}
 in the $U$ and $B$ bands.
-\color{black}
 
@@
 \end{table}
-
-\color{red}
 
@@
 \end{figure}
-
-\color{black}
 
@@
  Their Pearson correlation coefficients are given in the matrix
-\color{purple}
 \begin{multline}
@@
 \end{multline}
-\color{black}
 Their values for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
@@
 ($E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$)  parameters are
-\color{purple}
 directed by the prior and are ultimately consistent with zero.
@@
 between the parameters despite the prior would of complicated any claims of the detection of a third independent supernova parameter.
-\color{black}
 
@@
 
-\color{red}
 The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$) can be expressed 
 in terms of the $\mathbf{a}$ and $\mathbf{b}$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
-\color{black}
 \begin{equation}
@@
 of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
-\color{red}
  $\pmb{\delta}$ too
@@
 Model~I shown in Figure~\ref{sn2014j:fig}, except for larger error bars for the color excesses projected onto the dust model.
-\color{black}
 
@@
 
-\color{red}
 The results from  \S\ref{shape:sec} and this subsection demonstrate the model handling simultaneous
@@
 attributed to $EW_{Ca}$ over $v_{Si}$, and  $EW_{Si}$ over SALT2 $x_1$.
-\color{black}
 
@@
 This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
-\citet{2016arXiv160904470M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
+\citet{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
 To explore whether the Hubble residual may be due to unaccounted color,
 we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
-\color{purple}
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
@@
 can flatten extinction in the red and enhanced steepness in the UV relative to standard dust models  \citep[Figure~3 in][]{2015ApJ...807L..26G,
-2017ApJ...836...13H}.  Unfortunately, our signal-to-noise for $\pmb{\delta}$ is insufficient to test these physically-motivated
+2017ApJ...836...13H}.
+Unfortunately, our signal-to-noise for $\pmb{\delta}$ is insufficient to test these physically-motivated
 dust models.
+\color{red}
+\color{black}
 
@@
 distribution of $A_V$.  
-\color{purple}
 Nesting this model in an extended model produces a result that 
-\color{black}
 gives the first identification of  a new parameter that affects supernova
@@
 
-\color{purple}
 The current data does not show a statistically significant difference in the values of our new parameter for supernovae
@@
 global host mass.  The search for a correlation between our parameter and local star formation rate is planned for future work.
-
-\color{black}
 

### 2017-09-05 apj.tex
making way through Greg comment

@@
 \end{pmatrix}.
+\label{corr2p:eqn}
 \end{multline}
@@
 \subsection{Physical Interpretation of the Intrinsic Color Parameter}
-
-Based on its direction, a straightforward explanation for the third color term $\pmb{\delta} D$ is that it describes the absorption due to some form of dust
-that does not exactly obey the  \citetalias{1999PASP..111...63F} model.
-In one scenario,
-supernova light can encounter two
-dusts, first a 
-circumstellar dust that produces relatively low visual-to-selective extinction
-\citep{2008ApJ...686L.103G} and then
-an interstellar form  that resembles the \citetalias{1999PASP..111...63F} model.
+\color{red}
+Supernova colors are expected to be affected by interstellar Milky Way-like dust (e.g.\ as modeled by  \citetalias{1999PASP..111...63F})
+and by ``intrinsic'' color variations from the supernova itself and its surrounding circumstellar dust. Physical modeling
+shows that the complexity of interstellar dust shouldn't be expected to be captured by a single parameter \citep{2015ApJ...807L..26G,
+2017ApJ...836...13H}. Supernova models \citep[e.g.][]{2007ApJ...662..487W,2013MNRAS.436..333S,2014MNRAS.441..532D,2015MNRAS.454.2549B,
+2017ApJ...846...58H} and circumstellar dust \citep{2008ApJ...686L.103G} also predict color variations not  captured
+by  \citetalias{1999PASP..111...63F}.
+The $D$ parameter
+can be ascribed to either an increased accuracy in the description of interstellar dust or to a separate intrinsic mechanism.
+
+Evidence for the intrinsic origin of $\pmb{\delta}D$ is seen in the relation between observed magnitudes corrected for intrinsic magnitude correlations with
+spectral features (but not for the color parameters)
+and observed  color.  Figure~\ref{speccorr:fig} shows such a plot for corrected observed $B_o$ magnitudes
+as a function observed $B_o-V_o$, in correspondence with Figure~3 of  \citet{2017ApJ...842...93M}.  Supernovae with extreme blue colors exhibit a shallower slope than those
+with extreme red colors.   \citet{2017ApJ...842...93M} have demonstrated that this is the expected behavior for
+dust with constant $\beta$ (the SALT2 equivalent of $R$) with an exponential extinction distribution and an intrinsic source of color variablilty
+with a smaller value of $\beta$.  Without interstellar dust, supernovae are bluer and take the intrinsic $\beta$ slope for the color-magnitude
+relation.  When the intrinsic contribution to color is dwarfed by dust, supernovae are bluer and take the larger dust $\beta$ slope.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output25/speccorr_color.pdf}
+      \caption{
+      \color{red}Observed $B$-band magnitude corrected for intrinsic magnitude correlations with spectral features as a function of observed color $B_o-V_o$.
+      The two solid lines are the linear regressions for points with abscissa values less than and greater than zero.
+	\color{black}
+   \label{speccorr:fig}}
+\end{figure}
+
+In contrast, if the colors were due to a single physical dust described by three parameters,
+the observed correlation between the color-magnitude slope and observed color seen in Figure~\ref{speccorr:fig}
+would manifest itself in correlation between the $D$,
+$k_0$ and $k_1$ parameters.  To the contrary,
+the correlations between these parameters  are consistent with zero as given  in Eqn.~\ref{corr2p:eqn}.
+
+If  $\delta D$  is intrinsic, it can be attributed to an intrinsic supernova property  or a dust not described by $\gamma k$.
 To first order $\pmb{\delta}$ behaves like standard dust;   $>98$\% of its length projects onto the expectation of  \citetalias{1999PASP..111...63F}
 with constant $R^F$.
+Therefore, a straightforward explanation is that it describes the absorption due to some form of dust
+that does not exactly obey the  \citetalias{1999PASP..111...63F} model.
 The departure from   \citetalias{1999PASP..111...63F}
@@
 $D$ with $A_V$ would imply an unphysical $R^F=0.5$.
-
-An alternative scenario is that supernova light encounters one dust with a degree of freedom beyond that modeled by \citetalias{1999PASP..111...63F}.
-The $\pmb{\delta} D$ term represents an intrinsic dust parameter that is independent of $R^F$.
-The extra degree-of-freedom could be associated with the skewness in the distribution of dust grains, as an increase of smaller dust grains
-can flatten extinction in the red and enhanced steepness in the UV relative to standard dust models  \citep[Figure~3 in][]{2015ApJ...807L..26G,
-2017ApJ...836...13H}.
-Unfortunately, our signal-to-noise for $\pmb{\delta}$ is insufficient to test these physically-motivated
-dust models.
-\color{red}
+We do not have conclusive evidence that  $\delta$ is being a property of a different form of dust, rather
+than representing intrinsic supernova color variation.
 \color{black}

### 2017-09-07 apj.tex
more changes

@@
 %-----
-Our model
- is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
+%Our model
+% is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
 Inspired that with no conditioning our  two-parameter model produces behavior similar to that expected from Galactic dust,
@@
 
-\keywords{supernovae: general; supernovae: SN 2014J}
+\keywords{supernovae: general; supernovae}
 
@@
 first analysis with two extrinsic parameters and omitting the intrinsic parameter.  The properties of the two extrinsic parameters
-are consistent with the expectations of parameterized Milky Way extinction models, and do an excellent job of fitting the data of the out-of-sample
-supernova SN2014J that has an extremely low total-to-selective extinction.
+are consistent with the expectations of parameterized Milky Way extinction models.
+%, and do an excellent job of fitting the data of the out-of-sample
+%supernova SN2014J that has an extremely low total-to-selective extinction.
 In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
@@
 
-The Model~II fit of SN~2014J \citet{2014ApJ...788L..21A}  data 
-gives $k_0$ and $k_1$ that are qualitatively similar to  those from the fit to Model~I but with much larger uncertainties.
-These parameters are now highly correlated with $D$, which itself is consistent with zero.  The results resemble those of
-Model~I shown in Figure~\ref{sn2014j:fig}, except for larger error bars for the color excesses projected onto the dust model.
+%The Model~II fit of SN~2014J \citet{2014ApJ...788L..21A}  data 
+%gives $k_0$ and $k_1$ that are qualitatively similar to  those from the fit to Model~I but with much larger uncertainties.
+%These parameters are now highly correlated with $D$, which itself is consistent with zero.  The results resemble those of
+%Model~I shown in Figure~\ref{sn2014j:fig}, except for larger error bars for the color excesses projected onto the dust model.
 
@@
 
-Evidence for the intrinsic origin of $\pmb{\delta}D$ is seen in the relation between observed magnitudes corrected for intrinsic magnitude correlations with
-spectral features (but not for the color parameters)
-and observed  color.  Figure~\ref{speccorr:fig} shows such a plot for corrected observed $B_o$ magnitudes
-as a function observed $B_o-V_o$, in correspondence with Figure~3 of  \citet{2017ApJ...842...93M}.  Supernovae with extreme blue colors exhibit a shallower slope than those
-with extreme red colors.   \citet{2017ApJ...842...93M} have demonstrated that this is the expected behavior for
-dust with constant $\beta$ (the SALT2 equivalent of $R$) with an exponential extinction distribution and an intrinsic source of color variablilty
-with a smaller value of $\beta$.  Without interstellar dust, supernovae are bluer and take the intrinsic $\beta$ slope for the color-magnitude
-relation.  When the intrinsic contribution to color is dwarfed by dust, supernovae are bluer and take the larger dust $\beta$ slope.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output25/speccorr_color.pdf}
+Color-based magnitude corrections as a function of color excess provide a clue to ``intrinsic'' and ``dust'' attributions of
+the combined effect of the color terms $k_0$, $k_1$, and $D$.  
+All supernovae experience  intrinsic color variation.
+Only a subset encounter dust:
+geometric projection effects lead to the expectation for a subset of supernovae having zero
+dust column density and the
+complement subset having an approximate exponential distribution \citep{1998ApJ...502..177H}.
+Differences between the expected distributions of
+distinct intrinsic effects and dust lead to the prediction of a non-constant slope for the relationship between
+total (from both intrinsic and dust)  magnitude corrections and color excess.
+
+\citet{2017ApJ...842...93M} present an instructive simulation, producing magnitudes and colors of a set of
+supernovae 
+with an intrinsic source of color variability having relatively smaller value of $\beta$
+and a realistic distribution of dust extinction having a relatively larger $\beta$ value.  The expectation is for
+supernovae encountering no interstellar dust  to tend to be bluer and exhibit the intrinsic $\beta$ slope for the color-magnitude
+relation.  Supernovae encountering thick dust tend to be redder and exhibit the larger dust $\beta$ slope.
+The expectation is borne out in their Figure 3, which shows 
+observed color versus light-curve shape corrected magnitudes, and is seen in their data Figure 6.
+The distinctive expectations manifest in the plot  for the above model allow
+the authors to use  information inherent in the distributions to make distinct measurements of intrinsic and dust slopes (referred
+therein as $\beta$ using the terminology of SALT2),
+despite being
+restricted to using one color observable that is  affected by two sources of extinction.
+
+Our Model~II has for each supernova three color parameters that can contain information on more
+than one source of color variablility. This allows us to construct from our fit results per-supernova magnitude corrections as a function
+of color, to produce a model-based figure analogous to Figure~3 of \citet{2017ApJ...842...93M}.
+Such a result is shown in Figure~\ref{speccorr:fig}, which plots
+$U$-band magnitude corrections from the three color parameters $\gamma^0_{U} k_0 +\gamma^1_{U} k_1 + \delta_U D$
+as a function of $E_o(B-V)$, where the expected color accounts for spectral-feature corrections.
+The shallower slope at blue color transitioning to a larger slope at red color 
+is correspondence with the expectation of a mixed intrinsic--dust model of the form considered by  \citet{2017ApJ...842...93M}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{output25/ccorr1e.pdf}
+   \includegraphics[width=2.8in]{output25/ccorr2e.pdf}
       \caption{
-      \color{red}Observed $B$-band magnitude corrected for intrinsic magnitude correlations with spectral features as a function of observed color $B_o-V_o$.
-      The two solid lines are the linear regressions for points with abscissa values less than and greater than zero.
+      \color{red}
+      The $U$-band magnitude corrections from the three color parameters $\gamma^0_{U} k_0 +\gamma^1_{U} k_1 + \delta_U D$
+are plotted as a function of $E_o(B-V)$, where the expected color accounts for spectral-feature corrections.  The left plot shows the full
+range of values whereas the right zooms in the upper-left corner of the population.
 	\color{black}
@@
 \end{figure}
-
-In contrast, if the colors were due to a single physical dust described by three parameters,
-the observed correlation between the color-magnitude slope and observed color seen in Figure~\ref{speccorr:fig}
-would manifest itself in correlation between the $D$,
-$k_0$ and $k_1$ parameters.  To the contrary,
-the correlations between these parameters  are consistent with zero as given  in Eqn.~\ref{corr2p:eqn}.
 
@@
 $D$ with $A_V$ would imply an unphysical $R^F=0.5$.
-We do not have conclusive evidence that  $\delta$ is being a property of a different form of dust, rather
+We do not have conclusive evidence that  $\delta$ is being a property of dust distinct from that described by $\gamma$, rather
 than representing intrinsic supernova color variation.
@@
 extrinsic color parameters.  Analyzing SNfactory data with this model, we find significant evidence that the above parameters do
-affect supernova magnitudes and colors.  This model  does an excellent job in
-describing SN~2014J, a supernova with extreme colors that was not used in the training.  
+affect supernova magnitudes and colors.  
+%This model  does an excellent job in
+%describing SN~2014J, a supernova with extreme colors that was not used in the training.  
 This work represents the first determination of the dust extinction curve outside the Local Group

### 2017-09-07 apj.tex
refining things

@@
 a direct comparison can be made.
+\color{red}
+\citep{2017ApJ...842...93M}  find an intrinsic dispersion of the SALT2 $c$ parameter (associated with $B-V$) of $\approx 0.07$ mag.
+\color{black}
 %model11_rubin.py
@@
 
-\citet{2017ApJ...842...93M} present an instructive simulation, producing magnitudes and colors of a set of
+\citet{2017ApJ...842...93M} discuss an instructive simulation
+that considers a set of
 supernovae 
-with an intrinsic source of color variability having relatively smaller value of $\beta$
-and a realistic distribution of dust extinction having a relatively larger $\beta$ value.  The expectation is for
-supernovae encountering no interstellar dust  to tend to be bluer and exhibit the intrinsic $\beta$ slope for the color-magnitude
-relation.  Supernovae encountering thick dust tend to be redder and exhibit the larger dust $\beta$ slope.
-The expectation is borne out in their Figure 3, which shows 
-observed color versus light-curve shape corrected magnitudes, and is seen in their data Figure 6.
-The distinctive expectations manifest in the plot  for the above model allow
-the authors to use  information inherent in the distributions to make distinct measurements of intrinsic and dust slopes (referred
-therein as $\beta$ using the terminology of SALT2),
+having an intrinsic linear color-magnitude relationship with slope $\beta$.
+(The absence of an intrinsic color-magnitude relation corresponds to $\beta=0$.)
+Each supernova encounters dust with a relatively larger slope
+for the color-magnitude relationship and
+extinction drawn from a realistic extinction distribution.
+The expectation is for
+supernovae encountering no interstellar dust  to tend to be bluer and
+collectively exhibit the intrinsic $\beta$ slope for the color-magnitude
+relation.  Supernovae encountering thick dust tend to be redder and collectively exhibit the larger dust  slope.
+This expectation is borne out in Figure 3 of \citet{2017ApJ...842...93M}, which
+shows  simulated
+observed color versus light-curve shape corrected magnitudes.
+The distinctive distribution of supernovae in color-magnitude space  allows
+the authors to distinguish intrinsic $\beta$ and the dust slope,
 despite being
@@
 
-Our Model~II has for each supernova three color parameters that can contain information on more
+In our Model~II, each supernova has three color parameters that can contain information on more
 than one source of color variablility. This allows us to construct from our fit results per-supernova magnitude corrections as a function
@@
 as a function of $E_o(B-V)$, where the expected color accounts for spectral-feature corrections.
-The shallower slope at blue color transitioning to a larger slope at red color 
-is correspondence with the expectation of a mixed intrinsic--dust model of the form considered by  \citet{2017ApJ...842...93M}.
+The shallower (but non-zero) slope at blue color transitioning to a larger slope at red color 
+is correspondence with the expectation of a mixed intrinsic--dust model.
+The fact that
+, and is seen in their data Figure 6 of the form considered by  \citet{2017ApJ...842...93M}.
+Slope is not zero.
 
@@
 
-If  $\delta D$  is intrinsic, it can be attributed to an intrinsic supernova property  or a dust not described by $\gamma k$.
+Considering  $\delta D$  to be intrinsic, it can be attributed to an intrinsic supernova property  or a dust not described by $\gamma k$.
 To first order $\pmb{\delta}$ behaves like standard dust;   $>98$\% of its length projects onto the expectation of  \citetalias{1999PASP..111...63F}

### 2017-09-09 apj.tex
forging on with Greg's comments

@@
 \defcitealias{1999PASP..111...63F}{F99}
+\defcitealias{2017ApJ...842...93M}{M17}
 \linenumbers
@@
 The color changes allowed by the model are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F} with a free
-total-to-selective extinction parameter $R^F$.  As an ensemble, the supernova sample has an effective
-%-----
-$R^F = 2.44$.
-%-----
-%Our model
+total-to-selective extinction parameter $R^F$.  %Our model
 % is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
@@
 %-----
-confidence;
-this new parameter represents supernova color diversity
+confidence.
+\color{red}
+The 68\% credible interval for an effective
+%-----
+$R^F$ of the sample is 2.31 -- 2.69.
+%-----
+The third parameter is attributed to intrinsic supernova or circumstellar diversity
+\color{black}
 beyond that tracked by the spectral features and two-parameter dust models.
@@
 but  influence color can be included in such models.
-\citet{2017ApJ...842...93M} take the approach of modeling the distribution of their parameters, to find that
+\citet{2017ApJ...842...93M} \citepalias[henceforth referred to as][]{2017ApJ...842...93M}) take the approach of modeling the distribution of their parameters, to find that
 scatter in the Hubble diagram is better explained by a combination of intrinsic color dispersion and
@@
 two are assigned as extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
-properties.  (We subsequently find that extrinsic and intrinsic properties cannot be distinguished with our data.)
+properties.
 The data used in this analysis are described in \S\ref{data:sec}.
@@
 comprised of five 
-bands with the following wavelength ranges: $U$ $[3300.00 - 3978.02]$\AA;
-$B$ $[3978.02-4795.35]$\AA;
-$V$ $[4795.35-5780.60]$\AA;
-$R$ $[5780.60-6968.29]$\AA;
-$I$ $[6968.29-8400.00]$\AA.
+bands with the following wavelength ranges: ${\hat{U}}$ $[3300.00 - 3978.02]$\AA;
+${\hat{B}}$ $[3978.02-4795.35]$\AA;
+$\hat{V}$ $[4795.35-5780.60]$\AA;
+$\hat{R}$ $[5780.60-6968.29]$\AA;
+$\hat{I}$ $[6968.29-8400.00]$\AA.
+\color{red}
+The hat serves as a reminder that these are not standard filters.
+\color{black}
 For each supernova, the magnitudes within 5-days of peak brightness are used to regress single-band magnitudes
@@
 We assume 
-that  peak intrinsic $UBVRI$ magnitudes of a supernova are linearly dependent
+that  peak intrinsic ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
 on its
@@
 The observables
-$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
+$\hat{U}_o, {\hat{B}}_o, {\hat{V}}_o, {\hat{R}}_o, {\hat{I}}_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
 %shown in Table~\ref{data:tab}
@@
 \begin{pmatrix}
-U\\B\\V\\R\\I
+{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
 \end{pmatrix}
@@
 \begin{pmatrix}
-c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} \\
-c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si}  \\
-c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} \\
-c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} \\
-c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si}
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} \\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  \\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} \\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} \\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}
 \end{pmatrix}
@@
 \begin{pmatrix}
-U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
+{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
 \end{pmatrix}
@@
 \begin{pmatrix}
-U +\gamma^0_{U} k_0 +\gamma^1_{U} k_1 \\B +\gamma^0_{B} k_0 +\gamma^1_{B} k_1 \\
-V+\gamma^0_{V} k_0+\gamma^1_{V} k_1\\R+\gamma^0_{R} k_0 + \gamma^1_{R} k_1\\I+\gamma^0_{I} k_0+\gamma^1_{I} k_1\\
+{\hat{U}} +\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\
+{\hat{V}}+\gamma^0_{{\hat{V}}} k_0+\gamma^1_{{\hat{V}}} k_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} k_0 + \gamma^1_{{\hat{R}}} k_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} k_0+\gamma^1_{{\hat{I}}} k_1\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
@@
 The global parameter vectors that describe the SN~Ia population
-$\mathbf{c}$ (where $\mathbf{c}=(c_U, c_B, c_V, c_R, c_I) $),
+$\mathbf{c}$ (where $\mathbf{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $),
 $\pmb{\alpha}$, $\pmb{\beta}$,  and $\pmb{\eta}$,  are the intercept and slopes of the linear relationships that
@@
 \begin{equation}
-\gamma^0_U > 0, \gamma^1_U < 0.
+\gamma^0_{\hat{U}} > 0, \gamma^1_{\hat{U}} < 0.
 \end{equation}
@@
    \includegraphics[width=5.2in]{output11/coeff0.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $U$ band.
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{U}}$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
             projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.  Lines for zero value for $\alpha_U$, $\beta_U$, $\eta$, $\gamma_U^0$, $\gamma_U^1$, and $\sigma_U$ are shown for reference --
+            enclosed probability.  Lines for zero value for $\alpha_{\hat{U}}$, $\beta_{\hat{U}}$, $\eta$, $\gamma_{\hat{U}}^0$, $\gamma_{\hat{U}}^1$, and $\sigma_{\hat{U}}$ are shown for reference --
             in most cases they are outside the range of the plot.
@@
    \includegraphics[width=5.2in]{output11/coeff1.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $B$ band.
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{B}}$ band.
  \label{global2:fig}}
@@
    \includegraphics[width=5.2in]{output11/coeff2.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $V$ band.
+            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{V}}$ band.
  \label{global3:fig}}
@@
       \includegraphics[width=5.2in]{output11/coeff3.pdf} 
-            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $R$ band.
+            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{R}}$ band.
  \label{global4:fig}}
@@
          \includegraphics[width=5.2in]{output11/coeff4.pdf} 
-            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the $I$ band.
+            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{I}}$ band.
  \label{global5:fig}}
@@
 The 
-potential scale reduction statistic, $\hat{R}$ \citep{Gelman92}, measures the convergence of the target distribution
+potential scale reduction statistic, $\hat{R}$ (not the passband) \citep{Gelman92}, measures the convergence of the target distribution
 in iterative simulations 
@@
 For four selected colors, a plot of the
-observed versus deduced intrinsic colors and the histogram of their differences
+deduced versus observed intrinsic colors and the histogram of their differences
 are shown in Figure~\ref{residual:fig}. 
@@
             \caption{
-            Observed versus deduced intrinsic colors for four selected colors.  Plotted on the right for each color
+            Deduced versus observed intrinsic colors for four selected colors.  Plotted on the right for each color
 is the histogram of the difference between the observed and intrinsic colors.
@@
 are given in Table~\ref{global:tab}.
-As the $\pmb{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_V$,
-their results are shown in terms of $\gamma^i_X/\gamma^i_V-1$.
+As the $\pmb{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
+their results are shown in terms of $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
 
@@
 \hline
-Parameter & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+Parameter & $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
 $\alpha_X$
@@
 \\
-${\alpha_X/\alpha_V-1}$
+${\alpha_X/\alpha_{\hat{V}}-1}$
 &
@@
 \\
-${\beta_X/\beta_V-1}$
+${\beta_X/\beta_{\hat{V}}-1}$
 &
@@
 \\
-${\eta_X/\eta_V-1}$
+${\eta_X/\eta_{\hat{V}}-1}$
 &
@@
 \\
-${\gamma^0_X/\gamma^0_V-1}$
+${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
 &
@@
 \\
-${\gamma^1_X/\gamma^1_V-1}$
+${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
 &
@@
 The effect of spectral parameters on color (as opposed to magnitude)
-is shown in the rows of $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$
+is shown in the rows of $\alpha_X/\alpha_{\hat{V}}-1$,  $\beta_X/\beta_{\hat{V}}-1$, and  $\eta_X/\eta_{\hat{V}}-1$
 in Table~\ref{global:tab}.
 Values of zero signify no color changes associated with magnitude changes.
-Both $EW_{Ca}$ and $EW_{Si}$ are associated with color changes, though not in $B-V$ specifically.
+Both $EW_{Ca}$ and $EW_{Si}$ are associated with color changes, though not in ${\hat{B}}-{\hat{V}}$ specifically.
 We do not detect a significant association between
@@
 The signal in  $\pmb{\alpha}$ and $\pmb{\beta}$ cannot be attributed to the equivalent widths themselves.
-The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the $B$-band is 851~\AA, so that its direct affect on magnitude
+The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the ${\hat{B}}$-band is 851~\AA, so that its direct affect on magnitude
 is
 $2.5 \log{(20/850)} \sim 0.03$ mag.  
-The implied span in $B$ magnitude based on $\beta_B$ is 0.54~mag.  Therefore $\beta_B$ cannot wholly be attributed to the flux deficit
+The implied span in ${\hat{B}}$ magnitude based on $\beta_{\hat{B}}$ is 0.54~mag.  Therefore $\beta_{\hat{B}}$ cannot wholly be attributed to the flux deficit
 from the line itself.
-Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the $U$ band is
+Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the ${\hat{U}}$ band is
 701~\AA, so that its direct affect on magnitude
 is
-$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in $U$ magnitude is  0.21~mag, so $\alpha_U$ cannot be completely due to the 
+$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in ${\hat{U}}$ magnitude is  0.21~mag, so $\alpha_{\hat{U}}$ cannot be completely due to the 
 presence of the line itself.
@@
 than the dispersion in $\Delta$.
-Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in $V$ and colors with respect to $V$ are
+Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in ${\hat{V}}$ and colors with respect to ${\hat{V}}$ are
 \begin{multline}
-\sigma(V,U-V,B-V,V-R,V-I)=\\
+\sigma({\hat{V}},{\hat{U}}-{\hat{V}},{\hat{B}}-{\hat{V}},{\hat{V}}-{\hat{R}},{\hat{V}}-{\hat{I}})=\\
 %\begin{pmatrix}
@@
 \begin{multline}
-Cor(V,U-V,B-V,V-R,V-I)=\\
+Cor({\hat{V}},{\hat{U}}-{\hat{V}},{\hat{B}}-{\hat{V}},{\hat{V}}-{\hat{R}},{\hat{V}}-{\hat{I}})=\\
 \begin{pmatrix}
@@
 \color{red}
-\citep{2017ApJ...842...93M}  find an intrinsic dispersion of the SALT2 $c$ parameter (associated with $B-V$) of $\approx 0.07$ mag.
+\citetalias{2017ApJ...842...93M}  find an intrinsic dispersion of the SALT2 $c$ parameter (associated with ${\hat{B}}-{\hat{V}}$) of $\approx 0.07$ mag,
+though variation of dust properties accounts for some of that dispersion.
 \color{black}
@@
 
-%Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k_0$, and
-%$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
-%$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
-%There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
-%Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
-%heavily extinguished by host-galaxy dust.
-%Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.   
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=5.2in]{output11/perobject_corner.pdf} 
-%   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
-%$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
-%   \label{perobject:fig}}
-%\end{figure}
-
-Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$.
+ßEach supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, and $E_{\gamma^1}({\hat{B}}-{\hat{V}})$.
 Their Pearson correlation coefficients  are given in the matrix
 \begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}})) =\\
 \begin{pmatrix}
@@
 We find weak correlations between our color-excess parameters and the input features; 
-only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}(B-V)$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
+only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}({\hat{B}}-{\hat{V}})$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
 The feature $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
@@
 \begin{equation}
-A_X = a(X)  A_V + b(X) E(B-V)
+A_X = a(X)  A_{\hat{V}} + b(X) E({\hat{B}}-{\hat{V}})
 \label{f99:eqn}
@@
 $R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
-\citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
+\citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at ${\hat{B}}$-band peak, the 
+\citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F} model
 gives
@@
 \begin{equation}
-A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V),
+A_X = \frac{\gamma^0_X}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}}  E_{\gamma^0}({\hat{B}}-{\hat{V}}) +  \frac{\gamma^1_X}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}}  E_{\gamma^1}({\hat{B}}-{\hat{V}}),
 \end{equation}
-with $E_{\gamma^i}(B-V) \equiv  (\gamma^i_B-\gamma^i_V)k_i$ as defined in \S\ref{results:sec}.
+with $E_{\gamma^i}({\hat{B}}-{\hat{V}}) \equiv  (\gamma^i_{\hat{B}}-\gamma^i_{\hat{V}})k_i$ as defined in \S\ref{results:sec}.
 Our median-fit values for the $\pmb{\gamma}$ coefficients are
 %---- fitz11.py
-$\frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V}  =(4.80 ,   3.89,   2.89,   2.22,   1.59)$ and
-$ \frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V}=(-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71)$.
+$\frac{\pmb{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}}  =(4.80 ,   3.89,   2.89,   2.22,   1.59)$ and
+$ \frac{\pmb{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}}=(-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71)$.
 %----
@@
 \begin{pmatrix}
- \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
-\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} 
+ \frac{\pmb{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
+\frac{\pmb{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} 
 \end{pmatrix}=
@@
 quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.  The most significant
-deviation away from the plane is in the $R$-band.
+deviation away from the plane is in the ${\hat{R}}$-band.
 This result indicates that
-the allowed variations in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to almost identical
+the allowed variations in ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to almost identical
 2-dimensional
@@
 
-The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the $UVI$-subspace two perspectives (left and right columns)
+The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the ${\hat{U}}{\hat{V}}I$-subspace two perspectives (left and right columns)
 of the unit vectors corresponding to $\pmb{\gamma}^0$ and  $\pmb{\gamma}^1$ of our model (solid lines),
@@
 The two perspectives show that while the four vectors point in different directions for each band combination,
-they are almost coplanar in $UVI$ (they are slightly less coplanar in $BVR$).  The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
+they are almost coplanar in ${\hat{U}}{\hat{V}}{\hat{I}}$ (they are slightly less coplanar in ${\hat{B}}{\hat{V}}{\hat{R}}$).
+The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
 vectors span near-parallel planes in the 5-dimensional color space, and hence the latter can be almost entirely expressed in terms of
@@
    Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
-   magnitudes in 5-bands $UBVRI$ this visualization shows only $UVI$.   The left and right plots show the same information from
+   magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
    two different perspectives.
@@
 
-Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
+Given the association of  our parameter $\gamma^0_{\hat{V}} k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
 the former's distribution can be compared to the expectation for the latter.
 Figure~\ref{k0_med:fig} shows the histogram of
-median values and the ideogram of $\gamma^0_V k_0$ 
-relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
+median values and the ideogram of $\gamma^0_{\hat{V}} k_0$ 
+relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} k_0|_0$.
 (Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
 The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
-with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.
+with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H, 2007ApJ...659..122J}.
 This distribution is given by the data, and so is not dependent of any knowledge or prior
@@
       of
-median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
-(left) : $\gamma^1_V k_1-\gamma^1_V k_1|_0$,
+median values of $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
+(left) : $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
 which  is associated with extinction corrections due to deviations away from the canonical $R^F_{eff}$ value (right).
@@
 the color-excess parameter $E^F(B-V)$.
-Figure~\ref{k0_med:fig} shows the histogram of median values and ideogram of $\gamma^1_V k_1$
-relative to that of an arbitrary supernova  $\gamma^1_V k_1|_0$.
+Figure~\ref{k0_med:fig} shows the histogram of median values and ideogram of $\gamma^1_{\hat{V}} k_1$
+relative to that of an arbitrary supernova  $\gamma^1_{\hat{V}} k_1|_0$.
 
@@
 SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
-are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample
+are assigned $E^F(B-V)$ parameters equal to the ${\hat{B}}-{\hat{V}}$ color excesses determined in our sample
 (making an approximative correspondence between our observed top-hat filter colors and the 
@@
 Nevertheless, there do remain some small inconsistencies between our numbers and expectations from dust models.
-
-%
-%\subsection{SN 2014J in the Context of Our Model}
-%\label{sn2014j:sec}
-%SN~2014J   is one of several SNe~Ia that exhibit colors that imply a low $R_V<2.0$ \citep{2014ApJ...788L..21A, 2014MNRAS.443.2887F, 
-%2014arXiv1411.3332J,
-%2014ApJ...795L...4K, 2015ApJ...805...74B}.
-%The colors of this supernova can be studied in comparison to SN~2011fe, an object with similar
-%spectral evolution that 
-%suffers very low galactic and host reddening
-%\citep[this technique has been used in][]{2006MNRAS.369.1880E,2007AJ....133...58K,2008MNRAS.384..107E,2010AJ....139..120F, 2014ApJ...788L..21A,
-%2017arXiv170101422H}.
-%The overall higher photospheric velocities of
-%SN~2014J are unimportant  based on the findings of  \S\ref{results:sec}.
-%
-%Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
-%The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
-%following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
-%Their values 
-%$E(U_o-V_o) =   2.23 \pm   0.03$,
-%$E(B_o-V_o) =   1.28 \pm   0.04$,
-%$E(R_o-V)_o =  -0.47 \pm   0.03$,
-%$E(i_o-V_o) =  -0.92 \pm   0.03$
-%are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ denotes that this is an observed color excess.
-%The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
-%wavelengths 
-%3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  Despite the imperfect correspondence our synthetic passbands
-%and those used for the observations,
-%these data are fit to our model
-%\begin{equation}
-%E(X_o-V_o) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
-%\end{equation}
-%where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and $e_i $ are the fit
-%parameters.
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=5.2in]{output11/sn2014j.pdf} 
-%   \caption{Top: Measured color excess for SN~2014J and the best-fit predictions from this article.
-%   \color{purple}
-%   In addition to the prediction
-%   of our model, also shown is the prediction from the projection
-%   of our results onto the \citetalias{1999PASP..111...63F} extinction model.  Bottom: Residual color excess
-%   between the data and models, with a dotted line at zero shown for reference.
-%   \color{black}
-%   \label{sn2014j:fig}}
-%\end{figure}
-%
-%The best-fit parameters for SN~2014J are 
-%%----
-%$e_0= 2.60$, $ e_1=-1.89$ with covariance
-%%----
-%\begin{equation}
-%\begin{pmatrix}
-%\begin{array}{rr}
-%0.050 & 0.058 \\
-%0.058 & 0.315
-%\end{array}
-%\end{pmatrix}.
-%\end{equation}
-%The predicted values of observed $E(B_o-V_o)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
-%overlap with the data within the error bars. 
-%
-%
-%
-%In the fit to our model, the observed color excess is attributed to 
-%%----
-%$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
-%%-----
-%contributions.
-%Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
-%objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
-%%---
-%$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
-%$  0.06 \pm 0.03$. 
-%%---
-%The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
-%span of supernovae used to train the coefficients of the model, which is not unexpected if
-%attributable to dust. 
-%
-%\color{purple}
-%The  parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)=  0.34$ can be transformed into  the 
-%\citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
-%assuming that  SN~2011fe has zero extinction.  The colors predicted by this \citetalias{1999PASP..111...63F}--component
-%of our model are  shown in Figure~\ref{sn2014j:fig}. 
-%Significant differences between the projection and the data is apparent
-%in the $B-V$ and  $R-V$ colors.
-%The data and the full model both have shallower decline in color excess with increasing wavelength.
-%The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
-%in Figure 3 of  \citet{2014ApJ...788L..21A}, who fit
-%UV through NIR data to obtain $R_V^F=1.4$ and $E^F(B-V)=1.37$.
-%Notwithstanding their bias respect to the data, we present the transformed dust parameters
-%$A^F_V=0.77$ and $E^F(B-V)=1.28$ and covariance
-%\begin{equation}
-%\begin{pmatrix}
-%\begin{array}{rr}
-%0.430 & -0.004 \\
-%-0.004 & 0.007
-%\end{array}
-%\end{pmatrix},
-%\end{equation}
-%which together give $R^F= 0.59^{+ 0.53}_{-0.48}$.
-%\color{black}
-%
 
@@
 \begin{pmatrix}
-c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} + \delta_U D\\
-c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si} + \delta_B D \\
-c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} + \delta_V D\\
-c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} + \delta_R D\\
-c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si} + \delta_I D
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} + \delta_{\hat{U}} D\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} + \delta_{\hat{B}} D \\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} + \delta_{\hat{V}} D\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} + \delta_{\hat{R}} D\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si} + \delta_{\hat{I}} D
 \end{pmatrix}
@@
 \begin{pmatrix}
-U +\gamma^0_{U} k_0 +\gamma^1_{B} k_1 \\B +\gamma^0_{B} k_0 +\gamma^1_{B} k_1 \\
-V+\gamma^0_{V} k_0+\gamma^1_{V} k_1\\R+\gamma^0_{R} k_0 + \gamma^1_{R} k_1\\I+\gamma^0_{I} k_0+\gamma^1_{I} k_1\\
+{\hat{U}} +\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\
+{\hat{V}}+\gamma^0_{{\hat{V}}} k_0+\gamma^1_{{\hat{V}}} k_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} k_0 + \gamma^1_{{\hat{R}}} k_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} k_0+\gamma^1_{{\hat{I}}} k_1\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
@@
 does not significantly affect the results, meaning that data are not constraining enough
-to identify $\pmb{\delta} D$ as being physically intrinsic or extrinsic.  Nevertheless, $\pmb{\delta} D$ is referred to as ``intrinsic''  for convenience.
+to identify $\pmb{\delta} D$ as being physically intrinsic or extrinsic.
+\color{red}
+However, we present in \$\ref{interpret:sec} a separate physical argument for the intrinsic interpretation of the new term.
+\color{black}
 
@@
 deviations of the magnitude residuals $\sigma_X$
-in the $U$ and $B$ bands.
+in the ${\hat{U}}$ and ${\hat{B}}$ bands.
 
@@
 \hline
-Parameters& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
 $\alpha_X$
@@
 \\
-${{\delta_X/\delta_U-1}}$
+${{\delta_X/\delta_{\hat{U}}-1}}$
 &
@@
 resulting in changes in the shape of the $\pmb{\delta}$ posteriors when  $D$ to forced to be positive.   
-The modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in for $X=UBVRI$ respectively.
-The values of $\delta_X/\delta_U-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
+The modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in for $X={\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ respectively.
+The values of $\delta_X/\delta_{\hat{U}}-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
 
@@
       \includegraphics[width=5.2in]{output25/deltaratio.pdf}
-   \caption{Model~II median values  and corresponding 68\% intervals for $\delta_X/\delta_U$ in the 5 bands.
+   \caption{Model~II median values  and corresponding 68\% intervals for $\delta_X/\delta_{\hat{U}}$ in the 5 bands.
    A dotted line at zero is shown for reference.
@@
 
-%The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.
-
-The distributions of both sources of color excess $E(B-V)$ and
- $E_\delta(B-V) \equiv   (\delta_B-\delta_V)D$ are shown in the ideograms 
+The distributions of both sources of color excess $E({\hat{B}}-{\hat{V}})$ and
+ $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in the ideograms 
  and histogram in Figure~\ref{ebv:fig}.
  (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
-The range of $B-V$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
+The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
 component.  
-The standard deviations of  the median $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
+The standard deviations of  the median $E_\gamma({\hat{B}}-{\hat{V}})$ and $E_\delta({\hat{B}}-{\hat{V}})$ are
 %-----
@@
 mag respectively.
-The $E_\delta(B-V)$ standard deviation is comparable to its measurement uncertainty per-supernova.
+The $E_\delta({\hat{B}}-{\hat{V}})$ standard deviation is comparable to its measurement uncertainty per-supernova.
 The color excesses of individual supernovae have low signal-to-noise 
@@
    \includegraphics[width=2.8in]{output25/ebv_delta.pdf}
-      \caption{Left: Ideograms of the external $E(B-V)$ and
-   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
-   Right: Ideogram and histogram of the medians of $E_\delta(B-V)$ on an enlarged scale.
+      \caption{Left: Ideograms of the external $E({\hat{B}}-{\hat{V}})$ and
+   internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
+   Right: Ideogram and histogram of the medians of $E_\delta({\hat{B}}-{\hat{V}})$ on an enlarged scale.
    \label{ebv:fig}}
@@
 Each supernova is described by its parameters
- $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta U}=\delta_U D$.
+ $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  $A_{\delta {\hat{U}}}=\delta_{\hat{U}} D$.
  Their Pearson correlation coefficients are given in the matrix
 \begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta U}) =\\
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}),  A_{\delta {\hat{U}}}) =\\
 \begin{pmatrix}
@@
 There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
-Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
+Many outliers appear in the red tail of $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, as would be expected for the (infrequent) selection of supernovae
 heavily extinguished by host-galaxy dust.
@@
 
-%The distributions for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, 
-%$E_{\gamma^1}(B-V)$, and
-%$E_{\delta}(B-V)$ for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
-
-The correlation coefficients between the ``intrinsic''  ($A_{\delta U}$) and ``extrinsic''
-($E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$)  parameters are
+The correlation coefficients between the ``intrinsic''  ($A_{\delta {\hat{U}}}$) and ``extrinsic''
+($E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$)  parameters are
 directed by the prior and are ultimately consistent with zero.
@@
    \caption{
-   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$,  $E_{\gamma^1}(B-V)$,  and $E_{\delta}(B-V)$, as well as the grey offset
+   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and $E_{\delta}({\hat{B}}-{\hat{V}})$, as well as the grey offset
 $\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
@@
 
-The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$) can be expressed 
+The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_{\hat{U}}$) can be expressed 
 in terms of the $\mathbf{a}$ and $\mathbf{b}$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
@@
 \begin{pmatrix}
- \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
-\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} \\
-\frac{\delta_X}{\delta_U} \\
+ \frac{\pmb{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
+\frac{\pmb{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} \\
+\frac{\delta_X}{\delta_{\hat{U}}} \\
 \end{pmatrix}=
@@
    \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $U$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
@@
    \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $B$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
@@
    \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $V$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
@@
       \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $R$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
@@
          \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the $I$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
@@
 for our sample in \citet{2017Chotard}.
-On the other hand, there is no such correlation seen between $A_{\delta I} = \delta_I D$ and $x_1$, as shown in Figure~\ref{x1:fig}. 
+On the other hand, there is no such correlation seen between $A_{\delta {\hat{I}}} = \delta_{\hat{I}} D$ and $x_1$, as shown in Figure~\ref{x1:fig}. 
 Our magnitude residuals, $\sigma_X$, are comparable to the residuals after SALT2 training
@@
 Figure~\ref{x1res:fig},
-though there is a hint of nonlinearity in the $B-V$ and $R-V$ colors.
+though there is a hint of nonlinearity in the ${\hat{B}}-{\hat{V}}$ and ${\hat{R}}-{\hat{V}}$ colors.
 
@@
 from this analysis are given in Table~\ref{globalx1:tab}; there are no significant changes with respect to the reference model. 
-Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: $\zeta_R/\zeta_V$
+Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: $\zeta_{\hat{R}}/\zeta_{\hat{V}}$
 has the largest significance  at $1\sigma$.
-The evidence for the effect of a third parameter persists in the significant  non-zero  $\delta_X/\delta_I-1$ values
+The evidence for the effect of a third parameter persists in the significant  non-zero  $\delta_X/\delta_{\hat{I}}-1$ values
 in Table~\ref{globalx1:tab}, reinforcing the evidence that the $D$ of Model~II is not primarily related to light-curve shape.
@@
    \includegraphics[width=5in]{output25/x1D.pdf}
-    \caption{The SALT2 $x_1$ versus $A_{\delta U}  = \delta_U D$.
+    \caption{The SALT2 $x_1$ versus $A_{\delta {\hat{U}}}  = \delta_{\hat{U}} D$.
    \label{x1:fig}}
@@
 \hline
-Parameters & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
+Parameters & $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
 $\alpha_X$
@@
 \\
-${\zeta_X/\zeta_V-1}$
+${\zeta_X/\zeta_{\hat{V}}-1}$
 &
@@
 This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
-\citet{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
+\citetalias{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
 To explore whether the Hubble residual may be due to unaccounted color,
-we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta I}$  versus host mass 
+we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta {\hat{I}}}$  versus host mass 
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-The average $A_{\delta I}$'s of the two subsamples are
+The average $A_{\delta {\hat{I}}}$'s of the two subsamples are
 %---
-$\langle A_{\delta I} \rangle=     -0.0002 \pm    0.0089$ mag,
-$\langle A_{\delta I} \rangle= 0.0025 \pm   0.0073 $ mag
+$\langle A_{\delta {\hat{I}}} \rangle=     -0.0002 \pm    0.0089$ mag,
+$\langle A_{\delta {\hat{I}}} \rangle= 0.0025 \pm   0.0073 $ mag
 for low- and high-mass hosts respectively: there is no significant difference between them.
@@
    \includegraphics[width=2.8in]{output25/childress_pvalue.pdf}
-      \caption{Left: Intrinsic parameter $A_{\delta U}=\delta_U D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
+      \caption{Left: Intrinsic parameter $A_{\delta {\hat{U}}}=\delta_{\hat{U}} D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
       less than and greater than  $\log{(M/M_\sun)}=10$.
@@
 
-The Kolmogorov-Smirnov test is applied on the distribution of $A_{\delta I}$ of both low- and high-mass samples for
+The Kolmogorov-Smirnov test is applied on the distribution of $A_{\delta {\hat{I}}}$ of both low- and high-mass samples for
 each Monte Carlo link.
 The resulting distribution of the two-tailed $p$-value  over all chains spans the possible range from 0 to 1, as shown in Figure~\ref{childress:fig}.
-We are unable to perform a constraining test of whether the $A_{\delta I}$ distributions from low- and high-mass samples
+We are unable to perform a constraining test of whether the $A_{\delta {\hat{I}}}$ distributions from low- and high-mass samples
 are drawn from a common distribution.
@@
 \subsection{Physical Interpretation of the Intrinsic Color Parameter}
+\label{interpret:sec}
 \color{red}
@@
 
-\citet{2017ApJ...842...93M} discuss an instructive simulation
+\citetalias{2017ApJ...842...93M} discuss an instructive simulation
 that considers a set of
@@
 relation.  Supernovae encountering thick dust tend to be redder and collectively exhibit the larger dust  slope.
-This expectation is borne out in Figure 3 of \citet{2017ApJ...842...93M}, which
+This expectation is borne out in Figure 3 of \citetalias{2017ApJ...842...93M}, which
 shows  simulated
@@
 
-In our Model~II, each supernova has three color parameters that can contain information on more
-than one source of color variablility. This allows us to construct from our fit results per-supernova magnitude corrections as a function
-of color, to produce a model-based figure analogous to Figure~3 of \citet{2017ApJ...842...93M}.
-Such a result is shown in Figure~\ref{speccorr:fig}, which plots
-$U$-band magnitude corrections from the three color parameters $\gamma^0_{U} k_0 +\gamma^1_{U} k_1 + \delta_U D$
-as a function of $E_o(B-V)$, where the expected color accounts for spectral-feature corrections.
-The shallower (but non-zero) slope at blue color transitioning to a larger slope at red color 
-is correspondence with the expectation of a mixed intrinsic--dust model.
-The fact that
-, and is seen in their data Figure 6 of the form considered by  \citet{2017ApJ...842...93M}.
-Slope is not zero.
+In our Model~II, each supernova has three color parameters that can distinguish between
+intrinsic and dust contributions whose linear color-magnitude relations are simultaneously determined.
+We see where our best-fit model puts supernovae on a color-magnitude diagram.
+A representative example is shown in Figure~\ref{speccorr:fig}, which plots
+${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 + \delta_{\hat{U}} D$
+as a function of color excess $E_o({\hat{B}}-{\hat{V}})$, where the intrinsic color accounts for spectral-feature corrections.
+The shallower (but non-zero) slope at blue color transitions to a larger slope at red color, 
+as expected  for a mixed intrinsic--dust model.
+The non-zero blue slope implies that the new color term we detect is intrinsic (associated with all supernovae)
+and hence not attributable to dust.
 
@@
       \color{red}
-      The $U$-band magnitude corrections from the three color parameters $\gamma^0_{U} k_0 +\gamma^1_{U} k_1 + \delta_U D$
-are plotted as a function of $E_o(B-V)$, where the expected color accounts for spectral-feature corrections.  The left plot shows the full
+      The ${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 + \delta_{\hat{U}} D$
+are plotted as a function of $E_o({\hat{B}}-{\hat{V}})$, where the expected color accounts for spectral-feature corrections.  The left plot shows the full
 range of values whereas the right zooms in the upper-left corner of the population.
@@
 \end{figure}
+
+Our evidence for an intrinsic color effect is consistent with the conclusion of  \citetalias{2017ApJ...842...93M} (see their Figure~6.)
+Their intrinsic color-effect discerned using only one color parameter and a reasonable population model
+is likely traced to the additional supernova
+color parameter $D$ identified in this article without reference to a population model.
+We find $\delta_{\hat{B}}/(\delta_{\hat{B}}-\delta_{\hat{V}})=1.27^{ + 1.02}_{ - 1.16}$, which agrees with the  approximately corresponding (given that different broadband
+filters are used) $\beta_{int}=2.3\pm 0.3$ found by \citetalias{2017ApJ...842...93M}.
+\citetalias{2017ApJ...842...93M} treat dust as having constant $R$ whereas we allow $R$ to float 
+from supernova to supernova.  Nevertheless our 68\% credible interval for an
+effective $R^F$ of $2.31$--$2.69$ is consistent with their $R_V=2.8 \pm 0.3$.
 
@@
 Nesting this model in an extended model produces a result that 
-gives the first identification of  a new parameter that affects supernova
+gives the first identification of  a new
+\color{red}
+intrinsic
+\color{black} parameter that affects supernova
 colors in a manner that is distinct from the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
+\color{red}
+Not only do we detect an intrinsic color consistent with that
+found by \citetalias{2017ApJ...842...93M} using different model assumptions,
+we identify a new per-supernova observable parameter that distinguishes intrinsic
+and dust properties.
+\color{black}
 

### 2017-09-09 view11.py

@@ -169,7 +169,7 @@ crap = fit['gamma'][:,2][:,None]*fit['k']
 crap = crap-crap[:,0][:,None]
 plt.hist(numpy.median(crap,axis=0),bins,label='median',normed=True,alpha=0.5,width=0.025)
 plt.hist(crap.flatten(),bins,label='ideogram',normed=True,alpha=0.5)
-plt.xlabel(r'$\gamma^0_2 k_0 - \gamma^0_2 k_0|_0\approx A^F_V|_{R^F_{eff}=2.44}$')
+plt.xlabel(r'$\gamma^0_{\hat{V}} k_0 - \gamma^0_{\hat{V}} k_0|_0\approx A^F_V|_{R^F_{eff}=2.44}$')
 plt.legend()
 plt.tight_layout()
 pp = PdfPages('output11/deltagamma0_med.pdf')
@@ -182,7 +182,7 @@ crap2 = fit['rho1'][:,2][:,None]*fit['R']
 crap2 = crap2-crap2[:,0][:,None]
 plt.hist(numpy.median(crap2,axis=0),bins,label='median',normed=True,alpha=0.5,width=0.01)
 plt.hist(crap2.flatten(),bins,label='ideogram',normed=True,alpha=0.5)
-plt.xlabel(r'$\gamma^1_2 k_1 - \gamma^1_2 k_1|_0$')
+plt.xlabel(r'$\gamma^1_{\hat{V}} k_1 - \gamma^1_{\hat{V}} k_1|_0$')
 plt.legend(loc=2)
 plt.tight_layout()
 pp = PdfPages('output11/deltagamma1_med.pdf')
@@ -424,9 +424,9 @@ for i in xrange(4):
     maxy = (color_obs[:,i]+mag_mn[cind[i]]-mag_mn[2]).max()
     # axes[i].plot([miny,maxy],[miny,maxy])
 
-    axes[i,0].set_xlabel(r'$({0}-V)$'.format(cname[i]))
-    axes[i,0].set_ylabel(r'$({0}_o-V_o)$'.format(cname[i]))
-    lname = r'$\Delta({0}-V)$'.format(cname[i])
+    axes[i,0].set_xlabel(r'$(\hat{{{0}}}-\hat{{V}})$'.format(cname[i]))
+    axes[i,0].set_ylabel(r'$(\hat{{{0}}}_o-\hat{{V}}_o)$'.format(cname[i]))
[…]

### 2017-09-11 apj.tex
almost finished with Greg's comments

@@
 \color{red}
-The 68\% credible interval for an effective
+The 68\% credible interval for the sample effective
 %-----
-$R^F$ of the sample is 2.31 -- 2.69.
+$\langle R^F_{eff}\rangle$ is 2.31 -- 2.69.
 %-----
@@
 independent (to first order) of the amount of dust along the line of sight.
-\citet{2013ApJ...779...23M} find diversity in SNe~Ia UV emission, which they use to distinguish subclasses based on UV-optical colors.
+\color{red}
+Near and mid-UV photometry obtained by the Ultra-Violet/Optical Telescope on the Swift spacecraft cannot be entirely explained
+by dust absorption and hence imply intrinsic variability of supernova UV colors
+\citep{2017ApJ...836..232B}.
+\color{black}
+%\citet{2013ApJ...779...23M} find diversity in SNe~Ia UV emission, which they use to distinguish subclasses based on UV-optical colors.
 Measurements of color ratios are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
@@
 In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
-We summarize our findings, and relate our results to light-curve shape, SiII velocity, and the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
-residuals in \S\ref{discussion:sec}.
+\color{red}
+In  \S\ref{discussion:sec}
+we relate our results to known
+signatures of SN~Ia diversity.
+Conclusions are presented in \S\ref{conclusions:sec}.
+\color{black}
 
@@
 
+\color{red}
+This article presents the first application of a computationally intensive analysis, so although  high spectral resolution
+is available we here compress the information into low-resolution broadband photometry. 
+\color{black}
 Synthetic supernova-frame photometry is generated for a top-hat filter system
@@
 \color{red}
-The hat serves as a reminder that these are not standard filters.
+(The diacritic hat serves as a reminder that these are not standard Johnson-Cousins filters.)
 \color{black}
@@
 at $B$-band peak brightness.
-The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
+The equivalent widths of the SiII$\lambda 4141$ and CaII H\&K features are computed as
 in \citet{2008A&A...477..717B} and the 
@@
 
-Our analysis sample is comprised by the
+Our analysis sample is comprised of the
 172
-supernovae that have the data coverage to 
+supernovae that have been fully processed and have the data coverage to 
 give photometric and spectroscopic statistics described above.
@@
 
-In what is  referred to as Model~I, we hypothesize that at peak brightness
-SN~Ia broadband magnitudes and colors are correlated with
-spectral features: equivalent widths and line positions are considered in the model because their localization in wavelength
+In what is  referred to as Model~I, peak brightness
+SN~Ia broadband magnitudes and colors are 
+\color{red}
+directly
+\color{black}
+correlated with
+spectral features.
+Equivalent widths and line positions are considered in the model because their localization in wavelength
 makes their values insensitive to 
@@
 The per-supernova intrinsic magnitudes are then
-modified by an extrinsic physical process (i.e.\ dust) to produce apparent magnitudes that are subsequently measured by the observer.
+modified by an extrinsic 
+\color{red}
+latent
+physical process (that could be attributed to dust) 
+whose effect is manifest in the
+apparent magnitudes and colors
+\color{black}
+that are subsequently measured by the observer.
 
@@
 $C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
-to capture band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
+to capture 
+\color{red}
+potential
+\color{black}
+band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
 fluxes to luminosites.
@@
 The global parameter vectors that describe the SN~Ia population
-$\mathbf{c}$ (where $\mathbf{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $),
-$\pmb{\alpha}$, $\pmb{\beta}$,  and $\pmb{\eta}$,  are the intercept and slopes of the linear relationships that
+$\vec{c}$ (where $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $),
+$\vec{\alpha}$, $\vec{\beta}$,  and $\pmb{\eta}$,  are the intercept and slopes of the linear relationships that
 relate spectral-feature parameters with intrinsic magnitudes.
-The global parameter vectors $\pmb{\gamma}^0$, $\pmb{\gamma}^1$  are the slopes that relate 
+The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes that relate 
 the latent extrinsic-color parameters with apparent magnitudes.
@@
 The model as written has degeneracies that need to be constrained in order for fits to converge.
-The model does not specify the absolute magnitude nor the intrinsic color of a supernova that has no extrinsic color contribution,
+The model does not specify the absolute magnitude nor the intrinsic color of a supernova that has no extrinsic color contribution;
 in their place the zeropoints of the per-supernova magnitude and color parameters are set to the sample means
 \begin{equation}
-\langle \Delta \rangle=0, \langle k_0 \rangle=0, \langle k_1 \rangle=0.
+\langle \Delta \rangle=0,\ \langle k_0 \rangle=0,\ \langle k_1 \rangle=0.
 \end{equation}
 The model contains the product of latent parameters
-$\pmb{\gamma} k$, which leads to the degeneracy $\pmb{\gamma} \rightarrow a\pmb{\gamma}$, $k \rightarrow a^{-1} k$.
-To aid in the convergence of $\pmb{\gamma}$ and $k$ we impose a prior on the rms of $k$, though
+$\vec{\gamma} k$, which leads to the degeneracy $\vec{\gamma} \rightarrow a\vec{\gamma}$, $k \rightarrow a^{-1} k$.
+To aid in the convergence of $\vec{\gamma}$ and $k$ we impose a prior on the rms of $k$, though
 our physical interpretations are ultimately independent of this scaling.
-This prior does not specify the sign of $a$, which leaves a parity degeneracy.  As will be seen, the signal-to-noise in $\pmb{\gamma}$ is sufficiently
+This prior does not specify the sign of $a$, which leaves a parity degeneracy.  As will be seen, the signal-to-noise in $\vec{\gamma}$ is sufficiently
 high that our finite MCMC chains do not migrate between the degenerate solutions; to simplify the merging of multiple chains
@@
 \begin{equation}
-\gamma^0_{\hat{U}} > 0, \gamma^1_{\hat{U}} < 0.
+\gamma^0_{\hat{U}} > 0,\ \gamma^1_{\hat{U}} < 0.
 \end{equation}
@@
 %with the $\pm$ sign.
-As  in mixture models, the combinations $\pmb{\gamma}^0 k_0$ and $\pmb{\gamma}^1 k_1$ terms are degenerate under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
+As  in mixture models, the combinations $\vec{\gamma}^0 k_0$ and $\vec{\gamma}^1 k_1$ terms are degenerate under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
 we break that degeneracy  by setting consistent initial conditions that succeed in keeping indices consistent over all analysis chains.
@@
 Another form of degeneracy is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
- $\pmb{\gamma}^0 \rightarrow \pmb{\gamma}^0  + \epsilon_{\gamma^0}$, $\pmb{\gamma}^1 \rightarrow \pmb{\gamma}^1 + \epsilon_{\gamma^1}$
+ $\vec{\gamma}^0 \rightarrow \vec{\gamma}^0  + \epsilon_{\gamma^0}$, $\vec{\gamma}^1 \rightarrow \vec{\gamma}^1 + \epsilon_{\gamma^1}$
  under the condition
@@
 $$
-i.e.\ shifts in the global coefficients $\pmb{\gamma}$ can be compensated by shifts in $\pmb{\Delta}$ for each supernova while maintaining 
+i.e.\ shifts in the global coefficients $\vec{\gamma}$ can be compensated by shifts in $\pmb{\Delta}$ for each supernova while maintaining 
 $\langle \Delta \rangle=0$.
 Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
-$\pmb{\alpha} \rightarrow \pmb{\alpha} - \pmb{\gamma} \epsilon$, $\mathbf{c} \rightarrow \mathbf{c} + \langle EW_{Ca}\rangle \epsilon$, i.e. the
+$\vec{\alpha} \rightarrow \vec{\alpha} - \vec{\gamma} \epsilon$, $\vec{c} \rightarrow \vec{c} + \langle EW_{Ca}\rangle \epsilon$, i.e. the
 linear external terms can leak into the linear spectral feature corrections.
@@
 per-supernova parameters
-$\Delta$, $EW$, $\lambda$, $k$ are uncorrelated.
+$\Delta$, $EW$, $\lambda$, $k_0$, and $k_1$ are uncorrelated.
 
 The parameterized intrinsic dispersion, $C_c$, seemingly introduces degeneracy in the model, as magnitude and color variation
-ascribed to $\Delta$, $\pmb{\gamma}^0 k_0$, and $\pmb{\gamma}^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
+ascribed to $\Delta$, $\vec{\gamma}^0 k_0$, and $\vec{\gamma}^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
 that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$;
@@
 
+\color{red}
+No informative prior is used for each of the per-supernova parameters $\Delta$, $EW$, $\lambda$, $k_0$, and $k_1$:
+they are taken to be drawn independently from a flat distribution. 
+As a consequence, the prior has uncorrelated parameters as mentioned above.  
+\color{black}
+
 For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
@@
    \includegraphics[width=5.2in]{output11/coeff0.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{U}}$ band.
+            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{U}}$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
@@
    \includegraphics[width=5.2in]{output11/coeff1.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{B}}$ band.
+            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{B}}$ band.
  \label{global2:fig}}
@@
    \includegraphics[width=5.2in]{output11/coeff2.pdf} 
-            \caption{Model~I posterior contours for $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{V}}$ band.
+            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{V}}$ band.
  \label{global3:fig}}
@@
       \includegraphics[width=5.2in]{output11/coeff3.pdf} 
-            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$,  $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{R}}$ band.
+            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{R}}$ band.
  \label{global4:fig}}
@@
          \includegraphics[width=5.2in]{output11/coeff4.pdf} 
-            \caption{Model~I posterior contours for  $\mathbf{c}$, $\pmb{\alpha}$, $\pmb{\beta}$, $\pmb{\eta}$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$ in the ${\hat{I}}$ band.
+            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{I}}$ band.
  \label{global5:fig}}
@@
 $N_{eff}$ is an estimate of the number of independent draws. The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
-output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
+output also gives  $N_{eff} \gg 100$ for all parameters, indicating that all are densely sampled.
 Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig} -- \ref{global5:fig}.  In these tests there is no evidence that
@@
 deduced versus observed intrinsic colors and the histogram of their differences
-are shown in Figure~\ref{residual:fig}. 
-There is no evidence of a catastrophically poor model predictions nor of extreme
+is shown in Figure~\ref{residual:fig}. 
+There is no evidence of catastrophically poor model predictions nor of extreme
 outlying data.
-We have rurun the analysis with a variety of initial conditions, including one with $\pmb{\gamma}$ equal to zero, except for a small positive 
+We have rurun the analysis with a variety of initial conditions, including one with $\vec{\gamma}$ equal to zero, except for a small positive 
 $\gamma^0_0$ and small negative $\gamma^1_0$; the 68\% credible intervals
@@
             \caption{
-            Deduced versus observed intrinsic colors for four selected colors.  Plotted on the right for each color
+            Deduced versus observed intrinsic colors, for four selected colors.  Plotted on the right for each color
 is the histogram of the difference between the observed and intrinsic colors.
@@
 
-For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$, and $\sigma$
+For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$
 are given in Table~\ref{global:tab}.
-As the $\pmb{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
+As the $\vec{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
 their results are shown in terms of $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
@@
 
-We find significant non-zero values for $\pmb{\alpha}$ and $\pmb{\beta}$, indicating that $EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
-peak magnitudes.
-This validates our hypothesis that spectral indicators
-are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero
+We find significant non-zero values for $\vec{\alpha}$ and $\vec{\beta}$, indicating that
+$EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
+peak magnitudes
+\color{red}
+as expected.
+\color{black}
+On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero
 to  within one standard deviation.
@@
 Both $EW_{Ca}$ and $EW_{Si}$ are associated with color changes, though not in ${\hat{B}}-{\hat{V}}$ specifically.
-We do not detect a significant association between
-$\lambda_{Si}$ and color.
-
-The signal in  $\pmb{\alpha}$ and $\pmb{\beta}$ cannot be attributed to the equivalent widths themselves.
+\color{red}
+We do not detect a significant direct connection between
+$\lambda_{Si}$ and color, though their indirect correlation is discussed in \S\ref{velocity:sec}.
+\color{black}
+
+The signal in  $\vec{\alpha}$ and $\vec{\beta}$ cannot be attributed to the equivalent widths themselves.
 The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the ${\hat{B}}$-band is 851~\AA, so that its direct affect on magnitude
@@
    Normalized ideogram and histogram of the medians of the grey offset relative to one arbitrary supernova, $\Delta-\Delta|_0$.  
+   \color{red}
+   The supernovae with the highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
+   redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.
+   \color{black}
    \label{hist:fig}}
@@
 
-Non-trivial residual magnitude dispersions are captured in $C_c$.  The square
+Non-trivial residual magnitude
+\color{red}
+and color dispersions are captured in $C_c$
+at the level of 4--10$\sigma$.
+\color{black}
+The square
 root of the diagonal elements are denoted as $\sigma$, which
@@
 \left(
-0.021^{+0.004}_{-0.005} ,
-0.067^{+0.010}_{-0.010},
-0.034^{+0.005}_{-0.005},
-0.023^{+0.002}_{-0.002},
+0.021^{+0.004}_{-0.005} ,\, 
+0.067^{+0.010}_{-0.010},\, 
+0.034^{+0.005}_{-0.005},\, 
+0.023^{+0.002}_{-0.002},\, 
 0.053^{+0.004}_{-0.004}
@@
 \begin{array}{rrrrr}
-1 & -0.48^{+0.20}_{-0.18} & -0.34^{+0.21}_{-0.22} & 0.88^{+0.10}_{-0.25} & 0.60^{+0.11}_{-0.19} \\
--0.48^{+0.20}_{-0.18} & 1 & 0.60^{+0.10}_{-0.13} & -0.38^{+0.18}_{-0.17} & -0.33^{+0.15}_{-0.14} \\
--0.34^{+0.21}_{-0.22} & 0.60^{+0.10}_{-0.13} & 1 & -0.21^{+0.17}_{-0.17} & 0.08^{+0.14}_{-0.15} \\
-0.88^{+0.10}_{-0.25} & -0.38^{+0.18}_{-0.17} & -0.21^{+0.17}_{-0.17} & 1 & 0.65^{+0.06}_{-0.07} \\
-0.60^{+0.11}_{-0.19} & -0.33^{+0.15}_{-0.14} & 0.08^{+0.14}_{-0.15} & 0.65^{+0.06}_{-0.07} & 1 \\
+\hat{V} & -0.48^{+0.20}_{-0.18} & -0.34^{+0.21}_{-0.22} & 0.88^{+0.10}_{-0.25} & 0.60^{+0.11}_{-0.19} \\
+\ldots & {\hat{U}}-{\hat{V}} & 0.60^{+0.10}_{-0.13} & -0.38^{+0.18}_{-0.17} & -0.33^{+0.15}_{-0.14} \\
+\ldots  & \ldots & {\hat{V}}-{\hat{V}} & -0.21^{+0.17}_{-0.17} & 0.08^{+0.14}_{-0.15} \\
+\ldots  & \ldots  &\ldots  & {\hat{V}}-{\hat{R}} & 0.65^{+0.06}_{-0.07} \\
+\ldots  & \ldots  &\ldots  &\ldots & {\hat{V}}-{\hat{I}} \\
 \end{array}
@@
  \end{multline}
+\color{red}
+To reduce clutter only the upper triangular part of the otherwise symmetric matrix is shown.
+\color{black}
 These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where
@@
 Running an analysis assuming no intrinsic dispersion (replacing the probabilistic intrinsic magnitudes in Eqn.~\ref{ewsiv:eqn}
-with a strict equality), we find significant shifts in all slope parameters  and smaller statistical uncertainties.
+with a strict equality), we find significant shifts in all slope parameters  and 
+\color{red}
+artificially
+\color{black}
+smaller statistical uncertainties.
 
@@
 \begin{array}{rrrrrr}
-1 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
-0.00^{+0.06}_{-0.06} & 1 & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
--0.07^{+0.07}_{-0.06} & 0.10^{+0.03}_{-0.03} & 1 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
--0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1 & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
-0.10^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1 & 0.06^{+0.08}_{-0.08} \\
--0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.04^{+0.08}_{-0.07} & 0.03^{+0.08}_{-0.08} & 0.06^{+0.08}_{-0.08} & 1 \\
+\Delta & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
+\ldots  &EW_{Ca} & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
+\ldots  & \ldots &  EW_{Si} & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
+\ldots & \ldots  &\ldots  & \lambda_{Si} & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
+\ldots & \ldots & \ldots & \ldots & E_{\gamma^0}({\hat{B}}-{\hat{V}}) & 0.06^{+0.08}_{-0.08} \\
+\ldots &\ldots  & \ldots  &\ldots & \ldots & E_{\gamma^1}({\hat{B}}-{\hat{V}}) \\
 \end{array}
@@
 We find weak correlations between our color-excess parameters and the input features; 
-only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}({\hat{B}}-{\hat{V}})$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
+only the $ -0.17 \pm 0.05$ correlation
+between $E_{\gamma^0}({\hat{B}}-{\hat{V}})$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
 The feature $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
@@
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
-All elements of the two $\pmb{\gamma}$ parameter vectors  are significantly non-zero. 
+All elements of the two $\vec{\gamma}$ parameter vectors 
+\color{red}
+describing intrinsic color
+\color{black}
+are significantly non-zero. 
 None of the 20000 links of 
-our Monte Carlo chains for $\pmb{\gamma}$ extend to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
+our Monte Carlo chains for $\vec{\gamma}$ extend to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
 influence of $k_0$ and $k_1$  on supernova magnitudes
@@
 
-We compare our model's parameter vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ with the expectations of  dust models.
+We compare our model's parameter vectors $\vec{\gamma}^0$ and $\vec{\gamma}^1$ with the expectations of  
+\color{red}
+dust-extinction
+\color{black}
+models.
 The 2-parameter linear model
@@
 \end{equation}
-approximately describes dust models \citep[for example, the wavelength dependent model of ][is linear,
+approximately describes dust 
+\color{red}
+dust-extinction
+\color{black}
+models \citep[for example, the wavelength-dependent model of ][is linear,
 though its linearity is lost when integrated over broad-band filters]{1989ApJ...345..245C}.
@@
 gives
-$\mathbf{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\mathbf{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
-The $F$ superscript is used to distinguish parameters of the \citetalias{1999PASP..111...63F} model.
+$\vec{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\vec{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
+(The $F$ superscript is used to distinguish parameters of the \citetalias{1999PASP..111...63F} model.)
 Over the ranges of
  $R^F$ and $A^F_V$,
-and the wavelengths under consideration,  the values of the elements of $a$ and $b$ vary by $<5$\%;
-for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in extinction from the linear approximation of
+and the wavelengths under consideration here,  the values of the elements of $a$ and $b$ vary by $<5$\%
+\color{red}
+for the
+\citepalias{1999PASP..111...63F} model.
+Over the range
+\color{black}
+ $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in extinction from the linear approximation of
 Eqn.~\ref{f99:eqn} has amplitude $<0.008$ mag.
@@
 with $E_{\gamma^i}({\hat{B}}-{\hat{V}}) \equiv  (\gamma^i_{\hat{B}}-\gamma^i_{\hat{V}})k_i$ as defined in \S\ref{results:sec}.
-Our median-fit values for the $\pmb{\gamma}$ coefficients are
+Our median-fit values for the $\vec{\gamma}$ coefficients are
 %---- fitz11.py
-$\frac{\pmb{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}}  =(4.80 ,   3.89,   2.89,   2.22,   1.59)$ and
-$ \frac{\pmb{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}}=(-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71)$.
+$\frac{\vec{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}}  =(4.80 ,   3.89,   2.89,   2.22,   1.59)$ and
+$ \frac{\vec{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}}=(-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71)$.
 %----
@@
 Our model $\gamma$ vectors can be written in terms of the 
-dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\mathbf{a}$ and $\mathbf{b}$.
+dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\vec{a}$ and $\vec{b}$.
 The result is
@@
 \begin{pmatrix}
- \frac{\pmb{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
-\frac{\pmb{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} 
+ \frac{\vec{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
+\frac{\vec{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} 
 \end{pmatrix}=
@@
 \begin{pmatrix}
-\mathbf{a} \\
-\mathbf{b}
+\vec{a} \\
+\vec{b}
 \end{pmatrix}+
@@
 \end{align}
-quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.  The most significant
+quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\vec{\gamma}$ vectors.  The most significant
 deviation away from the plane is in the ${\hat{R}}$-band.
@@
 
-The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the ${\hat{U}}{\hat{V}}I$-subspace two perspectives (left and right columns)
-of the unit vectors corresponding to $\pmb{\gamma}^0$ and  $\pmb{\gamma}^1$ of our model (solid lines),
-and $\mathbf{a}$, $\mathbf{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All  vectors are set to intersect the origin.
+The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the ${\hat{U}}{\hat{V}}I$-subspace two perspectives (left and right panels)
+of the unit vectors corresponding to $\vec{\gamma}^0$ and  $\vec{\gamma}^1$ of our model (solid lines),
+and $\vec{a}$, $\vec{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All  vectors are set to intersect the origin.
 The two perspectives show that while the four vectors point in different directions for each band combination,
 they are almost coplanar in ${\hat{U}}{\hat{V}}{\hat{I}}$ (they are slightly less coplanar in ${\hat{B}}{\hat{V}}{\hat{R}}$).
-The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
+The $\vec{a}$ and $\vec{b}$ vectors and the $\vec{\gamma}^0$ and $\vec{\gamma}^1$
 vectors span near-parallel planes in the 5-dimensional color space, and hence the latter can be almost entirely expressed in terms of
@@
    two different perspectives.
-   Our model is shown in solid-line unit vectors in the directions of $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$. The only possible magnitudes possible
+   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes possible
    are a linear combination of these two vectors, and hence are confined to the plane that contains both.
    The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
-   in the directions of  $\mathbf{a}$, $\mathbf{b}$; the only possible magnitudes possible are confined to the plane that contains both.
+   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes possible are confined to the plane that contains both.
    The perspective on the right visually show that all four vectors are nearly coplanar.  
-   The combination $\mathbf{a}+\mathbf{b}/2.44$ is shown in the dotted red
-   line: it is almost perfectly superimposed on $\pmb{\gamma}^0$.
+   The combination $\vec{a}+\vec{b}/2.44$ is shown in the dotted red
+   line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
    \label{plane:fig}}
@@
 Our linear model would be satisfied by any two independent vectors  that span
-the plane defined by the $\pmb{\gamma}$ vectors.
-We begin discussion on the specific choice of $\pmb{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model.
+the plane defined by the $\vec{\gamma}$ vectors.
+We begin discussion on the specific choice of $\vec{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model.
 While
-Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\mathbf{a}$ and $\mathbf{b}$ and
+Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
 their corresponding parameters 
 $A_V$ and 
-$E(B-V)$, the linear dust model could be written in terms of any two other basis vectors  $\mathbf{a}+\kappa_1 \mathbf{b}$
-and $\kappa_2 \mathbf{a} + \mathbf{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
+$E(B-V)$, the linear dust model 
+\color{red}
+alternatively
+\color{black}
+could be written in terms of any two other basis vectors  $\vec{a}+\kappa_1 \vec{b}$
+and $\kappa_2 \vec{a} + \vec{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
 In this basis, the model is then
@@
 This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
-We use this interpretation to assign  $R^F_{eff} = \kappa_1^{-1}$ as
-the effective total-to-selective extinction of our sample.
-The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$.
-Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\pmb{\gamma}^0$ and  $\mathbf{a}+\mathbf{b}/2.44$.
-From the Monte Carlo chains, we find a 68\% credible interval for  $R^F_{eff}$ of 2.26--2.63.
-
-Given the association of  our parameter $\gamma^0_{\hat{V}} k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
+We use this interpretation to assign  $\langle R^F_{eff}\rangle = \kappa_1^{-1}$ as
+the
+\color{red}
+ensemble mean
+\color{black}
+effective total-to-selective extinction of our sample.
+The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}, 
+\color{red}
+giving
+\color{black}
+$\kappa^{-1}_1=2.82/1.15 =2.44$.
+Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.44$.
+From the Monte Carlo chains, we find a 68\% credible interval for  $\langle R^F_{eff}\rangle$ of 2.26--2.63.
+
+Given the association of  our parameter $\gamma^0_{\hat{V}} k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust-extinction
+model up to an additive offset,
 the former's distribution can be compared to the expectation for the latter.
@@
 The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
-with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H, 2007ApJ...659..122J}.
-This distribution is given by the data, and so is not dependent of any knowledge or prior
+with
+\color{red}
+simulations based on expected dust distributions
+\color{black}
+within galaxies and the distribution of galaxy orientations with respect to the observer,
+\color{red}
+which determine column densities along the lines of sight toward supernovae that are consistent with observations
+\color{black}
+\citep{1998ApJ...502..177H, 2007ApJ...659..122J}.  
+\color{red}
+We emphasize that unlike other analyses,
+\color{black}
+this distribution is given by the data, and so is not dependent on any knowledge or prior
 for the distribution of dust extinction the SN population is expected to suffer.
@@
 (left) : $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
-which  is associated with extinction corrections due to deviations away from the canonical $R^F_{eff}$ value (right).
+which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{eff}\rangle$ value (right).
    \label{k0_med:fig}}
@@
 
-We now consider the direction of $\pmb{\gamma}^1$. 
+We now consider the direction of $\vec{\gamma}^1$. 
 Different supernovae are expected to encounter dust with different $R^F$;
-having  associated $\pmb{\gamma}^0$ with an $R^F_{eff}$, $\pmb{\gamma}^1$ is associated with perturbations
-away that effective value.
-Let us introduce a new parameter for each supernova $\delta R$ such that its $R^F = R^F_{eff}(1+  \delta R)$.
+having  associated $\vec{\gamma}^0$ with an $\langle R^F_{eff}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
+away from that effective value.
+Let us introduce a new parameter for each supernova, $\delta R$, such that its $R^F =\langle R^F_{eff}\rangle(1+  \delta R)$.
 Variations in the value of $R^F$ (and hence $\delta R$) with the prior of the non-correlation between $k_0$ and $k_1$ lead 
@@
 \begin{equation}
-\kappa_2 = R^F_{eff} \left(1- \frac{\mbox{Var}(\delta R\, E^F(B-V))}{\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))}\right).
+\kappa_2 =\langle R^F_{eff}\rangle \left(1- \frac{\mbox{Var}(\delta R\, E^F(B-V))}{\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))}\right).
 \end{equation}
@@
 These findings are consistent with previous results:
+\color{red}
+using fixed dust-extinction models,
+\color{black}
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
-A per supernova determination $R^F$ requires the specification of the magnitude and colors of supernovae that experience
+A per supernova determination of $R^F$ requires the specification of the magnitude and colors of supernovae that experience
 no dust, which is unspecified in our model.
@@
 As a check of our analysis implementation and our
-interpretation of $R^F_{eff}$, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
-SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
+interpretation of $\langle R^F_{eff}\rangle$, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
+SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust-extinction model.  The supernovae
 are assigned $E^F(B-V)$ parameters equal to the ${\hat{B}}-{\hat{V}}$ color excesses determined in our sample
@@
 measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations that together yield a median
-$R^F_{eff}$ of 2.53, showing that our effective value is close to the  $R^F=2.5$ input into the simulations.
+$\langle R^F_{eff}\rangle$ of 2.53, showing that our effective value is close to the  $R^F=2.5$ input into the simulations.
 
@@
 $\{k_0, k_1\}$ describe for the most part the combination of the $\{A^F_V, E^F(B-V)\}$ parameters used
-in standard models of Milky Way dust.  
+in standard models of Milky Way dust extinction.  
 This conclusion is based on the
@@
 the distribution of $k_0$ is consistent with the expected distribution of $A^F_V$.
-Nevertheless, there do remain some small inconsistencies between our numbers and expectations from dust models.
+Nevertheless, there do remain some small inconsistencies between our numbers and expectations from
+\color{red}
+previous dust-extinction
+\color{black}
+models.
 
@@
 color parameter.
-The extended model, referred to as Model~II, is written as
+An extended model, referred to as Model~II, is written as
 \begin{equation}
@@
 \end{equation}
-In all aspects Model~II is identical to Model~I except for the addition of the term $\pmb{\delta} D$: for $\pmb{\delta}=0$ and arbitrary $D$, Model II
+In all aspects Model~II is identical to Model~I except for the addition of the term $\vec{\delta} D$: for $\vec{\delta}=0$ and arbitrary $D$, Model II
 and Model~I are the same.
@@
 Each supernova has an intrinsic $D$ parameter that is linearly related to
-absolute magnitudes through the global coefficients $\pmb{\delta}$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
+absolute magnitudes through the global coefficients $\vec{\delta}$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
 its effects on broadband magnitudes.
 
-The $\pmb{\delta} D$ term contributes to the means of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms.
+The $\vec{\delta} D$ term contributes to the means of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms.
 However, switching the placement of 
-$\pmb{\delta} D$ term from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from an intrinsic to extrinsic contribution,
+$\vec{\delta} D$ term from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from an intrinsic to extrinsic contribution,
 does not significantly affect the results, meaning that data are not constraining enough
-to identify $\pmb{\delta} D$ as being physically intrinsic or extrinsic.
+to identify $\vec{\delta} D$ as being physically intrinsic or extrinsic.
 \color{red}
@@
 to specify the zeropoint color.  We assign a prior on the amplitude of the ensemble of $D$ to break the
-degeneracy $\pmb{\delta} \rightarrow a\pmb{\delta}$, $D \rightarrow a^{-1}D$: as described
-in \S\ref{model:sec} this prior does not affect physics but aids in the convergence of fitting $D$ and $\pmb{\delta}$ as independent parameters.
+degeneracy $\vec{\delta} \rightarrow a\vec{\delta}$, $D \rightarrow a^{-1}D$: as described
+in \S\ref{model:sec} this prior does not affect physics but aids in the convergence of fitting $D$ and $\vec{\delta}$ as independent parameters.
 A sign degeneracy in $a$ remains.
-In contrast to our previous experience with $\pmb{\gamma}$ in Model~I, our MCMC chains migrate between
-the sign-degenerate solutions in  $\pmb{\delta}$.  We make
+In contrast to our previous experience with $\vec{\gamma}$ in Model~I, our MCMC chains migrate between
+the sign-degenerate solutions in  $\vec{\delta}$.  We make
 no attempt to resolve this degeneracy in the model.
 In the running of the Monte Carlo fit, the initial conditions and ranges for
-$\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ were set to be in the neighborhood of the best fit of Model~I
+$\vec{\gamma}^0$ and $\vec{\gamma}^1$ were set to be in the neighborhood of the best fit of Model~I
 to maintain their correspondence between the two models.
 Our finite MCMC chains do not migrate away from these ranges.
-The initial condition of $\pmb{\delta}$ is set to zero.
+The initial condition of $\vec{\delta}$ is set to zero.
 
@@
 
-The posteriors of the $\pmb{\delta}$ parameters are shown  in
+The posteriors of the $\vec{\delta}$ parameters are shown  in
+\color{red}
+the left panel of
+\color{black}
 Figure~\ref{deltacorner:fig}.
@@
 the point $\delta_X=0$, i.e.\ the nested Model~I with no effect on magnitude by a third parameter,  lies on the 85\%-ile contour.
-Model~II has a  $\pmb{\delta} \rightarrow -\pmb{\delta}$, $D \rightarrow -D$ degeneracy that results in a bimodal posterior.
+Model~II has a  $\vec{\delta} \rightarrow -\vec{\delta}$, $D \rightarrow -D$ degeneracy that results in a bimodal posterior.
 To aid in the visualization of the results,
 we break this degeneracy by imposing  that the $D$ of the one supernova with the highest signal-to-noise be positive.
-The new posterior contours of $\pmb{\delta}$ with this added
-condition are shown in Figure~\ref{deltacorner:fig}.
-The shapes of the new $\pmb{\delta}$ posteriors are somewhat distorted compared to the original;
+The new posterior contours of $\vec{\delta}$ with this added
+condition are shown in 
+\color{red}
+the right panel of
+\color{black}
+Figure~\ref{deltacorner:fig}.
+The shapes of the new $\vec{\delta}$ posteriors are somewhat distorted compared to the original;
 despite its relatively strong signal-to-noise, the original posterior for $D$ for the selected supernova does have significance on both sides of zero,
-resulting in changes in the shape of the $\pmb{\delta}$ posteriors when  $D$ to forced to be positive.   
-The modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$ in for $X={\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ respectively.
+resulting in changes in the shape of the $\vec{\delta}$ posteriors when  $D$ to forced to be positive.   
+The 
+\color{red}
+two (parity symmetric)
+\color{black}
+modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$~mag
+for $X={\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ respectively.
 The values of $\delta_X/\delta_{\hat{U}}-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
@@
      \includegraphics[width=2.8in]{output25/delta_corner_flipped.pdf}
-   \caption{Left:  Model~II posterior contours for $\pmb{\delta}$.
+   \caption{Left:  Model~II posterior contours for $\vec{\delta}$.
    Right: The same posteriors after imposing that $D$ of the one supernova with highest signal-to-noise be positive.
-     Lines for $\pmb{\delta}=0$ are overplotted.
+     Lines for $\vec{\delta}=0$ are overplotted.
    \label{deltacorner:fig}}
@@
  (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
-The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5$ times larger for the external contribution than for the extrinsic dust
+The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5 \times$ larger for the external contribution than for the extrinsic dust
 component.  
@@
 mag respectively.
-The $E_\delta({\hat{B}}-{\hat{V}})$ standard deviation is comparable to its measurement uncertainty per-supernova.
-The color excesses of individual supernovae have low signal-to-noise 
-and the significance of $\pmb{\delta}$
+\color{red}
+It should be noted that
+\color{black}
+the $E_\delta({\hat{B}}-{\hat{V}})$ standard deviation is comparable to its measurement uncertainty per-supernova.
+\color{red}
+Thus, since
+\color{black}
+the color excesses of individual supernovae have low signal-to-noise,
+the significance of $\vec{\delta}$
 is drawn from the ensemble of objects.
@@
 \begin{array}{rrrrrrr}
-1 & 0.01^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.07} & 0.10^{+0.07}_{-0.06} & 0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} \\
-0.01^{+0.06}_{-0.06} & 1 & 0.10^{+0.04}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.04^{+0.06}_{-0.06} & -0.00^{+0.07}_{-0.08} & -0.00^{+0.08}_{-0.08} \\
--0.07^{+0.07}_{-0.06} & 0.10^{+0.04}_{-0.04} & 1 & -0.14^{+0.03}_{-0.03} & -0.16^{+0.05}_{-0.05} & -0.03^{+0.08}_{-0.08} & 0.01^{+0.08}_{-0.08} \\
--0.04^{+0.06}_{-0.07} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.03}_{-0.03} & 1 & 0.03^{+0.05}_{-0.06} & 0.02^{+0.07}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
-0.10^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & -0.16^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1 & 0.05^{+0.08}_{-0.08} & -0.01^{+0.07}_{-0.07} \\
-0.00^{+0.08}_{-0.07} & -0.00^{+0.07}_{-0.08} & -0.03^{+0.08}_{-0.08} & 0.02^{+0.07}_{-0.08} & 0.05^{+0.08}_{-0.08} & 1 & -0.00^{+0.07}_{-0.08} \\
--0.01^{+0.08}_{-0.08} & -0.00^{+0.08}_{-0.08} & 0.01^{+0.08}_{-0.08} & -0.01^{+0.08}_{-0.08} & -0.01^{+0.07}_{-0.07} & -0.00^{+0.07}_{-0.08} & 1 \\
+\Delta& 0.01^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.07} & 0.10^{+0.07}_{-0.06} & 0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} \\
+\dots & EW_{Ca} & 0.10^{+0.04}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.04^{+0.06}_{-0.06} & -0.00^{+0.07}_{-0.08} & -0.00^{+0.08}_{-0.08} \\
+\dots  &\dots  &EW_{Si}& -0.14^{+0.03}_{-0.03} & -0.16^{+0.05}_{-0.05} & -0.03^{+0.08}_{-0.08} & 0.01^{+0.08}_{-0.08} \\
+\dots  &\dots  & \dots  & \lambda_{Si} & 0.03^{+0.05}_{-0.06} & 0.02^{+0.07}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
+\dots &\dots & \dots &\dots  &E_{\gamma^0}({\hat{B}}-{\hat{V}})& 0.05^{+0.08}_{-0.08} & -0.01^{+0.07}_{-0.07} \\
+\dots & \dots  &\dots & \dots &\dots  &  E_{\gamma^1}({\hat{B}}-{\hat{V}}) & -0.00^{+0.07}_{-0.08} \\
+\dots  &\dots & \dots  & \dots & \dots &\dots  & A_{\delta {\hat{U}}} \\
 \end{array}
@@
 heavily extinguished by host-galaxy dust.
-Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.
 
@@
 Their independence implies that a single physical parameter is not being artificially attributed to two
-model parameters.  One could have expected this to occur since our linear model does not precisely
+model parameters.  One could have
+\color{red}
+worried this might
+\color{black}
+occur since our linear model does not precisely
 describe the non-linearity between broad-band magnitudes and dust parameters. A
 correlation 
-between the parameters despite the prior would of complicated any claims of the detection of a third independent supernova parameter.
+between the parameters despite the prior would have complicated any claims of the detection of a third independent supernova parameter.
 
@@
 
-The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_{\hat{U}}$) can be expressed 
-in terms of the $\mathbf{a}$ and $\mathbf{b}$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
+The newly fitted $\vec{\gamma}$ and  $\vec{\delta}$ vectors (the latter normalized by $\delta_{\hat{U}}$) can be expressed 
+in terms of the $\vec{a}$ and $\vec{b}$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
 \begin{equation}
 \begin{pmatrix}
- \frac{\pmb{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
-\frac{\pmb{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} \\
+ \frac{\vec{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
+\frac{\vec{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} \\
 \frac{\delta_X}{\delta_{\hat{U}}} \\
@@
 \end{align}
-are perpendicular to $a$ and $b$.
-The $\pmb{\gamma}$ residuals $\pmb{\epsilon}_{\gamma^0}$ and
+are perpendicular to $\vec{a}$ and $\vec{b}$.
+The $\vec{\gamma}$ residuals $\pmb{\epsilon}_{\gamma^0}$ and
 $\pmb{\epsilon}_{\gamma^1} $
-quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that just as in Model~I most
-of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
- $\pmb{\delta}$ too
-has a significant projection onto the dust plane, as the $\pmb{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
-The transformation between the new set of $\pmb{\gamma}$'s and dust parameters yields
+quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that, just as in Model~I, most
+of the $\vec{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
+ $\vec{\delta}$ too
+has a significant projection onto the dust plane, as the $\pmb{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\vec{\delta}$ vector.
+The transformation between the new set of $\vec{\gamma}$'s and dust parameters yields
 a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, shifted to slightly  higher values relative to the results of Model~I.
 
-The significance of the $\pmb{\delta}$ measurement is evaluated using simulated datasets.
-For one set of tests, we realize 50 random realizations of data with input  parameters equal to the median values of the 
+The significance of the $\vec{\delta}$ measurement is evaluated using simulated datasets.
+For one set of tests, we generate 50 random realizations of data with input  parameters equal to the median values of the 
 parameter posteriors found in
-\S\ref{model:sec}, and using the same noise as our data.  To represent the null hypothesis, the input $\pmb{\delta}$-vector is set to zero.
+\S\ref{model:sec}, and using the same noise as our data.  
+\color{red}
+(Given the non-trivial computational time for the Monte Carlo, the 2\% precision from the 
+is deemed sufficient for our purposes.)
+\color{black}
+To represent the null hypothesis, the input $\vec{\delta}$-vector is set to zero.
 Figure~\ref{pvalues_delta2:fig} shows results of fits of these null-realizations next  to the results from the real data.
@@
 values of  the credible interval of our data relative to those from the simulations, we obtain
-three different $p$-values ranging from 0.90--0.98, indicating that the data result is incompatible with the null hypothesis. 
-As a point of comparison, recall that in the Bayesian posterior
-the null result
-$\pmb{\delta}=0$ lies on the 85\%-ile contour.
+three different $p$-values ranging from 0.90--0.98, indicating that the
+\color{red}
+null hypothesis is a poor representation of the data.
+\color{black}
 
@@
   \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
-            \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\pmb{\gamma}$, $\delta_\perp^2/\delta^2$, for 50 independent simulated data sets with input $\delta=0$.
+            \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\vec{\gamma}$, $\delta_\perp^2/\delta^2$, for 50 independent simulated data sets with input $\delta=0$.
 The fits
@@
 
-An interesting feature of $\pmb{\delta}$ is that its direction lies close to the plane defined by the
-$\pmb{\gamma}$ vectors.
+An interesting feature of $\vec{\delta}$ is that its direction lies close to the plane defined by the
+$\vec{\gamma}$ vectors.
 This leads to the concern that our model and analysis  could spontaneously generate a third
-vector almost degenerate with the others, despite the prior for the independence of $k_0$, $k_1$, and $D$.
-This hypothesis is tested using the 
-relative projection of $\pmb{\delta}$  perpendicular to the plane defined by the $\pmb{\gamma}$'s, $\delta_\perp^2/\delta^2$,
+vector almost degenerate with the others, despite the prior 
+\color{red}
+encouraging
+\color{black}
+ the independence of $k_0$, $k_1$, and $D$.
+This \color{red}
+possibility
+\color{black}
+ is tested using the 
+relative projection of $\vec{\delta}$  perpendicular to the plane defined by the $\vec{\gamma}$'s, $\delta_\perp^2/\delta^2$,
 for the same 50 null simulations that were just described.
 Figure~\ref{pvalues_delta2:fig} shows  that for none of the simulations does our analysis produce 
- $\delta_\perp^2/\delta^2$ as low as that from our data.  The $p$-values $>0.98$ indicate that the result from our data
- is incompatible with the null hypothesis.
+ $\delta_\perp^2/\delta^2$ as low as that from our data.  The $p$-values $>0.98$ indicate that 
+ \color{red}
+ the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be chance. 
+ \color{black}
 
 Potential biases in our results are measured through simulation.
-We realize 50 random realizations of data with input  parameters equal to the median values found in
-this Section, except for $\pmb{\delta}$ which is assigned the, and the same noise as our data.
-The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.
-The stack is sensitive to
+We generate 50 random realizations of data with input  parameters equal to the median values found in
+this Section, except for $\vec{\delta}$, which is assigned
+\color{red}
+the mode shown in Figure~\ref{deltacorner:fig},
+\color{black}
+ and the same noise as our data.  The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
 biases in the best fit value.
-The stack of  $\pmb{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias between
+The stack of  $\vec{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias between
 the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ and the mode of  the stacks $(-1.06, -0.95, -0.41, -0.11, 0.40)$.
@@
 
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
-            \caption{Stacked $\pmb{\delta}$ posterior contours for 50 independent simulated data sets.
-            The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
-            \label{simdelta:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of ten independent simulated data sets.
-The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
-            \label{simglobal1:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of ten independent simulated data sets.
-The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
- \label{simglobal2:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of ten independent simulated data sets.
-The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
-\label{simglobal3:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-      \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of ten independent simulated data sets.
-The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
-\label{simglobal4:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-         \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\pmb{\gamma}^0$, $\pmb{\gamma}^1$,  $\pmb{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of ten independent simulated data sets.
-The blue crosshairs denote the input $\pmb{\delta}$ used to generate the simulated data.
- \label{simglobal5:fig}}
-\end{figure}
-
 %The Model~II fit of SN~2014J \citet{2014ApJ...788L..21A}  data 
@@
 \label{discussion:sec}
-
+\color{red}
+In this Section
+we  reconcile our results with existing
+signatures of SN~Ia diversity that are not explicitly incorporated
+into our model: light-curve shape, SiII velocity, the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
+residuals.
+We also consider our results within the context of previous evidence from
+\citetalias{2017ApJ...842...93M}  for distinct intrinsic and dust-extinction-based
+color-magnitude relations.
+\color{black}
 \subsection{Light Curve Shape}
@@
    \includegraphics[width=5in]{output25/x1D.pdf}
-    \caption{The SALT2 $x_1$ versus $A_{\delta {\hat{U}}}  = \delta_{\hat{U}} D$.
+    \caption{The  \color{red}
+    intrinsic color component of Model~II as given by
+    $A_{\delta {\hat{U}}}  = \delta_{\hat{U}} D$
+    versus
+    the SALT2 $x_1$ versus
+    shows no correlation between the two.
+    \color{black}
    \label{x1:fig}}
@@
 \end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters including the light-curve shape parameter, $x_1$ \label{globalx1:tab}}
+\caption{68\% credible intervals for the Global Fit Parameters when adding the light-curve shape parameter, $x_1$ \label{globalx1:tab}}
 \end{table}
@@
 \citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
-To first order, the $\lambda_{Si}$ treated in this article varies linearly with $v_{Si}$.
+To first order, the $\lambda_{Si}$ treated in our study varies linearly with $v_{Si}$
+\color{red}
+neglecting the relativistic corrections due to the Doppler effect.
+\color{black}
 The values of the $v_{Si}$ coefficient, $\eta$, in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
@@
 but this correlation
-is absorbed into the equivalent-width corrections.
+is absorbed into the 
+\color{red}
+more-dominant
+\color{black}
+equivalent-width corrections.
 
@@
 To explore whether the Hubble residual may be due to unaccounted color,
-we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta {\hat{I}}}$  versus host mass 
+we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta {\hat{U}}}$  versus host mass 
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-The average $A_{\delta {\hat{I}}}$'s of the two subsamples are
+The average $A_{\delta {\hat{U}}}$'s of the two subsamples are
 %---
-$\langle A_{\delta {\hat{I}}} \rangle=     -0.0002 \pm    0.0089$ mag,
-$\langle A_{\delta {\hat{I}}} \rangle= 0.0025 \pm   0.0073 $ mag
-for low- and high-mass hosts respectively: there is no significant difference between them.
+$\langle A_{\delta {\hat{U}}} \rangle=     -0.0002 \pm    0.0089$ mag,
+$\langle A_{\delta {\hat{U}}} \rangle= 0.0025 \pm   0.0073 $ mag
+for low- and high-mass hosts respectively: there is no significant difference in $A_{\delta {\hat{U}}}$ between them.
 
@@
 
-The Kolmogorov-Smirnov test is applied on the distribution of $A_{\delta {\hat{I}}}$ of both low- and high-mass samples for
+The Kolmogorov-Smirnov test is applied to the distribution of $A_{\delta {\hat{U}}}$ of both low- and high-mass samples for
 each Monte Carlo link.
 The resulting distribution of the two-tailed $p$-value  over all chains spans the possible range from 0 to 1, as shown in Figure~\ref{childress:fig}.
-We are unable to perform a constraining test of whether the $A_{\delta {\hat{I}}}$ distributions from low- and high-mass samples
-are drawn from a common distribution.
-
-A more pertinent test is to see if a host-mass bias persists in Hubble diagram residuals
+We are unable to perform a constraining test of whether the $A_{\delta {\hat{U}}}$ distributions from low- and high-mass samples
+are drawn from a common distribution,
+\color{red}
+meaning there is as of yet no sign that our new color parameter is responsible for the mass step.
+\color{black}
+
+A more pertinent test 
+\color{red}
+would be to check whether
+\color{black}
+a host-mass bias persists in Hubble diagram residuals
 derived from a recalibration of SN~Ia absolute magnitudes using the parameters of the current article.
-The calibration of absolute magnitudes goes beyond the design of our model and analysis (see \S\ref{standard:sec}), so this test
-in not presented here.
-
-\subsection{Improving SNe~Ia as Standard Candles}
-\label{standard:sec}
-The approach of our analysis is to mine for new supernova properties based on colors and spectral features.
-Our model and results do carry information on absolute magnitude but are not tailored for its study.
-The grey parameter $\Delta$ with its $0.10$ mag dispersion, while containing information on absolute magnitude, 
-also conflates
-contributions from peculiar velocities and measurement uncertainties.  Studies
-focused on improving SNe~Ia as standard candles should modify  our model to
-distinguish between these sources of greyness and dispersion.
-Our
-mining exercise uses all supernovae that pass quality cuts, the approach taken by previous
-exploratory work.  In contrast, the calibration of SNe~Ia as standard candles needs procedures such
-as cross-validation to avoid overtraining.
-An absolute magnitude calibration using the parameters identified in this analysis is left to future work.
+The calibration of absolute magnitudes goes beyond the design of our model and analysis, so this test
+cannot be presented here.
 
@@
 \color{red}
-Supernova colors are expected to be affected by interstellar Milky Way-like dust (e.g.\ as modeled by  \citetalias{1999PASP..111...63F})
+Supernova colors are expected to be affected by interstellar Milky Way-like dust   (e.g.\ whose extinction is modeled as by  \citetalias{1999PASP..111...63F})
 and by ``intrinsic'' color variations from the supernova itself and its surrounding circumstellar dust. Physical modeling
@@
 2017ApJ...836...13H}. Supernova models \citep[e.g.][]{2007ApJ...662..487W,2013MNRAS.436..333S,2014MNRAS.441..532D,2015MNRAS.454.2549B,
-2017ApJ...846...58H} and circumstellar dust \citep{2008ApJ...686L.103G} also predict color variations not  captured
+2017ApJ...846...58H} and circumstellar dust \citep{2005ApJ...635L..33W,
+2008ApJ...686L.103G} also predict color variations not  captured
 by  \citetalias{1999PASP..111...63F}.
@@
 Considering  $\delta D$  to be intrinsic, it can be attributed to an intrinsic supernova property  or a dust not described by $\gamma k$.
-To first order $\pmb{\delta}$ behaves like standard dust;   $>98$\% of its length projects onto the expectation of  \citetalias{1999PASP..111...63F}
+To first order $\vec{\delta}$ behaves like standard dust;   $>98$\% of its length projects onto the expectation of  \citetalias{1999PASP..111...63F}
 with constant $R^F$.
@@
 The departure from   \citetalias{1999PASP..111...63F}
-can be seen qualitatively; the decrease in magnitude change toward redder wavelengths, seen in Figure~\ref{deltaratio:fig}, matches the 
-expectation for the circumstellar form of dust.
+can be seen qualitatively; the increase in magnitude change toward bluer wavelengths, seen in Figure~\ref{deltaratio:fig}, matches the 
+expectation for the multiple scattering of low-wavelength photons by circumstellar forms of dust.
 However, we
@@
 The best-fit elements $\delta_X$ do not all share the same sign, as would have been expected for dust.
-Confining ourselves to the 98\% of   $\pmb{\delta}$ that lies on the dust plane, associating 
+Confining ourselves to the 98\% of   $\vec{\delta}$ that lies on the dust plane, associating 
 $D$ with $A_V$ would imply an unphysical $R^F=0.5$.
@@
 
-\subsection{Conclusion}
+\section{Conclusions}
+\label{conclusions:sec}
 To summarize, we model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
@@
 affect supernova magnitudes and colors.  
-%This model  does an excellent job in
-%describing SN~2014J, a supernova with extreme colors that was not used in the training.  
 This work represents the first determination of the dust extinction curve outside the Local Group
@@
 distribution of $A_V$.  
+\color{red}
+The derived $A_V$ distribution has the quasi-exponential roll-over expected from simulations.
+The data show the need for at least two color parameters that can be attributed to a range of $R^F$ values, with a distribution that
+has a strong mode with an infrequent but extended scatter toward lower values.
+\color{black}
 Nesting this model in an extended model produces a result that 
@@
 Using the SNfactory sample,
-\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star formation rate, rather than
+\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star 
+\color{red}
+specific
+\color{black}
+formation rate, rather than
 global host mass.  The search for a correlation between our parameter and local star formation rate is planned for future work.
@@
 of dust models into our framework.
+
+Mandel sample.
+
+The approach of our analysis is to mine for new supernova properties based on colors and spectral features.
+Our model and results do carry information on absolute magnitude but are not tailored for its study.
+The grey parameter $\Delta$ with its
+\color{red}
+$0.08$
+\color{black} mag dispersion, while containing information on absolute magnitude, 
+also conflates
+contributions from peculiar velocities and measurement uncertainties.  Studies
+focused on improving SNe~Ia as standard candles 
+\color{red}
+would need to
+\color{black}
+modify  our model to
+distinguish between these sources of greyness and dispersion.
+Our
+mining exercise uses all supernovae that pass quality cuts, the approach taken by previous
+exploratory work.  In contrast, the calibration of SNe~Ia as standard candles needs procedures such
+as cross-validation to avoid overtraining.
+An absolute magnitude calibration using the parameters identified in this analysis is left to future work.
 
@@
 
+\appendix
+\color{red}
+\section{Testing for Parameter Bias Through Simultations}
+In \S\ref{model2:sec} we presented Model~II and tested for bias in our analysis.
+We generated 50 random realizations of data with the same input  parameters.
+The posterior for each realization was analyzed individually, and the posteriors of all realizations were stacked.
+The stacks and input parameter values are shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.
+We find that any differences between the peaks of the posterior stack and the input parameter values
+are much smaller than the per-realization statistical uncertainty.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
+            \caption{Stacked $\vec{\delta}$ posterior contours for 50 independent simulated data sets.
+            The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
+            \label{simdelta:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of ten independent simulated data sets.
+The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
+            \label{simglobal1:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of ten independent simulated data sets.
+The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
+ \label{simglobal2:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of ten independent simulated data sets.
+The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
+\label{simglobal3:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of ten independent simulated data sets.
+The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
+\label{simglobal4:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+         \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
+            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of ten independent simulated data sets.
+The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
+ \label{simglobal5:fig}}
+\end{figure}
+
+\color{black}
+
 \bibliographystyle{apj}

### 2017-09-11 view11.py

@@ -599,8 +599,9 @@ fig, axes = plt.subplots()
 # matplotlib.pyplot.rcdefaults()
 # dmean = fit['Delta'].mean()
 x, xmin, xmax = numpy.percentile(fit['Delta'],(50, 50-34,50+34),axis=0)
-dum = x>0.3
+dum = x>0.2
 print zhelio[dum],x[dum],snname[dum]
+
 plt.errorbar(zhelio,x,yerr=(x-xmin,xmax-x),fmt='o')
 plt.ylabel(r'$\Delta$')
 plt.xlabel(r'$z_{\odot}$')
@@ -655,7 +656,8 @@ plt.close()
 # plt.savefig(pp,format='pdf')
 # pp.close()
 # plt.close()
-
+print numpy.std(numpy.median((fit['Delta']-fit['Delta'][:,0][:,None]),axis=0))
+wefwe
 fig, axes = plt.subplots()
 bins = numpy.arange(-0.2,0.8001,0.02)
 print numpy.median((fit['Delta']-fit['Delta'][:,0][:,None]),axis=0).std()

### 2017-09-11 view25.py

@@ -423,6 +423,7 @@ for i in xrange(4):
     lname = r'$\Delta (\hat{{{0}}}-\hat{{V}})$'.format(cname[i])
     axes[i].set_ylabel(lname)
     axes[i].axhline(y=0,linestyle=':')
+    axes[i].set_xlim((-3,3))
 
 axes[3].set_xlabel(r'$x_1$')
 

### 2017-09-12 apj.tex
Jakob's comments

@@
 the most part been used to study SN~Ia heterogeneity.}
-They remain two-parameter models, with one parameter characterizing light-curve shape and the other
+They remain two-parameter models, with one parameter
+\color{red}
+primarily
+\color{black}
+characterizing light-curve shape and the other
 color.
@@
 In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
-the $R_V=3.1$ measured for the diffuse Milky Way dust is recovered on average and \citet{2017arXiv170101422H}
+the $R_V=3.1$ measured for the diffuse Milky Way dust is recovered on average and \citet{2017ApJ...836..157H}
 find $R_V=2.95 \pm 0.08$ for the highly-extincted SN~2012cu.
@@
 correlated with
-spectral features.
+spectral features
+\color{red}
+at peak.
+\color{black}
 Equivalent widths and line positions are considered in the model because their localization in wavelength
@@
 and the wavelength of the minimum of 
-the SiII$\lambda6355$ feature $\lambda_{Si}$:
+the SiII$\lambda6355$ feature $\lambda_{Si}$
+\color{red}
+around $B$-band peak brightness:
+\color{black}
 these spectral features are associated with SN~Ia  spectroscopic diversity  
@@
 $\vec{c}$ (where $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $),
-$\vec{\alpha}$, $\vec{\beta}$,  and $\pmb{\eta}$,  are the intercept and slopes of the linear relationships that
+$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept and slopes of the linear relationships that
 relate spectral-feature parameters with intrinsic magnitudes.
@@
    \includegraphics[width=5.2in]{output11/coeff0.pdf} 
-            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{U}}$ band.
+            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{U}}$ band.
             The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
@@
    \includegraphics[width=5.2in]{output11/coeff1.pdf} 
-            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{B}}$ band.
+            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{B}}$ band.
  \label{global2:fig}}
@@
    \includegraphics[width=5.2in]{output11/coeff2.pdf} 
-            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{V}}$ band.
+            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{V}}$ band.
  \label{global3:fig}}
@@
       \includegraphics[width=5.2in]{output11/coeff3.pdf} 
-            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{R}}$ band.
+            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{R}}$ band.
  \label{global4:fig}}
@@
          \includegraphics[width=5.2in]{output11/coeff4.pdf} 
-            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\pmb{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{I}}$ band.
+            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{I}}$ band.
  \label{global5:fig}}
@@
 
-ßEach supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, and $E_{\gamma^1}({\hat{B}}-{\hat{V}})$.
+Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$,
+\color{red}
+$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})k_0$, and $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})k_1$.
+\color{black}
 Their Pearson correlation coefficients  are given in the matrix
@@
 \begin{equation}
-A_X = a(X)  A_{\hat{V}} + b(X) E({\hat{B}}-{\hat{V}})
+A_X = a(X)  A_{V} + b(X) E(B-V)
 \label{f99:eqn}
@@
 the 5-dimensional magnitude space.
-Wiith no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
+With no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
 2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.
+\color{red}
+We show later that our per-supernova fit parameters under transformation are confined to $|A^F_V| < 1$ and $|E^F(B-V)| < 0.5$,
+where deviations of  the \citetalias{1999PASP..111...63F}  dust-extinction model from the plane approximation is less than 0.01 mag.
+\color{black}
 
@@
 
+We
+\color{red}
+now turn to
+\color{black}
+ the specific choice of $\vec{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust-extinction model. 
 Our linear model would be satisfied by any two independent vectors  that span
-the plane defined by the $\vec{\gamma}$ vectors.
-We begin discussion on the specific choice of $\vec{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model.
-While
+the plane defined by the $\vec{\gamma}$ vectors.  While
 Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
@@
 
-Given the association of  our parameter $\gamma^0_{\hat{V}} k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust-extinction
-model up to an additive offset,
-the former's distribution can be compared to the expectation for the latter.
+Given that
+\color{red}
+$\vec{\gamma_0}$  has nearly the same effect on color as dust extinction with constant $R^F$,
+the distribution of
+our parameter $\gamma^0_{\hat{V}} k_0$ can be compared with the expected distribution
+of $A^F_V$.
+\color{black}
 Figure~\ref{k0_med:fig} shows the histogram of
@@
 Different supernovae are expected to encounter dust with different $R^F$;
-having  associated $\vec{\gamma}^0$ with an $\langle R^F_{eff}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
+having  associated $\vec{\gamma}^0$ with
+\color{red}
+the extinction from a single effective
+\color{black}
+$\langle R^F_{eff}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
 away from that effective value.
-Let us introduce a new parameter for each supernova, $\delta R$, such that its $R^F =\langle R^F_{eff}\rangle(1+  \delta R)$.
-Variations in the value of $R^F$ (and hence $\delta R$) with the prior of the non-correlation between $k_0$ and $k_1$ lead 
+Let us introduce a new parameter for each supernova, $\delta R$, such that 
+\color{red}
+$A^F =\langle R^F_{eff}\rangle(1-  \delta R) E^F(B-V)$.
+\color{black} 
+Variations in the value of  $\delta R$, with the prior of the non-correlation between 
+\color{red}
+the coefficients in Eqn.~\ref{newdust:eqn},
+\color{black}
+lead 
 to 
@@
 The values of $\delta_X/\delta_{\hat{U}}-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
+\color{red}
+Unlike with $\gamma$, we normalize $\delta$ to $\hat{U}$ because the uncertainty in $\delta_{\hat{B}}-\delta_{\hat{V}}$ is relatively large with
+a credible intervals that easily cross zero. 
+\color{black}
 
@@
  (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
-The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5 \times$ larger for the external contribution than for the extrinsic dust
+The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5 \times$ larger for the external contribution than for the
+\color{red}
+intrinsic
+\color{black}
 component.  
@@
 
-The correlation coefficients between the ``intrinsic''  ($A_{\delta {\hat{U}}}$) and ``extrinsic''
-($E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$)  parameters are
-directed by the prior and are ultimately consistent with zero.
+\color{red}
+The priors of the correlation coefficients between the ``intrinsic''  ($A_{\delta {\hat{U}}}$) and ``extrinsic''
+($E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$)  parameters
+\color{red}
+are set for their values to be uncorrelated. The output correlation is
+\color{black}
+consistent with zero.
 Their independence implies that a single physical parameter is not being artificially attributed to two
@@
 Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: $\zeta_{\hat{R}}/\zeta_{\hat{V}}$
-has the largest significance  at $1\sigma$.
-The evidence for the effect of a third parameter persists in the significant  non-zero  $\delta_X/\delta_{\hat{I}}-1$ values
+has the largest significance  at 
+\color{red}
+only
+\color{black}
+$1\sigma$.
+The evidence for the effect of a third parameter persists in the significant  non-zero  $\delta_X/\delta_{\hat{U}}-1$ values
 in Table~\ref{globalx1:tab}, reinforcing the evidence that the $D$ of Model~II is not primarily related to light-curve shape.
@@
 
-The results from  \S\ref{shape:sec} and this subsection demonstrate the model handling simultaneous
-magnitude corrections 
-of  correlated observables.  The model prefers corrections that reduce intrinsic dispersion.
-The free parameters that describe the intrinsic dispersion enter the model likelihood through  the term $(\det{C_c})^{-0.5}$, which gives higher likelihood 
-for lower dispersions. This leads to magnitude corrections being preferentially
-attributed to $EW_{Ca}$ over $v_{Si}$, and  $EW_{Si}$ over SALT2 $x_1$.
+The results from  \S\ref{shape:sec} and this subsection 
+\color{red}
+present $EW_{Ca}$ with $v_{Si}$, and  $EW_{Si}$ with SALT2 $x_1$,  each a 
+case of parameter pairs that are correlated with each other, and each known to be related to
+supernova magnitudes.  We find that the simultaneous training of a pair
+preferentially assigns the magnitude correction to one parameter over the other
+without strong correlations between them in the posterior.  The implication is that the information about the correction is degenerately encoded in the two parameters,
+and is more efficiently captured in one.
+\color{black}
+%of  correlated observables.  The model prefers corrections that reduce intrinsic dispersion.
+%The free parameters that describe the intrinsic dispersion enter the model likelihood through  the term $(\det{C_c})^{-0.5}$, which gives higher likelihood 
+%for lower dispersions.
+%\color{red}
+%The fact that the maximum likelihood analysis attributes magnitude corrections to
+%$EW_{Ca}$ over $v_{Si}$, and  $EW_{Si}$ over SALT2 $x_1$  that $EW_{Ca}$  $EW_{Si}$
+%\color{black}
+%This leads to magnitude corrections being preferentially
+%attributed to.
 
@@
 To explore whether the Hubble residual may be due to unaccounted color,
-we plot in Figure~\ref{childress:fig} our intrinsic parameter  $A_{\delta {\hat{U}}}$  versus host mass 
+we plot in Figure~\ref{childress:fig} our intrinsic parameter
+\color{red} mass versus $A_{\delta {\hat{U}}}-A_{\delta {\hat{U}}}|_0$  (subtracting out a random supernova
+to suppress correlated errors)
+\color{black}
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
@@
 %---
-$\langle A_{\delta {\hat{U}}} \rangle=     -0.0002 \pm    0.0089$ mag,
-$\langle A_{\delta {\hat{U}}} \rangle= 0.0025 \pm   0.0073 $ mag
+\color{red}
+$\langle A_{\delta {\hat{U}}} \rangle=   0.000 \pm {    0.011 }$ mag,
+$\langle A_{\delta {\hat{U}}} \rangle= 0.003 \pm {    0.009 }$ mag
+\color{black}
 for low- and high-mass hosts respectively: there is no significant difference in $A_{\delta {\hat{U}}}$ between them.
@@
 $D$ with $A_V$ would imply an unphysical $R^F=0.5$.
+\color{red}
+(\citealt{Huang2017} find that in the limit of Rayleigh scattering, $R_V \approx 0.81$.)
+\color{black}
 We do not have conclusive evidence that  $\delta$ is being a property of dust distinct from that described by $\gamma$, rather
@@
 
+\color{red}
+Using different arguments based on expected populations, \citetalias{2017ApJ...842...93M} also infer
+separate intrinsic and dust-based color-magnitude relations based on an independent sample of 248 SNe~Ia
+mainly from the CfA \citep{1999AJ....117..707R, 2006AJ....131..527J, 2009ApJ...700.1097H, 2012ApJS..200...12H}
+and CSP \citep{2010AJ....139..519C, 2011AJ....142..156S} surveys.
+Finding slight color perturbations in the multi-band light curves 
+of those samples that are  consistent with our $\vec{\delta}$ would provide strong evidence for  an
+observational signature of the intrinsic SN color-magnitude relationship.
+\color{black}
+
 The current data does not show a statistically significant difference in the values of our new parameter for supernovae
@@
 of dust models into our framework.
-
-Mandel sample.
 

### 2017-09-13 apj.tex
done with responses

@@
             projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.  Lines for zero value for $\alpha_{\hat{U}}$, $\beta_{\hat{U}}$, $\eta$, $\gamma_{\hat{U}}^0$, $\gamma_{\hat{U}}^1$, and $\sigma_{\hat{U}}$ are shown for reference --
+            enclosed probability.
+Lines for zero value for $\alpha_{\hat{U}}$, $\beta_{\hat{U}}$, $\eta_{\hat{U}}$, $\gamma_{\hat{U}}^0$, $\gamma_{\hat{U}}^1$, and $\sigma_{\hat{U}}$ are shown for reference --
             in most cases they are outside the range of the plot.
@@
 The 
-potential scale reduction statistic, $\hat{R}$ (not the passband) \citep{Gelman92}, measures the convergence of the target distribution
+potential scale reduction statistic, $\hat{R}$
+\color{red}
+(in this paragraph not to be confused with the synthetic $R$ magnitude)
+\color{black}
+\citep{Gelman92}, measures the convergence of the target distribution
 in iterative simulations 
@@
 
-For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$
+For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$
 are given in Table~\ref{global:tab}.
@@
 
-The signal in  $\vec{\alpha}$ and $\vec{\beta}$ cannot be attributed to the equivalent widths themselves.
+The signal in  $\vec{\alpha}$ and $\vec{\beta}$ cannot
+\color{red}
+entirely
+\color{black}
+be attributed to the equivalent widths themselves.
 The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the ${\hat{B}}$-band is 851~\AA, so that its direct affect on magnitude
@@
 from the line itself.
-Similarly, the CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the ${\hat{U}}$ band is
+The CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the ${\hat{U}}$ band is
 701~\AA, so that its direct affect on magnitude
@@
 presence of the line itself.
+\color{red}
+More importantly, the spectral features correlate with broadband magnitudes with which they do not overlap in wavelength.
+\color{black}
 
@@
 mag, and a tail in the positive (fainter) direction.
-Of the three extreme outliers, the supernovae with largest and third largest $\Delta$'s have  heliocentric redshifts of 
- $0.0015$ and $0.0085$ respectively, and so have peculiar velocities that can cause a significant magnitude offset.
+\color{red}
+The supernovae with the highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
+ redshifts of 0.0228, 0.0086, 0.0565, and 0.0015, three of which have peculiar velocities that can cause a significant magnitude offset.
+\color{black}
 
@@
    \color{red}
-   The supernovae with the highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
+   The supernovae with the four highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
    redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.
@@
 with $E_{\gamma^i}({\hat{B}}-{\hat{V}}) \equiv  (\gamma^i_{\hat{B}}-\gamma^i_{\hat{V}})k_i$ as defined in \S\ref{results:sec}.
+\color{red}
+In this parameterization, the per-supernova parameters represent $\hat{B}-\hat{V}$ color excesses, and thus have a
+more familiar and physical interpretation than the $k$ parameters.
+\color{black}
 Our median-fit values for the $\vec{\gamma}$ coefficients are
@@
 \begin{pmatrix}
-\pmb{\epsilon}_{\gamma^0} \\
-\pmb{\epsilon}_{\gamma^1}
+\vec{\epsilon}_{\gamma^0} \\
+\vec{\epsilon}_{\gamma^1}
 \end{pmatrix},
@@
 \begin{split}
-\pmb{\epsilon}_{\gamma^0} &=(0.06, -0.07, -0.07,  0.07, 0.02), \\
-\pmb{\epsilon}_{\gamma^1} & =(-0.06, 0.16, -0.22, 0.33, -0.26)
+\vec{\epsilon}_{\gamma^0} &=(0.06, -0.07, -0.07,  0.07, 0.02), \\
+\vec{\epsilon}_{\gamma^1} & =(-0.06, 0.16, -0.22, 0.33, -0.26)
 \end{split}
@@
 \color{red}
-two (parity symmetric)
+two parity-symmetric
 \color{black}
@@
 \begin{pmatrix}
-\pmb{\epsilon}_{\gamma^0} \\
-\pmb{\epsilon}_{\gamma^1} \\
-\pmb{\epsilon}_{\delta}
+\vec{\epsilon}_{\gamma^0} \\
+\vec{\epsilon}_{\gamma^1} \\
+\vec{\epsilon}_{\delta}
 \end{pmatrix},
@@
 \begin{split}
-\pmb{\epsilon}_{\gamma^0} &=(0.07, -0.07, -0.07,  0.06,  0.02),\\
-\pmb{\epsilon}_{\gamma^1} &=( -0.04, 0.14,  -0.24,  0.32, -0.22),\\
-\pmb{\epsilon}_{\delta} &=(-0.05, 0.08,  -0.03,  -0.09, -0.12)
+\vec{\epsilon}_{\gamma^0} &=(0.07, -0.07, -0.07,  0.06,  0.02),\\
+\vec{\epsilon}_{\gamma^1} &=( -0.04, 0.14,  -0.24,  0.32, -0.22),\\
+\vec{\epsilon}_{\delta} &=(-0.05, 0.08,  -0.03,  -0.09, -0.12)
 \end{split}
@@
 are perpendicular to $\vec{a}$ and $\vec{b}$.
-The $\vec{\gamma}$ residuals $\pmb{\epsilon}_{\gamma^0}$ and
-$\pmb{\epsilon}_{\gamma^1} $
+The $\vec{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
+$\vec{\epsilon}_{\gamma^1} $
 quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that, just as in Model~I, most
@@
 $\vec{\delta}$ too
-has a significant projection onto the dust plane, as the $\pmb{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\vec{\delta}$ vector.
+has a significant projection onto the dust plane, as the $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\vec{\delta}$ vector.
 The transformation between the new set of $\vec{\gamma}$'s and dust parameters yields
 a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, shifted to slightly  higher values relative to the results of Model~I.
+\color{red}
+As a point of comparison with another standard SN~Ia model, 3\% of the color vector defined by 
+the  SALT2 (v2.4) color parameter, $c$, is  projected perpendicular to the plane defined by the $\vec{\gamma}$'s.
+\color{black}
 
@@
    \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
       \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
          \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
-            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of ten independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\alpha$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of ten independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.

### 2017-09-18 apj.tex
finished

@@
 in current models, and so consequently can lead to more precise per-object distances with smaller systematic uncertainties.  In this article, we present   
-an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
+an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of Ca~II, Si~II, and Si~II velocity
 as applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
@@
 %-----
-$\langle R^F_{eff}\rangle$ is 2.31 -- 2.69.
+$\langle R^F_{\mathit{\mathit{eff}}}\rangle$ is 2.31 -- 2.69.
 %-----
@@
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two subpopulations distinguished
-by SiII velocity with differing $B_{max}-V_{max}$; this color correlation, in addition to one with $B-R$, is confirmed by
+by Si~II velocity with differing $B_{\mathit{\mathit{max}}}-V_{\mathit{max}}$; this color correlation, in addition to one with $B-R$, is confirmed by
 \citet{2014ApJ...797...75M}.
 \citet{2015MNRAS.451.1973S}
-find that high-velocity SiII$\lambda$6355 is found in objects that have red ultraviolet/optical colors near maximum brightness.
+find that high-velocity Si~II~$\lambda$6355 is found in objects that have red ultraviolet/optical colors near maximum brightness.
 \citet{2011MNRAS.413.3075M} show evidence that supernova asymmetry and viewing angle,
@@
 \citet{2017ApJ...842...93M} \citepalias[henceforth referred to as][]{2017ApJ...842...93M}) take the approach of modeling the distribution of their parameters, to find that
-scatter in the Hubble diagram is better explained by a combination of intrinsic color dispersion and
+scatter in the Hubble diagram is better explained by a combination of 
+\color{red}
+an intrinsic color-magnitude relationship with slope $\beta_{\mathit{int}}\sim 2.3$. intrinsic
+color dispersion,
+\color{black}
+and
 $R_V=2.7$ dust, rather than by dust with no color dispersion.
-They draw these conclusions by using only the SALT2 (v2.4) $x_1$ parameter as the summary statistic that describes color.
+They draw these conclusions by using only the SALT2 (v2.4)
+\color{red}
+ $c$
+ \color{black}
+  parameter as the summary statistic that describes color.
 
@@
 at $B$-band peak brightness.
-The equivalent widths of the SiII$\lambda 4141$ and CaII H\&K features are computed as
+The equivalent widths of the Si~II~$\lambda 4141$ and Ca~II H\&K features are computed as
 in \citet{2008A&A...477..717B} and the 
-wavelength of the SiII$\lambda 6355$ feature
+wavelength of the Si~II~$\lambda 6355$ feature
 as in \citet{chotard:thesis, 2017Chotard}.
 Equivalent widths and the
-SiII$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from $B$-band maximum;
+Si~II~$\lambda 6355$ wavelength are taken from spectra  within $\pm 2.5$ days from $B$-band maximum;
 the average is used  in cases where there are multiple spectral measurements within that time window.
@@
 %based on data problems identified by Manu.}
-The data are given in \citet{2017Chotard}.
+The 
+\color{red}
+spectroscopic-feature measurements are presented
+\color{black}
+in \citet{2017Chotard}.
 %
@@
 on its
- equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
+ equivalent widths of the Ca~II H\&K and Si~II~$\lambda$4141 spectral features
 $EW_{Ca}$ and $EW_{Si}$,
 and the wavelength of the minimum of 
-the SiII$\lambda6355$ feature $\lambda_{Si}$
+the Si~II~$\lambda6355$ feature $\lambda_{Si}$
 \color{red}
@@
 half are used for warmup.
-Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig} .
+Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig}.
 
@@
 by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
-$N_{eff}$ is an estimate of the number of independent draws. The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
-output also gives  $N_{eff} \gg 100$ for all parameters, indicating that all are densely sampled.
+$N_{\mathit{eff}}$ is an estimate of the number of independent draws.
+The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.
+The
+output also gives  $N_{\mathit{eff}} \gg 100$ for all parameters, indicating that all are densely sampled.
 Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig} -- \ref{global5:fig}.  In these tests there is no evidence that
@@
 outlying data.
-We have rurun the analysis with a variety of initial conditions, including one with $\vec{\gamma}$ equal to zero, except for a small positive 
+We have rerun the analysis with a variety of initial conditions, including one with $\vec{\gamma}$ equal to zero, except for a small positive 
 $\gamma^0_0$ and small negative $\gamma^1_0$; the 68\% credible intervals
@@
 be attributed to the equivalent widths themselves.
-The range of SiII$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the ${\hat{B}}$-band is 851~\AA, so that its direct affect on magnitude
+The range of Si~II~$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the ${\hat{B}}$-band is 851~\AA, so that its direct affect on magnitude
 is
@@
 from the line itself.
-The CaII H\&K equivalent widths have range $\pm 50$~\AA, while the width of the ${\hat{U}}$ band is
+The Ca~II H\&K equivalent widths have range $\pm 50$~\AA, while the width of the ${\hat{U}}$ band is
 701~\AA, so that its direct affect on magnitude
 is
-$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in ${\hat{U}}$ magnitude is  0.21~mag, so $\alpha_{\hat{U}}$ cannot be completely due to the 
+$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in ${\hat{U}}$ magnitude is  0.21~mag, 
+\color{red}
+which would imply that  $\alpha_{\hat{U}}$ cannot be completely due to the 
 presence of the line itself.  
-\color{red}
-More importantly, the spectral features correlate with broadband magnitudes with which they do not overlap in wavelength.
+Supernova flux has a large gradient in our $\hat{U}$ and there is a variation in the effective, flux-weighted,  $\hat{U}$ bandwidth. 
+Nevertheless, the  correlation between spectral features with magnitudes in bands with no wavelength overlap is the
+important signal of importance in this study.
 \color{black}
@@
 The supernovae with the highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
- redshifts of 0.0228, 0.0086, 0.0565, and 0.0015, three of which have peculiar velocities that can cause a significant magnitude offset.
+ redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.  Peculiar velocities  can cause a significant magnitude offset for three.
 \color{black}
@@
 \ldots & {\hat{U}}-{\hat{V}} & 0.60^{+0.10}_{-0.13} & -0.38^{+0.18}_{-0.17} & -0.33^{+0.15}_{-0.14} \\
-\ldots  & \ldots & {\hat{V}}-{\hat{V}} & -0.21^{+0.17}_{-0.17} & 0.08^{+0.14}_{-0.15} \\
+\ldots  & \ldots & {\hat{B}}-{\hat{V}} & -0.21^{+0.17}_{-0.17} & 0.08^{+0.14}_{-0.15} \\
 \ldots  & \ldots  &\ldots  & {\hat{V}}-{\hat{R}} & 0.65^{+0.06}_{-0.07} \\
@@
 \end{equation}
-approximately describes dust 
+approximately describes  
 \color{red}
@@
 for the
-\citepalias{1999PASP..111...63F} model.
+\citetalias{1999PASP..111...63F} model.
 Over the range
@@
    two different perspectives.
-   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes possible
+   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes
    are a linear combination of these two vectors, and hence are confined to the plane that contains both.
    The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
-   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes possible are confined to the plane that contains both.
-   The perspective on the right visually show that all four vectors are nearly coplanar.  
+   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes are confined to the plane that contains both.
+   The perspective on the right visually shows that all four vectors are nearly coplanar.  
    The combination $\vec{a}+\vec{b}/2.44$ is shown in the dotted red
@@
 This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
-We use this interpretation to assign  $\langle R^F_{eff}\rangle = \kappa_1^{-1}$ as
+We use this interpretation to assign  $\langle R^F_{\mathit{eff}}\rangle = \kappa_1^{-1}$ as
 the
@@
 Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.44$.
-From the Monte Carlo chains, we find a 68\% credible interval for  $\langle R^F_{eff}\rangle$ of 2.26--2.63.
+From the Monte Carlo chains, we find a 68\% credible interval for  $\langle R^F_{\mathit{eff}}\rangle$ of 2.26--2.63.
 
@@
 Figure~\ref{k0_med:fig} shows the histogram of
-median values and the ideogram of $\gamma^0_{\hat{V}} k_0$ 
+median values
+\color{red}
+from the Monte Carlo chains
+\color{black}
+and the ideogram of $\gamma^0_{\hat{V}} k_0$ 
 relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} k_0|_0$.
@@
 (left) : $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
-which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{eff}\rangle$ value (right).
+which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{\mathit{eff}}\rangle$ value (right).
    \label{k0_med:fig}}
@@
 \color{black}
-$\langle R^F_{eff}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
+$\langle R^F_{\mathit{eff}}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
 away from that effective value.
@@
 \color{red}
-$A^F =\langle R^F_{eff}\rangle(1-  \delta R) E^F(B-V)$.
+$A^F =\langle R^F_{\mathit{eff}}\rangle(1-  \delta R) E^F(B-V)$.
 \color{black} 
@@
 \begin{equation}
-\kappa_2 =\langle R^F_{eff}\rangle \left(1- \frac{\mbox{Var}(\delta R\, E^F(B-V))}{\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))}\right).
+\kappa_2 =\langle R^F_{\mathit{eff}}\rangle \left(1- \frac{\mbox{Var}(\delta R \times E^F(B-V))}{\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))}\right).
 \end{equation}
-From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R\, E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))$.
+From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
 This result indicates that there is a small but significant covariance between  extinction contributions due to
@@
 the color-excess parameter $E^F(B-V)$.
-Figure~\ref{k0_med:fig} shows the histogram of median values and ideogram of $\gamma^1_{\hat{V}} k_1$
+Figure~\ref{k0_med:fig} shows the histogram of median values
+\color{red}
+from Monte Carlo chains
+\color{black}
+and ideogram of $\gamma^1_{\hat{V}} k_1$
 relative to that of an arbitrary supernova  $\gamma^1_{\hat{V}} k_1|_0$.
@@
 sample is shown in Figure~\ref{kk:fig}. 
-For reference, a line that represents $R^V_{eff}=2.44$ is overplotted.  The majority of supernovae lie within a narrow range above the line
-meaning they have $R^F > R^V_{eff}$,
-while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{eff}$.  
+For reference, a line that represents $R^V_{\mathit{eff}}=2.44$ is overplotted.  The majority of supernovae lie within a narrow range above the line
+meaning they have $R^F > R^V_{\mathit{eff}}$,
+while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{\mathit{eff}}$.  
 These findings are consistent with previous results:
@@
 As a check of our analysis implementation and our
-interpretation of $\langle R^F_{eff}\rangle$, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
+interpretation of $\langle R^F_{\mathit{eff}}\rangle$, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
 SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust-extinction model.  The supernovae
@@
 measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations that together yield a median
-$\langle R^F_{eff}\rangle$ of 2.53, showing that our effective value is close to the  $R^F=2.5$ input into the simulations.
+$\langle R^F_{\mathit{eff}}\rangle$ of 2.53, showing that our effective value is close to the  $R^F=2.5$ input into the simulations.
 
@@
 \color{red}
-However, we present in \$\ref{interpret:sec} a separate physical argument for the intrinsic interpretation of the new term.
+However, we present in \S\ref{interpret:sec} a separate physical argument for the intrinsic interpretation of the new term.
 \color{black}
@@
 Our finite MCMC chains do not migrate away from these ranges.
-The initial condition of $\vec{\delta}$ is set to zero.
-
-In Model II, for $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
+The
+\color{red}
+initial step of the MCMC is at $\vec{\delta}=0$.
+\color{black}
+
+In Model~II,
+\color{red}
+as in Model~I,
+\color{black}
+for $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
 color parameters, $(N-1)$ magnitude offsets,  $5 \times 7$ global coefficients, and $10$ parameters that describe the intrinsic
@@
 despite its relatively strong signal-to-noise, the original posterior for $D$ for the selected supernova does have significance on both sides of zero,
-resulting in changes in the shape of the $\vec{\delta}$ posteriors when  $D$ to forced to be positive.   
+resulting in changes in the shape of the $\vec{\delta}$ posteriors when  $D$ is forced to be positive.   
 The 
@@
 Unlike with $\gamma$, we normalize $\delta$ to $\hat{U}$ because the uncertainty in $\delta_{\hat{B}}-\delta_{\hat{V}}$ is relatively large with
-a credible intervals that easily cross zero. 
+credible intervals that easily cross zero. 
 \color{black}
@@
  and histogram in Figure~\ref{ebv:fig}.
- (These values are relative those of an arbitrary supernova in order to null out correlated errors.)
+ (These values are relative
+ \color{red}
+to
+\color{black}
+ those of an arbitrary supernova in order to null out correlated errors.)
 The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5 \times$ larger for the external contribution than for the
@@
    \includegraphics[width=2.8in]{output25/ebv_delta.pdf}
-      \caption{Left: Ideograms of the external $E({\hat{B}}-{\hat{V}})$ and
+      \caption{Left: Ideograms of the external $E({\hat{B}}-{\hat{V}})$ 
+      \color{red}
+      (including contributions from both $k_0$, $k_1$, and $D$)
+      \color{black}
+      and
    internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
@@
  \color{red}
- the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be chance. 
+ the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance. 
  \color{black}
@@
 signatures of SN~Ia diversity that are not explicitly incorporated
-into our model: light-curve shape, SiII velocity, the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
+into our model: light-curve shape, Si~II velocity, the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
 residuals.
@@
     the SALT2 $x_1$ versus
-    shows no correlation between the two.
+    shows no correlation between the two.  (Note that there remain correlated uncertainties between points.)
     \color{black}
@@
 
-\subsection{SiII Line Velocity}
+\subsection{Si~II Line Velocity}
 \label{velocity:sec}
@@
 \color{red}
-neglecting the relativistic corrections due to the Doppler effect.
+neglecting the tiny relativistic corrections due to the Doppler effect.
 \color{black}
@@
 are expected to be produced together in the thermonuclear burning into intermediate mass elements.
+\color{red}
+Nevertheless, Figures~\ref{global1:fig} -- \ref{global5:fig} show the low probability of  $\alpha=0$, $\beta=0$, $\eta\ne0$ in our Model~I.
+\color{black}
 We conclude that $v_{Si}$ is correlated with color, 
@@
 without strong correlations between them in the posterior.  The implication is that the information about the correction is degenerately encoded in the two parameters,
-and is more efficiently captured in one.
+and is more efficiently captured in one of them.
 \color{black}
@@
 All supernovae experience  intrinsic color variation.
-Only a subset encounter dust:
-geometric projection effects lead to the expectation for a subset of supernovae having zero
+Some encounter dust while others do not:  the distribution of the amount of  dust local to  supernovae within its host and
+geometric projection effects, together lead to the expectation for a small but nontrivial fraction  of supernovae of having zero
 dust column density and the
@@
 supernovae 
-having an intrinsic linear color-magnitude relationship with slope $\beta$.
+having an intrinsic linear color-magnitude relationship with slope $\beta_{\mathit{int}}$.
 (The absence of an intrinsic color-magnitude relation corresponds to $\beta=0$.)
@@
 The distinctive distribution of supernovae in color-magnitude space  allows
-the authors to distinguish intrinsic $\beta$ and the dust slope,
+the authors to distinguish intrinsic $\beta_{\mathit{int}}$ and the dust slope,
 despite being
@@
 We find $\delta_{\hat{B}}/(\delta_{\hat{B}}-\delta_{\hat{V}})=1.27^{ + 1.02}_{ - 1.16}$, which agrees with the  approximately corresponding (given that different broadband
-filters are used) $\beta_{int}=2.3\pm 0.3$ found by \citetalias{2017ApJ...842...93M}.
+filters are used) $\beta_{\mathit{int}}=2.3\pm 0.3$ found by \citetalias{2017ApJ...842...93M}.
 \citetalias{2017ApJ...842...93M} treat dust as having constant $R$ whereas we allow $R$ to float 
@@
 The best-fit elements $\delta_X$ do not all share the same sign, as would have been expected for dust.
-Confining ourselves to the 98\% of   $\vec{\delta}$ that lies on the dust plane, associating 
+Confining ourselves to the 98\% of   $\vec{\delta}$ that lie on the dust plane, associating 
 $D$ with $A_V$ would imply an unphysical $R^F=0.5$.
@@
 \color{black}
-We do not have conclusive evidence that  $\delta$ is being a property of dust distinct from that described by $\gamma$, rather
+We do not have conclusive evidence that  $\delta$ is a property of dust distinct from that described by $\gamma$, rather
 than representing intrinsic supernova color variation.
@@
 \color{black} parameter that affects supernova
-colors in a manner that is distinct from the expectations from dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
+colors in a manner that is distinct from the expectations for dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
 \color{red}
@@
 Using the SNfactory sample,
-\citet{2013A&A...560A..66R,2017Rigault} find that a step in Hubble residuals is better related to local star 
+\citet{2017Rigault} find that a step in Hubble residuals is better related to local 
 \color{red}
@@
 \color{black}
+star 
 formation rate, rather than
@@
 \color{black} mag dispersion, while containing information on absolute magnitude, 
-also conflates
+also 
+\color{red}
+includes
+\color{black}
 contributions from peculiar velocities and measurement uncertainties.  Studies

### 2017-09-29 apj.tex
100 simulation version

@@
 The significance of the $\vec{\delta}$ measurement is evaluated using simulated datasets.
-For one set of tests, we generate 50 random realizations of data with input  parameters equal to the median values of the 
+For one set of tests, we generate 100 random realizations of data with input  parameters equal to the median values of the 
 parameter posteriors found in
 \S\ref{model:sec}, and using the same noise as our data.  
-\color{red}
-(Given the non-trivial computational time for the Monte Carlo, the 2\% precision from the 
-is deemed sufficient for our purposes.)
-\color{black}
 To represent the null hypothesis, the input $\vec{\delta}$-vector is set to zero.
@@
 values of  the credible interval of our data relative to those from the simulations, we obtain
-three different $p$-values ranging from 0.90--0.98, indicating that the
+three different $p$-values ranging from 0.88--0.98, indicating that the
 \color{red}
@@
   \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
-            \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\vec{\gamma}$, $\delta_\perp^2/\delta^2$, for 50 independent simulated data sets with input $\delta=0$.
+            \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\vec{\gamma}$, $\delta_\perp^2/\delta^2$, for 100 independent simulated data sets with input $\delta=0$.
 The fits
@@
 relative projection of $\vec{\delta}$  perpendicular to the plane defined by the $\vec{\gamma}$'s, $\delta_\perp^2/\delta^2$,
-for the same 50 null simulations that were just described.
-Figure~\ref{pvalues_delta2:fig} shows  that for none of the simulations does our analysis produce 
- $\delta_\perp^2/\delta^2$ as low as that from our data.  The $p$-values $>0.98$ indicate that 
+for the same 100 null simulations that were just described.
+Figure~\ref{pvalues_delta2:fig} shows  that for 
+\color{red}
+ $-1$, 0, and $1$-sigma
+values of  the credible interval, only 0--2\% of the simulations have values of  $\delta_\perp^2/\delta^2$ as low as our data.
+\color{black}
+The $p$-values $>0.98$ indicate that 
  \color{red}
@@
 Potential biases in our results are measured through simulation.
-We generate 50 random realizations of data with input  parameters equal to the median values found in
+We generate 100 random realizations of data with input  parameters equal to the median values found in
 this Section, except for $\vec{\delta}$, which is assigned
@@
 The stack of  $\vec{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias between
-the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ and the mode of  the stacks $(-1.06, -0.95, -0.41, -0.11, 0.40)$.
+the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ and the mode of  the stacks $(-1.2, -1.06, -0.49, -0.25, 0.21)$.
 We do not consider this bias to be an issue in our detection of a third parameter, as the difference is significantly

### 2017-10-17 apj.tex
submitted version

@@
 in current models, and so consequently can lead to more precise per-object distances with smaller systematic uncertainties.  In this article, we present   
-an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of Ca~II, Si~II, and Si~II velocity
+an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of Ca~II and Si~II, and Si~II velocity
 as applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
@@
 The color changes allowed by the model are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F} with a free
-total-to-selective extinction parameter $R^F$.  %Our model
-% is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
+total-to-selective extinction parameter $R^F$. 
 Inspired that with no conditioning our  two-parameter model produces behavior similar to that expected from Galactic dust,
@@
 confidence.
-\color{red}
 The 68\% credible interval for the sample effective
@@
 The third parameter is attributed to intrinsic supernova or circumstellar diversity
-\color{black}
 beyond that tracked by the spectral features and two-parameter dust models.
@@
 They remain two-parameter models, with one parameter
-\color{red}
 primarily
-\color{black}
 characterizing light-curve shape and the other
 color.
-In SALT2 the light curve shapes are described by a multiplicative scaling (``stretch'')  of the time evolution,
- whereas MLCS2k2 varies shapes through additive time-dependent magnitude corrections.
+In SALT2 the light curve shapes are described by phase-dependent flux corrections,
+ whereas MLCS2k2 varies shapes through additive magnitude corrections.
 The physical cause of the color diversity is interpreted differently by the two sets of authors: 
@@
 \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find two subpopulations distinguished
-by Si~II velocity with differing $B_{\mathit{\mathit{max}}}-V_{\mathit{max}}$; this color correlation, in addition to one with $B-R$, is confirmed by
+by Si~II velocity that exhibit differing $B_{\mathit{\mathit{max}}}-V_{\mathit{max}}$; this color correlation, in addition to one with $B-R$, is confirmed by
 \citet{2014ApJ...797...75M}.
@@
 independent (to first order) of the amount of dust along the line of sight.
-\color{red}
 Near and mid-UV photometry obtained by the Ultra-Violet/Optical Telescope on the Swift spacecraft cannot be entirely explained
@@
 \citep{2017ApJ...836..232B}.
-\color{black}
-%\citet{2013ApJ...779...23M} find diversity in SNe~Ia UV emission, which they use to distinguish subclasses based on UV-optical colors.
 Measurements of color ratios are being advanced with the development of flexible empirical light curve models that accommodate flexibility in multi-band colors
@@
 
-Hierarchical modeling has recently opened
+Hierarchical modeling has recently enabled
 the study of intrinsic supernova color based on SN~Ia Hubble diagrams. Latent parameters that are not directly tied to observables
 but  influence color can be included in such models.
-\citet{2017ApJ...842...93M} \citepalias[henceforth referred to as][]{2017ApJ...842...93M}) take the approach of modeling the distribution of their parameters, to find that
+\citet{2017ApJ...842...93M} \citepalias[henceforth referred to as][]{2017ApJ...842...93M}) take the approach of modeling the distribution of their parameters to find that
 scatter in the Hubble diagram is better explained by a combination of 
-\color{red}
 an intrinsic color-magnitude relationship with slope $\beta_{\mathit{int}}\sim 2.3$. intrinsic
 color dispersion,
-\color{black}
 and
@@
 They draw these conclusions by using only the SALT2 (v2.4)
-\color{red}
  $c$
- \color{black}
 parameter as the summary statistic that describes color.
@@
 are consistent with the expectations of parameterized Milky Way extinction models.
-%, and do an excellent job of fitting the data of the out-of-sample
-%supernova SN2014J that has an extremely low total-to-selective extinction.
 In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
-\color{red}
 In  \S\ref{discussion:sec}
@@
 Conclusions are presented in \S\ref{conclusions:sec}.
-\color{black}
 
@@
 
-\color{red}
 This article presents the first application of a computationally intensive analysis, so although  high spectral resolution
 is available we here compress the information into low-resolution broadband photometry. 
-\color{black}
 Synthetic supernova-frame photometry is generated for a top-hat filter system
@@
 $\hat{I}$ $[6968.29-8400.00]$\AA.
-\color{red}
 (The diacritic hat serves as a reminder that these are not standard Johnson-Cousins filters.)
-\color{black}
-For each supernova, the magnitudes within 5-days of peak brightness are used to regress single-band magnitudes
+For each supernova, the magnitudes within 5-days of peak brightness are used to fit single-band magnitudes
 at $B$-band peak brightness.
@@
 The 
-\color{red}
 spectroscopic-feature measurements are presented
-\color{black}
 in \citet{2017Chotard}.
@@
 SN~Ia broadband magnitudes and colors are 
-\color{red}
 directly
-\color{black}
 correlated with
 spectral features
-\color{red}
 at peak.
-\color{black}
 Equivalent widths and line positions are considered in the model because their localization in wavelength
@@
 modified by an extrinsic 
-\color{red}
 latent
@@
 apparent magnitudes and colors
-\color{black}
 that are subsequently measured by the observer.
@@
 the Si~II~$\lambda6355$ feature $\lambda_{Si}$
-\color{red}
 around $B$-band peak brightness:
-\color{black}
 these spectral features are associated with SN~Ia  spectroscopic diversity  
@@
 to capture 
-\color{red}
 potential
-\color{black}
 band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
@@
 $\hat{U}_o, {\hat{B}}_o, {\hat{V}}_o, {\hat{R}}_o, {\hat{I}}_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
-%shown in Table~\ref{data:tab}
 have Gaussian measurement uncertainty with covariance $C$.
@@
 \end{equation}
-%to exclude degenerate posterior space
-%associated
-%with the $\pm$ sign.
 As  in mixture models, the combinations $\vec{\gamma}^0 k_0$ and $\vec{\gamma}^1 k_1$ terms are degenerate under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
@@
 
-\color{red}
 No informative prior is used for each of the per-supernova parameters $\Delta$, $EW$, $\lambda$, $k_0$, and $k_1$:
@@
 As a consequence, the prior has uncorrelated parameters as mentioned above.
-\color{black}
 
@@
 potential scale reduction statistic, $\hat{R}$
-\color{red}
 (in this paragraph not to be confused with the synthetic $R$ magnitude)
-\color{black}
 \citep{Gelman92}, measures the convergence of the target distribution
@@
 $\gamma^0_0$ and small negative $\gamma^1_0$; the 68\% credible intervals
-remain consistent.
+remain consistent.  Note that the MCMC chains do not migrate to the parity-degenerate solution of $\vec{\gamma}$ and $k$.
 
@@
 peak magnitudes
-\color{red}
 as expected.
-\color{black}
 On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero
@@
 Both $EW_{Ca}$ and $EW_{Si}$ are associated with color changes, though not in ${\hat{B}}-{\hat{V}}$ specifically.
-\color{red}
 We do not detect a significant direct connection between
 $\lambda_{Si}$ and color, though their indirect correlation is discussed in \S\ref{velocity:sec}.
-\color{black}
 
 The signal in  $\vec{\alpha}$ and $\vec{\beta}$ cannot
-\color{red}
 entirely
-\color{black}
 be attributed to the equivalent widths themselves.
@@
 $2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in ${\hat{U}}$ magnitude is  0.21~mag, 
-\color{red}
 which would imply that  $\alpha_{\hat{U}}$ cannot be completely due to the 
@@
 important signal of importance in this study.
-\color{black}
 
@@
 mag, and a tail in the positive (fainter) direction.
-\color{red}
 The supernovae with the highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
  redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.  Peculiar velocities  can cause a significant magnitude offset for three.
-\color{black}
 
@@
    Normalized ideogram and histogram of the medians of the grey offset relative to one arbitrary supernova, $\Delta-\Delta|_0$.  
-   \color{red}
    The supernovae with the four highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
    redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.
-   \color{black}
    \label{hist:fig}}
@@
 Non-trivial residual magnitude
-\color{red}
 and color dispersions are captured in $C_c$
 at the level of 4--10$\sigma$.
-\color{black}
 The square
@@
 \sigma({\hat{V}},{\hat{U}}-{\hat{V}},{\hat{B}}-{\hat{V}},{\hat{V}}-{\hat{R}},{\hat{V}}-{\hat{I}})=\\
-%\begin{pmatrix}
-%\begin{array}{rrrrr}
 \left(
@@
 \right)
-%\end{array}
-% \end{pmatrix} 
  \text{mag}.
@@
  \end{multline}
-\color{red}
 To reduce clutter only the upper triangular part of the otherwise symmetric matrix is shown.
-\color{black}
 These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where
 a direct comparison can be made.
-\color{red}
 \citetalias{2017ApJ...842...93M}  find an intrinsic dispersion of the SALT2 $c$ parameter (associated with ${\hat{B}}-{\hat{V}}$) of $\approx 0.07$ mag,
 though variation of dust properties accounts for some of that dispersion.
-\color{black}
 %model11_rubin.py
@@
 with a strict equality), we find significant shifts in all slope parameters  and 
-\color{red}
 artificially
-\color{black}
 smaller statistical uncertainties.
@@
 Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$,
-\color{red}
 $E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})k_0$, and $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})k_1$.
-\color{black}
 Their Pearson correlation coefficients  are given in the matrix
@@
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
+In our model, $k_0$ and $k_1$ are introduced as latent parameters that are related to linear shifts in band magnitudes through
+the  coefficients $\vec{\gamma}^0$ and
+$\vec{\gamma}^1$.  Otherwise, no physically-motivated suppositions on the properties of $k$ and $\vec{\gamma}$ are imposed.
+Attenuation of supernova light due to dust is expected to be mostly captured by the first-order affects described by our linear model.
+In this Section, we consider the results of our parameter fitting within the context of  dust-extinction models.
+
 All elements of the two $\vec{\gamma}$ parameter vectors 
-\color{red}
 describing intrinsic color
-\color{black}
 are significantly non-zero. 
@@
 We compare our model's parameter vectors $\vec{\gamma}^0$ and $\vec{\gamma}^1$ with the expectations of  
-\color{red}
 dust-extinction
-\color{black}
 models.
@@
 approximately describes  
-\color{red}
 dust-extinction
-\color{black}
 models \citep[for example, the wavelength-dependent model of ][is linear,
@@
 and the wavelengths under consideration here,  the values of the elements of $a$ and $b$ vary by $<5$\%
-\color{red}
 for the
@@
 Over the range
-\color{black}
  $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in extinction from the linear approximation of
@@
 with $E_{\gamma^i}({\hat{B}}-{\hat{V}}) \equiv  (\gamma^i_{\hat{B}}-\gamma^i_{\hat{V}})k_i$ as defined in \S\ref{results:sec}.
-\color{red}
 In this parameterization, the per-supernova parameters represent $\hat{B}-\hat{V}$ color excesses, and thus have a
-more familiar and physical interpretation than the $k$ parameters.
-\color{black}
+more familiar and physical interpretation that are used in dust-extinction models.
 Our median-fit values for the $\vec{\gamma}$ coefficients are
@@
 2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.
-\color{red}
 We show later that our per-supernova fit parameters under transformation are confined to $|A^F_V| < 1$ and $|E^F(B-V)| < 0.5$,
 where deviations of  the \citetalias{1999PASP..111...63F}  dust-extinction model from the plane approximation is less than 0.01 mag.
-\color{black}
 
@@
    \includegraphics[width=2.95in]{output11/plane1.pdf}
-%   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
-%   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
    \caption{
@@
 We
-\color{red}
 now turn to
-\color{black}
 the specific choice of $\vec{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust-extinction model. 
@@
 $E(B-V)$, the linear dust model 
-\color{red}
 alternatively
-\color{black}
 could be written in terms of any two other basis vectors  $\vec{a}+\kappa_1 \vec{b}$
@@
 In this basis, the model is then
-%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
-%be expressed in terms of new basis vectors parametrized by $\kappa$:
 \begin{equation}
@@
 the
-\color{red}
 ensemble mean
-\color{black}
 effective total-to-selective extinction of our sample.
 The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}, 
-\color{red}
 giving
-\color{black}
 $\kappa^{-1}_1=2.82/1.15 =2.44$.
@@
 Given that
-\color{red}
 $\vec{\gamma_0}$  has nearly the same effect on color as dust extinction with constant $R^F$,
@@
 of $A^F_V$.
-\color{black}
 Figure~\ref{k0_med:fig} shows the histogram of
 median values
-\color{red}
 from the Monte Carlo chains
-\color{black}
 and the ideogram of $\gamma^0_{\hat{V}} k_0$ 
@@
 with
-\color{red}
 simulations based on expected dust distributions
-\color{black}
 within galaxies and the distribution of galaxy orientations with respect to the observer,
-\color{red}
 which determine column densities along the lines of sight toward supernovae that are consistent with observations
-\color{black}
 \citep{1998ApJ...502..177H, 2007ApJ...659..122J}.  
-\color{red}
 We emphasize that unlike other analyses,
-\color{black}
 this distribution is given by the data, and so is not dependent on any knowledge or prior
@@
 having  associated $\vec{\gamma}^0$ with
-\color{red}
 the extinction from a single effective
-\color{black}
 $\langle R^F_{\mathit{eff}}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
@@
 Let us introduce a new parameter for each supernova, $\delta R$, such that 
-\color{red}
 $A^F =\langle R^F_{\mathit{eff}}\rangle(1-  \delta R) E^F(B-V)$.
-\color{black} 
 Variations in the value of  $\delta R$, with the prior of the non-correlation between 
-\color{red}
 the coefficients in Eqn.~\ref{newdust:eqn},
-\color{black}
 lead 
@@
 Figure~\ref{k0_med:fig} shows the histogram of median values
-\color{red}
 from Monte Carlo chains
-\color{black}
 and ideogram of $\gamma^1_{\hat{V}} k_1$
@@
 These findings are consistent with previous results:
-\color{red}
 using fixed dust-extinction models,
-\color{black}
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
@@
 Nevertheless, there do remain some small inconsistencies between our numbers and expectations from
-\color{red}
 previous dust-extinction
-\color{black}
 models.
@@
 to identify $\vec{\delta} D$ as being physically intrinsic or extrinsic.
-\color{red}
 However, we present in \S\ref{interpret:sec} a separate physical argument for the intrinsic interpretation of the new term.
-\color{black}
 
@@
 The
-\color{red}
 initial step of the MCMC is at $\vec{\delta}=0$.
-\color{black}
 
 In Model~II,
-\color{red}
 as in Model~I,
-\color{black}
 for $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
@@
 The posteriors of the $\vec{\delta}$ parameters are shown  in
-\color{red}
 the left panel of
-\color{black}
 Figure~\ref{deltacorner:fig}.
@@
 condition are shown in 
-\color{red}
 the right panel of
-\color{black}
 Figure~\ref{deltacorner:fig}.
@@
 The 
-\color{red}
 two parity-symmetric
-\color{black}
 modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$~mag
@@
 The values of $\delta_X/\delta_{\hat{U}}-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
-\color{red}
 Unlike with $\gamma$, we normalize $\delta$ to $\hat{U}$ because the uncertainty in $\delta_{\hat{B}}-\delta_{\hat{V}}$ is relatively large with
 credible intervals that easily cross zero.
-\color{black}
 
@@
  (These values are relative
- \color{red}
 to
-\color{black}
  those of an arbitrary supernova in order to null out correlated errors.)
 The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5 \times$ larger for the external contribution than for the
-\color{red}
 intrinsic
-\color{black}
 component.  
@@
 mag respectively.
-\color{red}
 It should be noted that
-\color{black}
 the $E_\delta({\hat{B}}-{\hat{V}})$ standard deviation is comparable to its measurement uncertainty per-supernova.
-\color{red}
 Thus, since
-\color{black}
 the color excesses of individual supernovae have low signal-to-noise,
@@
       \caption{Left: Ideograms of the external $E({\hat{B}}-{\hat{V}})$ 
-      \color{red}
       (including contributions from both $k_0$, $k_1$, and $D$)
-      \color{black}
       and
@@
 
-\color{red}
 The priors of the correlation coefficients between the ``intrinsic''  ($A_{\delta {\hat{U}}}$) and ``extrinsic''
 ($E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$)  parameters
-\color{red}
 are set for their values to be uncorrelated. The output correlation is
-\color{black}
 consistent with zero.
@@
 model parameters.  One could have
-\color{red}
 worried this might
-\color{black}
 occur since our linear model does not precisely
@@
 a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, shifted to slightly  higher values relative to the results of Model~I.
-\color{red}
 As a point of comparison with another standard SN~Ia model, 3\% of the color vector defined by 
 the  SALT2 (v2.4) color parameter, $c$, is  projected perpendicular to the plane defined by the $\vec{\gamma}$'s.
-\color{black}
 
@@
 three different $p$-values ranging from 0.88--0.98, indicating that the
-\color{red}
 null hypothesis is a poor representation of the data.
-\color{black}
 
@@
 vector almost degenerate with the others, despite the prior 
-\color{red}
 encouraging
-\color{black}
  the independence of $k_0$, $k_1$, and $D$.
-This \color{red}
+This
 possibility
-\color{black}
  is tested using the 
@@
 Figure~\ref{pvalues_delta2:fig} shows  that for 
-\color{red}
  $-1$, 0, and $1$-sigma
 values of  the credible interval, only 0--2\% of the simulations have values of  $\delta_\perp^2/\delta^2$ as low as our data.
-\color{black}
 The $p$-values $>0.98$ indicate that 
- \color{red}
  the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance.
- \color{black}
 
@@
 this Section, except for $\vec{\delta}$, which is assigned
-\color{red}
 the mode shown in Figure~\ref{deltacorner:fig},
-\color{black}
 and the same noise as our data.  The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
@@
 
-%The Model~II fit of SN~2014J \citet{2014ApJ...788L..21A}  data 
-%gives $k_0$ and $k_1$ that are qualitatively similar to  those from the fit to Model~I but with much larger uncertainties.
-%These parameters are now highly correlated with $D$, which itself is consistent with zero.  The results resemble those of
-%Model~I shown in Figure~\ref{sn2014j:fig}, except for larger error bars for the color excesses projected onto the dust model.
-
 \section{Discussion}
 \label{discussion:sec}
-\color{red}
 In this Section
@@
 color-magnitude relations.
-\color{black}
+
 \subsection{Light Curve Shape}
@@
 has the largest significance  at 
-\color{red}
 only
-\color{black}
 $1\sigma$.
@@
    \centering
-%   \includegraphics[width=2.8in]{output25/x1si.pdf}
    \includegraphics[width=5in]{output25/x1D.pdf}
-    \caption{The  \color{red}
+    \caption{The
     intrinsic color component of Model~II as given by
@@
     shows no correlation between the two.  (Note that there remain correlated uncertainties between points.)
-    \color{black}
    \label{x1:fig}}
@@
 To first order, the $\lambda_{Si}$ treated in our study varies linearly with $v_{Si}$
-\color{red}
 neglecting the tiny relativistic corrections due to the Doppler effect.
-\color{black}
 The values of the $v_{Si}$ coefficient, $\eta$, in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
@@
 are expected to be produced together in the thermonuclear burning into intermediate mass elements.
-\color{red}
 Nevertheless, Figures~\ref{global1:fig} -- \ref{global5:fig} show the low probability of  $\alpha=0$, $\beta=0$, $\eta\ne0$ in our Model~I.
-\color{black}
 We conclude that $v_{Si}$ is correlated with color, 
@@
 is absorbed into the 
-\color{red}
 more-dominant
-\color{black}
 equivalent-width corrections.
@@
 The results from  \S\ref{shape:sec} and this subsection 
-\color{red}
 present $EW_{Ca}$ with $v_{Si}$, and  $EW_{Si}$ with SALT2 $x_1$,  each a 
@@
 and is more efficiently captured in one of them.
-\color{black}
-%of  correlated observables.  The model prefers corrections that reduce intrinsic dispersion.
-%The free parameters that describe the intrinsic dispersion enter the model likelihood through  the term $(\det{C_c})^{-0.5}$, which gives higher likelihood 
-%for lower dispersions.
-%\color{red}
-%The fact that the maximum likelihood analysis attributes magnitude corrections to
-%$EW_{Ca}$ over $v_{Si}$, and  $EW_{Si}$ over SALT2 $x_1$  that $EW_{Ca}$  $EW_{Si}$
-%\color{black}
-%This leads to magnitude corrections being preferentially
-%attributed to.
 
@@
 we plot in Figure~\ref{childress:fig} our intrinsic parameter
-\color{red} mass versus $A_{\delta {\hat{U}}}-A_{\delta {\hat{U}}}|_0$  (subtracting out a random supernova
+mass versus $A_{\delta {\hat{U}}}-A_{\delta {\hat{U}}}|_0$  (subtracting out a random supernova
 to suppress correlated errors)
-\color{black}
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
@@
 %---
-\color{red}
 $\langle A_{\delta {\hat{U}}} \rangle=   0.000 \pm {    0.011 }$ mag,
 $\langle A_{\delta {\hat{U}}} \rangle= 0.003 \pm {    0.009 }$ mag
-\color{black}
 for low- and high-mass hosts respectively: there is no significant difference in $A_{\delta {\hat{U}}}$ between them.
@@
 are drawn from a common distribution,
-\color{red}
 meaning there is as of yet no sign that our new color parameter is responsible for the mass step.
-\color{black}
 
 A more pertinent test 
-\color{red}
 would be to check whether
-\color{black}
 a host-mass bias persists in Hubble diagram residuals
@@
 \label{interpret:sec}
-\color{red}
 Supernova colors are expected to be affected by interstellar Milky Way-like dust   (e.g.\ whose extinction is modeled as by  \citetalias{1999PASP..111...63F})
@@
 Some encounter dust while others do not:  the distribution of the amount of  dust local to  supernovae within its host and
-geometric projection effects, together lead to the expectation for a small but nontrivial fraction  of supernovae of having zero
+geometric projection effects together lead to the expectation for a small but nontrivial fraction  of supernovae of having zero
 dust column density and the
@@
       \caption{
-      \color{red}
       The ${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 + \delta_{\hat{U}} D$
@@
 range of values whereas the right zooms in the upper-left corner of the population.
-	\color{black}
    \label{speccorr:fig}}
@@
 $D$ with $A_V$ would imply an unphysical $R^F=0.5$.
-\color{red}
 (\citealt{Huang2017} find that in the limit of Rayleigh scattering, $R_V \approx 0.81$.)
-\color{black}
 We do not have conclusive evidence that  $\delta$ is a property of dust distinct from that described by $\gamma$, rather
 than representing intrinsic supernova color variation.
-\color{black}
 
@@
 distribution of $A_V$.  
-\color{red}
 The derived $A_V$ distribution has the quasi-exponential roll-over expected from simulations.
@@
 has a strong mode with an infrequent but extended scatter toward lower values.
-\color{black}
 Nesting this model in an extended model produces a result that 
 gives the first identification of  a new
-\color{red}
 intrinsic
-\color{black} parameter that affects supernova
+parameter that affects supernova
 colors in a manner that is distinct from the expectations for dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
-\color{red}
 Not only do we detect an intrinsic color consistent with that
@@
 and dust properties.
-\color{black}
-
-\color{red}
+
 Using different arguments based on expected populations, \citetalias{2017ApJ...842...93M} also infer
@@
 observational signature of the intrinsic SN color-magnitude relationship.
-\color{black}
 
@@
 \citet{2017Rigault} find that a step in Hubble residuals is better related to local 
-\color{red}
 specific
-\color{black}
 star 
@@
 The grey parameter $\Delta$ with its
-\color{red}
 $0.08$
-\color{black} mag dispersion, while containing information on absolute magnitude, 
+mag dispersion, while containing information on absolute magnitude, 
 also 
-\color{red}
 includes
-\color{black}
 contributions from peculiar velocities and measurement uncertainties.  Studies
 focused on improving SNe~Ia as standard candles 
-\color{red}
 would need to
-\color{black}
 modify  our model to
@@
 \appendix
-\color{red}
 \section{Testing for Parameter Bias Through Simultations}
@@
 
-\color{black}
-
 \bibliographystyle{apj}

### 2017-10-17 fitz11.py

@@ -205,7 +205,7 @@ ax.add_artist(a)
 crap = dAdAv + dAdebv*kappa1
 dum  = numpy.sqrt(crap[0]**2+crap[2]**2+crap[4]**2)
 ax.plot([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum],label=r'$a(X)+b(X)/{:4.2f}$'.format(1/kappa1),ls=':',color='black')
-a = Arrow3D([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum], mutation_scale=10, ls=':',color='black',
+a = Arrow3D([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum], mutation_scale=10, ls=':',color='black', linewidth=3.,
             arrowstyle="-|>")
 ax.add_artist(a)
 

### 2017-10-20 submit/apj.tex
finish comments from Final RFC

--- 2017-10-17 apj.tex
@@
 \author{     D.~Fouchez}
-\affiliation{    Centre de Physique des Particules de Marseille, 
-    Aix-Marseille Universit\'e , CNRS/IN2P3, 
+\affiliation{    Aix Marseille Univ, CNRS/IN2P3, CPPM, 
     163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France}
@@
 \affiliation{   Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China }
-\affiliation{    Centre de Physique des Particules de Marseille, 
-    Aix-Marseille Universit\'e , CNRS/IN2P3, 
+\affiliation{     Aix Marseille Univ, CNRS/IN2P3, CPPM, 
     163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France}
@@
 the average is used  in cases where there are multiple spectral measurements within that time window.
+\color{red}
+The spectral features are in \AA\ units.
+\color{black}
 
@@
 The 
-spectroscopic-feature measurements are presented
+spectroscopic-feature measurements 
+\color{red}
+and uncertainties
+\color{black}
+are presented
 in \citet{2017Chotard}.
@@
 Unlike the parameters associated with
-the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
+the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent,
+\color{red}
+dimensionless
+\color{black}
 parameters $k_0$ and $k_1$ are not directly associated
@@
 relate spectral-feature parameters with intrinsic magnitudes.
+\color{red}
+The units of $\vec{c}$ are mag, the units of $\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$ are mag~\AA$^{-1}$.
+\color{black}
 The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes that relate 
-the latent extrinsic-color parameters with apparent magnitudes.
+the latent extrinsic-color parameters with apparent magnitudes,
+\color{red}
+and have mag units.
+These global parameters act on each of the five bands; a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
+all components are written as a vector, e.g.\ $\vec{c}$.  This provides a notational distinction between these global parameters and per-supernova parameters.
+\color{black}
 
@@
 $$
-i.e.\ shifts in the global coefficients $\vec{\gamma}$ can be compensated by shifts in $\pmb{\Delta}$ for each supernova while maintaining 
+i.e.\ shifts in the global coefficients $\vec{\gamma}$ can be compensated by shifts in 
+\color{red}
+$\Delta$
+\color{black}
+for each supernova while maintaining 
 $\langle \Delta \rangle=0$.
@@
 ascribed to $\Delta$, $\vec{\gamma}^0 k_0$, and $\vec{\gamma}^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
-that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$;
+that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$
+\color{red}
+and hence favors $\gamma$'s that minimize residual dispersion;
+\color{black}
 The distributions of $\Delta$, $k_0$, and $k_1$ turn out to
@@
 In our Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
-for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior\footnote{
+for the covariance matrix $C_c$.
+\color{red}
+This is parameterized by the Choleksy factor of its
+\color{black}
+correlation matrix with a $\nu=4$  LKJ prior\footnote{
 Visualization of the LKJ correlation distribution can be found in \url{http://www.psychstatistics.com/2014/12/27/d-lkj-priors/}.}
-\citep{Lewandowski20091989} and standard
+\citep{Lewandowski20091989} and its standard
 deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
@@
    \centering
-   \includegraphics[width=5.2in]{output11/coeff0.pdf} 
+   \includegraphics[width=5.2in]{coeff0.pdf} 
             \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{U}}$ band.
@@
    \centering
-   \includegraphics[width=5.2in]{output11/coeff1.pdf} 
+   \includegraphics[width=5.2in]{coeff1.pdf} 
             \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{B}}$ band.
@@
    \centering
-   \includegraphics[width=5.2in]{output11/coeff2.pdf} 
+   \includegraphics[width=5.2in]{coeff2.pdf} 
             \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{V}}$ band.
@@
    \centering
-      \includegraphics[width=5.2in]{output11/coeff3.pdf} 
+      \includegraphics[width=5.2in]{coeff3.pdf} 
             \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{R}}$ band.
@@
    \centering
-         \includegraphics[width=5.2in]{output11/coeff4.pdf} 
+         \includegraphics[width=5.2in]{coeff4.pdf} 
             \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{I}}$ band.
@@
 For four selected colors, a plot of the
-deduced versus observed intrinsic colors and the histogram of their differences
+deduced colors versus observed colors and the histogram of their differences
 is shown in Figure~\ref{residual:fig}. 
+\color{red} The deduced colors  account for supernova-specific spectral features and $\gamma k$ terms.
+\color{black}
 There is no evidence of catastrophically poor model predictions nor of extreme
@@
 We have rerun the analysis with a variety of initial conditions, including one with $\vec{\gamma}$ equal to zero, except for a small positive 
-$\gamma^0_0$ and small negative $\gamma^1_0$; the 68\% credible intervals
+\color{red}
+$\gamma^0_{\hat{U}}$ and small negative $\gamma^1_{\hat{U}}$;
+\color{black}
+the 68\% credible intervals
 remain consistent.  Note that the MCMC chains do not migrate to the parity-degenerate solution of $\vec{\gamma}$ and $k$.
@@
    \centering
-   \includegraphics[width=5.2in]{output11/residual.pdf} 
+   \includegraphics[width=5.2in]{residual.pdf} 
             \caption{
-            Deduced versus observed intrinsic colors, for four selected colors.  Plotted on the right for each color
-is the histogram of the difference between the observed and intrinsic colors.
+            Deduced colors versus observed colors, for four selected colors. 
+            \color{red} The deduced colors  account for supernova-specific spectral features and $\gamma k$ terms.
+            \color{black}
+            Plotted on the right for each color
+is the histogram of the difference between the observed and
+\color{red}
+ deduced
+ \color{black}
+ colors.
             \label{residual:fig}}
@@
 The fit $\Delta$'s are highly correlated between supernovae.  To aid in visualization, we remove much of this
-correlation by subtracting out the $\Delta|_0$ of  an arbitrary supernova.
-The histogram of the medians of these relative  grey offsets $\Delta-\Delta|_0$,
+correlation by
+\color{red}
+selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, for each link of the MCMC. \color{black}
+The histogram of the \color{red} per-supernova \color{black} medians of these relative  grey offsets $\Delta-\Delta|_0$,
 is shown in Figure~\ref{hist:fig}.  The distribution
@@
    \centering
-   \includegraphics[width=5.2in]{output11/deltaDelta_hist.pdf} 
+   \includegraphics[width=5.2in]{deltaDelta_hist.pdf} 
    \caption{
-   Normalized ideogram and histogram of the medians of the grey offset relative to one arbitrary supernova, $\Delta-\Delta|_0$.  
+   Normalized \color{red} stack of the posteriors of all supernovae \color{black} and histogram of the \color{red} per-supernova \color{black} medians of the grey offset $\Delta$. 
+   \color{red}  To help null correlated errors, we select
+    an arbitrary supernova and subtract out its $\Delta|_0$ from those of all other objects, for each link of the MCMC.
+   \color{black}
    The supernovae with the four highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
@@
 Having no intrinsic color dispersion is disfavored, and not allowing for them can have important consequences.
-Running an analysis assuming no intrinsic dispersion (replacing the probabilistic intrinsic magnitudes in Eqn.~\ref{ewsiv:eqn}
+Running an analysis assuming no intrinsic dispersion (replacing the probabilistic intrinsic magnitudes in Eq.~\ref{ewsiv:eqn}
 with a strict equality), we find significant shifts in all slope parameters  and 
@@
 smaller statistical uncertainties.
+\color{red}
+Note that underestimated measurement uncertainties in $C$ could lead to non-intrinsic contributions to
+$C_c$; we do not further examine this systematic error in this article.
+\color{black}
 
@@
  $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in extinction from the linear approximation of
-Eqn.~\ref{f99:eqn} has amplitude $<0.008$ mag.
+Eq.~\ref{f99:eqn} has amplitude $<0.008$ mag.
 
@@
 
-The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the ${\hat{U}}{\hat{V}}I$-subspace two perspectives (left and right panels)
+The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the
+\color{red} ${\hat{U}}{\hat{V}}\hat{I}$-subspace \color{black}
+two perspectives (left and right panels)
 of the unit vectors corresponding to $\vec{\gamma}^0$ and  $\vec{\gamma}^1$ of our model (solid lines),
@@
    \centering
-   \includegraphics[width=2.95in]{output11/plane0.pdf}
-   \includegraphics[width=2.95in]{output11/plane1.pdf}
+   \includegraphics[width=2.95in]{plane0.pdf}
+   \includegraphics[width=2.95in]{plane1.pdf}
    \caption{
@@
 the plane defined by the $\vec{\gamma}$ vectors.  While
-Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
+Eq.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
 their corresponding parameters 
@@
 effective total-to-selective extinction of our sample.
-The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}, 
+The preferred values for $\kappa$ can be determined from the matrix elements of Eq.~\ref{trans_I:eqn}, 
 giving
@@
 from the Monte Carlo chains
-and the ideogram of $\gamma^0_{\hat{V}} k_0$ 
+and the  \color{red} stack of the posteriors of all supernovae \color{black}  of $\gamma^0_{\hat{V}} k_0$ 
 relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} k_0|_0$.
@@
    \centering
-   \includegraphics[width=2.8in]{output11/deltagamma0_med.pdf}
-   \includegraphics[width=2.8in]{output11/deltagamma1_med.pdf}
+   \includegraphics[width=2.8in]{deltagamma0_med.pdf}
+   \includegraphics[width=2.8in]{deltagamma1_med.pdf}
       \caption{
-      Normalized ideogram and histogram 
-      of
+      Normalized  \color{red} stack of the posteriors of all supernovae \color{black}  and histogram 
+      of $per-supernova$
 median values of $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
@@
 Variations in the value of  $\delta R$, with the prior of the non-correlation between 
-the coefficients in Eqn.~\ref{newdust:eqn},
+the coefficients in Eq.~\ref{newdust:eqn},
 lead 
@@
 \end{equation}
-From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
+From the matrix elements of Eq.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
 This result indicates that there is a small but significant covariance between  extinction contributions due to
@@
 from Monte Carlo chains
-and ideogram of $\gamma^1_{\hat{V}} k_1$
+and  \color{red} stack of the posteriors of all supernovae \color{black}  of $\gamma^1_{\hat{V}} k_1$
 relative to that of an arbitrary supernova  $\gamma^1_{\hat{V}} k_1|_0$.
@@
 Perhaps a more instructive way to consider $k_1$ is to not view it in isolation, but rather as part of a $\{k_0,k_1\}$ pair.
-A matrix such as the one in  Eqn.~\ref{trans_I:eqn} is used to transform this pair into an $\{A_V^F, E^F(B-V)\}$ pair
+A matrix such as the one in  Eq.~\ref{trans_I:eqn} is used to transform this pair into an $\{A_V^F, E^F(B-V)\}$ pair
 (modulo additive constants)  for each link in the Monte Carlo chains. A plot showing the expected values and 68\% credible intervals of these parameters
@@
    \centering
-   \includegraphics[width=5.2in]{output11/avebv_synth.pdf}
+   \includegraphics[width=5.2in]{avebv_synth.pdf}
       \caption{
@@
 absolute magnitudes. 
-Each supernova has an intrinsic $D$ parameter that is linearly related to
-absolute magnitudes through the global coefficients $\vec{\delta}$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
+Each supernova has an intrinsic,
+\color{red}
+dimensionless
+\color{black}
+$D$ parameter that is linearly related to
+absolute magnitudes through the global coefficients $\vec{\delta}$
+\color{red}
+with dimensions mag. 
+\color{black}
+As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
 its effects on broadband magnitudes.
@@
    \centering
-   \includegraphics[width=2.8in]{output25/delta_corner.pdf}
-     \includegraphics[width=2.8in]{output25/delta_corner_flipped.pdf}
+   \includegraphics[width=2.8in]{delta_corner.pdf}
+     \includegraphics[width=2.8in]{delta_corner_flipped.pdf}
    \caption{Left:  Model~II posterior contours for $\vec{\delta}$.
@@
    \centering
-      \includegraphics[width=5.2in]{output25/deltaratio.pdf}
+      \includegraphics[width=5.2in]{deltaratio.pdf}
    \caption{Model~II median values  and corresponding 68\% intervals for $\delta_X/\delta_{\hat{U}}$ in the 5 bands.
@@
 The distributions of both sources of color excess $E({\hat{B}}-{\hat{V}})$ and
- $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in the ideograms 
+ $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in the  \color{red} stack of the posteriors of all supernovae \color{black}  
  and histogram in Figure~\ref{ebv:fig}.
@@
    \centering
-   \includegraphics[width=2.8in]{output25/ebv.pdf}
-   \includegraphics[width=2.8in]{output25/ebv_delta.pdf}
-      \caption{Left: Ideograms of the external $E({\hat{B}}-{\hat{V}})$ 
+   \includegraphics[width=2.8in]{ebv.pdf}
+   \includegraphics[width=2.8in]{ebv_delta.pdf}
+      \caption{Left:  \color{red} stack of the posteriors of all supernovae \color{black}  of the external $E({\hat{B}}-{\hat{V}})$ 
       (including contributions from both $k_0$, $k_1$, and $D$)
@@
    internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
-   Right: Ideogram and histogram of the medians of $E_\delta({\hat{B}}-{\hat{V}})$ on an enlarged scale.
+   Right:  \color{red} stack of the posteriors of all supernovae \color{black}  and histogram of the \color{red} per-supernova \color{black}
+   medians of $E_\delta({\hat{B}}-{\hat{V}})$ on an enlarged scale.
    \label{ebv:fig}}
@@
    \centering
-   \includegraphics[width=5.2in]{output25/perobject_corner.pdf} 
+   \includegraphics[width=5.2in]{perobject_corner.pdf} 
    \caption{
@@
    \centering
-   \includegraphics[width=2.9in]{output25_sim_null/pvalues_delta2.pdf} 
-  \includegraphics[width=2.9in]{output25_sim_null/pvalues_relperp.pdf} 
+   \includegraphics[width=2.9in]{pvalues_delta2.pdf} 
+  \includegraphics[width=2.9in]{pvalues_relperp.pdf} 
             \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\vec{\gamma}$, $\delta_\perp^2/\delta^2$, for 100 independent simulated data sets with input $\delta=0$.
@@
 The $p$-values $>0.98$ indicate that 
- the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance.
+ the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance
+\color{red}
+or due to pathologies in our model or the evaluation of its posterior.
+\color{black}
 
@@
 relative to the statistical uncertainties. 
+\color{red}
+We also highlight that the standard deviations of $C_c$ are not biased high, which would be a signature of leakage of
+intrinsic color variations $\delta$ into intrinsic dispersion.
+\color{black}
 Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
@@
    \centering
-   \includegraphics[width=5in]{output25/x1D.pdf}
+   \includegraphics[width=5in]{x1D.pdf}
     \caption{The
@@
    \centering
-   \includegraphics[width=5.2in]{output25/residualx1.pdf}
-    \caption{Differences between observed colors and the colors predicted from the analysis, as a function
+   \includegraphics[width=5.2in]{residualx1.pdf}
+    \caption{Differences between observed colors and the colors
+    \color{red}
+    deduced \color{black}
+     from the analysis, as a function
             of the SALT2 light-curve shape parameter $x_1$.  Our model does not explicitly use $x_1$.  For reference a dotted line is plotted at zero difference.
@@
    \centering
-   \includegraphics[width=2.8in]{output25/childress.pdf}
-   \includegraphics[width=2.8in]{output25/childress_pvalue.pdf}
+   \includegraphics[width=2.8in]{childress.pdf}
+   \includegraphics[width=2.8in]{childress_pvalue.pdf}
       \caption{Left: Intrinsic parameter $A_{\delta {\hat{U}}}=\delta_{\hat{U}} D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
@@
    \centering
-   \includegraphics[width=2.8in]{output25/ccorr1e.pdf}
-   \includegraphics[width=2.8in]{output25/ccorr2e.pdf}
+   \includegraphics[width=2.8in]{ccorr1e.pdf}
+   \includegraphics[width=2.8in]{ccorr2e.pdf}
       \caption{
@@
 the ANR within the Investissements d'Avenir programme under reference
-ANR-11-IDEX-0004-02.  NC is grateful to the LABEX Lyon Institute
-of Origins (ANR-10-LABX-0066) of the Universit\'e de Lyon for its
-financial support within the program ``Investissements d'Avenir''
-(ANR-11-IDEX-0007) of the French government operated by the National
-Research Agency (ANR).  Support in Germany was provided by the DFG
+ANR-11-IDEX-0004-02.  Support in Germany was provided by the DFG
 through TRR33 ``The Dark Universe;'' and in China from Tsinghua
@@
    \centering
-   \includegraphics[width=5.2in]{output25_sim/delta_corner.pdf} 
-            \caption{Stacked $\vec{\delta}$ posterior contours for 50 independent simulated data sets.
+   \includegraphics[width=5.2in]{simdelta_corner.pdf} 
+            \caption{Stacked $\vec{\delta}$ posterior contours for \color{red} 100 \color{black} independent simulated data sets.
             The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \centering
-   \includegraphics[width=5.2in]{output25_sim/coeff0.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of ten independent simulated data sets.
+   \includegraphics[width=5.2in]{simcoeff0.pdf} 
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of \color{red} 100 \color{black} independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \centering
-   \includegraphics[width=5.2in]{output25_sim/coeff1.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of ten independent simulated data sets.
+   \includegraphics[width=5.2in]{simcoeff1.pdf} 
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of \color{red} 100 \color{black} independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \centering
-   \includegraphics[width=5.2in]{output25_sim/coeff2.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of ten independent simulated data sets.
+   \includegraphics[width=5.2in]{simcoeff2.pdf} 
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of \color{red} 100 \color{black} independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \centering
-      \includegraphics[width=5.2in]{output25_sim/coeff3.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of ten independent simulated data sets.
+      \includegraphics[width=5.2in]{simcoeff3.pdf} 
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of \color{red} 100 \color{black} independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \centering
-         \includegraphics[width=5.2in]{output25_sim/coeff4.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\alpha$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of ten independent simulated data sets.
+         \includegraphics[width=5.2in]{simcoeff4.pdf} 
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\alpha$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of \color{red} 100 \color{black} independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
 \bibliographystyle{apj}
-\bibliography{/Users/akim/Documents/alex}
+\bibliography{alex}
 

### 2017-10-20 fitz11.py

@@ -206,7 +206,7 @@ crap = dAdAv + dAdebv*kappa1
 dum  = numpy.sqrt(crap[0]**2+crap[2]**2+crap[4]**2)
 ax.plot([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum],label=r'$a(X)+b(X)/{:4.2f}$'.format(1/kappa1),ls=':',color='black')
 a = Arrow3D([0,crap[0]/dum],[0,crap[2]/dum],[0,crap[4]/dum], mutation_scale=10, ls=':',color='black', linewidth=3.,
-            arrowstyle="-|>")
+            arrowstyle="-|>",alpha=0.8)
 ax.add_artist(a)
 
 
@@ -239,23 +239,23 @@ ax.add_artist(a)
 ax.legend(prop={'size':14})
 ax.set_xlabel(r'$\hat{U}$',labelpad=18)
 ax.set_ylabel(r'$\hat{V}$',labelpad=18)
-ax.set_zlabel(r'$\hat{I}$',labelpad=18)
+ax.zaxis.set_rotate_label(False)
+ax.set_zlabel(r'$\hat{I}$',labelpad=9,rotation=0)
 ax.xaxis.set_ticks(numpy.arange(-.5,1.1,.25))
 ax.yaxis.set_ticks(numpy.arange(-.8,.81,.4))
 ax.view_init(elev=2, azim=-114)
 pp = PdfPages("output11/plane0.pdf")
-plt.tight_layout()
-plt.savefig(pp,format='pdf')
+# plt.tight_layout()
+plt.savefig(pp,format='pdf',bbox_inches='tight')
 pp.close()
 ax.view_init(elev=7, azim=-165)
 ax.yaxis.set_ticks(numpy.arange(-.75,.76,.25))
 ax.xaxis.set_ticks(numpy.arange(-.5,.76,.5))
 pp = PdfPages("output11/plane1.pdf")
-plt.tight_layout()
-plt.savefig(pp,format='pdf')
+# plt.tight_layout()
+plt.savefig(pp,format='pdf',bbox_inches='tight')
 pp.close()
 plt.close()
-
 
 # Plot vectors in BVR
 fig = plt.figure()

### 2017-10-21 submit/apj.tex
finished with Final comments

@@
 \author{     D.~Fouchez}
-\affiliation{    Aix Marseille Univ, CNRS/IN2P3, CPPM, 
-    163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France}
+\affiliation{ Aix Marseille Univ, CNRS/IN2P3, CPPM, Marseille, France
+}
 
@@
 \affiliation{   Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China }
-\affiliation{     Aix Marseille Univ, CNRS/IN2P3, CPPM, 
-    163 avenue de Luminy - Case 902 - 13288 Marseille Cedex 09, France}
+\affiliation{ Aix Marseille Univ, CNRS/IN2P3, CPPM, Marseille, France
+}
 
@@
 \color{red}
-The spectral features are in \AA\ units.
+All the above spectral features have units of \AA ngstroms.
 \color{black}
@@
 $\vec{c}$ (where $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $),
-$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept and slopes of the linear relationships that
+$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept
+\color{red}(with units of mag) and slopes (with units mag~\AA$^{-1}$)
+\color{black} of the linear relationships that
 relate spectral-feature parameters with intrinsic magnitudes.
+The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes (\color{red}
+with units of mag) \color{black} that relate 
+the latent extrinsic-color parameters with apparent magnitudes.
 \color{red}
-The units of $\vec{c}$ are mag, the units of $\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$ are mag~\AA$^{-1}$.
-\color{black}
-The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes that relate 
-the latent extrinsic-color parameters with apparent magnitudes,
-\color{red}
-and have mag units.
-These global parameters act on each of the five bands; a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
-all components are written as a vector, e.g.\ $\vec{c}$.  This provides a notational distinction between these global parameters and per-supernova parameters.
+These global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
+the combination of all components are written as a vector, e.g.\ $\vec{c}$.  This distinguishes
+notationally global versus per-supernova parameters.
 \color{black}
@@
 \color{red}
-and hence favors $\gamma$'s that minimize residual dispersion;
+and hence favors solutions of $\gamma$'s that minimize the residual dispersion described by $C_c$;
 \color{black}
@@
 \color{red}
-This is parameterized by the Choleksy factor of its
+This matrix is parameterized in two parts: by the Choleksy factor of its
 \color{black}
@@
 Visualization of the LKJ correlation distribution can be found in \url{http://www.psychstatistics.com/2014/12/27/d-lkj-priors/}.}
-\citep{Lewandowski20091989} and its standard
+\citep{Lewandowski20091989}; its standard
 deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
@@
  We find that a simpler intrinsic dispersion model with no correlations between bands
- (i.e.\ a  diagonal covariance matrix) produces little change in the posteriors of
+ (i.e.\ a  diagonal covariance matrix) produces \color{red} negligible \color{black} change in the posteriors of
  the other parameters.
@@
 For four selected colors, a plot of the
-deduced colors versus observed colors and the histogram of their differences
-is shown in Figure~\ref{residual:fig}. 
-\color{red} The deduced colors  account for supernova-specific spectral features and $\gamma k$ terms.
+\color{red}
+model-expectation colors (including  supernova-specific spectral features and $\gamma k$ terms)
 \color{black}
+ versus observed colors and the histogram of their differences
+are shown in Figure~\ref{residual:fig}. 
 There is no evidence of catastrophically poor model predictions nor of extreme
@@
             \caption{
-            Deduced colors versus observed colors, for four selected colors. 
-            \color{red} The deduced colors  account for supernova-specific spectral features and $\gamma k$ terms.
+            \color{red}
+            Model-expectation colors (including  supernova-specific spectral features and $\gamma k$ terms)
+            versus observed colors, for four selected colors. 
             \color{black}
             Plotted on the right for each color
-is the histogram of the difference between the observed and
-\color{red}
- deduced
+is the histogram of the difference between the expected and
+observed
+ colors.            \color{red}
+(Note that the $\Delta$ in the plot signifies the difference in colors, not the per-supernova magnitude offset.)
             \color{black}
- colors.
             \label{residual:fig}}
@@
 
-The fit $\Delta$'s are highly correlated between supernovae.  To aid in visualization, we remove much of this
+The fit $\Delta$'s are highly correlated between supernovae.  To aid 
+\color{red} visual interpretation, we remove much of this
 correlation by
-\color{red}
-selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, for each link of the MCMC. \color{black}
+selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, at the level of each MCMC link. \color{black}
 The histogram of the \color{red} per-supernova \color{black} medians of these relative  grey offsets $\Delta-\Delta|_0$,
@@
    \color{red}  To help null correlated errors, we select
-    an arbitrary supernova and subtract out its $\Delta|_0$ from those of all other objects, for each link of the MCMC.
+    an arbitrary supernova and subtract out its $\Delta|_0$ from those of all other objects at the level of each MCMC link.
    \color{black}
@@
 \color{red}
-Note that underestimated measurement uncertainties in $C$ could lead to non-intrinsic contributions to
-$C_c$; we do not further examine this systematic error in this article.
+Note that underestimated measurement uncertainties in $C$ could contribute to some of the dispersion in what we have considered as an intrinsic
+$C_c$; we do not explore this source of systematic error in this article.
 \color{black}
@@
 Figure~\ref{k0_med:fig} shows the histogram of
+\color{red}
+per-supernova
+\color{black}
 median values
 from the Monte Carlo chains
-and the  \color{red} stack of the posteriors of all supernovae \color{black}  of $\gamma^0_{\hat{V}} k_0$ 
+and the  \color{red} stack of the posteriors of all supernovae \color{black}  for $\gamma^0_{\hat{V}} k_0$ 
 relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} k_0|_0$.
@@
       Normalized  \color{red} stack of the posteriors of all supernovae \color{black}  and histogram 
-      of $per-supernova$
-median values of $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
-(left) : $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
-which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{\mathit{eff}}\rangle$ value (right).
+      of \color{red} per-supernova \color{black}
+median values of: (left) $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$, which is associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model;
+(right) $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
+which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{\mathit{eff}}\rangle$ value.
    \label{k0_med:fig}}
@@
 the color-excess parameter $E^F(B-V)$.
-Figure~\ref{k0_med:fig} shows the histogram of median values
+Figure~\ref{k0_med:fig} shows the histogram of \color{red} per-supernova \color{black}
+median values
 from Monte Carlo chains
@@
 \color{red}
-with dimensions mag. 
+with mag units. 
 \color{black}
@@
 The distributions of both sources of color excess $E({\hat{B}}-{\hat{V}})$ and
- $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in the  \color{red} stack of the posteriors of all supernovae \color{black}  
- and histogram in Figure~\ref{ebv:fig}.
+ $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in Figure~\ref{ebv:fig} as the  \color{red} stack of the posteriors of all supernovae 
+ and the histogram of per-supernova median values. \color{black} 
  (These values are relative
@@
 The $p$-values $>0.98$ indicate that 
- the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance
+ the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance,
 \color{red}
@@
 \color{red}
-We also highlight that the standard deviations of $C_c$ are not biased high, which would be a signature of leakage of
-intrinsic color variations $\delta$ into intrinsic dispersion.
+The standard deviations of $C_c$, $\vec{\sigma}$,  are not biased high, which would have been a signature of leakage of
+intrinsic color variations from $\delta$ into intrinsic dispersion.
 \color{black}
@@
    \includegraphics[width=5.2in]{residualx1.pdf}
-    \caption{Differences between observed colors and the colors
-    \color{red}
-    deduced \color{black}
+    \caption{Differences between observed colors and the     \color{red}
+    expected \color{black} colors
      from the analysis, as a function

### 2017-10-27 submit/apj.tex
changes for Manu

@@
 \subsection{Model}
+\label{modelmodel:sec}
 We assume 
@@
 
-The parameterized intrinsic dispersion, $C_c$, seemingly introduces degeneracy in the model, as magnitude and color variation
-ascribed to $\Delta$, $\vec{\gamma}^0 k_0$, and $\vec{\gamma}^1 k_1$ could also be attributed to intrinsic dispersion.  There are several features of the model
-that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$
-\color{red}
-and hence favors solutions of $\gamma$'s that minimize the residual dispersion described by $C_c$;
+The parameterized intrinsic dispersion, $C_c$,  introduces degeneracy in the model, as magnitude and color variation
+ascribed to $\Delta$, $\vec{\gamma}^0 k_0$, and $\vec{\gamma}^1 k_1$ can  be attributed to intrinsic dispersion
+\color{blue}
+and vice versa.
+In the case where there is independent intrinsic dispersion in all 5 bands, i.e.\  the input $C_c$ has rank-5, there exists degenerate solutions with a $C_c$ of rank 2.
+Those identical predictions generally do not yield the same likelihood, as the determinant of $C_c$ varies over those solutions.
+In a maximum-likelihood analysis the rank-2 is preferred over the rank-5 solution, resulting in some intrinsic dispersion getting attributed to $\Delta$, $k_0$, and $k_1$.
+In our Bayesian analysis we impose priors on $C_c$, so that a zero-value determinant is disfavored.    
+Thus, leakage from per-supernova intrinsic color parameters to intrinsic dispersion could bias the intrinsic color vectors of the SN Ia family,  or conversely, intrinsic dispersion could be spuriously attributed to an intrinsic color.
+We examine this effect in the discussion of the results in \S\ref{model2:sec}.
 \color{black}
-The distributions of $\Delta$, $k_0$, and $k_1$ turn out to
-be non-Gaussian, and so are not well described by the Normal covariance we impose in $C_c$; the grey magnitude offsets, $\Delta$, would appear as a constant
-in all elements of the covariance matrix, which is disfavored for the Bayesian prior selected for $C_c$.
+%
+%There are several features of the model
+%that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$
+%\color{red}
+%and hence favors solutions of $\gamma$'s that minimize the residual dispersion described by $C_c$;
+%\color{black}
+%The distributions of $\Delta$, $k_0$, and $k_1$ turn out to
+%be non-Gaussian, and so are not well described by the Normal covariance we impose in $C_c$; the grey magnitude offsets, $\Delta$, would appear as a constant
+%in all elements of the covariance matrix, which is disfavored for the Bayesian prior selected for $C_c$.
 
@@
 observed
- colors.            \color{red}
-(Note that the $\Delta$ in the plot signifies the difference in colors, not the per-supernova magnitude offset.)
-            \color{black}
+ colors. 
             \label{residual:fig}}
@@
 smaller statistical uncertainties.
-\color{red}
-Note that underestimated measurement uncertainties in $C$ could contribute to some of the dispersion in what we have considered as an intrinsic
-$C_c$; we do not explore this source of systematic error in this article.
-\color{black}
 
@@
 
-The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
+The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  
+\color{blue}
+The $\delta$ parameters are normalized to $\hat{U}$ instead of $\hat{V}$, since the posterior of $\delta_{\hat{V}}$ covers zero.
+\color{black}
+Comparison with the
 results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
@@
 in the ${\hat{U}}$ and ${\hat{B}}$ bands.
+\color{blue}
+The variance captured by the first two eigenvectors of $C_c$ from Model~II is $4.7 \times 10^{-3}$ mag$^2$, as
+compared to  $6.4 \times 10^{-3}$ mag$^2$ from Model~I; this reduction shows the amount of intrinsic dispersion in Model~I
+that  is now attributed to the explicit $\delta D$ term.
+\color{black}
 
@@
 relative to the statistical uncertainties. 
-\color{red}
-The standard deviations of $C_c$, $\vec{\sigma}$,  are not biased high, which would have been a signature of leakage of
-intrinsic color variations from $\delta$ into intrinsic dispersion.
-\color{black}
 Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
@@
 regression dilution \citep{spearman04}.
+
+\color{blue}
+We now return to a degeneracy of our models mentioned in \S\ref{modelmodel:sec}.
+Parameters are susceptible to the misassignment, in either direction, between intrinsic color, $\Delta$, $k$, and $D$, and intrinsic dispersion $C_c$.
+The first two eigenvectors of account for $0.89_{-0.05}^{+0.04}$ of the variance of $C_c$, meaning
+that potential leakage of intrinsic colors can account for less than 10\% of the variance, corresponding to 0.024 mag standard deviation.
+We establish through simulations that the standard deviations of $C_c$, $\vec{\sigma}$,  are not biased high, which would have been a signature of leakage of
+intrinsic color variations from $\delta$ into intrinsic dispersion.
+The simulations of input null intrinsic color terms and input intrinsic dispersion do not produce spurious detections of intrinsic color vectors.  We thus conclude that
+biases induced by this degeneracy are low relative to our statistical uncertainties.
+\color{black}
 

### 2017-10-27 view25.py

@@ -412,7 +412,7 @@ pp.close()
 # pp.close()
 
 # wefwe
-
+mpl.rcParams['font.size'] = 18
 
 cind=[0,1,3,4]
 cname = ['U','B','R','I']
@@ -607,7 +607,69 @@ plt.savefig(pp,format='pdf')
 pp.close()
 plt.close()
 
+corrmat = []
+ev = []
+nev=[]
+for x1, x2 in zip(fit['L_Omega'], fit['L_sigma']):
+    cormat = numpy.dot(x2[:,None],x2[None,:])*numpy.dot(x1,x1.T)
+    u,s, v  = numpy.linalg.svd(cormat)
+    temp = [s[0:i+1].sum() for i in xrange(5)]
+    temp = numpy.array(temp)
+    nev.append(temp)
+    temp=temp[:]/temp[-1]
+    ev.append(numpy.array(temp[:-1]))
 
+ev = numpy.array(ev)
+nev= numpy.array(nev)
+
+f2 = open('temp11.pkl','rb')
+(fit2,_) = pickle.load(f2)
+corrmat = []
+ev2 = []
+nev2 = []
+for x1, x2 in zip(fit2['L_Omega'], fit2['L_sigma']):
+    cormat = numpy.dot(x2[:,None],x2[None,:])*numpy.dot(x1,x1.T)
+    u,s, v  = numpy.linalg.svd(cormat)
+    temp = [s[0:i+1].sum() for i in xrange(5)]
+    temp = numpy.array(temp)
+    nev2.append(temp)
+    temp=temp[:]/temp[-1]
+    ev2.append(numpy.array(temp[:-1]))
+fit2=[]
+ev2 = numpy.array(ev2)
+nev2= numpy.array(nev2)
+
+dum = numpy.percentile(ev,(50,50-34,50+34),axis=0)
+dum2 = numpy.percentile(ev2,(50,50-34,50+34),axis=0)
+for i in xrange(4):
+    print "{:6.2f} _ {:6.2f} ^ {:6.2f}".format(dum[0,i],dum[0,i]-dum[1,i],dum[2,i]-dum[0,i]),
+    print "{:6.2f} _ {:6.2f} ^ {:6.2f}".format(dum2[0,i],dum2[0,i]-dum2[1,i],dum2[2,i]-dum2[0,i])
+
+ev = numpy.array(ev)
+plt.hist(ev, bins=20, label=['1','2','3','4'])
[…]

### 2017-11-02 submit/apj.tex
more numbers for intrinsic dispersion matrix

@@
 In a maximum-likelihood analysis the rank-2 is preferred over the rank-5 solution, resulting in some intrinsic dispersion getting attributed to $\Delta$, $k_0$, and $k_1$.
-In our Bayesian analysis we impose priors on $C_c$, so that a zero-value determinant is disfavored.    
-Thus, leakage from per-supernova intrinsic color parameters to intrinsic dispersion could bias the intrinsic color vectors of the SN Ia family,  or conversely, intrinsic dispersion could be spuriously attributed to an intrinsic color.
+In our Bayesian analysis the priors, though not totally disallowing rank-2 $C_c$, favor rank-5  and prevent convergence to this solution.    
+Leakage from per-supernova intrinsic color parameters to intrinsic dispersion could bias the intrinsic color vectors of the SN Ia family,  or conversely, intrinsic dispersion could be spuriously attributed to an intrinsic color.
 We examine this effect in the discussion of the results in \S\ref{model2:sec}.
@@
 than the dispersion in $\Delta$.
+\color{green}
+The posterior of $\sigma_{\hat{R}}$ seen in Figure~\ref{global4:fig} does not exclude values that approach zero, highlighting that non-rank 5
+$C_c$'s are accommodated by our prior.
+\color{black}
 Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in ${\hat{V}}$ and colors with respect to ${\hat{V}}$ are
@@
 Parameters are susceptible to the misassignment, in either direction, between intrinsic color, $\Delta$, $k$, and $D$, and intrinsic dispersion $C_c$.
-The first two eigenvectors of account for $0.89_{-0.05}^{+0.04}$ of the variance of $C_c$, meaning
+The first two eigenvectors of $C_c$ account for $0.89_{-0.05}^{+0.04}$ of its variance  meaning
 that potential leakage of intrinsic colors can account for less than 10\% of the variance, corresponding to 0.024 mag standard deviation.
@@
 biases induced by this degeneracy are low relative to our statistical uncertainties.
+\color{black}
+
+\color{green}
+Contour of sigma and delta.
+
+Results from diagonal covariance.
 \color{black}

### 2017-11-02 prior.py

@@ -1,0 +1,61 @@
+#!/usr/bin/env python
+
+import pickle
+import pystan
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import corner
+from matplotlib.backends.backend_pdf import PdfPages
+import numpy
+import sncosmo
+import scipy
+import cPickle
+import matplotlib as mpl
+import sivel
+import flip
+from matplotlib import rcParams
+rcParams['text.usetex'] = True
+
+dirname = 'output25/'
+
+
+labels = [r'$\hat{U}$',r'$\hat{B}$',r'$\hat{V}$',r'$\hat{R}$',r'$\hat{I}$']
+from matplotlib.ticker import FuncFormatter, MaxNLocator
+def format_fn2(tick_val, tick_pos):
+    if int(tick_val) in numpy.arange(5):
+        return labels[int(tick_val)]
+    else:
+        return ''
+
+mpl.rcParams['font.size'] = 18
+
+files = ['temp25.pkl','temp27.pkl','temp28.pkl','temp29.pkl','temp30.pkl','temp26.pkl']
+labe = [r"$\mbox{{{Cauchy}}}(x_0=0.1,\gamma=0.1)$, $\mbox{{{LKJ}}}(\nu=4)$", \
+        r'$\mbox{{{Cauchy}}}(x_0=0.1,\gamma=0.1)$, $\mbox{{{LKJ}}}(\nu=2)$', \
+        r'$\mbox{{{Cauchy}}}(x_0=0.1,\gamma=0.1)$, $\mbox{{{LKJ}}}(\nu=8)$', \
+        r'$\mbox{{{Cauchy}}}(x_0=0.07,\gamma=0.1)$, $\mbox{{{LKJ}}}(\nu=4)$', \
+        r'$\mbox{{{Cauchy}}}(x_0=0.13,\gamma=0.1)$, $\mbox{{{LKJ}}}(\nu=4)$', \
+        r'$\mbox{{{Cauchy}}}(x_0=0.1,\gamma=0.1)$, diagonal']
+fig = plt.figure()
+ax = fig.add_subplot(111)
+
+for ind,(f,lab) in enumerate(zip(files,labe)):
+    f = open(f,'rb')
+    (fit,_) = pickle.load(f)
+    (y, ymin, ymax) = numpy.percentile(fit['rho1']/fit['rho1'][:,0][:,None],(50,50-34,50+34),axis=0)
[…]

### 2017-11-09 submit/apj.tex
simulate covariance matrices with stan

@@
 the average is used  in cases where there are multiple spectral measurements within that time window.
-\color{red}
 All the above spectral features have units of \AA ngstroms.
-\color{black}
 
@@
 spectroscopic-feature measurements 
-\color{red}
 and uncertainties
-\color{black}
 are presented
@@
 band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
-fluxes to luminosites.
+fluxes to luminosities.
 The apparent magnitudes are the sum of the intrinsic magnitudes plus additional terms that are linearly dependent on the
@@
 the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent,
-\color{red}
 dimensionless
-\color{black}
 parameters $k_0$ and $k_1$ are not directly associated
@@
 $\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept
-\color{red}(with units of mag) and slopes (with units mag~\AA$^{-1}$)
-\color{black} of the linear relationships that
+with units of mag) and slopes (with units mag~\AA$^{-1}$)
+of the linear relationships that
 relate spectral-feature parameters with intrinsic magnitudes.
-The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes (\color{red}
-with units of mag) \color{black} that relate 
+The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes (with units of mag) that relate 
 the latent extrinsic-color parameters with apparent magnitudes.
-\color{red}
 These global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
@@
 notationally global versus per-supernova parameters.
-\color{black}
 
@@
 i.e.\ shifts in the global coefficients $\vec{\gamma}$ can be compensated by shifts in 
-\color{red}
 $\Delta$
-\color{black}
 for each supernova while maintaining 
@@
 ascribed to $\Delta$, $\vec{\gamma}^0 k_0$, and $\vec{\gamma}^1 k_1$ can  be attributed to intrinsic dispersion
-\color{blue}
 and vice versa.
@@
 Leakage from per-supernova intrinsic color parameters to intrinsic dispersion could bias the intrinsic color vectors of the SN Ia family,  or conversely, intrinsic dispersion could be spuriously attributed to an intrinsic color.
-We examine this effect in the discussion of the results in \S\ref{model2:sec}.
-\color{black}
+We examine this effect in the discussion of the results in \S\ref{degenerate:sec}.
+
 %
@@
 for the covariance matrix $C_c$.
-\color{red}
 This matrix is parameterized in two parts: by the Choleksy factor of its
-\color{black}
-correlation matrix with a $\nu=4$  LKJ prior\footnote{
-Visualization of the LKJ correlation distribution can be found in \url{http://www.psychstatistics.com/2014/12/27/d-lkj-priors/}.}
+correlation matrix with a $\eta=4$  LKJ prior
 \citep{Lewandowski20091989}; its standard
@@
 This covariance matrix prior is recommended by STAN \citep{stan}, the Monte Carlo program we use to evaluate the model.
- We find that a simpler intrinsic dispersion model with no correlations between bands
- (i.e.\ a  diagonal covariance matrix) produces \color{red} negligible \color{black} change in the posteriors of
- the other parameters.
+\color{blue}
+Further properties of the this prior are presented in \S\ref{priorappendix:sec}.
+\color{black}
 
@@
 For four selected colors, a plot of the
-\color{red}
 model-expectation colors (including  supernova-specific spectral features and $\gamma k$ terms)
-\color{black}
  versus observed colors and the histogram of their differences
@@
 We have rerun the analysis with a variety of initial conditions, including one with $\vec{\gamma}$ equal to zero, except for a small positive 
-\color{red}
 $\gamma^0_{\hat{U}}$ and small negative $\gamma^1_{\hat{U}}$;
-\color{black}
 the 68\% credible intervals
@@
             \caption{
-            \color{red}
             Model-expectation colors (including  supernova-specific spectral features and $\gamma k$ terms)
             versus observed colors, for four selected colors. 
-            \color{black}
             Plotted on the right for each color
@@
 The fit $\Delta$'s are highly correlated between supernovae.  To aid 
-\color{red} visual interpretation, we remove much of this
+visual interpretation, we remove much of this
 correlation by
-selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, at the level of each MCMC link. \color{black}
-The histogram of the \color{red} per-supernova \color{black} medians of these relative  grey offsets $\Delta-\Delta|_0$,
+selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, at the level of each MCMC link.
+The histogram of the per-supernova  medians of these relative  grey offsets $\Delta-\Delta|_0$,
 is shown in Figure~\ref{hist:fig}.  The distribution
@@
    \caption{
-   Normalized \color{red} stack of the posteriors of all supernovae \color{black} and histogram of the \color{red} per-supernova \color{black} medians of the grey offset $\Delta$. 
-   \color{red}  To help null correlated errors, we select
+   Normalized stack of the posteriors of all supernovae and histogram of the per-supernova medians of the grey offset $\Delta$. 
+   To help null correlated errors, we select
     an arbitrary supernova and subtract out its $\Delta|_0$ from those of all other objects at the level of each MCMC link.
-   \color{black}
    The supernovae with the four highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
@@
 than the dispersion in $\Delta$.
-\color{green}
-The posterior of $\sigma_{\hat{R}}$ seen in Figure~\ref{global4:fig} does not exclude values that approach zero, highlighting that non-rank 5
-$C_c$'s are accommodated by our prior.
-\color{black}
 Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in ${\hat{V}}$ and colors with respect to ${\hat{V}}$ are
@@
 The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the
-\color{red} ${\hat{U}}{\hat{V}}\hat{I}$-subspace \color{black}
+${\hat{U}}{\hat{V}}\hat{I}$-subspace
 two perspectives (left and right panels)
@@
 Figure~\ref{k0_med:fig} shows the histogram of
-\color{red}
 per-supernova
-\color{black}
 median values
 from the Monte Carlo chains
-and the  \color{red} stack of the posteriors of all supernovae \color{black}  for $\gamma^0_{\hat{V}} k_0$ 
+and the  stack of the posteriors of all supernovae  for $\gamma^0_{\hat{V}} k_0$ 
 relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} k_0|_0$.
@@
       \caption{
-      Normalized  \color{red} stack of the posteriors of all supernovae \color{black}  and histogram 
-      of \color{red} per-supernova \color{black}
+      Normalized stack of the posteriors of all supernovae  and histogram 
+      of  per-supernova 
 median values of: (left) $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$, which is associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model;
@@
 the color-excess parameter $E^F(B-V)$.
-Figure~\ref{k0_med:fig} shows the histogram of \color{red} per-supernova \color{black}
+Figure~\ref{k0_med:fig} shows the histogram of per-supernova
 median values
 from Monte Carlo chains
-and  \color{red} stack of the posteriors of all supernovae \color{black}  of $\gamma^1_{\hat{V}} k_1$
+and  stack of the posteriors of all supernovae  of $\gamma^1_{\hat{V}} k_1$
 relative to that of an arbitrary supernova  $\gamma^1_{\hat{V}} k_1|_0$.
@@
 \label{model2:sec}
+\subsection{Model}
 In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
@@
 Each supernova has an intrinsic,
-\color{red}
 dimensionless
-\color{black}
 $D$ parameter that is linearly related to
 absolute magnitudes through the global coefficients $\vec{\delta}$
-\color{red}
 with mag units. 
-\color{black}
 As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
@@
 $C_c$.  For $N=172$ supernovae, there are 1376 observables and 1242 top-level parameters.
+
+\subsection{Results}
 
@@
 The distributions of both sources of color excess $E({\hat{B}}-{\hat{V}})$ and
- $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in Figure~\ref{ebv:fig} as the  \color{red} stack of the posteriors of all supernovae 
- and the histogram of per-supernova median values. \color{black} 
+ $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in Figure~\ref{ebv:fig} as the  stack of the posteriors of all supernovae 
+ and the histogram of per-supernova median values.
  (These values are relative
@@
    \includegraphics[width=2.8in]{ebv_delta.pdf}
-      \caption{Left:  \color{red} stack of the posteriors of all supernovae \color{black}  of the external $E({\hat{B}}-{\hat{V}})$ 
+      \caption{Left:  Stack of the posteriors of all supernovae of the external $E({\hat{B}}-{\hat{V}})$ 
       (including contributions from both $k_0$, $k_1$, and $D$)
@@
    internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
-   Right:  \color{red} stack of the posteriors of all supernovae \color{black}  and histogram of the \color{red} per-supernova \color{black}
+   Right:  Stack of the posteriors of all supernovae  and histogram of the per-supernova
    medians of $E_\delta({\hat{B}}-{\hat{V}})$ on an enlarged scale.
@@
 values of  the credible interval of our data relative to those from the simulations, we obtain
-three different $p$-values ranging from 0.88--0.98, indicating that the
+three different $p$-values ranging from 
+\color{blue}
+0.87--0.90,
+\color{black}
+ indicating that the
 null hypothesis is a poor representation of the data.
@@
  $-1$, 0, and $1$-sigma
-values of  the credible interval, only 0--2\% of the simulations have values of  $\delta_\perp^2/\delta^2$ as low as our data.
-The $p$-values $>0.98$ indicate that 
+values of  the credible interval, only
+\color{blue}
+2--3\%
+\color{black}
+of the simulations have values of  $\delta_\perp^2/\delta^2$ as low as our data.
+The $p$-values $\ge 0.97$ indicate that 
  the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance,
-\color{red}
 or due to pathologies in our model or the evaluation of its posterior.
+
+Potential biases
+\color{blue}
+within the analysis
 \color{black}
-
-Potential biases in our results are measured through simulation.
+are measured through simulation.
 We generate 100 random realizations of data with input  parameters equal to the median values found in
@@
 
+\subsection{Per-Supernova Parameter -- Covariance Matrix Degeneracy}
+\label{degenerate:sec}
 \color{blue}
-We now return to a degeneracy of our models mentioned in \S\ref{modelmodel:sec}.
-Parameters are susceptible to the misassignment, in either direction, between intrinsic color, $\Delta$, $k$, and $D$, and intrinsic dispersion $C_c$.
+As discussed in \S\ref{modelmodel:sec}, our two models have degeneracy between per-supernova parameters and the covariance matrix.
+In the posterior, the degeneracy is broken by the determinant of the covariance matrix in the likelihood and by the priors.
+Given that the priors we use are not exactly correct,
+the parameters are susceptible to the misassignment, in either direction, between intrinsic color, $\Delta$, $k$, and $D$, and intrinsic dispersion $C_c$.
+\S\ref{priorappendix:sec}
+
 The first two eigenvectors of $C_c$ account for $0.89_{-0.05}^{+0.04}$ of its variance  meaning
@@
 
-\color{green}
-Contour of sigma and delta.
-
-Results from diagonal covariance.
-\color{black}
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{ccnvar.pdf}
+   \includegraphics[width=2.8in]{ccvar.pdf}
+      \caption{Left: Right: 
+      }
+\end{figure}
 
@@
 \appendix
+\section{Intrinsic Covariance Matrix Prior}
+\label{priorappendix:sec}
+\color{blue}
+The covariance matrix $C_c$
+is parameterized in two parts.
+The variance for each of the 5 bands comes from a  truncated $\text{Cauchy}(0.1,0.1)$ distribution
+restricted to positive values.
+The correlation matrix of $C_c$ is
+drawn from an LKJ prior \citep{Lewandowski20091989}
+that has the property
+\begin{equation}
+p(\text{corr}(C_c)| \eta) \propto \text{det}(\text{corr}(C_c))^{\eta-1}.
+\end{equation}
+For $\eta <1$, smaller determinants (stronger correlations)  are likely, for $\eta>1$ larger determinants (weaker correlations)
+are likely, 
+and $\eta=1$ the density is uniform.  For $\eta=\infty$ the prior is of a diagonal  matrix with no correlation.
+We choose $\eta=4$ for our prior.
+
+The distribution of determinants from which the covariance matrices are drawn is visualized in the left plot of Figure~\ref{priordet:fig},
+which shows
+histograms of $\ln{(\text{det}(C_c))}$  realizations for different $\eta$ priors.
+The distribution has a steep drop that counteracts the log-likelihood's linear increase with decreasing
+log-determinant.  There is little qualitative difference in the distributions from $\eta$'s ranging from 0.5 to 20.
+The diagonal prior  produces significantly higher determinants.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{priordet.pdf}
+   \includegraphics[width=2.8in]{prior.pdf}
+         \caption{Left: Histograms of $\ln{(\text{det}(C_c))}$ from realizations for different $\eta$ priors.
+         Right: Histograms of the normalized variance captured by the leading $n$ eigenvectors for $\eta=0.5$, 20,
+         and a diagonal prior.
+   \label{priordet:fig}}
+\end{figure}
+
+The distribution of the variance among the matrix eigenvectors is visualized in  right plot of Figure~\ref{priordet:fig},
+which shows histograms
+of the normalized variance captured by the leading $n$ eigenvectors for different $\eta$ priors.
+The variance is  broadly distributed in the diagonal case, whereas for finite $\eta$ variance is concentrated
+in fewer eigenvectors. As with the
+determinants, there is little qualitative difference in the distributions from $\eta$'s ranging from 0.5 to 20.
+
+\color{black}
 \section{Testing for Parameter Bias Through Simultations}
@@
 We generated 50 random realizations of data with the same input  parameters.
-The posterior for each realization was analyzed individually, and the posteriors of all realizations were stacked.
+The posterior for each realization was analyzed individually, and greeneriors of all realizations were stacked.
 The stacks and input parameter values are shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.

### 2017-11-17 submit/fix.tex
new slew of simulations and results

--- 2017-11-09 submit/apj.tex
@@
-\documentclass{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
+\documentclass[trackchanges]{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
@@
 The data used in this analysis are described in \S\ref{data:sec}.
+\replaced{
 In \S\ref{model:sec} we present a
@@
 In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
+}{wefwe}
 In  \S\ref{discussion:sec}
@@
 %\end{deluxetable}
+
+\section{Model~I: Extrinsic Colors}
+\label{modelI:sec}
+We begin by considering a model for supernova magnitudes that have linear dependence on spectral parameters
+and two extrinsic color parameters. This model is referred to as Model~I.  It is not the primary focus of this article, but its
+results are of interest.  The purpose of this Section is to introduce some basic concepts of our models,
+to show how the models can be expressed in terms of dust-extinction models, and to give Model~I results on dust. 
+We refrain from presenting the full results of Model~I in deference to the more complex Model~II that is the subject of Section~\ref{modelII:sec},
+
+\subsection{Model}
+We assume 
+that  peak intrinsic ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
+on its
+ equivalent widths of the Ca~II H\&K and Si~II~$\lambda$4141 spectral features
+$EW_{Ca}$ and $EW_{Si}$,
+and the wavelength of the minimum of 
+the Si~II~$\lambda6355$ feature $\lambda_{Si}$
+around $B$-band peak brightness:
+these spectral features are associated with SN~Ia  spectroscopic diversity  
+\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
+The explicit omission of light-curve shape in our model is compensated by its proxy,
+$EW_{Si}$, at peak brightness
+\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
+A grey magnitude offset, $\Delta$, is included for each supernova
+to capture 
+potential
+band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
+fluxes to luminosities.
+The intrinsic  magnitudes are
+\begin{equation}
+\begin{pmatrix}
+{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
+\end{pmatrix}
+=
+\Delta \vec{I} +
+\begin{pmatrix}
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} \\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  \\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} \\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} \\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}
+\end{pmatrix},
+\label{ewsiv:eqn}
+\end{equation}
+where $\vec{I}$ is the Identity vector.
+The global parameter vectors\footnote{Global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
+the combination of all components are written as a vector, e.g.\ $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) )$,.  This 
+notationally distinguishes between global versus per-supernova parameters.
+} that describe the SN~Ia population
+$\vec{c}$, 
+$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept
+(units of mag) and slopes (units of mag~\AA$^{-1}$)
+of the linear relationships that
+relate spectral-feature parameters with intrinsic magnitudes.
+
+The apparent magnitudes are the sum of the intrinsic magnitudes plus additional terms that are linearly dependent on the
+per-supernova
+extrinsic-color parameters $g_0$ and $g_1$.  
+Unlike the parameters associated with
+the spectral measurements ($EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$)  the latent,
+dimensionless
+parameters $g_0$ and $g_1$ are not directly associated
+with observables but rather are inferred as part of the analysis.
+The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes (units of mag) that relate 
+the latent extrinsic-color parameters with apparent magnitudes.
+The observables
+$\hat{U}_o, {\hat{B}}_o, {\hat{V}}_o, {\hat{R}}_o, {\hat{I}}_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
+have Gaussian measurement uncertainty with covariance $C$.
+The
+likelihood density for the described model
+corresponds to the probability distribution function described by
+\begin{equation}
+\begin{pmatrix}
+{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
+\end{pmatrix}
+\sim \mathcal{N}
+\left(
+\begin{pmatrix}
+{\hat{U}} +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
+{\hat{V}}+\gamma^0_{{\hat{V}}} g_0+\gamma^1_{{\hat{V}}} g_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} g_0 + \gamma^1_{{\hat{R}}} g_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} g_0+\gamma^1_{{\hat{I}}} g_1\\
+EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
+\end{pmatrix}
+,C
+\right).
+\label{dust:eqn}
+\end{equation}
+
+The model as written has degeneracies that need to be constrained in order for fits to converge.
+The model does not specify the absolute magnitude nor the intrinsic color of a supernova that has no extrinsic color contribution;
+in their place the zeropoints of the per-supernova magnitude and color parameters are set to the sample means
+\begin{equation}
+\langle \Delta \rangle=0,\ \langle g_0 \rangle=0,\ \langle g_1 \rangle=0.
+\end{equation}
+The model contains the product of latent parameters
+$\vec{\gamma} g$, which leads to the degeneracy $\vec{\gamma} \rightarrow a\vec{\gamma}$, $g \rightarrow a^{-1} g$.
+To aid in the convergence of $\vec{\gamma}$ and $g$ we impose a prior on the rms of $g$, though
+our physical interpretations are ultimately independent of this scaling.
+This prior does not specify the sign of $a$, which leaves a parity degeneracy.  As will be seen, the signal-to-noise in $\vec{\gamma}$ is sufficiently
+high that our finite MCMC chains do not migrate between the degenerate solutions; to simplify the merging of multiple chains
+we impose one of the degenerate solutions
+\begin{equation}
+\gamma^0_{\hat{U}} > 0,\ \gamma^1_{\hat{U}} < 0.
+\end{equation}
+As  in mixture models, the combinations $\vec{\gamma}^0 g_0$ and $\vec{\gamma}^1 g_1$ terms are degenerate under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
+we break that degeneracy  by setting consistent initial conditions that succeed in keeping indices consistent over all analysis chains.
+
+Another form of degeneracy is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
+ $\vec{\gamma}^0 \rightarrow \vec{\gamma}^0  + \epsilon_{\gamma^0}$, $\vec{\gamma}^1 \rightarrow \vec{\gamma}^1 + \epsilon_{\gamma^1}$
+ under the condition
+$$
+\epsilon_\Delta  +  \epsilon_{\gamma^0} g_0+  \epsilon_{\gamma^1} g_1=0,
+$$
+i.e.\ shifts in the global coefficients $\vec{\gamma}$ can be compensated by shifts in 
+$\Delta$
+for each supernova while maintaining 
+$\langle \Delta \rangle=0$.
+Another degeneracy is illustrated by $g_0 \rightarrow g_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
+$\vec{\alpha} \rightarrow \vec{\alpha} - \vec{\gamma} \epsilon$, $\vec{c} \rightarrow \vec{c} + \langle EW_{Ca}\rangle \epsilon$, i.e. the
+linear external terms can leak into the linear spectral feature corrections.
+These degeneracies are not broken within the model, but rather are constrained by the priors in which the
+per-supernova parameters
+$\Delta$, $EW$, $\lambda$, $g_0$, and $g_1$ are uncorrelated.
+
+Except where stated otherwise above, we adopt a flat prior for all parameters.
+
+\subsection{Results: $\gamma^0$ and $\gamma^1$}
+In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
+In our model, $g_0$ and $g_1$ are introduced as latent parameters that are related to linear shifts in band magnitudes through
+the  coefficients $\vec{\gamma}^0$ and
+$\vec{\gamma}^1$.  Otherwise, no physically-motivated suppositions on the properties of $g$ and $\vec{\gamma}$ are imposed.
+Attenuation of supernova light due to dust is expected to be mostly captured by the first-order affects described by our linear model.
+Here we  interpret our model $\gamma$'s in terms of
+the dust-extinction model of \citetalias{1999PASP..111...63F}.
+
+In the analysis of this and other sections of this article,
+the posterior of the model parameters is evaluated using Hamiltonian Monte Carlo with a No-U-Turn
+Sampler as implemented in
+STAN \citep{stan}.  We run eight chains, each with 5000 iterations of which
+half are used for warmup.
+Tests have revealed no evidence for the non-convergence of the MCMC run.
+STAN provides output statistics to assess
+the convergence of the output Markov chains.
+The 
+potential scale reduction statistic, $\hat{R}$
+(in this paragraph not to be confused with the synthetic $R$ magnitude)
+\citep{Gelman92}, measures the convergence of the target distribution
+in iterative simulations 
+by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
+$N_{\mathit{eff}}$ is an estimate of the number of independent draws.
+The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.
+The
+output also gives  $N_{\mathit{eff}} \gg 100$ for all parameters, indicating that all are densely sampled.
+
+All elements of the two $\vec{\gamma}$ parameter vectors 
+describing intrinsic color
+are significantly non-zero.
+None of the 20000 links of 
+our Monte Carlo chains for $\vec{\gamma}$ come close to the origin, we thus claim detection of the
+influence of $g_0$ and $g_1$  on supernova magnitudes
+with probability $1-5\times 10^{-5}$.
+We thus find a strong signal for a linear 
+extrinsic contribution to our model
+\begin{equation}
+A_X = \gamma^0_X g_0 +  \gamma^1_X g_1.
+\end{equation}
+
+A linear model with parameters $A_V$ and $E(B-V)$
+\begin{equation}
+A_X = a(X)  A_{V} + b(X) E(B-V)
+\label{f99:eqn}
+\end{equation}
+approximately describes  
+dust-extinction
+models.  For example,   the wavelength-dependent model of  \citet{1989ApJ...345..245C} is linear,
+though its linearity is lost when integrated over broad-band filters.
+For the case of
+$R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
+\citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at ${\hat{B}}$-band peak, the 
+\citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F} model
+can be approximated with
+$\vec{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\vec{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
+(The $F$ superscript is used to distinguish parameters of the \citetalias{1999PASP..111...63F} model.)
+Over the ranges
+ $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$ 
+and the wavelengths under consideration here,  the values of the elements of $a$ and $b$ vary by $<5$\%
+for the
+\citetalias{1999PASP..111...63F} model with
+ the largest error in extinction from the linear approximation having amplitude $<0.008$ mag.
+
+Our model $\gamma$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
+dust-based $a(X)$ and $b(X)$ vectors plus residual vectors perpendicular to $\vec{a}$ and $\vec{b}$,
+\begin{equation}
+\begin{pmatrix}
+\vec{\gamma}^0 \\
+\vec{\gamma}^1
+\end{pmatrix}=
+M
+\begin{pmatrix}
+\vec{a} \\
+\vec{b}
+\end{pmatrix}+
+\begin{pmatrix}
+\vec{\epsilon}_{\gamma^0} \\
+\vec{\epsilon}_{\gamma^1}
+\end{pmatrix}.
+\label{trans_I:eqn}
+\end{equation}
+The $\gamma$'s are almost entirely captured by the first term. 
+The Model~I posterior gives a quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ projected onto the plane defined by
+$a(X)$ and $b(X)$, the quadratic fraction of $\vec{\gamma}^1$ projected
+onto the dust plane is
+$0.959^{+0.013}_{-0.024}$.
+This result indicates that
+the allowed variations in ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to almost identical
+2-dimensional
+planes within
+the 5-dimensional magnitude space.
+With no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
+2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.
+
+The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the
+${\hat{U}}{\hat{V}}\hat{I}$-subspace
+two perspectives (left and right panels)
+of the unit vectors corresponding to $\vec{\gamma}^0$ and  $\vec{\gamma}^1$ of our model (solid lines),
+and $\vec{a}$, $\vec{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All  vectors are set to intersect the origin.
+The two perspectives show that while the four vectors point in different directions for each band combination,
+they are almost coplanar in ${\hat{U}}{\hat{V}}{\hat{I}}$ (they are slightly less coplanar in ${\hat{B}}{\hat{V}}{\hat{R}}$).
+The $\vec{a}$ and $\vec{b}$ vectors and the $\vec{\gamma}^0$ and $\vec{\gamma}^1$
+vectors span near-parallel planes in the 5-dimensional color space, and hence the latter can be almost entirely expressed in terms of
+the former.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.95in]{../output_fix1/plane0.pdf}
+   \includegraphics[width=2.95in]{../output_fix1/plane1.pdf}
+   \caption{
+   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
+   magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
+   two different perspectives.
+   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes
+   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
+   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
+   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes are confined to the plane that contains both.
+   The perspective on the right visually shows that all four vectors are nearly coplanar.  
+   The combination $\vec{a}+\vec{b}/2.18$ is shown in the dotted red
+   line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
+   \label{plane:fig}}
+\end{figure}
+
+We
+now turn to
+the specific choice of $\vec{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust-extinction model. 
+Our linear model would be satisfied by any two independent vectors  that span
+the plane defined by the $\vec{\gamma}$ vectors.  While
+Eq.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
+their corresponding parameters 
+$A_V$ and 
+$E(B-V)$, the linear dust model 
+alternatively
+could be written in terms of any two other basis vectors  $\vec{a}+\kappa_1 \vec{b}$
+and $\kappa_2 \vec{a} + \vec{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
+In this basis, the model is then
+\begin{equation}
+A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
+\label{newdust:eqn}
+\end{equation}
+with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  equal to  linear combinations of the original parameters.
+Comparing this equation with  Eq.~\ref{trans_I:eqn}, we see that $\kappa_1=M[1,2]/M[1,1]$, $\kappa_2=M[2,1]/M[2,2]$.
+
+Our posterior
+includes a prior in which the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
+The parameters $\kappa_1$ and $\kappa_2$ are set by this prior.
+If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
+to    $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ being uncorrelated in the supernova sample.
+A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
+All color changes would then be confined to the $a(X)+\kappa_1 b(X)$ direction.
+This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
+We use this interpretation to assign  $\langle R^F_{\mathit{eff}}\rangle = \kappa_1^{-1}$ as
+the
+ensemble mean
+effective total-to-selective extinction of our sample.
+With our posterior we
+get $\kappa^{-1}_1=2.18^{+0.14}_{-0.16}$.
+Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.18$.
+
+We now consider the direction of $\vec{\gamma}^1$. 
+Different supernovae are expected to encounter dust with different $R^F$;
+having  associated $\vec{\gamma}^0$ with
+the extinction from a single effective
+$\langle R^F_{\mathit{eff}}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
+away from that effective value.
+Let us introduce a new parameter for each supernova, $\delta R$, such that 
+$A^F =\langle R^F_{\mathit{eff}}\rangle(1-  \delta R) E^F(B-V)$.
+Variations in the value of  $\delta R$, with the prior of the non-correlation between 
+the coefficients in Eq.~\ref{newdust:eqn},
+lead 
+to 
+\begin{equation}
+\kappa_2 =\langle R^F_{\mathit{eff}}\rangle \left(1- \frac{\mbox{Var}(\delta R \times E^F(B-V))}{\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))}\right).
+\end{equation}
+From the matrix elements of Eq.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
+This result indicates that there is a small but significant covariance between  extinction contributions due to
+fractional deviations from an effective $R^F$ and
+the color-excess parameter $E^F(B-V)$.
+Figure~\ref{k0_med:fig} shows the histogram of per-supernova
+median values
+from Monte Carlo chains
+and  stack of the posteriors of all supernovae  of $\gamma^1_{\hat{V}} k_1$
+relative to that of an arbitrary supernova  $\gamma^1_{\hat{V}} k_1|_0$.
+
+Analysis of this model produces $\gamma$ vectors that can be
+transformed to the Fitzpatrick dust-extinction model with a corresponding $2.02 <R< 2.32$ 68\%-ile credible interval.
+
+Suppose supernova color are determined by more than two parameters.  For example, supernovae have some intrinsic color dispersion
+in addition to being obscured by two-parameter dust.  A feature of this model is that the two color vectors $\gamma$ try to capture all these effects.
+
+\section{Model~II: Extrinsic--Intrinsic Colors}
+\label{modelII:sec}
+Model~II introduces an intrinsic color dispersion described by a 1-dimensional Normal distribution.  The supernova population
+is described by an eigenvector $\vec{\phi}$ and the color offset of each supernova is parameterized by
+\begin{equation}
+p \sim \mathcal{N}(0, \sigma_p).
+\end{equation}
+The model reads
+\begin{equation}
+\begin{pmatrix}
+{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
+\end{pmatrix}
+=
+\Delta +
+\begin{pmatrix}
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} + \phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  + \phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} + \phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} + \phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+ \phi_{\hat{I}}  p
+\end{pmatrix},
+\label{ewsiv:eqn}
+\end{equation}
+\begin{equation}
+\begin{pmatrix}
+{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
+\end{pmatrix}
+\sim \mathcal{N}
+\left(
+\begin{pmatrix}
+{\hat{U}} +\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\
+{\hat{V}}+\gamma^0_{{\hat{V}}} k_0+\gamma^1_{{\hat{V}}} k_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} k_0 + \gamma^1_{{\hat{R}}} k_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} k_0+\gamma^1_{{\hat{I}}} k_1\\
+EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
+\end{pmatrix}
+,C
+\right).
+\label{dust:eqn}
+\end{equation}
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
+$\alpha_X$
+& $0.0048^{+0.0010}_{-0.0012}$
+& $0.0019^{+0.0009}_{-0.0010}$
+& $0.0018^{+0.0007}_{-0.0008}$
+& $0.0017^{+0.0006}_{-0.0006}$
+& $0.0027^{+0.0005}_{-0.0005}$
+\\
+${\alpha_X/\alpha_V-1}$
+& $   1.7^{+   1.0}_{  -0.4}$
+& $   0.1^{+   0.1}_{  -0.1}$
+& $   0.0^{+   0.0}_{   0.0}$
+& $  -0.0^{+   0.1}_{  -0.1}$
+& $   0.5^{+   0.7}_{  -0.3}$
+\\
+$\beta_X$
+& $ 0.040^{+ 0.003}_{-0.003}$
+& $ 0.031^{+ 0.002}_{-0.002}$
+& $ 0.033^{+ 0.002}_{-0.002}$
+& $ 0.027^{+ 0.002}_{-0.002}$
+& $ 0.027^{+ 0.002}_{-0.002}$
+\\
+${\beta_X/\beta_V-1}$
+& $  0.23^{+  0.04}_{ -0.04}$
+& $ -0.04^{+  0.02}_{ -0.02}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.16^{+  0.01}_{ -0.01}$
+& $ -0.18^{+  0.03}_{ -0.03}$
+\\
+$\eta_X$
+& $0.0020^{+0.0010}_{-0.0009}$
+& $0.0022^{+0.0009}_{-0.0008}$
+& $0.0031^{+0.0008}_{-0.0008}$
+& $0.0031^{+0.0007}_{-0.0007}$
+& $0.0025^{+0.0007}_{-0.0007}$
+\\
+${\eta_X/\eta_V-1}$
+& $ -0.35^{+  0.17}_{ -0.22}$
+& $ -0.29^{+  0.10}_{ -0.14}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $  0.01^{+  0.06}_{ -0.04}$
+& $ -0.19^{+  0.10}_{ -0.09}$
+\\
+$\gamma^0_X$
+& $ 71.32^{+  3.40}_{ -3.24}$
+& $ 58.31^{+  3.03}_{ -2.93}$
+& $ 43.90^{+  2.76}_{ -2.73}$
+& $ 33.23^{+  2.40}_{ -2.43}$
+& $ 24.74^{+  2.42}_{ -2.52}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
+& $  0.62^{+  0.06}_{ -0.05}$
+& $  0.33^{+  0.03}_{ -0.03}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.24^{+  0.01}_{ -0.01}$
+& $ -0.44^{+  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+& $ -0.29^{+  5.63}_{ -5.29}$
+& $ -7.82^{+  4.70}_{ -4.52}$
+& $-14.71^{+  3.79}_{ -3.78}$
+& $-12.48^{+  3.21}_{ -3.23}$
+& $-15.79^{+  2.98}_{ -2.99}$
+\\
+${\gamma^1_X/\gamma^1_V-1}$
+& $ -0.98^{+  0.29}_{ -0.50}$
+& $ -0.47^{+  0.15}_{ -0.25}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.15^{+  0.04}_{ -0.04}$
+& $  0.07^{+  0.18}_{ -0.12}$
+\\
+$\sigma_p \phi_X$
+& $ 0.010^{+ 0.009}_{-0.009}$
+& $-0.021^{+ 0.007}_{-0.007}$
+& $-0.021^{+ 0.006}_{-0.007}$
+& $-0.008^{+ 0.006}_{-0.006}$
+& $ 0.036^{+ 0.007}_{-0.007}$
+\\
+\hline
+\end{tabular}
+\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~II in \S\ref{modelII:sec}.\label{global2:tab}}
+\end{table}
+
+Analysis of this model produces $\gamma$ vectors that can be
+transformed to the Fitzpatrick dust-extinction model with a corresponding $2.34 <R< 2.73$ 68\% credible interval.
+
+The posterior for $\sigma_p \vec{\phi}$ is shown in Figure~\ref{M1ev:fig}.  It is inconsistent with zero.  
+The 68\% credible interval for $\sigma_p$ is $0.051^{+0.005}_{-0.004}$~mag, highly incompatible with zero, The median values
+for each element are $(0.010, -0.021, -0.021, -0.008, 0.036)$.  The direction of $\phi$ is not aligned with the plane defined by
+the $\gamma$ vectors; the 68\% credible interval for the  quadratic fraction of
+$\phi$ in the $\gamma_0$--$\gamma_1$ plane is $0.088^{+0.118}_{-0.063}$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{../output_fix3/sigev.pdf} 
+            \caption{Model~II posterior  contours for $\sigma_p \vec{\phi}$.           \label{M1ev:fig}}
+\end{figure}
+
+For supernovae with host-properties from Childress, we plot $p$ as a function of host-galaxy mass.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.5in]{../output_fix3/childress.pdf} 
+   \caption{Intrinsic parameter
+ $p$ as a function of host-galaxy mass
+    \label{childress:fig}}
+\end{figure}
+
+\section{Model I and Model II Comparison}
+Model~II introduces a degree of freedom that is associated with a Normal distribution.
+It is thus interesting to compare the distributions of the $k_0$ and $k_1$ parameters of Model~I and Model~II,
+which are shown in Figure~\ref{kcomp:fig}.  The apparent difference between Model~I and II is in the $\gamma^1k_1$ term,
+where it seems that a Normal distribution component in Model~I is no longer in Model~II but is  assigned to the $\sigma_P \vec{\phi}$.
+This results in a change in the direction of the fit $\gamma^1$ and shifts the inferred Fitzpatrick $R$ to higher values.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.6in]{../output_fix1/deltagamma0_med.pdf} 
+   \includegraphics[width=2.6in]{../output_fix1/deltagamma1_med.pdf} 
+   \includegraphics[width=2.6in]{../output_fix3/deltagamma0_med.pdf} 
+   \includegraphics[width=2.6in]{../output_fix3/deltagamma1_med.pdf} 
+   \caption{
+   Left:
+   Normalized stack of the posteriors of all supernovae  and histogram 
+      of  per-supernova 
+median values of $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$.  Right:  The same plots for $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
+Top: Model~I. Bottom: Model~II.
+    \label{kcomp:fig}}
+\end{figure}
+
+XXXXXX
+
 \section{Supernova Model I: Two Extrinsic Parameters}
@@
 \label{modelmodel:sec}
-We assume 
-that  peak intrinsic ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
-on its
- equivalent widths of the Ca~II H\&K and Si~II~$\lambda$4141 spectral features
-$EW_{Ca}$ and $EW_{Si}$,
-and the wavelength of the minimum of 
-the Si~II~$\lambda6355$ feature $\lambda_{Si}$
-around $B$-band peak brightness:
-these spectral features are associated with SN~Ia  spectroscopic diversity  
-\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
-The explicit omission of light-curve shape in our model is compensated by its proxy,
-$EW_{Si}$, at peak brightness
-\citep{2008A&A...492..535A, 2011A&A...529L...4C}. On top of these feature-dependent magnitudes, intrinsic dispersion
-gives each supernova a magnitude contribution drawn from a Normal distribution with a parameterized covariance matrix
-$C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
-to capture 
-potential
-band-independent intrinsic dispersion, while also absorbing peculiar-velocity errors introduced when converting
-fluxes to luminosities.
-The apparent magnitudes are the sum of the intrinsic magnitudes plus additional terms that are linearly dependent on the
-per-supernova
-extrinsic-color parameters $k_0$ and $k_1$.  
-Unlike the parameters associated with
-the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent,
-dimensionless
-parameters $k_0$ and $k_1$ are not directly associated
-with observables but rather are inferred as part of the analysis.
-The observables
-$\hat{U}_o, {\hat{B}}_o, {\hat{V}}_o, {\hat{R}}_o, {\hat{I}}_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
-have Gaussian measurement uncertainty with covariance $C$.
-The
-likelihood density for the described model
-is
 \begin{equation}
@@
 \end{equation}
-The global parameter vectors that describe the SN~Ia population
-$\vec{c}$ (where $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $),
-$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept
-with units of mag) and slopes (with units mag~\AA$^{-1}$)
-of the linear relationships that
-relate spectral-feature parameters with intrinsic magnitudes.
-The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes (with units of mag) that relate 
-the latent extrinsic-color parameters with apparent magnitudes.
-These global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
-the combination of all components are written as a vector, e.g.\ $\vec{c}$.  This distinguishes
-notationally global versus per-supernova parameters.
-
-The model as written has degeneracies that need to be constrained in order for fits to converge.
-The model does not specify the absolute magnitude nor the intrinsic color of a supernova that has no extrinsic color contribution;
-in their place the zeropoints of the per-supernova magnitude and color parameters are set to the sample means
-\begin{equation}
-\langle \Delta \rangle=0,\ \langle k_0 \rangle=0,\ \langle k_1 \rangle=0.
-\end{equation}
-The model contains the product of latent parameters
-$\vec{\gamma} k$, which leads to the degeneracy $\vec{\gamma} \rightarrow a\vec{\gamma}$, $k \rightarrow a^{-1} k$.
-To aid in the convergence of $\vec{\gamma}$ and $k$ we impose a prior on the rms of $k$, though
-our physical interpretations are ultimately independent of this scaling.
-This prior does not specify the sign of $a$, which leaves a parity degeneracy.  As will be seen, the signal-to-noise in $\vec{\gamma}$ is sufficiently
-high that our finite MCMC chains do not migrate between the degenerate solutions; to simplify the merging of multiple chains
-we impose one of the degenerate solutions
-\begin{equation}
-\gamma^0_{\hat{U}} > 0,\ \gamma^1_{\hat{U}} < 0.
-\end{equation}
-As  in mixture models, the combinations $\vec{\gamma}^0 k_0$ and $\vec{\gamma}^1 k_1$ terms are degenerate under exchange of the 0 and 1 indices. For a cleaner presentation of our results, 
-we break that degeneracy  by setting consistent initial conditions that succeed in keeping indices consistent over all analysis chains.
-
-Another form of degeneracy is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
- $\vec{\gamma}^0 \rightarrow \vec{\gamma}^0  + \epsilon_{\gamma^0}$, $\vec{\gamma}^1 \rightarrow \vec{\gamma}^1 + \epsilon_{\gamma^1}$
- under the condition
-$$
-\epsilon_\Delta  +  \epsilon_{\gamma^0} k_0+  \epsilon_{\gamma^1} k_1=0,
-$$
-i.e.\ shifts in the global coefficients $\vec{\gamma}$ can be compensated by shifts in 
-$\Delta$
-for each supernova while maintaining 
-$\langle \Delta \rangle=0$.
-Another degeneracy is illustrated by $k_0 \rightarrow k_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
-$\vec{\alpha} \rightarrow \vec{\alpha} - \vec{\gamma} \epsilon$, $\vec{c} \rightarrow \vec{c} + \langle EW_{Ca}\rangle \epsilon$, i.e. the
-linear external terms can leak into the linear spectral feature corrections.
-These degeneracies are not broken within the model, but rather are constrained by the priors in which the
-per-supernova parameters
-$\Delta$, $EW$, $\lambda$, $k_0$, and $k_1$ are uncorrelated.
-
-The parameterized intrinsic dispersion, $C_c$,  introduces degeneracy in the model, as magnitude and color variation
-ascribed to $\Delta$, $\vec{\gamma}^0 k_0$, and $\vec{\gamma}^1 k_1$ can  be attributed to intrinsic dispersion
-and vice versa.
-In the case where there is independent intrinsic dispersion in all 5 bands, i.e.\  the input $C_c$ has rank-5, there exists degenerate solutions with a $C_c$ of rank 2.
-Those identical predictions generally do not yield the same likelihood, as the determinant of $C_c$ varies over those solutions.
-In a maximum-likelihood analysis the rank-2 is preferred over the rank-5 solution, resulting in some intrinsic dispersion getting attributed to $\Delta$, $k_0$, and $k_1$.
-In our Bayesian analysis the priors, though not totally disallowing rank-2 $C_c$, favor rank-5  and prevent convergence to this solution.    
-Leakage from per-supernova intrinsic color parameters to intrinsic dispersion could bias the intrinsic color vectors of the SN Ia family,  or conversely, intrinsic dispersion could be spuriously attributed to an intrinsic color.
-We examine this effect in the discussion of the results in \S\ref{degenerate:sec}.
-
-%
-%There are several features of the model
-%that drive the assignation of variations away from $C_c$:  Maximizing the posterior disfavors the increase of $\det{(C_c)}$
-%\color{red}
-%and hence favors solutions of $\gamma$'s that minimize the residual dispersion described by $C_c$;
-%\color{black}
-%The distributions of $\Delta$, $k_0$, and $k_1$ turn out to
-%be non-Gaussian, and so are not well described by the Normal covariance we impose in $C_c$; the grey magnitude offsets, $\Delta$, would appear as a constant
-%in all elements of the covariance matrix, which is disfavored for the Bayesian prior selected for $C_c$.
-
-In our Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
-for the covariance matrix $C_c$.
-This matrix is parameterized in two parts: by the Choleksy factor of its
-correlation matrix with a $\eta=4$  LKJ prior
-\citep{Lewandowski20091989}; its standard
-deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
- $0.1$ and scale $0.1$ mag restricted to positive values.
-This covariance matrix prior is recommended by STAN \citep{stan}, the Monte Carlo program we use to evaluate the model.
-\color{blue}
-Further properties of the this prior are presented in \S\ref{priorappendix:sec}.
-\color{black}
-
-No informative prior is used for each of the per-supernova parameters $\Delta$, $EW$, $\lambda$, $k_0$, and $k_1$:
-they are taken to be drawn independently from a flat distribution. 
-As a consequence, the prior has uncorrelated parameters as mentioned above.
-
-For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $2(N-2)$
-color parameters, $(N-1)$ magnitude offsets,  $5 \times 6$ global coefficients, and $10$ parameters that describe the intrinsic
-$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1067 top-level independent parameters.
 
@@
 \label{results:sec}
-The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo with a No-U-Turn
-Sampler as implemented in
-STAN \citep{stan}.  We run eight chains, each with 5000 iterations of which
-half are used for warmup.
 Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig}.
@@
 
-Tests have revealed no evidence for the non-convergence of the MCMC run.
-STAN provides output statistics to assess
-the convergence of the output Markov chains.
-The 
-potential scale reduction statistic, $\hat{R}$
-(in this paragraph not to be confused with the synthetic $R$ magnitude)
-\citep{Gelman92}, measures the convergence of the target distribution
-in iterative simulations 
-by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
-$N_{\mathit{eff}}$ is an estimate of the number of independent draws.
-The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.
-The
-output also gives  $N_{\mathit{eff}} \gg 100$ for all parameters, indicating that all are densely sampled.
 Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig} -- \ref{global5:fig}.  In these tests there is no evidence that
@@
 the former.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.95in]{plane0.pdf}
-   \includegraphics[width=2.95in]{plane1.pdf}
-   \caption{
-   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
-   magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
-   two different perspectives.
-   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes
-   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
-   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
-   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes are confined to the plane that contains both.
-   The perspective on the right visually shows that all four vectors are nearly coplanar.  
-   The combination $\vec{a}+\vec{b}/2.44$ is shown in the dotted red
-   line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
-   \label{plane:fig}}
-\end{figure}
+%
+%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+%   \centering
+%   \includegraphics[width=2.95in]{plane0.pdf}
+%   \includegraphics[width=2.95in]{plane1.pdf}
+%   \caption{
+%   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
+%   magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
+%   two different perspectives.
+%   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes
+%   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
+%   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
+%   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes are confined to the plane that contains both.
+%   The perspective on the right visually shows that all four vectors are nearly coplanar.  
+%   The combination $\vec{a}+\vec{b}/2.44$ is shown in the dotted red
+%   line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
+%   \label{plane:fig}}
+%\end{figure}
+%
 
@@
 
-\subsection{Per-Supernova Parameter -- Covariance Matrix Degeneracy}
+\subsection{Per-Supernova Parameter -- Intrinsic Covariance Matrix Degeneracy}
 \label{degenerate:sec}
@@
 In the posterior, the degeneracy is broken by the determinant of the covariance matrix in the likelihood and by the priors.
-Given that the priors we use are not exactly correct,
-the parameters are susceptible to the misassignment, in either direction, between intrinsic color, $\Delta$, $k$, and $D$, and intrinsic dispersion $C_c$.
-\S\ref{priorappendix:sec}
+The posterior is thus sensitive to the prior, which being most likely biased at some level, means that the
+intrinsic color parameters, $\Delta$, $k$, and $D$, and intrinsic dispersion $C_c$ are susceptible to the misassignment between each other.
+The total variance and the allocation of that variance between the eigenvectors of $C_c$ in particular influence the location of the posterior
+maximum, and their distributions are shown in 
+\S\ref{priorappendix:sec}.  Given our particular interest in the new color term, in this Subsection we consider the possibility that
+$\delta$ is an artifact of leakage from intrinsic covariance.
+
+In our model, some intrinsic dispersion could be attributed to  $\delta$.  If this were the case, one would expect for the dominant eigenvector
+of $C_c$ to be aligned with $\delta$, as the corresponding eigenvalue decreases in exchange for the
+artificial creation of $D$.  No such alignment is seen: the median dot products between unit $\delta$ and the ordered five $C_c$ eigenvectors
+are 0.48, 0.53,
+0.34,
+0.24,
+0.31.
+
+The other possibility is for $\gamma^0$ and $\gamma^1$ to leak into $\delta$.  In Model~I, an estimate of leakage from
+$\gamma$  into intrinsic covariance is $0.00091_{- 0.00018}^ {+ 0.00023}$~mag$^2$,
+the variance in the  three  eigenvectors otherwise unconstrained in the model.    (The cumulative variances in successive
+eigenvectors are shown in Figure~\ref{ccvar:fig}.)
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+%   \includegraphics[width=2.8in]{ccnvar.pdf}
+   \includegraphics[width=5in]{ccvar.pdf}
+      \caption{Left: Right: \label{ccvar:fig}
+      }
+\end{figure}
+
+The change in the variance captured the intrinsic dispersions of Model~I and II is 0.002 mag$^2$,
+as shown in Figure~\ref{ccvar:fig}.  This bounds the amount of leakage
+
+The nature of the degeneracy is that each intrinsic SN parameter can be exchanged with one dimension of the intrinsic covariance
+matrix; given that
+Model~I  has three intrinsic vectors $\Delta$, $\gamma^0$, and $\gamma^1$,
 
@@
 \color{black}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{ccnvar.pdf}
-   \includegraphics[width=2.8in]{ccvar.pdf}
-      \caption{Left: Right: 
-      }
-\end{figure}
 
@@
    \includegraphics[width=5.2in]{residualx1.pdf}
-    \caption{Differences between observed colors and the     \color{red}
-    expected \color{black} colors
+    \caption{Differences between observed colors and the 
+    expected colors
      from the analysis, as a function
@@
 \appendix
-\section{Intrinsic Covariance Matrix Prior}
-\label{priorappendix:sec}
-\color{blue}
-The covariance matrix $C_c$
-is parameterized in two parts.
-The variance for each of the 5 bands comes from a  truncated $\text{Cauchy}(0.1,0.1)$ distribution
-restricted to positive values.
-The correlation matrix of $C_c$ is
-drawn from an LKJ prior \citep{Lewandowski20091989}
-that has the property
-\begin{equation}
-p(\text{corr}(C_c)| \eta) \propto \text{det}(\text{corr}(C_c))^{\eta-1}.
-\end{equation}
-For $\eta <1$, smaller determinants (stronger correlations)  are likely, for $\eta>1$ larger determinants (weaker correlations)
-are likely, 
-and $\eta=1$ the density is uniform.  For $\eta=\infty$ the prior is of a diagonal  matrix with no correlation.
-We choose $\eta=4$ for our prior.
-
-The distribution of determinants from which the covariance matrices are drawn is visualized in the left plot of Figure~\ref{priordet:fig},
-which shows
-histograms of $\ln{(\text{det}(C_c))}$  realizations for different $\eta$ priors.
-The distribution has a steep drop that counteracts the log-likelihood's linear increase with decreasing
-log-determinant.  There is little qualitative difference in the distributions from $\eta$'s ranging from 0.5 to 20.
-The diagonal prior  produces significantly higher determinants.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{priordet.pdf}
-   \includegraphics[width=2.8in]{prior.pdf}
-         \caption{Left: Histograms of $\ln{(\text{det}(C_c))}$ from realizations for different $\eta$ priors.
-         Right: Histograms of the normalized variance captured by the leading $n$ eigenvectors for $\eta=0.5$, 20,
-         and a diagonal prior.
-   \label{priordet:fig}}
-\end{figure}
-
-The distribution of the variance among the matrix eigenvectors is visualized in  right plot of Figure~\ref{priordet:fig},
-which shows histograms
-of the normalized variance captured by the leading $n$ eigenvectors for different $\eta$ priors.
-The variance is  broadly distributed in the diagonal case, whereas for finite $\eta$ variance is concentrated
-in fewer eigenvectors. As with the
-determinants, there is little qualitative difference in the distributions from $\eta$'s ranging from 0.5 to 20.
-
-\color{black}
+
 \section{Testing for Parameter Bias Through Simultations}
@@
    \includegraphics[width=5.2in]{simdelta_corner.pdf} 
-            \caption{Stacked $\vec{\delta}$ posterior contours for \color{red} 100 \color{black} independent simulated data sets.
+            \caption{Stacked $\vec{\delta}$ posterior contours for 100  independent simulated data sets.
             The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \includegraphics[width=5.2in]{simcoeff0.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of \color{red} 100 \color{black} independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of  100 independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \includegraphics[width=5.2in]{simcoeff1.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of \color{red} 100 \color{black} independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of  100 independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
    \includegraphics[width=5.2in]{simcoeff2.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of \color{red} 100 \color{black} independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of  100 independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
       \includegraphics[width=5.2in]{simcoeff3.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of \color{red} 100 \color{black} independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of  100  independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
@@
          \includegraphics[width=5.2in]{simcoeff4.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\alpha$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of \color{red} 100 \color{black} independent simulated data sets.
+            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\alpha$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of  100 independent simulated data sets.
 The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.

### 2017-11-17 childressf3.py

@@ -1,0 +1,181 @@
+#!/usr/bin/env python
+import numpy
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import rc
+import pickle
+import cPickle
+import scipy.stats
+import matplotlib as mpl
+
+mpl.rcParams['font.size'] = 18
+
+
+f = open('MJC_compile_SNdata.pkl','r')
+gal= pickle.load(f)
+
+f = open('fix3.pkl','rb')
+(fit, _) = pickle.load(f)
+f.close()
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+dic_phreno=cPickle.load(open("phrenology_2016_12_01_CABALLOv1.pkl"))
+
+dic_meta=cPickle.load(open("META.pkl"))
+
+sivel=[]
+sivel_err=[]
+for sn in data['snlist']:
+   if sn in dic_meta.keys() and sn in dic_phreno.keys():
+      meta = dic_meta[sn]
+      vSiII_6355_lbd=0.
+      vSiII_6355_lbd_err=0.
+      counter  = 0
+      for sp in dic_phreno[sn]["spectra"]:
+         if sp in meta['spectra'].keys() and  numpy.abs(meta['spectra'][sp]['salt2.phase']) < 2.5  and numpy.isfinite(dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]):
+            vSiII_6355_lbd += dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
+            vSiII_6355_lbd_err += 1/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
+            counter +=1
+      if counter !=0:
+         sivel.append(vSiII_6355_lbd / vSiII_6355_lbd_err)
+         sivel_err.append(1./numpy.sqrt(vSiII_6355_lbd_err))
+      else:
+         sivel.append(float('nan'))
+         sivel_err.append(float('nan'))
+   else:
[…]

### 2017-11-17 fitzf2.py

@@ -1,0 +1,389 @@
+#!/usr/bin/env python
+import pickle
+import numpy
+import sncosmo
+import scipy
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.pyplot as plt
+import f99_band
+import emcee
+import matplotlib as mpl
+from matplotlib.patches import FancyArrowPatch
+from mpl_toolkits.mplot3d import proj3d
+
+class Arrow3D(FancyArrowPatch):
+    def __init__(self, xs, ys, zs, *args, **kwargs):
+        FancyArrowPatch.__init__(self, (0,0), (0,0), *args, **kwargs)
+        self._verts3d = xs, ys, zs
+
+    def draw(self, renderer):
+        xs3d, ys3d, zs3d = self._verts3d
+        xs, ys, zs = proj3d.proj_transform(xs3d, ys3d, zs3d, renderer.M)
+        self.set_positions((xs[0],ys[0]),(xs[1],ys[1]))
+        FancyArrowPatch.draw(self, renderer)
+
+
+mpl.rcParams['font.size'] = 14
+
+# Get the data
+f = open('fix2.pkl','rb')
+(fit, _) = pickle.load(f)
+f.close()
+
+# Determine the plane approximaion for Fitzpatrick
+
+# Partial derivatives with respect to av and ebv
+av=0.1
+ebv=av/2.5
+A1= f99_band.A_X(r_v=av/ebv, ebv=ebv)
+
+# pkl_file = open('fitz.pkl', 'r')
+# a=pickle.load(pkl_file)
+# pkl_file.close()
+
+# AX = a[0]* av + a[1] * av**2 \
+#   + a[2]* ebv+ a[3] * ebv**2 \
+#   + a[4] * av* ebv \
+#   + a[5]* av**3 \
+#   + a[6] * ebv**3 \
+#   + a[7] * (av**2) * ebv \
+#   + a[8] * av * (ebv**2)
+
+# plt.plot(A1-AX)
+
+# plt.show()
+
+# wefe
+A2= f99_band.A_X(r_v=(av+0.01)/ebv, ebv=ebv)
[…]

### 2017-11-17 fitzf3.py

@@ -1,0 +1,564 @@
+#!/usr/bin/env python
+import pickle
+import numpy
+import sncosmo
+import scipy
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.pyplot as plt
+import f99_band
+import emcee
+import matplotlib as mpl
+
+from matplotlib.patches import FancyArrowPatch
+from mpl_toolkits.mplot3d import proj3d
+
+class Arrow3D(FancyArrowPatch):
+    def __init__(self, xs, ys, zs, *args, **kwargs):
+        FancyArrowPatch.__init__(self, (0,0), (0,0), *args, **kwargs)
+        self._verts3d = xs, ys, zs
+
+    def draw(self, renderer):
+        xs3d, ys3d, zs3d = self._verts3d
+        xs, ys, zs = proj3d.proj_transform(xs3d, ys3d, zs3d, renderer.M)
+        self.set_positions((xs[0],ys[0]),(xs[1],ys[1]))
+        FancyArrowPatch.draw(self, renderer)
+
+mpl.rcParams['font.size'] = 14
+
+# Get the data
+f = open('fix3.pkl','rb')
+(fit, _) = pickle.load(f)
+f.close()
+
+# Determine the plane approximaion for Fitzpatrick
+
+# Partial derivatives with respect to av and ebv
+av=0.1
+ebv=0.1/2.5
+A1= f99_band.A_X(r_v=av/ebv, ebv=ebv)
+
+# pkl_file = open('fitz.pkl', 'r')
+# a=pickle.load(pkl_file)
+# pkl_file.close()
+
+# AX = a[0]* av + a[1] * av**2 \
+#   + a[2]* ebv+ a[3] * ebv**2 \
+#   + a[4] * av* ebv \
+#   + a[5]* av**3 \
+#   + a[6] * ebv**3 \
+#   + a[7] * (av**2) * ebv \
+#   + a[8] * av * (ebv**2)
+
+# plt.plot(A1-AX)
+
+# plt.show()
+
+# wefe
[…]

### 2017-11-17 runfix1.py

@@ -1,0 +1,93 @@
+#!/usr/bin/env python
+
+import pickle
+import cPickle
+import numpy
+import pystan
+import sivel
+
+# two color parameter model
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
+sivel, sivel_err, _, _, _, _, _ = sivel.sivel(data)
+
+use = numpy.isfinite(sivel)
+
+#  The ordering is 'Ca','Si','U','B','V','R','I'
+
+EW_obs = data['obs'][:,0:2]
+mag_obs = data['obs'][:,2:]
+EW_cov = data['cov'][:,0:2,0:2]
+mag_cov = data['cov'][:,2:,2:]
+
+sivel=sivel[use]
+sivel_err = sivel_err[use]
+EW_obs=EW_obs[use]
+mag_obs=mag_obs[use]
+EW_cov= EW_cov[use]
+mag_cov=mag_cov[use]
+
+nsne, nmags = mag_obs.shape
+
+# # renormalize the data
+EW_mn = EW_obs.mean(axis=0)
+EW_renorm = (EW_obs - EW_mn)
+
+mag_mn = mag_obs.mean(axis=0)
+mag_renorm  = mag_obs-mag_mn
+
+sivel_mn = sivel.mean()
+sivel_renorm = sivel-sivel_mn
+data = {'D': nsne, 'N_mags': 5, 'N_EWs': 2, 'mag_obs': mag_renorm, 'EW_obs': EW_renorm, 'EW_cov': EW_cov, 'mag_cov':mag_cov, \
+   'sivel_obs': sivel_renorm, 'sivel_err': sivel_err}
+
+# pystan.misc.stan_rdump(data, 'data.R')
+# wefew
+
+Delta_simplex = numpy.zeros(nsne-1)
+# Delta_simplex = numpy.zeros(nsne)+1./nsne
+# k_simplex = numpy.zeros(nsne)
+R_simplex = ((-1.)**numpy.arange(nsne)*.25 + .5)*2./nsne
+R_simplex = R_simplex/R_simplex.sum()
+
+init = [{'EW' : EW_renorm, \
+         'sivel': sivel_renorm,\
+         'c_raw' : numpy.zeros(5), \
+         'alpha_raw' : numpy.zeros(5), \
+         'beta_raw' : numpy.zeros(5), \
[…]

### 2017-11-17 runfix2.py

@@ -1,0 +1,183 @@
+#!/usr/bin/env python
+
+import pickle
+import cPickle
+import numpy
+import pystan
+import sivel
+import matplotlib.pyplot as plt
+import corner
+
+# provide stan 3 eigenvectors with respect to try to align delta vector
+f = open('fix1.pkl','rb')
+(fit,_) = pickle.load(f)
+
+gamma0 = numpy.median(fit['gamma'],axis=0)
+gamma1 = numpy.median(fit['rho1'],axis=0)
+gamma0_cov = numpy.cov(fit['gamma'],rowvar=False)
+gamma1_cov = numpy.cov(fit['rho1'],rowvar=False)
+
+
+_, gamma0_ev = numpy.linalg.eigh(gamma0_cov)
+
+# print gamma0_ev[:,0]
+
+gamma0_eval = numpy.array(fit['gamma'])
+for i in xrange(gamma0_eval.shape[0]):
+   for j in xrange(5):
+      gamma0_eval[i,j]=numpy.dot(fit['gamma'][i,:], gamma0_ev[:,j])
+
+gamma0_min = numpy.min(gamma0_eval,axis=0)-0.05
+gamma0_max = numpy.max(gamma0_eval,axis=0)+0.05
+
+# for i in xrange(5):
+#    plt.hist(gamma0_eval[:,i])
+#    plt.show()
+
+_, gamma1_ev = numpy.linalg.eigh(gamma1_cov)
+
+gamma1_eval = numpy.array(fit['rho1'])
+for i in xrange(gamma1_eval.shape[0]):
+   for j in xrange(5):
+      gamma1_eval[i,j]=numpy.dot(fit['rho1'][i,:], gamma1_ev[:,j])
+
+gamma1_min = numpy.min(gamma1_eval,axis=0)-0.05
+gamma1_max = numpy.max(gamma1_eval,axis=0)+0.05
+
+
+gamma0median = numpy.median(gamma0_eval,axis=0)
+gamma1median = numpy.median(gamma1_eval,axis=0)
+
+fit=None
+
+m = numpy.zeros((2,5))
+m[0]=gamma0
+m[1]=gamma1
+m=m.T
+
+q, r = numpy.linalg.qr(m,mode='complete')
+q=q.T
+
+# two color parameter model
+
+pkl_file = open('gege_data.pkl', 'r')
+data = pickle.load(pkl_file)
+pkl_file.close()
+
[…]

### 2017-11-17 tablef3.py

@@ -1,0 +1,272 @@
+#!/usr/bin/env python
+
+import pickle
+import cPickle
+import numpy
+import sivel
+import sncosmo
+import fitz_band
+
+f = open('fix3.pkl','rb')
+(fit, _) = pickle.load(f)
+f.close()
+
+for key in fit.keys():
+    print key, fit[key].min(), fit[key].max()
+
+#special variables
+
+# ev flipped
+fixev = fit['ev']
+fixev = fixev * numpy.sign(fixev[:,4])[:,None]
+
+
+print "projection of ev in gamma plane"
+proj = []
+for ev, evorig, g1, g2 in zip(fixev, fit['ev'], fit['gamma'], fit['rho1']):
+    y=numpy.array([numpy.dot(evorig,g1), numpy.dot(evorig,g2)])
+    M = numpy.array([[numpy.dot(g1,g1), numpy.dot(g1,g2)], \
+        [numpy.dot(g2,g1), numpy.dot(g2,g2)]])
+    com = numpy.dot(numpy.linalg.inv(M),y)
+    proj.append(numpy.linalg.norm(com[0]*g1+com[1]*g2)**2 / numpy.linalg.norm(evorig)**2)
+dum1, dumm, dump =  numpy.percentile(proj,(50,50-34,50+34),axis=0)
+print "${:.3f}^{{+{:.3f}}}_{{{:.3f}}}$".format(dum1,dump-dum1,dumm-dum1)
+
+print "ev_sig size"
+dum1, dumm, dump =  numpy.percentile(fit['ev_sig'],(50,50-34,50+34),axis=0)
+print "{:.3f}^{{+{:.3f}}}_{{{:.3f}}}".format(dum1,dump-dum1,dumm-dum1)
+
+print "the table"
+
+pars = ['alpha','alpha','beta','beta','eta','eta','gamma','gamma','rho1','rho1']
+pars_n = ['\\alpha_X','{\\alpha_X/\\alpha_V-1}','\\beta_X','{\\beta_X/\\beta_V-1}',\
+  '\\eta_X','{\\eta_X/\\eta_V-1}', '\\gamma^0_X', '{\\gamma^0_X/\gamma^0_V-1}', '\\gamma^1_X','{\\gamma^1_X/\\gamma^1_V-1}',\
+  '\\sigma_X']
+sigfig = [4,1,3,2,4,2,2,2,2,2,3]
[…]

### 2017-11-22 submit/fix.tex
more change

@@
 signatures of SN~Ia diversity.
+Avoid repetitiiveness.
 Conclusions are presented in \S\ref{conclusions:sec}.
@@
 The 
-spectroscopic-feature measurements 
+spectroscopic-feature measurements, SALT light-curve fit parameters including the shape  $x_1$,
 and uncertainties
@@
 \langle \Delta \rangle=0,\ \langle g_0 \rangle=0,\ \langle g_1 \rangle=0.
+\label{zero:eqn}
 \end{equation}
@@
 
+For $N$ supernovae there are $8N$ observables.  There are $3N$ spectral parameters, each of
+$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters
+(recall the constraint in Eq.~\ref{zero:eqn}),  and $5 \times 7$ global coefficients.
+For $N=172$ supernovae, there are 1376 observables and 1064  parameters.
+
 \subsection{Results: $\gamma^0$ and $\gamma^1$}
-In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
+\label{results1:sec}
+In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$
+(the 68\% credible intervals for all global parameters are given in \S\ref{m12results:sec}.)
 In our model, $g_0$ and $g_1$ are introduced as latent parameters that are related to linear shifts in band magnitudes through
@@
 \begin{equation}
-A_X = a(X)  A_{V} + b(X) E(B-V)
+A_X = a_X  A_{V} + b_X E(B-V)
 \label{f99:eqn}
@@
 Our model $\gamma$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
-dust-based $a(X)$ and $b(X)$ vectors plus residual vectors perpendicular to $\vec{a}$ and $\vec{b}$,
+dust-based $a_X$ and $b_X$ vectors plus residual vectors perpendicular to $\vec{a}$ and $\vec{b}$,
 \begin{equation}
@@
 The Model~I posterior gives a quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ projected onto the plane defined by
-$a(X)$ and $b(X)$, the quadratic fraction of $\vec{\gamma}^1$ projected
+$a_X$ and $b_X$, the quadratic fraction of $\vec{\gamma}^1$ projected
 onto the dust plane is
@@
    \caption{
-   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
+   Visualization of how supernova magnitudes can vary in Model~I and that of \citetalias{1999PASP..111...63F}.  While the models describe
    magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
@@
 \begin{equation}
-A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
+A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a_X+\kappa_1 b_X \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a_X + b_X)],
 \label{newdust:eqn}
@@
 Our posterior
-includes a prior in which the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
+includes a prior in which the per-supernova parameters $g_0$ and  $g_1$ associated with $\gamma$ are uncorrelated.
 The parameters $\kappa_1$ and $\kappa_2$ are set by this prior.
@@
 A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
-All color changes would then be confined to the $a(X)+\kappa_1 b(X)$ direction.
+All color changes would then be confined to the $a_X+\kappa_1 b_X$ direction.
 This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
@@
 With our posterior we
-get $\kappa^{-1}_1=2.18^{+0.14}_{-0.16}$.
+define an effective $R^F_{\mathit{eff}} \equiv \kappa^{-1}_1=2.18^{+0.14}_{-0.16}$.
 Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.18$.
 
-We now consider the direction of $\vec{\gamma}^1$. 
-Different supernovae are expected to encounter dust with different $R^F$;
-having  associated $\vec{\gamma}^0$ with
-the extinction from a single effective
-$\langle R^F_{\mathit{eff}}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
-away from that effective value.
-Let us introduce a new parameter for each supernova, $\delta R$, such that 
-$A^F =\langle R^F_{\mathit{eff}}\rangle(1-  \delta R) E^F(B-V)$.
-Variations in the value of  $\delta R$, with the prior of the non-correlation between 
-the coefficients in Eq.~\ref{newdust:eqn},
-lead 
-to 
-\begin{equation}
-\kappa_2 =\langle R^F_{\mathit{eff}}\rangle \left(1- \frac{\mbox{Var}(\delta R \times E^F(B-V))}{\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))}\right).
-\end{equation}
-From the matrix elements of Eq.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
-This result indicates that there is a small but significant covariance between  extinction contributions due to
-fractional deviations from an effective $R^F$ and
-the color-excess parameter $E^F(B-V)$.
-Figure~\ref{k0_med:fig} shows the histogram of per-supernova
-median values
-from Monte Carlo chains
-and  stack of the posteriors of all supernovae  of $\gamma^1_{\hat{V}} k_1$
-relative to that of an arbitrary supernova  $\gamma^1_{\hat{V}} k_1|_0$.
-
-Analysis of this model produces $\gamma$ vectors that can be
-transformed to the Fitzpatrick dust-extinction model with a corresponding $2.02 <R< 2.32$ 68\%-ile credible interval.
-
-Suppose supernova color are determined by more than two parameters.  For example, supernovae have some intrinsic color dispersion
-in addition to being obscured by two-parameter dust.  A feature of this model is that the two color vectors $\gamma$ try to capture all these effects.
+For $\vec{\gamma}^1$ we find  $\kappa^{-1}_2=0.03^{+0.04}_{-0.04}$, meaning that this vector's direction is consistent with being parallel to $a_X$
+(also seen visually in Figure~\ref{plane:fig}.)
+That is,   $\vec{\gamma}^1$  captures magnitude variations that occur given fixed $E^F(B-V)$.
+
+\subsection{Remarks}
+Model~I is not of primary interest in this article.  However, there are  points to highlight from its results.
+
+\begin{itemize}
+\item Our model introduces two latent supernova parameters that can influence supernova colors with ``non-informative'' priors.  Fitting
+of our model gives a space of possible color variations highly consistent with those expected from two-parameter dust-extinction models. 
+This lends confidence to our modelling and analysis.
+\item In Model~I, any  intrinsic color variation that remains after spectral corrections is allocated to two parameters.  Color variations beyond
+those from two-parameter dust extinction contribute to those two parameters.   The effective $R^F$ we derive from our results
+is susceptible to leakage from intrinsic colors not associated with dust.
+\end{itemize}
 
@@
 \label{modelII:sec}
-Model~II introduces an intrinsic color dispersion described by a 1-dimensional Normal distribution.  The supernova population
-is described by an eigenvector $\vec{\phi}$ and the color offset of each supernova is parameterized by
+Model~II extends Model~I to include a third intrinsic color parameter.  This increase in the number of degrees of freedom accommodates
+the optical depth of dust, one parameter to capture variation in dust properties, and
+intrinsic color variability unrelated to dust.  In this section we  focus on describing the consequences of adding the new parameter.
+
+\subsection{Model}
+\label{modelIImodel:sec}
+Model~II is the same as Model~I except for the 
+addition of an intrinsic color parameter $p$.  The distribution of this parameter over all supernovae is
+assumed to be drawn from a Normal distribtion
 \begin{equation}
@@
 \end{equation}
-The model reads
+The influence of $p$ on supernova colors is described by the global parameters $\vec{\phi}$ (constrained to be a
+unit vector)
+so that the color offset of each supernova is  $\vec{\phi}p$.
+Model~II reads as
 \begin{equation}
@@
 \end{pmatrix},
-\label{ewsiv:eqn}
+\label{ewsiv2:eqn}
 \end{equation}
@@
 \begin{pmatrix}
-{\hat{U}} +\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\
-{\hat{V}}+\gamma^0_{{\hat{V}}} k_0+\gamma^1_{{\hat{V}}} k_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} k_0 + \gamma^1_{{\hat{R}}} k_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} k_0+\gamma^1_{{\hat{I}}} k_1\\
+{\hat{U}} +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
+{\hat{V}}+\gamma^0_{{\hat{V}}} g_0+\gamma^1_{{\hat{V}}} g_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} g_0 + \gamma^1_{{\hat{R}}} g_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} g_0+\gamma^1_{{\hat{I}}} g_1\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
@@
 \right).
-\label{dust:eqn}
+\label{dust2:eqn}
 \end{equation}
 
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
-$\alpha_X$
-& $0.0048^{+0.0010}_{-0.0012}$
-& $0.0019^{+0.0009}_{-0.0010}$
-& $0.0018^{+0.0007}_{-0.0008}$
-& $0.0017^{+0.0006}_{-0.0006}$
-& $0.0027^{+0.0005}_{-0.0005}$
-\\
-${\alpha_X/\alpha_V-1}$
-& $   1.7^{+   1.0}_{  -0.4}$
-& $   0.1^{+   0.1}_{  -0.1}$
-& $   0.0^{+   0.0}_{   0.0}$
-& $  -0.0^{+   0.1}_{  -0.1}$
-& $   0.5^{+   0.7}_{  -0.3}$
-\\
-$\beta_X$
-& $ 0.040^{+ 0.003}_{-0.003}$
-& $ 0.031^{+ 0.002}_{-0.002}$
-& $ 0.033^{+ 0.002}_{-0.002}$
-& $ 0.027^{+ 0.002}_{-0.002}$
-& $ 0.027^{+ 0.002}_{-0.002}$
-\\
-${\beta_X/\beta_V-1}$
-& $  0.23^{+  0.04}_{ -0.04}$
-& $ -0.04^{+  0.02}_{ -0.02}$
-& $  0.00^{+  0.00}_{  0.00}$
-& $ -0.16^{+  0.01}_{ -0.01}$
-& $ -0.18^{+  0.03}_{ -0.03}$
-\\
-$\eta_X$
-& $0.0020^{+0.0010}_{-0.0009}$
-& $0.0022^{+0.0009}_{-0.0008}$
-& $0.0031^{+0.0008}_{-0.0008}$
-& $0.0031^{+0.0007}_{-0.0007}$
-& $0.0025^{+0.0007}_{-0.0007}$
-\\
-${\eta_X/\eta_V-1}$
-& $ -0.35^{+  0.17}_{ -0.22}$
-& $ -0.29^{+  0.10}_{ -0.14}$
-& $  0.00^{+  0.00}_{  0.00}$
-& $  0.01^{+  0.06}_{ -0.04}$
-& $ -0.19^{+  0.10}_{ -0.09}$
-\\
-$\gamma^0_X$
-& $ 71.32^{+  3.40}_{ -3.24}$
-& $ 58.31^{+  3.03}_{ -2.93}$
-& $ 43.90^{+  2.76}_{ -2.73}$
-& $ 33.23^{+  2.40}_{ -2.43}$
-& $ 24.74^{+  2.42}_{ -2.52}$
-\\
-${\gamma^0_X/\gamma^0_V-1}$
-& $  0.62^{+  0.06}_{ -0.05}$
-& $  0.33^{+  0.03}_{ -0.03}$
-& $  0.00^{+  0.00}_{  0.00}$
-& $ -0.24^{+  0.01}_{ -0.01}$
-& $ -0.44^{+  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-& $ -0.29^{+  5.63}_{ -5.29}$
-& $ -7.82^{+  4.70}_{ -4.52}$
-& $-14.71^{+  3.79}_{ -3.78}$
-& $-12.48^{+  3.21}_{ -3.23}$
-& $-15.79^{+  2.98}_{ -2.99}$
-\\
-${\gamma^1_X/\gamma^1_V-1}$
-& $ -0.98^{+  0.29}_{ -0.50}$
-& $ -0.47^{+  0.15}_{ -0.25}$
-& $  0.00^{+  0.00}_{  0.00}$
-& $ -0.15^{+  0.04}_{ -0.04}$
-& $  0.07^{+  0.18}_{ -0.12}$
-\\
-$\sigma_p \phi_X$
-& $ 0.010^{+ 0.009}_{-0.009}$
-& $-0.021^{+ 0.007}_{-0.007}$
-& $-0.021^{+ 0.006}_{-0.007}$
-& $-0.008^{+ 0.006}_{-0.006}$
-& $ 0.036^{+ 0.007}_{-0.007}$
-\\
-\hline
-\end{tabular}
-\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~II in \S\ref{modelII:sec}.\label{global2:tab}}
-\end{table}
-
-Analysis of this model produces $\gamma$ vectors that can be
-transformed to the Fitzpatrick dust-extinction model with a corresponding $2.34 <R< 2.73$ 68\% credible interval.
-
-The posterior for $\sigma_p \vec{\phi}$ is shown in Figure~\ref{M1ev:fig}.  It is inconsistent with zero.  
-The 68\% credible interval for $\sigma_p$ is $0.051^{+0.005}_{-0.004}$~mag, highly incompatible with zero, The median values
-for each element are $(0.010, -0.021, -0.021, -0.008, 0.036)$.  The direction of $\phi$ is not aligned with the plane defined by
-the $\gamma$ vectors; the 68\% credible interval for the  quadratic fraction of
-$\phi$ in the $\gamma_0$--$\gamma_1$ plane is $0.088^{+0.118}_{-0.063}$.
+The new term is placed in Eq.~\ref{ewsiv2:eqn} as an intrinsic supernova property.  It is mathematically equivalent to
+put the term in the mean of Eq.~\ref{dust2:eqn} joining what we call extrinsic parameters.  Although we 
+use ``intrinsic'' and ``extrinsic'' as descriptive labels for $\phi$ and $\gamma$ respectively, the model cannot identify
+their physical origins.
+
+The model contains the product of latent parameters
+$\vec{\phi} p$, which leads to the degeneracy $\vec{\phi} \rightarrow -\vec{\phi}$, $p \rightarrow -p$.
+No conditions are added to break this degeneracy as we want to explore the possibility that
+$\sigma_p\phi$ is consistent with zero.  The degeneracy
+in $\vec{\phi}$ is apparent later in the article, but it does not affect the relevant science that
+comes with the combination $\vec{\phi} p$.
+
+For $N$ supernovae there are $8N$ observables.  There are $3N$ spectral parameters, each of
+$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$ plus one for their standard
+deviation $\sigma_p$,  and $5 \times 7$ global coefficients.
+For $N=172$ supernovae, there are 1376 observables and 1237  parameters.
+
+\subsection{Results: Effect of the Third Color Term}
+\label{results2:sec}
+In this subsection we focus on the effect of adding the third color term  $\sigma_p \vec{\phi}$.
+The 68\% credible intervals for relevant global parameters are given in \S\ref{m12results:sec}.
+
+There is strong evidence for a third color parameter.
+The 68\% credible interval for $\sigma_p$ is $0.051^{+0.005}_{-0.004}$~mag, highly incompatible with zero. 
+The posterior for $\sigma_p \vec{\phi}$ is shown in Figure~\ref{M1ev:fig}.  
+The two extrema are due to the sign degeneracy for $\vec{\phi}$, each of the MCMC chains converges to one of the solutions and does
+not migrate between them.
+The direction of $\vec{\phi}$ is not aligned with the plane defined by
+the $\vec{\gamma}$ vectors; the 68\% credible interval for the  quadratic fraction of
+$\vec{\phi}$ in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane is $0.088^{+0.118}_{-0.063}$.
 
@@
    \includegraphics[width=4in]{../output_fix3/sigev.pdf} 
-            \caption{Model~II posterior  contours for $\sigma_p \vec{\phi}$.           \label{M1ev:fig}}
+            \caption{Model~II posterior  contours for $\sigma_p \vec{\phi}$. 
+            The solid line shows the location of zero.          \label{M1ev:fig}}
 \end{figure}
 
-For supernovae with host-properties from Childress, we plot $p$ as a function of host-galaxy mass.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.5in]{../output_fix3/childress.pdf} 
-   \caption{Intrinsic parameter
- $p$ as a function of host-galaxy mass
-    \label{childress:fig}}
-\end{figure}
-
-\section{Model I and Model II Comparison}
 Model~II introduces a degree of freedom that is associated with a Normal distribution.
-It is thus interesting to compare the distributions of the $k_0$ and $k_1$ parameters of Model~I and Model~II,
-which are shown in Figure~\ref{kcomp:fig}.  The apparent difference between Model~I and II is in the $\gamma^1k_1$ term,
+It is thus interesting to compare the distributions of the $g_0$ and $g_1$ parameters of Model~I and Model~II,
+which are shown in Figure~\ref{kcomp:fig}.  The apparent difference between Model~I and II is in the $\gamma^1g_1$ term,
 where it seems that a Normal distribution component in Model~I is no longer in Model~II but is  assigned to the $\sigma_P \vec{\phi}$.
-This results in a change in the direction of the fit $\gamma^1$ and shifts the inferred Fitzpatrick $R$ to higher values.
 
@@
       of  per-supernova 
-median values of $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$.  Right:  The same plots for $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
+median values of $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$.  Right:  The same plots for $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$,
 Top: Model~I. Bottom: Model~II.
     \label{kcomp:fig}}
+\end{figure}
+
+The $\vec{\gamma}$ vectors, like those from Model~I, are almost entirely projected
+onto the plane defined by
+$a_X$ and $b_X$ of the \citetalias{1999PASP..111...63F} model.
+The 68\% credible interval is $R^F_{\mathit{eff}} = 2.54^{+0.20}_{-0.20}$.
+
+\subsection{Remarks}
+The inclusion of a third color term beyond the two (which are expected from dust-extinction models) of Model~I has important consequences.
+
+\begin{itemize}
+\item The data strongly supports the influence of an additional supernova parameter that affects supernova colors in a manner orthogonal to
+ dust extinction.
+\item The effective $R^F_{\mathit{eff}}$ shifts by $>1 \sigma$ when including the new color term.  This demonstrates,
+as has been noted by \citet{2011A&A...529L...4C}, that dust analyses
+that do not allow for additional color dispersion are susceptible to bias in inferred dust parameters.
+\end{itemize}
+
+\section{Model~III: Extrinsic--Intrinsic Colors and Light-Curve Shape}
+\label{modelIII:sec}
+The two models already presented standardize supernovae based on spectral features and colors at peak brightness.
+Nevertheless we know that multi-epoch data also trace supernova properties.
+Light-curve shape is an established indicator of SN~Ia diversity 
+\citep{1993ApJ...413L.105P, 1996ApJ...473...88R,
+1997ApJ...483..565P}
+associated with color \citep{1996ApJ...473...88R,2005A&A...443..781G}.
+Model~III introduced in this section explicitly includes light-curve shape
+along with the spectral features.  This model is of primary interest
+in this article and its results are described in depth.
+
+\subsection{Model}
+\label{modelIImodel:sec}
+Model~III is the same as Model~II except for the 
+addition of a new term  that relates magnitudes with the SALT2 light-curve-shape parameter,
+$x_1$, that is related to magnitudes with linear coefficients $\zeta$. 
+What is $x_1$ reference?
+The model reads as
+\begin{equation}
+p \sim \mathcal{N}(0, \sigma_p),
+\end{equation}
+\begin{equation}
+\begin{pmatrix}
+{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
+\end{pmatrix}
+=
+\Delta +
+\begin{pmatrix}
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} +\zeta_{\hat{U}} x_1 + \phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\zeta_{\hat{B}} x_1 + \phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\zeta_{\hat{V}} x_1+ \phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\zeta_{\hat{R}} x_1+ \phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\zeta_{\hat{I}} x_1+ \phi_{\hat{I}}  p
+\end{pmatrix},
+\label{ewsiv3:eqn}
+\end{equation}
+\begin{equation}
+\begin{pmatrix}
+{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
+\end{pmatrix}
+\sim \mathcal{N}
+\left(
+\begin{pmatrix}
+{\hat{U}} +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
+{\hat{V}}+\gamma^0_{{\hat{V}}} g_0+\gamma^1_{{\hat{V}}} g_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} g_0 + \gamma^1_{{\hat{R}}} g_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} g_0+\gamma^1_{{\hat{I}}} g_1\\
+EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
+\end{pmatrix}
+,C
+\right).
+\label{dust3:eqn}
+\end{equation}
+The only change from Model~II is the addition of the $\vec{\zeta} x_1$ terms in Eq.~\ref{ewsiv3:eqn}.
+
+For $N$ supernovae there are $9N$ observables.  There are $3N$ spectral parameters, each of
+$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$ plus one for their standard
+deviation $\sigma_p$,  and $6 \times 7$ global coefficients.
+For $N=172$ supernovae, there are 1548 observables and 1409  parameters.
+
+\subsection{Results}
+
+This section describes the evaluated posterior of the model parameters.  Before doing so, we show that the model provides
+a fair representation of the data.
+As a diagnostic that the model results do not give catastrophically poor color predictions and are not pulled by extreme
+outlying data, shown in Figure~\ref{residual:fig} are plots of observed  versus
+model-expectation colors (including  supernova-specific spectral features, light-curve shape $\gamma g$, and $\phi p$ terms) for four selected colors,
+and the histogram of their differences.  The residuals of the data away from the model have a compact Gaussian-like appearance, and
+show no bias with respect to observed color.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{../output_fix3_x1/residual.pdf} 
+            \caption{Observed  versus
+            Model~III-expectation colors (including  supernova-specific spectral features, $\gamma g$, and $\phi p$  terms)
+for four selected colors. 
+            Plotted on the right for each color
+is the histogram of the difference between the expected and
+observed
+ colors. 
+            \label{residual:fig}}
+\end{figure}
+
+Results from our analysis are shown through contours of the posterior surface for pairs of global parameters grouped by filter, 
+in Figures~\ref{global1:fig} -- \ref{global5:fig}.
+The confidence regions are localized and unimodal, except for the combination $\sigma_p \vec{\phi}$ that
+has the sign degeneracy already noted in \S\ref{results2:sec} and plotted in Figure~\ref{M1ev:fig}.
+Within the finite number of generated links, the MCMC chains do not migrate to the parity-degenerate solution of $\vec{\gamma}$ and $g$.
+Each chain converges to one of the  $\vec{\phi}$--$p$ degenerate solutions, away from which it does not migrate.  The 
+confined peak of the posterior surface, in addition to the MCMC-convergence tests described in  \S\ref{results1:sec}, provide evidence that the MCMC has not failed to converge.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{../output_fix3_x1/coeff0.pdf} 
+            \caption{Model~III posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{U}}$ band.
+            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
+            projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
+            enclosed probability.
+Lines for zero value for $\alpha_{\hat{U}}$, $\beta_{\hat{U}}$, $\eta_{\hat{U}}$, $\gamma_{\hat{U}}^0$, $\gamma_{\hat{U}}^1$, and $\sigma_p \phi_{\hat{U}}$ are shown for reference --
+            in most cases they are outside the range of the plot.
+            \label{global1:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{../output_fix3_x1/coeff1.pdf} 
+            \caption{Model~III posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{B}}$ band.
+ \label{global2:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{../output_fix3_x1/coeff2.pdf} 
+            \caption{Model~III posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{V}}$ band.
+ \label{global3:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.2in]{../output_fix3_x1/coeff3.pdf} 
+            \caption{Model~III posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{R}}$ band.
+ \label{global4:fig}}
+\end{figure}
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+         \includegraphics[width=5.2in]{../output_fix3_x1/coeff4.pdf} 
+            \caption{Model~III posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{I}}$ band.
+ \label{global5:fig}}
+\end{figure}
+
+For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\zeta}$,
+$\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p\vec{\phi}$
+are given in Table~\ref{global2:tab}.
+To break the sign degeneracy, we enforce that $\phi_{\hat{I}}$
+be positive such that  $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$;
+we use the $\hat{I}$-band because
+Figure~\ref{global5:fig} shows that it has
+the largest separation between the degenerate solutions of $\sigma_p \phi_X$.
+The effect of spectral parameters on color (as opposed to magnitude)
+is shown in the rows of $\alpha_X/\alpha_{\hat{V}}-1$,  $\beta_X/\beta_{\hat{V}}-1$, and  $\eta_X/\eta_{\hat{V}}-1$.
+The freedom to scale each of the terms of $\vec{\gamma}g$ is nulled out in the statistic
+ $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
+Note the analogy between these statistics and the common use of
+$R_V^{-1}=A_B/A_V-1$ as an observational descriptor of dust properties.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
+$\alpha_X$
+& $0.0059^{+0.0007}_{-0.0008}$
+& $0.0033^{+0.0006}_{-0.0007}$
+& $0.0029^{+0.0006}_{-0.0006}$
+& $0.0026^{+0.0005}_{-0.0005}$
+& $0.0041^{+0.0004}_{-0.0005}$
+\\
+${\alpha_X/\alpha_V-1}$
+& $   1.0^{+   0.2}_{  -0.2}$
+& $   0.1^{+   0.1}_{  -0.1}$
+& $   0.0^{+   0.0}_{   0.0}$
+& $  -0.1^{+   0.0}_{  -0.0}$
+& $   0.4^{+   0.2}_{  -0.1}$
+\\
+$\beta_X$
+& $ 0.032^{+ 0.006}_{-0.006}$
+& $ 0.021^{+ 0.005}_{-0.005}$
+& $ 0.018^{+ 0.005}_{-0.005}$
+& $ 0.016^{+ 0.004}_{-0.004}$
+& $ 0.008^{+ 0.004}_{-0.004}$
+\\
+${\beta_X/\beta_V-1}$
+& $  0.79^{+  0.29}_{ -0.19}$
+& $  0.16^{+  0.11}_{ -0.08}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.12^{+  0.04}_{ -0.04}$
+& $ -0.58^{+  0.11}_{ -0.17}$
+\\
+$\eta_X$
+& $0.0022^{+0.0011}_{-0.0011}$
+& $0.0024^{+0.0009}_{-0.0010}$
+& $0.0027^{+0.0008}_{-0.0008}$
+& $0.0025^{+0.0007}_{-0.0007}$
+& $0.0018^{+0.0006}_{-0.0006}$
+\\
+${\eta_X/\eta_V-1}$
+& $ -0.19^{+  0.17}_{ -0.28}$
+& $ -0.12^{+  0.09}_{ -0.15}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.06^{+  0.06}_{ -0.04}$
+& $ -0.33^{+  0.10}_{ -0.10}$
+\\
+$\zeta_X$
+& $ -0.06^{+  0.05}_{ -0.04}$
+& $ -0.09^{+  0.04}_{ -0.04}$
+& $ -0.12^{+  0.04}_{ -0.04}$
+& $ -0.09^{+  0.03}_{ -0.03}$
+& $ -0.14^{+  0.03}_{ -0.03}$
+\\
+${\zeta_X/\zeta_V-1}$
+& $ -0.45^{+  0.20}_{ -0.33}$
+& $ -0.26^{+  0.11}_{ -0.18}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.20^{+  0.05}_{ -0.07}$
+& $  0.22^{+  0.23}_{ -0.13}$
+\\
+$\gamma^0_X$
+& $ 68.29^{+  2.97}_{ -2.92}$
+& $ 54.90^{+  2.49}_{ -2.56}$
+& $ 40.89^{+  2.38}_{ -2.47}$
+& $ 30.95^{+  2.13}_{ -2.25}$
+& $ 22.34^{+  2.05}_{ -2.16}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
+& $  0.67^{+  0.05}_{ -0.05}$
+& $  0.34^{+  0.03}_{ -0.03}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.24^{+  0.01}_{ -0.01}$
+& $ -0.45^{+  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+& $-10.15^{+  4.45}_{ -4.49}$
+& $ -6.81^{+  3.88}_{ -3.82}$
+& $-15.06^{+  3.42}_{ -3.39}$
+& $-14.88^{+  3.01}_{ -3.00}$
+& $-15.91^{+  2.90}_{ -2.86}$
+\\
+${\gamma^1_X/\gamma^1_V-1}$
+& $ -0.32^{+  0.16}_{ -0.21}$
+& $ -0.55^{+  0.13}_{ -0.20}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.01^{+  0.05}_{ -0.04}$
+& $  0.06^{+  0.14}_{ -0.10}$
+\\
+$\sigma_p \phi_X$
+& $ 0.024^{+ 0.009}_{-0.009}$
+& $-0.018^{+ 0.007}_{-0.007}$
+& $-0.027^{+ 0.006}_{-0.006}$
+& $-0.010^{+ 0.006}_{-0.006}$
+& $ 0.022^{+ 0.006}_{-0.006}$
+\\
+\hline
+\end{tabular}
+\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~III in \S\ref{modelIII:sec}.\label{global3:tab}}
+\end{table}
+
+We find significant non-zero values for $\vec{\alpha}$, $\vec{\beta}$, and $\vec{\eta}$ indicating that
+$EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$ are indicators of broadband
+colors at peak
+as expected.  The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is also an indicator
+of broadband colors.
+
+The signal in  $\vec{\alpha}$ and $\vec{\beta}$ cannot
+entirely
+be attributed to the equivalent widths themselves.
+The range of Si~II~$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the ${\hat{B}}$-band is 851~\AA, so that its direct affect on magnitude
+is
+$2.5 \log{(20/850)} \sim 0.03$ mag.  
+The implied span in ${\hat{B}}$ magnitude based on $\beta_{\hat{B}}$ is 0.54~mag.  Therefore $\beta_{\hat{B}}$ cannot wholly be attributed to the flux deficit
+from the line itself.
+The Ca~II H\&K equivalent widths have range $\pm 50$~\AA, while the width of the ${\hat{U}}$ band is
+701~\AA, so that its direct affect on magnitude
+is
+$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in ${\hat{U}}$ magnitude is  0.21~mag, 
+which would imply that  $\alpha_{\hat{U}}$ cannot be completely due to the 
+presence of the line itself.  
+Supernova flux has a large gradient in our $\hat{U}$ and there is a variation in the effective, flux-weighted,  $\hat{U}$ bandwidth. 
+Nevertheless, the  correlation between spectral features with magnitudes in bands with no wavelength overlap is the
+important signal of importance in this study.
+
+The posterior visualized in
+Figures~\ref{global1:fig} -- \ref{global5:fig} shows
+ that $\vec{\zeta}$, the magnitude vector associated with $x_1$, is highly correlated with $\vec{\beta}$ the vector
+ associated with  $EW_{Si}$.
+The direct correlation between  $x_1$ and $EW_{Si}$ has already been established
+\citep{2008A&A...492..535A, 2011A&A...529L...4C}
+and exists
+in our sample as is shown late in  this section.  It is not surprising that our analysis does not entirely distinguish between
+their influence on supernova colors. Nevertheless, their posteriors are bounded and inconsistent with zero, so they do convey independent information.
+It is for this reason  that Model~III is highlighted in this article over Model~II.
+
+The posterior gives a significant magnitude influence of the $p$ parameter.
+The minimum value for $\sigma_p$ over all Monte Carlo chains is 0.039~mag and its 
+68\% credible interval is $\sigma_p=0.049^{+ 0.004}_{-0.003}$~mag. 
+The median data color uncertainty of 0.010~mag (the maximum is 0.042~mag) so we conclude that
+the is not a due to spurious noise.
+
+The chromatic effect of $\vec{\phi}$ is visualized in Figure~\ref{phiratio:fig}, which
+gives a different perspective of the posterior using the statistic $\phi_X/\phi_{\hat{I}}-1$.
+Unlike with $\gamma$, we normalize $\phi$ to $\hat{U}$ because the uncertainty in $\phi_{\hat{B}}-\phi_{\hat{V}}$ is relatively large with
+credible intervals that easily cross zero.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+      \includegraphics[width=5.2in]{../output_fix3_x1/phiratio.pdf}
+   \caption{Model~III median values  and corresponding 68\% intervals for $\phi_X/\phi_{\hat{I}}$ in the 5 bands.
+   A dotted line at zero is shown for reference.
+   \label{phiratio:fig}}
+\end{figure}
+
+As with Model~I in \S\ref{modelI:sec}, all elements of the two $\vec{\gamma}$ parameter vectors 
+describing intrinsic color
+are significantly non-zero with 
+none of the 20000 links of 
+our Monte Carlo chains for $\vec{\gamma}$ extending to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}).
+The direction of the vector is shown in Figure~\ref{plane3:fig}.
+The posterior gives a quadratic fraction of $0.9996^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ projected onto the plane defined by
+the  \citetalias{1999PASP..111...63F}-derived
+$a_X$ and $b_X$, the quadratic fraction of $\vec{\gamma}^1$ projected
+onto the dust plane is
+$0.959^{+0.015}_{-0.029}$.
+The corresponding 68\% credible is $R^F_{\mathit{eff}}=2.40^{+0.15}_{-0.15}$.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.95in]{../output_fix3_x1/plane0.pdf}
+   \includegraphics[width=2.95in]{../output_fix3_x1/plane1.pdf}
+   \caption{
+   Visualization of how supernova magnitudes can vary in Model~III IIand that of \citetalias{1999PASP..111...63F}.  While the models describe
+   magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
+   two different perspectives.
+   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes
+   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
+   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
+   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes are confined to the plane that contains both.
+   The perspective on the right visually shows that all four vectors are nearly coplanar.  
+   The combination $\vec{a}+\vec{b}/2.40$ is shown in the dotted red
+   line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
+   \label{plane3:fig}}
+\end{figure}
+
+An intuitive way to consider the effect of $\vec{\gamma}^1$ is through the deviation from linearity in the color-magnitude diagram.
+A matrix such as the one in  Eq.~\ref{trans_I:eqn} is used to transform this $\{g_0, g_1\}$ into an $\{A_V^F, E^F(B-V)\}$ pair
+(modulo additive constants)  for each link in the Monte Carlo chains. A plot showing the expected values and 68\% credible intervals of these parameters
+for our supernova
+sample is shown in Figure~\ref{kk:fig}. 
+For reference, a line that represents $R^V_{\mathit{eff}}=2.4$ is overplotted.  The majority of supernovae lie within a narrow range above the line
+meaning they have $R^F > R^V_{\mathit{eff}}$,
+while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{\mathit{eff}}$.  
+These findings are consistent with previous results:
+using fixed dust-extinction models,
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
+A per supernova determination of $R^F$ requires the specification of the magnitude and colors of supernovae that experience
+no dust, which is unspecified in our model.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{../output_fix3_x1/avebv_synth.pdf}
+      \caption{
+      Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $g_0$ and $g_1$ parameters, for the supernova in our sample.
+      Overplotted is a line with the slope expected for $R^F=2.4$.
+   \label{kk:fig}}
+\end{figure}
+
+Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$,
+$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})k_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})k_1$, and $p\sigma_p\phi_{\hat{I}}$.
+Their Pearson correlation coefficients  are given in the matrix
+\begin{multline}
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), p\sigma_p\phi_{\hat{I}} ) =\\
+\begin{pmatrix}
+\begin{array}{rrrrrrrr}
+\Delta & -0.07^{+0.06}_{-0.06} & -0.11^{+0.08}_{-0.07} & -0.17^{+0.06}_{-0.06} & 0.19^{+0.08}_{-0.08} & 0.08^{+0.07}_{-0.06} & 0.23^{+0.08}_{-0.08} & -0.13^{+0.06}_{-0.06} \\
+\ldots  & EW_{Ca} & 0.09^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & 0.07^{+0.03}_{-0.03} & -0.11^{+0.05}_{-0.05} & -0.18^{+0.06}_{-0.06} & -0.00^{+0.08}_{-0.07} \\
+\ldots & \ldots &EW_{Si} & -0.12^{+0.03}_{-0.03} & -0.84^{+0.01}_{-0.01} & -0.13^{+0.04}_{-0.04} & 0.27^{+0.08}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
+\ldots  & \ldots  & \ldots  &  \lambda_{Si} & 0.14^{+0.03}_{-0.03} & 0.01^{+0.05}_{-0.05} & 0.00^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
+\ldots  &\ldots  &\ldots & \ldots & x_1 & 0.13^{+0.04}_{-0.04} & -0.20^{+0.09}_{-0.09} & 0.00^{+0.08}_{-0.08} \\
+\ldots  &\ldots  & \ldots  &\ldots  & \ldots  & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 0.04^{+0.06}_{-0.06} & -0.00^{+0.07}_{-0.08} \\
+\ldots  & \ldots &\ldots  & \ldots  & \ldots & \ldots  &E_{\gamma^1}({\hat{B}}-{\hat{V}})  & 0.00^{+0.07}_{-0.07} \\
+\ldots  & \ldots & \ldots & \ldots  & \ldots  & \ldots  &\ldots  & p\sigma_p\phi_{\hat{I}} \\
+\end{array}
+\end{pmatrix}.
+\end{multline}
+To aid visualization, only the upper triangular part of the otherwise symmetric matrix is shown and the corresponding feature label is given on
+the diagonal.
+
+We find $>2 \sigma$ correlations between our extrinsic color-excess parameters and the input features  $EW_{Ca}$,
+$EW_{Si}$, and $x_1$.
+The correlation of $x_1$ with with host-galaxy (including dust) properties is known 
+\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
+There is no correlation between the  intrinsic parameter $p$ and the other features.
+As alluded to earlier, the feature $EW_{Si}$ is strongly correlated with $x_1$.
+An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
+and \citet{leget:thesis}.
+
+The color-standardization leaves magnitude residuals $\Delta$.
+The fit $\Delta$'s are highly correlated between supernovae.  To aid 
+visual interpretation, we remove much of this
+correlation by
+selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, at the level of each MCMC link.
+The histogram of the per-supernova  medians of these relative  grey offsets $\Delta-\Delta|_0$,
+is shown in Figure~\ref{hist:fig}.  The distribution
+has a standard deviation of
+%-----
+$0.15$
+%-----
+mag, and a tail in the positive (fainter) direction.
+Supernova peculiar velocities contribute to the standard deviation; of the four
+supernovae with the highest values of $\Delta$, two have 
+heliocentric
+redshifts of 0.0015 and 0.0086. 
+There are $>2 \sigma$ correlations between $\Delta$ and each of $\lambda_{Si}$, $x_1$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$, and
+$p\sigma_p\phi_{\hat{I}}$, showing that in addition to standardizing colors, these features can also be used to standardize
+absolute magnitudes.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{../output_fix3_x1/deltaDelta_hist.pdf} 
+   \caption{
+   Normalized stack of the posteriors of all supernovae and histogram of the per-supernova medians of the grey offset $\Delta$. 
+   To help null correlated errors, we select
+    an arbitrary supernova and subtract out its $\Delta|_0$ from those of all other objects at the level of each MCMC link.
+   The supernovae with the four highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
+   redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.
+   \label{hist:fig}}
+\end{figure}
+
+For supernovae with host-properties from Childress, we plot $p$ as a function of host-galaxy mass.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=3.5in]{../output_fix3_x1/childress.pdf} 
+   \caption{Intrinsic parameter
+ $p$ as a function of host-galaxy mass
+    \label{childress:fig}}
 \end{figure}
@@
 \subsection{Model}
-\label{modelmodel:sec}
-\begin{equation}
-\begin{pmatrix}
-{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
-\end{pmatrix}
-\sim \mathcal{N}
-\left(
-\Delta +
-\begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} \\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  \\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} \\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} \\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}
-\end{pmatrix}
-,C_{c}
-\right)
-\label{ewsiv:eqn}
-\end{equation}
-\begin{equation}
-\begin{pmatrix}
-{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
-\end{pmatrix}
-\sim \mathcal{N}
-\left(
-\begin{pmatrix}
-{\hat{U}} +\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\
-{\hat{V}}+\gamma^0_{{\hat{V}}} k_0+\gamma^1_{{\hat{V}}} k_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} k_0 + \gamma^1_{{\hat{R}}} k_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} k_0+\gamma^1_{{\hat{I}}} k_1\\
-EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
-\end{pmatrix}
-,C
-\right).
-\label{dust:eqn}
-\end{equation}
-
 \subsection{Results}
 \label{results:sec}
-Contours of the posterior surface for parameter pairs grouped by filter are shown in Figures~\ref{global1:fig} -- \ref{global5:fig}.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{coeff0.pdf} 
-            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{U}}$ band.
-            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
-            projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
-            enclosed probability.
-Lines for zero value for $\alpha_{\hat{U}}$, $\beta_{\hat{U}}$, $\eta_{\hat{U}}$, $\gamma_{\hat{U}}^0$, $\gamma_{\hat{U}}^1$, and $\sigma_{\hat{U}}$ are shown for reference --
-            in most cases they are outside the range of the plot.
-            \label{global1:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{coeff1.pdf} 
-            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{B}}$ band.
- \label{global2:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{coeff2.pdf} 
-            \caption{Model~I posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{V}}$ band.
- \label{global3:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-      \includegraphics[width=5.2in]{coeff3.pdf} 
-            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{R}}$ band.
- \label{global4:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-         \includegraphics[width=5.2in]{coeff4.pdf} 
-            \caption{Model~I posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$ in the ${\hat{I}}$ band.
- \label{global5:fig}}
-\end{figure}
-
-Empirically, the confidence regions are localized and unimodal as is seen in  Figures~\ref{global1:fig} -- \ref{global5:fig}.  In these tests there is no evidence that
-the Monte Carlo chains have not converged to the stationary posterior distribution.
-For four selected colors, a plot of the
-model-expectation colors (including  supernova-specific spectral features and $\gamma k$ terms)
- versus observed colors and the histogram of their differences
-are shown in Figure~\ref{residual:fig}. 
-There is no evidence of catastrophically poor model predictions nor of extreme
-outlying data.
-We have rerun the analysis with a variety of initial conditions, including one with $\vec{\gamma}$ equal to zero, except for a small positive 
-$\gamma^0_{\hat{U}}$ and small negative $\gamma^1_{\hat{U}}$;
-the 68\% credible intervals
-remain consistent.  Note that the MCMC chains do not migrate to the parity-degenerate solution of $\vec{\gamma}$ and $k$.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{residual.pdf} 
-            \caption{
-            Model-expectation colors (including  supernova-specific spectral features and $\gamma k$ terms)
-            versus observed colors, for four selected colors. 
-            Plotted on the right for each color
-is the histogram of the difference between the expected and
-observed
- colors. 
-            \label{residual:fig}}
-\end{figure}
-
-For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\eta$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma$
-are given in Table~\ref{global:tab}.
-As the $\vec{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
-their results are shown in terms of $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
-
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-Parameter & $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
-$\alpha_X$
-&
-$0.0043^{+0.0009}_{-0.0009}$
-&
-$0.0016^{+0.0008}_{-0.0007}$
-&
-$0.0015^{+0.0006}_{-0.0006}$
-&
-$0.0015^{+0.0005}_{-0.0005}$
-&
-$0.0027^{+0.0005}_{-0.0005}$
-\\
-${\alpha_X/\alpha_{\hat{V}}-1}$
-&
-$   1.9^{+   1.1}_{  -0.5}$
-&
-$   0.1^{+   0.1}_{  -0.2}$
-&
-$\dots$
-&
-$   0.0^{+   0.1}_{  -0.1}$
-&
-$   0.8^{+   0.8}_{  -0.3}$
-\\
-$\beta_X$
-&
-$ 0.032^{+ 0.003}_{-0.003}$
-&
-$ 0.026^{+ 0.002}_{-0.002}$
-&
-$ 0.026^{+ 0.002}_{-0.002}$
-&
-$ 0.021^{+ 0.002}_{-0.002}$
-&
-$ 0.020^{+ 0.002}_{-0.002}$
-\\
-${\beta_X/\beta_{\hat{V}}-1}$
-&
-$  0.25^{+  0.05}_{ -0.05}$
-&
-$ -0.01^{+  0.03}_{ -0.03}$
-&
-$\dots$
-&
-$ -0.19^{+  0.01}_{ -0.01}$
-&
-$ -0.23^{+  0.03}_{ -0.03}$
-\\
-$\eta_X$
-&
-$-0.0002^{+0.0012}_{-0.0011}$
-&
-$0.0000^{+0.0010}_{-0.0009}$
-&
-$0.0005^{+0.0008}_{-0.0008}$
-&
-$0.0006^{+0.0007}_{-0.0007}$
-&
-$-0.0002^{+0.0006}_{-0.0006}$
-\\
-${\eta_X/\eta_{\hat{V}}-1}$
-&
-$ -0.39^{+  2.22}_{ -1.82}$
-&
-$ -0.35^{+  1.58}_{ -1.20}$
-&
-$\dots$
-&
-$ -0.09^{+  0.29}_{ -0.28}$
-&
-$ -0.78^{+  1.48}_{ -1.11}$
-\\
-$\gamma^0_X$
-&
-$ 63.46^{+  3.70}_{ -3.66}$
-&
-$ 51.40^{+  3.09}_{ -3.07}$
-&
-$ 38.15^{+  2.70}_{ -2.63}$
-&
-$ 29.26^{+  2.40}_{ -2.35}$
-&
-$ 20.94^{+  2.24}_{ -2.25}$
-\\
-${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
-&
-$  0.66^{+  0.06}_{ -0.05}$
-&
-$  0.35^{+  0.03}_{ -0.03}$
-&
-$\dots$
-&
-$ -0.23^{+  0.01}_{ -0.02}$
-&
-$ -0.45^{+  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-&
-$-10.34^{+  3.61}_{ -4.29}$
-&
-$-11.89^{+  2.95}_{ -3.56}$
-&
-$-14.48^{+  2.47}_{ -2.89}$
-&
-$-13.71^{+  2.14}_{ -2.45}$
-&
-$-12.51^{+  2.10}_{ -2.23}$
-\\
-${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
-&
-$ -0.28^{+  0.17}_{ -0.19}$
-&
-$ -0.18^{+  0.10}_{ -0.10}$
-&
-$\dots$
-&
-$ -0.05^{+  0.05}_{ -0.04}$
-&
-$ -0.14^{+  0.10}_{ -0.09}$
-\\
-$\sigma_X$
-&
-$ 0.060^{+ 0.012}_{-0.012}$
-&
-$ 0.033^{+ 0.007}_{-0.007}$
-&
-$ 0.021^{+ 0.004}_{-0.005}$
-&
-$ 0.011^{+ 0.008}_{-0.007}$
-&
-$ 0.044^{+ 0.005}_{-0.004}$
-\\
-\hline
-\end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model~I in \S\ref{model:sec}.\label{global:tab}}
-\end{table}
-
-We find significant non-zero values for $\vec{\alpha}$ and $\vec{\beta}$, indicating that
-$EW_{Ca}$ and $EW_{Si}$ are indicators of broadband
-peak magnitudes
-as expected.
-On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero
-to  within one standard deviation.
-The effect of spectral parameters on color (as opposed to magnitude)
-is shown in the rows of $\alpha_X/\alpha_{\hat{V}}-1$,  $\beta_X/\beta_{\hat{V}}-1$, and  $\eta_X/\eta_{\hat{V}}-1$
-in Table~\ref{global:tab}.
-Values of zero signify no color changes associated with magnitude changes.
-Both $EW_{Ca}$ and $EW_{Si}$ are associated with color changes, though not in ${\hat{B}}-{\hat{V}}$ specifically.
-We do not detect a significant direct connection between
-$\lambda_{Si}$ and color, though their indirect correlation is discussed in \S\ref{velocity:sec}.
-
-The signal in  $\vec{\alpha}$ and $\vec{\beta}$ cannot
-entirely
-be attributed to the equivalent widths themselves.
-The range of Si~II~$\lambda$4130 equivalent widths is $\pm 20$~\AA\ whereas the width of the ${\hat{B}}$-band is 851~\AA, so that its direct affect on magnitude
-is
-$2.5 \log{(20/850)} \sim 0.03$ mag.  
-The implied span in ${\hat{B}}$ magnitude based on $\beta_{\hat{B}}$ is 0.54~mag.  Therefore $\beta_{\hat{B}}$ cannot wholly be attributed to the flux deficit
-from the line itself.
-The Ca~II H\&K equivalent widths have range $\pm 50$~\AA, while the width of the ${\hat{U}}$ band is
-701~\AA, so that its direct affect on magnitude
-is
-$2.5 \log{(50/701)} \sim 0.08$ mags.   The implied span in ${\hat{U}}$ magnitude is  0.21~mag, 
-which would imply that  $\alpha_{\hat{U}}$ cannot be completely due to the 
-presence of the line itself.  
-Supernova flux has a large gradient in our $\hat{U}$ and there is a variation in the effective, flux-weighted,  $\hat{U}$ bandwidth. 
-Nevertheless, the  correlation between spectral features with magnitudes in bands with no wavelength overlap is the
-important signal of importance in this study.
-
-The fit $\Delta$'s are highly correlated between supernovae.  To aid 
-visual interpretation, we remove much of this
-correlation by
-selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, at the level of each MCMC link.
-The histogram of the per-supernova  medians of these relative  grey offsets $\Delta-\Delta|_0$,
-is shown in Figure~\ref{hist:fig}.  The distribution
-has a standard deviation of
-%-----
-$0.08$
-%-----
-mag, and a tail in the positive (fainter) direction.
-The supernovae with the highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
- redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.  Peculiar velocities  can cause a significant magnitude offset for three.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{deltaDelta_hist.pdf} 
-   \caption{
-   Normalized stack of the posteriors of all supernovae and histogram of the per-supernova medians of the grey offset $\Delta$. 
-   To help null correlated errors, we select
-    an arbitrary supernova and subtract out its $\Delta|_0$ from those of all other objects at the level of each MCMC link.
-   The supernovae with the four highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
-   redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.
-   \label{hist:fig}}
-\end{figure}
-
-Non-trivial residual magnitude
-and color dispersions are captured in $C_c$
-at the level of 4--10$\sigma$.
-The square
-root of the diagonal elements are denoted as $\sigma$, which
-range from
-$\sim 0.01$ to 0.06 mag, significantly smaller
-than the dispersion in $\Delta$.
-Of particular interest within $C_c$ is intrinsic color dispersion.  The intrinsic dispersions in ${\hat{V}}$ and colors with respect to ${\hat{V}}$ are
-\begin{multline}
-\sigma({\hat{V}},{\hat{U}}-{\hat{V}},{\hat{B}}-{\hat{V}},{\hat{V}}-{\hat{R}},{\hat{V}}-{\hat{I}})=\\
-\left(
-0.021^{+0.004}_{-0.005} ,\, 
-0.067^{+0.010}_{-0.010},\, 
-0.034^{+0.005}_{-0.005},\, 
-0.023^{+0.002}_{-0.002},\, 
-0.053^{+0.004}_{-0.004}
-\right)
- \text{mag}.
- \label{sig_intrinsic:eqn}
- \end{multline}
-The correlations between these parameters are
-\begin{multline}
-Cor({\hat{V}},{\hat{U}}-{\hat{V}},{\hat{B}}-{\hat{V}},{\hat{V}}-{\hat{R}},{\hat{V}}-{\hat{I}})=\\
-\begin{pmatrix}
-\begin{array}{rrrrr}
-\hat{V} & -0.48^{+0.20}_{-0.18} & -0.34^{+0.21}_{-0.22} & 0.88^{+0.10}_{-0.25} & 0.60^{+0.11}_{-0.19} \\
-\ldots & {\hat{U}}-{\hat{V}} & 0.60^{+0.10}_{-0.13} & -0.38^{+0.18}_{-0.17} & -0.33^{+0.15}_{-0.14} \\
-\ldots  & \ldots & {\hat{B}}-{\hat{V}} & -0.21^{+0.17}_{-0.17} & 0.08^{+0.14}_{-0.15} \\
-\ldots  & \ldots  &\ldots  & {\hat{V}}-{\hat{R}} & 0.65^{+0.06}_{-0.07} \\
-\ldots  & \ldots  &\ldots  &\ldots & {\hat{V}}-{\hat{I}} \\
-\end{array}
- \end{pmatrix}.
- \label{cor_intrinsic:eqn}
- \end{multline}
-To reduce clutter only the upper triangular part of the otherwise symmetric matrix is shown.
-These color variances are smaller than those derived by \citet{2003A&A...404..901N} or \citet{2007ApJ...659..122J}, for cases where
-a direct comparison can be made.
-\citetalias{2017ApJ...842...93M}  find an intrinsic dispersion of the SALT2 $c$ parameter (associated with ${\hat{B}}-{\hat{V}}$) of $\approx 0.07$ mag,
-though variation of dust properties accounts for some of that dispersion.
-%model11_rubin.py
-Having no intrinsic color dispersion is disfavored, and not allowing for them can have important consequences.
-Running an analysis assuming no intrinsic dispersion (replacing the probabilistic intrinsic magnitudes in Eq.~\ref{ewsiv:eqn}
-with a strict equality), we find significant shifts in all slope parameters  and 
-artificially
-smaller statistical uncertainties.
-
-Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$,
-$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})k_0$, and $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})k_1$.
-Their Pearson correlation coefficients  are given in the matrix
-\begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}})) =\\
-\begin{pmatrix}
-\begin{array}{rrrrrr}
-\Delta & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
-\ldots  &EW_{Ca} & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
-\ldots  & \ldots &  EW_{Si} & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
-\ldots & \ldots  &\ldots  & \lambda_{Si} & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
-\ldots & \ldots & \ldots & \ldots & E_{\gamma^0}({\hat{B}}-{\hat{V}}) & 0.06^{+0.08}_{-0.08} \\
-\ldots &\ldots  & \ldots  &\ldots & \ldots & E_{\gamma^1}({\hat{B}}-{\hat{V}}) \\
-\end{array}
-\end{pmatrix}.
-\end{multline}
-
-We find weak correlations between our color-excess parameters and the input features; 
-only the $ -0.17 \pm 0.05$ correlation
-between $E_{\gamma^0}({\hat{B}}-{\hat{V}})$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
-The feature $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
-\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
-An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
-and \citet{leget:thesis}.
 
 \subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
-In our model, $k_0$ and $k_1$ are introduced as latent parameters that are related to linear shifts in band magnitudes through
-the  coefficients $\vec{\gamma}^0$ and
-$\vec{\gamma}^1$.  Otherwise, no physically-motivated suppositions on the properties of $k$ and $\vec{\gamma}$ are imposed.
-Attenuation of supernova light due to dust is expected to be mostly captured by the first-order affects described by our linear model.
-In this Section, we consider the results of our parameter fitting within the context of  dust-extinction models.
-
-All elements of the two $\vec{\gamma}$ parameter vectors 
-describing intrinsic color
-are significantly non-zero. 
-None of the 20000 links of 
-our Monte Carlo chains for $\vec{\gamma}$ extend to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}), we thus claim detection of the
-influence of $k_0$ and $k_1$  on supernova magnitudes
-with probability $1-5\times 10^{-5}$.
-
-We compare our model's parameter vectors $\vec{\gamma}^0$ and $\vec{\gamma}^1$ with the expectations of  
-dust-extinction
-models.
-The 2-parameter linear model
-\begin{equation}
-A_X = a(X)  A_{V} + b(X) E(B-V)
-\label{f99:eqn}
-\end{equation}
-approximately describes  
-dust-extinction
-models \citep[for example, the wavelength-dependent model of ][is linear,
-though its linearity is lost when integrated over broad-band filters]{1989ApJ...345..245C}.
-For the case of
-$R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
-\citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at ${\hat{B}}$-band peak, the 
-\citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F} model
-gives
-$\vec{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\vec{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
-(The $F$ superscript is used to distinguish parameters of the \citetalias{1999PASP..111...63F} model.)
-Over the ranges of
- $R^F$ and $A^F_V$,
-and the wavelengths under consideration here,  the values of the elements of $a$ and $b$ vary by $<5$\%
-for the
-\citetalias{1999PASP..111...63F} model.
-Over the range
- $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in extinction from the linear approximation of
-Eq.~\ref{f99:eqn} has amplitude $<0.008$ mag.
-
-The extrinsic contribution to our model can be re-expressed to have a similar parameterization
-\begin{equation}
-A_X = \frac{\gamma^0_X}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}}  E_{\gamma^0}({\hat{B}}-{\hat{V}}) +  \frac{\gamma^1_X}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}}  E_{\gamma^1}({\hat{B}}-{\hat{V}}),
-\end{equation}
-with $E_{\gamma^i}({\hat{B}}-{\hat{V}}) \equiv  (\gamma^i_{\hat{B}}-\gamma^i_{\hat{V}})k_i$ as defined in \S\ref{results:sec}.
-In this parameterization, the per-supernova parameters represent $\hat{B}-\hat{V}$ color excesses, and thus have a
-more familiar and physical interpretation that are used in dust-extinction models.
-Our median-fit values for the $\vec{\gamma}$ coefficients are
-%---- fitz11.py
-$\frac{\vec{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}}  =(4.80 ,   3.89,   2.89,   2.22,   1.59)$ and
-$ \frac{\vec{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}}=(-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71)$.
-%----
-
-Our model $\gamma$ vectors can be written in terms of the 
-dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\vec{a}$ and $\vec{b}$.
-The result is
-\begin{equation}
-\begin{pmatrix}
- \frac{\vec{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
-\frac{\vec{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} 
-\end{pmatrix}=
-\begin{pmatrix}
-\begin{array}{rr}
-2.82 & 1.15  \\
--5.27 & 0.72
-\end{array}
-\end{pmatrix} 
-\begin{pmatrix}
-\vec{a} \\
-\vec{b}
-\end{pmatrix}+
-\begin{pmatrix}
-\vec{\epsilon}_{\gamma^0} \\
-\vec{\epsilon}_{\gamma^1}
-\end{pmatrix},
-\label{trans_I:eqn}
-\end{equation}
-where the two residual vectors
-\begin{align}
-\begin{split}
-\vec{\epsilon}_{\gamma^0} &=(0.06, -0.07, -0.07,  0.07, 0.02), \\
-\vec{\epsilon}_{\gamma^1} & =(-0.06, 0.16, -0.22, 0.33, -0.26)
-\end{split}
-\label{res_I:eqn}
-\end{align}
-quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\vec{\gamma}$ vectors.  The most significant
-deviation away from the plane is in the ${\hat{R}}$-band.
-This result indicates that
-the allowed variations in ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to almost identical
-2-dimensional
-planes within
-the 5-dimensional magnitude space.
-With no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
-2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.
-We show later that our per-supernova fit parameters under transformation are confined to $|A^F_V| < 1$ and $|E^F(B-V)| < 0.5$,
-where deviations of  the \citetalias{1999PASP..111...63F}  dust-extinction model from the plane approximation is less than 0.01 mag.
-
-The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the
-${\hat{U}}{\hat{V}}\hat{I}$-subspace
-two perspectives (left and right panels)
-of the unit vectors corresponding to $\vec{\gamma}^0$ and  $\vec{\gamma}^1$ of our model (solid lines),
-and $\vec{a}$, $\vec{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All  vectors are set to intersect the origin.
-The two perspectives show that while the four vectors point in different directions for each band combination,
-they are almost coplanar in ${\hat{U}}{\hat{V}}{\hat{I}}$ (they are slightly less coplanar in ${\hat{B}}{\hat{V}}{\hat{R}}$).
-The $\vec{a}$ and $\vec{b}$ vectors and the $\vec{\gamma}^0$ and $\vec{\gamma}^1$
-vectors span near-parallel planes in the 5-dimensional color space, and hence the latter can be almost entirely expressed in terms of
-the former.
-%
-%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-%   \centering
-%   \includegraphics[width=2.95in]{plane0.pdf}
-%   \includegraphics[width=2.95in]{plane1.pdf}
-%   \caption{
-%   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
-%   magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
-%   two different perspectives.
-%   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes
-%   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
-%   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
-%   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes are confined to the plane that contains both.
-%   The perspective on the right visually shows that all four vectors are nearly coplanar.  
-%   The combination $\vec{a}+\vec{b}/2.44$ is shown in the dotted red
-%   line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
-%   \label{plane:fig}}
-%\end{figure}
-%
 
@@
    \label{k0_med:fig}}
-\end{figure}
-
-We now consider the direction of $\vec{\gamma}^1$. 
-Different supernovae are expected to encounter dust with different $R^F$;
-having  associated $\vec{\gamma}^0$ with
-the extinction from a single effective
-$\langle R^F_{\mathit{eff}}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
-away from that effective value.
-Let us introduce a new parameter for each supernova, $\delta R$, such that 
-$A^F =\langle R^F_{\mathit{eff}}\rangle(1-  \delta R) E^F(B-V)$.
-Variations in the value of  $\delta R$, with the prior of the non-correlation between 
-the coefficients in Eq.~\ref{newdust:eqn},
-lead 
-to 
-\begin{equation}
-\kappa_2 =\langle R^F_{\mathit{eff}}\rangle \left(1- \frac{\mbox{Var}(\delta R \times E^F(B-V))}{\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))}\right).
-\end{equation}
-From the matrix elements of Eq.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
-This result indicates that there is a small but significant covariance between  extinction contributions due to
-fractional deviations from an effective $R^F$ and
-the color-excess parameter $E^F(B-V)$.
-Figure~\ref{k0_med:fig} shows the histogram of per-supernova
-median values
-from Monte Carlo chains
-and  stack of the posteriors of all supernovae  of $\gamma^1_{\hat{V}} k_1$
-relative to that of an arbitrary supernova  $\gamma^1_{\hat{V}} k_1|_0$.
-
-Perhaps a more instructive way to consider $k_1$ is to not view it in isolation, but rather as part of a $\{k_0,k_1\}$ pair.
-A matrix such as the one in  Eq.~\ref{trans_I:eqn} is used to transform this pair into an $\{A_V^F, E^F(B-V)\}$ pair
-(modulo additive constants)  for each link in the Monte Carlo chains. A plot showing the expected values and 68\% credible intervals of these parameters
-for our supernova
-sample is shown in Figure~\ref{kk:fig}. 
-For reference, a line that represents $R^V_{\mathit{eff}}=2.44$ is overplotted.  The majority of supernovae lie within a narrow range above the line
-meaning they have $R^F > R^V_{\mathit{eff}}$,
-while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{\mathit{eff}}$.  
-These findings are consistent with previous results:
-using fixed dust-extinction models,
-\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
-A per supernova determination of $R^F$ requires the specification of the magnitude and colors of supernovae that experience
-no dust, which is unspecified in our model.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{avebv_synth.pdf}
-      \caption{
-      Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $k_0$ and $k_1$ parameters, for the supernova in our sample.
-      Overplotted is a line with the slope expected for $R^F=2.44$.
-   \label{kk:fig}}
 \end{figure}
@@
 \right)
-\label{ewsiv2:eqn}
+%\label{ewsiv2:eqn}
 \end{equation}
@@
 \right).
-\label{dust2:eqn}
+%\label{dust2:eqn}
 \end{equation}
@@
 initial step of the MCMC is at $\vec{\delta}=0$.
-
-In Model~II,
-as in Model~I,
-for $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
-color parameters, $(N-1)$ magnitude offsets,  $5 \times 7$ global coefficients, and $10$ parameters that describe the intrinsic
-$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1242 top-level parameters.
 
@@
 
-\subsection{Light Curve Shape}
-\label{shape:sec}
-The motivation of our analyses was to standardize supernovae based on spectral features and colors at peak brightness.
-As such, our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
-We now examine the effect of shape in more depth using the intrinsic--extrinsic Model~II of \S\ref{model2:sec}.
-The connection between the spectrum at peak and the light-curve decline rate, seen through
-the correlation between $EW_{Si}$ and the SALT2 $x_1$ light-curve shape parameter, is verified
-for our sample in \citet{2017Chotard}.
-On the other hand, there is no such correlation seen between $A_{\delta {\hat{I}}} = \delta_{\hat{I}} D$ and $x_1$, as shown in Figure~\ref{x1:fig}. 
-Our magnitude residuals, $\sigma_X$, are comparable to the residuals after SALT2 training
-\citep{2010A&A...523A...7G}, showing that our model exhibits little loss in its ability to standardize
-magnitudes even though $x_1$ is neglected.
-There is no apparent correlation
-between $x_1$ and the residuals between observed and model-predicted colors, as seen in
-Figure~\ref{x1res:fig},
-though there is a hint of nonlinearity in the ${\hat{B}}-{\hat{V}}$ and ${\hat{R}}-{\hat{V}}$ colors.
-
-A direct consideration of light-curve shape is
-performed by explicitly adding to Model~II a new linear term $\zeta x_1$ to the 
-intrinsic magnitude. The credible intervals
-from this analysis are given in Table~\ref{globalx1:tab}; there are no significant changes with respect to the reference model. 
-Light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: $\zeta_{\hat{R}}/\zeta_{\hat{V}}$
-has the largest significance  at 
-only
-$1\sigma$.
-The evidence for the effect of a third parameter persists in the significant  non-zero  $\delta_X/\delta_{\hat{U}}-1$ values
-in Table~\ref{globalx1:tab}, reinforcing the evidence that the $D$ of Model~II is not primarily related to light-curve shape.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5in]{x1D.pdf}
-    \caption{The
-    intrinsic color component of Model~II as given by
-    $A_{\delta {\hat{U}}}  = \delta_{\hat{U}} D$
-    versus
-    the SALT2 $x_1$ versus
-    shows no correlation between the two.  (Note that there remain correlated uncertainties between points.)
-   \label{x1:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{residualx1.pdf}
-    \caption{Differences between observed colors and the 
-    expected colors
-     from the analysis, as a function
-            of the SALT2 light-curve shape parameter $x_1$.  Our model does not explicitly use $x_1$.  For reference a dotted line is plotted at zero difference.
-   \label{x1res:fig}}
-\end{figure}
-
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-Parameters & $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
-$\alpha_X$
-&
-$0.0037^{+0.0010}_{-0.0010}$
-&
-$0.0011^{+0.0008}_{-0.0008}$
-&
-$0.0013^{+0.0007}_{-0.0007}$
-&
-$0.0013^{+0.0006}_{-0.0006}$
-&
-$0.0026^{+0.0005}_{-0.0005}$
-\\
-${\alpha_X/\alpha_{\hat{V}}-1}$
-&
-$   1.7^{+   1.3}_{  -0.5}$
-&
-$  -0.1^{+   0.2}_{  -0.4}$
-&
-$  \ldots$
-&
-$  -0.0^{+   0.2}_{  -0.1}$
-&
-$   1.0^{+   1.2}_{  -0.5}$
-\\
-$\beta_X$
-&
-$ 0.034^{+ 0.006}_{-0.005}$
-&
-$ 0.026^{+ 0.005}_{-0.005}$
-&
-$ 0.023^{+ 0.004}_{-0.004}$
-&
-$ 0.020^{+ 0.003}_{-0.003}$
-&
-$ 0.017^{+ 0.003}_{-0.003}$
-\\
-${\beta_X/\beta_{\hat{V}}-1}$
-&
-$  0.50^{+  0.11}_{ -0.10}$
-&
-$  0.15^{+  0.06}_{ -0.06}$
-&
-$  \ldots$
-&
-$ -0.12^{+  0.03}_{ -0.03}$
-&
-$ -0.26^{+  0.06}_{ -0.06}$
-\\
-$\eta_X$
-&
-$0.0002^{+0.0011}_{-0.0011}$
-&
-$0.0004^{+0.0009}_{-0.0009}$
-&
-$0.0009^{+0.0008}_{-0.0008}$
-&
-$0.0008^{+0.0007}_{-0.0007}$
-&
-$0.0000^{+0.0006}_{-0.0006}$
-\\
-${\eta_X/\eta_{\hat{V}}-1}$
-&
-$ -0.47^{+  0.69}_{ -1.37}$
-&
-$ -0.39^{+  0.41}_{ -0.93}$
-&
-$  \ldots$
-&
-$ -0.12^{+  0.19}_{ -0.16}$
-&
-$ -0.78^{+  0.42}_{ -0.88}$
-\\
-$\zeta_X$
-&
-$  0.01^{+  0.04}_{ -0.04}$
-&
-$ -0.00^{+  0.03}_{ -0.03}$
-&
-$ -0.03^{+  0.03}_{ -0.03}$
-&
-$ -0.01^{+  0.02}_{ -0.02}$
-&
-$ -0.03^{+  0.02}_{ -0.02}$
-\\
-${\zeta_X/\zeta_{\hat{V}}-1}$
-&
-$ -0.78^{+  1.55}_{ -1.96}$
-&
-$ -0.62^{+  1.21}_{ -1.33}$
-&
-$  \ldots$
-&
-$ -0.46^{+  0.45}_{ -0.52}$
-&
-$ -0.14^{+  0.51}_{ -0.42}$
-\\
-$\gamma^0_X$
-&
-$ 59.51^{+  4.09}_{ -4.09}$
-&
-$ 49.02^{+  3.32}_{ -3.30}$
-&
-$ 36.96^{+  2.69}_{ -2.70}$
-&
-$ 28.37^{+  2.36}_{ -2.36}$
-&
-$ 20.35^{+  2.16}_{ -2.16}$
-\\
-${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
-&
-$  0.61^{+  0.06}_{ -0.05}$
-&
-$  0.33^{+  0.03}_{ -0.03}$
-&
-$  \ldots$
-&
-$ -0.23^{+  0.01}_{ -0.01}$
-&
-$ -0.45^{+  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-&
-$ -7.57^{+  3.75}_{ -4.06}$
-&
-$ -9.63^{+  2.90}_{ -3.27}$
-&
-$-13.65^{+  2.36}_{ -2.60}$
-&
-$-12.98^{+  2.08}_{ -2.27}$
-&
-$-12.16^{+  2.08}_{ -2.19}$
-\\
-${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
-&
-$ -0.44^{+  0.19}_{ -0.24}$
-&
-$ -0.30^{+  0.11}_{ -0.13}$
-&
-$  \ldots$
-&
-$ -0.05^{+  0.05}_{ -0.05}$
-&
-$ -0.11^{+  0.11}_{ -0.10}$
-\\
-$\delta_X$
-&
-$  0.14^{+  1.13}_{ -1.41}$
-&
-$  0.11^{+  0.91}_{ -1.10}$
-&
-$  0.04^{+  0.56}_{ -0.60}$
-&
-$  0.01^{+  0.43}_{ -0.43}$
-&
-$ -0.02^{+  0.43}_{ -0.41}$
-\\
-${{\delta_X/\delta_{\hat{U}}-1}}$
-&
-$  \ldots$
-&
-$ -0.22^{+  0.28}_{ -0.21}$
-&
-$ -0.63^{+  0.33}_{ -0.36}$
-&
-$ -0.82^{+  0.30}_{ -0.44}$
-&
-$ -1.05^{+  0.35}_{ -0.63}$
-\\
-$\sigma_X$
-&
-$ 0.053^{+ 0.008}_{-0.011}$
-&
-$ 0.018^{+ 0.011}_{-0.011}$
-&
-$ 0.017^{+ 0.004}_{-0.006}$
-&
-$ 0.010^{+ 0.007}_{-0.007}$
-&
-$ 0.040^{+ 0.006}_{-0.005}$
-\\
-\hline
-\end{tabular}
-\caption{68\% credible intervals for the Global Fit Parameters when adding the light-curve shape parameter, $x_1$ \label{globalx1:tab}}
-\end{table}
-
 \subsection{Si~II Line Velocity}
@@
 \appendix
-
-\section{Testing for Parameter Bias Through Simultations}
-In \S\ref{model2:sec} we presented Model~II and tested for bias in our analysis.
-We generated 50 random realizations of data with the same input  parameters.
-The posterior for each realization was analyzed individually, and greeneriors of all realizations were stacked.
-The stacks and input parameter values are shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.
-We find that any differences between the peaks of the posterior stack and the input parameter values
-are much smaller than the per-realization statistical uncertainty.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{simdelta_corner.pdf} 
-            \caption{Stacked $\vec{\delta}$ posterior contours for 100  independent simulated data sets.
-            The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
-            \label{simdelta:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{simcoeff0.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{U}}$ band of  100 independent simulated data sets.
-The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
-            \label{simglobal1:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{simcoeff1.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{B}}$ band of  100 independent simulated data sets.
-The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
- \label{simglobal2:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{simcoeff2.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{V}}$ band of  100 independent simulated data sets.
-The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
-\label{simglobal3:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-      \includegraphics[width=5.2in]{simcoeff3.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{R}}$ band of  100  independent simulated data sets.
-The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
-\label{simglobal4:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-         \includegraphics[width=5.2in]{simcoeff4.pdf} 
-            \caption{Aggregated Model~II posterior contours for $\vec{c}$, $\alpha$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$,  $\vec{\delta}$, and $\sigma$ in the ${\hat{I}}$ band of  100 independent simulated data sets.
-The blue crosshairs denote the input $\vec{\delta}$ used to generate the simulated data.
- \label{simglobal5:fig}}
-\end{figure}
+\section{Results from Model~I and II}
+\label{m12results:sec}
+For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,
+$\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p\vec{\phi}$
+are given in Table~\ref{global2:tab}.
+Figure~\ref{global5:fig} shows that the $\hat{I}$-band has
+the largest separation between the degenerate solution of $\sigma_p \phi_X$.  To break the degeneracy we enforce a positive value for
+$\phi_{\hat{I}}$, 
+that is $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$.
+As the $\vec{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
+their results are shown in terms of $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
+$\alpha_X$
+& $0.0063^{+0.0006}_{-0.0006}$
+& $0.0029^{+0.0005}_{-0.0005}$
+& $0.0026^{+0.0005}_{-0.0005}$
+& $0.0026^{+0.0004}_{-0.0004}$
+& $0.0038^{+0.0004}_{-0.0004}$
+\\
+${\alpha_X/\alpha_V-1}$
+& $   1.5^{+   0.3}_{  -0.2}$
+& $   0.1^{+   0.0}_{  -0.0}$
+& $   0.0^{+   0.0}_{   0.0}$
+& $  -0.0^{+   0.0}_{  -0.0}$
+& $   0.5^{+   0.2}_{  -0.1}$
+\\
+$\beta_X$
+& $ 0.039^{+ 0.003}_{-0.003}$
+& $ 0.031^{+ 0.003}_{-0.003}$
+& $ 0.033^{+ 0.003}_{-0.003}$
+& $ 0.027^{+ 0.003}_{-0.003}$
+& $ 0.026^{+ 0.002}_{-0.002}$
+\\
+${\beta_X/\beta_V-1}$
+& $  0.18^{+  0.04}_{ -0.03}$
+& $ -0.05^{+  0.01}_{ -0.01}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.17^{+  0.01}_{ -0.01}$
+& $ -0.21^{+  0.03}_{ -0.02}$
+\\
+$\eta_X$
+& $0.0018^{+0.0009}_{-0.0010}$
+& $0.0016^{+0.0009}_{-0.0010}$
+& $0.0022^{+0.0008}_{-0.0009}$
+& $0.0021^{+0.0007}_{-0.0007}$
+& $0.0010^{+0.0006}_{-0.0006}$
+\\
+${\eta_X/\eta_V-1}$
+& $ -0.18^{+  0.17}_{ -0.25}$
+& $ -0.25^{+  0.11}_{ -0.24}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.03^{+  0.11}_{ -0.06}$
+& $ -0.55^{+  0.13}_{ -0.18}$
+\\
+$\gamma^0_X$
+& $ 76.37^{+  3.19}_{ -3.23}$
+& $ 60.22^{+  3.09}_{ -3.20}$
+& $ 43.06^{+  2.95}_{ -3.11}$
+& $ 32.93^{+  2.60}_{ -2.87}$
+& $ 22.89^{+  2.27}_{ -2.65}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
+& $  0.78^{+  0.06}_{ -0.06}$
+& $  0.40^{+  0.03}_{ -0.03}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.24^{+  0.01}_{ -0.01}$
+& $ -0.47^{+  0.02}_{ -0.03}$
+\\
+$\gamma^1_X$
+& $-18.64^{+  4.86}_{ -4.86}$
+& $-28.10^{+  4.23}_{ -4.20}$
+& $-28.71^{+  3.75}_{ -3.70}$
+& $-21.86^{+  3.49}_{ -3.32}$
+& $-11.49^{+  3.38}_{ -3.05}$
+\\
+${\gamma^1_X/\gamma^1_V-1}$
+& $ -0.35^{+  0.08}_{ -0.10}$
+& $ -0.02^{+  0.03}_{ -0.03}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.24^{+  0.02}_{ -0.03}$
+& $ -0.60^{+  0.06}_{ -0.08}$
+\\
+\hline
+\end{tabular}
+\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~I in \S\ref{modelI:sec}.\label{global1:tab}}
+\end{table}
+
+Figure~\ref{global5:fig} shows that the $\hat{I}$-band has
+the largest separation between the degenerate solution of $\sigma_p \phi_X$.  To break the degeneracy we enforce a positive value for
+$\phi_{\hat{I}}$, 
+that is $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$.
+As the $\vec{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
+their results are shown in terms of $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|c|c|}
+\hline
+Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
+$\alpha_X$
+& $0.0048^{+0.0010}_{-0.0012}$
+& $0.0019^{+0.0009}_{-0.0010}$
+& $0.0018^{+0.0007}_{-0.0008}$
+& $0.0017^{+0.0006}_{-0.0006}$
+& $0.0027^{+0.0005}_{-0.0005}$
+\\
+${\alpha_X/\alpha_V-1}$
+& $   1.7^{+   1.0}_{  -0.4}$
+& $   0.1^{+   0.1}_{  -0.1}$
+& $   0.0^{+   0.0}_{   0.0}$
+& $  -0.0^{+   0.1}_{  -0.1}$
+& $   0.5^{+   0.7}_{  -0.3}$
+\\
+$\beta_X$
+& $ 0.040^{+ 0.003}_{-0.003}$
+& $ 0.031^{+ 0.002}_{-0.002}$
+& $ 0.033^{+ 0.002}_{-0.002}$
+& $ 0.027^{+ 0.002}_{-0.002}$
+& $ 0.027^{+ 0.002}_{-0.002}$
+\\
+${\beta_X/\beta_V-1}$
+& $  0.23^{+  0.04}_{ -0.04}$
+& $ -0.04^{+  0.02}_{ -0.02}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.16^{+  0.01}_{ -0.01}$
+& $ -0.18^{+  0.03}_{ -0.03}$
+\\
+$\eta_X$
+& $0.0020^{+0.0010}_{-0.0009}$
+& $0.0022^{+0.0009}_{-0.0008}$
+& $0.0031^{+0.0008}_{-0.0008}$
+& $0.0031^{+0.0007}_{-0.0007}$
+& $0.0025^{+0.0007}_{-0.0007}$
+\\
+${\eta_X/\eta_V-1}$
+& $ -0.35^{+  0.17}_{ -0.22}$
+& $ -0.29^{+  0.10}_{ -0.14}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $  0.01^{+  0.06}_{ -0.04}$
+& $ -0.19^{+  0.10}_{ -0.09}$
+\\
+$\gamma^0_X$
+& $ 71.32^{+  3.40}_{ -3.24}$
+& $ 58.31^{+  3.03}_{ -2.93}$
+& $ 43.90^{+  2.76}_{ -2.73}$
+& $ 33.23^{+  2.40}_{ -2.43}$
+& $ 24.74^{+  2.42}_{ -2.52}$
+\\
+${\gamma^0_X/\gamma^0_V-1}$
+& $  0.62^{+  0.06}_{ -0.05}$
+& $  0.33^{+  0.03}_{ -0.03}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.24^{+  0.01}_{ -0.01}$
+& $ -0.44^{+  0.03}_{ -0.03}$
+\\
+$\gamma^1_X$
+& $ -0.29^{+  5.63}_{ -5.29}$
+& $ -7.82^{+  4.70}_{ -4.52}$
+& $-14.71^{+  3.79}_{ -3.78}$
+& $-12.48^{+  3.21}_{ -3.23}$
+& $-15.79^{+  2.98}_{ -2.99}$
+\\
+${\gamma^1_X/\gamma^1_V-1}$
+& $ -0.98^{+  0.29}_{ -0.50}$
+& $ -0.47^{+  0.15}_{ -0.25}$
+& $  0.00^{+  0.00}_{  0.00}$
+& $ -0.15^{+  0.04}_{ -0.04}$
+& $  0.07^{+  0.18}_{ -0.12}$
+\\
+$\sigma_p \phi_X$
+& $ 0.010^{+ 0.009}_{-0.009}$
+& $-0.021^{+ 0.007}_{-0.007}$
+& $-0.021^{+ 0.006}_{-0.007}$
+& $-0.008^{+ 0.006}_{-0.006}$
+& $ 0.036^{+ 0.007}_{-0.007}$
+\\
+\hline
+\end{tabular}
+\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~II in \S\ref{modelII:sec}.\label{global2:tab}}
+\end{table}
 

### 2017-11-22 fitzf1.py

@@ -103,11 +103,12 @@ for i in xrange(fit['gamma'].shape[0]):
 
 kappa = numpy.array(kappa)
 
-print "R1 (1/kappa1) terms"
+print "R1 (1/kappa1) term"
 dum1, dumm, dump =  numpy.percentile(kappa[:,0,0]/kappa[:,0,1],(50,50-34,50+34))
 print "{:.2f}^{{+{:.2f}}}_{{{:.2f}}}".format(dum1,dump-dum1,dumm-dum1)
+print "1/kappa2 term"
 dum1, dumm, dump =  numpy.percentile(kappa[:,1,1]/kappa[:,1,0],(50,50-34,50+34))
-print "{:.4f}^{{+{:.4f}}}_{{{:.4f}}}".format(dum1,dump-dum1,dumm-dum1)
+print "{:.2f}^{{+{:.2f}}}_{{{:.2f}}}".format(dum1,dump-dum1,dumm-dum1)
 
 
 print "projection of gamma0, gamma1 onto Fitzpatrick plane"
@@ -115,8 +116,6 @@ proj=numpy.array(proj)
 dum1, dumm, dump =  numpy.percentile(proj,(50,50-34,50+34),axis=0)
 print "{:.4f}^{{+{:.4f}}}_{{{:.4f}}}".format(dum1[0],dump[0]-dum1[0],dumm[0]-dum1[0])
 print "{:.4f}^{{+{:.4f}}}_{{{:.4f}}}".format(dum1[1],dump[1]-dum1[1],dumm[1]-dum1[1])
-
-wefwe
 
 tmat = []
 res = []
@@ -202,18 +201,18 @@ a = Arrow3D([0,cs[1][0]/dum],[0,cs[1][2]/dum],[0,cs[1][4]/dum], mutation_scale=1
 ax.add_artist(a)
 
 dum  = numpy.sqrt(dAdAv[0]**2+dAdAv[2]**2+dAdAv[4]**2)
-ax.plot([0,dAdAv[0]/dum],[0,dAdAv[2]/dum],[0,dAdAv[4]/dum],label=r'$\hat{a(X)}$',ls='--',color='blue')
+ax.plot([0,dAdAv[0]/dum],[0,dAdAv[2]/dum],[0,dAdAv[4]/dum],label=r'$a_X$',ls='--',color='blue')
[…]

### 2017-11-22 fitzf3_x1.py

@@ -26,7 +26,7 @@ class Arrow3D(FancyArrowPatch):
 mpl.rcParams['font.size'] = 14
 
 # Get the data
-f = open('fix3.pkl','rb')
+f = open('fix3_x1.pkl','rb')
 (fit, _) = pickle.load(f)
 f.close()
 
@@ -110,10 +110,6 @@ cross = numpy.dot(dAdebv, dAdAv)
 a = numpy.array([[norm_dAdAv,cross],[cross,norm_dAdebv]])
 a_save = numpy.array(a)
 
-
-a = numpy.array([[norm_dAdAv,cross],[cross,norm_dAdebv]])
-a_save = numpy.array(a)
-
 # calculate the projection onto the plane
 proj=[]
 kappa=[]
@@ -143,6 +139,7 @@ proj=numpy.array(proj)
 dum1, dumm, dump =  numpy.percentile(proj,(50,50-34,50+34),axis=0)
 print "{:.4f}^{{+{:.4f}}}_{{{:.4f}}}".format(dum1[0],dump[0]-dum1[0],dumm[0]-dum1[0])
 print "{:.4f}^{{+{:.4f}}}_{{{:.4f}}}".format(dum1[1],dump[1]-dum1[1],dumm[1]-dum1[1])
+
 
 tmat = []
 res = []
@@ -279,14 +276,14 @@ ax.set_zlabel(r'$\hat{I}$',labelpad=9,rotation=0)
 ax.xaxis.set_ticks(numpy.arange(-.5,1.1,.25))
 ax.yaxis.set_ticks(numpy.arange(-.8,.81,.4))
 ax.view_init(elev=2, azim=-114)
-pp = PdfPages("output_fix3/plane0.pdf")
+pp = PdfPages("output_fix3_x1/plane0.pdf")
 # plt.tight_layout()
 plt.savefig(pp,format='pdf',bbox_inches='tight')
 pp.close()
 ax.view_init(elev=7, azim=-165)
 ax.yaxis.set_ticks(numpy.arange(-.75,.76,.25))
 ax.xaxis.set_ticks(numpy.arange(-.5,.76,.5))
-pp = PdfPages("output_fix3/plane1.pdf")
+pp = PdfPages("output_fix3_x1/plane1.pdf")
 # plt.tight_layout()
 plt.savefig(pp,format='pdf',bbox_inches='tight')
 pp.close()
[…]

### 2017-11-26 submit/fix.tex
still ongoing fiex

@@
 
-In the analysis of this and other sections of this article,
-the posterior of the model parameters is evaluated using Hamiltonian Monte Carlo with a No-U-Turn
-Sampler as implemented in
-STAN \citep{stan}.  We run eight chains, each with 5000 iterations of which
-half are used for warmup.
-Tests have revealed no evidence for the non-convergence of the MCMC run.
-STAN provides output statistics to assess
-the convergence of the output Markov chains.
-The 
-potential scale reduction statistic, $\hat{R}$
-(in this paragraph not to be confused with the synthetic $R$ magnitude)
-\citep{Gelman92}, measures the convergence of the target distribution
-in iterative simulations 
-by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
-$N_{\mathit{eff}}$ is an estimate of the number of independent draws.
-The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.
-The
-output also gives  $N_{\mathit{eff}} \gg 100$ for all parameters, indicating that all are densely sampled.
-
 All elements of the two $\vec{\gamma}$ parameter vectors 
@@
 
-For $\vec{\gamma}^1$ we find  $\kappa^{-1}_2=0.03^{+0.04}_{-0.04}$, meaning that this vector's direction is consistent with being parallel to $a_X$
-(also seen visually in Figure~\ref{plane:fig}.)
-That is,   $\vec{\gamma}^1$  captures magnitude variations that occur given fixed $E^F(B-V)$.
+In the above context, the direction of the $\vec{\gamma}^1$ vector is described by $\kappa_2$.
+The prior that $g_0$ and  $g_1$ are uncorrelated leads  to  $\kappa_2$ being determined
+by the sample 
+distribution of $A^F_V$ and $E^F(B-V)$.  In this article, we do not further consider the direction of
+$\vec{\gamma}^1$ but rather focus on the distribution of the per-supernova parameters.
+
+%
+%We now consider the direction of $\vec{\gamma}^1$. 
+%Different supernovae are expected to encounter dust with different $R^F$;
+%having  associated $\vec{\gamma}^0$ with
+%the extinction from a single effective
+%$\langle R^F_{\mathit{eff}}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
+%away from that effective value.
+%Let us introduce a new parameter for each supernova, $\delta R$, such that 
+%$A^F =\langle R^F_{\mathit{eff}}\rangle(1-  \delta R) E^F(B-V)$.
+%Variations in the value of  $\delta R$, with the prior of the non-correlation between 
+%the coefficients in Eqn.~\ref{newdust:eqn},
+%lead 
+%to 
+%\begin{equation}
+%\kappa_2 =\langle R^F_{\mathit{eff}}\rangle \left(1- \frac{\mbox{Var}(\delta R \times E^F(B-V))}{\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))}\right).
+%\end{equation}
+%From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
+This result indicates that there is a small but significant covariance between  extinction contributions due to
+%fractional deviations from an effective $R^F$ and
+%the color-excess parameter $E^F(B-V)$.
+%
+%
+%For $\vec{\gamma}^1$ we find  $\kappa^{-1}_2=0.03^{+0.04}_{-0.04}$, meaning that this vector's direction is consistent with being parallel to $a_X$
+%(also seen visually in Figure~\ref{plane:fig}.)
+%That is,   $\vec{\gamma}^1$  captures magnitude variations that occur given fixed $E^F(B-V)$.
 
@@
 $x_1$, that is related to magnitudes with linear coefficients $\zeta$. 
-What is $x_1$ reference?
 The model reads as
@@
 \subsection{Results}
-
-This section describes the evaluated posterior of the model parameters.  Before doing so, we show that the model provides
-a fair representation of the data.
-As a diagnostic that the model results do not give catastrophically poor color predictions and are not pulled by extreme
-outlying data, shown in Figure~\ref{residual:fig} are plots of observed  versus
+\subsubsection{Analysis Method and Validation}
+
+In the analysis of this and other sections of this article,
+the posterior of the model parameters is evaluated using Hamiltonian Monte Carlo with a No-U-Turn
+Sampler as implemented in
+STAN \citep{stan}.  We run eight chains, each with 5000 iterations of which
+half are used for warmup.
+Tests have revealed no evidence for the non-convergence of the MCMC run.
+STAN provides output statistics to assess
+the convergence of the output Markov chains.
+The 
+potential scale reduction statistic, $\hat{R}$
+(in this paragraph not to be confused with the synthetic $R$ magnitude)
+\citep{Gelman92}, measures the convergence of the target distribution
+in iterative simulations 
+by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
+$N_{\mathit{eff}}$ is an estimate of the number of independent draws.
+The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.
+The
+output also gives  $N_{\mathit{eff}} \gg 100$ for all parameters, indicating that all are densely sampled.
+
+The algorithm is extensively tested with simulated data with known input signals and measurement uncertainties similar to those of our dataset.
+Stacks of the posteriors from 100 simulated datasets  exhibit no biases that are significant relative to the statistical uncertainties of a single posterior.
+
+The posterior that will be shown in  \S\ref{results3global:sec} exhibits a 
+confined peak, exhibiting no evidence that the MCMC has not failed to converge.
+
+The model provides a fair representation of the data, as seen in the difference between the data and the model prediction.
+Figure~\ref{residual:fig} has plots of the observed  versus
 model-expectation colors (including  supernova-specific spectral features, light-curve shape $\gamma g$, and $\phi p$ terms) for four selected colors,
-and the histogram of their differences.  The residuals of the data away from the model have a compact Gaussian-like appearance, and
-show no bias with respect to observed color.
+and the histogram of their differences.  
+There are no extreme residuals 
+from catastrophically poor color predictions.  There are no apparent trends between residuals and observed
+color.   The residuals of the data away from the model have a compact Gaussian-like appearance.
 
@@
    \centering
-   \includegraphics[width=5.2in]{../output_fix3_x1/residual.pdf} 
+   \includegraphics[width=4in]{../output_fix3_x1/residual.pdf} 
             \caption{Observed  versus
@@
 
+This suite of tests lend confidence in our model and the validity of the derived posterior.
+
+\subsubsection{Global Parameter Posterior Results}
+\label{results3global:sec}
 Results from our analysis are shown through contours of the posterior surface for pairs of global parameters grouped by filter, 
@@
 Within the finite number of generated links, the MCMC chains do not migrate to the parity-degenerate solution of $\vec{\gamma}$ and $g$.
-Each chain converges to one of the  $\vec{\phi}$--$p$ degenerate solutions, away from which it does not migrate.  The 
-confined peak of the posterior surface, in addition to the MCMC-convergence tests described in  \S\ref{results1:sec}, provide evidence that the MCMC has not failed to converge.
+Each chain converges to one of the  $\vec{\phi}$--$p$ degenerate solutions, away from which it does not migrate.
 
@@
 
-We find significant non-zero values for $\vec{\alpha}$, $\vec{\beta}$, and $\vec{\eta}$ indicating that
+\subsubsection{$\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\zeta}$: Cofactors of Observables}
+The cofactors  $\vec{\alpha}$, $\vec{\beta}$, and $\vec{\eta}$ have  significant non-zero values,  meaning that
 $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$ are indicators of broadband
-colors at peak
-as expected.  The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is also an indicator
+colors at peak.  The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is also an indicator
 of broadband colors.
@@
 and exists
-in our sample as is shown late in  this section.  It is not surprising that our analysis does not entirely distinguish between
-their influence on supernova colors. Nevertheless, their posteriors are bounded and inconsistent with zero, so they do convey independent information.
-It is for this reason  that Model~III is highlighted in this article over Model~II.
-
-The posterior gives a significant magnitude influence of the $p$ parameter.
-The minimum value for $\sigma_p$ over all Monte Carlo chains is 0.039~mag and its 
-68\% credible interval is $\sigma_p=0.049^{+ 0.004}_{-0.003}$~mag. 
-The median data color uncertainty of 0.010~mag (the maximum is 0.042~mag) so we conclude that
-the is not a due to spurious noise.
-
-The chromatic effect of $\vec{\phi}$ is visualized in Figure~\ref{phiratio:fig}, which
-gives a different perspective of the posterior using the statistic $\phi_X/\phi_{\hat{I}}-1$.
-Unlike with $\gamma$, we normalize $\phi$ to $\hat{U}$ because the uncertainty in $\phi_{\hat{B}}-\phi_{\hat{V}}$ is relatively large with
-credible intervals that easily cross zero.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-      \includegraphics[width=5.2in]{../output_fix3_x1/phiratio.pdf}
-   \caption{Model~III median values  and corresponding 68\% intervals for $\phi_X/\phi_{\hat{I}}$ in the 5 bands.
-   A dotted line at zero is shown for reference.
-   \label{phiratio:fig}}
-\end{figure}
+in our sample as is shown later in \S\ref{results3per:sec}.  
+Nevertheless the $\vec{\zeta}$ and $\vec{\beta}$   posteriors are bounded and inconsistent with zero, indicating that
+ $x_1$ and $EW_{Si}$ do convey independent color information.
+For this reason  Model~III is highlighted in this article over Model~II.
+
+\subsubsection{$\vec{\gamma}^0$, $\vec{\gamma}^1$: Cofactors of Extrinsic Latent Parameters}
 
 As with Model~I in \S\ref{modelI:sec}, all elements of the two $\vec{\gamma}$ parameter vectors 
-describing intrinsic color
+describing extrinsic color
 are significantly non-zero with 
@@
 our Monte Carlo chains for $\vec{\gamma}$ extending to 0 (see Figures~\ref{global1:fig}--\ref{global5:fig}).
-The direction of the vector is shown in Figure~\ref{plane3:fig}.
+The direction of the vector in the ${\hat{U}}{\hat{V}}{\hat{I}}$-subspace is shown in Figure~\ref{plane3:fig}.
 The posterior gives a quadratic fraction of $0.9996^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ projected onto the plane defined by
@@
 $0.959^{+0.015}_{-0.029}$.
-The corresponding 68\% credible is $R^F_{\mathit{eff}}=2.40^{+0.15}_{-0.15}$.
+The   $\vec{\gamma}$  vectors project  onto $R^F_{\mathit{eff}}=2.40^{+0.15}_{-0.15}$.
+This  is consistent with the $R_V=2.5$ found in the supernova samples of \citet{2011ApJ...729...55F}, and the
+center  of the range of per-supernova $R^F$ values found in the samples of \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}.
+Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are associated dust extinction.
+Further discussion on this association is given in the discussion of $g_0$ and $g_1$  in \S\ref{g0g1:sec}.
 
@@
 
-An intuitive way to consider the effect of $\vec{\gamma}^1$ is through the deviation from linearity in the color-magnitude diagram.
-A matrix such as the one in  Eq.~\ref{trans_I:eqn} is used to transform this $\{g_0, g_1\}$ into an $\{A_V^F, E^F(B-V)\}$ pair
-(modulo additive constants)  for each link in the Monte Carlo chains. A plot showing the expected values and 68\% credible intervals of these parameters
-for our supernova
-sample is shown in Figure~\ref{kk:fig}. 
-For reference, a line that represents $R^V_{\mathit{eff}}=2.4$ is overplotted.  The majority of supernovae lie within a narrow range above the line
-meaning they have $R^F > R^V_{\mathit{eff}}$,
-while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{\mathit{eff}}$.  
-These findings are consistent with previous results:
-using fixed dust-extinction models,
-\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
-A per supernova determination of $R^F$ requires the specification of the magnitude and colors of supernovae that experience
-no dust, which is unspecified in our model.
+\subsubsection{$\sigma_p \vec{\phi}$: Cofactor of Intrinsic Latent Parameter}
+
+The posterior shows a significant color influence of the $p$ parameter.
+The minimum value for $\sigma_p$ over all Monte Carlo chains is 0.039~mag and its 
+68\% credible interval is $\sigma_p=0.049^{+ 0.004}_{-0.003}$~mag. 
+This is significantly larger than the median data color uncertainty of 0.010~mag (the maximum is 0.042~mag).
+The evaluation of 100 simulated null data sets with no third color parameter produces no median $\sigma_p$'s  as
+high as that of the data, so we assign a $>99$\% confidence in the detection of this third color term.
+
+The values of $\vec{\phi}$ does not change  monotonically with wavelength, as is apparent  in 
+the combination $\phi_X/\phi_{\hat{V}}-1$ shown in Figure~\ref{phiratio:fig}.  They have the property that
+a reddening $\hat{B}-\hat{V}$ is associated with a bluing in $\hat{V}-\hat{R}$.  The color changes are largest
+in the extreme $\hat{U}$ and $\hat{I}$ bands. Absorption and re-emission of light
+over broad bands are the most obvious candidate for producing this behavior.
+This kind of behavior is already associated with SNe~Ia.
+\citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
+from doubly and singly ionized states, making the gas phosphorescent and efficient in redistributing energy from the UV/blue to redder
+wavelengths.  Qualitatively this would result in the structure for $\phi_X/\phi_V-1$ that we measure.
+We speculate that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth
+of the reionization front with respect to the core of the ejecta at peak, yielding the wavelength-dependent color behavior
+detected in this analysis.
 
@@
    \centering
-   \includegraphics[width=5.2in]{../output_fix3_x1/avebv_synth.pdf}
-      \caption{
-      Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $g_0$ and $g_1$ parameters, for the supernova in our sample.
-      Overplotted is a line with the slope expected for $R^F=2.4$.
-   \label{kk:fig}}
+      \includegraphics[width=4in]{../output_fix3_x1/phiratio.pdf}
+   \caption{Model~III median values  and corresponding 68\% intervals for $\phi_X/\phi_{\hat{V}}-1$ in the 5 bands.
+   A dotted line at zero is shown for reference.
+   \label{phiratio:fig}}
 \end{figure}
 
+We emphasize that
+although the $p\sigma_p \vec{\phi}$ colors have ben referred to as ``intrinsic'' due to its placement in the model, the analysis cannot quantitatively distinguish
+whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
+
+\subsubsection{Per-Supernova Parameter Results}
+\label{results3per:sec}
 Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$,
-$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})k_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})k_1$, and $p\sigma_p\phi_{\hat{I}}$.
-Their Pearson correlation coefficients  are given in the matrix
+$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $p\sigma_p\phi_{\hat{I}}$.
+The distributions of the Monte Carlo links for all supernovae are shown in Figure~\ref{perobject3:fig}.
+There is a core concentration in the  parameter-space, with around eight objects that occupy its outskirts.
+Many outliers appear in the red tail of $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, as would be expected for the (infrequent) selection of supernovae
+heavily extinguished by host-galaxy dust.
+
+The Pearson correlation coefficients of the per-supernova parameters are given in the matrix
 \begin{multline}
@@
 \end{multline}
-To aid visualization, only the upper triangular part of the otherwise symmetric matrix is shown and the corresponding feature label is given on
+To aid readability, only the upper triangular part of the otherwise symmetric matrix is shown and the corresponding feature label is given on
 the diagonal.
 
-We find $>2 \sigma$ correlations between our extrinsic color-excess parameters and the input features  $EW_{Ca}$,
-$EW_{Si}$, and $x_1$.
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=5.2in]{../output_fix3_x1/perobject_corner.pdf} 
+   \caption{
+   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and  $p\sigma_p\phi_{\hat{I}}$, as well as the grey offset
+$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
+   \label{perobject3:fig}}
+\end{figure}
+
+An extensive discussion of the correlations between the spectral features  and light-curve parameters of the SNfactory data
+set can be found in \citet{chotard:thesis, leget:thesis, 2017Chotard}. 
+We here confine ourselves to noting the strong anti-correlation between $EW_{Si}$ and $x_1$, which was alluded
+to in \S\ref{results3global:sec} when interpreting the correlation between the cofactors $\vec{\beta}$ and $\vec{\zeta}$ that connect them with magnitudes.
+
+\subsubsection{$g_0$, $g_1$: Extrinsic Parameters}
+\label{g0g1:sec}
+
+There are $>2 \sigma$ correlations between our extrinsic color-excess parameters $g_0$, $g_1$
+(equivalently $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$) and the input features  $EW_{Ca}$,
+$EW_{Si}$, and $x_1$.  This translates to correlations between dust and the input features, given the association
+of  $\vec{\gamma} g$ with dust.
 The correlation of $x_1$ with with host-galaxy (including dust) properties is known 
 \citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
+
+The per-supernova parameter $\gamma^0_{\hat{V}} g_0$ can be associated with the $\hat{V}$-band
+extinction for an effective $R^F_{\mathit{eff}}=2.40$ dust, as
+$\vec{\gamma}_0$  has nearly the same effect on color as dust extinction at that constant $R^F$.
+Figure~\ref{k0_med:fig} shows the histogram of
+per-supernova
+median values
+from the Monte Carlo chains
+and the  stack of the posteriors of all supernovae  for $\gamma^0_{\hat{V}} g_0$ 
+relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} g_0|_0$.
+(Subtracting the value of the one supernova suppresses correlated errors in $g_0$ common to all supernovae.)
+The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
+with
+simulations based on expected dust distributions
+within galaxies and the distribution of galaxy orientations with respect to the observer,
+which determine column densities along the lines of sight toward supernovae that are consistent with observations
+\citep{1998ApJ...502..177H, 2007ApJ...659..122J}.  
+We emphasize that unlike other analyses,
+this distribution is given by the data, and so is not dependent on any knowledge or prior
+for the distribution of dust extinction the SN population is expected to suffer.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=2.8in]{../output_fix3_x1/deltagamma0_med.pdf}
+   \includegraphics[width=2.8in]{../output_fix3_x1/deltagamma1_med.pdf}
+      \caption{
+      Normalized stack of the posteriors of all supernovae  and histogram 
+      of  per-supernova 
+median values of: (left) $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$, which is associated with the $A^F_V$ of an $R^F_{\mathit{eff}} \sim 2.4$ dust model;
+(right) $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$,
+which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{\mathit{eff}}\rangle$ value.
+   \label{k0_med:fig}}
+\end{figure}
+
+An instructive way to consider the  $\{g_0, g_1\}$ parameters
+is through their transformation to  $\{A_V^F, E^F(B-V)\}$ (modulo additive constants)   through the
+matrix in  Eq.~\ref{trans_I:eqn}.
+A plot showing the expected values and 68\% credible intervals of these parameters
+for our supernova
+sample is shown in Figure~\ref{kk:fig}. 
+For reference, a line that represents $R^V_{\mathit{eff}}=2.4$ is overplotted.  The majority of supernovae lie within a narrow range above the line
+meaning they have $R^F > R^V_{\mathit{eff}}$,
+while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{\mathit{eff}}$.  
+The negative tail in  $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$ of the right plot of Figure~\ref{k0_med:fig} is directed toward smaller $R^F$.
+These findings are consistent with previous results:
+using fixed dust-extinction models,
+\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
+A per supernova determination of $R^F$ requires the specification of the magnitude and colors of supernovae that experience
+no dust, which is unspecified in our model.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{../output_fix3_x1/avebv_synth.pdf}
+      \caption{
+      Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $g_0$ and $g_1$ parameters, for the supernova in our sample.
+      Overplotted is a line with the slope expected for $R^F=2.4$.
+   \label{kk:fig}}
+\end{figure}
+
+\subsubsection{$p$: Intrinsic Parameter}
+\label{p:sec}
+
 There is no correlation between the  intrinsic parameter $p$ and the other features.
-As alluded to earlier, the feature $EW_{Si}$ is strongly correlated with $x_1$.
-An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
-and \citet{leget:thesis}.
+The correlation coefficients between the ``intrinsic''  ($p\sigma_p\phi_{\hat{I}}$) and ``extrinsic''
+($E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$)  parameters
+are consistent with zero.
+Their independence implies that a single physical parameter is not being artificially attributed to two
+model parameters.  One could have
+worried this might
+occur since our linear model does not precisely
+describe the non-linearity between broad-band magnitudes and dust parameters. A
+correlation 
+between the parameters would have complicated any claims of the detection of a third independent supernova parameter.
+
+The distributions of extrinsic, $E_\gamma({\hat{B}}-{\hat{V}}) \equiv (\gamma^0_{\hat{B}} -\gamma^0_{\hat{V}}) g_0
++ (\gamma^1_{\hat{B}} -\gamma^1_{\hat{V}}) g_1$, and intrinsic, $E_p({\hat{B}}-{\hat{V}}) \equiv   p \sigma_p (\phi_{\hat{B}}-\phi_{\hat{V}})$,
+sources of color excess 
+  are shown in Figure~\ref{ebv:fig} as the  stack of the posteriors of all supernovae 
+ and the histogram of per-supernova median values.
+ (These values are relative
+to
+ those of an arbitrary supernova in order to null out correlated errors.)
+The standard deviations of  $E_\gamma({\hat{B}}-{\hat{V}})$ and $E_p({\hat{B}}-{\hat{V}})$ are
+%-----
+0.085
+and 0.011
+%-----
+mag respectively.
+The latter is comparable to its measurement uncertainty per-supernova.
+Previous analyses confined to $\hat{B}$ and $\hat{V}$ colors would have difficulty in detecting the intrinsic term.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{../output_fix3_x1/ebv.pdf}
+ %  \includegraphics[width=2.8in]{../output_fix3_x1/ebv_delta.pdf}
+      \caption{Left:  Stack of the posteriors of all supernovae of the external $E({\hat{B}}-{\hat{V}})$ 
+      (including contributions from both $k_0$, $k_1$, and $D$)
+      and
+   internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
+   Right:  Stack of the posteriors of all supernovae  and histogram of the per-supernova
+   medians of $E_\delta({\hat{B}}-{\hat{V}})$ on an enlarged scale.
+   \label{ebv:fig}}
+\end{figure}
+
+A correlation between Hubble residual and host-galaxy mass
+was first noted by \citet{2010ApJ...715..743K,2010MNRAS.406..782S}, a signal confirmed to exist in the SNfactory
+sample \citep{2013ApJ...770..108C}.
+This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
+\citetalias{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
+To explore whether the Hubble residual may be due to unaccounted color,
+we plot in Figure~\ref{childress:fig} our intrinsic parameter
+mass versus $A_{\delta {\hat{U}}}-A_{\delta {\hat{U}}}|_0$  (subtracting out a random supernova
+to suppress correlated errors)
+for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
+The average $A_{\delta {\hat{U}}}$'s of the two subsamples are
+%---
+$\langle A_{\delta {\hat{U}}} \rangle=   0.000 \pm {    0.011 }$ mag,
+$\langle A_{\delta {\hat{U}}} \rangle= 0.003 \pm {    0.009 }$ mag
+for low- and high-mass hosts respectively: there is no significant difference in $A_{\delta {\hat{U}}}$ between them.
+
+For supernovae with host-properties from Childress, we plot $p$ as a function of host-galaxy mass.
+$  -0.0186 \pm {    0.0034 }$
+$  -0.0293 \pm {    0.0033 }$
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{../output_fix3_x1/childress.pdf} 
+   \caption{Intrinsic parameter
+ $p$ as a function of host-galaxy mass
+    \label{childress:fig}}
+\end{figure}
+
+\subsubsection{$\Delta$: Magnitude Offset}
+\label{Delta:sec}
 
@@
    \centering
-   \includegraphics[width=5.2in]{../output_fix3_x1/deltaDelta_hist.pdf} 
+   \includegraphics[width=4in]{../output_fix3_x1/deltaDelta_hist.pdf} 
    \caption{
@@
 
-For supernovae with host-properties from Childress, we plot $p$ as a function of host-galaxy mass.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=3.5in]{../output_fix3_x1/childress.pdf} 
-   \caption{Intrinsic parameter
- $p$ as a function of host-galaxy mass
-    \label{childress:fig}}
-\end{figure}
-
 XXXXXX
@@
 \section{Supernova Model I: Two Extrinsic Parameters}
-\label{model:sec}
-
-In what is  referred to as Model~I, peak brightness
-SN~Ia broadband magnitudes and colors are 
-directly
-correlated with
-spectral features
-at peak.
-Equivalent widths and line positions are considered in the model because their localization in wavelength
-makes their values insensitive to 
-broadband color variations.
-These intrinsic spectral  parameters may not deterministically predict magnitudes, but rather do so with some intrinsic dispersion.
-The per-supernova intrinsic magnitudes are then
-modified by an extrinsic 
-latent
-physical process (that could be attributed to dust) 
-whose effect is manifest in the
-apparent magnitudes and colors
-that are subsequently measured by the observer.
 
@@
 \subsection{Results}
-\label{results:sec}
 
@@
 
-We
-now turn to
-the specific choice of $\vec{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust-extinction model. 
-Our linear model would be satisfied by any two independent vectors  that span
-the plane defined by the $\vec{\gamma}$ vectors.  While
-Eq.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
-their corresponding parameters 
-$A_V$ and 
-$E(B-V)$, the linear dust model 
-alternatively
-could be written in terms of any two other basis vectors  $\vec{a}+\kappa_1 \vec{b}$
-and $\kappa_2 \vec{a} + \vec{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
-In this basis, the model is then
-\begin{equation}
-A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a_X+\kappa_1 b_X \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a_X + b_X)],
-\label{newdust:eqn}
-\end{equation}
-with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  equal to  linear combinations of the original parameters.
-
-Our posterior
-includes a prior in which the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
-The parameters $\kappa_1$ and $\kappa_2$ are set by this prior.
-If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
-to    $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ being uncorrelated in the supernova sample.
-A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
-All color changes would then be confined to the $a_X+\kappa_1 b_X$ direction.
-This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
-We use this interpretation to assign  $\langle R^F_{\mathit{eff}}\rangle = \kappa_1^{-1}$ as
-the
-ensemble mean
-effective total-to-selective extinction of our sample.
-The preferred values for $\kappa$ can be determined from the matrix elements of Eq.~\ref{trans_I:eqn}, 
-giving
-$\kappa^{-1}_1=2.82/1.15 =2.44$.
-Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.44$.
-From the Monte Carlo chains, we find a 68\% credible interval for  $\langle R^F_{\mathit{eff}}\rangle$ of 2.26--2.63.
-
-Given that
-$\vec{\gamma_0}$  has nearly the same effect on color as dust extinction with constant $R^F$,
-the distribution of
-our parameter $\gamma^0_{\hat{V}} k_0$ can be compared with the expected distribution
-of $A^F_V$.
-Figure~\ref{k0_med:fig} shows the histogram of
-per-supernova
-median values
-from the Monte Carlo chains
-and the  stack of the posteriors of all supernovae  for $\gamma^0_{\hat{V}} k_0$ 
-relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} k_0|_0$.
-(Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
-The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
-with
-simulations based on expected dust distributions
-within galaxies and the distribution of galaxy orientations with respect to the observer,
-which determine column densities along the lines of sight toward supernovae that are consistent with observations
-\citep{1998ApJ...502..177H, 2007ApJ...659..122J}.  
-We emphasize that unlike other analyses,
-this distribution is given by the data, and so is not dependent on any knowledge or prior
-for the distribution of dust extinction the SN population is expected to suffer.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{deltagamma0_med.pdf}
-   \includegraphics[width=2.8in]{deltagamma1_med.pdf}
-      \caption{
-      Normalized stack of the posteriors of all supernovae  and histogram 
-      of  per-supernova 
-median values of: (left) $\gamma^0_{\hat{V}} k_0-\gamma^0_{\hat{V}} k_0|_0$, which is associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model;
-(right) $\gamma^1_{\hat{V}} k_1-\gamma^1_{\hat{V}} k_1|_0$,
-which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{\mathit{eff}}\rangle$ value.
-   \label{k0_med:fig}}
-\end{figure}
-
-As a check of our analysis implementation and our
-interpretation of $\langle R^F_{\mathit{eff}}\rangle$, we generate ten simulated datasets with the same numbers and uncertainties as our data, based on a
-SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust-extinction model.  The supernovae
-are assigned $E^F(B-V)$ parameters equal to the ${\hat{B}}-{\hat{V}}$ color excesses determined in our sample
-(making an approximative correspondence between our observed top-hat filter colors and the 
-model parameter $E^F(B-V)$) , and $R^F$ values drawn from a log-normal
-distribution with a mean of $\ln{2.5}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
-measurement uncertainty are the only sources of variation in magnitudes.  We stack the results of the 10 simulations that together yield a median
-$\langle R^F_{\mathit{eff}}\rangle$ of 2.53, showing that our effective value is close to the  $R^F=2.5$ input into the simulations.
-
-To summarize, in this subsection
-we conclude that the combination of
-$\{k_0, k_1\}$ describe for the most part the combination of the $\{A^F_V, E^F(B-V)\}$ parameters used
-in standard models of Milky Way dust extinction.  
-This conclusion is based on the
-near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that 
-the distribution of $k_0$ is consistent with the expected distribution of $A^F_V$.
-Nevertheless, there do remain some small inconsistencies between our numbers and expectations from
-previous dust-extinction
-models.
-
 \section{Supernova Model II: Two Extrinsic Parameters, One Intrinsic Parameter}
-\label{model2:sec}
+
 \subsection{Model}
-In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
-two extrinsic parameters yield magnitude variations
-similar
-to those from  two-parameter dust models established for stars in the Milky Way, LMC, and SMC.
-In this Section, our model is extended
-to probe the existence of
-an additional
-color parameter.
-An extended model, referred to as Model~II, is written as
-\begin{equation}
-\begin{pmatrix}
-{\hat{U}}\\{\hat{B}}\\{\hat{V}}\\{\hat{R}}\\{\hat{I}}
-\end{pmatrix}
-\sim \mathcal{N}
-\left(
-\Delta +
-\begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} + \delta_{\hat{U}} D\\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} + \delta_{\hat{B}} D \\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} + \delta_{\hat{V}} D\\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} + \delta_{\hat{R}} D\\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si} + \delta_{\hat{I}} D
-\end{pmatrix}
-,C_{c}
-\right)
-%\label{ewsiv2:eqn}
-\end{equation}
-\begin{equation}
-\begin{pmatrix}
-{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
-\end{pmatrix}
-\sim \mathcal{N}
-\left(
-\begin{pmatrix}
-{\hat{U}} +\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} k_0 +\gamma^1_{{\hat{B}}} k_1 \\
-{\hat{V}}+\gamma^0_{{\hat{V}}} k_0+\gamma^1_{{\hat{V}}} k_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} k_0 + \gamma^1_{{\hat{R}}} k_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} k_0+\gamma^1_{{\hat{I}}} k_1\\
-EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
-\end{pmatrix}
-,C
-\right).
-%\label{dust2:eqn}
-\end{equation}
-In all aspects Model~II is identical to Model~I except for the addition of the term $\vec{\delta} D$: for $\vec{\delta}=0$ and arbitrary $D$, Model II
-and Model~I are the same.
-The new term contributes to the mean intrinsic
-absolute magnitudes. 
-Each supernova has an intrinsic,
-dimensionless
-$D$ parameter that is linearly related to
-absolute magnitudes through the global coefficients $\vec{\delta}$
-with mag units. 
-As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
-its effects on broadband magnitudes.
-
-The $\vec{\delta} D$ term contributes to the means of the Normal distribution in Eq.~\ref{ewsiv2:eqn}, together with the spectral-feature terms.
-However, switching the placement of 
-$\vec{\delta} D$ term from Eq.~\ref{ewsiv2:eqn} to Eq.~\ref{dust2:eqn}, i.e.\ from an intrinsic to extrinsic contribution,
-does not significantly affect the results, meaning that data are not constraining enough
-to identify $\vec{\delta} D$ as being physically intrinsic or extrinsic.
-However, we present in \S\ref{interpret:sec} a separate physical argument for the intrinsic interpretation of the new term.
-
-We impose
-$\langle D\rangle=0$
-to specify the zeropoint color.  We assign a prior on the amplitude of the ensemble of $D$ to break the
-degeneracy $\vec{\delta} \rightarrow a\vec{\delta}$, $D \rightarrow a^{-1}D$: as described
-in \S\ref{model:sec} this prior does not affect physics but aids in the convergence of fitting $D$ and $\vec{\delta}$ as independent parameters.
-A sign degeneracy in $a$ remains.
-In contrast to our previous experience with $\vec{\gamma}$ in Model~I, our MCMC chains migrate between
-the sign-degenerate solutions in  $\vec{\delta}$.  We make
-no attempt to resolve this degeneracy in the model.
-In the running of the Monte Carlo fit, the initial conditions and ranges for
-$\vec{\gamma}^0$ and $\vec{\gamma}^1$ were set to be in the neighborhood of the best fit of Model~I
-to maintain their correspondence between the two models.
-Our finite MCMC chains do not migrate away from these ranges.
-The
-initial step of the MCMC is at $\vec{\delta}=0$.
 
 \subsection{Results}
-
-The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  
-\color{blue}
-The $\delta$ parameters are normalized to $\hat{U}$ instead of $\hat{V}$, since the posterior of $\delta_{\hat{V}}$ covers zero.
-\color{black}
-Comparison with the
-results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
-are consistent  to well within 1$\sigma$ uncertainties.  The most significant change is in the reduction of the standard
-deviations of the magnitude residuals $\sigma_X$
-in the ${\hat{U}}$ and ${\hat{B}}$ bands.
-\color{blue}
-The variance captured by the first two eigenvectors of $C_c$ from Model~II is $4.7 \times 10^{-3}$ mag$^2$, as
-compared to  $6.4 \times 10^{-3}$ mag$^2$ from Model~I; this reduction shows the amount of intrinsic dispersion in Model~I
-that  is now attributed to the explicit $\delta D$ term.
-\color{black}
-
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|c|c|}
-\hline
-Parameters& $X={\hat{U}}$ &${\hat{B}}$&${\hat{V}}$&${\hat{R}}$&${\hat{I}}$\\ \hline
-$\alpha_X$
-&
-$0.0039^{+0.0009}_{-0.0009}$
-&
-$0.0013^{+0.0008}_{-0.0007}$
-&
-$0.0013^{+0.0006}_{-0.0006}$
-&
-$0.0013^{+0.0005}_{-0.0005}$
-&
-$0.0025^{+0.0005}_{-0.0004}$
-\\
-${\alpha_X/\alpha_{\hat{V}}-1}$
-&
-$   2.1^{+   1.4}_{  -0.6}$
-&
-$   0.0^{+   0.1}_{  -0.2}$
-&
-$  \dots $
-&
-$   0.0^{+   0.2}_{  -0.1}$
-&
-$   1.0^{+   1.1}_{  -0.5}$
-\\
-$\beta_X$
-&
-$ 0.032^{+ 0.003}_{-0.003}$
-&
-$ 0.025^{+ 0.002}_{-0.002}$
-&
-$ 0.026^{+ 0.002}_{-0.002}$
-&
-$ 0.021^{+ 0.002}_{-0.002}$
-&
-$ 0.020^{+ 0.002}_{-0.002}$
-\\
-${\beta_X/\beta_{\hat{V}}-1}$
-&
-$  0.24^{+  0.05}_{ -0.05}$
-&
-$ -0.02^{+  0.03}_{ -0.03}$
-&
-$   \dots$
-&
-$ -0.19^{+  0.01}_{ -0.01}$
-&
-$ -0.23^{+  0.03}_{ -0.03}$
-\\
-$\eta_X$
-&
-$-0.0002^{+0.0011}_{-0.0011}$
-&
-$-0.0000^{+0.0009}_{-0.0009}$
-&
-$0.0005^{+0.0008}_{-0.0008}$
-&
-$0.0005^{+0.0007}_{-0.0007}$
-&
-$-0.0002^{+0.0006}_{-0.0006}$
-\\
-${\eta_X/\eta_{\hat{V}}-1}$
-&
-$ -0.41^{+  2.27}_{ -1.94}$
-&
-$ -0.37^{+  1.59}_{ -1.26}$
-&
-$   \dots$
-&
-$ -0.10^{+  0.30}_{ -0.29}$
-&
-$ -0.80^{+  1.54}_{ -1.29}$
-\\
-$\gamma^0_X$
-&
-$ 61.66^{+  3.97}_{ -3.86}$
-&
-$ 50.09^{+  3.25}_{ -3.16}$
-&
-$ 37.41^{+  2.69}_{ -2.60}$
-&
-$ 28.81^{+  2.35}_{ -2.31}$
-&
-$ 20.76^{+  2.17}_{ -2.12}$
-\\
-${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
-&
-$  0.65^{+  0.06}_{ -0.05}$
-&
-$  0.34^{+  0.03}_{ -0.03}$
-&
-$   \dots$
-&
-$ -0.23^{+  0.01}_{ -0.01}$
-&
-$ -0.45^{+  0.03}_{ -0.03}$
-\\
-$\gamma^1_X$
-&
-$ -9.47^{+  3.70}_{ -4.37}$
-&
-$-11.09^{+  3.02}_{ -3.57}$
-&
-$-13.59^{+  2.47}_{ -2.81}$
-&
-$-12.82^{+  2.14}_{ -2.40}$
-&
-$-11.66^{+  2.25}_{ -2.32}$
-\\
-${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
-&
-$ -0.30^{+  0.19}_{ -0.21}$
-&
-$ -0.18^{+  0.11}_{ -0.12}$
-&
-$   \dots$
-&
-$ -0.06^{+  0.06}_{ -0.06}$
-&
-$ -0.15^{+  0.12}_{ -0.12}$
-\\
-${{\delta_X/\delta_{\hat{U}}-1}}$
-&
-$   \dots$
-&
-$ -0.22^{+  0.35}_{ -0.32}$
-&
-$ -0.73^{+  0.51}_{ -0.61}$
-&
-$ -0.91^{+  0.43}_{ -0.69}$
-&
-$ -1.17^{+  0.46}_{ -0.93}$
-\\
-$\sigma_X$
-&
-$ 0.053^{+ 0.009}_{-0.011}$
-&
-$ 0.018^{+ 0.012}_{-0.012}$
-&
-$ 0.020^{+ 0.004}_{-0.005}$
-&
-$ 0.010^{+ 0.008}_{-0.007}$
-&
-$ 0.040^{+ 0.006}_{-0.005}$
-\\
-\hline
-\end{tabular}
-\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
-\end{table}
-
-The posteriors of the $\vec{\delta}$ parameters are shown  in
-the left panel of
-Figure~\ref{deltacorner:fig}.
-In the full 5-dimensional space,
-the point $\delta_X=0$, i.e.\ the nested Model~I with no effect on magnitude by a third parameter,  lies on the 85\%-ile contour.
-Model~II has a  $\vec{\delta} \rightarrow -\vec{\delta}$, $D \rightarrow -D$ degeneracy that results in a bimodal posterior.
-To aid in the visualization of the results,
-we break this degeneracy by imposing  that the $D$ of the one supernova with the highest signal-to-noise be positive.
-The new posterior contours of $\vec{\delta}$ with this added
-condition are shown in 
-the right panel of
-Figure~\ref{deltacorner:fig}.
-The shapes of the new $\vec{\delta}$ posteriors are somewhat distorted compared to the original;
-despite its relatively strong signal-to-noise, the original posterior for $D$ for the selected supernova does have significance on both sides of zero,
-resulting in changes in the shape of the $\vec{\delta}$ posteriors when  $D$ is forced to be positive.   
-The 
-two parity-symmetric
-modes of $\delta_X$ are at $\mp 1.12$, $\mp 0.89$, $\mp 0.36$,  $\mp0.16$, $\pm0.21$~mag
-for $X={\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ respectively.
-The values of $\delta_X/\delta_{\hat{U}}-1$, which are insensitive to the scaling (including the sign) degeneracy, are shown in Figure~\ref{deltaratio:fig}.
-Unlike with $\gamma$, we normalize $\delta$ to $\hat{U}$ because the uncertainty in $\delta_{\hat{B}}-\delta_{\hat{V}}$ is relatively large with
-credible intervals that easily cross zero.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{delta_corner.pdf}
-     \includegraphics[width=2.8in]{delta_corner_flipped.pdf}
-   \caption{Left:  Model~II posterior contours for $\vec{\delta}$.
-   Right: The same posteriors after imposing that $D$ of the one supernova with highest signal-to-noise be positive.
-     Lines for $\vec{\delta}=0$ are overplotted.
-   \label{deltacorner:fig}}
-\end{figure}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-      \includegraphics[width=5.2in]{deltaratio.pdf}
-   \caption{Model~II median values  and corresponding 68\% intervals for $\delta_X/\delta_{\hat{U}}$ in the 5 bands.
-   A dotted line at zero is shown for reference.
-   \label{deltaratio:fig}}
-\end{figure}
-
-The distributions of both sources of color excess $E({\hat{B}}-{\hat{V}})$ and
- $E_\delta({\hat{B}}-{\hat{V}}) \equiv   (\delta_{\hat{B}}-\delta_{\hat{V}})D$ are shown in Figure~\ref{ebv:fig} as the  stack of the posteriors of all supernovae 
- and the histogram of per-supernova median values.
- (These values are relative
-to
- those of an arbitrary supernova in order to null out correlated errors.)
-The range of ${\hat{B}}-{\hat{V}}$ colors is $> 5 \times$ larger for the external contribution than for the
-intrinsic
-component.  
-The standard deviations of  the median $E_\gamma({\hat{B}}-{\hat{V}})$ and $E_\delta({\hat{B}}-{\hat{V}})$ are
-%-----
-0.075
-and 0.014
-%-----
-mag respectively.
-It should be noted that
-the $E_\delta({\hat{B}}-{\hat{V}})$ standard deviation is comparable to its measurement uncertainty per-supernova.
-Thus, since
-the color excesses of individual supernovae have low signal-to-noise,
-the significance of $\vec{\delta}$
-is drawn from the ensemble of objects.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{ebv.pdf}
-   \includegraphics[width=2.8in]{ebv_delta.pdf}
-      \caption{Left:  Stack of the posteriors of all supernovae of the external $E({\hat{B}}-{\hat{V}})$ 
-      (including contributions from both $k_0$, $k_1$, and $D$)
-      and
-   internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
-   Right:  Stack of the posteriors of all supernovae  and histogram of the per-supernova
-   medians of $E_\delta({\hat{B}}-{\hat{V}})$ on an enlarged scale.
-   \label{ebv:fig}}
-\end{figure}
-
-Each supernova is described by its parameters
- $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  $A_{\delta {\hat{U}}}=\delta_{\hat{U}} D$.
- Their Pearson correlation coefficients are given in the matrix
-\begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}),  A_{\delta {\hat{U}}}) =\\
-\begin{pmatrix}
-\begin{array}{rrrrrrr}
-\Delta& 0.01^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.07} & 0.10^{+0.07}_{-0.06} & 0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} \\
-\dots & EW_{Ca} & 0.10^{+0.04}_{-0.04} & -0.26^{+0.03}_{-0.03} & -0.04^{+0.06}_{-0.06} & -0.00^{+0.07}_{-0.08} & -0.00^{+0.08}_{-0.08} \\
-\dots  &\dots  &EW_{Si}& -0.14^{+0.03}_{-0.03} & -0.16^{+0.05}_{-0.05} & -0.03^{+0.08}_{-0.08} & 0.01^{+0.08}_{-0.08} \\
-\dots  &\dots  & \dots  & \lambda_{Si} & 0.03^{+0.05}_{-0.06} & 0.02^{+0.07}_{-0.08} & -0.01^{+0.08}_{-0.08} \\
-\dots &\dots & \dots &\dots  &E_{\gamma^0}({\hat{B}}-{\hat{V}})& 0.05^{+0.08}_{-0.08} & -0.01^{+0.07}_{-0.07} \\
-\dots & \dots  &\dots & \dots &\dots  &  E_{\gamma^1}({\hat{B}}-{\hat{V}}) & -0.00^{+0.07}_{-0.08} \\
-\dots  &\dots & \dots  & \dots & \dots &\dots  & A_{\delta {\hat{U}}} \\
-\end{array}
-\end{pmatrix}.
-\label{corr2p:eqn}
-\end{multline}
-Their values for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject2:fig}.
-There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
-Many outliers appear in the red tail of $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, as would be expected for the (infrequent) selection of supernovae
-heavily extinguished by host-galaxy dust.
-
-The priors of the correlation coefficients between the ``intrinsic''  ($A_{\delta {\hat{U}}}$) and ``extrinsic''
-($E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$)  parameters
-are set for their values to be uncorrelated. The output correlation is
-consistent with zero.
-Their independence implies that a single physical parameter is not being artificially attributed to two
-model parameters.  One could have
-worried this might
-occur since our linear model does not precisely
-describe the non-linearity between broad-band magnitudes and dust parameters. A
-correlation 
-between the parameters despite the prior would have complicated any claims of the detection of a third independent supernova parameter.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=5.2in]{perobject_corner.pdf} 
-   \caption{
-   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and $E_{\delta}({\hat{B}}-{\hat{V}})$, as well as the grey offset
-$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
-   \label{perobject2:fig}}
-\end{figure}
-
-The newly fitted $\vec{\gamma}$ and  $\vec{\delta}$ vectors (the latter normalized by $\delta_{\hat{U}}$) can be expressed 
-in terms of the $\vec{a}$ and $\vec{b}$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
-\begin{equation}
-\begin{pmatrix}
- \frac{\vec{\gamma}^0}{\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}}} \\
-\frac{\vec{\gamma}^1}{\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}}} \\
-\frac{\delta_X}{\delta_{\hat{U}}} \\
-\end{pmatrix}=
-\begin{pmatrix}
-\begin{array}{rr}
-2.88 & 1.16 \\
--5.00 & 0.73 \\
-0.24 & 0.46
-\end{array}
-\end{pmatrix} 
-\begin{pmatrix}
-\vec{a} \\
-\vec{b}
-\end{pmatrix}+
-\begin{pmatrix}
-\vec{\epsilon}_{\gamma^0} \\
-\vec{\epsilon}_{\gamma^1} \\
-\vec{\epsilon}_{\delta}
-\end{pmatrix},
-\label{model2trans:eqn}
-\end{equation}
-where the residual vectors
-\begin{align}
-\begin{split}
-\vec{\epsilon}_{\gamma^0} &=(0.07, -0.07, -0.07,  0.06,  0.02),\\
-\vec{\epsilon}_{\gamma^1} &=( -0.04, 0.14,  -0.24,  0.32, -0.22),\\
-\vec{\epsilon}_{\delta} &=(-0.05, 0.08,  -0.03,  -0.09, -0.12)
-\end{split}
-\label{model2res:eqn}
-\end{align}
-are perpendicular to $\vec{a}$ and $\vec{b}$.
-The $\vec{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
-$\vec{\epsilon}_{\gamma^1} $
-quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that, just as in Model~I, most
-of the $\vec{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
-$\vec{\delta}$ too
-has a significant projection onto the dust plane, as the $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\vec{\delta}$ vector.
-The transformation between the new set of $\vec{\gamma}$'s and dust parameters yields
-a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, shifted to slightly  higher values relative to the results of Model~I.
-As a point of comparison with another standard SN~Ia model, 3\% of the color vector defined by 
-the  SALT2 (v2.4) color parameter, $c$, is  projected perpendicular to the plane defined by the $\vec{\gamma}$'s.
-
-The significance of the $\vec{\delta}$ measurement is evaluated using simulated datasets.
-For one set of tests, we generate 100 random realizations of data with input  parameters equal to the median values of the 
-parameter posteriors found in
-\S\ref{model:sec}, and using the same noise as our data.  
-To represent the null hypothesis, the input $\vec{\delta}$-vector is set to zero.
-Figure~\ref{pvalues_delta2:fig} shows results of fits of these null-realizations next  to the results from the real data.
-One statistic shown is the median and 68\% credible interval of the squared amplitude  $\delta^2$.
-As $\delta^2$ measures the magnitude response due to the third parameter, it is expected to have a small value
-when such a new parameter is not relevant.
-Comparing separately the  $-1$, 0, and $1$-sigma
-values of  the credible interval of our data relative to those from the simulations, we obtain
-three different $p$-values ranging from 
-\color{blue}
-0.87--0.90,
-\color{black}
- indicating that the
-null hypothesis is a poor representation of the data.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.9in]{pvalues_delta2.pdf} 
-  \includegraphics[width=2.9in]{pvalues_relperp.pdf} 
-            \caption{ Left: The squared length, $\delta^2$;  and Right: the relative length perpendicular to the plane defined by $\vec{\gamma}$, $\delta_\perp^2/\delta^2$, for 100 independent simulated data sets with input $\delta=0$.
-The fits
-            are ordered by the median value, the null realizations are shown in blue and the result from our data is shown in red.
-            \label{pvalues_delta2:fig}}
-\end{figure}
-
 An interesting feature of $\vec{\delta}$ is that its direction lies close to the plane defined by the
@@
 \subsection{Host-Galaxy Mass}
-A correlation between Hubble residual and host-galaxy mass
-was first noted by \citet{2010ApJ...715..743K,2010MNRAS.406..782S}, a signal confirmed to exist in the SNfactory
-sample \citep{2013ApJ...770..108C}.
-This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
-\citetalias{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
-To explore whether the Hubble residual may be due to unaccounted color,
-we plot in Figure~\ref{childress:fig} our intrinsic parameter
-mass versus $A_{\delta {\hat{U}}}-A_{\delta {\hat{U}}}|_0$  (subtracting out a random supernova
-to suppress correlated errors)
-for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-The average $A_{\delta {\hat{U}}}$'s of the two subsamples are
-%---
-$\langle A_{\delta {\hat{U}}} \rangle=   0.000 \pm {    0.011 }$ mag,
-$\langle A_{\delta {\hat{U}}} \rangle= 0.003 \pm {    0.009 }$ mag
-for low- and high-mass hosts respectively: there is no significant difference in $A_{\delta {\hat{U}}}$ between them.
 

### 2017-11-28 submit/fix.tex
forging on

@@
 
+\added{
+Even two parameters are probably not enough to capture supernova color diversity.  SNe~Ia 
+are affected by interstellar Milky Way-like dust  and by ``intrinsic'' color variations from the supernova itself and its surrounding circumstellar dust. Physical modeling
+shows that the complexity of interstellar dust shouldn't be expected to be captured by a single parameter \citep{2015ApJ...807L..26G,
+2017ApJ...836...13H}. Supernova models \citep[e.g.][]{2007ApJ...662..487W,2013MNRAS.436..333S,2014MNRAS.441..532D,2015MNRAS.454.2549B,
+2017ApJ...846...58H} and circumstellar dust \citep{2005ApJ...635L..33W,
+2008ApJ...686L.103G} produce color variations beyond those due to interstellar dust.  A third color
+parameter is therefore expected.}
+
 Hierarchical modeling has recently enabled
@@
 The data used in this analysis are described in \S\ref{data:sec}.
-\replaced{
-In \S\ref{model:sec} we present a
-first analysis with two extrinsic parameters and omitting the intrinsic parameter.  The properties of the two extrinsic parameters
-are consistent with the expectations of parameterized Milky Way extinction models.
-In \S\ref{model2:sec} we add the intrinsic parameter in the analysis, and find strong evidence for its influence on observed magnitudes.
-}{wefwe}
-In  \S\ref{discussion:sec}
-we relate our results to known
-signatures of SN~Ia diversity.
-Avoid repetitiiveness.
+\added{
+The analysis itself is presented as a series of three models of increasing complexity.
+\S\ref{modelI:sec}  and  \S\ref{modelII:sec} present the first two models, providing a soft introduction to
+our methodology and yielding results to be compared with those from the third model.
+That ultimate model and its results are discussed in detail in \S\ref{modelIII:sec}. 
+In \S\ref{modelI:sec} we present Model~I, 
+a first analysis using spectral features to standardize SN colors
+and two additional latent parameters to account for color diversity. 
+For Model~II described in \S\ref{modelII:sec}, we add a third latent parameter to the analysis.
+Light-curve shape is then added to constitute our final Model~III in \S\ref{modelII:sec}.}
 Conclusions are presented in \S\ref{conclusions:sec}.
@@
 The 
-spectroscopic-feature measurements, SALT light-curve fit parameters including the shape  $x_1$,
-and uncertainties
+spectroscopic-feature measurements, \added{SALT2 light-curve shape parameters  $x_1$,}
+and their uncertainties
 are presented
@@
 \label{modelI:sec}
-We begin by considering a model for supernova magnitudes that have linear dependence on spectral parameters
-and two extrinsic color parameters. This model is referred to as Model~I.  It is not the primary focus of this article, but its
-results are of interest.  The purpose of this Section is to introduce some basic concepts of our models,
-to show how the models can be expressed in terms of dust-extinction models, and to give Model~I results on dust. 
-We refrain from presenting the full results of Model~I in deference to the more complex Model~II that is the subject of Section~\ref{modelII:sec},
+\added{
+We begin by considering Model~I, in which supernova magnitudes  have linear dependence on spectral parameters
+and two extrinsic color parameters. The purpose of this section is to introduce some basic concepts of our models,
+to show how some of the  model parameters can be expressed in terms of dust-extinction models, and to give Model~I results on dust extinction. 
+To avoid repetitiveness,
+we refrain from going into full detail on Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}
+and is the focus of this article.}
 
@@
 fluxes to luminosities.
+\added{With this grey offset, the model standardizes colors without reference to an absolute magnitude.
 The intrinsic  magnitudes are
@@
 notationally distinguishes between global versus per-supernova parameters.
-} that describe the SN~Ia population
+}} that describe the SN~Ia population
 $\vec{c}$, 
@@
 
-Except where stated otherwise above, we adopt a flat prior for all parameters.
+\added{Except where noted above, we adopt a flat prior for all parameters.
 
@@
 
-\subsection{Results: $\gamma^0$ and $\gamma^1$}
+\subsection{Results -- $\vec{\gamma}^0$ and $\vec{\gamma}^1$:  Cofactors the of Extrinsic Color Parameters}
 \label{results1:sec}
-In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$
-(the 68\% credible intervals for all global parameters are given in \S\ref{m12results:sec}.)
+In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
 In our model, $g_0$ and $g_1$ are introduced as latent parameters that are related to linear shifts in band magnitudes through
@@
 Attenuation of supernova light due to dust is expected to be mostly captured by the first-order affects described by our linear model.
-Here we  interpret our model $\gamma$'s in terms of
-the dust-extinction model of \citetalias{1999PASP..111...63F}.
-
+We  interpret our model $\gamma$'s in terms of
+the dust-extinction model of \citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F}.
+
+The 68\% credible intervals for $\gamma^0$ and $\gamma^1$ (and all other global parameters) are given in \S\ref{m12results:sec}.}
 All elements of the two $\vec{\gamma}$ parameter vectors 
@@
 
-A linear model with parameters $A_V$ and $E(B-V)$
+\added{Dust-extinction
+models are also approximately described by a linear model, here 
+using the commonly-used parameterization of $A_V$ and $E(B-V)$
 \begin{equation}
-A_X = a_X  A_{V} + b_X E(B-V)
+A_X = a_X  A_{V} + b_X E(B-V).
 \label{f99:eqn}
 \end{equation}
-approximately describes  
-dust-extinction
-models.  For example,   the wavelength-dependent model of  \citet{1989ApJ...345..245C} is linear,
+}
+For example,   the wavelength-dependent model of  \citet{1989ApJ...345..245C} is linear,
 though its linearity is lost when integrated over broad-band filters.
@@
 \citep{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at ${\hat{B}}$-band peak, the 
-\citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F} model
+\citetalias{1999PASP..111...63F} model
 can be approximated with
@@
 
-Our model $\gamma$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
-dust-based $a_X$ and $b_X$ vectors plus residual vectors perpendicular to $\vec{a}$ and $\vec{b}$,
+\added{Our model $\vec{\gamma}$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
+dust-based $\vec{a}$ and $\vec{b}$ vectors plus residual vectors perpendicular to the plane spanned by $\vec{a}$ and $\vec{b}$,
 \begin{equation}
@@
 \end{equation}
-The $\gamma$'s are almost entirely captured by the first term. 
-The Model~I posterior gives a quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ projected onto the plane defined by
-$a_X$ and $b_X$, the quadratic fraction of $\vec{\gamma}^1$ projected
-onto the dust plane is
-$0.959^{+0.013}_{-0.024}$.
-This result indicates that
-the allowed variations in ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to almost identical
+The $\vec{\gamma}$'s are almost entirely captured by the first term. 
+A quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ is projected onto $\vec{a}$--$\vec{b}$ plane, as is
+$0.959^{+0.013}_{-0.024}$.of $\vec{\gamma}^1$.}
+The allowed color
+variations in ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to almost identical
 2-dimensional
@@
 with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  equal to  linear combinations of the original parameters.
-Comparing this equation with  Eq.~\ref{trans_I:eqn}, we see that $\kappa_1=M[1,2]/M[1,1]$, $\kappa_2=M[2,1]/M[2,2]$.
+\added{The color vectors in this equation are associated with those of  Eq.~\ref{trans_I:eqn} by assigning $\kappa_1=M[1,2]/M[1,1]$, $\kappa_2=M[2,1]/M[2,2]$.}
 
@@
 This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
-We use this interpretation to assign  $\langle R^F_{\mathit{eff}}\rangle = \kappa_1^{-1}$ as
+We use this interpretation to assign  $\langle R^F_{\mathit{eff}}\rangle \equiv \kappa_1^{-1}$ as
 the
@@
 effective total-to-selective extinction of our sample.
-With our posterior we
-define an effective $R^F_{\mathit{eff}} \equiv \kappa^{-1}_1=2.18^{+0.14}_{-0.16}$.
+\added{
+The posterior yields $R^F_{\mathit{eff}} =2.18^{+0.14}_{-0.16}$.
 Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.18$.
 
-In the above context, the direction of the $\vec{\gamma}^1$ vector is described by $\kappa_2$.
+The direction of the $\vec{\gamma}^1$ vector is described by $\kappa_2$.
 The prior that $g_0$ and  $g_1$ are uncorrelated leads  to  $\kappa_2$ being determined
-by the sample 
-distribution of $A^F_V$ and $E^F(B-V)$.  In this article, we do not further consider the direction of
-$\vec{\gamma}^1$ but rather focus on the distribution of the per-supernova parameters.
+by the
+distribution of $A^F_V$ and $E^F(B-V)$ for our supernova sample.  In this article, we do not further consider the direction of
+$\vec{\gamma}^1$ but will later focus on the distribution of the per-supernova $g_0$ and $g_1$ parameters.
 
@@
 \subsection{Remarks}
-Model~I is not of primary interest in this article.  However, there are  points to highlight from its results.
-
+There are two points to highlight from the analysis of
+Model~I.
 \begin{itemize}
-\item Our model introduces two latent supernova parameters that can influence supernova colors with ``non-informative'' priors.  Fitting
+\item This model introduces two latent supernova parameters that can influence supernova colors with ``non-informative'' priors.  Fitting
 of our model gives a space of possible color variations highly consistent with those expected from two-parameter dust-extinction models. 
-This lends confidence to our modelling and analysis.
+That we recover a physically-motivated  result lends confidence in the modeling and analysis.
 \item In Model~I, any  intrinsic color variation that remains after spectral corrections is allocated to two parameters.  Color variations beyond
-those from two-parameter dust extinction contribute to those two parameters.   The effective $R^F$ we derive from our results
-is susceptible to leakage from intrinsic colors not associated with dust.
+those from two-parameter dust extinction contribute to those two parameters.   The derived effective dust-parameter $R^F$ 
+is susceptible to leakage from intrinsic colors unassociated with dust.
 \end{itemize}
 
-\section{Model~II: Extrinsic--Intrinsic Colors}
+\section{Model~II: Extrinsic and Intrinsic Colors}
 \label{modelII:sec}
-Model~II extends Model~I to include a third intrinsic color parameter.  This increase in the number of degrees of freedom accommodates
-the optical depth of dust, one parameter to capture variation in dust properties, and
-intrinsic color variability unrelated to dust.  In this section we  focus on describing the consequences of adding the new parameter.
+Model~II extends Model~I to include a third intrinsic-color parameter.  This increase in the number of degrees of freedom accommodates
+one parameter for the optical depth of dust, one parameter to capture variation in dust properties, and
+another parameter for intrinsic color variability unrelated to dust.  In this section we  focus on describing the consequences of the addition of the
+new parameter.
 
@@
 \label{modelIImodel:sec}
-Model~II is the same as Model~I except for the 
+Model~II is identical to Model~I except for the 
 addition of an intrinsic color parameter $p$.  The distribution of this parameter over all supernovae is
-assumed to be drawn from a Normal distribtion
+assumed to be drawn from a Normal distribution with unit standard deviation.
+The relative effect on each band is specified by the global parameters 
+$\sigma_p\vec{\phi}$, where $\vec{\phi}$ is a unit vector.
+Model~II reads as
 \begin{equation}
-p \sim \mathcal{N}(0, \sigma_p).
+p  \sim \mathcal{N}(0,1 ),
 \end{equation}
-The influence of $p$ on supernova colors is described by the global parameters $\vec{\phi}$ (constrained to be a
-unit vector)
-so that the color offset of each supernova is  $\vec{\phi}p$.
-Model~II reads as
+\begin{equation}
+\sigma_p  \sim \text{Cauchy}(0.1,0.1),
+\end{equation}
 \begin{equation}
@@
 =
-\Delta +
+\Delta  \vec{I} +
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} + \phi_{\hat{U}} p\\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  + \phi_{\hat{B}} p\\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} + \phi_{\hat{V}}  p\\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} + \phi_{\hat{R}} p\\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+ \phi_{\hat{I}}  p
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} + \sigma_p\phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  + \sigma_p\phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} + \sigma_p\phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} + \sigma_p\phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+ \sigma_p\phi_{\hat{I}}  p
 \end{pmatrix},
@@
 put the term in the mean of Eq.~\ref{dust2:eqn} joining what we call extrinsic parameters.  Although we 
-use ``intrinsic'' and ``extrinsic'' as descriptive labels for $\phi$ and $\gamma$ respectively, the model cannot identify
+use ``intrinsic'' and ``extrinsic'' as descriptive labels for $\phi$ and $\gamma$ respectively, the model cannot distinguish between
 their physical origins.
 
-The model contains the product of latent parameters
-$\vec{\phi} p$, which leads to the degeneracy $\vec{\phi} \rightarrow -\vec{\phi}$, $p \rightarrow -p$.
+The model contains the product 
+$\vec{\phi} p$, which has the degeneracy $\vec{\phi} \rightarrow -\vec{\phi}$, $p \rightarrow -p$.
 No conditions are added to break this degeneracy as we want to explore the possibility that
-$\sigma_p\phi$ is consistent with zero.  The degeneracy
-in $\vec{\phi}$ is apparent later in the article, but it does not affect the relevant science that
-comes with the combination $\vec{\phi} p$.
+$\sigma_p\vec{\phi}$ is consistent with zero.  The degeneracy
+in $\vec{\phi}$ is apparent later in the article, but it does not affect the magnitude predictions.
 
 For $N$ supernovae there are $8N$ observables.  There are $3N$ spectral parameters, each of
-$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$ plus one for their standard
-deviation $\sigma_p$,  and $5 \times 7$ global coefficients.
-For $N=172$ supernovae, there are 1376 observables and 1237  parameters.
-
-\subsection{Results: Effect of the Third Color Term}
+$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$,  and $5 \times 7$ global coefficients.
+For $N=172$ supernovae, there are 1376 observables and 1236  parameters.
+
+\subsection{Results -- $\sigma_p \vec{\phi}$: Cofactor of the Intrinsic Color Parameter}
 \label{results2:sec}
 In this subsection we focus on the effect of adding the third color term  $\sigma_p \vec{\phi}$.
-The 68\% credible intervals for relevant global parameters are given in \S\ref{m12results:sec}.
-
 There is strong evidence for a third color parameter.
 The 68\% credible interval for $\sigma_p$ is $0.051^{+0.005}_{-0.004}$~mag, highly incompatible with zero. 
+(The credible intervals of all global parameters are given in  \S\ref{m12results:sec}.)
 The posterior for $\sigma_p \vec{\phi}$ is shown in Figure~\ref{M1ev:fig}.  
@@
 The direction of $\vec{\phi}$ is not aligned with the plane defined by
-the $\vec{\gamma}$ vectors; the 68\% credible interval for the  quadratic fraction of
-$\vec{\phi}$ in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane is $0.088^{+0.118}_{-0.063}$.
+the $\vec{\gamma}$ vectors; a quadratic fraction of
+ $0.088^{+0.118}_{-0.063}$ of 
+ $\vec{\phi}$ lies in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.
 
@@
 
-Model~II introduces a degree of freedom that is associated with a Normal distribution.
-It is thus interesting to compare the distributions of the $g_0$ and $g_1$ parameters of Model~I and Model~II,
-which are shown in Figure~\ref{kcomp:fig}.  The apparent difference between Model~I and II is in the $\gamma^1g_1$ term,
-where it seems that a Normal distribution component in Model~I is no longer in Model~II but is  assigned to the $\sigma_P \vec{\phi}$.
+Model~II introduces a new parameter whose distribution comes from a Normal distribution.
+It is thus interesting to compare the distributions of the $\gamma^0_{\hat{V}} g_0$ and $\gamma^1_{\hat{V}}g_1$ parameters of Model~I and Model~II,
+as shown in Figure~\ref{kcomp:fig}.  (Here and in future plots, the parameter value of one supernova,
+e.g.\ $\gamma^0_{\hat{V}} g_0|_0$, is subtracted
+out to null our some of the correlated error between supernovae.) The apparent difference between Model~I and II is in  $\gamma^1_{\hat{V}}g_1$ term,
+where it seems that a Normal distribution component in Model~I is  assigned to $p$ in Model~II.
 
@@
 onto the plane defined by
-$a_X$ and $b_X$ of the \citetalias{1999PASP..111...63F} model.
-The 68\% credible interval is $R^F_{\mathit{eff}} = 2.54^{+0.20}_{-0.20}$.
+$\vec{a}$ and $\vec{b}$ of the \citetalias{1999PASP..111...63F} model.
+The direction of the  $\vec{\gamma}^0$ vector corresponds to an effective $R^F_{\mathit{eff}} = 2.54^{+0.20}_{-0.20}$.
 
@@
 as has been noted by \citet{2011A&A...529L...4C}, that dust analyses
-that do not allow for additional color dispersion are susceptible to bias in inferred dust parameters.
+that do not allow for additional color dispersion are susceptible to bias when inferring dust parameters.
 \end{itemize}
 
-\section{Model~III: Extrinsic--Intrinsic Colors and Light-Curve Shape}
+\section{Model~III: Extrinsic and Intrinsic Colors and Light-Curve Shape}
 \label{modelIII:sec}
-The two models already presented standardize supernovae based on spectral features and colors at peak brightness.
-Nevertheless we know that multi-epoch data also trace supernova properties.
+
 Light-curve shape is an established indicator of SN~Ia diversity 
@@
 associated with color \citep{1996ApJ...473...88R,2005A&A...443..781G}.
-Model~III introduced in this section explicitly includes light-curve shape
-along with the spectral features.  This model is of primary interest
+Model~III explicitly includes light-curve shape as an additional feature used to standardize supernova colors, in contrast to
+the first two models that use spectral features.
+This model is of primary interest
 in this article and its results are described in depth.
@@
 \label{modelIImodel:sec}
-Model~III is the same as Model~II except for the 
+Model~III is identical to Model~II except for the 
 addition of a new term  that relates magnitudes with the SALT2 light-curve-shape parameter,
@@
 \begin{equation}
-p \sim \mathcal{N}(0, \sigma_p),
+p  \sim \mathcal{N}(0,1 ),
+\end{equation}
+\begin{equation}
+\sigma_p  \sim \text{Cauchy}(0.1,0.1),
 \end{equation}
@@
 =
-\Delta +
+\Delta  \vec{I} +
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} +\zeta_{\hat{U}} x_1 + \phi_{\hat{U}} p\\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\zeta_{\hat{B}} x_1 + \phi_{\hat{B}} p\\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\zeta_{\hat{V}} x_1+ \phi_{\hat{V}}  p\\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\zeta_{\hat{R}} x_1+ \phi_{\hat{R}} p\\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\zeta_{\hat{I}} x_1+ \phi_{\hat{I}}  p
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} +\zeta_{\hat{U}} x_1 + \sigma_p\phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\zeta_{\hat{B}} x_1 + \sigma_p\phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\zeta_{\hat{V}} x_1+ \sigma_p\phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\zeta_{\hat{R}} x_1+ \sigma_p\phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\zeta_{\hat{I}} x_1+ \sigma_p\phi_{\hat{I}}  p
 \end{pmatrix},
@@
 \begin{pmatrix}
-{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
+{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o} \\ x_{1, o}
 \end{pmatrix}
@@
 {\hat{V}}+\gamma^0_{{\hat{V}}} g_0+\gamma^1_{{\hat{V}}} g_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} g_0 + \gamma^1_{{\hat{R}}} g_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} g_0+\gamma^1_{{\hat{I}}} g_1\\
-EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
+EW_{Si}\\ EW_{Ca} \\ \lambda_{Si} \\ x_1
 \end{pmatrix}
@@
 \end{equation}
-The only change from Model~II is the addition of the $\vec{\zeta} x_1$ terms in Eq.~\ref{ewsiv3:eqn}.
-
-For $N$ supernovae there are $9N$ observables.  There are $3N$ spectral parameters, each of
-$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$ plus one for their standard
-deviation $\sigma_p$,  and $6 \times 7$ global coefficients.
-For $N=172$ supernovae, there are 1548 observables and 1409  parameters.
+The changes from Model~II are the addition of the $\vec{\zeta} x_1$ terms in Eq.~\ref{ewsiv3:eqn}, and
+the addition of the $x_1$ observation, parameter, and its implicit inclusion in the covariance matrix $C$, in Eq.~\ref{dust3:eqn}.
+
+For $N$ supernovae there are $9N$ observables.  There are $4N$ spectral and light-curve shape parameters, each of
+$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$,  and $5 \times 8$ global coefficients.
+For $N=172$ supernovae, there are 1548 observables and 1413  parameters.
+}
 
@@
 $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$ are indicators of broadband
-colors at peak.  The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is also an indicator
+colors at peak. \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color.
+The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is also an indicator
 of broadband colors.
@@
 high as that of the data, so we assign a $>99$\% confidence in the detection of this third color term.
+The direction of $\vec{\phi}$ is not aligned with the plane defined by
+the $\vec{\gamma}$ vectors; a quadratic fraction of
+$0.053^{+0.102}_{-0.040}$ of 
+ $\vec{\phi}$ lies in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.
 
@@
 \citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
-from doubly and singly ionized states, making the gas phosphorescent and efficient in redistributing energy from the UV/blue to redder
+from doubly and singly ionized states, making the gas fluorescent and efficient in redistributing energy from the UV/blue to redder
 wavelengths.  Qualitatively this would result in the structure for $\phi_X/\phi_V-1$ that we measure.
@@
 although the $p\sigma_p \vec{\phi}$ colors have ben referred to as ``intrinsic'' due to its placement in the model, the analysis cannot quantitatively distinguish
-whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
+whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.  Amalgamation
 
@@
 \end{pmatrix}.
+\label{corr:eqn}
 \end{multline}
@@
 \label{g0g1:sec}
-
-There are $>2 \sigma$ correlations between our extrinsic color-excess parameters $g_0$, $g_1$
-(equivalently $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$) and the input features  $EW_{Ca}$,
-$EW_{Si}$, and $x_1$.  This translates to correlations between dust and the input features, given the association
-of  $\vec{\gamma} g$ with dust.
-The correlation of $x_1$ with with host-galaxy (including dust) properties is known 
-\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
 
@@
 
+There are $>2 \sigma$ correlations between our extrinsic color-excess parameters $g_0$, $g_1$
+(equivalently $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$) and the input features  $EW_{Ca}$,
+$EW_{Si}$, and $x_1$.  This translates to correlations between dust and the input features, given the association
+of  $\vec{\gamma} g$ with dust.
+The correlation of $x_1$ with with host-galaxy (including dust) properties is known 
+\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
+
 \subsubsection{$p$: Intrinsic Parameter}
 \label{p:sec}
-
-There is no correlation between the  intrinsic parameter $p$ and the other features.
-The correlation coefficients between the ``intrinsic''  ($p\sigma_p\phi_{\hat{I}}$) and ``extrinsic''
-($E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$)  parameters
-are consistent with zero.
-Their independence implies that a single physical parameter is not being artificially attributed to two
+By definition $p$ has a Normal distribution, which is shown, in
+terms of the physically meaningful color-excess $E_p({\hat{B}}-{\hat{V}}) \equiv   p \sigma_p (\phi_{\hat{B}}-\phi_{\hat{V}})$ 
+as the  stack of the posteriors of all supernovae in Figure~\ref{ebv3:fig}.  Also shown for comparison is the distribution of
+the extrinsic  color-excess $E_\gamma({\hat{B}}-{\hat{V}}) \equiv (\gamma^0_{\hat{B}} -\gamma^0_{\hat{V}}) g_0
++ (\gamma^1_{\hat{B}} -\gamma^1_{\hat{V}}) g_1$.
+The standard deviations of  $E_\gamma({\hat{B}}-{\hat{V}})$ and $E_p({\hat{B}}-{\hat{V}})$ are
+%-----
+0.085
+and 0.011
+%-----
+mag respectively.
+The latter is comparable to the typical measurement uncertainty.
+The extrinsic color variation is much larger than that of the intrinsic and it is from the simultaneous analysis of an ensemble of objects that the intrinsic
+color is discerned.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{../output_fix3_x1/ebv.pdf}
+ %  \includegraphics[width=2.8in]{../output_fix3_x1/ebv_delta.pdf}
+      \caption{Left:  Stack of the posteriors of all supernovae of the external $E({\hat{B}}-{\hat{V}})$ 
+      (including contributions from both $k_0$, $k_1$, and $D$)
+      and
+   internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
+   \label{ebv3:fig}}
+\end{figure}
+
+There is no significant correlation between the  intrinsic parameter $p$ and the other features including the extrinsic parameters.
+Their independence implies that two physical parameters are not being artificially attributed to three
 model parameters.  One could have
@@
 
-The distributions of extrinsic, $E_\gamma({\hat{B}}-{\hat{V}}) \equiv (\gamma^0_{\hat{B}} -\gamma^0_{\hat{V}}) g_0
-+ (\gamma^1_{\hat{B}} -\gamma^1_{\hat{V}}) g_1$, and intrinsic, $E_p({\hat{B}}-{\hat{V}}) \equiv   p \sigma_p (\phi_{\hat{B}}-\phi_{\hat{V}})$,
-sources of color excess 
-  are shown in Figure~\ref{ebv:fig} as the  stack of the posteriors of all supernovae 
- and the histogram of per-supernova median values.
- (These values are relative
-to
- those of an arbitrary supernova in order to null out correlated errors.)
-The standard deviations of  $E_\gamma({\hat{B}}-{\hat{V}})$ and $E_p({\hat{B}}-{\hat{V}})$ are
-%-----
-0.085
-and 0.011
-%-----
-mag respectively.
-The latter is comparable to its measurement uncertainty per-supernova.
-Previous analyses confined to $\hat{B}$ and $\hat{V}$ colors would have difficulty in detecting the intrinsic term.
+Color-based magnitude corrections as a function of color excess provide a clue to ``intrinsic'' and ``dust'' attributions of
+the combined effect of the color terms $g_0$, $g_1$, and $p$.  
+All supernovae experience  intrinsic color variation.
+Some encounter dust while others do not:  the distribution of the amount of  dust local to  supernovae within its host and
+geometric projection effects together lead to the expectation for a small but nontrivial fraction  of supernovae of having zero
+dust column density and the
+complement subset having an approximate exponential distribution \citep{1998ApJ...502..177H}.
+Differences between the expected distributions of
+distinct intrinsic effects and dust lead to the prediction of a non-constant slope for the relationship between
+total (from both intrinsic and dust)  magnitude corrections and color excess.
+
+\citetalias{2017ApJ...842...93M} discuss an instructive simulation
+that considers a set of
+supernovae 
+having an intrinsic linear color-magnitude relationship with slope $\beta_{\mathit{int}}$.
+(The absence of an intrinsic color-magnitude relation corresponds to $\beta_{\mathit{int}}=0$.)
+Each supernova encounters dust with a relatively larger slope
+for the color-magnitude relationship and
+extinction drawn from a realistic extinction distribution.
+The expectation is for
+supernovae encountering no interstellar dust  to tend to be bluer and
+collectively exhibit the intrinsic $\beta$ slope for the color-magnitude
+relation.  Supernovae encountering thick dust tend to be redder and collectively exhibit the larger dust  slope.
+This expectation is borne out in Figure 3 of \citetalias{2017ApJ...842...93M}, which
+shows  simulated
+observed color versus light-curve shape corrected magnitudes.
+The distinctive distribution of supernovae in color-magnitude space  allows
+the authors to distinguish intrinsic $\beta_{\mathit{int}}$ and the dust slope,
+despite being
+restricted to using one color observable that is  affected by two sources of extinction.
+
+In our Model~III, each supernova has three color parameters that can distinguish between
+intrinsic and dust contributions whose linear color-magnitude relations are simultaneously determined.
+We see where our best-fit model puts supernovae on a color-magnitude diagram.
+A representative example is shown in Figure~\ref{speccorr:fig}, which plots
+${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 + \sigma_p \phi_{\hat{U}} p$
+as a function of color excess $E_o({\hat{B}}-{\hat{V}})$, where the intrinsic color accounts for spectral-feature corrections.
+The shallower (but non-zero) slope at blue color transitions to a larger slope at red color, 
+as expected  for a mixed intrinsic--dust model.
+The non-zero blue slope implies that the new color term we detect is intrinsic (associated with all supernovae)
+and hence not attributable to dust.
 
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3_x1/ebv.pdf}
- %  \includegraphics[width=2.8in]{../output_fix3_x1/ebv_delta.pdf}
-      \caption{Left:  Stack of the posteriors of all supernovae of the external $E({\hat{B}}-{\hat{V}})$ 
-      (including contributions from both $k_0$, $k_1$, and $D$)
-      and
-   internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
-   Right:  Stack of the posteriors of all supernovae  and histogram of the per-supernova
-   medians of $E_\delta({\hat{B}}-{\hat{V}})$ on an enlarged scale.
-   \label{ebv:fig}}
+   \includegraphics[width=4in]{../output_fix3_x1/ccorr1e.pdf}
+  % \includegraphics[width=2.8in]{../output_fix3_x1/ccorr2e.pdf}
+      \caption{
+      The ${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 + \sigma_p \phi_{\hat{U}} p$
+are plotted as a function of $E_o({\hat{B}}-{\hat{V}})$, where the expected color accounts for spectral-feature corrections.  The left plot shows the full
+range of values whereas the right zooms in the upper-left corner of the population.
+   \label{speccorr:fig}}
 \end{figure}
 
-A correlation between Hubble residual and host-galaxy mass
+Our evidence for an intrinsic color effect is consistent with the conclusion of  \citetalias{2017ApJ...842...93M} (see their Figure~6.)
+Their intrinsic color-effect discerned using only one color parameter and a reasonable population model
+is likely traced to the additional supernova
+color parameter $D$ identified in this article without reference to a population model.
+We find $\delta_{\hat{B}}/(\delta_{\hat{B}}-\delta_{\hat{V}})=1.27^{ + 1.02}_{ - 1.16}$, which agrees with the  approximately corresponding (given that different broadband
+filters are used) $\beta_{\mathit{int}}=2.3\pm 0.3$ found by \citetalias{2017ApJ...842...93M}.
+\citetalias{2017ApJ...842...93M} treat dust as having constant $R$ whereas we allow $R$ to float 
+from supernova to supernova.  Nevertheless our 68\% credible interval for an
+effective $R^F$ of $2.31$--$2.69$ is consistent with their $R_V=2.8 \pm 0.3$.
+
+An independent piece of information available for a subset of our supernova sample is host-galaxy mass \citep{2013ApJ...770..108C}.  
+This statistic is of interest, as a correlation between Hubble residual and host-galaxy mass
 was first noted by \citet{2010ApJ...715..743K,2010MNRAS.406..782S}, a signal confirmed to exist in the SNfactory
@@
 This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
-\citetalias{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect falls on the 95\%-level of their posterior.
+Indeed  \citetalias{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect becomes more probable.
+The intrinsic $p$ parameter is a possible supernova tracer of a population that to date has only been identified through host-galaxy tracers.
+
 To explore whether the Hubble residual may be due to unaccounted color,
-we plot in Figure~\ref{childress:fig} our intrinsic parameter
-mass versus $A_{\delta {\hat{U}}}-A_{\delta {\hat{U}}}|_0$  (subtracting out a random supernova
-to suppress correlated errors)
+we plot in Figure~\ref{childress3:fig} our intrinsic parameter
+ $\sigma_p\phi_{\hat{I}}(p-p|_0) $  (subtracting out a random supernova
+to suppress correlated errors) versus host mass
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-The average $A_{\delta {\hat{U}}}$'s of the two subsamples are
+The median and median uncertainties of the two subsamples are
 %---
-$\langle A_{\delta {\hat{U}}} \rangle=   0.000 \pm {    0.011 }$ mag,
-$\langle A_{\delta {\hat{U}}} \rangle= 0.003 \pm {    0.009 }$ mag
-for low- and high-mass hosts respectively: there is no significant difference in $A_{\delta {\hat{U}}}$ between them.
-
-For supernovae with host-properties from Childress, we plot $p$ as a function of host-galaxy mass.
-$  -0.0186 \pm {    0.0034 }$
-$  -0.0293 \pm {    0.0033 }$
+$\langle \sigma_p\phi_{\hat{I}}(p-p|_0) \rangle=   -0.0186 \pm {    0.0034 }$ mag,
+$\langle \sigma_p\phi_{\hat{I}}(p-p|_0)  \rangle= -0.0293 \pm {    0.0033 }$ mag
+for low- and high-mass hosts respectively, making a difference is $ 0.0141 \pm {    0.0037 }$~mag, significant at almost $4 \sigma$.
+Low- and high-mass galaxies ikely
+host supernovae with different $p$ distributions.  
+The two-tailed $p$-value of the Kolmogorov-Smirnov test is $ 0.02 _ {   -0.02 } ^{   + 0.04 }$.
+
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
    \includegraphics[width=4in]{../output_fix3_x1/childress.pdf} 
-   \caption{Intrinsic parameter
+   \caption{Intrinsic parameter $\sigma_p\phi_{\hat{I}}p$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
+      less than and greater than  $\log{(M/M_\sun)}=10$.
  $p$ as a function of host-galaxy mass
-    \label{childress:fig}}
+    \label{childress3:fig}}
 \end{figure}
+
+This article is confined to the standardization of SN~Ia colors.  Magnitude corrections related to our intrinsic $p$
+parameter that may eliminate the mass step are not pursued.  We confine ourselves to noting the differences in the $p$ distributions of
+low- and high-mass galaxies, and highlighting that there is room for magnitude corrections
+as seen in the correlation between $\Delta$ and $p\sigma_p\phi_{\hat{I}} $ in Eq.~\ref{corr:eqn}.
 
@@
 The color-standardization leaves magnitude residuals $\Delta$.
-The fit $\Delta$'s are highly correlated between supernovae.  To aid 
-visual interpretation, we remove much of this
-correlation by
-selecting an arbitrary supernova and subtracting out its $\Delta|_0$ from those of all other objects, at the level of each MCMC link.
+The fit $\Delta$'s are  correlated between supernovae so we consider
+their values elative to that of an arbitrary supernova  $\Delta_0$.
 The histogram of the per-supernova  medians of these relative  grey offsets $\Delta-\Delta|_0$,
@@
 
-XXXXXX
-
-\section{Supernova Model I: Two Extrinsic Parameters}
-
-\subsection{Model}
-\subsection{Results}
-
-\subsection{The Two Extrinsic Per-Supernova Parameters $k_0$ and $k_1$}
-
-\section{Supernova Model II: Two Extrinsic Parameters, One Intrinsic Parameter}
-
-\subsection{Model}
-
-\subsection{Results}
-An interesting feature of $\vec{\delta}$ is that its direction lies close to the plane defined by the
-$\vec{\gamma}$ vectors.
-This leads to the concern that our model and analysis  could spontaneously generate a third
-vector almost degenerate with the others, despite the prior 
-encouraging
- the independence of $k_0$, $k_1$, and $D$.
-This
-possibility
- is tested using the 
-relative projection of $\vec{\delta}$  perpendicular to the plane defined by the $\vec{\gamma}$'s, $\delta_\perp^2/\delta^2$,
-for the same 100 null simulations that were just described.
-Figure~\ref{pvalues_delta2:fig} shows  that for 
- $-1$, 0, and $1$-sigma
-values of  the credible interval, only
-\color{blue}
-2--3\%
-\color{black}
-of the simulations have values of  $\delta_\perp^2/\delta^2$ as low as our data.
-The $p$-values $\ge 0.97$ indicate that 
- the close alignment of $\vec{\delta}$  with  $\vec{\gamma}$'s is unlikely to be by chance,
-or due to pathologies in our model or the evaluation of its posterior.
-
-Potential biases
-\color{blue}
-within the analysis
-\color{black}
-are measured through simulation.
-We generate 100 random realizations of data with input  parameters equal to the median values found in
-this Section, except for $\vec{\delta}$, which is assigned
-the mode shown in Figure~\ref{deltacorner:fig},
-and the same noise as our data.  The posterior for each realization is analyzed individually, and the posteriors of all realizations are stacked.  The stack is sensitive to
-biases in the best fit value.
-The stack of  $\vec{\delta}$  is shown in Figure~\ref{simdelta:fig}.  There is a bias between
-the input  $(-1.12, -0.89, -0.36,  -0.16, 0.21)$ and the mode of  the stacks $(-1.2, -1.06, -0.49, -0.25, 0.21)$.
-We do not consider this bias to be an issue in our detection of a third parameter, as the difference is significantly
-smaller than the statistical uncertainty of a single analysis and the length of the vector changes by $< 3\%$.
-The posterior stacks for the other global parameters 
-are shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
-relative to the statistical uncertainties. 
-Note that some bias is expected: the priors for the distributions of $\Delta$, $k$, and $D$ are inconsistent
-with the extracted distributions.  Also, 
-there is a tendency for the slope parameters associated with the spectral features to be slightly underestimated, which is an expected consequence of 
-the uncertainties in the predictor variable that lead to 
-regression dilution \citep{spearman04}.
-
-\subsection{Per-Supernova Parameter -- Intrinsic Covariance Matrix Degeneracy}
-\label{degenerate:sec}
-\color{blue}
-As discussed in \S\ref{modelmodel:sec}, our two models have degeneracy between per-supernova parameters and the covariance matrix.
-In the posterior, the degeneracy is broken by the determinant of the covariance matrix in the likelihood and by the priors.
-The posterior is thus sensitive to the prior, which being most likely biased at some level, means that the
-intrinsic color parameters, $\Delta$, $k$, and $D$, and intrinsic dispersion $C_c$ are susceptible to the misassignment between each other.
-The total variance and the allocation of that variance between the eigenvectors of $C_c$ in particular influence the location of the posterior
-maximum, and their distributions are shown in 
-\S\ref{priorappendix:sec}.  Given our particular interest in the new color term, in this Subsection we consider the possibility that
-$\delta$ is an artifact of leakage from intrinsic covariance.
-
-In our model, some intrinsic dispersion could be attributed to  $\delta$.  If this were the case, one would expect for the dominant eigenvector
-of $C_c$ to be aligned with $\delta$, as the corresponding eigenvalue decreases in exchange for the
-artificial creation of $D$.  No such alignment is seen: the median dot products between unit $\delta$ and the ordered five $C_c$ eigenvectors
-are 0.48, 0.53,
-0.34,
-0.24,
-0.31.
-
-The other possibility is for $\gamma^0$ and $\gamma^1$ to leak into $\delta$.  In Model~I, an estimate of leakage from
-$\gamma$  into intrinsic covariance is $0.00091_{- 0.00018}^ {+ 0.00023}$~mag$^2$,
-the variance in the  three  eigenvectors otherwise unconstrained in the model.    (The cumulative variances in successive
-eigenvectors are shown in Figure~\ref{ccvar:fig}.)
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-%   \includegraphics[width=2.8in]{ccnvar.pdf}
-   \includegraphics[width=5in]{ccvar.pdf}
-      \caption{Left: Right: \label{ccvar:fig}
-      }
-\end{figure}
-
-The change in the variance captured the intrinsic dispersions of Model~I and II is 0.002 mag$^2$,
-as shown in Figure~\ref{ccvar:fig}.  This bounds the amount of leakage
-
-The nature of the degeneracy is that each intrinsic SN parameter can be exchanged with one dimension of the intrinsic covariance
-matrix; given that
-Model~I  has three intrinsic vectors $\Delta$, $\gamma^0$, and $\gamma^1$,
-
-The first two eigenvectors of $C_c$ account for $0.89_{-0.05}^{+0.04}$ of its variance  meaning
-that potential leakage of intrinsic colors can account for less than 10\% of the variance, corresponding to 0.024 mag standard deviation.
-We establish through simulations that the standard deviations of $C_c$, $\vec{\sigma}$,  are not biased high, which would have been a signature of leakage of
-intrinsic color variations from $\delta$ into intrinsic dispersion.
-The simulations of input null intrinsic color terms and input intrinsic dispersion do not produce spurious detections of intrinsic color vectors.  We thus conclude that
-biases induced by this degeneracy are low relative to our statistical uncertainties.
-\color{black}
-
-\section{Discussion}
-\label{discussion:sec}
-In this Section
-we  reconcile our results with existing
-signatures of SN~Ia diversity that are not explicitly incorporated
-into our model: light-curve shape, Si~II velocity, the host-galaxy global stellar ``mass step'' in SN~Ia Hubble
-residuals.
-We also consider our results within the context of previous evidence from
-\citetalias{2017ApJ...842...93M}  for distinct intrinsic and dust-extinction-based
-color-magnitude relations.
-
-\subsection{Si~II Line Velocity}
-\label{velocity:sec}
-\citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color, and  
-\citet{2015MNRAS.447.1247S} show that $v_{Si}$ is an important spectral classifier within the SNfactory data themselves.
-To first order, the $\lambda_{Si}$ treated in our study varies linearly with $v_{Si}$
-neglecting the tiny relativistic corrections due to the Doppler effect.
-The values of the $v_{Si}$ coefficient, $\eta$, in this article are consistent with zero.  $EW_{Ca}$ and $EW_{Si}$ have a significant effect on color,
-and in turn $\lambda_{Si}$ is correlated with $EW_{Ca}$.
-Removing from our model the dependence on equivalent widths (eliminating the  $\alpha$ and $\beta$ parameters), we recover
-non-zero $\eta$ values at  $\gtrsim 2\sigma$.
-The Ca and Si responsible for the equivalent widths and wavelength of our selected spectral features
-are expected to be produced together in the thermonuclear burning into intermediate mass elements.
-Nevertheless, Figures~\ref{global1:fig} -- \ref{global5:fig} show the low probability of  $\alpha=0$, $\beta=0$, $\eta\ne0$ in our Model~I.
-We conclude that $v_{Si}$ is correlated with color, 
-but this correlation
-is absorbed into the 
-more-dominant
-equivalent-width corrections.
-
-The results from  \S\ref{shape:sec} and this subsection 
-present $EW_{Ca}$ with $v_{Si}$, and  $EW_{Si}$ with SALT2 $x_1$,  each a 
-case of parameter pairs that are correlated with each other, and each known to be related to
-supernova magnitudes.  We find that the simultaneous training of a pair
-preferentially assigns the magnitude correction to one parameter over the other
-without strong correlations between them in the posterior.  The implication is that the information about the correction is degenerately encoded in the two parameters,
-and is more efficiently captured in one of them.
-
-\subsection{Host-Galaxy Mass}
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{childress.pdf}
-   \includegraphics[width=2.8in]{childress_pvalue.pdf}
-      \caption{Left: Intrinsic parameter $A_{\delta {\hat{U}}}=\delta_{\hat{U}} D$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
-      less than and greater than  $\log{(M/M_\sun)}=10$.
-Right: Histogram of the two-tailed $p$-value from  the Kolmogorov-Smirnov test applied to all links in the Monte Carlo chains.
-   \label{childress:fig}}
-\end{figure}
-
-The Kolmogorov-Smirnov test is applied to the distribution of $A_{\delta {\hat{U}}}$ of both low- and high-mass samples for
-each Monte Carlo link.
-The resulting distribution of the two-tailed $p$-value  over all chains spans the possible range from 0 to 1, as shown in Figure~\ref{childress:fig}.
-We are unable to perform a constraining test of whether the $A_{\delta {\hat{U}}}$ distributions from low- and high-mass samples
-are drawn from a common distribution,
-meaning there is as of yet no sign that our new color parameter is responsible for the mass step.
-
-A more pertinent test 
-would be to check whether
-a host-mass bias persists in Hubble diagram residuals
-derived from a recalibration of SN~Ia absolute magnitudes using the parameters of the current article.
-The calibration of absolute magnitudes goes beyond the design of our model and analysis, so this test
-cannot be presented here.
-
-\subsection{Physical Interpretation of the Intrinsic Color Parameter}
-\label{interpret:sec}
-Supernova colors are expected to be affected by interstellar Milky Way-like dust   (e.g.\ whose extinction is modeled as by  \citetalias{1999PASP..111...63F})
-and by ``intrinsic'' color variations from the supernova itself and its surrounding circumstellar dust. Physical modeling
-shows that the complexity of interstellar dust shouldn't be expected to be captured by a single parameter \citep{2015ApJ...807L..26G,
-2017ApJ...836...13H}. Supernova models \citep[e.g.][]{2007ApJ...662..487W,2013MNRAS.436..333S,2014MNRAS.441..532D,2015MNRAS.454.2549B,
-2017ApJ...846...58H} and circumstellar dust \citep{2005ApJ...635L..33W,
-2008ApJ...686L.103G} also predict color variations not  captured
-by  \citetalias{1999PASP..111...63F}.
-The $D$ parameter
-can be ascribed to either an increased accuracy in the description of interstellar dust or to a separate intrinsic mechanism.
-
-Color-based magnitude corrections as a function of color excess provide a clue to ``intrinsic'' and ``dust'' attributions of
-the combined effect of the color terms $k_0$, $k_1$, and $D$.  
-All supernovae experience  intrinsic color variation.
-Some encounter dust while others do not:  the distribution of the amount of  dust local to  supernovae within its host and
-geometric projection effects together lead to the expectation for a small but nontrivial fraction  of supernovae of having zero
-dust column density and the
-complement subset having an approximate exponential distribution \citep{1998ApJ...502..177H}.
-Differences between the expected distributions of
-distinct intrinsic effects and dust lead to the prediction of a non-constant slope for the relationship between
-total (from both intrinsic and dust)  magnitude corrections and color excess.
-
-\citetalias{2017ApJ...842...93M} discuss an instructive simulation
-that considers a set of
-supernovae 
-having an intrinsic linear color-magnitude relationship with slope $\beta_{\mathit{int}}$.
-(The absence of an intrinsic color-magnitude relation corresponds to $\beta=0$.)
-Each supernova encounters dust with a relatively larger slope
-for the color-magnitude relationship and
-extinction drawn from a realistic extinction distribution.
-The expectation is for
-supernovae encountering no interstellar dust  to tend to be bluer and
-collectively exhibit the intrinsic $\beta$ slope for the color-magnitude
-relation.  Supernovae encountering thick dust tend to be redder and collectively exhibit the larger dust  slope.
-This expectation is borne out in Figure 3 of \citetalias{2017ApJ...842...93M}, which
-shows  simulated
-observed color versus light-curve shape corrected magnitudes.
-The distinctive distribution of supernovae in color-magnitude space  allows
-the authors to distinguish intrinsic $\beta_{\mathit{int}}$ and the dust slope,
-despite being
-restricted to using one color observable that is  affected by two sources of extinction.
-
-In our Model~II, each supernova has three color parameters that can distinguish between
-intrinsic and dust contributions whose linear color-magnitude relations are simultaneously determined.
-We see where our best-fit model puts supernovae on a color-magnitude diagram.
-A representative example is shown in Figure~\ref{speccorr:fig}, which plots
-${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 + \delta_{\hat{U}} D$
-as a function of color excess $E_o({\hat{B}}-{\hat{V}})$, where the intrinsic color accounts for spectral-feature corrections.
-The shallower (but non-zero) slope at blue color transitions to a larger slope at red color, 
-as expected  for a mixed intrinsic--dust model.
-The non-zero blue slope implies that the new color term we detect is intrinsic (associated with all supernovae)
-and hence not attributable to dust.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=2.8in]{ccorr1e.pdf}
-   \includegraphics[width=2.8in]{ccorr2e.pdf}
-      \caption{
-      The ${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} k_0 +\gamma^1_{{\hat{U}}} k_1 + \delta_{\hat{U}} D$
-are plotted as a function of $E_o({\hat{B}}-{\hat{V}})$, where the expected color accounts for spectral-feature corrections.  The left plot shows the full
-range of values whereas the right zooms in the upper-left corner of the population.
-   \label{speccorr:fig}}
-\end{figure}
-
-Our evidence for an intrinsic color effect is consistent with the conclusion of  \citetalias{2017ApJ...842...93M} (see their Figure~6.)
-Their intrinsic color-effect discerned using only one color parameter and a reasonable population model
-is likely traced to the additional supernova
-color parameter $D$ identified in this article without reference to a population model.
-We find $\delta_{\hat{B}}/(\delta_{\hat{B}}-\delta_{\hat{V}})=1.27^{ + 1.02}_{ - 1.16}$, which agrees with the  approximately corresponding (given that different broadband
-filters are used) $\beta_{\mathit{int}}=2.3\pm 0.3$ found by \citetalias{2017ApJ...842...93M}.
-\citetalias{2017ApJ...842...93M} treat dust as having constant $R$ whereas we allow $R$ to float 
-from supernova to supernova.  Nevertheless our 68\% credible interval for an
-effective $R^F$ of $2.31$--$2.69$ is consistent with their $R_V=2.8 \pm 0.3$.
-
-Considering  $\delta D$  to be intrinsic, it can be attributed to an intrinsic supernova property  or a dust not described by $\gamma k$.
-To first order $\vec{\delta}$ behaves like standard dust;   $>98$\% of its length projects onto the expectation of  \citetalias{1999PASP..111...63F}
-with constant $R^F$.
-Therefore, a straightforward explanation is that it describes the absorption due to some form of dust
-that does not exactly obey the  \citetalias{1999PASP..111...63F} model.
-The departure from   \citetalias{1999PASP..111...63F}
-can be seen qualitatively; the increase in magnitude change toward bluer wavelengths, seen in Figure~\ref{deltaratio:fig}, matches the 
-expectation for the multiple scattering of low-wavelength photons by circumstellar forms of dust.
-However, we
-lack the signal-to-noise to show consistency with this explanation.
-The best-fit elements $\delta_X$ do not all share the same sign, as would have been expected for dust.
-Confining ourselves to the 98\% of   $\vec{\delta}$ that lie on the dust plane, associating 
-$D$ with $A_V$ would imply an unphysical $R^F=0.5$.
-(\citealt{Huang2017} find that in the limit of Rayleigh scattering, $R_V \approx 0.81$.)
-We do not have conclusive evidence that  $\delta$ is a property of dust distinct from that described by $\gamma$, rather
-than representing intrinsic supernova color variation.
-
 \section{Conclusions}
 \label{conclusions:sec}
-To summarize, we model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
-extrinsic color parameters.  Analyzing SNfactory data with this model, we find significant evidence that the above parameters do
-affect supernova magnitudes and colors.  
-This work represents the first determination of the dust extinction curve outside the Local Group
+To summarize, we model SN~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak,
+light-curve shape, and
+latent color parameters.  Analyzing SNfactory data with this model, we find significant evidence that the above parameters do
+affect supernova magnitudes and colors.  Two of the latent color parameters are consistent with the
+\citetalias{1999PASP..111...63F} dust-extinction model, making this
+the first determination of the dust extinction curve outside the Local Group
 derived entirely independently of assumptions about the shape of the extinction curve and/or assumptions about the
 distribution of $A_V$.  
-The derived $A_V$ distribution has the quasi-exponential roll-over expected from simulations.
-The data show the need for at least two color parameters that can be attributed to a range of $R^F$ values, with a distribution that
-has a strong mode with an infrequent but extended scatter toward lower values.
-Nesting this model in an extended model produces a result that 
-gives the first identification of  a new
-intrinsic
+The data show the need for at least two color parameters that can be attributed to a broad distribution  of
+$R^F$ parameter values,
+with an effective $R^F_\mathit{eff}=2.4$ and with an infrequent but extended scatter toward lower values.
+A significant bias in $R^F$ is obtained when the possibility of another source of color variation
+is unaccounted for.
+We identify a new
 parameter that affects supernova
-colors in a manner that is distinct from the expectations for dust or the spectral features $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$.
-Not only do we detect an intrinsic color consistent with that
-found by \citetalias{2017ApJ...842...93M} using different model assumptions,
-we identify a new per-supernova observable parameter that distinguishes intrinsic
-and dust properties.
+colors in a manner that is distinct from the expectations for dust
+and the SALT2 shape-parameter $x_1$.
+This new parameter correlates with host-galaxy mass, meaning it is a candidate supernova observable that may be linked
+with the Hubble diagram mass-step.
 
@@
 Finding slight color perturbations in the multi-band light curves 
-of those samples that are  consistent with our $\vec{\delta}$ would provide strong evidence for  an
+of those samples that are  consistent with our $\sigma_p \vec{\phi}$ would provide strong evidence for  an
 observational signature of the intrinsic SN color-magnitude relationship.
 
-The current data does not show a statistically significant difference in the values of our new parameter for supernovae
+The current data shows a statistically significant difference in the values of our new parameter for supernovae
 in low- and high-mass host-galaxies.
@@
 
+We speculate that the new parameter is related to the fluorescence in SN~Ia described by  \citep{2006ApJ...649..939K}.
+This downgrading of photons from blue to red is responsible for the secondary maximum in near-IR light curves.  There
+are variations
+in the properties of the secondary maximum \citep{1996AJ....112.2438H, 2005A&A...437..789N, 2010AJ....139..120F}.
+\citet{2016MNRAS.463.4311S} find that the date of the secondary $J$-band maximum is correlated with peak
+magnitude, although they do not find that it is independent of light-curve shape $x_1$.  We advocate
+the continued study of
+NIR light-curve properties and their relation with colors, host properties, and magnitudes.  Measuring the
+correlation between our parameter and infrared light curves  is also planned for future work.
+
 An interesting direction for future work is to use narrower bands for generating synthetic photometry
@@
 Our model and results do carry information on absolute magnitude but are not tailored for its study.
-The grey parameter $\Delta$ with its
-$0.08$
-mag dispersion, while containing information on absolute magnitude, 
+The grey parameter $\Delta$, while containing information on absolute magnitude, 
 also 

### 2017-11-28 viewf3.py

@@ -12,7 +12,7 @@ import scipy
 import cPickle
 import matplotlib as mpl
 import sivel
-mpl.rcParams['font.size'] = 16
+mpl.rcParams['font.size'] = 28
 
 f = open('fix3.pkl','rb')
 (fit,_) = pickle.load(f)
@@ -128,8 +128,13 @@ for i in xrange(nsne):
 # intrinsic = numpy.median(correction,axis=1)
 fixev = fit['ev']
 fixev = fixev * numpy.sign(fixev[:,4])[:,None]
-corner.corner(fit['ev_sig'][:,None]*fit['ev'],labels=[r"$\sigma_p \phi_{\hat{U}}$",r"$\sigma_p \phi_{\hat{B}}$",r"$\sigma_p \phi_{\hat{V}}$",r"$\sigma_p \phi_{\hat{R}}$",r"$\sigma_p \phi_{\hat{I}}$"], \
+figure=corner.corner(fit['ev_sig'][:,None]*fit['ev'],labels=[r"$\sigma_p \phi_{\hat{U}}$",r"$\sigma_p \phi_{\hat{B}}$",r"$\sigma_p \phi_{\hat{V}}$",r"$\sigma_p \phi_{\hat{R}}$",r"$\sigma_p \phi_{\hat{I}}$"], \
     truths=[0,0,0,0,0])
+for ax in figure.get_axes():
+    for tick in ax.xaxis.get_major_ticks():
+        tick.label.set_fontsize(18) 
+    for tick in ax.yaxis.get_major_ticks():
+        tick.label.set_fontsize(18)
 pp = PdfPages('output_fix3/sigev.pdf')
 plt.savefig(pp,format='pdf',bbox_inches='tight')
 pp.close()
@@ -182,7 +187,7 @@ crap = crap-crap[:,0][:,None]
 plt.hist(crap.flatten(),bins,label='posterior stack',normed=True,alpha=0.5)
 plt.hist(numpy.median(crap,axis=0),bins,label='median',normed=True,alpha=0.5,width=0.025)
 plt.xlabel(r'$\gamma^0_{\hat{V}} g_0 - \gamma^0_{\hat{V}} g_0|_0$')  #\\ approx A^F_V|_{R^F_{eff}=2.44}$')
-plt.legend()
+plt.legend(fontsize=20)
 plt.tight_layout()
 pp = PdfPages('output_fix3/deltagamma0_med.pdf')
[…]

### 2017-11-29 submit/fix.tex
forging ahead

@@
 addition of an intrinsic color parameter $p$.  The distribution of this parameter over all supernovae is
-assumed to be drawn from a Normal distribution with unit standard deviation.
+assumed to be drawn from a Normal distribution with unit standard deviation; leaving the distribution unconstrained,
+as was done for $g_0$ and $g_1$, yields many local maxima in the posterior and makes MCMC convergence difficult.
 The relative effect on each band is specified by the global parameters 
@@
 For $N$ supernovae there are $8N$ observables.  There are $3N$ spectral parameters, each of
-$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$,  and $5 \times 7$ global coefficients.
+$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters while $p$  contributes $N$ parameters,  and  there are $5 \times 7$ global coefficients.
 For $N=172$ supernovae, there are 1376 observables and 1236  parameters.
@@
 The 68\% credible interval for $\sigma_p$ is $0.051^{+0.005}_{-0.004}$~mag, highly incompatible with zero. 
-(The credible intervals of all global parameters are given in  \S\ref{m12results:sec}.)
 The posterior for $\sigma_p \vec{\phi}$ is shown in Figure~\ref{M1ev:fig}.  
-The two extrema are due to the sign degeneracy for $\vec{\phi}$, each of the MCMC chains converges to one of the solutions and does
+The two maxima are due to the sign degeneracy for $\vec{\phi}$, each of the MCMC chains converges to one of the solutions and does
 not migrate between them.
 The direction of $\vec{\phi}$ is not aligned with the plane defined by
-the $\vec{\gamma}$ vectors; a quadratic fraction of
+the $\vec{\gamma}$ vectors; only a quadratic fraction of
  $0.088^{+0.118}_{-0.063}$ of 
@@
 
-Model~II introduces a new parameter whose distribution comes from a Normal distribution.
-It is thus interesting to compare the distributions of the $\gamma^0_{\hat{V}} g_0$ and $\gamma^1_{\hat{V}}g_1$ parameters of Model~I and Model~II,
-as shown in Figure~\ref{kcomp:fig}.  (Here and in future plots, the parameter value of one supernova,
+Model~II introduces a new parameter  that can absorb color varability
+that was restricted to $g_0$ and $g_1$ in Model~I, and whose distribution comes from a Normal distribution.
+The change in the distributions of the $\gamma^0_{\hat{V}} g_0$ and $\gamma^1_{\hat{V}}g_1$ parameters from
+ Model~I to Model~II
+is apparent in Figure~\ref{kcomp:fig}.  (Here and in future plots, the parameter value of one supernova,
 e.g.\ $\gamma^0_{\hat{V}} g_0|_0$, is subtracted
-out to null our some of the correlated error between supernovae.) The apparent difference between Model~I and II is in  $\gamma^1_{\hat{V}}g_1$ term,
-where it seems that a Normal distribution component in Model~I is  assigned to $p$ in Model~II.
+out to null out correlated error between supernovae.) The  change from Model~I to II is pronounced in  $\gamma^1_{\hat{V}}g_1$,
+where it seems that a Normal distribution component in Model~I disappears in Model~II, presumably having been  assigned to $p$.
 
@@
 
+The credible intervals of all Model~II global parameters are given in  \S\ref{m12results:sec}.
+
 \subsection{Remarks}
@@
 1997ApJ...483..565P}
-associated with color \citep{1996ApJ...473...88R,2005A&A...443..781G}.
-Model~III explicitly includes light-curve shape as an additional feature used to standardize supernova colors, in contrast to
-the first two models that use spectral features.
-This model is of primary interest
-in this article and its results are described in depth.
+with its own color correlations \citep{2005A&A...443..781G, 2007ApJ...659..122J}.
+Model~III explicitly includes light-curve shape as a feature used to standardize supernova colors, in addition to the
+spectral features considered in the previous two models.
+We will show that light-curve shape does have a non-trivial relationship with color that is not already encoded
+in the spectral features.  Model~III is thus the focus of
+this article and its results are  described here in depth.
 
@@
 addition of a new term  that relates magnitudes with the SALT2 light-curve-shape parameter,
-$x_1$, that is related to magnitudes with linear coefficients $\zeta$. 
+$x_1$, through linear coefficients $\zeta$. 
 The model reads as
@@
 The changes from Model~II are the addition of the $\vec{\zeta} x_1$ terms in Eq.~\ref{ewsiv3:eqn}, and
-the addition of the $x_1$ observation, parameter, and its implicit inclusion in the covariance matrix $C$, in Eq.~\ref{dust3:eqn}.
+the addition of the shape measurement and uncertainty (implicit in the covariance matrix $C$) and $x_1$   in Eq.~\ref{dust3:eqn}.
 
 For $N$ supernovae there are $9N$ observables.  There are $4N$ spectral and light-curve shape parameters, each of
-$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters, there are $N$ parameters for $p$,  and $5 \times 8$ global coefficients.
-For $N=172$ supernovae, there are 1548 observables and 1413  parameters.
-}
+$\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters while $p$  contributes $N$ parameters,  and there are $5 \times 8$ global coefficients.
+For $N=172$ supernovae, this makes 1548 observables and 1413  parameters.
 
@@
 
-In the analysis of this and other sections of this article,
+In the analysis of this and previous sections of this article,
 the posterior of the model parameters is evaluated using Hamiltonian Monte Carlo with a No-U-Turn
 Sampler as implemented in
-STAN \citep{stan}.  We run eight chains, each with 5000 iterations of which
+STAN \citep{JSSv076i01}.  We run eight chains, each with 5000 iterations of which
 half are used for warmup.
-Tests have revealed no evidence for the non-convergence of the MCMC run.
 STAN provides output statistics to assess
@@
 potential scale reduction statistic, $\hat{R}$
-(in this paragraph not to be confused with the synthetic $R$ magnitude)
-\citep{Gelman92}, measures the convergence of the target distribution
+\citep[][in this paragraph not to be confused with the synthetic $\hat{R}$-band magnitude]{Gelman92}, measures the convergence of the target distribution
 in iterative simulations 
 by using multiple independent sequences to estimate how much that distribution would sharpen if the simulations were run longer.
-$N_{\mathit{eff}}$ is an estimate of the number of independent draws.
-The output for our data and model gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.
-The
-output also gives  $N_{\mathit{eff}} \gg 100$ for all parameters, indicating that all are densely sampled.
-
-The algorithm is extensively tested with simulated data with known input signals and measurement uncertainties similar to those of our dataset.
+$N_{\mathit{eff}}$ is an estimate of the number of independent draws. The STAN output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
+output also gives  $N_{\mathit{eff}} \gg 100$ for all parameters, indicating that they are densely sampled.
+
+The algorithm is run with input simulated data with known  signals and measurement uncertainties similar to those of our dataset.
 Stacks of the posteriors from 100 simulated datasets  exhibit no biases that are significant relative to the statistical uncertainties of a single posterior.
 
-The posterior that will be shown in  \S\ref{results3global:sec} exhibits a 
-confined peak, exhibiting no evidence that the MCMC has not failed to converge.
-
-The model provides a fair representation of the data, as seen in the difference between the data and the model prediction.
-Figure~\ref{residual:fig} has plots of the observed  versus
-model-expectation colors (including  supernova-specific spectral features, light-curve shape $\gamma g$, and $\phi p$ terms) for four selected colors,
-and the histogram of their differences.  
-There are no extreme residuals 
-from catastrophically poor color predictions.  There are no apparent trends between residuals and observed
-color.   The residuals of the data away from the model have a compact Gaussian-like appearance.
+As will be seen in  \S\ref{results3global:sec}, the final posterior has a distinct bounded  
+peak showing no indication that the MCMC has failed to converge.
+
+The model provides a fair representation of the data as seen in the residual differences between the data and the model prediction.
+Figure~\ref{residual:fig} shows plots of the observed  versus
+model-expectation colors (differences between band magnitudes in the mean of the Normal distribution of Eq.~\ref{dust3:eqn}) for four selected colors,
+and the histogram of the residuals.  The residuals have compact Gaussian-like appearance with
+no catastrophically poor color predictions.  There are no apparent trends between residuals and observed
+color.
 
@@
             \caption{Observed  versus
-            Model~III-expectation colors (including  supernova-specific spectral features, $\gamma g$, and $\phi p$  terms)
+            Model~III-expectation colors (including  contributions related to spectral features, light-curve shape, $\gamma g$, and $\phi p$  terms)
 for four selected colors. 
@@
 \label{results3global:sec}
-Results from our analysis are shown through contours of the posterior surface for pairs of global parameters grouped by filter, 
-in Figures~\ref{global1:fig} -- \ref{global5:fig}.
+Results from our analysis are shown in Figures~\ref{global1:fig} -- \ref{global5:fig}
+as contours of the posterior surface for pairs of global parameters grouped by filter.
 The confidence regions are localized and unimodal, except for the combination $\sigma_p \vec{\phi}$ that
-has the sign degeneracy already noted in \S\ref{results2:sec} and plotted in Figure~\ref{M1ev:fig}.
-Within the finite number of generated links, the MCMC chains do not migrate to the parity-degenerate solution of $\vec{\gamma}$ and $g$.
+has the sign degeneracy explained in \S\ref{results2:sec} and plotted in Figure~\ref{M1ev:fig}.
+Within the finite number of generated links, the MCMC chains do not migrate between the parity-degenerate $\vec{\gamma}$--$g$ solutions.
 Each chain converges to one of the  $\vec{\phi}$--$p$ degenerate solutions, away from which it does not migrate.
@@
 are given in Table~\ref{global2:tab}.
-To break the sign degeneracy, we enforce that $\phi_{\hat{I}}$
-be positive such that  $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$;
-we use the $\hat{I}$-band because
-Figure~\ref{global5:fig} shows that it has
-the largest separation between the degenerate solutions of $\sigma_p \phi_X$.
+In constructing the credible interval of $\sigma_p\vec{\phi}$ 
+we set $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$ to break its parity degeneracy;
+Figure~\ref{global5:fig} shows there the degenerate solutions are relatively well separated 
+in $\sigma_p \phi_{\hat{I}}$.
 The effect of spectral parameters on color (as opposed to magnitude)
 is shown in the rows of $\alpha_X/\alpha_{\hat{V}}-1$,  $\beta_X/\beta_{\hat{V}}-1$, and  $\eta_X/\eta_{\hat{V}}-1$.
-The freedom to scale each of the terms of $\vec{\gamma}g$ is nulled out in the statistic
- $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
-Note the analogy between these statistics and the common use of
+The normalization freedom of $\vec{\gamma}$ is nulled out in the statistic
+ $\gamma_X/\gamma_{\hat{V}}-1$.
+Note the analogy between these color statistics and the common use of
 $R_V^{-1}=A_B/A_V-1$ as an observational descriptor of dust properties.
@@
 \\
-${\alpha_X/\alpha_V-1}$
+${\alpha_X/\alpha_{\hat{V}}-1}$
 & $   1.0^{+   0.2}_{  -0.2}$
 & $   0.1^{+   0.1}_{  -0.1}$
-& $   0.0^{+   0.0}_{   0.0}$
+&\dots
 & $  -0.1^{+   0.0}_{  -0.0}$
@@
 \\
-${\beta_X/\beta_V-1}$
+${\beta_X/\beta_{\hat{V}}-1}$
 & $  0.79^{+  0.29}_{ -0.19}$
 & $  0.16^{+  0.11}_{ -0.08}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\dots
 & $ -0.12^{+  0.04}_{ -0.04}$
@@
 \\
-${\eta_X/\eta_V-1}$
+${\eta_X/\eta_{\hat{V}}-1}$
 & $ -0.19^{+  0.17}_{ -0.28}$
 & $ -0.12^{+  0.09}_{ -0.15}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\dots
 & $ -0.06^{+  0.06}_{ -0.04}$
@@
 \\
-${\zeta_X/\zeta_V-1}$
+${\zeta_X/\zeta_{\hat{V}}-1}$
 & $ -0.45^{+  0.20}_{ -0.33}$
 & $ -0.26^{+  0.11}_{ -0.18}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\dots
 & $ -0.20^{+  0.05}_{ -0.07}$
@@
 \\
-${\gamma^0_X/\gamma^0_V-1}$
+${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
 & $  0.67^{+  0.05}_{ -0.05}$
 & $  0.34^{+  0.03}_{ -0.03}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\dots
 & $ -0.24^{+  0.01}_{ -0.01}$
@@
 \\
-${\gamma^1_X/\gamma^1_V-1}$
+${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
 & $ -0.32^{+  0.16}_{ -0.21}$
 & $ -0.55^{+  0.13}_{ -0.20}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\dots
 & $ -0.01^{+  0.05}_{ -0.04}$
@@
 \end{tabular}
-\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~III in \S\ref{modelIII:sec}.\label{global3:tab}}
+\caption{68\% credible intervals for the global fit parameters of Model~III in \S\ref{modelIII:sec}.\label{global3:tab}}
 \end{table}
 
-\subsubsection{$\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\zeta}$: Cofactors of Observables}
+\subsubsection{Results for the Observables Cofactors $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\zeta}$}
+
 The cofactors  $\vec{\alpha}$, $\vec{\beta}$, and $\vec{\eta}$ have  significant non-zero values,  meaning that
 $EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$ are indicators of broadband
-colors at peak. \citet{2009ApJ...699L.139W, 2011ApJ...729...55F} find a connection between $v_{Si}$ and color.
+colors at peak.  The significance of their influence varies between  colors; in $\hat{B}-\hat{V}$, roughly the color
+where previous studies have focused, only $\vec{\beta}$ has a strong $>2\sigma$ correlation.  A positive
+dependence (consistent with the positive sign
+of $\beta_{\hat{B}}/\beta_{\hat{V}}-1$)
+of $B-V$ on the pseudo-equivalent width of Si~II~$\lambda$4130 has previously been reported by
+\citet{2013ApJ...773...53F}.
+The insignificance of  our $\alpha_{\hat{B}}/\alpha_{\hat{V}}-1$ is consistent with the
+lack of correlation between the  pseudo-equivalent width of Ca~II~H\&K measurements and
+intrinsic color reported by \citet{2011ApJ...742...89F}.
+
+The story on the Si~II~$\lambda$6355 is not as clear.
+ \citet{2011ApJ...742...89F, 2012ApJ...748..127F} find that
+higher-velocity SNe~Ia tend to be redder than those with lower velocity. \citet{2012AJ....143..126B} find a
+weaker relation than that reported by \citet{2011ApJ...742...89F},
+a difference attributed to a better treatment of uncertainties and host-galaxy dust. In contrast,
+\citet{2013ApJ...773...53F} find no significant relation.
+Our result for $\eta_{\hat{B}}/\eta_{\hat{V}}-1$ also gives no significant relation.
+
 The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is also an indicator
-of broadband colors.
+of broadband colors, in the sense that SNe~Ia with broader light curves are bluer in all colors.
+This is as expected based on the results of \citet{2007A&A...466...11G} and MLCS2k2
+\citep{2007ApJ...659..122J}.
+}
 
@@
 Supernova flux has a large gradient in our $\hat{U}$ and there is a variation in the effective, flux-weighted,  $\hat{U}$ bandwidth. 
-Nevertheless, the  correlation between spectral features with magnitudes in bands with no wavelength overlap is the
-important signal of importance in this study.
-
+Nevertheless, the  correlation between spectral features with magnitudes in bands with no wavelength overlap is a non-trivial
+signal detected in the analysis.
+
+\added{
 The posterior visualized in
 Figures~\ref{global1:fig} -- \ref{global5:fig} shows
- that $\vec{\zeta}$, the magnitude vector associated with $x_1$, is highly correlated with $\vec{\beta}$ the vector
+ that $\vec{\zeta}$, the magnitude vector associated with $x_1$, is highly correlated with $\vec{\beta}$, the vector
  associated with  $EW_{Si}$.
@@
 Nevertheless the $\vec{\zeta}$ and $\vec{\beta}$   posteriors are bounded and inconsistent with zero, indicating that
- $x_1$ and $EW_{Si}$ do convey independent color information.
-For this reason  Model~III is highlighted in this article over Model~II.
-
-\subsubsection{$\vec{\gamma}^0$, $\vec{\gamma}^1$: Cofactors of Extrinsic Latent Parameters}
-
+ $x_1$ does convey color information independent of our set of spectral features.
+For this reason  Model~III is highlighted in this article.
+
+\subsubsection{Results for the Extrinsic Latent Parameter Cofactors $\vec{\gamma}^0$, $\vec{\gamma}^1$}
+\label{results3gamma:sec}
 As with Model~I in \S\ref{modelI:sec}, all elements of the two $\vec{\gamma}$ parameter vectors 
@@
 The direction of the vector in the ${\hat{U}}{\hat{V}}{\hat{I}}$-subspace is shown in Figure~\ref{plane3:fig}.
-The posterior gives a quadratic fraction of $0.9996^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ projected onto the plane defined by
-the  \citetalias{1999PASP..111...63F}-derived
-$a_X$ and $b_X$, the quadratic fraction of $\vec{\gamma}^1$ projected
-onto the dust plane is
+The posterior gives a quadratic fraction of $0.9996^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ that projects onto the plane of
+color changes allowed by the \citetalias{1999PASP..111...63F} dust-extinction model
+as described by
+$\vec{a}$ and $\vec{b}$, the quadratic fraction of $\vec{\gamma}^1$ projected
+onto this plane is
 $0.959^{+0.015}_{-0.029}$.
-The   $\vec{\gamma}$  vectors project  onto $R^F_{\mathit{eff}}=2.40^{+0.15}_{-0.15}$.
-This  is consistent with the $R_V=2.5$ found in the supernova samples of \citet{2011ApJ...729...55F}, and the
+The   $\vec{\gamma}$  vectors project  onto an $R^F_{\mathit{eff}}=2.40^{+0.15}_{-0.15}$.
+This value is consistent with the $R_V=2.5$ found in the supernova samples of \citet{2011ApJ...729...55F}, and the
 center  of the range of per-supernova $R^F$ values found in the samples of \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}.
-Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are associated dust extinction.
+Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are attributed to dust extinction.
 Further discussion on this association is given in the discussion of $g_0$ and $g_1$  in \S\ref{g0g1:sec}.
@@
    \caption{
-   Visualization of how supernova magnitudes can vary in Model~III IIand that of \citetalias{1999PASP..111...63F}.  While the models describe
-   magnitudes in 5-bands ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ this visualization shows only ${\hat{U}}{\hat{V}}{\hat{I}}$.   The left and right plots show the same information from
-   two different perspectives.
-   Our model is shown in solid-line unit vectors in the directions of $\vec{\gamma}^0$ and $\vec{\gamma}^1$. The only possible magnitudes
-   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
-   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
-   in the directions of  $\vec{a}$, $\vec{b}$; the only possible magnitudes are confined to the plane that contains both.
-   The perspective on the right visually shows that all four vectors are nearly coplanar.  
+   Visualization of how supernova magnitudes can vary in Model~III and that of \citetalias{1999PASP..111...63F}.
+   See Figure~\ref{plane:fig}.
    The combination $\vec{a}+\vec{b}/2.40$ is shown in the dotted red
@@
 
-\subsubsection{$\sigma_p \vec{\phi}$: Cofactor of Intrinsic Latent Parameter}
-
-The posterior shows a significant color influence of the $p$ parameter.
-The minimum value for $\sigma_p$ over all Monte Carlo chains is 0.039~mag and its 
-68\% credible interval is $\sigma_p=0.049^{+ 0.004}_{-0.003}$~mag. 
-This is significantly larger than the median data color uncertainty of 0.010~mag (the maximum is 0.042~mag).
-The evaluation of 100 simulated null data sets with no third color parameter produces no median $\sigma_p$'s  as
+\subsubsection{Results for the Intrinsic Latent Parameter Cofactor $\sigma_p \vec{\phi}$}
+
+The  new intrinsic $p$ parameter has a significant influence on color.  The magnitude of its color effect is non-zero,
+with $\sigma_p = 0.049^{+ 0.004}_{-0.003}$~mag.  The smallest value of $\sigma_p$
+over all Monte Carlo chains is 0.039~mag.
+These numbers are significantly larger than the median data color uncertainty of 0.010~mag (the maximum is 0.042~mag).
+The evaluation of 100 simulated data sets with no third color parameter produces no median $\sigma_p$'s  as
 high as that of the data, so we assign a $>99$\% confidence in the detection of this third color term.
+
 The direction of $\vec{\phi}$ is not aligned with the plane defined by
-the $\vec{\gamma}$ vectors; a quadratic fraction of
+the $\vec{\gamma}$ vectors (nor of the  \citetalias{1999PASP..111...63F} dust-extinction model); a quadratic fraction of
 $0.053^{+0.102}_{-0.040}$ of 
- $\vec{\phi}$ lies in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.
+ $\vec{\phi}$ lies in the $\vec{\gamma}^0$--$\vec{\gamma}^1$ plane.
 
@@
 the combination $\phi_X/\phi_{\hat{V}}-1$ shown in Figure~\ref{phiratio:fig}.  They have the property that
-a reddening $\hat{B}-\hat{V}$ is associated with a bluing in $\hat{V}-\hat{R}$.  The color changes are largest
+a reddening $\hat{B}-\hat{V}$ is accompanied with a bluing in $\hat{V}-\hat{R}$.  The reddening and bluing are accentuated 
 in the extreme $\hat{U}$ and $\hat{I}$ bands. Absorption and re-emission of light
-over broad bands are the most obvious candidate for producing this behavior.
-This kind of behavior is already associated with SNe~Ia.
+over broad bands are the most obvious candidate for producing this behavior, a process
+already associated with SNe~Ia.
 \citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
@@
 
-We emphasize that
-although the $p\sigma_p \vec{\phi}$ colors have ben referred to as ``intrinsic'' due to its placement in the model, the analysis cannot quantitatively distinguish
-whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.  Amalgamation
-
-\subsubsection{Per-Supernova Parameter Results}
+To temper our physical interpretation of $p$, 
+we emphasize that
+although the $\sigma_p \vec{\phi}p$ colors have ben referred to as ``intrinsic'' due to their placement in the model, the analysis cannot quantitatively distinguish
+whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
+There is likely more than one physical affect being attributed to $p$, leading to a $\sigma_p \vec{\phi}$ that does not correspond to a single process.
+To simplify the model it is assumed that the $p$'s are drawn from a Normal distribution, which may not be a fair description of what occurs in nature.
+
+\subsubsection{Results for the Per-Supernova Parameters}
 \label{results3per:sec}
 Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$,
-$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $p\sigma_p\phi_{\hat{I}}$.
+$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $A_{p,I} =  \sigma_p\phi_{\hat{I}}p$.
+(The  three latent parameters are multiplied by select cofactors
+that give the physically color excess and extinction.)
 The distributions of the Monte Carlo links for all supernovae are shown in Figure~\ref{perobject3:fig}.
+Each supernova is represented by a cloud of its parameters from all links.
 There is a core concentration in the  parameter-space, with around eight objects that occupy its outskirts.
@@
 \begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), p\sigma_p\phi_{\hat{I}} ) =\\
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), \sigma_p\phi_{\hat{I}}p ) =\\
 \begin{pmatrix}
@@
 \ldots  & \ldots &\ldots  & \ldots  & \ldots & \ldots  &E_{\gamma^1}({\hat{B}}-{\hat{V}})  & 0.00^{+0.07}_{-0.07} \\
-\ldots  & \ldots & \ldots & \ldots  & \ldots  & \ldots  &\ldots  & p\sigma_p\phi_{\hat{I}} \\
+\ldots  & \ldots & \ldots & \ldots  & \ldots  & \ldots  &\ldots  & A_{p,I} \\
 \end{array}
@@
    \caption{
-   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and  $p\sigma_p\phi_{\hat{I}}$, as well as the grey offset
+   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and  $A_{p,I}$, as well as the grey offset
 $\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
@@
 
-\subsubsection{$g_0$, $g_1$: Extrinsic Parameters}
+\subsubsection{Results for the Latent Extrinsic Parameters $g_0$, $g_1$}
 \label{g0g1:sec}
-
-The per-supernova parameter $\gamma^0_{\hat{V}} g_0$ can be associated with the $\hat{V}$-band
-extinction for an effective $R^F_{\mathit{eff}}=2.40$ dust, as
-$\vec{\gamma}_0$  has nearly the same effect on color as dust extinction at that constant $R^F$.
+The vector
+$\vec{\gamma}^0$ describes color changes for an effective $R^F_{\mathit{eff}}=2.40$ dust, as shown 
+In  \S\ref{results3gamma:sec}.
+Hence, the per-supernova parameter $\gamma^0_{\hat{V}} g_0$ is associated with the $\hat{V}$-band
+extinction for a constant $R^F=2.40$.
+}
 Figure~\ref{k0_med:fig} shows the histogram of
@@
 relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} g_0|_0$.
-(Subtracting the value of the one supernova suppresses correlated errors in $g_0$ common to all supernovae.)
+(Subtracting the value of the one supernova suppresses correlated errors common to all supernovae.)
 The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
@@
 (right) $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$,
-which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{\mathit{eff}}\rangle$ value.
+which  is associated with extinction corrections due to deviations away from the canonical $R^F_{\mathit{eff}}$ value.
    \label{k0_med:fig}}
@@
 
+\added{
 An instructive way to consider the  $\{g_0, g_1\}$ parameters
-is through their transformation to  $\{A_V^F, E^F(B-V)\}$ (modulo additive constants)   through the
-matrix in  Eq.~\ref{trans_I:eqn}.
+to transform them to $\{A_V^F, E^F(B-V)\}$ (modulo additive constants)   using the
+matrix $M$ in  Eq.~\ref{trans_I:eqn}.
 A plot showing the expected values and 68\% credible intervals of these parameters
@@
 sample is shown in Figure~\ref{kk:fig}. 
-For reference, a line that represents $R^V_{\mathit{eff}}=2.4$ is overplotted.  The majority of supernovae lie within a narrow range above the line
-meaning they have $R^F > R^V_{\mathit{eff}}$,
-while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{\mathit{eff}}$.  
-The negative tail in  $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$ of the right plot of Figure~\ref{k0_med:fig} is directed toward smaller $R^F$.
-These findings are consistent with previous results:
+For reference, a line that represents $R^F_{\mathit{eff}}=2.4$ is overplotted; points above
+the line have larger $R^F$, points below have smaller $R^F$.  The majority of supernovae lie within a narrow range above the line,
+while the remaining fraction fall in a broader range below the line.
+Comparison with  $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$ of the right plot of Figure~\ref{k0_med:fig}
+shows that the 
+negative tail corresponds to smaller $R^F$, and the sharper positive edge to larger $R^F$.
+These findings are qualitatively consistent with previous results:
 using fixed dust-extinction models,
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
-A per supernova determination of $R^F$ requires the specification of the magnitude and colors of supernovae that experience
-no dust, which is unspecified in our model.
+Our model does not specify
+the magnitudes or colors of a supernova that does not experience dust.  Without further assumptions, it cannot give
+per-supernova determinations of $R^F$.
 
@@
 There are $>2 \sigma$ correlations between our extrinsic color-excess parameters $g_0$, $g_1$
-(equivalently $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$) and the input features  $EW_{Ca}$,
-$EW_{Si}$, and $x_1$.  This translates to correlations between dust and the input features, given the association
-of  $\vec{\gamma} g$ with dust.
-The correlation of $x_1$ with with host-galaxy (including dust) properties is known 
+and the input features  $EW_{Ca}$,
+$EW_{Si}$, and $x_1$. 
+Given the association
+of  $g$ with dust-extinction parameters, this implies that the host environment and the input features are connected.
+The correlation between $EW_{Si}$ and host has  already been noted \citep{2011ApJ...734...42N}.
+There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$.
+This contrasts with studies of high-velocity features (HVF) identified using
+Si~II~$\lambda$6355 that find correlations with host galaxy properties
+\citep[e.g.][]{2014MNRAS.444.3258M, 2015MNRAS.446..354P, 2015ApJS..220...20Z}.
+The population and properties of HVF SNe within the SNfactory sample will be presented in \citep{2018lin}.
+The correlation of $x_1$ with with host-galaxy (including dust) properties is  well established 
 \citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
 
-\subsubsection{$p$: Intrinsic Parameter}
+}
+
+\subsubsection{Results for the Intrinsic Parameter $p$}
 \label{p:sec}

### 2017-12-01 submit/fix.tex
leaving for day

@@
 Through empirical modeling of its observed signal, the peak absolute magnitude of a Type~Ia supernova (SN~Ia) can be accurately determined,
-making SNe~Ia  excellent distance indicators.  Improved modeling of SN~Ia absolute magnitudes can account for
+making SNe~Ia  excellent distance indicators.  Improved modeling of SN~Ia colors and magnitudes can account for
 further physical
@@
 in current models, and so consequently can lead to more precise per-object distances with smaller systematic uncertainties.  In this article, we present   
-an empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of Ca~II and Si~II, and Si~II velocity
-as applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
+an empirical model for SN~Ia peak colors with
+\added{three color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
+and the light-curve shape.
+This model is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
 broadband photometry and their colors are found to be 
-dependent on the spectral equivalent widths and the color parameters, to better than 
-%-----
-$(1-5\times10^{-5})$
-%------
-confidence.
-The color changes allowed by the model are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F} with a free
-total-to-selective extinction parameter $R^F$. 
-Inspired that with no conditioning our  two-parameter model produces behavior similar to that expected from Galactic dust,
-we extend  the model to three color parameters.
-In this new case we obtain consistent results for
-all the parameters in common,
-plus a detection of a third parameter at
+dependent on the observable features and on the three color parameters.
+The color changes allowed by two of the color parameters are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F}. 
+Correspondingly the sample has an effective value of $R^F_{\mathit{eff}} \sim 2.40$, though with a broad distribution of free
+total-to-selective extinctions. 
+We detect the influence on color by a third parameter at
 %--- table.py
-$\sim 90\%$
+$> 99\%$
 %-----
 confidence.
-The 68\% credible interval for the sample effective
-%-----
-$\langle R^F_{\mathit{\mathit{eff}}}\rangle$ is 2.31 -- 2.69.
-%-----
-The third parameter is attributed to intrinsic supernova or circumstellar diversity
-beyond that tracked by the spectral features and two-parameter dust models.
+The third parameter has  unique color characteristics that distinguish it from 
+those already  tracked by the spectral features, light-curve shape, and two-parameter dust models.}
 \end{abstract}
@@
 and two additional latent parameters to account for color diversity. 
-For Model~II described in \S\ref{modelII:sec}, we add a third latent parameter to the analysis.
-Light-curve shape is then added to constitute our final Model~III in \S\ref{modelII:sec}.}
+For Model~II described in \S\ref{modelII:sec}, we add a third latent color parameter to the analysis.
+In \S\ref{modelIII:sec} we present our final Model~III, which  includes light-curve shape as an additional standardization parameter.}
 Conclusions are presented in \S\ref{conclusions:sec}.
@@
 and two extrinsic color parameters. The purpose of this section is to introduce some basic concepts of our models,
-to show how some of the  model parameters can be expressed in terms of dust-extinction models, and to give Model~I results on dust extinction. 
+to show how the two  color terms can be associated with existing dust-extinction models, and to give Model~I results on dust extinction. 
 To avoid repetitiveness,
-we refrain from going into full detail on Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}
-and is the focus of this article.}
+we refrain from going into full detail on the results of Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}.}
 
@@
 fluxes to luminosities.
-\added{With this grey offset, the model standardizes colors without reference to an absolute magnitude.
+\added{With this grey offset the model standardizes colors, not absolute magnitude.
 The intrinsic  magnitudes are
@@
 The global parameter vectors\footnote{Global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
-the combination of all components are written as a vector, e.g.\ $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) )$,.  This 
-notationally distinguishes between global versus per-supernova parameters.
+the combination of all components are written as a vector, e.g.\ $\vec{c}=(c_{\hat{U}}, c_{\hat{B}}, c_{\hat{V}}, c_{\hat{R}}, c_{\hat{I}}) $.  The
+band subscript or arrow
+notationally identify global parameters, in contrast with the per-supernova parameters.
 }} that describe the SN~Ia population
@@
 
-\added{Except where noted above, we adopt a flat prior for all parameters.
+\added{All parameters not  otherwise noted above have flat priors.
 
@@
 $\Delta$, $g_0$, $g_1$ contributes $N-1$ parameters
-(recall the constraint in Eq.~\ref{zero:eqn}),  and $5 \times 7$ global coefficients.
+(recall the constraint in Eq.~\ref{zero:eqn}),  and there are $5 \times 7$ global coefficients.
 For $N=172$ supernovae, there are 1376 observables and 1064  parameters.
 
-\subsection{Results -- $\vec{\gamma}^0$ and $\vec{\gamma}^1$:  Cofactors the of Extrinsic Color Parameters}
+\subsection{Results for the Extrinsic Latent Parameter Cofactors  $\vec{\gamma}^0$ and $\vec{\gamma}^1$:  }
 \label{results1:sec}
@@
 $\vec{\gamma}^1$.  Otherwise, no physically-motivated suppositions on the properties of $g$ and $\vec{\gamma}$ are imposed.
-Attenuation of supernova light due to dust is expected to be mostly captured by the first-order affects described by our linear model.
-We  interpret our model $\gamma$'s in terms of
+Since dust extinction is a dominant determinant of supernova colors that is often described by a 2-parameter linear model, we expect
+for our two extrinsic color terms to capture the effects of dust.
+We  thus interpret our model $\vec{\gamma}$'s in terms of
 the dust-extinction model of \citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F}.
 
-The 68\% credible intervals for $\gamma^0$ and $\gamma^1$ (and all other global parameters) are given in \S\ref{m12results:sec}.}
+The 68\% credible intervals for $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (and all other global parameters) are given in \S\ref{m12results:sec}.
 All elements of the two $\vec{\gamma}$ parameter vectors 
@@
 None of the 20000 links of 
-our Monte Carlo chains for $\vec{\gamma}$ come close to the origin, we thus claim detection of the
-influence of $g_0$ and $g_1$  on supernova magnitudes
-with probability $1-5\times 10^{-5}$.
-We thus find a strong signal for a linear 
-extrinsic contribution to our model
+our Monte Carlo chains for $\vec{\gamma}$ come close to the origin.   We claim detection
+with probability $1-5\times 10^{-5}$ a magnitude term in the form of a 5-dimensional vector (for the 5 bands) spanned by two basis vectors
 \begin{equation}
-A_X = \gamma^0_X g_0 +  \gamma^1_X g_1.
+\vec{A} = \vec{\gamma}^0 g_0 +  \vec{\gamma}^1 g_1.
 \end{equation}
 
-\added{Dust-extinction
+Dust-extinction
 models are also approximately described by a linear model, here 
-using the commonly-used parameterization of $A_V$ and $E(B-V)$
+using the commonly-used parameters $A_V$ and $E(B-V)$
 \begin{equation}
-A_X = a_X  A_{V} + b_X E(B-V).
+\vec{A} =\vec{ a}  A_{V} + \vec{b} E(B-V).
 \label{f99:eqn}
@@
 In constructing the credible interval of $\sigma_p\vec{\phi}$ 
-we set $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$ to break its parity degeneracy;
-Figure~\ref{global5:fig} shows there the degenerate solutions are relatively well separated 
-in $\sigma_p \phi_{\hat{I}}$.
+we set $\vec{\phi} = -\text{sign}(\phi_{\hat{V}}) \vec{\phi}$ to break its parity degeneracy;
+Table~\ref{global3:tab} shows there the largest signal-to-noise in
+in $\sigma_p \phi_{\hat{V}}$.
 The effect of spectral parameters on color (as opposed to magnitude)
@@
 & $ 0.022^{+ 0.006}_{-0.006}$
+\\
+${\phi_X/\phi_{\hat{V}}-1}$
+& $-1.898^{+ 0.420}_{-0.611}$
+& $-0.333^{+ 0.156}_{-0.181}$
+&\dots
+& $-0.609^{+ 0.109}_{-0.163}$
+& $-1.834^{+ 0.329}_{-0.486}$
 \\
@@
 \begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), \sigma_p\phi_{\hat{I}}p ) =\\
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), \sigma_p\phi_{\hat{V}}p ) =\\
 \begin{pmatrix}
@@
 \ldots  & \ldots &\ldots  & \ldots  & \ldots & \ldots  &E_{\gamma^1}({\hat{B}}-{\hat{V}})  & 0.00^{+0.07}_{-0.07} \\
-\ldots  & \ldots & \ldots & \ldots  & \ldots  & \ldots  &\ldots  & A_{p,I} \\
+\ldots  & \ldots & \ldots & \ldots  & \ldots  & \ldots  &\ldots  & A_{p,V} \\
 \end{array}
@@
    \caption{
-   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and  $A_{p,I}$, as well as the grey offset
+   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and  $A_{p,V}$, as well as the grey offset
 $\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
@@
 extinction for a constant $R^F=2.40$.
-}
+
 Figure~\ref{k0_med:fig} shows the histogram of
@@
 of  $g$ with dust-extinction parameters, this implies that the host environment and the input features are connected.
-The correlation between $EW_{Si}$ and host has  already been noted \citep{2011ApJ...734...42N}.
+The correlations between$EW_{Si}$ and  $EW_{Ca}$  with host have already been noted \citep{2011ApJ...734...42N, 2015MNRAS.451.1973S}.
 There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$.
@@
 \label{p:sec}
-By definition $p$ has a Normal distribution, which is shown, in
-terms of the physically meaningful color-excess $E_p({\hat{B}}-{\hat{V}}) \equiv   p \sigma_p (\phi_{\hat{B}}-\phi_{\hat{V}})$ 
-as the  stack of the posteriors of all supernovae in Figure~\ref{ebv3:fig}.  Also shown for comparison is the distribution of
+The model assumes that $p$ has a Normal distribution, which is shown in
+terms of the color-excess $E_p({\hat{B}}-{\hat{V}}) \equiv   \sigma_p (\phi_{\hat{B}}-\phi_{\hat{V}})p$ 
+.  Also shown for comparison is the distribution of
 the extrinsic  color-excess $E_\gamma({\hat{B}}-{\hat{V}}) \equiv (\gamma^0_{\hat{B}} -\gamma^0_{\hat{V}}) g_0
@@
  %  \includegraphics[width=2.8in]{../output_fix3_x1/ebv_delta.pdf}
-      \caption{Left:  Stack of the posteriors of all supernovae of the external $E({\hat{B}}-{\hat{V}})$ 
-      (including contributions from both $k_0$, $k_1$, and $D$)
-      and
-   internal $E_\delta({\hat{B}}-{\hat{V}}) = (\delta_{\hat{B}}-\delta_{\hat{V}})D$  contributions to color excess relative to an arbitrary supernova, for the objects in our sample.
+      \caption{Stack of the posteriors of all supernovae of the external $E_{\gamma}({\hat{B}}-{\hat{V}})$ 
+      and the 
+   internal $E_p({\hat{B}}-{\hat{V}})$  contributions to color excess relative to an arbitrary supernova.
    \label{ebv3:fig}}
@@
 
-There is no significant correlation between the  intrinsic parameter $p$ and the other features including the extrinsic parameters.
-Their independence implies that two physical parameters are not being artificially attributed to three
+There is no significant correlation between the  intrinsic parameter $p$ and the other features.
+Their independence from the  extrinsic parameters $g_0$ and $g_1$
+implies that two physical parameters are not being artificially attributed to three
 model parameters.  One could have
@@
 
-Color-based magnitude corrections as a function of color excess provide a clue to ``intrinsic'' and ``dust'' attributions of
-the combined effect of the color terms $g_0$, $g_1$, and $p$.  
-All supernovae experience  intrinsic color variation.
-Some encounter dust while others do not:  the distribution of the amount of  dust local to  supernovae within its host and
-geometric projection effects together lead to the expectation for a small but nontrivial fraction  of supernovae of having zero
-dust column density and the
-complement subset having an approximate exponential distribution \citep{1998ApJ...502..177H}.
-Differences between the expected distributions of
-distinct intrinsic effects and dust lead to the prediction of a non-constant slope for the relationship between
-total (from both intrinsic and dust)  magnitude corrections and color excess.
-
-\citetalias{2017ApJ...842...93M} discuss an instructive simulation
-that considers a set of
-supernovae 
-having an intrinsic linear color-magnitude relationship with slope $\beta_{\mathit{int}}$.
-(The absence of an intrinsic color-magnitude relation corresponds to $\beta_{\mathit{int}}=0$.)
-Each supernova encounters dust with a relatively larger slope
-for the color-magnitude relationship and
-extinction drawn from a realistic extinction distribution.
-The expectation is for
-supernovae encountering no interstellar dust  to tend to be bluer and
-collectively exhibit the intrinsic $\beta$ slope for the color-magnitude
-relation.  Supernovae encountering thick dust tend to be redder and collectively exhibit the larger dust  slope.
-This expectation is borne out in Figure 3 of \citetalias{2017ApJ...842...93M}, which
-shows  simulated
-observed color versus light-curve shape corrected magnitudes.
-The distinctive distribution of supernovae in color-magnitude space  allows
-the authors to distinguish intrinsic $\beta_{\mathit{int}}$ and the dust slope,
-despite being
-restricted to using one color observable that is  affected by two sources of extinction.
-
-In our Model~III, each supernova has three color parameters that can distinguish between
-intrinsic and dust contributions whose linear color-magnitude relations are simultaneously determined.
-We see where our best-fit model puts supernovae on a color-magnitude diagram.
-A representative example is shown in Figure~\ref{speccorr:fig}, which plots
-${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 + \sigma_p \phi_{\hat{U}} p$
-as a function of color excess $E_o({\hat{B}}-{\hat{V}})$, where the intrinsic color accounts for spectral-feature corrections.
-The shallower (but non-zero) slope at blue color transitions to a larger slope at red color, 
-as expected  for a mixed intrinsic--dust model.
-The non-zero blue slope implies that the new color term we detect is intrinsic (associated with all supernovae)
-and hence not attributable to dust.
-
-\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=4in]{../output_fix3_x1/ccorr1e.pdf}
-  % \includegraphics[width=2.8in]{../output_fix3_x1/ccorr2e.pdf}
-      \caption{
-      The ${\hat{U}}$-band magnitude corrections from the three color parameters $\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 + \sigma_p \phi_{\hat{U}} p$
-are plotted as a function of $E_o({\hat{B}}-{\hat{V}})$, where the expected color accounts for spectral-feature corrections.  The left plot shows the full
-range of values whereas the right zooms in the upper-left corner of the population.
-   \label{speccorr:fig}}
-\end{figure}
-
-Our evidence for an intrinsic color effect is consistent with the conclusion of  \citetalias{2017ApJ...842...93M} (see their Figure~6.)
-Their intrinsic color-effect discerned using only one color parameter and a reasonable population model
-is likely traced to the additional supernova
-color parameter $D$ identified in this article without reference to a population model.
-We find $\delta_{\hat{B}}/(\delta_{\hat{B}}-\delta_{\hat{V}})=1.27^{ + 1.02}_{ - 1.16}$, which agrees with the  approximately corresponding (given that different broadband
-filters are used) $\beta_{\mathit{int}}=2.3\pm 0.3$ found by \citetalias{2017ApJ...842...93M}.
-\citetalias{2017ApJ...842...93M} treat dust as having constant $R$ whereas we allow $R$ to float 
-from supernova to supernova.  Nevertheless our 68\% credible interval for an
-effective $R^F$ of $2.31$--$2.69$ is consistent with their $R_V=2.8 \pm 0.3$.
+Detection of intrinsic color has been previously reported by \citetalias{2017ApJ...842...93M}.
+For data, they use the outputs of SALT2 fits: the $c$ color parameter associated with but not exactly $B-V$; the
+supernova absolute magnitude $M$ associated with but not exactly $B$.  In the \citetalias{2017ApJ...842...93M}
+model, the color contributes a linear   $\beta_{\mathit{int}} c$ the absolute
+magnitude.
+They find a significant $\beta_{\mathit{int}} = 2.2\pm 0.3$.
+While we also claim a detection of an intrinsic color parameter, the differences between our models and results make it
+difficult to determine whether the results are consistent.   Our results show effects on color that are not monotonic
+with wavelength.  For example, we find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
+is $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -1.9^{+1.0}_{-2.4}$, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.  
+However a change of the color baseline gives a significantly different
+$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =2.2^{+2.1}_{-0.9}$.  Our results indicate that $\beta_{\mathit{int}}$
+is sensitive to the color that $c$ corresponds to.  Although SALT2 $c$ is associated with $B-V$, it is
+determined using data from all bands with the wavelength extremes  typically providing the strongest leverage.
+The SALT2 $c$ parameter is an  amalgamation of all input colors.
+We therefore make no conclusions on the consistency between our intrinsic-color properties
+and those of \citetalias{2017ApJ...842...93M}.
 
@@
 This host-mass bias could be the result of a parameter that was not accounted for in the inference of SN~Ia absolute magnitude.
-Indeed  \citetalias{2017ApJ...842...93M} find that when introducing intrinsic color scatter as a latent parameter, the null mass-step effect becomes more probable.
-The intrinsic $p$ parameter is a possible supernova tracer of a population that to date has only been identified through host-galaxy tracers.
-
-To explore whether the Hubble residual may be due to unaccounted color,
-we plot in Figure~\ref{childress3:fig} our intrinsic parameter
+Indeed  \citetalias{2017ApJ...842...93M} find that the  introduction of intrinsic color as a latent parameter
+reduces the strength of  the mass-step.
+
+It is possible that the intrinsic $p$ parameter is a supernova-tracer of a population that to date has only been identified through host-galaxy tracers.
+We plot in Figure~\ref{childress3:fig} our intrinsic parameter
  $\sigma_p\phi_{\hat{I}}(p-p|_0) $  (subtracting out a random supernova
@@
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
+Low- and high-mass galaxies likely
+host supernovae with different $p$ distributions, as
+the two-tailed $p$-value of the Kolmogorov-Smirnov test is $ 0.02 _ {   -0.02 } ^{   + 0.04 }$.
 The median and median uncertainties of the two subsamples are
 %---
-$\langle \sigma_p\phi_{\hat{I}}(p-p|_0) \rangle=   -0.0186 \pm {    0.0034 }$ mag,
-$\langle \sigma_p\phi_{\hat{I}}(p-p|_0)  \rangle= -0.0293 \pm {    0.0033 }$ mag
-for low- and high-mass hosts respectively, making a difference is $ 0.0141 \pm {    0.0037 }$~mag, significant at almost $4 \sigma$.
-Low- and high-mass galaxies ikely
-host supernovae with different $p$ distributions.  
-The two-tailed $p$-value of the Kolmogorov-Smirnov test is $ 0.02 _ {   -0.02 } ^{   + 0.04 }$.
+$\langle \sigma_p\phi_{\hat{V}}(p-p|_0) \rangle=  0.023 \pm {     0.004}$ mag,
+$\langle \sigma_p\phi_{\hat{V}}(p-p|_0)  \rangle=0.036 \pm {     0.004 }$ mag
+for low- and high-mass hosts respectively, making a difference is $0.013 \pm {     0.005 }$~mag, significant at $>2 \sigma$.
+While we make an association between $p$ and host mass, 
+we refrain from directly associating $p$ with absolute magnitude corrections.
+We preview the discussion in \S\ref{Delta:sec} by mentioning that there is room for $p$-based magnitude corrections
+as seen in the correlation between $\Delta$ and $\sigma_p\phi_{\hat{V}}p$ in Eq.~\ref{corr:eqn}.
 
@@
    \includegraphics[width=4in]{../output_fix3_x1/childress.pdf} 
-   \caption{Intrinsic parameter $\sigma_p\phi_{\hat{I}}p$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
+   \caption{Intrinsic parameter $\sigma_p\phi_{\hat{V}}p$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
       less than and greater than  $\log{(M/M_\sun)}=10$.
@@
 
-This article is confined to the standardization of SN~Ia colors.  Magnitude corrections related to our intrinsic $p$
-parameter that may eliminate the mass step are not pursued.  We confine ourselves to noting the differences in the $p$ distributions of
-low- and high-mass galaxies, and highlighting that there is room for magnitude corrections
-as seen in the correlation between $\Delta$ and $p\sigma_p\phi_{\hat{I}} $ in Eq.~\ref{corr:eqn}.
-
-\subsubsection{$\Delta$: Magnitude Offset}
+\subsubsection{Results for the Magnitude Offset $\Delta$}
 \label{Delta:sec}
@@
 The fit $\Delta$'s are  correlated between supernovae so we consider
-their values elative to that of an arbitrary supernova  $\Delta_0$.
+their values relative to that of an arbitrary supernova  $\Delta_0$.
 The histogram of the per-supernova  medians of these relative  grey offsets $\Delta-\Delta|_0$,
@@
 redshifts of 0.0015 and 0.0086. 
-There are $>2 \sigma$ correlations between $\Delta$ and each of $\lambda_{Si}$, $x_1$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$, and
-$p\sigma_p\phi_{\hat{I}}$, showing that in addition to standardizing colors, these features can also be used to standardize
+Eq.~\ref{corr:eqn} shows $>2 \sigma$ correlations between $\Delta$ and each of $\lambda_{Si}$, $x_1$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$, and
+$\sigma_p\phi_{\hat{V}}p$, showing that in addition to standardizing colors, these features can also be used to standardize
 absolute magnitudes.   
+The focus of this article is color standardization so absolute magnitude standardization his is beyond the scope of this article
 
@@
     an arbitrary supernova and subtract out its $\Delta|_0$ from those of all other objects at the level of each MCMC link.
-   The supernovae with the four highest values of $\Delta$ have, with increasing $\Delta$, heliocentric
-   redshifts of 0.0228, 0.0086, 0.0565, and 0.0015.
+  Of the four
+supernovae with the highest values of $\Delta$, two have 
+heliocentric
+redshifts of 0.0015 and 0.0086. 
    \label{hist:fig}}
@@
 distribution of $A_V$.  
-The data show the need for at least two color parameters that can be attributed to a broad distribution  of
-$R^F$ parameter values,
-with an effective $R^F_\mathit{eff}=2.4$ and with an infrequent but extended scatter toward lower values.
-A significant bias in $R^F$ is obtained when the possibility of another source of color variation
-is unaccounted for.
+We find a broad distribution for $R^F$ with an effective $R^F_\mathit{eff}=2.4$ and an asymmetric tail extending toward lower values.
 We identify a new
@@
 with the Hubble diagram mass-step.
+A significant bias in $R^F$ is obtained when this third source of color variation
+is unaccounted for.
 
@@
 Finding slight color perturbations in the multi-band light curves 
-of those samples that are  consistent with our $\sigma_p \vec{\phi}$ would provide strong evidence for  an
-observational signature of the intrinsic SN color-magnitude relationship.
-
-The current data shows a statistically significant difference in the values of our new parameter for supernovae
+of those samples that are  consistent with our $\sigma_p \vec{\phi}$ would provide strong evidence 
+that we and  \citetalias{2017ApJ...842...93M}  are seeing the effect of the same intrinsic color and for an
+observational signature of the intrinsic SN color relationship.
+
+The current data shows a statistically significant difference in the distribution of our new parameter for supernovae
 in low- and high-mass host-galaxies.
@@
 the continued study of
-NIR light-curve properties and their relation with colors, host properties, and magnitudes.  Measuring the
-correlation between our parameter and infrared light curves  is also planned for future work.
+NIR light-curve properties and their relation with colors, host properties, and  magnitudes.
+
+}
 
@@
 For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,
-$\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p\vec{\phi}$
-are given in Table~\ref{global2:tab}.
-Figure~\ref{global5:fig} shows that the $\hat{I}$-band has
-the largest separation between the degenerate solution of $\sigma_p \phi_X$.  To break the degeneracy we enforce a positive value for
-$\phi_{\hat{I}}$, 
-that is $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$.
-As the $\vec{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
-their results are shown in terms of $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
+$\vec{\gamma}^0$ and $\vec{\gamma}^1$ of Model~I are given in  Table~\ref{global2:tab}.
+The results for the same parameters and $\sigma_p\vec{\phi}$
+of Model~II are given in Table~\ref{global2:tab}.  In contrast to Model~III,
+Figure~\ref{M1ev:fig} shows that the $\hat{I}$-band has
+the largest separation between the degenerate solution of $\sigma_p \phi_X$.  To break the degeneracy we enforce 
+$\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$.
 
@@
 & $   0.1^{+   0.0}_{  -0.0}$
-& $   0.0^{+   0.0}_{   0.0}$
+& \ldots
 & $  -0.0^{+   0.0}_{  -0.0}$
@@
 & $ -0.05^{+  0.01}_{ -0.01}$
-& $  0.00^{+  0.00}_{  0.00}$
+& \ldots
 & $ -0.17^{+  0.01}_{ -0.01}$
@@
 & $ -0.25^{+  0.11}_{ -0.24}$
-& $  0.00^{+  0.00}_{  0.00}$
+& \ldots
 & $ -0.03^{+  0.11}_{ -0.06}$
@@
 & $  0.40^{+  0.03}_{ -0.03}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\ldots
 & $ -0.24^{+  0.01}_{ -0.01}$
@@
 & $ -0.02^{+  0.03}_{ -0.03}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\ldots
 & $ -0.24^{+  0.02}_{ -0.03}$
@@
 \end{table}
-
-Figure~\ref{global5:fig} shows that the $\hat{I}$-band has
-the largest separation between the degenerate solution of $\sigma_p \phi_X$.  To break the degeneracy we enforce a positive value for
-$\phi_{\hat{I}}$, 
-that is $\vec{\phi} = \text{sign}(\phi_{\hat{I}}) \vec{\phi}$.
-As the $\vec{\gamma}$ parameters are free up to a multiplicative constant and have non-zero values of $\gamma^i_{\hat{V}}$,
-their results are shown in terms of $\gamma^i_X/\gamma^i_{\hat{V}}-1$.
 
@@
 & $   0.1^{+   0.1}_{  -0.1}$
-& $   0.0^{+   0.0}_{   0.0}$
+& \ldots
 & $  -0.0^{+   0.1}_{  -0.1}$
@@
 & $ -0.04^{+  0.02}_{ -0.02}$
-& $  0.00^{+  0.00}_{  0.00}$
+&\ldots
 & $ -0.16^{+  0.01}_{ -0.01}$
@@
 & $ -0.29^{+  0.10}_{ -0.14}$
-& $  0.00^{+  0.00}_{  0.00}$
+& \ldots
 & $  0.01^{+  0.06}_{ -0.04}$
@@
 & $  0.33^{+  0.03}_{ -0.03}$
-& $  0.00^{+  0.00}_{  0.00}$
+& \ldots
 & $ -0.24^{+  0.01}_{ -0.01}$
@@
 & $ -0.47^{+  0.15}_{ -0.25}$
-& $  0.00^{+  0.00}_{  0.00}$
+& \ldots
 & $ -0.15^{+  0.04}_{ -0.04}$
@@
 \\
+${\phi_X/\phi_{\hat{I}}-1}$
+& $-0.718^{+ 0.244}_{-0.254}$
+& $-1.574^{+ 0.233}_{-0.319}$
+& $-1.584^{+ 0.234}_{-0.342}$
+& $-1.230^{+ 0.170}_{-0.246}$
+& \ldots
+\\
 \hline

### 2017-12-02 submit/fix.tex
done going to push to PC

@@
 The color changes allowed by two of the color parameters are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F}. 
-Correspondingly the sample has an effective value of $R^F_{\mathit{eff}} \sim 2.40$, though with a broad distribution of free
+Correspondingly the sample has an effective value of $\langle R^F_{\mathit{eff}}\rangle \sim 2.40$, though with a broad distribution of 
 total-to-selective extinctions. 
@@
 None of the 20000 links of 
-our Monte Carlo chains for $\vec{\gamma}$ come close to the origin.   We claim detection
-with probability $1-5\times 10^{-5}$ a magnitude term in the form of a 5-dimensional vector (for the 5 bands) spanned by two basis vectors
+our Monte Carlo chains for $\vec{\gamma}$ come close to the origin.   We claim 
+a probability $(1-5\times 10^{-5})$-detection of
+a magnitude term in the form of a 5-dimensional vector spanned by two basis vectors
 \begin{equation}
@@
 \end{equation}
+All possible magnitude changes in our five bands due to $g_0$ and $g_1$ are confined to a two-dimensional
+plane defined by $\vec{\gamma}^0$ and  $\vec{\gamma}^1$.
 
 Dust-extinction
-models are also approximately described by a linear model, here 
+models are also approximately described by a 2-parameter linear model, here 
 using the commonly-used parameters $A_V$ and $E(B-V)$
@@
  the largest error in extinction from the linear approximation having amplitude $<0.008$ mag.
-
-\added{Our model $\vec{\gamma}$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
+\added{
+All possible magnitude changes in our five bands due to  \citetalias{1999PASP..111...63F}  dust extinction are confined to a two-dimensional
+plane defined by $\vec{a}$ and  $\vec{b}$.
+
+Our model $\vec{\gamma}$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
 dust-based $\vec{a}$ and $\vec{b}$ vectors plus residual vectors perpendicular to the plane spanned by $\vec{a}$ and $\vec{b}$,
@@
 \end{equation}
-The $\vec{\gamma}$'s are almost entirely captured by the first term. 
-A quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ is projected onto $\vec{a}$--$\vec{b}$ plane, as is
-$0.959^{+0.013}_{-0.024}$.of $\vec{\gamma}^1$.}
+The $\vec{\gamma}$'s derived from our analysis are almost entirely captured by the first term;
+a quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ and
+$0.959^{+0.013}_{-0.024}$ of $\vec{\gamma}^1$ project onto the $\vec{a}$--$\vec{b}$ plane.}
 The allowed color
@@
 now turn to
-the specific choice of $\vec{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust-extinction model. 
+the specific choice of $\vec{\gamma}$'s  returned by the fit in terms of the \citetalias{1999PASP..111...63F}  dust-extinction model. 
 Our linear model would be satisfied by any two independent vectors  that span
-the plane defined by the $\vec{\gamma}$ vectors.  While
+the plane defined by the $\vec{\gamma}$ vectors. 
+\added{While
 Eq.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
@@
 $A_V$ and 
-$E(B-V)$, the linear dust model 
-alternatively
-could be written in terms of any two other basis vectors  $\vec{a}+\kappa_1 \vec{b}$
-and $\kappa_2 \vec{a} + \vec{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
-In this basis, the model is then
+$E(B-V)$, it can be written more generally using arbitrary bases $\vec{a}+\kappa_1 \vec{b}$
+and $\kappa_2 \vec{a} + \vec{b}$, and parameter sets
+$A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  such that 
 \begin{equation}
@@
 \end{equation}
-with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  equal to  linear combinations of the original parameters.
-\added{The color vectors in this equation are associated with those of  Eq.~\ref{trans_I:eqn} by assigning $\kappa_1=M[1,2]/M[1,1]$, $\kappa_2=M[2,1]/M[2,2]$.}
+where $\kappa_1$ and $\kappa_2$ are free to float.
+In our analysis, the $\vec{\gamma}$ vectors converge to a specific direction, meaning that our result prefers specific values of
+$\kappa_1=M[1,2]/M[1,1]$ and $\kappa_2=M[2,1]/M[2,2]$, where $M$ is the matrix in  Eq.~\ref{trans_I:eqn}.}
 
@@
 \added{
-The posterior yields $R^F_{\mathit{eff}} =2.18^{+0.14}_{-0.16}$.
+The posterior yields $\langle R^F_{\mathit{eff}}\rangle =2.18^{+0.14}_{-0.16}$.
 Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.18$.
@@
 %the extinction from a single effective
-%$\langle R^F_{\mathit{eff}}\rangle$, $\vec{\gamma}^1$ is associated with perturbations
+%$\langle \langle R^F_{\mathit{eff}}\rangle\rangle$, $\vec{\gamma}^1$ is associated with perturbations
 %away from that effective value.
@@
 \begin{itemize}
-\item This model introduces two latent supernova parameters that can influence supernova colors with ``non-informative'' priors.  Fitting
+\item Model~I introduces two latent supernova parameters that can influence supernova colors.
+These parameters come  with ``non-informative'' priors.  Fitting
 of our model gives a space of possible color variations highly consistent with those expected from two-parameter dust-extinction models. 
@@
 one parameter for the optical depth of dust, one parameter to capture variation in dust properties, and
-another parameter for intrinsic color variability unrelated to dust.  In this section we  focus on describing the consequences of the addition of the
+another parameter for  color variability unrelated to dust.  In this section we  focus on describing the consequences of the addition of the
 new parameter.
@@
 Model~II is identical to Model~I except for the 
-addition of an intrinsic color parameter $p$.  The distribution of this parameter over all supernovae is
-assumed to be drawn from a Normal distribution with unit standard deviation; leaving the distribution unconstrained,
-as was done for $g_0$ and $g_1$, yields many local maxima in the posterior and makes MCMC convergence difficult.
-The relative effect on each band is specified by the global parameters 
-$\sigma_p\vec{\phi}$, where $\vec{\phi}$ is a unit vector.
+addition of an intrinsic color parameter $p$.  The distribution of $p$ in our sample
+is assumed to form a Normal distribution with unit standard deviation.  An unconstrained distribution,
+as taken for $g_0$ and $g_1$, yields multiple local maxima in the posterior and leads to difficulty in the convergence of the MCMC.
+The relative effect on the five magnitudes is specified by the global parameters 
+$\sigma_p\vec{\phi}$, where $\vec{\phi}$ is a 5-dimensional unit vector.
 Model~II reads as
@@
 put the term in the mean of Eq.~\ref{dust2:eqn} joining what we call extrinsic parameters.  Although we 
-use ``intrinsic'' and ``extrinsic'' as descriptive labels for $\phi$ and $\gamma$ respectively, the model cannot distinguish between
+use ``intrinsic'' and ``extrinsic'' as descriptive labels for $\vec{\phi}$ and $\vec{\gamma}$ respectively, the model cannot distinguish between
 their physical origins.
@@
 $\vec{\phi} p$, which has the degeneracy $\vec{\phi} \rightarrow -\vec{\phi}$, $p \rightarrow -p$.
-No conditions are added to break this degeneracy as we want to explore the possibility that
+No conditions are added to break this degeneracy to leave open the possibility that
 $\sigma_p\vec{\phi}$ is consistent with zero.  The degeneracy
@@
 
-\subsection{Results -- $\sigma_p \vec{\phi}$: Cofactor of the Intrinsic Color Parameter}
+\subsection{Results for the Intrinsic Latent Parameter Cofactor $\sigma_p \vec{\phi}$}
 \label{results2:sec}
+The credible intervals of all Model~II global parameters are given in  \S\ref{m12results:sec}.
 In this subsection we focus on the effect of adding the third color term  $\sigma_p \vec{\phi}$.
@@
 the $\vec{\gamma}$ vectors; only a quadratic fraction of
- $0.088^{+0.118}_{-0.063}$ of 
+ $0.09^{+0.12}_{-0.06}$ of 
  $\vec{\phi}$ lies in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.
@@
 
-Model~II introduces a new parameter  that can absorb color varability
-that was restricted to $g_0$ and $g_1$ in Model~I, and whose distribution comes from a Normal distribution.
+Model~II introduces a new parameter  that can absorb color variability
+that in Model~I is restricted to $g_0$ and $g_1$, and whose distribution comes from a Normal distribution.
 The change in the distributions of the $\gamma^0_{\hat{V}} g_0$ and $\gamma^1_{\hat{V}}g_1$ parameters from
  Model~I to Model~II
-is apparent in Figure~\ref{kcomp:fig}.  (Here and in future plots, the parameter value of one supernova,
+is apparent in Figure~\ref{kcomp:fig}.  (Here and in similar plots, the parameter value of one supernova,
 e.g.\ $\gamma^0_{\hat{V}} g_0|_0$, is subtracted
 out to null out correlated error between supernovae.) The  change from Model~I to II is pronounced in  $\gamma^1_{\hat{V}}g_1$,
-where it seems that a Normal distribution component in Model~I disappears in Model~II, presumably having been  assigned to $p$.
+where  a Normal distribution component apparent in Model~I disappears in Model~II, presumably having been  assigned to $p$.
 
@@
 $\vec{a}$ and $\vec{b}$ of the \citetalias{1999PASP..111...63F} model.
-The direction of the  $\vec{\gamma}^0$ vector corresponds to an effective $R^F_{\mathit{eff}} = 2.54^{+0.20}_{-0.20}$.
-
-The credible intervals of all Model~II global parameters are given in  \S\ref{m12results:sec}.
+The direction of the  $\vec{\gamma}^0$ vector corresponds to an effective $\langle R^F_{\mathit{eff}}\rangle = 2.54^{+0.20}_{-0.20}$.
+The change of $\langle R^F_{\mathit{eff}}\rangle$ from Model~I to II is anticipated by the change in the distribution of $g_1$,
+whose connection with $R^F$ is shown in \S\ref{g0g1:sec}.
 
 \subsection{Remarks}
-The inclusion of a third color term beyond the two (which are expected from dust-extinction models) of Model~I has important consequences.
+The inclusion of a third color term beyond the two of Model~I has important consequences.
 
@@
  dust extinction.
-\item The effective $R^F_{\mathit{eff}}$ shifts by $>1 \sigma$ when including the new color term.  This demonstrates,
+\item The effective $\langle R^F_{\mathit{eff}}\rangle$ shifts by $>1 \sigma$ when including the new color term.  This demonstrates,
 as has been noted by \citet{2011A&A...529L...4C}, that dust analyses
@@
 with its own color correlations \citep{2005A&A...443..781G, 2007ApJ...659..122J}.
-Model~III explicitly includes light-curve shape as a feature used to standardize supernova colors, in addition to the
+Model~III explicitly includes light-curve shape as a feature used to standardize supernova colors, to complement the
 spectral features considered in the previous two models.
@@
 addition of a new term  that relates magnitudes with the SALT2 light-curve-shape parameter,
-$x_1$, through linear coefficients $\zeta$. 
+$x_1$, through linear coefficients $\vec{\zeta}$. 
 The model reads as
@@
 For $N=172$ supernovae, this makes 1548 observables and 1413  parameters.
+}
 
@@
 
-The algorithm is run with input simulated data with known  signals and measurement uncertainties similar to those of our dataset.
+\added{
+
+Our analysis pipeline is run with input simulated data with known  signals and measurement uncertainties similar to those of our dataset.
 Stacks of the posteriors from 100 simulated datasets  exhibit no biases that are significant relative to the statistical uncertainties of a single posterior.
 
-As will be seen in  \S\ref{results3global:sec}, the final posterior has a distinct bounded  
+As will be seen in  \S\ref{results3global:sec}, the posterior derived from the analysis has a distinct bounded  
 peak showing no indication that the MCMC has failed to converge.
@@
             \caption{Observed  versus
-            Model~III-expectation colors (including  contributions related to spectral features, light-curve shape, $\gamma g$, and $\phi p$  terms)
+            Model~III-expectation colors (including  contributions related to spectral features, light-curve shape, $\vec{\gamma} g$, and $\vec{\phi} p$  terms)
 for four selected colors. 
@@
 Within the finite number of generated links, the MCMC chains do not migrate between the parity-degenerate $\vec{\gamma}$--$g$ solutions.
-Each chain converges to one of the  $\vec{\phi}$--$p$ degenerate solutions, away from which it does not migrate.
+Each chain converges to one of the  $\vec{\phi}$--$p$ degenerate solutions, away from which it does not depart.
 
@@
 we set $\vec{\phi} = -\text{sign}(\phi_{\hat{V}}) \vec{\phi}$ to break its parity degeneracy;
-Table~\ref{global3:tab} shows there the largest signal-to-noise in
-in $\sigma_p \phi_{\hat{V}}$.
+Table~\ref{global3:tab} shows it has the largest signal-to-noise in
+in the $\hat{V}$-band.
 The effect of spectral parameters on color (as opposed to magnitude)
@@
 
-The story on the Si~II~$\lambda$6355 is not as clear.
+The story on Si~II~$\lambda$6355 is not as clear.
  \citet{2011ApJ...742...89F, 2012ApJ...748..127F} find that
@@
 
-The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is also an indicator
+The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is  an indicator
 of broadband colors, in the sense that SNe~Ia with broader light curves are bluer in all colors.
-This is as expected based on the results of \citet{2007A&A...466...11G} and MLCS2k2
-\citep{2007ApJ...659..122J}.
+This is as expected based on the results of \citet{2007A&A...466...11G, 2007ApJ...659..122J}.
 }
@@
 The direction of the vector in the ${\hat{U}}{\hat{V}}{\hat{I}}$-subspace is shown in Figure~\ref{plane3:fig}.
-The posterior gives a quadratic fraction of $0.9996^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ that projects onto the plane of
+
+The transformation between the $\vec{\gamma}$  vectors and the   \citetalias{1999PASP..111...63F} vector given in
+Eq.~\ref{trans_I:eqn}, is satisfied by the transformation matrix
+\begin{equation}
+M=
+\begin{pmatrix}
+\begin{array}{rr}
+39.7^{+2.4}_{-2.5} & 16.6^{+0.6}_{-0.6}  \\
+-14.7^{+3.4}_{-3.4} & 3.7^{+1.0}_{-0.9}  
+\end{array}
+\end{pmatrix} 
+\end{equation}
+and the two residual vectors
+\begin{align}
+\begin{split}
+\vec{\epsilon}_{\gamma^0} &=\left(1.0^{+0.4}_{-0.4} , -1.2^{+0.4}_{-0.4} , -0.8^{+0.4}_{-0.4} , 0.7^{+0.2}_{-0.2} , 0.4^{+0.6}_{-0.6}\right), \\
+\vec{\epsilon}_{\gamma^1} & =\left(-2.7^{+0.6}_{-0.6} , 4.3^{+0.6}_{-0.6} , -0.8^{+0.6}_{-0.6} , 1.2^{+0.3}_{-0.3} , -2.6^{+0.9}_{-0.9}\right).
+\end{split}
+\label{res_3:eqn}
+\end{align}
+This corresponds to a quadratic fraction of $0.9996^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ that projects onto the plane of
 color changes allowed by the \citetalias{1999PASP..111...63F} dust-extinction model
 as described by
-$\vec{a}$ and $\vec{b}$, the quadratic fraction of $\vec{\gamma}^1$ projected
+$\vec{a}$ and $\vec{b}$. The quadratic fraction of $\vec{\gamma}^1$ projected
 onto this plane is
 $0.959^{+0.015}_{-0.029}$.
-The   $\vec{\gamma}$  vectors project  onto an $R^F_{\mathit{eff}}=2.40^{+0.15}_{-0.15}$.
+The   $\vec{\gamma}^0$  vector points in the $\langle R^F_{\mathit{eff}}\rangle=2.40^{+0.15}_{-0.15}$ dust-extinction direction.
 This value is consistent with the $R_V=2.5$ found in the supernova samples of \citet{2011ApJ...729...55F}, and the
@@
 Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are attributed to dust extinction.
-Further discussion on this association is given in the discussion of $g_0$ and $g_1$  in \S\ref{g0g1:sec}.
+This association is further discussed when $g_0$ and $g_1$ are considered in \S\ref{g0g1:sec}.
 
@@
    \caption{
-   Visualization of how supernova magnitudes can vary in Model~III and that of \citetalias{1999PASP..111...63F}.
+   Visualization of how supernova magnitudes can vary in Model~III and the dust extinction of \citetalias{1999PASP..111...63F}.
    See Figure~\ref{plane:fig}.
@@
 the combination $\phi_X/\phi_{\hat{V}}-1$ shown in Figure~\ref{phiratio:fig}.  They have the property that
-a reddening $\hat{B}-\hat{V}$ is accompanied with a bluing in $\hat{V}-\hat{R}$.  The reddening and bluing are accentuated 
-in the extreme $\hat{U}$ and $\hat{I}$ bands. Absorption and re-emission of light
-over broad bands are the most obvious candidate for producing this behavior, a process
+a reddening $\hat{B}-\hat{V}$ is accompanied with a bluing in $\hat{V}-\hat{R}$.  The reddening and bluing are
+further accentuated 
+in the extreme $\hat{U}$ and $\hat{I}$ bands. The absorption and re-emission of light
+over broad bands is the obvious candidate for producing this behavior, a process
 already associated with SNe~Ia.
@@
 
-To temper our physical interpretation of $p$, 
-we emphasize that
+We emphasize that
 although the $\sigma_p \vec{\phi}p$ colors have ben referred to as ``intrinsic'' due to their placement in the model, the analysis cannot quantitatively distinguish
 whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
-There is likely more than one physical affect being attributed to $p$, leading to a $\sigma_p \vec{\phi}$ that does not correspond to a single process.
+What is measured as $\sigma_p \vec{\phi}$ likely captures the effect of many physical processes.
 To simplify the model it is assumed that the $p$'s are drawn from a Normal distribution, which may not be a fair description of what occurs in nature.
+The physical interpretation of this intrinsic color should be tempered with caution.
 
@@
 Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$,
-$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $A_{p,I} =  \sigma_p\phi_{\hat{I}}p$.
-(The  three latent parameters are multiplied by select cofactors
-that give the physically color excess and extinction.)
+$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $A_{p,V} =  \sigma_p\phi_{\hat{I}}p$.
+(The  three latent parameters are cast as physically meaning
+quantities by multiplying them by select cofactors.)
 The distributions of the Monte Carlo links for all supernovae are shown in Figure~\ref{perobject3:fig}.
-Each supernova is represented by a cloud of its parameters from all links.
+Each supernova is represented by a cloud of its parameters' links.
 There is a core concentration in the  parameter-space, with around eight objects that occupy its outskirts.
@@
 \begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), \sigma_p\phi_{\hat{V}}p ) =\\
+Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}) =\\
 \begin{pmatrix}
@@
 The vector
-$\vec{\gamma}^0$ describes color changes for an effective $R^F_{\mathit{eff}}=2.40$ dust, as shown 
-In  \S\ref{results3gamma:sec}.
+$\vec{\gamma}^0$ describes color changes for an effective $\langle R^F_{\mathit{eff}}\rangle=2.40$ dust, as shown 
+in  \S\ref{results3gamma:sec}.
 Hence, the per-supernova parameter $\gamma^0_{\hat{V}} g_0$ is associated with the $\hat{V}$-band
-extinction for a constant $R^F=2.40$.
-
+extinction for a constant $R^F=2.40$.}
 Figure~\ref{k0_med:fig} shows the histogram of
@@
 relative to that of an arbitrary supernova  $\gamma^0_{\hat{V}} g_0|_0$.
-(Subtracting the value of the one supernova suppresses correlated errors common to all supernovae.)
 The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
@@
       of  per-supernova 
-median values of: (left) $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$, which is associated with the $A^F_V$ of an $R^F_{\mathit{eff}} \sim 2.4$ dust model;
+median values of: (left) $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$, which is associated with the $A^F_V$ of an $\langle R^F_{\mathit{eff}}\rangle \sim 2.4$ dust model;
 (right) $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$,
-which  is associated with extinction corrections due to deviations away from the canonical $R^F_{\mathit{eff}}$ value.
+which  is associated with extinction corrections due to deviations away from the canonical $\langle R^F_{\mathit{eff}}\rangle$ value.
    \label{k0_med:fig}}
@@
 \added{
-An instructive way to consider the  $\{g_0, g_1\}$ parameters
+An instructive way to consider the  $\{g_0, g_1\}$ parameters is
 to transform them to $\{A_V^F, E^F(B-V)\}$ (modulo additive constants)   using the
@@
 sample is shown in Figure~\ref{kk:fig}. 
-For reference, a line that represents $R^F_{\mathit{eff}}=2.4$ is overplotted; points above
+For reference, a line that represents $\langle R^F_{\mathit{eff}}\rangle=2.4$ is overplotted; points above
 the line have larger $R^F$, points below have smaller $R^F$.  The majority of supernovae lie within a narrow range above the line,
@@
 \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
-Our model does not specify
-the magnitudes or colors of a supernova that does not experience dust.  Without further assumptions, it cannot give
-per-supernova determinations of $R^F$.
+Our model cannot provide the range of $R^F$ in our sample nor per-supernova determinations of $R^F$ 
+without further assumptions.
 
@@
 of  $g$ with dust-extinction parameters, this implies that the host environment and the input features are connected.
-The correlations between$EW_{Si}$ and  $EW_{Ca}$  with host have already been noted \citep{2011ApJ...734...42N, 2015MNRAS.451.1973S}.
+The correlations between $EW_{Si}$ and  $EW_{Ca}$  with host have already been noted \citep{2011ApJ...734...42N, 2015MNRAS.451.1973S}.
 There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$.
-This contrasts with studies of high-velocity features (HVF) identified using
-Si~II~$\lambda$6355 that find correlations with host galaxy properties
+This contrasts with the subset of supernovae identified by their high-velocity features (HVF) in
+Si~II~$\lambda$6355, who are found to be distinguished by their host galaxy properties
 \citep[e.g.][]{2014MNRAS.444.3258M, 2015MNRAS.446..354P, 2015ApJS..220...20Z}.
-The population and properties of HVF SNe within the SNfactory sample will be presented in \citep{2018lin}.
-The correlation of $x_1$ with with host-galaxy (including dust) properties is  well established 
+The population and properties of HVF SNe within the SNfactory sample will be presented in \citet{2018lin}.
+The correlation of $x_1$ with  host-galaxy (including dust) properties is  well established 
 \citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
-
-}
 
@@
 \label{p:sec}
-The model assumes that $p$ has a Normal distribution, which is shown in
-terms of the color-excess $E_p({\hat{B}}-{\hat{V}}) \equiv   \sigma_p (\phi_{\hat{B}}-\phi_{\hat{V}})p$ 
-.  Also shown for comparison is the distribution of
+The model assumes that $p$ has a Normal distribution, which is shown in Figure~\ref{ebv3:fig} as the 
+stack of the posteriors of all supernovae of the external color-excess $E_{\gamma}({\hat{B}}-{\hat{V}})$.
+Also shown for comparison is the distribution of
 the extrinsic  color-excess $E_\gamma({\hat{B}}-{\hat{V}}) \equiv (\gamma^0_{\hat{B}} -\gamma^0_{\hat{V}}) g_0
@@
 The latter is comparable to the typical measurement uncertainty.
-The extrinsic color variation is much larger than that of the intrinsic and it is from the simultaneous analysis of an ensemble of objects that the intrinsic
-color is discerned.
+In $\hat{B}-\hat{V}$, 
+the extrinsic color variation is much larger than that of the intrinsic and its effect per-supernova would be difficult to discern.
 
@@
 Detection of intrinsic color has been previously reported by \citetalias{2017ApJ...842...93M}.
-For data, they use the outputs of SALT2 fits: the $c$ color parameter associated with but not exactly $B-V$; the
-supernova absolute magnitude $M$ associated with but not exactly $B$.  In the \citetalias{2017ApJ...842...93M}
-model, the color contributes a linear   $\beta_{\mathit{int}} c$ the absolute
+For data, they use the outputs of SALT2 fits: the $c$ color parameter ;
+%associated with but not exactly $B-V$
+the
+supernova absolute magnitude $M$.
+% associated with but not exactly $B$.
+In the \citetalias{2017ApJ...842...93M}
+model, intrinsic color contributes a linear   $\beta_{\mathit{int}} c$ to  the absolute
 magnitude.
 They find a significant $\beta_{\mathit{int}} = 2.2\pm 0.3$.
-While we also claim a detection of an intrinsic color parameter, the differences between our models and results make it
+While we also claim a detection of an intrinsic color parameter, the differences between our models make it
 difficult to determine whether the results are consistent.   Our results show effects on color that are not monotonic
 with wavelength.  For example, we find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
-is $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -1.9^{+1.0}_{-2.4}$, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.  
+to be $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -1.9^{+1.0}_{-2.4}$, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.  
 However a change of the color baseline gives a significantly different
 $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =2.2^{+2.1}_{-0.9}$.  Our results indicate that  $\beta_{\mathit{int}}$
-is sensitive to the color that $c$ corresponds to.  Although SALT2 $c$ is associated with $B-V$, it is
+is sensitive to the color that $c$ corresponds to.  Although SALT2 $c$ is calibrated to correspond with $B-V$, it is
 determined using data from all bands with the wavelength extremes  typically providing the strongest leverage.
-The SALT2 $c$ parameter is an  amalgamation of all input colors.
+The $c$ parameter is thus an  amalgamation of all input colors.
 We therefore make no conclusions on the consistency between our intrinsic-color properties
-and those of \citetalias{2017ApJ...842...93M}.
+and those found by \citetalias{2017ApJ...842...93M}.
 
 An independent piece of information available for a subset of our supernova sample is host-galaxy mass \citep{2013ApJ...770..108C}.  
-This statistic is of interest, as a correlation between Hubble residual and host-galaxy mass
-was first noted by \citet{2010ApJ...715..743K,2010MNRAS.406..782S}, a signal confirmed to exist in the SNfactory
+This statistic is of interest, as there is a correlation between Hubble residual and host-galaxy mass
+\citep[first noted by][]{2010ApJ...715..743K,2010MNRAS.406..782S}, a signal confirmed to exist in the SNfactory
 sample \citep{2013ApJ...770..108C}.
@@
 Indeed  \citetalias{2017ApJ...842...93M} find that the  introduction of intrinsic color as a latent parameter
-reduces the strength of  the mass-step.
+reduces the strength of  this bias.
 
@@
 for the subset of supernovae whose host measurements are given in \citet{2013ApJ...770..108C}.
-Low- and high-mass galaxies likely
-host supernovae with different $p$ distributions, as
-the two-tailed $p$-value of the Kolmogorov-Smirnov test is $ 0.02 _ {   -0.02 } ^{   + 0.04 }$.
+Low- and high-mass galaxies, divided by $\log{(M/M_\sun)}=10$, have high probability of hosting supernovae with different $p$ distributions, as
+the Kolmogorov-Smirnov test gives a two-tailed $p$-value of $ 0.02 _ {   -0.02 } ^{   + 0.04 }$.
 The median and median uncertainties of the two subsamples are
@@
 $\langle \sigma_p\phi_{\hat{V}}(p-p|_0)  \rangle=0.036 \pm {     0.004 }$ mag
-for low- and high-mass hosts respectively, making a difference is $0.013 \pm {     0.005 }$~mag, significant at $>2 \sigma$.
-While we make an association between $p$ and host mass, 
-we refrain from directly associating $p$ with absolute magnitude corrections.
-We preview the discussion in \S\ref{Delta:sec} by mentioning that there is room for $p$-based magnitude corrections
-as seen in the correlation between $\Delta$ and $\sigma_p\phi_{\hat{V}}p$ in Eq.~\ref{corr:eqn}.
+for low- and high-mass hosts respectively, with a difference of $0.013 \pm {     0.005 }$~mag that is significant at $>2 \sigma$.
+
+In this article we do not associate $p$ directly with Hubble residuals.  However,
+we briefly  preview the discussion in \S\ref{Delta:sec} by mentioning that there is room for $p$-based magnitude corrections
+given the correlation between $\Delta$ and $\sigma_p\phi_{\hat{V}}p$ in Eq.~\ref{corr:eqn}.
 
@@
 The color-standardization leaves magnitude residuals $\Delta$.
-The fit $\Delta$'s are  correlated between supernovae so we consider
-their values relative to that of an arbitrary supernova  $\Delta_0$.
 The histogram of the per-supernova  medians of these relative  grey offsets $\Delta-\Delta|_0$,
@@
 absolute magnitudes.   
-The focus of this article is color standardization so absolute magnitude standardization his is beyond the scope of this article
+The focus of this article is color standardization so we defer consideration of absolute-magnitude standardization to future work.
 
@@
 distribution of $A_V$.  
-We find a broad distribution for $R^F$ with an effective $R^F_\mathit{eff}=2.4$ and an asymmetric tail extending toward lower values.
+We find a broad distribution for total-to-selective extinction
+with an effective
+$\langle R^F_{\mathit{eff}}\rangle \sim 2.40$ and an asymmetric tail extending toward lower values.
 We identify a new
@@
 of those samples that are  consistent with our $\sigma_p \vec{\phi}$ would provide strong evidence 
-that we and  \citetalias{2017ApJ...842...93M}  are seeing the effect of the same intrinsic color and for an
+that we and  \citetalias{2017ApJ...842...93M}  are seeing the same intrinsic color and to confirm the
 observational signature of the intrinsic SN color relationship.
@@
 the continued study of
-NIR light-curve properties and their relation with colors, host properties, and  magnitudes.
+NIR light-curve shpae properties and their relation with colors, host properties, and  magnitudes.
 
@@
 \appendix
+\added{
 \section{Results from Model~I and II}
@@
 \end{table}
-
+}
 \bibliographystyle{apj}

### 2017-12-09 submit/fix.tex
fixed normalization bug in stan

@@
 The color changes allowed by two of the color parameters are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F}. 
-Correspondingly the sample has an effective value of $\langle R^F_{\mathit{eff}}\rangle \sim 2.40$, though with a broad distribution of 
+Correspondingly the sample has an effective value of $\langle R^F_{\mathit{eff}}\rangle \sim 2.39$, though with a broad distribution of 
 total-to-selective extinctions. 
@@
 & $0.0059^{+0.0007}_{-0.0008}$
-& $0.0033^{+0.0006}_{-0.0007}$
+& $0.0032^{+0.0006}_{-0.0007}$
 & $0.0029^{+0.0006}_{-0.0006}$
 & $0.0026^{+0.0005}_{-0.0005}$
-& $0.0041^{+0.0004}_{-0.0005}$
+& $0.0041^{+0.0004}_{-0.0004}$
 \\
@@
 & $   0.1^{+   0.1}_{  -0.1}$
-&\dots
+& \dots
 & $  -0.1^{+   0.0}_{  -0.0}$
@@
 & $ 0.016^{+ 0.004}_{-0.004}$
-& $ 0.008^{+ 0.004}_{-0.004}$
+& $ 0.007^{+ 0.004}_{-0.004}$
 \\
 ${\beta_X/\beta_{\hat{V}}-1}$
-& $  0.79^{+  0.29}_{ -0.19}$
-& $  0.16^{+  0.11}_{ -0.08}$
-&\dots
-& $ -0.12^{+  0.04}_{ -0.04}$
-& $ -0.58^{+  0.11}_{ -0.17}$
+& $  0.80^{+  0.29}_{ -0.19}$
+& $  0.17^{+  0.11}_{ -0.08}$
+& \dots
+& $ -0.13^{+  0.04}_{ -0.04}$
+& $ -0.59^{+  0.12}_{ -0.18}$
 \\
 $\eta_X$
-& $0.0022^{+0.0011}_{-0.0011}$
-& $0.0024^{+0.0009}_{-0.0010}$
-& $0.0027^{+0.0008}_{-0.0008}$
+& $0.0021^{+0.0011}_{-0.0012}$
+& $0.0023^{+0.0009}_{-0.0010}$
+& $0.0026^{+0.0008}_{-0.0008}$
 & $0.0025^{+0.0007}_{-0.0007}$
@@
 ${\eta_X/\eta_{\hat{V}}-1}$
-& $ -0.19^{+  0.17}_{ -0.28}$
-& $ -0.12^{+  0.09}_{ -0.15}$
-&\dots
-& $ -0.06^{+  0.06}_{ -0.04}$
-& $ -0.33^{+  0.10}_{ -0.10}$
+& $ -0.22^{+  0.19}_{ -0.33}$
+& $ -0.13^{+  0.10}_{ -0.17}$
+& \dots
+& $ -0.06^{+  0.07}_{ -0.05}$
+& $ -0.32^{+  0.10}_{ -0.11}$
 \\
@@
 & $ -0.06^{+  0.05}_{ -0.04}$
-& $ -0.09^{+  0.04}_{ -0.04}$
-& $ -0.12^{+  0.04}_{ -0.04}$
-& $ -0.09^{+  0.03}_{ -0.03}$
+& $ -0.08^{+  0.04}_{ -0.04}$
+& $ -0.11^{+  0.04}_{ -0.04}$
+& $ -0.09^{+  0.04}_{ -0.03}$
 & $ -0.14^{+  0.03}_{ -0.03}$
@@
 ${\zeta_X/\zeta_{\hat{V}}-1}$
-& $ -0.45^{+  0.20}_{ -0.33}$
-& $ -0.26^{+  0.11}_{ -0.18}$
-&\dots
+& $ -0.47^{+  0.20}_{ -0.35}$
+& $ -0.27^{+  0.11}_{ -0.19}$
+& \dots
 & $ -0.20^{+  0.05}_{ -0.07}$
-& $  0.22^{+  0.23}_{ -0.13}$
+& $  0.24^{+  0.25}_{ -0.14}$
 \\
 $\gamma^0_X$
-& $ 68.29^{+  2.97}_{ -2.92}$
-& $ 54.90^{+  2.49}_{ -2.56}$
-& $ 40.89^{+  2.38}_{ -2.47}$
-& $ 30.95^{+  2.13}_{ -2.25}$
-& $ 22.34^{+  2.05}_{ -2.16}$
+& $ 68.30^{+  2.98}_{ -2.99}$
+& $ 54.82^{+  2.57}_{ -2.64}$
+& $ 40.81^{+  2.45}_{ -2.56}$
+& $ 30.89^{+  2.19}_{ -2.28}$
+& $ 22.34^{+  2.11}_{ -2.17}$
 \\
 ${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
-& $  0.67^{+  0.05}_{ -0.05}$
+& $  0.68^{+  0.05}_{ -0.05}$
 & $  0.34^{+  0.03}_{ -0.03}$
-&\dots
+& \dots
 & $ -0.24^{+  0.01}_{ -0.01}$
@@
 $\gamma^1_X$
-& $-10.15^{+  4.45}_{ -4.49}$
-& $ -6.81^{+  3.88}_{ -3.82}$
-& $-15.06^{+  3.42}_{ -3.39}$
-& $-14.88^{+  3.01}_{ -3.00}$
-& $-15.91^{+  2.90}_{ -2.86}$
+& $ -9.92^{+  4.29}_{ -4.39}$
+& $ -6.59^{+  3.87}_{ -3.90}$
+& $-14.86^{+  3.51}_{ -3.43}$
+& $-14.70^{+  3.03}_{ -3.00}$
+& $-15.74^{+  2.82}_{ -2.80}$
 \\
 ${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
-& $ -0.32^{+  0.16}_{ -0.21}$
-& $ -0.55^{+  0.13}_{ -0.20}$
-&\dots
-& $ -0.01^{+  0.05}_{ -0.04}$
-& $  0.06^{+  0.14}_{ -0.10}$
+& $ -0.33^{+  0.16}_{ -0.21}$
+& $ -0.56^{+  0.14}_{ -0.21}$
+& \dots
+& $ -0.01^{+  0.06}_{ -0.04}$
+& $  0.06^{+  0.15}_{ -0.11}$
 \\
 $\sigma_p \phi_X$
-& $ 0.024^{+ 0.009}_{-0.009}$
-& $-0.018^{+ 0.007}_{-0.007}$
-& $-0.027^{+ 0.006}_{-0.006}$
-& $-0.010^{+ 0.006}_{-0.006}$
-& $ 0.022^{+ 0.006}_{-0.006}$
+& $ 0.020^{+ 0.014}_{-0.016}$
+& $-0.022^{+ 0.012}_{-0.013}$
+& $-0.031^{+ 0.010}_{-0.012}$
+& $-0.014^{+ 0.009}_{-0.010}$
+& $ 0.020^{+ 0.009}_{-0.010}$
 \\
 ${\phi_X/\phi_{\hat{V}}-1}$
-& $-1.898^{+ 0.420}_{-0.611}$
-& $-0.333^{+ 0.156}_{-0.181}$
-&\dots
-& $-0.609^{+ 0.109}_{-0.163}$
-& $-1.834^{+ 0.329}_{-0.486}$
+& $-1.658^{+ 0.559}_{-0.960}$
+& $-0.278^{+ 0.168}_{-0.245}$
+& \dots
+& $-0.555^{+ 0.123}_{-0.219}$
+& $-1.654^{+ 0.394}_{-0.701}$
 \\
@@
 \begin{array}{rr}
-39.7^{+2.4}_{-2.5} & 16.6^{+0.6}_{-0.6}  \\
--14.7^{+3.4}_{-3.4} & 3.7^{+1.0}_{-0.9}  
+39.7^{+2.4}_{-2.5} & 16.6^{+0.7}_{-0.6} \\
+-14.5^{+3.4}_{-3.4} & 3.7^{+1.0}_{-1.0}
 \end{array}
@@
 \begin{split}
-\vec{\epsilon}_{\gamma^0} &=\left(1.0^{+0.4}_{-0.4} , -1.2^{+0.4}_{-0.4} , -0.8^{+0.4}_{-0.4} , 0.7^{+0.2}_{-0.2} , 0.4^{+0.6}_{-0.6}\right), \\
-\vec{\epsilon}_{\gamma^1} & =\left(-2.7^{+0.6}_{-0.6} , 4.3^{+0.6}_{-0.6} , -0.8^{+0.6}_{-0.6} , 1.2^{+0.3}_{-0.3} , -2.6^{+0.9}_{-0.9}\right).
+\vec{\epsilon}_{\gamma^0} &=\left(1.1^{+0.4}_{-0.4} , -1.2^{+0.4}_{-0.4} , -0.8^{+0.4}_{-0.4} , 0.7^{+0.2}_{-0.2} , 0.4^{+0.6}_{-0.6}\right), \\
+\vec{\epsilon}_{\gamma^1} & =\left(-2.8^{+0.6}_{-0.6} , 4.3^{+0.6}_{-0.6} , -0.8^{+0.6}_{-0.6} , 1.2^{+0.3}_{-0.3} , -2.6^{+0.9}_{-0.9}\right).
 \end{split}
@@
 $0.959^{+0.015}_{-0.029}$.
-The   $\vec{\gamma}^0$  vector points in the $\langle R^F_{\mathit{eff}}\rangle=2.40^{+0.15}_{-0.15}$ dust-extinction direction.
+The   $\vec{\gamma}^0$  vector points in the $\langle R^F_{\mathit{eff}}\rangle=2.39^{+0.15}_{-0.16}$ dust-extinction direction.
 This value is consistent with the $R_V=2.5$ found in the supernova samples of \citet{2011ApJ...729...55F}, and the
@@
    See Figure~\ref{plane:fig}.
-   The combination $\vec{a}+\vec{b}/2.40$ is shown in the dotted red
+   The combination $\vec{a}+\vec{b}/2.39$ is shown in the dotted red
    line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
@@
 The  new intrinsic $p$ parameter has a significant influence on color.  The magnitude of its color effect is non-zero,
-with $\sigma_p = 0.049^{+ 0.004}_{-0.003}$~mag.  The smallest value of $\sigma_p$
-over all Monte Carlo chains is 0.039~mag.
+with $\sigma_p = 0.053^{+ 0.010}_{-0.005}$~mag.  The smallest value of $\sigma_p$ % new
+over all Monte Carlo chains is 0.040~mag.
 These numbers are significantly larger than the median data color uncertainty of 0.010~mag (the maximum is 0.042~mag).
@@
 the $\vec{\gamma}$ vectors (nor of the  \citetalias{1999PASP..111...63F} dust-extinction model); a quadratic fraction of
-$0.053^{+0.102}_{-0.040}$ of 
+$0.130^{+0.262}_{-0.104}$ of  %new
  $\vec{\phi}$ lies in the $\vec{\gamma}^0$--$\vec{\gamma}^1$ plane.
@@
 \begin{array}{rrrrrrrr}
-\Delta & -0.07^{+0.06}_{-0.06} & -0.11^{+0.08}_{-0.07} & -0.17^{+0.06}_{-0.06} & 0.19^{+0.08}_{-0.08} & 0.08^{+0.07}_{-0.06} & 0.23^{+0.08}_{-0.08} & -0.13^{+0.06}_{-0.06} \\
-\ldots  & EW_{Ca} & 0.09^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & 0.07^{+0.03}_{-0.03} & -0.11^{+0.05}_{-0.05} & -0.18^{+0.06}_{-0.06} & -0.00^{+0.08}_{-0.07} \\
-\ldots & \ldots &EW_{Si} & -0.12^{+0.03}_{-0.03} & -0.84^{+0.01}_{-0.01} & -0.13^{+0.04}_{-0.04} & 0.27^{+0.08}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
-\ldots  & \ldots  & \ldots  &  \lambda_{Si} & 0.14^{+0.03}_{-0.03} & 0.01^{+0.05}_{-0.05} & 0.00^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
-\ldots  &\ldots  &\ldots & \ldots & x_1 & 0.13^{+0.04}_{-0.04} & -0.20^{+0.09}_{-0.09} & 0.00^{+0.08}_{-0.08} \\
-\ldots  &\ldots  & \ldots  &\ldots  & \ldots  & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 0.04^{+0.06}_{-0.06} & -0.00^{+0.07}_{-0.08} \\
-\ldots  & \ldots &\ldots  & \ldots  & \ldots & \ldots  &E_{\gamma^1}({\hat{B}}-{\hat{V}})  & 0.00^{+0.07}_{-0.07} \\
+\Delta& -0.08^{+0.06}_{-0.06} & -0.11^{+0.08}_{-0.07} & -0.17^{+0.06}_{-0.06} & 0.19^{+0.08}_{-0.09} & 0.07^{+0.07}_{-0.06} & 0.23^{+0.08}_{-0.08} & 0.12^{+0.06}_{-0.06} \\
+\ldots  & EW_{Ca} & 0.10^{+0.03}_{-0.03} & -0.25^{+0.03}_{-0.03} & 0.07^{+0.03}_{-0.03} & -0.10^{+0.05}_{-0.05} & -0.18^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
+\ldots & \ldots &EW_{Si}  & -0.12^{+0.03}_{-0.03} & -0.84^{+0.01}_{-0.01} & -0.13^{+0.04}_{-0.04} & 0.27^{+0.08}_{-0.09} & -0.00^{+0.08}_{-0.07} \\
+\ldots  & \ldots  & \ldots  &  \lambda_{Si}& 0.14^{+0.03}_{-0.03} & 0.01^{+0.06}_{-0.05} & 0.00^{+0.06}_{-0.06} & -0.00^{+0.08}_{-0.08} \\
+\ldots  &\ldots  &\ldots & \ldots & x_1 & 0.13^{+0.04}_{-0.04} & -0.20^{+0.09}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
+\ldots  &\ldots  & \ldots  &\ldots  & \ldots  & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 0.04^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
+\ldots  & \ldots &\ldots  & \ldots  & \ldots & \ldots  &E_{\gamma^1}({\hat{B}}-{\hat{V}})  & -0.00^{+0.08}_{-0.08} \\
 \ldots  & \ldots & \ldots & \ldots  & \ldots  & \ldots  &\ldots  & A_{p,V} \\
@@
 The vector
-$\vec{\gamma}^0$ describes color changes for an effective $\langle R^F_{\mathit{eff}}\rangle=2.40$ dust, as shown 
+$\vec{\gamma}^0$ describes color changes for an effective $\langle R^F_{\mathit{eff}}\rangle=2.39$ dust, as shown 
 in  \S\ref{results3gamma:sec}.
 Hence, the per-supernova parameter $\gamma^0_{\hat{V}} g_0$ is associated with the $\hat{V}$-band
-extinction for a constant $R^F=2.40$.}
+extinction for a constant $R^F=2.39$.}
 Figure~\ref{k0_med:fig} shows the histogram of
@@
       of  per-supernova 
-median values of: (left) $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$, which is associated with the $A^F_V$ of an $\langle R^F_{\mathit{eff}}\rangle \sim 2.4$ dust model;
+median values of: (left) $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$, which is associated with the $A^F_V$ of an $\langle R^F_{\mathit{eff}}\rangle \sim 2.39$ dust model;
 (right) $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$,
@@
 sample is shown in Figure~\ref{kk:fig}. 
-For reference, a line that represents $\langle R^F_{\mathit{eff}}\rangle=2.4$ is overplotted; points above
+For reference, a line that represents $\langle R^F_{\mathit{eff}}\rangle=2.39$ is overplotted; points above
 the line have larger $R^F$, points below have smaller $R^F$.  The majority of supernovae lie within a narrow range above the line,
@@
       Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $g_0$ and $g_1$ parameters, for the supernova in our sample.
-      Overplotted is a line with the slope expected for $R^F=2.4$.
+      Overplotted is a line with the slope expected for $R^F=2.39$.
    \label{kk:fig}}
@@
 %-----
-0.085
-and 0.011
+0.085 %new
+and 0.010
 %-----
@@
 with wavelength.  For example, we find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
-to be $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -1.9^{+1.0}_{-2.4}$, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.  
+to be $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -2.4_{  -4.1}^{+   1.6}$, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.  
 However a change of the color baseline gives a significantly different
-$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =2.2^{+2.1}_{-0.9}$.  Our results indicate that  $\beta_{\mathit{int}}$
+$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =2.4_{  -1.2}^{+   2.1}$.  Our results indicate that  $\beta_{\mathit{int}}$ %new
 is sensitive to the color that $c$ corresponds to.  Although SALT2 $c$ is calibrated to correspond with $B-V$, it is
@@
 Low- and high-mass galaxies, divided by $\log{(M/M_\sun)}=10$, have high probability of hosting supernovae with different $p$ distributions, as
-the Kolmogorov-Smirnov test gives a two-tailed $p$-value of $ 0.02 _ {   -0.02 } ^{   + 0.04 }$.
+the Kolmogorov-Smirnov test gives a two-tailed $p$-value of $  0.016 _ {     0.011 } ^{     0.044 }$. %fix
 The median and median uncertainties of the two subsamples are
 %---
-$\langle \sigma_p\phi_{\hat{V}}(p-p|_0) \rangle=  0.023 \pm {     0.004}$ mag,
-$\langle \sigma_p\phi_{\hat{V}}(p-p|_0)  \rangle=0.036 \pm {     0.004 }$ mag
-for low- and high-mass hosts respectively, with a difference of $0.013 \pm {     0.005 }$~mag that is significant at $>2 \sigma$.
+$\langle \sigma_p\phi_{\hat{V}}(p-p|_0) \rangle=  0.024 \pm {     0.005 }$ mag, %new
+$\langle \sigma_p\phi_{\hat{V}}(p-p|_0)  \rangle=0.038 \pm {     0.005 }$ mag
+for low- and high-mass hosts respectively, with a difference of $ 0.015 \pm {     0.006 }$~mag that is significant at $>2 \sigma$.
 
@@
 with an effective
-$\langle R^F_{\mathit{eff}}\rangle \sim 2.40$ and an asymmetric tail extending toward lower values.
+$\langle R^F_{\mathit{eff}}\rangle \sim 2.39$ and an asymmetric tail extending toward lower values.
 We identify a new

### 2018-01-30 submit/fix.tex
Hinton reference
extrinsic intrinsic purge

@@
 
-\title{Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory}
+\title{Evidence for a Third Color  Parameter Within the Type~Ia Supernovae of the Nearby Supernova Factory}
 \author[0000-0001-6315-8743]{A.~G.~Kim}
@@
 an empirical model for SN~Ia peak colors with
-\added{three color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
+three color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
 and the light-curve shape.
@@
 The third parameter has  unique color characteristics that distinguish it from 
-those already  tracked by the spectral features, light-curve shape, and two-parameter dust models.}
+those already  tracked by the spectral features, light-curve shape, and two-parameter dust models.
 \end{abstract}
@@
 
-\added{
 Even two parameters are probably not enough to capture supernova color diversity.  SNe~Ia 
@@
 2008ApJ...686L.103G} produce color variations beyond those due to interstellar dust.  A third color
-parameter is therefore expected.}
+parameter is therefore expected.
 
@@
 variation is consistent with Milky Way dust models.
-We accommodate up to  three independent color parameters: the model is constructed such that 
+We accommodate up to  three independent color parameters
+\deleted{
+: the model is constructed such that 
 two are assigned as extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
-properties.
+properties.}
 The data used in this analysis are described in \S\ref{data:sec}.
-\added{
 The analysis itself is presented as a series of three models of increasing complexity.
@@
 For Model~II described in \S\ref{modelII:sec}, we add a third latent color parameter to the analysis.
-In \S\ref{modelIII:sec} we present our final Model~III, which  includes light-curve shape as an additional standardization parameter.}
+In \S\ref{modelIII:sec} we present our final Model~III, which  includes light-curve shape as an additional standardization parameter.
 Conclusions are presented in \S\ref{conclusions:sec}.
@@
 The 
-spectroscopic-feature measurements, \added{SALT2 light-curve shape parameters  $x_1$,}
+spectroscopic-feature measurements, SALT2 light-curve shape parameters  $x_1$,
 and their uncertainties
@@
 
-\section{Model~I: Extrinsic Colors}
+\section{Model~I: Two Color Parameters}
 \label{modelI:sec}
-\added{
 We begin by considering Model~I, in which supernova magnitudes  have linear dependence on spectral parameters
-and two extrinsic color parameters. The purpose of this section is to introduce some basic concepts of our models,
+and two \deleted{extrinsic} color parameters. The purpose of this section is to introduce some basic concepts of our models,
 to show how the two  color terms can be associated with existing dust-extinction models, and to give Model~I results on dust extinction. 
 To avoid repetitiveness,
-we refrain from going into full detail on the results of Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}.}
+we refrain from going into full detail on the results of Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}.
 
@@
 We assume 
-that  peak intrinsic ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
+that  peak
+\replaced{
+intrinsic}
+{underlying}
+ ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
 on its
@@
 \citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
+\added{
+The underlying magnitudes are also linearly dependent on the per-supernova parameters $g_0$ and $g_1$.
+Unlike
+the spectral parameters ($EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$),  the latent
+parameters $g_0$ and $g_1$ are not directly associated
+with observables but rather are inferred as part of the analysis.
+}
 A grey magnitude offset, $\Delta$, is included for each supernova
@@
 fluxes to luminosities.
-\added{With this grey offset the model standardizes colors, not absolute magnitude.
-The intrinsic  magnitudes are
+With this grey offset the model standardizes colors, not absolute magnitude.
+The \added{
+underlying magnitudes are
 \begin{equation}
@@
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} \\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  \\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} \\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} \\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si}  +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 \\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si}  +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 \\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}  +\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1
 \end{pmatrix},
@@
 \end{equation}
+}
 where $\vec{I}$ is the Identity vector.
@@
 notationally identify global parameters, in contrast with the per-supernova parameters.
-}} that describe the SN~Ia population
+} that describe the SN~Ia population
+\replaced{
 $\vec{c}$, 
-$\vec{\alpha}$, $\vec{\beta}$,  and $\vec{\eta}$,  are the intercept
-(units of mag) and slopes (units of mag~\AA$^{-1}$)
+$\vec{\alpha}$, $\vec{\beta}$,
+and $\vec{\eta}$,}
+{
+$\vec{c}$  (units of mag);
+$\vec{\alpha}$, $\vec{\beta}$,
+$\vec{\eta}$ (units of mag~\AA$^{-1}$), $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (unitless)}
+ are the intercept
+and slopes
 of the linear relationships that
-relate spectral-feature parameters with intrinsic magnitudes.
-
-The apparent magnitudes are the sum of the intrinsic magnitudes plus additional terms that are linearly dependent on the
-per-supernova
-extrinsic-color parameters $g_0$ and $g_1$.  
-Unlike the parameters associated with
-the spectral measurements ($EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$)  the latent,
-dimensionless
-parameters $g_0$ and $g_1$ are not directly associated
-with observables but rather are inferred as part of the analysis.
-The global parameter vectors $\vec{\gamma}^0$, $\vec{\gamma}^1$  are the slopes (units of mag) that relate 
-the latent extrinsic-color parameters with apparent magnitudes.
+relate
+\replaced{
+spectral-feature}
+{per-supernova}
+parameters with \replaced{
+intrinsic}
+{underlying} magnitudes.
+
 The observables
@@
 corresponds to the probability distribution function described by
+\added{
 \begin{equation}
@@
 \begin{pmatrix}
-{\hat{U}} +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
-{\hat{V}}+\gamma^0_{{\hat{V}}} g_0+\gamma^1_{{\hat{V}}} g_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} g_0 + \gamma^1_{{\hat{R}}} g_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} g_0+\gamma^1_{{\hat{I}}} g_1\\
+{\hat{U}}  \\{\hat{B}}  \\
+{\hat{V}}\\{\hat{R}}\\{\hat{I}}\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
@@
 \end{equation}
+}
 
 The model as written has degeneracies that need to be constrained in order for fits to converge.
-The model does not specify the absolute magnitude nor the intrinsic color of a supernova that has no extrinsic color contribution;
+The model does not specify the absolute magnitude nor the 
+\replaced{
+intrinsic color of a supernova that has no extrinsic color contribution;}
+{color of a $g_0=0$, $g_1=0$ supernova;}
 in their place the zeropoints of the per-supernova magnitude and color parameters are set to the sample means
@@
 
-\added{All parameters not  otherwise noted above have flat priors.
+All parameters not  otherwise noted above have flat priors.
 
@@
 
-\subsection{Results for the Extrinsic Latent Parameter Cofactors  $\vec{\gamma}^0$ and $\vec{\gamma}^1$:  }
+\subsection{Results for the Latent Parameter Cofactors  $\vec{\gamma}^0$ and $\vec{\gamma}^1$  }
 \label{results1:sec}
@@
 Since dust extinction is a dominant determinant of supernova colors that is often described by a 2-parameter linear model, we expect
-for our two extrinsic color terms to capture the effects of dust.
+for our two \deleted{extrinsic} color terms to capture the effects of dust.
 We  thus interpret our model $\vec{\gamma}$'s in terms of
@@
 All elements of the two $\vec{\gamma}$ parameter vectors 
-describing intrinsic color
+describing \deleted{intrinsic} color
 are significantly non-zero.
@@
 \end{equation}
-}
+
 For example,   the wavelength-dependent model of  \citet{1989ApJ...345..245C} is linear,
@@
  the largest error in extinction from the linear approximation having amplitude $<0.008$ mag.
-\added{
 All possible magnitude changes in our five bands due to  \citetalias{1999PASP..111...63F}  dust extinction are confined to a two-dimensional
@@
 a quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ and
-$0.959^{+0.013}_{-0.024}$ of $\vec{\gamma}^1$ project onto the $\vec{a}$--$\vec{b}$ plane.}
+$0.959^{+0.013}_{-0.024}$ of $\vec{\gamma}^1$ project onto the $\vec{a}$--$\vec{b}$ plane.
 The allowed color
@@
 the plane defined by the $\vec{\gamma}$ vectors. 
-\added{While
+While
 Eq.~\ref{f99:eqn} expresses that model using basis vectors $\vec{a}$ and $\vec{b}$ and
@@
 In our analysis, the $\vec{\gamma}$ vectors converge to a specific direction, meaning that our result prefers specific values of
-$\kappa_1=M[1,2]/M[1,1]$ and $\kappa_2=M[2,1]/M[2,2]$, where $M$ is the matrix in  Eq.~\ref{trans_I:eqn}.}
+$\kappa_1=M[1,2]/M[1,1]$ and $\kappa_2=M[2,1]/M[2,2]$, where $M$ is the matrix in  Eq.~\ref{trans_I:eqn}.
 
@@
 effective total-to-selective extinction of our sample.
-\added{
 The posterior yields $\langle R^F_{\mathit{eff}}\rangle =2.18^{+0.14}_{-0.16}$.
@@
 That we recover a physically-motivated  result lends confidence in the modeling and analysis.
-\item In Model~I, any  intrinsic color variation that remains after spectral corrections is allocated to two parameters.  Color variations beyond
+\item In Model~I, any  \deleted{intrinsic} color variation that remains after spectral corrections is allocated to two parameters.
+\replaced{ Color variations beyond
 those from two-parameter dust extinction contribute to those two parameters.  The derived effective dust-parameter $R^F$ 
 is susceptible to leakage from intrinsic colors unassociated with dust.
-\end{itemize}
-
-\section{Model~II: Extrinsic and Intrinsic Colors}
+}
+{Dust extinction is not the only effect that can contribute to $g_0$ and $g_1$.}  \end{itemize}
+
+\section{Model~II: Three Color Parameters}
 \label{modelII:sec}
-Model~II extends Model~I to include a third intrinsic-color parameter.  This increase in the number of degrees of freedom accommodates
+Model~II extends Model~I to include a third \deleted{intrinsic-}color parameter.  This increase in the number of degrees of freedom 
+\replaced{accommodates
 one parameter for the optical depth of dust, one parameter to capture variation in dust properties, and
-another parameter for  color variability unrelated to dust.  In this section we  focus on describing the consequences of the addition of the
+another parameter for  color variability unrelated to dust.}
+{goes beyond the two of dust-extinction models used in supernova analysis.}
+ In this section we  focus on describing the consequences of the addition of the
 new parameter.
@@
 Model~II is identical to Model~I except for the 
-addition of an intrinsic color parameter $p$.  The distribution of $p$ in our sample
+addition of a \replaced{n intrinsic}{third} color parameter $p$.  The distribution of $p$ in our sample
 is assumed to form a Normal distribution with unit standard deviation.  An unconstrained distribution,
@@
 \end{equation}
+\added{
 \begin{equation}
@@
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} + \sigma_p\phi_{\hat{U}} p\\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  + \sigma_p\phi_{\hat{B}} p\\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} + \sigma_p\phi_{\hat{V}}  p\\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} + \sigma_p\phi_{\hat{R}} p\\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+ \sigma_p\phi_{\hat{I}}  p
-\end{pmatrix},
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si}+\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1  + \sigma_p\phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1  + \sigma_p\phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 + \sigma_p\phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 + \sigma_p\phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1 + \sigma_p\phi_{\hat{I}}  p
+\end{pmatrix}
 \label{ewsiv2:eqn}
 \end{equation}
-\begin{equation}
-\begin{pmatrix}
-{\hat{U}}_o\\{\hat{B}}_o\\ {\hat{V}}_o\\{\hat{R}}_o\\{\hat{I}}_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
-\end{pmatrix}
-\sim \mathcal{N}
-\left(
-\begin{pmatrix}
-{\hat{U}} +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
-{\hat{V}}+\gamma^0_{{\hat{V}}} g_0+\gamma^1_{{\hat{V}}} g_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} g_0 + \gamma^1_{{\hat{R}}} g_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} g_0+\gamma^1_{{\hat{I}}} g_1\\
-EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
-\end{pmatrix}
-,C
-\right).
-\label{dust2:eqn}
-\end{equation}
-
+}
+
+\deleted{
 The new term is placed in Eq.~\ref{ewsiv2:eqn} as an intrinsic supernova property.  It is mathematically equivalent to
@@
 their physical origins.
+}
 
@@
 
-\subsection{Results for the Intrinsic Latent Parameter Cofactor $\sigma_p \vec{\phi}$}
+\subsection{Results for the Latent Parameter Cofactor $\sigma_p \vec{\phi}$}
 \label{results2:sec}
@@
 
-\section{Model~III: Extrinsic and Intrinsic Colors and Light-Curve Shape}
+\section{Model~III: Three Color Parameters and Light-Curve Shape}
 \label{modelIII:sec}
@@
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} +\zeta_{\hat{U}} x_1 + \sigma_p\phi_{\hat{U}} p\\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\zeta_{\hat{B}} x_1 + \sigma_p\phi_{\hat{B}} p\\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\zeta_{\hat{V}} x_1+ \sigma_p\phi_{\hat{V}}  p\\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\zeta_{\hat{R}} x_1+ \sigma_p\phi_{\hat{R}} p\\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\zeta_{\hat{I}} x_1+ \sigma_p\phi_{\hat{I}}  p
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} +\zeta_{\hat{U}} x_1 +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 + \sigma_p\phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\zeta_{\hat{B}} x_1 +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 + \sigma_p\phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\zeta_{\hat{V}} x_1+\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 + \sigma_p\phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\zeta_{\hat{R}} x_1+\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 + \sigma_p\phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\zeta_{\hat{I}} x_1+\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1 + \sigma_p\phi_{\hat{I}}  p
 \end{pmatrix},
@@
 \end{equation}
+
 \begin{equation}
@@
 \begin{pmatrix}
-{\hat{U}} +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\{\hat{B}} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
-{\hat{V}}+\gamma^0_{{\hat{V}}} g_0+\gamma^1_{{\hat{V}}} g_1\\{\hat{R}}+\gamma^0_{{\hat{R}}} g_0 + \gamma^1_{{\hat{R}}} g_1\\{\hat{I}}+\gamma^0_{{\hat{I}}} g_0+\gamma^1_{{\hat{I}}} g_1\\
+{\hat{U}}  \\{\hat{B}}  \\
+{\hat{V}}\\{\hat{R}}\\{\hat{I}}\\
 EW_{Si}\\ EW_{Ca} \\ \lambda_{Si} \\ x_1
@@
 \end{equation}
+}
 The changes from Model~II are the addition of the $\vec{\zeta} x_1$ terms in Eq.~\ref{ewsiv3:eqn}, and
@@
 For $N=172$ supernovae, this makes 1548 observables and 1413  parameters.
-}
 
@@
 
-\added{
-
 Our analysis pipeline is run with input simulated data with known  signals and measurement uncertainties similar to those of our dataset.
@@
 This is as expected based on the results of \citet{2007A&A...466...11G, 2007ApJ...659..122J}.
-}
 
@@
 
-\added{
 The posterior visualized in
@@
 
-\subsubsection{Results for the Extrinsic Latent Parameter Cofactors $\vec{\gamma}^0$, $\vec{\gamma}^1$}
+\subsubsection{Results for the Latent Parameter Cofactors $\vec{\gamma}^0$, $\vec{\gamma}^1$}
 \label{results3gamma:sec}
 As with Model~I in \S\ref{modelI:sec}, all elements of the two $\vec{\gamma}$ parameter vectors 
-describing extrinsic color
+\deleted{describing extrinsic color}
 are significantly non-zero with 
@@
 center  of the range of per-supernova $R^F$ values found in the samples of \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}.
-Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are attributed to dust extinction.
-This association is further discussed when $g_0$ and $g_1$ are considered in \S\ref{g0g1:sec}.
+\deleted{Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are attributed to dust extinction.
+This association is further discussed when $g_0$ and $g_1$ are considered in \S\ref{g0g1:sec}.}
 
@@
 
-\subsubsection{Results for the Intrinsic Latent Parameter Cofactor $\sigma_p \vec{\phi}$}
-
-The  new intrinsic $p$ parameter has a significant influence on color.  The magnitude of its color effect is non-zero,
+\subsubsection{Results for the Latent Parameter Cofactor $\sigma_p \vec{\phi}$}
+
+The  new \deleted{intrinsic} $p$ parameter has a significant influence on color.  The magnitude of its color effect is non-zero,
 with $\sigma_p = 0.053^{+ 0.010}_{-0.005}$~mag.  The smallest value of $\sigma_p$ % new
@@
 The values of $\vec{\phi}$ does not change  monotonically with wavelength, as is apparent  in 
-the combination $\phi_X/\phi_{\hat{V}}-1$ shown in Figure~\ref{phiratio:fig}.  They have the property that
-a reddening $\hat{B}-\hat{V}$ is accompanied with a bluing in $\hat{V}-\hat{R}$.  The reddening and bluing are
-further accentuated 
-in the extreme $\hat{U}$ and $\hat{I}$ bands. The absorption and re-emission of light
-over broad bands is the obvious candidate for producing this behavior, a process
-already associated with SNe~Ia.
-\citet{2006ApJ...649..939K} points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
-from doubly and singly ionized states, making the gas fluorescent and efficient in redistributing energy from the UV/blue to redder
-wavelengths.  Qualitatively this would result in the structure for $\phi_X/\phi_V-1$ that we measure.
-We speculate that varying $^{56}$Ni mass affects the rise-time to peak $B$ brightness and hence the optical depth
-of the reionization front with respect to the core of the ejecta at peak, yielding the wavelength-dependent color behavior
-detected in this analysis.
+the combination $\phi_X/\phi_{\hat{V}}-1$ shown in Figure~\ref{phiratio:fig}.  An object that has fainter  $\hat{U}$$\hat{I}$-band peak magnitudes
+has brighter  $\hat{B}$$\hat{V}$$\hat{R}$  peaks.  That brightening is non-uniform, in that
+the reddening of $\hat{U}-\hat{B}$ and $\hat{B}-\hat{V}$ is accompanied
+by a bluing in $\hat{V}-\hat{R}$ and  $\hat{R}-\hat{I}$.
+
+\deleted{We emphasize that
+although the $\sigma_p \vec{\phi}p$ colors have ben referred to as ``intrinsic'' due to their placement in the model, the analysis cannot quantitatively distinguish
+whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.}
+What is measured as $\sigma_p \vec{\phi}$ likely captures the effect of many physical processes.
+To simplify the model it is assumed that the $p$'s are drawn from a Normal distribution, which may not be a fair description of what occurs in nature
+\added{and result in model bias}.
+The physical interpretation of this \deleted{intrinsic} color should be tempered with caution.
+
+%The redistribution of UV  photons into redder photons
+%is already associated with SNe~Ia around 35 days after maximum, when flourescence from singly-ionized iron/cobalt gas in the
+%ejecta gives rise to the NIR secondary light-curve peak
+%\citep{2006ApJ...649..939K}.   We speculate that our $\sigma_p \vec{\phi}$
+%is associated with a redistribution of UV light, but at peak brightness when the NIR emission is dominated by
+%the optically thick core and is not  significantly enhanced by fluorescence.
+
+% points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
+%from doubly and singly ionized states, making the gas fluorescent and efficient in redistributing energy from the UV/blue to redder
+%wavelengths.
+%We speculate that varying $^{56}$Ni mixing and/or mass affects the rise-time to peak $B$ brightness and hence the optical depth
+%of the reionization front with respect to the core of the ejecta at peak, yielding the wavelength-dependent color behavior
+%detected in this analysis.
 
@@
 \end{figure}
-
-We emphasize that
-although the $\sigma_p \vec{\phi}p$ colors have ben referred to as ``intrinsic'' due to their placement in the model, the analysis cannot quantitatively distinguish
-whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.
-What is measured as $\sigma_p \vec{\phi}$ likely captures the effect of many physical processes.
-To simplify the model it is assumed that the $p$'s are drawn from a Normal distribution, which may not be a fair description of what occurs in nature.
-The physical interpretation of this intrinsic color should be tempered with caution.
 
@@
 
-\subsubsection{Results for the Latent Extrinsic Parameters $g_0$, $g_1$}
+\subsubsection{Results for the Latent  Parameters $g_0$, $g_1$}
 \label{g0g1:sec}
@@
 Hence, the per-supernova parameter $\gamma^0_{\hat{V}} g_0$ is associated with the $\hat{V}$-band
-extinction for a constant $R^F=2.39$.}
+extinction for a constant $R^F=2.39$.
 Figure~\ref{k0_med:fig} shows the histogram of
@@
 
-\added{
 An instructive way to consider the  $\{g_0, g_1\}$ parameters is
@@
 
-There are $>2 \sigma$ correlations between our extrinsic color-excess parameters $g_0$, $g_1$
+There are $>2 \sigma$ correlations between our  color-excess parameters $g_0$, $g_1$
 and the input features  $EW_{Ca}$,
@@
 
-\subsubsection{Results for the Intrinsic Parameter $p$}
+\subsubsection{Results for the Parameter $p$}
 \label{p:sec}
@@
 Also shown for comparison is the distribution of
-the extrinsic  color-excess $E_\gamma({\hat{B}}-{\hat{V}}) \equiv (\gamma^0_{\hat{B}} -\gamma^0_{\hat{V}}) g_0
+the   color-excess $E_\gamma({\hat{B}}-{\hat{V}}) \equiv (\gamma^0_{\hat{B}} -\gamma^0_{\hat{V}}) g_0
 + (\gamma^1_{\hat{B}} -\gamma^1_{\hat{V}}) g_1$.
@@
 In $\hat{B}-\hat{V}$, 
-the extrinsic color variation is much larger than that of the intrinsic and its effect per-supernova would be difficult to discern.
+the \replaced{extrinsic}{$g$-based} color variation is much larger than that of the \replaced{intrinsic}{$p$-based} and its effect per-supernova would be difficult to discern.
 
@@
  %  \includegraphics[width=2.8in]{../output_fix3_x1/ebv_delta.pdf}
-      \caption{Stack of the posteriors of all supernovae of the external $E_{\gamma}({\hat{B}}-{\hat{V}})$ 
+      \caption{Stack of the posteriors of all supernovae of the  $E_{\gamma}({\hat{B}}-{\hat{V}})$ 
       and the 
-   internal $E_p({\hat{B}}-{\hat{V}})$  contributions to color excess relative to an arbitrary supernova.
+ $E_p({\hat{B}}-{\hat{V}})$  contributions to color excess relative to an arbitrary supernova.
    \label{ebv3:fig}}
@@
 
-There is no significant correlation between the  intrinsic parameter $p$ and the other features.
-Their independence from the  extrinsic parameters $g_0$ and $g_1$
+There is no significant correlation between the parameter $p$ and the other features.
+Their independence from the  $g_0$ and $g_1$ parameters
 implies that two physical parameters are not being artificially attributed to three
@@
 They find a significant $\beta_{\mathit{int}} = 2.2\pm 0.3$.
-While we also claim a detection of an intrinsic color parameter, the differences between our models make it
+\replaced{
+While we also claim a detection of an intrinsic color parameter, }
+{While we claim the detection of a color parameter incompatible with dust,}
+the differences between our models make it
 difficult to determine whether the results are consistent.   Our results show effects on color that are not monotonic
@@
 The $c$ parameter is thus an  amalgamation of all input colors.
-We therefore make no conclusions on the consistency between our intrinsic-color properties
+We therefore make no conclusions on the consistency between our \replaced{intrinsic}{$\vec{\phi}$}-color properties
 and those found by \citetalias{2017ApJ...842...93M}.
@@
 
-It is possible that the intrinsic $p$ parameter is a supernova-tracer of a population that to date has only been identified through host-galaxy tracers.
-We plot in Figure~\ref{childress3:fig} our intrinsic parameter
+It is possible that the  $p$ parameter is a supernova-tracer of a population that to date has only been identified through host-galaxy tracers.
+We plot in Figure~\ref{childress3:fig} our parameter
  $\sigma_p\phi_{\hat{I}}(p-p|_0) $  (subtracting out a random supernova
@@
    \includegraphics[width=4in]{../output_fix3_x1/childress.pdf} 
-   \caption{Intrinsic parameter $\sigma_p\phi_{\hat{V}}p$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
+   \caption{Parameter $\sigma_p\phi_{\hat{V}}p$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
       less than and greater than  $\log{(M/M_\sun)}=10$.
@@
 
-Using different arguments based on expected populations, \citetalias{2017ApJ...842...93M} also infer
+Using different arguments based on expected populations, \citetalias{2017ApJ...842...93M} \deleted{also} infer
 separate intrinsic and dust-based color-magnitude relations based on an independent sample of 248 SNe~Ia
@@
 of those samples that are  consistent with our $\sigma_p \vec{\phi}$ would provide strong evidence 
-that we and  \citetalias{2017ApJ...842...93M}  are seeing the same intrinsic color and to confirm the
-observational signature of the intrinsic SN color relationship.
+that we and  \citetalias{2017ApJ...842...93M}  are seeing the same \replaced{intrinsic color  and to confirm the
+observational signature of the intrinsic SN color relationship.}{color effect.}
 
@@
 
-We speculate that the new parameter is related to the fluorescence in SN~Ia described by  \citep{2006ApJ...649..939K}.
-This downgrading of photons from blue to red is responsible for the secondary maximum in near-IR light curves.  There
-are variations
-in the properties of the secondary maximum \citep{1996AJ....112.2438H, 2005A&A...437..789N, 2010AJ....139..120F}.
-\citet{2016MNRAS.463.4311S} find that the date of the secondary $J$-band maximum is correlated with peak
-magnitude, although they do not find that it is independent of light-curve shape $x_1$.  We advocate
-the continued study of
-NIR light-curve shpae properties and their relation with colors, host properties, and  magnitudes.
-
-}
+%We speculate that the new parameter is related to the fluorescence in SN~Ia described by  \citep{2006ApJ...649..939K}.
+%This downgrading of photons from blue to red is responsible for the secondary maximum in near-IR light curves.  There
+%are variations
+%in the properties of the secondary maximum \citep{1996AJ....112.2438H, 2005A&A...437..789N, 2010AJ....139..120F}.
+%\citet{2016MNRAS.463.4311S} find that the date of the secondary $J$-band maximum is correlated with peak
+%magnitude, although they do not find that it is independent of light-curve shape $x_1$.  We advocate
+%the continued study of
+%NIR light-curve shpae properties and their relation with colors, host properties, and  magnitudes.
 
@@
 We thank the STAN team for providing the statistical tool without which this analysis would not have been possible,
-and Michael Betancourt specifically for his helpful guidance.  We thank Danny Goldstein and
+and Michael Betancourt specifically for his helpful guidance.  
+Distribution surfaces are plotted using the ChainConsumer package \citep{Hinton2016}.
+We thank Danny Goldstein and
 Xiaosheng Huang for useful discussions.
@@
 \appendix
-\added{
 \section{Results from Model~I and II}
@@
 \end{tabular}
-\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~I in \S\ref{modelI:sec}.\label{global1:tab}}
+\caption{68\% credible intervals for the global fit parameters of the Two Color Parameter Model~I in \S\ref{modelI:sec}.\label{global1:tab}}
 \end{table}
@@
 \end{tabular}
-\caption{68\% credible intervals for the global fit parameters of the Extrinsic--Intrinsic Model~II in \S\ref{modelII:sec}.\label{global2:tab}}
+\caption{68\% credible intervals for the global fit parameters of the Three Color Parameter Model~II in \S\ref{modelII:sec}.\label{global2:tab}}
 \end{table}
-}
+
 \bibliographystyle{apj}

### 2018-02-01 submit/fix.tex
big changes to article

@@
 The color changes allowed by two of the color parameters are similar to those allowed by the extinction model of  \citet{1999PASP..111...63F}. 
-Correspondingly the sample has an effective value of $\langle R^F_{\mathit{eff}}\rangle \sim 2.39$, though with a broad distribution of 
+Correspondingly the sample has an effective value of $\langle R^F_{\mathit{eff}}\rangle \sim 2.43$, though with a broad distribution of 
 total-to-selective extinctions. 
@@
 those already  tracked by the spectral features, light-curve shape, and two-parameter dust models.
+\added{
+The existence of the third color parameter has implications on the accuracy of SN~Ia distance determinations.
+}
 \end{abstract}
@@
 \citet{2014ApJ...797...75M}.
-\citet{2015MNRAS.451.1973S}
+\citet{2009ApJ...699L.139W,2015MNRAS.451.1973S}
 find that high-velocity Si~II~$\lambda$6355 is found in objects that have red ultraviolet/optical colors near maximum brightness.
@@
 the canonical value for diffuse Milky Way dust.
-They also confirm the \citet{2011ApJ...731..120M, 2011ApJ...729...55F} finding that low $R_V$ is associated with high-extinction supernovae.
+They also confirm the \citet{2006MNRAS.369.1880E,, 2011ApJ...731..120M} finding that low $R_V$ is associated with high-extinction supernovae.
 In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
@@
 Hierarchical modeling has recently enabled
-the study of intrinsic supernova color based on SN~Ia Hubble diagrams. Latent parameters that are not directly tied to observables
+the study of intrinsic supernova color based on SN~Ia Hubble diagrams
+\added{by allowing the addition of a supernova population model as an extra level within in the larger model.
+}
+Latent parameters that are not directly tied to observables
 but  influence color can be included in such models.
@@
 The analysis itself is presented as a series of three models of increasing complexity.
-\S\ref{modelI:sec}  and  \S\ref{modelII:sec} present the first two models, providing a soft introduction to
+\S\ref{modelI:sec}  and  \S\ref{modelII:sec} present the first two models, providing an introduction to
 our methodology and yielding results to be compared with those from the third model.
@@
 moderate spectral resolution ($R \sim 500$).  It consists of a
-high-throughput wide-band lenslet integral field spectrograph, a mult-band
+high-throughput wide-band lenslet integral field spectrograph, a multi-band
 imager that covers the field in the vicinity of
@@
 to show how the two  color terms can be associated with existing dust-extinction models, and to give Model~I results on dust extinction.
+\added{
+Deficiencies in this model are addressed in the subsequent models presented in the article.
+}
 To avoid repetitiveness,
@@
 our physical interpretations are ultimately independent of this scaling.
-This prior does not specify the sign of $a$, which leaves a parity degeneracy.  As will be seen, the signal-to-noise in $\vec{\gamma}$ is sufficiently
+This prior does not specify the sign of $a$, which leaves a parity degeneracy. 
+\added{In the presentation of our results $\vec{\gamma}g$ is shown, never $g$ alone.
+}
+As will be seen, the signal-to-noise in $\vec{\gamma}$ is sufficiently
 high that our finite MCMC chains do not migrate between the degenerate solutions; to simplify the merging of multiple chains
@@
 
-Another form of degeneracy is illustrated by the  transformations $\Delta \rightarrow \Delta  + \epsilon_\Delta$,
- $\vec{\gamma}^0 \rightarrow \vec{\gamma}^0  + \epsilon_{\gamma^0}$, $\vec{\gamma}^1 \rightarrow \vec{\gamma}^1 + \epsilon_{\gamma^1}$
+\added{
+Each of the multiplicative cofactors has a degeneracy with the zeropoint.  Consider
+$\vec{\alpha} \rightarrow \vec{\alpha} +   \epsilon_{\alpha}$,
+$\vec{\beta} \rightarrow \vec{\beta} +   \epsilon_{\beta}$,
+$\vec{\eta} \rightarrow \vec{\eta} +   \epsilon_{\eta}$,
+$\vec{\gamma}^0 \rightarrow \vec{\gamma}^0 +   \epsilon_{\gamma^0}$,
+$\vec{\gamma}^1 \rightarrow \vec{\gamma}^1 +   \epsilon_{\gamma^1}$.
+Then
+each supernova's magnitude can shift as
+$\Delta \rightarrow \Delta  + \epsilon_\Delta$
 under the condition 
 $$
-\epsilon_\Delta  +  \epsilon_{\gamma^0} g_0+  \epsilon_{\gamma^1} g_1=0,
+\epsilon_\Delta  = -  \epsilon_{\alpha} (EW_{\text{Ca}}-\langle EW_{\text{Ca}}\rangle)- 
+ \epsilon_{\beta} (EW_{\text{Si}}-\langle EW_{\text{Si}}\rangle) -  \epsilon_{\eta} (\lambda_{\text{Si}}-\langle \lambda_{\text{Si}}\rangle)
+- \epsilon_{\gamma^0}g_0 -  \epsilon_{\gamma^1}g_1.
 $$
-i.e.\ shifts in the global coefficients $\vec{\gamma}$ can be compensated by shifts in 
-$\Delta$
-for each supernova while maintaining 
-$\langle \Delta \rangle=0$.
-Another degeneracy is illustrated by $g_0 \rightarrow g_0 + (EW_{Ca}-\langle EW_{Ca}\rangle)\epsilon$,
-$\vec{\alpha} \rightarrow \vec{\alpha} - \vec{\gamma} \epsilon$, $\vec{c} \rightarrow \vec{c} + \langle EW_{Ca}\rangle \epsilon$, i.e. the
-linear external terms can leak into the linear spectral feature corrections.
-These degeneracies are not broken within the model, but rather are constrained by the priors in which the
-per-supernova parameters
-$\Delta$, $EW$, $\lambda$, $g_0$, and $g_1$ are uncorrelated.
+We break this degeneracy by fixing the values of $\epsilon$ such that $\Delta$ is
+uncorrelated with  $EW_{\text{Ca}}$, $EW_{\text{Si}}$, $\lambda_{\text{Ca}}$,
+$g_0$, and $g_1$.
+Our preference is for feature affects to be confined to the cofactors and not the grey magnitude offsets.}
 
@@
 \label{results1:sec}
+\added{
+Recall that the purpose of this section is to introduce concepts rather than emphasize the specific results,
+which for this simple model is expected to have systematic biases.
+}
+
 In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
@@
 \end{equation}
-The $\vec{\gamma}$'s derived from our analysis are almost entirely captured by the first term;
-a quadratic fraction of $0.9993^{+0.0002}_{-0.0002}$ of $\vec{\gamma}^0$ and
-$0.959^{+0.013}_{-0.024}$ of $\vec{\gamma}^1$ project onto the $\vec{a}$--$\vec{b}$ plane.
+The $\vec{\gamma}$'s derived from our analysis are almost entirely captured by the first term.
+\added{
+The credible interval for $\vec{\gamma}$'s and other parameters are presented in Table~\ref{global1:tab}.
+We find
+\begin{equation}
+M=
+\begin{pmatrix}
+\begin{array}{rr}
+43.7^{+2.3}_{-2.1} & 19.4^{+0.5}_{-0.5} \\
+-18.7^{+3.0}_{-3.1} & -0.8^{+0.9}_{-1.0} \\
+\end{array}
+\end{pmatrix} 
+\end{equation}
+and
+\begin{align}
+\begin{split}
+\vec{\epsilon}_{\gamma^0} &=\left(1.5^{+0.3}_{-0.3} , -1.4^{+0.3}_{-0.3} , -1.8^{+0.4}_{-0.3} , 1.4^{+0.1}_{-0.1} , 0.5^{+0.4}_{-0.5} \right), \\
+\vec{\epsilon}_{\gamma^1} & =\left(4.8^{+0.3}_{-0.3} , -4.3^{+0.3}_{-0.3} , -5.7^{+0.4}_{-0.4} , 0.1^{+0.2}_{-0.2} , 6.8^{+0.5}_{-0.5}\right),
+\end{split}
+\label{res_1:eqn}
+\end{align}
+which correspond to
+a quadratic fraction of $0.9993^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ and
+$0.9303^{+0.0210}_{-0.0341}$ of $\vec{\gamma}^1$ project onto the $\vec{a}$--$\vec{b}$ plane.
+For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals from $\vec{\epsilon}$ are 
+$\left(0.025, 0.023,0.029, 0.008, 0.027\right)$.}
 The allowed color
@@
    The perspective on the right visually shows that all four vectors are nearly coplanar.  
-   The combination $\vec{a}+\vec{b}/2.18$ is shown in the dotted red
+   The combination $\vec{a}+\vec{b}/2.25$ is shown in the dotted red
    line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
@@
 effective total-to-selective extinction of our sample.
-The posterior yields $\langle R^F_{\mathit{eff}}\rangle =2.18^{+0.14}_{-0.16}$.
-Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.18$.
+The posterior yields $\langle R^F_{\mathit{eff}}\rangle =2.25^{+0.11}_{-0.10}$.
+Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.25$.
 
@@
 }
-{Dust extinction is not the only effect that can contribute to $g_0$ and $g_1$.}  \end{itemize}
+{Dust extinction is not the only effect that can contribute to $g_0$ and $g_1$ so interpreting
+them as pure dust parameters is subject to systematic errors.}  \end{itemize}
 
@@
 in $\vec{\phi}$ is apparent later in the article, but it does not affect the magnitude predictions. 
+\added{
+As in \S\ref{modelI:sec}, the degeneracy between $\vec{\phi}$ and $\Delta$ is fixed by enforcing zero correlation between $\Delta$ and $p$.
+}
 
@@
 not migrate between them.
+\replaced{
 The direction of $\vec{\phi}$ is not aligned with the plane defined by
@@
  $0.09^{+0.12}_{-0.06}$ of 
- $\vec{\phi}$ lies in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.
+ $\vec{\phi}$ lies in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.}
+ {
+ The new parameter does affect colors in a distinct manner from $g_0$ and $g_1$.
+A quadratic fraction of
+$0.48^{+0.25}_{-0.17}$ of 
+ $\vec{\phi}$ lies perpendicular to the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.
+ }
 
@@
 $\vec{a}$ and $\vec{b}$ of the \citetalias{1999PASP..111...63F} model.
-The direction of the  $\vec{\gamma}^0$ vector corresponds to an effective $\langle R^F_{\mathit{eff}}\rangle = 2.54^{+0.20}_{-0.20}$.
+The direction of the  $\vec{\gamma}^0$ vector corresponds to an effective
+\replaced{$\langle R^F_{\mathit{eff}}\rangle = 2.54^{+0.20}_{-0.20}$}
+{$\langle R^F_{\mathit{eff}}\rangle = 2.54^{+0.13}_{-0.12}$}.
 The change of $\langle R^F_{\mathit{eff}}\rangle$ from Model~I to II is anticipated by the change in the distribution of $g_1$,
@@
 the addition of the shape measurement and uncertainty (implicit in the covariance matrix $C$) and $x_1$   in Eq.~\ref{dust3:eqn}.
-
+\added{
+As in \S\ref{modelI:sec}, the degeneracy between $\vec{\phi}$ and $\Delta$ is fixed by enforcing zero correlation between $\Delta$ and $x_1$.
+}
 For $N$ supernovae there are $9N$ observables.  There are $4N$ spectral and light-curve shape parameters, each of
@@
 The model provides a fair representation of the data as seen in the residual differences between the data and the model prediction.
-Figure~\ref{residual:fig} shows plots of the observed  versus
-model-expectation colors (differences between band magnitudes in the mean of the Normal distribution of Eq.~\ref{dust3:eqn}) for four selected colors,
-and the histogram of the residuals.  The residuals have compact Gaussian-like appearance with
-no catastrophically poor color predictions.  There are no apparent trends between residuals and observed
-color.
+Figure~\ref{residual:fig} shows plots of 
+\added{residuals between measured and model-expectation colors as a function of observed $\hat{B}_o-\hat{V}_o$.
+This and similar plots for the other permutations of observed colors show  no apparent trend between residuals and observed
+color nor of extreme catastrophic outliers.
+}
 
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3_x1/residual.pdf} 
-            \caption{Observed  versus
-            Model~III-expectation colors (including  contributions related to spectral features, light-curve shape, $\vec{\gamma} g$, and $\vec{\phi} p$  terms)
-for four selected colors. 
-            Plotted on the right for each color
-is the histogram of the difference between the expected and
-observed
- colors. 
+%   \includegraphics[width=4in]{../output_fix3_x1/residual.pdf} 
+   \includegraphics[width=4in]{../output_fix3_x1/cpull.pdf} 
+               \caption{
+               \added{Residuals between measured and model-expectation colors as a function of observed $\hat{B}_o-\hat{V}_o$.  Plots that show
+               residual
+               colors containing $\hat{B}_o$ or $\hat{V}_o$ are shaded. to highlight that these residuals are highly correlated with the measurements. }
             \label{residual:fig}}
@@
 $\alpha_X$
-& $0.0059^{+0.0007}_{-0.0008}$
-& $0.0032^{+0.0006}_{-0.0007}$
-& $0.0029^{+0.0006}_{-0.0006}$
-& $0.0026^{+0.0005}_{-0.0005}$
-& $0.0041^{+0.0004}_{-0.0004}$
-\\
-${\alpha_X/\alpha_{\hat{V}}-1}$
-& $   1.0^{+   0.2}_{  -0.2}$
+& $0.0051^{+0.0007}_{-0.0008}$
+& $0.0025^{+0.0006}_{-0.0007}$
+& $0.0022^{+0.0005}_{-0.0005}$
+& $0.0019^{+0.0004}_{-0.0004}$
+& $0.0034^{+0.0003}_{-0.0004}$
+\\
+${\alpha_X}/\alpha_{\hat{V}}-1$
+& $   1.3^{+   0.4}_{  -0.2}$
 & $   0.1^{+   0.1}_{  -0.1}$
-& \dots
+& \ldots
 & $  -0.1^{+   0.0}_{  -0.0}$
-& $   0.4^{+   0.2}_{  -0.1}$
+& $   0.5^{+   0.3}_{  -0.2}$
 \\
 $\beta_X$
-& $ 0.032^{+ 0.006}_{-0.006}$
-& $ 0.021^{+ 0.005}_{-0.005}$
-& $ 0.018^{+ 0.005}_{-0.005}$
-& $ 0.016^{+ 0.004}_{-0.004}$
-& $ 0.007^{+ 0.004}_{-0.004}$
-\\
-${\beta_X/\beta_{\hat{V}}-1}$
-& $  0.80^{+  0.29}_{ -0.19}$
-& $  0.17^{+  0.11}_{ -0.08}$
-& \dots
-& $ -0.13^{+  0.04}_{ -0.04}$
-& $ -0.59^{+  0.12}_{ -0.18}$
+& $ 0.035^{+ 0.005}_{-0.005}$
+& $ 0.024^{+ 0.004}_{-0.004}$
+& $ 0.021^{+ 0.004}_{-0.004}$
+& $ 0.019^{+ 0.003}_{-0.003}$
+& $ 0.010^{+ 0.003}_{-0.003}$
+\\
+${\beta_X}/\beta_{\hat{V}}-1$
+& $  0.68^{+  0.16}_{ -0.13}$
+& $  0.14^{+  0.07}_{ -0.07}$
+&\ldots
+& $ -0.11^{+  0.03}_{ -0.02}$
+& $ -0.50^{+  0.06}_{ -0.07}$
 \\
 $\eta_X$
-& $0.0021^{+0.0011}_{-0.0012}$
-& $0.0023^{+0.0009}_{-0.0010}$
-& $0.0026^{+0.0008}_{-0.0008}$
-& $0.0025^{+0.0007}_{-0.0007}$
-& $0.0018^{+0.0006}_{-0.0006}$
-\\
-${\eta_X/\eta_{\hat{V}}-1}$
-& $ -0.22^{+  0.19}_{ -0.33}$
-& $ -0.13^{+  0.10}_{ -0.17}$
-& \dots
-& $ -0.06^{+  0.07}_{ -0.05}$
-& $ -0.32^{+  0.10}_{ -0.11}$
+& $0.0003^{+0.0011}_{-0.0011}$
+& $0.0005^{+0.0009}_{-0.0009}$
+& $0.0008^{+0.0007}_{-0.0007}$
+& $0.0007^{+0.0006}_{-0.0006}$
+& $-0.0000^{+0.0005}_{-0.0005}$
+\\
+${\eta_X}/\eta_{\hat{V}}-1$
+& $ -0.39^{+  0.64}_{ -1.36}$
+& $ -0.26^{+  0.35}_{ -0.77}$
+&\ldots
+& $ -0.19^{+  0.12}_{ -0.11}$
+& $ -0.86^{+  0.33}_{ -0.71}$
 \\
 $\zeta_X$
-& $ -0.06^{+  0.05}_{ -0.04}$
-& $ -0.08^{+  0.04}_{ -0.04}$
-& $ -0.11^{+  0.04}_{ -0.04}$
-& $ -0.09^{+  0.04}_{ -0.03}$
-& $ -0.14^{+  0.03}_{ -0.03}$
-\\
-${\zeta_X/\zeta_{\hat{V}}-1}$
-& $ -0.47^{+  0.20}_{ -0.35}$
-& $ -0.27^{+  0.11}_{ -0.19}$
-& \dots
-& $ -0.20^{+  0.05}_{ -0.07}$
-& $  0.24^{+  0.25}_{ -0.14}$
+& $ -0.00^{+  0.04}_{ -0.04}$
+& $ -0.02^{+  0.03}_{ -0.03}$
+& $ -0.05^{+  0.03}_{ -0.03}$
+& $ -0.03^{+  0.02}_{ -0.02}$
+& $ -0.08^{+  0.02}_{ -0.02}$
+\\
+${\zeta_X}/\zeta_{\hat{V}}-1$
+& $ -0.94^{+  0.48}_{ -1.15}$
+& $ -0.54^{+  0.28}_{ -0.65}$
+& \ldots
+& $ -0.42^{+  0.09}_{ -0.21}$
+& $  0.47^{+  0.83}_{ -0.32}$
 \\
 $\gamma^0_X$
-& $ 68.30^{+  2.98}_{ -2.99}$
-& $ 54.82^{+  2.57}_{ -2.64}$
-& $ 40.81^{+  2.45}_{ -2.56}$
-& $ 30.89^{+  2.19}_{ -2.28}$
-& $ 22.34^{+  2.11}_{ -2.17}$
-\\
-${\gamma^0_X/\gamma^0_{\hat{V}}-1}$
-& $  0.68^{+  0.05}_{ -0.05}$
-& $  0.34^{+  0.03}_{ -0.03}$
-& \dots
+& $ 68.91^{+  2.62}_{ -2.56}$
+& $ 55.44^{+  2.22}_{ -2.25}$
+& $ 41.41^{+  1.98}_{ -1.98}$
+& $ 31.49^{+  1.61}_{ -1.62}$
+& $ 22.92^{+  1.35}_{ -1.30}$
+\\
+${\gamma^0_X}/\gamma^0_{\hat{V}}-1$
+& $  0.67^{+  0.04}_{ -0.04}$
+& $  0.34^{+  0.02}_{ -0.02}$
+&\ldots
 & $ -0.24^{+  0.01}_{ -0.01}$
-& $ -0.45^{+  0.03}_{ -0.03}$
+& $ -0.45^{+  0.02}_{ -0.02}$
 \\
 $\gamma^1_X$
-& $ -9.92^{+  4.29}_{ -4.39}$
-& $ -6.59^{+  3.87}_{ -3.90}$
-& $-14.86^{+  3.51}_{ -3.43}$
-& $-14.70^{+  3.03}_{ -3.00}$
-& $-15.74^{+  2.82}_{ -2.80}$
-\\
-${\gamma^1_X/\gamma^1_{\hat{V}}-1}$
-& $ -0.33^{+  0.16}_{ -0.21}$
-& $ -0.56^{+  0.14}_{ -0.21}$
-& \dots
-& $ -0.01^{+  0.06}_{ -0.04}$
-& $  0.06^{+  0.15}_{ -0.11}$
+& $ -1.85^{+  4.11}_{ -4.05}$
+& $  1.47^{+  3.74}_{ -3.58}$
+& $ -6.75^{+  3.21}_{ -3.15}$
+& $ -6.60^{+  2.71}_{ -2.65}$
+& $ -7.65^{+  2.33}_{ -2.24}$
+\\
+${\gamma^1_X}/\gamma^1_{\hat{V}}-1$
+& $ -0.70^{+  0.38}_{ -0.76}$
+& $ -1.18^{+  0.43}_{ -1.08}$
+& \ldots
+& $ -0.03^{+  0.14}_{ -0.08}$
+& $  0.12^{+  0.45}_{ -0.22}$
 \\
 $\sigma_p \phi_X$
-& $ 0.020^{+ 0.014}_{-0.016}$
-& $-0.022^{+ 0.012}_{-0.013}$
-& $-0.031^{+ 0.010}_{-0.012}$
-& $-0.014^{+ 0.009}_{-0.010}$
-& $ 0.020^{+ 0.009}_{-0.010}$
+& $ 0.002^{+ 0.016}_{-0.017}$
+& $-0.041^{+ 0.013}_{-0.014}$
+& $-0.050^{+ 0.011}_{-0.012}$
+& $-0.032^{+ 0.009}_{-0.010}$
+& $ 0.002^{+ 0.008}_{-0.008}$
 \\
 ${\phi_X/\phi_{\hat{V}}-1}$
-& $-1.658^{+ 0.559}_{-0.960}$
-& $-0.278^{+ 0.168}_{-0.245}$
-& \dots
-& $-0.555^{+ 0.123}_{-0.219}$
-& $-1.654^{+ 0.394}_{-0.701}$
+& $-1.034^{+ 0.291}_{-0.409}$
+& $-0.174^{+ 0.103}_{-0.134}$
+& \ldots
+& $-0.347^{+ 0.042}_{-0.060}$
+& $-1.032^{+ 0.141}_{-0.208}$
 \\
@@
 
-The non-zero values for $\vec{\zeta}$ demonstrate that light-curve shape $x_1$ is  an indicator
+The non-zero values for $\vec{\zeta}$ \added{and their effect on color $\vec{\zeta}-\zeta_{\hat{V}}$}  demonstrate that light-curve shape $x_1$ is  an indicator
 of broadband colors, in the sense that SNe~Ia with broader light curves are bluer in all colors.
@@
 Eq.~\ref{trans_I:eqn}, is satisfied by the transformation matrix
+\added{
 \begin{equation}
@@
 \begin{array}{rr}
-39.7^{+2.4}_{-2.5} & 16.6^{+0.7}_{-0.6} \\
--14.5^{+3.4}_{-3.4} & 3.7^{+1.0}_{-1.0}
+40.3^{+1.8}_{-1.8} & 16.6^{+0.6}_{-0.6} \\
+-5.8^{+3.1}_{-3.0} & 3.4^{+1.0}_{-0.9}
 \end{array}
@@
 \begin{split}
-\vec{\epsilon}_{\gamma^0} &=\left(1.1^{+0.4}_{-0.4} , -1.2^{+0.4}_{-0.4} , -0.8^{+0.4}_{-0.4} , 0.7^{+0.2}_{-0.2} , 0.4^{+0.6}_{-0.6}\right), \\
-\vec{\epsilon}_{\gamma^1} & =\left(-2.8^{+0.6}_{-0.6} , 4.3^{+0.6}_{-0.6} , -0.8^{+0.6}_{-0.6} , 1.2^{+0.3}_{-0.3} , -2.6^{+0.9}_{-0.9}\right).
+\vec{\epsilon}_{\gamma^0} &=\left(1.1^{+0.4}_{-0.4} , -1.2^{+0.4}_{-0.4} , -0.9^{+0.4}_{-0.4} , 0.7^{+0.2}_{-0.2} , 0.5^{+0.6}_{-0.5}\right), \\
+\vec{\epsilon}_{\gamma^1} & =\left(-2.3^{+0.6}_{-0.5} , 4.0^{+0.6}_{-0.6} , -1.3^{+0.6}_{-0.6} , 0.7^{+0.3}_{-0.3} , -1.4^{+0.8}_{-0.8}\right).
 \end{split}
@@
 onto this plane is
-$0.959^{+0.015}_{-0.029}$.
-The   $\vec{\gamma}^0$  vector points in the $\langle R^F_{\mathit{eff}}\rangle=2.39^{+0.15}_{-0.16}$ dust-extinction direction.
+$0.8426^{+0.0780}_{-0.1236}$.
+\added{For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals from $\vec{\epsilon}$ are 
+$\left(0.005, 0.012,0.011, 0.007, 0.004 \right)$.
+}
+The   $\vec{\gamma}^0$  vector points in the $\langle R^F_{\mathit{eff}}\rangle=2.43^{+0.10}_{-0.10}$ dust-extinction direction.
+}
 This value is consistent with the $R_V=2.5$ found in the supernova samples of \citet{2011ApJ...729...55F}, and the
@@
    See Figure~\ref{plane:fig}.
-   The combination $\vec{a}+\vec{b}/2.39$ is shown in the dotted red
+   The combination $\vec{a}+\vec{b}/2.43$ is shown in the dotted red
    line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
@@
 the $\vec{\gamma}$ vectors (nor of the  \citetalias{1999PASP..111...63F} dust-extinction model); a quadratic fraction of
-$0.130^{+0.262}_{-0.104}$ of  %new
- $\vec{\phi}$ lies in the $\vec{\gamma}^0$--$\vec{\gamma}^1$ plane.
+\added{
+$0.49^{+0.27}_{-0.19}$ of  $\vec{\phi}$ lies perpendicular to the $\vec{\gamma}^0$--$\vec{\gamma}^1$ plane.}
 
@@
 The Pearson correlation coefficients of the per-supernova parameters are given in the matrix
+\added{
 \begin{multline}
-Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}) =\\
+Cor(EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}) =\\
 \begin{pmatrix}
-\begin{array}{rrrrrrrr}
-\Delta& -0.08^{+0.06}_{-0.06} & -0.11^{+0.08}_{-0.07} & -0.17^{+0.06}_{-0.06} & 0.19^{+0.08}_{-0.09} & 0.07^{+0.07}_{-0.06} & 0.23^{+0.08}_{-0.08} & 0.12^{+0.06}_{-0.06} \\
-\ldots  & EW_{Ca} & 0.10^{+0.03}_{-0.03} & -0.25^{+0.03}_{-0.03} & 0.07^{+0.03}_{-0.03} & -0.10^{+0.05}_{-0.05} & -0.18^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
-\ldots & \ldots &EW_{Si}  & -0.12^{+0.03}_{-0.03} & -0.84^{+0.01}_{-0.01} & -0.13^{+0.04}_{-0.04} & 0.27^{+0.08}_{-0.09} & -0.00^{+0.08}_{-0.07} \\
-\ldots  & \ldots  & \ldots  &  \lambda_{Si}& 0.14^{+0.03}_{-0.03} & 0.01^{+0.06}_{-0.05} & 0.00^{+0.06}_{-0.06} & -0.00^{+0.08}_{-0.08} \\
-\ldots  &\ldots  &\ldots & \ldots & x_1 & 0.13^{+0.04}_{-0.04} & -0.20^{+0.09}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
-\ldots  &\ldots  & \ldots  &\ldots  & \ldots  & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 0.04^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
-\ldots  & \ldots &\ldots  & \ldots  & \ldots & \ldots  &E_{\gamma^1}({\hat{B}}-{\hat{V}})  & -0.00^{+0.08}_{-0.08} \\
-\ldots  & \ldots & \ldots & \ldots  & \ldots  & \ldots  &\ldots  & A_{p,V} \\
+\begin{array}{rrrrrrr}
+EW_{Ca} & 0.10^{+0.03}_{-0.03} & -0.25^{+0.03}_{-0.03} & 0.07^{+0.03}_{-0.03} & -0.10^{+0.05}_{-0.05} & -0.18^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
+\ldots &EW_{Si} & -0.12^{+0.03}_{-0.03} & -0.84^{+0.01}_{-0.01} & -0.13^{+0.04}_{-0.04} & 0.27^{+0.08}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
+\ldots & \ldots& \lambda_{Si} & 0.14^{+0.03}_{-0.03} & 0.01^{+0.06}_{-0.05} & 0.00^{+0.06}_{-0.06} & -0.00^{+0.08}_{-0.08} \\
+\ldots& \ldots& \ldots& x_1 & 0.13^{+0.04}_{-0.04} & -0.20^{+0.09}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
+\ldots& \ldots& \ldots & \ldots& E_{\gamma^0}({\hat{B}}-{\hat{V}})& 0.04^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
+\ldots & \ldots & \ldots& \ldots&\ldots & E_{\gamma^1}({\hat{B}}-{\hat{V}})  & 0.00^{+0.08}_{-0.08} \\
+\ldots & \ldots & \ldots&\ldots &\ldots &\ldots &  A_{p,V} \\
 \end{array}
@@
 \end{multline}
+Recall that the $\Delta$-cofactor degeneracy is broken by assigning zero correlation between $\Delta$ and the features.}
 To aid readability, only the upper triangular part of the otherwise symmetric matrix is shown and the corresponding feature label is given on
@@
 The vector
-$\vec{\gamma}^0$ describes color changes for an effective $\langle R^F_{\mathit{eff}}\rangle=2.39$ dust, as shown 
+$\vec{\gamma}^0$ describes color changes for an effective $\langle R^F_{\mathit{eff}}\rangle=2.43$ dust, as shown 
 in  \S\ref{results3gamma:sec}.
 Hence, the per-supernova parameter $\gamma^0_{\hat{V}} g_0$ is associated with the $\hat{V}$-band
-extinction for a constant $R^F=2.39$.
+extinction for a constant $R^F=2.43$.
 Figure~\ref{k0_med:fig} shows the histogram of
@@
       of  per-supernova 
-median values of: (left) $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$, which is associated with the $A^F_V$ of an $\langle R^F_{\mathit{eff}}\rangle \sim 2.39$ dust model;
+median values of: (left) $\gamma^0_{\hat{V}} g_0-\gamma^0_{\hat{V}} g_0|_0$, which is associated with the $A^F_V$ of an $\langle R^F_{\mathit{eff}}\rangle \sim 2.43$ dust model;
 (right) $\gamma^1_{\hat{V}} g_1-\gamma^1_{\hat{V}} g_1|_0$,
@@
 sample is shown in Figure~\ref{kk:fig}. 
-For reference, a line that represents $\langle R^F_{\mathit{eff}}\rangle=2.39$ is overplotted; points above
+For reference, a line that represents $\langle R^F_{\mathit{eff}}\rangle=2.43$ is overplotted; points above
 the line have larger $R^F$, points below have smaller $R^F$.  The majority of supernovae lie within a narrow range above the line,
@@
       Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $g_0$ and $g_1$ parameters, for the supernova in our sample.
-      Overplotted is a line with the slope expected for $R^F=2.39$.
+      Overplotted is a line with the slope expected for $R^F=2.43$.
    \label{kk:fig}}
@@
 with wavelength.  For example, we find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
-to be $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -2.4_{  -4.1}^{+   1.6}$, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.  
+to be
+\replaced{ $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -2.4_{  -4.1}^{+   1.6}$}{$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) =-4.4_{  -6.4}^{+   2.4}$}, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.
 However a change of the color baseline gives a significantly different
-$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =2.4_{  -1.2}^{+   2.1}$.  Our results indicate that  $\beta_{\mathit{int}}$ %new
+$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =4.3_{  -1.4}^{+   3.8}$.  Our results indicate that  $\beta_{\mathit{int}}$ %new
 is sensitive to the color that $c$ corresponds to.  Although SALT2 $c$ is calibrated to correspond with $B-V$, it is
@@
 We plot in Figure~\ref{childress3:fig} our parameter
- $\sigma_p\phi_{\hat{I}}(p-p|_0) $  (subtracting out a random supernova
+ $\sigma_p\phi_{\hat{V}}(p-p|_0) $  (subtracting out a random supernova
 to suppress correlated errors) versus host mass
@@
 %---
-$\langle \sigma_p\phi_{\hat{V}}(p-p|_0) \rangle=  0.024 \pm {     0.005 }$ mag, %new
-$\langle \sigma_p\phi_{\hat{V}}(p-p|_0)  \rangle=0.038 \pm {     0.005 }$ mag
-for low- and high-mass hosts respectively, with a difference of $ 0.015 \pm {     0.006 }$~mag that is significant at $>2 \sigma$.
+$\langle \sigma_p\phi_{\hat{V}}(p-p|_0) \rangle=  0.041 \pm {     0.007 }$ mag, %new
+$\langle \sigma_p\phi_{\hat{V}}(p-p|_0)  \rangle=0.065 \pm {     0.007 }$ mag
+for low- and high-mass hosts respectively, with a difference of $ 0.024 \pm {     0.010 }$~mag that is significant at $>2 \sigma$.
 
@@
 %-----
-$0.15$
+\replaced{$0.15$}{$0.13$}
 %-----
@@
 with an effective
-$\langle R^F_{\mathit{eff}}\rangle \sim 2.39$ and an asymmetric tail extending toward lower values.
+$\langle R^F_{\mathit{eff}}\rangle \sim 2.43$ and an asymmetric tail extending toward lower values.
 We identify a new
@@
 $\alpha_X$
-& $0.0063^{+0.0006}_{-0.0006}$
-& $0.0029^{+0.0005}_{-0.0005}$
-& $0.0026^{+0.0005}_{-0.0005}$
-& $0.0026^{+0.0004}_{-0.0004}$
-& $0.0038^{+0.0004}_{-0.0004}$
+& $0.0037^{+0.0003}_{-0.0004}$
+& $0.0011^{+0.0003}_{-0.0003}$
+& $0.0012^{+0.0003}_{-0.0003}$
+& $0.0013^{+0.0003}_{-0.0003}$
+& $0.0026^{+0.0002}_{-0.0003}$
 \\
 ${\alpha_X/\alpha_V-1}$
-& $   1.5^{+   0.3}_{  -0.2}$
-& $   0.1^{+   0.0}_{  -0.0}$
+& $   2.0^{+   0.5}_{  -0.3}$
+& $  -0.1^{+   0.1}_{  -0.1}$
 & \ldots
-& $  -0.0^{+   0.0}_{  -0.0}$
-& $   0.5^{+   0.2}_{  -0.1}$
+& $   0.1^{+   0.1}_{  -0.0}$
+& $   1.1^{+   0.4}_{  -0.2}$
 \\
 $\beta_X$
-& $ 0.039^{+ 0.003}_{-0.003}$
-& $ 0.031^{+ 0.003}_{-0.003}$
-& $ 0.033^{+ 0.003}_{-0.003}$
-& $ 0.027^{+ 0.003}_{-0.003}$
 & $ 0.026^{+ 0.002}_{-0.002}$
+& $ 0.019^{+ 0.001}_{-0.001}$
+& $ 0.022^{+ 0.001}_{-0.001}$
+& $ 0.018^{+ 0.001}_{-0.001}$
+& $ 0.018^{+ 0.001}_{-0.001}$
 \\
 ${\beta_X/\beta_V-1}$
-& $  0.18^{+  0.04}_{ -0.03}$
-& $ -0.05^{+  0.01}_{ -0.01}$
+& $  0.17^{+  0.02}_{ -0.02}$
+& $ -0.14^{+  0.02}_{ -0.02}$
 & \ldots
-& $ -0.17^{+  0.01}_{ -0.01}$
-& $ -0.21^{+  0.03}_{ -0.02}$
+& $ -0.18^{+  0.01}_{ -0.01}$
+& $ -0.16^{+  0.01}_{ -0.01}$
 \\
 $\eta_X$
-& $0.0018^{+0.0009}_{-0.0010}$
-& $0.0016^{+0.0009}_{-0.0010}$
-& $0.0022^{+0.0008}_{-0.0009}$
-& $0.0021^{+0.0007}_{-0.0007}$
-& $0.0010^{+0.0006}_{-0.0006}$
+& $-0.0006^{+0.0005}_{-0.0005}$
+& $-0.0007^{+0.0004}_{-0.0004}$
+& \ldots
+& $0.0002^{+0.0003}_{-0.0004}$
+& $-0.0007^{+0.0003}_{-0.0003}$
 \\
 ${\eta_X/\eta_V-1}$
-& $ -0.18^{+  0.17}_{ -0.25}$
-& $ -0.25^{+  0.11}_{ -0.24}$
+& $ -0.30^{+  4.06}_{ -3.18}$
+& $ -0.73^{+  5.16}_{ -3.69}$
 & \ldots
-& $ -0.03^{+  0.11}_{ -0.06}$
-& $ -0.55^{+  0.13}_{ -0.18}$
+& $ -0.02^{+  0.81}_{ -0.97}$
+& $ -1.03^{+  5.25}_{ -3.77}$
 \\
@@
 & $  0.40^{+  0.03}_{ -0.03}$
-&\ldots
+& \ldots
 & $ -0.24^{+  0.01}_{ -0.01}$
@@
 & $ -0.02^{+  0.03}_{ -0.03}$
-&\ldots
+& \ldots
 & $ -0.24^{+  0.02}_{ -0.03}$
@@
 $\alpha_X$
-& $0.0048^{+0.0010}_{-0.0012}$
-& $0.0019^{+0.0009}_{-0.0010}$
-& $0.0018^{+0.0007}_{-0.0008}$
-& $0.0017^{+0.0006}_{-0.0006}$
-& $0.0027^{+0.0005}_{-0.0005}$
-\\
-${\alpha_X/\alpha_V-1}$
-& $   1.7^{+   1.0}_{  -0.4}$
+& $0.0048^{+0.0010}_{-0.0011}$
+& $0.0019^{+0.0008}_{-0.0009}$
+& $0.0018^{+0.0007}_{-0.0007}$
+& $0.0017^{+0.0005}_{-0.0005}$
+& $0.0027^{+0.0004}_{-0.0004}$
+\\
+${\alpha_X}/\alpha_{\hat{V}-1}$
+& $   1.7^{+   0.8}_{  -0.4}$
 & $   0.1^{+   0.1}_{  -0.1}$
@@
 & $  -0.0^{+   0.1}_{  -0.1}$
-& $   0.5^{+   0.7}_{  -0.3}$
+& $   0.5^{+   0.6}_{  -0.3}$
 \\
 $\beta_X$
-& $ 0.040^{+ 0.003}_{-0.003}$
-& $ 0.031^{+ 0.002}_{-0.002}$
-& $ 0.033^{+ 0.002}_{-0.002}$
+& $ 0.035^{+ 0.002}_{-0.003}$
+& $ 0.026^{+ 0.002}_{-0.002}$
 & $ 0.027^{+ 0.002}_{-0.002}$
-& $ 0.027^{+ 0.002}_{-0.002}$
-\\
-${\beta_X/\beta_V-1}$
-& $  0.23^{+  0.04}_{ -0.04}$
-& $ -0.04^{+  0.02}_{ -0.02}$
-&\ldots
-& $ -0.16^{+  0.01}_{ -0.01}$
-& $ -0.18^{+  0.03}_{ -0.03}$
+& $ 0.022^{+ 0.001}_{-0.001}$
+& $ 0.021^{+ 0.001}_{-0.001}$
+\\
+${\beta_X}/\beta_{\hat{V}-1}$
+& $  0.27^{+  0.04}_{ -0.04}$
+& $ -0.05^{+  0.02}_{ -0.02}$
+&  \ldots
+& $ -0.19^{+  0.01}_{ -0.01}$
+& $ -0.22^{+  0.03}_{ -0.02}$
 \\
 $\eta_X$
-& $0.0020^{+0.0010}_{-0.0009}$
-& $0.0022^{+0.0009}_{-0.0008}$
-& $0.0031^{+0.0008}_{-0.0008}$
-& $0.0031^{+0.0007}_{-0.0007}$
-& $0.0025^{+0.0007}_{-0.0007}$
-\\
-${\eta_X/\eta_V-1}$
-& $ -0.35^{+  0.17}_{ -0.22}$
-& $ -0.29^{+  0.10}_{ -0.14}$
+& $-0.0005^{+0.0008}_{-0.0008}$
+& $-0.0003^{+0.0007}_{-0.0007}$
+& $0.0006^{+0.0006}_{-0.0006}$
+& $0.0006^{+0.0005}_{-0.0005}$
+& $0.0000^{+0.0004}_{-0.0004}$
+\\
+${\eta_X}/\eta_{\hat{V}-1}$
+& $ -1.17^{+  1.20}_{ -2.44}$
+& $ -1.01^{+  0.76}_{ -1.89}$
 &  \ldots
-& $  0.01^{+  0.06}_{ -0.04}$
-& $ -0.19^{+  0.10}_{ -0.09}$
+& $ -0.03^{+  0.33}_{ -0.19}$
+& $ -0.78^{+  0.51}_{ -0.78}$
 \\
 $\gamma^0_X$
-& $ 71.32^{+  3.40}_{ -3.24}$
-& $ 58.31^{+  3.03}_{ -2.93}$
-& $ 43.90^{+  2.76}_{ -2.73}$
-& $ 33.23^{+  2.40}_{ -2.43}$
-& $ 24.74^{+  2.42}_{ -2.52}$
-\\
-${\gamma^0_X/\gamma^0_V-1}$
-& $  0.62^{+  0.06}_{ -0.05}$
-& $  0.33^{+  0.03}_{ -0.03}$
+& $ 71.40^{+  3.29}_{ -3.14}$
+& $ 58.39^{+  2.79}_{ -2.62}$
+& $ 43.99^{+  2.27}_{ -2.12}$
+& $ 33.29^{+  1.87}_{ -1.72}$
+& $ 24.81^{+  1.64}_{ -1.53}$
+\\
+${\gamma^0_X}/\gamma^0_{\hat{V}-1}$
+& $  0.62^{+  0.04}_{ -0.04}$
+& $  0.33^{+  0.02}_{ -0.02}$
 & \ldots
 & $ -0.24^{+  0.01}_{ -0.01}$
-& $ -0.44^{+  0.03}_{ -0.03}$
+& $ -0.44^{+  0.02}_{ -0.02}$
 \\
 $\gamma^1_X$
-& $ -0.29^{+  5.63}_{ -5.29}$
-& $ -7.82^{+  4.70}_{ -4.52}$
-& $-14.71^{+  3.79}_{ -3.78}$
-& $-12.48^{+  3.21}_{ -3.23}$
-& $-15.79^{+  2.98}_{ -2.99}$
-\\
-${\gamma^1_X/\gamma^1_V-1}$
-& $ -0.98^{+  0.29}_{ -0.50}$
-& $ -0.47^{+  0.15}_{ -0.25}$
+& $  9.83^{+  5.44}_{ -4.90}$
+& $  2.34^{+  4.44}_{ -4.18}$
+& $ -4.58^{+  3.40}_{ -3.32}$
+& $ -2.41^{+  2.72}_{ -2.63}$
+& $ -5.77^{+  2.22}_{ -2.15}$
+\\
+${\gamma^1_X}/\gamma^1_{\hat{V}-1}$
+& $ -2.62^{+  1.37}_{ -4.02}$
+& $ -1.25^{+  0.68}_{ -1.99}$
 & \ldots
-& $ -0.15^{+  0.04}_{ -0.04}$
-& $  0.07^{+  0.18}_{ -0.12}$
+& $ -0.43^{+  0.12}_{ -0.32}$
+& $  0.15^{+  0.88}_{ -0.37}$
 \\
 $\sigma_p \phi_X$
-& $ 0.010^{+ 0.009}_{-0.009}$
-& $-0.021^{+ 0.007}_{-0.007}$
-& $-0.021^{+ 0.006}_{-0.007}$
-& $-0.008^{+ 0.006}_{-0.006}$
-& $ 0.036^{+ 0.007}_{-0.007}$
-\\
-${\phi_X/\phi_{\hat{I}}-1}$
-& $-0.718^{+ 0.244}_{-0.254}$
-& $-1.574^{+ 0.233}_{-0.319}$
-& $-1.584^{+ 0.234}_{-0.342}$
-& $-1.230^{+ 0.170}_{-0.246}$
+& $-0.007^{+ 0.012}_{-0.012}$
+& $-0.039^{+ 0.010}_{-0.010}$
+& $-0.039^{+ 0.009}_{-0.008}$
+& $-0.026^{+ 0.007}_{-0.007}$
+& $ 0.018^{+ 0.007}_{-0.007}$
+\\
+${\phi_X/\phi_{\hat{V}}-1}$
+& $-0.804^{+ 0.245}_{-0.342}$
+& $-0.009^{+ 0.095}_{-0.109}$
 & \ldots
-\\
-\hline
+& $-0.328^{+ 0.047}_{-0.066}$
+& $-1.465^{+ 0.220}_{-0.349}$
+\\\hline
 \end{tabular}

### 2018-02-01 decorrelate.py

@@ -48,7 +48,8 @@ def fix3_x1():
             #     fit['eta'][i,:]* fit['sivel'][i,j] + fit['zeta'][i,:]* fit['x1'][i,j]
 
             newDelta.append(fit['Delta'][i,j] - \
-                numpy.dot(c,numpy.array([fit['EW'][i,j,0],fit['EW'][i,j,1],fit['sivel'][i,j], fit['x1'][i,j], fit['k'][i,j], fit['R'][i,j], fit['ev_sig'][i]* fit['mag_int_raw'][i,j]])))
+                numpy.dot(c,numpy.array([fit['EW'][i,j,0],fit['EW'][i,j,1],fit['sivel'][i,j], fit['x1'][i,j], \
+                fit['k'][i,j], fit['R'][i,j],fit['ev_sig'][i]* fit['mag_int_raw'][i,j]])))
 
             # print "new" 
             # print newDelta + newalpha*fit['EW'][i,j,0]+newbeta* fit['EW'][i,j,1] +\
@@ -56,39 +57,39 @@ def fix3_x1():
 
         newDelta = numpy.array(newDelta)
 
-        # # now do latent parameters
-        latents =[fit['k'][i,:],fit['R'][i,:],fit['ev_sig'][i]*fit['mag_int_raw'][i,:]]
-        cofactors =[newgamma,newrho1,newev]
-        newpars = []
-        for lat, cof in zip(latents,cofactors):
-            hs = numpy.array([fit['EW'][i,:,0],fit['EW'][i,:,1],fit['sivel'][i,:], fit['x1'][i,:],lat])
-            bigcov = numpy.cov(hs)
-            hscov = bigcov[:4,:4]
-            hdcov = bigcov[:4,4]
-            c = numpy.dot(numpy.linalg.inv(hscov), hdcov)
+        # # # now do latent parameters
+        # latents =[fit['k'][i,:],fit['R'][i,:],fit['ev_sig'][i]*fit['mag_int_raw'][i,:]]
+        # cofactors =[newgamma,newrho1,newev]
+        # newpars = []
+        # for lat, cof in zip(latents,cofactors):
+        #     hs = numpy.array([fit['EW'][i,:,0],fit['EW'][i,:,1],fit['sivel'][i,:], fit['x1'][i,:],lat])
+        #     bigcov = numpy.cov(hs)
+        #     hscov = bigcov[:4,:4]
+        #     hdcov = bigcov[:4,4]
[…]

### 2018-02-01 tablef3.py

@@ -7,8 +7,8 @@ import sivel
 import sncosmo
 import fitz_band
 
-f = open('fix3.pkl','rb')
-(fit, _) = pickle.load(f)
+f = open('fix3_decorr.pkl','rb')
+fit = pickle.load(f)
 f.close()
 
 for key in fit.keys():
@@ -21,16 +21,16 @@ fixev = fit['ev']
 fixev = fixev * numpy.sign(fixev[:,4])[:,None]
 
 
-print "projection of ev in gamma plane"
+print "projection of ev outside of gamma plane"
 proj = []
 for ev, evorig, g1, g2 in zip(fixev, fit['ev'], fit['gamma'], fit['rho1']):
     y=numpy.array([numpy.dot(evorig,g1), numpy.dot(evorig,g2)])
     M = numpy.array([[numpy.dot(g1,g1), numpy.dot(g1,g2)], \
         [numpy.dot(g2,g1), numpy.dot(g2,g2)]])
     com = numpy.dot(numpy.linalg.inv(M),y)
-    proj.append(numpy.linalg.norm(com[0]*g1+com[1]*g2)**2 / numpy.linalg.norm(evorig)**2)
+    proj.append(1-numpy.linalg.norm(com[0]*g1+com[1]*g2)**2 / numpy.linalg.norm(evorig)**2)
 dum1, dumm, dump =  numpy.percentile(proj,(50,50-34,50+34),axis=0)
-print "${:.3f}^{{+{:.3f}}}_{{{:.3f}}}$".format(dum1,dump-dum1,dumm-dum1)
+print "${:.2f}^{{+{:.2f}}}_{{{:.2f}}}$".format(dum1,dump-dum1,dumm-dum1)
 
 print "ev_sig size"
 dum1, dumm, dump =  numpy.percentile(fit['ev_sig'],(50,50-34,50+34),axis=0)
@@ -39,8 +39,8 @@ print "{:.3f}^{{+{:.3f}}}_{{{:.3f}}}".format(dum1,dump-dum1,dumm-dum1)
 print "the table"
 
 pars = ['alpha','alpha','beta','beta','eta','eta','gamma','gamma','rho1','rho1']
[…]

### 2018-02-01 tablef3_x1.py

@@ -7,8 +7,9 @@ import sivel
 import sncosmo
 import fitz_band
 
-f = open('fix3_x1.pkl','rb')
-(fit, _) = pickle.load(f)
+f = open('fix3_x1_decorr.pkl','rb')
+# (fit, _) = pickle.load(f)
+fit = pickle.load(f)
 f.close()
 
 for key in fit.keys():
@@ -21,14 +22,14 @@ fixev = fit['ev']
 fixev = -fixev * numpy.sign(fixev[:,2])[:,None]
 
 
-print "projection of ev in gamma plane"
+print "projection of ev out of gamma plane"
 proj = []
 for ev, evorig, g1, g2 in zip(fixev, fit['ev'], fit['gamma'], fit['rho1']):
     y=numpy.array([numpy.dot(evorig,g1), numpy.dot(evorig,g2)])
     M = numpy.array([[numpy.dot(g1,g1), numpy.dot(g1,g2)], \
         [numpy.dot(g2,g1), numpy.dot(g2,g2)]])
     com = numpy.dot(numpy.linalg.inv(M),y)
-    proj.append(numpy.linalg.norm(com[0]*g1+com[1]*g2)**2 / numpy.linalg.norm(evorig)**2)
+    proj.append(1-numpy.linalg.norm(com[0]*g1+com[1]*g2)**2 / numpy.linalg.norm(evorig)**2)
 dum1, dumm, dump =  numpy.percentile(proj,(50,50-34,50+34),axis=0)
 print "${:.3f}^{{+{:.3f}}}_{{{:.3f}}}$".format(dum1,dump-dum1,dumm-dum1)
 
@@ -39,8 +40,8 @@ print "{:.3f}^{{+{:.3f}}}_{{{:.3f}}}".format(dum1,dump-dum1,dumm-dum1)
 print "the table"
 
 pars = ['alpha','alpha','beta','beta','eta','eta','zeta','zeta','gamma','gamma','rho1','rho1']
-pars_n = ['\\alpha_X','{\\alpha_X/\\alpha_{\hat{V}}-1}','\\beta_X','{\\beta_X/\\beta_{\hat{V}}-1}',\
[…]

### 2018-02-02 submit/fix.tex
address Jakob's comments

@@
 \epsilon_\Delta  = -  \epsilon_{\alpha} (EW_{\text{Ca}}-\langle EW_{\text{Ca}}\rangle)- 
- \epsilon_{\beta} (EW_{\text{Si}}-\langle EW_{\text{Si}}\rangle) -  \epsilon_{\eta} (\lambda_{\text{Si}}-\langle \lambda_{\text{Si}}\rangle)
+ \epsilon_{\beta} (EW_{Si}-\langle EW_{Si}\rangle) -  \epsilon_{\eta} (\lambda_{Si}-\langle \lambda_{Si}\rangle)
 - \epsilon_{\gamma^0}g_0 -  \epsilon_{\gamma^1}g_1.
@@
 We break this degeneracy by fixing the values of $\epsilon$ such that $\Delta$ is
-uncorrelated with  $EW_{\text{Ca}}$, $EW_{\text{Si}}$, $\lambda_{\text{Ca}}$,
+uncorrelated with  $EW_{\text{Ca}}$, $EW_{Si}$, $\lambda_{\text{Ca}}$,
 $g_0$, and $g_1$.
@@
 
-\subsection{Remarks}
+\subsection{Model~I Summary}
 There are two points to highlight from the analysis of
@@
 c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1 + \sigma_p\phi_{\hat{I}}  p
-\end{pmatrix}
+\end{pmatrix}.
 \label{ewsiv2:eqn}
 \end{equation}
-}
+
+The Cauchy prior is commonly used to concentrate probability around a specific value while having fat tails with infinite variance.}
 
@@
 
-\subsection{Remarks}
+\subsection{Model~II Summary}
 The inclusion of a third color term beyond the two of Model~I has important consequences.
@@
 This and similar plots for the other permutations of observed colors show  no apparent trend between residuals and observed
-color nor of extreme catastrophic outliers.
+color nor any catastrophic outliers.
 }
@@
  $\gamma_X/\gamma_{\hat{V}}-1$.
-Note the analogy between these color statistics and the common use of
+ \added{These statistics give the change in $X-\hat{V}$ color normalized to the change in $\hat{V}$ magnitude, and are analogous to}
 $R_V^{-1}=A_B/A_V-1$ as an observational descriptor of dust properties.
@@
 of $B-V$ on the pseudo-equivalent width of Si~II~$\lambda$4130 has previously been reported by
-\citet{2013ApJ...773...53F}.
+\citet{2011ApJ...734...42N, 2013ApJ...773...53F}.
 The insignificance of  our $\alpha_{\hat{B}}/\alpha_{\hat{V}}-1$ is consistent with the
@@
 The story on Si~II~$\lambda$6355 is not as clear.
- \citet{2011ApJ...742...89F, 2012ApJ...748..127F} find that
+ \citet{2009ApJ...699L.139W,2011ApJ...742...89F, 2012ApJ...748..127F} find that
 higher-velocity SNe~Ia tend to be redder than those with lower velocity. \citet{2012AJ....143..126B} find a
@@
 The correlations between $EW_{Si}$ and  $EW_{Ca}$  with host have already been noted \citep{2011ApJ...734...42N, 2015MNRAS.451.1973S}.
-There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$.
+There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$
+\added{(measured at peak brightness)}.
 This contrasts with the subset of supernovae identified by their high-velocity features (HVF) in
-Si~II~$\lambda$6355, who are found to be distinguished by their host galaxy properties
+Si~II~$\lambda$6355
+\added{(typically detected pre-maximum)}, who are found to be distinguished by their host galaxy properties
 \citep[e.g.][]{2014MNRAS.444.3258M, 2015MNRAS.446..354P, 2015ApJS..220...20Z}.
@@
 The model assumes that $p$ has a Normal distribution, which is shown in Figure~\ref{ebv3:fig} as the 
-stack of the posteriors of all supernovae of the external color-excess $E_{\gamma}({\hat{B}}-{\hat{V}})$.
+stack of the posteriors of all supernovae of the color-excess $E_p({\hat{B}}-{\hat{V}})$.
 Also shown for comparison is the distribution of
@@
 difficult to determine whether the results are consistent.   Our results show effects on color that are not monotonic
-with wavelength.  For example, we find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
+with wavelength.  \deleted{For example,} We find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
 to be
@@
 
-In this article we do not associate $p$ directly with Hubble residuals.  However,
+In this article we do not associate $p$ directly with Hubble residuals. 
+\deleted{However,
 we briefly  preview the discussion in \S\ref{Delta:sec} by mentioning that there is room for $p$-based magnitude corrections
-given the correlation between $\Delta$ and $\sigma_p\phi_{\hat{V}}p$ in Eq.~\ref{corr:eqn}.
+given the correlation between $\Delta$ and $\sigma_p\phi_{\hat{V}}p$ in Eq.~\ref{corr:eqn}.}
 
@@
 An absolute magnitude calibration using the parameters identified in this analysis is left to future work.
+
+\added{
+The existence of three color parameters  has important implications when SNe~Ia are used as distance indicators.
+Measurements in at least four bands are necessary to obtain three colors.  
+Supernova distance determinations that do not account for three color parameters are susceptible to 
+systematic errors.  
+Parameter populations evolving with redshift would result in errors in
+Hubble diagrams.
+The use of  correlators with the SN parameters, such as host-galaxy properties,
+can mitigate such errors.
+}
 

### 2018-02-02 viewf3_x1.py

@@ -1330,10 +1330,10 @@ c.add_chain(mega, \
 fig = c.plotter.plot(figsize="column", truth=numpy.zeros(5))
 
 for ax in fig.axes:
-    ax.xaxis.set_tick_params(labelsize=6)
-    ax.xaxis.label.set_size(6)
-    ax.yaxis.set_tick_params(labelsize=6)
-    ax.yaxis.label.set_size(6)
+    ax.xaxis.set_tick_params(labelsize=4)
+    ax.xaxis.label.set_size(5)
+    ax.yaxis.set_tick_params(labelsize=4)
+    ax.yaxis.label.set_size(5)
 fig.savefig('output_fix3_x1/perobject_corner.pdf',bbox_inches='tight')
 
 # figure = corner.corner(mega,labels=[r"$\Delta$",r"$EW_{Ca}$",r"$EW_{Si}$",r"$\lambda_{Si}$",r"$x_1$",r"$E_{\gamma^0}(B-V)$",r"$E_{\gamma^1}(B-V)$",r"$A_{p,V}$"],range=numpy.zeros(8)+.9995,label_kwargs={'fontsize':22})
@@ -1359,7 +1359,7 @@ for index in xrange(5):
     c.add_chain(mega[index,:,:],parameters=[r"$c_{{{}}}$".format(cname[index]), r"$\alpha_{{{}}}$".format(cname[index]),\
                     r"$\beta_{{{}}}$".format(cname[index]),r"$\eta_{{{}}}$".format(cname[index]),r"$\zeta_{{{}}}$".format(cname[index]),r"$\gamma^0_{{{}}}$".format(cname[index]),\
                     r"$\gamma^1_{{{}}}$".format(cname[index]),r"$\sigma_p \phi_{{{}}}$".format(cname[index])])
-    fig = c.plotter.plot( figsize="column", truth=numpy.zeros(5))
+    fig = c.plotter.plot( figsize="column", truth=[None,0,0,0,0,0,0,0])
 
     for ax in fig.axes:
         ax.xaxis.set_tick_params(labelsize=7)

### 2018-02-13 submit/fix.tex
more changes

@@
 an empirical model for SN~Ia peak colors with
-three color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
+three \added{latent} color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
 and the light-curve shape.
@@
 \added{
-The existence of the third color parameter has implications on the accuracy of SN~Ia distance determinations.
+These color parameters must be accounted for when using SNe~Ia as distance indicators.
 }
@@
 variation is consistent with Milky Way dust models.
-We accommodate up to  three independent color parameters
+We accommodate up to  three independent color parameters.
 \deleted{
@@
 and two additional latent parameters to account for color diversity. 
+\added{By latent, we mean that the parameters are not directly associated with a single observable but rather deduced
+as part of a hierarchical
+model.}
 For Model~II described in \S\ref{modelII:sec}, we add a third latent color parameter to the analysis.
@@
 \added{
-Deficiencies in this model are addressed in the subsequent models presented in the article.
+Deficiencies of this model are addressed in the subsequent models presented in the article.
 }
@@
 these spectral features are associated with SN~Ia  spectroscopic diversity  
-\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
+\citep{2005ApJ...623.1011B, 2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F,2012AJ....143..126B}.
 The explicit omission of light-curve shape in our model is compensated by its proxy,
@@
 \added{
-The underlying magnitudes are also linearly dependent on the per-supernova parameters $g_0$ and $g_1$.
+The underlying magnitudes are also linearly dependent on the per-supernova latent parameters $g_0$ and $g_1$.
 Unlike
-the spectral parameters ($EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$),  the latent
-parameters $g_0$ and $g_1$ are not directly associated
+the spectral parameters ($EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$),  $g_0$ and $g_1$ are not directly associated
 with observables but rather are inferred as part of the analysis.
@@
 c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}  +\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1
-\end{pmatrix},
+\end{pmatrix}.
 \label{ewsiv:eqn}
@@
 }
-where $\vec{I}$ is the Identity vector.
+$\vec{I}$ is the Identity vector.
 The global parameter vectors\footnote{Global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
@@
 $\vec{\alpha}$, $\vec{\beta}$,
-$\vec{\eta}$ (units of mag~\AA$^{-1}$), $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (unitless)}
+$\vec{\eta}$ (units of mag~\AA$^{-1}$), $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (units of mag)}
  are the intercept
@@
 {underlying} magnitudes.
+\added{The notation used in this article is not to be associated with the those from previous works.}
 
@@
 \end{equation}
-The model contains the product of latent parameters
+The model contains the product of parameters
 $\vec{\gamma} g$, which leads to the degeneracy $\vec{\gamma} \rightarrow a\vec{\gamma}$, $g \rightarrow a^{-1} g$.
@@
 This prior does not specify the sign of $a$, which leaves a parity degeneracy. 
-\added{In the presentation of our results $\vec{\gamma}g$ is shown, never $g$ alone.
+\added{Results in this article are given in terms of $\vec{\gamma}g$, not $g$ alone.
 }
@@
 Then
-each supernova's magnitude can shift as
+each supernova's grey term can shift as
 $\Delta \rightarrow \Delta  + \epsilon_\Delta$
-under the condition 
+with
 $$
@@
 uncorrelated with  $EW_{\text{Ca}}$, $EW_{Si}$, $\lambda_{\text{Ca}}$,
-$g_0$, and $g_1$.
-Our preference is for feature affects to be confined to the cofactors and not the grey magnitude offsets.}
+$g_0$, and $g_1$ reflecting
+our preference for feature affects to be confined to the cofactors and not the grey magnitude offsets.}
 
@@
 \label{results1:sec}
-\added{
-Recall that the purpose of this section is to introduce concepts rather than emphasize the specific results,
-which for this simple model is expected to have systematic biases.
-}
-
 In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
@@
 for our two \deleted{extrinsic} color terms to capture the effects of dust.
-We  thus interpret our model $\vec{\gamma}$'s in terms of
+\replaced{
+We  thus interpret}{In this section we reexpress our model $\vec{\gamma}$'s in terms of}
 the dust-extinction model of \citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F}.
@@
 
+\added{
+The credible interval for $\vec{\gamma}$'s and other parameters are presented in Table~\ref{global1:tab}.
+}
 Our model $\vec{\gamma}$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
@@
 \end{equation}
-The $\vec{\gamma}$'s derived from our analysis are almost entirely captured by the first term.
+%The $\vec{\gamma}$'s derived from our analysis are almost entirely captured by the first term.
 \added{
-The credible interval for $\vec{\gamma}$'s and other parameters are presented in Table~\ref{global1:tab}.
 We find
@@
 \end{array}
-\end{pmatrix} 
+\end{pmatrix} ,
 \end{equation}
-and
 \begin{align}
 \begin{split}
-\vec{\epsilon}_{\gamma^0} &=\left(1.5^{+0.3}_{-0.3} , -1.4^{+0.3}_{-0.3} , -1.8^{+0.4}_{-0.3} , 1.4^{+0.1}_{-0.1} , 0.5^{+0.4}_{-0.5} \right), \\
-\vec{\epsilon}_{\gamma^1} & =\left(4.8^{+0.3}_{-0.3} , -4.3^{+0.3}_{-0.3} , -5.7^{+0.4}_{-0.4} , 0.1^{+0.2}_{-0.2} , 6.8^{+0.5}_{-0.5}\right),
+\vec{\epsilon}_{\gamma^0} &=\left(1.5^{+0.3}_{-0.3} , -1.4^{+0.3}_{-0.3} , -1.8^{+0.4}_{-0.3} , 1.4^{+0.1}_{-0.1} , 0.5^{+0.4}_{-0.5} \right) \text{mag}, \\
+\vec{\epsilon}_{\gamma^1} & =\left(4.8^{+0.3}_{-0.3} , -4.3^{+0.3}_{-0.3} , -5.7^{+0.4}_{-0.4} , 0.1^{+0.2}_{-0.2} , 6.8^{+0.5}_{-0.5}\right) \text{mag},
 \end{split}
@@
 a quadratic fraction of $0.9993^{+0.0002}_{-0.0003}$ of $\vec{\gamma}^0$ and
-$0.9303^{+0.0210}_{-0.0341}$ of $\vec{\gamma}^1$ project onto the $\vec{a}$--$\vec{b}$ plane.
-For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals from $\vec{\epsilon}$ are 
-$\left(0.025, 0.023,0.029, 0.008, 0.027\right)$.}
+$0.9303^{+0.0210}_{-0.0341}$ of $\vec{\gamma}^1$ projecting onto the $\vec{a}$--$\vec{b}$ plane.
+The  contributions of these residuals to magnitudes are relatively small compared to
+the values of $\vec{\gamma}^0$ and $\vec{\gamma}^1$ in Table~\ref{global1:tab}.
+For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals due to $\vec{\epsilon}$ are 
+$\left(0.025, 0.023,0.029, 0.008, 0.027\right)$ mag.}
 The allowed color
@@
 
-Our posterior
-includes a prior in which the per-supernova parameters $g_0$ and  $g_1$ associated with $\gamma$ are uncorrelated.
-The parameters $\kappa_1$ and $\kappa_2$ are set by this prior.
-If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
-to    $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ being uncorrelated in the supernova sample.
-A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
-All color changes would then be confined to the $a_X+\kappa_1 b_X$ direction.
-This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.
-We use this interpretation to assign  $\langle R^F_{\mathit{eff}}\rangle \equiv \kappa_1^{-1}$ as
-the
-ensemble mean
-effective total-to-selective extinction of our sample.
-The posterior yields $\langle R^F_{\mathit{eff}}\rangle =2.25^{+0.11}_{-0.10}$.
+\added{The values of $\kappa$'s are determined by the conditions that the components $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ be
+uncorrelated with $\Delta$.   The corresponding basis vectors are $a_X+\kappa_1 b_X $ and $\kappa_2 a_X + b_X$.
+Defining an effective total to selective extinction $\langle R^F \rangle \equiv \kappa_1^{-1}$ so that the first basis vector is
+$a_X+ b_X/\langle R^F \rangle  $, we find from the 68\%-ile credible interval of $\kappa_1^{-1}$ that
+$\langle R^F \rangle=2.25^{+0.11}_{-0.10}$.
+The non-correlation condition does not strongly constrain the  second basis vector as
+$\kappa_2 =  15.60^{+26.19}_{-32.47}$.}
 Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.25$.
-
-The direction of the $\vec{\gamma}^1$ vector is described by $\kappa_2$.
-The prior that $g_0$ and  $g_1$ are uncorrelated leads  to  $\kappa_2$ being determined
-by the
-distribution of $A^F_V$ and $E^F(B-V)$ for our supernova sample.  In this article, we do not further consider the direction of
-$\vec{\gamma}^1$ but will later focus on the distribution of the per-supernova $g_0$ and $g_1$ parameters.
 
@@
  {
- The new parameter does affect colors in a distinct manner from $g_0$ and $g_1$.
+ The new parameter does affect colors in a  manner distinct from $g_0$ and $g_1$.
 A quadratic fraction of
@@
 e.g.\ $\gamma^0_{\hat{V}} g_0|_0$, is subtracted
-out to null out correlated error between supernovae.) The  change from Model~I to II is pronounced in  $\gamma^1_{\hat{V}}g_1$,
+out to null out correlated
+\added{parameter uncertainty between supernovae; recall the $\langle \Delta \rangle=0$, $\langle g_0 \rangle=0$, $\langle g_1 \rangle=0$,
+and $p  \sim \mathcal{N}(0,1)$ conditions.}) The  change from Model~I to II is pronounced in  $\gamma^1_{\hat{V}}g_1$,
 where  a Normal distribution component apparent in Model~I disappears in Model~II, presumably having been  assigned to $p$.
@@
 \item The effective $\langle R^F_{\mathit{eff}}\rangle$ shifts by $>1 \sigma$ when including the new color term.  This demonstrates,
-as has been noted by \citet{2011A&A...529L...4C}, that dust analyses
+as has been noted by \citet{2009ApJ...704.1036F,2009ApJS..185...32K}, that dust analyses
 that do not allow for additional color dispersion are susceptible to bias when inferring dust parameters.
@@
 \added{
-As in \S\ref{modelI:sec}, the degeneracy between $\vec{\phi}$ and $\Delta$ is fixed by enforcing zero correlation between $\Delta$ and $x_1$.
+As in \S\ref{modelI:sec}, the degeneracy between $\vec{\zeta}$ and $\Delta$ is fixed by enforcing zero correlation between $\Delta$ and $x_1$.
 }
@@
                residual
-               colors containing $\hat{B}_o$ or $\hat{V}_o$ are shaded. to highlight that these residuals are highly correlated with the measurements. }
+               colors containing $\hat{B}_o$ or $\hat{V}_o$ are shaded to highlight that the abscissa and ordinate have contributions
+               from  a common measurement. }
             \label{residual:fig}}
@@
 \\
+
 \hline
@@
 Our result for $\eta_{\hat{B}}/\eta_{\hat{V}}-1$ also gives no significant relation.
+
+\added{The significantly non-zero values for  $\alpha_{\hat{U}}$ and $\beta_{\hat{U}}$ from this study can be compared with the $U$-band study of
+\citet{2018arXiv180101834N} carried out on a subset of the same supernovae.
+Both analyses find a strong correlation between $U$ and the Si and Ca features.}
 
@@
 for the distribution of dust extinction the SN population is expected to suffer. 
+\added{There is no sign of two populations in $\gamma^1_{\hat{V}} g_1$, which would be expected from a subpopulation
+experiencing circumsteallar dust.}.
 
@@
 \end{table}
-
+\section{Degeneracy}
+Global parameters $\alpha$, $\beta$.  Per supernova parameters $\mu_i$, $x_i$, $c_i$, $M_i$.
+
+There are two arbitrary numbers $\epsilon_\alpha$ and $\epsilon_\beta$.
+
+The per supernova expected magnitude is
+
+\begin{align}
+m_i & = \mu_i + \langle M\rangle + \delta_{mi}  -\alpha x_i + \beta c_i\\
+& = \mu_i + \langle M\rangle + \epsilon_\alpha x_i - \epsilon_\beta   c_i+ \delta_{mi}  -(\alpha+ \epsilon_\alpha) x_i + (\beta+\epsilon_\beta) c_i\\
+& = \mu_i + \langle M\rangle' + \delta'_{mi}  -\alpha' x_i+ \beta' c_i .
+\end{align}
+where
+$\langle M\rangle' = \langle M\rangle + \epsilon_\alpha \langle x_i\rangle  - \epsilon_\beta   \langle c_i \rangle$ and
+$\delta'_{mi} =  \delta_{mi} +\epsilon_\alpha (x_i-\langle x_i \rangle) - \epsilon_\beta   (c_i-\langle c_i\rangle)   $, $\alpha' =\alpha+\epsilon_\alpha$, $\beta' =\beta+\epsilon_\beta$.
+There are two degrees of freedom between the unprimed
+and primed variables of Eqs.~1 and 2.
+
+Impose $\delta_{mi} \sim \mathcal{N}(0,\sigma_\delta)$.  If $x_i$ and $c_i$ have Normal distributions this condition does not break the degeneracy.
+A Baysian model (e.g.\ UNITY) that assumes Normal distributions for these parameters thus does not break the degeneracy.
+If  $x_i$ and $c_i$ do not have Normal distributions, the prior will drive $\epsilon$ to 0.
+
+SUGAR assumes normal distributions for its features.  It breaks its  degeneracy  by enforcing the analogue of $cov(\delta_{mi}, x_i)=0$ and $cov(\delta_{mi}, c_i)=0$.
+
+I do not impose the distribution from which $\Delta$ comes.
 \bibliographystyle{apj}

### 2018-02-13 submit/fix.tex
after Greg's comments

@@
 {Dust extinction is not the only effect that can contribute to $g_0$ and $g_1$ so interpreting
-them as pure dust parameters is subject to systematic errors.}  \end{itemize}
+them as pure dust parameters is subject to systematic errors.} 
+\item \added{We have defined an effective parameter $\langle R^F\rangle$ whose value may be compared with dust models.
+Such comparisons must be taken with a grain of salt,
+as this value is not fundamentally constrained by the model but is fixed by the added condition that $\Delta$ is
+uncorrelated with  $EW_{\text{Ca}}$, $EW_{Si}$, $\lambda_{\text{Ca}}$,
+$g_0$, and $g_1$.  The value of  $\langle R^F\rangle$ changes given different ansatzes  for breaking the $\Delta$--cofactor degeneracy 
+}
+\end{itemize}
 
@@
    Left:
-   Normalized stack of the posteriors of all supernovae  and histogram 
+   Normalized stack of the posteriors (includes parameter uncertainties) of all supernovae  and histogram 
       of  per-supernova 
@@
 \begin{split}
-\vec{\epsilon}_{\gamma^0} &=\left(1.1^{+0.4}_{-0.4} , -1.2^{+0.4}_{-0.4} , -0.9^{+0.4}_{-0.4} , 0.7^{+0.2}_{-0.2} , 0.5^{+0.6}_{-0.5}\right), \\
-\vec{\epsilon}_{\gamma^1} & =\left(-2.3^{+0.6}_{-0.5} , 4.0^{+0.6}_{-0.6} , -1.3^{+0.6}_{-0.6} , 0.7^{+0.3}_{-0.3} , -1.4^{+0.8}_{-0.8}\right).
+\vec{\epsilon}_{\gamma^0} &=\left(1.1^{+0.4}_{-0.4} , -1.2^{+0.4}_{-0.4} , -0.9^{+0.4}_{-0.4} , 0.7^{+0.2}_{-0.2} , 0.5^{+0.6}_{-0.5}\right) \text{mag}, \\
+\vec{\epsilon}_{\gamma^1} & =\left(-2.3^{+0.6}_{-0.5} , 4.0^{+0.6}_{-0.6} , -1.3^{+0.6}_{-0.6} , 0.7^{+0.3}_{-0.3} , -1.4^{+0.8}_{-0.8}\right) \text{mag}.
 \end{split}
@@
 \added{For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals from $\vec{\epsilon}$ are 
-$\left(0.005, 0.012,0.011, 0.007, 0.004 \right)$.
+$\left(0.005, 0.012,0.011, 0.007, 0.004 \right)$~mag.
 }
@@
 center  of the range of per-supernova $R^F$ values found in the samples of \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}.
-\deleted{Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are attributed to dust extinction.
+\replaced{Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are attributed to dust extinction.
 This association is further discussed when $g_0$ and $g_1$ are considered in \S\ref{g0g1:sec}.}
+{Although the model $\vec{\gamma}$'s cannot be attributed to dust, they behave like the   \citetalias{1999PASP..111...63F} model.}
 
@@
 The values of $\vec{\phi}$ does not change  monotonically with wavelength, as is apparent  in 
-the combination $\phi_X/\phi_{\hat{V}}-1$ shown in Figure~\ref{phiratio:fig}.  An object that has fainter  $\hat{U}$$\hat{I}$-band peak magnitudes
+the combination $\phi_X/\phi_{\hat{V}}-1$ shown in Figure~\ref{phiratio:fig}.  An object that has fainter  $\hat{U}$ or $\hat{I}$-band peak magnitudes
 has brighter  $\hat{B}$$\hat{V}$$\hat{R}$  peaks.  That brightening is non-uniform, in that
@@
 \end{multline}
-Recall that the $\Delta$-cofactor degeneracy is broken by assigning zero correlation between $\Delta$ and the features.}
+Recall that the $\Delta$-cofactor degeneracy is broken by enforcing zero correlation between $\Delta$ and the features.}
 To aid readability, only the upper triangular part of the otherwise symmetric matrix is shown and the corresponding feature label is given on
@@
 \added{There is no sign of two populations in $\gamma^1_{\hat{V}} g_1$, which would be expected from a subpopulation
-experiencing circumsteallar dust.}.
+experiencing extinction and scattering by circumstellar dust.}.
 
@@
       \caption{
-      Normalized stack of the posteriors of all supernovae  and histogram 
+      Normalized stack of the posteriors (includes parameter uncertainty) of all supernovae  and histogram 
       of  per-supernova 
@@
  %  \includegraphics[width=2.8in]{../output_fix3_x1/ebv_delta.pdf}
-      \caption{Stack of the posteriors of all supernovae of the  $E_{\gamma}({\hat{B}}-{\hat{V}})$ 
+      \caption{Stack of the posteriors  (includes parameter uncertainty) of all supernovae of the  $E_{\gamma}({\hat{B}}-{\hat{V}})$ 
       and the 
@@
 While we also claim a detection of an intrinsic color parameter, }
-{While we claim the detection of a color parameter incompatible with dust,}
+{While we too claim the detection of a color parameter incompatible with dust,}
 the differences between our models make it
@@
 is shown in Figure~\ref{hist:fig}.  The distribution
-has a standard deviation of
+has a total standard deviation of
 %-----
@@
    \caption{
-   Normalized stack of the posteriors of all supernovae and histogram of the per-supernova medians of the grey offset $\Delta$. 
+   Normalized stack of the posteriors  (includes parameter uncertainty) of all supernovae and histogram of the per-supernova medians of the grey offset $\Delta$. 
    To help null correlated errors, we select
@@
 Hubble diagrams.
-The use of  correlators with the SN parameters, such as host-galaxy properties,
-can mitigate such errors.
+The use of  correlators with the SN parameters, such as host-galaxy properties e.g.\ as shown for our $p$ parameter,
+may partially mitigate such errors.
 }

### 2018-03-14 submit/fix.tex
before submission version

@@
 \author{     P.~Antilogus}
-\affiliation{    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
-    Universit\'e Pierre et Marie Curie Paris 6, Universit\'e Paris Diderot Paris 7, CNRS-IN2P3, 
-    4 place Jussieu, 75252 Paris Cedex 05, France}
+\affiliation{    Sorbonne Universit\'e, Universit\'e Paris Diderot, CNRS/IN2P3, Laboratoire de Physique Nucl\'eaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252, Paris, France}
 
@@
 \author{     S.~Bongard}
-\affiliation{    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
-    Universit\'e Pierre et Marie Curie Paris 6, Universit\'e Paris Diderot Paris 7, CNRS-IN2P3, 
-    4 place Jussieu, 75252 Paris Cedex 05, France}
+\affiliation{ Sorbonne Universit\'e, Universit\'e Paris Diderot, CNRS/IN2P3, Laboratoire de Physique Nucl\'eaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252, Paris, France}
 
@@
 \author{     R.~Pain}
-\affiliation{    Laboratoire de Physique Nucl\'eaire et des Hautes \'Energies,
-    Universit\'e Pierre et Marie Curie Paris 6, Universit\'e Paris Diderot Paris 7, CNRS-IN2P3, 
-    4 place Jussieu, 75252 Paris Cedex 05, France}
+\affiliation{ Sorbonne Universit\'e, Universit\'e Paris Diderot, CNRS/IN2P3, Laboratoire de Physique Nucl\'eaire et de Hautes Energies, LPNHE, 4 Place Jussieu, F-75252, Paris, France}
 
@@
  \author{    M.~Rigault} 
-\affiliation{    Institut fur Physik,  Humboldt-Universitat zu Berlin,
-    Newtonstr. 15, 12489 Berlin}
+\affiliation{ Clermont Universit\'e, Universit\'e Blaise Pascal, CNRS/IN2P3, Laboratoire de Physique Corpusculaire,
+    BP 10448, F-63000 Clermont-Ferrand, France}
 
@@
     1 Cyclotron Road, Berkeley, CA, 94720}
+ \affiliation{Sorbonne Universit\'es, Institut Lagrange de Paris (ILP), 98 bis Boulevard Arago, 75014 Paris, France}
 
@@
 an empirical model for SN~Ia peak colors with
-three \added{latent} color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
+three latent color parameters and dependence on the equivalent widths of Ca~II and Si~II, the Si~II velocity,
 and the light-curve shape.
@@
 those already  tracked by the spectral features, light-curve shape, and two-parameter dust models.
-\added{
 These color parameters must be accounted for when using SNe~Ia as distance indicators.
-}
 \end{abstract}
@@
 the study of intrinsic supernova color based on SN~Ia Hubble diagrams
-\added{by allowing the addition of a supernova population model as an extra level within in the larger model.
-}
+by allowing the addition of a supernova population model as an extra level within in the larger model.
 Latent parameters that are not directly tied to observables
@@
 scatter in the Hubble diagram is better explained by a combination of 
-an intrinsic color-magnitude relationship with slope $\beta_{\mathit{int}}\sim 2.3$. intrinsic
+an intrinsic color-magnitude relationship with slope $\beta_{\mathit{int}}\sim 2.3$ intrinsic
 color dispersion,
@@
 We accommodate up to  three independent color parameters.
-\deleted{
-: the model is constructed such that 
-two are assigned as extrinsic processes attributed to dust, and one is attributed to intrinsic supernova
-properties.}
 The data used in this analysis are described in \S\ref{data:sec}.
@@
 and two additional latent parameters to account for color diversity. 
-\added{By latent, we mean that the parameters are not directly associated with a single observable but rather deduced
+By latent, we mean that the parameters are not directly associated with a single observable but rather deduced
 as part of a hierarchical
-model.}
+model.
 For Model~II described in \S\ref{modelII:sec}, we add a third latent color parameter to the analysis.
@@
 We begin by considering Model~I, in which supernova magnitudes  have linear dependence on spectral parameters
-and two \deleted{extrinsic} color parameters. The purpose of this section is to introduce some basic concepts of our models,
+and two color parameters. The purpose of this section is to introduce some basic concepts of our models,
 to show how the two  color terms can be associated with existing dust-extinction models, and to give Model~I results on dust extinction.
-\added{
 Deficiencies of this model are addressed in the subsequent models presented in the article.
-}
 To avoid repetitiveness,
@@
 that  peak
-\replaced{
-intrinsic}
-{underlying}
- ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova are linearly dependent
+underlying
+ ${\hat{U}}{\hat{B}}\hat{V}\hat{R}\hat{I}$ magnitudes of a supernova  with effects from  astrophysical foregrounds are linearly dependent
 on its
@@
 \citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
-\added{
 The underlying magnitudes are also linearly dependent on the per-supernova latent parameters $g_0$ and $g_1$.
@@
 with observables but rather are inferred as part of the analysis.
-}
 A grey magnitude offset, $\Delta$, is included for each supernova
@@
 With this grey offset the model standardizes colors, not absolute magnitude.
-The \added{
-underlying magnitudes are
+The underlying magnitudes are
 \begin{equation}
@@
 =
-\Delta \vec{I} +
+\Delta \vec{1} +
 \begin{pmatrix}
@@
 \end{equation}
-}
-$\vec{I}$ is the Identity vector.
+
+$\vec{1}$ is the Identity vector.
 The global parameter vectors\footnote{Global parameters act on each of the five bands: a single component is written with a subscript for the corresponding band, e.g.\  $c_{\hat{U}}$; 
@@
 } that describe the SN~Ia population
-\replaced{
-$\vec{c}$, 
-$\vec{\alpha}$, $\vec{\beta}$,
-and $\vec{\eta}$,}
-{
 $\vec{c}$  (units of mag);
 $\vec{\alpha}$, $\vec{\beta}$,
-$\vec{\eta}$ (units of mag~\AA$^{-1}$), $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (units of mag)}
+$\vec{\eta}$ (units of mag~\AA$^{-1}$), $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (units of mag)
  are the intercept
@@
 relate
-\replaced{
-spectral-feature}
-{per-supernova}
-parameters with \replaced{
-intrinsic}
-{underlying} magnitudes.
-\added{The notation used in this article is not to be associated with the those from previous works.}
+per-supernova
+parameters with 
+underlying magnitudes.
+The notation used in this article is not to be associated with those from previous works.
 
@@
 corresponds to the probability distribution function described by
-\added{
 \begin{equation}
@@
 \end{equation}
-}
 
@@
 The model does not specify the absolute magnitude nor the 
-\replaced{
-intrinsic color of a supernova that has no extrinsic color contribution;}
-{color of a $g_0=0$, $g_1=0$ supernova;}
+color of a $g_0=0$, $g_1=0$ supernova;
 in their place the zeropoints of the per-supernova magnitude and color parameters are set to the sample means
@@
 This prior does not specify the sign of $a$, which leaves a parity degeneracy. 
-\added{Results in this article are given in terms of $\vec{\gamma}g$, not $g$ alone.
-}
+Results in this article are given in terms of $\vec{\gamma}g$, not $g$ alone.
 As will be seen, the signal-to-noise in $\vec{\gamma}$ is sufficiently
@@
 
-\added{
 Each of the multiplicative cofactors has a degeneracy with the zeropoint.  Consider
@@
 $g_0$, and $g_1$ reflecting
-our preference for feature affects to be confined to the cofactors and not the grey magnitude offsets.}
+our preference for feature affects to be confined to the cofactors and not the grey magnitude offsets.
 
@@
 Since dust extinction is a dominant determinant of supernova colors that is often described by a 2-parameter linear model, we expect
-for our two \deleted{extrinsic} color terms to capture the effects of dust.
-\replaced{
-We  thus interpret}{In this section we reexpress our model $\vec{\gamma}$'s in terms of}
+for our two  color terms to capture the effects of dust.
+In this section we reexpress our model $\vec{\gamma}$'s in terms of
 the dust-extinction model of \citet{1999PASP..111...63F} \citepalias[henceforth referred to as][]{1999PASP..111...63F}.
@@
 All elements of the two $\vec{\gamma}$ parameter vectors 
-describing \deleted{intrinsic} color
+describing color
 are significantly non-zero.
@@
 
-\added{
 The credible interval for $\vec{\gamma}$'s and other parameters are presented in Table~\ref{global1:tab}.
-}
 Our model $\vec{\gamma}$ vectors can be written as a linear combination (described by the $2 \times 2$ matrix M) of the
@@
 %The $\vec{\gamma}$'s derived from our analysis are almost entirely captured by the first term.
-\added{
 We find
@@
 For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals due to $\vec{\epsilon}$ are 
-$\left(0.025, 0.023,0.029, 0.008, 0.027\right)$ mag.}
+$\left(0.025, 0.023,0.029, 0.008, 0.027\right)$ mag.
 The allowed color
@@
    \centering
-   \includegraphics[width=2.95in]{../output_fix1/plane0.pdf}
+   \includegraphics[width=2.95in]{fix1plane0.pdf}
    \includegraphics[width=2.95in]{../output_fix1/plane1.pdf}
@@
 
-\added{The values of $\kappa$'s are determined by the conditions that the components $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ be
+The values of $\kappa$'s are determined by the conditions that the components $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ be
 uncorrelated with $\Delta$.   The corresponding basis vectors are $a_X+\kappa_1 b_X $ and $\kappa_2 a_X + b_X$.
@@
 The non-correlation condition does not strongly constrain the  second basis vector as
-$\kappa_2 =  15.60^{+26.19}_{-32.47}$.}
+$\kappa_2 =  15.60^{+26.19}_{-32.47}$.
 Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\vec{\gamma}^0$ and  $\vec{a}+\vec{b}/2.25$.
@@
 That we recover a physically-motivated  result lends confidence in the modeling and analysis.
-\item In Model~I, any  \deleted{intrinsic} color variation that remains after spectral corrections is allocated to two parameters.
-\replaced{ Color variations beyond
-those from two-parameter dust extinction contribute to those two parameters.  The derived effective dust-parameter $R^F$ 
-is susceptible to leakage from intrinsic colors unassociated with dust.
-}
-{Dust extinction is not the only effect that can contribute to $g_0$ and $g_1$ so interpreting
-them as pure dust parameters is subject to systematic errors.} 
-\item \added{We have defined an effective parameter $\langle R^F\rangle$ whose value may be compared with dust models.
+\item In Model~I, any  color variation that remains after spectral corrections is allocated to two parameters.
+Dust extinction is not the only effect that can contribute to $g_0$ and $g_1$ so interpreting
+them as pure dust parameters is subject to systematic errors.
+\item We have defined an effective parameter $\langle R^F\rangle$ whose value may be compared with dust models.
 Such comparisons must be taken with a grain of salt,
@@
 $g_0$, and $g_1$.  The value of  $\langle R^F\rangle$ changes given different ansatzes  for breaking the $\Delta$--cofactor degeneracy 
-}
 \end{itemize}
@@
 \label{modelII:sec}
-Model~II extends Model~I to include a third \deleted{intrinsic-}color parameter.  This increase in the number of degrees of freedom 
-\replaced{accommodates
-one parameter for the optical depth of dust, one parameter to capture variation in dust properties, and
-another parameter for  color variability unrelated to dust.}
-{goes beyond the two of dust-extinction models used in supernova analysis.}
+Model~II extends Model~I to include a third color parameter.  This increase in the number of degrees of freedom 
+goes beyond the two of dust-extinction models used in supernova analysis.
  In this section we  focus on describing the consequences of the addition of the
@@
 Model~II is identical to Model~I except for the 
-addition of a \replaced{n intrinsic}{third} color parameter $p$.  The distribution of $p$ in our sample
+addition of a third color parameter $p$.  The distribution of $p$ in our sample
 is assumed to form a Normal distribution with unit standard deviation.  An unconstrained distribution,
@@
 \end{equation}
-\added{
 \begin{equation}
@@
 =
-\Delta  \vec{I} +
+\Delta  \vec{1} +
 \begin{pmatrix}
@@
 
-The Cauchy prior is commonly used to concentrate probability around a specific value while having fat tails with infinite variance.}
-
-\deleted{
-The new term is placed in Eq.~\ref{ewsiv2:eqn} as an intrinsic supernova property.  It is mathematically equivalent to
-put the term in the mean of Eq.~\ref{dust2:eqn} joining what we call extrinsic parameters.  Although we 
-use ``intrinsic'' and ``extrinsic'' as descriptive labels for $\vec{\phi}$ and $\vec{\gamma}$ respectively, the model cannot distinguish between
-their physical origins.
-}
+The Cauchy prior is commonly used to concentrate probability around a specific value while having fat tails with infinite variance.
 
@@
 in $\vec{\phi}$ is apparent later in the article, but it does not affect the magnitude predictions. 
-\added{
 As in \S\ref{modelI:sec}, the degeneracy between $\vec{\phi}$ and $\Delta$ is fixed by enforcing zero correlation between $\Delta$ and $p$.
-}
 
@@
 The posterior for $\sigma_p \vec{\phi}$ is shown in Figure~\ref{M1ev:fig}.  
-The two maxima are due to the sign degeneracy for $\vec{\phi}$, each of the MCMC chains converges to one of the solutions and does
-not migrate between them.
-\replaced{
-The direction of $\vec{\phi}$ is not aligned with the plane defined by
-the $\vec{\gamma}$ vectors; only a quadratic fraction of
- $0.09^{+0.12}_{-0.06}$ of 
- $\vec{\phi}$ lies in the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.}
- {
+Two maxima are allowed due to the sign degeneracy for $\vec{\phi}$.  Practically each of the MCMC chains converges to one of the solutions and does
+not migrate between them by crossing zero.  To aid visibility of this figure we thus impose $\phi_I > 0$.  
  The new parameter does affect colors in a  manner distinct from $g_0$ and $g_1$.
@@
  $\vec{\phi}$ lies perpendicular to the $\vec{\gamma}_0$--$\vec{\gamma}_1$ plane.
- }
 
@@
 out to null out correlated
-\added{parameter uncertainty between supernovae; recall the $\langle \Delta \rangle=0$, $\langle g_0 \rangle=0$, $\langle g_1 \rangle=0$,
-and $p  \sim \mathcal{N}(0,1)$ conditions.}) The  change from Model~I to II is pronounced in  $\gamma^1_{\hat{V}}g_1$,
+parameter uncertainty between supernovae; recall the $\langle \Delta \rangle=0$, $\langle g_0 \rangle=0$, $\langle g_1 \rangle=0$,
+and $p  \sim \mathcal{N}(0,1)$ conditions.) The  change from Model~I to II is pronounced in  $\gamma^1_{\hat{V}}g_1$,
 where  a Normal distribution component apparent in Model~I disappears in Model~II, presumably having been  assigned to $p$.
@@
 The direction of the  $\vec{\gamma}^0$ vector corresponds to an effective
-\replaced{$\langle R^F_{\mathit{eff}}\rangle = 2.54^{+0.20}_{-0.20}$}
-{$\langle R^F_{\mathit{eff}}\rangle = 2.54^{+0.13}_{-0.12}$}.
+$\langle R^F_{\mathit{eff}}\rangle = 2.54^{+0.13}_{-0.12}$.
 The change of $\langle R^F_{\mathit{eff}}\rangle$ from Model~I to II is anticipated by the change in the distribution of $g_1$,
@@
 \end{equation}
-}
 The changes from Model~II are the addition of the $\vec{\zeta} x_1$ terms in Eq.~\ref{ewsiv3:eqn}, and
 the addition of the shape measurement and uncertainty (implicit in the covariance matrix $C$) and $x_1$   in Eq.~\ref{dust3:eqn}.
-\added{
 As in \S\ref{modelI:sec}, the degeneracy between $\vec{\zeta}$ and $\Delta$ is fixed by enforcing zero correlation between $\Delta$ and $x_1$.
-}
 For $N$ supernovae there are $9N$ observables.  There are $4N$ spectral and light-curve shape parameters, each of
@@
 Figure~\ref{residual:fig} shows plots of 
-\added{residuals between measured and model-expectation colors as a function of observed $\hat{B}_o-\hat{V}_o$.
+residuals between measured and model-expectation colors as a function of observed $\hat{B}_o-\hat{V}_o$.
 This and similar plots for the other permutations of observed colors show  no apparent trend between residuals and observed
 color nor any catastrophic outliers.
-}
 
@@
    \centering
-%   \includegraphics[width=4in]{../output_fix3_x1/residual.pdf} 
    \includegraphics[width=4in]{../output_fix3_x1/cpull.pdf} 
                \caption{
-               \added{Residuals between measured and model-expectation colors as a function of observed $\hat{B}_o-\hat{V}_o$.  Plots that show
+               Residuals between measured and model-expectation colors as a function of observed $\hat{B}_o-\hat{V}_o$.  The colors are
+               relative to on arbitrary supernova. Plots that show
                residual
                colors containing $\hat{B}_o$ or $\hat{V}_o$ are shaded to highlight that the abscissa and ordinate have contributions
-               from  a common measurement. }
+               from  a common measurement.
             \label{residual:fig}}
@@
  $\gamma_X/\gamma_{\hat{V}}-1$.
- \added{These statistics give the change in $X-\hat{V}$ color normalized to the change in $\hat{V}$ magnitude, and are analogous to}
+ These statistics give the change in $X-\hat{V}$ color normalized to the change in $\hat{V}$ magnitude, and are analogous to
 $R_V^{-1}=A_B/A_V-1$ as an observational descriptor of dust properties.
@@
 
-\added{The significantly non-zero values for  $\alpha_{\hat{U}}$ and $\beta_{\hat{U}}$ from this study can be compared with the $U$-band study of
+The significantly non-zero values for  $\alpha_{\hat{U}}$ and $\beta_{\hat{U}}$ from this study can be compared with the $U$-band study of
 \citet{2018arXiv180101834N} carried out on a subset of the same supernovae.
-Both analyses find a strong correlation between $U$ and the Si and Ca features.}
-
-The non-zero values for $\vec{\zeta}$ \added{and their effect on color $\vec{\zeta}-\zeta_{\hat{V}}$}  demonstrate that light-curve shape $x_1$ is  an indicator
+Both analyses find a strong correlation between $U$ and the Si and Ca features.
+
+The non-zero values for $\vec{\zeta}$ and their effect on color $\vec{\zeta}-\zeta_{\hat{V}}$  demonstrate that light-curve shape $x_1$ is  an indicator
 of broadband colors, in the sense that SNe~Ia with broader light curves are bluer in all colors.
@@
 As with Model~I in \S\ref{modelI:sec}, all elements of the two $\vec{\gamma}$ parameter vectors 
-\deleted{describing extrinsic color}
 are significantly non-zero with 
@@
 Eq.~\ref{trans_I:eqn}, is satisfied by the transformation matrix
-\added{
 \begin{equation}
@@
 $0.8426^{+0.0780}_{-0.1236}$.
-\added{For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals from $\vec{\epsilon}$ are 
+For the standard deviation values of $g_0$ and $g_1$ of the supernovae in our sample, the amplitude of the magnitude residuals from $\vec{\epsilon}$ are 
 $\left(0.005, 0.012,0.011, 0.007, 0.004 \right)$~mag.
-}
 The   $\vec{\gamma}^0$  vector points in the $\langle R^F_{\mathit{eff}}\rangle=2.43^{+0.10}_{-0.10}$ dust-extinction direction.
-}
 This value is consistent with the $R_V=2.5$ found in the supernova samples of \citet{2011ApJ...729...55F}, and the
 center  of the range of per-supernova $R^F$ values found in the samples of \citet{2014ApJ...789...32B, 2015MNRAS.453.3300A}.
-\replaced{Based on these facts, the supernova ``extrinsic'' colors $\vec{\gamma}^0 g_0 + \vec{\gamma}^1 g_1$  of our model are attributed to dust extinction.
-This association is further discussed when $g_0$ and $g_1$ are considered in \S\ref{g0g1:sec}.}
-{Although the model $\vec{\gamma}$'s cannot be attributed to dust, they behave like the   \citetalias{1999PASP..111...63F} model.}
+Although the model $\vec{\gamma}$'s cannot be attributed to dust, they behave like the   \citetalias{1999PASP..111...63F} model.
 
@@
 
-The  new \deleted{intrinsic} $p$ parameter has a significant influence on color.  The magnitude of its color effect is non-zero,
+The  new  $p$ parameter has a significant influence on color.  The magnitude of its color effect is non-zero,
 with $\sigma_p = 0.053^{+ 0.010}_{-0.005}$~mag.  The smallest value of $\sigma_p$ % new
@@
 the $\vec{\gamma}$ vectors (nor of the  \citetalias{1999PASP..111...63F} dust-extinction model); a quadratic fraction of
-\added{
-$0.49^{+0.27}_{-0.19}$ of  $\vec{\phi}$ lies perpendicular to the $\vec{\gamma}^0$--$\vec{\gamma}^1$ plane.}
+$0.49^{+0.27}_{-0.19}$ of  $\vec{\phi}$ lies perpendicular to the $\vec{\gamma}^0$--$\vec{\gamma}^1$ plane.
 
@@
 
-\deleted{We emphasize that
-although the $\sigma_p \vec{\phi}p$ colors have ben referred to as ``intrinsic'' due to their placement in the model, the analysis cannot quantitatively distinguish
-whether its origin is intrinsic or due to a third dust parameter or some other extrinsic effect.}
 What is measured as $\sigma_p \vec{\phi}$ likely captures the effect of many physical processes.
 To simplify the model it is assumed that the $p$'s are drawn from a Normal distribution, which may not be a fair description of what occurs in nature
-\added{and result in model bias}.
-The physical interpretation of this \deleted{intrinsic} color should be tempered with caution.
+and result in model bias.
+The physical interpretation of this color should be tempered with caution.
 
@@
 The Pearson correlation coefficients of the per-supernova parameters are given in the matrix
-\added{
 \begin{multline}
@@
 \end{multline}
-Recall that the $\Delta$-cofactor degeneracy is broken by enforcing zero correlation between $\Delta$ and the features.}
+Recall that the $\Delta$-cofactor degeneracy is broken by enforcing zero correlation between $\Delta$ and the features.
 To aid readability, only the upper triangular part of the otherwise symmetric matrix is shown and the corresponding feature label is given on
@@
 to in \S\ref{results3global:sec} when interpreting the correlation between the cofactors $\vec{\beta}$ and $\vec{\zeta}$ that connect them with magnitudes.
+
+The $\Delta$ parameter will be discussed in its own subsection \S\ref{Delta:sec}.
 
@@
 for the distribution of dust extinction the SN population is expected to suffer. 
-\added{There is no sign of two populations in $\gamma^1_{\hat{V}} g_1$, which would be expected from a subpopulation
-experiencing extinction and scattering by circumstellar dust.}.
+There is no sign of two populations in $\gamma^1_{\hat{V}} g_1$, which would be expected from a subpopulation
+experiencing extinction and scattering by circumstellar dust.
 
@@
 There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$
-\added{(measured at peak brightness)}.
+(measured at peak brightness).
 This contrasts with the subset of supernovae identified by their high-velocity features (HVF) in
 Si~II~$\lambda$6355
-\added{(typically detected pre-maximum)}, who are found to be distinguished by their host galaxy properties
+(typically detected pre-maximum), who are found to be distinguished by their host galaxy properties
 \citep[e.g.][]{2014MNRAS.444.3258M, 2015MNRAS.446..354P, 2015ApJS..220...20Z}.
@@
 In $\hat{B}-\hat{V}$, 
-the \replaced{extrinsic}{$g$-based} color variation is much larger than that of the \replaced{intrinsic}{$p$-based} and its effect per-supernova would be difficult to discern.
+the $g$-based color variation is much larger than that of the $p$-based and its effect per-supernova would be difficult to discern.
 
@@
    \includegraphics[width=4in]{../output_fix3_x1/ebv.pdf}
- %  \includegraphics[width=2.8in]{../output_fix3_x1/ebv_delta.pdf}
       \caption{Stack of the posteriors  (includes parameter uncertainty) of all supernovae of the  $E_{\gamma}({\hat{B}}-{\hat{V}})$ 
@@
 They find a significant $\beta_{\mathit{int}} = 2.2\pm 0.3$.
-\replaced{
-While we also claim a detection of an intrinsic color parameter, }
-{While we too claim the detection of a color parameter incompatible with dust,}
+While we too claim the detection of a color parameter incompatible with dust,
 the differences between our models make it
 difficult to determine whether the results are consistent.   Our results show effects on color that are not monotonic
-with wavelength.  \deleted{For example,} We find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
+with wavelength.  We find that the statistic that nominally best corresponds to  $\beta_{\mathit{int}}$
 to be
-\replaced{ $\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) = -2.4_{  -4.1}^{+   1.6}$}{$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) =-4.4_{  -6.4}^{+   2.4}$}, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.
+$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{V}}) =-4.4_{  -6.4}^{+   2.4}$, which appears to be inconsistent with  \citetalias{2017ApJ...842...93M}.  
 However a change of the color baseline gives a significantly different
@@
 The $c$ parameter is thus an  amalgamation of all input colors.
-We therefore make no conclusions on the consistency between our \replaced{intrinsic}{$\vec{\phi}$}-color properties
+We therefore make no conclusions on the consistency between our $\vec{\phi}$-color properties
 and those found by \citetalias{2017ApJ...842...93M}.
@@
 
-In this article we do not associate $p$ directly with Hubble residuals. 
-\deleted{However,
-we briefly  preview the discussion in \S\ref{Delta:sec} by mentioning that there is room for $p$-based magnitude corrections
-given the correlation between $\Delta$ and $\sigma_p\phi_{\hat{V}}p$ in Eq.~\ref{corr:eqn}.}
+In this article we do not associate $p$ directly with Hubble residuals. This is left for future work.
 
@@
 %-----
-\replaced{$0.15$}{$0.13$}
+$0.13$
 %-----
@@
 
-Using different arguments based on expected populations, \citetalias{2017ApJ...842...93M} \deleted{also} infer
+Using different arguments based on expected populations, \citetalias{2017ApJ...842...93M} infer
 separate intrinsic and dust-based color-magnitude relations based on an independent sample of 248 SNe~Ia
@@
 of those samples that are  consistent with our $\sigma_p \vec{\phi}$ would provide strong evidence 
-that we and  \citetalias{2017ApJ...842...93M}  are seeing the same \replaced{intrinsic color  and to confirm the
-observational signature of the intrinsic SN color relationship.}{color effect.}
+that we and  \citetalias{2017ApJ...842...93M}  are seeing the same color effect.
 
@@
 global host mass.  The search for a correlation between our parameter and local star formation rate is planned for future work.
-
-%We speculate that the new parameter is related to the fluorescence in SN~Ia described by  \citep{2006ApJ...649..939K}.
-%This downgrading of photons from blue to red is responsible for the secondary maximum in near-IR light curves.  There
-%are variations
-%in the properties of the secondary maximum \citep{1996AJ....112.2438H, 2005A&A...437..789N, 2010AJ....139..120F}.
-%\citet{2016MNRAS.463.4311S} find that the date of the secondary $J$-band maximum is correlated with peak
-%magnitude, although they do not find that it is independent of light-curve shape $x_1$.  We advocate
-%the continued study of
-%NIR light-curve shpae properties and their relation with colors, host properties, and  magnitudes.
 
@@
 
-\added{
 The existence of three color parameters  has important implications when SNe~Ia are used as distance indicators.
@@
 may partially mitigate such errors.
-}
 
@@
 ANI-0087344, and the University of California, San Diego.
+This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 759194 - USNAC
 
@@
 \end{table}
-\section{Degeneracy}
-Global parameters $\alpha$, $\beta$.  Per supernova parameters $\mu_i$, $x_i$, $c_i$, $M_i$.
-
-There are two arbitrary numbers $\epsilon_\alpha$ and $\epsilon_\beta$.
-
-The per supernova expected magnitude is
-
-\begin{align}
-m_i & = \mu_i + \langle M\rangle + \delta_{mi}  -\alpha x_i + \beta c_i\\
-& = \mu_i + \langle M\rangle + \epsilon_\alpha x_i - \epsilon_\beta   c_i+ \delta_{mi}  -(\alpha+ \epsilon_\alpha) x_i + (\beta+\epsilon_\beta) c_i\\
-& = \mu_i + \langle M\rangle' + \delta'_{mi}  -\alpha' x_i+ \beta' c_i .
-\end{align}
-where
-$\langle M\rangle' = \langle M\rangle + \epsilon_\alpha \langle x_i\rangle  - \epsilon_\beta   \langle c_i \rangle$ and
-$\delta'_{mi} =  \delta_{mi} +\epsilon_\alpha (x_i-\langle x_i \rangle) - \epsilon_\beta   (c_i-\langle c_i\rangle)   $, $\alpha' =\alpha+\epsilon_\alpha$, $\beta' =\beta+\epsilon_\beta$.
-There are two degrees of freedom between the unprimed
-and primed variables of Eqs.~1 and 2.
-
-Impose $\delta_{mi} \sim \mathcal{N}(0,\sigma_\delta)$.  If $x_i$ and $c_i$ have Normal distributions this condition does not break the degeneracy.
-A Baysian model (e.g.\ UNITY) that assumes Normal distributions for these parameters thus does not break the degeneracy.
-If  $x_i$ and $c_i$ do not have Normal distributions, the prior will drive $\epsilon$ to 0.
-
-SUGAR assumes normal distributions for its features.  It breaks its  degeneracy  by enforcing the analogue of $cov(\delta_{mi}, x_i)=0$ and $cov(\delta_{mi}, c_i)=0$.
-
-I do not impose the distribution from which $\Delta$ comes.
+%\section{Degeneracy}
+%Global parameters $\alpha$, $\beta$.  Per supernova parameters $\mu_i$, $x_i$, $c_i$, $M_i$.
+%
+%There are two arbitrary numbers $\epsilon_\alpha$ and $\epsilon_\beta$.
+%
+%The per supernova expected magnitude is
+%
+%\begin{align}
+%m_i & = \mu_i + \langle M\rangle + \delta_{mi}  -\alpha x_i + \beta c_i\\
+%& = \mu_i + \langle M\rangle + \epsilon_\alpha x_i - \epsilon_\beta   c_i+ \delta_{mi}  -(\alpha+ \epsilon_\alpha) x_i + (\beta+\epsilon_\beta) c_i\\
+%& = \mu_i + \langle M\rangle' + \delta'_{mi}  -\alpha' x_i+ \beta' c_i .
+%\end{align}
+%where
+%$\langle M\rangle' = \langle M\rangle + \epsilon_\alpha \langle x_i\rangle  - \epsilon_\beta   \langle c_i \rangle$ and
+%$\delta'_{mi} =  \delta_{mi} +\epsilon_\alpha (x_i-\langle x_i \rangle) - \epsilon_\beta   (c_i-\langle c_i\rangle)   $, $\alpha' =\alpha+\epsilon_\alpha$, $\beta' =\beta+\epsilon_\beta$.
+%There are two degrees of freedom between the unprimed
+%and primed variables of Eqs.~1 and 2.
+%
+%Impose $\delta_{mi} \sim \mathcal{N}(0,\sigma_\delta)$.  If $x_i$ and $c_i$ have Normal distributions this condition does not break the degeneracy.
+%A Baysian model (e.g.\ UNITY) that assumes Normal distributions for these parameters thus does not break the degeneracy.
+%If  $x_i$ and $c_i$ do not have Normal distributions, the prior will drive $\epsilon$ to 0.
+%
+%SUGAR assumes normal distributions for its features.  It breaks its  degeneracy  by enforcing the analogue of $cov(\delta_{mi}, x_i)=0$ and $cov(\delta_{mi}, c_i)=0$.
+%
+%I do not impose the distribution from which $\Delta$ comes.
 \bibliographystyle{apj}

### 2018-03-14 submit/fix.tex
candidate version for submission

@@
    \includegraphics[width=2.95in]{fix1plane0.pdf}
-   \includegraphics[width=2.95in]{../output_fix1/plane1.pdf}
+   \includegraphics[width=2.95in]{fix1plane1.pdf}
    \caption{
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3/sigev.pdf} 
+   \includegraphics[width=4in]{fix3sigev.pdf} 
             \caption{Model~II posterior  contours for $\sigma_p \vec{\phi}$. 
@@
    \centering
-   \includegraphics[width=2.6in]{../output_fix1/deltagamma0_med.pdf} 
-   \includegraphics[width=2.6in]{../output_fix1/deltagamma1_med.pdf} 
-   \includegraphics[width=2.6in]{../output_fix3/deltagamma0_med.pdf} 
-   \includegraphics[width=2.6in]{../output_fix3/deltagamma1_med.pdf} 
+   \includegraphics[width=2.6in]{fix1deltagamma0_med.pdf} 
+   \includegraphics[width=2.6in]{fix1deltagamma1_med.pdf} 
+   \includegraphics[width=2.6in]{fix3deltagamma0_med.pdf} 
+   \includegraphics[width=2.6in]{fix3deltagamma1_med.pdf} 
    \caption{
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3_x1/cpull.pdf} 
+   \includegraphics[width=4in]{cpull.pdf} 
                \caption{
@@
    \centering
-   \includegraphics[width=2.95in]{../output_fix3_x1/plane0.pdf}
-   \includegraphics[width=2.95in]{../output_fix3_x1/plane1.pdf}
+   \includegraphics[width=2.95in]{plane0.pdf}
+   \includegraphics[width=2.95in]{plane1.pdf}
    \caption{
@@
    \centering
-      \includegraphics[width=4in]{../output_fix3_x1/phiratio.pdf}
+      \includegraphics[width=4in]{phiratio.pdf}
    \caption{Model~III median values  and corresponding 68\% intervals for $\phi_X/\phi_{\hat{V}}-1$ in the 5 bands.
@@
    \centering
-   \includegraphics[width=5.2in]{../output_fix3_x1/perobject_corner.pdf} 
+   \includegraphics[width=5.2in]{perobject_corner.pdf} 
    \caption{
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3_x1/avebv_synth.pdf}
+   \includegraphics[width=4in]{avebv_synth.pdf}
       \caption{
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3_x1/ebv.pdf}
+   \includegraphics[width=4in]{ebv.pdf}
       \caption{Stack of the posteriors  (includes parameter uncertainty) of all supernovae of the  $E_{\gamma}({\hat{B}}-{\hat{V}})$ 
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3_x1/childress.pdf} 
+   \includegraphics[width=4in]{childress.pdf} 
    \caption{Parameter $\sigma_p\phi_{\hat{V}}p$  versus host galaxy mass. Overplotted are the mean and 1$\sigma$ uncertainty on the mean for supernovae with hosts
@@
    \centering
-   \includegraphics[width=4in]{../output_fix3_x1/deltaDelta_hist.pdf} 
+   \includegraphics[width=4in]{deltaDelta_hist.pdf} 
    \caption{
@@
 is unaccounted for.
+
+Just as supernova spectral and light curve features are associated with distinct color variations, the latent parameter $p$
+identified through color variation may be associated with a spectral and/or light curve feature not included
+in our analysis.  It
+is of intererst to look for tracers other than color to account for this supernova diversity.
+We leave to future work the search for correlations between $p$ and other
+observable features accessed by SNfactory data.
 

### 2018-03-15 submit/fix.tex
submitted to ApJ

@@
-\documentclass[trackchanges]{aastex61}   	% use "amsart" instead of "article" for AMSLaTeX format
+\documentclass[trackchanges]{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
@@
 
- \author{    M.~Rigault} 
+ \author[0000-0002-8121-2560]{    M.~Rigault} 
 \affiliation{ Clermont Universit\'e, Universit\'e Blaise Pascal, CNRS/IN2P3, Laboratoire de Physique Corpusculaire,
@@
 
-\keywords{supernovae: general; supernovae}
+\keywords{supernovae: general; cosmology: distance scale; methods: data analysis}
 
@@
 give photometric and spectroscopic statistics described above.
-%\textcolor{red}{FOR INTERNAL REFERENCE: The CABALLO2 validation and training sets are used with SN2012cu, SNF20061108-001, SNF20080905-005, SNNGC7589 excised
-%based on data problems identified by Manu.}
 The 
@@
 in \citet{2017Chotard}.
-%
-%
-%Table~\ref{data:tab} \textcolor{red}{[TABLE CAN GO IF THERE IS A NICO PAPER]}.
-%The peak magnitude uncertainties do have covariance, which is accounted
-%for in the analysis; only the standard deviation is included in the table.
-%
-%\startlongtable
-%\begin{deluxetable}{crrrrrrrr}
-%\tabletypesize{\tiny}
-%\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data
-%\label{data:tab}}
-%\tablehead{
-%\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$}
-%}
-%\startdata
-%SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\
-%PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ \\
-%SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ \\
-%PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ \\
-%SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ \\
-%PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ \\
-%PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-%PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
-%SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ \\
-%PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ \\
-%PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ \\
-%SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ \\
-%SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ \\
-%SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ \\
-%SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ \\
-%PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ \\
-%PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\
-%SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ \\
-%PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ \\
-%SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ \\
-%PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ \\
-%PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ \\
-%SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ \\
-%SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ \\
-%PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ \\
-%PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ \\
-%SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ \\
-%LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ \\
-%SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-%SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ \\
-%PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ \\
-%PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ \\
-%SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ \\
-%SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ \\
-%LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ \\
-%PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ \\
-%PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ \\
-%PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\
-%SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ \\
-%PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ \\
-%SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ \\
-%PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\
-%PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ \\
-%SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ \\
-%SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ \\
-%SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ \\
-%PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ \\
-%PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ \\
-%CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ \\
-%SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ \\
-%SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ \\
-%SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ \\
-%PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ \\
-%SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ \\
-%SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ \\
-%SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ \\
-%PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ \\
-%PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ \\
-%SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ \\
-%SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ \\
-%SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ \\
-%SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ \\
-%SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ \\
-%SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ \\
-%SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ \\
-%SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ \\
-%SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ \\
-%SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ \\
-%PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ \\
-%PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ \\
-%SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ \\
-%SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
-%SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\
-%CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ \\
-%SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\
-%SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ \\
-%PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ \\
-%SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ \\
-%SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ \\
-%SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ \\
-%SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ \\
-%SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ \\
-%SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ \\
-%SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ \\
-%CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ \\
-%SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ \\
-%SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-%SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ \\
-%SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ \\
-%SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ \\
-%PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ \\
-%SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ \\
-%PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ \\
-%SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ \\
-%SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ \\
-%SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ \\
-%SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-%CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ \\
-%SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ \\
-%SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ \\
-%SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ \\
-%SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ \\
-%SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ \\
-%SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ \\
-%SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ \\
-%SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ \\
-%SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ \\
-%SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ \\
-%PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ \\
-%PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ \\
-%SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\
-%SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ \\
-%SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ \\
-%SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ \\
-%SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ \\
-%SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ \\
-%SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ \\
-%SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ \\
-%SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ \\
-%SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ \\
-%SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\
-%SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ \\
-%SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ \\
-%PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ \\
-%SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ \\
-%SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ \\
-%SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ \\
-%SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ \\
-%SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ \\
-%SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
-%SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ \\
-%SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ \\
-%SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ \\
-%PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ \\
-%SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ \\
-%PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ \\
-%SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ \\
-%PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ \\
-%PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ \\
-%SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ \\
-%SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ \\
-%SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ \\
-%SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ \\
-%SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ \\
-%SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ \\
-%LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ \\
-%LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ \\
-%SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ \\
-%SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ \\
-%PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ \\
-%SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ \\
-%SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ \\
-%SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ \\
-%SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ \\
-%SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ \\
-%SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ \\
-%SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ \\
-%SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ \\
-%PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ \\
-%SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ \\
-%SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ \\
-%SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ \\
-%PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ \\
-%SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ \\
-%PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ \\
-%PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ \\
-%SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ \\
-%SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ \\
-%SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ \\
-%SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ \\
-%SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ \\
-%SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ \\
-%\enddata
-%\end{deluxetable}
 
@@
 \end{equation}
-%The $\vec{\gamma}$'s derived from our analysis are almost entirely captured by the first term.
 We find
@@
 
-%
-%We now consider the direction of $\vec{\gamma}^1$. 
-%Different supernovae are expected to encounter dust with different $R^F$;
-%having  associated $\vec{\gamma}^0$ with
-%the extinction from a single effective
-%$\langle \langle R^F_{\mathit{eff}}\rangle\rangle$, $\vec{\gamma}^1$ is associated with perturbations
-%away from that effective value.
-%Let us introduce a new parameter for each supernova, $\delta R$, such that 
-%$A^F =\langle R^F_{\mathit{eff}}\rangle(1-  \delta R) E^F(B-V)$.
-%Variations in the value of  $\delta R$, with the prior of the non-correlation between 
-%the coefficients in Eqn.~\ref{newdust:eqn},
-%lead 
-%to 
-%\begin{equation}
-%\kappa_2 =\langle R^F_{\mathit{eff}}\rangle \left(1- \frac{\mbox{Var}(\delta R \times E^F(B-V))}{\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))}\right).
-%\end{equation}
-%From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R \times E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R \times E^F(B-V), E^F(B-V))$.
-This result indicates that there is a small but significant covariance between  extinction contributions due to
-%fractional deviations from an effective $R^F$ and
-%the color-excess parameter $E^F(B-V)$.
-%
-%
-%For $\vec{\gamma}^1$ we find  $\kappa^{-1}_2=0.03^{+0.04}_{-0.04}$, meaning that this vector's direction is consistent with being parallel to $a_X$
-%(also seen visually in Figure~\ref{plane:fig}.)
-%That is,   $\vec{\gamma}^1$  captures magnitude variations that occur given fixed $E^F(B-V)$.
-
 \subsection{Model~I Summary}
@@
    \centering
-   \includegraphics[width=5.2in]{../output_fix3_x1/coeff0.pdf} 
+   \includegraphics[width=5.2in]{coeff0.pdf} 
             \caption{Model~III posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{U}}$ band.
@@
    \centering
-   \includegraphics[width=5.2in]{../output_fix3_x1/coeff1.pdf} 
+   \includegraphics[width=5.2in]{coeff1.pdf} 
             \caption{Model~III posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{B}}$ band.
@@
    \centering
-   \includegraphics[width=5.2in]{../output_fix3_x1/coeff2.pdf} 
+   \includegraphics[width=5.2in]{coeff2.pdf} 
             \caption{Model~III posterior contours for $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{V}}$ band.
@@
    \centering
-      \includegraphics[width=5.2in]{../output_fix3_x1/coeff3.pdf} 
+      \includegraphics[width=5.2in]{coeff3.pdf} 
             \caption{Model~III posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,  $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{R}}$ band.
@@
    \centering
-         \includegraphics[width=5.2in]{../output_fix3_x1/coeff4.pdf} 
+         \includegraphics[width=5.2in]{coeff4.pdf} 
             \caption{Model~III posterior contours for  $\vec{c}$, $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$, $\vec{\gamma}^0$, $\vec{\gamma}^1$, and $\sigma_p \vec{\phi}$ in the ${\hat{I}}$ band.
@@
 
-%The redistribution of UV  photons into redder photons
-%is already associated with SNe~Ia around 35 days after maximum, when flourescence from singly-ionized iron/cobalt gas in the
-%ejecta gives rise to the NIR secondary light-curve peak
-%\citep{2006ApJ...649..939K}.   We speculate that our $\sigma_p \vec{\phi}$
-%is associated with a redistribution of UV light, but at peak brightness when the NIR emission is dominated by
-%the optically thick core and is not  significantly enhanced by fluorescence.
-
-% points out that at a temperature of 7000~K, the iron/cobalt gas in the ejecta transition
-%from doubly and singly ionized states, making the gas fluorescent and efficient in redistributing energy from the UV/blue to redder
-%wavelengths.
-%We speculate that varying $^{56}$Ni mixing and/or mass affects the rise-time to peak $B$ brightness and hence the optical depth
-%of the reionization front with respect to the core of the ejecta at peak, yielding the wavelength-dependent color behavior
-%detected in this analysis.
-
 \begin{figure}[htbp] %  figure placement: here, top, bottom, or page
@@
    \centering
-   \includegraphics[width=2.8in]{../output_fix3_x1/deltagamma0_med.pdf}
-   \includegraphics[width=2.8in]{../output_fix3_x1/deltagamma1_med.pdf}
+   \includegraphics[width=2.8in]{deltagamma0_med.pdf}
+   \includegraphics[width=2.8in]{deltagamma1_med.pdf}
       \caption{
@@
 Detection of intrinsic color has been previously reported by \citetalias{2017ApJ...842...93M}.
-For data, they use the outputs of SALT2 fits: the $c$ color parameter ;
-%associated with but not exactly $B-V$
+For data, they use the outputs of SALT2 fits: the $c$ color parameter;
 the
 supernova absolute magnitude $M$.
-% associated with but not exactly $B$.
 In the \citetalias{2017ApJ...842...93M}
@@
 However a change of the color baseline gives a significantly different
-$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =4.3_{  -1.4}^{+   3.8}$.  Our results indicate that  $\beta_{\mathit{int}}$ %new
+$\phi_{\hat{B}}/(\phi_{\hat{B}}-\phi_{\hat{R}}) =4.3_{  -1.4}^{+   3.8}$.  Our results indicate that  $\beta_{\mathit{int}}$
 is sensitive to the color that $c$ corresponds to.  Although SALT2 $c$ is calibrated to correspond with $B-V$, it is
@@
 Low- and high-mass galaxies, divided by $\log{(M/M_\sun)}=10$, have high probability of hosting supernovae with different $p$ distributions, as
-the Kolmogorov-Smirnov test gives a two-tailed $p$-value of $  0.016 _ {     0.011 } ^{     0.044 }$. %fix
+the Kolmogorov-Smirnov test gives a two-tailed $p$-value of $  0.016 _ {     0.011 } ^{     0.044 }$.
 The median and median uncertainties of the two subsamples are
 %---
-$\langle \sigma_p\phi_{\hat{V}}(p-p|_0) \rangle=  0.041 \pm {     0.007 }$ mag, %new
+$\langle \sigma_p\phi_{\hat{V}}(p-p|_0) \rangle=  0.041 \pm {     0.007 }$ mag,
 $\langle \sigma_p\phi_{\hat{V}}(p-p|_0)  \rangle=0.065 \pm {     0.007 }$ mag
@@
 in our analysis.  It
-is of intererst to look for tracers other than color to account for this supernova diversity.
+is of interest to look for tracers other than color to account for this supernova diversity.
 We leave to future work the search for correlations between $p$ and other
@@
 \end{table}
-%\section{Degeneracy}
-%Global parameters $\alpha$, $\beta$.  Per supernova parameters $\mu_i$, $x_i$, $c_i$, $M_i$.
-%
-%There are two arbitrary numbers $\epsilon_\alpha$ and $\epsilon_\beta$.
-%
-%The per supernova expected magnitude is
-%
-%\begin{align}
-%m_i & = \mu_i + \langle M\rangle + \delta_{mi}  -\alpha x_i + \beta c_i\\
-%& = \mu_i + \langle M\rangle + \epsilon_\alpha x_i - \epsilon_\beta   c_i+ \delta_{mi}  -(\alpha+ \epsilon_\alpha) x_i + (\beta+\epsilon_\beta) c_i\\
-%& = \mu_i + \langle M\rangle' + \delta'_{mi}  -\alpha' x_i+ \beta' c_i .
-%\end{align}
-%where
-%$\langle M\rangle' = \langle M\rangle + \epsilon_\alpha \langle x_i\rangle  - \epsilon_\beta   \langle c_i \rangle$ and
-%$\delta'_{mi} =  \delta_{mi} +\epsilon_\alpha (x_i-\langle x_i \rangle) - \epsilon_\beta   (c_i-\langle c_i\rangle)   $, $\alpha' =\alpha+\epsilon_\alpha$, $\beta' =\beta+\epsilon_\beta$.
-%There are two degrees of freedom between the unprimed
-%and primed variables of Eqs.~1 and 2.
-%
-%Impose $\delta_{mi} \sim \mathcal{N}(0,\sigma_\delta)$.  If $x_i$ and $c_i$ have Normal distributions this condition does not break the degeneracy.
-%A Baysian model (e.g.\ UNITY) that assumes Normal distributions for these parameters thus does not break the degeneracy.
-%If  $x_i$ and $c_i$ do not have Normal distributions, the prior will drive $\epsilon$ to 0.
-%
-%SUGAR assumes normal distributions for its features.  It breaks its  degeneracy  by enforcing the analogue of $cov(\delta_{mi}, x_i)=0$ and $cov(\delta_{mi}, c_i)=0$.
-%
-%I do not impose the distribution from which $\Delta$ comes.
-\bibliographystyle{apj}
-\bibliography{alex}
-
+
+%\bibliographystyle{aasjournal}
+%\bibliography{alex}
+\input{fix.bbl}
 \end{document}

### 2018-03-15 sivel.py

@@ -16,6 +16,8 @@ def sivel(data):
    zcmb = []
    zerr= []
    EWCAIIHK = []
+   EWFe4800 = []
+   EWFe4800_err = []
    mwebv=[]
    for sn in data['snlist']:
       if sn in dic_meta.keys() and sn in dic_phreno.keys():
@@ -23,8 +25,10 @@ def sivel(data):
 
          vSiII_6355_lbd=0.
          vSiII_6355_lbd_err=0.
-         dum1=0
-         dum1_err=0
+         dum1=0.
+         dum1_err=0.
+         dum2=0.
+         dum2_err=0.
          counter  = 0
          for sp in dic_phreno[sn]["spectra"]:
             if sp in meta['spectra'].keys() and  numpy.abs(meta['spectra'][sp]['salt2.phase']) < 2.5 and numpy.isfinite(dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]):
@@ -32,15 +36,22 @@ def sivel(data):
                vSiII_6355_lbd_err += 1/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
                dum1 += dic_phreno[sn]["spectra"][sp]["phrenology.EWCaIIHK"]/dic_phreno[sn]['spectra'][sp]["phrenology.EWCaIIHK.err"]**2
                dum1_err += 1/dic_phreno[sn]['spectra'][sp]["phrenology.EWCaIIHK.err"]**2
+               dum2 += dic_phreno[sn]["spectra"][sp]["phrenology.EWFe4800"]/dic_phreno[sn]['spectra'][sp]["phrenology.EWFe4800.err"]**2
+               dum2_err += 1/dic_phreno[sn]['spectra'][sp]["phrenology.EWFe4800.err"]**2
                counter +=1
          if counter !=0:
             sivel.append(vSiII_6355_lbd / vSiII_6355_lbd_err)
             sivel_err.append(1./numpy.sqrt(vSiII_6355_lbd_err))
             EWCAIIHK.append(dum1/dum1_err)
+            EWFe4800.append(dum2/dum2_err)
+            EWFe4800_err.append(1/numpy.sqrt(dum2_err))
+
          else:
             sivel.append(float('nan'))
             sivel_err.append(float('nan'))
             EWCAIIHK.append(float('nan'))
[…]

### 2018-03-15 tablef3_x1.py

@@ -191,7 +191,8 @@ pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)
 pkl_file.close()
 
-sivel, sivel_err, _, _, _,_,_ = sivel.sivel(data)
+sivel, sivel_err, _,_,_,_,_,EWFe4800 = sivel.sivel(data)
+
 
 use = numpy.isfinite(sivel)
 
@@ -204,6 +205,7 @@ mag_cov = data['cov'][:,2:,2:]
 
 sivel=sivel[use]
 sivel_err = sivel_err[use]
+EWFe4800=EWFe4800[use]
 EW_obs=EW_obs[use]
 mag_obs=mag_obs[use]
 EW_cov= EW_cov[use]
@@ -213,6 +215,14 @@ shit = []
 for m in mag_cov:
     shit.append(numpy.sqrt(numpy.diag(m)))
 print numpy.median(shit)
+
+shit=[]
+for i in xrange(fit['mag_int_raw'].shape[0]):
+    shit.append(numpy.corrcoef(numpy.array([EWFe4800, fit['mag_int_raw'][i,:]]))[0,1])
+(y,ymin,ymax) = numpy.percentile(shit,(50,50-34,50+34),axis=0)
+print y, y-ymin,ymax-y
+
+wefwe
 
 trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1]]
 trans = numpy.array(trans)
@@ -225,7 +235,6 @@ for i in xrange(nsne):
 print numpy.max(shit)
 print numpy.median(shit)
 
-wefwe
 # ebvdelta  = (fit['rho1'][:,1]-fit['rho1'][:,2])[:,None] * fit['R']
 # ebvgamma  = (fit['gamma'][:,1]-fit['gamma'][:,2])[:,None] * fit['k']
 

### 2018-05-08 submit/response.txt
observable parameters and Pantheon nearby

Comment 1:

While much of the narrative within the paper is compelling, it is currently unverifiable. Despite the SNFactory project starting 2 decades ago, that most of the data for this paper were taken >1 decade ago, and the data being used in many publications, the spectrophotometric series critical for this analysis (except for perhaps 3 SNe: SNe 2006D, 2011fe, 2012cg) have never been published. there isn't even a table listing the SNe used.

It is impossible to verify any claims without making these data public, and
I cannot accept this paper until the data are released publicly.

Response 1:

We have added two tables to the article.

Comment 2:

Beyond the basic critical idea of providing sufficient data to verify the results, a fundamental aspect of scientific inquiry, the authors do not satisfactory describe their sample. They simply state that the sample of 172 SNe have been processed and have sufficient data to provide some parameters. Does this mean that peculiar SNe Ia are included? Was it harder to reduce the data for some SNe than others (highly embedded SNe)? Presumably there are different selection effects, but none are listed. Without this basic information, it is impossible to fully evaluate this work.

The authors do not discuss if their sample is representative of the broader SN Ia sample or the cosmology samples. In fact, the demographics and parameters are not discussed at all, deferring to Chotard et al. Before any referee can properly review this paper (and in addition to the data being released publicly), Chotard et al. must be submitted to a journal and provided to the referee of this paper.

Response 2:

Comment 3:

1. It would be useful to show the covariance matrices for all models and discuss how necessary each measurement is. For instance, the Si EW and x1 are highly correlated, and perhaps only one measurement is required.

Response 3:

Comment 4:

2. Although there is some discussion about the host mass step, it seems like the authors should have a model with this parameter. That is, the mass step is already used for cosmological analyses and it seems prudent to determine if the new parameter is truly a new color parameter or if it is simply the mass step repackaged.

3. Section 5.2.9 says that the correlation between Delta and the other parameters is shown in Eq. 20. But Delta isn't included there.

### 2018-05-08 submit/fix.tex
fix typo in reference
observable parameters and Pantheon nearby

@@
 
-\author{     Y.~Copin}
+\author[0000-0002-5317-7518]{     Y.~Copin}
 \affiliation{    Universit\'e de Lyon, F-69622, Lyon, France ; Universit\'e de Lyon 1, Villeurbanne ; 
@@
 
-\author{     E.~Gangler}  
+\author[0000-0001-6728-1423]{     E.~Gangler}  
 \affiliation{    Clermont Universit\'e, Universit\'e Blaise Pascal, CNRS/IN2P3, Laboratoire de Physique Corpusculaire,
@@
 the canonical value for diffuse Milky Way dust.
-They also confirm the \citet{2006MNRAS.369.1880E,, 2011ApJ...731..120M} finding that low $R_V$ is associated with high-extinction supernovae.
+They also confirm the \citet{2006MNRAS.369.1880E, 2011ApJ...731..120M} finding that low $R_V$ is associated with high-extinction supernovae.
 In contrast, \citet{2011A&A...529L...4C} argue that after accounting for the diversity of spectral features,
@@
 are presented
-in \citet{2017Chotard}.
+in \replaced{\citet{2017Chotard}}{Table~\ref{data:tab}.   
+For the subset supernovae for whom it is available, we use the host-galaxy mass given in \citep{2013ApJ...770..108C}.
+
+\startlongtable
+\begin{deluxetable}{crrrrrrrrr}
+\tabletypesize{\tiny}
+\tablecaption{Supernova Spectral-Feature and Peak-Magnitude Data
+\label{data:tab}}
+\tablehead{
+\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} & \colhead{$x_1$}
+}
+\startdata
+SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.85 \pm   0.34$\\
+PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ & $  0.18 \pm   0.17$\\
+SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ & $ -1.78 \pm   0.18$\\
+PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.72 \pm   0.13$\\
+SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ & $  0.27 \pm   0.14$\\
+PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.74 \pm   0.24$\\
+PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -0.07 \pm   0.17$\\
+PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.69 \pm   0.19$\\
+SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ & $ -1.56 \pm   0.13$\\
+PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ & $  0.03 \pm   0.21$\\
+PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.00 \pm   0.34$\\
+SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ & $ -1.28 \pm   0.16$\\
+SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.15 \pm   0.16$\\
+SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.10 \pm   0.11$\\
+SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ & $ -2.45 \pm   0.28$\\
+PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ & $  0.68 \pm   0.16$\\
+PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ & $ -0.62 \pm   0.13$\\
+SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ & $ -1.57 \pm   0.11$\\
+PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.74 \pm   0.15$\\
+SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ & $ -2.12 \pm   0.17$\\
+PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ & $  0.37 \pm   0.13$\\
+PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ & $  1.21 \pm   0.20$\\
+SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ & $  0.37 \pm   0.12$\\
+SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ & $  0.20 \pm   0.14$\\
+PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ & $  1.34 \pm   0.17$\\
+PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ & $ -1.09 \pm   0.16$\\
+SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ & $  0.17 \pm   0.17$\\
+LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ & $  0.05 \pm   0.15$\\
+SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.70 \pm   0.19$\\
+SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.08 \pm   0.16$\\
+PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.63 \pm   0.16$\\
+PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ & $ -0.68 \pm   0.10$\\
+SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ & $ -0.03 \pm   0.10$\\
+SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ & $  0.01 \pm   0.13$\\
+LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ & $  1.07 \pm   0.19$\\
+PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ & $  1.04 \pm   0.20$\\
+PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.68 \pm   0.27$\\
+PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ & $ -1.72 \pm   0.29$\\
+SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.10 \pm   0.12$\\
+PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.83 \pm   0.16$\\
+SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ & $ -1.24 \pm   0.26$\\
+PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ & $  0.60 \pm   0.15$\\
+PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.43 \pm   0.14$\\
+SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ & $ -1.67 \pm   0.20$\\
+SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ & $  1.71 \pm   0.69$\\
+SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.70 \pm   0.14$\\
+PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ & $  0.65 \pm   0.16$\\
+PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ & $ -0.28 \pm   0.17$\\
+CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ & $  0.92 \pm   0.17$\\
+SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ & $ -1.39 \pm   0.19$\\
+SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.17 \pm   0.13$\\
+SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ & $ -0.54 \pm   0.13$\\
+PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ & $  1.39 \pm   0.18$\\
+SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ & $  1.36 \pm   0.37$\\
+SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ & $ -1.83 \pm   0.18$\\
+SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ & $ -0.43 \pm   0.10$\\
+PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.11 \pm   0.12$\\
+PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ & $ -1.59 \pm   0.22$\\
+SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ & $ -0.13 \pm   0.11$\\
+SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ & $  0.84 \pm   0.18$\\
+SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ & $ -2.26 \pm   0.40$\\
+SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ & $  0.01 \pm   0.15$\\
+SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ & $ -1.10 \pm   0.13$\\
+SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ & $  0.81 \pm   0.19$\\
+SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.27 \pm   0.21$\\
+SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ & $ -2.09 \pm   0.25$\\
+SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ & $  0.74 \pm   0.29$\\
+SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ & $ -0.77 \pm   0.18$\\
+PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ & $  0.53 \pm   0.16$\\
+PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ & $  0.16 \pm   0.13$\\
+SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ & $  1.50 \pm   0.30$\\
+SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ & $  1.24 \pm   0.26$\\
+SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ & $ -0.31 \pm   0.17$\\
+CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ & $ -0.00 \pm   0.24$\\
+SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ & $ -1.04 \pm   0.16$\\
+SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ & $ -2.08 \pm   0.18$\\
+PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.06 \pm   0.19$\\
+SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ & $ -0.68 \pm   0.18$\\
+SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ & $  0.71 \pm   0.21$\\
+SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ & $  1.04 \pm   0.23$\\
+SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ & $  0.43 \pm   0.20$\\
+SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ & $  1.17 \pm   0.34$\\
+SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ & $ -0.43 \pm   0.16$\\
+SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ & $ -1.27 \pm   0.18$\\
+CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ & $  0.76 \pm   0.19$\\
+SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ & $  0.12 \pm   0.16$\\
+SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  0.06 \pm   0.17$\\
+SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ & $  0.52 \pm   0.18$\\
+SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ & $  0.70 \pm   0.19$\\
+SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.17 \pm   0.16$\\
+PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ & $ -0.33 \pm   0.12$\\
+SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ & $  0.98 \pm   0.18$\\
+PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ & $  0.50 \pm   0.11$\\
+SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ & $ -1.73 \pm   0.17$\\
+SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ & $  0.62 \pm   0.21$\\
+SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  2.14 \pm   0.42$\\
+SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $  0.24 \pm   0.20$\\
+CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ & $ -0.27 \pm   0.17$\\
+SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.09$\\
+SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ & $  0.35 \pm   0.19$\\
+SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ & $  0.60 \pm   0.14$\\
+SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ & $  0.27 \pm   0.27$\\
+SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ & $  0.96 \pm   0.10$\\
+SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ & $ -0.92 \pm   0.19$\\
+SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.69 \pm   0.15$\\
+SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ & $ -0.25 \pm   0.15$\\
+SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.17 \pm   0.32$\\
+SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ & $  0.88 \pm   0.18$\\
+PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ & $ -1.14 \pm   0.26$\\
+PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ & $ -1.17 \pm   0.13$\\
+SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ & $  0.18 \pm   0.13$\\
+SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.87 \pm   0.11$\\
+SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ & $  0.57 \pm   0.34$\\
+SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ & $ -1.05 \pm   0.12$\\
+SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ & $ -0.72 \pm   0.10$\\
+SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ & $  0.31 \pm   0.11$\\
+SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.48 \pm   0.18$\\
+SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ & $ -1.89 \pm   0.26$\\
+SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ & $ -0.57 \pm   0.13$\\
+SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ & $ -1.96 \pm   0.19$\\
+SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ & $  1.72 \pm   0.44$\\
+SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.01 \pm   0.12$\\
+SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ & $  0.27 \pm   0.12$\\
+PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.34 \pm   0.12$\\
+SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ & $ -0.29 \pm   0.13$\\
+SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ & $  0.68 \pm   0.17$\\
+SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.00 \pm   0.21$\\
+SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ & $ -0.11 \pm   0.17$\\
+SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ & $  0.07 \pm   0.15$\\
+SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ & $  0.69 \pm   0.62$\\
+SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ & $  0.12 \pm   0.18$\\
+SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ & $ -0.49 \pm   0.18$\\
+SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ & $ -2.32 \pm   0.54$\\
+PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ & $ -0.35 \pm   0.11$\\
+SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ & $ -1.88 \pm   0.34$\\
+PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ & $ -0.02 \pm   0.12$\\
+SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ & $  1.85 \pm   0.59$\\
+PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ & $ -1.30 \pm   0.12$\\
+PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.87 \pm   0.18$\\
+SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ & $ -1.52 \pm   0.14$\\
+SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ & $  0.22 \pm   0.26$\\
+SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ & $  0.34 \pm   0.29$\\
+SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ & $  0.14 \pm   0.25$\\
+SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ & $  0.20 \pm   0.24$\\
+SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.87 \pm   0.31$\\
+LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ & $  1.12 \pm   0.14$\\
+LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.21$\\
+SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ & $ -1.22 \pm   0.26$\\
+SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ & $  0.35 \pm   0.12$\\
+PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.21 \pm   0.37$\\
+SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $ -0.10 \pm   0.17$\\
+SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ & $ -0.53 \pm   0.18$\\
+SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ & $  0.41 \pm   0.14$\\
+SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ & $  0.29 \pm   0.17$\\
+SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ & $  0.64 \pm   0.16$\\
+SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.37 \pm   0.14$\\
+SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ & $  0.56 \pm   0.23$\\
+SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.97 \pm   0.21$\\
+PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ & $ -0.48 \pm   0.12$\\
+SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ & $ -1.82 \pm   0.25$\\
+SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.85 \pm   0.23$\\
+SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ & $ -1.37 \pm   0.11$\\
+PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ & $  0.18 \pm   0.15$\\
+SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ & $  1.02 \pm   0.13$\\
+PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ & $ -0.35 \pm   0.11$\\
+PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -1.98 \pm   0.20$\\
+SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ & $  0.25 \pm   0.18$\\
+SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.90 \pm   0.26$\\
+SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.89 \pm   0.25$\\
+SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ & $  0.03 \pm   0.21$\\
+SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ & $  0.43 \pm   0.18$\\
+SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ & $  0.42 \pm   0.18$\\
+\enddata
+\end{deluxetable}
+}
 
@@
 Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$,
-$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $A_{p,V} =  \sigma_p\phi_{\hat{I}}p$.
+$E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $A_{p,V} =  \sigma_p\phi_{\hat{V}}p$.
 (The  three latent parameters are cast as physically meaning
 quantities by multiplying them by select cofactors.)
+\added{The 68\% credible intervals for these parameters for all supernovae are given in Table~\ref{results:tab}.
+\startlongtable
+\begin{deluxetable}{crrrrrrrrr}
+\tabletypesize{\tiny}
+\tablecaption{Supernova Parameter Credible Intervals
+\label{results:tab}}
+\tablehead{
+\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$x_1$} & \colhead{$\Delta$}
+& \colhead{$E_{\gamma^0}({\hat{B}}-{\hat{V}})$} & \colhead{$E_{\gamma^1}({\hat{B}}-{\hat{V}})$} & \colhead{$A_{p,V} $}
+}
+\startdata
+SN2007bd & $113.3^{+5.4}_{-5.4}$ & $ 17.8^{+0.7}_{-0.7}$ & $ 6101^{+  3}_{-  3}$ & $ -1.02^{+  0.18}_{-  0.18}$ & $-0.071^{+0.027}_{-0.027}$  & $-0.050^{+0.011}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
+PTF10zdk & $149.7^{+1.2}_{-1.2}$ & $ 14.9^{+0.6}_{-0.6}$ & $ 6150^{+  3}_{-  3}$ & $  0.37^{+  0.14}_{-  0.13}$ & $-0.029^{+0.026}_{-0.025}$  & $0.062^{+0.012}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
+SNF20080815-017 & $ 90.9^{+14.3}_{-14.5}$ & $ 19.6^{+2.4}_{-2.3}$ & $ 6131^{+  6}_{-  6}$ & $ -1.96^{+  0.16}_{-  0.16}$ & $0.041^{+0.070}_{-0.064}$  & $-0.008^{+0.025}_{-0.026}$ & $-0.011^{+0.028}_{-0.022}$ & $-0.011^{+0.028}_{-0.022}$\\
+PTF09dnl & $130.0^{+0.8}_{-0.9}$ & $  9.1^{+0.7}_{-0.7}$ & $ 6092^{+  3}_{-  3}$ & $  0.59^{+  0.10}_{-  0.10}$ & $-0.061^{+0.021}_{-0.021}$  & $0.014^{+0.009}_{-0.009}$ & $0.000^{+0.011}_{-0.011}$ & $0.000^{+0.011}_{-0.011}$\\
+SN2010ex & $114.5^{+0.9}_{-0.9}$ & $  8.4^{+0.4}_{-0.4}$ & $ 6129^{+  6}_{-  6}$ & $  0.17^{+  0.12}_{-  0.11}$ & $0.266^{+0.026}_{-0.026}$  & $-0.042^{+0.008}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+PTF09dnp & $ 66.9^{+4.5}_{-4.6}$ & $ 17.5^{+0.7}_{-0.7}$ & $ 6098^{+  5}_{-  4}$ & $ -0.53^{+  0.17}_{-  0.17}$ & $-0.249^{+0.026}_{-0.026}$  & $-0.008^{+0.020}_{-0.021}$ & $-0.044^{+0.006}_{-0.006}$ & $-0.044^{+0.006}_{-0.006}$\\
+PTF11bnx & $150.7^{+3.0}_{-2.9}$ & $ 14.6^{+1.0}_{-1.0}$ & $ 6143^{+  5}_{-  5}$ & $  0.07^{+  0.14}_{-  0.14}$ & $0.043^{+0.029}_{-0.029}$  & $0.049^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
+PTF12jqh & $151.8^{+1.4}_{-1.5}$ & $  7.9^{+0.6}_{-0.7}$ & $ 6118^{+ 10}_{- 10}$ & $  0.73^{+  0.14}_{-  0.14}$ & $0.069^{+0.028}_{-0.028}$  & $-0.056^{+0.010}_{-0.010}$ & $0.009^{+0.014}_{-0.015}$ & $0.009^{+0.014}_{-0.015}$\\
+SNF20080802-006 & $108.7^{+5.6}_{-5.8}$ & $ 19.1^{+1.6}_{-1.6}$ & $ 6122^{+  5}_{-  5}$ & $ -1.61^{+  0.12}_{-  0.12}$ & $-0.042^{+0.059}_{-0.055}$  & $-0.001^{+0.016}_{-0.016}$ & $0.033^{+0.020}_{-0.020}$ & $0.033^{+0.020}_{-0.020}$\\
+PTF10xyt & $120.2^{+6.3}_{-6.4}$ & $ 21.5^{+3.2}_{-3.1}$ & $ 6102^{+  4}_{-  4}$ & $  0.18^{+  0.20}_{-  0.20}$ & $0.241^{+0.049}_{-0.049}$  & $0.070^{+0.026}_{-0.028}$ & $0.014^{+0.029}_{-0.027}$ & $0.014^{+0.029}_{-0.027}$\\
+PTF11qmo & $101.7^{+1.1}_{-1.1}$ & $  7.8^{+0.7}_{-0.7}$ & $ 6151^{+  7}_{-  8}$ & $  0.41^{+  0.18}_{-  0.18}$ & $-0.078^{+0.031}_{-0.028}$  & $-0.058^{+0.010}_{-0.010}$ & $0.004^{+0.014}_{-0.015}$ & $0.004^{+0.014}_{-0.015}$\\
+SNF20070331-025 & $118.7^{+6.9}_{-7.0}$ & $ 15.4^{+2.0}_{-2.0}$ & $ 6121^{+ 10}_{- 10}$ & $ -1.22^{+  0.15}_{-  0.15}$ & $0.190^{+0.037}_{-0.037}$  & $-0.015^{+0.020}_{-0.020}$ & $0.001^{+0.023}_{-0.022}$ & $0.001^{+0.023}_{-0.022}$\\
+SNF20070818-001 & $160.6^{+6.7}_{-6.8}$ & $ 16.4^{+1.5}_{-1.5}$ & $ 6113^{+  5}_{-  5}$ & $  0.14^{+  0.14}_{-  0.14}$ & $-0.178^{+0.021}_{-0.020}$  & $0.005^{+0.014}_{-0.014}$ & $0.014^{+0.016}_{-0.015}$ & $0.014^{+0.016}_{-0.015}$\\
+SNBOSS38 & $ 57.1^{+0.4}_{-0.4}$ & $ 17.8^{+0.3}_{-0.3}$ & $ 6127^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $0.018^{+0.038}_{-0.039}$  & $0.017^{+0.021}_{-0.023}$ & $-0.002^{+0.019}_{-0.020}$ & $-0.002^{+0.019}_{-0.020}$\\
+SN2006ob & $ 75.9^{+12.1}_{-12.4}$ & $ 26.8^{+1.3}_{-1.4}$ & $ 6113^{+  5}_{-  5}$ & $ -2.26^{+  0.21}_{-  0.21}$ & $0.039^{+0.035}_{-0.035}$  & $-0.051^{+0.019}_{-0.017}$ & $0.084^{+0.021}_{-0.021}$ & $0.084^{+0.021}_{-0.021}$\\
+PTF12eer & $169.4^{+8.9}_{-8.8}$ & $ 12.2^{+1.8}_{-1.8}$ & $ 6148^{+ 10}_{- 10}$ & $  0.64^{+  0.14}_{-  0.15}$ & $-0.053^{+0.028}_{-0.027}$  & $0.039^{+0.018}_{-0.019}$ & $-0.029^{+0.017}_{-0.012}$ & $-0.029^{+0.017}_{-0.012}$\\
+PTF10ops & $ 38.0^{+9.2}_{-9.2}$ & $ 21.9^{+4.6}_{-4.6}$ & $ 6140^{+  6}_{-  5}$ & $ -0.58^{+  0.12}_{-  0.12}$ & $-0.091^{+0.221}_{-0.154}$  & $0.190^{+0.040}_{-0.041}$ & $0.181^{+0.038}_{-0.036}$ & $0.181^{+0.038}_{-0.036}$\\
+SNF20080514-002 & $ 83.1^{+0.7}_{-0.7}$ & $ 19.2^{+0.5}_{-0.5}$ & $ 6131^{+  3}_{-  3}$ & $ -1.55^{+  0.09}_{-  0.09}$ & $0.174^{+0.019}_{-0.019}$  & $-0.074^{+0.007}_{-0.006}$ & $0.006^{+0.011}_{-0.012}$ & $0.006^{+0.011}_{-0.012}$\\
+PTF12evo & $129.1^{+2.6}_{-2.7}$ & $  9.9^{+1.1}_{-1.1}$ & $ 6157^{+  4}_{-  4}$ & $  0.81^{+  0.13}_{-  0.12}$ & $0.024^{+0.027}_{-0.027}$  & $0.004^{+0.011}_{-0.011}$ & $-0.034^{+0.012}_{-0.010}$ & $-0.034^{+0.012}_{-0.010}$\\
+SNF20080614-010 & $118.9^{+4.9}_{-4.8}$ & $ 28.9^{+1.2}_{-1.2}$ & $ 6129^{+  3}_{-  3}$ & $ -1.81^{+  0.15}_{-  0.15}$ & $-0.114^{+0.046}_{-0.042}$  & $-0.068^{+0.012}_{-0.009}$ & $0.049^{+0.019}_{-0.019}$ & $0.049^{+0.019}_{-0.019}$\\
+PTF10icb & $104.8^{+0.9}_{-0.9}$ & $ 12.6^{+0.3}_{-0.3}$ & $ 6138^{+  2}_{-  2}$ & $  0.23^{+  0.10}_{-  0.10}$ & $0.410^{+0.024}_{-0.025}$  & $0.046^{+0.006}_{-0.006}$ & $-0.019^{+0.010}_{-0.010}$ & $-0.019^{+0.010}_{-0.010}$\\
+PTF12efn & $145.5^{+3.3}_{-3.2}$ & $  5.4^{+1.4}_{-1.5}$ & $ 6115^{+  3}_{-  3}$ & $  1.04^{+  0.16}_{-  0.16}$ & $0.177^{+0.030}_{-0.029}$  & $-0.058^{+0.014}_{-0.012}$ & $0.051^{+0.017}_{-0.017}$ & $0.051^{+0.017}_{-0.017}$\\
+SNNGC4424 & $109.0^{+0.3}_{-0.3}$ & $  8.6^{+0.1}_{-0.1}$ & $ 6138^{+  2}_{-  2}$ & $  0.44^{+  0.09}_{-  0.09}$ & $0.600^{+0.022}_{-0.023}$  & $0.078^{+0.007}_{-0.006}$ & $-0.025^{+0.011}_{-0.011}$ & $-0.025^{+0.011}_{-0.011}$\\
+SNF20080516-022 & $ 99.1^{+2.2}_{-2.1}$ & $ 15.3^{+0.9}_{-0.9}$ & $ 6159^{+  3}_{-  3}$ & $  0.48^{+  0.12}_{-  0.11}$ & $0.001^{+0.026}_{-0.026}$  & $-0.064^{+0.010}_{-0.009}$ & $-0.025^{+0.014}_{-0.013}$ & $-0.025^{+0.014}_{-0.013}$\\
+PTF12hwb & $139.4^{+25.9}_{-23.8}$ & $ -0.9^{+4.4}_{-4.3}$ & $ 6090^{+ 14}_{- 14}$ & $  1.34^{+  0.17}_{-  0.17}$ & $0.471^{+0.042}_{-0.044}$  & $0.151^{+0.037}_{-0.043}$ & $0.004^{+0.040}_{-0.032}$ & $0.004^{+0.040}_{-0.032}$\\
+PTF10qyz & $108.1^{+2.1}_{-2.1}$ & $ 21.0^{+0.8}_{-0.8}$ & $ 6117^{+  5}_{-  5}$ & $ -1.67^{+  0.13}_{-  0.13}$ & $0.099^{+0.133}_{-0.095}$  & $-0.067^{+0.014}_{-0.010}$ & $-0.038^{+0.012}_{-0.008}$ & $-0.038^{+0.012}_{-0.008}$\\
+SNF20060907-000 & $ 87.8^{+7.5}_{-7.3}$ & $ 15.9^{+0.9}_{-0.9}$ & $ 6150^{+  4}_{-  4}$ & $  0.16^{+  0.17}_{-  0.17}$ & $0.037^{+0.033}_{-0.033}$  & $-0.079^{+0.005}_{-0.005}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+LSQ12fxd & $122.8^{+1.6}_{-1.7}$ & $ 11.7^{+0.8}_{-0.7}$ & $ 6119^{+  4}_{-  4}$ & $  0.16^{+  0.12}_{-  0.12}$ & $-0.154^{+0.044}_{-0.032}$  & $-0.052^{+0.008}_{-0.008}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
+SNF20080821-000 & $104.8^{+2.2}_{-2.2}$ & $  8.8^{+1.2}_{-1.2}$ & $ 6121^{+  4}_{-  4}$ & $  0.77^{+  0.15}_{-  0.14}$ & $-0.104^{+0.023}_{-0.023}$  & $0.025^{+0.011}_{-0.011}$ & $-0.006^{+0.013}_{-0.013}$ & $-0.006^{+0.013}_{-0.013}$\\
+SNF20070802-000 & $157.9^{+3.3}_{-3.3}$ & $ 16.0^{+1.4}_{-1.4}$ & $ 6103^{+  5}_{-  5}$ & $  0.07^{+  0.13}_{-  0.13}$ & $-0.074^{+0.028}_{-0.028}$  & $0.005^{+0.014}_{-0.014}$ & $0.005^{+0.016}_{-0.016}$ & $0.005^{+0.016}_{-0.016}$\\
+PTF10wnm & $105.5^{+2.3}_{-2.3}$ & $  6.8^{+0.9}_{-0.9}$ & $ 6125^{+  3}_{-  3}$ & $  0.73^{+  0.12}_{-  0.12}$ & $0.123^{+0.022}_{-0.021}$  & $-0.014^{+0.009}_{-0.009}$ & $0.015^{+0.012}_{-0.012}$ & $0.015^{+0.012}_{-0.012}$\\
+PTF10mwb & $116.2^{+1.2}_{-1.2}$ & $ 21.1^{+0.7}_{-0.7}$ & $ 6139^{+  2}_{-  2}$ & $ -0.48^{+  0.09}_{-  0.09}$ & $-0.000^{+0.071}_{-0.070}$  & $-0.036^{+0.008}_{-0.008}$ & $-0.011^{+0.011}_{-0.011}$ & $-0.011^{+0.011}_{-0.011}$\\
+SN2010dt & $133.3^{+8.4}_{-8.6}$ & $ 16.0^{+0.6}_{-0.6}$ & $ 6141^{+  5}_{-  5}$ & $ -0.02^{+  0.09}_{-  0.09}$ & $-0.046^{+0.024}_{-0.024}$  & $-0.063^{+0.010}_{-0.009}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
+SNF20080623-001 & $149.2^{+1.4}_{-1.4}$ & $ 14.8^{+0.6}_{-0.6}$ & $ 6131^{+  3}_{-  3}$ & $ -0.07^{+  0.11}_{-  0.10}$ & $0.072^{+0.025}_{-0.025}$  & $-0.054^{+0.010}_{-0.009}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
+LSQ12fhe & $ 42.9^{+1.2}_{-1.2}$ & $  2.3^{+1.9}_{-1.9}$ & $ 6108^{+  4}_{-  4}$ & $  1.01^{+  0.17}_{-  0.17}$ & $-0.183^{+0.032}_{-0.033}$  & $0.067^{+0.017}_{-0.018}$ & $-0.017^{+0.018}_{-0.016}$ & $-0.017^{+0.018}_{-0.016}$\\
+PTF11bju & $ 31.3^{+4.3}_{-4.2}$ & $  3.3^{+2.0}_{-2.0}$ & $ 6138^{+  5}_{-  5}$ & $  1.02^{+  0.17}_{-  0.18}$ & $0.073^{+0.036}_{-0.036}$  & $0.077^{+0.019}_{-0.019}$ & $-0.014^{+0.020}_{-0.018}$ & $-0.014^{+0.020}_{-0.018}$\\
+PTF09fox & $118.5^{+2.7}_{-2.7}$ & $  9.8^{+0.9}_{-0.8}$ & $ 6117^{+  3}_{-  3}$ & $  0.52^{+  0.16}_{-  0.15}$ & $0.027^{+0.039}_{-0.039}$  & $-0.047^{+0.009}_{-0.009}$ & $-0.043^{+0.007}_{-0.006}$ & $-0.043^{+0.007}_{-0.006}$\\
+PTF13ayw & $103.8^{+2.4}_{-2.4}$ & $ 23.1^{+1.8}_{-1.9}$ & $ 6116^{+  6}_{-  6}$ & $ -1.67^{+  0.23}_{-  0.24}$ & $0.068^{+0.041}_{-0.041}$  & $-0.069^{+0.014}_{-0.009}$ & $0.101^{+0.019}_{-0.020}$ & $0.101^{+0.019}_{-0.020}$\\
+SNF20070810-004 & $127.0^{+1.8}_{-1.8}$ & $ 20.1^{+0.9}_{-0.9}$ & $ 6117^{+  7}_{-  7}$ & $ -0.01^{+  0.11}_{-  0.11}$ & $-0.044^{+0.026}_{-0.025}$  & $-0.068^{+0.011}_{-0.009}$ & $-0.033^{+0.012}_{-0.010}$ & $-0.033^{+0.012}_{-0.010}$\\
+PTF11mty & $110.5^{+2.2}_{-2.2}$ & $ 11.3^{+1.0}_{-1.1}$ & $ 6140^{+  5}_{-  5}$ & $  1.03^{+  0.13}_{-  0.13}$ & $0.062^{+0.025}_{-0.024}$  & $-0.072^{+0.009}_{-0.007}$ & $0.024^{+0.013}_{-0.014}$ & $0.024^{+0.013}_{-0.014}$\\
+SNF20080512-010 & $ 96.0^{+3.4}_{-3.4}$ & $ 21.9^{+1.3}_{-1.3}$ & $ 6128^{+  5}_{-  5}$ & $ -1.64^{+  0.18}_{-  0.18}$ & $-0.032^{+0.072}_{-0.061}$  & $-0.051^{+0.013}_{-0.012}$ & $0.018^{+0.016}_{-0.016}$ & $0.018^{+0.016}_{-0.016}$\\
+PTF11mkx & $ 34.8^{+3.5}_{-3.5}$ & $  5.5^{+1.3}_{-1.3}$ & $ 6169^{+  5}_{-  5}$ & $  0.53^{+  0.14}_{-  0.14}$ & $0.022^{+0.135}_{-0.080}$  & $0.102^{+0.017}_{-0.016}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+PTF10tce & $135.8^{+1.1}_{-1.1}$ & $ 10.6^{+1.2}_{-1.2}$ & $ 6090^{+  4}_{-  4}$ & $  0.38^{+  0.12}_{-  0.12}$ & $0.041^{+0.028}_{-0.027}$  & $-0.005^{+0.013}_{-0.014}$ & $-0.019^{+0.015}_{-0.015}$ & $-0.019^{+0.015}_{-0.015}$\\
+SNF20061020-000 & $ 90.3^{+13.4}_{-13.3}$ & $ 23.9^{+0.9}_{-0.9}$ & $ 6120^{+  4}_{-  5}$ & $ -1.75^{+  0.17}_{-  0.17}$ & $-0.096^{+0.039}_{-0.034}$  & $0.000^{+0.016}_{-0.016}$ & $0.006^{+0.022}_{-0.020}$ & $0.006^{+0.022}_{-0.020}$\\
+SN2005ir & $115.7^{+2.8}_{-2.7}$ & $  8.7^{+4.6}_{-4.8}$ & $ 6069^{+  5}_{-  5}$ & $  1.64^{+  0.49}_{-  0.48}$ & $0.112^{+0.042}_{-0.043}$  & $-0.022^{+0.036}_{-0.033}$ & $0.067^{+0.037}_{-0.037}$ & $0.067^{+0.037}_{-0.037}$\\
+SNF20080717-000 & $ 92.7^{+2.6}_{-2.6}$ & $ 12.4^{+1.7}_{-1.7}$ & $ 6105^{+  3}_{-  3}$ & $  0.87^{+  0.13}_{-  0.12}$ & $0.115^{+0.034}_{-0.033}$  & $0.126^{+0.018}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$\\
+PTF12ena & $101.0^{+1.6}_{-1.6}$ & $  8.2^{+0.9}_{-0.9}$ & $ 6130^{+  3}_{-  3}$ & $  0.76^{+  0.13}_{-  0.13}$ & $-0.039^{+0.028}_{-0.028}$  & $0.289^{+0.011}_{-0.012}$ & $-0.038^{+0.010}_{-0.008}$ & $-0.038^{+0.010}_{-0.008}$\\
+PTF13anh & $167.2^{+1.8}_{-1.8}$ & $ 21.6^{+1.0}_{-1.0}$ & $ 6174^{+  3}_{-  4}$ & $ -0.38^{+  0.14}_{-  0.14}$ & $0.092^{+0.108}_{-0.067}$  & $-0.032^{+0.020}_{-0.019}$ & $-0.034^{+0.014}_{-0.010}$ & $-0.034^{+0.014}_{-0.010}$\\
+CSS110918\_01 & $110.4^{+1.0}_{-1.0}$ & $  5.0^{+0.9}_{-0.9}$ & $ 6101^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.077^{+0.187}_{-0.094}$  & $-0.078^{+0.006}_{-0.005}$ & $-0.028^{+0.013}_{-0.012}$ & $-0.028^{+0.013}_{-0.012}$\\
+SNF20061024-000 & $ 98.9^{+15.7}_{-16.7}$ & $ 29.1^{+1.4}_{-1.4}$ & $ 6127^{+  5}_{-  5}$ & $ -1.51^{+  0.18}_{-  0.18}$ & $0.045^{+0.062}_{-0.059}$  & $-0.049^{+0.021}_{-0.019}$ & $0.003^{+0.031}_{-0.028}$ & $0.003^{+0.031}_{-0.028}$\\
+SNF20070506-006 & $ 94.3^{+1.3}_{-1.2}$ & $  6.4^{+0.6}_{-0.5}$ & $ 6152^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $-0.075^{+0.027}_{-0.026}$  & $-0.029^{+0.009}_{-0.009}$ & $0.006^{+0.013}_{-0.013}$ & $0.006^{+0.013}_{-0.013}$\\
+SNF20070403-001 & $107.8^{+5.0}_{-5.1}$ & $ 17.1^{+1.4}_{-1.4}$ & $ 6123^{+  4}_{-  4}$ & $ -0.60^{+  0.12}_{-  0.12}$ & $0.007^{+0.029}_{-0.028}$  & $-0.036^{+0.014}_{-0.014}$ & $0.020^{+0.017}_{-0.017}$ & $0.020^{+0.017}_{-0.017}$\\
+PTF10hmv & $109.8^{+1.3}_{-1.4}$ & $  8.5^{+0.7}_{-0.6}$ & $ 6143^{+  3}_{-  3}$ & $  1.15^{+  0.13}_{-  0.12}$ & $0.284^{+0.024}_{-0.023}$  & $0.106^{+0.009}_{-0.009}$ & $-0.010^{+0.012}_{-0.012}$ & $-0.010^{+0.012}_{-0.012}$\\
+SNF20071015-000 & $104.8^{+3.1}_{-3.1}$ & $  6.5^{+1.1}_{-1.1}$ & $ 6125^{+  7}_{-  7}$ & $  0.90^{+  0.28}_{-  0.29}$ & $0.116^{+0.040}_{-0.040}$  & $0.293^{+0.016}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$\\
+SNhunt89 & $ 88.6^{+2.7}_{-2.7}$ & $ 29.8^{+1.7}_{-1.7}$ & $ 6109^{+  7}_{-  7}$ & $ -2.02^{+  0.16}_{-  0.16}$ & $0.202^{+0.049}_{-0.047}$  & $0.030^{+0.018}_{-0.019}$ & $0.032^{+0.027}_{-0.026}$ & $0.032^{+0.027}_{-0.026}$\\
+SNF20070902-021 & $109.0^{+3.3}_{-3.3}$ & $ 16.8^{+0.9}_{-0.9}$ & $ 6131^{+  5}_{-  5}$ & $ -0.46^{+  0.09}_{-  0.09}$ & $-0.082^{+0.027}_{-0.026}$  & $-0.023^{+0.010}_{-0.010}$ & $-0.028^{+0.014}_{-0.012}$ & $-0.028^{+0.014}_{-0.012}$\\
+PTF09dlc & $143.8^{+2.1}_{-2.1}$ & $  9.7^{+0.8}_{-0.8}$ & $ 6143^{+  3}_{-  3}$ & $  0.01^{+  0.10}_{-  0.10}$ & $0.008^{+0.027}_{-0.026}$  & $-0.054^{+0.012}_{-0.012}$ & $-0.017^{+0.014}_{-0.015}$ & $-0.017^{+0.014}_{-0.015}$\\
+PTF13ajv & $149.9^{+8.1}_{-8.2}$ & $ 22.0^{+2.7}_{-3.0}$ & $ 6107^{+ 20}_{- 20}$ & $ -1.64^{+  0.20}_{-  0.21}$ & $0.263^{+0.046}_{-0.045}$  & $-0.062^{+0.021}_{-0.014}$ & $-0.005^{+0.023}_{-0.022}$ & $-0.005^{+0.023}_{-0.022}$\\
+SNF20080919-000 & $115.6^{+2.7}_{-2.7}$ & $  8.8^{+0.9}_{-0.8}$ & $ 6144^{+  5}_{-  5}$ & $ -0.24^{+  0.10}_{-  0.10}$ & $-0.043^{+0.027}_{-0.026}$  & $0.165^{+0.013}_{-0.012}$ & $-0.035^{+0.013}_{-0.010}$ & $-0.035^{+0.013}_{-0.010}$\\
+SNF20080919-001 & $ 85.0^{+1.1}_{-1.1}$ & $  6.1^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  1.05^{+  0.12}_{-  0.12}$ & $-0.183^{+0.020}_{-0.019}$  & $0.001^{+0.008}_{-0.008}$ & $0.006^{+0.012}_{-0.012}$ & $0.006^{+0.012}_{-0.012}$\\
+SN2010kg & $ 99.4^{+17.2}_{-17.5}$ & $ 21.8^{+0.7}_{-0.7}$ & $ 6077^{+  5}_{-  5}$ & $ -1.87^{+  0.24}_{-  0.25}$ & $-0.073^{+0.030}_{-0.029}$  & $0.035^{+0.021}_{-0.020}$ & $0.034^{+0.020}_{-0.021}$ & $0.034^{+0.020}_{-0.021}$\\
+SNF20080714-008 & $155.6^{+11.0}_{-10.8}$ & $ 16.6^{+1.9}_{-1.8}$ & $ 6099^{+  6}_{-  6}$ & $ -0.07^{+  0.14}_{-  0.14}$ & $-0.141^{+0.024}_{-0.022}$  & $0.082^{+0.018}_{-0.020}$ & $-0.029^{+0.017}_{-0.013}$ & $-0.029^{+0.017}_{-0.013}$\\
+SNF20070714-007 & $132.6^{+5.5}_{-5.5}$ & $ 33.5^{+4.3}_{-4.2}$ & $ 6145^{+  4}_{-  4}$ & $ -1.09^{+  0.13}_{-  0.13}$ & $-0.094^{+0.046}_{-0.047}$  & $0.118^{+0.035}_{-0.038}$ & $0.117^{+0.036}_{-0.032}$ & $0.117^{+0.036}_{-0.032}$\\
+SNF20080522-011 & $122.1^{+1.7}_{-1.7}$ & $  8.3^{+0.5}_{-0.5}$ & $ 6125^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.124^{+0.023}_{-0.023}$  & $-0.045^{+0.008}_{-0.008}$ & $-0.031^{+0.011}_{-0.010}$ & $-0.031^{+0.011}_{-0.010}$\\
+SNF20061111-002 & $117.1^{+8.6}_{-8.8}$ & $ 19.8^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  0.07^{+  0.17}_{-  0.17}$ & $0.056^{+0.032}_{-0.032}$  & $-0.062^{+0.013}_{-0.011}$ & $0.026^{+0.017}_{-0.017}$ & $0.026^{+0.017}_{-0.017}$\\
+SNNGC6343 & $ 86.9^{+1.5}_{-1.4}$ & $ 21.2^{+0.7}_{-0.7}$ & $ 6136^{+  3}_{-  3}$ & $ -1.49^{+  0.16}_{-  0.16}$ & $0.055^{+0.029}_{-0.030}$  & $0.036^{+0.013}_{-0.012}$ & $0.020^{+0.016}_{-0.014}$ & $0.020^{+0.016}_{-0.014}$\\
+SNF20061011-005 & $120.5^{+1.1}_{-1.1}$ & $  9.2^{+0.3}_{-0.3}$ & $ 6132^{+  4}_{-  4}$ & $  0.66^{+  0.22}_{-  0.21}$ & $-0.091^{+0.043}_{-0.041}$  & $-0.073^{+0.008}_{-0.007}$ & $0.003^{+0.021}_{-0.021}$ & $0.003^{+0.021}_{-0.021}$\\
+SNF20080825-010 & $ 96.4^{+10.2}_{-10.2}$ & $ 19.2^{+0.6}_{-0.6}$ & $ 6116^{+  4}_{-  4}$ & $ -0.76^{+  0.13}_{-  0.13}$ & $-0.192^{+0.020}_{-0.020}$  & $-0.045^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
+PTF10ufj & $141.4^{+3.3}_{-3.3}$ & $ 12.0^{+1.1}_{-1.0}$ & $ 6131^{+  6}_{-  5}$ & $  0.56^{+  0.13}_{-  0.13}$ & $-0.043^{+0.106}_{-0.068}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
+PTF10wof & $130.5^{+2.6}_{-2.7}$ & $ 16.5^{+0.9}_{-0.9}$ & $ 6102^{+  2}_{-  2}$ & $  0.06^{+  0.11}_{-  0.11}$ & $0.096^{+0.023}_{-0.023}$  & $-0.009^{+0.011}_{-0.011}$ & $-0.013^{+0.013}_{-0.012}$ & $-0.013^{+0.013}_{-0.012}$\\
+SNF20080918-000 & $146.6^{+3.5}_{-3.5}$ & $  5.6^{+2.1}_{-2.0}$ & $ 6110^{+  5}_{-  5}$ & $  1.28^{+  0.23}_{-  0.23}$ & $0.112^{+0.038}_{-0.037}$  & $0.073^{+0.019}_{-0.019}$ & $-0.004^{+0.023}_{-0.022}$ & $-0.004^{+0.023}_{-0.022}$\\
+SNF20080516-000 & $117.6^{+2.1}_{-2.1}$ & $  8.2^{+1.2}_{-1.1}$ & $ 6135^{+  3}_{-  3}$ & $  0.96^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.028}$  & $-0.054^{+0.011}_{-0.010}$ & $0.004^{+0.015}_{-0.015}$ & $0.004^{+0.015}_{-0.015}$\\
+SN2005cf & $158.9^{+0.7}_{-0.7}$ & $ 15.2^{+0.8}_{-0.7}$ & $ 6140^{+  3}_{-  3}$ & $ -0.19^{+  0.13}_{-  0.13}$ & $-0.122^{+0.028}_{-0.027}$  & $-0.077^{+0.007}_{-0.005}$ & $0.002^{+0.014}_{-0.015}$ & $0.002^{+0.014}_{-0.015}$\\
+CSS130502\_01 & $ 87.3^{+8.0}_{-8.7}$ & $ 15.4^{+0.5}_{-0.5}$ & $ 6128^{+  3}_{-  3}$ & $ -0.15^{+  0.20}_{-  0.20}$ & $0.121^{+0.032}_{-0.032}$  & $-0.069^{+0.011}_{-0.009}$ & $-0.017^{+0.015}_{-0.015}$ & $-0.017^{+0.015}_{-0.015}$\\
+SNF20080620-000 & $125.3^{+9.5}_{-9.7}$ & $ 20.6^{+0.6}_{-0.6}$ & $ 6133^{+  3}_{-  3}$ & $ -0.97^{+  0.14}_{-  0.14}$ & $-0.007^{+0.029}_{-0.028}$  & $0.001^{+0.012}_{-0.012}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
+SNPGC51271 & $ 64.0^{+12.0}_{-13.2}$ & $ 21.4^{+0.7}_{-0.7}$ & $ 6121^{+  2}_{-  2}$ & $ -1.85^{+  0.16}_{-  0.17}$ & $0.125^{+0.034}_{-0.034}$  & $-0.057^{+0.017}_{-0.014}$ & $0.011^{+0.018}_{-0.019}$ & $0.011^{+0.018}_{-0.019}$\\
+PTF11pdk & $127.7^{+2.6}_{-2.7}$ & $ 16.1^{+1.2}_{-1.2}$ & $ 6154^{+  5}_{-  5}$ & $  0.16^{+  0.16}_{-  0.17}$ & $-0.027^{+0.035}_{-0.035}$  & $-0.070^{+0.010}_{-0.008}$ & $-0.033^{+0.015}_{-0.011}$ & $-0.033^{+0.015}_{-0.011}$\\
+SNF20060511-014 & $102.9^{+2.8}_{-2.8}$ & $ 17.1^{+1.0}_{-1.0}$ & $ 6144^{+  8}_{-  7}$ & $ -0.50^{+  0.15}_{-  0.15}$ & $-0.042^{+0.047}_{-0.037}$  & $-0.008^{+0.011}_{-0.010}$ & $-0.041^{+0.009}_{-0.007}$ & $-0.041^{+0.009}_{-0.007}$\\
+SNF20080612-003 & $120.0^{+1.1}_{-1.1}$ & $  7.5^{+0.6}_{-0.6}$ & $ 6122^{+  3}_{-  3}$ & $  0.96^{+  0.15}_{-  0.15}$ & $-0.221^{+0.018}_{-0.017}$  & $-0.015^{+0.007}_{-0.007}$ & $-0.001^{+0.013}_{-0.014}$ & $-0.001^{+0.013}_{-0.014}$\\
+SNF20080626-002 & $130.0^{+1.0}_{-1.0}$ & $  5.8^{+2.1}_{-2.0}$ & $ 6111^{+  3}_{-  3}$ & $  1.03^{+  0.19}_{-  0.19}$ & $-0.043^{+0.026}_{-0.025}$  & $-0.009^{+0.015}_{-0.016}$ & $-0.022^{+0.017}_{-0.015}$ & $-0.022^{+0.017}_{-0.015}$\\
+SNF20060621-015 & $111.8^{+1.3}_{-1.3}$ & $  9.9^{+0.7}_{-0.7}$ & $ 6144^{+  3}_{-  3}$ & $  0.52^{+  0.14}_{-  0.14}$ & $-0.015^{+0.026}_{-0.027}$  & $-0.067^{+0.008}_{-0.008}$ & $-0.020^{+0.013}_{-0.013}$ & $-0.020^{+0.013}_{-0.013}$\\
+SNF20080920-000 & $135.1^{+1.4}_{-1.4}$ & $  5.3^{+1.5}_{-1.5}$ & $ 6085^{+  3}_{-  3}$ & $  1.08^{+  0.23}_{-  0.23}$ & $-0.002^{+0.038}_{-0.037}$  & $-0.020^{+0.017}_{-0.017}$ & $-0.012^{+0.020}_{-0.019}$ & $-0.012^{+0.020}_{-0.019}$\\
+SN2007cq & $ 63.7^{+3.9}_{-3.9}$ & $ 11.6^{+0.8}_{-0.8}$ & $ 6138^{+  3}_{-  3}$ & $  0.05^{+  0.13}_{-  0.13}$ & $-0.111^{+0.029}_{-0.027}$  & $0.008^{+0.011}_{-0.011}$ & $-0.015^{+0.015}_{-0.015}$ & $-0.015^{+0.015}_{-0.015}$\\
+SNF20080918-004 & $ 91.9^{+6.6}_{-6.6}$ & $ 21.2^{+0.9}_{-0.9}$ & $ 6141^{+  4}_{-  4}$ & $ -1.37^{+  0.15}_{-  0.15}$ & $0.035^{+0.142}_{-0.087}$  & $-0.021^{+0.014}_{-0.013}$ & $-0.012^{+0.019}_{-0.018}$ & $-0.012^{+0.019}_{-0.018}$\\
+CSS120424\_01 & $138.5^{+2.1}_{-2.1}$ & $ 11.5^{+0.6}_{-0.6}$ & $ 6138^{+  3}_{-  3}$ & $  0.58^{+  0.14}_{-  0.14}$ & $-0.010^{+0.028}_{-0.028}$  & $-0.061^{+0.009}_{-0.009}$ & $-0.024^{+0.013}_{-0.012}$ & $-0.024^{+0.013}_{-0.012}$\\
+SNF20080610-000 & $119.5^{+8.6}_{-8.8}$ & $ 17.0^{+1.4}_{-1.4}$ & $ 6131^{+  6}_{-  6}$ & $  0.16^{+  0.14}_{-  0.14}$ & $0.013^{+0.068}_{-0.068}$  & $-0.019^{+0.014}_{-0.015}$ & $-0.027^{+0.017}_{-0.013}$ & $-0.027^{+0.017}_{-0.013}$\\
+SNF20070701-005 & $101.6^{+2.6}_{-2.6}$ & $ 13.6^{+0.9}_{-1.0}$ & $ 6155^{+  5}_{-  5}$ & $  0.39^{+  0.14}_{-  0.14}$ & $-0.187^{+0.021}_{-0.021}$  & $-0.012^{+0.011}_{-0.011}$ & $0.037^{+0.015}_{-0.015}$ & $0.037^{+0.015}_{-0.015}$\\
+SN2007kk & $128.6^{+1.4}_{-1.4}$ & $ 11.0^{+0.9}_{-0.9}$ & $ 6099^{+  4}_{-  4}$ & $  0.59^{+  0.14}_{-  0.14}$ & $-0.087^{+0.029}_{-0.029}$  & $-0.048^{+0.012}_{-0.012}$ & $-0.035^{+0.012}_{-0.010}$ & $-0.035^{+0.012}_{-0.010}$\\
+SNF20060908-004 & $114.4^{+1.2}_{-1.2}$ & $ 12.4^{+0.6}_{-0.6}$ & $ 6136^{+  3}_{-  3}$ & $  0.63^{+  0.15}_{-  0.15}$ & $-0.099^{+0.138}_{-0.081}$  & $-0.068^{+0.009}_{-0.008}$ & $0.021^{+0.017}_{-0.017}$ & $0.021^{+0.017}_{-0.017}$\\
+SNF20080909-030 & $ 93.8^{+1.0}_{-0.9}$ & $  7.7^{+0.4}_{-0.4}$ & $ 6171^{+  3}_{-  3}$ & $  0.99^{+  0.13}_{-  0.13}$ & $0.030^{+0.030}_{-0.030}$  & $0.008^{+0.013}_{-0.012}$ & $0.008^{+0.015}_{-0.014}$ & $0.008^{+0.015}_{-0.014}$\\
+PTF11bgv & $ 78.3^{+3.1}_{-3.1}$ & $ 12.7^{+0.6}_{-0.6}$ & $ 6146^{+  3}_{-  3}$ & $ -0.27^{+  0.11}_{-  0.10}$ & $0.057^{+0.028}_{-0.028}$  & $0.081^{+0.010}_{-0.010}$ & $0.006^{+0.015}_{-0.015}$ & $0.006^{+0.015}_{-0.015}$\\
+SNNGC2691 & $ 55.7^{+14.4}_{-14.5}$ & $  4.5^{+0.2}_{-0.2}$ & $ 6138^{+  8}_{-  8}$ & $  0.82^{+  0.16}_{-  0.16}$ & $-0.031^{+0.039}_{-0.038}$  & $0.069^{+0.018}_{-0.019}$ & $0.041^{+0.020}_{-0.020}$ & $0.041^{+0.020}_{-0.020}$\\
+PTF13asv & $ 75.4^{+1.1}_{-1.1}$ & $  2.4^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  0.66^{+  0.10}_{-  0.10}$ & $-0.018^{+0.184}_{-0.105}$  & $-0.068^{+0.012}_{-0.009}$ & $0.015^{+0.015}_{-0.015}$ & $0.015^{+0.015}_{-0.015}$\\
+SNF20070806-026 & $102.2^{+8.4}_{-9.0}$ & $ 25.3^{+0.7}_{-0.7}$ & $ 6112^{+  7}_{-  7}$ & $ -1.93^{+  0.14}_{-  0.14}$ & $0.010^{+0.032}_{-0.033}$  & $-0.071^{+0.011}_{-0.008}$ & $0.015^{+0.017}_{-0.017}$ & $0.015^{+0.017}_{-0.017}$\\
+SNF20070427-001 & $ 80.7^{+2.3}_{-2.3}$ & $  6.5^{+0.8}_{-0.8}$ & $ 6143^{+  5}_{-  5}$ & $  0.82^{+  0.17}_{-  0.17}$ & $-0.009^{+0.031}_{-0.031}$  & $-0.066^{+0.011}_{-0.009}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
+SNF20061108-004 & $128.2^{+5.4}_{-5.4}$ & $  6.8^{+2.1}_{-2.1}$ & $ 6110^{+  6}_{-  6}$ & $  2.36^{+  0.27}_{-  0.27}$ & $-0.089^{+0.038}_{-0.036}$  & $-0.025^{+0.021}_{-0.023}$ & $-0.005^{+0.024}_{-0.022}$ & $-0.005^{+0.024}_{-0.022}$\\
+SNF20060912-000 & $106.9^{+1.7}_{-1.7}$ & $ 19.8^{+1.5}_{-1.5}$ & $ 6158^{+  7}_{-  7}$ & $  0.06^{+  0.17}_{-  0.17}$ & $-0.177^{+0.032}_{-0.033}$  & $0.034^{+0.018}_{-0.019}$ & $0.080^{+0.021}_{-0.020}$ & $0.080^{+0.021}_{-0.020}$\\
+CSS110918\_02 & $109.1^{+8.1}_{-8.1}$ & $ 15.0^{+0.6}_{-0.6}$ & $ 6137^{+  3}_{-  3}$ & $ -0.26^{+  0.13}_{-  0.13}$ & $-0.052^{+0.027}_{-0.027}$  & $-0.039^{+0.010}_{-0.010}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
+SNF20080918-002 & $ 96.6^{+2.8}_{-2.7}$ & $ 13.3^{+1.2}_{-1.2}$ & $ 6143^{+  6}_{-  6}$ & $ -0.47^{+  0.08}_{-  0.08}$ & $0.021^{+0.034}_{-0.035}$  & $-0.056^{+0.014}_{-0.013}$ & $-0.005^{+0.020}_{-0.021}$ & $-0.005^{+0.020}_{-0.021}$\\
+SNIC3573 & $103.0^{+1.8}_{-1.7}$ & $ 12.1^{+0.9}_{-0.9}$ & $ 6141^{+  5}_{-  5}$ & $  0.39^{+  0.16}_{-  0.16}$ & $-0.109^{+0.026}_{-0.024}$  & $0.015^{+0.009}_{-0.010}$ & $-0.025^{+0.014}_{-0.012}$ & $-0.025^{+0.014}_{-0.012}$\\
+SNF20080725-004 & $133.8^{+2.1}_{-2.1}$ & $  6.7^{+0.9}_{-0.9}$ & $ 6131^{+  6}_{-  5}$ & $  0.59^{+  0.13}_{-  0.13}$ & $0.078^{+0.032}_{-0.032}$  & $0.025^{+0.012}_{-0.011}$ & $0.016^{+0.015}_{-0.014}$ & $0.016^{+0.015}_{-0.014}$\\
+SNF20050728-006 & $127.7^{+2.5}_{-2.4}$ & $ 15.3^{+1.2}_{-1.2}$ & $ 6124^{+  6}_{-  6}$ & $  0.11^{+  0.19}_{-  0.19}$ & $-0.088^{+0.034}_{-0.032}$  & $0.064^{+0.011}_{-0.012}$ & $0.012^{+0.017}_{-0.017}$ & $0.012^{+0.017}_{-0.017}$\\
+SN2012fr & $134.2^{+0.5}_{-0.5}$ & $  7.4^{+0.2}_{-0.2}$ & $ 6101^{+  1}_{-  1}$ & $  0.88^{+  0.08}_{-  0.09}$ & $-0.248^{+0.021}_{-0.021}$  & $-0.077^{+0.005}_{-0.005}$ & $0.044^{+0.012}_{-0.011}$ & $0.044^{+0.012}_{-0.011}$\\
+SNF20060512-002 & $100.4^{+2.7}_{-2.8}$ & $ 13.5^{+1.1}_{-1.1}$ & $ 6106^{+  7}_{-  7}$ & $ -0.87^{+  0.15}_{-  0.16}$ & $-0.186^{+0.030}_{-0.028}$  & $0.018^{+0.012}_{-0.012}$ & $0.056^{+0.017}_{-0.016}$ & $0.056^{+0.017}_{-0.016}$\\
+SNF20060512-001 & $ 88.2^{+1.2}_{-1.2}$ & $  5.5^{+0.4}_{-0.4}$ & $ 6169^{+  3}_{-  3}$ & $  0.87^{+  0.11}_{-  0.11}$ & $-0.025^{+0.025}_{-0.025}$  & $0.050^{+0.011}_{-0.011}$ & $-0.010^{+0.011}_{-0.012}$ & $-0.010^{+0.011}_{-0.012}$\\
+SNF20071003-016 & $126.5^{+4.5}_{-4.4}$ & $ 16.7^{+1.5}_{-1.5}$ & $ 6123^{+ 10}_{- 10}$ & $ -0.30^{+  0.14}_{-  0.14}$ & $0.058^{+0.032}_{-0.032}$  & $0.068^{+0.013}_{-0.014}$ & $-0.030^{+0.016}_{-0.012}$ & $-0.030^{+0.016}_{-0.012}$\\
+SNF20050821-007 & $141.8^{+2.6}_{-2.6}$ & $  7.8^{+0.9}_{-0.9}$ & $ 6140^{+  9}_{-  8}$ & $  0.34^{+  0.20}_{-  0.19}$ & $-0.024^{+0.034}_{-0.033}$  & $-0.030^{+0.014}_{-0.013}$ & $-0.012^{+0.017}_{-0.017}$ & $-0.012^{+0.017}_{-0.017}$\\
+SNF20070803-005 & $ 45.4^{+14.0}_{-13.8}$ & $  0.8^{+0.6}_{-0.6}$ & $ 6138^{+ 22}_{- 22}$ & $  0.81^{+  0.15}_{-  0.15}$ & $-0.137^{+0.031}_{-0.031}$  & $0.043^{+0.019}_{-0.019}$ & $-0.005^{+0.021}_{-0.021}$ & $-0.005^{+0.021}_{-0.021}$\\
+PTF09foz & $127.2^{+1.9}_{-1.9}$ & $ 22.1^{+1.1}_{-1.1}$ & $ 6135^{+  4}_{-  4}$ & $ -0.92^{+  0.16}_{-  0.16}$ & $-0.141^{+0.019}_{-0.018}$  & $-0.042^{+0.009}_{-0.010}$ & $0.031^{+0.013}_{-0.012}$ & $0.031^{+0.013}_{-0.012}$\\
+PTF12grk & $158.1^{+8.3}_{-8.4}$ & $ 22.1^{+1.2}_{-1.2}$ & $ 6089^{+  8}_{-  8}$ & $ -1.02^{+  0.12}_{-  0.12}$ & $-0.117^{+0.027}_{-0.026}$  & $-0.025^{+0.016}_{-0.017}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+SNF20080720-001 & $138.3^{+3.9}_{-4.0}$ & $ 14.0^{+1.5}_{-1.5}$ & $ 6107^{+  3}_{-  3}$ & $  0.19^{+  0.12}_{-  0.12}$ & $-0.176^{+0.028}_{-0.028}$  & $0.325^{+0.018}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$\\
+SNF20080810-001 & $ 98.8^{+12.2}_{-12.3}$ & $ 21.7^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.93^{+  0.10}_{-  0.11}$ & $-0.058^{+0.024}_{-0.024}$  & $-0.023^{+0.016}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$\\
+SNF20050729-002 & $110.4^{+2.3}_{-2.2}$ & $ 10.7^{+1.5}_{-1.4}$ & $ 6141^{+  6}_{-  6}$ & $ -0.22^{+  0.21}_{-  0.22}$ & $0.052^{+0.102}_{-0.075}$  & $-0.039^{+0.015}_{-0.014}$ & $-0.039^{+0.011}_{-0.008}$ & $-0.039^{+0.011}_{-0.008}$\\
+SN2008ec & $ 97.7^{+10.6}_{-10.6}$ & $ 23.0^{+0.4}_{-0.4}$ & $ 6125^{+  3}_{-  3}$ & $ -1.09^{+  0.10}_{-  0.10}$ & $-0.076^{+0.025}_{-0.026}$  & $0.064^{+0.012}_{-0.012}$ & $0.017^{+0.015}_{-0.015}$ & $0.017^{+0.015}_{-0.015}$\\
+SNF20070902-018 & $108.6^{+9.5}_{-9.7}$ & $ 18.1^{+1.7}_{-1.7}$ & $ 6119^{+  7}_{-  7}$ & $ -0.81^{+  0.10}_{-  0.09}$ & $0.032^{+0.030}_{-0.030}$  & $0.023^{+0.016}_{-0.017}$ & $-0.035^{+0.014}_{-0.010}$ & $-0.035^{+0.014}_{-0.010}$\\
+SNF20070424-003 & $123.6^{+3.6}_{-3.6}$ & $ 14.2^{+1.2}_{-1.1}$ & $ 6134^{+  6}_{-  6}$ & $  0.30^{+  0.10}_{-  0.10}$ & $0.008^{+0.023}_{-0.023}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+SN2006cj & $101.4^{+1.3}_{-1.3}$ & $  5.5^{+0.8}_{-0.8}$ & $ 6128^{+  3}_{-  3}$ & $  0.86^{+  0.13}_{-  0.13}$ & $0.028^{+0.025}_{-0.025}$  & $0.006^{+0.008}_{-0.009}$ & $-0.017^{+0.013}_{-0.013}$ & $-0.017^{+0.013}_{-0.013}$\\
+SN2007nq & $ 91.2^{+9.1}_{-9.0}$ & $ 23.3^{+1.0}_{-1.0}$ & $ 6109^{+  5}_{-  5}$ & $ -1.90^{+  0.20}_{-  0.20}$ & $-0.075^{+0.038}_{-0.035}$  & $-0.022^{+0.015}_{-0.015}$ & $0.031^{+0.021}_{-0.020}$ & $0.031^{+0.021}_{-0.020}$\\
+SNF20070817-003 & $ 94.5^{+2.4}_{-2.4}$ & $ 18.1^{+1.1}_{-1.1}$ & $ 6115^{+  6}_{-  6}$ & $ -0.61^{+  0.12}_{-  0.12}$ & $0.050^{+0.031}_{-0.032}$  & $-0.031^{+0.012}_{-0.012}$ & $-0.024^{+0.015}_{-0.014}$ & $-0.024^{+0.015}_{-0.014}$\\
+SNF20070403-000 & $ 62.8^{+6.1}_{-6.2}$ & $ 27.6^{+1.6}_{-1.6}$ & $ 6154^{+  7}_{-  7}$ & $ -1.88^{+  0.17}_{-  0.17}$ & $0.147^{+0.040}_{-0.041}$  & $0.081^{+0.021}_{-0.021}$ & $0.041^{+0.025}_{-0.023}$ & $0.041^{+0.025}_{-0.023}$\\
+SNF20061022-005 & $ 63.4^{+3.6}_{-3.8}$ & $  3.9^{+1.4}_{-1.4}$ & $ 6147^{+  7}_{-  7}$ & $  2.03^{+  0.25}_{-  0.25}$ & $0.056^{+0.038}_{-0.038}$  & $0.041^{+0.018}_{-0.020}$ & $-0.000^{+0.022}_{-0.021}$ & $-0.000^{+0.022}_{-0.021}$\\
+SNNGC4076 & $127.1^{+2.4}_{-2.4}$ & $ 15.7^{+1.1}_{-1.1}$ & $ 6152^{+  4}_{-  4}$ & $  0.04^{+  0.10}_{-  0.10}$ & $-0.004^{+0.030}_{-0.029}$  & $0.049^{+0.013}_{-0.013}$ & $0.045^{+0.016}_{-0.015}$ & $0.045^{+0.016}_{-0.015}$\\
+SNF20070727-016 & $ 78.3^{+2.4}_{-2.5}$ & $  4.6^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  0.16^{+  0.11}_{-  0.10}$ & $-0.097^{+0.043}_{-0.036}$  & $-0.037^{+0.011}_{-0.011}$ & $-0.025^{+0.015}_{-0.014}$ & $-0.025^{+0.015}_{-0.014}$\\
+PTF12fuu & $105.4^{+3.0}_{-3.0}$ & $  6.5^{+1.0}_{-1.0}$ & $ 6124^{+  5}_{-  5}$ & $  0.37^{+  0.11}_{-  0.11}$ & $0.178^{+0.026}_{-0.026}$  & $-0.057^{+0.010}_{-0.010}$ & $-0.026^{+0.014}_{-0.013}$ & $-0.026^{+0.014}_{-0.013}$\\
+SNF20070820-000 & $107.1^{+3.4}_{-3.4}$ & $ 18.7^{+1.2}_{-1.2}$ & $ 6133^{+ 13}_{- 13}$ & $ -0.28^{+  0.12}_{-  0.12}$ & $-0.054^{+0.031}_{-0.030}$  & $0.051^{+0.012}_{-0.013}$ & $-0.015^{+0.018}_{-0.016}$ & $-0.015^{+0.018}_{-0.016}$\\
+SNF20070725-001 & $108.3^{+1.9}_{-1.9}$ & $  9.5^{+1.0}_{-1.1}$ & $ 6139^{+  6}_{-  6}$ & $  0.61^{+  0.15}_{-  0.15}$ & $0.058^{+0.033}_{-0.033}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.018^{+0.016}_{-0.015}$ & $-0.018^{+0.016}_{-0.015}$\\
+SNF20071108-021 & $ 98.7^{+2.7}_{-2.7}$ & $  6.0^{+0.8}_{-0.8}$ & $ 6165^{+  5}_{-  5}$ & $  1.15^{+  0.16}_{-  0.15}$ & $-0.045^{+0.028}_{-0.028}$  & $-0.028^{+0.012}_{-0.012}$ & $0.024^{+0.015}_{-0.014}$ & $0.024^{+0.015}_{-0.014}$\\
+SNF20080914-001 & $126.4^{+1.2}_{-1.2}$ & $ 16.3^{+1.0}_{-1.0}$ & $ 6159^{+  3}_{-  3}$ & $  0.10^{+  0.14}_{-  0.14}$ & $-0.144^{+0.026}_{-0.024}$  & $0.094^{+0.012}_{-0.012}$ & $0.022^{+0.016}_{-0.015}$ & $0.022^{+0.016}_{-0.015}$\\
+SNF20060609-002 & $ 86.3^{+3.5}_{-3.5}$ & $  8.1^{+1.2}_{-1.1}$ & $ 6132^{+  4}_{-  4}$ & $  0.18^{+  0.12}_{-  0.13}$ & $-0.069^{+0.033}_{-0.032}$  & $0.192^{+0.014}_{-0.014}$ & $-0.008^{+0.018}_{-0.017}$ & $-0.008^{+0.018}_{-0.017}$\\
+SNF20050624-000 & $119.9^{+5.1}_{-5.1}$ & $  7.9^{+2.4}_{-2.6}$ & $ 6126^{+  5}_{-  5}$ & $  0.47^{+  0.29}_{-  0.29}$ & $-0.171^{+0.026}_{-0.024}$  & $-0.051^{+0.019}_{-0.017}$ & $0.022^{+0.019}_{-0.021}$ & $0.022^{+0.019}_{-0.021}$\\
+SNF20060618-023 & $ 73.3^{+4.7}_{-4.7}$ & $  5.3^{+1.6}_{-1.5}$ & $ 6140^{+ 18}_{- 18}$ & $  0.18^{+  0.16}_{-  0.16}$ & $-0.229^{+0.039}_{-0.038}$  & $0.059^{+0.020}_{-0.020}$ & $0.092^{+0.023}_{-0.022}$ & $0.092^{+0.023}_{-0.022}$\\
+SNF20080531-000 & $133.2^{+1.5}_{-1.5}$ & $ 17.2^{+0.8}_{-0.8}$ & $ 6113^{+  5}_{-  5}$ & $ -0.63^{+  0.13}_{-  0.13}$ & $0.002^{+0.024}_{-0.024}$  & $-0.040^{+0.009}_{-0.009}$ & $-0.009^{+0.012}_{-0.013}$ & $-0.009^{+0.012}_{-0.013}$\\
+SN2006do & $106.3^{+2.1}_{-2.1}$ & $ 26.8^{+1.3}_{-1.2}$ & $ 6101^{+  2}_{-  2}$ & $ -1.95^{+  0.34}_{-  0.34}$ & $-0.077^{+0.031}_{-0.030}$  & $-0.038^{+0.012}_{-0.013}$ & $0.035^{+0.018}_{-0.017}$ & $0.035^{+0.018}_{-0.017}$\\
+PTF12ikt & $110.3^{+1.5}_{-1.6}$ & $ 14.0^{+0.7}_{-0.7}$ & $ 6141^{+  4}_{-  4}$ & $ -0.40^{+  0.10}_{-  0.10}$ & $-0.023^{+0.025}_{-0.025}$  & $-0.034^{+0.009}_{-0.008}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
+SN2006dm & $ 99.6^{+1.6}_{-1.6}$ & $ 29.8^{+0.7}_{-0.7}$ & $ 6118^{+  3}_{-  3}$ & $ -2.35^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.029}$  & $-0.047^{+0.011}_{-0.011}$ & $0.047^{+0.017}_{-0.016}$ & $0.047^{+0.017}_{-0.016}$\\
+PTF13azs & $140.6^{+4.8}_{-4.8}$ & $ 15.2^{+1.3}_{-1.3}$ & $ 6124^{+ 10}_{- 10}$ & $ -0.12^{+  0.11}_{-  0.11}$ & $0.148^{+0.029}_{-0.029}$  & $0.195^{+0.012}_{-0.013}$ & $-0.037^{+0.012}_{-0.009}$ & $-0.037^{+0.012}_{-0.009}$\\
+SN2005hj & $ 80.4^{+2.4}_{-2.4}$ & $  4.4^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  2.58^{+  0.24}_{-  0.24}$ & $0.076^{+0.039}_{-0.037}$  & $0.009^{+0.018}_{-0.020}$ & $0.066^{+0.022}_{-0.022}$ & $0.066^{+0.022}_{-0.022}$\\
+PTF12iiq & $149.1^{+2.1}_{-2.2}$ & $ 24.8^{+0.8}_{-0.7}$ & $ 6048^{+  7}_{-  7}$ & $ -0.83^{+  0.10}_{-  0.11}$ & $0.005^{+0.033}_{-0.033}$  & $-0.005^{+0.019}_{-0.020}$ & $-0.034^{+0.017}_{-0.010}$ & $-0.034^{+0.017}_{-0.010}$\\
+PTF10ndc & $124.1^{+2.4}_{-2.4}$ & $  6.7^{+1.0}_{-1.0}$ & $ 6119^{+  3}_{-  3}$ & $  0.86^{+  0.14}_{-  0.14}$ & $0.007^{+0.026}_{-0.025}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.023^{+0.014}_{-0.013}$ & $-0.023^{+0.014}_{-0.013}$\\
+SNF20080919-002 & $100.4^{+6.7}_{-6.6}$ & $ 26.3^{+1.7}_{-1.7}$ & $ 6133^{+  8}_{-  8}$ & $ -1.54^{+  0.13}_{-  0.13}$ & $0.340^{+0.043}_{-0.044}$  & $-0.058^{+0.017}_{-0.014}$ & $0.114^{+0.020}_{-0.021}$ & $0.114^{+0.020}_{-0.021}$\\
+SNPGC027923 & $ 85.4^{+0.6}_{-0.6}$ & $  5.8^{+0.3}_{-0.3}$ & $ 6130^{+  4}_{-  4}$ & $  0.45^{+  0.17}_{-  0.17}$ & $0.078^{+0.032}_{-0.031}$  & $-0.077^{+0.006}_{-0.005}$ & $-0.026^{+0.015}_{-0.013}$ & $-0.026^{+0.015}_{-0.013}$\\
+SNF20070330-024 & $118.3^{+2.1}_{-2.1}$ & $  5.5^{+1.8}_{-1.8}$ & $ 6101^{+  3}_{-  3}$ & $  0.48^{+  0.19}_{-  0.21}$ & $-0.166^{+0.025}_{-0.024}$  & $-0.040^{+0.014}_{-0.014}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
+SNF20061030-010 & $131.6^{+2.2}_{-2.2}$ & $ 16.9^{+1.1}_{-1.1}$ & $ 6116^{+  4}_{-  4}$ & $ -0.10^{+  0.20}_{-  0.20}$ & $0.103^{+0.041}_{-0.041}$  & $0.049^{+0.012}_{-0.012}$ & $0.019^{+0.021}_{-0.021}$ & $0.019^{+0.021}_{-0.021}$\\
+SNhunt46 & $ 93.8^{+2.0}_{-2.0}$ & $ 11.2^{+0.6}_{-0.6}$ & $ 6133^{+  4}_{-  4}$ & $  0.22^{+  0.17}_{-  0.17}$ & $0.150^{+0.032}_{-0.032}$  & $-0.062^{+0.010}_{-0.010}$ & $0.035^{+0.016}_{-0.015}$ & $0.035^{+0.016}_{-0.015}$\\
+SN2005hc & $127.2^{+2.4}_{-2.5}$ & $  9.7^{+0.7}_{-0.7}$ & $ 6122^{+  3}_{-  3}$ & $  0.47^{+  0.16}_{-  0.15}$ & $0.137^{+0.025}_{-0.025}$  & $-0.062^{+0.008}_{-0.008}$ & $0.001^{+0.012}_{-0.012}$ & $0.001^{+0.012}_{-0.012}$\\
+LSQ12dbr & $106.9^{+0.6}_{-0.6}$ & $  6.4^{+0.6}_{-0.6}$ & $ 6137^{+  4}_{-  4}$ & $  0.86^{+  0.11}_{-  0.11}$ & $0.004^{+0.226}_{-0.109}$  & $-0.071^{+0.008}_{-0.007}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
+LSQ12hjm & $ 65.3^{+10.8}_{-11.3}$ & $ 15.3^{+1.1}_{-1.1}$ & $ 6147^{+  5}_{-  5}$ & $ -0.16^{+  0.17}_{-  0.17}$ & $0.112^{+0.030}_{-0.031}$  & $-0.062^{+0.013}_{-0.011}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
+SNF20060521-001 & $ 89.1^{+11.4}_{-12.2}$ & $ 19.1^{+1.1}_{-1.1}$ & $ 6119^{+ 10}_{-  9}$ & $ -1.70^{+  0.20}_{-  0.20}$ & $0.029^{+0.061}_{-0.059}$  & $-0.068^{+0.014}_{-0.010}$ & $0.010^{+0.019}_{-0.020}$ & $0.010^{+0.019}_{-0.020}$\\
+SNF20070630-006 & $126.3^{+3.1}_{-3.1}$ & $ 10.3^{+1.1}_{-1.2}$ & $ 6126^{+  4}_{-  4}$ & $  0.30^{+  0.11}_{-  0.11}$ & $-0.018^{+0.025}_{-0.025}$  & $-0.027^{+0.010}_{-0.010}$ & $-0.040^{+0.010}_{-0.008}$ & $-0.040^{+0.010}_{-0.008}$\\
+PTF11drz & $132.6^{+1.4}_{-1.4}$ & $ 14.9^{+0.9}_{-0.9}$ & $ 6116^{+  4}_{-  4}$ & $ -0.11^{+  0.17}_{-  0.18}$ & $-0.007^{+0.025}_{-0.026}$  & $-0.021^{+0.010}_{-0.009}$ & $-0.016^{+0.013}_{-0.013}$ & $-0.016^{+0.013}_{-0.013}$\\
+SNF20080323-009 & $ 96.0^{+2.2}_{-2.2}$ & $ 11.1^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.15^{+  0.14}_{-  0.14}$ & $-0.029^{+0.030}_{-0.029}$  & $-0.051^{+0.011}_{-0.011}$ & $-0.041^{+0.009}_{-0.008}$ & $-0.041^{+0.009}_{-0.008}$\\
+SNF20071021-000 & $167.9^{+2.2}_{-2.2}$ & $ 20.2^{+0.6}_{-0.6}$ & $ 6111^{+  4}_{-  4}$ & $ -0.66^{+  0.13}_{-  0.13}$ & $-0.105^{+0.025}_{-0.023}$  & $-0.001^{+0.010}_{-0.010}$ & $-0.004^{+0.013}_{-0.013}$ & $-0.004^{+0.013}_{-0.013}$\\
+SNNGC0927 & $155.2^{+1.3}_{-1.3}$ & $ 10.9^{+0.7}_{-0.7}$ & $ 6109^{+  4}_{-  4}$ & $  0.39^{+  0.12}_{-  0.12}$ & $-0.031^{+0.027}_{-0.027}$  & $0.039^{+0.010}_{-0.010}$ & $-0.018^{+0.014}_{-0.013}$ & $-0.018^{+0.014}_{-0.013}$\\
+SNF20060526-003 & $111.8^{+2.5}_{-2.5}$ & $  9.9^{+1.0}_{-1.0}$ & $ 6121^{+  3}_{-  3}$ & $  0.34^{+  0.13}_{-  0.13}$ & $-0.004^{+0.026}_{-0.027}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.011^{+0.014}_{-0.014}$ & $-0.011^{+0.014}_{-0.014}$\\
+SNF20080806-002 & $135.4^{+1.8}_{-1.9}$ & $  8.3^{+0.9}_{-0.9}$ & $ 6136^{+  4}_{-  4}$ & $  0.83^{+  0.14}_{-  0.14}$ & $-0.106^{+0.028}_{-0.027}$  & $0.020^{+0.010}_{-0.010}$ & $-0.036^{+0.013}_{-0.009}$ & $-0.036^{+0.013}_{-0.009}$\\
+SNF20080803-000 & $118.3^{+2.5}_{-2.6}$ & $  8.4^{+1.3}_{-1.4}$ & $ 6125^{+  4}_{-  4}$ & $  0.25^{+  0.12}_{-  0.12}$ & $-0.030^{+0.023}_{-0.024}$  & $0.100^{+0.011}_{-0.011}$ & $-0.040^{+0.009}_{-0.008}$ & $-0.040^{+0.009}_{-0.008}$\\
+SNF20080822-005 & $ 78.6^{+1.8}_{-1.8}$ & $  6.2^{+0.8}_{-0.8}$ & $ 6138^{+  4}_{-  4}$ & $  0.51^{+  0.16}_{-  0.16}$ & $-0.027^{+0.030}_{-0.030}$  & $-0.018^{+0.011}_{-0.010}$ & $0.014^{+0.015}_{-0.015}$ & $0.014^{+0.015}_{-0.015}$\\
+SNF20060618-014 & $136.8^{+2.4}_{-2.5}$ & $  9.8^{+1.1}_{-1.1}$ & $ 6113^{+  7}_{-  7}$ & $  1.20^{+  0.18}_{-  0.18}$ & $0.077^{+0.047}_{-0.047}$  & $-0.037^{+0.014}_{-0.014}$ & $0.019^{+0.025}_{-0.024}$ & $0.019^{+0.025}_{-0.024}$\\
+PTF12ghy & $100.6^{+3.5}_{-3.5}$ & $ 16.4^{+0.7}_{-0.7}$ & $ 6133^{+  3}_{-  3}$ & $ -0.58^{+  0.10}_{-  0.10}$ & $-0.138^{+0.023}_{-0.022}$  & $0.196^{+0.011}_{-0.011}$ & $0.001^{+0.013}_{-0.013}$ & $0.001^{+0.013}_{-0.013}$\\
+SNF20070531-011 & $122.2^{+2.6}_{-2.6}$ & $ 21.5^{+0.8}_{-0.8}$ & $ 6114^{+  3}_{-  4}$ & $ -1.56^{+  0.20}_{-  0.20}$ & $-0.081^{+0.027}_{-0.025}$  & $-0.032^{+0.011}_{-0.011}$ & $-0.000^{+0.015}_{-0.014}$ & $-0.000^{+0.015}_{-0.014}$\\
+SNF20070831-015 & $112.9^{+2.6}_{-2.6}$ & $  6.9^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  1.38^{+  0.16}_{-  0.16}$ & $0.042^{+0.027}_{-0.027}$  & $-0.016^{+0.010}_{-0.010}$ & $0.002^{+0.014}_{-0.014}$ & $0.002^{+0.014}_{-0.014}$\\
+SNF20070417-002 & $103.8^{+5.0}_{-4.9}$ & $ 24.1^{+1.3}_{-1.3}$ & $ 6125^{+  8}_{-  9}$ & $ -1.37^{+  0.10}_{-  0.10}$ & $-0.032^{+0.050}_{-0.044}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+PTF11cao & $143.4^{+1.5}_{-1.6}$ & $ 19.0^{+1.1}_{-1.1}$ & $ 6104^{+  4}_{-  4}$ & $  0.20^{+  0.13}_{-  0.13}$ & $-0.014^{+0.032}_{-0.031}$  & $0.009^{+0.013}_{-0.013}$ & $-0.017^{+0.017}_{-0.015}$ & $-0.017^{+0.017}_{-0.015}$\\
+SNF20080522-000 & $ 62.1^{+3.5}_{-3.5}$ & $  3.1^{+0.8}_{-0.8}$ & $ 6130^{+  7}_{-  7}$ & $  0.99^{+  0.11}_{-  0.11}$ & $-0.021^{+0.028}_{-0.028}$  & $-0.009^{+0.012}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$\\
+PTF10qjq & $ 74.4^{+2.3}_{-2.4}$ & $ 12.0^{+0.7}_{-0.7}$ & $ 6132^{+  3}_{-  3}$ & $ -0.50^{+  0.10}_{-  0.09}$ & $-0.127^{+0.026}_{-0.024}$  & $0.049^{+0.010}_{-0.011}$ & $-0.010^{+0.015}_{-0.015}$ & $-0.010^{+0.015}_{-0.015}$\\
+PTF12dxm & $119.3^{+15.5}_{-16.8}$ & $ 31.3^{+1.9}_{-2.1}$ & $ 6136^{+  4}_{-  4}$ & $ -2.14^{+  0.18}_{-  0.18}$ & $0.034^{+0.034}_{-0.033}$  & $-0.047^{+0.027}_{-0.021}$ & $0.067^{+0.023}_{-0.024}$ & $0.067^{+0.023}_{-0.024}$\\
+SNF20061021-003 & $122.5^{+2.2}_{-2.2}$ & $ 10.8^{+1.5}_{-1.5}$ & $ 6131^{+  4}_{-  4}$ & $  0.39^{+  0.15}_{-  0.15}$ & $-0.012^{+0.035}_{-0.033}$  & $0.036^{+0.014}_{-0.014}$ & $0.047^{+0.019}_{-0.017}$ & $0.047^{+0.019}_{-0.017}$\\
+SNF20080510-005 & $112.2^{+2.5}_{-2.5}$ & $  7.0^{+1.0}_{-1.0}$ & $ 6117^{+  4}_{-  4}$ & $  1.68^{+  0.22}_{-  0.22}$ & $0.116^{+0.030}_{-0.030}$  & $-0.029^{+0.013}_{-0.015}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
+SNF20080507-000 & $ 98.4^{+1.6}_{-1.6}$ & $  8.0^{+1.7}_{-1.6}$ & $ 6142^{+  5}_{-  5}$ & $  0.56^{+  0.18}_{-  0.18}$ & $-0.126^{+0.023}_{-0.022}$  & $0.063^{+0.014}_{-0.013}$ & $-0.003^{+0.015}_{-0.014}$ & $-0.003^{+0.015}_{-0.014}$\\
+SNF20080913-031 & $117.9^{+1.5}_{-1.5}$ & $ 14.7^{+1.6}_{-1.6}$ & $ 6159^{+  5}_{-  5}$ & $  0.49^{+  0.17}_{-  0.17}$ & $-0.048^{+0.067}_{-0.052}$  & $-0.003^{+0.015}_{-0.015}$ & $-0.009^{+0.020}_{-0.018}$ & $-0.009^{+0.020}_{-0.018}$\\
+SNF20080510-001 & $118.9^{+2.0}_{-2.1}$ & $ 15.0^{+1.1}_{-1.0}$ & $ 6115^{+  4}_{-  4}$ & $  0.34^{+  0.14}_{-  0.14}$ & $0.001^{+0.026}_{-0.026}$  & $-0.058^{+0.011}_{-0.012}$ & $-0.032^{+0.012}_{-0.011}$ & $-0.032^{+0.012}_{-0.011}$\\
+SNF20070712-003 & $108.1^{+2.7}_{-2.6}$ & $ 14.1^{+0.9}_{-0.9}$ & $ 6157^{+  6}_{-  6}$ & $  0.62^{+  0.14}_{-  0.14}$ & $-0.034^{+0.030}_{-0.029}$  & $-0.052^{+0.010}_{-0.011}$ & $-0.021^{+0.015}_{-0.014}$ & $-0.021^{+0.015}_{-0.014}$\\
+\enddata
+\end{deluxetable}
+}
+
 The distributions of the Monte Carlo links for all supernovae are shown in Figure~\ref{perobject3:fig}.

### 2018-05-08 tablef3_x1.py

@@ -12,6 +12,7 @@ f = open('fix3_x1_decorr.pkl','rb')
 fit = pickle.load(f)
 f.close()
 
+
 for key in fit.keys():
     print key, fit[key].min(), fit[key].max()
 
@@ -191,7 +192,7 @@ pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)
 pkl_file.close()
 
-sivel, sivel_err, _,_,_,_,_,EWFe4800 = sivel.sivel(data)
+sivel, sivel_err,x1,x1_err,_,_,_,EWFe4800 = sivel.sivel(data)
 
 
 use = numpy.isfinite(sivel)
@@ -205,6 +206,8 @@ mag_cov = data['cov'][:,2:,2:]
 
 sivel=sivel[use]
 sivel_err = sivel_err[use]
+x1 = x1[use]
+x1_err = x1_err[use]
 EWFe4800=EWFe4800[use]
 EW_obs=EW_obs[use]
 mag_obs=mag_obs[use]
@@ -221,8 +224,6 @@ for i in xrange(fit['mag_int_raw'].shape[0]):
     shit.append(numpy.corrcoef(numpy.array([EWFe4800, fit['mag_int_raw'][i,:]]))[0,1])
 (y,ymin,ymax) = numpy.percentile(shit,(50,50-34,50+34),axis=0)
 print y, y-ymin,ymax-y
-
-wefwe
 
 trans = [[1.,0,-1,0,0],[0.,1,-1,0,0],[0.,0,1,-1,0],[0.,0,1,0,-1]]
 trans = numpy.array(trans)
@@ -244,7 +245,31 @@ print numpy.median(shit)
 
 snname=numpy.array(data['snlist'])[use]
 
+print 'outputs'
+
+EW_mn = EW_obs.mean(axis=0)
+sivel_mn = sivel.mean()
 for i in xrange(len(sivel)):
[…]

### 2018-05-08 viewf3_x1.py

@@ -32,41 +32,8 @@ pkl_file.close()
 
 # dic_meta=cPickle.load(open("META.pkl"))
 
-# sivel=[]
-# sivel_err=[]
-# x1 = []
-# x1_err = []
-# for sn in data['snlist']:
-#    if sn in dic_meta.keys() and sn in dic_phreno.keys():
-#       meta = dic_meta[sn]
-#       vSiII_6355_lbd=0.
-#       vSiII_6355_lbd_err=0.
-#       counter  = 0
-#       for sp in dic_phreno[sn]["spectra"]:
-#          if sp in meta['spectra'].keys() and  numpy.abs(meta['spectra'][sp]['salt2.phase']) < 2.5  and numpy.isfinite(dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]):
-#             vSiII_6355_lbd += dic_phreno[sn]["spectra"][sp]["phrenology.vSiII_6355_lbd"]/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
-#             vSiII_6355_lbd_err += 1/dic_phreno[sn]['spectra'][sp]["phrenology.vSiII_6355_lbd.err"]**2
-#             counter +=1
-#       if counter !=0:
-#          sivel.append(vSiII_6355_lbd / vSiII_6355_lbd_err)
-#          sivel_err.append(1./numpy.sqrt(vSiII_6355_lbd_err))
-#       else:
-#          sivel.append(float('nan'))
-#          sivel_err.append(float('nan'))
-#       x1.append(meta['salt2.X1'])
-#       x1_err.append(numpy.sqrt(meta['salt2.CovX1X1']))
-#    else:
-#       sivel.append(float('nan'))
-#       sivel_err.append(float('nan'))
-#       x1.append(float('nan'))
-#       x1_err.append(float('nan'))
 
-# sivel = numpy.array(sivel)
-# sivel_err = numpy.array(sivel_err)
-# x1 = numpy.array(x1)
-# x1_err = numpy.array(x1_err)
-
-sivel,sivel_err,x1,x1_err, zcmb, _, _ = sivel.sivel(data)
+sivel,sivel_err,x1,x1_err, zcmb, _, _, _, c = sivel.sivel(data)
 use = numpy.isfinite(sivel)
 
 #  The ordering is 'Ca','Si','U','B','V','R','I'
[…]

### 2018-05-16 submit/fix.tex
progress to printing covariance matrix

@@
 
+\added{
+SNfactory observed supernovae in the redshift range $z \lesssim 0.09$, with a preference for $0.03 < z < 0.08$,
+whose first SNIFS observation was projected to be $\lesssim -5$ days before $B$-band peak brightness.
+Telescope availability and observing conditions dictated which supernovae eventually would accumulate multiple observations 
+over the course of their light curves that would give constraining light curve (e.g.\ SALT2) fits.  At an occurence of $< 10\%$ individual spectral extractions 
+}
+
 Our analysis sample is comprised of the
@@
 \tablehead{
-\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} & \colhead{$x_1$}
+\colhead{Name} & \colhead{$EW_{\mathrm{Ca}}$ (\AA)} & \colhead{$EW_{\mathrm{Si}}$ (\AA)} & \colhead{$\lambda_{\mathrm{Si}}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} & \colhead{$x_1$}
 }
@@
 \end{deluxetable}
+
+The distributions of the central values of the inputs  $EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$,
+$\lambda_{\mathrm{Si}}$ , $x_1$, and the SALT2 color parameter $C$ are shown in Table~\ref{input:fig}.
+For reference, the $x_1$ and $C$ distributions of the $0.03<z< 0.08$ Pantheon sample,
+predominantly supernovae from CFA3 \citep{2009ApJ...700..331H}, CFA4 \citep{2012ApJS..200...12H}, and CSP
+\citep{2010AJ....139..519C, 2011AJ....142..156S}, that were used as part of the low-redshift anchor in the recent cosmology analysis of \citet{2017arXiv171000845S}.
+
+\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
+   \centering
+   \includegraphics[width=4in]{perobject_input.pdf}
+   \caption{Distributions of the central values of the inputs  $EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$,
+$\lambda_{\mathrm{Si}}$ , $x_1$, and $C$ of the sample used in this article, and
+the $x_1$ and $C$ distributions of the $0.03<z< 0.08$ Pantheon sample,
+   \label{input:fig}}
+\end{figure}
 }
@@
  equivalent widths of the Ca~II H\&K and Si~II~$\lambda$4141 spectral features
-$EW_{Ca}$ and $EW_{Si}$,
+$EW_{\mathrm{Ca}}$ and $EW_{\mathrm{Si}}$,
 and the wavelength of the minimum of 
-the Si~II~$\lambda6355$ feature $\lambda_{Si}$
+the Si~II~$\lambda6355$ feature $\lambda_{\mathrm{Si}}$
 around $B$-band peak brightness:
@@
 The explicit omission of light-curve shape in our model is compensated by its proxy,
-$EW_{Si}$, at peak brightness
+$EW_{\mathrm{Si}}$, at peak brightness
 \citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
@@
 Unlike
-the spectral parameters ($EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$),  $g_0$ and $g_1$ are not directly associated
+the spectral parameters ($EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$ and $\lambda_{\mathrm{Si}}$),  $g_0$ and $g_1$ are not directly associated
 with observables but rather are inferred as part of the analysis.
@@
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si}  +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 \\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si}  +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 \\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}  +\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{\mathrm{Ca}} + \beta_{\hat{U}} EW_{\mathrm{Si}} + \eta_{\hat{U}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{\mathrm{Ca}} + \beta_{\hat{B}} EW_{\mathrm{Si}} + \eta_{\hat{B}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{\mathrm{Ca}} + \beta_{\hat{V}} EW_{\mathrm{Si}} + \eta_{\hat{V}} \lambda_{\mathrm{Si}} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 \\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{\mathrm{Ca}} + \beta_{\hat{R}} EW_{\mathrm{Si}} + \eta_{\hat{R}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 \\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{\mathrm{Ca}} + \beta_{\hat{I}} EW_{\mathrm{Si}}+ \eta_{\hat{I}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1
 \end{pmatrix}.
@@
 {\hat{V}}\\{\hat{R}}\\{\hat{I}}\\
-EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
+EW_{\mathrm{Si}}\\ EW_{\mathrm{Ca}} \\ \lambda_{\mathrm{Si}}
 \end{pmatrix}
@@
 \epsilon_\Delta  = -  \epsilon_{\alpha} (EW_{\text{Ca}}-\langle EW_{\text{Ca}}\rangle)- 
- \epsilon_{\beta} (EW_{Si}-\langle EW_{Si}\rangle) -  \epsilon_{\eta} (\lambda_{Si}-\langle \lambda_{Si}\rangle)
+ \epsilon_{\beta} (EW_{\mathrm{Si}}-\langle EW_{\mathrm{Si}}\rangle) -  \epsilon_{\eta} (\lambda_{\mathrm{Si}}-\langle \lambda_{\mathrm{Si}}\rangle)
 - \epsilon_{\gamma^0}g_0 -  \epsilon_{\gamma^1}g_1.
@@
 We break this degeneracy by fixing the values of $\epsilon$ such that $\Delta$ is
-uncorrelated with  $EW_{\text{Ca}}$, $EW_{Si}$, $\lambda_{\text{Ca}}$,
+uncorrelated with  $EW_{\text{Ca}}$, $EW_{\mathrm{Si}}$, $\lambda_{\text{Ca}}$,
 $g_0$, and $g_1$ reflecting
@@
 as this value is not fundamentally constrained by the model but is fixed by the added condition that $\Delta$ is
-uncorrelated with  $EW_{\text{Ca}}$, $EW_{Si}$, $\lambda_{\text{Ca}}$,
+uncorrelated with  $EW_{\text{Ca}}$, $EW_{\mathrm{Si}}$, $\lambda_{\text{Ca}}$,
 $g_0$, and $g_1$.  The value of  $\langle R^F\rangle$ changes given different ansatzes  for breaking the $\Delta$--cofactor degeneracy 
@@
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si}+\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1  + \sigma_p\phi_{\hat{U}} p\\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1  + \sigma_p\phi_{\hat{B}} p\\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 + \sigma_p\phi_{\hat{V}}  p\\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 + \sigma_p\phi_{\hat{R}} p\\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1 + \sigma_p\phi_{\hat{I}}  p
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{\mathrm{Ca}} + \beta_{\hat{U}} EW_{\mathrm{Si}} + \eta_{\hat{U}} \lambda_{\mathrm{Si}}+\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1  + \sigma_p\phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{\mathrm{Ca}} + \beta_{\hat{B}} EW_{\mathrm{Si}} + \eta_{\hat{B}} \lambda_{\mathrm{Si}} +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1  + \sigma_p\phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{\mathrm{Ca}} + \beta_{\hat{V}} EW_{\mathrm{Si}} + \eta_{\hat{V}} \lambda_{\mathrm{Si}} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 + \sigma_p\phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{\mathrm{Ca}} + \beta_{\hat{R}} EW_{\mathrm{Si}} + \eta_{\hat{R}} \lambda_{\mathrm{Si}} +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 + \sigma_p\phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{\mathrm{Ca}} + \beta_{\hat{I}} EW_{\mathrm{Si}}+ \eta_{\hat{I}} \lambda_{\mathrm{Si}}+\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1 + \sigma_p\phi_{\hat{I}}  p
 \end{pmatrix}.
@@
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si} +\zeta_{\hat{U}} x_1 +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 + \sigma_p\phi_{\hat{U}} p\\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si} +\zeta_{\hat{B}} x_1 +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 + \sigma_p\phi_{\hat{B}} p\\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\zeta_{\hat{V}} x_1+\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 + \sigma_p\phi_{\hat{V}}  p\\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si} +\zeta_{\hat{R}} x_1+\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 + \sigma_p\phi_{\hat{R}} p\\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}+\zeta_{\hat{I}} x_1+\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1 + \sigma_p\phi_{\hat{I}}  p
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{\mathrm{Ca}} + \beta_{\hat{U}} EW_{\mathrm{Si}} + \eta_{\hat{U}} \lambda_{\mathrm{Si}} +\zeta_{\hat{U}} x_1 +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 + \sigma_p\phi_{\hat{U}} p\\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{\mathrm{Ca}} + \beta_{\hat{B}} EW_{\mathrm{Si}} + \eta_{\hat{B}} \lambda_{\mathrm{Si}} +\zeta_{\hat{B}} x_1 +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 + \sigma_p\phi_{\hat{B}} p\\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{\mathrm{Ca}} + \beta_{\hat{V}} EW_{\mathrm{Si}} + \eta_{\hat{V}} \lambda_{\mathrm{Si}} +\zeta_{\hat{V}} x_1+\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 + \sigma_p\phi_{\hat{V}}  p\\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{\mathrm{Ca}} + \beta_{\hat{R}} EW_{\mathrm{Si}} + \eta_{\hat{R}} \lambda_{\mathrm{Si}} +\zeta_{\hat{R}} x_1+\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 + \sigma_p\phi_{\hat{R}} p\\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{\mathrm{Ca}} + \beta_{\hat{I}} EW_{\mathrm{Si}}+ \eta_{\hat{I}} \lambda_{\mathrm{Si}}+\zeta_{\hat{I}} x_1+\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1 + \sigma_p\phi_{\hat{I}}  p
 \end{pmatrix},
@@
 {\hat{V}}\\{\hat{R}}\\{\hat{I}}\\
-EW_{Si}\\ EW_{Ca} \\ \lambda_{Si} \\ x_1
+EW_{\mathrm{Si}}\\ EW_{\mathrm{Ca}} \\ \lambda_{\mathrm{Si}} \\ x_1
 \end{pmatrix}
@@
 The cofactors  $\vec{\alpha}$, $\vec{\beta}$, and $\vec{\eta}$ have  significant non-zero values,  meaning that
-$EW_{Ca}$, $EW_{Si}$, and $\lambda_{Si}$ are indicators of broadband
+$EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$, and $\lambda_{\mathrm{Si}}$ are indicators of broadband
 colors at peak.  The significance of their influence varies between  colors; in $\hat{B}-\hat{V}$, roughly the color
@@
  that $\vec{\zeta}$, the magnitude vector associated with $x_1$, is highly correlated with $\vec{\beta}$, the vector
- associated with  $EW_{Si}$.
-The direct correlation between  $x_1$ and $EW_{Si}$ has already been established
+ associated with  $EW_{\mathrm{Si}}$.
+The direct correlation between  $x_1$ and $EW_{\mathrm{Si}}$ has already been established
 \citep{2008A&A...492..535A, 2011A&A...529L...4C}
@@
 \label{results3per:sec}
-Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$,
+Each supernova is described by its parameters $\Delta$, $EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$, $\lambda_{\mathrm{Si}}$, $x_1$,
 $E_{\gamma^0}({\hat{B}}-{\hat{V}})=(\gamma^0_{\hat{B}}-\gamma^0_{\hat{V}})g_0$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})=(\gamma^1_{\hat{B}}-\gamma^1_{\hat{V}})g_1$, and $A_{p,V} =  \sigma_p\phi_{\hat{V}}p$.
@@
 \tablehead{
-\colhead{Name} & \colhead{$EW_{Ca}$ (\AA)} & \colhead{$EW_{Si}$ (\AA)} & \colhead{$\lambda_{Si}$ (\AA)} & \colhead{$x_1$} & \colhead{$\Delta$}
+\colhead{Name} & \colhead{$EW_{\mathrm{Ca}}$ (\AA)} & \colhead{$EW_{\mathrm{Si}}$ (\AA)} & \colhead{$\lambda_{\mathrm{Si}}$ (\AA)} & \colhead{$x_1$} & \colhead{$\Delta$}
 & \colhead{$E_{\gamma^0}({\hat{B}}-{\hat{V}})$} & \colhead{$E_{\gamma^1}({\hat{B}}-{\hat{V}})$} & \colhead{$A_{p,V} $}
@@
 \begin{multline}
-Cor(EW_{Ca}, EW_{Si}, \lambda_{Si}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}) =\\
+Cor(EW_{\mathrm{Ca}}, EW_{\mathrm{Si}}, \lambda_{\mathrm{Si}}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}) =\\
 \begin{pmatrix}
 \begin{array}{rrrrrrr}
-EW_{Ca} & 0.10^{+0.03}_{-0.03} & -0.25^{+0.03}_{-0.03} & 0.07^{+0.03}_{-0.03} & -0.10^{+0.05}_{-0.05} & -0.18^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
-\ldots &EW_{Si} & -0.12^{+0.03}_{-0.03} & -0.84^{+0.01}_{-0.01} & -0.13^{+0.04}_{-0.04} & 0.27^{+0.08}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
-\ldots & \ldots& \lambda_{Si} & 0.14^{+0.03}_{-0.03} & 0.01^{+0.06}_{-0.05} & 0.00^{+0.06}_{-0.06} & -0.00^{+0.08}_{-0.08} \\
+EW_{\mathrm{Ca}} & 0.10^{+0.03}_{-0.03} & -0.25^{+0.03}_{-0.03} & 0.07^{+0.03}_{-0.03} & -0.10^{+0.05}_{-0.05} & -0.18^{+0.06}_{-0.06} & 0.00^{+0.08}_{-0.08} \\
+\ldots &EW_{\mathrm{Si}} & -0.12^{+0.03}_{-0.03} & -0.84^{+0.01}_{-0.01} & -0.13^{+0.04}_{-0.04} & 0.27^{+0.08}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
+\ldots & \ldots& \lambda_{\mathrm{Si}} & 0.14^{+0.03}_{-0.03} & 0.01^{+0.06}_{-0.05} & 0.00^{+0.06}_{-0.06} & -0.00^{+0.08}_{-0.08} \\
 \ldots& \ldots& \ldots& x_1 & 0.13^{+0.04}_{-0.04} & -0.20^{+0.09}_{-0.09} & -0.00^{+0.08}_{-0.08} \\
@@
    \caption{
-   Distributions for the supernova parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $x_1$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and  $A_{p,V}$, as well as the grey offset
+   Distributions for the supernova parameters $\Delta$, $EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$, $\lambda_{\mathrm{Si}}$, $x_1$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$,  $E_{\gamma^1}({\hat{B}}-{\hat{V}})$,  and  $A_{p,V}$, as well as the grey offset
 $\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
@@
 set can be found in \citet{chotard:thesis, leget:thesis, 2017Chotard}. 
-We here confine ourselves to noting the strong anti-correlation between $EW_{Si}$ and $x_1$, which was alluded
+We here confine ourselves to noting the strong anti-correlation between $EW_{\mathrm{Si}}$ and $x_1$, which was alluded
 to in \S\ref{results3global:sec} when interpreting the correlation between the cofactors $\vec{\beta}$ and $\vec{\zeta}$ that connect them with magnitudes.
@@
 There are $>2 \sigma$ correlations between our  color-excess parameters $g_0$, $g_1$
-and the input features  $EW_{Ca}$,
-$EW_{Si}$, and $x_1$. 
+and the input features  $EW_{\mathrm{Ca}}$,
+$EW_{\mathrm{Si}}$, and $x_1$. 
 Given the association
 of  $g$ with dust-extinction parameters, this implies that the host environment and the input features are connected.
-The correlations between $EW_{Si}$ and  $EW_{Ca}$  with host have already been noted \citep{2011ApJ...734...42N, 2015MNRAS.451.1973S}.
-There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{Si}$
+The correlations between $EW_{\mathrm{Si}}$ and  $EW_{\mathrm{Ca}}$  with host have already been noted \citep{2011ApJ...734...42N, 2015MNRAS.451.1973S}.
+There is a lack of correlation between  $g_0$, $g_1$ and  our velocity parameter $\lambda_{\mathrm{Si}}$
 (measured at peak brightness).
@@
 redshifts of 0.0015 and 0.0086. 
-Eq.~\ref{corr:eqn} shows $>2 \sigma$ correlations between $\Delta$ and each of $\lambda_{Si}$, $x_1$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$, and
+\replaced{
+Eq.~\ref{corr:eqn} shows $>2 \sigma$ correlations between $\Delta$ and each of $\lambda_{\mathrm{Si}}$, $x_1$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$, and
 $\sigma_p\phi_{\hat{V}}p$, showing that in addition to standardizing colors, these features can also be used to standardize
-absolute magnitudes.   
+absolute magnitudes.  }{Recall that model degeneracy between $\Delta$ and the cofactors such as $\alpha$, $\beta$ is removed by enforcing
+zero correlation between $\Delta$ and the per-supernova parameters such as $EW_{\mathrm{Ca}}$,  $EW_{\mathrm{Si}}$.
+An alternative method to break the degeneracy is to minimize the dispersion in $\Delta$.
+}
 The focus of this article is color standardization so we defer consideration of absolute-magnitude standardization to future work.
@@
 
-%\bibliographystyle{aasjournal}
-%\bibliography{alex}
-\input{fix.bbl}
+\section{Covariance Matrix for Model~III Global Parameters}
+\setcounter{MaxMatrixCols}{40}
+\begin{equation}
+\tiny
+\begin{bmatrix}
+5.48e-07 & -1.77e-06 & 3.87e-07 & -1.63e-05 & 2.14e-04 & -2.59e-04 & 3.59e-06 & 4.51e-07 & -1.46e-06 & 3.12e-07 & -1.32e-05 & 2.60e-04 & -1.34e-04 & 2.78e-06 & 3.58e-07 & -1.16e-06 & 2.40e-07 & -1.04e-05 & 1.90e-04 & -5.51e-05 & 1.70e-06 & 2.87e-07 & -9.20e-07 & 1.88e-07 & -8.14e-06 & 1.09e-04 & -1.66e-05 & 1.05e-06 & 2.24e-07 & -7.21e-07 & 1.43e-07 & -6.30e-06 & -3.58e-05 & -6.71e-06 & 4.73e-07 \\
+-1.77e-06 & 2.70e-05 & -2.60e-06 & 1.85e-04 & -4.04e-03 & -3.01e-03 & -1.78e-05 & -1.45e-06 & 2.18e-05 & -2.12e-06 & 1.49e-04 & -3.25e-03 & -2.66e-03 & -1.43e-05 & -1.14e-06 & 1.72e-05 & -1.59e-06 & 1.17e-04 & -2.58e-03 & -2.14e-03 & -1.00e-05 & -9.23e-07 & 1.40e-05 & -1.22e-06 & 9.43e-05 & -2.01e-03 & -1.63e-03 & -7.87e-06 & -7.31e-07 & 1.14e-05 & -8.85e-07 & 7.62e-05 & -1.09e-03 & -1.17e-03 & -5.25e-06 \\
+3.87e-07 & -2.60e-06 & 1.26e-06 & -2.22e-05 & 3.88e-04 & 1.66e-03 & 1.04e-05 & 3.23e-07 & -2.15e-06 & 1.02e-06 & -1.82e-05 & 4.99e-04 & 1.38e-03 & 8.28e-06 & 2.38e-07 & -1.47e-06 & 7.79e-07 & -1.31e-05 & 5.44e-04 & 1.02e-03 & 6.05e-06 & 1.86e-07 & -1.12e-06 & 6.13e-07 & -1.01e-05 & 4.13e-04 & 8.00e-04 & 4.56e-06 & 1.39e-07 & -8.12e-07 & 4.67e-07 & -7.36e-06 & 1.56e-04 & 5.93e-04 & 3.15e-06 \\
+-1.63e-05 & 1.85e-04 & -2.22e-05 & 1.57e-03 & -2.93e-02 & -1.45e-02 & -2.66e-04 & -1.33e-05 & 1.50e-04 & -1.80e-05 & 1.27e-03 & -2.77e-02 & -1.31e-02 & -2.13e-04 & -1.04e-05 & 1.17e-04 & -1.36e-05 & 9.90e-04 & -2.33e-02 & -1.02e-02 & -1.52e-04 & -8.29e-06 & 9.49e-05 & -1.05e-05 & 7.94e-04 & -1.77e-02 & -7.72e-03 & -1.16e-04 & -6.36e-06 & 7.71e-05 & -7.70e-06 & 6.34e-04 & -8.10e-03 & -4.86e-03 & -7.93e-05 \\
+2.14e-04 & -4.04e-03 & 3.88e-04 & -2.93e-02 & 6.88e+00 & 1.25e+00 & 6.67e-03 & 1.42e-04 & -2.96e-03 & 3.19e-04 & -2.17e-02 & 5.55e+00 & 1.07e+00 & 5.15e-03 & 9.62e-05 & -2.17e-03 & 2.27e-04 & -1.62e-02 & 4.46e+00 & 9.67e-01 & 3.67e-03 & 6.03e-05 & -1.67e-03 & 1.74e-04 & -1.27e-02 & 3.66e+00 & 8.52e-01 & 3.02e-03 & 3.86e-05 & -1.42e-03 & 1.29e-04 & -1.09e-02 & 2.89e+00 & 6.67e-01 & 2.09e-03 \\
+-2.59e-04 & -3.01e-03 & 1.66e-03 & -1.45e-02 & 1.25e+00 & 1.73e+01 & 8.74e-03 & -1.90e-04 & -2.82e-03 & 1.32e-03 & -1.33e-02 & 1.09e+00 & 1.44e+01 & 7.09e-03 & -1.66e-04 & -1.50e-03 & 9.73e-04 & -6.78e-03 & 1.84e+00 & 1.15e+01 & 4.92e-03 & -1.22e-04 & -1.02e-03 & 7.56e-04 & -4.36e-03 & 1.63e+00 & 9.61e+00 & 3.16e-03 & -9.95e-05 & -3.83e-04 & 5.60e-04 & -7.65e-04 & 1.36e+00 & 7.93e+00 & 1.78e-03 \\
+3.59e-06 & -1.78e-05 & 1.04e-05 & -2.66e-04 & 6.67e-03 & 8.74e-03 & 2.83e-04 & 2.89e-06 & -1.38e-05 & 8.38e-06 & -2.14e-04 & 1.06e-02 & 6.79e-03 & 2.29e-04 & 1.97e-06 & -9.39e-06 & 6.36e-06 & -1.60e-04 & 1.09e-02 & 4.07e-03 & 1.76e-04 & 1.38e-06 & -7.40e-06 & 4.92e-06 & -1.23e-04 & 7.97e-03 & 3.03e-03 & 1.41e-04 & 9.17e-07 & -7.22e-06 & 3.61e-06 & -9.91e-05 & 2.61e-03 & 2.30e-03 & 1.08e-04 \\
+4.51e-07 & -1.45e-06 & 3.23e-07 & -1.33e-05 & 1.42e-04 & -1.90e-04 & 2.89e-06 & 3.98e-07 & -1.28e-06 & 2.69e-07 & -1.13e-05 & 1.97e-04 & -2.55e-05 & 2.25e-06 & 3.23e-07 & -1.04e-06 & 2.11e-07 & -9.09e-06 & 1.44e-04 & 4.26e-05 & 1.25e-06 & 2.58e-07 & -8.18e-07 & 1.66e-07 & -7.11e-06 & 7.38e-05 & 5.08e-05 & 6.94e-07 & 1.88e-07 & -6.00e-07 & 1.23e-07 & -5.27e-06 & -5.22e-05 & 9.50e-06 & 2.40e-07 \\
+-1.46e-06 & 2.18e-05 & -2.15e-06 & 1.50e-04 & -2.96e-03 & -2.82e-03 & -1.38e-05 & -1.28e-06 & 1.93e-05 & -1.77e-06 & 1.30e-04 & -2.43e-03 & -2.99e-03 & -1.18e-05 & -1.04e-06 & 1.56e-05 & -1.35e-06 & 1.05e-04 & -1.96e-03 & -2.59e-03 & -7.61e-06 & -8.41e-07 & 1.25e-05 & -1.05e-06 & 8.38e-05 & -1.49e-03 & -1.96e-03 & -5.57e-06 & -6.24e-07 & 9.33e-06 & -7.68e-07 & 6.29e-05 & -7.66e-04 & -1.11e-03 & -4.00e-06 \\
+3.12e-07 & -2.12e-06 & 1.02e-06 & -1.80e-05 & 3.19e-04 & 1.32e-03 & 8.38e-06 & 2.69e-07 & -1.77e-06 & 8.55e-07 & -1.50e-05 & 4.09e-04 & 1.11e-03 & 6.69e-06 & 2.02e-07 & -1.23e-06 & 6.67e-07 & -1.10e-05 & 4.43e-04 & 8.16e-04 & 4.94e-06 & 1.57e-07 & -9.42e-07 & 5.21e-07 & -8.46e-06 & 3.37e-04 & 6.40e-04 & 3.75e-06 & 1.14e-07 & -6.87e-07 & 3.81e-07 & -6.16e-06 & 1.31e-04 & 4.77e-04 & 2.65e-06 \\
+-1.32e-05 & 1.49e-04 & -1.82e-05 & 1.27e-03 & -2.17e-02 & -1.33e-02 & -2.14e-04 & -1.13e-05 & 1.30e-04 & -1.50e-05 & 1.10e-03 & -2.15e-02 & -1.35e-02 & -1.75e-04 & -9.01e-06 & 1.04e-04 & -1.15e-05 & 8.72e-04 & -1.85e-02 & -1.11e-02 & -1.24e-04 & -7.18e-06 & 8.32e-05 & -8.95e-06 & 6.92e-04 & -1.39e-02 & -8.33e-03 & -9.24e-05 & -5.25e-06 & 6.25e-05 & -6.56e-06 & 5.15e-04 & -5.96e-03 & -4.09e-03 & -6.74e-05 \\
+2.60e-04 & -3.25e-03 & 4.99e-04 & -2.77e-02 & 5.55e+00 & 1.09e+00 & 1.06e-02 & 1.97e-04 & -2.43e-03 & 4.09e-04 & -2.15e-02 & 5.14e+00 & 9.38e-01 & 8.36e-03 & 1.44e-04 & -1.81e-03 & 3.04e-04 & -1.65e-02 & 4.30e+00 & 8.58e-01 & 5.98e-03 & 9.79e-05 & -1.38e-03 & 2.32e-04 & -1.28e-02 & 3.43e+00 & 7.80e-01 & 4.61e-03 & 5.79e-05 & -1.14e-03 & 1.72e-04 & -1.02e-02 & 2.35e+00 & 6.50e-01 & 3.24e-03 \\
+-1.34e-04 & -2.66e-03 & 1.38e-03 & -1.31e-02 & 1.07e+00 & 1.44e+01 & 6.79e-03 & -2.55e-05 & -2.99e-03 & 1.11e-03 & -1.35e-02 & 9.38e-01 & 1.37e+01 & 6.42e-03 & 1.80e-05 & -2.22e-03 & 8.57e-04 & -1.08e-02 & 1.49e+00 & 1.16e+01 & 1.63e-03 & 1.96e-05 & -1.57e-03 & 6.72e-04 & -7.66e-03 & 1.31e+00 & 9.54e+00 & 3.93e-06 & -2.30e-05 & -5.99e-04 & 5.06e-04 & -3.06e-03 & 1.08e+00 & 7.15e+00 & -1.30e-03 \\
+2.78e-06 & -1.43e-05 & 8.28e-06 & -2.13e-04 & 5.15e-03 & 7.09e-03 & 2.29e-04 & 2.25e-06 & -1.18e-05 & 6.69e-06 & -1.75e-04 & 8.36e-03 & 6.42e-03 & 1.94e-04 & 1.57e-06 & -8.81e-06 & 5.16e-06 & -1.35e-04 & 8.63e-03 & 4.45e-03 & 1.50e-04 & 1.09e-06 & -6.98e-06 & 4.01e-06 & -1.05e-04 & 6.28e-03 & 3.21e-03 & 1.19e-04 & 6.68e-07 & -6.26e-06 & 2.97e-06 & -8.31e-05 & 2.07e-03 & 1.95e-03 & 8.89e-05 \\
+3.58e-07 & -1.14e-06 & 2.38e-07 & -1.04e-05 & 9.62e-05 & -1.66e-04 & 1.97e-06 & 3.23e-07 & -1.04e-06 & 2.02e-07 & -9.01e-06 & 1.44e-04 & 1.80e-05 & 1.57e-06 & 2.82e-07 & -9.34e-07 & 1.66e-07 & -7.83e-06 & 9.39e-05 & 1.01e-04 & 6.81e-07 & 2.27e-07 & -7.44e-07 & 1.30e-07 & -6.18e-06 & 3.58e-05 & 8.41e-05 & 2.43e-07 & 1.67e-07 & -5.47e-07 & 9.84e-08 & -4.62e-06 & -6.31e-05 & 3.16e-05 & -5.49e-08 \\
+-1.16e-06 & 1.72e-05 & -1.47e-06 & 1.17e-04 & -2.17e-03 & -1.50e-03 & -9.39e-06 & -1.04e-06 & 1.56e-05 & -1.23e-06 & 1.04e-04 & -1.81e-03 & -2.22e-03 & -8.81e-06 & -9.34e-07 & 1.41e-05 & -9.72e-07 & 9.37e-05 & -1.32e-03 & -2.18e-03 & -5.00e-06 & -7.59e-07 & 1.15e-05 & -7.50e-07 & 7.59e-05 & -9.56e-04 & -1.55e-03 & -3.43e-06 & -5.69e-07 & 8.69e-06 & -5.57e-07 & 5.80e-05 & -4.18e-04 & -8.99e-04 & -2.79e-06 \\
+2.40e-07 & -1.59e-06 & 7.79e-07 & -1.36e-05 & 2.27e-04 & 9.73e-04 & 6.36e-06 & 2.11e-07 & -1.35e-06 & 6.67e-07 & -1.15e-05 & 3.04e-04 & 8.57e-04 & 5.16e-06 & 1.66e-07 & -9.72e-07 & 5.47e-07 & -8.75e-06 & 3.25e-04 & 6.57e-04 & 3.71e-06 & 1.30e-07 & -7.44e-07 & 4.31e-07 & -6.79e-06 & 2.47e-04 & 5.11e-04 & 2.81e-06 & 9.40e-08 & -5.37e-07 & 3.18e-07 & -4.97e-06 & 9.24e-05 & 3.58e-04 & 1.99e-06 \\
+-1.04e-05 & 1.17e-04 & -1.31e-05 & 9.90e-04 & -1.62e-02 & -6.78e-03 & -1.60e-04 & -9.09e-06 & 1.05e-04 & -1.10e-05 & 8.72e-04 & -1.65e-02 & -1.08e-02 & -1.35e-04 & -7.83e-06 & 9.37e-05 & -8.75e-06 & 7.76e-04 & -1.38e-02 & -1.03e-02 & -9.19e-05 & -6.28e-06 & 7.58e-05 & -6.80e-06 & 6.24e-04 & -1.01e-02 & -7.01e-03 & -6.68e-05 & -4.66e-06 & 5.77e-05 & -5.07e-06 & 4.74e-04 & -4.00e-03 & -3.86e-03 & -5.10e-05 \\
+1.90e-04 & -2.58e-03 & 5.44e-04 & -2.33e-02 & 4.46e+00 & 1.84e+00 & 1.09e-02 & 1.44e-04 & -1.96e-03 & 4.43e-04 & -1.85e-02 & 4.30e+00 & 1.49e+00 & 8.63e-03 & 9.39e-05 & -1.32e-03 & 3.25e-04 & -1.38e-02 & 3.99e+00 & 1.20e+00 & 6.47e-03 & 5.76e-05 & -9.90e-04 & 2.49e-04 & -1.06e-02 & 3.20e+00 & 1.04e+00 & 4.99e-03 & 2.60e-05 & -7.80e-04 & 1.84e-04 & -8.18e-03 & 2.21e+00 & 8.94e-01 & 3.63e-03 \\
+-5.51e-05 & -2.14e-03 & 1.02e-03 & -1.02e-02 & 9.67e-01 & 1.15e+01 & 4.07e-03 & 4.26e-05 & -2.59e-03 & 8.16e-04 & -1.11e-02 & 8.58e-01 & 1.16e+01 & 4.45e-03 & 1.01e-04 & -2.18e-03 & 6.57e-04 & -1.03e-02 & 1.20e+00 & 1.04e+01 & -3.81e-04 & 8.39e-05 & -1.55e-03 & 5.18e-04 & -7.33e-03 & 1.05e+00 & 8.61e+00 & -1.61e-03 & 2.13e-05 & -6.03e-04 & 3.97e-04 & -3.07e-03 & 8.81e-01 & 6.41e+00 & -2.52e-03 \\
+1.70e-06 & -1.00e-05 & 6.05e-06 & -1.52e-04 & 3.67e-03 & 4.92e-03 & 1.76e-04 & 1.25e-06 & -7.61e-06 & 4.94e-06 & -1.24e-04 & 5.98e-03 & 1.63e-03 & 1.50e-04 & 6.81e-07 & -5.00e-06 & 3.71e-06 & -9.19e-05 & 6.47e-03 & -3.81e-04 & 1.30e-04 & 3.89e-07 & -4.13e-06 & 2.87e-06 & -7.16e-05 & 4.86e-03 & -3.90e-04 & 1.06e-04 & 2.10e-07 & -4.36e-06 & 2.13e-06 & -5.81e-05 & 1.91e-03 & 6.81e-04 & 8.25e-05 \\
+2.87e-07 & -9.23e-07 & 1.86e-07 & -8.29e-06 & 6.03e-05 & -1.22e-04 & 1.38e-06 & 2.58e-07 & -8.41e-07 & 1.57e-07 & -7.18e-06 & 9.79e-05 & 1.96e-05 & 1.09e-06 & 2.27e-07 & -7.59e-07 & 1.30e-07 & -6.28e-06 & 5.76e-05 & 8.39e-05 & 3.89e-07 & 1.87e-07 & -6.16e-07 & 1.04e-07 & -5.04e-06 & 1.24e-05 & 7.22e-05 & 4.62e-08 & 1.42e-07 & -4.64e-07 & 8.05e-08 & -3.85e-06 & -6.45e-05 & 3.01e-05 & -1.89e-07 \\
+-9.20e-07 & 1.40e-05 & -1.12e-06 & 9.49e-05 & -1.67e-03 & -1.02e-03 & -7.40e-06 & -8.18e-07 & 1.25e-05 & -9.42e-07 & 8.32e-05 & -1.38e-03 & -1.57e-03 & -6.98e-06 & -7.44e-07 & 1.15e-05 & -7.44e-07 & 7.58e-05 & -9.90e-04 & -1.55e-03 & -4.13e-06 & -6.16e-07 & 9.55e-06 & -5.79e-07 & 6.29e-05 & -7.12e-04 & -1.09e-03 & -2.97e-06 & -4.78e-07 & 7.52e-06 & -4.35e-07 & 4.98e-05 & -3.00e-04 & -6.51e-04 & -2.44e-06 \\
+1.88e-07 & -1.22e-06 & 6.13e-07 & -1.05e-05 & 1.74e-04 & 7.56e-04 & 4.92e-06 & 1.66e-07 & -1.05e-06 & 5.21e-07 & -8.95e-06 & 2.32e-04 & 6.72e-04 & 4.01e-06 & 1.30e-07 & -7.50e-07 & 4.31e-07 & -6.80e-06 & 2.49e-04 & 5.18e-04 & 2.87e-06 & 1.04e-07 & -5.79e-07 & 3.46e-07 & -5.33e-06 & 1.90e-04 & 4.07e-04 & 2.19e-06 & 7.71e-08 & -4.22e-07 & 2.62e-07 & -3.96e-06 & 7.30e-05 & 2.81e-04 & 1.55e-06 \\
+-8.14e-06 & 9.43e-05 & -1.01e-05 & 7.94e-04 & -1.27e-02 & -4.36e-03 & -1.23e-04 & -7.11e-06 & 8.38e-05 & -8.46e-06 & 6.92e-04 & -1.28e-02 & -7.66e-03 & -1.05e-04 & -6.18e-06 & 7.59e-05 & -6.79e-06 & 6.24e-04 & -1.06e-02 & -7.33e-03 & -7.16e-05 & -5.04e-06 & 6.29e-05 & -5.33e-06 & 5.12e-04 & -7.82e-03 & -4.81e-03 & -5.28e-05 & -3.85e-06 & 4.96e-05 & -4.02e-06 & 4.02e-04 & -3.20e-03 & -2.62e-03 & -4.03e-05 \\
+1.09e-04 & -2.01e-03 & 4.13e-04 & -1.77e-02 & 3.66e+00 & 1.63e+00 & 7.97e-03 & 7.38e-05 & -1.49e-03 & 3.37e-04 & -1.39e-02 & 3.43e+00 & 1.31e+00 & 6.28e-03 & 3.58e-05 & -9.56e-04 & 2.47e-04 & -1.01e-02 & 3.20e+00 & 1.05e+00 & 4.86e-03 & 1.24e-05 & -7.12e-04 & 1.90e-04 & -7.82e-03 & 2.65e+00 & 9.25e-01 & 3.86e-03 & -6.02e-06 & -5.70e-04 & 1.41e-04 & -6.16e-03 & 1.94e+00 & 8.11e-01 & 2.87e-03 \\
+-1.66e-05 & -1.63e-03 & 8.00e-04 & -7.72e-03 & 8.52e-01 & 9.61e+00 & 3.03e-03 & 5.08e-05 & -1.96e-03 & 6.40e-04 & -8.33e-03 & 7.80e-01 & 9.54e+00 & 3.21e-03 & 8.41e-05 & -1.55e-03 & 5.11e-04 & -7.01e-03 & 1.04e+00 & 8.61e+00 & -3.90e-04 & 7.22e-05 & -1.09e-03 & 4.07e-04 & -4.81e-03 & 9.25e-01 & 7.33e+00 & -1.38e-03 & 2.35e-05 & -3.85e-04 & 3.14e-04 & -1.61e-03 & 7.80e-01 & 5.67e+00 & -2.14e-03 \\
+1.05e-06 & -7.87e-06 & 4.56e-06 & -1.16e-04 & 3.02e-03 & 3.16e-03 & 1.41e-04 & 6.94e-07 & -5.57e-06 & 3.75e-06 & -9.24e-05 & 4.61e-03 & 3.93e-06 & 1.19e-04 & 2.43e-07 & -3.43e-06 & 2.81e-06 & -6.68e-05 & 4.99e-03 & -1.61e-03 & 1.06e-04 & 4.62e-08 & -2.97e-06 & 2.19e-06 & -5.28e-05 & 3.86e-03 & -1.38e-03 & 8.88e-05 & -3.18e-08 & -3.62e-06 & 1.63e-06 & -4.51e-05 & 1.72e-03 & -4.81e-05 & 7.16e-05 \\
+2.24e-07 & -7.31e-07 & 1.39e-07 & -6.36e-06 & 3.86e-05 & -9.95e-05 & 9.17e-07 & 1.88e-07 & -6.24e-07 & 1.14e-07 & -5.25e-06 & 5.79e-05 & -2.30e-05 & 6.68e-07 & 1.67e-07 & -5.69e-07 & 9.40e-08 & -4.66e-06 & 2.60e-05 & 2.13e-05 & 2.10e-07 & 1.42e-07 & -4.78e-07 & 7.71e-08 & -3.85e-06 & -6.02e-06 & 2.35e-05 & -3.18e-08 & 1.26e-07 & -4.21e-07 & 6.61e-08 & -3.34e-06 & -5.81e-05 & 3.45e-05 & -2.39e-07 \\
+-7.21e-07 & 1.14e-05 & -8.12e-07 & 7.71e-05 & -1.42e-03 & -3.83e-04 & -7.22e-06 & -6.00e-07 & 9.33e-06 & -6.87e-07 & 6.25e-05 & -1.14e-03 & -5.99e-04 & -6.26e-06 & -5.47e-07 & 8.69e-06 & -5.37e-07 & 5.77e-05 & -7.80e-04 & -6.03e-04 & -4.36e-06 & -4.64e-07 & 7.52e-06 & -4.22e-07 & 4.96e-05 & -5.70e-04 & -3.85e-04 & -3.62e-06 & -4.21e-07 & 7.00e-06 & -3.26e-07 & 4.58e-05 & -2.70e-04 & -3.78e-04 & -2.81e-06 \\
+1.43e-07 & -8.85e-07 & 4.67e-07 & -7.70e-06 & 1.29e-04 & 5.60e-04 & 3.61e-06 & 1.23e-07 & -7.68e-07 & 3.81e-07 & -6.56e-06 & 1.72e-04 & 5.06e-04 & 2.97e-06 & 9.84e-08 & -5.57e-07 & 3.18e-07 & -5.07e-06 & 1.84e-04 & 3.97e-04 & 2.13e-06 & 8.05e-08 & -4.35e-07 & 2.62e-07 & -4.02e-06 & 1.41e-04 & 3.14e-04 & 1.63e-06 & 6.61e-08 & -3.26e-07 & 2.25e-07 & -3.16e-06 & 5.74e-05 & 2.22e-04 & 1.20e-06 \\
+-6.30e-06 & 7.62e-05 & -7.36e-06 & 6.34e-04 & -1.09e-02 & -7.65e-04 & -9.91e-05 & -5.27e-06 & 6.29e-05 & -6.16e-06 & 5.15e-04 & -1.02e-02 & -3.06e-03 & -8.31e-05 & -4.62e-06 & 5.80e-05 & -4.97e-06 & 4.74e-04 & -8.18e-03 & -3.07e-03 & -5.81e-05 & -3.85e-06 & 4.98e-05 & -3.96e-06 & 4.02e-04 & -6.16e-03 & -1.61e-03 & -4.51e-05 & -3.34e-06 & 4.58e-05 & -3.16e-06 & 3.66e-04 & -2.98e-03 & -1.23e-03 & -3.34e-05 \\
+-3.58e-05 & -1.09e-03 & 1.56e-04 & -8.10e-03 & 2.89e+00 & 1.36e+00 & 2.61e-03 & -5.22e-05 & -7.66e-04 & 1.31e-04 & -5.96e-03 & 2.35e+00 & 1.08e+00 & 2.07e-03 & -6.31e-05 & -4.18e-04 & 9.24e-05 & -4.00e-03 & 2.21e+00 & 8.81e-01 & 1.91e-03 & -6.45e-05 & -3.00e-04 & 7.30e-05 & -3.20e-03 & 1.94e+00 & 7.80e-01 & 1.72e-03 & -5.81e-05 & -2.70e-04 & 5.74e-05 & -2.98e-03 & 1.80e+00 & 6.92e-01 & 1.55e-03 \\
+-6.71e-06 & -1.17e-03 & 5.93e-04 & -4.86e-03 & 6.67e-01 & 7.93e+00 & 2.30e-03 & 9.50e-06 & -1.11e-03 & 4.77e-04 & -4.09e-03 & 6.50e-01 & 7.15e+00 & 1.95e-03 & 3.16e-05 & -8.99e-04 & 3.58e-04 & -3.86e-03 & 8.94e-01 & 6.41e+00 & 6.81e-04 & 3.01e-05 & -6.51e-04 & 2.81e-04 & -2.62e-03 & 8.11e-01 & 5.67e+00 & -4.81e-05 & 3.45e-05 & -3.78e-04 & 2.22e-04 & -1.23e-03 & 6.92e-01 & 5.36e+00 & -6.37e-04 \\
+4.73e-07 & -5.25e-06 & 3.15e-06 & -7.93e-05 & 2.09e-03 & 1.78e-03 & 1.08e-04 & 2.40e-07 & -4.00e-06 & 2.65e-06 & -6.74e-05 & 3.24e-03 & -1.30e-03 & 8.89e-05 & -5.49e-08 & -2.79e-06 & 1.99e-06 & -5.10e-05 & 3.63e-03 & -2.52e-03 & 8.25e-05 & -1.89e-07 & -2.44e-06 & 1.55e-06 & -4.03e-05 & 2.87e-03 & -2.14e-03 & 7.16e-05 & -2.39e-07 & -2.81e-06 & 1.20e-06 & -3.34e-05 & 1.55e-03 & -6.37e-04 & 6.60e-05
+\end{bmatrix}
+\end{equation}
+\bibliographystyle{aasjournal}
+\bibliography{alex}
+%\input{fix.bbl}
 \end{document}

### 2018-05-16 tablef3_x1.py

@@ -38,6 +38,30 @@ print "ev_sig size"
 dum1, dumm, dump =  numpy.percentile(fit['ev_sig'],(50,50-34,50+34),axis=0)
 print "{:.3f}^{{+{:.3f}}}_{{{:.3f}}}".format(dum1,dump-dum1,dumm-dum1)
 
+print "global parameter covariance matrix"
+nlinks = fit['gamma'].shape[0]
+mega = [] 
+for i in xrange(5):
+    mega.append([fit['alpha'][:,i],fit['beta'][:,i],fit['eta'][:,i],\
+        fit['zeta'][:,i],fit['gamma'][:,i],fit['rho1'][:,i],fit['ev_sig'][:]*fit['ev'][:,i]])
+mega = numpy.array(mega)
+mega = numpy.reshape(mega, (35,nlinks))
+print mega.shape
+ans = numpy.cov(mega)
+def frexp10(x):
+    exp = int(numpy.floor(numpy.log10(abs(x))))
+    return x / 10**exp, exp
+
+for i1 in xrange(35):
+    for i2 in xrange(35):
+        print "{0}^{{{1:+03}}}".format(*frexp10(ans[i1,i2])),
+        if (i2 != 34):
+            print "&",
+    print "\\\\" 
+wefew
+
+
+
 print "the table"
 
 pars = ['alpha','alpha','beta','beta','eta','eta','zeta','zeta','gamma','gamma','rho1','rho1']

### 2018-05-17 submit/fix.tex
residuals given one fixed

@@
 
+\added{
+\begin{equation}
+\begin{pmatrix}
+\small
+\begin{array}{rrrrrrr}
+EW_{\mathrm{Ca}} & 7.0  \pm 0.5 \times 10^{ 2} & 6.7  \pm 0.3 \times 10^{ 2} & 3.7  \pm 1.1 \times 10^{ 2} & 3.3  \pm 6.2 \times 10^{ 1} & 7.7  \pm 17.0 \times 10^{ 0} & 6.3  \pm 11.2 \times 10^{ 1} \\
+5.0  \pm 0.2 \times 10^{ 1} & EW_{\mathrm{Si}} & 4.9  \pm 0.2 \times 10^{ 1} & 2.5  \pm 0.2 \times 10^{ 0} & 4.7  \pm 3.3 \times 10^{ 0} & 1.2  \pm 1.5 \times 10^{ 0} & 1.1  \pm 1.2 \times 10^{ 1} \\
+3.8  \pm 0.2 \times 10^{ 2} & 3.9  \pm 0.2 \times 10^{ 2} & \lambda_{\mathrm{Si}} & 1.4  \pm 0.3 \times 10^{ 2} & 7.4  \pm 8.8 \times 10^{ 1} & 4.3  \pm 6.8 \times 10^{ 1} & 4.5  \pm 7.0 \times 10^{ 1} \\
+9.9  \pm 0.4 \times 10^{-1} & 2.9  \pm 0.2 \times 10^{-1} & 9.7  \pm 0.4 \times 10^{-1} & x_1 & 5.2  \pm 1.4 \times 10^{-1} & 2.3  \pm 1.6 \times 10^{-1} & 6.7  \pm 2.3 \times 10^{-1} \\
+5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} \\
+1.5  \pm 0.3 \times 10^{-3} & 1.4  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} &  E_{\gamma^1}({\hat{B}}-{\hat{V}}) & 1.5  \pm 0.3 \times 10^{-3} \\
+2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & A_{p,V} \\
+\end{array}
+\end{pmatrix}.
+\label{ellipse:eqn}
+\end{equation}
+}
+
 An extensive discussion of the correlations between the spectral features  and light-curve parameters of the SNfactory data
@@
 \section{Covariance Matrix for Model~III Global Parameters}
+\added{The following is the  covariance matrix for the global cofactors $\{ \alpha_{\hat{U}}, \beta_{\hat{U}}, \eta_{\hat{U}}, \zeta_{\hat{U}}, \gamma^0_{\hat{U}},\gamma^1_{\hat{U}}, \sigma_p \phi_{\hat{U}},
+\ldots,
+\alpha_{\hat{I}}, \beta_{\hat{I}}, \eta_{\hat{I}}, \zeta_{\hat{I}}, \gamma^0_{\hat{I}},\gamma^1_{\hat{I}}, \sigma_p \phi_{\hat{I}}
+ \}$.  The matrix 35x35 is big so will have to go in supplemental material.}
 \setcounter{MaxMatrixCols}{40}
@@
 \begin{bmatrix}
-5.48e-07 & -1.77e-06 & 3.87e-07 & -1.63e-05 & 2.14e-04 & -2.59e-04 & 3.59e-06 & 4.51e-07 & -1.46e-06 & 3.12e-07 & -1.32e-05 & 2.60e-04 & -1.34e-04 & 2.78e-06 & 3.58e-07 & -1.16e-06 & 2.40e-07 & -1.04e-05 & 1.90e-04 & -5.51e-05 & 1.70e-06 & 2.87e-07 & -9.20e-07 & 1.88e-07 & -8.14e-06 & 1.09e-04 & -1.66e-05 & 1.05e-06 & 2.24e-07 & -7.21e-07 & 1.43e-07 & -6.30e-06 & -3.58e-05 & -6.71e-06 & 4.73e-07 \\
--1.77e-06 & 2.70e-05 & -2.60e-06 & 1.85e-04 & -4.04e-03 & -3.01e-03 & -1.78e-05 & -1.45e-06 & 2.18e-05 & -2.12e-06 & 1.49e-04 & -3.25e-03 & -2.66e-03 & -1.43e-05 & -1.14e-06 & 1.72e-05 & -1.59e-06 & 1.17e-04 & -2.58e-03 & -2.14e-03 & -1.00e-05 & -9.23e-07 & 1.40e-05 & -1.22e-06 & 9.43e-05 & -2.01e-03 & -1.63e-03 & -7.87e-06 & -7.31e-07 & 1.14e-05 & -8.85e-07 & 7.62e-05 & -1.09e-03 & -1.17e-03 & -5.25e-06 \\
-3.87e-07 & -2.60e-06 & 1.26e-06 & -2.22e-05 & 3.88e-04 & 1.66e-03 & 1.04e-05 & 3.23e-07 & -2.15e-06 & 1.02e-06 & -1.82e-05 & 4.99e-04 & 1.38e-03 & 8.28e-06 & 2.38e-07 & -1.47e-06 & 7.79e-07 & -1.31e-05 & 5.44e-04 & 1.02e-03 & 6.05e-06 & 1.86e-07 & -1.12e-06 & 6.13e-07 & -1.01e-05 & 4.13e-04 & 8.00e-04 & 4.56e-06 & 1.39e-07 & -8.12e-07 & 4.67e-07 & -7.36e-06 & 1.56e-04 & 5.93e-04 & 3.15e-06 \\
--1.63e-05 & 1.85e-04 & -2.22e-05 & 1.57e-03 & -2.93e-02 & -1.45e-02 & -2.66e-04 & -1.33e-05 & 1.50e-04 & -1.80e-05 & 1.27e-03 & -2.77e-02 & -1.31e-02 & -2.13e-04 & -1.04e-05 & 1.17e-04 & -1.36e-05 & 9.90e-04 & -2.33e-02 & -1.02e-02 & -1.52e-04 & -8.29e-06 & 9.49e-05 & -1.05e-05 & 7.94e-04 & -1.77e-02 & -7.72e-03 & -1.16e-04 & -6.36e-06 & 7.71e-05 & -7.70e-06 & 6.34e-04 & -8.10e-03 & -4.86e-03 & -7.93e-05 \\
-2.14e-04 & -4.04e-03 & 3.88e-04 & -2.93e-02 & 6.88e+00 & 1.25e+00 & 6.67e-03 & 1.42e-04 & -2.96e-03 & 3.19e-04 & -2.17e-02 & 5.55e+00 & 1.07e+00 & 5.15e-03 & 9.62e-05 & -2.17e-03 & 2.27e-04 & -1.62e-02 & 4.46e+00 & 9.67e-01 & 3.67e-03 & 6.03e-05 & -1.67e-03 & 1.74e-04 & -1.27e-02 & 3.66e+00 & 8.52e-01 & 3.02e-03 & 3.86e-05 & -1.42e-03 & 1.29e-04 & -1.09e-02 & 2.89e+00 & 6.67e-01 & 2.09e-03 \\
--2.59e-04 & -3.01e-03 & 1.66e-03 & -1.45e-02 & 1.25e+00 & 1.73e+01 & 8.74e-03 & -1.90e-04 & -2.82e-03 & 1.32e-03 & -1.33e-02 & 1.09e+00 & 1.44e+01 & 7.09e-03 & -1.66e-04 & -1.50e-03 & 9.73e-04 & -6.78e-03 & 1.84e+00 & 1.15e+01 & 4.92e-03 & -1.22e-04 & -1.02e-03 & 7.56e-04 & -4.36e-03 & 1.63e+00 & 9.61e+00 & 3.16e-03 & -9.95e-05 & -3.83e-04 & 5.60e-04 & -7.65e-04 & 1.36e+00 & 7.93e+00 & 1.78e-03 \\
-3.59e-06 & -1.78e-05 & 1.04e-05 & -2.66e-04 & 6.67e-03 & 8.74e-03 & 2.83e-04 & 2.89e-06 & -1.38e-05 & 8.38e-06 & -2.14e-04 & 1.06e-02 & 6.79e-03 & 2.29e-04 & 1.97e-06 & -9.39e-06 & 6.36e-06 & -1.60e-04 & 1.09e-02 & 4.07e-03 & 1.76e-04 & 1.38e-06 & -7.40e-06 & 4.92e-06 & -1.23e-04 & 7.97e-03 & 3.03e-03 & 1.41e-04 & 9.17e-07 & -7.22e-06 & 3.61e-06 & -9.91e-05 & 2.61e-03 & 2.30e-03 & 1.08e-04 \\
-4.51e-07 & -1.45e-06 & 3.23e-07 & -1.33e-05 & 1.42e-04 & -1.90e-04 & 2.89e-06 & 3.98e-07 & -1.28e-06 & 2.69e-07 & -1.13e-05 & 1.97e-04 & -2.55e-05 & 2.25e-06 & 3.23e-07 & -1.04e-06 & 2.11e-07 & -9.09e-06 & 1.44e-04 & 4.26e-05 & 1.25e-06 & 2.58e-07 & -8.18e-07 & 1.66e-07 & -7.11e-06 & 7.38e-05 & 5.08e-05 & 6.94e-07 & 1.88e-07 & -6.00e-07 & 1.23e-07 & -5.27e-06 & -5.22e-05 & 9.50e-06 & 2.40e-07 \\
--1.46e-06 & 2.18e-05 & -2.15e-06 & 1.50e-04 & -2.96e-03 & -2.82e-03 & -1.38e-05 & -1.28e-06 & 1.93e-05 & -1.77e-06 & 1.30e-04 & -2.43e-03 & -2.99e-03 & -1.18e-05 & -1.04e-06 & 1.56e-05 & -1.35e-06 & 1.05e-04 & -1.96e-03 & -2.59e-03 & -7.61e-06 & -8.41e-07 & 1.25e-05 & -1.05e-06 & 8.38e-05 & -1.49e-03 & -1.96e-03 & -5.57e-06 & -6.24e-07 & 9.33e-06 & -7.68e-07 & 6.29e-05 & -7.66e-04 & -1.11e-03 & -4.00e-06 \\
-3.12e-07 & -2.12e-06 & 1.02e-06 & -1.80e-05 & 3.19e-04 & 1.32e-03 & 8.38e-06 & 2.69e-07 & -1.77e-06 & 8.55e-07 & -1.50e-05 & 4.09e-04 & 1.11e-03 & 6.69e-06 & 2.02e-07 & -1.23e-06 & 6.67e-07 & -1.10e-05 & 4.43e-04 & 8.16e-04 & 4.94e-06 & 1.57e-07 & -9.42e-07 & 5.21e-07 & -8.46e-06 & 3.37e-04 & 6.40e-04 & 3.75e-06 & 1.14e-07 & -6.87e-07 & 3.81e-07 & -6.16e-06 & 1.31e-04 & 4.77e-04 & 2.65e-06 \\
--1.32e-05 & 1.49e-04 & -1.82e-05 & 1.27e-03 & -2.17e-02 & -1.33e-02 & -2.14e-04 & -1.13e-05 & 1.30e-04 & -1.50e-05 & 1.10e-03 & -2.15e-02 & -1.35e-02 & -1.75e-04 & -9.01e-06 & 1.04e-04 & -1.15e-05 & 8.72e-04 & -1.85e-02 & -1.11e-02 & -1.24e-04 & -7.18e-06 & 8.32e-05 & -8.95e-06 & 6.92e-04 & -1.39e-02 & -8.33e-03 & -9.24e-05 & -5.25e-06 & 6.25e-05 & -6.56e-06 & 5.15e-04 & -5.96e-03 & -4.09e-03 & -6.74e-05 \\
-2.60e-04 & -3.25e-03 & 4.99e-04 & -2.77e-02 & 5.55e+00 & 1.09e+00 & 1.06e-02 & 1.97e-04 & -2.43e-03 & 4.09e-04 & -2.15e-02 & 5.14e+00 & 9.38e-01 & 8.36e-03 & 1.44e-04 & -1.81e-03 & 3.04e-04 & -1.65e-02 & 4.30e+00 & 8.58e-01 & 5.98e-03 & 9.79e-05 & -1.38e-03 & 2.32e-04 & -1.28e-02 & 3.43e+00 & 7.80e-01 & 4.61e-03 & 5.79e-05 & -1.14e-03 & 1.72e-04 & -1.02e-02 & 2.35e+00 & 6.50e-01 & 3.24e-03 \\
--1.34e-04 & -2.66e-03 & 1.38e-03 & -1.31e-02 & 1.07e+00 & 1.44e+01 & 6.79e-03 & -2.55e-05 & -2.99e-03 & 1.11e-03 & -1.35e-02 & 9.38e-01 & 1.37e+01 & 6.42e-03 & 1.80e-05 & -2.22e-03 & 8.57e-04 & -1.08e-02 & 1.49e+00 & 1.16e+01 & 1.63e-03 & 1.96e-05 & -1.57e-03 & 6.72e-04 & -7.66e-03 & 1.31e+00 & 9.54e+00 & 3.93e-06 & -2.30e-05 & -5.99e-04 & 5.06e-04 & -3.06e-03 & 1.08e+00 & 7.15e+00 & -1.30e-03 \\
-2.78e-06 & -1.43e-05 & 8.28e-06 & -2.13e-04 & 5.15e-03 & 7.09e-03 & 2.29e-04 & 2.25e-06 & -1.18e-05 & 6.69e-06 & -1.75e-04 & 8.36e-03 & 6.42e-03 & 1.94e-04 & 1.57e-06 & -8.81e-06 & 5.16e-06 & -1.35e-04 & 8.63e-03 & 4.45e-03 & 1.50e-04 & 1.09e-06 & -6.98e-06 & 4.01e-06 & -1.05e-04 & 6.28e-03 & 3.21e-03 & 1.19e-04 & 6.68e-07 & -6.26e-06 & 2.97e-06 & -8.31e-05 & 2.07e-03 & 1.95e-03 & 8.89e-05 \\
-3.58e-07 & -1.14e-06 & 2.38e-07 & -1.04e-05 & 9.62e-05 & -1.66e-04 & 1.97e-06 & 3.23e-07 & -1.04e-06 & 2.02e-07 & -9.01e-06 & 1.44e-04 & 1.80e-05 & 1.57e-06 & 2.82e-07 & -9.34e-07 & 1.66e-07 & -7.83e-06 & 9.39e-05 & 1.01e-04 & 6.81e-07 & 2.27e-07 & -7.44e-07 & 1.30e-07 & -6.18e-06 & 3.58e-05 & 8.41e-05 & 2.43e-07 & 1.67e-07 & -5.47e-07 & 9.84e-08 & -4.62e-06 & -6.31e-05 & 3.16e-05 & -5.49e-08 \\
--1.16e-06 & 1.72e-05 & -1.47e-06 & 1.17e-04 & -2.17e-03 & -1.50e-03 & -9.39e-06 & -1.04e-06 & 1.56e-05 & -1.23e-06 & 1.04e-04 & -1.81e-03 & -2.22e-03 & -8.81e-06 & -9.34e-07 & 1.41e-05 & -9.72e-07 & 9.37e-05 & -1.32e-03 & -2.18e-03 & -5.00e-06 & -7.59e-07 & 1.15e-05 & -7.50e-07 & 7.59e-05 & -9.56e-04 & -1.55e-03 & -3.43e-06 & -5.69e-07 & 8.69e-06 & -5.57e-07 & 5.80e-05 & -4.18e-04 & -8.99e-04 & -2.79e-06 \\
-2.40e-07 & -1.59e-06 & 7.79e-07 & -1.36e-05 & 2.27e-04 & 9.73e-04 & 6.36e-06 & 2.11e-07 & -1.35e-06 & 6.67e-07 & -1.15e-05 & 3.04e-04 & 8.57e-04 & 5.16e-06 & 1.66e-07 & -9.72e-07 & 5.47e-07 & -8.75e-06 & 3.25e-04 & 6.57e-04 & 3.71e-06 & 1.30e-07 & -7.44e-07 & 4.31e-07 & -6.79e-06 & 2.47e-04 & 5.11e-04 & 2.81e-06 & 9.40e-08 & -5.37e-07 & 3.18e-07 & -4.97e-06 & 9.24e-05 & 3.58e-04 & 1.99e-06 \\
--1.04e-05 & 1.17e-04 & -1.31e-05 & 9.90e-04 & -1.62e-02 & -6.78e-03 & -1.60e-04 & -9.09e-06 & 1.05e-04 & -1.10e-05 & 8.72e-04 & -1.65e-02 & -1.08e-02 & -1.35e-04 & -7.83e-06 & 9.37e-05 & -8.75e-06 & 7.76e-04 & -1.38e-02 & -1.03e-02 & -9.19e-05 & -6.28e-06 & 7.58e-05 & -6.80e-06 & 6.24e-04 & -1.01e-02 & -7.01e-03 & -6.68e-05 & -4.66e-06 & 5.77e-05 & -5.07e-06 & 4.74e-04 & -4.00e-03 & -3.86e-03 & -5.10e-05 \\
-1.90e-04 & -2.58e-03 & 5.44e-04 & -2.33e-02 & 4.46e+00 & 1.84e+00 & 1.09e-02 & 1.44e-04 & -1.96e-03 & 4.43e-04 & -1.85e-02 & 4.30e+00 & 1.49e+00 & 8.63e-03 & 9.39e-05 & -1.32e-03 & 3.25e-04 & -1.38e-02 & 3.99e+00 & 1.20e+00 & 6.47e-03 & 5.76e-05 & -9.90e-04 & 2.49e-04 & -1.06e-02 & 3.20e+00 & 1.04e+00 & 4.99e-03 & 2.60e-05 & -7.80e-04 & 1.84e-04 & -8.18e-03 & 2.21e+00 & 8.94e-01 & 3.63e-03 \\
--5.51e-05 & -2.14e-03 & 1.02e-03 & -1.02e-02 & 9.67e-01 & 1.15e+01 & 4.07e-03 & 4.26e-05 & -2.59e-03 & 8.16e-04 & -1.11e-02 & 8.58e-01 & 1.16e+01 & 4.45e-03 & 1.01e-04 & -2.18e-03 & 6.57e-04 & -1.03e-02 & 1.20e+00 & 1.04e+01 & -3.81e-04 & 8.39e-05 & -1.55e-03 & 5.18e-04 & -7.33e-03 & 1.05e+00 & 8.61e+00 & -1.61e-03 & 2.13e-05 & -6.03e-04 & 3.97e-04 & -3.07e-03 & 8.81e-01 & 6.41e+00 & -2.52e-03 \\
-1.70e-06 & -1.00e-05 & 6.05e-06 & -1.52e-04 & 3.67e-03 & 4.92e-03 & 1.76e-04 & 1.25e-06 & -7.61e-06 & 4.94e-06 & -1.24e-04 & 5.98e-03 & 1.63e-03 & 1.50e-04 & 6.81e-07 & -5.00e-06 & 3.71e-06 & -9.19e-05 & 6.47e-03 & -3.81e-04 & 1.30e-04 & 3.89e-07 & -4.13e-06 & 2.87e-06 & -7.16e-05 & 4.86e-03 & -3.90e-04 & 1.06e-04 & 2.10e-07 & -4.36e-06 & 2.13e-06 & -5.81e-05 & 1.91e-03 & 6.81e-04 & 8.25e-05 \\
-2.87e-07 & -9.23e-07 & 1.86e-07 & -8.29e-06 & 6.03e-05 & -1.22e-04 & 1.38e-06 & 2.58e-07 & -8.41e-07 & 1.57e-07 & -7.18e-06 & 9.79e-05 & 1.96e-05 & 1.09e-06 & 2.27e-07 & -7.59e-07 & 1.30e-07 & -6.28e-06 & 5.76e-05 & 8.39e-05 & 3.89e-07 & 1.87e-07 & -6.16e-07 & 1.04e-07 & -5.04e-06 & 1.24e-05 & 7.22e-05 & 4.62e-08 & 1.42e-07 & -4.64e-07 & 8.05e-08 & -3.85e-06 & -6.45e-05 & 3.01e-05 & -1.89e-07 \\
--9.20e-07 & 1.40e-05 & -1.12e-06 & 9.49e-05 & -1.67e-03 & -1.02e-03 & -7.40e-06 & -8.18e-07 & 1.25e-05 & -9.42e-07 & 8.32e-05 & -1.38e-03 & -1.57e-03 & -6.98e-06 & -7.44e-07 & 1.15e-05 & -7.44e-07 & 7.58e-05 & -9.90e-04 & -1.55e-03 & -4.13e-06 & -6.16e-07 & 9.55e-06 & -5.79e-07 & 6.29e-05 & -7.12e-04 & -1.09e-03 & -2.97e-06 & -4.78e-07 & 7.52e-06 & -4.35e-07 & 4.98e-05 & -3.00e-04 & -6.51e-04 & -2.44e-06 \\
-1.88e-07 & -1.22e-06 & 6.13e-07 & -1.05e-05 & 1.74e-04 & 7.56e-04 & 4.92e-06 & 1.66e-07 & -1.05e-06 & 5.21e-07 & -8.95e-06 & 2.32e-04 & 6.72e-04 & 4.01e-06 & 1.30e-07 & -7.50e-07 & 4.31e-07 & -6.80e-06 & 2.49e-04 & 5.18e-04 & 2.87e-06 & 1.04e-07 & -5.79e-07 & 3.46e-07 & -5.33e-06 & 1.90e-04 & 4.07e-04 & 2.19e-06 & 7.71e-08 & -4.22e-07 & 2.62e-07 & -3.96e-06 & 7.30e-05 & 2.81e-04 & 1.55e-06 \\
--8.14e-06 & 9.43e-05 & -1.01e-05 & 7.94e-04 & -1.27e-02 & -4.36e-03 & -1.23e-04 & -7.11e-06 & 8.38e-05 & -8.46e-06 & 6.92e-04 & -1.28e-02 & -7.66e-03 & -1.05e-04 & -6.18e-06 & 7.59e-05 & -6.79e-06 & 6.24e-04 & -1.06e-02 & -7.33e-03 & -7.16e-05 & -5.04e-06 & 6.29e-05 & -5.33e-06 & 5.12e-04 & -7.82e-03 & -4.81e-03 & -5.28e-05 & -3.85e-06 & 4.96e-05 & -4.02e-06 & 4.02e-04 & -3.20e-03 & -2.62e-03 & -4.03e-05 \\
-1.09e-04 & -2.01e-03 & 4.13e-04 & -1.77e-02 & 3.66e+00 & 1.63e+00 & 7.97e-03 & 7.38e-05 & -1.49e-03 & 3.37e-04 & -1.39e-02 & 3.43e+00 & 1.31e+00 & 6.28e-03 & 3.58e-05 & -9.56e-04 & 2.47e-04 & -1.01e-02 & 3.20e+00 & 1.05e+00 & 4.86e-03 & 1.24e-05 & -7.12e-04 & 1.90e-04 & -7.82e-03 & 2.65e+00 & 9.25e-01 & 3.86e-03 & -6.02e-06 & -5.70e-04 & 1.41e-04 & -6.16e-03 & 1.94e+00 & 8.11e-01 & 2.87e-03 \\
--1.66e-05 & -1.63e-03 & 8.00e-04 & -7.72e-03 & 8.52e-01 & 9.61e+00 & 3.03e-03 & 5.08e-05 & -1.96e-03 & 6.40e-04 & -8.33e-03 & 7.80e-01 & 9.54e+00 & 3.21e-03 & 8.41e-05 & -1.55e-03 & 5.11e-04 & -7.01e-03 & 1.04e+00 & 8.61e+00 & -3.90e-04 & 7.22e-05 & -1.09e-03 & 4.07e-04 & -4.81e-03 & 9.25e-01 & 7.33e+00 & -1.38e-03 & 2.35e-05 & -3.85e-04 & 3.14e-04 & -1.61e-03 & 7.80e-01 & 5.67e+00 & -2.14e-03 \\
-1.05e-06 & -7.87e-06 & 4.56e-06 & -1.16e-04 & 3.02e-03 & 3.16e-03 & 1.41e-04 & 6.94e-07 & -5.57e-06 & 3.75e-06 & -9.24e-05 & 4.61e-03 & 3.93e-06 & 1.19e-04 & 2.43e-07 & -3.43e-06 & 2.81e-06 & -6.68e-05 & 4.99e-03 & -1.61e-03 & 1.06e-04 & 4.62e-08 & -2.97e-06 & 2.19e-06 & -5.28e-05 & 3.86e-03 & -1.38e-03 & 8.88e-05 & -3.18e-08 & -3.62e-06 & 1.63e-06 & -4.51e-05 & 1.72e-03 & -4.81e-05 & 7.16e-05 \\
-2.24e-07 & -7.31e-07 & 1.39e-07 & -6.36e-06 & 3.86e-05 & -9.95e-05 & 9.17e-07 & 1.88e-07 & -6.24e-07 & 1.14e-07 & -5.25e-06 & 5.79e-05 & -2.30e-05 & 6.68e-07 & 1.67e-07 & -5.69e-07 & 9.40e-08 & -4.66e-06 & 2.60e-05 & 2.13e-05 & 2.10e-07 & 1.42e-07 & -4.78e-07 & 7.71e-08 & -3.85e-06 & -6.02e-06 & 2.35e-05 & -3.18e-08 & 1.26e-07 & -4.21e-07 & 6.61e-08 & -3.34e-06 & -5.81e-05 & 3.45e-05 & -2.39e-07 \\
--7.21e-07 & 1.14e-05 & -8.12e-07 & 7.71e-05 & -1.42e-03 & -3.83e-04 & -7.22e-06 & -6.00e-07 & 9.33e-06 & -6.87e-07 & 6.25e-05 & -1.14e-03 & -5.99e-04 & -6.26e-06 & -5.47e-07 & 8.69e-06 & -5.37e-07 & 5.77e-05 & -7.80e-04 & -6.03e-04 & -4.36e-06 & -4.64e-07 & 7.52e-06 & -4.22e-07 & 4.96e-05 & -5.70e-04 & -3.85e-04 & -3.62e-06 & -4.21e-07 & 7.00e-06 & -3.26e-07 & 4.58e-05 & -2.70e-04 & -3.78e-04 & -2.81e-06 \\
-1.43e-07 & -8.85e-07 & 4.67e-07 & -7.70e-06 & 1.29e-04 & 5.60e-04 & 3.61e-06 & 1.23e-07 & -7.68e-07 & 3.81e-07 & -6.56e-06 & 1.72e-04 & 5.06e-04 & 2.97e-06 & 9.84e-08 & -5.57e-07 & 3.18e-07 & -5.07e-06 & 1.84e-04 & 3.97e-04 & 2.13e-06 & 8.05e-08 & -4.35e-07 & 2.62e-07 & -4.02e-06 & 1.41e-04 & 3.14e-04 & 1.63e-06 & 6.61e-08 & -3.26e-07 & 2.25e-07 & -3.16e-06 & 5.74e-05 & 2.22e-04 & 1.20e-06 \\
--6.30e-06 & 7.62e-05 & -7.36e-06 & 6.34e-04 & -1.09e-02 & -7.65e-04 & -9.91e-05 & -5.27e-06 & 6.29e-05 & -6.16e-06 & 5.15e-04 & -1.02e-02 & -3.06e-03 & -8.31e-05 & -4.62e-06 & 5.80e-05 & -4.97e-06 & 4.74e-04 & -8.18e-03 & -3.07e-03 & -5.81e-05 & -3.85e-06 & 4.98e-05 & -3.96e-06 & 4.02e-04 & -6.16e-03 & -1.61e-03 & -4.51e-05 & -3.34e-06 & 4.58e-05 & -3.16e-06 & 3.66e-04 & -2.98e-03 & -1.23e-03 & -3.34e-05 \\
--3.58e-05 & -1.09e-03 & 1.56e-04 & -8.10e-03 & 2.89e+00 & 1.36e+00 & 2.61e-03 & -5.22e-05 & -7.66e-04 & 1.31e-04 & -5.96e-03 & 2.35e+00 & 1.08e+00 & 2.07e-03 & -6.31e-05 & -4.18e-04 & 9.24e-05 & -4.00e-03 & 2.21e+00 & 8.81e-01 & 1.91e-03 & -6.45e-05 & -3.00e-04 & 7.30e-05 & -3.20e-03 & 1.94e+00 & 7.80e-01 & 1.72e-03 & -5.81e-05 & -2.70e-04 & 5.74e-05 & -2.98e-03 & 1.80e+00 & 6.92e-01 & 1.55e-03 \\
--6.71e-06 & -1.17e-03 & 5.93e-04 & -4.86e-03 & 6.67e-01 & 7.93e+00 & 2.30e-03 & 9.50e-06 & -1.11e-03 & 4.77e-04 & -4.09e-03 & 6.50e-01 & 7.15e+00 & 1.95e-03 & 3.16e-05 & -8.99e-04 & 3.58e-04 & -3.86e-03 & 8.94e-01 & 6.41e+00 & 6.81e-04 & 3.01e-05 & -6.51e-04 & 2.81e-04 & -2.62e-03 & 8.11e-01 & 5.67e+00 & -4.81e-05 & 3.45e-05 & -3.78e-04 & 2.22e-04 & -1.23e-03 & 6.92e-01 & 5.36e+00 & -6.37e-04 \\
-4.73e-07 & -5.25e-06 & 3.15e-06 & -7.93e-05 & 2.09e-03 & 1.78e-03 & 1.08e-04 & 2.40e-07 & -4.00e-06 & 2.65e-06 & -6.74e-05 & 3.24e-03 & -1.30e-03 & 8.89e-05 & -5.49e-08 & -2.79e-06 & 1.99e-06 & -5.10e-05 & 3.63e-03 & -2.52e-03 & 8.25e-05 & -1.89e-07 & -2.44e-06 & 1.55e-06 & -4.03e-05 & 2.87e-03 & -2.14e-03 & 7.16e-05 & -2.39e-07 & -2.81e-06 & 1.20e-06 & -3.34e-05 & 1.55e-03 & -6.37e-04 & 6.60e-05
+5.5\times 10^{-7} & -1.8\times 10^{-6} & 3.9\times 10^{-7} & -1.6\times 10^{-5} & 2.1\times 10^{-4} & -2.6\times 10^{-4} & 3.6\times 10^{-6} & 4.5\times 10^{-7} & -1.5\times 10^{-6} & 3.1\times 10^{-7} & -1.3\times 10^{-5} & 2.6\times 10^{-4} & -1.3\times 10^{-4} & 2.8\times 10^{-6} & 3.6\times 10^{-7} & -1.2\times 10^{-6} & 2.4\times 10^{-7} & -1.0\times 10^{-5} & 1.9\times 10^{-4} & -5.5\times 10^{-5} & 1.7\times 10^{-6} & 2.9\times 10^{-7} & -9.2\times 10^{-7} & 1.9\times 10^{-7} & -8.1\times 10^{-6} & 1.1\times 10^{-4} & -1.7\times 10^{-5} & 1.1\times 10^{-6} & 2.2\times 10^{-7} & -7.2\times 10^{-7} & 1.4\times 10^{-7} & -6.3\times 10^{-6} & -3.6\times 10^{-5} & -6.7\times 10^{-6} & 4.7\times 10^{-7} \\
+-1.8\times 10^{-6} & 2.7\times 10^{-5} & -2.6\times 10^{-6} & 1.9\times 10^{-4} & -4.0\times 10^{-3} & -3.0\times 10^{-3} & -1.8\times 10^{-5} & -1.4\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.2\times 10^{-3} & -2.7\times 10^{-3} & -1.4\times 10^{-5} & -1.1\times 10^{-6} & 1.7\times 10^{-5} & -1.6\times 10^{-6} & 1.2\times 10^{-4} & -2.6\times 10^{-3} & -2.1\times 10^{-3} & -1.0\times 10^{-5} & -9.2\times 10^{-7} & 1.4\times 10^{-5} & -1.2\times 10^{-6} & 9.4\times 10^{-5} & -2.0\times 10^{-3} & -1.6\times 10^{-3} & -7.9\times 10^{-6} & -7.3\times 10^{-7} & 1.1\times 10^{-5} & -8.8\times 10^{-7} & 7.6\times 10^{-5} & -1.1\times 10^{-3} & -1.2\times 10^{-3} & -5.2\times 10^{-6} \\
+3.9\times 10^{-7} & -2.6\times 10^{-6} & 1.3\times 10^{-6} & -2.2\times 10^{-5} & 3.9\times 10^{-4} & 1.7\times 10^{-3} & 1.0\times 10^{-5} & 3.2\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 5.0\times 10^{-4} & 1.4\times 10^{-3} & 8.3\times 10^{-6} & 2.4\times 10^{-7} & -1.5\times 10^{-6} & 7.8\times 10^{-7} & -1.3\times 10^{-5} & 5.4\times 10^{-4} & 1.0\times 10^{-3} & 6.0\times 10^{-6} & 1.9\times 10^{-7} & -1.1\times 10^{-6} & 6.1\times 10^{-7} & -1.0\times 10^{-5} & 4.1\times 10^{-4} & 8.0\times 10^{-4} & 4.6\times 10^{-6} & 1.4\times 10^{-7} & -8.1\times 10^{-7} & 4.7\times 10^{-7} & -7.4\times 10^{-6} & 1.6\times 10^{-4} & 5.9\times 10^{-4} & 3.1\times 10^{-6} \\
+-1.6\times 10^{-5} & 1.9\times 10^{-4} & -2.2\times 10^{-5} & 1.6\times 10^{-3} & -2.9\times 10^{-2} & -1.4\times 10^{-2} & -2.7\times 10^{-4} & -1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.8\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.0\times 10^{-5} & 1.2\times 10^{-4} & -1.4\times 10^{-5} & 9.9\times 10^{-4} & -2.3\times 10^{-2} & -1.0\times 10^{-2} & -1.5\times 10^{-4} & -8.3\times 10^{-6} & 9.5\times 10^{-5} & -1.1\times 10^{-5} & 7.9\times 10^{-4} & -1.8\times 10^{-2} & -7.7\times 10^{-3} & -1.2\times 10^{-4} & -6.4\times 10^{-6} & 7.7\times 10^{-5} & -7.7\times 10^{-6} & 6.3\times 10^{-4} & -8.1\times 10^{-3} & -4.9\times 10^{-3} & -7.9\times 10^{-5} \\
+2.1\times 10^{-4} & -4.0\times 10^{-3} & 3.9\times 10^{-4} & -2.9\times 10^{-2} & 6.9\times 10^{+0} & 1.3\times 10^{+0} & 6.7\times 10^{-3} & 1.4\times 10^{-4} & -3.0\times 10^{-3} & 3.2\times 10^{-4} & -2.2\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 5.1\times 10^{-3} & 9.6\times 10^{-5} & -2.2\times 10^{-3} & 2.3\times 10^{-4} & -1.6\times 10^{-2} & 4.5\times 10^{+0} & 9.7\times 10^{-1} & 3.7\times 10^{-3} & 6.0\times 10^{-5} & -1.7\times 10^{-3} & 1.7\times 10^{-4} & -1.3\times 10^{-2} & 3.7\times 10^{+0} & 8.5\times 10^{-1} & 3.0\times 10^{-3} & 3.9\times 10^{-5} & -1.4\times 10^{-3} & 1.3\times 10^{-4} & -1.1\times 10^{-2} & 2.9\times 10^{+0} & 6.7\times 10^{-1} & 2.1\times 10^{-3} \\
+-2.6\times 10^{-4} & -3.0\times 10^{-3} & 1.7\times 10^{-3} & -1.4\times 10^{-2} & 1.3\times 10^{+0} & 1.7\times 10^{+1} & 8.7\times 10^{-3} & -1.9\times 10^{-4} & -2.8\times 10^{-3} & 1.3\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 7.1\times 10^{-3} & -1.7\times 10^{-4} & -1.5\times 10^{-3} & 9.7\times 10^{-4} & -6.8\times 10^{-3} & 1.8\times 10^{+0} & 1.1\times 10^{+1} & 4.9\times 10^{-3} & -1.2\times 10^{-4} & -1.0\times 10^{-3} & 7.6\times 10^{-4} & -4.4\times 10^{-3} & 1.6\times 10^{+0} & 9.6\times 10^{+0} & 3.2\times 10^{-3} & -10.0\times 10^{-5} & -3.8\times 10^{-4} & 5.6\times 10^{-4} & -7.6\times 10^{-4} & 1.4\times 10^{+0} & 7.9\times 10^{+0} & 1.8\times 10^{-3} \\
+3.6\times 10^{-6} & -1.8\times 10^{-5} & 1.0\times 10^{-5} & -2.7\times 10^{-4} & 6.7\times 10^{-3} & 8.7\times 10^{-3} & 2.8\times 10^{-4} & 2.9\times 10^{-6} & -1.4\times 10^{-5} & 8.4\times 10^{-6} & -2.1\times 10^{-4} & 1.1\times 10^{-2} & 6.8\times 10^{-3} & 2.3\times 10^{-4} & 2.0\times 10^{-6} & -9.4\times 10^{-6} & 6.4\times 10^{-6} & -1.6\times 10^{-4} & 1.1\times 10^{-2} & 4.1\times 10^{-3} & 1.8\times 10^{-4} & 1.4\times 10^{-6} & -7.4\times 10^{-6} & 4.9\times 10^{-6} & -1.2\times 10^{-4} & 8.0\times 10^{-3} & 3.0\times 10^{-3} & 1.4\times 10^{-4} & 9.2\times 10^{-7} & -7.2\times 10^{-6} & 3.6\times 10^{-6} & -9.9\times 10^{-5} & 2.6\times 10^{-3} & 2.3\times 10^{-3} & 1.1\times 10^{-4} \\
+4.5\times 10^{-7} & -1.4\times 10^{-6} & 3.2\times 10^{-7} & -1.3\times 10^{-5} & 1.4\times 10^{-4} & -1.9\times 10^{-4} & 2.9\times 10^{-6} & 4.0\times 10^{-7} & -1.3\times 10^{-6} & 2.7\times 10^{-7} & -1.1\times 10^{-5} & 2.0\times 10^{-4} & -2.5\times 10^{-5} & 2.3\times 10^{-6} & 3.2\times 10^{-7} & -1.0\times 10^{-6} & 2.1\times 10^{-7} & -9.1\times 10^{-6} & 1.4\times 10^{-4} & 4.3\times 10^{-5} & 1.3\times 10^{-6} & 2.6\times 10^{-7} & -8.2\times 10^{-7} & 1.7\times 10^{-7} & -7.1\times 10^{-6} & 7.4\times 10^{-5} & 5.1\times 10^{-5} & 6.9\times 10^{-7} & 1.9\times 10^{-7} & -6.0\times 10^{-7} & 1.2\times 10^{-7} & -5.3\times 10^{-6} & -5.2\times 10^{-5} & 9.5\times 10^{-6} & 2.4\times 10^{-7} \\
+-1.5\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.0\times 10^{-3} & -2.8\times 10^{-3} & -1.4\times 10^{-5} & -1.3\times 10^{-6} & 1.9\times 10^{-5} & -1.8\times 10^{-6} & 1.3\times 10^{-4} & -2.4\times 10^{-3} & -3.0\times 10^{-3} & -1.2\times 10^{-5} & -1.0\times 10^{-6} & 1.6\times 10^{-5} & -1.4\times 10^{-6} & 1.0\times 10^{-4} & -2.0\times 10^{-3} & -2.6\times 10^{-3} & -7.6\times 10^{-6} & -8.4\times 10^{-7} & 1.2\times 10^{-5} & -1.0\times 10^{-6} & 8.4\times 10^{-5} & -1.5\times 10^{-3} & -2.0\times 10^{-3} & -5.6\times 10^{-6} & -6.2\times 10^{-7} & 9.3\times 10^{-6} & -7.7\times 10^{-7} & 6.3\times 10^{-5} & -7.7\times 10^{-4} & -1.1\times 10^{-3} & -4.0\times 10^{-6} \\
+3.1\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 3.2\times 10^{-4} & 1.3\times 10^{-3} & 8.4\times 10^{-6} & 2.7\times 10^{-7} & -1.8\times 10^{-6} & 8.5\times 10^{-7} & -1.5\times 10^{-5} & 4.1\times 10^{-4} & 1.1\times 10^{-3} & 6.7\times 10^{-6} & 2.0\times 10^{-7} & -1.2\times 10^{-6} & 6.7\times 10^{-7} & -1.1\times 10^{-5} & 4.4\times 10^{-4} & 8.2\times 10^{-4} & 4.9\times 10^{-6} & 1.6\times 10^{-7} & -9.4\times 10^{-7} & 5.2\times 10^{-7} & -8.5\times 10^{-6} & 3.4\times 10^{-4} & 6.4\times 10^{-4} & 3.7\times 10^{-6} & 1.1\times 10^{-7} & -6.9\times 10^{-7} & 3.8\times 10^{-7} & -6.2\times 10^{-6} & 1.3\times 10^{-4} & 4.8\times 10^{-4} & 2.6\times 10^{-6} \\
+-1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.1\times 10^{-5} & 1.3\times 10^{-4} & -1.5\times 10^{-5} & 1.1\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -1.7\times 10^{-4} & -9.0\times 10^{-6} & 1.0\times 10^{-4} & -1.2\times 10^{-5} & 8.7\times 10^{-4} & -1.8\times 10^{-2} & -1.1\times 10^{-2} & -1.2\times 10^{-4} & -7.2\times 10^{-6} & 8.3\times 10^{-5} & -8.9\times 10^{-6} & 6.9\times 10^{-4} & -1.4\times 10^{-2} & -8.3\times 10^{-3} & -9.2\times 10^{-5} & -5.3\times 10^{-6} & 6.2\times 10^{-5} & -6.6\times 10^{-6} & 5.1\times 10^{-4} & -6.0\times 10^{-3} & -4.1\times 10^{-3} & -6.7\times 10^{-5} \\
+2.6\times 10^{-4} & -3.2\times 10^{-3} & 5.0\times 10^{-4} & -2.8\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 1.1\times 10^{-2} & 2.0\times 10^{-4} & -2.4\times 10^{-3} & 4.1\times 10^{-4} & -2.2\times 10^{-2} & 5.1\times 10^{+0} & 9.4\times 10^{-1} & 8.4\times 10^{-3} & 1.4\times 10^{-4} & -1.8\times 10^{-3} & 3.0\times 10^{-4} & -1.6\times 10^{-2} & 4.3\times 10^{+0} & 8.6\times 10^{-1} & 6.0\times 10^{-3} & 9.8\times 10^{-5} & -1.4\times 10^{-3} & 2.3\times 10^{-4} & -1.3\times 10^{-2} & 3.4\times 10^{+0} & 7.8\times 10^{-1} & 4.6\times 10^{-3} & 5.8\times 10^{-5} & -1.1\times 10^{-3} & 1.7\times 10^{-4} & -1.0\times 10^{-2} & 2.4\times 10^{+0} & 6.5\times 10^{-1} & 3.2\times 10^{-3} \\
+-1.3\times 10^{-4} & -2.7\times 10^{-3} & 1.4\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 6.8\times 10^{-3} & -2.5\times 10^{-5} & -3.0\times 10^{-3} & 1.1\times 10^{-3} & -1.3\times 10^{-2} & 9.4\times 10^{-1} & 1.4\times 10^{+1} & 6.4\times 10^{-3} & 1.8\times 10^{-5} & -2.2\times 10^{-3} & 8.6\times 10^{-4} & -1.1\times 10^{-2} & 1.5\times 10^{+0} & 1.2\times 10^{+1} & 1.6\times 10^{-3} & 2.0\times 10^{-5} & -1.6\times 10^{-3} & 6.7\times 10^{-4} & -7.7\times 10^{-3} & 1.3\times 10^{+0} & 9.5\times 10^{+0} & 3.9\times 10^{-6} & -2.3\times 10^{-5} & -6.0\times 10^{-4} & 5.1\times 10^{-4} & -3.1\times 10^{-3} & 1.1\times 10^{+0} & 7.1\times 10^{+0} & -1.3\times 10^{-3} \\
+2.8\times 10^{-6} & -1.4\times 10^{-5} & 8.3\times 10^{-6} & -2.1\times 10^{-4} & 5.1\times 10^{-3} & 7.1\times 10^{-3} & 2.3\times 10^{-4} & 2.3\times 10^{-6} & -1.2\times 10^{-5} & 6.7\times 10^{-6} & -1.7\times 10^{-4} & 8.4\times 10^{-3} & 6.4\times 10^{-3} & 1.9\times 10^{-4} & 1.6\times 10^{-6} & -8.8\times 10^{-6} & 5.2\times 10^{-6} & -1.4\times 10^{-4} & 8.6\times 10^{-3} & 4.5\times 10^{-3} & 1.5\times 10^{-4} & 1.1\times 10^{-6} & -7.0\times 10^{-6} & 4.0\times 10^{-6} & -1.1\times 10^{-4} & 6.3\times 10^{-3} & 3.2\times 10^{-3} & 1.2\times 10^{-4} & 6.7\times 10^{-7} & -6.3\times 10^{-6} & 3.0\times 10^{-6} & -8.3\times 10^{-5} & 2.1\times 10^{-3} & 2.0\times 10^{-3} & 8.9\times 10^{-5} \\
+3.6\times 10^{-7} & -1.1\times 10^{-6} & 2.4\times 10^{-7} & -1.0\times 10^{-5} & 9.6\times 10^{-5} & -1.7\times 10^{-4} & 2.0\times 10^{-6} & 3.2\times 10^{-7} & -1.0\times 10^{-6} & 2.0\times 10^{-7} & -9.0\times 10^{-6} & 1.4\times 10^{-4} & 1.8\times 10^{-5} & 1.6\times 10^{-6} & 2.8\times 10^{-7} & -9.3\times 10^{-7} & 1.7\times 10^{-7} & -7.8\times 10^{-6} & 9.4\times 10^{-5} & 1.0\times 10^{-4} & 6.8\times 10^{-7} & 2.3\times 10^{-7} & -7.4\times 10^{-7} & 1.3\times 10^{-7} & -6.2\times 10^{-6} & 3.6\times 10^{-5} & 8.4\times 10^{-5} & 2.4\times 10^{-7} & 1.7\times 10^{-7} & -5.5\times 10^{-7} & 9.8\times 10^{-8} & -4.6\times 10^{-6} & -6.3\times 10^{-5} & 3.2\times 10^{-5} & -5.5\times 10^{-8} \\
+-1.2\times 10^{-6} & 1.7\times 10^{-5} & -1.5\times 10^{-6} & 1.2\times 10^{-4} & -2.2\times 10^{-3} & -1.5\times 10^{-3} & -9.4\times 10^{-6} & -1.0\times 10^{-6} & 1.6\times 10^{-5} & -1.2\times 10^{-6} & 1.0\times 10^{-4} & -1.8\times 10^{-3} & -2.2\times 10^{-3} & -8.8\times 10^{-6} & -9.3\times 10^{-7} & 1.4\times 10^{-5} & -9.7\times 10^{-7} & 9.4\times 10^{-5} & -1.3\times 10^{-3} & -2.2\times 10^{-3} & -5.0\times 10^{-6} & -7.6\times 10^{-7} & 1.1\times 10^{-5} & -7.5\times 10^{-7} & 7.6\times 10^{-5} & -9.6\times 10^{-4} & -1.6\times 10^{-3} & -3.4\times 10^{-6} & -5.7\times 10^{-7} & 8.7\times 10^{-6} & -5.6\times 10^{-7} & 5.8\times 10^{-5} & -4.2\times 10^{-4} & -9.0\times 10^{-4} & -2.8\times 10^{-6} \\
+2.4\times 10^{-7} & -1.6\times 10^{-6} & 7.8\times 10^{-7} & -1.4\times 10^{-5} & 2.3\times 10^{-4} & 9.7\times 10^{-4} & 6.4\times 10^{-6} & 2.1\times 10^{-7} & -1.4\times 10^{-6} & 6.7\times 10^{-7} & -1.2\times 10^{-5} & 3.0\times 10^{-4} & 8.6\times 10^{-4} & 5.2\times 10^{-6} & 1.7\times 10^{-7} & -9.7\times 10^{-7} & 5.5\times 10^{-7} & -8.8\times 10^{-6} & 3.3\times 10^{-4} & 6.6\times 10^{-4} & 3.7\times 10^{-6} & 1.3\times 10^{-7} & -7.4\times 10^{-7} & 4.3\times 10^{-7} & -6.8\times 10^{-6} & 2.5\times 10^{-4} & 5.1\times 10^{-4} & 2.8\times 10^{-6} & 9.4\times 10^{-8} & -5.4\times 10^{-7} & 3.2\times 10^{-7} & -5.0\times 10^{-6} & 9.2\times 10^{-5} & 3.6\times 10^{-4} & 2.0\times 10^{-6} \\
+-1.0\times 10^{-5} & 1.2\times 10^{-4} & -1.3\times 10^{-5} & 9.9\times 10^{-4} & -1.6\times 10^{-2} & -6.8\times 10^{-3} & -1.6\times 10^{-4} & -9.1\times 10^{-6} & 1.0\times 10^{-4} & -1.1\times 10^{-5} & 8.7\times 10^{-4} & -1.6\times 10^{-2} & -1.1\times 10^{-2} & -1.4\times 10^{-4} & -7.8\times 10^{-6} & 9.4\times 10^{-5} & -8.8\times 10^{-6} & 7.8\times 10^{-4} & -1.4\times 10^{-2} & -1.0\times 10^{-2} & -9.2\times 10^{-5} & -6.3\times 10^{-6} & 7.6\times 10^{-5} & -6.8\times 10^{-6} & 6.2\times 10^{-4} & -1.0\times 10^{-2} & -7.0\times 10^{-3} & -6.7\times 10^{-5} & -4.7\times 10^{-6} & 5.8\times 10^{-5} & -5.1\times 10^{-6} & 4.7\times 10^{-4} & -4.0\times 10^{-3} & -3.9\times 10^{-3} & -5.1\times 10^{-5} \\
+1.9\times 10^{-4} & -2.6\times 10^{-3} & 5.4\times 10^{-4} & -2.3\times 10^{-2} & 4.5\times 10^{+0} & 1.8\times 10^{+0} & 1.1\times 10^{-2} & 1.4\times 10^{-4} & -2.0\times 10^{-3} & 4.4\times 10^{-4} & -1.8\times 10^{-2} & 4.3\times 10^{+0} & 1.5\times 10^{+0} & 8.6\times 10^{-3} & 9.4\times 10^{-5} & -1.3\times 10^{-3} & 3.3\times 10^{-4} & -1.4\times 10^{-2} & 4.0\times 10^{+0} & 1.2\times 10^{+0} & 6.5\times 10^{-3} & 5.8\times 10^{-5} & -9.9\times 10^{-4} & 2.5\times 10^{-4} & -1.1\times 10^{-2} & 3.2\times 10^{+0} & 1.0\times 10^{+0} & 5.0\times 10^{-3} & 2.6\times 10^{-5} & -7.8\times 10^{-4} & 1.8\times 10^{-4} & -8.2\times 10^{-3} & 2.2\times 10^{+0} & 8.9\times 10^{-1} & 3.6\times 10^{-3} \\
+-5.5\times 10^{-5} & -2.1\times 10^{-3} & 1.0\times 10^{-3} & -1.0\times 10^{-2} & 9.7\times 10^{-1} & 1.1\times 10^{+1} & 4.1\times 10^{-3} & 4.3\times 10^{-5} & -2.6\times 10^{-3} & 8.2\times 10^{-4} & -1.1\times 10^{-2} & 8.6\times 10^{-1} & 1.2\times 10^{+1} & 4.5\times 10^{-3} & 1.0\times 10^{-4} & -2.2\times 10^{-3} & 6.6\times 10^{-4} & -1.0\times 10^{-2} & 1.2\times 10^{+0} & 1.0\times 10^{+1} & -3.8\times 10^{-4} & 8.4\times 10^{-5} & -1.6\times 10^{-3} & 5.2\times 10^{-4} & -7.3\times 10^{-3} & 1.1\times 10^{+0} & 8.6\times 10^{+0} & -1.6\times 10^{-3} & 2.1\times 10^{-5} & -6.0\times 10^{-4} & 4.0\times 10^{-4} & -3.1\times 10^{-3} & 8.8\times 10^{-1} & 6.4\times 10^{+0} & -2.5\times 10^{-3} \\
+1.7\times 10^{-6} & -1.0\times 10^{-5} & 6.0\times 10^{-6} & -1.5\times 10^{-4} & 3.7\times 10^{-3} & 4.9\times 10^{-3} & 1.8\times 10^{-4} & 1.3\times 10^{-6} & -7.6\times 10^{-6} & 4.9\times 10^{-6} & -1.2\times 10^{-4} & 6.0\times 10^{-3} & 1.6\times 10^{-3} & 1.5\times 10^{-4} & 6.8\times 10^{-7} & -5.0\times 10^{-6} & 3.7\times 10^{-6} & -9.2\times 10^{-5} & 6.5\times 10^{-3} & -3.8\times 10^{-4} & 1.3\times 10^{-4} & 3.9\times 10^{-7} & -4.1\times 10^{-6} & 2.9\times 10^{-6} & -7.2\times 10^{-5} & 4.9\times 10^{-3} & -3.9\times 10^{-4} & 1.1\times 10^{-4} & 2.1\times 10^{-7} & -4.4\times 10^{-6} & 2.1\times 10^{-6} & -5.8\times 10^{-5} & 1.9\times 10^{-3} & 6.8\times 10^{-4} & 8.3\times 10^{-5} \\
+2.9\times 10^{-7} & -9.2\times 10^{-7} & 1.9\times 10^{-7} & -8.3\times 10^{-6} & 6.0\times 10^{-5} & -1.2\times 10^{-4} & 1.4\times 10^{-6} & 2.6\times 10^{-7} & -8.4\times 10^{-7} & 1.6\times 10^{-7} & -7.2\times 10^{-6} & 9.8\times 10^{-5} & 2.0\times 10^{-5} & 1.1\times 10^{-6} & 2.3\times 10^{-7} & -7.6\times 10^{-7} & 1.3\times 10^{-7} & -6.3\times 10^{-6} & 5.8\times 10^{-5} & 8.4\times 10^{-5} & 3.9\times 10^{-7} & 1.9\times 10^{-7} & -6.2\times 10^{-7} & 1.0\times 10^{-7} & -5.0\times 10^{-6} & 1.2\times 10^{-5} & 7.2\times 10^{-5} & 4.6\times 10^{-8} & 1.4\times 10^{-7} & -4.6\times 10^{-7} & 8.0\times 10^{-8} & -3.9\times 10^{-6} & -6.4\times 10^{-5} & 3.0\times 10^{-5} & -1.9\times 10^{-7} \\
+-9.2\times 10^{-7} & 1.4\times 10^{-5} & -1.1\times 10^{-6} & 9.5\times 10^{-5} & -1.7\times 10^{-3} & -1.0\times 10^{-3} & -7.4\times 10^{-6} & -8.2\times 10^{-7} & 1.2\times 10^{-5} & -9.4\times 10^{-7} & 8.3\times 10^{-5} & -1.4\times 10^{-3} & -1.6\times 10^{-3} & -7.0\times 10^{-6} & -7.4\times 10^{-7} & 1.1\times 10^{-5} & -7.4\times 10^{-7} & 7.6\times 10^{-5} & -9.9\times 10^{-4} & -1.6\times 10^{-3} & -4.1\times 10^{-6} & -6.2\times 10^{-7} & 9.5\times 10^{-6} & -5.8\times 10^{-7} & 6.3\times 10^{-5} & -7.1\times 10^{-4} & -1.1\times 10^{-3} & -3.0\times 10^{-6} & -4.8\times 10^{-7} & 7.5\times 10^{-6} & -4.4\times 10^{-7} & 5.0\times 10^{-5} & -3.0\times 10^{-4} & -6.5\times 10^{-4} & -2.4\times 10^{-6} \\
+1.9\times 10^{-7} & -1.2\times 10^{-6} & 6.1\times 10^{-7} & -1.1\times 10^{-5} & 1.7\times 10^{-4} & 7.6\times 10^{-4} & 4.9\times 10^{-6} & 1.7\times 10^{-7} & -1.0\times 10^{-6} & 5.2\times 10^{-7} & -8.9\times 10^{-6} & 2.3\times 10^{-4} & 6.7\times 10^{-4} & 4.0\times 10^{-6} & 1.3\times 10^{-7} & -7.5\times 10^{-7} & 4.3\times 10^{-7} & -6.8\times 10^{-6} & 2.5\times 10^{-4} & 5.2\times 10^{-4} & 2.9\times 10^{-6} & 1.0\times 10^{-7} & -5.8\times 10^{-7} & 3.5\times 10^{-7} & -5.3\times 10^{-6} & 1.9\times 10^{-4} & 4.1\times 10^{-4} & 2.2\times 10^{-6} & 7.7\times 10^{-8} & -4.2\times 10^{-7} & 2.6\times 10^{-7} & -4.0\times 10^{-6} & 7.3\times 10^{-5} & 2.8\times 10^{-4} & 1.6\times 10^{-6} \\
+-8.1\times 10^{-6} & 9.4\times 10^{-5} & -1.0\times 10^{-5} & 7.9\times 10^{-4} & -1.3\times 10^{-2} & -4.4\times 10^{-3} & -1.2\times 10^{-4} & -7.1\times 10^{-6} & 8.4\times 10^{-5} & -8.5\times 10^{-6} & 6.9\times 10^{-4} & -1.3\times 10^{-2} & -7.7\times 10^{-3} & -1.1\times 10^{-4} & -6.2\times 10^{-6} & 7.6\times 10^{-5} & -6.8\times 10^{-6} & 6.2\times 10^{-4} & -1.1\times 10^{-2} & -7.3\times 10^{-3} & -7.2\times 10^{-5} & -5.0\times 10^{-6} & 6.3\times 10^{-5} & -5.3\times 10^{-6} & 5.1\times 10^{-4} & -7.8\times 10^{-3} & -4.8\times 10^{-3} & -5.3\times 10^{-5} & -3.9\times 10^{-6} & 5.0\times 10^{-5} & -4.0\times 10^{-6} & 4.0\times 10^{-4} & -3.2\times 10^{-3} & -2.6\times 10^{-3} & -4.0\times 10^{-5} \\
+1.1\times 10^{-4} & -2.0\times 10^{-3} & 4.1\times 10^{-4} & -1.8\times 10^{-2} & 3.7\times 10^{+0} & 1.6\times 10^{+0} & 8.0\times 10^{-3} & 7.4\times 10^{-5} & -1.5\times 10^{-3} & 3.4\times 10^{-4} & -1.4\times 10^{-2} & 3.4\times 10^{+0} & 1.3\times 10^{+0} & 6.3\times 10^{-3} & 3.6\times 10^{-5} & -9.6\times 10^{-4} & 2.5\times 10^{-4} & -1.0\times 10^{-2} & 3.2\times 10^{+0} & 1.1\times 10^{+0} & 4.9\times 10^{-3} & 1.2\times 10^{-5} & -7.1\times 10^{-4} & 1.9\times 10^{-4} & -7.8\times 10^{-3} & 2.6\times 10^{+0} & 9.3\times 10^{-1} & 3.9\times 10^{-3} & -6.0\times 10^{-6} & -5.7\times 10^{-4} & 1.4\times 10^{-4} & -6.2\times 10^{-3} & 1.9\times 10^{+0} & 8.1\times 10^{-1} & 2.9\times 10^{-3} \\
+-1.7\times 10^{-5} & -1.6\times 10^{-3} & 8.0\times 10^{-4} & -7.7\times 10^{-3} & 8.5\times 10^{-1} & 9.6\times 10^{+0} & 3.0\times 10^{-3} & 5.1\times 10^{-5} & -2.0\times 10^{-3} & 6.4\times 10^{-4} & -8.3\times 10^{-3} & 7.8\times 10^{-1} & 9.5\times 10^{+0} & 3.2\times 10^{-3} & 8.4\times 10^{-5} & -1.6\times 10^{-3} & 5.1\times 10^{-4} & -7.0\times 10^{-3} & 1.0\times 10^{+0} & 8.6\times 10^{+0} & -3.9\times 10^{-4} & 7.2\times 10^{-5} & -1.1\times 10^{-3} & 4.1\times 10^{-4} & -4.8\times 10^{-3} & 9.3\times 10^{-1} & 7.3\times 10^{+0} & -1.4\times 10^{-3} & 2.3\times 10^{-5} & -3.9\times 10^{-4} & 3.1\times 10^{-4} & -1.6\times 10^{-3} & 7.8\times 10^{-1} & 5.7\times 10^{+0} & -2.1\times 10^{-3} \\
+1.1\times 10^{-6} & -7.9\times 10^{-6} & 4.6\times 10^{-6} & -1.2\times 10^{-4} & 3.0\times 10^{-3} & 3.2\times 10^{-3} & 1.4\times 10^{-4} & 6.9\times 10^{-7} & -5.6\times 10^{-6} & 3.7\times 10^{-6} & -9.2\times 10^{-5} & 4.6\times 10^{-3} & 3.9\times 10^{-6} & 1.2\times 10^{-4} & 2.4\times 10^{-7} & -3.4\times 10^{-6} & 2.8\times 10^{-6} & -6.7\times 10^{-5} & 5.0\times 10^{-3} & -1.6\times 10^{-3} & 1.1\times 10^{-4} & 4.6\times 10^{-8} & -3.0\times 10^{-6} & 2.2\times 10^{-6} & -5.3\times 10^{-5} & 3.9\times 10^{-3} & -1.4\times 10^{-3} & 8.9\times 10^{-5} & -3.2\times 10^{-8} & -3.6\times 10^{-6} & 1.6\times 10^{-6} & -4.5\times 10^{-5} & 1.7\times 10^{-3} & -4.8\times 10^{-5} & 7.2\times 10^{-5} \\
+2.2\times 10^{-7} & -7.3\times 10^{-7} & 1.4\times 10^{-7} & -6.4\times 10^{-6} & 3.9\times 10^{-5} & -10.0\times 10^{-5} & 9.2\times 10^{-7} & 1.9\times 10^{-7} & -6.2\times 10^{-7} & 1.1\times 10^{-7} & -5.3\times 10^{-6} & 5.8\times 10^{-5} & -2.3\times 10^{-5} & 6.7\times 10^{-7} & 1.7\times 10^{-7} & -5.7\times 10^{-7} & 9.4\times 10^{-8} & -4.7\times 10^{-6} & 2.6\times 10^{-5} & 2.1\times 10^{-5} & 2.1\times 10^{-7} & 1.4\times 10^{-7} & -4.8\times 10^{-7} & 7.7\times 10^{-8} & -3.9\times 10^{-6} & -6.0\times 10^{-6} & 2.3\times 10^{-5} & -3.2\times 10^{-8} & 1.3\times 10^{-7} & -4.2\times 10^{-7} & 6.6\times 10^{-8} & -3.3\times 10^{-6} & -5.8\times 10^{-5} & 3.4\times 10^{-5} & -2.4\times 10^{-7} \\
+-7.2\times 10^{-7} & 1.1\times 10^{-5} & -8.1\times 10^{-7} & 7.7\times 10^{-5} & -1.4\times 10^{-3} & -3.8\times 10^{-4} & -7.2\times 10^{-6} & -6.0\times 10^{-7} & 9.3\times 10^{-6} & -6.9\times 10^{-7} & 6.2\times 10^{-5} & -1.1\times 10^{-3} & -6.0\times 10^{-4} & -6.3\times 10^{-6} & -5.5\times 10^{-7} & 8.7\times 10^{-6} & -5.4\times 10^{-7} & 5.8\times 10^{-5} & -7.8\times 10^{-4} & -6.0\times 10^{-4} & -4.4\times 10^{-6} & -4.6\times 10^{-7} & 7.5\times 10^{-6} & -4.2\times 10^{-7} & 5.0\times 10^{-5} & -5.7\times 10^{-4} & -3.9\times 10^{-4} & -3.6\times 10^{-6} & -4.2\times 10^{-7} & 7.0\times 10^{-6} & -3.3\times 10^{-7} & 4.6\times 10^{-5} & -2.7\times 10^{-4} & -3.8\times 10^{-4} & -2.8\times 10^{-6} \\
+1.4\times 10^{-7} & -8.8\times 10^{-7} & 4.7\times 10^{-7} & -7.7\times 10^{-6} & 1.3\times 10^{-4} & 5.6\times 10^{-4} & 3.6\times 10^{-6} & 1.2\times 10^{-7} & -7.7\times 10^{-7} & 3.8\times 10^{-7} & -6.6\times 10^{-6} & 1.7\times 10^{-4} & 5.1\times 10^{-4} & 3.0\times 10^{-6} & 9.8\times 10^{-8} & -5.6\times 10^{-7} & 3.2\times 10^{-7} & -5.1\times 10^{-6} & 1.8\times 10^{-4} & 4.0\times 10^{-4} & 2.1\times 10^{-6} & 8.0\times 10^{-8} & -4.4\times 10^{-7} & 2.6\times 10^{-7} & -4.0\times 10^{-6} & 1.4\times 10^{-4} & 3.1\times 10^{-4} & 1.6\times 10^{-6} & 6.6\times 10^{-8} & -3.3\times 10^{-7} & 2.2\times 10^{-7} & -3.2\times 10^{-6} & 5.7\times 10^{-5} & 2.2\times 10^{-4} & 1.2\times 10^{-6} \\
+-6.3\times 10^{-6} & 7.6\times 10^{-5} & -7.4\times 10^{-6} & 6.3\times 10^{-4} & -1.1\times 10^{-2} & -7.6\times 10^{-4} & -9.9\times 10^{-5} & -5.3\times 10^{-6} & 6.3\times 10^{-5} & -6.2\times 10^{-6} & 5.1\times 10^{-4} & -1.0\times 10^{-2} & -3.1\times 10^{-3} & -8.3\times 10^{-5} & -4.6\times 10^{-6} & 5.8\times 10^{-5} & -5.0\times 10^{-6} & 4.7\times 10^{-4} & -8.2\times 10^{-3} & -3.1\times 10^{-3} & -5.8\times 10^{-5} & -3.9\times 10^{-6} & 5.0\times 10^{-5} & -4.0\times 10^{-6} & 4.0\times 10^{-4} & -6.2\times 10^{-3} & -1.6\times 10^{-3} & -4.5\times 10^{-5} & -3.3\times 10^{-6} & 4.6\times 10^{-5} & -3.2\times 10^{-6} & 3.7\times 10^{-4} & -3.0\times 10^{-3} & -1.2\times 10^{-3} & -3.3\times 10^{-5} \\
+-3.6\times 10^{-5} & -1.1\times 10^{-3} & 1.6\times 10^{-4} & -8.1\times 10^{-3} & 2.9\times 10^{+0} & 1.4\times 10^{+0} & 2.6\times 10^{-3} & -5.2\times 10^{-5} & -7.7\times 10^{-4} & 1.3\times 10^{-4} & -6.0\times 10^{-3} & 2.4\times 10^{+0} & 1.1\times 10^{+0} & 2.1\times 10^{-3} & -6.3\times 10^{-5} & -4.2\times 10^{-4} & 9.2\times 10^{-5} & -4.0\times 10^{-3} & 2.2\times 10^{+0} & 8.8\times 10^{-1} & 1.9\times 10^{-3} & -6.4\times 10^{-5} & -3.0\times 10^{-4} & 7.3\times 10^{-5} & -3.2\times 10^{-3} & 1.9\times 10^{+0} & 7.8\times 10^{-1} & 1.7\times 10^{-3} & -5.8\times 10^{-5} & -2.7\times 10^{-4} & 5.7\times 10^{-5} & -3.0\times 10^{-3} & 1.8\times 10^{+0} & 6.9\times 10^{-1} & 1.5\times 10^{-3} \\
+-6.7\times 10^{-6} & -1.2\times 10^{-3} & 5.9\times 10^{-4} & -4.9\times 10^{-3} & 6.7\times 10^{-1} & 7.9\times 10^{+0} & 2.3\times 10^{-3} & 9.5\times 10^{-6} & -1.1\times 10^{-3} & 4.8\times 10^{-4} & -4.1\times 10^{-3} & 6.5\times 10^{-1} & 7.1\times 10^{+0} & 2.0\times 10^{-3} & 3.2\times 10^{-5} & -9.0\times 10^{-4} & 3.6\times 10^{-4} & -3.9\times 10^{-3} & 8.9\times 10^{-1} & 6.4\times 10^{+0} & 6.8\times 10^{-4} & 3.0\times 10^{-5} & -6.5\times 10^{-4} & 2.8\times 10^{-4} & -2.6\times 10^{-3} & 8.1\times 10^{-1} & 5.7\times 10^{+0} & -4.8\times 10^{-5} & 3.4\times 10^{-5} & -3.8\times 10^{-4} & 2.2\times 10^{-4} & -1.2\times 10^{-3} & 6.9\times 10^{-1} & 5.4\times 10^{+0} & -6.4\times 10^{-4} \\
+4.7\times 10^{-7} & -5.2\times 10^{-6} & 3.1\times 10^{-6} & -7.9\times 10^{-5} & 2.1\times 10^{-3} & 1.8\times 10^{-3} & 1.1\times 10^{-4} & 2.4\times 10^{-7} & -4.0\times 10^{-6} & 2.6\times 10^{-6} & -6.7\times 10^{-5} & 3.2\times 10^{-3} & -1.3\times 10^{-3} & 8.9\times 10^{-5} & -5.5\times 10^{-8} & -2.8\times 10^{-6} & 2.0\times 10^{-6} & -5.1\times 10^{-5} & 3.6\times 10^{-3} & -2.5\times 10^{-3} & 8.3\times 10^{-5} & -1.9\times 10^{-7} & -2.4\times 10^{-6} & 1.6\times 10^{-6} & -4.0\times 10^{-5} & 2.9\times 10^{-3} & -2.1\times 10^{-3} & 7.2\times 10^{-5} & -2.4\times 10^{-7} & -2.8\times 10^{-6} & 1.2\times 10^{-6} & -3.3\times 10^{-5} & 1.5\times 10^{-3} & -6.4\times 10^{-4} & 6.6\times 10^{-5} \\
 \end{bmatrix}

### 2018-05-17 ellipse_perp.py

@@ -1,0 +1,24 @@
+#!/usr/bin/env python
+
+import numpy
+
+def anglestuff(l1,l2,a1,a2):
+    if a2==0:
+        cosphi=0.
+        sinphi=1.
+    else:
+        temp = numpy.arctan(-l1*a1/l2/a2)
+        cosphi = numpy.cos(temp)
+        sinphi = numpy.sin(temp)  
+    return cosphi,sinphi
+
+def ellipse_perp(m):
+    # 1, 2, eigenvector; a,b == x,y 
+    (l1, l2),((a1, b1),(a2,b2)) = numpy.linalg.eig(m)
+
+    cosphi,sinphi = anglestuff(l1,l2,a1,a2)
+    y = l1*b1*cosphi + l2*b2*sinphi
+
+    cosphi,sinphi = anglestuff(l1,l2,b1,b2)
+    x = l1*a1*cosphi + l2*a2*sinphi
+    return numpy.abs(x),numpy.abs(y)

### 2018-05-17 submit/fix.tex
address a referee comment on measuring one but not another feature

@@
 \added{
+The correlation matrix in Eq.~\ref{corr:eqn} is not close to being singular, meaning that the each of the features conveys
+independent supernova variability.  Nevertheless, a strong correlation between two features means that the determination
+of one would reduce the residual dispersion in the other.  This information is conveyed in the matrix
 \begin{equation}
+M =
 \begin{pmatrix}
-\small
+\tiny
 \begin{array}{rrrrrrr}
-EW_{\mathrm{Ca}} & 7.0  \pm 0.5 \times 10^{ 2} & 6.7  \pm 0.3 \times 10^{ 2} & 3.7  \pm 1.1 \times 10^{ 2} & 3.3  \pm 6.2 \times 10^{ 1} & 7.7  \pm 17.0 \times 10^{ 0} & 6.3  \pm 11.2 \times 10^{ 1} \\
-5.0  \pm 0.2 \times 10^{ 1} & EW_{\mathrm{Si}} & 4.9  \pm 0.2 \times 10^{ 1} & 2.5  \pm 0.2 \times 10^{ 0} & 4.7  \pm 3.3 \times 10^{ 0} & 1.2  \pm 1.5 \times 10^{ 0} & 1.1  \pm 1.2 \times 10^{ 1} \\
-3.8  \pm 0.2 \times 10^{ 2} & 3.9  \pm 0.2 \times 10^{ 2} & \lambda_{\mathrm{Si}} & 1.4  \pm 0.3 \times 10^{ 2} & 7.4  \pm 8.8 \times 10^{ 1} & 4.3  \pm 6.8 \times 10^{ 1} & 4.5  \pm 7.0 \times 10^{ 1} \\
-9.9  \pm 0.4 \times 10^{-1} & 2.9  \pm 0.2 \times 10^{-1} & 9.7  \pm 0.4 \times 10^{-1} & x_1 & 5.2  \pm 1.4 \times 10^{-1} & 2.3  \pm 1.6 \times 10^{-1} & 6.7  \pm 2.3 \times 10^{-1} \\
-5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} \\
-1.5  \pm 0.3 \times 10^{-3} & 1.4  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} &  E_{\gamma^1}({\hat{B}}-{\hat{V}}) & 1.5  \pm 0.3 \times 10^{-3} \\
-2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & A_{p,V} \\
-\end{array}
+2.76  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.06 \times 10^{ 1} & 2.67  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.05 \times 10^{ 1} & 2.74  \pm 0.06 \times 10^{ 1} & 2.71  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.06 \times 10^{ 1} \\
+7.04  \pm 0.16 \times 10^{ 0} & 7.08  \pm 0.16 \times 10^{ 0} & 7.02  \pm 0.16 \times 10^{ 0} & 3.86  \pm 0.19 \times 10^{ 0} & 7.01  \pm 0.16 \times 10^{ 0} & 6.79  \pm 0.21 \times 10^{ 0} & 7.06  \pm 0.16 \times 10^{ 0} \\
+1.98  \pm 0.04 \times 10^{ 1} & 2.03  \pm 0.05 \times 10^{ 1} & 2.05  \pm 0.05 \times 10^{ 1} & 2.03  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} \\
+9.92  \pm 0.18 \times 10^{-1} & 5.43  \pm 0.23 \times 10^{-1} & 9.86  \pm 0.19 \times 10^{-1} & 9.95  \pm 0.18 \times 10^{-1} & 9.86  \pm 0.19 \times 10^{-1} & 9.71  \pm 0.26 \times 10^{-1} & 9.92  \pm 0.19 \times 10^{-1} \\
+7.33  \pm 0.31 \times 10^{-2} & 7.32  \pm 0.32 \times 10^{-2} & 7.37  \pm 0.32 \times 10^{-2} & 7.32  \pm 0.32 \times 10^{-2} & 7.38  \pm 0.32 \times 10^{-2} & 7.36  \pm 0.33 \times 10^{-2} & 7.36  \pm 0.32 \times 10^{-2} \\
+3.82  \pm 0.42 \times 10^{-2} & 3.73  \pm 0.41 \times 10^{-2} & 3.88  \pm 0.43 \times 10^{-2} & 3.79  \pm 0.42 \times 10^{-2} & 3.88  \pm 0.44 \times 10^{-2} & 3.89  \pm 0.44 \times 10^{-2} & 3.88  \pm 0.44 \times 10^{-2} \\
+4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.97  \pm 1.10 \times 10^{-2}
+\\\end{array}
 \end{pmatrix}.
@@
 \end{equation}
+For indeces $i, j \in \{EW_{\mathrm{Ca}}, EW_{\mathrm{Si}}, \lambda_{\mathrm{Si}}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}\}$, $M_{ii}$ is the standard deviation in the distribution of parameter $i$, and for $i \ne j$ $M_{ij}$ is the standard deviation in parameter $i$
+if parameter $j$ were known perfectly.  For example, for $i= EW_{\mathrm{Si}}$ the standard deviation is 7.08 but when $j=x_1$
+is fixed its
+standard deviation drops to 3.86.  Therefore, an analysis that considers $x_1$ but not $EW_{\mathrm{Si}}$ would not account for
+$3.86\vec{\beta}=\{0.14 ,  0.09,  0.08,  0.07,  0.04 \}$ ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ magnitude dispersions
+that are not intrinsically random.
 }

### 2018-05-30 submit/response.txt
version for VC

@@
 
-We have added two tables to the article.
+For quick reference we have added a table containing a list of the supernovae and their measurements used in this analysis and a second table listing the supernovae and values of their output parameters.
+For completeness, the input data and output Monte Carlo chains are made available in a tar archive on a persistent repository (TODO).
+The publicly available spectrophotometric series can be used to check how our pipeline transformation the series into the measures used in this article.
+
+It is unfortunate that the spectrophotometric series of all the supernovae used in this analysis are not yet public.
+Nevertheless, there is precedent in astrophysics for interesting results that could stimulate public interest and activity (e.g.
+verification using independent data sets) to be published before all antecedent data products are made public.
+This article fits that category.
+
+Despite the time delay pointing to the contrary, there is a concentrated effort within the SNfactory collaboration on making a public data release.
 
@@
 
+We have added paragraphs in the Data section that describe the selection of our sample.
+
+A new Figure has been added to show the distributions of the observables in our sample, and the distributions the light—curve observables of the Pantheon sample as a point of reference.
+
+More importantly, we add a discussion on why sample selection is not important for the scope of this analysis.
+To summarize, this analysis seeks to detect and model diversity within the Type Ia family.
+Diversity found in a biased subsample remains as diversity of the whole family.
+While sample selection is critical in the standardization and application of the model across different subsamples, that isn’t the focus of the current article.
+
 Comment 3:
@@
 
+Note that the correlation/covariance between a subset of parameters are already in the article.
+For example the correlation matrix of the per-supernova parameters is given and there is a figure of their distribution.
+However, there are too many parameters to make providing their covariance matrix within the article unwieldy.
+Instead we provide the Monte Carlo chains in the tar archive from which the covariance of any possible parameter pair can be determined.
+
+We add, in Section 5.2.6. the determination of how much dispersion remains in an individual parameter assuming that a second (correlated) parameter is perfectly measured.
+
 Comment 4:
@@
 
+Response 4:
+
+The purpose of this article is to model supernova colors based on properties directly linked to the supernova.
+We are then interested in whether the mass-step is a repackaging of our newly-discovered parameter.
+The model used in this article is not really suited to capture the mass-step effect, as it does not account for absolute magnitudes.
+
+Comment 5:
+
 3. Section 5.2.9 says that the correlation between Delta and the other parameters is shown in Eq. 20. But Delta isn't included there.
+
+Response 5:
+
+The text in 5.2.9.
+is a remnant of an old version of the article.
+The offending text is now replaced with a reminder of how correlations between Delta and the other parameters are handled in the analysis.

### 2018-05-30 submit/fix.tex
version for VC

@@
 
+\added{The current SNfactory sample consists of 198 SNe~Ia
+having fully-processed spectrophotometric lightcurve data, including
+observations on at least two photometric nights, final references, and a
+host spectroscopic redshift. 
+These all have at least 5 spectra while the SN is
+active, and pass the quality cuts suggested by \citet{2010A&A...523A...7G}.
+More than 80\% of our SNe are from searches where there was no
+pre-selection based on host galaxy properties (those
+whose names start with ``SNF'', ``LSQ'', or ``PTF'' in Table~\ref{data:tab}).
+
+From that sample, we further require at least one spectrum with $\pm 2.5$ days of B-band peak brightness.
+We exclude six SNe~Ia in the
+SN~1991T, SN~1991bg and SN~2002cx subclasses, two objects 
+SNF20080905-005 and SNNGC7589 described in \citet{leget:thesis} as
+being spectroscopically peculiar, and two objects SN2012cu and SNF20061108-001 whose SALT2
+fits are peculiar.
+
+For the purposes of this article, it is not important whether the population in our sample is representative
+of the underlying distribution, either at low- or high-redshift.  This article considers
+underlying parameters that
+affect SN~Ia colors; such parameters found in a subsample are still
+relevant parameters when dealing with the population as a whole.
+
+There is a fraction of SNfactory-observed supernovae that do have the
+observations to satisfy the selection criteria, but are excluded due to some observations
+having not completed full processing.  Incomplete processing can occur for data taken during poor
+observing conditions, when there are instrumental artifacts, and when the supernova is late in its
+light-curve and its signal-to-noise and contrast are low.  The sample-selection exclusion of these supernovae are not related,
+at least directly, to the observables used in this analysis.  Our results are insensitive to potential sample-selection
+bias due to stochasticity in the measurements.
+
+??
+The sample selection is insensitive to the above measurements of the spectral features of the spectra that are
+closest to maximum light nor of the  peak magnitudes in synthetic
+bands interpolated from multiple spectra.
+Therefore the results are insensitive
+biased due to stochastic measurement uncertainty.
+
+}
+
 A recent description of the data is presented in \citet{2015ApJ...815...58F}.
@@
 All the above spectral features have units of \AA ngstroms.
-
-\added{
-SNfactory observed supernovae in the redshift range $z \lesssim 0.09$, with a preference for $0.03 < z < 0.08$,
-whose first SNIFS observation was projected to be $\lesssim -5$ days before $B$-band peak brightness.
-Telescope availability and observing conditions dictated which supernovae eventually would accumulate multiple observations 
-over the course of their light curves that would give constraining light curve (e.g.\ SALT2) fits.  At an occurence of $< 10\%$ individual spectral extractions 
-}
 
@@
    \includegraphics[width=4in]{perobject_input.pdf}
-   \caption{Distributions of the central values of the inputs  $EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$,
+   \caption{\added{Distributions of the central values of the inputs  $EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$,
 $\lambda_{\mathrm{Si}}$ , $x_1$, and $C$ of the sample used in this article, and
-the $x_1$ and $C$ distributions of the $0.03<z< 0.08$ Pantheon sample,
+the $x_1$ and $C$ distributions of the $0.03<z< 0.08$ Pantheon sample.}
    \label{input:fig}}
@@
 \end{equation}
-
 $\vec{1}$ is the Identity vector.
@@
 For $N=172$ supernovae, there are 1376 observables and 1064  parameters.
+
+\added{This model is applied to our supernova sample and so the ensuing results describe the the SN~Ia population
+weighted by our sample selection.}
 

### 2018-06-13 submit/fix.tex
json table and edits

@@
 host spectroscopic redshift. 
-These all have at least 5 spectra while the SN is
-active, and pass the quality cuts suggested by \citet{2010A&A...523A...7G}.
+These supernovae have well-sampled lightcurves, as defined by having
+at minimum 5 spectra while still active, with at least four within
+epochs  $[-10, 35]$ days, at least one within $[-10, 7]$ days, at least one within $[7, 20]$ days,
+and at least one color (?) within $[-8, 10]$ days of peak $B$ brightness.
+Synthetic-photometric lightcurves derived from the spectra are fit to the SALT2~(v2.4)
+model; we require that supernovae have no more than 20\% points that are
+$>0.2$ mag from the best-fit model, and require an Normalized Median Absolute Deviation (nMAD) of residuals
+to be  $< 0.12$ mag.
+%These all have at least 5 spectra while the SN is
+%active, and pass the quality cuts suggested by \citet{2010A&A...523A...7G}.
 More than 80\% of our SNe are from searches where there was no
@@
 whose names start with ``SNF'', ``LSQ'', or ``PTF'' in Table~\ref{data:tab}).
+
+%Quality criteria for a 'good' lightcurve are the following: At least 5 nights of observation
+%No more than 20\% of rejection (after outlier cut>0.2mag) nMAD of residuals < 0.12 mag
+%Phase coverage (4 epochs in [-10 < p < +35] days, 1 epochs in [-10 < p < +7] days, 1 epochs in [+7 < p < +20] days,1 color in [-8 < p < +10] days)
 
@@
 SNF20080905-005 and SNNGC7589 described in \citet{leget:thesis} as
-being spectroscopically peculiar, and two objects SN2012cu and SNF20061108-001 whose SALT2
+being spectroscopically peculiar
+(For SNNGC7589 this is wrong, because it does not appear in the table 5.1 of my Ph.D. I rejected it because it was took after 2010..
+), and two objects SN2012cu
+\citep[which is highly reddened][]{2017ApJ...836..157H}
+and SNF20061108-001 whose SALT2
 fits are peculiar.

### 2018-06-13 tablef3_x1.py

@@ -14,6 +14,7 @@ fit = pickle.load(f)
 f.close()
 
 
+
 for key in fit.keys():
     print key, fit[key].min(), fit[key].max()
 
@@ -182,7 +183,6 @@ for i1 in xrange(7):
 
     print "\\\\" 
 
-wefwefwe
 
 # Effecrive RB and other numbers
 print "Effecrive RB and other numbers"
@@ -252,7 +252,7 @@ pkl_file = open('gege_data.pkl', 'r')
 data = pickle.load(pkl_file)
 pkl_file.close()
 
-sivel, sivel_err,x1,x1_err,_,_,_,EWFe4800 = sivel.sivel(data)
+sivel, sivel_err,x1,x1_err,_,_,_,EWFe4800,_ = sivel.sivel(data)
 
 
 use = numpy.isfinite(sivel)
@@ -309,6 +309,35 @@ print 'outputs'
 
 EW_mn = EW_obs.mean(axis=0)
 sivel_mn = sivel.mean()
+import json, codecs
+def convert(fit,EW_mn,sivel_mn):
+    rm = ['c_raw','alpha_raw','beta_raw','eta_raw','gamma01','gamma02','gamma03','gamma04','gamma05','k_unit','lp__', \
+        'Delta_scale','Delta_unit','R_unit','rho11','rho12','rho13','rho14','rho15','EW','sivel','gamma','rho1','k','R', \
+        'ev_sig','ev','mag_int_raw','mag_int']
+
+    use = dict(fit)
+    use['EWCa'] = use['EW'][:,:,0]+EW_mn[0]
+    use['EWSi'] = use['EW'][:,:,1]+EW_mn[1]
+    use['lSi']=use['sivel'] + sivel_mn
+    use['gamma0']=use['gamma']
+    use['gamma1']=use['rho1']
+    use['g0'] = use['k']
+    use['g1'] = use['R']
+    use['sigmap']=use['ev_sig']
+    use['phi']=use['ev']
+    use['p'] = use['mag_int_raw']
+    for r in rm:
+        del use[r]
+
+    for key in use.keys():
+        use[key] = use[key].tolist()
+
[…]

### 2018-06-16 submit/response.txt
continuing edits

@@
 Despite the time delay pointing to the contrary, there is a concentrated effort within the SNfactory collaboration on making a public data release.
+https://drive.google.com/drive/folders/1d52nxfF7eS3HblfbmT3fxgiZod_Z-Gjg?usp=sharing.
+DOI number.
 
@@
 However, there are too many parameters to make providing their covariance matrix within the article unwieldy.
+We did insert out the 35x35 covariance matrix of the global parameters, but it did not have a clean appearance in the manuscript.
 Instead we provide the Monte Carlo chains in the tar archive from which the covariance of any possible parameter pair can be determined.
+The chains are available at  https://drive.google.com/drive/folders/1d52nxfF7eS3HblfbmT3fxgiZod Z-Gjg?usp=sharing.
+The
 

### 2018-06-16 submit/fix.tex
continuing edits

--- 2018-05-17 submit/fix.tex
@@
 
+\added{The current SNfactory sample consists of 198 SNe~Ia
+having fully-processed spectrophotometric lightcurve data, including
+observations on at least two photometric nights, final references, and a
+host spectroscopic redshift. 
+These supernovae have well-sampled lightcurves as defined by having
+at minimum 5 spectra while still active, with at least four within
+epochs  $[-10, 35]$ days, at least one within $[-10, 7]$ days, at least one within $[7, 20]$ days,
+and at least one color (Anyone know what this means? See slide 3 of
+\url{https://snf-doc.lbl.gov/twiki/pub/Conf/VideoConf20160317/IDR_03-17-2016.pdf}) within $[-8, 10]$ days of peak $B$ brightness.
+Synthetic-photometric lightcurves derived from the spectra are fit to the SALT2~(v2.4)
+model; we require that supernovae have no more than 20\% points that are
+$>0.2$ mag from the best-fit model, and require a Normalized Median Absolute Deviation (nMAD) of residuals
+of  $< 0.12$ mag.
+%These all have at least 5 spectra while the SN is
+%active, and pass the quality cuts suggested by \citet{2010A&A...523A...7G}.
+More than 80\% of our SNe are from searches where there was no
+pre-selection based on host galaxy properties (those
+whose names start with ``SNF'', ``LSQ'', or ``PTF'' in Table~\ref{data:tab}).
+
+%Quality criteria for a 'good' lightcurve are the following: At least 5 nights of observation
+%No more than 20\% of rejection (after outlier cut>0.2mag) nMAD of residuals < 0.12 mag
+%Phase coverage (4 epochs in [-10 < p < +35] days, 1 epochs in [-10 < p < +7] days, 1 epochs in [+7 < p < +20] days,1 color in [-8 < p < +10] days)
+
+From that sample, we further require at least one spectrum with $\pm 2.5$ days of B-band peak brightness.
+We exclude six SNe~Ia in the
+SN~1991T, SN~1991bg and SN~2002cx subclasses,
+SNF20080905-005 described in \citet{leget:thesis} as
+being spectroscopically peculiar, and
+the extremely red SN2012cu  who has a SALT2 $C \approx 1$ \citep{2017ApJ...836..157H} that is several times larger than the colors
+of in-sample supernovae.
+
+For the purposes of this article, it is not important whether our sample population is representative
+of the underlying population.  This article seeks
+underlying parameters that
+affect SN~Ia colors; any such parameters found in a subsample are still
+relevant parameters when dealing with the population as a whole.
+
+There is a fraction of SNfactory-observed supernovae that do have the
+observations to satisfy the well-sampled light-curve criteria, but are excluded due to some observations
+having not completed full processing.  Incomplete processing can occur for data taken during poor
+observing conditions, when there are instrumental artifacts, and late in a supernova's
+light-curve when the signal-to-noise and contrast relative to the host are low.  The sample-selection exclusion of these supernovae are not related,
+at least directly, to the at-maximum observables used in this analysis.  Our results are insensitive to potential sample-selection
+bias due to stochasticity in the measurements.
+}
+
 A recent description of the data is presented in \citet{2015ApJ...815...58F}.
@@
 
-\added{
-SNfactory observed supernovae in the redshift range $z \lesssim 0.09$, with a preference for $0.03 < z < 0.08$,
-whose first SNIFS observation was projected to be $\lesssim -5$ days before $B$-band peak brightness.
-Telescope availability and observing conditions dictated which supernovae eventually would accumulate multiple observations 
-over the course of their light curves that would give constraining light curve (e.g.\ SALT2) fits.  At an occurence of $< 10\%$ individual spectral extractions 
-}
-
 Our analysis sample is comprised of the
@@
 in \replaced{\citet{2017Chotard}}{Table~\ref{data:tab}. 
-For the subset supernovae for whom it is available, we use the host-galaxy mass given in \citep{2013ApJ...770..108C}.
+For the subset supernovae for whom it is available, we use the host-galaxy mass given in \citet{2013ApJ...770..108C}.
 
@@
 we refrain from going into full detail on the results of Model~I in deference to Model~III, which is presented in Section~\ref{modelIII:sec}.
+
+\added{It is important to note that the model and those in subsequent sections are applied to our supernova sample;
+the ensuing results thus describe our SN~Ia sample's underlying population. }
 
@@
 \label{results1:sec}
+\added{The MCMC chain for all parameters are accessible from a DOI link \citep{colordata}.}
 In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
@@
 \label{results2:sec}
+\added{The MCMC chain for all parameters are accessible from a DOI link \citep{colordata}.}
 The credible intervals of all Model~II global parameters are given in  \S\ref{m12results:sec}.
@@
 \subsection{Results}
+\added{The MCMC chain for all parameters are accessible from a DOI link \citep{colordata}.}
+
 \subsubsection{Analysis Method and Validation}
@@
 independent supernova variability.  Nevertheless, a strong correlation between two features means that the determination
-of one would reduce the residual dispersion in the other.  This information is conveyed in the matrix
+of one would reduce the residual dispersion in the other.  The amount of residual dispersion is conveyed in the matrix
 \begin{equation}
@@
 \end{equation}
-For indeces $i, j \in \{EW_{\mathrm{Ca}}, EW_{\mathrm{Si}}, \lambda_{\mathrm{Si}}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}\}$, $M_{ii}$ is the standard deviation in the distribution of parameter $i$, and for $i \ne j$ $M_{ij}$ is the standard deviation in parameter $i$
+For indeces $i, j \in \{EW_{\mathrm{Ca}}, EW_{\mathrm{Si}}, \lambda_{\mathrm{Si}}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}\}$, $M_{ii}$ is the standard deviation of the parameter $i$ distribution, and for $i \ne j$ $M_{ij}$ is the standard deviation in parameter $i$
 if parameter $j$ were known perfectly.  For example, for $i= EW_{\mathrm{Si}}$ the standard deviation is 7.08 but when $j=x_1$
@@
 $\sigma_p\phi_{\hat{V}}p$, showing that in addition to standardizing colors, these features can also be used to standardize
-absolute magnitudes.  }{Recall that model degeneracy between $\Delta$ and the cofactors such as $\alpha$, $\beta$ is removed by enforcing
-zero correlation between $\Delta$ and the per-supernova parameters such as $EW_{\mathrm{Ca}}$,  $EW_{\mathrm{Si}}$.
+absolute magnitudes.  }{Recall that the model degeneracy between $\Delta$ and the cofactors (e.g.\ $\alpha$, $\beta$) is removed by enforcing
+zero correlation between $\Delta$ and the per-supernova parameters (e.g.\ $EW_{\mathrm{Ca}}$,  $EW_{\mathrm{Si}}$).
 An alternative method to break the degeneracy is to minimize the dispersion in $\Delta$.
@@
 \end{table}
-
-\section{Covariance Matrix for Model~III Global Parameters}
-\added{The following is the  covariance matrix for the global cofactors $\{ \alpha_{\hat{U}}, \beta_{\hat{U}}, \eta_{\hat{U}}, \zeta_{\hat{U}}, \gamma^0_{\hat{U}},\gamma^1_{\hat{U}}, \sigma_p \phi_{\hat{U}},
-\ldots,
-\alpha_{\hat{I}}, \beta_{\hat{I}}, \eta_{\hat{I}}, \zeta_{\hat{I}}, \gamma^0_{\hat{I}},\gamma^1_{\hat{I}}, \sigma_p \phi_{\hat{I}}
- \}$.  The matrix 35x35 is big so will have to go in supplemental material.}
-\setcounter{MaxMatrixCols}{40}
-\begin{equation}
-\tiny
-\begin{bmatrix}
-5.5\times 10^{-7} & -1.8\times 10^{-6} & 3.9\times 10^{-7} & -1.6\times 10^{-5} & 2.1\times 10^{-4} & -2.6\times 10^{-4} & 3.6\times 10^{-6} & 4.5\times 10^{-7} & -1.5\times 10^{-6} & 3.1\times 10^{-7} & -1.3\times 10^{-5} & 2.6\times 10^{-4} & -1.3\times 10^{-4} & 2.8\times 10^{-6} & 3.6\times 10^{-7} & -1.2\times 10^{-6} & 2.4\times 10^{-7} & -1.0\times 10^{-5} & 1.9\times 10^{-4} & -5.5\times 10^{-5} & 1.7\times 10^{-6} & 2.9\times 10^{-7} & -9.2\times 10^{-7} & 1.9\times 10^{-7} & -8.1\times 10^{-6} & 1.1\times 10^{-4} & -1.7\times 10^{-5} & 1.1\times 10^{-6} & 2.2\times 10^{-7} & -7.2\times 10^{-7} & 1.4\times 10^{-7} & -6.3\times 10^{-6} & -3.6\times 10^{-5} & -6.7\times 10^{-6} & 4.7\times 10^{-7} \\
--1.8\times 10^{-6} & 2.7\times 10^{-5} & -2.6\times 10^{-6} & 1.9\times 10^{-4} & -4.0\times 10^{-3} & -3.0\times 10^{-3} & -1.8\times 10^{-5} & -1.4\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.2\times 10^{-3} & -2.7\times 10^{-3} & -1.4\times 10^{-5} & -1.1\times 10^{-6} & 1.7\times 10^{-5} & -1.6\times 10^{-6} & 1.2\times 10^{-4} & -2.6\times 10^{-3} & -2.1\times 10^{-3} & -1.0\times 10^{-5} & -9.2\times 10^{-7} & 1.4\times 10^{-5} & -1.2\times 10^{-6} & 9.4\times 10^{-5} & -2.0\times 10^{-3} & -1.6\times 10^{-3} & -7.9\times 10^{-6} & -7.3\times 10^{-7} & 1.1\times 10^{-5} & -8.8\times 10^{-7} & 7.6\times 10^{-5} & -1.1\times 10^{-3} & -1.2\times 10^{-3} & -5.2\times 10^{-6} \\
-3.9\times 10^{-7} & -2.6\times 10^{-6} & 1.3\times 10^{-6} & -2.2\times 10^{-5} & 3.9\times 10^{-4} & 1.7\times 10^{-3} & 1.0\times 10^{-5} & 3.2\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 5.0\times 10^{-4} & 1.4\times 10^{-3} & 8.3\times 10^{-6} & 2.4\times 10^{-7} & -1.5\times 10^{-6} & 7.8\times 10^{-7} & -1.3\times 10^{-5} & 5.4\times 10^{-4} & 1.0\times 10^{-3} & 6.0\times 10^{-6} & 1.9\times 10^{-7} & -1.1\times 10^{-6} & 6.1\times 10^{-7} & -1.0\times 10^{-5} & 4.1\times 10^{-4} & 8.0\times 10^{-4} & 4.6\times 10^{-6} & 1.4\times 10^{-7} & -8.1\times 10^{-7} & 4.7\times 10^{-7} & -7.4\times 10^{-6} & 1.6\times 10^{-4} & 5.9\times 10^{-4} & 3.1\times 10^{-6} \\
--1.6\times 10^{-5} & 1.9\times 10^{-4} & -2.2\times 10^{-5} & 1.6\times 10^{-3} & -2.9\times 10^{-2} & -1.4\times 10^{-2} & -2.7\times 10^{-4} & -1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.8\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.0\times 10^{-5} & 1.2\times 10^{-4} & -1.4\times 10^{-5} & 9.9\times 10^{-4} & -2.3\times 10^{-2} & -1.0\times 10^{-2} & -1.5\times 10^{-4} & -8.3\times 10^{-6} & 9.5\times 10^{-5} & -1.1\times 10^{-5} & 7.9\times 10^{-4} & -1.8\times 10^{-2} & -7.7\times 10^{-3} & -1.2\times 10^{-4} & -6.4\times 10^{-6} & 7.7\times 10^{-5} & -7.7\times 10^{-6} & 6.3\times 10^{-4} & -8.1\times 10^{-3} & -4.9\times 10^{-3} & -7.9\times 10^{-5} \\
-2.1\times 10^{-4} & -4.0\times 10^{-3} & 3.9\times 10^{-4} & -2.9\times 10^{-2} & 6.9\times 10^{+0} & 1.3\times 10^{+0} & 6.7\times 10^{-3} & 1.4\times 10^{-4} & -3.0\times 10^{-3} & 3.2\times 10^{-4} & -2.2\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 5.1\times 10^{-3} & 9.6\times 10^{-5} & -2.2\times 10^{-3} & 2.3\times 10^{-4} & -1.6\times 10^{-2} & 4.5\times 10^{+0} & 9.7\times 10^{-1} & 3.7\times 10^{-3} & 6.0\times 10^{-5} & -1.7\times 10^{-3} & 1.7\times 10^{-4} & -1.3\times 10^{-2} & 3.7\times 10^{+0} & 8.5\times 10^{-1} & 3.0\times 10^{-3} & 3.9\times 10^{-5} & -1.4\times 10^{-3} & 1.3\times 10^{-4} & -1.1\times 10^{-2} & 2.9\times 10^{+0} & 6.7\times 10^{-1} & 2.1\times 10^{-3} \\
--2.6\times 10^{-4} & -3.0\times 10^{-3} & 1.7\times 10^{-3} & -1.4\times 10^{-2} & 1.3\times 10^{+0} & 1.7\times 10^{+1} & 8.7\times 10^{-3} & -1.9\times 10^{-4} & -2.8\times 10^{-3} & 1.3\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 7.1\times 10^{-3} & -1.7\times 10^{-4} & -1.5\times 10^{-3} & 9.7\times 10^{-4} & -6.8\times 10^{-3} & 1.8\times 10^{+0} & 1.1\times 10^{+1} & 4.9\times 10^{-3} & -1.2\times 10^{-4} & -1.0\times 10^{-3} & 7.6\times 10^{-4} & -4.4\times 10^{-3} & 1.6\times 10^{+0} & 9.6\times 10^{+0} & 3.2\times 10^{-3} & -10.0\times 10^{-5} & -3.8\times 10^{-4} & 5.6\times 10^{-4} & -7.6\times 10^{-4} & 1.4\times 10^{+0} & 7.9\times 10^{+0} & 1.8\times 10^{-3} \\
-3.6\times 10^{-6} & -1.8\times 10^{-5} & 1.0\times 10^{-5} & -2.7\times 10^{-4} & 6.7\times 10^{-3} & 8.7\times 10^{-3} & 2.8\times 10^{-4} & 2.9\times 10^{-6} & -1.4\times 10^{-5} & 8.4\times 10^{-6} & -2.1\times 10^{-4} & 1.1\times 10^{-2} & 6.8\times 10^{-3} & 2.3\times 10^{-4} & 2.0\times 10^{-6} & -9.4\times 10^{-6} & 6.4\times 10^{-6} & -1.6\times 10^{-4} & 1.1\times 10^{-2} & 4.1\times 10^{-3} & 1.8\times 10^{-4} & 1.4\times 10^{-6} & -7.4\times 10^{-6} & 4.9\times 10^{-6} & -1.2\times 10^{-4} & 8.0\times 10^{-3} & 3.0\times 10^{-3} & 1.4\times 10^{-4} & 9.2\times 10^{-7} & -7.2\times 10^{-6} & 3.6\times 10^{-6} & -9.9\times 10^{-5} & 2.6\times 10^{-3} & 2.3\times 10^{-3} & 1.1\times 10^{-4} \\
-4.5\times 10^{-7} & -1.4\times 10^{-6} & 3.2\times 10^{-7} & -1.3\times 10^{-5} & 1.4\times 10^{-4} & -1.9\times 10^{-4} & 2.9\times 10^{-6} & 4.0\times 10^{-7} & -1.3\times 10^{-6} & 2.7\times 10^{-7} & -1.1\times 10^{-5} & 2.0\times 10^{-4} & -2.5\times 10^{-5} & 2.3\times 10^{-6} & 3.2\times 10^{-7} & -1.0\times 10^{-6} & 2.1\times 10^{-7} & -9.1\times 10^{-6} & 1.4\times 10^{-4} & 4.3\times 10^{-5} & 1.3\times 10^{-6} & 2.6\times 10^{-7} & -8.2\times 10^{-7} & 1.7\times 10^{-7} & -7.1\times 10^{-6} & 7.4\times 10^{-5} & 5.1\times 10^{-5} & 6.9\times 10^{-7} & 1.9\times 10^{-7} & -6.0\times 10^{-7} & 1.2\times 10^{-7} & -5.3\times 10^{-6} & -5.2\times 10^{-5} & 9.5\times 10^{-6} & 2.4\times 10^{-7} \\
--1.5\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.0\times 10^{-3} & -2.8\times 10^{-3} & -1.4\times 10^{-5} & -1.3\times 10^{-6} & 1.9\times 10^{-5} & -1.8\times 10^{-6} & 1.3\times 10^{-4} & -2.4\times 10^{-3} & -3.0\times 10^{-3} & -1.2\times 10^{-5} & -1.0\times 10^{-6} & 1.6\times 10^{-5} & -1.4\times 10^{-6} & 1.0\times 10^{-4} & -2.0\times 10^{-3} & -2.6\times 10^{-3} & -7.6\times 10^{-6} & -8.4\times 10^{-7} & 1.2\times 10^{-5} & -1.0\times 10^{-6} & 8.4\times 10^{-5} & -1.5\times 10^{-3} & -2.0\times 10^{-3} & -5.6\times 10^{-6} & -6.2\times 10^{-7} & 9.3\times 10^{-6} & -7.7\times 10^{-7} & 6.3\times 10^{-5} & -7.7\times 10^{-4} & -1.1\times 10^{-3} & -4.0\times 10^{-6} \\
-3.1\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 3.2\times 10^{-4} & 1.3\times 10^{-3} & 8.4\times 10^{-6} & 2.7\times 10^{-7} & -1.8\times 10^{-6} & 8.5\times 10^{-7} & -1.5\times 10^{-5} & 4.1\times 10^{-4} & 1.1\times 10^{-3} & 6.7\times 10^{-6} & 2.0\times 10^{-7} & -1.2\times 10^{-6} & 6.7\times 10^{-7} & -1.1\times 10^{-5} & 4.4\times 10^{-4} & 8.2\times 10^{-4} & 4.9\times 10^{-6} & 1.6\times 10^{-7} & -9.4\times 10^{-7} & 5.2\times 10^{-7} & -8.5\times 10^{-6} & 3.4\times 10^{-4} & 6.4\times 10^{-4} & 3.7\times 10^{-6} & 1.1\times 10^{-7} & -6.9\times 10^{-7} & 3.8\times 10^{-7} & -6.2\times 10^{-6} & 1.3\times 10^{-4} & 4.8\times 10^{-4} & 2.6\times 10^{-6} \\
--1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.1\times 10^{-5} & 1.3\times 10^{-4} & -1.5\times 10^{-5} & 1.1\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -1.7\times 10^{-4} & -9.0\times 10^{-6} & 1.0\times 10^{-4} & -1.2\times 10^{-5} & 8.7\times 10^{-4} & -1.8\times 10^{-2} & -1.1\times 10^{-2} & -1.2\times 10^{-4} & -7.2\times 10^{-6} & 8.3\times 10^{-5} & -8.9\times 10^{-6} & 6.9\times 10^{-4} & -1.4\times 10^{-2} & -8.3\times 10^{-3} & -9.2\times 10^{-5} & -5.3\times 10^{-6} & 6.2\times 10^{-5} & -6.6\times 10^{-6} & 5.1\times 10^{-4} & -6.0\times 10^{-3} & -4.1\times 10^{-3} & -6.7\times 10^{-5} \\
-2.6\times 10^{-4} & -3.2\times 10^{-3} & 5.0\times 10^{-4} & -2.8\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 1.1\times 10^{-2} & 2.0\times 10^{-4} & -2.4\times 10^{-3} & 4.1\times 10^{-4} & -2.2\times 10^{-2} & 5.1\times 10^{+0} & 9.4\times 10^{-1} & 8.4\times 10^{-3} & 1.4\times 10^{-4} & -1.8\times 10^{-3} & 3.0\times 10^{-4} & -1.6\times 10^{-2} & 4.3\times 10^{+0} & 8.6\times 10^{-1} & 6.0\times 10^{-3} & 9.8\times 10^{-5} & -1.4\times 10^{-3} & 2.3\times 10^{-4} & -1.3\times 10^{-2} & 3.4\times 10^{+0} & 7.8\times 10^{-1} & 4.6\times 10^{-3} & 5.8\times 10^{-5} & -1.1\times 10^{-3} & 1.7\times 10^{-4} & -1.0\times 10^{-2} & 2.4\times 10^{+0} & 6.5\times 10^{-1} & 3.2\times 10^{-3} \\
--1.3\times 10^{-4} & -2.7\times 10^{-3} & 1.4\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 6.8\times 10^{-3} & -2.5\times 10^{-5} & -3.0\times 10^{-3} & 1.1\times 10^{-3} & -1.3\times 10^{-2} & 9.4\times 10^{-1} & 1.4\times 10^{+1} & 6.4\times 10^{-3} & 1.8\times 10^{-5} & -2.2\times 10^{-3} & 8.6\times 10^{-4} & -1.1\times 10^{-2} & 1.5\times 10^{+0} & 1.2\times 10^{+1} & 1.6\times 10^{-3} & 2.0\times 10^{-5} & -1.6\times 10^{-3} & 6.7\times 10^{-4} & -7.7\times 10^{-3} & 1.3\times 10^{+0} & 9.5\times 10^{+0} & 3.9\times 10^{-6} & -2.3\times 10^{-5} & -6.0\times 10^{-4} & 5.1\times 10^{-4} & -3.1\times 10^{-3} & 1.1\times 10^{+0} & 7.1\times 10^{+0} & -1.3\times 10^{-3} \\
-2.8\times 10^{-6} & -1.4\times 10^{-5} & 8.3\times 10^{-6} & -2.1\times 10^{-4} & 5.1\times 10^{-3} & 7.1\times 10^{-3} & 2.3\times 10^{-4} & 2.3\times 10^{-6} & -1.2\times 10^{-5} & 6.7\times 10^{-6} & -1.7\times 10^{-4} & 8.4\times 10^{-3} & 6.4\times 10^{-3} & 1.9\times 10^{-4} & 1.6\times 10^{-6} & -8.8\times 10^{-6} & 5.2\times 10^{-6} & -1.4\times 10^{-4} & 8.6\times 10^{-3} & 4.5\times 10^{-3} & 1.5\times 10^{-4} & 1.1\times 10^{-6} & -7.0\times 10^{-6} & 4.0\times 10^{-6} & -1.1\times 10^{-4} & 6.3\times 10^{-3} & 3.2\times 10^{-3} & 1.2\times 10^{-4} & 6.7\times 10^{-7} & -6.3\times 10^{-6} & 3.0\times 10^{-6} & -8.3\times 10^{-5} & 2.1\times 10^{-3} & 2.0\times 10^{-3} & 8.9\times 10^{-5} \\
-3.6\times 10^{-7} & -1.1\times 10^{-6} & 2.4\times 10^{-7} & -1.0\times 10^{-5} & 9.6\times 10^{-5} & -1.7\times 10^{-4} & 2.0\times 10^{-6} & 3.2\times 10^{-7} & -1.0\times 10^{-6} & 2.0\times 10^{-7} & -9.0\times 10^{-6} & 1.4\times 10^{-4} & 1.8\times 10^{-5} & 1.6\times 10^{-6} & 2.8\times 10^{-7} & -9.3\times 10^{-7} & 1.7\times 10^{-7} & -7.8\times 10^{-6} & 9.4\times 10^{-5} & 1.0\times 10^{-4} & 6.8\times 10^{-7} & 2.3\times 10^{-7} & -7.4\times 10^{-7} & 1.3\times 10^{-7} & -6.2\times 10^{-6} & 3.6\times 10^{-5} & 8.4\times 10^{-5} & 2.4\times 10^{-7} & 1.7\times 10^{-7} & -5.5\times 10^{-7} & 9.8\times 10^{-8} & -4.6\times 10^{-6} & -6.3\times 10^{-5} & 3.2\times 10^{-5} & -5.5\times 10^{-8} \\
--1.2\times 10^{-6} & 1.7\times 10^{-5} & -1.5\times 10^{-6} & 1.2\times 10^{-4} & -2.2\times 10^{-3} & -1.5\times 10^{-3} & -9.4\times 10^{-6} & -1.0\times 10^{-6} & 1.6\times 10^{-5} & -1.2\times 10^{-6} & 1.0\times 10^{-4} & -1.8\times 10^{-3} & -2.2\times 10^{-3} & -8.8\times 10^{-6} & -9.3\times 10^{-7} & 1.4\times 10^{-5} & -9.7\times 10^{-7} & 9.4\times 10^{-5} & -1.3\times 10^{-3} & -2.2\times 10^{-3} & -5.0\times 10^{-6} & -7.6\times 10^{-7} & 1.1\times 10^{-5} & -7.5\times 10^{-7} & 7.6\times 10^{-5} & -9.6\times 10^{-4} & -1.6\times 10^{-3} & -3.4\times 10^{-6} & -5.7\times 10^{-7} & 8.7\times 10^{-6} & -5.6\times 10^{-7} & 5.8\times 10^{-5} & -4.2\times 10^{-4} & -9.0\times 10^{-4} & -2.8\times 10^{-6} \\
-2.4\times 10^{-7} & -1.6\times 10^{-6} & 7.8\times 10^{-7} & -1.4\times 10^{-5} & 2.3\times 10^{-4} & 9.7\times 10^{-4} & 6.4\times 10^{-6} & 2.1\times 10^{-7} & -1.4\times 10^{-6} & 6.7\times 10^{-7} & -1.2\times 10^{-5} & 3.0\times 10^{-4} & 8.6\times 10^{-4} & 5.2\times 10^{-6} & 1.7\times 10^{-7} & -9.7\times 10^{-7} & 5.5\times 10^{-7} & -8.8\times 10^{-6} & 3.3\times 10^{-4} & 6.6\times 10^{-4} & 3.7\times 10^{-6} & 1.3\times 10^{-7} & -7.4\times 10^{-7} & 4.3\times 10^{-7} & -6.8\times 10^{-6} & 2.5\times 10^{-4} & 5.1\times 10^{-4} & 2.8\times 10^{-6} & 9.4\times 10^{-8} & -5.4\times 10^{-7} & 3.2\times 10^{-7} & -5.0\times 10^{-6} & 9.2\times 10^{-5} & 3.6\times 10^{-4} & 2.0\times 10^{-6} \\
--1.0\times 10^{-5} & 1.2\times 10^{-4} & -1.3\times 10^{-5} & 9.9\times 10^{-4} & -1.6\times 10^{-2} & -6.8\times 10^{-3} & -1.6\times 10^{-4} & -9.1\times 10^{-6} & 1.0\times 10^{-4} & -1.1\times 10^{-5} & 8.7\times 10^{-4} & -1.6\times 10^{-2} & -1.1\times 10^{-2} & -1.4\times 10^{-4} & -7.8\times 10^{-6} & 9.4\times 10^{-5} & -8.8\times 10^{-6} & 7.8\times 10^{-4} & -1.4\times 10^{-2} & -1.0\times 10^{-2} & -9.2\times 10^{-5} & -6.3\times 10^{-6} & 7.6\times 10^{-5} & -6.8\times 10^{-6} & 6.2\times 10^{-4} & -1.0\times 10^{-2} & -7.0\times 10^{-3} & -6.7\times 10^{-5} & -4.7\times 10^{-6} & 5.8\times 10^{-5} & -5.1\times 10^{-6} & 4.7\times 10^{-4} & -4.0\times 10^{-3} & -3.9\times 10^{-3} & -5.1\times 10^{-5} \\
-1.9\times 10^{-4} & -2.6\times 10^{-3} & 5.4\times 10^{-4} & -2.3\times 10^{-2} & 4.5\times 10^{+0} & 1.8\times 10^{+0} & 1.1\times 10^{-2} & 1.4\times 10^{-4} & -2.0\times 10^{-3} & 4.4\times 10^{-4} & -1.8\times 10^{-2} & 4.3\times 10^{+0} & 1.5\times 10^{+0} & 8.6\times 10^{-3} & 9.4\times 10^{-5} & -1.3\times 10^{-3} & 3.3\times 10^{-4} & -1.4\times 10^{-2} & 4.0\times 10^{+0} & 1.2\times 10^{+0} & 6.5\times 10^{-3} & 5.8\times 10^{-5} & -9.9\times 10^{-4} & 2.5\times 10^{-4} & -1.1\times 10^{-2} & 3.2\times 10^{+0} & 1.0\times 10^{+0} & 5.0\times 10^{-3} & 2.6\times 10^{-5} & -7.8\times 10^{-4} & 1.8\times 10^{-4} & -8.2\times 10^{-3} & 2.2\times 10^{+0} & 8.9\times 10^{-1} & 3.6\times 10^{-3} \\
--5.5\times 10^{-5} & -2.1\times 10^{-3} & 1.0\times 10^{-3} & -1.0\times 10^{-2} & 9.7\times 10^{-1} & 1.1\times 10^{+1} & 4.1\times 10^{-3} & 4.3\times 10^{-5} & -2.6\times 10^{-3} & 8.2\times 10^{-4} & -1.1\times 10^{-2} & 8.6\times 10^{-1} & 1.2\times 10^{+1} & 4.5\times 10^{-3} & 1.0\times 10^{-4} & -2.2\times 10^{-3} & 6.6\times 10^{-4} & -1.0\times 10^{-2} & 1.2\times 10^{+0} & 1.0\times 10^{+1} & -3.8\times 10^{-4} & 8.4\times 10^{-5} & -1.6\times 10^{-3} & 5.2\times 10^{-4} & -7.3\times 10^{-3} & 1.1\times 10^{+0} & 8.6\times 10^{+0} & -1.6\times 10^{-3} & 2.1\times 10^{-5} & -6.0\times 10^{-4} & 4.0\times 10^{-4} & -3.1\times 10^{-3} & 8.8\times 10^{-1} & 6.4\times 10^{+0} & -2.5\times 10^{-3} \\
-1.7\times 10^{-6} & -1.0\times 10^{-5} & 6.0\times 10^{-6} & -1.5\times 10^{-4} & 3.7\times 10^{-3} & 4.9\times 10^{-3} & 1.8\times 10^{-4} & 1.3\times 10^{-6} & -7.6\times 10^{-6} & 4.9\times 10^{-6} & -1.2\times 10^{-4} & 6.0\times 10^{-3} & 1.6\times 10^{-3} & 1.5\times 10^{-4} & 6.8\times 10^{-7} & -5.0\times 10^{-6} & 3.7\times 10^{-6} & -9.2\times 10^{-5} & 6.5\times 10^{-3} & -3.8\times 10^{-4} & 1.3\times 10^{-4} & 3.9\times 10^{-7} & -4.1\times 10^{-6} & 2.9\times 10^{-6} & -7.2\times 10^{-5} & 4.9\times 10^{-3} & -3.9\times 10^{-4} & 1.1\times 10^{-4} & 2.1\times 10^{-7} & -4.4\times 10^{-6} & 2.1\times 10^{-6} & -5.8\times 10^{-5} & 1.9\times 10^{-3} & 6.8\times 10^{-4} & 8.3\times 10^{-5} \\
-2.9\times 10^{-7} & -9.2\times 10^{-7} & 1.9\times 10^{-7} & -8.3\times 10^{-6} & 6.0\times 10^{-5} & -1.2\times 10^{-4} & 1.4\times 10^{-6} & 2.6\times 10^{-7} & -8.4\times 10^{-7} & 1.6\times 10^{-7} & -7.2\times 10^{-6} & 9.8\times 10^{-5} & 2.0\times 10^{-5} & 1.1\times 10^{-6} & 2.3\times 10^{-7} & -7.6\times 10^{-7} & 1.3\times 10^{-7} & -6.3\times 10^{-6} & 5.8\times 10^{-5} & 8.4\times 10^{-5} & 3.9\times 10^{-7} & 1.9\times 10^{-7} & -6.2\times 10^{-7} & 1.0\times 10^{-7} & -5.0\times 10^{-6} & 1.2\times 10^{-5} & 7.2\times 10^{-5} & 4.6\times 10^{-8} & 1.4\times 10^{-7} & -4.6\times 10^{-7} & 8.0\times 10^{-8} & -3.9\times 10^{-6} & -6.4\times 10^{-5} & 3.0\times 10^{-5} & -1.9\times 10^{-7} \\
--9.2\times 10^{-7} & 1.4\times 10^{-5} & -1.1\times 10^{-6} & 9.5\times 10^{-5} & -1.7\times 10^{-3} & -1.0\times 10^{-3} & -7.4\times 10^{-6} & -8.2\times 10^{-7} & 1.2\times 10^{-5} & -9.4\times 10^{-7} & 8.3\times 10^{-5} & -1.4\times 10^{-3} & -1.6\times 10^{-3} & -7.0\times 10^{-6} & -7.4\times 10^{-7} & 1.1\times 10^{-5} & -7.4\times 10^{-7} & 7.6\times 10^{-5} & -9.9\times 10^{-4} & -1.6\times 10^{-3} & -4.1\times 10^{-6} & -6.2\times 10^{-7} & 9.5\times 10^{-6} & -5.8\times 10^{-7} & 6.3\times 10^{-5} & -7.1\times 10^{-4} & -1.1\times 10^{-3} & -3.0\times 10^{-6} & -4.8\times 10^{-7} & 7.5\times 10^{-6} & -4.4\times 10^{-7} & 5.0\times 10^{-5} & -3.0\times 10^{-4} & -6.5\times 10^{-4} & -2.4\times 10^{-6} \\
-1.9\times 10^{-7} & -1.2\times 10^{-6} & 6.1\times 10^{-7} & -1.1\times 10^{-5} & 1.7\times 10^{-4} & 7.6\times 10^{-4} & 4.9\times 10^{-6} & 1.7\times 10^{-7} & -1.0\times 10^{-6} & 5.2\times 10^{-7} & -8.9\times 10^{-6} & 2.3\times 10^{-4} & 6.7\times 10^{-4} & 4.0\times 10^{-6} & 1.3\times 10^{-7} & -7.5\times 10^{-7} & 4.3\times 10^{-7} & -6.8\times 10^{-6} & 2.5\times 10^{-4} & 5.2\times 10^{-4} & 2.9\times 10^{-6} & 1.0\times 10^{-7} & -5.8\times 10^{-7} & 3.5\times 10^{-7} & -5.3\times 10^{-6} & 1.9\times 10^{-4} & 4.1\times 10^{-4} & 2.2\times 10^{-6} & 7.7\times 10^{-8} & -4.2\times 10^{-7} & 2.6\times 10^{-7} & -4.0\times 10^{-6} & 7.3\times 10^{-5} & 2.8\times 10^{-4} & 1.6\times 10^{-6} \\
--8.1\times 10^{-6} & 9.4\times 10^{-5} & -1.0\times 10^{-5} & 7.9\times 10^{-4} & -1.3\times 10^{-2} & -4.4\times 10^{-3} & -1.2\times 10^{-4} & -7.1\times 10^{-6} & 8.4\times 10^{-5} & -8.5\times 10^{-6} & 6.9\times 10^{-4} & -1.3\times 10^{-2} & -7.7\times 10^{-3} & -1.1\times 10^{-4} & -6.2\times 10^{-6} & 7.6\times 10^{-5} & -6.8\times 10^{-6} & 6.2\times 10^{-4} & -1.1\times 10^{-2} & -7.3\times 10^{-3} & -7.2\times 10^{-5} & -5.0\times 10^{-6} & 6.3\times 10^{-5} & -5.3\times 10^{-6} & 5.1\times 10^{-4} & -7.8\times 10^{-3} & -4.8\times 10^{-3} & -5.3\times 10^{-5} & -3.9\times 10^{-6} & 5.0\times 10^{-5} & -4.0\times 10^{-6} & 4.0\times 10^{-4} & -3.2\times 10^{-3} & -2.6\times 10^{-3} & -4.0\times 10^{-5} \\
-1.1\times 10^{-4} & -2.0\times 10^{-3} & 4.1\times 10^{-4} & -1.8\times 10^{-2} & 3.7\times 10^{+0} & 1.6\times 10^{+0} & 8.0\times 10^{-3} & 7.4\times 10^{-5} & -1.5\times 10^{-3} & 3.4\times 10^{-4} & -1.4\times 10^{-2} & 3.4\times 10^{+0} & 1.3\times 10^{+0} & 6.3\times 10^{-3} & 3.6\times 10^{-5} & -9.6\times 10^{-4} & 2.5\times 10^{-4} & -1.0\times 10^{-2} & 3.2\times 10^{+0} & 1.1\times 10^{+0} & 4.9\times 10^{-3} & 1.2\times 10^{-5} & -7.1\times 10^{-4} & 1.9\times 10^{-4} & -7.8\times 10^{-3} & 2.6\times 10^{+0} & 9.3\times 10^{-1} & 3.9\times 10^{-3} & -6.0\times 10^{-6} & -5.7\times 10^{-4} & 1.4\times 10^{-4} & -6.2\times 10^{-3} & 1.9\times 10^{+0} & 8.1\times 10^{-1} & 2.9\times 10^{-3} \\
--1.7\times 10^{-5} & -1.6\times 10^{-3} & 8.0\times 10^{-4} & -7.7\times 10^{-3} & 8.5\times 10^{-1} & 9.6\times 10^{+0} & 3.0\times 10^{-3} & 5.1\times 10^{-5} & -2.0\times 10^{-3} & 6.4\times 10^{-4} & -8.3\times 10^{-3} & 7.8\times 10^{-1} & 9.5\times 10^{+0} & 3.2\times 10^{-3} & 8.4\times 10^{-5} & -1.6\times 10^{-3} & 5.1\times 10^{-4} & -7.0\times 10^{-3} & 1.0\times 10^{+0} & 8.6\times 10^{+0} & -3.9\times 10^{-4} & 7.2\times 10^{-5} & -1.1\times 10^{-3} & 4.1\times 10^{-4} & -4.8\times 10^{-3} & 9.3\times 10^{-1} & 7.3\times 10^{+0} & -1.4\times 10^{-3} & 2.3\times 10^{-5} & -3.9\times 10^{-4} & 3.1\times 10^{-4} & -1.6\times 10^{-3} & 7.8\times 10^{-1} & 5.7\times 10^{+0} & -2.1\times 10^{-3} \\
-1.1\times 10^{-6} & -7.9\times 10^{-6} & 4.6\times 10^{-6} & -1.2\times 10^{-4} & 3.0\times 10^{-3} & 3.2\times 10^{-3} & 1.4\times 10^{-4} & 6.9\times 10^{-7} & -5.6\times 10^{-6} & 3.7\times 10^{-6} & -9.2\times 10^{-5} & 4.6\times 10^{-3} & 3.9\times 10^{-6} & 1.2\times 10^{-4} & 2.4\times 10^{-7} & -3.4\times 10^{-6} & 2.8\times 10^{-6} & -6.7\times 10^{-5} & 5.0\times 10^{-3} & -1.6\times 10^{-3} & 1.1\times 10^{-4} & 4.6\times 10^{-8} & -3.0\times 10^{-6} & 2.2\times 10^{-6} & -5.3\times 10^{-5} & 3.9\times 10^{-3} & -1.4\times 10^{-3} & 8.9\times 10^{-5} & -3.2\times 10^{-8} & -3.6\times 10^{-6} & 1.6\times 10^{-6} & -4.5\times 10^{-5} & 1.7\times 10^{-3} & -4.8\times 10^{-5} & 7.2\times 10^{-5} \\
-2.2\times 10^{-7} & -7.3\times 10^{-7} & 1.4\times 10^{-7} & -6.4\times 10^{-6} & 3.9\times 10^{-5} & -10.0\times 10^{-5} & 9.2\times 10^{-7} & 1.9\times 10^{-7} & -6.2\times 10^{-7} & 1.1\times 10^{-7} & -5.3\times 10^{-6} & 5.8\times 10^{-5} & -2.3\times 10^{-5} & 6.7\times 10^{-7} & 1.7\times 10^{-7} & -5.7\times 10^{-7} & 9.4\times 10^{-8} & -4.7\times 10^{-6} & 2.6\times 10^{-5} & 2.1\times 10^{-5} & 2.1\times 10^{-7} & 1.4\times 10^{-7} & -4.8\times 10^{-7} & 7.7\times 10^{-8} & -3.9\times 10^{-6} & -6.0\times 10^{-6} & 2.3\times 10^{-5} & -3.2\times 10^{-8} & 1.3\times 10^{-7} & -4.2\times 10^{-7} & 6.6\times 10^{-8} & -3.3\times 10^{-6} & -5.8\times 10^{-5} & 3.4\times 10^{-5} & -2.4\times 10^{-7} \\
--7.2\times 10^{-7} & 1.1\times 10^{-5} & -8.1\times 10^{-7} & 7.7\times 10^{-5} & -1.4\times 10^{-3} & -3.8\times 10^{-4} & -7.2\times 10^{-6} & -6.0\times 10^{-7} & 9.3\times 10^{-6} & -6.9\times 10^{-7} & 6.2\times 10^{-5} & -1.1\times 10^{-3} & -6.0\times 10^{-4} & -6.3\times 10^{-6} & -5.5\times 10^{-7} & 8.7\times 10^{-6} & -5.4\times 10^{-7} & 5.8\times 10^{-5} & -7.8\times 10^{-4} & -6.0\times 10^{-4} & -4.4\times 10^{-6} & -4.6\times 10^{-7} & 7.5\times 10^{-6} & -4.2\times 10^{-7} & 5.0\times 10^{-5} & -5.7\times 10^{-4} & -3.9\times 10^{-4} & -3.6\times 10^{-6} & -4.2\times 10^{-7} & 7.0\times 10^{-6} & -3.3\times 10^{-7} & 4.6\times 10^{-5} & -2.7\times 10^{-4} & -3.8\times 10^{-4} & -2.8\times 10^{-6} \\
-1.4\times 10^{-7} & -8.8\times 10^{-7} & 4.7\times 10^{-7} & -7.7\times 10^{-6} & 1.3\times 10^{-4} & 5.6\times 10^{-4} & 3.6\times 10^{-6} & 1.2\times 10^{-7} & -7.7\times 10^{-7} & 3.8\times 10^{-7} & -6.6\times 10^{-6} & 1.7\times 10^{-4} & 5.1\times 10^{-4} & 3.0\times 10^{-6} & 9.8\times 10^{-8} & -5.6\times 10^{-7} & 3.2\times 10^{-7} & -5.1\times 10^{-6} & 1.8\times 10^{-4} & 4.0\times 10^{-4} & 2.1\times 10^{-6} & 8.0\times 10^{-8} & -4.4\times 10^{-7} & 2.6\times 10^{-7} & -4.0\times 10^{-6} & 1.4\times 10^{-4} & 3.1\times 10^{-4} & 1.6\times 10^{-6} & 6.6\times 10^{-8} & -3.3\times 10^{-7} & 2.2\times 10^{-7} & -3.2\times 10^{-6} & 5.7\times 10^{-5} & 2.2\times 10^{-4} & 1.2\times 10^{-6} \\
--6.3\times 10^{-6} & 7.6\times 10^{-5} & -7.4\times 10^{-6} & 6.3\times 10^{-4} & -1.1\times 10^{-2} & -7.6\times 10^{-4} & -9.9\times 10^{-5} & -5.3\times 10^{-6} & 6.3\times 10^{-5} & -6.2\times 10^{-6} & 5.1\times 10^{-4} & -1.0\times 10^{-2} & -3.1\times 10^{-3} & -8.3\times 10^{-5} & -4.6\times 10^{-6} & 5.8\times 10^{-5} & -5.0\times 10^{-6} & 4.7\times 10^{-4} & -8.2\times 10^{-3} & -3.1\times 10^{-3} & -5.8\times 10^{-5} & -3.9\times 10^{-6} & 5.0\times 10^{-5} & -4.0\times 10^{-6} & 4.0\times 10^{-4} & -6.2\times 10^{-3} & -1.6\times 10^{-3} & -4.5\times 10^{-5} & -3.3\times 10^{-6} & 4.6\times 10^{-5} & -3.2\times 10^{-6} & 3.7\times 10^{-4} & -3.0\times 10^{-3} & -1.2\times 10^{-3} & -3.3\times 10^{-5} \\
--3.6\times 10^{-5} & -1.1\times 10^{-3} & 1.6\times 10^{-4} & -8.1\times 10^{-3} & 2.9\times 10^{+0} & 1.4\times 10^{+0} & 2.6\times 10^{-3} & -5.2\times 10^{-5} & -7.7\times 10^{-4} & 1.3\times 10^{-4} & -6.0\times 10^{-3} & 2.4\times 10^{+0} & 1.1\times 10^{+0} & 2.1\times 10^{-3} & -6.3\times 10^{-5} & -4.2\times 10^{-4} & 9.2\times 10^{-5} & -4.0\times 10^{-3} & 2.2\times 10^{+0} & 8.8\times 10^{-1} & 1.9\times 10^{-3} & -6.4\times 10^{-5} & -3.0\times 10^{-4} & 7.3\times 10^{-5} & -3.2\times 10^{-3} & 1.9\times 10^{+0} & 7.8\times 10^{-1} & 1.7\times 10^{-3} & -5.8\times 10^{-5} & -2.7\times 10^{-4} & 5.7\times 10^{-5} & -3.0\times 10^{-3} & 1.8\times 10^{+0} & 6.9\times 10^{-1} & 1.5\times 10^{-3} \\
--6.7\times 10^{-6} & -1.2\times 10^{-3} & 5.9\times 10^{-4} & -4.9\times 10^{-3} & 6.7\times 10^{-1} & 7.9\times 10^{+0} & 2.3\times 10^{-3} & 9.5\times 10^{-6} & -1.1\times 10^{-3} & 4.8\times 10^{-4} & -4.1\times 10^{-3} & 6.5\times 10^{-1} & 7.1\times 10^{+0} & 2.0\times 10^{-3} & 3.2\times 10^{-5} & -9.0\times 10^{-4} & 3.6\times 10^{-4} & -3.9\times 10^{-3} & 8.9\times 10^{-1} & 6.4\times 10^{+0} & 6.8\times 10^{-4} & 3.0\times 10^{-5} & -6.5\times 10^{-4} & 2.8\times 10^{-4} & -2.6\times 10^{-3} & 8.1\times 10^{-1} & 5.7\times 10^{+0} & -4.8\times 10^{-5} & 3.4\times 10^{-5} & -3.8\times 10^{-4} & 2.2\times 10^{-4} & -1.2\times 10^{-3} & 6.9\times 10^{-1} & 5.4\times 10^{+0} & -6.4\times 10^{-4} \\
-4.7\times 10^{-7} & -5.2\times 10^{-6} & 3.1\times 10^{-6} & -7.9\times 10^{-5} & 2.1\times 10^{-3} & 1.8\times 10^{-3} & 1.1\times 10^{-4} & 2.4\times 10^{-7} & -4.0\times 10^{-6} & 2.6\times 10^{-6} & -6.7\times 10^{-5} & 3.2\times 10^{-3} & -1.3\times 10^{-3} & 8.9\times 10^{-5} & -5.5\times 10^{-8} & -2.8\times 10^{-6} & 2.0\times 10^{-6} & -5.1\times 10^{-5} & 3.6\times 10^{-3} & -2.5\times 10^{-3} & 8.3\times 10^{-5} & -1.9\times 10^{-7} & -2.4\times 10^{-6} & 1.6\times 10^{-6} & -4.0\times 10^{-5} & 2.9\times 10^{-3} & -2.1\times 10^{-3} & 7.2\times 10^{-5} & -2.4\times 10^{-7} & -2.8\times 10^{-6} & 1.2\times 10^{-6} & -3.3\times 10^{-5} & 1.5\times 10^{-3} & -6.4\times 10^{-4} & 6.6\times 10^{-5} \\
-\end{bmatrix}
-\end{equation}
+%
+%\section{Covariance Matrix for Model~III Global Parameters}
+%\added{The following is the  covariance matrix for the global cofactors $\{ \alpha_{\hat{U}}, \beta_{\hat{U}}, \eta_{\hat{U}}, \zeta_{\hat{U}}, \gamma^0_{\hat{U}},\gamma^1_{\hat{U}}, \sigma_p \phi_{\hat{U}},
+%\ldots,
+%\alpha_{\hat{I}}, \beta_{\hat{I}}, \eta_{\hat{I}}, \zeta_{\hat{I}}, \gamma^0_{\hat{I}},\gamma^1_{\hat{I}}, \sigma_p \phi_{\hat{I}}
+% \}$.  The matrix 35x35 is big so will have to go in supplemental material.}
+%\setcounter{MaxMatrixCols}{40}
+%\begin{equation}
+%\tiny
+%\begin{bmatrix}
+%5.5\times 10^{-7} & -1.8\times 10^{-6} & 3.9\times 10^{-7} & -1.6\times 10^{-5} & 2.1\times 10^{-4} & -2.6\times 10^{-4} & 3.6\times 10^{-6} & 4.5\times 10^{-7} & -1.5\times 10^{-6} & 3.1\times 10^{-7} & -1.3\times 10^{-5} & 2.6\times 10^{-4} & -1.3\times 10^{-4} & 2.8\times 10^{-6} & 3.6\times 10^{-7} & -1.2\times 10^{-6} & 2.4\times 10^{-7} & -1.0\times 10^{-5} & 1.9\times 10^{-4} & -5.5\times 10^{-5} & 1.7\times 10^{-6} & 2.9\times 10^{-7} & -9.2\times 10^{-7} & 1.9\times 10^{-7} & -8.1\times 10^{-6} & 1.1\times 10^{-4} & -1.7\times 10^{-5} & 1.1\times 10^{-6} & 2.2\times 10^{-7} & -7.2\times 10^{-7} & 1.4\times 10^{-7} & -6.3\times 10^{-6} & -3.6\times 10^{-5} & -6.7\times 10^{-6} & 4.7\times 10^{-7} \\
+%-1.8\times 10^{-6} & 2.7\times 10^{-5} & -2.6\times 10^{-6} & 1.9\times 10^{-4} & -4.0\times 10^{-3} & -3.0\times 10^{-3} & -1.8\times 10^{-5} & -1.4\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.2\times 10^{-3} & -2.7\times 10^{-3} & -1.4\times 10^{-5} & -1.1\times 10^{-6} & 1.7\times 10^{-5} & -1.6\times 10^{-6} & 1.2\times 10^{-4} & -2.6\times 10^{-3} & -2.1\times 10^{-3} & -1.0\times 10^{-5} & -9.2\times 10^{-7} & 1.4\times 10^{-5} & -1.2\times 10^{-6} & 9.4\times 10^{-5} & -2.0\times 10^{-3} & -1.6\times 10^{-3} & -7.9\times 10^{-6} & -7.3\times 10^{-7} & 1.1\times 10^{-5} & -8.8\times 10^{-7} & 7.6\times 10^{-5} & -1.1\times 10^{-3} & -1.2\times 10^{-3} & -5.2\times 10^{-6} \\
+%3.9\times 10^{-7} & -2.6\times 10^{-6} & 1.3\times 10^{-6} & -2.2\times 10^{-5} & 3.9\times 10^{-4} & 1.7\times 10^{-3} & 1.0\times 10^{-5} & 3.2\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 5.0\times 10^{-4} & 1.4\times 10^{-3} & 8.3\times 10^{-6} & 2.4\times 10^{-7} & -1.5\times 10^{-6} & 7.8\times 10^{-7} & -1.3\times 10^{-5} & 5.4\times 10^{-4} & 1.0\times 10^{-3} & 6.0\times 10^{-6} & 1.9\times 10^{-7} & -1.1\times 10^{-6} & 6.1\times 10^{-7} & -1.0\times 10^{-5} & 4.1\times 10^{-4} & 8.0\times 10^{-4} & 4.6\times 10^{-6} & 1.4\times 10^{-7} & -8.1\times 10^{-7} & 4.7\times 10^{-7} & -7.4\times 10^{-6} & 1.6\times 10^{-4} & 5.9\times 10^{-4} & 3.1\times 10^{-6} \\
+%-1.6\times 10^{-5} & 1.9\times 10^{-4} & -2.2\times 10^{-5} & 1.6\times 10^{-3} & -2.9\times 10^{-2} & -1.4\times 10^{-2} & -2.7\times 10^{-4} & -1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.8\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.0\times 10^{-5} & 1.2\times 10^{-4} & -1.4\times 10^{-5} & 9.9\times 10^{-4} & -2.3\times 10^{-2} & -1.0\times 10^{-2} & -1.5\times 10^{-4} & -8.3\times 10^{-6} & 9.5\times 10^{-5} & -1.1\times 10^{-5} & 7.9\times 10^{-4} & -1.8\times 10^{-2} & -7.7\times 10^{-3} & -1.2\times 10^{-4} & -6.4\times 10^{-6} & 7.7\times 10^{-5} & -7.7\times 10^{-6} & 6.3\times 10^{-4} & -8.1\times 10^{-3} & -4.9\times 10^{-3} & -7.9\times 10^{-5} \\
+%2.1\times 10^{-4} & -4.0\times 10^{-3} & 3.9\times 10^{-4} & -2.9\times 10^{-2} & 6.9\times 10^{+0} & 1.3\times 10^{+0} & 6.7\times 10^{-3} & 1.4\times 10^{-4} & -3.0\times 10^{-3} & 3.2\times 10^{-4} & -2.2\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 5.1\times 10^{-3} & 9.6\times 10^{-5} & -2.2\times 10^{-3} & 2.3\times 10^{-4} & -1.6\times 10^{-2} & 4.5\times 10^{+0} & 9.7\times 10^{-1} & 3.7\times 10^{-3} & 6.0\times 10^{-5} & -1.7\times 10^{-3} & 1.7\times 10^{-4} & -1.3\times 10^{-2} & 3.7\times 10^{+0} & 8.5\times 10^{-1} & 3.0\times 10^{-3} & 3.9\times 10^{-5} & -1.4\times 10^{-3} & 1.3\times 10^{-4} & -1.1\times 10^{-2} & 2.9\times 10^{+0} & 6.7\times 10^{-1} & 2.1\times 10^{-3} \\
+%-2.6\times 10^{-4} & -3.0\times 10^{-3} & 1.7\times 10^{-3} & -1.4\times 10^{-2} & 1.3\times 10^{+0} & 1.7\times 10^{+1} & 8.7\times 10^{-3} & -1.9\times 10^{-4} & -2.8\times 10^{-3} & 1.3\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 7.1\times 10^{-3} & -1.7\times 10^{-4} & -1.5\times 10^{-3} & 9.7\times 10^{-4} & -6.8\times 10^{-3} & 1.8\times 10^{+0} & 1.1\times 10^{+1} & 4.9\times 10^{-3} & -1.2\times 10^{-4} & -1.0\times 10^{-3} & 7.6\times 10^{-4} & -4.4\times 10^{-3} & 1.6\times 10^{+0} & 9.6\times 10^{+0} & 3.2\times 10^{-3} & -10.0\times 10^{-5} & -3.8\times 10^{-4} & 5.6\times 10^{-4} & -7.6\times 10^{-4} & 1.4\times 10^{+0} & 7.9\times 10^{+0} & 1.8\times 10^{-3} \\
+%3.6\times 10^{-6} & -1.8\times 10^{-5} & 1.0\times 10^{-5} & -2.7\times 10^{-4} & 6.7\times 10^{-3} & 8.7\times 10^{-3} & 2.8\times 10^{-4} & 2.9\times 10^{-6} & -1.4\times 10^{-5} & 8.4\times 10^{-6} & -2.1\times 10^{-4} & 1.1\times 10^{-2} & 6.8\times 10^{-3} & 2.3\times 10^{-4} & 2.0\times 10^{-6} & -9.4\times 10^{-6} & 6.4\times 10^{-6} & -1.6\times 10^{-4} & 1.1\times 10^{-2} & 4.1\times 10^{-3} & 1.8\times 10^{-4} & 1.4\times 10^{-6} & -7.4\times 10^{-6} & 4.9\times 10^{-6} & -1.2\times 10^{-4} & 8.0\times 10^{-3} & 3.0\times 10^{-3} & 1.4\times 10^{-4} & 9.2\times 10^{-7} & -7.2\times 10^{-6} & 3.6\times 10^{-6} & -9.9\times 10^{-5} & 2.6\times 10^{-3} & 2.3\times 10^{-3} & 1.1\times 10^{-4} \\
+%4.5\times 10^{-7} & -1.4\times 10^{-6} & 3.2\times 10^{-7} & -1.3\times 10^{-5} & 1.4\times 10^{-4} & -1.9\times 10^{-4} & 2.9\times 10^{-6} & 4.0\times 10^{-7} & -1.3\times 10^{-6} & 2.7\times 10^{-7} & -1.1\times 10^{-5} & 2.0\times 10^{-4} & -2.5\times 10^{-5} & 2.3\times 10^{-6} & 3.2\times 10^{-7} & -1.0\times 10^{-6} & 2.1\times 10^{-7} & -9.1\times 10^{-6} & 1.4\times 10^{-4} & 4.3\times 10^{-5} & 1.3\times 10^{-6} & 2.6\times 10^{-7} & -8.2\times 10^{-7} & 1.7\times 10^{-7} & -7.1\times 10^{-6} & 7.4\times 10^{-5} & 5.1\times 10^{-5} & 6.9\times 10^{-7} & 1.9\times 10^{-7} & -6.0\times 10^{-7} & 1.2\times 10^{-7} & -5.3\times 10^{-6} & -5.2\times 10^{-5} & 9.5\times 10^{-6} & 2.4\times 10^{-7} \\
+%-1.5\times 10^{-6} & 2.2\times 10^{-5} & -2.1\times 10^{-6} & 1.5\times 10^{-4} & -3.0\times 10^{-3} & -2.8\times 10^{-3} & -1.4\times 10^{-5} & -1.3\times 10^{-6} & 1.9\times 10^{-5} & -1.8\times 10^{-6} & 1.3\times 10^{-4} & -2.4\times 10^{-3} & -3.0\times 10^{-3} & -1.2\times 10^{-5} & -1.0\times 10^{-6} & 1.6\times 10^{-5} & -1.4\times 10^{-6} & 1.0\times 10^{-4} & -2.0\times 10^{-3} & -2.6\times 10^{-3} & -7.6\times 10^{-6} & -8.4\times 10^{-7} & 1.2\times 10^{-5} & -1.0\times 10^{-6} & 8.4\times 10^{-5} & -1.5\times 10^{-3} & -2.0\times 10^{-3} & -5.6\times 10^{-6} & -6.2\times 10^{-7} & 9.3\times 10^{-6} & -7.7\times 10^{-7} & 6.3\times 10^{-5} & -7.7\times 10^{-4} & -1.1\times 10^{-3} & -4.0\times 10^{-6} \\
+%3.1\times 10^{-7} & -2.1\times 10^{-6} & 1.0\times 10^{-6} & -1.8\times 10^{-5} & 3.2\times 10^{-4} & 1.3\times 10^{-3} & 8.4\times 10^{-6} & 2.7\times 10^{-7} & -1.8\times 10^{-6} & 8.5\times 10^{-7} & -1.5\times 10^{-5} & 4.1\times 10^{-4} & 1.1\times 10^{-3} & 6.7\times 10^{-6} & 2.0\times 10^{-7} & -1.2\times 10^{-6} & 6.7\times 10^{-7} & -1.1\times 10^{-5} & 4.4\times 10^{-4} & 8.2\times 10^{-4} & 4.9\times 10^{-6} & 1.6\times 10^{-7} & -9.4\times 10^{-7} & 5.2\times 10^{-7} & -8.5\times 10^{-6} & 3.4\times 10^{-4} & 6.4\times 10^{-4} & 3.7\times 10^{-6} & 1.1\times 10^{-7} & -6.9\times 10^{-7} & 3.8\times 10^{-7} & -6.2\times 10^{-6} & 1.3\times 10^{-4} & 4.8\times 10^{-4} & 2.6\times 10^{-6} \\
+%-1.3\times 10^{-5} & 1.5\times 10^{-4} & -1.8\times 10^{-5} & 1.3\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -2.1\times 10^{-4} & -1.1\times 10^{-5} & 1.3\times 10^{-4} & -1.5\times 10^{-5} & 1.1\times 10^{-3} & -2.2\times 10^{-2} & -1.3\times 10^{-2} & -1.7\times 10^{-4} & -9.0\times 10^{-6} & 1.0\times 10^{-4} & -1.2\times 10^{-5} & 8.7\times 10^{-4} & -1.8\times 10^{-2} & -1.1\times 10^{-2} & -1.2\times 10^{-4} & -7.2\times 10^{-6} & 8.3\times 10^{-5} & -8.9\times 10^{-6} & 6.9\times 10^{-4} & -1.4\times 10^{-2} & -8.3\times 10^{-3} & -9.2\times 10^{-5} & -5.3\times 10^{-6} & 6.2\times 10^{-5} & -6.6\times 10^{-6} & 5.1\times 10^{-4} & -6.0\times 10^{-3} & -4.1\times 10^{-3} & -6.7\times 10^{-5} \\
+%2.6\times 10^{-4} & -3.2\times 10^{-3} & 5.0\times 10^{-4} & -2.8\times 10^{-2} & 5.5\times 10^{+0} & 1.1\times 10^{+0} & 1.1\times 10^{-2} & 2.0\times 10^{-4} & -2.4\times 10^{-3} & 4.1\times 10^{-4} & -2.2\times 10^{-2} & 5.1\times 10^{+0} & 9.4\times 10^{-1} & 8.4\times 10^{-3} & 1.4\times 10^{-4} & -1.8\times 10^{-3} & 3.0\times 10^{-4} & -1.6\times 10^{-2} & 4.3\times 10^{+0} & 8.6\times 10^{-1} & 6.0\times 10^{-3} & 9.8\times 10^{-5} & -1.4\times 10^{-3} & 2.3\times 10^{-4} & -1.3\times 10^{-2} & 3.4\times 10^{+0} & 7.8\times 10^{-1} & 4.6\times 10^{-3} & 5.8\times 10^{-5} & -1.1\times 10^{-3} & 1.7\times 10^{-4} & -1.0\times 10^{-2} & 2.4\times 10^{+0} & 6.5\times 10^{-1} & 3.2\times 10^{-3} \\
+%-1.3\times 10^{-4} & -2.7\times 10^{-3} & 1.4\times 10^{-3} & -1.3\times 10^{-2} & 1.1\times 10^{+0} & 1.4\times 10^{+1} & 6.8\times 10^{-3} & -2.5\times 10^{-5} & -3.0\times 10^{-3} & 1.1\times 10^{-3} & -1.3\times 10^{-2} & 9.4\times 10^{-1} & 1.4\times 10^{+1} & 6.4\times 10^{-3} & 1.8\times 10^{-5} & -2.2\times 10^{-3} & 8.6\times 10^{-4} & -1.1\times 10^{-2} & 1.5\times 10^{+0} & 1.2\times 10^{+1} & 1.6\times 10^{-3} & 2.0\times 10^{-5} & -1.6\times 10^{-3} & 6.7\times 10^{-4} & -7.7\times 10^{-3} & 1.3\times 10^{+0} & 9.5\times 10^{+0} & 3.9\times 10^{-6} & -2.3\times 10^{-5} & -6.0\times 10^{-4} & 5.1\times 10^{-4} & -3.1\times 10^{-3} & 1.1\times 10^{+0} & 7.1\times 10^{+0} & -1.3\times 10^{-3} \\
+%2.8\times 10^{-6} & -1.4\times 10^{-5} & 8.3\times 10^{-6} & -2.1\times 10^{-4} & 5.1\times 10^{-3} & 7.1\times 10^{-3} & 2.3\times 10^{-4} & 2.3\times 10^{-6} & -1.2\times 10^{-5} & 6.7\times 10^{-6} & -1.7\times 10^{-4} & 8.4\times 10^{-3} & 6.4\times 10^{-3} & 1.9\times 10^{-4} & 1.6\times 10^{-6} & -8.8\times 10^{-6} & 5.2\times 10^{-6} & -1.4\times 10^{-4} & 8.6\times 10^{-3} & 4.5\times 10^{-3} & 1.5\times 10^{-4} & 1.1\times 10^{-6} & -7.0\times 10^{-6} & 4.0\times 10^{-6} & -1.1\times 10^{-4} & 6.3\times 10^{-3} & 3.2\times 10^{-3} & 1.2\times 10^{-4} & 6.7\times 10^{-7} & -6.3\times 10^{-6} & 3.0\times 10^{-6} & -8.3\times 10^{-5} & 2.1\times 10^{-3} & 2.0\times 10^{-3} & 8.9\times 10^{-5} \\
+%3.6\times 10^{-7} & -1.1\times 10^{-6} & 2.4\times 10^{-7} & -1.0\times 10^{-5} & 9.6\times 10^{-5} & -1.7\times 10^{-4} & 2.0\times 10^{-6} & 3.2\times 10^{-7} & -1.0\times 10^{-6} & 2.0\times 10^{-7} & -9.0\times 10^{-6} & 1.4\times 10^{-4} & 1.8\times 10^{-5} & 1.6\times 10^{-6} & 2.8\times 10^{-7} & -9.3\times 10^{-7} & 1.7\times 10^{-7} & -7.8\times 10^{-6} & 9.4\times 10^{-5} & 1.0\times 10^{-4} & 6.8\times 10^{-7} & 2.3\times 10^{-7} & -7.4\times 10^{-7} & 1.3\times 10^{-7} & -6.2\times 10^{-6} & 3.6\times 10^{-5} & 8.4\times 10^{-5} & 2.4\times 10^{-7} & 1.7\times 10^{-7} & -5.5\times 10^{-7} & 9.8\times 10^{-8} & -4.6\times 10^{-6} & -6.3\times 10^{-5} & 3.2\times 10^{-5} & -5.5\times 10^{-8} \\
+%-1.2\times 10^{-6} & 1.7\times 10^{-5} & -1.5\times 10^{-6} & 1.2\times 10^{-4} & -2.2\times 10^{-3} & -1.5\times 10^{-3} & -9.4\times 10^{-6} & -1.0\times 10^{-6} & 1.6\times 10^{-5} & -1.2\times 10^{-6} & 1.0\times 10^{-4} & -1.8\times 10^{-3} & -2.2\times 10^{-3} & -8.8\times 10^{-6} & -9.3\times 10^{-7} & 1.4\times 10^{-5} & -9.7\times 10^{-7} & 9.4\times 10^{-5} & -1.3\times 10^{-3} & -2.2\times 10^{-3} & -5.0\times 10^{-6} & -7.6\times 10^{-7} & 1.1\times 10^{-5} & -7.5\times 10^{-7} & 7.6\times 10^{-5} & -9.6\times 10^{-4} & -1.6\times 10^{-3} & -3.4\times 10^{-6} & -5.7\times 10^{-7} & 8.7\times 10^{-6} & -5.6\times 10^{-7} & 5.8\times 10^{-5} & -4.2\times 10^{-4} & -9.0\times 10^{-4} & -2.8\times 10^{-6} \\
+%2.4\times 10^{-7} & -1.6\times 10^{-6} & 7.8\times 10^{-7} & -1.4\times 10^{-5} & 2.3\times 10^{-4} & 9.7\times 10^{-4} & 6.4\times 10^{-6} & 2.1\times 10^{-7} & -1.4\times 10^{-6} & 6.7\times 10^{-7} & -1.2\times 10^{-5} & 3.0\times 10^{-4} & 8.6\times 10^{-4} & 5.2\times 10^{-6} & 1.7\times 10^{-7} & -9.7\times 10^{-7} & 5.5\times 10^{-7} & -8.8\times 10^{-6} & 3.3\times 10^{-4} & 6.6\times 10^{-4} & 3.7\times 10^{-6} & 1.3\times 10^{-7} & -7.4\times 10^{-7} & 4.3\times 10^{-7} & -6.8\times 10^{-6} & 2.5\times 10^{-4} & 5.1\times 10^{-4} & 2.8\times 10^{-6} & 9.4\times 10^{-8} & -5.4\times 10^{-7} & 3.2\times 10^{-7} & -5.0\times 10^{-6} & 9.2\times 10^{-5} & 3.6\times 10^{-4} & 2.0\times 10^{-6} \\
+%-1.0\times 10^{-5} & 1.2\times 10^{-4} & -1.3\times 10^{-5} & 9.9\times 10^{-4} & -1.6\times 10^{-2} & -6.8\times 10^{-3} & -1.6\times 10^{-4} & -9.1\times 10^{-6} & 1.0\times 10^{-4} & -1.1\times 10^{-5} & 8.7\times 10^{-4} & -1.6\times 10^{-2} & -1.1\times 10^{-2} & -1.4\times 10^{-4} & -7.8\times 10^{-6} & 9.4\times 10^{-5} & -8.8\times 10^{-6} & 7.8\times 10^{-4} & -1.4\times 10^{-2} & -1.0\times 10^{-2} & -9.2\times 10^{-5} & -6.3\times 10^{-6} & 7.6\times 10^{-5} & -6.8\times 10^{-6} & 6.2\times 10^{-4} & -1.0\times 10^{-2} & -7.0\times 10^{-3} & -6.7\times 10^{-5} & -4.7\times 10^{-6} & 5.8\times 10^{-5} & -5.1\times 10^{-6} & 4.7\times 10^{-4} & -4.0\times 10^{-3} & -3.9\times 10^{-3} & -5.1\times 10^{-5} \\
+%1.9\times 10^{-4} & -2.6\times 10^{-3} & 5.4\times 10^{-4} & -2.3\times 10^{-2} & 4.5\times 10^{+0} & 1.8\times 10^{+0} & 1.1\times 10^{-2} & 1.4\times 10^{-4} & -2.0\times 10^{-3} & 4.4\times 10^{-4} & -1.8\times 10^{-2} & 4.3\times 10^{+0} & 1.5\times 10^{+0} & 8.6\times 10^{-3} & 9.4\times 10^{-5} & -1.3\times 10^{-3} & 3.3\times 10^{-4} & -1.4\times 10^{-2} & 4.0\times 10^{+0} & 1.2\times 10^{+0} & 6.5\times 10^{-3} & 5.8\times 10^{-5} & -9.9\times 10^{-4} & 2.5\times 10^{-4} & -1.1\times 10^{-2} & 3.2\times 10^{+0} & 1.0\times 10^{+0} & 5.0\times 10^{-3} & 2.6\times 10^{-5} & -7.8\times 10^{-4} & 1.8\times 10^{-4} & -8.2\times 10^{-3} & 2.2\times 10^{+0} & 8.9\times 10^{-1} & 3.6\times 10^{-3} \\
+%-5.5\times 10^{-5} & -2.1\times 10^{-3} & 1.0\times 10^{-3} & -1.0\times 10^{-2} & 9.7\times 10^{-1} & 1.1\times 10^{+1} & 4.1\times 10^{-3} & 4.3\times 10^{-5} & -2.6\times 10^{-3} & 8.2\times 10^{-4} & -1.1\times 10^{-2} & 8.6\times 10^{-1} & 1.2\times 10^{+1} & 4.5\times 10^{-3} & 1.0\times 10^{-4} & -2.2\times 10^{-3} & 6.6\times 10^{-4} & -1.0\times 10^{-2} & 1.2\times 10^{+0} & 1.0\times 10^{+1} & -3.8\times 10^{-4} & 8.4\times 10^{-5} & -1.6\times 10^{-3} & 5.2\times 10^{-4} & -7.3\times 10^{-3} & 1.1\times 10^{+0} & 8.6\times 10^{+0} & -1.6\times 10^{-3} & 2.1\times 10^{-5} & -6.0\times 10^{-4} & 4.0\times 10^{-4} & -3.1\times 10^{-3} & 8.8\times 10^{-1} & 6.4\times 10^{+0} & -2.5\times 10^{-3} \\
+%1.7\times 10^{-6} & -1.0\times 10^{-5} & 6.0\times 10^{-6} & -1.5\times 10^{-4} & 3.7\times 10^{-3} & 4.9\times 10^{-3} & 1.8\times 10^{-4} & 1.3\times 10^{-6} & -7.6\times 10^{-6} & 4.9\times 10^{-6} & -1.2\times 10^{-4} & 6.0\times 10^{-3} & 1.6\times 10^{-3} & 1.5\times 10^{-4} & 6.8\times 10^{-7} & -5.0\times 10^{-6} & 3.7\times 10^{-6} & -9.2\times 10^{-5} & 6.5\times 10^{-3} & -3.8\times 10^{-4} & 1.3\times 10^{-4} & 3.9\times 10^{-7} & -4.1\times 10^{-6} & 2.9\times 10^{-6} & -7.2\times 10^{-5} & 4.9\times 10^{-3} & -3.9\times 10^{-4} & 1.1\times 10^{-4} & 2.1\times 10^{-7} & -4.4\times 10^{-6} & 2.1\times 10^{-6} & -5.8\times 10^{-5} & 1.9\times 10^{-3} & 6.8\times 10^{-4} & 8.3\times 10^{-5} \\
+%2.9\times 10^{-7} & -9.2\times 10^{-7} & 1.9\times 10^{-7} & -8.3\times 10^{-6} & 6.0\times 10^{-5} & -1.2\times 10^{-4} & 1.4\times 10^{-6} & 2.6\times 10^{-7} & -8.4\times 10^{-7} & 1.6\times 10^{-7} & -7.2\times 10^{-6} & 9.8\times 10^{-5} & 2.0\times 10^{-5} & 1.1\times 10^{-6} & 2.3\times 10^{-7} & -7.6\times 10^{-7} & 1.3\times 10^{-7} & -6.3\times 10^{-6} & 5.8\times 10^{-5} & 8.4\times 10^{-5} & 3.9\times 10^{-7} & 1.9\times 10^{-7} & -6.2\times 10^{-7} & 1.0\times 10^{-7} & -5.0\times 10^{-6} & 1.2\times 10^{-5} & 7.2\times 10^{-5} & 4.6\times 10^{-8} & 1.4\times 10^{-7} & -4.6\times 10^{-7} & 8.0\times 10^{-8} & -3.9\times 10^{-6} & -6.4\times 10^{-5} & 3.0\times 10^{-5} & -1.9\times 10^{-7} \\
+%-9.2\times 10^{-7} & 1.4\times 10^{-5} & -1.1\times 10^{-6} & 9.5\times 10^{-5} & -1.7\times 10^{-3} & -1.0\times 10^{-3} & -7.4\times 10^{-6} & -8.2\times 10^{-7} & 1.2\times 10^{-5} & -9.4\times 10^{-7} & 8.3\times 10^{-5} & -1.4\times 10^{-3} & -1.6\times 10^{-3} & -7.0\times 10^{-6} & -7.4\times 10^{-7} & 1.1\times 10^{-5} & -7.4\times 10^{-7} & 7.6\times 10^{-5} & -9.9\times 10^{-4} & -1.6\times 10^{-3} & -4.1\times 10^{-6} & -6.2\times 10^{-7} & 9.5\times 10^{-6} & -5.8\times 10^{-7} & 6.3\times 10^{-5} & -7.1\times 10^{-4} & -1.1\times 10^{-3} & -3.0\times 10^{-6} & -4.8\times 10^{-7} & 7.5\times 10^{-6} & -4.4\times 10^{-7} & 5.0\times 10^{-5} & -3.0\times 10^{-4} & -6.5\times 10^{-4} & -2.4\times 10^{-6} \\
+%1.9\times 10^{-7} & -1.2\times 10^{-6} & 6.1\times 10^{-7} & -1.1\times 10^{-5} & 1.7\times 10^{-4} & 7.6\times 10^{-4} & 4.9\times 10^{-6} & 1.7\times 10^{-7} & -1.0\times 10^{-6} & 5.2\times 10^{-7} & -8.9\times 10^{-6} & 2.3\times 10^{-4} & 6.7\times 10^{-4} & 4.0\times 10^{-6} & 1.3\times 10^{-7} & -7.5\times 10^{-7} & 4.3\times 10^{-7} & -6.8\times 10^{-6} & 2.5\times 10^{-4} & 5.2\times 10^{-4} & 2.9\times 10^{-6} & 1.0\times 10^{-7} & -5.8\times 10^{-7} & 3.5\times 10^{-7} & -5.3\times 10^{-6} & 1.9\times 10^{-4} & 4.1\times 10^{-4} & 2.2\times 10^{-6} & 7.7\times 10^{-8} & -4.2\times 10^{-7} & 2.6\times 10^{-7} & -4.0\times 10^{-6} & 7.3\times 10^{-5} & 2.8\times 10^{-4} & 1.6\times 10^{-6} \\
+%-8.1\times 10^{-6} & 9.4\times 10^{-5} & -1.0\times 10^{-5} & 7.9\times 10^{-4} & -1.3\times 10^{-2} & -4.4\times 10^{-3} & -1.2\times 10^{-4} & -7.1\times 10^{-6} & 8.4\times 10^{-5} & -8.5\times 10^{-6} & 6.9\times 10^{-4} & -1.3\times 10^{-2} & -7.7\times 10^{-3} & -1.1\times 10^{-4} & -6.2\times 10^{-6} & 7.6\times 10^{-5} & -6.8\times 10^{-6} & 6.2\times 10^{-4} & -1.1\times 10^{-2} & -7.3\times 10^{-3} & -7.2\times 10^{-5} & -5.0\times 10^{-6} & 6.3\times 10^{-5} & -5.3\times 10^{-6} & 5.1\times 10^{-4} & -7.8\times 10^{-3} & -4.8\times 10^{-3} & -5.3\times 10^{-5} & -3.9\times 10^{-6} & 5.0\times 10^{-5} & -4.0\times 10^{-6} & 4.0\times 10^{-4} & -3.2\times 10^{-3} & -2.6\times 10^{-3} & -4.0\times 10^{-5} \\
+%1.1\times 10^{-4} & -2.0\times 10^{-3} & 4.1\times 10^{-4} & -1.8\times 10^{-2} & 3.7\times 10^{+0} & 1.6\times 10^{+0} & 8.0\times 10^{-3} & 7.4\times 10^{-5} & -1.5\times 10^{-3} & 3.4\times 10^{-4} & -1.4\times 10^{-2} & 3.4\times 10^{+0} & 1.3\times 10^{+0} & 6.3\times 10^{-3} & 3.6\times 10^{-5} & -9.6\times 10^{-4} & 2.5\times 10^{-4} & -1.0\times 10^{-2} & 3.2\times 10^{+0} & 1.1\times 10^{+0} & 4.9\times 10^{-3} & 1.2\times 10^{-5} & -7.1\times 10^{-4} & 1.9\times 10^{-4} & -7.8\times 10^{-3} & 2.6\times 10^{+0} & 9.3\times 10^{-1} & 3.9\times 10^{-3} & -6.0\times 10^{-6} & -5.7\times 10^{-4} & 1.4\times 10^{-4} & -6.2\times 10^{-3} & 1.9\times 10^{+0} & 8.1\times 10^{-1} & 2.9\times 10^{-3} \\
+%-1.7\times 10^{-5} & -1.6\times 10^{-3} & 8.0\times 10^{-4} & -7.7\times 10^{-3} & 8.5\times 10^{-1} & 9.6\times 10^{+0} & 3.0\times 10^{-3} & 5.1\times 10^{-5} & -2.0\times 10^{-3} & 6.4\times 10^{-4} & -8.3\times 10^{-3} & 7.8\times 10^{-1} & 9.5\times 10^{+0} & 3.2\times 10^{-3} & 8.4\times 10^{-5} & -1.6\times 10^{-3} & 5.1\times 10^{-4} & -7.0\times 10^{-3} & 1.0\times 10^{+0} & 8.6\times 10^{+0} & -3.9\times 10^{-4} & 7.2\times 10^{-5} & -1.1\times 10^{-3} & 4.1\times 10^{-4} & -4.8\times 10^{-3} & 9.3\times 10^{-1} & 7.3\times 10^{+0} & -1.4\times 10^{-3} & 2.3\times 10^{-5} & -3.9\times 10^{-4} & 3.1\times 10^{-4} & -1.6\times 10^{-3} & 7.8\times 10^{-1} & 5.7\times 10^{+0} & -2.1\times 10^{-3} \\
+%1.1\times 10^{-6} & -7.9\times 10^{-6} & 4.6\times 10^{-6} & -1.2\times 10^{-4} & 3.0\times 10^{-3} & 3.2\times 10^{-3} & 1.4\times 10^{-4} & 6.9\times 10^{-7} & -5.6\times 10^{-6} & 3.7\times 10^{-6} & -9.2\times 10^{-5} & 4.6\times 10^{-3} & 3.9\times 10^{-6} & 1.2\times 10^{-4} & 2.4\times 10^{-7} & -3.4\times 10^{-6} & 2.8\times 10^{-6} & -6.7\times 10^{-5} & 5.0\times 10^{-3} & -1.6\times 10^{-3} & 1.1\times 10^{-4} & 4.6\times 10^{-8} & -3.0\times 10^{-6} & 2.2\times 10^{-6} & -5.3\times 10^{-5} & 3.9\times 10^{-3} & -1.4\times 10^{-3} & 8.9\times 10^{-5} & -3.2\times 10^{-8} & -3.6\times 10^{-6} & 1.6\times 10^{-6} & -4.5\times 10^{-5} & 1.7\times 10^{-3} & -4.8\times 10^{-5} & 7.2\times 10^{-5} \\
+%2.2\times 10^{-7} & -7.3\times 10^{-7} & 1.4\times 10^{-7} & -6.4\times 10^{-6} & 3.9\times 10^{-5} & -10.0\times 10^{-5} & 9.2\times 10^{-7} & 1.9\times 10^{-7} & -6.2\times 10^{-7} & 1.1\times 10^{-7} & -5.3\times 10^{-6} & 5.8\times 10^{-5} & -2.3\times 10^{-5} & 6.7\times 10^{-7} & 1.7\times 10^{-7} & -5.7\times 10^{-7} & 9.4\times 10^{-8} & -4.7\times 10^{-6} & 2.6\times 10^{-5} & 2.1\times 10^{-5} & 2.1\times 10^{-7} & 1.4\times 10^{-7} & -4.8\times 10^{-7} & 7.7\times 10^{-8} & -3.9\times 10^{-6} & -6.0\times 10^{-6} & 2.3\times 10^{-5} & -3.2\times 10^{-8} & 1.3\times 10^{-7} & -4.2\times 10^{-7} & 6.6\times 10^{-8} & -3.3\times 10^{-6} & -5.8\times 10^{-5} & 3.4\times 10^{-5} & -2.4\times 10^{-7} \\
+%-7.2\times 10^{-7} & 1.1\times 10^{-5} & -8.1\times 10^{-7} & 7.7\times 10^{-5} & -1.4\times 10^{-3} & -3.8\times 10^{-4} & -7.2\times 10^{-6} & -6.0\times 10^{-7} & 9.3\times 10^{-6} & -6.9\times 10^{-7} & 6.2\times 10^{-5} & -1.1\times 10^{-3} & -6.0\times 10^{-4} & -6.3\times 10^{-6} & -5.5\times 10^{-7} & 8.7\times 10^{-6} & -5.4\times 10^{-7} & 5.8\times 10^{-5} & -7.8\times 10^{-4} & -6.0\times 10^{-4} & -4.4\times 10^{-6} & -4.6\times 10^{-7} & 7.5\times 10^{-6} & -4.2\times 10^{-7} & 5.0\times 10^{-5} & -5.7\times 10^{-4} & -3.9\times 10^{-4} & -3.6\times 10^{-6} & -4.2\times 10^{-7} & 7.0\times 10^{-6} & -3.3\times 10^{-7} & 4.6\times 10^{-5} & -2.7\times 10^{-4} & -3.8\times 10^{-4} & -2.8\times 10^{-6} \\
+%1.4\times 10^{-7} & -8.8\times 10^{-7} & 4.7\times 10^{-7} & -7.7\times 10^{-6} & 1.3\times 10^{-4} & 5.6\times 10^{-4} & 3.6\times 10^{-6} & 1.2\times 10^{-7} & -7.7\times 10^{-7} & 3.8\times 10^{-7} & -6.6\times 10^{-6} & 1.7\times 10^{-4} & 5.1\times 10^{-4} & 3.0\times 10^{-6} & 9.8\times 10^{-8} & -5.6\times 10^{-7} & 3.2\times 10^{-7} & -5.1\times 10^{-6} & 1.8\times 10^{-4} & 4.0\times 10^{-4} & 2.1\times 10^{-6} & 8.0\times 10^{-8} & -4.4\times 10^{-7} & 2.6\times 10^{-7} & -4.0\times 10^{-6} & 1.4\times 10^{-4} & 3.1\times 10^{-4} & 1.6\times 10^{-6} & 6.6\times 10^{-8} & -3.3\times 10^{-7} & 2.2\times 10^{-7} & -3.2\times 10^{-6} & 5.7\times 10^{-5} & 2.2\times 10^{-4} & 1.2\times 10^{-6} \\
+%-6.3\times 10^{-6} & 7.6\times 10^{-5} & -7.4\times 10^{-6} & 6.3\times 10^{-4} & -1.1\times 10^{-2} & -7.6\times 10^{-4} & -9.9\times 10^{-5} & -5.3\times 10^{-6} & 6.3\times 10^{-5} & -6.2\times 10^{-6} & 5.1\times 10^{-4} & -1.0\times 10^{-2} & -3.1\times 10^{-3} & -8.3\times 10^{-5} & -4.6\times 10^{-6} & 5.8\times 10^{-5} & -5.0\times 10^{-6} & 4.7\times 10^{-4} & -8.2\times 10^{-3} & -3.1\times 10^{-3} & -5.8\times 10^{-5} & -3.9\times 10^{-6} & 5.0\times 10^{-5} & -4.0\times 10^{-6} & 4.0\times 10^{-4} & -6.2\times 10^{-3} & -1.6\times 10^{-3} & -4.5\times 10^{-5} & -3.3\times 10^{-6} & 4.6\times 10^{-5} & -3.2\times 10^{-6} & 3.7\times 10^{-4} & -3.0\times 10^{-3} & -1.2\times 10^{-3} & -3.3\times 10^{-5} \\
+%-3.6\times 10^{-5} & -1.1\times 10^{-3} & 1.6\times 10^{-4} & -8.1\times 10^{-3} & 2.9\times 10^{+0} & 1.4\times 10^{+0} & 2.6\times 10^{-3} & -5.2\times 10^{-5} & -7.7\times 10^{-4} & 1.3\times 10^{-4} & -6.0\times 10^{-3} & 2.4\times 10^{+0} & 1.1\times 10^{+0} & 2.1\times 10^{-3} & -6.3\times 10^{-5} & -4.2\times 10^{-4} & 9.2\times 10^{-5} & -4.0\times 10^{-3} & 2.2\times 10^{+0} & 8.8\times 10^{-1} & 1.9\times 10^{-3} & -6.4\times 10^{-5} & -3.0\times 10^{-4} & 7.3\times 10^{-5} & -3.2\times 10^{-3} & 1.9\times 10^{+0} & 7.8\times 10^{-1} & 1.7\times 10^{-3} & -5.8\times 10^{-5} & -2.7\times 10^{-4} & 5.7\times 10^{-5} & -3.0\times 10^{-3} & 1.8\times 10^{+0} & 6.9\times 10^{-1} & 1.5\times 10^{-3} \\
+%-6.7\times 10^{-6} & -1.2\times 10^{-3} & 5.9\times 10^{-4} & -4.9\times 10^{-3} & 6.7\times 10^{-1} & 7.9\times 10^{+0} & 2.3\times 10^{-3} & 9.5\times 10^{-6} & -1.1\times 10^{-3} & 4.8\times 10^{-4} & -4.1\times 10^{-3} & 6.5\times 10^{-1} & 7.1\times 10^{+0} & 2.0\times 10^{-3} & 3.2\times 10^{-5} & -9.0\times 10^{-4} & 3.6\times 10^{-4} & -3.9\times 10^{-3} & 8.9\times 10^{-1} & 6.4\times 10^{+0} & 6.8\times 10^{-4} & 3.0\times 10^{-5} & -6.5\times 10^{-4} & 2.8\times 10^{-4} & -2.6\times 10^{-3} & 8.1\times 10^{-1} & 5.7\times 10^{+0} & -4.8\times 10^{-5} & 3.4\times 10^{-5} & -3.8\times 10^{-4} & 2.2\times 10^{-4} & -1.2\times 10^{-3} & 6.9\times 10^{-1} & 5.4\times 10^{+0} & -6.4\times 10^{-4} \\
+%4.7\times 10^{-7} & -5.2\times 10^{-6} & 3.1\times 10^{-6} & -7.9\times 10^{-5} & 2.1\times 10^{-3} & 1.8\times 10^{-3} & 1.1\times 10^{-4} & 2.4\times 10^{-7} & -4.0\times 10^{-6} & 2.6\times 10^{-6} & -6.7\times 10^{-5} & 3.2\times 10^{-3} & -1.3\times 10^{-3} & 8.9\times 10^{-5} & -5.5\times 10^{-8} & -2.8\times 10^{-6} & 2.0\times 10^{-6} & -5.1\times 10^{-5} & 3.6\times 10^{-3} & -2.5\times 10^{-3} & 8.3\times 10^{-5} & -1.9\times 10^{-7} & -2.4\times 10^{-6} & 1.6\times 10^{-6} & -4.0\times 10^{-5} & 2.9\times 10^{-3} & -2.1\times 10^{-3} & 7.2\times 10^{-5} & -2.4\times 10^{-7} & -2.8\times 10^{-6} & 1.2\times 10^{-6} & -3.3\times 10^{-5} & 1.5\times 10^{-3} & -6.4\times 10^{-4} & 6.6\times 10^{-5} \\
+%\end{bmatrix}
+%\end{equation}
 \bibliographystyle{aasjournal}

### 2018-06-19 submit/response.txt
ready for PC

--- 2018-05-08 submit/response.txt
@@
+We thank the referee for the comments, which have led to a revision of the article.  All changes are denoted in red.  We have grouped the referee’s comments thematically, which we address below.
+
 Comment 1:
@@
 
-We have added two tables to the article.
+The data that we use as features are now included in the article.  These are in a new table containing a list of the supernovae, their feature measurements, and uncertainties.
+
+The referee correctly points out that the spectrophotometric time series from which these features are extracted are not yet public.
+Nevertheless, there is a history in astrophysics for results that could stimulate public interest and activity (e.g.
+verification of identified trends using independent data sets) to be published before all antecedent data products are made public.
+We believe that the article fits that category.
+On the point of making all the spectroscopy public before publication of this article, we defer to the Journal’s editorial policies.
 
@@
 
+We have added paragraphs in the Data section that describe the selection of our sample.
+To address the referees’s specific questions, supernovae of the SN 1991T, SN 1991bg and SN 2002cx subclasses are excluded, one object SN2012c with an SALT2 C parameter much larger than the rest of the sample is excluded, one object whose spectral features make it a $>3\sigma$ outlier in the sample population as described in Leget (2016) is excluded.
+The host-galaxy contrast is not found to affect spectral-extraction success when the supernova is at peak brightness.
+
+A new Figure has been added to show the distributions of the observables in our sample, and the distributions the SALT2 light—curve observables x1 and C of the Pantheon sample as a point of reference.
+
+More importantly, we add a discussion on why sample selection is not important for the scope of this analysis.
+To summarize, this analysis seeks to detect and model diversity within the Type Ia family.
+Diversity found in a biased subsample remains as diversity of the whole family.
+For example, the important detection of the effect of Delta m_15 by Phillips (1993) was done on a biased sample.
+While sample selection is critical in the standardization and application of the model across different subsamples, that isn’t the focus of the current article.
+
 Comment 3:
@@
 
+We added a table listing the supernovae and the credible intervals of their parameters.
+
+Note that the correlation/covariance between a subset of parameters are already in the article.
+For example the correlation matrix of the per-supernova parameters is given and there is a figure of their distribution.
+However, there are so many parameters that presenting their covariance matrix within the article is unwieldy.
+For example, we did try to insert the 35x35 covariance matrix of the global parameters, but it did not come close to fitting neatly into a manuscript page.
+We suggest as an alternative that we provide the Monte Carlo chains in the tar archive from which the covariance of any possible parameter pair can be determined.
+The chains from the three runs are now available at https://drive.google.com/drive/folders/1d52nxfF7eS3HblfbmT3fxgiZod Z-Gjg?usp=sharing.
+If this is acceptable to the referee and editor, we will get a DOI number for the page and add it to the manuscript.
+
+We add, in Section 5.2.6.
+the determination of how much dispersion remains in an individual parameter assuming that a second (correlated) parameter is perfectly measured.
+The case of Si EW and x1 is singled out as an example in the text.
+
 Comment 4:
@@
 
+Response 4:
+
+The purpose of this article is to model supernova colors based on properties directly linked to the supernova.
+We then check whether the mass-step is could be due to our newly-discovered parameter.
+So we do the check but in the opposite (but equivalent) sense that the referee suggests.
+
+A proper association of the mass step and our parameter is better left to a different model that accounts for absolute magnitude.
+(Our model does not account for absolute magnitudes.)  This is because the effect of the mass step is attached to absolute magnitude.
+
+Comment 5:
+
 3. Section 5.2.9 says that the correlation between Delta and the other parameters is shown in Eq. 20. But Delta isn't included there.
+
+Response 5:
+
+The text in 5.2.9.
+is a remnant of an old version of the article.
+The offending text is now replaced with a reminder of how correlations between Delta and the other parameters are handled in the analysis.

### 2018-06-19 submit/fix.tex
ready for PC

@@
 SN~1991T, SN~1991bg and SN~2002cx subclasses,
-SNF20080905-005 described in \citet{leget:thesis} as
-being spectroscopically peculiar, and
+SNF20080905-005 described in \citet{leget:thesis} whose spectral features make it a $>3\sigma$ outlier in the
+sample population, and
 the extremely red SN2012cu  who has a SALT2 $C \approx 1$ \citep{2017ApJ...836..157H} that is several times larger than the colors
@@
 
-For the purposes of this article, it is not important whether our sample population is representative
-of the underlying population.  This article seeks
-underlying parameters that
+Considering that our empirical parameters
+are not fundamental supernova parameters, their best-fit values are dependent on sample selection.
+Nevertheless, this  article seeks
+underlying parameters that significantly
 affect SN~Ia colors; any such parameters found in a subsample are still
 relevant parameters when dealing with the population as a whole.
+Within this context, it is not important whether our sample population is representative
+of the underlying population.
 

### 2018-07-11 submit/response.txt
After Greg's comments

@@
 We believe that the article fits that category.
-On the point of making all the spectroscopy public before publication of this article, we defer to the Journal’s editorial policies.
+We believe that the condition of making all the spectroscopy public before publication of this article should be adjudicated by the editor, based on the precedents and standards of ApJ.
 
@@
 The host-galaxy contrast is not found to affect spectral-extraction success when the supernova is at peak brightness.
+
+We refer to previously published articles showing distributions of spectral,
+light-curve, and host-galaxy properties of a large subset of our sample.
 
@@
 We suggest as an alternative that we provide the Monte Carlo chains in the tar archive from which the covariance of any possible parameter pair can be determined.
-The chains from the three runs are now available at https://drive.google.com/drive/folders/1d52nxfF7eS3HblfbmT3fxgiZod Z-Gjg?usp=sharing.
-If this is acceptable to the referee and editor, we will get a DOI number for the page and add it to the manuscript.
+The chains from the three runs are now available at https://drive.google.com/open?id=1d52nxfF7eS3HblfbmT3fxgiZod_Z-Gjg for the referee’s perusal.
+If this is acceptable to the referee and editor, we will move these data products onto SNfactory’s webpage.
+We will get a DOI number for this page and include it to the manuscript.
 
@@
 The purpose of this article is to model supernova colors based on properties directly linked to the supernova.
-We then check whether the mass-step is could be due to our newly-discovered parameter.
+We then check whether the mass-step could be related to our newly-discovered parameter.
 So we do the check but in the opposite (but equivalent) sense that the referee suggests.

### 2018-07-11 submit/fix.tex
After Greg's comments

@@
 
-\added{The current SNfactory sample consists of 198 SNe~Ia
+\added{The SNfactory sample used here consists of 198 SNe~Ia
 having fully-processed spectrophotometric lightcurve data, including
 observations on at least two photometric nights, final references, and a
-host spectroscopic redshift. 
+host spectroscopic redshift.   This sample was defined for use in \citet{leget:thesis}.
 These supernovae have well-sampled lightcurves as defined by having
@@
 model; we require that supernovae have no more than 20\% points that are
-$>0.2$ mag from the best-fit model, and require a Normalized Median Absolute Deviation (nMAD) of residuals
-of  $< 0.12$ mag.
+$>0.2$ mag from the best-fit SALT2 model, and require a Normalized Median Absolute Deviation (nMAD) of residuals
+of  $< 0.12$ mag relative to this model.  \citep[It is known that more flexibility than available to SALT2 is required to capture
+the full range of observed SN~Ia behavior, e.g.\ ][]{2011AJ....141...19B, 2011ApJ...731..120M}.
 %These all have at least 5 spectra while the SN is
@@
 whose names start with ``SNF'', ``LSQ'', or ``PTF'' in Table~\ref{data:tab}).
+
+\citet{2013ApJ...770..108C}  present the distribution of host-galaxy parameters for a subset of the  above sample.
+\citet{2015MNRAS.447.1247S} show scatter plots of the peak Si~II~$\lambda 5972$ and
+Si~II~$\lambda 6355$ velocities and pseudo-equivalent
+widths, absolute $B$ and $V$ magnitudes, $B-V$, SALTII $c$ and $x_1$ parameters, and $\Delta m_{15}$ for 
+an preceding sample of 151 SNe.
 
@@
 relevant parameters when dealing with the population as a whole.
-Within this context, it is not important whether our sample population is representative
+Within this context, it is not so important whether our sample population is representative
 of the underlying population.
@@
 The 
-spectroscopic-feature measurements, SALT2 light-curve shape parameters  $x_1$,
+spectroscopic-feature measurements, 
+\replaced{SALT2 light-curve shape parameters  $x_1$,
 and their uncertainties
 are presented
-in \replaced{\citet{2017Chotard}}{Table~\ref{data:tab}. 
+in \citet{2017Chotard}}{
+synthetic magnitudes (plus a constant offset), SALT2 light-curve shape parameters  $x_1$,
+and their uncertainties
+are presented
+in 
+Table~\ref{data:tab}. 
 For the subset supernovae for whom it is available, we use the host-galaxy mass given in \citet{2013ApJ...770..108C}.
@@
 \tablehead{
-\colhead{Name} & \colhead{$EW_{\mathrm{Ca}}$ (\AA)} & \colhead{$EW_{\mathrm{Si}}$ (\AA)} & \colhead{$\lambda_{\mathrm{Si}}$ (\AA)} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} & \colhead{$x_1$}
+\colhead{Name} & \colhead{$EW_{\mathrm{Ca}}$ (\AA)} & \colhead{$EW_{\mathrm{Si}}$ (\AA)} & \colhead{$\lambda_{\mathrm{Si}}$ (\AA)} & \colhead{$U$+offset} & \colhead{$B$+offset} & \colhead{$V$+offset} & \colhead{$R$+offset} & \colhead{$I$+offset} & \colhead{$x_1$}
 }
@@
 \added{It is important to note that the model and those in subsequent sections are applied to our supernova sample;
-the ensuing results thus describe our SN~Ia sample's underlying population. }
+the ensuing results thus correspond to our SN~Ia sample's underlying population. }
 
@@
 \label{results1:sec}
-\added{The MCMC chain for all parameters are accessible from a DOI link \citep{colordata}.}
+\added{The MCMC chains for all parameters from this and subsequent sections are accessible from the SNfactory website\footnote{For the referee the parameters
+are available at \url{https://drive.google.com/open?id=1d52nxfF7eS3HblfbmT3fxgiZod_Z-Gjg}. Concurrent with publication the chain will be
+made available
+at \url{https://snfactory.lbl.gov/snf/data/index.html}.}.}
 In this subsection we concentrate on the results for $\vec{\gamma}^0$ and $\vec{\gamma}^1$.
@@
 \label{results2:sec}
-\added{The MCMC chain for all parameters are accessible from a DOI link \citep{colordata}.}
 The credible intervals of all Model~II global parameters are given in  \S\ref{m12results:sec}.
@@
 \subsection{Results}
-\added{The MCMC chain for all parameters are accessible from a DOI link \citep{colordata}.}
-
 \subsubsection{Analysis Method and Validation}
@@
 \begin{equation}
-M =
+Z =
 \begin{pmatrix}
-\tiny
+\scriptsize
 \begin{array}{rrrrrrr}
-2.76  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.06 \times 10^{ 1} & 2.67  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.05 \times 10^{ 1} & 2.74  \pm 0.06 \times 10^{ 1} & 2.71  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.06 \times 10^{ 1} \\
-7.04  \pm 0.16 \times 10^{ 0} & 7.08  \pm 0.16 \times 10^{ 0} & 7.02  \pm 0.16 \times 10^{ 0} & 3.86  \pm 0.19 \times 10^{ 0} & 7.01  \pm 0.16 \times 10^{ 0} & 6.79  \pm 0.21 \times 10^{ 0} & 7.06  \pm 0.16 \times 10^{ 0} \\
-1.98  \pm 0.04 \times 10^{ 1} & 2.03  \pm 0.05 \times 10^{ 1} & 2.05  \pm 0.05 \times 10^{ 1} & 2.03  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} \\
-9.92  \pm 0.18 \times 10^{-1} & 5.43  \pm 0.23 \times 10^{-1} & 9.86  \pm 0.19 \times 10^{-1} & 9.95  \pm 0.18 \times 10^{-1} & 9.86  \pm 0.19 \times 10^{-1} & 9.71  \pm 0.26 \times 10^{-1} & 9.92  \pm 0.19 \times 10^{-1} \\
-7.33  \pm 0.31 \times 10^{-2} & 7.32  \pm 0.32 \times 10^{-2} & 7.37  \pm 0.32 \times 10^{-2} & 7.32  \pm 0.32 \times 10^{-2} & 7.38  \pm 0.32 \times 10^{-2} & 7.36  \pm 0.33 \times 10^{-2} & 7.36  \pm 0.32 \times 10^{-2} \\
-3.82  \pm 0.42 \times 10^{-2} & 3.73  \pm 0.41 \times 10^{-2} & 3.88  \pm 0.43 \times 10^{-2} & 3.79  \pm 0.42 \times 10^{-2} & 3.88  \pm 0.44 \times 10^{-2} & 3.89  \pm 0.44 \times 10^{-2} & 3.88  \pm 0.44 \times 10^{-2} \\
-4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.97  \pm 1.10 \times 10^{-2}
+27.589  \pm 0.554 & 27.451  \pm 0.572 & 26.668  \pm 0.589 & 27.509  \pm 0.542 & 27.408  \pm 0.563 & 27.099  \pm 0.640 & 27.506  \pm 0.562 \\
+7.041  \pm 0.160 & 7.076  \pm 0.157 & 7.019  \pm 0.165 & 3.860  \pm 0.186 & 7.011  \pm 0.158 & 6.790  \pm 0.206 & 7.056  \pm 0.159 \\
+19.779  \pm 0.449 & 20.295  \pm 0.458 & 20.463  \pm 0.460 & 20.267  \pm 0.456 & 20.430  \pm 0.461 & 20.423  \pm 0.462 & 20.404  \pm 0.465 \\
+0.992  \pm 0.018 & 0.543  \pm 0.023 & 0.986  \pm 0.019 & 0.995  \pm 0.018 & 0.986  \pm 0.019 & 0.971  \pm 0.026 & 0.992  \pm 0.019 \\
+0.073  \pm 0.003 & 0.073  \pm 0.003 & 0.074  \pm 0.003 & 0.073  \pm 0.003 & 0.074  \pm 0.003 & 0.074  \pm 0.003 & 0.074  \pm 0.003 \\
+0.038  \pm 0.004 & 0.037  \pm 0.004 & 0.039  \pm 0.004 & 0.038  \pm 0.004 & 0.039  \pm 0.004 & 0.039  \pm 0.004 & 0.039  \pm 0.004 \\
+0.050  \pm 0.011 & 0.050  \pm 0.011 & 0.050  \pm 0.011 & 0.050  \pm 0.011 & 0.050  \pm 0.011 & 0.050  \pm 0.011 & 0.050  \pm 0.011 
 \\\end{array}
-\end{pmatrix}.
+\end{pmatrix},
 \label{ellipse:eqn}
 \end{equation}
-For indeces $i, j \in \{EW_{\mathrm{Ca}}, EW_{\mathrm{Si}}, \lambda_{\mathrm{Si}}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}\}$, $M_{ii}$ is the standard deviation of the parameter $i$ distribution, and for $i \ne j$ $M_{ij}$ is the standard deviation in parameter $i$
-if parameter $j$ were known perfectly.  For example, for $i= EW_{\mathrm{Si}}$ the standard deviation is 7.08 but when $j=x_1$
+where the associated units are [\AA, \AA, \AA, 1, mag, mag, mag]$\cdot$[\AA, \AA, \AA, 1, mag, mag, mag]$^{T}$.
+
+For indices $i, j \in \{EW_{\mathrm{Ca}}, EW_{\mathrm{Si}}, \lambda_{\mathrm{Si}}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}\}$, $M_{ii}$ is the standard deviation of the parameter $i$ distribution, and for $i \ne j$ $Z_{ij}$ is the standard deviation in parameter $i$
+if parameter $j$ were known perfectly.  For example, for $i=EW_{\mathrm{Si}}$ the standard deviation is 7.08\AA\ but when $j=x_1$
 is fixed its
-standard deviation drops to 3.86.  Therefore, an analysis that considers $x_1$ but not $EW_{\mathrm{Si}}$ would not account for
-$3.86\vec{\beta}=\{0.14 ,  0.09,  0.08,  0.07,  0.04 \}$ ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ magnitude dispersions
+standard deviation drops to 3.86\AA.  Therefore, an analysis that considers $x_1$ but not $EW_{\mathrm{Si}}$ would not account for
+3.86\AA$\vec{\beta}=\{0.14 ,  0.09,  0.08,  0.07,  0.04 \}$~mag ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ magnitude dispersions
 that are not intrinsically random.

### 2018-09-11 submit/fix.tex
slight modification to the iPTF blurb

@@
 This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 759194 - USNAC 
+\added{Based in part on observations obtained with the Samuel Oschin Telescope and the 60 inch Telescope at the Palomar Observatory as part of the Palomar Transient Factory project, a scientific collaboration between the California Institute of Technology, Columbia University, Las Cumbres Observatory, the Lawrence Berkeley National Laboratory, the National Energy Research Scientific Computing Center, the University of Oxford, and the Weizmann Institute of Science.}
 

### 2018-09-26 submit/fix.tex
reorder the tables
changes to table order and renaming of sne

@@
-\documentclass[trackchanges]{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
+\documentclass{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
@@
 epochs  $[-10, 35]$ days, at least one within $[-10, 7]$ days, at least one within $[7, 20]$ days,
-and at least one color (Anyone know what this means? See slide 3 of
-\url{https://snf-doc.lbl.gov/twiki/pub/Conf/VideoConf20160317/IDR_03-17-2016.pdf}) within $[-8, 10]$ days of peak $B$ brightness.
+and at least one color
+%(Anyone know what this means? See slide 3 of
+%\url{https://snf-doc.lbl.gov/twiki/pub/Conf/VideoConf20160317/IDR_03-17-2016.pdf}) 
+within $[-8, 10]$ days of peak $B$ brightness.
 Synthetic-photometric lightcurves derived from the spectra are fit to the SALT2~(v2.4)
@@
 \startdata
-SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.85 \pm   0.34$\\
-PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ & $  0.18 \pm   0.17$\\
+%SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.85 \pm   0.34$\\
+%PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ & $  0.18 \pm   0.17$\\
+%SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ & $ -1.78 \pm   0.18$\\
+%PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.72 \pm   0.13$\\
+%SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ & $  0.27 \pm   0.14$\\
+%PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.74 \pm   0.24$\\
+%PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -0.07 \pm   0.17$\\
+%PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.69 \pm   0.19$\\
+%SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ & $ -1.56 \pm   0.13$\\
+%PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ & $  0.03 \pm   0.21$\\
+%PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.00 \pm   0.34$\\
+%SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ & $ -1.28 \pm   0.16$\\
+%SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.15 \pm   0.16$\\
+%SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.10 \pm   0.11$\\
+%SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ & $ -2.45 \pm   0.28$\\
+%PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ & $  0.68 \pm   0.16$\\
+%PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ & $ -0.62 \pm   0.13$\\
+%SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ & $ -1.57 \pm   0.11$\\
+%PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.74 \pm   0.15$\\
+%SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ & $ -2.12 \pm   0.17$\\
+%PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ & $  0.37 \pm   0.13$\\
+%PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ & $  1.21 \pm   0.20$\\
+%SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ & $  0.37 \pm   0.12$\\
+%SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ & $  0.20 \pm   0.14$\\
+%PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ & $  1.34 \pm   0.17$\\
+%PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ & $ -1.09 \pm   0.16$\\
+%SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ & $  0.17 \pm   0.17$\\
+%LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ & $  0.05 \pm   0.15$\\
+%SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.70 \pm   0.19$\\
+%SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.08 \pm   0.16$\\
+%PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.63 \pm   0.16$\\
+%PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ & $ -0.68 \pm   0.10$\\
+%SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ & $ -0.03 \pm   0.10$\\
+%SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ & $  0.01 \pm   0.13$\\
+%LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ & $  1.07 \pm   0.19$\\
+%PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ & $  1.04 \pm   0.20$\\
+%PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.68 \pm   0.27$\\
+%PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ & $ -1.72 \pm   0.29$\\
+%SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.10 \pm   0.12$\\
+%PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.83 \pm   0.16$\\
+%SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ & $ -1.24 \pm   0.26$\\
+%PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ & $  0.60 \pm   0.15$\\
+%PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.43 \pm   0.14$\\
+%SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ & $ -1.67 \pm   0.20$\\
+%SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ & $  1.71 \pm   0.69$\\
+%SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.70 \pm   0.14$\\
+%PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ & $  0.65 \pm   0.16$\\
+%PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ & $ -0.28 \pm   0.17$\\
+%CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ & $  0.92 \pm   0.17$\\
+%SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ & $ -1.39 \pm   0.19$\\
+%SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.17 \pm   0.13$\\
+%SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ & $ -0.54 \pm   0.13$\\
+%PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ & $  1.39 \pm   0.18$\\
+%SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ & $  1.36 \pm   0.37$\\
+%SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ & $ -1.83 \pm   0.18$\\
+%SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ & $ -0.43 \pm   0.10$\\
+%PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.11 \pm   0.12$\\
+%PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ & $ -1.59 \pm   0.22$\\
+%SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ & $ -0.13 \pm   0.11$\\
+%SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ & $  0.84 \pm   0.18$\\
+%SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ & $ -2.26 \pm   0.40$\\
+%SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ & $  0.01 \pm   0.15$\\
+%SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ & $ -1.10 \pm   0.13$\\
+%SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ & $  0.81 \pm   0.19$\\
+%SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.27 \pm   0.21$\\
+%SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ & $ -2.09 \pm   0.25$\\
+%SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ & $  0.74 \pm   0.29$\\
+%SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ & $ -0.77 \pm   0.18$\\
+%PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ & $  0.53 \pm   0.16$\\
+%PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ & $  0.16 \pm   0.13$\\
+%SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ & $  1.50 \pm   0.30$\\
+%SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ & $  1.24 \pm   0.26$\\
+%SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ & $ -0.31 \pm   0.17$\\
+%CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ & $ -0.00 \pm   0.24$\\
+%SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ & $ -1.04 \pm   0.16$\\
+%SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ & $ -2.08 \pm   0.18$\\
+%PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.06 \pm   0.19$\\
+%SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ & $ -0.68 \pm   0.18$\\
+%SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ & $  0.71 \pm   0.21$\\
+%SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ & $  1.04 \pm   0.23$\\
+%SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ & $  0.43 \pm   0.20$\\
+%SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ & $  1.17 \pm   0.34$\\
+%SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ & $ -0.43 \pm   0.16$\\
+%SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ & $ -1.27 \pm   0.18$\\
+%CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ & $  0.76 \pm   0.19$\\
+%SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ & $  0.12 \pm   0.16$\\
+%SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  0.06 \pm   0.17$\\
+%SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ & $  0.52 \pm   0.18$\\
+%SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ & $  0.70 \pm   0.19$\\
+%SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.17 \pm   0.16$\\
+%PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ & $ -0.33 \pm   0.12$\\
+%SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ & $  0.98 \pm   0.18$\\
+%PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ & $  0.50 \pm   0.11$\\
+%SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ & $ -1.73 \pm   0.17$\\
+%SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ & $  0.62 \pm   0.21$\\
+%SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  2.14 \pm   0.42$\\
+%SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $  0.24 \pm   0.20$\\
+%CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ & $ -0.27 \pm   0.17$\\
+%SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.09$\\
+%SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ & $  0.35 \pm   0.19$\\
+%SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ & $  0.60 \pm   0.14$\\
+%SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ & $  0.27 \pm   0.27$\\
+%SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ & $  0.96 \pm   0.10$\\
+%SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ & $ -0.92 \pm   0.19$\\
+%SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.69 \pm   0.15$\\
+%SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ & $ -0.25 \pm   0.15$\\
+%SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.17 \pm   0.32$\\
+%SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ & $  0.88 \pm   0.18$\\
+%PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ & $ -1.14 \pm   0.26$\\
+%PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ & $ -1.17 \pm   0.13$\\
+%SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ & $  0.18 \pm   0.13$\\
+%SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.87 \pm   0.11$\\
+%SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ & $  0.57 \pm   0.34$\\
+%SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ & $ -1.05 \pm   0.12$\\
+%SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ & $ -0.72 \pm   0.10$\\
+%SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ & $  0.31 \pm   0.11$\\
+%SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.48 \pm   0.18$\\
+%SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ & $ -1.89 \pm   0.26$\\
+%SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ & $ -0.57 \pm   0.13$\\
+%SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ & $ -1.96 \pm   0.19$\\
+%SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ & $  1.72 \pm   0.44$\\
+%SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.01 \pm   0.12$\\
+%SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ & $  0.27 \pm   0.12$\\
+%PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.34 \pm   0.12$\\
+%SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ & $ -0.29 \pm   0.13$\\
+%SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ & $  0.68 \pm   0.17$\\
+%SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.00 \pm   0.21$\\
+%SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ & $ -0.11 \pm   0.17$\\
+%SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ & $  0.07 \pm   0.15$\\
+%SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ & $  0.69 \pm   0.62$\\
+%SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ & $  0.12 \pm   0.18$\\
+%SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ & $ -0.49 \pm   0.18$\\
+%SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ & $ -2.32 \pm   0.54$\\
+%PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ & $ -0.35 \pm   0.11$\\
+%SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ & $ -1.88 \pm   0.34$\\
+%PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ & $ -0.02 \pm   0.12$\\
+%SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ & $  1.85 \pm   0.59$\\
+%PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ & $ -1.30 \pm   0.12$\\
+%PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.87 \pm   0.18$\\
+%SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ & $ -1.52 \pm   0.14$\\
+%SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ & $  0.22 \pm   0.26$\\
+%SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ & $  0.34 \pm   0.29$\\
+%SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ & $  0.14 \pm   0.25$\\
+%SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ & $  0.20 \pm   0.24$\\
+%SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.87 \pm   0.31$\\
+%LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ & $  1.12 \pm   0.14$\\
+%LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.21$\\
+%SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ & $ -1.22 \pm   0.26$\\
+%SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ & $  0.35 \pm   0.12$\\
+%PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.21 \pm   0.37$\\
+%SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $ -0.10 \pm   0.17$\\
+%SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ & $ -0.53 \pm   0.18$\\
+%SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ & $  0.41 \pm   0.14$\\
+%SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ & $  0.29 \pm   0.17$\\
+%SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ & $  0.64 \pm   0.16$\\
+%SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.37 \pm   0.14$\\
+%SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ & $  0.56 \pm   0.23$\\
+%SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.97 \pm   0.21$\\
+%PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ & $ -0.48 \pm   0.12$\\
+%SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ & $ -1.82 \pm   0.25$\\
+%SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.85 \pm   0.23$\\
+%SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ & $ -1.37 \pm   0.11$\\
+%PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ & $  0.18 \pm   0.15$\\
+%SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ & $  1.02 \pm   0.13$\\
+%PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ & $ -0.35 \pm   0.11$\\
+%PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -1.98 \pm   0.20$\\
+%SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ & $  0.25 \pm   0.18$\\
+%SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.90 \pm   0.26$\\
+%SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.89 \pm   0.25$\\
+%SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ & $  0.03 \pm   0.21$\\
+%SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ & $  0.43 \pm   0.18$\\
+%SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ & $  0.42 \pm   0.18$\\
+%\\
+SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ & $  0.69 \pm   0.62$\\
+SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ & $  0.27 \pm   0.27$\\
+SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ & $  0.57 \pm   0.34$\\
+SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.17 \pm   0.32$\\
+SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ & $ -0.68 \pm   0.18$\\
+SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.69 \pm   0.15$\\
+SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ & $ -0.92 \pm   0.19$\\
+SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ & $ -1.22 \pm   0.26$\\
+SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ & $  0.29 \pm   0.17$\\
+SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ & $  0.07 \pm   0.15$\\
+SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.97 \pm   0.21$\\
+SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ & $  0.12 \pm   0.18$\\
+SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ & $  0.43 \pm   0.20$\\
+SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ & $  0.17 \pm   0.17$\\
+SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ & $  0.70 \pm   0.19$\\
+SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $  0.24 \pm   0.20$\\
+SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ & $  0.74 \pm   0.29$\\
+SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ & $ -1.67 \pm   0.20$\\
+SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ & $  0.25 \pm   0.18$\\
+SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ & $  1.72 \pm   0.44$\\
+SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ & $ -1.39 \pm   0.19$\\
+SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ & $  0.14 \pm   0.25$\\
+SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  2.14 \pm   0.42$\\
+SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.27 \pm   0.21$\\
+SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ & $  0.34 \pm   0.29$\\
+SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ & $ -1.28 \pm   0.16$\\
+SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ & $ -1.96 \pm   0.19$\\
+SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ & $ -0.54 \pm   0.13$\\
+SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ & $ -1.37 \pm   0.11$\\
+SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ & $  0.31 \pm   0.11$\\
+SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ & $  0.62 \pm   0.21$\\
+SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.17 \pm   0.13$\\
+SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ & $ -1.82 \pm   0.25$\\
+SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ & $  0.35 \pm   0.12$\\
+SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  0.06 \pm   0.17$\\
+SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ & $  0.42 \pm   0.18$\\
+SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ & $ -1.10 \pm   0.13$\\
+SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ & $  0.68 \pm   0.17$\\
+SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ & $  0.27 \pm   0.12$\\
+SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.08 \pm   0.16$\\
+SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ & $  0.88 \pm   0.18$\\
+SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ & $ -1.73 \pm   0.17$\\
+SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.10 \pm   0.12$\\
+SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ & $ -0.57 \pm   0.13$\\
+SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.15 \pm   0.16$\\
+SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ & $ -0.29 \pm   0.13$\\
+SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.85 \pm   0.23$\\
+SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ & $ -0.72 \pm   0.10$\\
+SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ & $ -0.43 \pm   0.10$\\
+SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ & $ -0.25 \pm   0.15$\\
+SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ & $  1.36 \pm   0.37$\\
+SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ & $ -0.53 \pm   0.18$\\
+SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.00 \pm   0.21$\\
+SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $ -0.10 \pm   0.17$\\
+SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.89 \pm   0.25$\\
+SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ & $  0.43 \pm   0.18$\\
+SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.90 \pm   0.26$\\
+SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ & $ -1.24 \pm   0.26$\\
+SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ & $ -1.57 \pm   0.11$\\
+SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ & $  1.24 \pm   0.26$\\
+SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ & $  0.20 \pm   0.14$\\
+SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ & $  1.02 \pm   0.13$\\
+SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ & $  0.81 \pm   0.19$\\
+SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ & $ -0.49 \pm   0.18$\\
+SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ & $  0.12 \pm   0.16$\\
+SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ & $  0.71 \pm   0.21$\\
+SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ & $ -2.12 \pm   0.17$\\
+SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ & $ -1.04 \pm   0.16$\\
+SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ & $  0.01 \pm   0.13$\\
+SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ & $  1.04 \pm   0.23$\\
+SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ & $  0.01 \pm   0.15$\\
+SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.70 \pm   0.14$\\
+SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ & $  0.18 \pm   0.13$\\
+SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ & $  0.60 \pm   0.14$\\
+SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ & $ -1.56 \pm   0.13$\\
+SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.37 \pm   0.14$\\
+SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ & $  0.64 \pm   0.16$\\
+SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.87 \pm   0.11$\\
 SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ & $ -1.78 \pm   0.18$\\
-PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.72 \pm   0.13$\\
-SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ & $  0.27 \pm   0.14$\\
-PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.74 \pm   0.24$\\
-PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -0.07 \pm   0.17$\\
-PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.69 \pm   0.19$\\
-SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ & $ -1.56 \pm   0.13$\\
-PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ & $  0.03 \pm   0.21$\\
-PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.00 \pm   0.34$\\
-SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ & $ -1.28 \pm   0.16$\\
-SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.15 \pm   0.16$\\
-SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.10 \pm   0.11$\\
-SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ & $ -2.45 \pm   0.28$\\
-PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ & $  0.68 \pm   0.16$\\
-PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ & $ -0.62 \pm   0.13$\\
-SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ & $ -1.57 \pm   0.11$\\
-PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.74 \pm   0.15$\\
-SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ & $ -2.12 \pm   0.17$\\
-PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ & $  0.37 \pm   0.13$\\
-PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ & $  1.21 \pm   0.20$\\
-SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ & $  0.37 \pm   0.12$\\
-SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ & $  0.20 \pm   0.14$\\
-PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ & $  1.34 \pm   0.17$\\
-PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ & $ -1.09 \pm   0.16$\\
-SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ & $  0.17 \pm   0.17$\\
-LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ & $  0.05 \pm   0.15$\\
 SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.70 \pm   0.19$\\
-SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.08 \pm   0.16$\\
-PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.63 \pm   0.16$\\
-PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ & $ -0.68 \pm   0.10$\\
-SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ & $ -0.03 \pm   0.10$\\
-SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ & $  0.01 \pm   0.13$\\
-LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ & $  1.07 \pm   0.19$\\
-PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ & $  1.04 \pm   0.20$\\
-PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.68 \pm   0.27$\\
-PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ & $ -1.72 \pm   0.29$\\
-SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.10 \pm   0.12$\\
-PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.83 \pm   0.16$\\
-SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ & $ -1.24 \pm   0.26$\\
-PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ & $  0.60 \pm   0.15$\\
-PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.43 \pm   0.14$\\
-SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ & $ -1.67 \pm   0.20$\\
-SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ & $  1.71 \pm   0.69$\\
-SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.70 \pm   0.14$\\
-PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ & $  0.65 \pm   0.16$\\
-PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ & $ -0.28 \pm   0.17$\\
-CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ & $  0.92 \pm   0.17$\\
-SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ & $ -1.39 \pm   0.19$\\
-SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.17 \pm   0.13$\\
-SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ & $ -0.54 \pm   0.13$\\
-PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ & $  1.39 \pm   0.18$\\
-SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ & $  1.36 \pm   0.37$\\
-SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ & $ -1.83 \pm   0.18$\\
-SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ & $ -0.43 \pm   0.10$\\
-PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.11 \pm   0.12$\\
-PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ & $ -1.59 \pm   0.22$\\
+SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ & $  0.56 \pm   0.23$\\
+SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ & $ -0.77 \pm   0.18$\\
+SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.17 \pm   0.16$\\
+SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ & $  0.03 \pm   0.21$\\
+SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ & $ -0.11 \pm   0.17$\\
+SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ & $  1.50 \pm   0.30$\\
+SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.09$\\
+SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ & $ -1.27 \pm   0.18$\\
 SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ & $ -0.13 \pm   0.11$\\
 SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ & $  0.84 \pm   0.18$\\
+SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ & $ -1.52 \pm   0.14$\\
+SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ & $  1.17 \pm   0.34$\\
+CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ & $  0.92 \pm   0.17$\\
+CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ & $ -0.27 \pm   0.17$\\
+CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ & $  0.76 \pm   0.19$\\
+CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ & $ -0.00 \pm   0.24$\\
+LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ & $  1.12 \pm   0.14$\\
+LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ & $  1.07 \pm   0.19$\\
+LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ & $  0.05 \pm   0.15$\\
+LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.21$\\
+PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.11 \pm   0.12$\\
+PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.72 \pm   0.13$\\
+PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.74 \pm   0.24$\\
+PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.68 \pm   0.27$\\
+PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ & $ -1.14 \pm   0.26$\\
+PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ & $  1.39 \pm   0.18$\\
+PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ & $  0.37 \pm   0.13$\\
+PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ & $ -0.68 \pm   0.10$\\
+PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.87 \pm   0.18$\\
+PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ & $ -0.62 \pm   0.13$\\
+PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ & $ -0.35 \pm   0.11$\\
+PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ & $ -1.09 \pm   0.16$\\
+PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.43 \pm   0.14$\\
+PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ & $  0.53 \pm   0.16$\\
+PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.63 \pm   0.16$\\
+PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ & $  0.16 \pm   0.13$\\
+PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ & $  0.03 \pm   0.21$\\
+PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ & $  0.18 \pm   0.17$\\
+PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ & $ -0.33 \pm   0.12$\\
+PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ & $  1.04 \pm   0.20$\\
+PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -0.07 \pm   0.17$\\
+PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ & $  0.18 \pm   0.15$\\
+PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.21 \pm   0.37$\\
+PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ & $  0.60 \pm   0.15$\\
+PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.83 \pm   0.16$\\
+PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.06 \pm   0.19$\\
+PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.00 \pm   0.34$\\
+PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -1.98 \pm   0.20$\\
+PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ & $  0.68 \pm   0.16$\\
+PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ & $  1.21 \pm   0.20$\\
+PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ & $  0.65 \pm   0.16$\\
+PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.74 \pm   0.15$\\
+PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.34 \pm   0.12$\\
+PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ & $ -0.48 \pm   0.12$\\
+PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ & $ -1.17 \pm   0.13$\\
+PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ & $  1.34 \pm   0.17$\\
+PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ & $ -1.30 \pm   0.12$\\
+PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ & $ -0.35 \pm   0.11$\\
+PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.69 \pm   0.19$\\
+PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ & $ -1.59 \pm   0.22$\\
+PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ & $ -0.28 \pm   0.17$\\
+PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ & $  0.50 \pm   0.11$\\
+PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ & $ -1.72 \pm   0.29$\\
+PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ & $ -0.02 \pm   0.12$\\
+SN2003bt & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ & $ -2.08 \pm   0.18$\\
+SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ & $ -0.31 \pm   0.17$\\
+SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.87 \pm   0.31$\\
+SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ & $  1.85 \pm   0.59$\\
+SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ & $  1.71 \pm   0.69$\\
+SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.48 \pm   0.18$\\
+SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ & $ -1.88 \pm   0.34$\\
+SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ & $ -2.32 \pm   0.54$\\
+SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ & $ -2.45 \pm   0.28$\\
+SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.85 \pm   0.34$\\
+SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ & $ -0.43 \pm   0.16$\\
+SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ & $  0.52 \pm   0.18$\\
+SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ & $ -1.89 \pm   0.26$\\
+SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ & $ -1.05 \pm   0.12$\\
+SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ & $ -0.03 \pm   0.10$\\
+SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ & $  0.27 \pm   0.14$\\
 SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ & $ -2.26 \pm   0.40$\\
-SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ & $  0.01 \pm   0.15$\\
-SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ & $ -1.10 \pm   0.13$\\
-SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ & $  0.81 \pm   0.19$\\
-SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.27 \pm   0.21$\\
-SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ & $ -2.09 \pm   0.25$\\
-SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ & $  0.74 \pm   0.29$\\
-SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ & $ -0.77 \pm   0.18$\\
-PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ & $  0.53 \pm   0.16$\\
-PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ & $  0.16 \pm   0.13$\\
-SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ & $  1.50 \pm   0.30$\\
-SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ & $  1.24 \pm   0.26$\\
-SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ & $ -0.31 \pm   0.17$\\
-CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ & $ -0.00 \pm   0.24$\\
-SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ & $ -1.04 \pm   0.16$\\
-SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ & $ -2.08 \pm   0.18$\\
-PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.06 \pm   0.19$\\
-SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ & $ -0.68 \pm   0.18$\\
-SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ & $  0.71 \pm   0.21$\\
-SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ & $  1.04 \pm   0.23$\\
-SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ & $  0.43 \pm   0.20$\\
-SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ & $  1.17 \pm   0.34$\\
-SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ & $ -0.43 \pm   0.16$\\
-SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ & $ -1.27 \pm   0.18$\\
-CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ & $  0.76 \pm   0.19$\\
-SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ & $  0.12 \pm   0.16$\\
-SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  0.06 \pm   0.17$\\
-SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ & $  0.52 \pm   0.18$\\
-SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ & $  0.70 \pm   0.19$\\
-SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.17 \pm   0.16$\\
-PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ & $ -0.33 \pm   0.12$\\
-SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ & $  0.98 \pm   0.18$\\
-PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ & $  0.50 \pm   0.11$\\
-SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ & $ -1.73 \pm   0.17$\\
-SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ & $  0.62 \pm   0.21$\\
-SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  2.14 \pm   0.42$\\
-SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $  0.24 \pm   0.20$\\
-CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ & $ -0.27 \pm   0.17$\\
-SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.09$\\
-SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ & $  0.35 \pm   0.19$\\
-SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ & $  0.60 \pm   0.14$\\
-SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ & $  0.27 \pm   0.27$\\
+SN2011bc & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.01 \pm   0.12$\\
+SN2011be & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ & $  0.20 \pm   0.24$\\
+SN2011ho & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ & $ -1.83 \pm   0.18$\\
+SN2011hr & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ & $  0.98 \pm   0.18$\\
+SN2011ia & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ & $  0.22 \pm   0.26$\\
+SN2012cg & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ & $  0.37 \pm   0.12$\\
 SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ & $  0.96 \pm   0.10$\\
-SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ & $ -0.92 \pm   0.19$\\
-SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.69 \pm   0.15$\\
-SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ & $ -0.25 \pm   0.15$\\
-SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.17 \pm   0.32$\\
-SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ & $  0.88 \pm   0.18$\\
-PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ & $ -1.14 \pm   0.26$\\
-PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ & $ -1.17 \pm   0.13$\\
-SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ & $  0.18 \pm   0.13$\\
-SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.87 \pm   0.11$\\
-SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ & $  0.57 \pm   0.34$\\
-SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ & $ -1.05 \pm   0.12$\\
-SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ & $ -0.72 \pm   0.10$\\
-SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ & $  0.31 \pm   0.11$\\
-SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.48 \pm   0.18$\\
-SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ & $ -1.89 \pm   0.26$\\
-SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ & $ -0.57 \pm   0.13$\\
-SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ & $ -1.96 \pm   0.19$\\
-SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ & $  1.72 \pm   0.44$\\
-SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.01 \pm   0.12$\\
-SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ & $  0.27 \pm   0.12$\\
-PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.34 \pm   0.12$\\
-SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ & $ -0.29 \pm   0.13$\\
-SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ & $  0.68 \pm   0.17$\\
-SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.00 \pm   0.21$\\
-SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ & $ -0.11 \pm   0.17$\\
-SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ & $  0.07 \pm   0.15$\\
-SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ & $  0.69 \pm   0.62$\\
-SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ & $  0.12 \pm   0.18$\\
-SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ & $ -0.49 \pm   0.18$\\
-SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ & $ -2.32 \pm   0.54$\\
-PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ & $ -0.35 \pm   0.11$\\
-SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ & $ -1.88 \pm   0.34$\\
-PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ & $ -0.02 \pm   0.12$\\
-SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ & $  1.85 \pm   0.59$\\
-PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ & $ -1.30 \pm   0.12$\\
-PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.87 \pm   0.18$\\
-SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ & $ -1.52 \pm   0.14$\\
-SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ & $  0.22 \pm   0.26$\\
-SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ & $  0.34 \pm   0.29$\\
-SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ & $  0.14 \pm   0.25$\\
-SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ & $  0.20 \pm   0.24$\\
-SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.87 \pm   0.31$\\
-LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ & $  1.12 \pm   0.14$\\
-LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.21$\\
-SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ & $ -1.22 \pm   0.26$\\
-SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ & $  0.35 \pm   0.12$\\
-PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.21 \pm   0.37$\\
-SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $ -0.10 \pm   0.17$\\
-SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ & $ -0.53 \pm   0.18$\\
-SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ & $  0.41 \pm   0.14$\\
-SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ & $  0.29 \pm   0.17$\\
-SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ & $  0.64 \pm   0.16$\\
-SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.37 \pm   0.14$\\
-SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ & $  0.56 \pm   0.23$\\
-SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.97 \pm   0.21$\\
-PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ & $ -0.48 \pm   0.12$\\
-SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ & $ -1.82 \pm   0.25$\\
-SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.85 \pm   0.23$\\
-SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ & $ -1.37 \pm   0.11$\\
-PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ & $  0.18 \pm   0.15$\\
-SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ & $  1.02 \pm   0.13$\\
-PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ & $ -0.35 \pm   0.11$\\
-PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -1.98 \pm   0.20$\\
-SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ & $  0.25 \pm   0.18$\\
-SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.90 \pm   0.26$\\
-SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.89 \pm   0.25$\\
-SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ & $  0.03 \pm   0.21$\\
-SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ & $  0.43 \pm   0.18$\\
-SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ & $  0.42 \pm   0.18$\\
+SN2013be & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ & $  0.35 \pm   0.19$\\
+SN2013bs & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ & $ -2.09 \pm   0.25$\\
+SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.10 \pm   0.11$\\
+TBD & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ & $  0.41 \pm   0.14$\\
 \enddata
@@
 \startdata
-SN2007bd & $113.3^{+5.4}_{-5.4}$ & $ 17.8^{+0.7}_{-0.7}$ & $ 6101^{+  3}_{-  3}$ & $ -1.02^{+  0.18}_{-  0.18}$ & $-0.071^{+0.027}_{-0.027}$  & $-0.050^{+0.011}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
-PTF10zdk & $149.7^{+1.2}_{-1.2}$ & $ 14.9^{+0.6}_{-0.6}$ & $ 6150^{+  3}_{-  3}$ & $  0.37^{+  0.14}_{-  0.13}$ & $-0.029^{+0.026}_{-0.025}$  & $0.062^{+0.012}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
+%SN2007bd & $113.3^{+5.4}_{-5.4}$ & $ 17.8^{+0.7}_{-0.7}$ & $ 6101^{+  3}_{-  3}$ & $ -1.02^{+  0.18}_{-  0.18}$ & $-0.071^{+0.027}_{-0.027}$  & $-0.050^{+0.011}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
+%PTF10zdk & $149.7^{+1.2}_{-1.2}$ & $ 14.9^{+0.6}_{-0.6}$ & $ 6150^{+  3}_{-  3}$ & $  0.37^{+  0.14}_{-  0.13}$ & $-0.029^{+0.026}_{-0.025}$  & $0.062^{+0.012}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
+%SNF20080815-017 & $ 90.9^{+14.3}_{-14.5}$ & $ 19.6^{+2.4}_{-2.3}$ & $ 6131^{+  6}_{-  6}$ & $ -1.96^{+  0.16}_{-  0.16}$ & $0.041^{+0.070}_{-0.064}$  & $-0.008^{+0.025}_{-0.026}$ & $-0.011^{+0.028}_{-0.022}$ & $-0.011^{+0.028}_{-0.022}$\\
+%PTF09dnl & $130.0^{+0.8}_{-0.9}$ & $  9.1^{+0.7}_{-0.7}$ & $ 6092^{+  3}_{-  3}$ & $  0.59^{+  0.10}_{-  0.10}$ & $-0.061^{+0.021}_{-0.021}$  & $0.014^{+0.009}_{-0.009}$ & $0.000^{+0.011}_{-0.011}$ & $0.000^{+0.011}_{-0.011}$\\
+%SN2010ex & $114.5^{+0.9}_{-0.9}$ & $  8.4^{+0.4}_{-0.4}$ & $ 6129^{+  6}_{-  6}$ & $  0.17^{+  0.12}_{-  0.11}$ & $0.266^{+0.026}_{-0.026}$  & $-0.042^{+0.008}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+%PTF09dnp & $ 66.9^{+4.5}_{-4.6}$ & $ 17.5^{+0.7}_{-0.7}$ & $ 6098^{+  5}_{-  4}$ & $ -0.53^{+  0.17}_{-  0.17}$ & $-0.249^{+0.026}_{-0.026}$  & $-0.008^{+0.020}_{-0.021}$ & $-0.044^{+0.006}_{-0.006}$ & $-0.044^{+0.006}_{-0.006}$\\
+%PTF11bnx & $150.7^{+3.0}_{-2.9}$ & $ 14.6^{+1.0}_{-1.0}$ & $ 6143^{+  5}_{-  5}$ & $  0.07^{+  0.14}_{-  0.14}$ & $0.043^{+0.029}_{-0.029}$  & $0.049^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
+%PTF12jqh & $151.8^{+1.4}_{-1.5}$ & $  7.9^{+0.6}_{-0.7}$ & $ 6118^{+ 10}_{- 10}$ & $  0.73^{+  0.14}_{-  0.14}$ & $0.069^{+0.028}_{-0.028}$  & $-0.056^{+0.010}_{-0.010}$ & $0.009^{+0.014}_{-0.015}$ & $0.009^{+0.014}_{-0.015}$\\
+%SNF20080802-006 & $108.7^{+5.6}_{-5.8}$ & $ 19.1^{+1.6}_{-1.6}$ & $ 6122^{+  5}_{-  5}$ & $ -1.61^{+  0.12}_{-  0.12}$ & $-0.042^{+0.059}_{-0.055}$  & $-0.001^{+0.016}_{-0.016}$ & $0.033^{+0.020}_{-0.020}$ & $0.033^{+0.020}_{-0.020}$\\
+%PTF10xyt & $120.2^{+6.3}_{-6.4}$ & $ 21.5^{+3.2}_{-3.1}$ & $ 6102^{+  4}_{-  4}$ & $  0.18^{+  0.20}_{-  0.20}$ & $0.241^{+0.049}_{-0.049}$  & $0.070^{+0.026}_{-0.028}$ & $0.014^{+0.029}_{-0.027}$ & $0.014^{+0.029}_{-0.027}$\\
+%PTF11qmo & $101.7^{+1.1}_{-1.1}$ & $  7.8^{+0.7}_{-0.7}$ & $ 6151^{+  7}_{-  8}$ & $  0.41^{+  0.18}_{-  0.18}$ & $-0.078^{+0.031}_{-0.028}$  & $-0.058^{+0.010}_{-0.010}$ & $0.004^{+0.014}_{-0.015}$ & $0.004^{+0.014}_{-0.015}$\\
+%SNF20070331-025 & $118.7^{+6.9}_{-7.0}$ & $ 15.4^{+2.0}_{-2.0}$ & $ 6121^{+ 10}_{- 10}$ & $ -1.22^{+  0.15}_{-  0.15}$ & $0.190^{+0.037}_{-0.037}$  & $-0.015^{+0.020}_{-0.020}$ & $0.001^{+0.023}_{-0.022}$ & $0.001^{+0.023}_{-0.022}$\\
+%SNF20070818-001 & $160.6^{+6.7}_{-6.8}$ & $ 16.4^{+1.5}_{-1.5}$ & $ 6113^{+  5}_{-  5}$ & $  0.14^{+  0.14}_{-  0.14}$ & $-0.178^{+0.021}_{-0.020}$  & $0.005^{+0.014}_{-0.014}$ & $0.014^{+0.016}_{-0.015}$ & $0.014^{+0.016}_{-0.015}$\\
+%SNBOSS38 & $ 57.1^{+0.4}_{-0.4}$ & $ 17.8^{+0.3}_{-0.3}$ & $ 6127^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $0.018^{+0.038}_{-0.039}$  & $0.017^{+0.021}_{-0.023}$ & $-0.002^{+0.019}_{-0.020}$ & $-0.002^{+0.019}_{-0.020}$\\
+%SN2006ob & $ 75.9^{+12.1}_{-12.4}$ & $ 26.8^{+1.3}_{-1.4}$ & $ 6113^{+  5}_{-  5}$ & $ -2.26^{+  0.21}_{-  0.21}$ & $0.039^{+0.035}_{-0.035}$  & $-0.051^{+0.019}_{-0.017}$ & $0.084^{+0.021}_{-0.021}$ & $0.084^{+0.021}_{-0.021}$\\
+%PTF12eer & $169.4^{+8.9}_{-8.8}$ & $ 12.2^{+1.8}_{-1.8}$ & $ 6148^{+ 10}_{- 10}$ & $  0.64^{+  0.14}_{-  0.15}$ & $-0.053^{+0.028}_{-0.027}$  & $0.039^{+0.018}_{-0.019}$ & $-0.029^{+0.017}_{-0.012}$ & $-0.029^{+0.017}_{-0.012}$\\
+%PTF10ops & $ 38.0^{+9.2}_{-9.2}$ & $ 21.9^{+4.6}_{-4.6}$ & $ 6140^{+  6}_{-  5}$ & $ -0.58^{+  0.12}_{-  0.12}$ & $-0.091^{+0.221}_{-0.154}$  & $0.190^{+0.040}_{-0.041}$ & $0.181^{+0.038}_{-0.036}$ & $0.181^{+0.038}_{-0.036}$\\
+%SNF20080514-002 & $ 83.1^{+0.7}_{-0.7}$ & $ 19.2^{+0.5}_{-0.5}$ & $ 6131^{+  3}_{-  3}$ & $ -1.55^{+  0.09}_{-  0.09}$ & $0.174^{+0.019}_{-0.019}$  & $-0.074^{+0.007}_{-0.006}$ & $0.006^{+0.011}_{-0.012}$ & $0.006^{+0.011}_{-0.012}$\\
+%PTF12evo & $129.1^{+2.6}_{-2.7}$ & $  9.9^{+1.1}_{-1.1}$ & $ 6157^{+  4}_{-  4}$ & $  0.81^{+  0.13}_{-  0.12}$ & $0.024^{+0.027}_{-0.027}$  & $0.004^{+0.011}_{-0.011}$ & $-0.034^{+0.012}_{-0.010}$ & $-0.034^{+0.012}_{-0.010}$\\
+%SNF20080614-010 & $118.9^{+4.9}_{-4.8}$ & $ 28.9^{+1.2}_{-1.2}$ & $ 6129^{+  3}_{-  3}$ & $ -1.81^{+  0.15}_{-  0.15}$ & $-0.114^{+0.046}_{-0.042}$  & $-0.068^{+0.012}_{-0.009}$ & $0.049^{+0.019}_{-0.019}$ & $0.049^{+0.019}_{-0.019}$\\
+%PTF10icb & $104.8^{+0.9}_{-0.9}$ & $ 12.6^{+0.3}_{-0.3}$ & $ 6138^{+  2}_{-  2}$ & $  0.23^{+  0.10}_{-  0.10}$ & $0.410^{+0.024}_{-0.025}$  & $0.046^{+0.006}_{-0.006}$ & $-0.019^{+0.010}_{-0.010}$ & $-0.019^{+0.010}_{-0.010}$\\
+%PTF12efn & $145.5^{+3.3}_{-3.2}$ & $  5.4^{+1.4}_{-1.5}$ & $ 6115^{+  3}_{-  3}$ & $  1.04^{+  0.16}_{-  0.16}$ & $0.177^{+0.030}_{-0.029}$  & $-0.058^{+0.014}_{-0.012}$ & $0.051^{+0.017}_{-0.017}$ & $0.051^{+0.017}_{-0.017}$\\
+%SNNGC4424 & $109.0^{+0.3}_{-0.3}$ & $  8.6^{+0.1}_{-0.1}$ & $ 6138^{+  2}_{-  2}$ & $  0.44^{+  0.09}_{-  0.09}$ & $0.600^{+0.022}_{-0.023}$  & $0.078^{+0.007}_{-0.006}$ & $-0.025^{+0.011}_{-0.011}$ & $-0.025^{+0.011}_{-0.011}$\\
+%SNF20080516-022 & $ 99.1^{+2.2}_{-2.1}$ & $ 15.3^{+0.9}_{-0.9}$ & $ 6159^{+  3}_{-  3}$ & $  0.48^{+  0.12}_{-  0.11}$ & $0.001^{+0.026}_{-0.026}$  & $-0.064^{+0.010}_{-0.009}$ & $-0.025^{+0.014}_{-0.013}$ & $-0.025^{+0.014}_{-0.013}$\\
+%PTF12hwb & $139.4^{+25.9}_{-23.8}$ & $ -0.9^{+4.4}_{-4.3}$ & $ 6090^{+ 14}_{- 14}$ & $  1.34^{+  0.17}_{-  0.17}$ & $0.471^{+0.042}_{-0.044}$  & $0.151^{+0.037}_{-0.043}$ & $0.004^{+0.040}_{-0.032}$ & $0.004^{+0.040}_{-0.032}$\\
+%PTF10qyz & $108.1^{+2.1}_{-2.1}$ & $ 21.0^{+0.8}_{-0.8}$ & $ 6117^{+  5}_{-  5}$ & $ -1.67^{+  0.13}_{-  0.13}$ & $0.099^{+0.133}_{-0.095}$  & $-0.067^{+0.014}_{-0.010}$ & $-0.038^{+0.012}_{-0.008}$ & $-0.038^{+0.012}_{-0.008}$\\
+%SNF20060907-000 & $ 87.8^{+7.5}_{-7.3}$ & $ 15.9^{+0.9}_{-0.9}$ & $ 6150^{+  4}_{-  4}$ & $  0.16^{+  0.17}_{-  0.17}$ & $0.037^{+0.033}_{-0.033}$  & $-0.079^{+0.005}_{-0.005}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+%LSQ12fxd & $122.8^{+1.6}_{-1.7}$ & $ 11.7^{+0.8}_{-0.7}$ & $ 6119^{+  4}_{-  4}$ & $  0.16^{+  0.12}_{-  0.12}$ & $-0.154^{+0.044}_{-0.032}$  & $-0.052^{+0.008}_{-0.008}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
+%SNF20080821-000 & $104.8^{+2.2}_{-2.2}$ & $  8.8^{+1.2}_{-1.2}$ & $ 6121^{+  4}_{-  4}$ & $  0.77^{+  0.15}_{-  0.14}$ & $-0.104^{+0.023}_{-0.023}$  & $0.025^{+0.011}_{-0.011}$ & $-0.006^{+0.013}_{-0.013}$ & $-0.006^{+0.013}_{-0.013}$\\
+%SNF20070802-000 & $157.9^{+3.3}_{-3.3}$ & $ 16.0^{+1.4}_{-1.4}$ & $ 6103^{+  5}_{-  5}$ & $  0.07^{+  0.13}_{-  0.13}$ & $-0.074^{+0.028}_{-0.028}$  & $0.005^{+0.014}_{-0.014}$ & $0.005^{+0.016}_{-0.016}$ & $0.005^{+0.016}_{-0.016}$\\
+%PTF10wnm & $105.5^{+2.3}_{-2.3}$ & $  6.8^{+0.9}_{-0.9}$ & $ 6125^{+  3}_{-  3}$ & $  0.73^{+  0.12}_{-  0.12}$ & $0.123^{+0.022}_{-0.021}$  & $-0.014^{+0.009}_{-0.009}$ & $0.015^{+0.012}_{-0.012}$ & $0.015^{+0.012}_{-0.012}$\\
+%PTF10mwb & $116.2^{+1.2}_{-1.2}$ & $ 21.1^{+0.7}_{-0.7}$ & $ 6139^{+  2}_{-  2}$ & $ -0.48^{+  0.09}_{-  0.09}$ & $-0.000^{+0.071}_{-0.070}$  & $-0.036^{+0.008}_{-0.008}$ & $-0.011^{+0.011}_{-0.011}$ & $-0.011^{+0.011}_{-0.011}$\\
+%SN2010dt & $133.3^{+8.4}_{-8.6}$ & $ 16.0^{+0.6}_{-0.6}$ & $ 6141^{+  5}_{-  5}$ & $ -0.02^{+  0.09}_{-  0.09}$ & $-0.046^{+0.024}_{-0.024}$  & $-0.063^{+0.010}_{-0.009}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
+%SNF20080623-001 & $149.2^{+1.4}_{-1.4}$ & $ 14.8^{+0.6}_{-0.6}$ & $ 6131^{+  3}_{-  3}$ & $ -0.07^{+  0.11}_{-  0.10}$ & $0.072^{+0.025}_{-0.025}$  & $-0.054^{+0.010}_{-0.009}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
+%LSQ12fhe & $ 42.9^{+1.2}_{-1.2}$ & $  2.3^{+1.9}_{-1.9}$ & $ 6108^{+  4}_{-  4}$ & $  1.01^{+  0.17}_{-  0.17}$ & $-0.183^{+0.032}_{-0.033}$  & $0.067^{+0.017}_{-0.018}$ & $-0.017^{+0.018}_{-0.016}$ & $-0.017^{+0.018}_{-0.016}$\\
+%PTF11bju & $ 31.3^{+4.3}_{-4.2}$ & $  3.3^{+2.0}_{-2.0}$ & $ 6138^{+  5}_{-  5}$ & $  1.02^{+  0.17}_{-  0.18}$ & $0.073^{+0.036}_{-0.036}$  & $0.077^{+0.019}_{-0.019}$ & $-0.014^{+0.020}_{-0.018}$ & $-0.014^{+0.020}_{-0.018}$\\
+%PTF09fox & $118.5^{+2.7}_{-2.7}$ & $  9.8^{+0.9}_{-0.8}$ & $ 6117^{+  3}_{-  3}$ & $  0.52^{+  0.16}_{-  0.15}$ & $0.027^{+0.039}_{-0.039}$  & $-0.047^{+0.009}_{-0.009}$ & $-0.043^{+0.007}_{-0.006}$ & $-0.043^{+0.007}_{-0.006}$\\
+%PTF13ayw & $103.8^{+2.4}_{-2.4}$ & $ 23.1^{+1.8}_{-1.9}$ & $ 6116^{+  6}_{-  6}$ & $ -1.67^{+  0.23}_{-  0.24}$ & $0.068^{+0.041}_{-0.041}$  & $-0.069^{+0.014}_{-0.009}$ & $0.101^{+0.019}_{-0.020}$ & $0.101^{+0.019}_{-0.020}$\\
+%SNF20070810-004 & $127.0^{+1.8}_{-1.8}$ & $ 20.1^{+0.9}_{-0.9}$ & $ 6117^{+  7}_{-  7}$ & $ -0.01^{+  0.11}_{-  0.11}$ & $-0.044^{+0.026}_{-0.025}$  & $-0.068^{+0.011}_{-0.009}$ & $-0.033^{+0.012}_{-0.010}$ & $-0.033^{+0.012}_{-0.010}$\\
+%PTF11mty & $110.5^{+2.2}_{-2.2}$ & $ 11.3^{+1.0}_{-1.1}$ & $ 6140^{+  5}_{-  5}$ & $  1.03^{+  0.13}_{-  0.13}$ & $0.062^{+0.025}_{-0.024}$  & $-0.072^{+0.009}_{-0.007}$ & $0.024^{+0.013}_{-0.014}$ & $0.024^{+0.013}_{-0.014}$\\
+%SNF20080512-010 & $ 96.0^{+3.4}_{-3.4}$ & $ 21.9^{+1.3}_{-1.3}$ & $ 6128^{+  5}_{-  5}$ & $ -1.64^{+  0.18}_{-  0.18}$ & $-0.032^{+0.072}_{-0.061}$  & $-0.051^{+0.013}_{-0.012}$ & $0.018^{+0.016}_{-0.016}$ & $0.018^{+0.016}_{-0.016}$\\
+%PTF11mkx & $ 34.8^{+3.5}_{-3.5}$ & $  5.5^{+1.3}_{-1.3}$ & $ 6169^{+  5}_{-  5}$ & $  0.53^{+  0.14}_{-  0.14}$ & $0.022^{+0.135}_{-0.080}$  & $0.102^{+0.017}_{-0.016}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+%PTF10tce & $135.8^{+1.1}_{-1.1}$ & $ 10.6^{+1.2}_{-1.2}$ & $ 6090^{+  4}_{-  4}$ & $  0.38^{+  0.12}_{-  0.12}$ & $0.041^{+0.028}_{-0.027}$  & $-0.005^{+0.013}_{-0.014}$ & $-0.019^{+0.015}_{-0.015}$ & $-0.019^{+0.015}_{-0.015}$\\
+%SNF20061020-000 & $ 90.3^{+13.4}_{-13.3}$ & $ 23.9^{+0.9}_{-0.9}$ & $ 6120^{+  4}_{-  5}$ & $ -1.75^{+  0.17}_{-  0.17}$ & $-0.096^{+0.039}_{-0.034}$  & $0.000^{+0.016}_{-0.016}$ & $0.006^{+0.022}_{-0.020}$ & $0.006^{+0.022}_{-0.020}$\\
+%SN2005ir & $115.7^{+2.8}_{-2.7}$ & $  8.7^{+4.6}_{-4.8}$ & $ 6069^{+  5}_{-  5}$ & $  1.64^{+  0.49}_{-  0.48}$ & $0.112^{+0.042}_{-0.043}$  & $-0.022^{+0.036}_{-0.033}$ & $0.067^{+0.037}_{-0.037}$ & $0.067^{+0.037}_{-0.037}$\\
+%SNF20080717-000 & $ 92.7^{+2.6}_{-2.6}$ & $ 12.4^{+1.7}_{-1.7}$ & $ 6105^{+  3}_{-  3}$ & $  0.87^{+  0.13}_{-  0.12}$ & $0.115^{+0.034}_{-0.033}$  & $0.126^{+0.018}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$\\
+%PTF12ena & $101.0^{+1.6}_{-1.6}$ & $  8.2^{+0.9}_{-0.9}$ & $ 6130^{+  3}_{-  3}$ & $  0.76^{+  0.13}_{-  0.13}$ & $-0.039^{+0.028}_{-0.028}$  & $0.289^{+0.011}_{-0.012}$ & $-0.038^{+0.010}_{-0.008}$ & $-0.038^{+0.010}_{-0.008}$\\
+%PTF13anh & $167.2^{+1.8}_{-1.8}$ & $ 21.6^{+1.0}_{-1.0}$ & $ 6174^{+  3}_{-  4}$ & $ -0.38^{+  0.14}_{-  0.14}$ & $0.092^{+0.108}_{-0.067}$  & $-0.032^{+0.020}_{-0.019}$ & $-0.034^{+0.014}_{-0.010}$ & $-0.034^{+0.014}_{-0.010}$\\
+%CSS110918\_01 & $110.4^{+1.0}_{-1.0}$ & $  5.0^{+0.9}_{-0.9}$ & $ 6101^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.077^{+0.187}_{-0.094}$  & $-0.078^{+0.006}_{-0.005}$ & $-0.028^{+0.013}_{-0.012}$ & $-0.028^{+0.013}_{-0.012}$\\
+%SNF20061024-000 & $ 98.9^{+15.7}_{-16.7}$ & $ 29.1^{+1.4}_{-1.4}$ & $ 6127^{+  5}_{-  5}$ & $ -1.51^{+  0.18}_{-  0.18}$ & $0.045^{+0.062}_{-0.059}$  & $-0.049^{+0.021}_{-0.019}$ & $0.003^{+0.031}_{-0.028}$ & $0.003^{+0.031}_{-0.028}$\\
+%SNF20070506-006 & $ 94.3^{+1.3}_{-1.2}$ & $  6.4^{+0.6}_{-0.5}$ & $ 6152^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $-0.075^{+0.027}_{-0.026}$  & $-0.029^{+0.009}_{-0.009}$ & $0.006^{+0.013}_{-0.013}$ & $0.006^{+0.013}_{-0.013}$\\
+%SNF20070403-001 & $107.8^{+5.0}_{-5.1}$ & $ 17.1^{+1.4}_{-1.4}$ & $ 6123^{+  4}_{-  4}$ & $ -0.60^{+  0.12}_{-  0.12}$ & $0.007^{+0.029}_{-0.028}$  & $-0.036^{+0.014}_{-0.014}$ & $0.020^{+0.017}_{-0.017}$ & $0.020^{+0.017}_{-0.017}$\\
+%PTF10hmv & $109.8^{+1.3}_{-1.4}$ & $  8.5^{+0.7}_{-0.6}$ & $ 6143^{+  3}_{-  3}$ & $  1.15^{+  0.13}_{-  0.12}$ & $0.284^{+0.024}_{-0.023}$  & $0.106^{+0.009}_{-0.009}$ & $-0.010^{+0.012}_{-0.012}$ & $-0.010^{+0.012}_{-0.012}$\\
+%SNF20071015-000 & $104.8^{+3.1}_{-3.1}$ & $  6.5^{+1.1}_{-1.1}$ & $ 6125^{+  7}_{-  7}$ & $  0.90^{+  0.28}_{-  0.29}$ & $0.116^{+0.040}_{-0.040}$  & $0.293^{+0.016}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$\\
+%SNhunt89 & $ 88.6^{+2.7}_{-2.7}$ & $ 29.8^{+1.7}_{-1.7}$ & $ 6109^{+  7}_{-  7}$ & $ -2.02^{+  0.16}_{-  0.16}$ & $0.202^{+0.049}_{-0.047}$  & $0.030^{+0.018}_{-0.019}$ & $0.032^{+0.027}_{-0.026}$ & $0.032^{+0.027}_{-0.026}$\\
+%SNF20070902-021 & $109.0^{+3.3}_{-3.3}$ & $ 16.8^{+0.9}_{-0.9}$ & $ 6131^{+  5}_{-  5}$ & $ -0.46^{+  0.09}_{-  0.09}$ & $-0.082^{+0.027}_{-0.026}$  & $-0.023^{+0.010}_{-0.010}$ & $-0.028^{+0.014}_{-0.012}$ & $-0.028^{+0.014}_{-0.012}$\\
+%PTF09dlc & $143.8^{+2.1}_{-2.1}$ & $  9.7^{+0.8}_{-0.8}$ & $ 6143^{+  3}_{-  3}$ & $  0.01^{+  0.10}_{-  0.10}$ & $0.008^{+0.027}_{-0.026}$  & $-0.054^{+0.012}_{-0.012}$ & $-0.017^{+0.014}_{-0.015}$ & $-0.017^{+0.014}_{-0.015}$\\
+%PTF13ajv & $149.9^{+8.1}_{-8.2}$ & $ 22.0^{+2.7}_{-3.0}$ & $ 6107^{+ 20}_{- 20}$ & $ -1.64^{+  0.20}_{-  0.21}$ & $0.263^{+0.046}_{-0.045}$  & $-0.062^{+0.021}_{-0.014}$ & $-0.005^{+0.023}_{-0.022}$ & $-0.005^{+0.023}_{-0.022}$\\
+%SNF20080919-000 & $115.6^{+2.7}_{-2.7}$ & $  8.8^{+0.9}_{-0.8}$ & $ 6144^{+  5}_{-  5}$ & $ -0.24^{+  0.10}_{-  0.10}$ & $-0.043^{+0.027}_{-0.026}$  & $0.165^{+0.013}_{-0.012}$ & $-0.035^{+0.013}_{-0.010}$ & $-0.035^{+0.013}_{-0.010}$\\
+%SNF20080919-001 & $ 85.0^{+1.1}_{-1.1}$ & $  6.1^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  1.05^{+  0.12}_{-  0.12}$ & $-0.183^{+0.020}_{-0.019}$  & $0.001^{+0.008}_{-0.008}$ & $0.006^{+0.012}_{-0.012}$ & $0.006^{+0.012}_{-0.012}$\\
+%SN2010kg & $ 99.4^{+17.2}_{-17.5}$ & $ 21.8^{+0.7}_{-0.7}$ & $ 6077^{+  5}_{-  5}$ & $ -1.87^{+  0.24}_{-  0.25}$ & $-0.073^{+0.030}_{-0.029}$  & $0.035^{+0.021}_{-0.020}$ & $0.034^{+0.020}_{-0.021}$ & $0.034^{+0.020}_{-0.021}$\\
+%SNF20080714-008 & $155.6^{+11.0}_{-10.8}$ & $ 16.6^{+1.9}_{-1.8}$ & $ 6099^{+  6}_{-  6}$ & $ -0.07^{+  0.14}_{-  0.14}$ & $-0.141^{+0.024}_{-0.022}$  & $0.082^{+0.018}_{-0.020}$ & $-0.029^{+0.017}_{-0.013}$ & $-0.029^{+0.017}_{-0.013}$\\
+%SNF20070714-007 & $132.6^{+5.5}_{-5.5}$ & $ 33.5^{+4.3}_{-4.2}$ & $ 6145^{+  4}_{-  4}$ & $ -1.09^{+  0.13}_{-  0.13}$ & $-0.094^{+0.046}_{-0.047}$  & $0.118^{+0.035}_{-0.038}$ & $0.117^{+0.036}_{-0.032}$ & $0.117^{+0.036}_{-0.032}$\\
+%SNF20080522-011 & $122.1^{+1.7}_{-1.7}$ & $  8.3^{+0.5}_{-0.5}$ & $ 6125^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.124^{+0.023}_{-0.023}$  & $-0.045^{+0.008}_{-0.008}$ & $-0.031^{+0.011}_{-0.010}$ & $-0.031^{+0.011}_{-0.010}$\\
+%SNF20061111-002 & $117.1^{+8.6}_{-8.8}$ & $ 19.8^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  0.07^{+  0.17}_{-  0.17}$ & $0.056^{+0.032}_{-0.032}$  & $-0.062^{+0.013}_{-0.011}$ & $0.026^{+0.017}_{-0.017}$ & $0.026^{+0.017}_{-0.017}$\\
+%SNNGC6343 & $ 86.9^{+1.5}_{-1.4}$ & $ 21.2^{+0.7}_{-0.7}$ & $ 6136^{+  3}_{-  3}$ & $ -1.49^{+  0.16}_{-  0.16}$ & $0.055^{+0.029}_{-0.030}$  & $0.036^{+0.013}_{-0.012}$ & $0.020^{+0.016}_{-0.014}$ & $0.020^{+0.016}_{-0.014}$\\
+%SNF20061011-005 & $120.5^{+1.1}_{-1.1}$ & $  9.2^{+0.3}_{-0.3}$ & $ 6132^{+  4}_{-  4}$ & $  0.66^{+  0.22}_{-  0.21}$ & $-0.091^{+0.043}_{-0.041}$  & $-0.073^{+0.008}_{-0.007}$ & $0.003^{+0.021}_{-0.021}$ & $0.003^{+0.021}_{-0.021}$\\
+%SNF20080825-010 & $ 96.4^{+10.2}_{-10.2}$ & $ 19.2^{+0.6}_{-0.6}$ & $ 6116^{+  4}_{-  4}$ & $ -0.76^{+  0.13}_{-  0.13}$ & $-0.192^{+0.020}_{-0.020}$  & $-0.045^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
+%PTF10ufj & $141.4^{+3.3}_{-3.3}$ & $ 12.0^{+1.1}_{-1.0}$ & $ 6131^{+  6}_{-  5}$ & $  0.56^{+  0.13}_{-  0.13}$ & $-0.043^{+0.106}_{-0.068}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
+%PTF10wof & $130.5^{+2.6}_{-2.7}$ & $ 16.5^{+0.9}_{-0.9}$ & $ 6102^{+  2}_{-  2}$ & $  0.06^{+  0.11}_{-  0.11}$ & $0.096^{+0.023}_{-0.023}$  & $-0.009^{+0.011}_{-0.011}$ & $-0.013^{+0.013}_{-0.012}$ & $-0.013^{+0.013}_{-0.012}$\\
+%SNF20080918-000 & $146.6^{+3.5}_{-3.5}$ & $  5.6^{+2.1}_{-2.0}$ & $ 6110^{+  5}_{-  5}$ & $  1.28^{+  0.23}_{-  0.23}$ & $0.112^{+0.038}_{-0.037}$  & $0.073^{+0.019}_{-0.019}$ & $-0.004^{+0.023}_{-0.022}$ & $-0.004^{+0.023}_{-0.022}$\\
+%SNF20080516-000 & $117.6^{+2.1}_{-2.1}$ & $  8.2^{+1.2}_{-1.1}$ & $ 6135^{+  3}_{-  3}$ & $  0.96^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.028}$  & $-0.054^{+0.011}_{-0.010}$ & $0.004^{+0.015}_{-0.015}$ & $0.004^{+0.015}_{-0.015}$\\
+%SN2005cf & $158.9^{+0.7}_{-0.7}$ & $ 15.2^{+0.8}_{-0.7}$ & $ 6140^{+  3}_{-  3}$ & $ -0.19^{+  0.13}_{-  0.13}$ & $-0.122^{+0.028}_{-0.027}$  & $-0.077^{+0.007}_{-0.005}$ & $0.002^{+0.014}_{-0.015}$ & $0.002^{+0.014}_{-0.015}$\\
+%CSS130502\_01 & $ 87.3^{+8.0}_{-8.7}$ & $ 15.4^{+0.5}_{-0.5}$ & $ 6128^{+  3}_{-  3}$ & $ -0.15^{+  0.20}_{-  0.20}$ & $0.121^{+0.032}_{-0.032}$  & $-0.069^{+0.011}_{-0.009}$ & $-0.017^{+0.015}_{-0.015}$ & $-0.017^{+0.015}_{-0.015}$\\
+%SNF20080620-000 & $125.3^{+9.5}_{-9.7}$ & $ 20.6^{+0.6}_{-0.6}$ & $ 6133^{+  3}_{-  3}$ & $ -0.97^{+  0.14}_{-  0.14}$ & $-0.007^{+0.029}_{-0.028}$  & $0.001^{+0.012}_{-0.012}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
+%SNPGC51271 & $ 64.0^{+12.0}_{-13.2}$ & $ 21.4^{+0.7}_{-0.7}$ & $ 6121^{+  2}_{-  2}$ & $ -1.85^{+  0.16}_{-  0.17}$ & $0.125^{+0.034}_{-0.034}$  & $-0.057^{+0.017}_{-0.014}$ & $0.011^{+0.018}_{-0.019}$ & $0.011^{+0.018}_{-0.019}$\\
+%PTF11pdk & $127.7^{+2.6}_{-2.7}$ & $ 16.1^{+1.2}_{-1.2}$ & $ 6154^{+  5}_{-  5}$ & $  0.16^{+  0.16}_{-  0.17}$ & $-0.027^{+0.035}_{-0.035}$  & $-0.070^{+0.010}_{-0.008}$ & $-0.033^{+0.015}_{-0.011}$ & $-0.033^{+0.015}_{-0.011}$\\
+%SNF20060511-014 & $102.9^{+2.8}_{-2.8}$ & $ 17.1^{+1.0}_{-1.0}$ & $ 6144^{+  8}_{-  7}$ & $ -0.50^{+  0.15}_{-  0.15}$ & $-0.042^{+0.047}_{-0.037}$  & $-0.008^{+0.011}_{-0.010}$ & $-0.041^{+0.009}_{-0.007}$ & $-0.041^{+0.009}_{-0.007}$\\
+%SNF20080612-003 & $120.0^{+1.1}_{-1.1}$ & $  7.5^{+0.6}_{-0.6}$ & $ 6122^{+  3}_{-  3}$ & $  0.96^{+  0.15}_{-  0.15}$ & $-0.221^{+0.018}_{-0.017}$  & $-0.015^{+0.007}_{-0.007}$ & $-0.001^{+0.013}_{-0.014}$ & $-0.001^{+0.013}_{-0.014}$\\
+%SNF20080626-002 & $130.0^{+1.0}_{-1.0}$ & $  5.8^{+2.1}_{-2.0}$ & $ 6111^{+  3}_{-  3}$ & $  1.03^{+  0.19}_{-  0.19}$ & $-0.043^{+0.026}_{-0.025}$  & $-0.009^{+0.015}_{-0.016}$ & $-0.022^{+0.017}_{-0.015}$ & $-0.022^{+0.017}_{-0.015}$\\
+%SNF20060621-015 & $111.8^{+1.3}_{-1.3}$ & $  9.9^{+0.7}_{-0.7}$ & $ 6144^{+  3}_{-  3}$ & $  0.52^{+  0.14}_{-  0.14}$ & $-0.015^{+0.026}_{-0.027}$  & $-0.067^{+0.008}_{-0.008}$ & $-0.020^{+0.013}_{-0.013}$ & $-0.020^{+0.013}_{-0.013}$\\
+%SNF20080920-000 & $135.1^{+1.4}_{-1.4}$ & $  5.3^{+1.5}_{-1.5}$ & $ 6085^{+  3}_{-  3}$ & $  1.08^{+  0.23}_{-  0.23}$ & $-0.002^{+0.038}_{-0.037}$  & $-0.020^{+0.017}_{-0.017}$ & $-0.012^{+0.020}_{-0.019}$ & $-0.012^{+0.020}_{-0.019}$\\
+%SN2007cq & $ 63.7^{+3.9}_{-3.9}$ & $ 11.6^{+0.8}_{-0.8}$ & $ 6138^{+  3}_{-  3}$ & $  0.05^{+  0.13}_{-  0.13}$ & $-0.111^{+0.029}_{-0.027}$  & $0.008^{+0.011}_{-0.011}$ & $-0.015^{+0.015}_{-0.015}$ & $-0.015^{+0.015}_{-0.015}$\\
+%SNF20080918-004 & $ 91.9^{+6.6}_{-6.6}$ & $ 21.2^{+0.9}_{-0.9}$ & $ 6141^{+  4}_{-  4}$ & $ -1.37^{+  0.15}_{-  0.15}$ & $0.035^{+0.142}_{-0.087}$  & $-0.021^{+0.014}_{-0.013}$ & $-0.012^{+0.019}_{-0.018}$ & $-0.012^{+0.019}_{-0.018}$\\
+%CSS120424\_01 & $138.5^{+2.1}_{-2.1}$ & $ 11.5^{+0.6}_{-0.6}$ & $ 6138^{+  3}_{-  3}$ & $  0.58^{+  0.14}_{-  0.14}$ & $-0.010^{+0.028}_{-0.028}$  & $-0.061^{+0.009}_{-0.009}$ & $-0.024^{+0.013}_{-0.012}$ & $-0.024^{+0.013}_{-0.012}$\\
+%SNF20080610-000 & $119.5^{+8.6}_{-8.8}$ & $ 17.0^{+1.4}_{-1.4}$ & $ 6131^{+  6}_{-  6}$ & $  0.16^{+  0.14}_{-  0.14}$ & $0.013^{+0.068}_{-0.068}$  & $-0.019^{+0.014}_{-0.015}$ & $-0.027^{+0.017}_{-0.013}$ & $-0.027^{+0.017}_{-0.013}$\\
+%SNF20070701-005 & $101.6^{+2.6}_{-2.6}$ & $ 13.6^{+0.9}_{-1.0}$ & $ 6155^{+  5}_{-  5}$ & $  0.39^{+  0.14}_{-  0.14}$ & $-0.187^{+0.021}_{-0.021}$  & $-0.012^{+0.011}_{-0.011}$ & $0.037^{+0.015}_{-0.015}$ & $0.037^{+0.015}_{-0.015}$\\
+%SN2007kk & $128.6^{+1.4}_{-1.4}$ & $ 11.0^{+0.9}_{-0.9}$ & $ 6099^{+  4}_{-  4}$ & $  0.59^{+  0.14}_{-  0.14}$ & $-0.087^{+0.029}_{-0.029}$  & $-0.048^{+0.012}_{-0.012}$ & $-0.035^{+0.012}_{-0.010}$ & $-0.035^{+0.012}_{-0.010}$\\
+%SNF20060908-004 & $114.4^{+1.2}_{-1.2}$ & $ 12.4^{+0.6}_{-0.6}$ & $ 6136^{+  3}_{-  3}$ & $  0.63^{+  0.15}_{-  0.15}$ & $-0.099^{+0.138}_{-0.081}$  & $-0.068^{+0.009}_{-0.008}$ & $0.021^{+0.017}_{-0.017}$ & $0.021^{+0.017}_{-0.017}$\\
+%SNF20080909-030 & $ 93.8^{+1.0}_{-0.9}$ & $  7.7^{+0.4}_{-0.4}$ & $ 6171^{+  3}_{-  3}$ & $  0.99^{+  0.13}_{-  0.13}$ & $0.030^{+0.030}_{-0.030}$  & $0.008^{+0.013}_{-0.012}$ & $0.008^{+0.015}_{-0.014}$ & $0.008^{+0.015}_{-0.014}$\\
+%PTF11bgv & $ 78.3^{+3.1}_{-3.1}$ & $ 12.7^{+0.6}_{-0.6}$ & $ 6146^{+  3}_{-  3}$ & $ -0.27^{+  0.11}_{-  0.10}$ & $0.057^{+0.028}_{-0.028}$  & $0.081^{+0.010}_{-0.010}$ & $0.006^{+0.015}_{-0.015}$ & $0.006^{+0.015}_{-0.015}$\\
+%SNNGC2691 & $ 55.7^{+14.4}_{-14.5}$ & $  4.5^{+0.2}_{-0.2}$ & $ 6138^{+  8}_{-  8}$ & $  0.82^{+  0.16}_{-  0.16}$ & $-0.031^{+0.039}_{-0.038}$  & $0.069^{+0.018}_{-0.019}$ & $0.041^{+0.020}_{-0.020}$ & $0.041^{+0.020}_{-0.020}$\\
+%PTF13asv & $ 75.4^{+1.1}_{-1.1}$ & $  2.4^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  0.66^{+  0.10}_{-  0.10}$ & $-0.018^{+0.184}_{-0.105}$  & $-0.068^{+0.012}_{-0.009}$ & $0.015^{+0.015}_{-0.015}$ & $0.015^{+0.015}_{-0.015}$\\
+%SNF20070806-026 & $102.2^{+8.4}_{-9.0}$ & $ 25.3^{+0.7}_{-0.7}$ & $ 6112^{+  7}_{-  7}$ & $ -1.93^{+  0.14}_{-  0.14}$ & $0.010^{+0.032}_{-0.033}$  & $-0.071^{+0.011}_{-0.008}$ & $0.015^{+0.017}_{-0.017}$ & $0.015^{+0.017}_{-0.017}$\\
+%SNF20070427-001 & $ 80.7^{+2.3}_{-2.3}$ & $  6.5^{+0.8}_{-0.8}$ & $ 6143^{+  5}_{-  5}$ & $  0.82^{+  0.17}_{-  0.17}$ & $-0.009^{+0.031}_{-0.031}$  & $-0.066^{+0.011}_{-0.009}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
+%SNF20061108-004 & $128.2^{+5.4}_{-5.4}$ & $  6.8^{+2.1}_{-2.1}$ & $ 6110^{+  6}_{-  6}$ & $  2.36^{+  0.27}_{-  0.27}$ & $-0.089^{+0.038}_{-0.036}$  & $-0.025^{+0.021}_{-0.023}$ & $-0.005^{+0.024}_{-0.022}$ & $-0.005^{+0.024}_{-0.022}$\\
+%SNF20060912-000 & $106.9^{+1.7}_{-1.7}$ & $ 19.8^{+1.5}_{-1.5}$ & $ 6158^{+  7}_{-  7}$ & $  0.06^{+  0.17}_{-  0.17}$ & $-0.177^{+0.032}_{-0.033}$  & $0.034^{+0.018}_{-0.019}$ & $0.080^{+0.021}_{-0.020}$ & $0.080^{+0.021}_{-0.020}$\\
+%CSS110918\_02 & $109.1^{+8.1}_{-8.1}$ & $ 15.0^{+0.6}_{-0.6}$ & $ 6137^{+  3}_{-  3}$ & $ -0.26^{+  0.13}_{-  0.13}$ & $-0.052^{+0.027}_{-0.027}$  & $-0.039^{+0.010}_{-0.010}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
+%SNF20080918-002 & $ 96.6^{+2.8}_{-2.7}$ & $ 13.3^{+1.2}_{-1.2}$ & $ 6143^{+  6}_{-  6}$ & $ -0.47^{+  0.08}_{-  0.08}$ & $0.021^{+0.034}_{-0.035}$  & $-0.056^{+0.014}_{-0.013}$ & $-0.005^{+0.020}_{-0.021}$ & $-0.005^{+0.020}_{-0.021}$\\
+%SNIC3573 & $103.0^{+1.8}_{-1.7}$ & $ 12.1^{+0.9}_{-0.9}$ & $ 6141^{+  5}_{-  5}$ & $  0.39^{+  0.16}_{-  0.16}$ & $-0.109^{+0.026}_{-0.024}$  & $0.015^{+0.009}_{-0.010}$ & $-0.025^{+0.014}_{-0.012}$ & $-0.025^{+0.014}_{-0.012}$\\
+%SNF20080725-004 & $133.8^{+2.1}_{-2.1}$ & $  6.7^{+0.9}_{-0.9}$ & $ 6131^{+  6}_{-  5}$ & $  0.59^{+  0.13}_{-  0.13}$ & $0.078^{+0.032}_{-0.032}$  & $0.025^{+0.012}_{-0.011}$ & $0.016^{+0.015}_{-0.014}$ & $0.016^{+0.015}_{-0.014}$\\
+%SNF20050728-006 & $127.7^{+2.5}_{-2.4}$ & $ 15.3^{+1.2}_{-1.2}$ & $ 6124^{+  6}_{-  6}$ & $  0.11^{+  0.19}_{-  0.19}$ & $-0.088^{+0.034}_{-0.032}$  & $0.064^{+0.011}_{-0.012}$ & $0.012^{+0.017}_{-0.017}$ & $0.012^{+0.017}_{-0.017}$\\
+%SN2012fr & $134.2^{+0.5}_{-0.5}$ & $  7.4^{+0.2}_{-0.2}$ & $ 6101^{+  1}_{-  1}$ & $  0.88^{+  0.08}_{-  0.09}$ & $-0.248^{+0.021}_{-0.021}$  & $-0.077^{+0.005}_{-0.005}$ & $0.044^{+0.012}_{-0.011}$ & $0.044^{+0.012}_{-0.011}$\\
+%SNF20060512-002 & $100.4^{+2.7}_{-2.8}$ & $ 13.5^{+1.1}_{-1.1}$ & $ 6106^{+  7}_{-  7}$ & $ -0.87^{+  0.15}_{-  0.16}$ & $-0.186^{+0.030}_{-0.028}$  & $0.018^{+0.012}_{-0.012}$ & $0.056^{+0.017}_{-0.016}$ & $0.056^{+0.017}_{-0.016}$\\
+%SNF20060512-001 & $ 88.2^{+1.2}_{-1.2}$ & $  5.5^{+0.4}_{-0.4}$ & $ 6169^{+  3}_{-  3}$ & $  0.87^{+  0.11}_{-  0.11}$ & $-0.025^{+0.025}_{-0.025}$  & $0.050^{+0.011}_{-0.011}$ & $-0.010^{+0.011}_{-0.012}$ & $-0.010^{+0.011}_{-0.012}$\\
+%SNF20071003-016 & $126.5^{+4.5}_{-4.4}$ & $ 16.7^{+1.5}_{-1.5}$ & $ 6123^{+ 10}_{- 10}$ & $ -0.30^{+  0.14}_{-  0.14}$ & $0.058^{+0.032}_{-0.032}$  & $0.068^{+0.013}_{-0.014}$ & $-0.030^{+0.016}_{-0.012}$ & $-0.030^{+0.016}_{-0.012}$\\
+%SNF20050821-007 & $141.8^{+2.6}_{-2.6}$ & $  7.8^{+0.9}_{-0.9}$ & $ 6140^{+  9}_{-  8}$ & $  0.34^{+  0.20}_{-  0.19}$ & $-0.024^{+0.034}_{-0.033}$  & $-0.030^{+0.014}_{-0.013}$ & $-0.012^{+0.017}_{-0.017}$ & $-0.012^{+0.017}_{-0.017}$\\
+%SNF20070803-005 & $ 45.4^{+14.0}_{-13.8}$ & $  0.8^{+0.6}_{-0.6}$ & $ 6138^{+ 22}_{- 22}$ & $  0.81^{+  0.15}_{-  0.15}$ & $-0.137^{+0.031}_{-0.031}$  & $0.043^{+0.019}_{-0.019}$ & $-0.005^{+0.021}_{-0.021}$ & $-0.005^{+0.021}_{-0.021}$\\
+%PTF09foz & $127.2^{+1.9}_{-1.9}$ & $ 22.1^{+1.1}_{-1.1}$ & $ 6135^{+  4}_{-  4}$ & $ -0.92^{+  0.16}_{-  0.16}$ & $-0.141^{+0.019}_{-0.018}$  & $-0.042^{+0.009}_{-0.010}$ & $0.031^{+0.013}_{-0.012}$ & $0.031^{+0.013}_{-0.012}$\\
+%PTF12grk & $158.1^{+8.3}_{-8.4}$ & $ 22.1^{+1.2}_{-1.2}$ & $ 6089^{+  8}_{-  8}$ & $ -1.02^{+  0.12}_{-  0.12}$ & $-0.117^{+0.027}_{-0.026}$  & $-0.025^{+0.016}_{-0.017}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+%SNF20080720-001 & $138.3^{+3.9}_{-4.0}$ & $ 14.0^{+1.5}_{-1.5}$ & $ 6107^{+  3}_{-  3}$ & $  0.19^{+  0.12}_{-  0.12}$ & $-0.176^{+0.028}_{-0.028}$  & $0.325^{+0.018}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$\\
+%SNF20080810-001 & $ 98.8^{+12.2}_{-12.3}$ & $ 21.7^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.93^{+  0.10}_{-  0.11}$ & $-0.058^{+0.024}_{-0.024}$  & $-0.023^{+0.016}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$\\
+%SNF20050729-002 & $110.4^{+2.3}_{-2.2}$ & $ 10.7^{+1.5}_{-1.4}$ & $ 6141^{+  6}_{-  6}$ & $ -0.22^{+  0.21}_{-  0.22}$ & $0.052^{+0.102}_{-0.075}$  & $-0.039^{+0.015}_{-0.014}$ & $-0.039^{+0.011}_{-0.008}$ & $-0.039^{+0.011}_{-0.008}$\\
+%SN2008ec & $ 97.7^{+10.6}_{-10.6}$ & $ 23.0^{+0.4}_{-0.4}$ & $ 6125^{+  3}_{-  3}$ & $ -1.09^{+  0.10}_{-  0.10}$ & $-0.076^{+0.025}_{-0.026}$  & $0.064^{+0.012}_{-0.012}$ & $0.017^{+0.015}_{-0.015}$ & $0.017^{+0.015}_{-0.015}$\\
+%SNF20070902-018 & $108.6^{+9.5}_{-9.7}$ & $ 18.1^{+1.7}_{-1.7}$ & $ 6119^{+  7}_{-  7}$ & $ -0.81^{+  0.10}_{-  0.09}$ & $0.032^{+0.030}_{-0.030}$  & $0.023^{+0.016}_{-0.017}$ & $-0.035^{+0.014}_{-0.010}$ & $-0.035^{+0.014}_{-0.010}$\\
+%SNF20070424-003 & $123.6^{+3.6}_{-3.6}$ & $ 14.2^{+1.2}_{-1.1}$ & $ 6134^{+  6}_{-  6}$ & $  0.30^{+  0.10}_{-  0.10}$ & $0.008^{+0.023}_{-0.023}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+%SN2006cj & $101.4^{+1.3}_{-1.3}$ & $  5.5^{+0.8}_{-0.8}$ & $ 6128^{+  3}_{-  3}$ & $  0.86^{+  0.13}_{-  0.13}$ & $0.028^{+0.025}_{-0.025}$  & $0.006^{+0.008}_{-0.009}$ & $-0.017^{+0.013}_{-0.013}$ & $-0.017^{+0.013}_{-0.013}$\\
+%SN2007nq & $ 91.2^{+9.1}_{-9.0}$ & $ 23.3^{+1.0}_{-1.0}$ & $ 6109^{+  5}_{-  5}$ & $ -1.90^{+  0.20}_{-  0.20}$ & $-0.075^{+0.038}_{-0.035}$  & $-0.022^{+0.015}_{-0.015}$ & $0.031^{+0.021}_{-0.020}$ & $0.031^{+0.021}_{-0.020}$\\
+%SNF20070817-003 & $ 94.5^{+2.4}_{-2.4}$ & $ 18.1^{+1.1}_{-1.1}$ & $ 6115^{+  6}_{-  6}$ & $ -0.61^{+  0.12}_{-  0.12}$ & $0.050^{+0.031}_{-0.032}$  & $-0.031^{+0.012}_{-0.012}$ & $-0.024^{+0.015}_{-0.014}$ & $-0.024^{+0.015}_{-0.014}$\\
+%SNF20070403-000 & $ 62.8^{+6.1}_{-6.2}$ & $ 27.6^{+1.6}_{-1.6}$ & $ 6154^{+  7}_{-  7}$ & $ -1.88^{+  0.17}_{-  0.17}$ & $0.147^{+0.040}_{-0.041}$  & $0.081^{+0.021}_{-0.021}$ & $0.041^{+0.025}_{-0.023}$ & $0.041^{+0.025}_{-0.023}$\\
+%SNF20061022-005 & $ 63.4^{+3.6}_{-3.8}$ & $  3.9^{+1.4}_{-1.4}$ & $ 6147^{+  7}_{-  7}$ & $  2.03^{+  0.25}_{-  0.25}$ & $0.056^{+0.038}_{-0.038}$  & $0.041^{+0.018}_{-0.020}$ & $-0.000^{+0.022}_{-0.021}$ & $-0.000^{+0.022}_{-0.021}$\\
+%SNNGC4076 & $127.1^{+2.4}_{-2.4}$ & $ 15.7^{+1.1}_{-1.1}$ & $ 6152^{+  4}_{-  4}$ & $  0.04^{+  0.10}_{-  0.10}$ & $-0.004^{+0.030}_{-0.029}$  & $0.049^{+0.013}_{-0.013}$ & $0.045^{+0.016}_{-0.015}$ & $0.045^{+0.016}_{-0.015}$\\
+%SNF20070727-016 & $ 78.3^{+2.4}_{-2.5}$ & $  4.6^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  0.16^{+  0.11}_{-  0.10}$ & $-0.097^{+0.043}_{-0.036}$  & $-0.037^{+0.011}_{-0.011}$ & $-0.025^{+0.015}_{-0.014}$ & $-0.025^{+0.015}_{-0.014}$\\
+%PTF12fuu & $105.4^{+3.0}_{-3.0}$ & $  6.5^{+1.0}_{-1.0}$ & $ 6124^{+  5}_{-  5}$ & $  0.37^{+  0.11}_{-  0.11}$ & $0.178^{+0.026}_{-0.026}$  & $-0.057^{+0.010}_{-0.010}$ & $-0.026^{+0.014}_{-0.013}$ & $-0.026^{+0.014}_{-0.013}$\\
+%SNF20070820-000 & $107.1^{+3.4}_{-3.4}$ & $ 18.7^{+1.2}_{-1.2}$ & $ 6133^{+ 13}_{- 13}$ & $ -0.28^{+  0.12}_{-  0.12}$ & $-0.054^{+0.031}_{-0.030}$  & $0.051^{+0.012}_{-0.013}$ & $-0.015^{+0.018}_{-0.016}$ & $-0.015^{+0.018}_{-0.016}$\\
+%SNF20070725-001 & $108.3^{+1.9}_{-1.9}$ & $  9.5^{+1.0}_{-1.1}$ & $ 6139^{+  6}_{-  6}$ & $  0.61^{+  0.15}_{-  0.15}$ & $0.058^{+0.033}_{-0.033}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.018^{+0.016}_{-0.015}$ & $-0.018^{+0.016}_{-0.015}$\\
+%SNF20071108-021 & $ 98.7^{+2.7}_{-2.7}$ & $  6.0^{+0.8}_{-0.8}$ & $ 6165^{+  5}_{-  5}$ & $  1.15^{+  0.16}_{-  0.15}$ & $-0.045^{+0.028}_{-0.028}$  & $-0.028^{+0.012}_{-0.012}$ & $0.024^{+0.015}_{-0.014}$ & $0.024^{+0.015}_{-0.014}$\\
+%SNF20080914-001 & $126.4^{+1.2}_{-1.2}$ & $ 16.3^{+1.0}_{-1.0}$ & $ 6159^{+  3}_{-  3}$ & $  0.10^{+  0.14}_{-  0.14}$ & $-0.144^{+0.026}_{-0.024}$  & $0.094^{+0.012}_{-0.012}$ & $0.022^{+0.016}_{-0.015}$ & $0.022^{+0.016}_{-0.015}$\\
+%SNF20060609-002 & $ 86.3^{+3.5}_{-3.5}$ & $  8.1^{+1.2}_{-1.1}$ & $ 6132^{+  4}_{-  4}$ & $  0.18^{+  0.12}_{-  0.13}$ & $-0.069^{+0.033}_{-0.032}$  & $0.192^{+0.014}_{-0.014}$ & $-0.008^{+0.018}_{-0.017}$ & $-0.008^{+0.018}_{-0.017}$\\
+%SNF20050624-000 & $119.9^{+5.1}_{-5.1}$ & $  7.9^{+2.4}_{-2.6}$ & $ 6126^{+  5}_{-  5}$ & $  0.47^{+  0.29}_{-  0.29}$ & $-0.171^{+0.026}_{-0.024}$  & $-0.051^{+0.019}_{-0.017}$ & $0.022^{+0.019}_{-0.021}$ & $0.022^{+0.019}_{-0.021}$\\
+%SNF20060618-023 & $ 73.3^{+4.7}_{-4.7}$ & $  5.3^{+1.6}_{-1.5}$ & $ 6140^{+ 18}_{- 18}$ & $  0.18^{+  0.16}_{-  0.16}$ & $-0.229^{+0.039}_{-0.038}$  & $0.059^{+0.020}_{-0.020}$ & $0.092^{+0.023}_{-0.022}$ & $0.092^{+0.023}_{-0.022}$\\
+%SNF20080531-000 & $133.2^{+1.5}_{-1.5}$ & $ 17.2^{+0.8}_{-0.8}$ & $ 6113^{+  5}_{-  5}$ & $ -0.63^{+  0.13}_{-  0.13}$ & $0.002^{+0.024}_{-0.024}$  & $-0.040^{+0.009}_{-0.009}$ & $-0.009^{+0.012}_{-0.013}$ & $-0.009^{+0.012}_{-0.013}$\\
+%SN2006do & $106.3^{+2.1}_{-2.1}$ & $ 26.8^{+1.3}_{-1.2}$ & $ 6101^{+  2}_{-  2}$ & $ -1.95^{+  0.34}_{-  0.34}$ & $-0.077^{+0.031}_{-0.030}$  & $-0.038^{+0.012}_{-0.013}$ & $0.035^{+0.018}_{-0.017}$ & $0.035^{+0.018}_{-0.017}$\\
+%PTF12ikt & $110.3^{+1.5}_{-1.6}$ & $ 14.0^{+0.7}_{-0.7}$ & $ 6141^{+  4}_{-  4}$ & $ -0.40^{+  0.10}_{-  0.10}$ & $-0.023^{+0.025}_{-0.025}$  & $-0.034^{+0.009}_{-0.008}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
+%SN2006dm & $ 99.6^{+1.6}_{-1.6}$ & $ 29.8^{+0.7}_{-0.7}$ & $ 6118^{+  3}_{-  3}$ & $ -2.35^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.029}$  & $-0.047^{+0.011}_{-0.011}$ & $0.047^{+0.017}_{-0.016}$ & $0.047^{+0.017}_{-0.016}$\\
+%PTF13azs & $140.6^{+4.8}_{-4.8}$ & $ 15.2^{+1.3}_{-1.3}$ & $ 6124^{+ 10}_{- 10}$ & $ -0.12^{+  0.11}_{-  0.11}$ & $0.148^{+0.029}_{-0.029}$  & $0.195^{+0.012}_{-0.013}$ & $-0.037^{+0.012}_{-0.009}$ & $-0.037^{+0.012}_{-0.009}$\\
+%SN2005hj & $ 80.4^{+2.4}_{-2.4}$ & $  4.4^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  2.58^{+  0.24}_{-  0.24}$ & $0.076^{+0.039}_{-0.037}$  & $0.009^{+0.018}_{-0.020}$ & $0.066^{+0.022}_{-0.022}$ & $0.066^{+0.022}_{-0.022}$\\
+%PTF12iiq & $149.1^{+2.1}_{-2.2}$ & $ 24.8^{+0.8}_{-0.7}$ & $ 6048^{+  7}_{-  7}$ & $ -0.83^{+  0.10}_{-  0.11}$ & $0.005^{+0.033}_{-0.033}$  & $-0.005^{+0.019}_{-0.020}$ & $-0.034^{+0.017}_{-0.010}$ & $-0.034^{+0.017}_{-0.010}$\\
+%PTF10ndc & $124.1^{+2.4}_{-2.4}$ & $  6.7^{+1.0}_{-1.0}$ & $ 6119^{+  3}_{-  3}$ & $  0.86^{+  0.14}_{-  0.14}$ & $0.007^{+0.026}_{-0.025}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.023^{+0.014}_{-0.013}$ & $-0.023^{+0.014}_{-0.013}$\\
+%SNF20080919-002 & $100.4^{+6.7}_{-6.6}$ & $ 26.3^{+1.7}_{-1.7}$ & $ 6133^{+  8}_{-  8}$ & $ -1.54^{+  0.13}_{-  0.13}$ & $0.340^{+0.043}_{-0.044}$  & $-0.058^{+0.017}_{-0.014}$ & $0.114^{+0.020}_{-0.021}$ & $0.114^{+0.020}_{-0.021}$\\
+%SNPGC027923 & $ 85.4^{+0.6}_{-0.6}$ & $  5.8^{+0.3}_{-0.3}$ & $ 6130^{+  4}_{-  4}$ & $  0.45^{+  0.17}_{-  0.17}$ & $0.078^{+0.032}_{-0.031}$  & $-0.077^{+0.006}_{-0.005}$ & $-0.026^{+0.015}_{-0.013}$ & $-0.026^{+0.015}_{-0.013}$\\
+%SNF20070330-024 & $118.3^{+2.1}_{-2.1}$ & $  5.5^{+1.8}_{-1.8}$ & $ 6101^{+  3}_{-  3}$ & $  0.48^{+  0.19}_{-  0.21}$ & $-0.166^{+0.025}_{-0.024}$  & $-0.040^{+0.014}_{-0.014}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
+%SNF20061030-010 & $131.6^{+2.2}_{-2.2}$ & $ 16.9^{+1.1}_{-1.1}$ & $ 6116^{+  4}_{-  4}$ & $ -0.10^{+  0.20}_{-  0.20}$ & $0.103^{+0.041}_{-0.041}$  & $0.049^{+0.012}_{-0.012}$ & $0.019^{+0.021}_{-0.021}$ & $0.019^{+0.021}_{-0.021}$\\
+%SNhunt46 & $ 93.8^{+2.0}_{-2.0}$ & $ 11.2^{+0.6}_{-0.6}$ & $ 6133^{+  4}_{-  4}$ & $  0.22^{+  0.17}_{-  0.17}$ & $0.150^{+0.032}_{-0.032}$  & $-0.062^{+0.010}_{-0.010}$ & $0.035^{+0.016}_{-0.015}$ & $0.035^{+0.016}_{-0.015}$\\
+%SN2005hc & $127.2^{+2.4}_{-2.5}$ & $  9.7^{+0.7}_{-0.7}$ & $ 6122^{+  3}_{-  3}$ & $  0.47^{+  0.16}_{-  0.15}$ & $0.137^{+0.025}_{-0.025}$  & $-0.062^{+0.008}_{-0.008}$ & $0.001^{+0.012}_{-0.012}$ & $0.001^{+0.012}_{-0.012}$\\
+%LSQ12dbr & $106.9^{+0.6}_{-0.6}$ & $  6.4^{+0.6}_{-0.6}$ & $ 6137^{+  4}_{-  4}$ & $  0.86^{+  0.11}_{-  0.11}$ & $0.004^{+0.226}_{-0.109}$  & $-0.071^{+0.008}_{-0.007}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
+%LSQ12hjm & $ 65.3^{+10.8}_{-11.3}$ & $ 15.3^{+1.1}_{-1.1}$ & $ 6147^{+  5}_{-  5}$ & $ -0.16^{+  0.17}_{-  0.17}$ & $0.112^{+0.030}_{-0.031}$  & $-0.062^{+0.013}_{-0.011}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
+%SNF20060521-001 & $ 89.1^{+11.4}_{-12.2}$ & $ 19.1^{+1.1}_{-1.1}$ & $ 6119^{+ 10}_{-  9}$ & $ -1.70^{+  0.20}_{-  0.20}$ & $0.029^{+0.061}_{-0.059}$  & $-0.068^{+0.014}_{-0.010}$ & $0.010^{+0.019}_{-0.020}$ & $0.010^{+0.019}_{-0.020}$\\
+%SNF20070630-006 & $126.3^{+3.1}_{-3.1}$ & $ 10.3^{+1.1}_{-1.2}$ & $ 6126^{+  4}_{-  4}$ & $  0.30^{+  0.11}_{-  0.11}$ & $-0.018^{+0.025}_{-0.025}$  & $-0.027^{+0.010}_{-0.010}$ & $-0.040^{+0.010}_{-0.008}$ & $-0.040^{+0.010}_{-0.008}$\\
+%PTF11drz & $132.6^{+1.4}_{-1.4}$ & $ 14.9^{+0.9}_{-0.9}$ & $ 6116^{+  4}_{-  4}$ & $ -0.11^{+  0.17}_{-  0.18}$ & $-0.007^{+0.025}_{-0.026}$  & $-0.021^{+0.010}_{-0.009}$ & $-0.016^{+0.013}_{-0.013}$ & $-0.016^{+0.013}_{-0.013}$\\
+%SNF20080323-009 & $ 96.0^{+2.2}_{-2.2}$ & $ 11.1^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.15^{+  0.14}_{-  0.14}$ & $-0.029^{+0.030}_{-0.029}$  & $-0.051^{+0.011}_{-0.011}$ & $-0.041^{+0.009}_{-0.008}$ & $-0.041^{+0.009}_{-0.008}$\\
+%SNF20071021-000 & $167.9^{+2.2}_{-2.2}$ & $ 20.2^{+0.6}_{-0.6}$ & $ 6111^{+  4}_{-  4}$ & $ -0.66^{+  0.13}_{-  0.13}$ & $-0.105^{+0.025}_{-0.023}$  & $-0.001^{+0.010}_{-0.010}$ & $-0.004^{+0.013}_{-0.013}$ & $-0.004^{+0.013}_{-0.013}$\\
+%SNNGC0927 & $155.2^{+1.3}_{-1.3}$ & $ 10.9^{+0.7}_{-0.7}$ & $ 6109^{+  4}_{-  4}$ & $  0.39^{+  0.12}_{-  0.12}$ & $-0.031^{+0.027}_{-0.027}$  & $0.039^{+0.010}_{-0.010}$ & $-0.018^{+0.014}_{-0.013}$ & $-0.018^{+0.014}_{-0.013}$\\
+%SNF20060526-003 & $111.8^{+2.5}_{-2.5}$ & $  9.9^{+1.0}_{-1.0}$ & $ 6121^{+  3}_{-  3}$ & $  0.34^{+  0.13}_{-  0.13}$ & $-0.004^{+0.026}_{-0.027}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.011^{+0.014}_{-0.014}$ & $-0.011^{+0.014}_{-0.014}$\\
+%SNF20080806-002 & $135.4^{+1.8}_{-1.9}$ & $  8.3^{+0.9}_{-0.9}$ & $ 6136^{+  4}_{-  4}$ & $  0.83^{+  0.14}_{-  0.14}$ & $-0.106^{+0.028}_{-0.027}$  & $0.020^{+0.010}_{-0.010}$ & $-0.036^{+0.013}_{-0.009}$ & $-0.036^{+0.013}_{-0.009}$\\
+%SNF20080803-000 & $118.3^{+2.5}_{-2.6}$ & $  8.4^{+1.3}_{-1.4}$ & $ 6125^{+  4}_{-  4}$ & $  0.25^{+  0.12}_{-  0.12}$ & $-0.030^{+0.023}_{-0.024}$  & $0.100^{+0.011}_{-0.011}$ & $-0.040^{+0.009}_{-0.008}$ & $-0.040^{+0.009}_{-0.008}$\\
+%SNF20080822-005 & $ 78.6^{+1.8}_{-1.8}$ & $  6.2^{+0.8}_{-0.8}$ & $ 6138^{+  4}_{-  4}$ & $  0.51^{+  0.16}_{-  0.16}$ & $-0.027^{+0.030}_{-0.030}$  & $-0.018^{+0.011}_{-0.010}$ & $0.014^{+0.015}_{-0.015}$ & $0.014^{+0.015}_{-0.015}$\\
+%SNF20060618-014 & $136.8^{+2.4}_{-2.5}$ & $  9.8^{+1.1}_{-1.1}$ & $ 6113^{+  7}_{-  7}$ & $  1.20^{+  0.18}_{-  0.18}$ & $0.077^{+0.047}_{-0.047}$  & $-0.037^{+0.014}_{-0.014}$ & $0.019^{+0.025}_{-0.024}$ & $0.019^{+0.025}_{-0.024}$\\
+%PTF12ghy & $100.6^{+3.5}_{-3.5}$ & $ 16.4^{+0.7}_{-0.7}$ & $ 6133^{+  3}_{-  3}$ & $ -0.58^{+  0.10}_{-  0.10}$ & $-0.138^{+0.023}_{-0.022}$  & $0.196^{+0.011}_{-0.011}$ & $0.001^{+0.013}_{-0.013}$ & $0.001^{+0.013}_{-0.013}$\\
+%SNF20070531-011 & $122.2^{+2.6}_{-2.6}$ & $ 21.5^{+0.8}_{-0.8}$ & $ 6114^{+  3}_{-  4}$ & $ -1.56^{+  0.20}_{-  0.20}$ & $-0.081^{+0.027}_{-0.025}$  & $-0.032^{+0.011}_{-0.011}$ & $-0.000^{+0.015}_{-0.014}$ & $-0.000^{+0.015}_{-0.014}$\\
+%SNF20070831-015 & $112.9^{+2.6}_{-2.6}$ & $  6.9^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  1.38^{+  0.16}_{-  0.16}$ & $0.042^{+0.027}_{-0.027}$  & $-0.016^{+0.010}_{-0.010}$ & $0.002^{+0.014}_{-0.014}$ & $0.002^{+0.014}_{-0.014}$\\
+%SNF20070417-002 & $103.8^{+5.0}_{-4.9}$ & $ 24.1^{+1.3}_{-1.3}$ & $ 6125^{+  8}_{-  9}$ & $ -1.37^{+  0.10}_{-  0.10}$ & $-0.032^{+0.050}_{-0.044}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+%PTF11cao & $143.4^{+1.5}_{-1.6}$ & $ 19.0^{+1.1}_{-1.1}$ & $ 6104^{+  4}_{-  4}$ & $  0.20^{+  0.13}_{-  0.13}$ & $-0.014^{+0.032}_{-0.031}$  & $0.009^{+0.013}_{-0.013}$ & $-0.017^{+0.017}_{-0.015}$ & $-0.017^{+0.017}_{-0.015}$\\
+%SNF20080522-000 & $ 62.1^{+3.5}_{-3.5}$ & $  3.1^{+0.8}_{-0.8}$ & $ 6130^{+  7}_{-  7}$ & $  0.99^{+  0.11}_{-  0.11}$ & $-0.021^{+0.028}_{-0.028}$  & $-0.009^{+0.012}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$\\
+%PTF10qjq & $ 74.4^{+2.3}_{-2.4}$ & $ 12.0^{+0.7}_{-0.7}$ & $ 6132^{+  3}_{-  3}$ & $ -0.50^{+  0.10}_{-  0.09}$ & $-0.127^{+0.026}_{-0.024}$  & $0.049^{+0.010}_{-0.011}$ & $-0.010^{+0.015}_{-0.015}$ & $-0.010^{+0.015}_{-0.015}$\\
+%PTF12dxm & $119.3^{+15.5}_{-16.8}$ & $ 31.3^{+1.9}_{-2.1}$ & $ 6136^{+  4}_{-  4}$ & $ -2.14^{+  0.18}_{-  0.18}$ & $0.034^{+0.034}_{-0.033}$  & $-0.047^{+0.027}_{-0.021}$ & $0.067^{+0.023}_{-0.024}$ & $0.067^{+0.023}_{-0.024}$\\
+%SNF20061021-003 & $122.5^{+2.2}_{-2.2}$ & $ 10.8^{+1.5}_{-1.5}$ & $ 6131^{+  4}_{-  4}$ & $  0.39^{+  0.15}_{-  0.15}$ & $-0.012^{+0.035}_{-0.033}$  & $0.036^{+0.014}_{-0.014}$ & $0.047^{+0.019}_{-0.017}$ & $0.047^{+0.019}_{-0.017}$\\
+%SNF20080510-005 & $112.2^{+2.5}_{-2.5}$ & $  7.0^{+1.0}_{-1.0}$ & $ 6117^{+  4}_{-  4}$ & $  1.68^{+  0.22}_{-  0.22}$ & $0.116^{+0.030}_{-0.030}$  & $-0.029^{+0.013}_{-0.015}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
+%SNF20080507-000 & $ 98.4^{+1.6}_{-1.6}$ & $  8.0^{+1.7}_{-1.6}$ & $ 6142^{+  5}_{-  5}$ & $  0.56^{+  0.18}_{-  0.18}$ & $-0.126^{+0.023}_{-0.022}$  & $0.063^{+0.014}_{-0.013}$ & $-0.003^{+0.015}_{-0.014}$ & $-0.003^{+0.015}_{-0.014}$\\
+%SNF20080913-031 & $117.9^{+1.5}_{-1.5}$ & $ 14.7^{+1.6}_{-1.6}$ & $ 6159^{+  5}_{-  5}$ & $  0.49^{+  0.17}_{-  0.17}$ & $-0.048^{+0.067}_{-0.052}$  & $-0.003^{+0.015}_{-0.015}$ & $-0.009^{+0.020}_{-0.018}$ & $-0.009^{+0.020}_{-0.018}$\\
+%SNF20080510-001 & $118.9^{+2.0}_{-2.1}$ & $ 15.0^{+1.1}_{-1.0}$ & $ 6115^{+  4}_{-  4}$ & $  0.34^{+  0.14}_{-  0.14}$ & $0.001^{+0.026}_{-0.026}$  & $-0.058^{+0.011}_{-0.012}$ & $-0.032^{+0.012}_{-0.011}$ & $-0.032^{+0.012}_{-0.011}$\\
+%SNF20070712-003 & $108.1^{+2.7}_{-2.6}$ & $ 14.1^{+0.9}_{-0.9}$ & $ 6157^{+  6}_{-  6}$ & $  0.62^{+  0.14}_{-  0.14}$ & $-0.034^{+0.030}_{-0.029}$  & $-0.052^{+0.010}_{-0.011}$ & $-0.021^{+0.015}_{-0.014}$ & $-0.021^{+0.015}_{-0.014}$\\
+%\\
+SNF20050624-000 & $119.9^{+5.1}_{-5.1}$ & $  7.9^{+2.4}_{-2.6}$ & $ 6126^{+  5}_{-  5}$ & $  0.47^{+  0.29}_{-  0.29}$ & $-0.171^{+0.026}_{-0.024}$  & $-0.051^{+0.019}_{-0.017}$ & $0.022^{+0.019}_{-0.021}$ & $0.022^{+0.019}_{-0.021}$\\
+SNF20050728-006 & $127.7^{+2.5}_{-2.4}$ & $ 15.3^{+1.2}_{-1.2}$ & $ 6124^{+  6}_{-  6}$ & $  0.11^{+  0.19}_{-  0.19}$ & $-0.088^{+0.034}_{-0.032}$  & $0.064^{+0.011}_{-0.012}$ & $0.012^{+0.017}_{-0.017}$ & $0.012^{+0.017}_{-0.017}$\\
+SNF20050729-002 & $110.4^{+2.3}_{-2.2}$ & $ 10.7^{+1.5}_{-1.4}$ & $ 6141^{+  6}_{-  6}$ & $ -0.22^{+  0.21}_{-  0.22}$ & $0.052^{+0.102}_{-0.075}$  & $-0.039^{+0.015}_{-0.014}$ & $-0.039^{+0.011}_{-0.008}$ & $-0.039^{+0.011}_{-0.008}$\\
+SNF20050821-007 & $141.8^{+2.6}_{-2.6}$ & $  7.8^{+0.9}_{-0.9}$ & $ 6140^{+  9}_{-  8}$ & $  0.34^{+  0.20}_{-  0.19}$ & $-0.024^{+0.034}_{-0.033}$  & $-0.030^{+0.014}_{-0.013}$ & $-0.012^{+0.017}_{-0.017}$ & $-0.012^{+0.017}_{-0.017}$\\
+SNF20060511-014 & $102.9^{+2.8}_{-2.8}$ & $ 17.1^{+1.0}_{-1.0}$ & $ 6144^{+  8}_{-  7}$ & $ -0.50^{+  0.15}_{-  0.15}$ & $-0.042^{+0.047}_{-0.037}$  & $-0.008^{+0.011}_{-0.010}$ & $-0.041^{+0.009}_{-0.007}$ & $-0.041^{+0.009}_{-0.007}$\\
+SNF20060512-001 & $ 88.2^{+1.2}_{-1.2}$ & $  5.5^{+0.4}_{-0.4}$ & $ 6169^{+  3}_{-  3}$ & $  0.87^{+  0.11}_{-  0.11}$ & $-0.025^{+0.025}_{-0.025}$  & $0.050^{+0.011}_{-0.011}$ & $-0.010^{+0.011}_{-0.012}$ & $-0.010^{+0.011}_{-0.012}$\\
+SNF20060512-002 & $100.4^{+2.7}_{-2.8}$ & $ 13.5^{+1.1}_{-1.1}$ & $ 6106^{+  7}_{-  7}$ & $ -0.87^{+  0.15}_{-  0.16}$ & $-0.186^{+0.030}_{-0.028}$  & $0.018^{+0.012}_{-0.012}$ & $0.056^{+0.017}_{-0.016}$ & $0.056^{+0.017}_{-0.016}$\\
+SNF20060521-001 & $ 89.1^{+11.4}_{-12.2}$ & $ 19.1^{+1.1}_{-1.1}$ & $ 6119^{+ 10}_{-  9}$ & $ -1.70^{+  0.20}_{-  0.20}$ & $0.029^{+0.061}_{-0.059}$  & $-0.068^{+0.014}_{-0.010}$ & $0.010^{+0.019}_{-0.020}$ & $0.010^{+0.019}_{-0.020}$\\
+SNF20060526-003 & $111.8^{+2.5}_{-2.5}$ & $  9.9^{+1.0}_{-1.0}$ & $ 6121^{+  3}_{-  3}$ & $  0.34^{+  0.13}_{-  0.13}$ & $-0.004^{+0.026}_{-0.027}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.011^{+0.014}_{-0.014}$ & $-0.011^{+0.014}_{-0.014}$\\
+SNF20060609-002 & $ 86.3^{+3.5}_{-3.5}$ & $  8.1^{+1.2}_{-1.1}$ & $ 6132^{+  4}_{-  4}$ & $  0.18^{+  0.12}_{-  0.13}$ & $-0.069^{+0.033}_{-0.032}$  & $0.192^{+0.014}_{-0.014}$ & $-0.008^{+0.018}_{-0.017}$ & $-0.008^{+0.018}_{-0.017}$\\
+SNF20060618-014 & $136.8^{+2.4}_{-2.5}$ & $  9.8^{+1.1}_{-1.1}$ & $ 6113^{+  7}_{-  7}$ & $  1.20^{+  0.18}_{-  0.18}$ & $0.077^{+0.047}_{-0.047}$  & $-0.037^{+0.014}_{-0.014}$ & $0.019^{+0.025}_{-0.024}$ & $0.019^{+0.025}_{-0.024}$\\
+SNF20060618-023 & $ 73.3^{+4.7}_{-4.7}$ & $  5.3^{+1.6}_{-1.5}$ & $ 6140^{+ 18}_{- 18}$ & $  0.18^{+  0.16}_{-  0.16}$ & $-0.229^{+0.039}_{-0.038}$  & $0.059^{+0.020}_{-0.020}$ & $0.092^{+0.023}_{-0.022}$ & $0.092^{+0.023}_{-0.022}$\\
+SNF20060621-015 & $111.8^{+1.3}_{-1.3}$ & $  9.9^{+0.7}_{-0.7}$ & $ 6144^{+  3}_{-  3}$ & $  0.52^{+  0.14}_{-  0.14}$ & $-0.015^{+0.026}_{-0.027}$  & $-0.067^{+0.008}_{-0.008}$ & $-0.020^{+0.013}_{-0.013}$ & $-0.020^{+0.013}_{-0.013}$\\
+SNF20060907-000 & $ 87.8^{+7.5}_{-7.3}$ & $ 15.9^{+0.9}_{-0.9}$ & $ 6150^{+  4}_{-  4}$ & $  0.16^{+  0.17}_{-  0.17}$ & $0.037^{+0.033}_{-0.033}$  & $-0.079^{+0.005}_{-0.005}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+SNF20060908-004 & $114.4^{+1.2}_{-1.2}$ & $ 12.4^{+0.6}_{-0.6}$ & $ 6136^{+  3}_{-  3}$ & $  0.63^{+  0.15}_{-  0.15}$ & $-0.099^{+0.138}_{-0.081}$  & $-0.068^{+0.009}_{-0.008}$ & $0.021^{+0.017}_{-0.017}$ & $0.021^{+0.017}_{-0.017}$\\
+SNF20060912-000 & $106.9^{+1.7}_{-1.7}$ & $ 19.8^{+1.5}_{-1.5}$ & $ 6158^{+  7}_{-  7}$ & $  0.06^{+  0.17}_{-  0.17}$ & $-0.177^{+0.032}_{-0.033}$  & $0.034^{+0.018}_{-0.019}$ & $0.080^{+0.021}_{-0.020}$ & $0.080^{+0.021}_{-0.020}$\\
+SNF20061011-005 & $120.5^{+1.1}_{-1.1}$ & $  9.2^{+0.3}_{-0.3}$ & $ 6132^{+  4}_{-  4}$ & $  0.66^{+  0.22}_{-  0.21}$ & $-0.091^{+0.043}_{-0.041}$  & $-0.073^{+0.008}_{-0.007}$ & $0.003^{+0.021}_{-0.021}$ & $0.003^{+0.021}_{-0.021}$\\
+SNF20061020-000 & $ 90.3^{+13.4}_{-13.3}$ & $ 23.9^{+0.9}_{-0.9}$ & $ 6120^{+  4}_{-  5}$ & $ -1.75^{+  0.17}_{-  0.17}$ & $-0.096^{+0.039}_{-0.034}$  & $0.000^{+0.016}_{-0.016}$ & $0.006^{+0.022}_{-0.020}$ & $0.006^{+0.022}_{-0.020}$\\
+SNF20061021-003 & $122.5^{+2.2}_{-2.2}$ & $ 10.8^{+1.5}_{-1.5}$ & $ 6131^{+  4}_{-  4}$ & $  0.39^{+  0.15}_{-  0.15}$ & $-0.012^{+0.035}_{-0.033}$  & $0.036^{+0.014}_{-0.014}$ & $0.047^{+0.019}_{-0.017}$ & $0.047^{+0.019}_{-0.017}$\\
+SNF20061022-005 & $ 63.4^{+3.6}_{-3.8}$ & $  3.9^{+1.4}_{-1.4}$ & $ 6147^{+  7}_{-  7}$ & $  2.03^{+  0.25}_{-  0.25}$ & $0.056^{+0.038}_{-0.038}$  & $0.041^{+0.018}_{-0.020}$ & $-0.000^{+0.022}_{-0.021}$ & $-0.000^{+0.022}_{-0.021}$\\
+SNF20061024-000 & $ 98.9^{+15.7}_{-16.7}$ & $ 29.1^{+1.4}_{-1.4}$ & $ 6127^{+  5}_{-  5}$ & $ -1.51^{+  0.18}_{-  0.18}$ & $0.045^{+0.062}_{-0.059}$  & $-0.049^{+0.021}_{-0.019}$ & $0.003^{+0.031}_{-0.028}$ & $0.003^{+0.031}_{-0.028}$\\
+SNF20061030-010 & $131.6^{+2.2}_{-2.2}$ & $ 16.9^{+1.1}_{-1.1}$ & $ 6116^{+  4}_{-  4}$ & $ -0.10^{+  0.20}_{-  0.20}$ & $0.103^{+0.041}_{-0.041}$  & $0.049^{+0.012}_{-0.012}$ & $0.019^{+0.021}_{-0.021}$ & $0.019^{+0.021}_{-0.021}$\\
+SNF20061108-004 & $128.2^{+5.4}_{-5.4}$ & $  6.8^{+2.1}_{-2.1}$ & $ 6110^{+  6}_{-  6}$ & $  2.36^{+  0.27}_{-  0.27}$ & $-0.089^{+0.038}_{-0.036}$  & $-0.025^{+0.021}_{-0.023}$ & $-0.005^{+0.024}_{-0.022}$ & $-0.005^{+0.024}_{-0.022}$\\
+SNF20061111-002 & $117.1^{+8.6}_{-8.8}$ & $ 19.8^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  0.07^{+  0.17}_{-  0.17}$ & $0.056^{+0.032}_{-0.032}$  & $-0.062^{+0.013}_{-0.011}$ & $0.026^{+0.017}_{-0.017}$ & $0.026^{+0.017}_{-0.017}$\\
+SNF20070330-024 & $118.3^{+2.1}_{-2.1}$ & $  5.5^{+1.8}_{-1.8}$ & $ 6101^{+  3}_{-  3}$ & $  0.48^{+  0.19}_{-  0.21}$ & $-0.166^{+0.025}_{-0.024}$  & $-0.040^{+0.014}_{-0.014}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
+SNF20070331-025 & $118.7^{+6.9}_{-7.0}$ & $ 15.4^{+2.0}_{-2.0}$ & $ 6121^{+ 10}_{- 10}$ & $ -1.22^{+  0.15}_{-  0.15}$ & $0.190^{+0.037}_{-0.037}$  & $-0.015^{+0.020}_{-0.020}$ & $0.001^{+0.023}_{-0.022}$ & $0.001^{+0.023}_{-0.022}$\\
+SNF20070403-000 & $ 62.8^{+6.1}_{-6.2}$ & $ 27.6^{+1.6}_{-1.6}$ & $ 6154^{+  7}_{-  7}$ & $ -1.88^{+  0.17}_{-  0.17}$ & $0.147^{+0.040}_{-0.041}$  & $0.081^{+0.021}_{-0.021}$ & $0.041^{+0.025}_{-0.023}$ & $0.041^{+0.025}_{-0.023}$\\
+SNF20070403-001 & $107.8^{+5.0}_{-5.1}$ & $ 17.1^{+1.4}_{-1.4}$ & $ 6123^{+  4}_{-  4}$ & $ -0.60^{+  0.12}_{-  0.12}$ & $0.007^{+0.029}_{-0.028}$  & $-0.036^{+0.014}_{-0.014}$ & $0.020^{+0.017}_{-0.017}$ & $0.020^{+0.017}_{-0.017}$\\
+SNF20070417-002 & $103.8^{+5.0}_{-4.9}$ & $ 24.1^{+1.3}_{-1.3}$ & $ 6125^{+  8}_{-  9}$ & $ -1.37^{+  0.10}_{-  0.10}$ & $-0.032^{+0.050}_{-0.044}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+SNF20070424-003 & $123.6^{+3.6}_{-3.6}$ & $ 14.2^{+1.2}_{-1.1}$ & $ 6134^{+  6}_{-  6}$ & $  0.30^{+  0.10}_{-  0.10}$ & $0.008^{+0.023}_{-0.023}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+SNF20070427-001 & $ 80.7^{+2.3}_{-2.3}$ & $  6.5^{+0.8}_{-0.8}$ & $ 6143^{+  5}_{-  5}$ & $  0.82^{+  0.17}_{-  0.17}$ & $-0.009^{+0.031}_{-0.031}$  & $-0.066^{+0.011}_{-0.009}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
+SNF20070506-006 & $ 94.3^{+1.3}_{-1.2}$ & $  6.4^{+0.6}_{-0.5}$ & $ 6152^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $-0.075^{+0.027}_{-0.026}$  & $-0.029^{+0.009}_{-0.009}$ & $0.006^{+0.013}_{-0.013}$ & $0.006^{+0.013}_{-0.013}$\\
+SNF20070531-011 & $122.2^{+2.6}_{-2.6}$ & $ 21.5^{+0.8}_{-0.8}$ & $ 6114^{+  3}_{-  4}$ & $ -1.56^{+  0.20}_{-  0.20}$ & $-0.081^{+0.027}_{-0.025}$  & $-0.032^{+0.011}_{-0.011}$ & $-0.000^{+0.015}_{-0.014}$ & $-0.000^{+0.015}_{-0.014}$\\
+SNF20070630-006 & $126.3^{+3.1}_{-3.1}$ & $ 10.3^{+1.1}_{-1.2}$ & $ 6126^{+  4}_{-  4}$ & $  0.30^{+  0.11}_{-  0.11}$ & $-0.018^{+0.025}_{-0.025}$  & $-0.027^{+0.010}_{-0.010}$ & $-0.040^{+0.010}_{-0.008}$ & $-0.040^{+0.010}_{-0.008}$\\
+SNF20070701-005 & $101.6^{+2.6}_{-2.6}$ & $ 13.6^{+0.9}_{-1.0}$ & $ 6155^{+  5}_{-  5}$ & $  0.39^{+  0.14}_{-  0.14}$ & $-0.187^{+0.021}_{-0.021}$  & $-0.012^{+0.011}_{-0.011}$ & $0.037^{+0.015}_{-0.015}$ & $0.037^{+0.015}_{-0.015}$\\
+SNF20070712-003 & $108.1^{+2.7}_{-2.6}$ & $ 14.1^{+0.9}_{-0.9}$ & $ 6157^{+  6}_{-  6}$ & $  0.62^{+  0.14}_{-  0.14}$ & $-0.034^{+0.030}_{-0.029}$  & $-0.052^{+0.010}_{-0.011}$ & $-0.021^{+0.015}_{-0.014}$ & $-0.021^{+0.015}_{-0.014}$\\
+SNF20070714-007 & $132.6^{+5.5}_{-5.5}$ & $ 33.5^{+4.3}_{-4.2}$ & $ 6145^{+  4}_{-  4}$ & $ -1.09^{+  0.13}_{-  0.13}$ & $-0.094^{+0.046}_{-0.047}$  & $0.118^{+0.035}_{-0.038}$ & $0.117^{+0.036}_{-0.032}$ & $0.117^{+0.036}_{-0.032}$\\
+SNF20070725-001 & $108.3^{+1.9}_{-1.9}$ & $  9.5^{+1.0}_{-1.1}$ & $ 6139^{+  6}_{-  6}$ & $  0.61^{+  0.15}_{-  0.15}$ & $0.058^{+0.033}_{-0.033}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.018^{+0.016}_{-0.015}$ & $-0.018^{+0.016}_{-0.015}$\\
+SNF20070727-016 & $ 78.3^{+2.4}_{-2.5}$ & $  4.6^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  0.16^{+  0.11}_{-  0.10}$ & $-0.097^{+0.043}_{-0.036}$  & $-0.037^{+0.011}_{-0.011}$ & $-0.025^{+0.015}_{-0.014}$ & $-0.025^{+0.015}_{-0.014}$\\
+SNF20070802-000 & $157.9^{+3.3}_{-3.3}$ & $ 16.0^{+1.4}_{-1.4}$ & $ 6103^{+  5}_{-  5}$ & $  0.07^{+  0.13}_{-  0.13}$ & $-0.074^{+0.028}_{-0.028}$  & $0.005^{+0.014}_{-0.014}$ & $0.005^{+0.016}_{-0.016}$ & $0.005^{+0.016}_{-0.016}$\\
+SNF20070803-005 & $ 45.4^{+14.0}_{-13.8}$ & $  0.8^{+0.6}_{-0.6}$ & $ 6138^{+ 22}_{- 22}$ & $  0.81^{+  0.15}_{-  0.15}$ & $-0.137^{+0.031}_{-0.031}$  & $0.043^{+0.019}_{-0.019}$ & $-0.005^{+0.021}_{-0.021}$ & $-0.005^{+0.021}_{-0.021}$\\
+SNF20070806-026 & $102.2^{+8.4}_{-9.0}$ & $ 25.3^{+0.7}_{-0.7}$ & $ 6112^{+  7}_{-  7}$ & $ -1.93^{+  0.14}_{-  0.14}$ & $0.010^{+0.032}_{-0.033}$  & $-0.071^{+0.011}_{-0.008}$ & $0.015^{+0.017}_{-0.017}$ & $0.015^{+0.017}_{-0.017}$\\
+SNF20070810-004 & $127.0^{+1.8}_{-1.8}$ & $ 20.1^{+0.9}_{-0.9}$ & $ 6117^{+  7}_{-  7}$ & $ -0.01^{+  0.11}_{-  0.11}$ & $-0.044^{+0.026}_{-0.025}$  & $-0.068^{+0.011}_{-0.009}$ & $-0.033^{+0.012}_{-0.010}$ & $-0.033^{+0.012}_{-0.010}$\\
+SNF20070817-003 & $ 94.5^{+2.4}_{-2.4}$ & $ 18.1^{+1.1}_{-1.1}$ & $ 6115^{+  6}_{-  6}$ & $ -0.61^{+  0.12}_{-  0.12}$ & $0.050^{+0.031}_{-0.032}$  & $-0.031^{+0.012}_{-0.012}$ & $-0.024^{+0.015}_{-0.014}$ & $-0.024^{+0.015}_{-0.014}$\\
+SNF20070818-001 & $160.6^{+6.7}_{-6.8}$ & $ 16.4^{+1.5}_{-1.5}$ & $ 6113^{+  5}_{-  5}$ & $  0.14^{+  0.14}_{-  0.14}$ & $-0.178^{+0.021}_{-0.020}$  & $0.005^{+0.014}_{-0.014}$ & $0.014^{+0.016}_{-0.015}$ & $0.014^{+0.016}_{-0.015}$\\
+SNF20070820-000 & $107.1^{+3.4}_{-3.4}$ & $ 18.7^{+1.2}_{-1.2}$ & $ 6133^{+ 13}_{- 13}$ & $ -0.28^{+  0.12}_{-  0.12}$ & $-0.054^{+0.031}_{-0.030}$  & $0.051^{+0.012}_{-0.013}$ & $-0.015^{+0.018}_{-0.016}$ & $-0.015^{+0.018}_{-0.016}$\\
+SNF20070831-015 & $112.9^{+2.6}_{-2.6}$ & $  6.9^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  1.38^{+  0.16}_{-  0.16}$ & $0.042^{+0.027}_{-0.027}$  & $-0.016^{+0.010}_{-0.010}$ & $0.002^{+0.014}_{-0.014}$ & $0.002^{+0.014}_{-0.014}$\\
+SNF20070902-018 & $108.6^{+9.5}_{-9.7}$ & $ 18.1^{+1.7}_{-1.7}$ & $ 6119^{+  7}_{-  7}$ & $ -0.81^{+  0.10}_{-  0.09}$ & $0.032^{+0.030}_{-0.030}$  & $0.023^{+0.016}_{-0.017}$ & $-0.035^{+0.014}_{-0.010}$ & $-0.035^{+0.014}_{-0.010}$\\
+SNF20070902-021 & $109.0^{+3.3}_{-3.3}$ & $ 16.8^{+0.9}_{-0.9}$ & $ 6131^{+  5}_{-  5}$ & $ -0.46^{+  0.09}_{-  0.09}$ & $-0.082^{+0.027}_{-0.026}$  & $-0.023^{+0.010}_{-0.010}$ & $-0.028^{+0.014}_{-0.012}$ & $-0.028^{+0.014}_{-0.012}$\\
+SNF20071003-016 & $126.5^{+4.5}_{-4.4}$ & $ 16.7^{+1.5}_{-1.5}$ & $ 6123^{+ 10}_{- 10}$ & $ -0.30^{+  0.14}_{-  0.14}$ & $0.058^{+0.032}_{-0.032}$  & $0.068^{+0.013}_{-0.014}$ & $-0.030^{+0.016}_{-0.012}$ & $-0.030^{+0.016}_{-0.012}$\\
+SNF20071015-000 & $104.8^{+3.1}_{-3.1}$ & $  6.5^{+1.1}_{-1.1}$ & $ 6125^{+  7}_{-  7}$ & $  0.90^{+  0.28}_{-  0.29}$ & $0.116^{+0.040}_{-0.040}$  & $0.293^{+0.016}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$\\
+SNF20071021-000 & $167.9^{+2.2}_{-2.2}$ & $ 20.2^{+0.6}_{-0.6}$ & $ 6111^{+  4}_{-  4}$ & $ -0.66^{+  0.13}_{-  0.13}$ & $-0.105^{+0.025}_{-0.023}$  & $-0.001^{+0.010}_{-0.010}$ & $-0.004^{+0.013}_{-0.013}$ & $-0.004^{+0.013}_{-0.013}$\\
+SNF20071108-021 & $ 98.7^{+2.7}_{-2.7}$ & $  6.0^{+0.8}_{-0.8}$ & $ 6165^{+  5}_{-  5}$ & $  1.15^{+  0.16}_{-  0.15}$ & $-0.045^{+0.028}_{-0.028}$  & $-0.028^{+0.012}_{-0.012}$ & $0.024^{+0.015}_{-0.014}$ & $0.024^{+0.015}_{-0.014}$\\
+SNF20080323-009 & $ 96.0^{+2.2}_{-2.2}$ & $ 11.1^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.15^{+  0.14}_{-  0.14}$ & $-0.029^{+0.030}_{-0.029}$  & $-0.051^{+0.011}_{-0.011}$ & $-0.041^{+0.009}_{-0.008}$ & $-0.041^{+0.009}_{-0.008}$\\
+SNF20080507-000 & $ 98.4^{+1.6}_{-1.6}$ & $  8.0^{+1.7}_{-1.6}$ & $ 6142^{+  5}_{-  5}$ & $  0.56^{+  0.18}_{-  0.18}$ & $-0.126^{+0.023}_{-0.022}$  & $0.063^{+0.014}_{-0.013}$ & $-0.003^{+0.015}_{-0.014}$ & $-0.003^{+0.015}_{-0.014}$\\
+SNF20080510-001 & $118.9^{+2.0}_{-2.1}$ & $ 15.0^{+1.1}_{-1.0}$ & $ 6115^{+  4}_{-  4}$ & $  0.34^{+  0.14}_{-  0.14}$ & $0.001^{+0.026}_{-0.026}$  & $-0.058^{+0.011}_{-0.012}$ & $-0.032^{+0.012}_{-0.011}$ & $-0.032^{+0.012}_{-0.011}$\\
+SNF20080510-005 & $112.2^{+2.5}_{-2.5}$ & $  7.0^{+1.0}_{-1.0}$ & $ 6117^{+  4}_{-  4}$ & $  1.68^{+  0.22}_{-  0.22}$ & $0.116^{+0.030}_{-0.030}$  & $-0.029^{+0.013}_{-0.015}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
+SNF20080512-010 & $ 96.0^{+3.4}_{-3.4}$ & $ 21.9^{+1.3}_{-1.3}$ & $ 6128^{+  5}_{-  5}$ & $ -1.64^{+  0.18}_{-  0.18}$ & $-0.032^{+0.072}_{-0.061}$  & $-0.051^{+0.013}_{-0.012}$ & $0.018^{+0.016}_{-0.016}$ & $0.018^{+0.016}_{-0.016}$\\
+SNF20080514-002 & $ 83.1^{+0.7}_{-0.7}$ & $ 19.2^{+0.5}_{-0.5}$ & $ 6131^{+  3}_{-  3}$ & $ -1.55^{+  0.09}_{-  0.09}$ & $0.174^{+0.019}_{-0.019}$  & $-0.074^{+0.007}_{-0.006}$ & $0.006^{+0.011}_{-0.012}$ & $0.006^{+0.011}_{-0.012}$\\
+SNF20080516-000 & $117.6^{+2.1}_{-2.1}$ & $  8.2^{+1.2}_{-1.1}$ & $ 6135^{+  3}_{-  3}$ & $  0.96^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.028}$  & $-0.054^{+0.011}_{-0.010}$ & $0.004^{+0.015}_{-0.015}$ & $0.004^{+0.015}_{-0.015}$\\
+SNF20080516-022 & $ 99.1^{+2.2}_{-2.1}$ & $ 15.3^{+0.9}_{-0.9}$ & $ 6159^{+  3}_{-  3}$ & $  0.48^{+  0.12}_{-  0.11}$ & $0.001^{+0.026}_{-0.026}$  & $-0.064^{+0.010}_{-0.009}$ & $-0.025^{+0.014}_{-0.013}$ & $-0.025^{+0.014}_{-0.013}$\\
+SNF20080522-000 & $ 62.1^{+3.5}_{-3.5}$ & $  3.1^{+0.8}_{-0.8}$ & $ 6130^{+  7}_{-  7}$ & $  0.99^{+  0.11}_{-  0.11}$ & $-0.021^{+0.028}_{-0.028}$  & $-0.009^{+0.012}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$\\
+SNF20080522-011 & $122.1^{+1.7}_{-1.7}$ & $  8.3^{+0.5}_{-0.5}$ & $ 6125^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.124^{+0.023}_{-0.023}$  & $-0.045^{+0.008}_{-0.008}$ & $-0.031^{+0.011}_{-0.010}$ & $-0.031^{+0.011}_{-0.010}$\\
+SNF20080531-000 & $133.2^{+1.5}_{-1.5}$ & $ 17.2^{+0.8}_{-0.8}$ & $ 6113^{+  5}_{-  5}$ & $ -0.63^{+  0.13}_{-  0.13}$ & $0.002^{+0.024}_{-0.024}$  & $-0.040^{+0.009}_{-0.009}$ & $-0.009^{+0.012}_{-0.013}$ & $-0.009^{+0.012}_{-0.013}$\\
+SNF20080610-000 & $119.5^{+8.6}_{-8.8}$ & $ 17.0^{+1.4}_{-1.4}$ & $ 6131^{+  6}_{-  6}$ & $  0.16^{+  0.14}_{-  0.14}$ & $0.013^{+0.068}_{-0.068}$  & $-0.019^{+0.014}_{-0.015}$ & $-0.027^{+0.017}_{-0.013}$ & $-0.027^{+0.017}_{-0.013}$\\
+SNF20080612-003 & $120.0^{+1.1}_{-1.1}$ & $  7.5^{+0.6}_{-0.6}$ & $ 6122^{+  3}_{-  3}$ & $  0.96^{+  0.15}_{-  0.15}$ & $-0.221^{+0.018}_{-0.017}$  & $-0.015^{+0.007}_{-0.007}$ & $-0.001^{+0.013}_{-0.014}$ & $-0.001^{+0.013}_{-0.014}$\\
+SNF20080614-010 & $118.9^{+4.9}_{-4.8}$ & $ 28.9^{+1.2}_{-1.2}$ & $ 6129^{+  3}_{-  3}$ & $ -1.81^{+  0.15}_{-  0.15}$ & $-0.114^{+0.046}_{-0.042}$  & $-0.068^{+0.012}_{-0.009}$ & $0.049^{+0.019}_{-0.019}$ & $0.049^{+0.019}_{-0.019}$\\
+SNF20080620-000 & $125.3^{+9.5}_{-9.7}$ & $ 20.6^{+0.6}_{-0.6}$ & $ 6133^{+  3}_{-  3}$ & $ -0.97^{+  0.14}_{-  0.14}$ & $-0.007^{+0.029}_{-0.028}$  & $0.001^{+0.012}_{-0.012}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
+SNF20080623-001 & $149.2^{+1.4}_{-1.4}$ & $ 14.8^{+0.6}_{-0.6}$ & $ 6131^{+  3}_{-  3}$ & $ -0.07^{+  0.11}_{-  0.10}$ & $0.072^{+0.025}_{-0.025}$  & $-0.054^{+0.010}_{-0.009}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
+SNF20080626-002 & $130.0^{+1.0}_{-1.0}$ & $  5.8^{+2.1}_{-2.0}$ & $ 6111^{+  3}_{-  3}$ & $  1.03^{+  0.19}_{-  0.19}$ & $-0.043^{+0.026}_{-0.025}$  & $-0.009^{+0.015}_{-0.016}$ & $-0.022^{+0.017}_{-0.015}$ & $-0.022^{+0.017}_{-0.015}$\\
+SNF20080714-008 & $155.6^{+11.0}_{-10.8}$ & $ 16.6^{+1.9}_{-1.8}$ & $ 6099^{+  6}_{-  6}$ & $ -0.07^{+  0.14}_{-  0.14}$ & $-0.141^{+0.024}_{-0.022}$  & $0.082^{+0.018}_{-0.020}$ & $-0.029^{+0.017}_{-0.013}$ & $-0.029^{+0.017}_{-0.013}$\\
+SNF20080717-000 & $ 92.7^{+2.6}_{-2.6}$ & $ 12.4^{+1.7}_{-1.7}$ & $ 6105^{+  3}_{-  3}$ & $  0.87^{+  0.13}_{-  0.12}$ & $0.115^{+0.034}_{-0.033}$  & $0.126^{+0.018}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$\\
+SNF20080720-001 & $138.3^{+3.9}_{-4.0}$ & $ 14.0^{+1.5}_{-1.5}$ & $ 6107^{+  3}_{-  3}$ & $  0.19^{+  0.12}_{-  0.12}$ & $-0.176^{+0.028}_{-0.028}$  & $0.325^{+0.018}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$\\
+SNF20080725-004 & $133.8^{+2.1}_{-2.1}$ & $  6.7^{+0.9}_{-0.9}$ & $ 6131^{+  6}_{-  5}$ & $  0.59^{+  0.13}_{-  0.13}$ & $0.078^{+0.032}_{-0.032}$  & $0.025^{+0.012}_{-0.011}$ & $0.016^{+0.015}_{-0.014}$ & $0.016^{+0.015}_{-0.014}$\\
+SNF20080802-006 & $108.7^{+5.6}_{-5.8}$ & $ 19.1^{+1.6}_{-1.6}$ & $ 6122^{+  5}_{-  5}$ & $ -1.61^{+  0.12}_{-  0.12}$ & $-0.042^{+0.059}_{-0.055}$  & $-0.001^{+0.016}_{-0.016}$ & $0.033^{+0.020}_{-0.020}$ & $0.033^{+0.020}_{-0.020}$\\
+SNF20080803-000 & $118.3^{+2.5}_{-2.6}$ & $  8.4^{+1.3}_{-1.4}$ & $ 6125^{+  4}_{-  4}$ & $  0.25^{+  0.12}_{-  0.12}$ & $-0.030^{+0.023}_{-0.024}$  & $0.100^{+0.011}_{-0.011}$ & $-0.040^{+0.009}_{-0.008}$ & $-0.040^{+0.009}_{-0.008}$\\
+SNF20080806-002 & $135.4^{+1.8}_{-1.9}$ & $  8.3^{+0.9}_{-0.9}$ & $ 6136^{+  4}_{-  4}$ & $  0.83^{+  0.14}_{-  0.14}$ & $-0.106^{+0.028}_{-0.027}$  & $0.020^{+0.010}_{-0.010}$ & $-0.036^{+0.013}_{-0.009}$ & $-0.036^{+0.013}_{-0.009}$\\
+SNF20080810-001 & $ 98.8^{+12.2}_{-12.3}$ & $ 21.7^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.93^{+  0.10}_{-  0.11}$ & $-0.058^{+0.024}_{-0.024}$  & $-0.023^{+0.016}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$\\
 SNF20080815-017 & $ 90.9^{+14.3}_{-14.5}$ & $ 19.6^{+2.4}_{-2.3}$ & $ 6131^{+  6}_{-  6}$ & $ -1.96^{+  0.16}_{-  0.16}$ & $0.041^{+0.070}_{-0.064}$  & $-0.008^{+0.025}_{-0.026}$ & $-0.011^{+0.028}_{-0.022}$ & $-0.011^{+0.028}_{-0.022}$\\
-PTF09dnl & $130.0^{+0.8}_{-0.9}$ & $  9.1^{+0.7}_{-0.7}$ & $ 6092^{+  3}_{-  3}$ & $  0.59^{+  0.10}_{-  0.10}$ & $-0.061^{+0.021}_{-0.021}$  & $0.014^{+0.009}_{-0.009}$ & $0.000^{+0.011}_{-0.011}$ & $0.000^{+0.011}_{-0.011}$\\
-SN2010ex & $114.5^{+0.9}_{-0.9}$ & $  8.4^{+0.4}_{-0.4}$ & $ 6129^{+  6}_{-  6}$ & $  0.17^{+  0.12}_{-  0.11}$ & $0.266^{+0.026}_{-0.026}$  & $-0.042^{+0.008}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
-PTF09dnp & $ 66.9^{+4.5}_{-4.6}$ & $ 17.5^{+0.7}_{-0.7}$ & $ 6098^{+  5}_{-  4}$ & $ -0.53^{+  0.17}_{-  0.17}$ & $-0.249^{+0.026}_{-0.026}$  & $-0.008^{+0.020}_{-0.021}$ & $-0.044^{+0.006}_{-0.006}$ & $-0.044^{+0.006}_{-0.006}$\\
-PTF11bnx & $150.7^{+3.0}_{-2.9}$ & $ 14.6^{+1.0}_{-1.0}$ & $ 6143^{+  5}_{-  5}$ & $  0.07^{+  0.14}_{-  0.14}$ & $0.043^{+0.029}_{-0.029}$  & $0.049^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
-PTF12jqh & $151.8^{+1.4}_{-1.5}$ & $  7.9^{+0.6}_{-0.7}$ & $ 6118^{+ 10}_{- 10}$ & $  0.73^{+  0.14}_{-  0.14}$ & $0.069^{+0.028}_{-0.028}$  & $-0.056^{+0.010}_{-0.010}$ & $0.009^{+0.014}_{-0.015}$ & $0.009^{+0.014}_{-0.015}$\\
-SNF20080802-006 & $108.7^{+5.6}_{-5.8}$ & $ 19.1^{+1.6}_{-1.6}$ & $ 6122^{+  5}_{-  5}$ & $ -1.61^{+  0.12}_{-  0.12}$ & $-0.042^{+0.059}_{-0.055}$  & $-0.001^{+0.016}_{-0.016}$ & $0.033^{+0.020}_{-0.020}$ & $0.033^{+0.020}_{-0.020}$\\
-PTF10xyt & $120.2^{+6.3}_{-6.4}$ & $ 21.5^{+3.2}_{-3.1}$ & $ 6102^{+  4}_{-  4}$ & $  0.18^{+  0.20}_{-  0.20}$ & $0.241^{+0.049}_{-0.049}$  & $0.070^{+0.026}_{-0.028}$ & $0.014^{+0.029}_{-0.027}$ & $0.014^{+0.029}_{-0.027}$\\
-PTF11qmo & $101.7^{+1.1}_{-1.1}$ & $  7.8^{+0.7}_{-0.7}$ & $ 6151^{+  7}_{-  8}$ & $  0.41^{+  0.18}_{-  0.18}$ & $-0.078^{+0.031}_{-0.028}$  & $-0.058^{+0.010}_{-0.010}$ & $0.004^{+0.014}_{-0.015}$ & $0.004^{+0.014}_{-0.015}$\\
-SNF20070331-025 & $118.7^{+6.9}_{-7.0}$ & $ 15.4^{+2.0}_{-2.0}$ & $ 6121^{+ 10}_{- 10}$ & $ -1.22^{+  0.15}_{-  0.15}$ & $0.190^{+0.037}_{-0.037}$  & $-0.015^{+0.020}_{-0.020}$ & $0.001^{+0.023}_{-0.022}$ & $0.001^{+0.023}_{-0.022}$\\
-SNF20070818-001 & $160.6^{+6.7}_{-6.8}$ & $ 16.4^{+1.5}_{-1.5}$ & $ 6113^{+  5}_{-  5}$ & $  0.14^{+  0.14}_{-  0.14}$ & $-0.178^{+0.021}_{-0.020}$  & $0.005^{+0.014}_{-0.014}$ & $0.014^{+0.016}_{-0.015}$ & $0.014^{+0.016}_{-0.015}$\\
-SNBOSS38 & $ 57.1^{+0.4}_{-0.4}$ & $ 17.8^{+0.3}_{-0.3}$ & $ 6127^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $0.018^{+0.038}_{-0.039}$  & $0.017^{+0.021}_{-0.023}$ & $-0.002^{+0.019}_{-0.020}$ & $-0.002^{+0.019}_{-0.020}$\\
-SN2006ob & $ 75.9^{+12.1}_{-12.4}$ & $ 26.8^{+1.3}_{-1.4}$ & $ 6113^{+  5}_{-  5}$ & $ -2.26^{+  0.21}_{-  0.21}$ & $0.039^{+0.035}_{-0.035}$  & $-0.051^{+0.019}_{-0.017}$ & $0.084^{+0.021}_{-0.021}$ & $0.084^{+0.021}_{-0.021}$\\
-PTF12eer & $169.4^{+8.9}_{-8.8}$ & $ 12.2^{+1.8}_{-1.8}$ & $ 6148^{+ 10}_{- 10}$ & $  0.64^{+  0.14}_{-  0.15}$ & $-0.053^{+0.028}_{-0.027}$  & $0.039^{+0.018}_{-0.019}$ & $-0.029^{+0.017}_{-0.012}$ & $-0.029^{+0.017}_{-0.012}$\\
-PTF10ops & $ 38.0^{+9.2}_{-9.2}$ & $ 21.9^{+4.6}_{-4.6}$ & $ 6140^{+  6}_{-  5}$ & $ -0.58^{+  0.12}_{-  0.12}$ & $-0.091^{+0.221}_{-0.154}$  & $0.190^{+0.040}_{-0.041}$ & $0.181^{+0.038}_{-0.036}$ & $0.181^{+0.038}_{-0.036}$\\
-SNF20080514-002 & $ 83.1^{+0.7}_{-0.7}$ & $ 19.2^{+0.5}_{-0.5}$ & $ 6131^{+  3}_{-  3}$ & $ -1.55^{+  0.09}_{-  0.09}$ & $0.174^{+0.019}_{-0.019}$  & $-0.074^{+0.007}_{-0.006}$ & $0.006^{+0.011}_{-0.012}$ & $0.006^{+0.011}_{-0.012}$\\
-PTF12evo & $129.1^{+2.6}_{-2.7}$ & $  9.9^{+1.1}_{-1.1}$ & $ 6157^{+  4}_{-  4}$ & $  0.81^{+  0.13}_{-  0.12}$ & $0.024^{+0.027}_{-0.027}$  & $0.004^{+0.011}_{-0.011}$ & $-0.034^{+0.012}_{-0.010}$ & $-0.034^{+0.012}_{-0.010}$\\
-SNF20080614-010 & $118.9^{+4.9}_{-4.8}$ & $ 28.9^{+1.2}_{-1.2}$ & $ 6129^{+  3}_{-  3}$ & $ -1.81^{+  0.15}_{-  0.15}$ & $-0.114^{+0.046}_{-0.042}$  & $-0.068^{+0.012}_{-0.009}$ & $0.049^{+0.019}_{-0.019}$ & $0.049^{+0.019}_{-0.019}$\\
-PTF10icb & $104.8^{+0.9}_{-0.9}$ & $ 12.6^{+0.3}_{-0.3}$ & $ 6138^{+  2}_{-  2}$ & $  0.23^{+  0.10}_{-  0.10}$ & $0.410^{+0.024}_{-0.025}$  & $0.046^{+0.006}_{-0.006}$ & $-0.019^{+0.010}_{-0.010}$ & $-0.019^{+0.010}_{-0.010}$\\
-PTF12efn & $145.5^{+3.3}_{-3.2}$ & $  5.4^{+1.4}_{-1.5}$ & $ 6115^{+  3}_{-  3}$ & $  1.04^{+  0.16}_{-  0.16}$ & $0.177^{+0.030}_{-0.029}$  & $-0.058^{+0.014}_{-0.012}$ & $0.051^{+0.017}_{-0.017}$ & $0.051^{+0.017}_{-0.017}$\\
-SNNGC4424 & $109.0^{+0.3}_{-0.3}$ & $  8.6^{+0.1}_{-0.1}$ & $ 6138^{+  2}_{-  2}$ & $  0.44^{+  0.09}_{-  0.09}$ & $0.600^{+0.022}_{-0.023}$  & $0.078^{+0.007}_{-0.006}$ & $-0.025^{+0.011}_{-0.011}$ & $-0.025^{+0.011}_{-0.011}$\\
-SNF20080516-022 & $ 99.1^{+2.2}_{-2.1}$ & $ 15.3^{+0.9}_{-0.9}$ & $ 6159^{+  3}_{-  3}$ & $  0.48^{+  0.12}_{-  0.11}$ & $0.001^{+0.026}_{-0.026}$  & $-0.064^{+0.010}_{-0.009}$ & $-0.025^{+0.014}_{-0.013}$ & $-0.025^{+0.014}_{-0.013}$\\
-PTF12hwb & $139.4^{+25.9}_{-23.8}$ & $ -0.9^{+4.4}_{-4.3}$ & $ 6090^{+ 14}_{- 14}$ & $  1.34^{+  0.17}_{-  0.17}$ & $0.471^{+0.042}_{-0.044}$  & $0.151^{+0.037}_{-0.043}$ & $0.004^{+0.040}_{-0.032}$ & $0.004^{+0.040}_{-0.032}$\\
-PTF10qyz & $108.1^{+2.1}_{-2.1}$ & $ 21.0^{+0.8}_{-0.8}$ & $ 6117^{+  5}_{-  5}$ & $ -1.67^{+  0.13}_{-  0.13}$ & $0.099^{+0.133}_{-0.095}$  & $-0.067^{+0.014}_{-0.010}$ & $-0.038^{+0.012}_{-0.008}$ & $-0.038^{+0.012}_{-0.008}$\\
-SNF20060907-000 & $ 87.8^{+7.5}_{-7.3}$ & $ 15.9^{+0.9}_{-0.9}$ & $ 6150^{+  4}_{-  4}$ & $  0.16^{+  0.17}_{-  0.17}$ & $0.037^{+0.033}_{-0.033}$  & $-0.079^{+0.005}_{-0.005}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
-LSQ12fxd & $122.8^{+1.6}_{-1.7}$ & $ 11.7^{+0.8}_{-0.7}$ & $ 6119^{+  4}_{-  4}$ & $  0.16^{+  0.12}_{-  0.12}$ & $-0.154^{+0.044}_{-0.032}$  & $-0.052^{+0.008}_{-0.008}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
 SNF20080821-000 & $104.8^{+2.2}_{-2.2}$ & $  8.8^{+1.2}_{-1.2}$ & $ 6121^{+  4}_{-  4}$ & $  0.77^{+  0.15}_{-  0.14}$ & $-0.104^{+0.023}_{-0.023}$  & $0.025^{+0.011}_{-0.011}$ & $-0.006^{+0.013}_{-0.013}$ & $-0.006^{+0.013}_{-0.013}$\\
-SNF20070802-000 & $157.9^{+3.3}_{-3.3}$ & $ 16.0^{+1.4}_{-1.4}$ & $ 6103^{+  5}_{-  5}$ & $  0.07^{+  0.13}_{-  0.13}$ & $-0.074^{+0.028}_{-0.028}$  & $0.005^{+0.014}_{-0.014}$ & $0.005^{+0.016}_{-0.016}$ & $0.005^{+0.016}_{-0.016}$\\
-PTF10wnm & $105.5^{+2.3}_{-2.3}$ & $  6.8^{+0.9}_{-0.9}$ & $ 6125^{+  3}_{-  3}$ & $  0.73^{+  0.12}_{-  0.12}$ & $0.123^{+0.022}_{-0.021}$  & $-0.014^{+0.009}_{-0.009}$ & $0.015^{+0.012}_{-0.012}$ & $0.015^{+0.012}_{-0.012}$\\
-PTF10mwb & $116.2^{+1.2}_{-1.2}$ & $ 21.1^{+0.7}_{-0.7}$ & $ 6139^{+  2}_{-  2}$ & $ -0.48^{+  0.09}_{-  0.09}$ & $-0.000^{+0.071}_{-0.070}$  & $-0.036^{+0.008}_{-0.008}$ & $-0.011^{+0.011}_{-0.011}$ & $-0.011^{+0.011}_{-0.011}$\\
-SN2010dt & $133.3^{+8.4}_{-8.6}$ & $ 16.0^{+0.6}_{-0.6}$ & $ 6141^{+  5}_{-  5}$ & $ -0.02^{+  0.09}_{-  0.09}$ & $-0.046^{+0.024}_{-0.024}$  & $-0.063^{+0.010}_{-0.009}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
-SNF20080623-001 & $149.2^{+1.4}_{-1.4}$ & $ 14.8^{+0.6}_{-0.6}$ & $ 6131^{+  3}_{-  3}$ & $ -0.07^{+  0.11}_{-  0.10}$ & $0.072^{+0.025}_{-0.025}$  & $-0.054^{+0.010}_{-0.009}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
-LSQ12fhe & $ 42.9^{+1.2}_{-1.2}$ & $  2.3^{+1.9}_{-1.9}$ & $ 6108^{+  4}_{-  4}$ & $  1.01^{+  0.17}_{-  0.17}$ & $-0.183^{+0.032}_{-0.033}$  & $0.067^{+0.017}_{-0.018}$ & $-0.017^{+0.018}_{-0.016}$ & $-0.017^{+0.018}_{-0.016}$\\
-PTF11bju & $ 31.3^{+4.3}_{-4.2}$ & $  3.3^{+2.0}_{-2.0}$ & $ 6138^{+  5}_{-  5}$ & $  1.02^{+  0.17}_{-  0.18}$ & $0.073^{+0.036}_{-0.036}$  & $0.077^{+0.019}_{-0.019}$ & $-0.014^{+0.020}_{-0.018}$ & $-0.014^{+0.020}_{-0.018}$\\
-PTF09fox & $118.5^{+2.7}_{-2.7}$ & $  9.8^{+0.9}_{-0.8}$ & $ 6117^{+  3}_{-  3}$ & $  0.52^{+  0.16}_{-  0.15}$ & $0.027^{+0.039}_{-0.039}$  & $-0.047^{+0.009}_{-0.009}$ & $-0.043^{+0.007}_{-0.006}$ & $-0.043^{+0.007}_{-0.006}$\\
-PTF13ayw & $103.8^{+2.4}_{-2.4}$ & $ 23.1^{+1.8}_{-1.9}$ & $ 6116^{+  6}_{-  6}$ & $ -1.67^{+  0.23}_{-  0.24}$ & $0.068^{+0.041}_{-0.041}$  & $-0.069^{+0.014}_{-0.009}$ & $0.101^{+0.019}_{-0.020}$ & $0.101^{+0.019}_{-0.020}$\\
-SNF20070810-004 & $127.0^{+1.8}_{-1.8}$ & $ 20.1^{+0.9}_{-0.9}$ & $ 6117^{+  7}_{-  7}$ & $ -0.01^{+  0.11}_{-  0.11}$ & $-0.044^{+0.026}_{-0.025}$  & $-0.068^{+0.011}_{-0.009}$ & $-0.033^{+0.012}_{-0.010}$ & $-0.033^{+0.012}_{-0.010}$\\
-PTF11mty & $110.5^{+2.2}_{-2.2}$ & $ 11.3^{+1.0}_{-1.1}$ & $ 6140^{+  5}_{-  5}$ & $  1.03^{+  0.13}_{-  0.13}$ & $0.062^{+0.025}_{-0.024}$  & $-0.072^{+0.009}_{-0.007}$ & $0.024^{+0.013}_{-0.014}$ & $0.024^{+0.013}_{-0.014}$\\
-SNF20080512-010 & $ 96.0^{+3.4}_{-3.4}$ & $ 21.9^{+1.3}_{-1.3}$ & $ 6128^{+  5}_{-  5}$ & $ -1.64^{+  0.18}_{-  0.18}$ & $-0.032^{+0.072}_{-0.061}$  & $-0.051^{+0.013}_{-0.012}$ & $0.018^{+0.016}_{-0.016}$ & $0.018^{+0.016}_{-0.016}$\\
-PTF11mkx & $ 34.8^{+3.5}_{-3.5}$ & $  5.5^{+1.3}_{-1.3}$ & $ 6169^{+  5}_{-  5}$ & $  0.53^{+  0.14}_{-  0.14}$ & $0.022^{+0.135}_{-0.080}$  & $0.102^{+0.017}_{-0.016}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
-PTF10tce & $135.8^{+1.1}_{-1.1}$ & $ 10.6^{+1.2}_{-1.2}$ & $ 6090^{+  4}_{-  4}$ & $  0.38^{+  0.12}_{-  0.12}$ & $0.041^{+0.028}_{-0.027}$  & $-0.005^{+0.013}_{-0.014}$ & $-0.019^{+0.015}_{-0.015}$ & $-0.019^{+0.015}_{-0.015}$\\
-SNF20061020-000 & $ 90.3^{+13.4}_{-13.3}$ & $ 23.9^{+0.9}_{-0.9}$ & $ 6120^{+  4}_{-  5}$ & $ -1.75^{+  0.17}_{-  0.17}$ & $-0.096^{+0.039}_{-0.034}$  & $0.000^{+0.016}_{-0.016}$ & $0.006^{+0.022}_{-0.020}$ & $0.006^{+0.022}_{-0.020}$\\
-SN2005ir & $115.7^{+2.8}_{-2.7}$ & $  8.7^{+4.6}_{-4.8}$ & $ 6069^{+  5}_{-  5}$ & $  1.64^{+  0.49}_{-  0.48}$ & $0.112^{+0.042}_{-0.043}$  & $-0.022^{+0.036}_{-0.033}$ & $0.067^{+0.037}_{-0.037}$ & $0.067^{+0.037}_{-0.037}$\\
-SNF20080717-000 & $ 92.7^{+2.6}_{-2.6}$ & $ 12.4^{+1.7}_{-1.7}$ & $ 6105^{+  3}_{-  3}$ & $  0.87^{+  0.13}_{-  0.12}$ & $0.115^{+0.034}_{-0.033}$  & $0.126^{+0.018}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$\\
-PTF12ena & $101.0^{+1.6}_{-1.6}$ & $  8.2^{+0.9}_{-0.9}$ & $ 6130^{+  3}_{-  3}$ & $  0.76^{+  0.13}_{-  0.13}$ & $-0.039^{+0.028}_{-0.028}$  & $0.289^{+0.011}_{-0.012}$ & $-0.038^{+0.010}_{-0.008}$ & $-0.038^{+0.010}_{-0.008}$\\
-PTF13anh & $167.2^{+1.8}_{-1.8}$ & $ 21.6^{+1.0}_{-1.0}$ & $ 6174^{+  3}_{-  4}$ & $ -0.38^{+  0.14}_{-  0.14}$ & $0.092^{+0.108}_{-0.067}$  & $-0.032^{+0.020}_{-0.019}$ & $-0.034^{+0.014}_{-0.010}$ & $-0.034^{+0.014}_{-0.010}$\\
-CSS110918\_01 & $110.4^{+1.0}_{-1.0}$ & $  5.0^{+0.9}_{-0.9}$ & $ 6101^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.077^{+0.187}_{-0.094}$  & $-0.078^{+0.006}_{-0.005}$ & $-0.028^{+0.013}_{-0.012}$ & $-0.028^{+0.013}_{-0.012}$\\
-SNF20061024-000 & $ 98.9^{+15.7}_{-16.7}$ & $ 29.1^{+1.4}_{-1.4}$ & $ 6127^{+  5}_{-  5}$ & $ -1.51^{+  0.18}_{-  0.18}$ & $0.045^{+0.062}_{-0.059}$  & $-0.049^{+0.021}_{-0.019}$ & $0.003^{+0.031}_{-0.028}$ & $0.003^{+0.031}_{-0.028}$\\
-SNF20070506-006 & $ 94.3^{+1.3}_{-1.2}$ & $  6.4^{+0.6}_{-0.5}$ & $ 6152^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $-0.075^{+0.027}_{-0.026}$  & $-0.029^{+0.009}_{-0.009}$ & $0.006^{+0.013}_{-0.013}$ & $0.006^{+0.013}_{-0.013}$\\
-SNF20070403-001 & $107.8^{+5.0}_{-5.1}$ & $ 17.1^{+1.4}_{-1.4}$ & $ 6123^{+  4}_{-  4}$ & $ -0.60^{+  0.12}_{-  0.12}$ & $0.007^{+0.029}_{-0.028}$  & $-0.036^{+0.014}_{-0.014}$ & $0.020^{+0.017}_{-0.017}$ & $0.020^{+0.017}_{-0.017}$\\
-PTF10hmv & $109.8^{+1.3}_{-1.4}$ & $  8.5^{+0.7}_{-0.6}$ & $ 6143^{+  3}_{-  3}$ & $  1.15^{+  0.13}_{-  0.12}$ & $0.284^{+0.024}_{-0.023}$  & $0.106^{+0.009}_{-0.009}$ & $-0.010^{+0.012}_{-0.012}$ & $-0.010^{+0.012}_{-0.012}$\\
-SNF20071015-000 & $104.8^{+3.1}_{-3.1}$ & $  6.5^{+1.1}_{-1.1}$ & $ 6125^{+  7}_{-  7}$ & $  0.90^{+  0.28}_{-  0.29}$ & $0.116^{+0.040}_{-0.040}$  & $0.293^{+0.016}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$\\
-SNhunt89 & $ 88.6^{+2.7}_{-2.7}$ & $ 29.8^{+1.7}_{-1.7}$ & $ 6109^{+  7}_{-  7}$ & $ -2.02^{+  0.16}_{-  0.16}$ & $0.202^{+0.049}_{-0.047}$  & $0.030^{+0.018}_{-0.019}$ & $0.032^{+0.027}_{-0.026}$ & $0.032^{+0.027}_{-0.026}$\\
-SNF20070902-021 & $109.0^{+3.3}_{-3.3}$ & $ 16.8^{+0.9}_{-0.9}$ & $ 6131^{+  5}_{-  5}$ & $ -0.46^{+  0.09}_{-  0.09}$ & $-0.082^{+0.027}_{-0.026}$  & $-0.023^{+0.010}_{-0.010}$ & $-0.028^{+0.014}_{-0.012}$ & $-0.028^{+0.014}_{-0.012}$\\
-PTF09dlc & $143.8^{+2.1}_{-2.1}$ & $  9.7^{+0.8}_{-0.8}$ & $ 6143^{+  3}_{-  3}$ & $  0.01^{+  0.10}_{-  0.10}$ & $0.008^{+0.027}_{-0.026}$  & $-0.054^{+0.012}_{-0.012}$ & $-0.017^{+0.014}_{-0.015}$ & $-0.017^{+0.014}_{-0.015}$\\
-PTF13ajv & $149.9^{+8.1}_{-8.2}$ & $ 22.0^{+2.7}_{-3.0}$ & $ 6107^{+ 20}_{- 20}$ & $ -1.64^{+  0.20}_{-  0.21}$ & $0.263^{+0.046}_{-0.045}$  & $-0.062^{+0.021}_{-0.014}$ & $-0.005^{+0.023}_{-0.022}$ & $-0.005^{+0.023}_{-0.022}$\\
+SNF20080822-005 & $ 78.6^{+1.8}_{-1.8}$ & $  6.2^{+0.8}_{-0.8}$ & $ 6138^{+  4}_{-  4}$ & $  0.51^{+  0.16}_{-  0.16}$ & $-0.027^{+0.030}_{-0.030}$  & $-0.018^{+0.011}_{-0.010}$ & $0.014^{+0.015}_{-0.015}$ & $0.014^{+0.015}_{-0.015}$\\
+SNF20080825-010 & $ 96.4^{+10.2}_{-10.2}$ & $ 19.2^{+0.6}_{-0.6}$ & $ 6116^{+  4}_{-  4}$ & $ -0.76^{+  0.13}_{-  0.13}$ & $-0.192^{+0.020}_{-0.020}$  & $-0.045^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
+SNF20080909-030 & $ 93.8^{+1.0}_{-0.9}$ & $  7.7^{+0.4}_{-0.4}$ & $ 6171^{+  3}_{-  3}$ & $  0.99^{+  0.13}_{-  0.13}$ & $0.030^{+0.030}_{-0.030}$  & $0.008^{+0.013}_{-0.012}$ & $0.008^{+0.015}_{-0.014}$ & $0.008^{+0.015}_{-0.014}$\\
+SNF20080913-031 & $117.9^{+1.5}_{-1.5}$ & $ 14.7^{+1.6}_{-1.6}$ & $ 6159^{+  5}_{-  5}$ & $  0.49^{+  0.17}_{-  0.17}$ & $-0.048^{+0.067}_{-0.052}$  & $-0.003^{+0.015}_{-0.015}$ & $-0.009^{+0.020}_{-0.018}$ & $-0.009^{+0.020}_{-0.018}$\\
+SNF20080914-001 & $126.4^{+1.2}_{-1.2}$ & $ 16.3^{+1.0}_{-1.0}$ & $ 6159^{+  3}_{-  3}$ & $  0.10^{+  0.14}_{-  0.14}$ & $-0.144^{+0.026}_{-0.024}$  & $0.094^{+0.012}_{-0.012}$ & $0.022^{+0.016}_{-0.015}$ & $0.022^{+0.016}_{-0.015}$\\
+SNF20080918-000 & $146.6^{+3.5}_{-3.5}$ & $  5.6^{+2.1}_{-2.0}$ & $ 6110^{+  5}_{-  5}$ & $  1.28^{+  0.23}_{-  0.23}$ & $0.112^{+0.038}_{-0.037}$  & $0.073^{+0.019}_{-0.019}$ & $-0.004^{+0.023}_{-0.022}$ & $-0.004^{+0.023}_{-0.022}$\\
+SNF20080918-002 & $ 96.6^{+2.8}_{-2.7}$ & $ 13.3^{+1.2}_{-1.2}$ & $ 6143^{+  6}_{-  6}$ & $ -0.47^{+  0.08}_{-  0.08}$ & $0.021^{+0.034}_{-0.035}$  & $-0.056^{+0.014}_{-0.013}$ & $-0.005^{+0.020}_{-0.021}$ & $-0.005^{+0.020}_{-0.021}$\\
+SNF20080918-004 & $ 91.9^{+6.6}_{-6.6}$ & $ 21.2^{+0.9}_{-0.9}$ & $ 6141^{+  4}_{-  4}$ & $ -1.37^{+  0.15}_{-  0.15}$ & $0.035^{+0.142}_{-0.087}$  & $-0.021^{+0.014}_{-0.013}$ & $-0.012^{+0.019}_{-0.018}$ & $-0.012^{+0.019}_{-0.018}$\\
 SNF20080919-000 & $115.6^{+2.7}_{-2.7}$ & $  8.8^{+0.9}_{-0.8}$ & $ 6144^{+  5}_{-  5}$ & $ -0.24^{+  0.10}_{-  0.10}$ & $-0.043^{+0.027}_{-0.026}$  & $0.165^{+0.013}_{-0.012}$ & $-0.035^{+0.013}_{-0.010}$ & $-0.035^{+0.013}_{-0.010}$\\
 SNF20080919-001 & $ 85.0^{+1.1}_{-1.1}$ & $  6.1^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  1.05^{+  0.12}_{-  0.12}$ & $-0.183^{+0.020}_{-0.019}$  & $0.001^{+0.008}_{-0.008}$ & $0.006^{+0.012}_{-0.012}$ & $0.006^{+0.012}_{-0.012}$\\
+SNF20080919-002 & $100.4^{+6.7}_{-6.6}$ & $ 26.3^{+1.7}_{-1.7}$ & $ 6133^{+  8}_{-  8}$ & $ -1.54^{+  0.13}_{-  0.13}$ & $0.340^{+0.043}_{-0.044}$  & $-0.058^{+0.017}_{-0.014}$ & $0.114^{+0.020}_{-0.021}$ & $0.114^{+0.020}_{-0.021}$\\
+SNF20080920-000 & $135.1^{+1.4}_{-1.4}$ & $  5.3^{+1.5}_{-1.5}$ & $ 6085^{+  3}_{-  3}$ & $  1.08^{+  0.23}_{-  0.23}$ & $-0.002^{+0.038}_{-0.037}$  & $-0.020^{+0.017}_{-0.017}$ & $-0.012^{+0.020}_{-0.019}$ & $-0.012^{+0.020}_{-0.019}$\\
+CSS110918\_01 & $110.4^{+1.0}_{-1.0}$ & $  5.0^{+0.9}_{-0.9}$ & $ 6101^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.077^{+0.187}_{-0.094}$  & $-0.078^{+0.006}_{-0.005}$ & $-0.028^{+0.013}_{-0.012}$ & $-0.028^{+0.013}_{-0.012}$\\
+CSS110918\_02 & $109.1^{+8.1}_{-8.1}$ & $ 15.0^{+0.6}_{-0.6}$ & $ 6137^{+  3}_{-  3}$ & $ -0.26^{+  0.13}_{-  0.13}$ & $-0.052^{+0.027}_{-0.027}$  & $-0.039^{+0.010}_{-0.010}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
+CSS120424\_01 & $138.5^{+2.1}_{-2.1}$ & $ 11.5^{+0.6}_{-0.6}$ & $ 6138^{+  3}_{-  3}$ & $  0.58^{+  0.14}_{-  0.14}$ & $-0.010^{+0.028}_{-0.028}$  & $-0.061^{+0.009}_{-0.009}$ & $-0.024^{+0.013}_{-0.012}$ & $-0.024^{+0.013}_{-0.012}$\\
+CSS130502\_01 & $ 87.3^{+8.0}_{-8.7}$ & $ 15.4^{+0.5}_{-0.5}$ & $ 6128^{+  3}_{-  3}$ & $ -0.15^{+  0.20}_{-  0.20}$ & $0.121^{+0.032}_{-0.032}$  & $-0.069^{+0.011}_{-0.009}$ & $-0.017^{+0.015}_{-0.015}$ & $-0.017^{+0.015}_{-0.015}$\\
+LSQ12dbr & $106.9^{+0.6}_{-0.6}$ & $  6.4^{+0.6}_{-0.6}$ & $ 6137^{+  4}_{-  4}$ & $  0.86^{+  0.11}_{-  0.11}$ & $0.004^{+0.226}_{-0.109}$  & $-0.071^{+0.008}_{-0.007}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
+LSQ12fhe & $ 42.9^{+1.2}_{-1.2}$ & $  2.3^{+1.9}_{-1.9}$ & $ 6108^{+  4}_{-  4}$ & $  1.01^{+  0.17}_{-  0.17}$ & $-0.183^{+0.032}_{-0.033}$  & $0.067^{+0.017}_{-0.018}$ & $-0.017^{+0.018}_{-0.016}$ & $-0.017^{+0.018}_{-0.016}$\\
+LSQ12fxd & $122.8^{+1.6}_{-1.7}$ & $ 11.7^{+0.8}_{-0.7}$ & $ 6119^{+  4}_{-  4}$ & $  0.16^{+  0.12}_{-  0.12}$ & $-0.154^{+0.044}_{-0.032}$  & $-0.052^{+0.008}_{-0.008}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
+LSQ12hjm & $ 65.3^{+10.8}_{-11.3}$ & $ 15.3^{+1.1}_{-1.1}$ & $ 6147^{+  5}_{-  5}$ & $ -0.16^{+  0.17}_{-  0.17}$ & $0.112^{+0.030}_{-0.031}$  & $-0.062^{+0.013}_{-0.011}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
+PTF09dlc & $143.8^{+2.1}_{-2.1}$ & $  9.7^{+0.8}_{-0.8}$ & $ 6143^{+  3}_{-  3}$ & $  0.01^{+  0.10}_{-  0.10}$ & $0.008^{+0.027}_{-0.026}$  & $-0.054^{+0.012}_{-0.012}$ & $-0.017^{+0.014}_{-0.015}$ & $-0.017^{+0.014}_{-0.015}$\\
+PTF09dnl & $130.0^{+0.8}_{-0.9}$ & $  9.1^{+0.7}_{-0.7}$ & $ 6092^{+  3}_{-  3}$ & $  0.59^{+  0.10}_{-  0.10}$ & $-0.061^{+0.021}_{-0.021}$  & $0.014^{+0.009}_{-0.009}$ & $0.000^{+0.011}_{-0.011}$ & $0.000^{+0.011}_{-0.011}$\\
+PTF09dnp & $ 66.9^{+4.5}_{-4.6}$ & $ 17.5^{+0.7}_{-0.7}$ & $ 6098^{+  5}_{-  4}$ & $ -0.53^{+  0.17}_{-  0.17}$ & $-0.249^{+0.026}_{-0.026}$  & $-0.008^{+0.020}_{-0.021}$ & $-0.044^{+0.006}_{-0.006}$ & $-0.044^{+0.006}_{-0.006}$\\
+PTF09fox & $118.5^{+2.7}_{-2.7}$ & $  9.8^{+0.9}_{-0.8}$ & $ 6117^{+  3}_{-  3}$ & $  0.52^{+  0.16}_{-  0.15}$ & $0.027^{+0.039}_{-0.039}$  & $-0.047^{+0.009}_{-0.009}$ & $-0.043^{+0.007}_{-0.006}$ & $-0.043^{+0.007}_{-0.006}$\\
+PTF09foz & $127.2^{+1.9}_{-1.9}$ & $ 22.1^{+1.1}_{-1.1}$ & $ 6135^{+  4}_{-  4}$ & $ -0.92^{+  0.16}_{-  0.16}$ & $-0.141^{+0.019}_{-0.018}$  & $-0.042^{+0.009}_{-0.010}$ & $0.031^{+0.013}_{-0.012}$ & $0.031^{+0.013}_{-0.012}$\\
+PTF10hmv & $109.8^{+1.3}_{-1.4}$ & $  8.5^{+0.7}_{-0.6}$ & $ 6143^{+  3}_{-  3}$ & $  1.15^{+  0.13}_{-  0.12}$ & $0.284^{+0.024}_{-0.023}$  & $0.106^{+0.009}_{-0.009}$ & $-0.010^{+0.012}_{-0.012}$ & $-0.010^{+0.012}_{-0.012}$\\
+PTF10icb & $104.8^{+0.9}_{-0.9}$ & $ 12.6^{+0.3}_{-0.3}$ & $ 6138^{+  2}_{-  2}$ & $  0.23^{+  0.10}_{-  0.10}$ & $0.410^{+0.024}_{-0.025}$  & $0.046^{+0.006}_{-0.006}$ & $-0.019^{+0.010}_{-0.010}$ & $-0.019^{+0.010}_{-0.010}$\\
+PTF10mwb & $116.2^{+1.2}_{-1.2}$ & $ 21.1^{+0.7}_{-0.7}$ & $ 6139^{+  2}_{-  2}$ & $ -0.48^{+  0.09}_{-  0.09}$ & $-0.000^{+0.071}_{-0.070}$  & $-0.036^{+0.008}_{-0.008}$ & $-0.011^{+0.011}_{-0.011}$ & $-0.011^{+0.011}_{-0.011}$\\
+PTF10ndc & $124.1^{+2.4}_{-2.4}$ & $  6.7^{+1.0}_{-1.0}$ & $ 6119^{+  3}_{-  3}$ & $  0.86^{+  0.14}_{-  0.14}$ & $0.007^{+0.026}_{-0.025}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.023^{+0.014}_{-0.013}$ & $-0.023^{+0.014}_{-0.013}$\\
+PTF10ops & $ 38.0^{+9.2}_{-9.2}$ & $ 21.9^{+4.6}_{-4.6}$ & $ 6140^{+  6}_{-  5}$ & $ -0.58^{+  0.12}_{-  0.12}$ & $-0.091^{+0.221}_{-0.154}$  & $0.190^{+0.040}_{-0.041}$ & $0.181^{+0.038}_{-0.036}$ & $0.181^{+0.038}_{-0.036}$\\
+PTF10qjq & $ 74.4^{+2.3}_{-2.4}$ & $ 12.0^{+0.7}_{-0.7}$ & $ 6132^{+  3}_{-  3}$ & $ -0.50^{+  0.10}_{-  0.09}$ & $-0.127^{+0.026}_{-0.024}$  & $0.049^{+0.010}_{-0.011}$ & $-0.010^{+0.015}_{-0.015}$ & $-0.010^{+0.015}_{-0.015}$\\
+PTF10qyz & $108.1^{+2.1}_{-2.1}$ & $ 21.0^{+0.8}_{-0.8}$ & $ 6117^{+  5}_{-  5}$ & $ -1.67^{+  0.13}_{-  0.13}$ & $0.099^{+0.133}_{-0.095}$  & $-0.067^{+0.014}_{-0.010}$ & $-0.038^{+0.012}_{-0.008}$ & $-0.038^{+0.012}_{-0.008}$\\
+PTF10tce & $135.8^{+1.1}_{-1.1}$ & $ 10.6^{+1.2}_{-1.2}$ & $ 6090^{+  4}_{-  4}$ & $  0.38^{+  0.12}_{-  0.12}$ & $0.041^{+0.028}_{-0.027}$  & $-0.005^{+0.013}_{-0.014}$ & $-0.019^{+0.015}_{-0.015}$ & $-0.019^{+0.015}_{-0.015}$\\
+PTF10ufj & $141.4^{+3.3}_{-3.3}$ & $ 12.0^{+1.1}_{-1.0}$ & $ 6131^{+  6}_{-  5}$ & $  0.56^{+  0.13}_{-  0.13}$ & $-0.043^{+0.106}_{-0.068}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
+PTF10wnm & $105.5^{+2.3}_{-2.3}$ & $  6.8^{+0.9}_{-0.9}$ & $ 6125^{+  3}_{-  3}$ & $  0.73^{+  0.12}_{-  0.12}$ & $0.123^{+0.022}_{-0.021}$  & $-0.014^{+0.009}_{-0.009}$ & $0.015^{+0.012}_{-0.012}$ & $0.015^{+0.012}_{-0.012}$\\
+PTF10wof & $130.5^{+2.6}_{-2.7}$ & $ 16.5^{+0.9}_{-0.9}$ & $ 6102^{+  2}_{-  2}$ & $  0.06^{+  0.11}_{-  0.11}$ & $0.096^{+0.023}_{-0.023}$  & $-0.009^{+0.011}_{-0.011}$ & $-0.013^{+0.013}_{-0.012}$ & $-0.013^{+0.013}_{-0.012}$\\
+PTF10xyt & $120.2^{+6.3}_{-6.4}$ & $ 21.5^{+3.2}_{-3.1}$ & $ 6102^{+  4}_{-  4}$ & $  0.18^{+  0.20}_{-  0.20}$ & $0.241^{+0.049}_{-0.049}$  & $0.070^{+0.026}_{-0.028}$ & $0.014^{+0.029}_{-0.027}$ & $0.014^{+0.029}_{-0.027}$\\
+PTF10zdk & $149.7^{+1.2}_{-1.2}$ & $ 14.9^{+0.6}_{-0.6}$ & $ 6150^{+  3}_{-  3}$ & $  0.37^{+  0.14}_{-  0.13}$ & $-0.029^{+0.026}_{-0.025}$  & $0.062^{+0.012}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
+PTF11bgv & $ 78.3^{+3.1}_{-3.1}$ & $ 12.7^{+0.6}_{-0.6}$ & $ 6146^{+  3}_{-  3}$ & $ -0.27^{+  0.11}_{-  0.10}$ & $0.057^{+0.028}_{-0.028}$  & $0.081^{+0.010}_{-0.010}$ & $0.006^{+0.015}_{-0.015}$ & $0.006^{+0.015}_{-0.015}$\\
+PTF11bju & $ 31.3^{+4.3}_{-4.2}$ & $  3.3^{+2.0}_{-2.0}$ & $ 6138^{+  5}_{-  5}$ & $  1.02^{+  0.17}_{-  0.18}$ & $0.073^{+0.036}_{-0.036}$  & $0.077^{+0.019}_{-0.019}$ & $-0.014^{+0.020}_{-0.018}$ & $-0.014^{+0.020}_{-0.018}$\\
+PTF11bnx & $150.7^{+3.0}_{-2.9}$ & $ 14.6^{+1.0}_{-1.0}$ & $ 6143^{+  5}_{-  5}$ & $  0.07^{+  0.14}_{-  0.14}$ & $0.043^{+0.029}_{-0.029}$  & $0.049^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
+PTF11cao & $143.4^{+1.5}_{-1.6}$ & $ 19.0^{+1.1}_{-1.1}$ & $ 6104^{+  4}_{-  4}$ & $  0.20^{+  0.13}_{-  0.13}$ & $-0.014^{+0.032}_{-0.031}$  & $0.009^{+0.013}_{-0.013}$ & $-0.017^{+0.017}_{-0.015}$ & $-0.017^{+0.017}_{-0.015}$\\
+PTF11drz & $132.6^{+1.4}_{-1.4}$ & $ 14.9^{+0.9}_{-0.9}$ & $ 6116^{+  4}_{-  4}$ & $ -0.11^{+  0.17}_{-  0.18}$ & $-0.007^{+0.025}_{-0.026}$  & $-0.021^{+0.010}_{-0.009}$ & $-0.016^{+0.013}_{-0.013}$ & $-0.016^{+0.013}_{-0.013}$\\
+PTF11mkx & $ 34.8^{+3.5}_{-3.5}$ & $  5.5^{+1.3}_{-1.3}$ & $ 6169^{+  5}_{-  5}$ & $  0.53^{+  0.14}_{-  0.14}$ & $0.022^{+0.135}_{-0.080}$  & $0.102^{+0.017}_{-0.016}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
+PTF11mty & $110.5^{+2.2}_{-2.2}$ & $ 11.3^{+1.0}_{-1.1}$ & $ 6140^{+  5}_{-  5}$ & $  1.03^{+  0.13}_{-  0.13}$ & $0.062^{+0.025}_{-0.024}$  & $-0.072^{+0.009}_{-0.007}$ & $0.024^{+0.013}_{-0.014}$ & $0.024^{+0.013}_{-0.014}$\\
+PTF11pdk & $127.7^{+2.6}_{-2.7}$ & $ 16.1^{+1.2}_{-1.2}$ & $ 6154^{+  5}_{-  5}$ & $  0.16^{+  0.16}_{-  0.17}$ & $-0.027^{+0.035}_{-0.035}$  & $-0.070^{+0.010}_{-0.008}$ & $-0.033^{+0.015}_{-0.011}$ & $-0.033^{+0.015}_{-0.011}$\\
+PTF11qmo & $101.7^{+1.1}_{-1.1}$ & $  7.8^{+0.7}_{-0.7}$ & $ 6151^{+  7}_{-  8}$ & $  0.41^{+  0.18}_{-  0.18}$ & $-0.078^{+0.031}_{-0.028}$  & $-0.058^{+0.010}_{-0.010}$ & $0.004^{+0.014}_{-0.015}$ & $0.004^{+0.014}_{-0.015}$\\
+PTF12dxm & $119.3^{+15.5}_{-16.8}$ & $ 31.3^{+1.9}_{-2.1}$ & $ 6136^{+  4}_{-  4}$ & $ -2.14^{+  0.18}_{-  0.18}$ & $0.034^{+0.034}_{-0.033}$  & $-0.047^{+0.027}_{-0.021}$ & $0.067^{+0.023}_{-0.024}$ & $0.067^{+0.023}_{-0.024}$\\
+PTF12eer & $169.4^{+8.9}_{-8.8}$ & $ 12.2^{+1.8}_{-1.8}$ & $ 6148^{+ 10}_{- 10}$ & $  0.64^{+  0.14}_{-  0.15}$ & $-0.053^{+0.028}_{-0.027}$  & $0.039^{+0.018}_{-0.019}$ & $-0.029^{+0.017}_{-0.012}$ & $-0.029^{+0.017}_{-0.012}$\\
+PTF12efn & $145.5^{+3.3}_{-3.2}$ & $  5.4^{+1.4}_{-1.5}$ & $ 6115^{+  3}_{-  3}$ & $  1.04^{+  0.16}_{-  0.16}$ & $0.177^{+0.030}_{-0.029}$  & $-0.058^{+0.014}_{-0.012}$ & $0.051^{+0.017}_{-0.017}$ & $0.051^{+0.017}_{-0.017}$\\
+PTF12ena & $101.0^{+1.6}_{-1.6}$ & $  8.2^{+0.9}_{-0.9}$ & $ 6130^{+  3}_{-  3}$ & $  0.76^{+  0.13}_{-  0.13}$ & $-0.039^{+0.028}_{-0.028}$  & $0.289^{+0.011}_{-0.012}$ & $-0.038^{+0.010}_{-0.008}$ & $-0.038^{+0.010}_{-0.008}$\\
+PTF12evo & $129.1^{+2.6}_{-2.7}$ & $  9.9^{+1.1}_{-1.1}$ & $ 6157^{+  4}_{-  4}$ & $  0.81^{+  0.13}_{-  0.12}$ & $0.024^{+0.027}_{-0.027}$  & $0.004^{+0.011}_{-0.011}$ & $-0.034^{+0.012}_{-0.010}$ & $-0.034^{+0.012}_{-0.010}$\\
+PTF12fuu & $105.4^{+3.0}_{-3.0}$ & $  6.5^{+1.0}_{-1.0}$ & $ 6124^{+  5}_{-  5}$ & $  0.37^{+  0.11}_{-  0.11}$ & $0.178^{+0.026}_{-0.026}$  & $-0.057^{+0.010}_{-0.010}$ & $-0.026^{+0.014}_{-0.013}$ & $-0.026^{+0.014}_{-0.013}$\\
+PTF12ghy & $100.6^{+3.5}_{-3.5}$ & $ 16.4^{+0.7}_{-0.7}$ & $ 6133^{+  3}_{-  3}$ & $ -0.58^{+  0.10}_{-  0.10}$ & $-0.138^{+0.023}_{-0.022}$  & $0.196^{+0.011}_{-0.011}$ & $0.001^{+0.013}_{-0.013}$ & $0.001^{+0.013}_{-0.013}$\\
+PTF12grk & $158.1^{+8.3}_{-8.4}$ & $ 22.1^{+1.2}_{-1.2}$ & $ 6089^{+  8}_{-  8}$ & $ -1.02^{+  0.12}_{-  0.12}$ & $-0.117^{+0.027}_{-0.026}$  & $-0.025^{+0.016}_{-0.017}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
+PTF12hwb & $139.4^{+25.9}_{-23.8}$ & $ -0.9^{+4.4}_{-4.3}$ & $ 6090^{+ 14}_{- 14}$ & $  1.34^{+  0.17}_{-  0.17}$ & $0.471^{+0.042}_{-0.044}$  & $0.151^{+0.037}_{-0.043}$ & $0.004^{+0.040}_{-0.032}$ & $0.004^{+0.040}_{-0.032}$\\
+PTF12iiq & $149.1^{+2.1}_{-2.2}$ & $ 24.8^{+0.8}_{-0.7}$ & $ 6048^{+  7}_{-  7}$ & $ -0.83^{+  0.10}_{-  0.11}$ & $0.005^{+0.033}_{-0.033}$  & $-0.005^{+0.019}_{-0.020}$ & $-0.034^{+0.017}_{-0.010}$ & $-0.034^{+0.017}_{-0.010}$\\
+PTF12ikt & $110.3^{+1.5}_{-1.6}$ & $ 14.0^{+0.7}_{-0.7}$ & $ 6141^{+  4}_{-  4}$ & $ -0.40^{+  0.10}_{-  0.10}$ & $-0.023^{+0.025}_{-0.025}$  & $-0.034^{+0.009}_{-0.008}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
+PTF12jqh & $151.8^{+1.4}_{-1.5}$ & $  7.9^{+0.6}_{-0.7}$ & $ 6118^{+ 10}_{- 10}$ & $  0.73^{+  0.14}_{-  0.14}$ & $0.069^{+0.028}_{-0.028}$  & $-0.056^{+0.010}_{-0.010}$ & $0.009^{+0.014}_{-0.015}$ & $0.009^{+0.014}_{-0.015}$\\
+PTF13ajv & $149.9^{+8.1}_{-8.2}$ & $ 22.0^{+2.7}_{-3.0}$ & $ 6107^{+ 20}_{- 20}$ & $ -1.64^{+  0.20}_{-  0.21}$ & $0.263^{+0.046}_{-0.045}$  & $-0.062^{+0.021}_{-0.014}$ & $-0.005^{+0.023}_{-0.022}$ & $-0.005^{+0.023}_{-0.022}$\\
+PTF13anh & $167.2^{+1.8}_{-1.8}$ & $ 21.6^{+1.0}_{-1.0}$ & $ 6174^{+  3}_{-  4}$ & $ -0.38^{+  0.14}_{-  0.14}$ & $0.092^{+0.108}_{-0.067}$  & $-0.032^{+0.020}_{-0.019}$ & $-0.034^{+0.014}_{-0.010}$ & $-0.034^{+0.014}_{-0.010}$\\
+PTF13asv & $ 75.4^{+1.1}_{-1.1}$ & $  2.4^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  0.66^{+  0.10}_{-  0.10}$ & $-0.018^{+0.184}_{-0.105}$  & $-0.068^{+0.012}_{-0.009}$ & $0.015^{+0.015}_{-0.015}$ & $0.015^{+0.015}_{-0.015}$\\
+PTF13ayw & $103.8^{+2.4}_{-2.4}$ & $ 23.1^{+1.8}_{-1.9}$ & $ 6116^{+  6}_{-  6}$ & $ -1.67^{+  0.23}_{-  0.24}$ & $0.068^{+0.041}_{-0.041}$  & $-0.069^{+0.014}_{-0.009}$ & $0.101^{+0.019}_{-0.020}$ & $0.101^{+0.019}_{-0.020}$\\
+PTF13azs & $140.6^{+4.8}_{-4.8}$ & $ 15.2^{+1.3}_{-1.3}$ & $ 6124^{+ 10}_{- 10}$ & $ -0.12^{+  0.11}_{-  0.11}$ & $0.148^{+0.029}_{-0.029}$  & $0.195^{+0.012}_{-0.013}$ & $-0.037^{+0.012}_{-0.009}$ & $-0.037^{+0.012}_{-0.009}$\\
+SN2003bt & $ 64.0^{+12.0}_{-13.2}$ & $ 21.4^{+0.7}_{-0.7}$ & $ 6121^{+  2}_{-  2}$ & $ -1.85^{+  0.16}_{-  0.17}$ & $0.125^{+0.034}_{-0.034}$  & $-0.057^{+0.017}_{-0.014}$ & $0.011^{+0.018}_{-0.019}$ & $0.011^{+0.018}_{-0.019}$\\
+SN2005cf & $158.9^{+0.7}_{-0.7}$ & $ 15.2^{+0.8}_{-0.7}$ & $ 6140^{+  3}_{-  3}$ & $ -0.19^{+  0.13}_{-  0.13}$ & $-0.122^{+0.028}_{-0.027}$  & $-0.077^{+0.007}_{-0.005}$ & $0.002^{+0.014}_{-0.015}$ & $0.002^{+0.014}_{-0.015}$\\
+SN2005hc & $127.2^{+2.4}_{-2.5}$ & $  9.7^{+0.7}_{-0.7}$ & $ 6122^{+  3}_{-  3}$ & $  0.47^{+  0.16}_{-  0.15}$ & $0.137^{+0.025}_{-0.025}$  & $-0.062^{+0.008}_{-0.008}$ & $0.001^{+0.012}_{-0.012}$ & $0.001^{+0.012}_{-0.012}$\\
+SN2005hj & $ 80.4^{+2.4}_{-2.4}$ & $  4.4^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  2.58^{+  0.24}_{-  0.24}$ & $0.076^{+0.039}_{-0.037}$  & $0.009^{+0.018}_{-0.020}$ & $0.066^{+0.022}_{-0.022}$ & $0.066^{+0.022}_{-0.022}$\\
+SN2005ir & $115.7^{+2.8}_{-2.7}$ & $  8.7^{+4.6}_{-4.8}$ & $ 6069^{+  5}_{-  5}$ & $  1.64^{+  0.49}_{-  0.48}$ & $0.112^{+0.042}_{-0.043}$  & $-0.022^{+0.036}_{-0.033}$ & $0.067^{+0.037}_{-0.037}$ & $0.067^{+0.037}_{-0.037}$\\
+SN2006cj & $101.4^{+1.3}_{-1.3}$ & $  5.5^{+0.8}_{-0.8}$ & $ 6128^{+  3}_{-  3}$ & $  0.86^{+  0.13}_{-  0.13}$ & $0.028^{+0.025}_{-0.025}$  & $0.006^{+0.008}_{-0.009}$ & $-0.017^{+0.013}_{-0.013}$ & $-0.017^{+0.013}_{-0.013}$\\
+SN2006dm & $ 99.6^{+1.6}_{-1.6}$ & $ 29.8^{+0.7}_{-0.7}$ & $ 6118^{+  3}_{-  3}$ & $ -2.35^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.029}$  & $-0.047^{+0.011}_{-0.011}$ & $0.047^{+0.017}_{-0.016}$ & $0.047^{+0.017}_{-0.016}$\\
+SN2006do & $106.3^{+2.1}_{-2.1}$ & $ 26.8^{+1.3}_{-1.2}$ & $ 6101^{+  2}_{-  2}$ & $ -1.95^{+  0.34}_{-  0.34}$ & $-0.077^{+0.031}_{-0.030}$  & $-0.038^{+0.012}_{-0.013}$ & $0.035^{+0.018}_{-0.017}$ & $0.035^{+0.018}_{-0.017}$\\
+SN2006ob & $ 75.9^{+12.1}_{-12.4}$ & $ 26.8^{+1.3}_{-1.4}$ & $ 6113^{+  5}_{-  5}$ & $ -2.26^{+  0.21}_{-  0.21}$ & $0.039^{+0.035}_{-0.035}$  & $-0.051^{+0.019}_{-0.017}$ & $0.084^{+0.021}_{-0.021}$ & $0.084^{+0.021}_{-0.021}$\\
+SN2007bd & $113.3^{+5.4}_{-5.4}$ & $ 17.8^{+0.7}_{-0.7}$ & $ 6101^{+  3}_{-  3}$ & $ -1.02^{+  0.18}_{-  0.18}$ & $-0.071^{+0.027}_{-0.027}$  & $-0.050^{+0.011}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
+SN2007cq & $ 63.7^{+3.9}_{-3.9}$ & $ 11.6^{+0.8}_{-0.8}$ & $ 6138^{+  3}_{-  3}$ & $  0.05^{+  0.13}_{-  0.13}$ & $-0.111^{+0.029}_{-0.027}$  & $0.008^{+0.011}_{-0.011}$ & $-0.015^{+0.015}_{-0.015}$ & $-0.015^{+0.015}_{-0.015}$\\
+SN2007kk & $128.6^{+1.4}_{-1.4}$ & $ 11.0^{+0.9}_{-0.9}$ & $ 6099^{+  4}_{-  4}$ & $  0.59^{+  0.14}_{-  0.14}$ & $-0.087^{+0.029}_{-0.029}$  & $-0.048^{+0.012}_{-0.012}$ & $-0.035^{+0.012}_{-0.010}$ & $-0.035^{+0.012}_{-0.010}$\\
+SN2007nq & $ 91.2^{+9.1}_{-9.0}$ & $ 23.3^{+1.0}_{-1.0}$ & $ 6109^{+  5}_{-  5}$ & $ -1.90^{+  0.20}_{-  0.20}$ & $-0.075^{+0.038}_{-0.035}$  & $-0.022^{+0.015}_{-0.015}$ & $0.031^{+0.021}_{-0.020}$ & $0.031^{+0.021}_{-0.020}$\\
+SN2008ec & $ 97.7^{+10.6}_{-10.6}$ & $ 23.0^{+0.4}_{-0.4}$ & $ 6125^{+  3}_{-  3}$ & $ -1.09^{+  0.10}_{-  0.10}$ & $-0.076^{+0.025}_{-0.026}$  & $0.064^{+0.012}_{-0.012}$ & $0.017^{+0.015}_{-0.015}$ & $0.017^{+0.015}_{-0.015}$\\
+SN2010dt & $133.3^{+8.4}_{-8.6}$ & $ 16.0^{+0.6}_{-0.6}$ & $ 6141^{+  5}_{-  5}$ & $ -0.02^{+  0.09}_{-  0.09}$ & $-0.046^{+0.024}_{-0.024}$  & $-0.063^{+0.010}_{-0.009}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
+SN2010ex & $114.5^{+0.9}_{-0.9}$ & $  8.4^{+0.4}_{-0.4}$ & $ 6129^{+  6}_{-  6}$ & $  0.17^{+  0.12}_{-  0.11}$ & $0.266^{+0.026}_{-0.026}$  & $-0.042^{+0.008}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
 SN2010kg & $ 99.4^{+17.2}_{-17.5}$ & $ 21.8^{+0.7}_{-0.7}$ & $ 6077^{+  5}_{-  5}$ & $ -1.87^{+  0.24}_{-  0.25}$ & $-0.073^{+0.030}_{-0.029}$  & $0.035^{+0.021}_{-0.020}$ & $0.034^{+0.020}_{-0.021}$ & $0.034^{+0.020}_{-0.021}$\\
-SNF20080714-008 & $155.6^{+11.0}_{-10.8}$ & $ 16.6^{+1.9}_{-1.8}$ & $ 6099^{+  6}_{-  6}$ & $ -0.07^{+  0.14}_{-  0.14}$ & $-0.141^{+0.024}_{-0.022}$  & $0.082^{+0.018}_{-0.020}$ & $-0.029^{+0.017}_{-0.013}$ & $-0.029^{+0.017}_{-0.013}$\\
-SNF20070714-007 & $132.6^{+5.5}_{-5.5}$ & $ 33.5^{+4.3}_{-4.2}$ & $ 6145^{+  4}_{-  4}$ & $ -1.09^{+  0.13}_{-  0.13}$ & $-0.094^{+0.046}_{-0.047}$  & $0.118^{+0.035}_{-0.038}$ & $0.117^{+0.036}_{-0.032}$ & $0.117^{+0.036}_{-0.032}$\\
-SNF20080522-011 & $122.1^{+1.7}_{-1.7}$ & $  8.3^{+0.5}_{-0.5}$ & $ 6125^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.124^{+0.023}_{-0.023}$  & $-0.045^{+0.008}_{-0.008}$ & $-0.031^{+0.011}_{-0.010}$ & $-0.031^{+0.011}_{-0.010}$\\
-SNF20061111-002 & $117.1^{+8.6}_{-8.8}$ & $ 19.8^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  0.07^{+  0.17}_{-  0.17}$ & $0.056^{+0.032}_{-0.032}$  & $-0.062^{+0.013}_{-0.011}$ & $0.026^{+0.017}_{-0.017}$ & $0.026^{+0.017}_{-0.017}$\\
-SNNGC6343 & $ 86.9^{+1.5}_{-1.4}$ & $ 21.2^{+0.7}_{-0.7}$ & $ 6136^{+  3}_{-  3}$ & $ -1.49^{+  0.16}_{-  0.16}$ & $0.055^{+0.029}_{-0.030}$  & $0.036^{+0.013}_{-0.012}$ & $0.020^{+0.016}_{-0.014}$ & $0.020^{+0.016}_{-0.014}$\\
-SNF20061011-005 & $120.5^{+1.1}_{-1.1}$ & $  9.2^{+0.3}_{-0.3}$ & $ 6132^{+  4}_{-  4}$ & $  0.66^{+  0.22}_{-  0.21}$ & $-0.091^{+0.043}_{-0.041}$  & $-0.073^{+0.008}_{-0.007}$ & $0.003^{+0.021}_{-0.021}$ & $0.003^{+0.021}_{-0.021}$\\
-SNF20080825-010 & $ 96.4^{+10.2}_{-10.2}$ & $ 19.2^{+0.6}_{-0.6}$ & $ 6116^{+  4}_{-  4}$ & $ -0.76^{+  0.13}_{-  0.13}$ & $-0.192^{+0.020}_{-0.020}$  & $-0.045^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
-PTF10ufj & $141.4^{+3.3}_{-3.3}$ & $ 12.0^{+1.1}_{-1.0}$ & $ 6131^{+  6}_{-  5}$ & $  0.56^{+  0.13}_{-  0.13}$ & $-0.043^{+0.106}_{-0.068}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
-PTF10wof & $130.5^{+2.6}_{-2.7}$ & $ 16.5^{+0.9}_{-0.9}$ & $ 6102^{+  2}_{-  2}$ & $  0.06^{+  0.11}_{-  0.11}$ & $0.096^{+0.023}_{-0.023}$  & $-0.009^{+0.011}_{-0.011}$ & $-0.013^{+0.013}_{-0.012}$ & $-0.013^{+0.013}_{-0.012}$\\
-SNF20080918-000 & $146.6^{+3.5}_{-3.5}$ & $  5.6^{+2.1}_{-2.0}$ & $ 6110^{+  5}_{-  5}$ & $  1.28^{+  0.23}_{-  0.23}$ & $0.112^{+0.038}_{-0.037}$  & $0.073^{+0.019}_{-0.019}$ & $-0.004^{+0.023}_{-0.022}$ & $-0.004^{+0.023}_{-0.022}$\\
-SNF20080516-000 & $117.6^{+2.1}_{-2.1}$ & $  8.2^{+1.2}_{-1.1}$ & $ 6135^{+  3}_{-  3}$ & $  0.96^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.028}$  & $-0.054^{+0.011}_{-0.010}$ & $0.004^{+0.015}_{-0.015}$ & $0.004^{+0.015}_{-0.015}$\\
-SN2005cf & $158.9^{+0.7}_{-0.7}$ & $ 15.2^{+0.8}_{-0.7}$ & $ 6140^{+  3}_{-  3}$ & $ -0.19^{+  0.13}_{-  0.13}$ & $-0.122^{+0.028}_{-0.027}$  & $-0.077^{+0.007}_{-0.005}$ & $0.002^{+0.014}_{-0.015}$ & $0.002^{+0.014}_{-0.015}$\\
-CSS130502\_01 & $ 87.3^{+8.0}_{-8.7}$ & $ 15.4^{+0.5}_{-0.5}$ & $ 6128^{+  3}_{-  3}$ & $ -0.15^{+  0.20}_{-  0.20}$ & $0.121^{+0.032}_{-0.032}$  & $-0.069^{+0.011}_{-0.009}$ & $-0.017^{+0.015}_{-0.015}$ & $-0.017^{+0.015}_{-0.015}$\\
-SNF20080620-000 & $125.3^{+9.5}_{-9.7}$ & $ 20.6^{+0.6}_{-0.6}$ & $ 6133^{+  3}_{-  3}$ & $ -0.97^{+  0.14}_{-  0.14}$ & $-0.007^{+0.029}_{-0.028}$  & $0.001^{+0.012}_{-0.012}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
-SNPGC51271 & $ 64.0^{+12.0}_{-13.2}$ & $ 21.4^{+0.7}_{-0.7}$ & $ 6121^{+  2}_{-  2}$ & $ -1.85^{+  0.16}_{-  0.17}$ & $0.125^{+0.034}_{-0.034}$  & $-0.057^{+0.017}_{-0.014}$ & $0.011^{+0.018}_{-0.019}$ & $0.011^{+0.018}_{-0.019}$\\
-PTF11pdk & $127.7^{+2.6}_{-2.7}$ & $ 16.1^{+1.2}_{-1.2}$ & $ 6154^{+  5}_{-  5}$ & $  0.16^{+  0.16}_{-  0.17}$ & $-0.027^{+0.035}_{-0.035}$  & $-0.070^{+0.010}_{-0.008}$ & $-0.033^{+0.015}_{-0.011}$ & $-0.033^{+0.015}_{-0.011}$\\
-SNF20060511-014 & $102.9^{+2.8}_{-2.8}$ & $ 17.1^{+1.0}_{-1.0}$ & $ 6144^{+  8}_{-  7}$ & $ -0.50^{+  0.15}_{-  0.15}$ & $-0.042^{+0.047}_{-0.037}$  & $-0.008^{+0.011}_{-0.010}$ & $-0.041^{+0.009}_{-0.007}$ & $-0.041^{+0.009}_{-0.007}$\\
-SNF20080612-003 & $120.0^{+1.1}_{-1.1}$ & $  7.5^{+0.6}_{-0.6}$ & $ 6122^{+  3}_{-  3}$ & $  0.96^{+  0.15}_{-  0.15}$ & $-0.221^{+0.018}_{-0.017}$  & $-0.015^{+0.007}_{-0.007}$ & $-0.001^{+0.013}_{-0.014}$ & $-0.001^{+0.013}_{-0.014}$\\
-SNF20080626-002 & $130.0^{+1.0}_{-1.0}$ & $  5.8^{+2.1}_{-2.0}$ & $ 6111^{+  3}_{-  3}$ & $  1.03^{+  0.19}_{-  0.19}$ & $-0.043^{+0.026}_{-0.025}$  & $-0.009^{+0.015}_{-0.016}$ & $-0.022^{+0.017}_{-0.015}$ & $-0.022^{+0.017}_{-0.015}$\\
-SNF20060621-015 & $111.8^{+1.3}_{-1.3}$ & $  9.9^{+0.7}_{-0.7}$ & $ 6144^{+  3}_{-  3}$ & $  0.52^{+  0.14}_{-  0.14}$ & $-0.015^{+0.026}_{-0.027}$  & $-0.067^{+0.008}_{-0.008}$ & $-0.020^{+0.013}_{-0.013}$ & $-0.020^{+0.013}_{-0.013}$\\
-SNF20080920-000 & $135.1^{+1.4}_{-1.4}$ & $  5.3^{+1.5}_{-1.5}$ & $ 6085^{+  3}_{-  3}$ & $  1.08^{+  0.23}_{-  0.23}$ & $-0.002^{+0.038}_{-0.037}$  & $-0.020^{+0.017}_{-0.017}$ & $-0.012^{+0.020}_{-0.019}$ & $-0.012^{+0.020}_{-0.019}$\\
-SN2007cq & $ 63.7^{+3.9}_{-3.9}$ & $ 11.6^{+0.8}_{-0.8}$ & $ 6138^{+  3}_{-  3}$ & $  0.05^{+  0.13}_{-  0.13}$ & $-0.111^{+0.029}_{-0.027}$  & $0.008^{+0.011}_{-0.011}$ & $-0.015^{+0.015}_{-0.015}$ & $-0.015^{+0.015}_{-0.015}$\\
-SNF20080918-004 & $ 91.9^{+6.6}_{-6.6}$ & $ 21.2^{+0.9}_{-0.9}$ & $ 6141^{+  4}_{-  4}$ & $ -1.37^{+  0.15}_{-  0.15}$ & $0.035^{+0.142}_{-0.087}$  & $-0.021^{+0.014}_{-0.013}$ & $-0.012^{+0.019}_{-0.018}$ & $-0.012^{+0.019}_{-0.018}$\\
-CSS120424\_01 & $138.5^{+2.1}_{-2.1}$ & $ 11.5^{+0.6}_{-0.6}$ & $ 6138^{+  3}_{-  3}$ & $  0.58^{+  0.14}_{-  0.14}$ & $-0.010^{+0.028}_{-0.028}$  & $-0.061^{+0.009}_{-0.009}$ & $-0.024^{+0.013}_{-0.012}$ & $-0.024^{+0.013}_{-0.012}$\\
-SNF20080610-000 & $119.5^{+8.6}_{-8.8}$ & $ 17.0^{+1.4}_{-1.4}$ & $ 6131^{+  6}_{-  6}$ & $  0.16^{+  0.14}_{-  0.14}$ & $0.013^{+0.068}_{-0.068}$  & $-0.019^{+0.014}_{-0.015}$ & $-0.027^{+0.017}_{-0.013}$ & $-0.027^{+0.017}_{-0.013}$\\
-SNF20070701-005 & $101.6^{+2.6}_{-2.6}$ & $ 13.6^{+0.9}_{-1.0}$ & $ 6155^{+  5}_{-  5}$ & $  0.39^{+  0.14}_{-  0.14}$ & $-0.187^{+0.021}_{-0.021}$  & $-0.012^{+0.011}_{-0.011}$ & $0.037^{+0.015}_{-0.015}$ & $0.037^{+0.015}_{-0.015}$\\
-SN2007kk & $128.6^{+1.4}_{-1.4}$ & $ 11.0^{+0.9}_{-0.9}$ & $ 6099^{+  4}_{-  4}$ & $  0.59^{+  0.14}_{-  0.14}$ & $-0.087^{+0.029}_{-0.029}$  & $-0.048^{+0.012}_{-0.012}$ & $-0.035^{+0.012}_{-0.010}$ & $-0.035^{+0.012}_{-0.010}$\\
-SNF20060908-004 & $114.4^{+1.2}_{-1.2}$ & $ 12.4^{+0.6}_{-0.6}$ & $ 6136^{+  3}_{-  3}$ & $  0.63^{+  0.15}_{-  0.15}$ & $-0.099^{+0.138}_{-0.081}$  & $-0.068^{+0.009}_{-0.008}$ & $0.021^{+0.017}_{-0.017}$ & $0.021^{+0.017}_{-0.017}$\\
-SNF20080909-030 & $ 93.8^{+1.0}_{-0.9}$ & $  7.7^{+0.4}_{-0.4}$ & $ 6171^{+  3}_{-  3}$ & $  0.99^{+  0.13}_{-  0.13}$ & $0.030^{+0.030}_{-0.030}$  & $0.008^{+0.013}_{-0.012}$ & $0.008^{+0.015}_{-0.014}$ & $0.008^{+0.015}_{-0.014}$\\
-PTF11bgv & $ 78.3^{+3.1}_{-3.1}$ & $ 12.7^{+0.6}_{-0.6}$ & $ 6146^{+  3}_{-  3}$ & $ -0.27^{+  0.11}_{-  0.10}$ & $0.057^{+0.028}_{-0.028}$  & $0.081^{+0.010}_{-0.010}$ & $0.006^{+0.015}_{-0.015}$ & $0.006^{+0.015}_{-0.015}$\\
-SNNGC2691 & $ 55.7^{+14.4}_{-14.5}$ & $  4.5^{+0.2}_{-0.2}$ & $ 6138^{+  8}_{-  8}$ & $  0.82^{+  0.16}_{-  0.16}$ & $-0.031^{+0.039}_{-0.038}$  & $0.069^{+0.018}_{-0.019}$ & $0.041^{+0.020}_{-0.020}$ & $0.041^{+0.020}_{-0.020}$\\
-PTF13asv & $ 75.4^{+1.1}_{-1.1}$ & $  2.4^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  0.66^{+  0.10}_{-  0.10}$ & $-0.018^{+0.184}_{-0.105}$  & $-0.068^{+0.012}_{-0.009}$ & $0.015^{+0.015}_{-0.015}$ & $0.015^{+0.015}_{-0.015}$\\
-SNF20070806-026 & $102.2^{+8.4}_{-9.0}$ & $ 25.3^{+0.7}_{-0.7}$ & $ 6112^{+  7}_{-  7}$ & $ -1.93^{+  0.14}_{-  0.14}$ & $0.010^{+0.032}_{-0.033}$  & $-0.071^{+0.011}_{-0.008}$ & $0.015^{+0.017}_{-0.017}$ & $0.015^{+0.017}_{-0.017}$\\
-SNF20070427-001 & $ 80.7^{+2.3}_{-2.3}$ & $  6.5^{+0.8}_{-0.8}$ & $ 6143^{+  5}_{-  5}$ & $  0.82^{+  0.17}_{-  0.17}$ & $-0.009^{+0.031}_{-0.031}$  & $-0.066^{+0.011}_{-0.009}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
-SNF20061108-004 & $128.2^{+5.4}_{-5.4}$ & $  6.8^{+2.1}_{-2.1}$ & $ 6110^{+  6}_{-  6}$ & $  2.36^{+  0.27}_{-  0.27}$ & $-0.089^{+0.038}_{-0.036}$  & $-0.025^{+0.021}_{-0.023}$ & $-0.005^{+0.024}_{-0.022}$ & $-0.005^{+0.024}_{-0.022}$\\
-SNF20060912-000 & $106.9^{+1.7}_{-1.7}$ & $ 19.8^{+1.5}_{-1.5}$ & $ 6158^{+  7}_{-  7}$ & $  0.06^{+  0.17}_{-  0.17}$ & $-0.177^{+0.032}_{-0.033}$  & $0.034^{+0.018}_{-0.019}$ & $0.080^{+0.021}_{-0.020}$ & $0.080^{+0.021}_{-0.020}$\\
-CSS110918\_02 & $109.1^{+8.1}_{-8.1}$ & $ 15.0^{+0.6}_{-0.6}$ & $ 6137^{+  3}_{-  3}$ & $ -0.26^{+  0.13}_{-  0.13}$ & $-0.052^{+0.027}_{-0.027}$  & $-0.039^{+0.010}_{-0.010}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
-SNF20080918-002 & $ 96.6^{+2.8}_{-2.7}$ & $ 13.3^{+1.2}_{-1.2}$ & $ 6143^{+  6}_{-  6}$ & $ -0.47^{+  0.08}_{-  0.08}$ & $0.021^{+0.034}_{-0.035}$  & $-0.056^{+0.014}_{-0.013}$ & $-0.005^{+0.020}_{-0.021}$ & $-0.005^{+0.020}_{-0.021}$\\
-SNIC3573 & $103.0^{+1.8}_{-1.7}$ & $ 12.1^{+0.9}_{-0.9}$ & $ 6141^{+  5}_{-  5}$ & $  0.39^{+  0.16}_{-  0.16}$ & $-0.109^{+0.026}_{-0.024}$  & $0.015^{+0.009}_{-0.010}$ & $-0.025^{+0.014}_{-0.012}$ & $-0.025^{+0.014}_{-0.012}$\\
-SNF20080725-004 & $133.8^{+2.1}_{-2.1}$ & $  6.7^{+0.9}_{-0.9}$ & $ 6131^{+  6}_{-  5}$ & $  0.59^{+  0.13}_{-  0.13}$ & $0.078^{+0.032}_{-0.032}$  & $0.025^{+0.012}_{-0.011}$ & $0.016^{+0.015}_{-0.014}$ & $0.016^{+0.015}_{-0.014}$\\
-SNF20050728-006 & $127.7^{+2.5}_{-2.4}$ & $ 15.3^{+1.2}_{-1.2}$ & $ 6124^{+  6}_{-  6}$ & $  0.11^{+  0.19}_{-  0.19}$ & $-0.088^{+0.034}_{-0.032}$  & $0.064^{+0.011}_{-0.012}$ & $0.012^{+0.017}_{-0.017}$ & $0.012^{+0.017}_{-0.017}$\\
+SN2011bc & $127.1^{+2.4}_{-2.4}$ & $ 15.7^{+1.1}_{-1.1}$ & $ 6152^{+  4}_{-  4}$ & $  0.04^{+  0.10}_{-  0.10}$ & $-0.004^{+0.030}_{-0.029}$  & $0.049^{+0.013}_{-0.013}$ & $0.045^{+0.016}_{-0.015}$ & $0.045^{+0.016}_{-0.015}$\\
+SN2011be & $ 93.8^{+2.0}_{-2.0}$ & $ 11.2^{+0.6}_{-0.6}$ & $ 6133^{+  4}_{-  4}$ & $  0.22^{+  0.17}_{-  0.17}$ & $0.150^{+0.032}_{-0.032}$  & $-0.062^{+0.010}_{-0.010}$ & $0.035^{+0.016}_{-0.015}$ & $0.035^{+0.016}_{-0.015}$\\
+SN2011ho & $ 88.6^{+2.7}_{-2.7}$ & $ 29.8^{+1.7}_{-1.7}$ & $ 6109^{+  7}_{-  7}$ & $ -2.02^{+  0.16}_{-  0.16}$ & $0.202^{+0.049}_{-0.047}$  & $0.030^{+0.018}_{-0.019}$ & $0.032^{+0.027}_{-0.026}$ & $0.032^{+0.027}_{-0.026}$\\
+SN2011hr & $ 55.7^{+14.4}_{-14.5}$ & $  4.5^{+0.2}_{-0.2}$ & $ 6138^{+  8}_{-  8}$ & $  0.82^{+  0.16}_{-  0.16}$ & $-0.031^{+0.039}_{-0.038}$  & $0.069^{+0.018}_{-0.019}$ & $0.041^{+0.020}_{-0.020}$ & $0.041^{+0.020}_{-0.020}$\\
+SN2011ia & $ 85.4^{+0.6}_{-0.6}$ & $  5.8^{+0.3}_{-0.3}$ & $ 6130^{+  4}_{-  4}$ & $  0.45^{+  0.17}_{-  0.17}$ & $0.078^{+0.032}_{-0.031}$  & $-0.077^{+0.006}_{-0.005}$ & $-0.026^{+0.015}_{-0.013}$ & $-0.026^{+0.015}_{-0.013}$\\
+SN2012cg & $109.0^{+0.3}_{-0.3}$ & $  8.6^{+0.1}_{-0.1}$ & $ 6138^{+  2}_{-  2}$ & $  0.44^{+  0.09}_{-  0.09}$ & $0.600^{+0.022}_{-0.023}$  & $0.078^{+0.007}_{-0.006}$ & $-0.025^{+0.011}_{-0.011}$ & $-0.025^{+0.011}_{-0.011}$\\
 SN2012fr & $134.2^{+0.5}_{-0.5}$ & $  7.4^{+0.2}_{-0.2}$ & $ 6101^{+  1}_{-  1}$ & $  0.88^{+  0.08}_{-  0.09}$ & $-0.248^{+0.021}_{-0.021}$  & $-0.077^{+0.005}_{-0.005}$ & $0.044^{+0.012}_{-0.011}$ & $0.044^{+0.012}_{-0.011}$\\
-SNF20060512-002 & $100.4^{+2.7}_{-2.8}$ & $ 13.5^{+1.1}_{-1.1}$ & $ 6106^{+  7}_{-  7}$ & $ -0.87^{+  0.15}_{-  0.16}$ & $-0.186^{+0.030}_{-0.028}$  & $0.018^{+0.012}_{-0.012}$ & $0.056^{+0.017}_{-0.016}$ & $0.056^{+0.017}_{-0.016}$\\
-SNF20060512-001 & $ 88.2^{+1.2}_{-1.2}$ & $  5.5^{+0.4}_{-0.4}$ & $ 6169^{+  3}_{-  3}$ & $  0.87^{+  0.11}_{-  0.11}$ & $-0.025^{+0.025}_{-0.025}$  & $0.050^{+0.011}_{-0.011}$ & $-0.010^{+0.011}_{-0.012}$ & $-0.010^{+0.011}_{-0.012}$\\
-SNF20071003-016 & $126.5^{+4.5}_{-4.4}$ & $ 16.7^{+1.5}_{-1.5}$ & $ 6123^{+ 10}_{- 10}$ & $ -0.30^{+  0.14}_{-  0.14}$ & $0.058^{+0.032}_{-0.032}$  & $0.068^{+0.013}_{-0.014}$ & $-0.030^{+0.016}_{-0.012}$ & $-0.030^{+0.016}_{-0.012}$\\
-SNF20050821-007 & $141.8^{+2.6}_{-2.6}$ & $  7.8^{+0.9}_{-0.9}$ & $ 6140^{+  9}_{-  8}$ & $  0.34^{+  0.20}_{-  0.19}$ & $-0.024^{+0.034}_{-0.033}$  & $-0.030^{+0.014}_{-0.013}$ & $-0.012^{+0.017}_{-0.017}$ & $-0.012^{+0.017}_{-0.017}$\\
-SNF20070803-005 & $ 45.4^{+14.0}_{-13.8}$ & $  0.8^{+0.6}_{-0.6}$ & $ 6138^{+ 22}_{- 22}$ & $  0.81^{+  0.15}_{-  0.15}$ & $-0.137^{+0.031}_{-0.031}$  & $0.043^{+0.019}_{-0.019}$ & $-0.005^{+0.021}_{-0.021}$ & $-0.005^{+0.021}_{-0.021}$\\
-PTF09foz & $127.2^{+1.9}_{-1.9}$ & $ 22.1^{+1.1}_{-1.1}$ & $ 6135^{+  4}_{-  4}$ & $ -0.92^{+  0.16}_{-  0.16}$ & $-0.141^{+0.019}_{-0.018}$  & $-0.042^{+0.009}_{-0.010}$ & $0.031^{+0.013}_{-0.012}$ & $0.031^{+0.013}_{-0.012}$\\
-PTF12grk & $158.1^{+8.3}_{-8.4}$ & $ 22.1^{+1.2}_{-1.2}$ & $ 6089^{+  8}_{-  8}$ & $ -1.02^{+  0.12}_{-  0.12}$ & $-0.117^{+0.027}_{-0.026}$  & $-0.025^{+0.016}_{-0.017}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
-SNF20080720-001 & $138.3^{+3.9}_{-4.0}$ & $ 14.0^{+1.5}_{-1.5}$ & $ 6107^{+  3}_{-  3}$ & $  0.19^{+  0.12}_{-  0.12}$ & $-0.176^{+0.028}_{-0.028}$  & $0.325^{+0.018}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$\\
-SNF20080810-001 & $ 98.8^{+12.2}_{-12.3}$ & $ 21.7^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.93^{+  0.10}_{-  0.11}$ & $-0.058^{+0.024}_{-0.024}$  & $-0.023^{+0.016}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$\\
-SNF20050729-002 & $110.4^{+2.3}_{-2.2}$ & $ 10.7^{+1.5}_{-1.4}$ & $ 6141^{+  6}_{-  6}$ & $ -0.22^{+  0.21}_{-  0.22}$ & $0.052^{+0.102}_{-0.075}$  & $-0.039^{+0.015}_{-0.014}$ & $-0.039^{+0.011}_{-0.008}$ & $-0.039^{+0.011}_{-0.008}$\\
-SN2008ec & $ 97.7^{+10.6}_{-10.6}$ & $ 23.0^{+0.4}_{-0.4}$ & $ 6125^{+  3}_{-  3}$ & $ -1.09^{+  0.10}_{-  0.10}$ & $-0.076^{+0.025}_{-0.026}$  & $0.064^{+0.012}_{-0.012}$ & $0.017^{+0.015}_{-0.015}$ & $0.017^{+0.015}_{-0.015}$\\
-SNF20070902-018 & $108.6^{+9.5}_{-9.7}$ & $ 18.1^{+1.7}_{-1.7}$ & $ 6119^{+  7}_{-  7}$ & $ -0.81^{+  0.10}_{-  0.09}$ & $0.032^{+0.030}_{-0.030}$  & $0.023^{+0.016}_{-0.017}$ & $-0.035^{+0.014}_{-0.010}$ & $-0.035^{+0.014}_{-0.010}$\\
-SNF20070424-003 & $123.6^{+3.6}_{-3.6}$ & $ 14.2^{+1.2}_{-1.1}$ & $ 6134^{+  6}_{-  6}$ & $  0.30^{+  0.10}_{-  0.10}$ & $0.008^{+0.023}_{-0.023}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
-SN2006cj & $101.4^{+1.3}_{-1.3}$ & $  5.5^{+0.8}_{-0.8}$ & $ 6128^{+  3}_{-  3}$ & $  0.86^{+  0.13}_{-  0.13}$ & $0.028^{+0.025}_{-0.025}$  & $0.006^{+0.008}_{-0.009}$ & $-0.017^{+0.013}_{-0.013}$ & $-0.017^{+0.013}_{-0.013}$\\
-SN2007nq & $ 91.2^{+9.1}_{-9.0}$ & $ 23.3^{+1.0}_{-1.0}$ & $ 6109^{+  5}_{-  5}$ & $ -1.90^{+  0.20}_{-  0.20}$ & $-0.075^{+0.038}_{-0.035}$  & $-0.022^{+0.015}_{-0.015}$ & $0.031^{+0.021}_{-0.020}$ & $0.031^{+0.021}_{-0.020}$\\
-SNF20070817-003 & $ 94.5^{+2.4}_{-2.4}$ & $ 18.1^{+1.1}_{-1.1}$ & $ 6115^{+  6}_{-  6}$ & $ -0.61^{+  0.12}_{-  0.12}$ & $0.050^{+0.031}_{-0.032}$  & $-0.031^{+0.012}_{-0.012}$ & $-0.024^{+0.015}_{-0.014}$ & $-0.024^{+0.015}_{-0.014}$\\
-SNF20070403-000 & $ 62.8^{+6.1}_{-6.2}$ & $ 27.6^{+1.6}_{-1.6}$ & $ 6154^{+  7}_{-  7}$ & $ -1.88^{+  0.17}_{-  0.17}$ & $0.147^{+0.040}_{-0.041}$  & $0.081^{+0.021}_{-0.021}$ & $0.041^{+0.025}_{-0.023}$ & $0.041^{+0.025}_{-0.023}$\\
-SNF20061022-005 & $ 63.4^{+3.6}_{-3.8}$ & $  3.9^{+1.4}_{-1.4}$ & $ 6147^{+  7}_{-  7}$ & $  2.03^{+  0.25}_{-  0.25}$ & $0.056^{+0.038}_{-0.038}$  & $0.041^{+0.018}_{-0.020}$ & $-0.000^{+0.022}_{-0.021}$ & $-0.000^{+0.022}_{-0.021}$\\
-SNNGC4076 & $127.1^{+2.4}_{-2.4}$ & $ 15.7^{+1.1}_{-1.1}$ & $ 6152^{+  4}_{-  4}$ & $  0.04^{+  0.10}_{-  0.10}$ & $-0.004^{+0.030}_{-0.029}$  & $0.049^{+0.013}_{-0.013}$ & $0.045^{+0.016}_{-0.015}$ & $0.045^{+0.016}_{-0.015}$\\
-SNF20070727-016 & $ 78.3^{+2.4}_{-2.5}$ & $  4.6^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  0.16^{+  0.11}_{-  0.10}$ & $-0.097^{+0.043}_{-0.036}$  & $-0.037^{+0.011}_{-0.011}$ & $-0.025^{+0.015}_{-0.014}$ & $-0.025^{+0.015}_{-0.014}$\\
-PTF12fuu & $105.4^{+3.0}_{-3.0}$ & $  6.5^{+1.0}_{-1.0}$ & $ 6124^{+  5}_{-  5}$ & $  0.37^{+  0.11}_{-  0.11}$ & $0.178^{+0.026}_{-0.026}$  & $-0.057^{+0.010}_{-0.010}$ & $-0.026^{+0.014}_{-0.013}$ & $-0.026^{+0.014}_{-0.013}$\\
-SNF20070820-000 & $107.1^{+3.4}_{-3.4}$ & $ 18.7^{+1.2}_{-1.2}$ & $ 6133^{+ 13}_{- 13}$ & $ -0.28^{+  0.12}_{-  0.12}$ & $-0.054^{+0.031}_{-0.030}$  & $0.051^{+0.012}_{-0.013}$ & $-0.015^{+0.018}_{-0.016}$ & $-0.015^{+0.018}_{-0.016}$\\
-SNF20070725-001 & $108.3^{+1.9}_{-1.9}$ & $  9.5^{+1.0}_{-1.1}$ & $ 6139^{+  6}_{-  6}$ & $  0.61^{+  0.15}_{-  0.15}$ & $0.058^{+0.033}_{-0.033}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.018^{+0.016}_{-0.015}$ & $-0.018^{+0.016}_{-0.015}$\\
-SNF20071108-021 & $ 98.7^{+2.7}_{-2.7}$ & $  6.0^{+0.8}_{-0.8}$ & $ 6165^{+  5}_{-  5}$ & $  1.15^{+  0.16}_{-  0.15}$ & $-0.045^{+0.028}_{-0.028}$  & $-0.028^{+0.012}_{-0.012}$ & $0.024^{+0.015}_{-0.014}$ & $0.024^{+0.015}_{-0.014}$\\
-SNF20080914-001 & $126.4^{+1.2}_{-1.2}$ & $ 16.3^{+1.0}_{-1.0}$ & $ 6159^{+  3}_{-  3}$ & $  0.10^{+  0.14}_{-  0.14}$ & $-0.144^{+0.026}_{-0.024}$  & $0.094^{+0.012}_{-0.012}$ & $0.022^{+0.016}_{-0.015}$ & $0.022^{+0.016}_{-0.015}$\\
-SNF20060609-002 & $ 86.3^{+3.5}_{-3.5}$ & $  8.1^{+1.2}_{-1.1}$ & $ 6132^{+  4}_{-  4}$ & $  0.18^{+  0.12}_{-  0.13}$ & $-0.069^{+0.033}_{-0.032}$  & $0.192^{+0.014}_{-0.014}$ & $-0.008^{+0.018}_{-0.017}$ & $-0.008^{+0.018}_{-0.017}$\\
-SNF20050624-000 & $119.9^{+5.1}_{-5.1}$ & $  7.9^{+2.4}_{-2.6}$ & $ 6126^{+  5}_{-  5}$ & $  0.47^{+  0.29}_{-  0.29}$ & $-0.171^{+0.026}_{-0.024}$  & $-0.051^{+0.019}_{-0.017}$ & $0.022^{+0.019}_{-0.021}$ & $0.022^{+0.019}_{-0.021}$\\
-SNF20060618-023 & $ 73.3^{+4.7}_{-4.7}$ & $  5.3^{+1.6}_{-1.5}$ & $ 6140^{+ 18}_{- 18}$ & $  0.18^{+  0.16}_{-  0.16}$ & $-0.229^{+0.039}_{-0.038}$  & $0.059^{+0.020}_{-0.020}$ & $0.092^{+0.023}_{-0.022}$ & $0.092^{+0.023}_{-0.022}$\\
-SNF20080531-000 & $133.2^{+1.5}_{-1.5}$ & $ 17.2^{+0.8}_{-0.8}$ & $ 6113^{+  5}_{-  5}$ & $ -0.63^{+  0.13}_{-  0.13}$ & $0.002^{+0.024}_{-0.024}$  & $-0.040^{+0.009}_{-0.009}$ & $-0.009^{+0.012}_{-0.013}$ & $-0.009^{+0.012}_{-0.013}$\\
-SN2006do & $106.3^{+2.1}_{-2.1}$ & $ 26.8^{+1.3}_{-1.2}$ & $ 6101^{+  2}_{-  2}$ & $ -1.95^{+  0.34}_{-  0.34}$ & $-0.077^{+0.031}_{-0.030}$  & $-0.038^{+0.012}_{-0.013}$ & $0.035^{+0.018}_{-0.017}$ & $0.035^{+0.018}_{-0.017}$\\
-PTF12ikt & $110.3^{+1.5}_{-1.6}$ & $ 14.0^{+0.7}_{-0.7}$ & $ 6141^{+  4}_{-  4}$ & $ -0.40^{+  0.10}_{-  0.10}$ & $-0.023^{+0.025}_{-0.025}$  & $-0.034^{+0.009}_{-0.008}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
-SN2006dm & $ 99.6^{+1.6}_{-1.6}$ & $ 29.8^{+0.7}_{-0.7}$ & $ 6118^{+  3}_{-  3}$ & $ -2.35^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.029}$  & $-0.047^{+0.011}_{-0.011}$ & $0.047^{+0.017}_{-0.016}$ & $0.047^{+0.017}_{-0.016}$\\
-PTF13azs & $140.6^{+4.8}_{-4.8}$ & $ 15.2^{+1.3}_{-1.3}$ & $ 6124^{+ 10}_{- 10}$ & $ -0.12^{+  0.11}_{-  0.11}$ & $0.148^{+0.029}_{-0.029}$  & $0.195^{+0.012}_{-0.013}$ & $-0.037^{+0.012}_{-0.009}$ & $-0.037^{+0.012}_{-0.009}$\\
-SN2005hj & $ 80.4^{+2.4}_{-2.4}$ & $  4.4^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  2.58^{+  0.24}_{-  0.24}$ & $0.076^{+0.039}_{-0.037}$  & $0.009^{+0.018}_{-0.020}$ & $0.066^{+0.022}_{-0.022}$ & $0.066^{+0.022}_{-0.022}$\\
-PTF12iiq & $149.1^{+2.1}_{-2.2}$ & $ 24.8^{+0.8}_{-0.7}$ & $ 6048^{+  7}_{-  7}$ & $ -0.83^{+  0.10}_{-  0.11}$ & $0.005^{+0.033}_{-0.033}$  & $-0.005^{+0.019}_{-0.020}$ & $-0.034^{+0.017}_{-0.010}$ & $-0.034^{+0.017}_{-0.010}$\\
-PTF10ndc & $124.1^{+2.4}_{-2.4}$ & $  6.7^{+1.0}_{-1.0}$ & $ 6119^{+  3}_{-  3}$ & $  0.86^{+  0.14}_{-  0.14}$ & $0.007^{+0.026}_{-0.025}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.023^{+0.014}_{-0.013}$ & $-0.023^{+0.014}_{-0.013}$\\
-SNF20080919-002 & $100.4^{+6.7}_{-6.6}$ & $ 26.3^{+1.7}_{-1.7}$ & $ 6133^{+  8}_{-  8}$ & $ -1.54^{+  0.13}_{-  0.13}$ & $0.340^{+0.043}_{-0.044}$  & $-0.058^{+0.017}_{-0.014}$ & $0.114^{+0.020}_{-0.021}$ & $0.114^{+0.020}_{-0.021}$\\
-SNPGC027923 & $ 85.4^{+0.6}_{-0.6}$ & $  5.8^{+0.3}_{-0.3}$ & $ 6130^{+  4}_{-  4}$ & $  0.45^{+  0.17}_{-  0.17}$ & $0.078^{+0.032}_{-0.031}$  & $-0.077^{+0.006}_{-0.005}$ & $-0.026^{+0.015}_{-0.013}$ & $-0.026^{+0.015}_{-0.013}$\\
-SNF20070330-024 & $118.3^{+2.1}_{-2.1}$ & $  5.5^{+1.8}_{-1.8}$ & $ 6101^{+  3}_{-  3}$ & $  0.48^{+  0.19}_{-  0.21}$ & $-0.166^{+0.025}_{-0.024}$  & $-0.040^{+0.014}_{-0.014}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
-SNF20061030-010 & $131.6^{+2.2}_{-2.2}$ & $ 16.9^{+1.1}_{-1.1}$ & $ 6116^{+  4}_{-  4}$ & $ -0.10^{+  0.20}_{-  0.20}$ & $0.103^{+0.041}_{-0.041}$  & $0.049^{+0.012}_{-0.012}$ & $0.019^{+0.021}_{-0.021}$ & $0.019^{+0.021}_{-0.021}$\\
-SNhunt46 & $ 93.8^{+2.0}_{-2.0}$ & $ 11.2^{+0.6}_{-0.6}$ & $ 6133^{+  4}_{-  4}$ & $  0.22^{+  0.17}_{-  0.17}$ & $0.150^{+0.032}_{-0.032}$  & $-0.062^{+0.010}_{-0.010}$ & $0.035^{+0.016}_{-0.015}$ & $0.035^{+0.016}_{-0.015}$\\
-SN2005hc & $127.2^{+2.4}_{-2.5}$ & $  9.7^{+0.7}_{-0.7}$ & $ 6122^{+  3}_{-  3}$ & $  0.47^{+  0.16}_{-  0.15}$ & $0.137^{+0.025}_{-0.025}$  & $-0.062^{+0.008}_{-0.008}$ & $0.001^{+0.012}_{-0.012}$ & $0.001^{+0.012}_{-0.012}$\\
-LSQ12dbr & $106.9^{+0.6}_{-0.6}$ & $  6.4^{+0.6}_{-0.6}$ & $ 6137^{+  4}_{-  4}$ & $  0.86^{+  0.11}_{-  0.11}$ & $0.004^{+0.226}_{-0.109}$  & $-0.071^{+0.008}_{-0.007}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
-LSQ12hjm & $ 65.3^{+10.8}_{-11.3}$ & $ 15.3^{+1.1}_{-1.1}$ & $ 6147^{+  5}_{-  5}$ & $ -0.16^{+  0.17}_{-  0.17}$ & $0.112^{+0.030}_{-0.031}$  & $-0.062^{+0.013}_{-0.011}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
-SNF20060521-001 & $ 89.1^{+11.4}_{-12.2}$ & $ 19.1^{+1.1}_{-1.1}$ & $ 6119^{+ 10}_{-  9}$ & $ -1.70^{+  0.20}_{-  0.20}$ & $0.029^{+0.061}_{-0.059}$  & $-0.068^{+0.014}_{-0.010}$ & $0.010^{+0.019}_{-0.020}$ & $0.010^{+0.019}_{-0.020}$\\
-SNF20070630-006 & $126.3^{+3.1}_{-3.1}$ & $ 10.3^{+1.1}_{-1.2}$ & $ 6126^{+  4}_{-  4}$ & $  0.30^{+  0.11}_{-  0.11}$ & $-0.018^{+0.025}_{-0.025}$  & $-0.027^{+0.010}_{-0.010}$ & $-0.040^{+0.010}_{-0.008}$ & $-0.040^{+0.010}_{-0.008}$\\
-PTF11drz & $132.6^{+1.4}_{-1.4}$ & $ 14.9^{+0.9}_{-0.9}$ & $ 6116^{+  4}_{-  4}$ & $ -0.11^{+  0.17}_{-  0.18}$ & $-0.007^{+0.025}_{-0.026}$  & $-0.021^{+0.010}_{-0.009}$ & $-0.016^{+0.013}_{-0.013}$ & $-0.016^{+0.013}_{-0.013}$\\
-SNF20080323-009 & $ 96.0^{+2.2}_{-2.2}$ & $ 11.1^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.15^{+  0.14}_{-  0.14}$ & $-0.029^{+0.030}_{-0.029}$  & $-0.051^{+0.011}_{-0.011}$ & $-0.041^{+0.009}_{-0.008}$ & $-0.041^{+0.009}_{-0.008}$\\
-SNF20071021-000 & $167.9^{+2.2}_{-2.2}$ & $ 20.2^{+0.6}_{-0.6}$ & $ 6111^{+  4}_{-  4}$ & $ -0.66^{+  0.13}_{-  0.13}$ & $-0.105^{+0.025}_{-0.023}$  & $-0.001^{+0.010}_{-0.010}$ & $-0.004^{+0.013}_{-0.013}$ & $-0.004^{+0.013}_{-0.013}$\\
-SNNGC0927 & $155.2^{+1.3}_{-1.3}$ & $ 10.9^{+0.7}_{-0.7}$ & $ 6109^{+  4}_{-  4}$ & $  0.39^{+  0.12}_{-  0.12}$ & $-0.031^{+0.027}_{-0.027}$  & $0.039^{+0.010}_{-0.010}$ & $-0.018^{+0.014}_{-0.013}$ & $-0.018^{+0.014}_{-0.013}$\\
-SNF20060526-003 & $111.8^{+2.5}_{-2.5}$ & $  9.9^{+1.0}_{-1.0}$ & $ 6121^{+  3}_{-  3}$ & $  0.34^{+  0.13}_{-  0.13}$ & $-0.004^{+0.026}_{-0.027}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.011^{+0.014}_{-0.014}$ & $-0.011^{+0.014}_{-0.014}$\\
-SNF20080806-002 & $135.4^{+1.8}_{-1.9}$ & $  8.3^{+0.9}_{-0.9}$ & $ 6136^{+  4}_{-  4}$ & $  0.83^{+  0.14}_{-  0.14}$ & $-0.106^{+0.028}_{-0.027}$  & $0.020^{+0.010}_{-0.010}$ & $-0.036^{+0.013}_{-0.009}$ & $-0.036^{+0.013}_{-0.009}$\\
-SNF20080803-000 & $118.3^{+2.5}_{-2.6}$ & $  8.4^{+1.3}_{-1.4}$ & $ 6125^{+  4}_{-  4}$ & $  0.25^{+  0.12}_{-  0.12}$ & $-0.030^{+0.023}_{-0.024}$  & $0.100^{+0.011}_{-0.011}$ & $-0.040^{+0.009}_{-0.008}$ & $-0.040^{+0.009}_{-0.008}$\\
-SNF20080822-005 & $ 78.6^{+1.8}_{-1.8}$ & $  6.2^{+0.8}_{-0.8}$ & $ 6138^{+  4}_{-  4}$ & $  0.51^{+  0.16}_{-  0.16}$ & $-0.027^{+0.030}_{-0.030}$  & $-0.018^{+0.011}_{-0.010}$ & $0.014^{+0.015}_{-0.015}$ & $0.014^{+0.015}_{-0.015}$\\
-SNF20060618-014 & $136.8^{+2.4}_{-2.5}$ & $  9.8^{+1.1}_{-1.1}$ & $ 6113^{+  7}_{-  7}$ & $  1.20^{+  0.18}_{-  0.18}$ & $0.077^{+0.047}_{-0.047}$  & $-0.037^{+0.014}_{-0.014}$ & $0.019^{+0.025}_{-0.024}$ & $0.019^{+0.025}_{-0.024}$\\
-PTF12ghy & $100.6^{+3.5}_{-3.5}$ & $ 16.4^{+0.7}_{-0.7}$ & $ 6133^{+  3}_{-  3}$ & $ -0.58^{+  0.10}_{-  0.10}$ & $-0.138^{+0.023}_{-0.022}$  & $0.196^{+0.011}_{-0.011}$ & $0.001^{+0.013}_{-0.013}$ & $0.001^{+0.013}_{-0.013}$\\
-SNF20070531-011 & $122.2^{+2.6}_{-2.6}$ & $ 21.5^{+0.8}_{-0.8}$ & $ 6114^{+  3}_{-  4}$ & $ -1.56^{+  0.20}_{-  0.20}$ & $-0.081^{+0.027}_{-0.025}$  & $-0.032^{+0.011}_{-0.011}$ & $-0.000^{+0.015}_{-0.014}$ & $-0.000^{+0.015}_{-0.014}$\\
-SNF20070831-015 & $112.9^{+2.6}_{-2.6}$ & $  6.9^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  1.38^{+  0.16}_{-  0.16}$ & $0.042^{+0.027}_{-0.027}$  & $-0.016^{+0.010}_{-0.010}$ & $0.002^{+0.014}_{-0.014}$ & $0.002^{+0.014}_{-0.014}$\\
-SNF20070417-002 & $103.8^{+5.0}_{-4.9}$ & $ 24.1^{+1.3}_{-1.3}$ & $ 6125^{+  8}_{-  9}$ & $ -1.37^{+  0.10}_{-  0.10}$ & $-0.032^{+0.050}_{-0.044}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
-PTF11cao & $143.4^{+1.5}_{-1.6}$ & $ 19.0^{+1.1}_{-1.1}$ & $ 6104^{+  4}_{-  4}$ & $  0.20^{+  0.13}_{-  0.13}$ & $-0.014^{+0.032}_{-0.031}$  & $0.009^{+0.013}_{-0.013}$ & $-0.017^{+0.017}_{-0.015}$ & $-0.017^{+0.017}_{-0.015}$\\
-SNF20080522-000 & $ 62.1^{+3.5}_{-3.5}$ & $  3.1^{+0.8}_{-0.8}$ & $ 6130^{+  7}_{-  7}$ & $  0.99^{+  0.11}_{-  0.11}$ & $-0.021^{+0.028}_{-0.028}$  & $-0.009^{+0.012}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$\\
-PTF10qjq & $ 74.4^{+2.3}_{-2.4}$ & $ 12.0^{+0.7}_{-0.7}$ & $ 6132^{+  3}_{-  3}$ & $ -0.50^{+  0.10}_{-  0.09}$ & $-0.127^{+0.026}_{-0.024}$  & $0.049^{+0.010}_{-0.011}$ & $-0.010^{+0.015}_{-0.015}$ & $-0.010^{+0.015}_{-0.015}$\\
-PTF12dxm & $119.3^{+15.5}_{-16.8}$ & $ 31.3^{+1.9}_{-2.1}$ & $ 6136^{+  4}_{-  4}$ & $ -2.14^{+  0.18}_{-  0.18}$ & $0.034^{+0.034}_{-0.033}$  & $-0.047^{+0.027}_{-0.021}$ & $0.067^{+0.023}_{-0.024}$ & $0.067^{+0.023}_{-0.024}$\\
-SNF20061021-003 & $122.5^{+2.2}_{-2.2}$ & $ 10.8^{+1.5}_{-1.5}$ & $ 6131^{+  4}_{-  4}$ & $  0.39^{+  0.15}_{-  0.15}$ & $-0.012^{+0.035}_{-0.033}$  & $0.036^{+0.014}_{-0.014}$ & $0.047^{+0.019}_{-0.017}$ & $0.047^{+0.019}_{-0.017}$\\
-SNF20080510-005 & $112.2^{+2.5}_{-2.5}$ & $  7.0^{+1.0}_{-1.0}$ & $ 6117^{+  4}_{-  4}$ & $  1.68^{+  0.22}_{-  0.22}$ & $0.116^{+0.030}_{-0.030}$  & $-0.029^{+0.013}_{-0.015}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
-SNF20080507-000 & $ 98.4^{+1.6}_{-1.6}$ & $  8.0^{+1.7}_{-1.6}$ & $ 6142^{+  5}_{-  5}$ & $  0.56^{+  0.18}_{-  0.18}$ & $-0.126^{+0.023}_{-0.022}$  & $0.063^{+0.014}_{-0.013}$ & $-0.003^{+0.015}_{-0.014}$ & $-0.003^{+0.015}_{-0.014}$\\
-SNF20080913-031 & $117.9^{+1.5}_{-1.5}$ & $ 14.7^{+1.6}_{-1.6}$ & $ 6159^{+  5}_{-  5}$ & $  0.49^{+  0.17}_{-  0.17}$ & $-0.048^{+0.067}_{-0.052}$  & $-0.003^{+0.015}_{-0.015}$ & $-0.009^{+0.020}_{-0.018}$ & $-0.009^{+0.020}_{-0.018}$\\
-SNF20080510-001 & $118.9^{+2.0}_{-2.1}$ & $ 15.0^{+1.1}_{-1.0}$ & $ 6115^{+  4}_{-  4}$ & $  0.34^{+  0.14}_{-  0.14}$ & $0.001^{+0.026}_{-0.026}$  & $-0.058^{+0.011}_{-0.012}$ & $-0.032^{+0.012}_{-0.011}$ & $-0.032^{+0.012}_{-0.011}$\\
-SNF20070712-003 & $108.1^{+2.7}_{-2.6}$ & $ 14.1^{+0.9}_{-0.9}$ & $ 6157^{+  6}_{-  6}$ & $  0.62^{+  0.14}_{-  0.14}$ & $-0.034^{+0.030}_{-0.029}$  & $-0.052^{+0.010}_{-0.011}$ & $-0.021^{+0.015}_{-0.014}$ & $-0.021^{+0.015}_{-0.014}$\\
+SN2013be & $103.0^{+1.8}_{-1.7}$ & $ 12.1^{+0.9}_{-0.9}$ & $ 6141^{+  5}_{-  5}$ & $  0.39^{+  0.16}_{-  0.16}$ & $-0.109^{+0.026}_{-0.024}$  & $0.015^{+0.009}_{-0.010}$ & $-0.025^{+0.014}_{-0.012}$ & $-0.025^{+0.014}_{-0.012}$\\
+SN2013bs & $ 86.9^{+1.5}_{-1.4}$ & $ 21.2^{+0.7}_{-0.7}$ & $ 6136^{+  3}_{-  3}$ & $ -1.49^{+  0.16}_{-  0.16}$ & $0.055^{+0.029}_{-0.030}$  & $0.036^{+0.013}_{-0.012}$ & $0.020^{+0.016}_{-0.014}$ & $0.020^{+0.016}_{-0.014}$\\
+SNBOSS38 & $ 57.1^{+0.4}_{-0.4}$ & $ 17.8^{+0.3}_{-0.3}$ & $ 6127^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $0.018^{+0.038}_{-0.039}$  & $0.017^{+0.021}_{-0.023}$ & $-0.002^{+0.019}_{-0.020}$ & $-0.002^{+0.019}_{-0.020}$\\
+TBD & $155.2^{+1.3}_{-1.3}$ & $ 10.9^{+0.7}_{-0.7}$ & $ 6109^{+  4}_{-  4}$ & $  0.39^{+  0.12}_{-  0.12}$ & $-0.031^{+0.027}_{-0.027}$  & $0.039^{+0.010}_{-0.010}$ & $-0.018^{+0.014}_{-0.013}$ & $-0.018^{+0.014}_{-0.013}$\\
 \enddata

### 2018-09-28 submit/fix.tex
changes of Ariel

@@
-\documentclass{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
+\documentclass[trackchanges]{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
@@
 2017ApJ...846...58H} and circumstellar dust \citep{2005ApJ...635L..33W,
-2008ApJ...686L.103G} produce color variations beyond those due to interstellar dust.  A third color
+2008ApJ...686L.103G} produce
+color variations beyond those due to interstellar dust. 
+\added{
+\citet{doi:10.1093/mnras/sty1619} report time-variation in apparent dust properties
+though \citet{2017ApJ...850...84H} argue that the expected observational effect of the non-uniform ISM should be weak.
+}
+A third color
 parameter is therefore expected.

### 2018-10-10 submit/fix.tex
last comments by Greg

@@
 though \citet{2017ApJ...850...84H} argue that the expected observational effect of the non-uniform ISM should be weak.
+While  \citet{2017ApJ...850...84H} have shown that ISM structure will generally be insufficient to result in detectable dust transmission variations as a SN expands, a foreground ISM dust sheet close enough to a SN can lead to light echoes, e.g.\ as reported in \citet{doi:10.1093/mnras/sty1619}, that can introduce time dependence in the SN flux and resulting colors.
  }
@@
 SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.10 \pm   0.11$\\
-TBD & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ & $  0.41 \pm   0.14$\\
+SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ & $  0.41 \pm   0.14$\\
 \enddata
@@
 SNBOSS38 & $ 57.1^{+0.4}_{-0.4}$ & $ 17.8^{+0.3}_{-0.3}$ & $ 6127^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $0.018^{+0.038}_{-0.039}$  & $0.017^{+0.021}_{-0.023}$ & $-0.002^{+0.019}_{-0.020}$ & $-0.002^{+0.019}_{-0.020}$\\
-TBD & $155.2^{+1.3}_{-1.3}$ & $ 10.9^{+0.7}_{-0.7}$ & $ 6109^{+  4}_{-  4}$ & $  0.39^{+  0.12}_{-  0.12}$ & $-0.031^{+0.027}_{-0.027}$  & $0.039^{+0.010}_{-0.010}$ & $-0.018^{+0.014}_{-0.013}$ & $-0.018^{+0.014}_{-0.013}$\\
+SNNGC0927 & $155.2^{+1.3}_{-1.3}$ & $ 10.9^{+0.7}_{-0.7}$ & $ 6109^{+  4}_{-  4}$ & $  0.39^{+  0.12}_{-  0.12}$ & $-0.031^{+0.027}_{-0.027}$  & $0.039^{+0.010}_{-0.010}$ & $-0.018^{+0.014}_{-0.013}$ & $-0.018^{+0.014}_{-0.013}$\\
 \enddata

### 2018-10-12 submit/fix.tex
Yannick's comments

@@
 \added{
-\citet{doi:10.1093/mnras/sty1619} report time-variation in apparent dust properties
-though \citet{2017ApJ...850...84H} argue that the expected observational effect of the non-uniform ISM should be weak.
 While  \citet{2017ApJ...850...84H} have shown that ISM structure will generally be insufficient to result in detectable dust transmission variations as a SN expands, a foreground ISM dust sheet close enough to a SN can lead to light echoes, e.g.\ as reported in \citet{doi:10.1093/mnras/sty1619}, that can introduce time dependence in the SN flux and resulting colors.
@@
 sample population, and
-the extremely red SN2012cu  who has a SALT2 $C \approx 1$ \citep{2017ApJ...836..157H} that is several times larger than the colors
+the extremely red SN2012cu  which has a SALT2 $C \approx 1$ \citep{2017ApJ...836..157H} that is several times larger than the colors
 of in-sample supernovae.
@@
 \startdata
-%SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.85 \pm   0.34$\\
-%PTF10zdk & $149.7 \pm 1.2$ & $ 14.3 \pm 0.6$& $ 6150 \pm   3$ & $-28.61 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.32 \pm   0.02$& $-28.08 \pm   0.02$& $-27.40 \pm   0.02$ & $  0.18 \pm   0.17$\\
-%SNF20080815-017 & $ 63.8 \pm 21.5$ & $ 27.6 \pm 3.8$& $ 6132 \pm   6$ & $-29.04 \pm   0.07$ & $-28.79 \pm   0.07$& $-28.32 \pm   0.07$& $-28.12 \pm   0.07$& $-27.41 \pm   0.07$ & $ -1.78 \pm   0.18$\\
-%PTF09dnl & $129.9 \pm 0.9$ & $  9.5 \pm 0.7$& $ 6093 \pm   3$ & $-29.23 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.72 \pm   0.01$& $-28.44 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.72 \pm   0.13$\\
-%SN2010ex & $114.4 \pm 0.9$ & $  8.4 \pm 0.4$& $ 6129 \pm   6$ & $-29.26 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.50 \pm   0.01$& $-28.20 \pm   0.01$& $-27.44 \pm   0.01$ & $  0.27 \pm   0.14$\\
-%PTF09dnp & $ 64.9 \pm 4.5$ & $ 16.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.55 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.68 \pm   0.02$& $-28.48 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.74 \pm   0.24$\\
-%PTF11bnx & $151.4 \pm 3.0$ & $ 13.9 \pm 1.1$& $ 6142 \pm   5$ & $-28.63 \pm   0.02$ & $-28.57 \pm   0.01$& $-28.20 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -0.07 \pm   0.17$\\
-%PTF12jqh & $151.9 \pm 1.5$ & $  7.9 \pm 0.7$& $ 6116 \pm  10$ & $-29.37 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.71 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.69 \pm   0.19$\\
-%SNF20080802-006 & $108.2 \pm 6.0$ & $ 20.6 \pm 1.9$& $ 6122 \pm   5$ & $-29.02 \pm   0.06$ & $-28.80 \pm   0.06$& $-28.40 \pm   0.06$& $-28.20 \pm   0.06$& $-27.50 \pm   0.06$ & $ -1.56 \pm   0.13$\\
-%PTF10xyt & $123.7 \pm 6.6$ & $ 16.4 \pm 4.3$& $ 6101 \pm   4$ & $-28.26 \pm   0.02$ & $-28.20 \pm   0.02$& $-27.93 \pm   0.02$& $-27.74 \pm   0.02$& $-27.22 \pm   0.04$ & $  0.03 \pm   0.21$\\
-%PTF11qmo & $101.7 \pm 1.1$ & $  7.7 \pm 0.7$& $ 6150 \pm   8$ & $-29.77 \pm   0.02$ & $-29.43 \pm   0.02$& $-28.97 \pm   0.02$& $-28.64 \pm   0.02$& $-27.93 \pm   0.02$ & $ -0.00 \pm   0.34$\\
-%SNF20070331-025 & $119.8 \pm 7.4$ & $ 14.2 \pm 2.7$& $ 6120 \pm  10$ & $-28.94 \pm   0.02$ & $-28.75 \pm   0.02$& $-28.32 \pm   0.02$& $-28.07 \pm   0.02$& $-27.31 \pm   0.02$ & $ -1.28 \pm   0.16$\\
-%SNF20070818-001 & $157.5 \pm 7.5$ & $ 16.7 \pm 1.8$& $ 6115 \pm   5$ & $-28.97 \pm   0.02$ & $-28.96 \pm   0.01$& $-28.61 \pm   0.01$& $-28.37 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.15 \pm   0.16$\\
-%SNBOSS38 & $ 57.1 \pm 0.4$ & $ 17.9 \pm 0.3$& $ 6127 \pm   3$ & $-29.20 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.47 \pm   0.01$& $-28.23 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.10 \pm   0.11$\\
-%SN2006ob & $ 90.0 \pm 16.5$ & $ 26.5 \pm 1.5$& $ 6112 \pm   5$ & $-29.11 \pm   0.02$ & $-28.82 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.54 \pm   0.01$ & $ -2.45 \pm   0.28$\\
-%PTF12eer & $165.6 \pm 10.7$ & $ 12.7 \pm 2.8$& $ 6150 \pm  10$ & $-28.76 \pm   0.01$ & $-28.76 \pm   0.01$& $-28.40 \pm   0.01$& $-28.17 \pm   0.01$& $-27.45 \pm   0.02$ & $  0.68 \pm   0.16$\\
-%PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ & $ -0.62 \pm   0.13$\\
-%SNF20080514-002 & $ 83.2 \pm 0.7$ & $ 19.4 \pm 0.6$& $ 6131 \pm   3$ & $-29.30 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.44 \pm   0.01$& $-28.17 \pm   0.01$& $-27.49 \pm   0.01$ & $ -1.57 \pm   0.11$\\
-%PTF12evo & $129.2 \pm 2.8$ & $  9.1 \pm 1.3$& $ 6156 \pm   4$ & $-29.14 \pm   0.02$ & $-28.98 \pm   0.01$& $-28.56 \pm   0.01$& $-28.28 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.74 \pm   0.15$\\
-%SNF20080614-010 & $125.4 \pm 5.1$ & $ 26.9 \pm 1.6$& $ 6128 \pm   3$ & $-29.04 \pm   0.04$ & $-28.81 \pm   0.04$& $-28.38 \pm   0.04$& $-28.16 \pm   0.04$& $-27.57 \pm   0.04$ & $ -2.12 \pm   0.17$\\
-%PTF10icb & $104.8 \pm 0.9$ & $ 12.7 \pm 0.3$& $ 6138 \pm   3$ & $-28.58 \pm   0.02$ & $-28.36 \pm   0.02$& $-27.98 \pm   0.02$& $-27.77 \pm   0.02$& $-27.17 \pm   0.02$ & $  0.37 \pm   0.13$\\
-%PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ & $  1.21 \pm   0.20$\\
-%SNNGC4424 & $109.0 \pm 0.3$ & $  8.6 \pm 0.1$& $ 6138 \pm   2$ & $-28.35 \pm   0.01$ & $-28.15 \pm   0.01$& $-27.79 \pm   0.01$& $-27.58 \pm   0.01$& $-26.97 \pm   0.01$ & $  0.37 \pm   0.12$\\
-%SNF20080516-022 & $100.1 \pm 2.1$ & $ 13.7 \pm 1.1$& $ 6158 \pm   3$ & $-29.46 \pm   0.01$ & $-29.19 \pm   0.01$& $-28.71 \pm   0.01$& $-28.39 \pm   0.01$& $-27.77 \pm   0.01$ & $  0.20 \pm   0.14$\\
-%PTF12hwb & $ 21.1 \pm 78.0$ & $ -1.8 \pm 8.9$& $ 6090 \pm  14$ & $-28.32 \pm   0.02$ & $-28.24 \pm   0.02$& $-28.03 \pm   0.02$& $-27.79 \pm   0.02$& $-27.05 \pm   0.04$ & $  1.34 \pm   0.17$\\
-%PTF10qyz & $106.4 \pm 2.1$ & $ 23.0 \pm 1.0$& $ 6120 \pm   5$ & $-29.05 \pm   0.17$ & $-28.92 \pm   0.17$& $-28.41 \pm   0.17$& $-28.14 \pm   0.17$& $-27.30 \pm   0.17$ & $ -1.09 \pm   0.16$\\
-%SNF20060907-000 & $106.1 \pm 10.4$ & $ 17.0 \pm 0.9$& $ 6149 \pm   4$ & $-29.54 \pm   0.02$ & $-29.28 \pm   0.01$& $-28.76 \pm   0.01$& $-28.42 \pm   0.01$& $-27.74 \pm   0.04$ & $  0.17 \pm   0.17$\\
-%LSQ12fxd & $122.9 \pm 1.7$ & $ 11.4 \pm 0.8$& $ 6119 \pm   4$ & $-29.62 \pm   0.07$ & $-29.39 \pm   0.07$& $-28.95 \pm   0.07$& $-28.64 \pm   0.07$& $-27.91 \pm   0.07$ & $  0.05 \pm   0.15$\\
-%SNF20080821-000 & $105.1 \pm 2.2$ & $  8.6 \pm 1.3$& $ 6121 \pm   4$ & $-29.34 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.73 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.70 \pm   0.19$\\
-%SNF20070802-000 & $158.3 \pm 3.3$ & $ 16.3 \pm 1.7$& $ 6102 \pm   5$ & $-28.90 \pm   0.01$ & $-28.81 \pm   0.01$& $-28.45 \pm   0.01$& $-28.22 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.08 \pm   0.16$\\
-%PTF10wnm & $105.8 \pm 2.3$ & $  6.5 \pm 1.0$& $ 6124 \pm   3$ & $-29.38 \pm   0.01$ & $-29.07 \pm   0.01$& $-28.68 \pm   0.01$& $-28.37 \pm   0.01$& $-27.69 \pm   0.01$ & $  0.63 \pm   0.16$\\
-%PTF10mwb & $116.5 \pm 1.2$ & $ 19.8 \pm 0.9$& $ 6138 \pm   2$ & $-29.02 \pm   0.07$ & $-28.84 \pm   0.07$& $-28.40 \pm   0.07$& $-28.14 \pm   0.07$& $-27.52 \pm   0.07$ & $ -0.68 \pm   0.10$\\
-%SN2010dt & $116.2 \pm 14.9$ & $ 15.5 \pm 0.7$& $ 6138 \pm   6$ & $-29.30 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.64 \pm   0.01$& $-28.35 \pm   0.01$& $-27.63 \pm   0.01$ & $ -0.03 \pm   0.10$\\
-%SNF20080623-001 & $149.1 \pm 1.4$ & $ 14.9 \pm 0.7$& $ 6131 \pm   3$ & $-29.11 \pm   0.01$ & $-28.97 \pm   0.01$& $-28.50 \pm   0.01$& $-28.22 \pm   0.01$& $-27.46 \pm   0.01$ & $  0.01 \pm   0.13$\\
-%LSQ12fhe & $ 42.8 \pm 1.2$ & $  4.0 \pm 3.1$& $ 6108 \pm   4$ & $-29.76 \pm   0.02$ & $-29.40 \pm   0.02$& $-29.04 \pm   0.02$& $-28.74 \pm   0.02$& $-28.11 \pm   0.02$ & $  1.07 \pm   0.19$\\
-%PTF11bju & $ 30.2 \pm 4.4$ & $  4.0 \pm 3.0$& $ 6139 \pm   5$ & $-29.47 \pm   0.02$ & $-29.10 \pm   0.01$& $-28.75 \pm   0.01$& $-28.45 \pm   0.01$& $-27.87 \pm   0.01$ & $  1.04 \pm   0.20$\\
-%PTF09fox & $117.6 \pm 2.7$ & $  9.1 \pm 1.0$& $ 6116 \pm   3$ & $-29.44 \pm   0.03$ & $-29.21 \pm   0.03$& $-28.72 \pm   0.03$& $-28.42 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.68 \pm   0.27$\\
-%PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ & $ -1.72 \pm   0.29$\\
-%SNF20070810-004 & $126.7 \pm 1.8$ & $ 21.1 \pm 1.1$& $ 6118 \pm   7$ & $-29.22 \pm   0.01$ & $-29.10 \pm   0.01$& $-28.63 \pm   0.01$& $-28.34 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.10 \pm   0.12$\\
-%PTF11mty & $111.4 \pm 2.3$ & $ 10.6 \pm 1.5$& $ 6138 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.46 \pm   0.01$& $-27.82 \pm   0.01$ & $  0.83 \pm   0.16$\\
-%SNF20080512-010 & $ 95.3 \pm 3.5$ & $ 23.3 \pm 1.5$& $ 6129 \pm   5$ & $-29.22 \pm   0.08$ & $-28.96 \pm   0.08$& $-28.50 \pm   0.08$& $-28.26 \pm   0.08$& $-27.56 \pm   0.08$ & $ -1.24 \pm   0.26$\\
-%PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ & $  0.60 \pm   0.15$\\
-%PTF10tce & $135.7 \pm 1.1$ & $ 11.2 \pm 1.5$& $ 6090 \pm   4$ & $-29.13 \pm   0.02$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.43 \pm   0.14$\\
-%SNF20061020-000 & $ 95.4 \pm 18.8$ & $ 24.1 \pm 1.0$& $ 6120 \pm   5$ & $-29.01 \pm   0.03$ & $-28.78 \pm   0.03$& $-28.35 \pm   0.03$& $-28.17 \pm   0.03$& $-27.54 \pm   0.03$ & $ -1.67 \pm   0.20$\\
-%SN2005ir & $115.6 \pm 2.8$ & $ 13.5 \pm 6.9$& $ 6069 \pm   5$ & $-29.33 \pm   0.02$ & $-29.12 \pm   0.02$& $-28.84 \pm   0.02$& $-28.49 \pm   0.02$& $-27.77 \pm   0.02$ & $  1.71 \pm   0.69$\\
-%SNF20080717-000 & $ 93.3 \pm 2.6$ & $  8.3 \pm 2.2$& $ 6104 \pm   3$ & $-28.58 \pm   0.01$ & $-28.47 \pm   0.01$& $-28.29 \pm   0.01$& $-28.05 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.70 \pm   0.14$\\
-%PTF12ena & $101.1 \pm 1.6$ & $  7.4 \pm 1.0$& $ 6129 \pm   4$ & $-28.01 \pm   0.01$ & $-28.00 \pm   0.01$& $-27.85 \pm   0.01$& $-27.77 \pm   0.01$& $-27.31 \pm   0.01$ & $  0.65 \pm   0.16$\\
-%PTF13anh & $166.8 \pm 1.8$ & $ 21.8 \pm 1.2$& $ 6175 \pm   4$ & $-28.67 \pm   0.20$ & $-28.74 \pm   0.20$& $-28.30 \pm   0.20$& $-28.05 \pm   0.20$& $-27.28 \pm   0.20$ & $ -0.28 \pm   0.17$\\
-%CSS110918\_01 & $110.6 \pm 1.0$ & $  8.0 \pm 1.3$& $ 6101 \pm   2$ & $-29.88 \pm   0.76$ & $-29.58 \pm   0.76$& $-29.09 \pm   0.76$& $-28.71 \pm   0.76$& $-27.91 \pm   0.76$ & $  0.92 \pm   0.17$\\
-%SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ & $ -1.39 \pm   0.19$\\
-%SNF20070506-006 & $ 94.1 \pm 1.3$ & $  6.7 \pm 0.6$& $ 6153 \pm   3$ & $-29.72 \pm   0.01$ & $-29.39 \pm   0.01$& $-28.97 \pm   0.01$& $-28.64 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.17 \pm   0.13$\\
-%SNF20070403-001 & $105.9 \pm 5.4$ & $ 18.3 \pm 1.8$& $ 6124 \pm   4$ & $-29.23 \pm   0.02$ & $-29.04 \pm   0.01$& $-28.63 \pm   0.01$& $-28.35 \pm   0.01$& $-27.62 \pm   0.01$ & $ -0.54 \pm   0.13$\\
-%PTF10hmv & $109.6 \pm 1.3$ & $  8.9 \pm 0.7$& $ 6143 \pm   3$ & $-28.54 \pm   0.01$ & $-28.40 \pm   0.01$& $-28.11 \pm   0.01$& $-27.89 \pm   0.01$& $-27.31 \pm   0.01$ & $  1.39 \pm   0.18$\\
-%SNF20071015-000 & $105.0 \pm 3.2$ & $  6.9 \pm 1.1$& $ 6124 \pm   7$ & $-27.89 \pm   0.02$ & $-27.82 \pm   0.02$& $-27.69 \pm   0.02$& $-27.63 \pm   0.02$& $-27.16 \pm   0.04$ & $  1.36 \pm   0.37$\\
-%SNhunt89 & $ 88.0 \pm 2.7$ & $ 32.2 \pm 1.9$& $ 6111 \pm   7$ & $-28.37 \pm   0.03$ & $-28.26 \pm   0.03$& $-27.92 \pm   0.03$& $-27.77 \pm   0.03$& $-27.13 \pm   0.03$ & $ -1.83 \pm   0.18$\\
-%SNF20070902-021 & $108.9 \pm 3.5$ & $ 17.1 \pm 1.0$& $ 6131 \pm   6$ & $-29.25 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.56 \pm   0.02$& $-28.32 \pm   0.01$& $-27.65 \pm   0.02$ & $ -0.43 \pm   0.10$\\
-%PTF09dlc & $143.5 \pm 2.2$ & $ 10.2 \pm 0.9$& $ 6143 \pm   3$ & $-29.38 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.69 \pm   0.01$& $-28.40 \pm   0.01$& $-27.62 \pm   0.01$ & $  0.11 \pm   0.12$\\
-%PTF13ajv & $150.5 \pm 8.9$ & $ 46.3 \pm 8.6$& $ 6110 \pm  21$ & $-28.70 \pm   0.02$ & $-28.61 \pm   0.02$& $-28.16 \pm   0.02$& $-27.91 \pm   0.02$& $-27.07 \pm   0.04$ & $ -1.59 \pm   0.22$\\
-%SNF20080919-000 & $114.7 \pm 2.8$ & $  9.4 \pm 0.9$& $ 6145 \pm   5$ & $-28.53 \pm   0.02$ & $-28.41 \pm   0.01$& $-28.11 \pm   0.01$& $-27.99 \pm   0.01$& $-27.38 \pm   0.01$ & $ -0.13 \pm   0.11$\\
-%SNF20080919-001 & $ 85.0 \pm 1.1$ & $  6.0 \pm 0.4$& $ 6150 \pm   5$ & $-29.73 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.72 \pm   0.01$& $-28.07 \pm   0.01$ & $  0.84 \pm   0.18$\\
-%SN2010kg & $ 95.1 \pm 28.5$ & $ 21.7 \pm 0.7$& $ 6077 \pm   5$ & $-28.85 \pm   0.01$ & $-28.74 \pm   0.01$& $-28.41 \pm   0.01$& $-28.20 \pm   0.01$& $-27.47 \pm   0.01$ & $ -2.26 \pm   0.40$\\
-%SNF20080714-008 & $134.8 \pm 15.7$ & $ 19.7 \pm 3.7$& $ 6100 \pm   6$ & $-28.56 \pm   0.02$ & $-28.63 \pm   0.01$& $-28.32 \pm   0.01$& $-28.13 \pm   0.01$& $-27.42 \pm   0.01$ & $  0.01 \pm   0.15$\\
-%SNF20070714-007 & $129.6 \pm 5.6$ & $ 31.1 \pm 23.8$& $ 6146 \pm   5$ & $-27.88 \pm   0.02$ & $-28.12 \pm   0.01$& $-28.02 \pm   0.01$& $-27.86 \pm   0.01$& $-27.24 \pm   0.03$ & $ -1.10 \pm   0.13$\\
-%SNF20080522-011 & $122.1 \pm 1.7$ & $  8.3 \pm 0.5$& $ 6125 \pm   3$ & $-29.63 \pm   0.01$ & $-29.38 \pm   0.01$& $-28.92 \pm   0.01$& $-28.60 \pm   0.01$& $-27.88 \pm   0.01$ & $  0.81 \pm   0.19$\\
-%SNF20061111-002 & $110.8 \pm 10.7$ & $ 20.4 \pm 1.0$& $ 6145 \pm   6$ & $-29.16 \pm   0.01$ & $-28.99 \pm   0.01$& $-28.59 \pm   0.01$& $-28.29 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.27 \pm   0.21$\\
-%SNNGC6343 & $ 87.0 \pm 1.4$ & $ 20.7 \pm 0.7$& $ 6136 \pm   3$ & $-28.78 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.30 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.01$ & $ -2.09 \pm   0.25$\\
-%SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ & $  0.74 \pm   0.29$\\
-%SNF20080825-010 & $102.4 \pm 13.4$ & $ 19.2 \pm 0.6$& $ 6116 \pm   4$ & $-29.46 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.71 \pm   0.01$& $-28.47 \pm   0.01$& $-27.83 \pm   0.01$ & $ -0.77 \pm   0.18$\\
-%PTF10ufj & $141.1 \pm 3.4$ & $ 11.7 \pm 1.2$& $ 6131 \pm   6$ & $-29.28 \pm   0.15$ & $-29.16 \pm   0.15$& $-28.72 \pm   0.15$& $-28.41 \pm   0.15$& $-27.65 \pm   0.15$ & $  0.53 \pm   0.16$\\
-%PTF10wof & $129.6 \pm 2.7$ & $ 17.3 \pm 1.0$& $ 6102 \pm   2$ & $-28.91 \pm   0.01$ & $-28.84 \pm   0.01$& $-28.46 \pm   0.01$& $-28.18 \pm   0.01$& $-27.43 \pm   0.01$ & $  0.16 \pm   0.13$\\
-%SNF20080918-000 & $146.8 \pm 3.5$ & $  7.5 \pm 2.5$& $ 6110 \pm   5$ & $-28.79 \pm   0.02$ & $-28.65 \pm   0.02$& $-28.35 \pm   0.02$& $-28.12 \pm   0.02$& $-27.46 \pm   0.02$ & $  1.50 \pm   0.30$\\
-%SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ & $  1.24 \pm   0.26$\\
-%SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ & $ -0.31 \pm   0.17$\\
-%CSS130502\_01 & $ 91.5 \pm 10.9$ & $ 15.6 \pm 0.5$& $ 6128 \pm   3$ & $-29.43 \pm   0.02$ & $-29.09 \pm   0.02$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.62 \pm   0.04$ & $ -0.00 \pm   0.24$\\
-%SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ & $ -1.04 \pm   0.16$\\
-%SNPGC51271 & $ 92.1 \pm 16.5$ & $ 21.1 \pm 0.7$& $ 6121 \pm   2$ & $-29.28 \pm   0.02$ & $-28.95 \pm   0.02$& $-28.46 \pm   0.02$& $-28.20 \pm   0.02$& $-27.62 \pm   0.04$ & $ -2.08 \pm   0.18$\\
-%PTF11pdk & $128.6 \pm 2.8$ & $ 15.6 \pm 1.7$& $ 6153 \pm   5$ & $-29.35 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.32 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.06 \pm   0.19$\\
-%SNF20060511-014 & $102.6 \pm 2.8$ & $ 15.6 \pm 1.1$& $ 6141 \pm   8$ & $-29.16 \pm   0.07$ & $-29.04 \pm   0.06$& $-28.56 \pm   0.06$& $-28.30 \pm   0.06$& $-27.63 \pm   0.06$ & $ -0.68 \pm   0.18$\\
-%SNF20080612-003 & $120.0 \pm 1.1$ & $  7.3 \pm 0.6$& $ 6123 \pm   3$ & $-29.64 \pm   0.02$ & $-29.41 \pm   0.02$& $-28.99 \pm   0.02$& $-28.70 \pm   0.02$& $-28.00 \pm   0.02$ & $  0.71 \pm   0.21$\\
-%SNF20080626-002 & $130.0 \pm 1.0$ & $  6.1 \pm 4.2$& $ 6111 \pm   3$ & $-29.42 \pm   0.01$ & $-29.24 \pm   0.01$& $-28.84 \pm   0.01$& $-28.52 \pm   0.01$& $-27.76 \pm   0.01$ & $  1.04 \pm   0.23$\\
-%SNF20060621-015 & $111.9 \pm 1.3$ & $  9.8 \pm 0.7$& $ 6144 \pm   3$ & $-29.63 \pm   0.01$ & $-29.36 \pm   0.01$& $-28.88 \pm   0.01$& $-28.54 \pm   0.01$& $-27.81 \pm   0.01$ & $  0.43 \pm   0.20$\\
-%SNF20080920-000 & $135.2 \pm 1.4$ & $  5.6 \pm 1.6$& $ 6085 \pm   3$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.02$& $-28.79 \pm   0.02$& $-28.49 \pm   0.02$& $-27.74 \pm   0.02$ & $  1.17 \pm   0.34$\\
-%SN2007cq & $ 65.8 \pm 4.1$ & $ 10.2 \pm 0.9$& $ 6137 \pm   3$ & $-29.53 \pm   0.02$ & $-29.30 \pm   0.02$& $-28.89 \pm   0.02$& $-28.56 \pm   0.02$& $-27.90 \pm   0.02$ & $ -0.43 \pm   0.16$\\
-%SNF20080918-004 & $ 87.8 \pm 7.2$ & $ 21.5 \pm 0.9$& $ 6141 \pm   4$ & $-29.00 \pm   0.22$ & $-28.82 \pm   0.22$& $-28.37 \pm   0.22$& $-28.13 \pm   0.22$& $-27.43 \pm   0.22$ & $ -1.27 \pm   0.18$\\
-%CSS120424\_01 & $138.1 \pm 2.1$ & $ 11.7 \pm 0.7$& $ 6138 \pm   3$ & $-29.40 \pm   0.02$ & $-29.23 \pm   0.02$& $-28.77 \pm   0.01$& $-28.45 \pm   0.02$& $-27.68 \pm   0.02$ & $  0.76 \pm   0.19$\\
-%SNF20080610-000 & $119.9 \pm 10.4$ & $ 16.4 \pm 1.7$& $ 6131 \pm   6$ & $-29.05 \pm   0.07$ & $-28.92 \pm   0.07$& $-28.50 \pm   0.07$& $-28.22 \pm   0.07$& $-27.55 \pm   0.07$ & $  0.12 \pm   0.16$\\
-%SNF20070701-005 & $101.8 \pm 2.6$ & $ 12.4 \pm 1.0$& $ 6158 \pm   5$ & $-29.46 \pm   0.02$ & $-29.27 \pm   0.02$& $-28.87 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  0.06 \pm   0.17$\\
-%SN2007kk & $128.5 \pm 1.4$ & $ 10.6 \pm 1.0$& $ 6098 \pm   4$ & $-29.48 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-27.77 \pm   0.02$ & $  0.52 \pm   0.18$\\
-%SNF20060908-004 & $114.4 \pm 1.2$ & $ 12.6 \pm 0.6$& $ 6136 \pm   3$ & $-29.59 \pm   0.23$ & $-29.34 \pm   0.23$& $-28.91 \pm   0.23$& $-28.58 \pm   0.23$& $-27.87 \pm   0.23$ & $  0.70 \pm   0.19$\\
-%SNF20080909-030 & $ 93.7 \pm 1.0$ & $  7.8 \pm 0.4$& $ 6171 \pm   3$ & $-29.38 \pm   0.02$ & $-29.12 \pm   0.01$& $-28.74 \pm   0.01$& $-28.44 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.17 \pm   0.16$\\
-%PTF11bgv & $ 79.4 \pm 3.2$ & $ 12.6 \pm 0.7$& $ 6146 \pm   3$ & $-28.90 \pm   0.02$ & $-28.62 \pm   0.01$& $-28.27 \pm   0.01$& $-28.08 \pm   0.01$& $-27.54 \pm   0.01$ & $ -0.33 \pm   0.12$\\
-%SNNGC2691 & $ 39.0 \pm 22.2$ & $  4.5 \pm 0.2$& $ 6139 \pm   8$ & $-29.46 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.75 \pm   0.02$& $-28.49 \pm   0.02$& $-27.93 \pm   0.02$ & $  0.98 \pm   0.18$\\
-%PTF13asv & $ 75.6 \pm 1.1$ & $  2.2 \pm 0.4$& $ 6148 \pm   4$ & $-29.92 \pm   0.32$ & $-29.49 \pm   0.32$& $-29.02 \pm   0.32$& $-28.63 \pm   0.32$& $-27.90 \pm   0.32$ & $  0.50 \pm   0.11$\\
-%SNF20070806-026 & $ 98.8 \pm 12.1$ & $ 25.9 \pm 0.7$& $ 6114 \pm   7$ & $-29.14 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.44 \pm   0.02$& $-28.21 \pm   0.02$& $-27.49 \pm   0.02$ & $ -1.73 \pm   0.17$\\
-%SNF20070427-001 & $ 81.3 \pm 2.3$ & $  6.3 \pm 0.9$& $ 6142 \pm   5$ & $-29.89 \pm   0.02$ & $-29.46 \pm   0.02$& $-28.97 \pm   0.02$& $-28.62 \pm   0.02$& $-27.97 \pm   0.02$ & $  0.62 \pm   0.21$\\
-%SNF20061108-004 & $129.5 \pm 5.6$ & $  6.3 \pm 2.5$& $ 6110 \pm   6$ & $-29.53 \pm   0.02$ & $-29.31 \pm   0.02$& $-28.95 \pm   0.02$& $-28.60 \pm   0.02$& $-27.96 \pm   0.02$ & $  2.14 \pm   0.42$\\
-%SNF20060912-000 & $106.5 \pm 1.8$ & $ 21.4 \pm 1.7$& $ 6163 \pm   7$ & $-28.98 \pm   0.02$ & $-28.92 \pm   0.02$& $-28.66 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $  0.24 \pm   0.20$\\
-%CSS110918\_02 & $109.1 \pm 9.4$ & $ 15.0 \pm 0.6$& $ 6137 \pm   3$ & $-29.36 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.69 \pm   0.01$& $-28.41 \pm   0.01$& $-27.70 \pm   0.01$ & $ -0.27 \pm   0.17$\\
-%SNF20080918-002 & $ 97.7 \pm 2.8$ & $ 12.6 \pm 1.4$& $ 6141 \pm   6$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.61 \pm   0.02$& $-28.34 \pm   0.02$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.09$\\
-%SNIC3573 & $102.7 \pm 1.8$ & $ 11.9 \pm 1.0$& $ 6142 \pm   5$ & $-29.28 \pm   0.02$ & $-29.14 \pm   0.02$& $-28.74 \pm   0.02$& $-28.46 \pm   0.01$& $-27.76 \pm   0.03$ & $  0.35 \pm   0.19$\\
-%SNF20080725-004 & $133.6 \pm 2.1$ & $  6.9 \pm 0.9$& $ 6131 \pm   6$ & $-29.09 \pm   0.01$ & $-28.93 \pm   0.01$& $-28.59 \pm   0.01$& $-28.31 \pm   0.01$& $-27.55 \pm   0.03$ & $  0.60 \pm   0.14$\\
-%SNF20050728-006 & $127.8 \pm 2.5$ & $ 15.8 \pm 1.3$& $ 6124 \pm   6$ & $-28.80 \pm   0.02$ & $-28.68 \pm   0.02$& $-28.37 \pm   0.02$& $-28.18 \pm   0.02$& $-27.55 \pm   0.02$ & $  0.27 \pm   0.27$\\
-%SN2012fr & $134.2 \pm 0.5$ & $  7.4 \pm 0.2$& $ 6102 \pm   1$ & $-29.91 \pm   0.01$ & $-29.70 \pm   0.01$& $-29.31 \pm   0.01$& $-28.94 \pm   0.01$& $-28.10 \pm   0.01$ & $  0.96 \pm   0.10$\\
-%SNF20060512-002 & $100.2 \pm 2.8$ & $ 13.4 \pm 1.1$& $ 6107 \pm   8$ & $-29.33 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.77 \pm   0.02$& $-28.52 \pm   0.02$& $-27.80 \pm   0.02$ & $ -0.92 \pm   0.19$\\
-%SNF20060512-001 & $ 88.4 \pm 1.2$ & $  5.4 \pm 0.4$& $ 6169 \pm   3$ & $-29.33 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.68 \pm   0.01$& $-28.40 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.69 \pm   0.15$\\
-%SNF20071003-016 & $125.2 \pm 4.6$ & $ 17.1 \pm 2.0$& $ 6124 \pm  11$ & $-28.58 \pm   0.02$ & $-28.54 \pm   0.02$& $-28.19 \pm   0.02$& $-27.99 \pm   0.02$& $-27.31 \pm   0.02$ & $ -0.25 \pm   0.15$\\
-%SNF20050821-007 & $141.7 \pm 2.6$ & $  7.7 \pm 1.0$& $ 6140 \pm   9$ & $-29.38 \pm   0.02$ & $-29.20 \pm   0.02$& $-28.77 \pm   0.02$& $-28.46 \pm   0.02$& $-27.67 \pm   0.02$ & $  0.17 \pm   0.32$\\
-%SNF20070803-005 & $ 22.7 \pm 21.4$ & $  0.9 \pm 0.6$& $ 6157 \pm  27$ & $-29.87 \pm   0.01$ & $-29.43 \pm   0.01$& $-29.04 \pm   0.01$& $-28.74 \pm   0.01$& $-28.11 \pm   0.01$ & $  0.88 \pm   0.18$\\
-%PTF09foz & $127.2 \pm 1.9$ & $ 21.7 \pm 1.2$& $ 6136 \pm   4$ & $-29.14 \pm   0.01$ & $-29.00 \pm   0.01$& $-28.59 \pm   0.01$& $-28.35 \pm   0.01$& $-27.65 \pm   0.01$ & $ -1.14 \pm   0.26$\\
-%PTF12grk & $162.3 \pm 9.8$ & $ 19.6 \pm 1.4$& $ 6085 \pm   8$ & $-28.86 \pm   0.02$ & $-28.87 \pm   0.01$& $-28.42 \pm   0.01$& $-28.19 \pm   0.01$& $-27.50 \pm   0.03$ & $ -1.17 \pm   0.13$\\
-%SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ & $  0.18 \pm   0.13$\\
-%SNF20080810-001 & $ 88.4 \pm 21.6$ & $ 22.3 \pm 1.1$& $ 6145 \pm   5$ & $-29.11 \pm   0.01$ & $-28.89 \pm   0.01$& $-28.45 \pm   0.01$& $-28.23 \pm   0.01$& $-27.60 \pm   0.01$ & $ -0.87 \pm   0.11$\\
-%SNF20050729-002 & $109.4 \pm 2.2$ & $ 11.5 \pm 1.7$& $ 6142 \pm   6$ & $-29.35 \pm   0.13$ & $-29.17 \pm   0.13$& $-28.68 \pm   0.13$& $-28.38 \pm   0.13$& $-27.56 \pm   0.13$ & $  0.57 \pm   0.34$\\
-%SN2008ec & $103.7 \pm 17.0$ & $ 23.1 \pm 0.4$& $ 6125 \pm   3$ & $-28.67 \pm   0.01$ & $-28.52 \pm   0.01$& $-28.18 \pm   0.01$& $-28.03 \pm   0.01$& $-27.47 \pm   0.01$ & $ -1.05 \pm   0.12$\\
-%SNF20070902-018 & $ 93.8 \pm 12.2$ & $ 23.8 \pm 3.0$& $ 6120 \pm   8$ & $-28.87 \pm   0.02$ & $-28.70 \pm   0.01$& $-28.26 \pm   0.01$& $-28.08 \pm   0.01$& $-27.41 \pm   0.02$ & $ -0.72 \pm   0.10$\\
-%SNF20070424-003 & $122.5 \pm 3.8$ & $ 12.7 \pm 1.6$& $ 6132 \pm   6$ & $-29.10 \pm   0.01$ & $-28.96 \pm   0.01$& $-28.51 \pm   0.01$& $-28.25 \pm   0.01$& $-27.57 \pm   0.01$ & $  0.31 \pm   0.11$\\
-%SN2006cj & $101.7 \pm 1.3$ & $  4.8 \pm 0.8$& $ 6127 \pm   3$ & $-29.43 \pm   0.01$ & $-29.14 \pm   0.01$& $-28.74 \pm   0.01$& $-28.43 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.48 \pm   0.18$\\
-%SN2007nq & $ 89.8 \pm 9.9$ & $ 23.4 \pm 1.1$& $ 6109 \pm   5$ & $-29.11 \pm   0.02$ & $-28.91 \pm   0.02$& $-28.50 \pm   0.02$& $-28.27 \pm   0.02$& $-27.57 \pm   0.02$ & $ -1.89 \pm   0.26$\\
-%SNF20070817-003 & $ 93.9 \pm 2.4$ & $ 18.5 \pm 1.3$& $ 6116 \pm   6$ & $-29.19 \pm   0.02$ & $-29.03 \pm   0.01$& $-28.59 \pm   0.01$& $-28.30 \pm   0.01$& $-27.55 \pm   0.02$ & $ -0.57 \pm   0.13$\\
-%SNF20070403-000 & $ 61.8 \pm 6.5$ & $ 27.1 \pm 1.8$& $ 6154 \pm   8$ & $-28.37 \pm   0.02$ & $-28.27 \pm   0.02$& $-27.97 \pm   0.02$& $-27.80 \pm   0.02$& $-27.24 \pm   0.02$ & $ -1.96 \pm   0.19$\\
-%SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ & $  1.72 \pm   0.44$\\
-%SNNGC4076 & $127.3 \pm 2.4$ & $ 15.5 \pm 1.2$& $ 6152 \pm   4$ & $-28.77 \pm   0.01$ & $-28.66 \pm   0.01$& $-28.37 \pm   0.01$& $-28.15 \pm   0.01$& $-27.52 \pm   0.01$ & $  0.01 \pm   0.12$\\
-%SNF20070727-016 & $ 77.5 \pm 2.5$ & $  5.1 \pm 0.8$& $ 6140 \pm   4$ & $-29.96 \pm   0.06$ & $-29.56 \pm   0.06$& $-29.06 \pm   0.06$& $-28.75 \pm   0.06$& $-28.01 \pm   0.06$ & $  0.27 \pm   0.12$\\
-%PTF12fuu & $105.5 \pm 3.0$ & $  6.2 \pm 1.2$& $ 6124 \pm   5$ & $-29.54 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.74 \pm   0.01$& $-28.40 \pm   0.01$& $-27.64 \pm   0.01$ & $  0.34 \pm   0.12$\\
-%SNF20070820-000 & $107.2 \pm 3.5$ & $ 18.6 \pm 1.3$& $ 6132 \pm  14$ & $-28.80 \pm   0.02$ & $-28.69 \pm   0.02$& $-28.34 \pm   0.02$& $-28.13 \pm   0.02$& $-27.52 \pm   0.02$ & $ -0.29 \pm   0.13$\\
-%SNF20070725-001 & $108.4 \pm 2.0$ & $ 11.1 \pm 1.5$& $ 6140 \pm   7$ & $-29.61 \pm   0.02$ & $-29.32 \pm   0.02$& $-28.84 \pm   0.02$& $-28.50 \pm   0.02$& $-27.76 \pm   0.02$ & $  0.68 \pm   0.17$\\
-%SNF20071108-021 & $ 99.1 \pm 2.7$ & $  5.8 \pm 0.8$& $ 6164 \pm   5$ & $-29.67 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.94 \pm   0.01$& $-28.60 \pm   0.01$& $-27.96 \pm   0.01$ & $  1.00 \pm   0.21$\\
-%SNF20080914-001 & $126.5 \pm 1.2$ & $ 15.4 \pm 1.1$& $ 6159 \pm   3$ & $-28.67 \pm   0.02$ & $-28.60 \pm   0.02$& $-28.31 \pm   0.02$& $-28.13 \pm   0.02$& $-27.58 \pm   0.02$ & $ -0.11 \pm   0.17$\\
-%SNF20060609-002 & $ 87.7 \pm 3.6$ & $  7.3 \pm 1.3$& $ 6132 \pm   4$ & $-28.60 \pm   0.02$ & $-28.42 \pm   0.02$& $-28.19 \pm   0.02$& $-28.05 \pm   0.02$& $-27.53 \pm   0.02$ & $  0.07 \pm   0.15$\\
-%SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ & $  0.69 \pm   0.62$\\
-%SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ & $  0.12 \pm   0.18$\\
-%SNF20080531-000 & $133.0 \pm 1.5$ & $ 17.6 \pm 0.8$& $ 6114 \pm   5$ & $-29.12 \pm   0.01$ & $-28.98 \pm   0.01$& $-28.54 \pm   0.01$& $-28.28 \pm   0.01$& $-27.51 \pm   0.01$ & $ -0.49 \pm   0.18$\\
-%SN2006do & $106.4 \pm 2.1$ & $ 26.7 \pm 1.3$& $ 6101 \pm   2$ & $-29.00 \pm   0.01$ & $-28.83 \pm   0.01$& $-28.42 \pm   0.01$& $-28.20 \pm   0.01$& $-27.53 \pm   0.04$ & $ -2.32 \pm   0.54$\\
-%PTF12ikt & $110.3 \pm 1.6$ & $ 14.2 \pm 0.7$& $ 6141 \pm   4$ & $-29.34 \pm   0.01$ & $-29.04 \pm   0.01$& $-28.57 \pm   0.01$& $-28.32 \pm   0.01$& $-27.66 \pm   0.01$ & $ -0.35 \pm   0.11$\\
-%SN2006dm & $ 99.5 \pm 1.6$ & $ 30.0 \pm 0.7$& $ 6118 \pm   3$ & $-28.81 \pm   0.01$ & $-28.65 \pm   0.01$& $-28.23 \pm   0.01$& $-28.02 \pm   0.01$& $-27.33 \pm   0.01$ & $ -1.88 \pm   0.34$\\
-%PTF13azs & $138.0 \pm 5.1$ & $ 16.2 \pm 1.6$& $ 6125 \pm  10$ & $-27.84 \pm   0.02$ & $-27.92 \pm   0.02$& $-27.69 \pm   0.02$& $-27.60 \pm   0.02$& $-26.99 \pm   0.02$ & $ -0.02 \pm   0.12$\\
-%SN2005hj & $ 80.8 \pm 2.4$ & $  4.3 \pm 0.8$& $ 6138 \pm   4$ & $-29.54 \pm   0.02$ & $-29.16 \pm   0.01$& $-28.87 \pm   0.01$& $-28.54 \pm   0.01$& $-28.01 \pm   0.01$ & $  1.85 \pm   0.59$\\
-%PTF12iiq & $150.4 \pm 2.2$ & $ 22.5 \pm 0.8$& $ 6041 \pm   6$ & $-28.60 \pm   0.01$ & $-28.77 \pm   0.01$& $-28.41 \pm   0.01$& $-28.10 \pm   0.01$& $-27.29 \pm   0.01$ & $ -1.30 \pm   0.12$\\
-%PTF10ndc & $124.2 \pm 2.4$ & $  6.8 \pm 1.1$& $ 6119 \pm   3$ & $-29.52 \pm   0.01$ & $-29.25 \pm   0.01$& $-28.80 \pm   0.01$& $-28.49 \pm   0.01$& $-27.76 \pm   0.01$ & $  0.87 \pm   0.18$\\
-%SNF20080919-002 & $103.6 \pm 7.2$ & $ 27.2 \pm 1.9$& $ 6133 \pm   8$ & $-28.74 \pm   0.02$ & $-28.46 \pm   0.01$& $-28.09 \pm   0.01$& $-27.87 \pm   0.01$& $-27.26 \pm   0.04$ & $ -1.52 \pm   0.14$\\
-%SNPGC027923 & $ 85.5 \pm 0.6$ & $  5.9 \pm 0.3$& $ 6130 \pm   4$ & $-29.87 \pm   0.02$ & $-29.45 \pm   0.02$& $-28.94 \pm   0.02$& $-28.57 \pm   0.02$& $-27.85 \pm   0.02$ & $  0.22 \pm   0.26$\\
-%SNF20070330-024 & $118.1 \pm 2.1$ & $  4.6 \pm 2.2$& $ 6101 \pm   3$ & $-29.77 \pm   0.02$ & $-29.52 \pm   0.02$& $-29.08 \pm   0.02$& $-28.74 \pm   0.01$& $-27.94 \pm   0.02$ & $  0.34 \pm   0.29$\\
-%SNF20061030-010 & $131.4 \pm 2.2$ & $ 17.4 \pm 1.1$& $ 6116 \pm   4$ & $-28.60 \pm   0.02$ & $-28.55 \pm   0.02$& $-28.25 \pm   0.02$& $-28.03 \pm   0.02$& $-27.34 \pm   0.02$ & $  0.14 \pm   0.25$\\
-%SNhunt46 & $ 94.1 \pm 2.0$ & $ 11.2 \pm 0.6$& $ 6132 \pm   4$ & $-29.50 \pm   0.02$ & $-29.11 \pm   0.02$& $-28.67 \pm   0.02$& $-28.37 \pm   0.02$& $-27.71 \pm   0.02$ & $  0.20 \pm   0.24$\\
-%SN2005hc & $126.9 \pm 2.5$ & $ 10.0 \pm 0.7$& $ 6123 \pm   3$ & $-29.38 \pm   0.01$ & $-29.13 \pm   0.01$& $-28.69 \pm   0.01$& $-28.37 \pm   0.01$& $-27.61 \pm   0.01$ & $  0.87 \pm   0.31$\\
-%LSQ12dbr & $106.9 \pm 0.6$ & $  7.1 \pm 0.7$& $ 6138 \pm   4$ & $-29.29 \pm   0.73$ & $-29.00 \pm   0.73$& $-28.51 \pm   0.73$& $-28.15 \pm   0.73$& $-27.38 \pm   0.73$ & $  1.12 \pm   0.14$\\
-%LSQ12hjm & $ 82.6 \pm 17.5$ & $ 12.2 \pm 1.4$& $ 6144 \pm   5$ & $-29.51 \pm   0.02$ & $-29.14 \pm   0.01$& $-28.60 \pm   0.01$& $-28.30 \pm   0.01$& $-27.71 \pm   0.02$ & $ -0.50 \pm   0.21$\\
-%SNF20060521-001 & $ 78.9 \pm 20.2$ & $ 21.1 \pm 1.4$& $ 6123 \pm  10$ & $-29.37 \pm   0.05$ & $-29.04 \pm   0.05$& $-28.54 \pm   0.05$& $-28.30 \pm   0.05$& $-27.57 \pm   0.05$ & $ -1.22 \pm   0.26$\\
-%SNF20070630-006 & $125.5 \pm 3.2$ & $ 10.1 \pm 1.6$& $ 6126 \pm   4$ & $-29.34 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.65 \pm   0.01$& $-28.38 \pm   0.01$& $-27.66 \pm   0.01$ & $  0.35 \pm   0.12$\\
-%PTF11drz & $132.6 \pm 1.4$ & $ 15.2 \pm 1.0$& $ 6116 \pm   5$ & $-29.12 \pm   0.01$ & $-28.95 \pm   0.01$& $-28.53 \pm   0.01$& $-28.27 \pm   0.01$& $-27.55 \pm   0.01$ & $  0.21 \pm   0.37$\\
-%SNF20080323-009 & $ 95.9 \pm 2.3$ & $ 10.6 \pm 1.1$& $ 6143 \pm   6$ & $-29.59 \pm   0.02$ & $-29.22 \pm   0.02$& $-28.68 \pm   0.02$& $-28.42 \pm   0.02$& $-27.77 \pm   0.02$ & $ -0.10 \pm   0.17$\\
-%SNF20071021-000 & $167.5 \pm 2.2$ & $ 20.4 \pm 0.6$& $ 6112 \pm   4$ & $-28.75 \pm   0.02$ & $-28.78 \pm   0.02$& $-28.40 \pm   0.02$& $-28.18 \pm   0.02$& $-27.41 \pm   0.02$ & $ -0.53 \pm   0.18$\\
-%SNNGC0927 & $155.2 \pm 1.4$ & $ 11.0 \pm 0.7$& $ 6109 \pm   4$ & $-28.87 \pm   0.02$ & $-28.81 \pm   0.01$& $-28.46 \pm   0.01$& $-28.22 \pm   0.01$& $-27.48 \pm   0.01$ & $  0.41 \pm   0.14$\\
-%SNF20060526-003 & $112.1 \pm 2.5$ & $  9.8 \pm 1.0$& $ 6121 \pm   3$ & $-29.34 \pm   0.01$ & $-29.09 \pm   0.01$& $-28.68 \pm   0.01$& $-28.39 \pm   0.01$& $-27.70 \pm   0.01$ & $  0.29 \pm   0.17$\\
-%SNF20080806-002 & $135.8 \pm 1.8$ & $  7.5 \pm 0.9$& $ 6135 \pm   4$ & $-29.22 \pm   0.02$ & $-29.02 \pm   0.02$& $-28.61 \pm   0.02$& $-28.35 \pm   0.01$& $-27.71 \pm   0.02$ & $  0.64 \pm   0.16$\\
-%SNF20080803-000 & $117.6 \pm 2.6$ & $  8.9 \pm 2.0$& $ 6125 \pm   4$ & $-28.84 \pm   0.01$ & $-28.70 \pm   0.01$& $-28.35 \pm   0.01$& $-28.16 \pm   0.01$& $-27.50 \pm   0.01$ & $  0.37 \pm   0.14$\\
-%SNF20080822-005 & $ 78.5 \pm 1.8$ & $  6.3 \pm 0.9$& $ 6138 \pm   4$ & $-29.71 \pm   0.01$ & $-29.34 \pm   0.01$& $-28.93 \pm   0.01$& $-28.61 \pm   0.01$& $-27.92 \pm   0.01$ & $  0.56 \pm   0.23$\\
-%SNF20060618-014 & $137.2 \pm 2.5$ & $  9.3 \pm 1.1$& $ 6112 \pm   7$ & $-29.27 \pm   0.03$ & $-29.09 \pm   0.03$& $-28.73 \pm   0.03$& $-28.38 \pm   0.03$& $-27.68 \pm   0.03$ & $  0.97 \pm   0.21$\\
-%PTF12ghy & $ 99.3 \pm 3.6$ & $ 16.8 \pm 0.7$& $ 6134 \pm   3$ & $-28.29 \pm   0.02$ & $-28.27 \pm   0.01$& $-28.05 \pm   0.01$& $-27.95 \pm   0.01$& $-27.40 \pm   0.01$ & $ -0.48 \pm   0.12$\\
-%SNF20070531-011 & $122.4 \pm 2.7$ & $ 21.2 \pm 0.8$& $ 6114 \pm   4$ & $-29.07 \pm   0.01$ & $-28.94 \pm   0.01$& $-28.50 \pm   0.01$& $-28.26 \pm   0.01$& $-27.53 \pm   0.03$ & $ -1.82 \pm   0.25$\\
-%SNF20070831-015 & $112.2 \pm 2.7$ & $  7.8 \pm 1.0$& $ 6145 \pm   6$ & $-29.42 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.78 \pm   0.01$& $-28.46 \pm   0.01$& $-27.78 \pm   0.01$ & $  1.85 \pm   0.23$\\
-%SNF20070417-002 & $104.5 \pm 5.5$ & $ 24.4 \pm 2.2$& $ 6123 \pm   9$ & $-29.20 \pm   0.05$ & $-29.01 \pm   0.05$& $-28.48 \pm   0.05$& $-28.23 \pm   0.05$& $-27.54 \pm   0.05$ & $ -1.37 \pm   0.11$\\
-%PTF11cao & $143.3 \pm 1.6$ & $ 18.9 \pm 1.3$& $ 6104 \pm   5$ & $-28.78 \pm   0.02$ & $-28.79 \pm   0.02$& $-28.44 \pm   0.02$& $-28.18 \pm   0.02$& $-27.45 \pm   0.02$ & $  0.18 \pm   0.15$\\
-%SNF20080522-000 & $ 61.8 \pm 3.5$ & $  3.3 \pm 0.9$& $ 6131 \pm   7$ & $-29.86 \pm   0.01$ & $-29.41 \pm   0.01$& $-29.03 \pm   0.01$& $-28.70 \pm   0.01$& $-28.06 \pm   0.01$ & $  1.02 \pm   0.13$\\
-%PTF10qjq & $ 73.9 \pm 2.4$ & $ 12.8 \pm 0.8$& $ 6133 \pm   3$ & $-29.29 \pm   0.02$ & $-28.94 \pm   0.02$& $-28.53 \pm   0.01$& $-28.35 \pm   0.01$& $-27.76 \pm   0.01$ & $ -0.35 \pm   0.11$\\
-%PTF12dxm & $ 95.4 \pm 41.8$ & $ 35.7 \pm 2.8$& $ 6136 \pm   4$ & $-28.71 \pm   0.01$ & $-28.58 \pm   0.01$& $-28.19 \pm   0.01$& $-27.99 \pm   0.01$& $-27.34 \pm   0.01$ & $ -1.98 \pm   0.20$\\
-%SNF20061021-003 & $122.8 \pm 2.3$ & $  9.7 \pm 1.7$& $ 6131 \pm   4$ & $-29.04 \pm   0.02$ & $-28.86 \pm   0.02$& $-28.56 \pm   0.02$& $-28.30 \pm   0.02$& $-27.64 \pm   0.02$ & $  0.25 \pm   0.18$\\
-%SNF20080510-005 & $111.6 \pm 2.6$ & $  6.4 \pm 1.1$& $ 6115 \pm   4$ & $-29.41 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.70 \pm   0.01$& $-28.38 \pm   0.01$& $-27.73 \pm   0.04$ & $  1.90 \pm   0.26$\\
-%SNF20080507-000 & $ 98.1 \pm 1.6$ & $ 10.6 \pm 2.1$& $ 6143 \pm   5$ & $-29.23 \pm   0.01$ & $-29.05 \pm   0.01$& $-28.71 \pm   0.01$& $-28.45 \pm   0.01$& $-27.79 \pm   0.01$ & $  0.89 \pm   0.25$\\
-%SNF20080913-031 & $118.2 \pm 1.5$ & $ 11.3 \pm 1.8$& $ 6158 \pm   5$ & $-29.13 \pm   0.08$ & $-29.01 \pm   0.07$& $-28.62 \pm   0.07$& $-28.32 \pm   0.07$& $-27.68 \pm   0.07$ & $  0.03 \pm   0.21$\\
-%SNF20080510-001 & $118.8 \pm 2.1$ & $ 15.3 \pm 1.3$& $ 6115 \pm   4$ & $-29.35 \pm   0.01$ & $-29.15 \pm   0.01$& $-28.69 \pm   0.01$& $-28.38 \pm   0.01$& $-27.68 \pm   0.01$ & $  0.43 \pm   0.18$\\
-%SNF20070712-003 & $108.8 \pm 2.7$ & $ 13.5 \pm 0.9$& $ 6155 \pm   6$ & $-29.44 \pm   0.02$ & $-29.19 \pm   0.01$& $-28.74 \pm   0.01$& $-28.42 \pm   0.01$& $-27.78 \pm   0.01$ & $  0.42 \pm   0.18$\\
-%\\
 SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ & $  0.69 \pm   0.62$\\
@@
 The underlying magnitudes are
-\begin{equation}
+\replaced{\begin{equation}
 \begin{pmatrix}
@@
 \begin{pmatrix}
-c_{\hat{U}}+\alpha_{\hat{U}} EW_{\mathrm{Ca}} + \beta_{\hat{U}} EW_{\mathrm{Si}} + \eta_{\hat{U}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\
-c_{\hat{B}}+\alpha_{\hat{B}} EW_{\mathrm{Ca}} + \beta_{\hat{B}} EW_{\mathrm{Si}} + \eta_{\hat{B}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
-c_{\hat{V}}+\alpha_{\hat{V}} EW_{\mathrm{Ca}} + \beta_{\hat{V}} EW_{\mathrm{Si}} + \eta_{\hat{V}} \lambda_{\mathrm{Si}} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 \\
-c_{\hat{R}}+\alpha_{\hat{R}} EW_{\mathrm{Ca}} + \beta_{\hat{R}} EW_{\mathrm{Si}} + \eta_{\hat{R}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 \\
-c_{\hat{I}}+\alpha_{\hat{I}} EW_{\mathrm{Ca}} + \beta_{\hat{I}} EW_{\mathrm{Si}}+ \eta_{\hat{I}} \lambda_{\mathrm{Si}}  +\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1
+c_{\hat{U}}+\alpha_{\hat{U}} EW_{Ca} + \beta_{\hat{U}} EW_{Si} + \eta_{\hat{U}} \lambda_{Si}  +\gamma^0_{{\hat{U}}} g_0 +\gamma^1_{{\hat{U}}} g_1 \\
+c_{\hat{B}}+\alpha_{\hat{B}} EW_{Ca} + \beta_{\hat{B}} EW_{Si} + \eta_{\hat{B}} \lambda_{Si}  +\gamma^0_{{\hat{B}}} g_0 +\gamma^1_{{\hat{B}}} g_1 \\
+c_{\hat{V}}+\alpha_{\hat{V}} EW_{Ca} + \beta_{\hat{V}} EW_{Si} + \eta_{\hat{V}} \lambda_{Si} +\gamma^0_{{\hat{V}}} g_0 +\gamma^1_{{\hat{V}}} g_1 \\
+c_{\hat{R}}+\alpha_{\hat{R}} EW_{Ca} + \beta_{\hat{R}} EW_{Si} + \eta_{\hat{R}} \lambda_{Si}  +\gamma^0_{{\hat{R}}} g_0 +\gamma^1_{{\hat{R}}} g_1 \\
+c_{\hat{I}}+\alpha_{\hat{I}} EW_{Ca} + \beta_{\hat{I}} EW_{Si}+ \eta_{\hat{I}} \lambda_{Si}  +\gamma^0_{{\hat{I}}} g_0 +\gamma^1_{{\hat{I}}} g_1
 \end{pmatrix}.
 \label{ewsiv:eqn}
+\end{equation}}{
+\begin{equation}
+\vec{m}=
+ \vec{c} +  \vec{1} \, \Delta + \vec{\alpha} \, EW_{\mathrm{Ca}}+
+\vec{\alpha} \,  EW_{\mathrm{Ca}}+
+\vec{\beta}  \, EW_{\mathrm{Si}} +
+\vec{\eta}  \, \lambda_{\mathrm{Si}} +
+\vec{\gamma}^0  \,  g_0 +
+\vec{\gamma}^1  \,  g_1,
+\label{ewsiv:eqn}
 \end{equation}
+where $\vec{m} = \{ \hat{U}, \hat{B}, \hat{V}, \hat{R}, \hat{I} \}$ and}
 $\vec{1}$ is the Identity vector.
@@
 } that describe the SN~Ia population
+\replaced{
 $\vec{c}$  (units of mag);
@@
 parameters with 
+underlying magnitudes.}
+{
+are the intercept $\vec{c}$  (units of mag),
+and slopes $\vec{\alpha}$, $\vec{\beta}$,
+$\vec{\eta}$ (units of mag~\AA$^{-1}$), $\vec{\gamma}^0$ and $\vec{\gamma}^1$ (units of mag)
+of the linear relationships that
+relate
+per-supernova
+parameters with 
 underlying magnitudes.
+}
 The notation used in this article is not to be associated with those from previous works.
@@
    The perspective on the right visually shows that all four vectors are nearly coplanar.  
-   The combination $\vec{a}+\vec{b}/2.25$ is shown in the dotted red
+   The combination $\vec{a}+\vec{b}/2.25$ is shown in the dotted \replaced{red}{black}
    line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
@@
 \end{equation}
+\replaced{
 \begin{equation}
@@
 \label{ewsiv2:eqn}
+\end{equation}}
+{\begin{equation}
+\vec{m}=
+ \vec{c} +  \vec{1} \, \Delta + \vec{\alpha} \, EW_{\mathrm{Ca}}+
+\vec{\alpha} \,  EW_{\mathrm{Ca}}+
+\vec{\beta}  \, EW_{\mathrm{Si}} +
+\vec{\eta}  \, \lambda_{\mathrm{Si}} +
+\vec{\gamma}^0  \,  g_0 +
+\vec{\gamma}^1  \,  g_1 +
+\sigma_p \vec{\phi}\,p.
+\label{ewsiv2:eqn}
 \end{equation}
+}
 
@@
 \label{ewsiv3:eqn}
+\end{equation}}
+{\begin{equation}
+\vec{m}=
+ \vec{c} +  \vec{1} \, \Delta + \vec{\alpha} \, EW_{\mathrm{Ca}}+
+\vec{\alpha} \,  EW_{\mathrm{Ca}}+
+\vec{\beta}  \, EW_{\mathrm{Si}} +
+\vec{\eta}  \, \lambda_{\mathrm{Si}} +
+\vec{\zeta} x_1 +
+\vec{\gamma}^0  \,  g_0 +
+\vec{\gamma}^1  \,  g_1 +
+\sigma_p \vec{\phi}\,p.
+\label{ewsiv3:eqn}
 \end{equation}
+}
 
@@
    See Figure~\ref{plane:fig}.
-   The combination $\vec{a}+\vec{b}/2.43$ is shown in the dotted red
+   The combination $\vec{a}+\vec{b}/2.43$ is shown in the dotted \replaced{red}{black}
    line: it is almost perfectly superimposed on $\vec{\gamma}^0$.
@@
       less than and greater than  $\log{(M/M_\sun)}=10$.
- $p$ as a function of host-galaxy mass
     \label{childress3:fig}}
@@
 For each of the five filters, the 68\%  equal-tailed credible intervals for the global parameters $\vec{\alpha}$, $\vec{\beta}$, $\vec{\eta}$,
-$\vec{\gamma}^0$ and $\vec{\gamma}^1$ of Model~I are given in  Table~\ref{global2:tab}.
+$\vec{\gamma}^0$ and $\vec{\gamma}^1$ of Model~I are given in  Table~\ref{global1:tab}.
 The results for the same parameters and $\sigma_p\vec{\phi}$

### 2018-10-12 submit/fix.tex
91T stuff

@@
 of in-sample supernovae. 
+\added{Subsequent to the analysis four supernovae, SNBOSS38, LSQ12fhe, PTF11bju, and PTF11mkx 
+were identified as SN1991T/SN2009dc-like \citep{2018lin, 2018Taubenberger}, the results for these objects are discussed later. }
 
@@
 \startdata
-%SN2007bd & $113.3^{+5.4}_{-5.4}$ & $ 17.8^{+0.7}_{-0.7}$ & $ 6101^{+  3}_{-  3}$ & $ -1.02^{+  0.18}_{-  0.18}$ & $-0.071^{+0.027}_{-0.027}$  & $-0.050^{+0.011}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
-%PTF10zdk & $149.7^{+1.2}_{-1.2}$ & $ 14.9^{+0.6}_{-0.6}$ & $ 6150^{+  3}_{-  3}$ & $  0.37^{+  0.14}_{-  0.13}$ & $-0.029^{+0.026}_{-0.025}$  & $0.062^{+0.012}_{-0.012}$ & $-0.042^{+0.007}_{-0.007}$ & $-0.042^{+0.007}_{-0.007}$\\
-%SNF20080815-017 & $ 90.9^{+14.3}_{-14.5}$ & $ 19.6^{+2.4}_{-2.3}$ & $ 6131^{+  6}_{-  6}$ & $ -1.96^{+  0.16}_{-  0.16}$ & $0.041^{+0.070}_{-0.064}$  & $-0.008^{+0.025}_{-0.026}$ & $-0.011^{+0.028}_{-0.022}$ & $-0.011^{+0.028}_{-0.022}$\\
-%PTF09dnl & $130.0^{+0.8}_{-0.9}$ & $  9.1^{+0.7}_{-0.7}$ & $ 6092^{+  3}_{-  3}$ & $  0.59^{+  0.10}_{-  0.10}$ & $-0.061^{+0.021}_{-0.021}$  & $0.014^{+0.009}_{-0.009}$ & $0.000^{+0.011}_{-0.011}$ & $0.000^{+0.011}_{-0.011}$\\
-%SN2010ex & $114.5^{+0.9}_{-0.9}$ & $  8.4^{+0.4}_{-0.4}$ & $ 6129^{+  6}_{-  6}$ & $  0.17^{+  0.12}_{-  0.11}$ & $0.266^{+0.026}_{-0.026}$  & $-0.042^{+0.008}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
-%PTF09dnp & $ 66.9^{+4.5}_{-4.6}$ & $ 17.5^{+0.7}_{-0.7}$ & $ 6098^{+  5}_{-  4}$ & $ -0.53^{+  0.17}_{-  0.17}$ & $-0.249^{+0.026}_{-0.026}$  & $-0.008^{+0.020}_{-0.021}$ & $-0.044^{+0.006}_{-0.006}$ & $-0.044^{+0.006}_{-0.006}$\\
-%PTF11bnx & $150.7^{+3.0}_{-2.9}$ & $ 14.6^{+1.0}_{-1.0}$ & $ 6143^{+  5}_{-  5}$ & $  0.07^{+  0.14}_{-  0.14}$ & $0.043^{+0.029}_{-0.029}$  & $0.049^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
-%PTF12jqh & $151.8^{+1.4}_{-1.5}$ & $  7.9^{+0.6}_{-0.7}$ & $ 6118^{+ 10}_{- 10}$ & $  0.73^{+  0.14}_{-  0.14}$ & $0.069^{+0.028}_{-0.028}$  & $-0.056^{+0.010}_{-0.010}$ & $0.009^{+0.014}_{-0.015}$ & $0.009^{+0.014}_{-0.015}$\\
-%SNF20080802-006 & $108.7^{+5.6}_{-5.8}$ & $ 19.1^{+1.6}_{-1.6}$ & $ 6122^{+  5}_{-  5}$ & $ -1.61^{+  0.12}_{-  0.12}$ & $-0.042^{+0.059}_{-0.055}$  & $-0.001^{+0.016}_{-0.016}$ & $0.033^{+0.020}_{-0.020}$ & $0.033^{+0.020}_{-0.020}$\\
-%PTF10xyt & $120.2^{+6.3}_{-6.4}$ & $ 21.5^{+3.2}_{-3.1}$ & $ 6102^{+  4}_{-  4}$ & $  0.18^{+  0.20}_{-  0.20}$ & $0.241^{+0.049}_{-0.049}$  & $0.070^{+0.026}_{-0.028}$ & $0.014^{+0.029}_{-0.027}$ & $0.014^{+0.029}_{-0.027}$\\
-%PTF11qmo & $101.7^{+1.1}_{-1.1}$ & $  7.8^{+0.7}_{-0.7}$ & $ 6151^{+  7}_{-  8}$ & $  0.41^{+  0.18}_{-  0.18}$ & $-0.078^{+0.031}_{-0.028}$  & $-0.058^{+0.010}_{-0.010}$ & $0.004^{+0.014}_{-0.015}$ & $0.004^{+0.014}_{-0.015}$\\
-%SNF20070331-025 & $118.7^{+6.9}_{-7.0}$ & $ 15.4^{+2.0}_{-2.0}$ & $ 6121^{+ 10}_{- 10}$ & $ -1.22^{+  0.15}_{-  0.15}$ & $0.190^{+0.037}_{-0.037}$  & $-0.015^{+0.020}_{-0.020}$ & $0.001^{+0.023}_{-0.022}$ & $0.001^{+0.023}_{-0.022}$\\
-%SNF20070818-001 & $160.6^{+6.7}_{-6.8}$ & $ 16.4^{+1.5}_{-1.5}$ & $ 6113^{+  5}_{-  5}$ & $  0.14^{+  0.14}_{-  0.14}$ & $-0.178^{+0.021}_{-0.020}$  & $0.005^{+0.014}_{-0.014}$ & $0.014^{+0.016}_{-0.015}$ & $0.014^{+0.016}_{-0.015}$\\
-%SNBOSS38 & $ 57.1^{+0.4}_{-0.4}$ & $ 17.8^{+0.3}_{-0.3}$ & $ 6127^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $0.018^{+0.038}_{-0.039}$  & $0.017^{+0.021}_{-0.023}$ & $-0.002^{+0.019}_{-0.020}$ & $-0.002^{+0.019}_{-0.020}$\\
-%SN2006ob & $ 75.9^{+12.1}_{-12.4}$ & $ 26.8^{+1.3}_{-1.4}$ & $ 6113^{+  5}_{-  5}$ & $ -2.26^{+  0.21}_{-  0.21}$ & $0.039^{+0.035}_{-0.035}$  & $-0.051^{+0.019}_{-0.017}$ & $0.084^{+0.021}_{-0.021}$ & $0.084^{+0.021}_{-0.021}$\\
-%PTF12eer & $169.4^{+8.9}_{-8.8}$ & $ 12.2^{+1.8}_{-1.8}$ & $ 6148^{+ 10}_{- 10}$ & $  0.64^{+  0.14}_{-  0.15}$ & $-0.053^{+0.028}_{-0.027}$  & $0.039^{+0.018}_{-0.019}$ & $-0.029^{+0.017}_{-0.012}$ & $-0.029^{+0.017}_{-0.012}$\\
-%PTF10ops & $ 38.0^{+9.2}_{-9.2}$ & $ 21.9^{+4.6}_{-4.6}$ & $ 6140^{+  6}_{-  5}$ & $ -0.58^{+  0.12}_{-  0.12}$ & $-0.091^{+0.221}_{-0.154}$  & $0.190^{+0.040}_{-0.041}$ & $0.181^{+0.038}_{-0.036}$ & $0.181^{+0.038}_{-0.036}$\\
-%SNF20080514-002 & $ 83.1^{+0.7}_{-0.7}$ & $ 19.2^{+0.5}_{-0.5}$ & $ 6131^{+  3}_{-  3}$ & $ -1.55^{+  0.09}_{-  0.09}$ & $0.174^{+0.019}_{-0.019}$  & $-0.074^{+0.007}_{-0.006}$ & $0.006^{+0.011}_{-0.012}$ & $0.006^{+0.011}_{-0.012}$\\
-%PTF12evo & $129.1^{+2.6}_{-2.7}$ & $  9.9^{+1.1}_{-1.1}$ & $ 6157^{+  4}_{-  4}$ & $  0.81^{+  0.13}_{-  0.12}$ & $0.024^{+0.027}_{-0.027}$  & $0.004^{+0.011}_{-0.011}$ & $-0.034^{+0.012}_{-0.010}$ & $-0.034^{+0.012}_{-0.010}$\\
-%SNF20080614-010 & $118.9^{+4.9}_{-4.8}$ & $ 28.9^{+1.2}_{-1.2}$ & $ 6129^{+  3}_{-  3}$ & $ -1.81^{+  0.15}_{-  0.15}$ & $-0.114^{+0.046}_{-0.042}$  & $-0.068^{+0.012}_{-0.009}$ & $0.049^{+0.019}_{-0.019}$ & $0.049^{+0.019}_{-0.019}$\\
-%PTF10icb & $104.8^{+0.9}_{-0.9}$ & $ 12.6^{+0.3}_{-0.3}$ & $ 6138^{+  2}_{-  2}$ & $  0.23^{+  0.10}_{-  0.10}$ & $0.410^{+0.024}_{-0.025}$  & $0.046^{+0.006}_{-0.006}$ & $-0.019^{+0.010}_{-0.010}$ & $-0.019^{+0.010}_{-0.010}$\\
-%PTF12efn & $145.5^{+3.3}_{-3.2}$ & $  5.4^{+1.4}_{-1.5}$ & $ 6115^{+  3}_{-  3}$ & $  1.04^{+  0.16}_{-  0.16}$ & $0.177^{+0.030}_{-0.029}$  & $-0.058^{+0.014}_{-0.012}$ & $0.051^{+0.017}_{-0.017}$ & $0.051^{+0.017}_{-0.017}$\\
-%SNNGC4424 & $109.0^{+0.3}_{-0.3}$ & $  8.6^{+0.1}_{-0.1}$ & $ 6138^{+  2}_{-  2}$ & $  0.44^{+  0.09}_{-  0.09}$ & $0.600^{+0.022}_{-0.023}$  & $0.078^{+0.007}_{-0.006}$ & $-0.025^{+0.011}_{-0.011}$ & $-0.025^{+0.011}_{-0.011}$\\
-%SNF20080516-022 & $ 99.1^{+2.2}_{-2.1}$ & $ 15.3^{+0.9}_{-0.9}$ & $ 6159^{+  3}_{-  3}$ & $  0.48^{+  0.12}_{-  0.11}$ & $0.001^{+0.026}_{-0.026}$  & $-0.064^{+0.010}_{-0.009}$ & $-0.025^{+0.014}_{-0.013}$ & $-0.025^{+0.014}_{-0.013}$\\
-%PTF12hwb & $139.4^{+25.9}_{-23.8}$ & $ -0.9^{+4.4}_{-4.3}$ & $ 6090^{+ 14}_{- 14}$ & $  1.34^{+  0.17}_{-  0.17}$ & $0.471^{+0.042}_{-0.044}$  & $0.151^{+0.037}_{-0.043}$ & $0.004^{+0.040}_{-0.032}$ & $0.004^{+0.040}_{-0.032}$\\
-%PTF10qyz & $108.1^{+2.1}_{-2.1}$ & $ 21.0^{+0.8}_{-0.8}$ & $ 6117^{+  5}_{-  5}$ & $ -1.67^{+  0.13}_{-  0.13}$ & $0.099^{+0.133}_{-0.095}$  & $-0.067^{+0.014}_{-0.010}$ & $-0.038^{+0.012}_{-0.008}$ & $-0.038^{+0.012}_{-0.008}$\\
-%SNF20060907-000 & $ 87.8^{+7.5}_{-7.3}$ & $ 15.9^{+0.9}_{-0.9}$ & $ 6150^{+  4}_{-  4}$ & $  0.16^{+  0.17}_{-  0.17}$ & $0.037^{+0.033}_{-0.033}$  & $-0.079^{+0.005}_{-0.005}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
-%LSQ12fxd & $122.8^{+1.6}_{-1.7}$ & $ 11.7^{+0.8}_{-0.7}$ & $ 6119^{+  4}_{-  4}$ & $  0.16^{+  0.12}_{-  0.12}$ & $-0.154^{+0.044}_{-0.032}$  & $-0.052^{+0.008}_{-0.008}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
-%SNF20080821-000 & $104.8^{+2.2}_{-2.2}$ & $  8.8^{+1.2}_{-1.2}$ & $ 6121^{+  4}_{-  4}$ & $  0.77^{+  0.15}_{-  0.14}$ & $-0.104^{+0.023}_{-0.023}$  & $0.025^{+0.011}_{-0.011}$ & $-0.006^{+0.013}_{-0.013}$ & $-0.006^{+0.013}_{-0.013}$\\
-%SNF20070802-000 & $157.9^{+3.3}_{-3.3}$ & $ 16.0^{+1.4}_{-1.4}$ & $ 6103^{+  5}_{-  5}$ & $  0.07^{+  0.13}_{-  0.13}$ & $-0.074^{+0.028}_{-0.028}$  & $0.005^{+0.014}_{-0.014}$ & $0.005^{+0.016}_{-0.016}$ & $0.005^{+0.016}_{-0.016}$\\
-%PTF10wnm & $105.5^{+2.3}_{-2.3}$ & $  6.8^{+0.9}_{-0.9}$ & $ 6125^{+  3}_{-  3}$ & $  0.73^{+  0.12}_{-  0.12}$ & $0.123^{+0.022}_{-0.021}$  & $-0.014^{+0.009}_{-0.009}$ & $0.015^{+0.012}_{-0.012}$ & $0.015^{+0.012}_{-0.012}$\\
-%PTF10mwb & $116.2^{+1.2}_{-1.2}$ & $ 21.1^{+0.7}_{-0.7}$ & $ 6139^{+  2}_{-  2}$ & $ -0.48^{+  0.09}_{-  0.09}$ & $-0.000^{+0.071}_{-0.070}$  & $-0.036^{+0.008}_{-0.008}$ & $-0.011^{+0.011}_{-0.011}$ & $-0.011^{+0.011}_{-0.011}$\\
-%SN2010dt & $133.3^{+8.4}_{-8.6}$ & $ 16.0^{+0.6}_{-0.6}$ & $ 6141^{+  5}_{-  5}$ & $ -0.02^{+  0.09}_{-  0.09}$ & $-0.046^{+0.024}_{-0.024}$  & $-0.063^{+0.010}_{-0.009}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
-%SNF20080623-001 & $149.2^{+1.4}_{-1.4}$ & $ 14.8^{+0.6}_{-0.6}$ & $ 6131^{+  3}_{-  3}$ & $ -0.07^{+  0.11}_{-  0.10}$ & $0.072^{+0.025}_{-0.025}$  & $-0.054^{+0.010}_{-0.009}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
-%LSQ12fhe & $ 42.9^{+1.2}_{-1.2}$ & $  2.3^{+1.9}_{-1.9}$ & $ 6108^{+  4}_{-  4}$ & $  1.01^{+  0.17}_{-  0.17}$ & $-0.183^{+0.032}_{-0.033}$  & $0.067^{+0.017}_{-0.018}$ & $-0.017^{+0.018}_{-0.016}$ & $-0.017^{+0.018}_{-0.016}$\\
-%PTF11bju & $ 31.3^{+4.3}_{-4.2}$ & $  3.3^{+2.0}_{-2.0}$ & $ 6138^{+  5}_{-  5}$ & $  1.02^{+  0.17}_{-  0.18}$ & $0.073^{+0.036}_{-0.036}$  & $0.077^{+0.019}_{-0.019}$ & $-0.014^{+0.020}_{-0.018}$ & $-0.014^{+0.020}_{-0.018}$\\
-%PTF09fox & $118.5^{+2.7}_{-2.7}$ & $  9.8^{+0.9}_{-0.8}$ & $ 6117^{+  3}_{-  3}$ & $  0.52^{+  0.16}_{-  0.15}$ & $0.027^{+0.039}_{-0.039}$  & $-0.047^{+0.009}_{-0.009}$ & $-0.043^{+0.007}_{-0.006}$ & $-0.043^{+0.007}_{-0.006}$\\
-%PTF13ayw & $103.8^{+2.4}_{-2.4}$ & $ 23.1^{+1.8}_{-1.9}$ & $ 6116^{+  6}_{-  6}$ & $ -1.67^{+  0.23}_{-  0.24}$ & $0.068^{+0.041}_{-0.041}$  & $-0.069^{+0.014}_{-0.009}$ & $0.101^{+0.019}_{-0.020}$ & $0.101^{+0.019}_{-0.020}$\\
-%SNF20070810-004 & $127.0^{+1.8}_{-1.8}$ & $ 20.1^{+0.9}_{-0.9}$ & $ 6117^{+  7}_{-  7}$ & $ -0.01^{+  0.11}_{-  0.11}$ & $-0.044^{+0.026}_{-0.025}$  & $-0.068^{+0.011}_{-0.009}$ & $-0.033^{+0.012}_{-0.010}$ & $-0.033^{+0.012}_{-0.010}$\\
-%PTF11mty & $110.5^{+2.2}_{-2.2}$ & $ 11.3^{+1.0}_{-1.1}$ & $ 6140^{+  5}_{-  5}$ & $  1.03^{+  0.13}_{-  0.13}$ & $0.062^{+0.025}_{-0.024}$  & $-0.072^{+0.009}_{-0.007}$ & $0.024^{+0.013}_{-0.014}$ & $0.024^{+0.013}_{-0.014}$\\
-%SNF20080512-010 & $ 96.0^{+3.4}_{-3.4}$ & $ 21.9^{+1.3}_{-1.3}$ & $ 6128^{+  5}_{-  5}$ & $ -1.64^{+  0.18}_{-  0.18}$ & $-0.032^{+0.072}_{-0.061}$  & $-0.051^{+0.013}_{-0.012}$ & $0.018^{+0.016}_{-0.016}$ & $0.018^{+0.016}_{-0.016}$\\
-%PTF11mkx & $ 34.8^{+3.5}_{-3.5}$ & $  5.5^{+1.3}_{-1.3}$ & $ 6169^{+  5}_{-  5}$ & $  0.53^{+  0.14}_{-  0.14}$ & $0.022^{+0.135}_{-0.080}$  & $0.102^{+0.017}_{-0.016}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
-%PTF10tce & $135.8^{+1.1}_{-1.1}$ & $ 10.6^{+1.2}_{-1.2}$ & $ 6090^{+  4}_{-  4}$ & $  0.38^{+  0.12}_{-  0.12}$ & $0.041^{+0.028}_{-0.027}$  & $-0.005^{+0.013}_{-0.014}$ & $-0.019^{+0.015}_{-0.015}$ & $-0.019^{+0.015}_{-0.015}$\\
-%SNF20061020-000 & $ 90.3^{+13.4}_{-13.3}$ & $ 23.9^{+0.9}_{-0.9}$ & $ 6120^{+  4}_{-  5}$ & $ -1.75^{+  0.17}_{-  0.17}$ & $-0.096^{+0.039}_{-0.034}$  & $0.000^{+0.016}_{-0.016}$ & $0.006^{+0.022}_{-0.020}$ & $0.006^{+0.022}_{-0.020}$\\
-%SN2005ir & $115.7^{+2.8}_{-2.7}$ & $  8.7^{+4.6}_{-4.8}$ & $ 6069^{+  5}_{-  5}$ & $  1.64^{+  0.49}_{-  0.48}$ & $0.112^{+0.042}_{-0.043}$  & $-0.022^{+0.036}_{-0.033}$ & $0.067^{+0.037}_{-0.037}$ & $0.067^{+0.037}_{-0.037}$\\
-%SNF20080717-000 & $ 92.7^{+2.6}_{-2.6}$ & $ 12.4^{+1.7}_{-1.7}$ & $ 6105^{+  3}_{-  3}$ & $  0.87^{+  0.13}_{-  0.12}$ & $0.115^{+0.034}_{-0.033}$  & $0.126^{+0.018}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$ & $0.050^{+0.021}_{-0.019}$\\
-%PTF12ena & $101.0^{+1.6}_{-1.6}$ & $  8.2^{+0.9}_{-0.9}$ & $ 6130^{+  3}_{-  3}$ & $  0.76^{+  0.13}_{-  0.13}$ & $-0.039^{+0.028}_{-0.028}$  & $0.289^{+0.011}_{-0.012}$ & $-0.038^{+0.010}_{-0.008}$ & $-0.038^{+0.010}_{-0.008}$\\
-%PTF13anh & $167.2^{+1.8}_{-1.8}$ & $ 21.6^{+1.0}_{-1.0}$ & $ 6174^{+  3}_{-  4}$ & $ -0.38^{+  0.14}_{-  0.14}$ & $0.092^{+0.108}_{-0.067}$  & $-0.032^{+0.020}_{-0.019}$ & $-0.034^{+0.014}_{-0.010}$ & $-0.034^{+0.014}_{-0.010}$\\
-%CSS110918\_01 & $110.4^{+1.0}_{-1.0}$ & $  5.0^{+0.9}_{-0.9}$ & $ 6101^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.077^{+0.187}_{-0.094}$  & $-0.078^{+0.006}_{-0.005}$ & $-0.028^{+0.013}_{-0.012}$ & $-0.028^{+0.013}_{-0.012}$\\
-%SNF20061024-000 & $ 98.9^{+15.7}_{-16.7}$ & $ 29.1^{+1.4}_{-1.4}$ & $ 6127^{+  5}_{-  5}$ & $ -1.51^{+  0.18}_{-  0.18}$ & $0.045^{+0.062}_{-0.059}$  & $-0.049^{+0.021}_{-0.019}$ & $0.003^{+0.031}_{-0.028}$ & $0.003^{+0.031}_{-0.028}$\\
-%SNF20070506-006 & $ 94.3^{+1.3}_{-1.2}$ & $  6.4^{+0.6}_{-0.5}$ & $ 6152^{+  3}_{-  3}$ & $  1.02^{+  0.11}_{-  0.11}$ & $-0.075^{+0.027}_{-0.026}$  & $-0.029^{+0.009}_{-0.009}$ & $0.006^{+0.013}_{-0.013}$ & $0.006^{+0.013}_{-0.013}$\\
-%SNF20070403-001 & $107.8^{+5.0}_{-5.1}$ & $ 17.1^{+1.4}_{-1.4}$ & $ 6123^{+  4}_{-  4}$ & $ -0.60^{+  0.12}_{-  0.12}$ & $0.007^{+0.029}_{-0.028}$  & $-0.036^{+0.014}_{-0.014}$ & $0.020^{+0.017}_{-0.017}$ & $0.020^{+0.017}_{-0.017}$\\
-%PTF10hmv & $109.8^{+1.3}_{-1.4}$ & $  8.5^{+0.7}_{-0.6}$ & $ 6143^{+  3}_{-  3}$ & $  1.15^{+  0.13}_{-  0.12}$ & $0.284^{+0.024}_{-0.023}$  & $0.106^{+0.009}_{-0.009}$ & $-0.010^{+0.012}_{-0.012}$ & $-0.010^{+0.012}_{-0.012}$\\
-%SNF20071015-000 & $104.8^{+3.1}_{-3.1}$ & $  6.5^{+1.1}_{-1.1}$ & $ 6125^{+  7}_{-  7}$ & $  0.90^{+  0.28}_{-  0.29}$ & $0.116^{+0.040}_{-0.040}$  & $0.293^{+0.016}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$ & $-0.018^{+0.021}_{-0.017}$\\
-%SNhunt89 & $ 88.6^{+2.7}_{-2.7}$ & $ 29.8^{+1.7}_{-1.7}$ & $ 6109^{+  7}_{-  7}$ & $ -2.02^{+  0.16}_{-  0.16}$ & $0.202^{+0.049}_{-0.047}$  & $0.030^{+0.018}_{-0.019}$ & $0.032^{+0.027}_{-0.026}$ & $0.032^{+0.027}_{-0.026}$\\
-%SNF20070902-021 & $109.0^{+3.3}_{-3.3}$ & $ 16.8^{+0.9}_{-0.9}$ & $ 6131^{+  5}_{-  5}$ & $ -0.46^{+  0.09}_{-  0.09}$ & $-0.082^{+0.027}_{-0.026}$  & $-0.023^{+0.010}_{-0.010}$ & $-0.028^{+0.014}_{-0.012}$ & $-0.028^{+0.014}_{-0.012}$\\
-%PTF09dlc & $143.8^{+2.1}_{-2.1}$ & $  9.7^{+0.8}_{-0.8}$ & $ 6143^{+  3}_{-  3}$ & $  0.01^{+  0.10}_{-  0.10}$ & $0.008^{+0.027}_{-0.026}$  & $-0.054^{+0.012}_{-0.012}$ & $-0.017^{+0.014}_{-0.015}$ & $-0.017^{+0.014}_{-0.015}$\\
-%PTF13ajv & $149.9^{+8.1}_{-8.2}$ & $ 22.0^{+2.7}_{-3.0}$ & $ 6107^{+ 20}_{- 20}$ & $ -1.64^{+  0.20}_{-  0.21}$ & $0.263^{+0.046}_{-0.045}$  & $-0.062^{+0.021}_{-0.014}$ & $-0.005^{+0.023}_{-0.022}$ & $-0.005^{+0.023}_{-0.022}$\\
-%SNF20080919-000 & $115.6^{+2.7}_{-2.7}$ & $  8.8^{+0.9}_{-0.8}$ & $ 6144^{+  5}_{-  5}$ & $ -0.24^{+  0.10}_{-  0.10}$ & $-0.043^{+0.027}_{-0.026}$  & $0.165^{+0.013}_{-0.012}$ & $-0.035^{+0.013}_{-0.010}$ & $-0.035^{+0.013}_{-0.010}$\\
-%SNF20080919-001 & $ 85.0^{+1.1}_{-1.1}$ & $  6.1^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  1.05^{+  0.12}_{-  0.12}$ & $-0.183^{+0.020}_{-0.019}$  & $0.001^{+0.008}_{-0.008}$ & $0.006^{+0.012}_{-0.012}$ & $0.006^{+0.012}_{-0.012}$\\
-%SN2010kg & $ 99.4^{+17.2}_{-17.5}$ & $ 21.8^{+0.7}_{-0.7}$ & $ 6077^{+  5}_{-  5}$ & $ -1.87^{+  0.24}_{-  0.25}$ & $-0.073^{+0.030}_{-0.029}$  & $0.035^{+0.021}_{-0.020}$ & $0.034^{+0.020}_{-0.021}$ & $0.034^{+0.020}_{-0.021}$\\
-%SNF20080714-008 & $155.6^{+11.0}_{-10.8}$ & $ 16.6^{+1.9}_{-1.8}$ & $ 6099^{+  6}_{-  6}$ & $ -0.07^{+  0.14}_{-  0.14}$ & $-0.141^{+0.024}_{-0.022}$  & $0.082^{+0.018}_{-0.020}$ & $-0.029^{+0.017}_{-0.013}$ & $-0.029^{+0.017}_{-0.013}$\\
-%SNF20070714-007 & $132.6^{+5.5}_{-5.5}$ & $ 33.5^{+4.3}_{-4.2}$ & $ 6145^{+  4}_{-  4}$ & $ -1.09^{+  0.13}_{-  0.13}$ & $-0.094^{+0.046}_{-0.047}$  & $0.118^{+0.035}_{-0.038}$ & $0.117^{+0.036}_{-0.032}$ & $0.117^{+0.036}_{-0.032}$\\
-%SNF20080522-011 & $122.1^{+1.7}_{-1.7}$ & $  8.3^{+0.5}_{-0.5}$ & $ 6125^{+  2}_{-  2}$ & $  0.82^{+  0.13}_{-  0.13}$ & $-0.124^{+0.023}_{-0.023}$  & $-0.045^{+0.008}_{-0.008}$ & $-0.031^{+0.011}_{-0.010}$ & $-0.031^{+0.011}_{-0.010}$\\
-%SNF20061111-002 & $117.1^{+8.6}_{-8.8}$ & $ 19.8^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  0.07^{+  0.17}_{-  0.17}$ & $0.056^{+0.032}_{-0.032}$  & $-0.062^{+0.013}_{-0.011}$ & $0.026^{+0.017}_{-0.017}$ & $0.026^{+0.017}_{-0.017}$\\
-%SNNGC6343 & $ 86.9^{+1.5}_{-1.4}$ & $ 21.2^{+0.7}_{-0.7}$ & $ 6136^{+  3}_{-  3}$ & $ -1.49^{+  0.16}_{-  0.16}$ & $0.055^{+0.029}_{-0.030}$  & $0.036^{+0.013}_{-0.012}$ & $0.020^{+0.016}_{-0.014}$ & $0.020^{+0.016}_{-0.014}$\\
-%SNF20061011-005 & $120.5^{+1.1}_{-1.1}$ & $  9.2^{+0.3}_{-0.3}$ & $ 6132^{+  4}_{-  4}$ & $  0.66^{+  0.22}_{-  0.21}$ & $-0.091^{+0.043}_{-0.041}$  & $-0.073^{+0.008}_{-0.007}$ & $0.003^{+0.021}_{-0.021}$ & $0.003^{+0.021}_{-0.021}$\\
-%SNF20080825-010 & $ 96.4^{+10.2}_{-10.2}$ & $ 19.2^{+0.6}_{-0.6}$ & $ 6116^{+  4}_{-  4}$ & $ -0.76^{+  0.13}_{-  0.13}$ & $-0.192^{+0.020}_{-0.020}$  & $-0.045^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$ & $0.002^{+0.013}_{-0.013}$\\
-%PTF10ufj & $141.4^{+3.3}_{-3.3}$ & $ 12.0^{+1.1}_{-1.0}$ & $ 6131^{+  6}_{-  5}$ & $  0.56^{+  0.13}_{-  0.13}$ & $-0.043^{+0.106}_{-0.068}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$ & $-0.030^{+0.014}_{-0.011}$\\
-%PTF10wof & $130.5^{+2.6}_{-2.7}$ & $ 16.5^{+0.9}_{-0.9}$ & $ 6102^{+  2}_{-  2}$ & $  0.06^{+  0.11}_{-  0.11}$ & $0.096^{+0.023}_{-0.023}$  & $-0.009^{+0.011}_{-0.011}$ & $-0.013^{+0.013}_{-0.012}$ & $-0.013^{+0.013}_{-0.012}$\\
-%SNF20080918-000 & $146.6^{+3.5}_{-3.5}$ & $  5.6^{+2.1}_{-2.0}$ & $ 6110^{+  5}_{-  5}$ & $  1.28^{+  0.23}_{-  0.23}$ & $0.112^{+0.038}_{-0.037}$  & $0.073^{+0.019}_{-0.019}$ & $-0.004^{+0.023}_{-0.022}$ & $-0.004^{+0.023}_{-0.022}$\\
-%SNF20080516-000 & $117.6^{+2.1}_{-2.1}$ & $  8.2^{+1.2}_{-1.1}$ & $ 6135^{+  3}_{-  3}$ & $  0.96^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.028}$  & $-0.054^{+0.011}_{-0.010}$ & $0.004^{+0.015}_{-0.015}$ & $0.004^{+0.015}_{-0.015}$\\
-%SN2005cf & $158.9^{+0.7}_{-0.7}$ & $ 15.2^{+0.8}_{-0.7}$ & $ 6140^{+  3}_{-  3}$ & $ -0.19^{+  0.13}_{-  0.13}$ & $-0.122^{+0.028}_{-0.027}$  & $-0.077^{+0.007}_{-0.005}$ & $0.002^{+0.014}_{-0.015}$ & $0.002^{+0.014}_{-0.015}$\\
-%CSS130502\_01 & $ 87.3^{+8.0}_{-8.7}$ & $ 15.4^{+0.5}_{-0.5}$ & $ 6128^{+  3}_{-  3}$ & $ -0.15^{+  0.20}_{-  0.20}$ & $0.121^{+0.032}_{-0.032}$  & $-0.069^{+0.011}_{-0.009}$ & $-0.017^{+0.015}_{-0.015}$ & $-0.017^{+0.015}_{-0.015}$\\
-%SNF20080620-000 & $125.3^{+9.5}_{-9.7}$ & $ 20.6^{+0.6}_{-0.6}$ & $ 6133^{+  3}_{-  3}$ & $ -0.97^{+  0.14}_{-  0.14}$ & $-0.007^{+0.029}_{-0.028}$  & $0.001^{+0.012}_{-0.012}$ & $-0.043^{+0.007}_{-0.007}$ & $-0.043^{+0.007}_{-0.007}$\\
-%SNPGC51271 & $ 64.0^{+12.0}_{-13.2}$ & $ 21.4^{+0.7}_{-0.7}$ & $ 6121^{+  2}_{-  2}$ & $ -1.85^{+  0.16}_{-  0.17}$ & $0.125^{+0.034}_{-0.034}$  & $-0.057^{+0.017}_{-0.014}$ & $0.011^{+0.018}_{-0.019}$ & $0.011^{+0.018}_{-0.019}$\\
-%PTF11pdk & $127.7^{+2.6}_{-2.7}$ & $ 16.1^{+1.2}_{-1.2}$ & $ 6154^{+  5}_{-  5}$ & $  0.16^{+  0.16}_{-  0.17}$ & $-0.027^{+0.035}_{-0.035}$  & $-0.070^{+0.010}_{-0.008}$ & $-0.033^{+0.015}_{-0.011}$ & $-0.033^{+0.015}_{-0.011}$\\
-%SNF20060511-014 & $102.9^{+2.8}_{-2.8}$ & $ 17.1^{+1.0}_{-1.0}$ & $ 6144^{+  8}_{-  7}$ & $ -0.50^{+  0.15}_{-  0.15}$ & $-0.042^{+0.047}_{-0.037}$  & $-0.008^{+0.011}_{-0.010}$ & $-0.041^{+0.009}_{-0.007}$ & $-0.041^{+0.009}_{-0.007}$\\
-%SNF20080612-003 & $120.0^{+1.1}_{-1.1}$ & $  7.5^{+0.6}_{-0.6}$ & $ 6122^{+  3}_{-  3}$ & $  0.96^{+  0.15}_{-  0.15}$ & $-0.221^{+0.018}_{-0.017}$  & $-0.015^{+0.007}_{-0.007}$ & $-0.001^{+0.013}_{-0.014}$ & $-0.001^{+0.013}_{-0.014}$\\
-%SNF20080626-002 & $130.0^{+1.0}_{-1.0}$ & $  5.8^{+2.1}_{-2.0}$ & $ 6111^{+  3}_{-  3}$ & $  1.03^{+  0.19}_{-  0.19}$ & $-0.043^{+0.026}_{-0.025}$  & $-0.009^{+0.015}_{-0.016}$ & $-0.022^{+0.017}_{-0.015}$ & $-0.022^{+0.017}_{-0.015}$\\
-%SNF20060621-015 & $111.8^{+1.3}_{-1.3}$ & $  9.9^{+0.7}_{-0.7}$ & $ 6144^{+  3}_{-  3}$ & $  0.52^{+  0.14}_{-  0.14}$ & $-0.015^{+0.026}_{-0.027}$  & $-0.067^{+0.008}_{-0.008}$ & $-0.020^{+0.013}_{-0.013}$ & $-0.020^{+0.013}_{-0.013}$\\
-%SNF20080920-000 & $135.1^{+1.4}_{-1.4}$ & $  5.3^{+1.5}_{-1.5}$ & $ 6085^{+  3}_{-  3}$ & $  1.08^{+  0.23}_{-  0.23}$ & $-0.002^{+0.038}_{-0.037}$  & $-0.020^{+0.017}_{-0.017}$ & $-0.012^{+0.020}_{-0.019}$ & $-0.012^{+0.020}_{-0.019}$\\
-%SN2007cq & $ 63.7^{+3.9}_{-3.9}$ & $ 11.6^{+0.8}_{-0.8}$ & $ 6138^{+  3}_{-  3}$ & $  0.05^{+  0.13}_{-  0.13}$ & $-0.111^{+0.029}_{-0.027}$  & $0.008^{+0.011}_{-0.011}$ & $-0.015^{+0.015}_{-0.015}$ & $-0.015^{+0.015}_{-0.015}$\\
-%SNF20080918-004 & $ 91.9^{+6.6}_{-6.6}$ & $ 21.2^{+0.9}_{-0.9}$ & $ 6141^{+  4}_{-  4}$ & $ -1.37^{+  0.15}_{-  0.15}$ & $0.035^{+0.142}_{-0.087}$  & $-0.021^{+0.014}_{-0.013}$ & $-0.012^{+0.019}_{-0.018}$ & $-0.012^{+0.019}_{-0.018}$\\
-%CSS120424\_01 & $138.5^{+2.1}_{-2.1}$ & $ 11.5^{+0.6}_{-0.6}$ & $ 6138^{+  3}_{-  3}$ & $  0.58^{+  0.14}_{-  0.14}$ & $-0.010^{+0.028}_{-0.028}$  & $-0.061^{+0.009}_{-0.009}$ & $-0.024^{+0.013}_{-0.012}$ & $-0.024^{+0.013}_{-0.012}$\\
-%SNF20080610-000 & $119.5^{+8.6}_{-8.8}$ & $ 17.0^{+1.4}_{-1.4}$ & $ 6131^{+  6}_{-  6}$ & $  0.16^{+  0.14}_{-  0.14}$ & $0.013^{+0.068}_{-0.068}$  & $-0.019^{+0.014}_{-0.015}$ & $-0.027^{+0.017}_{-0.013}$ & $-0.027^{+0.017}_{-0.013}$\\
-%SNF20070701-005 & $101.6^{+2.6}_{-2.6}$ & $ 13.6^{+0.9}_{-1.0}$ & $ 6155^{+  5}_{-  5}$ & $  0.39^{+  0.14}_{-  0.14}$ & $-0.187^{+0.021}_{-0.021}$  & $-0.012^{+0.011}_{-0.011}$ & $0.037^{+0.015}_{-0.015}$ & $0.037^{+0.015}_{-0.015}$\\
-%SN2007kk & $128.6^{+1.4}_{-1.4}$ & $ 11.0^{+0.9}_{-0.9}$ & $ 6099^{+  4}_{-  4}$ & $  0.59^{+  0.14}_{-  0.14}$ & $-0.087^{+0.029}_{-0.029}$  & $-0.048^{+0.012}_{-0.012}$ & $-0.035^{+0.012}_{-0.010}$ & $-0.035^{+0.012}_{-0.010}$\\
-%SNF20060908-004 & $114.4^{+1.2}_{-1.2}$ & $ 12.4^{+0.6}_{-0.6}$ & $ 6136^{+  3}_{-  3}$ & $  0.63^{+  0.15}_{-  0.15}$ & $-0.099^{+0.138}_{-0.081}$  & $-0.068^{+0.009}_{-0.008}$ & $0.021^{+0.017}_{-0.017}$ & $0.021^{+0.017}_{-0.017}$\\
-%SNF20080909-030 & $ 93.8^{+1.0}_{-0.9}$ & $  7.7^{+0.4}_{-0.4}$ & $ 6171^{+  3}_{-  3}$ & $  0.99^{+  0.13}_{-  0.13}$ & $0.030^{+0.030}_{-0.030}$  & $0.008^{+0.013}_{-0.012}$ & $0.008^{+0.015}_{-0.014}$ & $0.008^{+0.015}_{-0.014}$\\
-%PTF11bgv & $ 78.3^{+3.1}_{-3.1}$ & $ 12.7^{+0.6}_{-0.6}$ & $ 6146^{+  3}_{-  3}$ & $ -0.27^{+  0.11}_{-  0.10}$ & $0.057^{+0.028}_{-0.028}$  & $0.081^{+0.010}_{-0.010}$ & $0.006^{+0.015}_{-0.015}$ & $0.006^{+0.015}_{-0.015}$\\
-%SNNGC2691 & $ 55.7^{+14.4}_{-14.5}$ & $  4.5^{+0.2}_{-0.2}$ & $ 6138^{+  8}_{-  8}$ & $  0.82^{+  0.16}_{-  0.16}$ & $-0.031^{+0.039}_{-0.038}$  & $0.069^{+0.018}_{-0.019}$ & $0.041^{+0.020}_{-0.020}$ & $0.041^{+0.020}_{-0.020}$\\
-%PTF13asv & $ 75.4^{+1.1}_{-1.1}$ & $  2.4^{+0.4}_{-0.4}$ & $ 6149^{+  4}_{-  4}$ & $  0.66^{+  0.10}_{-  0.10}$ & $-0.018^{+0.184}_{-0.105}$  & $-0.068^{+0.012}_{-0.009}$ & $0.015^{+0.015}_{-0.015}$ & $0.015^{+0.015}_{-0.015}$\\
-%SNF20070806-026 & $102.2^{+8.4}_{-9.0}$ & $ 25.3^{+0.7}_{-0.7}$ & $ 6112^{+  7}_{-  7}$ & $ -1.93^{+  0.14}_{-  0.14}$ & $0.010^{+0.032}_{-0.033}$  & $-0.071^{+0.011}_{-0.008}$ & $0.015^{+0.017}_{-0.017}$ & $0.015^{+0.017}_{-0.017}$\\
-%SNF20070427-001 & $ 80.7^{+2.3}_{-2.3}$ & $  6.5^{+0.8}_{-0.8}$ & $ 6143^{+  5}_{-  5}$ & $  0.82^{+  0.17}_{-  0.17}$ & $-0.009^{+0.031}_{-0.031}$  & $-0.066^{+0.011}_{-0.009}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
-%SNF20061108-004 & $128.2^{+5.4}_{-5.4}$ & $  6.8^{+2.1}_{-2.1}$ & $ 6110^{+  6}_{-  6}$ & $  2.36^{+  0.27}_{-  0.27}$ & $-0.089^{+0.038}_{-0.036}$  & $-0.025^{+0.021}_{-0.023}$ & $-0.005^{+0.024}_{-0.022}$ & $-0.005^{+0.024}_{-0.022}$\\
-%SNF20060912-000 & $106.9^{+1.7}_{-1.7}$ & $ 19.8^{+1.5}_{-1.5}$ & $ 6158^{+  7}_{-  7}$ & $  0.06^{+  0.17}_{-  0.17}$ & $-0.177^{+0.032}_{-0.033}$  & $0.034^{+0.018}_{-0.019}$ & $0.080^{+0.021}_{-0.020}$ & $0.080^{+0.021}_{-0.020}$\\
-%CSS110918\_02 & $109.1^{+8.1}_{-8.1}$ & $ 15.0^{+0.6}_{-0.6}$ & $ 6137^{+  3}_{-  3}$ & $ -0.26^{+  0.13}_{-  0.13}$ & $-0.052^{+0.027}_{-0.027}$  & $-0.039^{+0.010}_{-0.010}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
-%SNF20080918-002 & $ 96.6^{+2.8}_{-2.7}$ & $ 13.3^{+1.2}_{-1.2}$ & $ 6143^{+  6}_{-  6}$ & $ -0.47^{+  0.08}_{-  0.08}$ & $0.021^{+0.034}_{-0.035}$  & $-0.056^{+0.014}_{-0.013}$ & $-0.005^{+0.020}_{-0.021}$ & $-0.005^{+0.020}_{-0.021}$\\
-%SNIC3573 & $103.0^{+1.8}_{-1.7}$ & $ 12.1^{+0.9}_{-0.9}$ & $ 6141^{+  5}_{-  5}$ & $  0.39^{+  0.16}_{-  0.16}$ & $-0.109^{+0.026}_{-0.024}$  & $0.015^{+0.009}_{-0.010}$ & $-0.025^{+0.014}_{-0.012}$ & $-0.025^{+0.014}_{-0.012}$\\
-%SNF20080725-004 & $133.8^{+2.1}_{-2.1}$ & $  6.7^{+0.9}_{-0.9}$ & $ 6131^{+  6}_{-  5}$ & $  0.59^{+  0.13}_{-  0.13}$ & $0.078^{+0.032}_{-0.032}$  & $0.025^{+0.012}_{-0.011}$ & $0.016^{+0.015}_{-0.014}$ & $0.016^{+0.015}_{-0.014}$\\
-%SNF20050728-006 & $127.7^{+2.5}_{-2.4}$ & $ 15.3^{+1.2}_{-1.2}$ & $ 6124^{+  6}_{-  6}$ & $  0.11^{+  0.19}_{-  0.19}$ & $-0.088^{+0.034}_{-0.032}$  & $0.064^{+0.011}_{-0.012}$ & $0.012^{+0.017}_{-0.017}$ & $0.012^{+0.017}_{-0.017}$\\
-%SN2012fr & $134.2^{+0.5}_{-0.5}$ & $  7.4^{+0.2}_{-0.2}$ & $ 6101^{+  1}_{-  1}$ & $  0.88^{+  0.08}_{-  0.09}$ & $-0.248^{+0.021}_{-0.021}$  & $-0.077^{+0.005}_{-0.005}$ & $0.044^{+0.012}_{-0.011}$ & $0.044^{+0.012}_{-0.011}$\\
-%SNF20060512-002 & $100.4^{+2.7}_{-2.8}$ & $ 13.5^{+1.1}_{-1.1}$ & $ 6106^{+  7}_{-  7}$ & $ -0.87^{+  0.15}_{-  0.16}$ & $-0.186^{+0.030}_{-0.028}$  & $0.018^{+0.012}_{-0.012}$ & $0.056^{+0.017}_{-0.016}$ & $0.056^{+0.017}_{-0.016}$\\
-%SNF20060512-001 & $ 88.2^{+1.2}_{-1.2}$ & $  5.5^{+0.4}_{-0.4}$ & $ 6169^{+  3}_{-  3}$ & $  0.87^{+  0.11}_{-  0.11}$ & $-0.025^{+0.025}_{-0.025}$  & $0.050^{+0.011}_{-0.011}$ & $-0.010^{+0.011}_{-0.012}$ & $-0.010^{+0.011}_{-0.012}$\\
-%SNF20071003-016 & $126.5^{+4.5}_{-4.4}$ & $ 16.7^{+1.5}_{-1.5}$ & $ 6123^{+ 10}_{- 10}$ & $ -0.30^{+  0.14}_{-  0.14}$ & $0.058^{+0.032}_{-0.032}$  & $0.068^{+0.013}_{-0.014}$ & $-0.030^{+0.016}_{-0.012}$ & $-0.030^{+0.016}_{-0.012}$\\
-%SNF20050821-007 & $141.8^{+2.6}_{-2.6}$ & $  7.8^{+0.9}_{-0.9}$ & $ 6140^{+  9}_{-  8}$ & $  0.34^{+  0.20}_{-  0.19}$ & $-0.024^{+0.034}_{-0.033}$  & $-0.030^{+0.014}_{-0.013}$ & $-0.012^{+0.017}_{-0.017}$ & $-0.012^{+0.017}_{-0.017}$\\
-%SNF20070803-005 & $ 45.4^{+14.0}_{-13.8}$ & $  0.8^{+0.6}_{-0.6}$ & $ 6138^{+ 22}_{- 22}$ & $  0.81^{+  0.15}_{-  0.15}$ & $-0.137^{+0.031}_{-0.031}$  & $0.043^{+0.019}_{-0.019}$ & $-0.005^{+0.021}_{-0.021}$ & $-0.005^{+0.021}_{-0.021}$\\
-%PTF09foz & $127.2^{+1.9}_{-1.9}$ & $ 22.1^{+1.1}_{-1.1}$ & $ 6135^{+  4}_{-  4}$ & $ -0.92^{+  0.16}_{-  0.16}$ & $-0.141^{+0.019}_{-0.018}$  & $-0.042^{+0.009}_{-0.010}$ & $0.031^{+0.013}_{-0.012}$ & $0.031^{+0.013}_{-0.012}$\\
-%PTF12grk & $158.1^{+8.3}_{-8.4}$ & $ 22.1^{+1.2}_{-1.2}$ & $ 6089^{+  8}_{-  8}$ & $ -1.02^{+  0.12}_{-  0.12}$ & $-0.117^{+0.027}_{-0.026}$  & $-0.025^{+0.016}_{-0.017}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
-%SNF20080720-001 & $138.3^{+3.9}_{-4.0}$ & $ 14.0^{+1.5}_{-1.5}$ & $ 6107^{+  3}_{-  3}$ & $  0.19^{+  0.12}_{-  0.12}$ & $-0.176^{+0.028}_{-0.028}$  & $0.325^{+0.018}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$ & $0.007^{+0.019}_{-0.018}$\\
-%SNF20080810-001 & $ 98.8^{+12.2}_{-12.3}$ & $ 21.7^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.93^{+  0.10}_{-  0.11}$ & $-0.058^{+0.024}_{-0.024}$  & $-0.023^{+0.016}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$ & $-0.000^{+0.017}_{-0.016}$\\
-%SNF20050729-002 & $110.4^{+2.3}_{-2.2}$ & $ 10.7^{+1.5}_{-1.4}$ & $ 6141^{+  6}_{-  6}$ & $ -0.22^{+  0.21}_{-  0.22}$ & $0.052^{+0.102}_{-0.075}$  & $-0.039^{+0.015}_{-0.014}$ & $-0.039^{+0.011}_{-0.008}$ & $-0.039^{+0.011}_{-0.008}$\\
-%SN2008ec & $ 97.7^{+10.6}_{-10.6}$ & $ 23.0^{+0.4}_{-0.4}$ & $ 6125^{+  3}_{-  3}$ & $ -1.09^{+  0.10}_{-  0.10}$ & $-0.076^{+0.025}_{-0.026}$  & $0.064^{+0.012}_{-0.012}$ & $0.017^{+0.015}_{-0.015}$ & $0.017^{+0.015}_{-0.015}$\\
-%SNF20070902-018 & $108.6^{+9.5}_{-9.7}$ & $ 18.1^{+1.7}_{-1.7}$ & $ 6119^{+  7}_{-  7}$ & $ -0.81^{+  0.10}_{-  0.09}$ & $0.032^{+0.030}_{-0.030}$  & $0.023^{+0.016}_{-0.017}$ & $-0.035^{+0.014}_{-0.010}$ & $-0.035^{+0.014}_{-0.010}$\\
-%SNF20070424-003 & $123.6^{+3.6}_{-3.6}$ & $ 14.2^{+1.2}_{-1.1}$ & $ 6134^{+  6}_{-  6}$ & $  0.30^{+  0.10}_{-  0.10}$ & $0.008^{+0.023}_{-0.023}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.041^{+0.008}_{-0.007}$ & $-0.041^{+0.008}_{-0.007}$\\
-%SN2006cj & $101.4^{+1.3}_{-1.3}$ & $  5.5^{+0.8}_{-0.8}$ & $ 6128^{+  3}_{-  3}$ & $  0.86^{+  0.13}_{-  0.13}$ & $0.028^{+0.025}_{-0.025}$  & $0.006^{+0.008}_{-0.009}$ & $-0.017^{+0.013}_{-0.013}$ & $-0.017^{+0.013}_{-0.013}$\\
-%SN2007nq & $ 91.2^{+9.1}_{-9.0}$ & $ 23.3^{+1.0}_{-1.0}$ & $ 6109^{+  5}_{-  5}$ & $ -1.90^{+  0.20}_{-  0.20}$ & $-0.075^{+0.038}_{-0.035}$  & $-0.022^{+0.015}_{-0.015}$ & $0.031^{+0.021}_{-0.020}$ & $0.031^{+0.021}_{-0.020}$\\
-%SNF20070817-003 & $ 94.5^{+2.4}_{-2.4}$ & $ 18.1^{+1.1}_{-1.1}$ & $ 6115^{+  6}_{-  6}$ & $ -0.61^{+  0.12}_{-  0.12}$ & $0.050^{+0.031}_{-0.032}$  & $-0.031^{+0.012}_{-0.012}$ & $-0.024^{+0.015}_{-0.014}$ & $-0.024^{+0.015}_{-0.014}$\\
-%SNF20070403-000 & $ 62.8^{+6.1}_{-6.2}$ & $ 27.6^{+1.6}_{-1.6}$ & $ 6154^{+  7}_{-  7}$ & $ -1.88^{+  0.17}_{-  0.17}$ & $0.147^{+0.040}_{-0.041}$  & $0.081^{+0.021}_{-0.021}$ & $0.041^{+0.025}_{-0.023}$ & $0.041^{+0.025}_{-0.023}$\\
-%SNF20061022-005 & $ 63.4^{+3.6}_{-3.8}$ & $  3.9^{+1.4}_{-1.4}$ & $ 6147^{+  7}_{-  7}$ & $  2.03^{+  0.25}_{-  0.25}$ & $0.056^{+0.038}_{-0.038}$  & $0.041^{+0.018}_{-0.020}$ & $-0.000^{+0.022}_{-0.021}$ & $-0.000^{+0.022}_{-0.021}$\\
-%SNNGC4076 & $127.1^{+2.4}_{-2.4}$ & $ 15.7^{+1.1}_{-1.1}$ & $ 6152^{+  4}_{-  4}$ & $  0.04^{+  0.10}_{-  0.10}$ & $-0.004^{+0.030}_{-0.029}$  & $0.049^{+0.013}_{-0.013}$ & $0.045^{+0.016}_{-0.015}$ & $0.045^{+0.016}_{-0.015}$\\
-%SNF20070727-016 & $ 78.3^{+2.4}_{-2.5}$ & $  4.6^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  0.16^{+  0.11}_{-  0.10}$ & $-0.097^{+0.043}_{-0.036}$  & $-0.037^{+0.011}_{-0.011}$ & $-0.025^{+0.015}_{-0.014}$ & $-0.025^{+0.015}_{-0.014}$\\
-%PTF12fuu & $105.4^{+3.0}_{-3.0}$ & $  6.5^{+1.0}_{-1.0}$ & $ 6124^{+  5}_{-  5}$ & $  0.37^{+  0.11}_{-  0.11}$ & $0.178^{+0.026}_{-0.026}$  & $-0.057^{+0.010}_{-0.010}$ & $-0.026^{+0.014}_{-0.013}$ & $-0.026^{+0.014}_{-0.013}$\\
-%SNF20070820-000 & $107.1^{+3.4}_{-3.4}$ & $ 18.7^{+1.2}_{-1.2}$ & $ 6133^{+ 13}_{- 13}$ & $ -0.28^{+  0.12}_{-  0.12}$ & $-0.054^{+0.031}_{-0.030}$  & $0.051^{+0.012}_{-0.013}$ & $-0.015^{+0.018}_{-0.016}$ & $-0.015^{+0.018}_{-0.016}$\\
-%SNF20070725-001 & $108.3^{+1.9}_{-1.9}$ & $  9.5^{+1.0}_{-1.1}$ & $ 6139^{+  6}_{-  6}$ & $  0.61^{+  0.15}_{-  0.15}$ & $0.058^{+0.033}_{-0.033}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.018^{+0.016}_{-0.015}$ & $-0.018^{+0.016}_{-0.015}$\\
-%SNF20071108-021 & $ 98.7^{+2.7}_{-2.7}$ & $  6.0^{+0.8}_{-0.8}$ & $ 6165^{+  5}_{-  5}$ & $  1.15^{+  0.16}_{-  0.15}$ & $-0.045^{+0.028}_{-0.028}$  & $-0.028^{+0.012}_{-0.012}$ & $0.024^{+0.015}_{-0.014}$ & $0.024^{+0.015}_{-0.014}$\\
-%SNF20080914-001 & $126.4^{+1.2}_{-1.2}$ & $ 16.3^{+1.0}_{-1.0}$ & $ 6159^{+  3}_{-  3}$ & $  0.10^{+  0.14}_{-  0.14}$ & $-0.144^{+0.026}_{-0.024}$  & $0.094^{+0.012}_{-0.012}$ & $0.022^{+0.016}_{-0.015}$ & $0.022^{+0.016}_{-0.015}$\\
-%SNF20060609-002 & $ 86.3^{+3.5}_{-3.5}$ & $  8.1^{+1.2}_{-1.1}$ & $ 6132^{+  4}_{-  4}$ & $  0.18^{+  0.12}_{-  0.13}$ & $-0.069^{+0.033}_{-0.032}$  & $0.192^{+0.014}_{-0.014}$ & $-0.008^{+0.018}_{-0.017}$ & $-0.008^{+0.018}_{-0.017}$\\
-%SNF20050624-000 & $119.9^{+5.1}_{-5.1}$ & $  7.9^{+2.4}_{-2.6}$ & $ 6126^{+  5}_{-  5}$ & $  0.47^{+  0.29}_{-  0.29}$ & $-0.171^{+0.026}_{-0.024}$  & $-0.051^{+0.019}_{-0.017}$ & $0.022^{+0.019}_{-0.021}$ & $0.022^{+0.019}_{-0.021}$\\
-%SNF20060618-023 & $ 73.3^{+4.7}_{-4.7}$ & $  5.3^{+1.6}_{-1.5}$ & $ 6140^{+ 18}_{- 18}$ & $  0.18^{+  0.16}_{-  0.16}$ & $-0.229^{+0.039}_{-0.038}$  & $0.059^{+0.020}_{-0.020}$ & $0.092^{+0.023}_{-0.022}$ & $0.092^{+0.023}_{-0.022}$\\
-%SNF20080531-000 & $133.2^{+1.5}_{-1.5}$ & $ 17.2^{+0.8}_{-0.8}$ & $ 6113^{+  5}_{-  5}$ & $ -0.63^{+  0.13}_{-  0.13}$ & $0.002^{+0.024}_{-0.024}$  & $-0.040^{+0.009}_{-0.009}$ & $-0.009^{+0.012}_{-0.013}$ & $-0.009^{+0.012}_{-0.013}$\\
-%SN2006do & $106.3^{+2.1}_{-2.1}$ & $ 26.8^{+1.3}_{-1.2}$ & $ 6101^{+  2}_{-  2}$ & $ -1.95^{+  0.34}_{-  0.34}$ & $-0.077^{+0.031}_{-0.030}$  & $-0.038^{+0.012}_{-0.013}$ & $0.035^{+0.018}_{-0.017}$ & $0.035^{+0.018}_{-0.017}$\\
-%PTF12ikt & $110.3^{+1.5}_{-1.6}$ & $ 14.0^{+0.7}_{-0.7}$ & $ 6141^{+  4}_{-  4}$ & $ -0.40^{+  0.10}_{-  0.10}$ & $-0.023^{+0.025}_{-0.025}$  & $-0.034^{+0.009}_{-0.008}$ & $-0.009^{+0.014}_{-0.014}$ & $-0.009^{+0.014}_{-0.014}$\\
-%SN2006dm & $ 99.6^{+1.6}_{-1.6}$ & $ 29.8^{+0.7}_{-0.7}$ & $ 6118^{+  3}_{-  3}$ & $ -2.35^{+  0.18}_{-  0.18}$ & $0.084^{+0.029}_{-0.029}$  & $-0.047^{+0.011}_{-0.011}$ & $0.047^{+0.017}_{-0.016}$ & $0.047^{+0.017}_{-0.016}$\\
-%PTF13azs & $140.6^{+4.8}_{-4.8}$ & $ 15.2^{+1.3}_{-1.3}$ & $ 6124^{+ 10}_{- 10}$ & $ -0.12^{+  0.11}_{-  0.11}$ & $0.148^{+0.029}_{-0.029}$  & $0.195^{+0.012}_{-0.013}$ & $-0.037^{+0.012}_{-0.009}$ & $-0.037^{+0.012}_{-0.009}$\\
-%SN2005hj & $ 80.4^{+2.4}_{-2.4}$ & $  4.4^{+0.8}_{-0.8}$ & $ 6139^{+  4}_{-  4}$ & $  2.58^{+  0.24}_{-  0.24}$ & $0.076^{+0.039}_{-0.037}$  & $0.009^{+0.018}_{-0.020}$ & $0.066^{+0.022}_{-0.022}$ & $0.066^{+0.022}_{-0.022}$\\
-%PTF12iiq & $149.1^{+2.1}_{-2.2}$ & $ 24.8^{+0.8}_{-0.7}$ & $ 6048^{+  7}_{-  7}$ & $ -0.83^{+  0.10}_{-  0.11}$ & $0.005^{+0.033}_{-0.033}$  & $-0.005^{+0.019}_{-0.020}$ & $-0.034^{+0.017}_{-0.010}$ & $-0.034^{+0.017}_{-0.010}$\\
-%PTF10ndc & $124.1^{+2.4}_{-2.4}$ & $  6.7^{+1.0}_{-1.0}$ & $ 6119^{+  3}_{-  3}$ & $  0.86^{+  0.14}_{-  0.14}$ & $0.007^{+0.026}_{-0.025}$  & $-0.040^{+0.011}_{-0.011}$ & $-0.023^{+0.014}_{-0.013}$ & $-0.023^{+0.014}_{-0.013}$\\
-%SNF20080919-002 & $100.4^{+6.7}_{-6.6}$ & $ 26.3^{+1.7}_{-1.7}$ & $ 6133^{+  8}_{-  8}$ & $ -1.54^{+  0.13}_{-  0.13}$ & $0.340^{+0.043}_{-0.044}$  & $-0.058^{+0.017}_{-0.014}$ & $0.114^{+0.020}_{-0.021}$ & $0.114^{+0.020}_{-0.021}$\\
-%SNPGC027923 & $ 85.4^{+0.6}_{-0.6}$ & $  5.8^{+0.3}_{-0.3}$ & $ 6130^{+  4}_{-  4}$ & $  0.45^{+  0.17}_{-  0.17}$ & $0.078^{+0.032}_{-0.031}$  & $-0.077^{+0.006}_{-0.005}$ & $-0.026^{+0.015}_{-0.013}$ & $-0.026^{+0.015}_{-0.013}$\\
-%SNF20070330-024 & $118.3^{+2.1}_{-2.1}$ & $  5.5^{+1.8}_{-1.8}$ & $ 6101^{+  3}_{-  3}$ & $  0.48^{+  0.19}_{-  0.21}$ & $-0.166^{+0.025}_{-0.024}$  & $-0.040^{+0.014}_{-0.014}$ & $-0.018^{+0.017}_{-0.016}$ & $-0.018^{+0.017}_{-0.016}$\\
-%SNF20061030-010 & $131.6^{+2.2}_{-2.2}$ & $ 16.9^{+1.1}_{-1.1}$ & $ 6116^{+  4}_{-  4}$ & $ -0.10^{+  0.20}_{-  0.20}$ & $0.103^{+0.041}_{-0.041}$  & $0.049^{+0.012}_{-0.012}$ & $0.019^{+0.021}_{-0.021}$ & $0.019^{+0.021}_{-0.021}$\\
-%SNhunt46 & $ 93.8^{+2.0}_{-2.0}$ & $ 11.2^{+0.6}_{-0.6}$ & $ 6133^{+  4}_{-  4}$ & $  0.22^{+  0.17}_{-  0.17}$ & $0.150^{+0.032}_{-0.032}$  & $-0.062^{+0.010}_{-0.010}$ & $0.035^{+0.016}_{-0.015}$ & $0.035^{+0.016}_{-0.015}$\\
-%SN2005hc & $127.2^{+2.4}_{-2.5}$ & $  9.7^{+0.7}_{-0.7}$ & $ 6122^{+  3}_{-  3}$ & $  0.47^{+  0.16}_{-  0.15}$ & $0.137^{+0.025}_{-0.025}$  & $-0.062^{+0.008}_{-0.008}$ & $0.001^{+0.012}_{-0.012}$ & $0.001^{+0.012}_{-0.012}$\\
-%LSQ12dbr & $106.9^{+0.6}_{-0.6}$ & $  6.4^{+0.6}_{-0.6}$ & $ 6137^{+  4}_{-  4}$ & $  0.86^{+  0.11}_{-  0.11}$ & $0.004^{+0.226}_{-0.109}$  & $-0.071^{+0.008}_{-0.007}$ & $-0.034^{+0.011}_{-0.010}$ & $-0.034^{+0.011}_{-0.010}$\\
-%LSQ12hjm & $ 65.3^{+10.8}_{-11.3}$ & $ 15.3^{+1.1}_{-1.1}$ & $ 6147^{+  5}_{-  5}$ & $ -0.16^{+  0.17}_{-  0.17}$ & $0.112^{+0.030}_{-0.031}$  & $-0.062^{+0.013}_{-0.011}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
-%SNF20060521-001 & $ 89.1^{+11.4}_{-12.2}$ & $ 19.1^{+1.1}_{-1.1}$ & $ 6119^{+ 10}_{-  9}$ & $ -1.70^{+  0.20}_{-  0.20}$ & $0.029^{+0.061}_{-0.059}$  & $-0.068^{+0.014}_{-0.010}$ & $0.010^{+0.019}_{-0.020}$ & $0.010^{+0.019}_{-0.020}$\\
-%SNF20070630-006 & $126.3^{+3.1}_{-3.1}$ & $ 10.3^{+1.1}_{-1.2}$ & $ 6126^{+  4}_{-  4}$ & $  0.30^{+  0.11}_{-  0.11}$ & $-0.018^{+0.025}_{-0.025}$  & $-0.027^{+0.010}_{-0.010}$ & $-0.040^{+0.010}_{-0.008}$ & $-0.040^{+0.010}_{-0.008}$\\
-%PTF11drz & $132.6^{+1.4}_{-1.4}$ & $ 14.9^{+0.9}_{-0.9}$ & $ 6116^{+  4}_{-  4}$ & $ -0.11^{+  0.17}_{-  0.18}$ & $-0.007^{+0.025}_{-0.026}$  & $-0.021^{+0.010}_{-0.009}$ & $-0.016^{+0.013}_{-0.013}$ & $-0.016^{+0.013}_{-0.013}$\\
-%SNF20080323-009 & $ 96.0^{+2.2}_{-2.2}$ & $ 11.1^{+1.0}_{-1.0}$ & $ 6145^{+  5}_{-  5}$ & $ -0.15^{+  0.14}_{-  0.14}$ & $-0.029^{+0.030}_{-0.029}$  & $-0.051^{+0.011}_{-0.011}$ & $-0.041^{+0.009}_{-0.008}$ & $-0.041^{+0.009}_{-0.008}$\\
-%SNF20071021-000 & $167.9^{+2.2}_{-2.2}$ & $ 20.2^{+0.6}_{-0.6}$ & $ 6111^{+  4}_{-  4}$ & $ -0.66^{+  0.13}_{-  0.13}$ & $-0.105^{+0.025}_{-0.023}$  & $-0.001^{+0.010}_{-0.010}$ & $-0.004^{+0.013}_{-0.013}$ & $-0.004^{+0.013}_{-0.013}$\\
-%SNNGC0927 & $155.2^{+1.3}_{-1.3}$ & $ 10.9^{+0.7}_{-0.7}$ & $ 6109^{+  4}_{-  4}$ & $  0.39^{+  0.12}_{-  0.12}$ & $-0.031^{+0.027}_{-0.027}$  & $0.039^{+0.010}_{-0.010}$ & $-0.018^{+0.014}_{-0.013}$ & $-0.018^{+0.014}_{-0.013}$\\
-%SNF20060526-003 & $111.8^{+2.5}_{-2.5}$ & $  9.9^{+1.0}_{-1.0}$ & $ 6121^{+  3}_{-  3}$ & $  0.34^{+  0.13}_{-  0.13}$ & $-0.004^{+0.026}_{-0.027}$  & $-0.010^{+0.010}_{-0.010}$ & $-0.011^{+0.014}_{-0.014}$ & $-0.011^{+0.014}_{-0.014}$\\
-%SNF20080806-002 & $135.4^{+1.8}_{-1.9}$ & $  8.3^{+0.9}_{-0.9}$ & $ 6136^{+  4}_{-  4}$ & $  0.83^{+  0.14}_{-  0.14}$ & $-0.106^{+0.028}_{-0.027}$  & $0.020^{+0.010}_{-0.010}$ & $-0.036^{+0.013}_{-0.009}$ & $-0.036^{+0.013}_{-0.009}$\\
-%SNF20080803-000 & $118.3^{+2.5}_{-2.6}$ & $  8.4^{+1.3}_{-1.4}$ & $ 6125^{+  4}_{-  4}$ & $  0.25^{+  0.12}_{-  0.12}$ & $-0.030^{+0.023}_{-0.024}$  & $0.100^{+0.011}_{-0.011}$ & $-0.040^{+0.009}_{-0.008}$ & $-0.040^{+0.009}_{-0.008}$\\
-%SNF20080822-005 & $ 78.6^{+1.8}_{-1.8}$ & $  6.2^{+0.8}_{-0.8}$ & $ 6138^{+  4}_{-  4}$ & $  0.51^{+  0.16}_{-  0.16}$ & $-0.027^{+0.030}_{-0.030}$  & $-0.018^{+0.011}_{-0.010}$ & $0.014^{+0.015}_{-0.015}$ & $0.014^{+0.015}_{-0.015}$\\
-%SNF20060618-014 & $136.8^{+2.4}_{-2.5}$ & $  9.8^{+1.1}_{-1.1}$ & $ 6113^{+  7}_{-  7}$ & $  1.20^{+  0.18}_{-  0.18}$ & $0.077^{+0.047}_{-0.047}$  & $-0.037^{+0.014}_{-0.014}$ & $0.019^{+0.025}_{-0.024}$ & $0.019^{+0.025}_{-0.024}$\\
-%PTF12ghy & $100.6^{+3.5}_{-3.5}$ & $ 16.4^{+0.7}_{-0.7}$ & $ 6133^{+  3}_{-  3}$ & $ -0.58^{+  0.10}_{-  0.10}$ & $-0.138^{+0.023}_{-0.022}$  & $0.196^{+0.011}_{-0.011}$ & $0.001^{+0.013}_{-0.013}$ & $0.001^{+0.013}_{-0.013}$\\
-%SNF20070531-011 & $122.2^{+2.6}_{-2.6}$ & $ 21.5^{+0.8}_{-0.8}$ & $ 6114^{+  3}_{-  4}$ & $ -1.56^{+  0.20}_{-  0.20}$ & $-0.081^{+0.027}_{-0.025}$  & $-0.032^{+0.011}_{-0.011}$ & $-0.000^{+0.015}_{-0.014}$ & $-0.000^{+0.015}_{-0.014}$\\
-%SNF20070831-015 & $112.9^{+2.6}_{-2.6}$ & $  6.9^{+0.9}_{-0.9}$ & $ 6144^{+  6}_{-  6}$ & $  1.38^{+  0.16}_{-  0.16}$ & $0.042^{+0.027}_{-0.027}$  & $-0.016^{+0.010}_{-0.010}$ & $0.002^{+0.014}_{-0.014}$ & $0.002^{+0.014}_{-0.014}$\\
-%SNF20070417-002 & $103.8^{+5.0}_{-4.9}$ & $ 24.1^{+1.3}_{-1.3}$ & $ 6125^{+  8}_{-  9}$ & $ -1.37^{+  0.10}_{-  0.10}$ & $-0.032^{+0.050}_{-0.044}$  & $-0.072^{+0.010}_{-0.007}$ & $-0.039^{+0.010}_{-0.008}$ & $-0.039^{+0.010}_{-0.008}$\\
-%PTF11cao & $143.4^{+1.5}_{-1.6}$ & $ 19.0^{+1.1}_{-1.1}$ & $ 6104^{+  4}_{-  4}$ & $  0.20^{+  0.13}_{-  0.13}$ & $-0.014^{+0.032}_{-0.031}$  & $0.009^{+0.013}_{-0.013}$ & $-0.017^{+0.017}_{-0.015}$ & $-0.017^{+0.017}_{-0.015}$\\
-%SNF20080522-000 & $ 62.1^{+3.5}_{-3.5}$ & $  3.1^{+0.8}_{-0.8}$ & $ 6130^{+  7}_{-  7}$ & $  0.99^{+  0.11}_{-  0.11}$ & $-0.021^{+0.028}_{-0.028}$  & $-0.009^{+0.012}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$ & $0.047^{+0.014}_{-0.013}$\\
-%PTF10qjq & $ 74.4^{+2.3}_{-2.4}$ & $ 12.0^{+0.7}_{-0.7}$ & $ 6132^{+  3}_{-  3}$ & $ -0.50^{+  0.10}_{-  0.09}$ & $-0.127^{+0.026}_{-0.024}$  & $0.049^{+0.010}_{-0.011}$ & $-0.010^{+0.015}_{-0.015}$ & $-0.010^{+0.015}_{-0.015}$\\
-%PTF12dxm & $119.3^{+15.5}_{-16.8}$ & $ 31.3^{+1.9}_{-2.1}$ & $ 6136^{+  4}_{-  4}$ & $ -2.14^{+  0.18}_{-  0.18}$ & $0.034^{+0.034}_{-0.033}$  & $-0.047^{+0.027}_{-0.021}$ & $0.067^{+0.023}_{-0.024}$ & $0.067^{+0.023}_{-0.024}$\\
-%SNF20061021-003 & $122.5^{+2.2}_{-2.2}$ & $ 10.8^{+1.5}_{-1.5}$ & $ 6131^{+  4}_{-  4}$ & $  0.39^{+  0.15}_{-  0.15}$ & $-0.012^{+0.035}_{-0.033}$  & $0.036^{+0.014}_{-0.014}$ & $0.047^{+0.019}_{-0.017}$ & $0.047^{+0.019}_{-0.017}$\\
-%SNF20080510-005 & $112.2^{+2.5}_{-2.5}$ & $  7.0^{+1.0}_{-1.0}$ & $ 6117^{+  4}_{-  4}$ & $  1.68^{+  0.22}_{-  0.22}$ & $0.116^{+0.030}_{-0.030}$  & $-0.029^{+0.013}_{-0.015}$ & $-0.042^{+0.008}_{-0.007}$ & $-0.042^{+0.008}_{-0.007}$\\
-%SNF20080507-000 & $ 98.4^{+1.6}_{-1.6}$ & $  8.0^{+1.7}_{-1.6}$ & $ 6142^{+  5}_{-  5}$ & $  0.56^{+  0.18}_{-  0.18}$ & $-0.126^{+0.023}_{-0.022}$  & $0.063^{+0.014}_{-0.013}$ & $-0.003^{+0.015}_{-0.014}$ & $-0.003^{+0.015}_{-0.014}$\\
-%SNF20080913-031 & $117.9^{+1.5}_{-1.5}$ & $ 14.7^{+1.6}_{-1.6}$ & $ 6159^{+  5}_{-  5}$ & $  0.49^{+  0.17}_{-  0.17}$ & $-0.048^{+0.067}_{-0.052}$  & $-0.003^{+0.015}_{-0.015}$ & $-0.009^{+0.020}_{-0.018}$ & $-0.009^{+0.020}_{-0.018}$\\
-%SNF20080510-001 & $118.9^{+2.0}_{-2.1}$ & $ 15.0^{+1.1}_{-1.0}$ & $ 6115^{+  4}_{-  4}$ & $  0.34^{+  0.14}_{-  0.14}$ & $0.001^{+0.026}_{-0.026}$  & $-0.058^{+0.011}_{-0.012}$ & $-0.032^{+0.012}_{-0.011}$ & $-0.032^{+0.012}_{-0.011}$\\
-%SNF20070712-003 & $108.1^{+2.7}_{-2.6}$ & $ 14.1^{+0.9}_{-0.9}$ & $ 6157^{+  6}_{-  6}$ & $  0.62^{+  0.14}_{-  0.14}$ & $-0.034^{+0.030}_{-0.029}$  & $-0.052^{+0.010}_{-0.011}$ & $-0.021^{+0.015}_{-0.014}$ & $-0.021^{+0.015}_{-0.014}$\\
-%\\
 SNF20050624-000 & $119.9^{+5.1}_{-5.1}$ & $  7.9^{+2.4}_{-2.6}$ & $ 6126^{+  5}_{-  5}$ & $  0.47^{+  0.29}_{-  0.29}$ & $-0.171^{+0.026}_{-0.024}$  & $-0.051^{+0.019}_{-0.017}$ & $0.022^{+0.019}_{-0.021}$ & $0.022^{+0.019}_{-0.021}$\\
@@
 
+\added{
+The
+observed parameters
+$EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$, $\lambda_{\mathrm{Si}}$, $x_1$ and their associated latent values are
+statistically equivalent for the  SN1991T/SN2009dc-like LSQ12fhe, PTF11bju, and PTF11mkx.
+In addition, their inferred  $\Delta$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$, $A_{p,V}$
+lie well within the distributions of the full sample.  We thus conclude that these objects are not extreme outliers and
+that their inclusion does not significantly bias our results.
+}
+
 The $\Delta$ parameter will be discussed in its own subsection \S\ref{Delta:sec}.
@@
 Using the SNfactory sample,
-\citet{2017Rigault} find that a step in Hubble residuals is better related to local 
+\citet{2018arXiv180603849R} find that a step in Hubble residuals is better related to local 
 specific

### 2018-10-22 submit/response.txt
resubmitted version

@@
 Comment 1:
-
 While much of the narrative within the paper is compelling, it is currently unverifiable.
@@
 there isn't even a table listing the SNe used.
-
-It is impossible to verify any claims without making these data public, and
-I cannot accept this paper until the data are released publicly.
+It is impossible to verify any claims without making these data public, andI cannot accept this paper until the data are released publicly.
 
@@
 
-The data that we use as features are now included in the article.  These are in a new table containing a list of the supernovae, their feature measurements, and uncertainties.
+The data that we use as features are now included in the article.
+These are in a new table containing a list of the supernovae, their feature measurements, and uncertainties.
+All data used as input into the analysis are now available in the tables or in previously published articles.
 
@@
 
-Comment 2:
-
-Beyond the basic critical idea of providing sufficient data to verify the results, a fundamental aspect of scientific inquiry, the authors do not satisfactory describe their sample.
+Comment 2: Beyond the basic critical idea of providing sufficient data to verify the results, a fundamental aspect of scientific inquiry, the authors do not satisfactory describe their sample.
 They simply state that the sample of 172 SNe have been processed and have sufficient data to provide some parameters.
@@
 Response 2:
-
 We have added paragraphs in the Data section that describe the selection of our sample.
@@
 Comment 3:
-
 1.
@@
 Comment 5:
-
 3. Section 5.2.9 says that the correlation between Delta and the other parameters is shown in Eq. 20. But Delta isn't included there.

### 2018-10-22 submit/cover2.tex
resubmitted version

\documentclass[a4paper,12pt]{letter}

% Some of the article customisations are relevant for this class

\name{Alex Kim} % To be used for the return address on the envelope
\signature{Alex Kim} % Goes after the closing (ie at the end of the letter, with space for a signature)
\address{1 Cyclotron Road, MS: 50R6048 \\ Berkeley, CA 94720-8164}
% Alternatively, these may be set on an individual basis within each letter environment.

\makelabels % this command prints envelope labels on the final page of the document

\begin{document}
\begin{letter}{The Editors\\AAS Publishing}

\opening{Hello.} % eg Hello.

This cover letter accompanies the resubmission 
{\bf Evidence for a Third Color  Parameter Within the Type~Ia Supernovae of the Nearby Supernova Factory} authored by myself on behalf
of the Nearby Supernova Factory Collaboration.  It presents a novel analysis, a first detection of a  color parameter within Type~Ia supernovae,
and analyzes timely data.  As such we believe that  it is appropriate for the Astrophysical Journal.

Also included is our response to the referees comments.  Changes to the text are included using the aastex ``trackchanges'' calls.

\closing{Regards,} % eg Regards,

%\cc{} % people this letter is cc-ed to
%\encl{} % list of anything enclosed
%\ps{} % any post scriptums. ``PS'' labels must be put in manually

\end{letter}
\end{document}

### 2018-10-22 submit/fix.tex
resubmitted version

@@
 of in-sample supernovae. 
-\added{Subsequent to the analysis four supernovae, SNBOSS38, LSQ12fhe, PTF11bju, and PTF11mkx 
-were identified as SN1991T/SN2009dc-like \citep{2018lin, 2018Taubenberger}, the results for these objects are discussed later. }
+\added{Subsequent to the analysis, LSQ12fhe, PTF11bju, and PTF11mkx 
+were identified as SN1991T-like \citep{2018lin} and SNBOSS38 as SN2009dc-like \citep{2018Taubenberger}, the results for these objects are discussed later. }
 
@@
 \vec{m}=
- \vec{c} +  \vec{1} \, \Delta + \vec{\alpha} \, EW_{\mathrm{Ca}}+
+ \vec{c} +  \vec{1} \, \Delta +
 \vec{\alpha} \,  EW_{\mathrm{Ca}}+
@@
 \vec{m}=
- \vec{c} +  \vec{1} \, \Delta + \vec{\alpha} \, EW_{\mathrm{Ca}}+
+ \vec{c} +  \vec{1} \, \Delta + 
 \vec{\alpha} \,  EW_{\mathrm{Ca}}+
@@
 $EW_{\mathrm{Ca}}$, $EW_{\mathrm{Si}}$, $\lambda_{\mathrm{Si}}$, $x_1$ and their associated latent values are
-statistically equivalent for the  SN1991T/SN2009dc-like LSQ12fhe, PTF11bju, and PTF11mkx.
+statistically equivalent for the  SN1991T-like LSQ12fhe, PTF11bju, and PTF11mkx and the SN2009dc-like SNBOSS38.
 In addition, their inferred  $\Delta$, $E_{\gamma^0}({\hat{B}}-{\hat{V}})$, $E_{\gamma^1}({\hat{B}}-{\hat{V}})$, $A_{p,V}$
